### 2011-03-25 paper.tex
updated Sect. II A

\documentclass[10pt,aps,pra,reprint,amsmath,amsfonts,amssymb,showpacs]{revtex4-1}
\usepackage{epsfig,psfrag,graphicx,bm,color}

%\def\del#1{{}}
\def\del#1{{\bf (DELETED TEXT)}}
%\def\C#1{#1}
\def\C#1{{\bf #1}}

% --- journals --- %
\newcommand{\aap}{A{\&}A}
\newcommand{\aaps}{A{\&}AS}
\newcommand{\aj}{AJ}
%\newcommand{\apj}{ApJ}
\newcommand{\apjl}{ApJL}
\newcommand{\apjs}{ApJS}
\newcommand{\apss}{Ap{\&}SS}
\newcommand{\araa}{ARA{\&}A}
%\newcommand{\prd}{Phys. Rev. D}
%\newcommand{\pre}{PRE}
\newcommand{\mnras}{MNRAS}
\newcommand{\ssr}{SSRv}
%\newcommand{\nat}{Nature}
\newcommand{\physrep}{Phys.~Rep.}
\newcommand{\jcomp}{J.~Comput.~Phys.}
\newcommand{\jcap}{JCAP}

%NEW
\newcommand{\bx}{{\bf x}}
\newcommand{\fg}{{F_\gamma}}
\newcommand{\sg}{{S_\gamma}}
\newcommand{\psf}{\theta_\rmn{res}}
\newcommand{\ph}{{\rm ph}}
\newcommand{\eph}{E_\ph}
\newcommand{\nph}{N_\ph}
\newcommand{\vir}{{\rmn vir}}
\newcommand{\gal}{{\rmn gal}}
\newcommand{\iruv}{{\rmn sd}}
\newcommand{\clu}{{\rmn cl}}
\newcommand{\sfe}{{\rmn sfe}}
\newcommand{\sub}{{\rmn sub}}
\newcommand{\msun}{{M_\odot}}

%OLD
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\rmn}{\mathrm}
\newcommand{\GeV}{\,{\rm GeV}}
\newcommand{\TeV}{\,{\rm TeV}}
\newcommand{\eV}{\,{\rm eV}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\mx}{\ensuremath{m_{\chi}}}
\newcommand{\ga}{\gamma}
\newcommand{\ngamma}{\ensuremath{N_{\gamma}}}
\newcommand{\ngammaj}{\ensuremath{N_{\gamma,j}}}
\newcommand{\sigmaannv}{\ensuremath{\langle\sigma v\rangle}}
\newcommand{\sigv}{\ensuremath{\sigma_v}}
\newcommand{\ic}{\mathrm{IC}}
\newcommand{\egamma}{\ensuremath{E_{\gamma}}}
\newcommand{\dic}{\mathrm{dIC}}
\newcommand{\fsr}{\mathrm{FSR}}
\newcommand{\CR}{\mathrm{CR}}
\newcommand{\rhos}{\ensuremath{\rho_s}}
\newcommand{\rs}{\ensuremath{r_s}}
\newcommand{\rvir}{r_{200}}
\newcommand{\mvir}{M_{200}}
\newcommand{\rhoc}{\ensuremath{\rho_c}}
\newcommand{\B}{\rmn{B}}
\newcommand{\e}{\rmn{e}}
\newcommand{\eg}{E_\gamma}
\newcommand{\ir}{\rmn{ir}}
\newcommand{\Km}{\rmn{K}`}
\newcommand{\Imm}{\rmn{I}`}
\newcommand{\Jm}{\rmn{J}^*}
\newcommand{\Jmm}{\rmn{J}`}

\begin{document}

\title{Prospects of detecting gamma-ray emission from galaxy clusters:
  cosmic rays and dark matter annihilations}

\author{Anders Pinzke$^{1}$} \email{apinzke@physics.ucsb.edu} 
\author{Christoph Pfrommer$^{2}$}\email{pfrommer@cita.utoronto.ca}
\author{Lars Bergstr\"om$^{3}$}\email{lbe@fysik.su.se}

\affiliation{$^{1}$University of California - Santa Barbara,
  Department of Physics, CA 93106-9530, USA}

\affiliation{$^{2}$Heidelberg Institute for Theoretical Studies (HITS), Schloss-Wolfsbrunnenweg 33, DE - 69118 Heidelberg, Germany}

\affiliation{$^{3}$The Oskar Klein Centre for Cosmoparticle Physics, Department
  of Physics, Stockholm University, AlbaNova University Center, SE - 106 91
  Stockholm, Sweden}

\date{\today}

\pacs{95.35.+d, 95.85.Pw, 98.62.Gq, 98.65.-r, 98.70.Sa}

\begin{abstract}
... to be written...
\end{abstract}

\maketitle
\section{Introduction}

Dark matter has been searched for in direct detection experiments
\cite{Pato:2010zk}, at accelerators
\cite{Ellis:2001hv,Baer:2006ff,Khachatryan:2011tk} and also in
indirect detection experiments looking for signals in the cosmic-ray
spectra of antiprotons, positrons, neutrinos and all of the
electromagnetic spectrum from radio waves to gamma rays
\cite{Bergstrom:2009ib}. So far, the improvements in direct detection
sensitivity have put this method into focus, but the situation may
change considerably the coming few years as the CERN LHC experiments
collect data, and new gamma-ray detectors are being planned, such as
the CTA \cite{Consortium:2010bc}. In fact, it has recently been
pointed out \cite{Bergstrom:2010gh} that a dedicated ground-based
gamma-ray detector would have potential that goes far beyond that of
the other methods, depending on presently unknown parameters in the
particle physics models for dark matter.

Among the astrophysical systems which will be very interesting to
detect, and study, with coming gamma-ray detectors (Fermi, HESS,
MAGIC, VERITAS, and eventually large detectors like CTA) belong galaxy
clusters. The most promising directions in which to search for a
gamma-ray annihilation signal (from the annihilation process itself,
and also the accompanying bremsstrahlung and inverse Compton
components coming from charged particles produce in the annihilations)
are basically three:

1. The galactic centre (g.c.). This is where all numerical simulations
of cold dark matter predict the highest density. However, the detailed
dark matter density in the very central part is difficult to predict,
due a to a possibly very complicated interplay between baryons, dark
matter, and the central galactic black hole. Also, it is a very
crowded region with many gamma-ray sources like pulsars and other
supernova recants, which have to be subtracted from the data to
extract the dark matter induced signal. In fact, there is a recent
claim of an indication of a relatively light dark matter particle
contribution to the gamma-ray flux from the
g.c. \cite{2010arXiv1010.2752H}, but other hypotheses seem to work at
least as well \cite{2010arXiv1012.5839B}.

2. The dwarf spheroidal galaxies orbiting the Milky Way, like Segue-1,
Ursa Minor, Draco, Sagittarius, Sculptor, Carina or Willman-1
\cite{2009JCAP...01..016B,2010ApJ...720.1174A,2010JCAP...01..031S,2010JCAP...01..031S}. The
problem here is that the nature of many of these small, dark
matter-dominated galaxies is not entirely clear, and the velocity
dispersion estimates are based on rather small numbers of stars. Tidal
disruption and confusion with star clusters are other
complications. Thus the dark matter density profile is very uncertain
for most of them. Nonetheless, by stacking the data together from many
dwarf spheroidals these uncertainties can be made less severe, and
preliminary results from Fermi-LAT shows this method to give quite
promising results \cite{garde}.

3. Galaxy clusters. This possibility has been less studied, however we
noted in a previous Letter \cite{2009PhRvL.103r1302P} that the are
certain advantages that work in favour of this possible target for
gamma-ray detection of dark matter annihilation.  Galaxy clusters
constitute the most massive objects in our Universe that are forming
today. This causes their DM subhalo mass function to be less affected
by tidal stripping compared to galaxy sized halos that formed long
ago.  The annihilation luminosities of the DM halo component for
e.g. the Virgo cluster and the Draco dwarf scales in a way (see
\cite{2009PhRvL.103r1302P}) that the ratio of gamma-ray luminosities
from the smooth components is around 4, in favour of Virgo. In
addition, there may be a further enhancement due to substructure,
which to a large extent should be unaffected by tidal disruption, at
least in the outer regions.  According to a recent estimate
\cite{2011MNRAS.410.2309G}, more massive haloes tend to have a larger
mass fraction in subhalos.  For example, cluster size haloes typically
have 7.5 per cent of the mass within $r_{200}$ in substructures of
fractional mass larger than $10^{-5}$, which is 25 per cent higher
than galactic haloes \footnote{All halo masses and length scales in
  this paper are scaled to the currently favored value of Hubble's
  constant, $H_0 = 70\, \rm{km~s}^{-1}\,\rm{Mpc}^{-1}$. We define the
  virial mass $\mvir$ and virial radius $\rvir$ as the mass and radius
  of a sphere enclosing a mean density that is 200 times the critical
  density of the Universe $\rho_{\rm{cr}}$.}.

For a satellite dwarf galaxy, however, once it is accreted by the
Milky Way, the outer regions are severely affected by tidal
stripping. The longer a satellite has been part of our Galaxy, and the
closer it comes to the center during its pericentral passage, the more
material is removed \cite{2004MNRAS.355..819G}.

In this paper, we will investigate in some more detail the potential
of several of the most promising galaxy clusters to yield an
annihilation gamma-ray yield which could be observable with present
and planned gamma-ray detectors.

For previous work related to dark matter in clusters, see, e.g.,
\cite{2006A&A...455...21C,2009PhRvD..80b3005J}.

%***********************************************
{\bf Anders, insert your flux table for various clusters, and discuss it}

This yields Fornax ($\mvir=10^{14}\,\msun$) and Virgo
($\mvir=2.1\times10^{14}\,\msun$) \cite{} as the prime targets for DM
observations, Perseus ($\mvir=7.7\times10^{14}\,\msun$) for CR induced
emission and we additionally decide in favor of the well studied
cluster Coma ($\mvir=1.4\times10^{15}\,\msun$) for comparison.

% --- section:  --- %
\section{Theory}
\label{sect:theory}

\subsection{Astrophysics}
\label{sect:AP}

The differential photon flux within a given solid angle $\Delta
\Omega$ along a line-of-sight (los) is given by
\begin{equation}
\label{eq:dflux}
\frac{\dd \fg}{\dd \eg} \equiv \frac{\dd^3 \ngamma}{\dd A \,\dd t\, \dd
  \egamma} = \frac{1}{2}\int_{\Delta\Omega} \dd\psi \sin\psi \frac{\dd \sg}{\dd \eg}(\psi,\eg)\,,
\end{equation}
where
\begin{equation}
\label{eq:dtildeflux}
\frac{\dd \sg}{\dd \eg}(\psi,\eg) = \int_{\Delta\Omega} \dd\Omega \int_{\rm los}
\dd l\, q_{\rm sum}\left(\eg,r\right)\Lambda(\theta)\,,
\end{equation}
and $\sg(\psi, >\eg)$ denotes the surface brightness above the photon
energy $\eg$.  The integration along the line-of-sight $l$, in the
direction $\psi$ that the detector is pointing, is parameterized such
that the radius of the source $r=\sqrt{l^2+D^2-2Dl\cos\Psi}$, where
$D$ is the distance to the source from the galactic center and
$\cos\Psi\equiv\cos\theta\cos\psi-\cos\varphi\sin\theta\sin\psi$. The
angular integration $\dd \Omega= \sin\theta\dd \theta \,\dd \varphi$
is performed over a cone centered around $\psi$ and the opening angle
$\Delta \Omega$ is typically taken to be a few times the point spread
function (PSF) $\psf$. The limited angular resolution results in a
probability that a photon coming from a direction $\psi$' is instead
reconstructed to a direction $\psi$, where the underlying probability
distribution follow a Gaussian:
\begin{equation}
\Lambda(\theta)=\frac{1}{2\pi\psf^2}
\,\rmn{exp}\left[-\frac{\theta^2}{2\psf^2}\right]\,,
\quad \rmn{where}\quad \theta=\psi'-\psi \,.
\end{equation}
We denote the total source function by $q_{\rm sum}(\eg,r)$, where we
include contributions from four main processes; leptophilic DM
annihilating to $\mu^+/\mu^-$ decaying to $\rm{e}^+/\rm{e}^-$ pairs
that up-scatter background photons (IC), leptophilic DM emitting final
state radiation (FSR), DM benchmark models where neutralino
annihilations generate electrons that up-scatter background photons
(BM-IC) and emit a continuum as well as final state radiation
(BM-Cont), and CR induced $\pi^0$:s decaying into gamma-rays. The
source function is given by
\begin{equation}
q_\rmn{sum} (\eg,r) = q_{\pi^0-\gamma}(\eg,r)+
\sum_i \,q_{\rmn{sm},i}(\eg,r)\,\B_{\rmn{tot},i}(\sigv,r)
\end{equation}
where $ q_{\pi^0-\gamma}(\eg,r)$ denotes the CR to gamma-ray source
function (see Sect.~\ref{sect:CRs} and \cite{2010MNRAS.409..449P}
for more details). The total differerntial boost factor for DM is the
product of enhancement factors from SFE $\B_\sfe(\sigv)$ (see
Sect.~\ref{sect:LP}) and from substructure enhancement over the
smooth halo contribution $\B_{\sub,i}(r) = 1+q_\sub(r)/q_{\rmn{sm},i}(r)$
(see Sect.~\ref{sect:subst}) and is denoted by
$\B_{\rmn{tot},i}(r,\sigv) = \B_\sfe(\sigv)\,\B_{\sub,i}(r)$. The DM
source function from the smooth halo for each process is written on
the form:
\begin{equation}
\quad q_{\rmn{sm},i} (\egamma,r) = \sum_j
\frac{\dd \ngammaj}{\dd E_\gamma} \Gamma_j(r)\,.
\end{equation}
We represent the annihilation rate density with $\Gamma_j =
(\rho/\mx)^2 \, \sigmaannv_j/2$, where $j$ runs over all $\gamma$-ray
producing channels each with the spectrum $\frac{\dd
  \ngammaj}{\dd\eg}$ and annihilation cross-section $\sigmaannv_j$.
The DM density is modeled by an Einasto density profile
\begin{equation}
\rho_{\rm ein}(r) = \rho_{-2}\,\exp\left\{-\frac{2}{\alpha}
  \left[\left(\frac{r}{r_{-2}}\right)^\alpha -1 \right] \right\},\,
\alpha=0.17 \,,
\end{equation}
that is slightly shallower than the conventional Navaro-Frenk-White
(NFW) profile in the center, but provide a better fit to simulated DM
halos \cite{2010MNRAS.402...21N}. We denote the density where the
profile has a slope of $-2$ by $\rho_{-2}$, and the radius by
$r_{-2}$. Assuming that all the flux from an NFW profile originate
from within the scale radius $\rs=\rvir/c$, and all the flux from an
Einasto profile originate within $r_{-2}=\rvir/c$, it follows that
$\rho_{-2} = \rhos/4$. The virial radius $\rvir$ of a halo is defined
to be the radius at which the mean density within is a factor
$\Delta=200$ times the critical density $\rhoc$ of the universe. The
characteristic density of the NFW profile $\rhos=(\Delta\rhoc/3)\,
c^3/(\log(1+c)-(c/(1+c)))$, where the halo mass dependent
concentration parameter $c$ is derived from a power-law fit to
cosmological simulations with $\mvir \gtrsim 10^{10} \msun$
\cite{2008MNRAS.391.1940M},
\begin{equation}
\label{eq:cfit}
  c=3.56 \times \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-0.098}\,.
\end{equation}
This mass scaling agrees well with \cite{2009ApJ...707..354Z} for
cluster-mass halos after converting the concentration definitions
according to \cite{2003ApJ...584..702H}.

\subsubsection{Substructures}
\label{sect:subst}
High-resolution DM simulations of the Milky Way (MW) find vast amount
of substrucures in the periphery of DM halos. Since the rate of which
DM is annihilating depends on the density squared, the resulting flux
is boosted compared to the smooth density distribution. Recent
simulations suggest a boost from substructures of the order of ten up
to a few 100 \cite{2008MNRAS.391.1685S, 2008JPhCS.125a2008K} for a MW
size halo. Based on the result from \cite{2008Natur.456...73S}, we
find the best fit\footnote{Our approach of fitting the scaling
  behavior of $\rmn{L_{sub}}(<r)$ directly from numerical simulations
  self-consistently accounts for the radial dependence of the
  substructure concentration \cite{2008MNRAS.391.1685S}.} to the
luminosity from smooth substructures (i.e. substructures within
substructures are not included) inside radius $r$ with
\begin{equation}
  {\rm L_{sub}}(<r)= 0.76\,C_1\,C_2(\mvir)\,{\rm L_{200sm}}\,x^{0.95
    \displaystyle{x}^{-0.27}}\,,
  \label{eq:LSub}
\end{equation}
where ${\rm L_{200sm}}$ is the luminosity from the smooth halo without
substructures within $\rvir$ and $x=
\left(\frac{r}{\rvir}\right)$. The first normalization constant is
given by
\begin{equation}
  C_1=\left(\frac{M_{\rm res,sim}}{M_{\rm lim}}\right)^{0.226}\,,
   \label{eq:C1}
\end{equation}
where $M_{\rm res,sim}=10^5\msun$ is the minimum subhalo mass in the
MW simulation, and $M_{\rm lim}$ the free streaming mass. Here we
assume that the power-law scaling relation in Eq.~(\ref{eq:C1}) is
valid down to the minimum mass of DM halos, which is conventionaly in
the cold dark matter universe
\cite{2001PhRvD..64h3507H,2005JCAP...08..003G} taken to be
$10^{-6}\msun$. Note that potentially the power-law could flatten
torwards smaller mass scales although current simulations show no hits
of such a behaviour and in addition we are approaching the asymptotic
behavior in the power spectrum on these scales(CHECK). For DM halos
more (less) massive than the MW we expect a larger (smaller) boost
from substructures, simply because of the larger (smaller) mass range
down to the minimum mass $M_\rmn{lim}$. We capture this halo mass
dependence with the second normalization in Eq.~(\ref{eq:LSub}):
\begin{equation}
C_2(\mvir)=\left(\frac{\mvir}{M_{\rm 200sim}}\right)^{0.226}\,,
 \label{eq:C2}
\end{equation}
where $M_{\rm 200,sim}=1.9\times10^{12}\msun$ is the mass of the MW
halo in the simulation \cite{2008Natur.456...73S}.

large uncertaint observationally in density profiles

In Fig.~\ref{fig:radial_lum} we compare the radial dependence of the
accumulative luminosity from different smooth cluster density profiles
to the substructure boosted luminosity at different mass scles. The

\begin{figure}%[t]
 \includegraphics[width=0.99\columnwidth]{figures/dens.prof.eps}
\caption{\it Radial dependence of various luminosity
  contributions. The solid lines show the accumulative smooth
  luminosity from a cluster with the mass $\mvir=10^{15}\,\msun$ for
  three different density profiles; an Einasto profile with
  $\alpha=0.17$ (light blue), a cuspy NFW profile with $\beta=1.0$
  (dark blue), and a core NFW profile with $\beta=0.6$ (purple). The
  dashed lines show the accumulative luminosity from substructures for
  three different mass scales; an $\mvir=10^{15}\,\msun$ galaxy
  cluster (red), an $\mvir=10^{12}\,\msun$ galaxy (orange), and an
  $\mvir=10^{8}\,\msun$ dwarf galaxy (green). All luminosities have
  been normalized with the luminosity within $\rvir$ from a cuspy NFW
  profile. Note the large expected boost from substructures in
  clusters ($\sim1000$), and the relative small boost in dwarf
  galaxies ($\sim20$).}
 \label{fig:radial_lum}
\end{figure}

\begin{figure}
  \includegraphics[width=0.99\columnwidth]{figures/emissiv.sub.eps}
  \caption{\it Volume weighted luminosity for different at different
    scales. The solid lines show the emissivity from a NFW density
    profile for three different mass scales; a $\mvir=10^{15}\,\msun$
    galaxy cluster (red), a $\mvir=10^{12}\,\msun$ galaxy (orange), a
    $\mvir=10^{8}\,\msun$ dwarf galaxy (green). The dashed lines show
    the emissivity from substructures for the same three mass
    scales. All emissivities have been normalized with the luminosity
    from a NFW profile within $\rvir$.}
  \label{fig2}
\end{figure}

\subsubsection{Cosmic-ray induced gamma-ray emission}
\label{sect:CRs}
The formation process of a galaxy cluster is a very energetic
processes that induces both turbulence as well as frequently occurring
merging and accretion shocks. These processes are thought to
accelerate large quantities of relativistic non-thermal electrons and
protons to high energies. On smaller scales, such as galaxies, there
is convincing evidence of such non-thermal populations. Especially, in
the MW, the cosmic rays are observed directly as well as indirectly
through radio, X-ray, and gamma-ray emission. On larger scales of the
order of few 100 kpc up to Mpc, there are a vast number of
observations of radio emission coming from radio mini halos in the
center of cooling flow clusters, radio relics in the periphery of
clusters \cite{2004rcfg.proc..335K} as well smooth giant radio halos
that have been observed in more than 50 clusters
\cite{2003ASPC..301..143F,2008SSRv..134...93F}. Most of this observed
radio emission is expected to emerge from synchrotron emitting
cosmic-ray electrons whose precise origin in especially relics and
giant radio halos is still not settled. However, due to the smoothness
of the extended emission and the observed power-law slope it seems
quite natural that they are of hadronic origin. Especilly since the
long cooling time of cosmic ray protons (CRs) allows for both an
extended and large population of CRs to build up over the cluster
history \cite{1997ApJ...487..529B}.

When the CRs interact with ambient gas protons, it results in the
production of both charged and neutral pions that decay into
electrons, neutrinos, and gamma-rays. The production of these
secondaries depend both on the gas and CR densities in the cluster,
where the CR density roughly trace the gas outside the core regime and
is slightly enhance in the center. This density scaling implies that
clusters are great targets for Cherenkov telescopes with a high
sensitivity for the central parts of close by clusters. Detecting the
cluster gamma-ray emission is crucial in this respect as it
potentially provides the unique and unambiguous evidence of CR
populations in clusters through observing the $\pi^0$ bump at about
100~MeV in the spectra. We adopt the spectrally and spatially
universal gamma-ray model developed by Pinzke \& Pfrommer
\cite{2010MNRAS.409..449P} to estimate the emission from decaying
$\pi^0$:s that dominates over the inverse Compton emission from
primary and secondary electrons above 100~MeV in clusters. The
gamma-ray formalism was derived from high resolution simulations of
clusters of galaxies that included radiative hydrodynamics, star
formation, supernova feedback, and followed CR physics using a novel
formulation that trace the most important injection and loss processes
self-consistently while accounting for the CR pressure in the equation
of motion
\cite{2008A&A...481...33J,2007A&A...473...41E,2006MNRAS.367..113P}.
We note that the overall normalization of the CR and gamma-ray
distribution scales with the maximum acceleration efficiency at
structure formation shock waves. Following recent observations at
supernova remnants \cite{2009Sci...325..719H} as well as theoretical
studies \cite{2005ApJ...620...44K}, we adopt a realistic value of this
parameter and assume that 50\% of the dissipated energy at strong
shocks is injected into CRs while this efficiency rapidly decreases
for weaker shocks \cite{2007A&A...473...41E}.

\subsection{Particle physics}

\subsubsection{Leptophilic models}
\label{sect:LP}
Sommerfeld enhancement, electron spectra

\subsubsection{Supersymetric dark matter}
neutralino, benchmark models, continuum emission, electron spectra

\subsubsection{Final state radiation}
The photon spectrum from resulting from FSR is universal with only a
weak dependence of the underlying particle physics model. The photon
yield from this process is given by (see
e.g. \cite{2008JHEP...01..049B})
\begin{equation}
\frac{\dd N_{X \bar{X}}}{\dd x} \approx \frac{\alpha Q_X^2}{\pi}
\mathcal{F}_X(x) \log\left[\frac{4 m_\chi^2\left(1-x\right)}{m_X^2}\right]\,.
\end{equation}
Here, the normalized photon energy $x=\eg/m_\chi c^2$, $\alpha =
e^2/\hbar c$ is the fine-structure constant, $Q_X^2$ and $m_X$ the
charge and mass of the particle $X$, respectively. The function
$\mathcal{F}_X(x)$ depends on the spin of the final state and is given
by
\begin{equation}
\mathcal{F}_\rmn{fermion}(x) = \frac{1+\left(1-x\right)^2}{x}\,
\end{equation}
for fermions.

\subsection{Radiative processes}

\subsubsection{Inverse Compton}
The source function of inverse Compton emission resulting from DM
annihilating is given by
\begin{equation}
  q_{\rm IC}\left(E_\gamma, r\right) = \int
  \dd E_\e\, \frac{\dd n_\e}{\dd E_\e} 
  P_{\rm IC}\left(E_\gamma,E_\e\right) ,
  \label{eq:ICemiss}
\end{equation}
where $P_{\rm IC}$ is derived by convolving the IC cross-section with
the differential target photon number density:
\begin{eqnarray}
\label{eq:KN_spec}
P_\rmn{IC} &=&
\frac{3\sigma_\rmn{T}m^2_\e c^5}{4E_\e^2}
\int\frac{n_\rmn{ph}(\eph)\dd \eph}{\eph}\nonumber \\
&\times&\left[2q
  \ln{q}+(1+2q)(1-q)+ \frac{1}{2}\frac{\left(\Gamma_\e q\right)^2}
     {1+\Gamma_\e q}\left(1-q\right)\right]\,,\nonumber \\
&&
\end{eqnarray}
where
\begin{equation}
\Gamma_\e=\frac{4\eph E_\e}{\left(m_\e c^2\right)^2}\,,\qquad \rmn{and} \qquad  
q=\frac{\eg}{\Gamma_\e(E_\e-\eg)}\,.
\end{equation}
We account for two major contributions to the radiative background
field $n_\ph$; the IR and UV light coming from emitting dust and
starlight where $n_\ph\equiv\frac{\dd^2 N_\ph^\clu}{\dd V \,\dd
  \eph}(\eph,r)= \frac{u_\iruv^\clu(\eph,r)}{\eph^2}$ and
$u_\iruv^\clu(\eph,r)$ is given by Eq.~(\ref{eq:E_IR_UV}). We model the
CMB photon spectrum as a photon gas that is isotropically distributed and
follows a black body spectrum with temperature $T$:
\begin{equation}
\label{eq:photon_gas}
  n_\rmn{ph}(\eph) = \frac{\dd^2 N_\ph}{\dd V \,\dd \eph} =
  \frac{1}{\pi^2(\hbar c)^3}\frac{\eph^2}{\exp(\eph/k_\B T)-1}\,.
\end{equation}
Here the the typical energy of a photon before scattering is given by
$<E_\ph>=\epsilon_\ph/n_\ph\approx\,2.70 k_\B T$, where $n_\ph$ and
$\epsilon_\ph$ are the number- and energy-density derived by
integrating $n_\ph(E_\ph)$ and $E_\ph n_\ph(\eph)$ over the photon
energy $\eph$, respectively.

The equilibrium spectrum of the electrons plus positrons in
Eq.~(\ref{eq:ICemiss}) is given by $\frac{\dd n_\e}{\dd E_\e}$ and
derived from the CRe diffusion equation:
\begin{eqnarray}
\label{eq:CRdiffusion}
\frac{\partial}{\partial t}\left(\frac{\dd n_\e}{\dd E_\e}\right) = 
&\nabla& \left[D\left(E_\e,\bx\right)\nabla\frac{\dd n_\e}{\dd E_\e}\right] + 
\frac{\partial}{\partial E_\e}
\left[b\left(E_\e,\bx\right) \frac{\dd n_\e}{\dd E_\e}\right]
 \nonumber \\
&+& Q(E_\e,\bx)\,,
\end{eqnarray}
where $D(E_\e,\bx)$ the diffusion coefficient and $b(E_\e,\bx)$ the
electron energy loss term. The source function $Q(E_\e,\bx)$ shows
the number of particles produced per unit time, energy and volume
element that are produced at the position $\bx$:
\begin{equation}
Q(E_\e,r)=\sum_f\frac{\dd N_\e^f}{\dd E_\e}(E_\e) B_f \Gamma(r)\,.
\end{equation}
The subscript $f$ ...(see cola), and $B_f$ is the branching factor.
Here $\frac{\dd N_\e^f}{\dd E_\e}$ denote the differential number of
electrons plus positrons resulting from an annihilation event. For
neutralinos annihilating directly into an electron and positron we
model the differential spectrum with $\frac{\dd N_\e^f}{\dd E_\e}=
2\delta(E_\e-m_\chi c^2)$. We use DarkSUSY to compute both the spectra
when neutralinos annihilate directly into a $\mu^+$ and $\mu^-$ in
the leptophilic model as well as in the four BM models where a
fraction of the annihilating neutralinos is converted into electrons
and positrons (see \cite{2009JCAP...01..016B} and references therein,
also see fit).

The electrons and positrons loose their energy on a timescale that is
shorter than the diffusive timescale in the ICM of galaxy clusters for
CRe energies above MeV (CHECK). Hence, we neglect the first term of
the r.h.s. in Eq.~\ref{eq:CRdiffusion}, and derive an expression for
the equilibrium number density:
\begin{eqnarray}
{\frac{\dd n_\e}{\dd E_\e}}\left(E_\e, r \right) &=&
 \frac{1}{b(E_\e, r)} \int_{E_\e}^{\mx c^2} \dd E_\e' \, 
  Q(E_\e', r),
\label{eq:nds}\\
b(E_\e,r) &=& \tilde{b}
\left[\frac{B^2_{\rm CMB}}{8\pi}+\frac{B^2(r)}{8\pi}+u_\iruv(r)\right] E_\e^2\,,
\\\tilde{b}&=&\frac{4\sigma_{\rm T}c}{3(m_{\rm e}c^2)^2}\,.
\end{eqnarray}
Here we have included three main loss processes for the electrons;
$B_{\rm CMB}=3.24(1+z)^2\mu {\rm G}$ denotes the equivalent field
strength of the CMB, we parameterize the magnetic field of the galaxy
cluster by $B(r) = 3\mu\rmn{G} \,[n_{\rm e}(r)/n_{\rm e}(0)]^{0.7}$,
which follows from flux frozen magnetic fields. In the following
subsection we derive a semi-analytic formula that estimates the
energy density of the dust and starlight component $u_\iruv(r)$
given by Eq.~(\ref{eq:E_IR_UV}).

{\it IC -- dust and starlight}\\
Galaxy clusters are typically characterized by the hot gas in the ICM
and the collection of gravitationally bound galaxies. The emission in
the IR and UV wavelengths emerge from dust and starlight in both the
galaxies and the ICM (e.g. \cite{2006ApJ...648L..29P} and
\cite{2009MNRAS.399.1694G}). Most of this radiation leaks out from the
galaxy into the ICM, which explains the very similar spectral shape
for these wavelengths. We use the light from galactic dust and
starlight that is emitted in the IR and UV band and is accurately
measured for the ISM \cite{2006ApJ...648L..29P}. We model these
spectra through a fit to the galactic spectra presented in
\cite{2006ApJ...648L..29P}. We extract the spatial cluster profile of
the emission from a stacked analysis of Sloan Digital Sky Survey
(SDSS) data at the redshift $\sim 0.25$
\cite{2005MNRAS.358..949Z}. Finally, we derive the normalization for
the emission from the galaxy cluster using the IR to X-ray luminosity
relation presented in the IR cluster luminosity analysis
\cite{2008A&A...490..547G}.

{\it Spectra -- galactic} \\
best fit, IR with a power-law function, UV with three power laws,
similar to Porter, vary normalization to account for uncertainties,
taken at $r=0$ in the galaxy
\begin{eqnarray}
  \eph^2\frac{\dd^2 N_\ph^\gal}{\dd \eph \dd V}
  &\equiv& u_\iruv^\gal(\eph) \nonumber \\ 
  &=& u_\rmn{ir}^\gal(\eph) +  u_\rmn{uv}^\gal(\eph)  \nonumber \\ 
  \\
  u_\rmn{uv}^\gal(\eph) &=& \frac{23\,\rmn{eV}}{\rmn{cm}^3} 
  \left(\frac{1.23\,\rmn{eV}}{\eph}\right)^{1.9} \nonumber \\
  &\times&\left[1+\left(\frac{2.04\,\rmn{eV}}{\eph}\right)^{20}\right]
  ^{-\frac{1.9}{20}}\nonumber \\
  &\times& \left[1+\left(\frac{0.78\,\rmn{eV}}{\eph}\right)^{20}\right]^{-\frac{2.6}{20}} \\
  u_\rmn{ir}^\gal(\eph) &=& 
  \frac{40\,\rmn{eV}}{\rmn{cm}^3} 
  \left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{4.9}\nonumber \\
  &\times& \left[1+\left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{1.9}\right]^{-4.9}\,,
\end{eqnarray}

{\it Spatial distribution - galaxy cluster}\\
 Instead of modelling the surface brightness with a de Vauocouleurs
 with the addition of a power law, we use a double beta profile model
 for simplicity of deprojection.

\begin{equation}
 S(\rmn{mag}\,\rmn{arcsec}^{-2}) = 
\mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})
\end{equation}
\cite{2010...book} where the sun's absolute magnitude in the red ban is given by
$\mathcal{M}_\odot=27.1$ \cite{2000asqu.book..339L}, and the luminosity
of the sun by $L_\odot=3.85\,10^{33} \rmn{erg}\,\rmn{s}^{-1}$.

surface brightness double $\beta$ models
\begin{equation}
S_\mathrm{IR} (r_\bot)= \sum_{i=1}^2 \,S_i\, 
\left[1 + \left( \frac{r_\bot}{r_{\mathrm{c}_i}}\right)^2\right]
^{-3\beta_i + 1/2},
\label{double_beta}
\end{equation}
where we found the following values as the best fit,
\begin{eqnarray}
 S_1&=&1.4\times10^{-5}\,\rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1},\,
r_{\mathrm{c}_1}=210\,\rmn{kpc},\,
\beta_1=0.44\nonumber\\
 S_2&=&6.0\times10^{-3}\,\rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1},\,
r_{\mathrm{c}_2}=2.8\,\rmn{kpc},\,
\beta_2=0.45\nonumber\\
\label{fit_spatial_IR}
\end{eqnarray}
%\begin{eqnarray}
% S = 1.8\times10^{-5}\left(1+\left(\frac{R}{0.4\,\rmn{Mpc}}\right)^{-2.4}+
% 3\times10^{-3}\left(1+\left(\frac{R}{0.004\,\rmn{Mpc}}\right)^{4.1}\right)^{-0.4}
%\end{eqnarray}

deprojection
\begin{eqnarray}
  j(r)  = \sum_{i=1}^2 \frac{S_i}{2\pi\,r_{\mathrm{c}_i}}\,
  \frac{6 \beta_i - 1}{\left(1 + r^2/r^2_{\mathrm{c}_i}\right)^{3\beta_i}}\,
  \mathcal{B}\left(\frac{1}{2},3\beta_i\right)\,,
\end{eqnarray}
where $\mathcal{B}(a,b)$ denotes the beta-function (abrahamovich and
stegun).  (Pfrommer and ensslin 2003)

{\it Normalization}\\
The spatial and spectral part of the IR and UV have an arbitrary
normalization where the specific energy density is given by
$u_\iruv^\clu(\eph, r) \propto u_\iruv^\gal(\eph)\,j(r)/j(0)$. We fix the
unitless normalization $N$ using the total IR energy
($E_{\ir,\vir}$) within $\rvir$
\begin{eqnarray} 
  E_{\ir,\vir} &=& L_\ir \frac{\rvir}{c} \nonumber \\
  &=&N\int_{\rvir} \int_{\ir} \,\frac{j(r)}{j(0)} 
  \frac{u_\ir^\gal(\eph)}{\eph}\,\dd V\dd \eph\,,\nonumber \\
\end{eqnarray}
where we in the first equality sign approximate the total energy of
the IR photons within $\rvir$ with the IR luminosity $L_\ir$
\cite{2008A&A...490..547G} times the typical timescale it takes for a
photon to propagate through the cluster (we assume that the cluster is
optically thin). From \cite{2008A&A...490..547G} we derive the
following luminosity scaling relation, $L_\ir=10^{21.7}\times
(L_\rmn{X}/\rmn{erg\,s}^{-1})^{0.53}\,\rmn{erg\,s}^{-1}$, where
$L_\rmn{X}$ is the X-ray luminosity within $\rvir$.

{\it Energy density}\\
The energy density from starlight and dust in al galaxy cluster is given by
\begin{eqnarray}
\label{eq:E_IR_UV}
u_\iruv^\clu(r) &=& \int \dd \eph \frac{\dd^2 N_\ph^\clu}{\dd \eph \dd V}\,\eph
=\int \dd \eph \frac{u_\iruv^\clu(\eph, r)}{\eph}
\nonumber \\
&=&  N\frac{j(r)}{j(0)} \int \dd \eph \frac{u_\iruv^\gal(\eph)}{\eph}\,. \nonumber \\
\end{eqnarray}

\del{In this section we present the formalism for the different
galaxy cluster emission components and show their contribution to the
total dark matter gamma-ray spectrum. We account for the emission
radiated both by final state radiation and inverse Compton where we
allow for upscattering through CMB, starlight, and dust.}

%Using a typical
%X-ray luminosity of $L_\rmn{X}=10^{44}\,\rmn{erg\,s}^{-1}$ results in a
%IR energy density
%$N\,E_\IR\,f_\rmn{tot}(E_\IR)\,j(20\,\rmn{kpc})=u_\IR\simeq 4\,\rmn{erg\,
%  cm}^{-1}$ in the region around 20~kpc from the cluster center at the
%energy of the maximum IR energy density $E_\IR=0.011\,\rmn{eV}$.

\section{Spectral gamma-ray distribution}

\section{Surface brightness profiles}

\section{Population studies}
Model predictions

%-) Consider having one figure where we compare the Einasto profile, to
%NFW, NFW w/ beta 0.6, and also the effect of a different concentration
%mass-scaling relation
%
%-) also, plot BM flux vs. psf, for models w/ and w/o substructures

%***********************************************

\begin{figure}%[t]
 \includegraphics[width=0.99\columnwidth]{figures/SB.photon.eps}
\caption{\it Spatial dependence of light from dust and stars. We show
  2D surface brightness profiles obtained from stacked clusters in the
  Sloan Digital Sky Survey (SDSS) at the redshift $z \sim 0.25$
  \cite{2005MNRAS.358..949Z}. The brightness profiles have been
  weighted with the $\rvir$ normalized area inside radius $r$, and
  trace the radial dependence of the luminosity from stars and
  galaxies. The crosses show the total observed light including the
  diffuse intracluster (ICL), the galaxies, and the brightest cluster
  galaxy (BCG) in the center of the cluster. The diamonds denote the
  observed light from the ICL and the BCG. The solid line show the fit
  to the data of the total light including the ICL, the BCG, and the
  galaxies, while the smooth component is represented by the dashed
  line that is fitted to only the ICL and the BCG.}
 \label{fig3}
\end{figure}

\begin{figure}%[t]
 \includegraphics[width=0.99\columnwidth]{figures/fit.porter.v2.eps}
\caption{\it Spectral dependence of radiation fields in a cluster of
  galaxies. The black dotted line in the left peak show the spectrum
  of CMB photons using a black body with a temperature of 2.7 K. The
  crosses in the middle and right peaks represent the measured spectra
  from dust and stars (SD), respectively, and are derived in
  \cite{2006ApJ...648L..29P} for a galaxy. We normalize the individual
  spectra from SD separately using the observed luminosity from SD in
  clusters. The SD luminosity is related to the cluster mass through
  Eq, where we use have used the mass $\mvir=4.0\,10^{13}\msun$ in this
  figure. Finally we renormalize the SD spectra to the radius
  $r=0.071\rvir$, where the smooth energy density of the SD light (see
  fig~\ref{fig3}) equals the energy density of the CMB. The red dashed
  lines show the fitted SD spectral model.}
 \label{fig4}
\end{figure}

\begin{figure}%[t]
 \includegraphics[width=0.99\columnwidth]{figures/ucool.eps}
\caption{\it Spatial dependence of the energy density of radiation
  fields in a cluster of galaxies. The energy density of the CMB, shown
  by the blue dotted line, is isotropic throughout the cluster, hence
  represented by a flat profile with
  $u_\rmn{cmb}=0.26\,\rmn{eV}\,\rmn{cm}^{-3}$. The energy density of
  the light from dust and stars (SD) is denoted by the red dashed line
  and the solid purple line for the total SD light and the smooth SD
  light, respectively. The SD light has been renormalized to a cluster
  with the mass $\mvir=4.0\,10^{13}\msun$. Finally we show the energy density
  two magnetic field models with a central magnetic field of 3~$\mu
  G$. The magnetic field scales with the gas density to the power
  $\alpha_\rmn{B}$; green dash-dotted line ($\alpha_\rmn{B}=0.5$) and
  orange dash-dotted line ($\alpha_\rmn{B}=0.7$). Note that the SD
  radiation is dominating the energy density inside $\sim0.1\,\rvir$.}
 \label{fig5}
\end{figure}

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
 \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v8.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v8.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v8.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v8.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
\caption{\it Comparing the differential flux from different models: we
  show the continuum emission from DM benchmark (BM) models
  (blue), electrons and positrons from DM BM models that inverse
  Compton upscattered both CMB photons (orange) as well as dust and
  star photons (green), and CR induced gamma-ray emission (red
  solid). The various linestyles are associated with individual DM BM
  models; $\Imm$ (dotted), $\Km$ (dashed), and $\Jm$
  (dash-dotted). The emission is calculated for the Fornax cluster
  using a point spread function of $0.1\deg$ and a boost from
  substructures of ...  We find bright prospects for detecting the
  continuum emission that is dominating the total emission in the GeV
  energy range. Also note that, above 100 MeV the total inverse
  Compton emission is at least a factor 10 smaller than the emission
  expected from both the continuum emission and the emission coming
  from CRs.}
 \label{fig7}
\end{minipage}
\end{figure*}

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v8.0.1deg.1.6T.SubMass.elmu.SF300.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv8.0.1deg.SubMass.noMW.woGal.eps}
\caption{\it Comparing the differential flux from different inverse
  Compton upscattered radiation fields in the Fornax cluster. We show
  the inverse Compton emissin induced by leptophilic DM in the left
  panel and by the $\Km$ benchmark model in the right panel. The
  contribution from each individual radiation field from top line to
  bottom line; CMB (green dashed-double-dotted), dust (blue dashed),
  stars (purple dashed-dotted). The sum of the three components are
  shown with the orange solid line. The black dotted line represents
  the upscattered CMB photons without any cooling from dust and
  stars. The red solid line show the CR induced gamma-ray flux. The
  black arrow show the differential upper limit from Fermi ADD
  REF. All fluxes are calculated within $\rvir$ with a point spread
  function of $0.1\deg$. The boost from Sommerfeld is ..., and from
  substructures is .}
 \label{fig6}
\end{minipage}
\end{figure*}

\begin{figure}
 \includegraphics[width=0.99\columnwidth]{figures/flux.int.v8.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
\caption{\it Comparing the energy integrated flux from different
  models: we show the emission from leptophilic (LP) models with green
  lines, $\Km$ benchmark model (BM) with blue lines, and the CR
  induced emission with a red line. The dotted and dashed lines show
  the inverse Compton (IC) upscattered CMB photons and star and dust
  photons, respectively. The green solid line show the final state
  radiation from the LP model, and the solid blue line show the
  continuum emission from the DM. The black arrow show the integrated
  flux upper limit set by Fermi.  The emission is calculated for the
  Fornax cluster using a point spread function of $0.1\deg$ and a
  boost from substructures of ...  We find that LP models are
  dominating the total flux in the entire energy range, where the IC
  upscattered CMB photons overproduce the upper limit by a factor 3.}
 \label{fig8}
\end{figure}

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
 \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v8.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v8.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v8.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v8.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}

\caption{\it Comparing the emission from different clusters. The
  emission from the clusters is calculated using a point spread
  function of $0.1\deg$ and includes the boost from substructures. We
  show the differential flux from four clusters; Fornax (upper left),
  Coma (upper right), Virgo (lower left), and Perseus (lower
  right). The different linestyles show; CR induced emission (solid),
  leptophilic models (LP) include both final state radiation and IC
  upscattered CMB, dust and star light (dotted), and benchmark $\Km$
  models (BM) include continuum emission, and IC upscattered CMB, dust
  and star light (dashed). The arrows have colors matching each
  cluster and show the differential upper limits set by Fermi in the
  energy ranges $0.2-1$~GeV, $1-10$~GeV, and $10-100$~GeV from left to
  right. For visualization we offset the arrows by increasing the mean
  energy by 30 percent in the opposite order as they appear in the
  figure, i.e. starting with Perseus. All fluxes are calculated within
  $\rvir$. We find that the lower GeV energy regime is most
  constraining, and induce upper limits on boost factors.}
 \label{fig9}
\end{minipage}
\end{figure*}

\begin{figure}
 \includegraphics[width=0.99\columnwidth]{figures/SB.v8.1GeV.SF300.SubMass.elmu.eps}
\caption{\it Comparing the surface brightness from different
  clusters. We show the surface brightness above the energy 1~GeV. The
  boost from substructures is included and we usie a point spread
  function of $0.1\deg$.}
 \label{fig20}
\end{figure}

\begin{figure}%[t]
 \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v8.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
\caption{\it Constraining leptophilic boost factors using flux upper
  limits. The emission is derived within $\rvir$ using a point spread
  function of $0.1\deg$. In order not to overproduce the Fermi
  differential flux upper limits in the energy interval $1-10$~GeV the
  boost from substructures and Sommerfeld enhancement (SFE) is
  constrained for four clusters; Fornax (red), Virgo (orange), M49
  (green), and NGC4636 (Blue). The arrows have colors matching each
  cluster and indicate the SFE in each cluster. The SFE has been
  rescaled from 300 that is required to explain the electron and
  positron excess observed in the Milky Way (MW) with leptophilic dark
  matter (refer to equation). If the DM interpretation is correct, we
  can constrain the smallest size of halos to be larger than
  $10\,\msun$. However, if the smallest size of DM halos is
  $10^{-6}\,\msun$, we can constrain the SFE to about 4 in Fornax,
  corresponding to a maximum SFE in the MW of about 10.}
 \label{fig10}
\end{figure}

\begin{figure}%[t]
 \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v8.1GeV.SF300.noSuB.vs.SubMass.elmu.eps}
\caption{\it The impact of substructures on surface brightness. We
  show the surface brightness at 1~GeV for the Fornax cluster using a
  very small point spread function of $10^{-5}\deg$ that reveals the
  details of the spatial profiles. The emission induced by CRs is
  denoted by the red solid line, the leptophilic models by green
  lines, and the DM $\Km$ benchmark model by blue lines. The dashed
  and dotted lines include and exclude substructures,
  respectively. Notice the nearly flat profiles when substructures are
  included, and the relative large boost at a percent of $\rvir$.}
 \label{fig11}
\end{figure}

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.49\columnwidth]{figures/SB.v8.1GeV.SF300.noSuB.elmu.eps}
  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v8.1GeV.SF300.noSuB.elmu.eps}
\caption{\it The surface brightness without substructures. We show the
  CR induced emission (red), leptophilic emission (green), and
  emission from the $\Km$ benchmark model (blue). The surface
  brightness above 1~GeV is derived using a very small point spread
  function ($\theta_\rmn{psf}=10^{-5}\deg$). LEFT PANEL: compare the
  surface brightness for different clusters; Fornax (solid), Coma
  (dotted), Virgo (dashed), and Perseus (dash-dotted).  RIGHT PANEL:
  compare different emission components in Fornax; dotted lines show
  the inverse Compton (IC) upscattered CMB photons, dashed lines show
  the IC upscattered photons from dust and stars, and blue solid line
  show the continuum emission from the $\Km$ benchmark
  model. \del{Since cooling is dominated by IR and UV processes in the
    center, the spatial dependence of the equilibrium electron spectra
    cancels the spatial dependence on the upscattered IR photon,
    resulting in a smooth halo dependence (density square) in the
    center. The spatial profile for the upscattered CMB photons is
    flatter in the center since the strong spatial dependence inferred
    from cooling counteracts the smooth halo contribution. Cluster
    outskirts dominated by the emission from DM, although large
    uncertainty in the gas density profile.}}
 \label{fig12}
\end{minipage}
\end{figure*}

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v8.SF300.SubMass.elmu.eps}
  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v8.SF300.SubMass.elmu.eps}
\caption{\it Surface brightness predicted for Cherenkov telescopes. We
  show the emission above $\eg=100$~GeV, include the boost from
  substructures and use a point spread function of $0.1\deg$. Left
  panel show the Fornax cluster and right panel the Virgo cluster. The
  emission is derived for the following components; CRs (red solid),
  continuum emission from the DM $\Km$ benchmark model (blue
  dash-dotted), as well as final state radiation (green dashed) and
  inverse Compton upscattered dust and star light (green dotted) from
  leptophilic DM. \del{GeV energies give rise to small BM model fluxes
    but high LP fluxes, other words BM models good for Cerenkov
    telescopes and LP good for Fermi (although the flat LP spectra
    give rise to high fluxes at high energies as well).}}
 \label{fig13}
\end{minipage}
\end{figure*}

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.DM.eps}
  \caption{\it Fermi flux upper limits contrasted to the predicted DM
    gamma-ray flux. We show the mean differential flux in the energy
    range $E_\gamma=1-10$~GeV for 32 clusters. The Fermi upper limits
    are shown with black arrows. The predicted fluxes are derived from
    both a leptophilic DM model that result in inverse Compton
    upscattered CMB photons (red), and the continuum emission from the
    DM $\Km$ benchmark model (blue). The leptophilic fluxes are ruled
    out by 14 of the clusters, with the strongest constraints set by
    Fornax and M49. We can not constrain the benchmark models,
    although our predictions are approaching the upper limits.}
 \label{fig14}
\end{minipage}
\end{figure*}

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.CR.diff.eps}
  \caption{\it Fermi flux upper limits contrasted to the predictions
    by the semi-analytic Pinzke and Pfrommer model for CR induced
    gamma-ray emission. We show the mean differential flux in the
    energy range $E_\gamma=1-10$~GeV for 32 clusters. The Fermi upper
    limits are shown with black arrows. The blue boxes show the
    gamma-ray emission from CR induced $\pi^0$\:s decaying, where the
    upper bound shows the estimates for an optemistic model and the
    lower bound a more conservative model excluding point sources (the
    realistic case is more likely in between, see
    \cite{2010MNRAS.409..449P} for details). Note that there is
    currently no tension between our predictions and upper limits from
    Fermi, although Virgo, Norma, and Coma are close and will in the
    coming years enforce constraints on the hadronic models.}
 \label{fig15}
\end{minipage}
\end{figure*}

%------------------------------------------------------------------

\smallskip
We wish to thank...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-0.7cm}
\bibliography{bibtex/paper}
%\bibliography{apssamp}
%\bibliographystyle{apsrev4-1}

\clearpage
\appendix

\begin{figure*}
\begin{minipage}{2.0\columnwidth}
 \includegraphics[width=0.49\columnwidth]{figures/fit.ds.flux.eps}
 \includegraphics[width=0.49\columnwidth]{figures/fit.epflux.int.eps}
\caption{\it The underlying source functions for different DM
  models. Crosses show the simulated data from DarkSUSY and the solid
  lines show the fit to the data using Eq.... LEFT PANEL: normalized
  differential continuum spectra for four different DM benchmark (BM)
  models; $\Imm$ model (red), $\Jmm$ (orange), $\Km$ (green), and
  $\Jm$ (blue). RIGHT PANEL: number of electron and positron per DM
  annihilation above the electron energy $E_\e$ for different dark
  matter models; $\Imm$ BM model (red), $\Jmm$ BM model (orange),
  $\Km$ BM model (green), and $\Jm$ BM model (blue), leptophilic (LP)
  DM annihilating into electrons and positrons (purple), and LP DM
  annihilating into muons (black).}
 \label{fig17}
\end{minipage}
\end{figure*}

\begin{figure}%[t]
 \includegraphics[width=0.99\columnwidth]{figures/dens.fornax.eps}
\caption{\it Comparing different electron number density profiles for
  the Fornax cluster. Black crosses show the density profile inferred
  from deprojected Chandra and Rosat X-ray surface brightness
  observations CITE. The total hybrid profile shown by the red solid
  line represent the best fit to the data, where the fitted individual
  density components are shown by the black dotted lines. The blue
  solid line show the single beta density profile inferred from the
  HIFLUGCS catalogue. Due to insufficient sensitivity to the outer part
  in the plotted data, we infer the outer slope found in the HIFLUGCS
  catalogue.}
 \label{fig18}
\end{figure}

\begin{figure*}%[t]
\begin{minipage}{2.0\columnwidth}
 \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.CR.eps}
\caption{\it Comparing the flux from clusters in the extended HIFLUGCS
  catalogue. We show the energy integrated gamma-ray flux induced by
  CRs for the 106 clusters included in the extended HIFLUGCS
  catalogue. The fluxes are calculated within $\rvir$, and are derived
  using a single beta profile for each cluster's gas density profile
  (see text for details). The upper panel show the energy integrated
  flux above 100~MeV (left side) and above 100~GeV (right side), both
  as a function of HIFLUGCS cluster ID. The name of the eight
  brightest clusters are written out. The lower panel show the
  relative difference between the gamma-ray flux predicted by
  mass-luminosity scaling relations compared to the flux computed
  using the semi-analytically model CITE The name of the
  clusters with the largest offset are printed out, which correlate
  with cool core clusters.}
 \label{fig19}
\end{minipage}
\end{figure*}

\begin{figure*}%[t]
\begin{minipage}{2.0\columnwidth}
 \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.DM.eps}
\caption{\it Comparing the flux from clusters in the extended HIFLUGCS
  catalogue. We show the energy integrated gamma-ray fluxes derived
  from both leptophilic DM that result in inverse Compton upscattered
  CMB photons (red), and the continuum emission from the DM $\Km$
  benchmark model (blue). The fluxes are calculated within $\rvir$
  for each of the 106 clusters included in the extended HIFLUGCS
  catalogue, and are derived using a single beta profile for each
  cluster's gas density profile (see text for details). The upper
  panel show the energy integrated flux above 100~MeV and the lower
  panel above 10~GeV, both as a function of HIFLUGCS cluster ID. The
  name of the four brightest clusters are written out, where Fornax
  and M49 are the brightest targets.}
 \label{fig21}
\end{minipage}
\end{figure*}

\end{document}

### 2011-03-29 paper.tex
test
updated figures+Theory

@@
 %NEW
+\newcommand{\rmn}{\mathrm}
 \newcommand{\bx}{{\bf x}}
@@
 \newcommand{\psf}{\theta_\rmn{res}}
-\newcommand{\ph}{{\rm ph}}
+\newcommand{\ph}{\rmn{ph}}
 \newcommand{\eph}{E_\ph}
 \newcommand{\nph}{N_\ph}
-\newcommand{\vir}{{\rmn vir}}
-\newcommand{\gal}{{\rmn gal}}
-\newcommand{\iruv}{{\rmn sd}}
-\newcommand{\clu}{{\rmn cl}}
-\newcommand{\sfe}{{\rmn sfe}}
-\newcommand{\sub}{{\rmn sub}}
-\newcommand{\msun}{{M_\odot}}
+\newcommand{\vir}{\rmn{vir}}
+\newcommand{\gal}{\rmn{gal}}
+\newcommand{\sd}{\rmn{SD}}
+\newcommand{\clu}{\rmn{cl}}
+\newcommand{\sfe}{\rmn{sfe}}
+\newcommand{\sub}{\rmn{sub}}
+\newcommand{\msun}{M_\odot}
+\newcommand{\ee}{E_\rmn{e}}
+\newcommand{\stars}{\rmn{stars}}
+\newcommand{\dust}{\rmn{dust}}
+\newcommand{\lx}{L_\rmn{X}}
+\newcommand{\s}{\rmn{s}}
 
@@
 \newcommand{\eeq}{\end{equation}}
-\newcommand{\rmn}{\mathrm}
-\newcommand{\GeV}{\,{\rm GeV}}
-\newcommand{\TeV}{\,{\rm TeV}}
-\newcommand{\eV}{\,{\rm eV}}
-\newcommand{\dd}{\mathrm{d}}
+\newcommand{\gev}{\rm{GeV}}
+\newcommand{\tev}{\rm{TeV}}
+\newcommand{\ev}{\rm{eV}}
+\newcommand{\dd}{\rmn{d}}
 \newcommand{\mx}{\ensuremath{m_{\chi}}}
@@
 \newcommand{\sigv}{\ensuremath{\sigma_v}}
-\newcommand{\ic}{\mathrm{IC}}
+\newcommand{\ic}{\rmn{IC}}
 \newcommand{\egamma}{\ensuremath{E_{\gamma}}}
-\newcommand{\dic}{\mathrm{dIC}}
-\newcommand{\fsr}{\mathrm{FSR}}
-\newcommand{\CR}{\mathrm{CR}}
+\newcommand{\dic}{\rmn{dIC}}
+\newcommand{\fsr}{\rmn{FSR}}
+\newcommand{\CR}{\rmn{CR}}
 \newcommand{\rhos}{\ensuremath{\rho_s}}
@@
 We denote the total source function by $q_{\rm sum}(\eg,r)$, where we
-include contributions from four main processes; leptophilic DM
+include contributions from five main processes; leptophilic DM
 annihilating to $\mu^+/\mu^-$ decaying to $\rm{e}^+/\rm{e}^-$ pairs
@@
 \end{equation}
-where $ q_{\pi^0-\gamma}(\eg,r)$ denotes the CR to gamma-ray source
-function (see Sect.~\ref{sect:CRs} and \cite{2010MNRAS.409..449P}
-for more details). The total differerntial boost factor for DM is the
-product of enhancement factors from SFE $\B_\sfe(\sigv)$ (see
-Sect.~\ref{sect:LP}) and from substructure enhancement over the
-smooth halo contribution $\B_{\sub,i}(r) = 1+q_\sub(r)/q_{\rmn{sm},i}(r)$
+where the subscript $i$ runs over the gamma-ray producing DM
+channels. The differential CR to gamma-ray source function is denoted
+by $q_{\pi^0-\gamma}(\eg,r)$, where we refer the reader to
+Sect.~\ref{sect:CRs} and \cite{2010MNRAS.409..449P} for further
+details. The total differential boost factor for DM is the product of
+enhancement factors from SFE $\B_\sfe(\sigv)$ (see
+Sect.~\ref{sect:LP}) and from substructure enhancement over the smooth
+halo contribution $\B_{\sub,i}(r) = 1+q_\sub(r)/q_{\rmn{sm},i}(r)$
 (see Sect.~\ref{sect:subst}) and is denoted by
@@
 \begin{equation}
-\quad q_{\rmn{sm},i} (\egamma,r) = \sum_j
+\label{eq:q_sm}
+q_{\rmn{sm},i} (\egamma,r) = \sum_j
 \frac{\dd \ngammaj}{\dd E_\gamma} \Gamma_j(r)\,.
 \end{equation}
-We represent the annihilation rate density with $\Gamma_j =
-(\rho/\mx)^2 \, \sigmaannv_j/2$, where $j$ runs over all $\gamma$-ray
+Here the annihilation rate density is given by 
+\begin{equation}
+\label{eq:ann_rate}
+\Gamma_j(r) = \frac{1}{2} \left(\frac{\rho(r)}{\mx}\right)^2 
+\, \sigmaannv_j\,
+\end{equation}
+where the subscript $j$ runs over all kinematically allowed gamma-ray
 producing channels each with the spectrum $\frac{\dd
-  \ngammaj}{\dd\eg}$ and annihilation cross-section $\sigmaannv_j$.
-The DM density is modeled by an Einasto density profile
+  \ngammaj}{\dd\eg}$ and annihilation cross-section $\sigmaannv_j$. We
+denote the DM mass with $\mx$ and the DM density profile with
+$\rho(r)$. Typically the universal Navarro-Frenk-White (NFW) density
+profile provide a good fit to both the observed and simulated
+clusters. It can be considered as a special case of the 5-parameter profile:
+\begin{equation}
+\rho(r) = \frac{\rho_\s}{\left(r/r_\s+\right)^\gamma
+  \left[1+\left(r/r_\s\right)^\alpha\right]^\delta}\,,\quad
+\delta=\frac{\beta-\gamma}{\alpha}\,,
+\label{eq:rho_nfw}
+\end{equation}
+where a cuspy NFW profile is given by
+$(\alpha,\beta,\gamma)=(1,3,1)$. The scaling radius is given by $r_\s$
+and the characteristic density by $\rhos=(\Delta\rhoc/3)\,
+c^3/(\log(1+c)-(c/(1+c)))$, where the halo mass dependent
+concentration parameter $c$ is derived from a power-law fit to
+cosmological simulations with $\mvir \gtrsim 10^{10} \msun$
+\cite{2008MNRAS.391.1940M},
+\begin{equation}
+\label{eq:cfit}
+  c=3.56 \times \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-0.098}\,.
+\end{equation}
+This mass scaling agrees well with \cite{2009ApJ...707..354Z} for
+cluster-mass halos after converting the concentration definitions
+according to \cite{2003ApJ...584..702H}. In this work we choose to
+model the DM density by an Einasto density profile
 \begin{equation}
@@
 \end{equation}
-that is slightly shallower than the conventional Navaro-Frenk-White
-(NFW) profile in the center, but provide a better fit to simulated DM
-halos \cite{2010MNRAS.402...21N}. We denote the density where the
-profile has a slope of $-2$ by $\rho_{-2}$, and the radius by
-$r_{-2}$. Assuming that all the flux from an NFW profile originate
+that is slightly shallower in the center than the conventional
+Navarro-Frenk-White (NFW) profile, but provide a better fit to
+simulated DM halos \cite{2010MNRAS.402...21N}. We denote the density
+where the profile has a slope of $-2$ by $\rho_{-2}$, and the radius
+by $r_{-2}$. Assuming that all the flux from an NFW profile originate
 from within the scale radius $\rs=\rvir/c$, and all the flux from an
@@
 to be the radius at which the mean density within is a factor
-$\Delta=200$ times the critical density $\rhoc$ of the universe. The
-characteristic density of the NFW profile $\rhos=(\Delta\rhoc/3)\,
-c^3/(\log(1+c)-(c/(1+c)))$, where the halo mass dependent
-concentration parameter $c$ is derived from a power-law fit to
-cosmological simulations with $\mvir \gtrsim 10^{10} \msun$
-\cite{2008MNRAS.391.1940M},
-\begin{equation}
-\label{eq:cfit}
-  c=3.56 \times \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-0.098}\,.
-\end{equation}
-This mass scaling agrees well with \cite{2009ApJ...707..354Z} for
-cluster-mass halos after converting the concentration definitions
-according to \cite{2003ApJ...584..702H}.
+$\Delta=200$ times the critical density $\rhoc$ of the universe.
 
@@
 \label{sect:subst}
-High-resolution DM simulations of the Milky Way (MW) find vast amount
-of substrucures in the periphery of DM halos. Since the rate of which
-DM is annihilating depends on the density squared, the resulting flux
-is boosted compared to the smooth density distribution. Recent
-simulations suggest a boost from substructures of the order of ten up
-to a few 100 \cite{2008MNRAS.391.1685S, 2008JPhCS.125a2008K} for a MW
-size halo. Based on the result from \cite{2008Natur.456...73S}, we
-find the best fit\footnote{Our approach of fitting the scaling
-  behavior of $\rmn{L_{sub}}(<r)$ directly from numerical simulations
+High-resolution DM only simulations of Milky Way (MW) type halos find
+substantial amount of substructures in the periphery of DM halos,
+while the substructures in the center are erased due to dynamical
+disruption. Since the rate of which DM is annihilating depends on the
+density squared, the resulting flux is boosted compared to the smooth
+density distribution. Recent simulations suggest a flux enhancement
+from substructures of the order of ten up to a few 100
+\cite{2008MNRAS.391.1685S, 2008JPhCS.125a2008K} for a MW size
+halo. Using the Aquarius simulations \cite{2008Natur.456...73S}, we
+fit \footnote{Our approach of fitting the scaling behavior of
+  $\rmn{L_{sub}}(<r)$ directly from numerical simulations
   self-consistently accounts for the radial dependence of the
@@
 luminosity from smooth substructures (i.e. substructures within
-substructures are not included) inside radius $r$ with
+substructures are not included) inside radius $r$. The best fit is
+given by
 \begin{equation}
@@
 \left(\frac{r}{\rvir}\right)$. The first normalization constant is
-given by
+derived from the simulations:
 \begin{equation}
@@
 assume that the power-law scaling relation in Eq.~(\ref{eq:C1}) is
-valid down to the minimum mass of DM halos, which is conventionaly in
+valid down to the minimum mass of DM halos, which is conventionally in
 the cold dark matter universe
@@
 $10^{-6}\msun$. Note that potentially the power-law could flatten
-torwards smaller mass scales although current simulations show no hits
-of such a behaviour and in addition we are approaching the asymptotic
+towards smaller mass scales although current simulations show no hits
+of such a behavior and in addition we are approaching the asymptotic
 behavior in the power spectrum on these scales(CHECK). For DM halos
@@
 \end{equation}
-where $M_{\rm 200,sim}=1.9\times10^{12}\msun$ is the mass of the MW
+where $M_{\rm 200sim}=1.9\times10^{12}\msun$ is the mass of the MW
 halo in the simulation \cite{2008Natur.456...73S}.
 
-large uncertaint observationally in density profiles
-
-In Fig.~\ref{fig:radial_lum} we compare the radial dependence of the
-accumulative luminosity from different smooth cluster density profiles
-to the substructure boosted luminosity at different mass scles. The
-
+Recent detailed galaxy cluster observations find a core like density
+profile with an inner slope of $\beta=0.6$, where $\beta\gtrsim 1$ can
+be ruled out to a $>95$\% confidence \cite{2011ApJ...728L..39N}. This
+finding is hard to reconcile with simulations that typically prefere a
+steeper central profile. The different density profiles have a large
+impact on the luminosity from annihilating DM, although the details of
+the density profile can be neglected compared to the dominating boost
+from substructures. In Fig.~\ref{fig:radial_lum} we compare the radial
+dependence of the accumulative luminosity from different smooth
+cluster density profiles to the substructure boosted luminosity at
+different mass scales. We recalculate the density contrast for the
+core like density profile $\rhos$ and rescale the concentration
+parameter in Eq.~(\ref{eq:cfit}) with $300/160$
+\cite{2011ApJ...728L..39N} to account for the more centralized scale
+radius in a core like cluster. The emission coming from the core
+compared to a cuspy like density profile is about 30\% larger within
+$\rvir$. This difference is build up within 10\% of $\rvir$
+(i.e. close to $r_\rmn{s}$). The emission from an Einasto density
+profile is about 50\% larger than the cuspy NFW profile in the
+periphery of the cluster, where the difference is mainly build up at a
+few percent of $\rvir$. The substructure boosted luminosities is
+neglible in the center of halos, but integrated out to $\rvir$ the
+boost is about; 10 for dwarf galaxies, $10^2$ for galaxies, and $10^3$
+for galaxy clusters.
 \begin{figure}%[t]
@@
   been normalized with the luminosity within $\rvir$ from a cuspy NFW
-  profile. Note the large expected boost from substructures in
-  clusters ($\sim1000$), and the relative small boost in dwarf
-  galaxies ($\sim20$).}
+  profile. We have assumed the standard value for the limiting
+  substructure mass of $10^{-6}\,\msun$. Note the large expected
+  boost from substructures in clusters ($\sim1000$), and the relative
+  small boost in dwarf galaxies ($\sim20$).}
  \label{fig:radial_lum}
@@
 
+Even though the bulk of substructures have been erased in the central
+regions of DM halos, a cluster in projection has a significant
+enhancement due to substructures at a radius of just a few percent of
+$\rvir$. In Fig.~\ref{fig:radial_emis} we show the luminosity
+dominating radius for substructures and smooth density profiles, both
+for three different mass scales. It clearly shows how that the main
+contribution from the substructures is coming from outer parts of the
+DM halos, while the main contribution from the smooth density profiles
+peaks around the scale radius. NOT QUITE, ALSO FIGURE IS SHOWING DIFF
+VOLUME, FAC 3 DIFFERENCE, WHAT DO WE REALLY LEARN FROM THE FIGURE
 \begin{figure}
   \includegraphics[width=0.99\columnwidth]{figures/emissiv.sub.eps}
-  \caption{\it Volume weighted luminosity for different at different
-    scales. The solid lines show the emissivity from a NFW density
-    profile for three different mass scales; a $\mvir=10^{15}\,\msun$
-    galaxy cluster (red), a $\mvir=10^{12}\,\msun$ galaxy (orange), a
+  \caption{\it Radial dependence of differential luminosity at
+    different mass scales. The solid lines show the emissivity from a
+    cuspy $\beta=1.0$ NFW density profile for three different mass
+    scales; an $\mvir=10^{15}\,\msun$ galaxy cluster (red), an
+    $\mvir=10^{12}\,\msun$ galaxy (orange), and an
     $\mvir=10^{8}\,\msun$ dwarf galaxy (green). The dashed lines show
@@
     scales. All emissivities have been normalized with the luminosity
-    from a NFW profile within $\rvir$.}
-  \label{fig2}
+    within $\rvir$ from a cuspy NFW profile. We have assumed the
+    standard value for the limiting substructure mass of
+    $10^{-6}\,\msun$.}
+  \label{fig:radial_emis}
 \end{figure}
@@
 of the extended emission and the observed power-law slope it seems
-quite natural that they are of hadronic origin. Especilly since the
+quite natural that they are of hadronic origin. Especially since the
 long cooling time of cosmic ray protons (CRs) allows for both an
@@
 populations in clusters through observing the $\pi^0$ bump at about
-100~MeV in the spectra. We adopt the spectrally and spatially
-universal gamma-ray model developed by Pinzke \& Pfrommer
-\cite{2010MNRAS.409..449P} to estimate the emission from decaying
-$\pi^0$:s that dominates over the inverse Compton emission from
-primary and secondary electrons above 100~MeV in clusters. The
-gamma-ray formalism was derived from high resolution simulations of
-clusters of galaxies that included radiative hydrodynamics, star
-formation, supernova feedback, and followed CR physics using a novel
-formulation that trace the most important injection and loss processes
-self-consistently while accounting for the CR pressure in the equation
-of motion
+100~MeV in the spectra.
+
+We adopt the spectrally and spatially universal gamma-ray model
+developed by Pinzke \& Pfrommer \cite{2010MNRAS.409..449P} to estimate
+the emission from decaying $\pi^0$:s that dominates over the inverse
+Compton emission from primary and secondary electrons above 100~MeV in
+clusters. The gamma-ray formalism was derived from high resolution
+simulations of clusters of galaxies that included radiative
+hydrodynamics, star formation, supernova feedback, and followed CR
+physics using a novel formulation that trace the most important
+injection and loss processes self-consistently while accounting for
+the CR pressure in the equation of motion
 \cite{2008A&A...481...33J,2007A&A...473...41E,2006MNRAS.367..113P}.
@@
 \subsection{Particle physics}
+\label{sect:PF}
 
@@
 
-\subsubsection{Supersymetric dark matter}
+\subsubsection{Supersymmetric dark matter}
 neutralino, benchmark models, continuum emission, electron spectra
@@
 \subsection{Radiative processes}
+In this section we outline the basics of inverse Compton (IC)
+emission. As target radiation fields we consider both cosmic microwave
+background (CMB) photons, and the light from stars and dust (SD). We
+derive a semi-analytic model from which we can estimate the SD
+spectral and spatial distributions as a simple function of cluster
+mass.
 
 \subsubsection{Inverse Compton}
-The source function of inverse Compton emission resulting from DM
-annihilating is given by
-\begin{equation}
-  q_{\rm IC}\left(E_\gamma, r\right) = \int
-  \dd E_\e\, \frac{\dd n_\e}{\dd E_\e} 
-  P_{\rm IC}\left(E_\gamma,E_\e\right) ,
+\label{sect:IC}
+The standard IC source function is given by
+\cite{1979rpa..book.....R}:
+\begin{eqnarray}
+  q_{\rmn IC}(\eg, r) &=&  \frac{\dd^3 N_\gamma}{\dd V\,\dd t\,\dd \eg} = 
+ \frac{3}{4}c\,\sigma_\rmn{T}
+\int\dd \eph \frac{n_\rmn{ph}(\eph)}{\eph}\nonumber\\
+&\times& \int \dd \ee\,\frac{\dd n_\e}{\dd \ee}(\ee,r)\,
+ \frac{\left(m_\e c^2\right)^2}{\ee^2}G(\Gamma_\e,q)\,,\nonumber\\
   \label{eq:ICemiss}
-\end{equation}
-where $P_{\rm IC}$ is derived by convolving the IC cross-section with
-the differential target photon number density:
-\begin{eqnarray}
+\end{eqnarray}
+where $\ee$ is the energy of the upscattering electrons and $\eph$ is
+the energy of the background photon field. We represent the Thomson
+cross-section with $\sigma_\rmn{T}$ and the full differential
+Klein-Nishina (KN) cross-section is captured by
+\cite{1970RvMP...42..237B}:
+\begin{equation}
 \label{eq:KN_spec}
-P_\rmn{IC} &=&
-\frac{3\sigma_\rmn{T}m^2_\e c^5}{4E_\e^2}
-\int\frac{n_\rmn{ph}(\eph)\dd \eph}{\eph}\nonumber \\
-&\times&\left[2q
-  \ln{q}+(1+2q)(1-q)+ \frac{1}{2}\frac{\left(\Gamma_\e q\right)^2}
-     {1+\Gamma_\e q}\left(1-q\right)\right]\,,\nonumber \\
-&&
-\end{eqnarray}
+G(\Gamma_\e,q) = 2q\ln{q}+(1+2q)(1-q)+ 
+\frac{1}{2}\frac{\left(\Gamma_\e q\right)^2\left(1-q\right)}
+     {1+\Gamma_\e q}\,,
+\end{equation}
 where
 \begin{equation}
-\Gamma_\e=\frac{4\eph E_\e}{\left(m_\e c^2\right)^2}\,,\qquad \rmn{and} \qquad  
-q=\frac{\eg}{\Gamma_\e(E_\e-\eg)}\,.
-\end{equation}
-We account for two major contributions to the radiative background
-field $n_\ph$; the IR and UV light coming from emitting dust and
-starlight where $n_\ph\equiv\frac{\dd^2 N_\ph^\clu}{\dd V \,\dd
-  \eph}(\eph,r)= \frac{u_\iruv^\clu(\eph,r)}{\eph^2}$ and
-$u_\iruv^\clu(\eph,r)$ is given by Eq.~(\ref{eq:E_IR_UV}). We model the
-CMB photon spectrum as a photon gas that is isotropically distributed and
-follows a black body spectrum with temperature $T$:
+\Gamma_\e=\frac{4\eph \ee}{\left(m_\e c^2\right)^2}\,,\qquad \rmn{and} \qquad  
+q=\frac{\eg}{\Gamma_\e\left(\ee-\eg\right)}\,.
+\end{equation}
+The full KN cross-section accounts for the less efficient energy
+transfer between the photon and electron and results in a steepening
+of the IC gamma-ray spectrum. In the low energy Thomson regime the IC
+spectrum is given by $E_\gamma^{-(\alpha_\e-1)/2}$, however when
+$\Gamma_\e \gg 1$ the IC spectrum steepens due to the KN suppression
+to $\eg^{-\alpha_\e}\log(\eg)$ .
+
+We account for two major contributions to the number density of
+radiative background fields $n_\ph$; the cosmic microwave background
+(CMB) photons and the infra-red (IR) to ultra-violet (UV) light
+emitted by starlight and dust (SD). The number density for the SD is
+given by $n_\ph\equiv\frac{\dd^2 N_\ph}{\dd V \,\dd
+  \eph}(\eph,r)= \frac{u_\sd(\eph,r)}{\eph^2}$ where the SD
+energy density $u_\sd(\eph,r)$ is given in Eq.~(\ref{eq:U_SD}). We
+model the CMB photon spectrum as a photon gas that is isotropically
+distributed and follows a black body spectrum with the temperature
+$T=2.73\,$~K:
 \begin{equation}
@@
 \end{equation}
-Here the the typical energy of a photon before scattering is given by
-$<E_\ph>=\epsilon_\ph/n_\ph\approx\,2.70 k_\B T$, where $n_\ph$ and
-$\epsilon_\ph$ are the number- and energy-density derived by
-integrating $n_\ph(E_\ph)$ and $E_\ph n_\ph(\eph)$ over the photon
-energy $\eph$, respectively.
-
-The equilibrium spectrum of the electrons plus positrons in
-Eq.~(\ref{eq:ICemiss}) is given by $\frac{\dd n_\e}{\dd E_\e}$ and
-derived from the CRe diffusion equation:
+Note that the typical energy of a black body photon before scattering
+is given by $<\eph>=\epsilon_\ph/\tilde{n}_\ph\approx\,2.70 k_\B T$,
+where $\tilde{n}_\ph$ and $\epsilon_\ph$ are the number- and
+energy-density derived by integrating $n_\ph(\eph)$ and $\eph
+n_\ph(\eph)$ over the photon energy $\eph$, respectively.
+
+The electrons injected from annihilating DM also suffer from diffusive
+and radiative losses. Hence we have to calculate the equilibrium
+spectrum of the electrons plus positrons denoted by $\frac{\dd
+  n_\e}{\dd \ee}$ in Eq.~(\ref{eq:ICemiss}). We derive this stationary
+solution using the CR transport equation (neglecting convection and
+re-acceleration effects):
 \begin{eqnarray}
 \label{eq:CRdiffusion}
-\frac{\partial}{\partial t}\left(\frac{\dd n_\e}{\dd E_\e}\right) = 
-&\nabla& \left[D\left(E_\e,\bx\right)\nabla\frac{\dd n_\e}{\dd E_\e}\right] + 
-\frac{\partial}{\partial E_\e}
-\left[b\left(E_\e,\bx\right) \frac{\dd n_\e}{\dd E_\e}\right]
+\frac{\partial}{\partial t}\left(\frac{\dd n_\e}{\dd \ee}\right) = 
+&\nabla& \left[D\left(\ee,\bx\right)\nabla\frac{\dd n_\e}{\dd \ee}\right] + 
+\frac{\partial}{\partial \ee}
+\left[b\left(\ee,\bx\right) \frac{\dd n_\e}{\dd \ee}\right]
  \nonumber \\
-&+& Q(E_\e,\bx)\,,
+&+& q_\e(\ee,\bx)\,,
 \end{eqnarray}
-where $D(E_\e,\bx)$ the diffusion coefficient and $b(E_\e,\bx)$ the
-electron energy loss term. The source function $Q(E_\e,\bx)$ shows
-the number of particles produced per unit time, energy and volume
-element that are produced at the position $\bx$:
-\begin{equation}
-Q(E_\e,r)=\sum_f\frac{\dd N_\e^f}{\dd E_\e}(E_\e) B_f \Gamma(r)\,.
-\end{equation}
-The subscript $f$ ...(see cola), and $B_f$ is the branching factor.
-Here $\frac{\dd N_\e^f}{\dd E_\e}$ denote the differential number of
-electrons plus positrons resulting from an annihilation event. For
-neutralinos annihilating directly into an electron and positron we
-model the differential spectrum with $\frac{\dd N_\e^f}{\dd E_\e}=
-2\delta(E_\e-m_\chi c^2)$. We use DarkSUSY to compute both the spectra
-when neutralinos annihilate directly into a $\mu^+$ and $\mu^-$ in
-the leptophilic model as well as in the four BM models where a
-fraction of the annihilating neutralinos is converted into electrons
-and positrons (see \cite{2009JCAP...01..016B} and references therein,
-also see fit).
+where $D(\ee,\bx)$ denotes the diffusion coefficient and $b(\ee,\bx)$
+the energy loss term. The source function $q_\e(\ee,\bx)$ yields the
+number of electrons and positrons produced per unit time, energy and
+volume element at the position $\bx$:
+\begin{equation}
+q_\e(\ee,r)=\sum_f\frac{\dd N_{\e,f}}{\dd \ee}(\ee) B_f \Gamma_f(r) \,,
+\end{equation}
+where the annihilation rate density $\Gamma_f(r)$ is defined in
+Eq.~(\ref{eq:ann_rate}). The sum runs over the kinematically allowed
+annihilation final states $f$, each with a branching ratio $B_f$ and a
+differential spectrum $\frac{\dd N_\e^f}{\dd \ee}$ that represents the
+number of electrons plus positrons resulting from an annihilation
+event. For neutralinos annihilating directly into electrons and
+positrons we model the spectral distribution with $\frac{\dd
+  N_\e^f}{\dd \ee}= 2\delta(\ee-m_\chi c^2)$. We use DarkSUSY to
+compute both the spectra when neutralinos annihilate directly into a
+$\mu^+$ and $\mu^-$ in the leptophilic model as well as in the four BM
+models where a fraction of the annihilating neutralinos is converted
+into electrons and positrons (see Sect.~\ref{sect:PF} for further
+details).
+%(see \cite{2009JCAP...01..016B} and references therein,
+%also see fit).
 
@@
 shorter than the diffusive timescale in the ICM of galaxy clusters for
-CRe energies above MeV (CHECK). Hence, we neglect the first term of
-the r.h.s. in Eq.~\ref{eq:CRdiffusion}, and derive an expression for
-the equilibrium number density:
+CR electrons with $\ee \gtrsim\,$~MeV (CHECK). Hence, we neglect the
+first term of the r.h.s. in Eq.~(\ref{eq:CRdiffusion}), and derive an
+expression for the equilibrium number density:
 \begin{eqnarray}
-{\frac{\dd n_\e}{\dd E_\e}}\left(E_\e, r \right) &=&
- \frac{1}{b(E_\e, r)} \int_{E_\e}^{\mx c^2} \dd E_\e' \, 
-  Q(E_\e', r),
+{\frac{\dd n_\e}{\dd \ee}}\left(\ee, r \right) &=&
+ \frac{1}{b(\ee, r)} \int_{\ee}^{\mx c^2} \dd \ee' \, 
+  Q(\ee', r),
 \label{eq:nds}\\
-b(E_\e,r) &=& \tilde{b}
-\left[\frac{B^2_{\rm CMB}}{8\pi}+\frac{B^2(r)}{8\pi}+u_\iruv(r)\right] E_\e^2\,,
+b(\ee,r) &=& \tilde{b}
+\left[\frac{B^2_{\rm CMB}}{8\pi}+\frac{B^2(r)}{8\pi}+u_\sd(r)\right] \ee^2\,,
 \\\tilde{b}&=&\frac{4\sigma_{\rm T}c}{3(m_{\rm e}c^2)^2}\,.
 \end{eqnarray}
-Here we have included three main loss processes for the electrons;
-$B_{\rm CMB}=3.24(1+z)^2\mu {\rm G}$ denotes the equivalent field
-strength of the CMB, we parameterize the magnetic field of the galaxy
-cluster by $B(r) = 3\mu\rmn{G} \,[n_{\rm e}(r)/n_{\rm e}(0)]^{0.7}$,
-which follows from flux frozen magnetic fields. In the following
-subsection we derive a semi-analytic formula that estimates the
-energy density of the dust and starlight component $u_\iruv(r)$
-given by Eq.~(\ref{eq:E_IR_UV}).
-
-{\it IC -- dust and starlight}\\
-Galaxy clusters are typically characterized by the hot gas in the ICM
-and the collection of gravitationally bound galaxies. The emission in
-the IR and UV wavelengths emerge from dust and starlight in both the
-galaxies and the ICM (e.g. \cite{2006ApJ...648L..29P} and
-\cite{2009MNRAS.399.1694G}). Most of this radiation leaks out from the
-galaxy into the ICM, which explains the very similar spectral shape
-for these wavelengths. We use the light from galactic dust and
-starlight that is emitted in the IR and UV band and is accurately
-measured for the ISM \cite{2006ApJ...648L..29P}. We model these
-spectra through a fit to the galactic spectra presented in
-\cite{2006ApJ...648L..29P}. We extract the spatial cluster profile of
-the emission from a stacked analysis of Sloan Digital Sky Survey
-(SDSS) data at the redshift $\sim 0.25$
-\cite{2005MNRAS.358..949Z}. Finally, we derive the normalization for
-the emission from the galaxy cluster using the IR to X-ray luminosity
-relation presented in the IR cluster luminosity analysis
-\cite{2008A&A...490..547G}.
-
-{\it Spectra -- galactic} \\
-best fit, IR with a power-law function, UV with three power laws,
-similar to Porter, vary normalization to account for uncertainties,
-taken at $r=0$ in the galaxy
-\begin{eqnarray}
-  \eph^2\frac{\dd^2 N_\ph^\gal}{\dd \eph \dd V}
-  &\equiv& u_\iruv^\gal(\eph) \nonumber \\ 
-  &=& u_\rmn{ir}^\gal(\eph) +  u_\rmn{uv}^\gal(\eph)  \nonumber \\ 
-  \\
-  u_\rmn{uv}^\gal(\eph) &=& \frac{23\,\rmn{eV}}{\rmn{cm}^3} 
-  \left(\frac{1.23\,\rmn{eV}}{\eph}\right)^{1.9} \nonumber \\
-  &\times&\left[1+\left(\frac{2.04\,\rmn{eV}}{\eph}\right)^{20}\right]
-  ^{-\frac{1.9}{20}}\nonumber \\
-  &\times& \left[1+\left(\frac{0.78\,\rmn{eV}}{\eph}\right)^{20}\right]^{-\frac{2.6}{20}} \\
-  u_\rmn{ir}^\gal(\eph) &=& 
-  \frac{40\,\rmn{eV}}{\rmn{cm}^3} 
-  \left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{4.9}\nonumber \\
-  &\times& \left[1+\left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{1.9}\right]^{-4.9}\,,
-\end{eqnarray}
-
-{\it Spatial distribution - galaxy cluster}\\
- Instead of modelling the surface brightness with a de Vauocouleurs
- with the addition of a power law, we use a double beta profile model
- for simplicity of deprojection.
-
-\begin{equation}
- S(\rmn{mag}\,\rmn{arcsec}^{-2}) = 
-\mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})
-\end{equation}
-\cite{2010...book} where the sun's absolute magnitude in the red ban is given by
-$\mathcal{M}_\odot=27.1$ \cite{2000asqu.book..339L}, and the luminosity
-of the sun by $L_\odot=3.85\,10^{33} \rmn{erg}\,\rmn{s}^{-1}$.
-
-surface brightness double $\beta$ models
-\begin{equation}
-S_\mathrm{IR} (r_\bot)= \sum_{i=1}^2 \,S_i\, 
+Here we include the three main radiative loss processes for the CR
+electrons and positrons: (1) IC losses on CMB photons where the
+equivalent field strength of the CMB is denoted by $B_{\rm
+  CMB}=3.24(1+z)^2\mu\rmn{G}$. (2) Synchrotron losses on ambient
+magnetic fields where we parameterize the magnetic field in the galaxy
+cluster by $B(r) = 3\mu\rmn{G} \,[n_{\rm e}(r)/n_{\rm
+    e}(0)]^{\alpha_\B}$, which follows from flux frozen magnetic
+fields. We adopt a magnetic decline of $\alpha_\B=0.7$ in this
+work. (3) IC losses on starlight and dust with an energy density
+$u_\sd(r)$ given by Eq.~(\ref{eq:U_SD}), which we derive in the
+following subsection.
+
+{\it IC -- dust and starlight}\\ Galaxy clusters are typically
+characterized by the hot gas in the ICM and the collection of
+gravitationally bound galaxies. The emission in the IR and UV
+wavelengths emerge from dust and starlight in both the galaxies and
+the ICM (e.g. \cite{2006ApJ...648L..29P} and
+\cite{2009MNRAS.399.1694G}). Much of the radiation leaks out from the
+galaxy into the ICM, which give rise to similar spectral distributions
+for the galaxies and the ICM in these wavelengths. Hence, we use the
+accurately measured light from galactic dust and starlight for the ISM
+to model the ICM. We characterize the spectra through a fit to the
+galactic spectra presented in \cite{2006ApJ...648L..29P}. The spatial
+distribution of the SD light in clusters is extracted from a stacked
+emission analysis of Sloan Digital Sky Survey (SDSS) data at the
+redshift $\sim 0.25$ \cite{2005MNRAS.358..949Z}. Finally, we fix the
+normalization for the light from stars and dust in an galaxy cluster
+individually using using the IR to X-ray luminosity scaling relation
+found in \cite{2008A&A...490..547G}. The X-ray luminosities for the
+clusters used in this work are listed in the extended HIghest X-ray
+FLUx Galaxy Cluster Sample (HIFLUGCS) \cite{2002ApJ...567..716R} from
+the Rosat all-sky survey. Note that we have added the Virgo cluster to
+the sample that we nevertheless refer to as extended HIFLUGCS
+catalogue in the following.
+
+{\it Spatial distribution -- stars and dust}\\ Our goal in this
+section is to derive a simple spatial model for the distribution of
+stars and dust in galaxy clusters. For this reason we use stacked
+cluster observations by Sloan in the $r$-band that trace the stars. We
+assume that the dust trace the stars in the clusters, which should be
+accurate to the order of magnitude estimate that we are interested in
+here. The stacked surface brightness profiles in
+\cite{2005MNRAS.358..949Z} are measured at redshift $z \sim 0.25$ with
+an average mass of the clusters of $4.0\times10^{13}\,\msun$. The
+profiles are build up out of three components; diffuse intracluster
+light (ICL), galaxies, and the brightest cluster galaxy (BCG) in the
+center of clusters. However, the total volume overlap of the ISM to
+the cluster is very small compared to the ICL- and BCG overlap with
+the cluster, thus the relative contribution of the galaxies to the IC
+emission is suppressed. To remove this bias we cut out the galaxies
+that have been smoothed over the cluster in the stacked analysis. In
+Fig.~\ref{fig:SD_spatial} we show the SDSS stacked brightness profiles
+as well as the fitted profiles\footnote{The measured brightness is
+  converted into units of $\rmn{erg}\,\rmn{s}^{-1}$ using
+  \cite{2010...book} $S(\rmn{mag}\,''^{-2}) =
+  \mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})$,
+  where the sun's absolute magnitude in the $r$-band is given by
+  $\mathcal{M}_\odot=27.1$ \cite{2000asqu.book..339L} and the
+  luminosity of the sun by $L_\odot=3.85\,10^{33}
+  \rmn{erg}\,\rmn{s}^{-1}$.}. Our benchmark spatial model are show
+with the solid black line, and include the contribution from the ICL
+and BCG.
+
+\begin{figure}%[t]
+ \includegraphics[width=0.99\columnwidth]{figures/SB.photon.eps}
+\caption{\it Spatial dependence of light from stars and dust. We show
+  2D surface brightness profiles in the $r$-band ($\sim 1\,\ev$)
+  obtained from stacked clusters in the Sloan Digital Sky Survey
+  (SDSS) at the redshift $z \sim 0.25$ \cite{2005MNRAS.358..949Z}. The
+  brightness profiles have been weighted with the $\rvir$ normalized
+  area inside radius $r$, and trace the radial dependence of the
+  luminosity from stars and galaxies. The crosses show the total
+  observed star light including the diffuse intracluster (ICL), the
+  galaxies, and the brightest cluster galaxy (BCG) in the center of
+  the cluster. The diamonds denote the observed star light from the
+  ICL and the BCG. The solid line show the fit to the data of the
+  total light including the ICL, the BCG, and the galaxies, while the
+  smooth component is represented by the dashed line that is fitted to
+  only the ICL and the BCG.}
+ \label{fig:SD_spatial}
+\end{figure}
+
+Instead of modelling the surface brightness with a de Vaucouleur
+profile with the addition of a power-law, we use a double beta profile
+model for simplicity of deprojection given by:
+\begin{equation}
+S_\sd (r_\bot)= \sum_{i=1}^2 \,S_i\, 
 \left[1 + \left( \frac{r_\bot}{r_{\mathrm{c}_i}}\right)^2\right]
-^{-3\beta_i + 1/2},
+^{-3\beta_i + 1/2}\,,
 \label{double_beta}
 \end{equation}
-where we found the following values as the best fit,
+where we found the following best fitted central brightness ($S_i$),
+core radius ($r_{\mathrm{c}_i}$), and slope ($\beta_i$):
 \begin{eqnarray}
@@
 r_{\mathrm{c}_2}=2.8\,\rmn{kpc},\,
-\beta_2=0.45\nonumber\\
+\beta_2=0.45\,.\nonumber\\
 \label{fit_spatial_IR}
 \end{eqnarray}
-%\begin{eqnarray}
-% S = 1.8\times10^{-5}\left(1+\left(\frac{R}{0.4\,\rmn{Mpc}}\right)^{-2.4}+
-% 3\times10^{-3}\left(1+\left(\frac{R}{0.004\,\rmn{Mpc}}\right)^{4.1}\right)^{-0.4}
-%\end{eqnarray}
-
-deprojection
+The 3D spatial profile is derived by deprojecting the surface
+brightness in Eq.~(\ref{double_beta}) (see
+e.g. \cite{2004A&A...413...17P} for details about the deprojection):
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $\mathcal{B}(a,b)$ denotes the beta-function (abrahamovich and
-stegun).  (Pfrommer and ensslin 2003)
-
-{\it Normalization}\\
-The spatial and spectral part of the IR and UV have an arbitrary
-normalization where the specific energy density is given by
-$u_\iruv^\clu(\eph, r) \propto u_\iruv^\gal(\eph)\,j(r)/j(0)$. We fix the
-unitless normalization $N$ using the total IR energy
-($E_{\ir,\vir}$) within $\rvir$
+where $\mathcal{B}(a,b)$ denotes the beta-function
+\cite{1965hmfw.book.....A}.
+
+{\it Spectral distribution -- stars and dust} \\ Our goal in this
+section is to derive a simple spectral model for stars and dust in
+galaxy clusters. Since the radiation from galaxies are expected to
+leak out into the ICM, we expect similar spectral distributions, at
+least to the order of magnitude that we are interested in here. Hence, we
+use the IR to UV spectrum derived in \cite{2006ApJ...648L..29P} for a
+MW type galaxy to characterize the spectral distribution of dust and
+starlight in a cluster. Note, however, that we only keep the spectral
+shape, and renormalize the spectral distribution using the luminosity
+from stars and dust.
+
+In Fig.~\ref{fig:SD_spectra} we show the SD spectral distribution
+together with the CMB black-body distribution in a galaxy cluster,
+both at the radius $r=0.071\rvir$ where the smooth energy density of
+the SD light (see Fig.~\ref{fig:SD_Edens}) equals the energy density
+of the CMB. We have renormalized both the spectral SD data and the
+fitted SD spectra using the luminosity from stars and dust
+individually (see below for further details about the
+renormalization).
+\begin{figure}%[t]
+ \includegraphics[width=0.99\columnwidth]{figures/fit.porter.v2.eps}
+\caption{\it Spectral dependence of radiation fields in a cluster of
+  galaxies. The black dotted line in the left peak show the spectrum
+  of CMB photons using a black body with a temperature of 2.73 K. The
+  crosses in the middle and right peaks represent the measured spectra
+  from stars and dust (SD), respectively, and are derived in
+  \cite{2006ApJ...648L..29P} for a galaxy. We normalize the individual
+  SD spectrum separately using the observed luminosity from SD in
+  clusters. The SD luminosity is related to the cluster mass through
+  Eq, where we use have used the mass $\mvir=4.0\,10^{13}\msun$ in
+  this figure. Finally we renormalize the SD spectra to the radius
+  $r=0.071\rvir$, where the smooth energy density of the SD light (see
+  fig~\ref{fig:SD_Edens}) equals the energy density of the CMB. The
+  red dashed lines show the fitted SD spectral model.}
+ \label{fig:SD_spectra}
+\end{figure}
+We choose to fit the spectrum of the dust that peaks at about
+$10^{-2}\,\ev$ with a double power-law, and the slightly wider
+spectral distribution of the stars that peaks at about $1\,\ev$ with a
+tipple power-law. We find the best fit spectra for the SD in a
+cluster through:
 \begin{eqnarray}
-  E_{\ir,\vir} &=& L_\ir \frac{\rvir}{c} \nonumber \\
-  &=&N\int_{\rvir} \int_{\ir} \,\frac{j(r)}{j(0)} 
-  \frac{u_\ir^\gal(\eph)}{\eph}\,\dd V\dd \eph\,,\nonumber \\
+  \eph^2\frac{\dd^2 N_\ph}{\dd \eph \dd V}
+  &\equiv& u_\sd(\eph) =  \sum_i N_i(\lx) u_i^\gal(\eph)\,,\nonumber \\ 
+\rmn{where}\quad i&=&\{\rmn{stars,dust}\} \qquad \rmn{and}\\ 
+% &=&  N_\dust(\lx) u_\dust^\gal(\eph) + N_\stars(\lx) u_\stars^\gal(\eph)  \nonumber \\ 
+%  \\
+  u_\stars^\gal(\eph) &=& \frac{23\,\rmn{eV}}{\rmn{cm}^3} 
+  \left(\frac{1.23\,\rmn{eV}}{\eph}\right)^{1.9} \nonumber \\
+  &\times&\left[1+\left(\frac{2.04\,\rmn{eV}}{\eph}\right)^{20}\right]
+  ^{-\frac{1.9}{20}}\nonumber \\
+  &\times& \left[1+\left(\frac{0.78\,\rmn{eV}}{\eph}\right)^{20}\right]^{-\frac{2.6}{20}}\,, \\
+  u_\dust^\gal(\eph) &=& 
+  \frac{40\,\rmn{eV}}{\rmn{cm}^3} 
+  \left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{4.9}\nonumber \\
+  &\times& \left[1+\left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{1.9}\right]^{-4.9}\,.
 \end{eqnarray}
-where we in the first equality sign approximate the total energy of
-the IR photons within $\rvir$ with the IR luminosity $L_\ir$
-\cite{2008A&A...490..547G} times the typical timescale it takes for a
-photon to propagate through the cluster (we assume that the cluster is
-optically thin). From \cite{2008A&A...490..547G} we derive the
-following luminosity scaling relation, $L_\ir=10^{21.7}\times
-(L_\rmn{X}/\rmn{erg\,s}^{-1})^{0.53}\,\rmn{erg\,s}^{-1}$, where
-$L_\rmn{X}$ is the X-ray luminosity within $\rvir$.
-
-{\it Energy density}\\
-The energy density from starlight and dust in al galaxy cluster is given by
+
+{\it Normalization}\\ HARD TO READ, TO MUCH DETAIL, MOVE TO APPENDIX?,
+MABEY KEEP NORM CONSTATS AND A VERY SHORT SUMMARY?? The spatial and
+spectral distribution functions of the light from stars and dust in a
+cluster are both normalized with a constant determined from the
+luminosity in each respective wavelength. The specific energy density
+is given by
 \begin{eqnarray} 
-\label{eq:E_IR_UV}
-u_\iruv^\clu(r) &=& \int \dd \eph \frac{\dd^2 N_\ph^\clu}{\dd \eph \dd V}\,\eph
-=\int \dd \eph \frac{u_\iruv^\clu(\eph, r)}{\eph}
+u_\sd(\eph, r) &=& \frac{j(r)}{j(0)}\,u_\sd(\eph) \nonumber\\
+&=& \frac{j(r)}{j(0)}\,\sum_i N_i(\lx) u_i^\gal(\eph)\,,
+\end{eqnarray}
+where we fix the unitless normalization $N_i(\lx)$ using the total
+energy of the light in stars and dust ($E_{i,\vir}$) within $\rvir$:
+\begin{eqnarray} 
+  E_{i,\vir} &=& L_i \frac{\rvir}{c} \nonumber \\
+  &=&N_i(\lx)\int_{\rvir} \int_i \,\frac{j(r)}{j(0)} 
+  \frac{u_i^\gal(\eph)}{\eph}\,\dd V\dd \eph\,,\nonumber \\
+ &\rmn{for}&\qquad i=\{\rmn{stars,dust}\}\,.
+\label{eq:E_SD}
+\end{eqnarray}
+Here we approximate the total energy of the photons within $\rvir$
+with the luminosity $L_i$ \cite{2008A&A...490..547G} times the typical
+timescale it takes for a photon to propagate through the cluster (we
+assume that the cluster is optically thin). Once we estimated the SD
+luminosities for a well representative cluster, we use a IR to X-ray
+scaling relation to estimate the luminosity from an arbitrary cluster
+with mass $\mvir$:
+\begin{equation}
+L=1.05\times10^{45}\,\rmn{erg\,s}^{-1}\,
+\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,,
+\label{eq:SD-X}
+\end{equation}
+where $\lx$ is the luminosity of the X-ray emitting gas within
+$\rvir$.
+
+The normalization constant for the star light [$N_\stars(\lx)$] is derived
+in the following three steps: (1) We use the average apparent magnitude
+in the $(r+i)$-band $m_{(r+i),0.25}\approx 15.5$
+\cite{2005MNRAS.358..949Z} of a cluster with the average mass
+$\mvir=4.0\times10^{13}\msun$ at a redshift $z=0.25$ to derive the
+luminosity from the stars:
+\begin{equation}
+L_\stars=10^{\frac{m_\odot-m_{(r+i),0.25}}{2.5}}
+\left(\frac{d_\clu}{d_\odot}\right)^2 L_\odot
+\approx 7.1\times10^{44}\,\rmn{erg}\,\rmn{s}^{-1}\,,
+\label{eq:L_star}
+\end{equation}
+where the apparent magnitude of the sun $m_\odot\approx -27.1$, the
+distance to the sun $d_\odot=4.85\times10^{-6}\,\rmn{pc}$, the
+luminosity of the sun $L_\odot=3.85\times10^{34}\,\rmn{erg\,s}^{-1}$,
+and the distance to the cluster $d_\clu=1.26\times10^9\,\rmn{pc}$. (2)
+We use the IR to X-ray scaling relation in Eq.~(\ref{eq:SD-X}) to find
+a more general form of the luminosity from stars in
+Eq.~(\ref{eq:L_star}) that is valid for an arbitrary cluster mass. The
+cluster X-ray luminosities are found in the extended HIFLUGCS
+catalogue \cite{2002ApJ...567..716R} to which we have added the Virgo
+cluster. (3) The normalization constant for the stars is
+determined from the above steps together with Eq.~(\ref{eq:E_SD})
+where we integrate over the cluster volume and spectral distribution
+of the stars. It is given by
+\begin{equation}
+ N_\stars(\lx) = 1.2\times10^{-9}\,
+\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,.
+\label{eq:N_stars}
+\end{equation}
+Note that since the luminosities include the contribution from
+galaxies, we have integrated the spatial distribution including
+galaxies to derive the normalization. Once the normalization is fixed,
+the SD energy densities are derived from the spatial distribution
+where galaxies have been excluded.
+
+The normalization constant for the dust [$N_\dust(\lx)$] is derived in the
+following four steps: (1) We use a cluster with the the average mass
+$\mvir=4.0\times10^{13}\msun$ and estimate the X-ray luminosity from
+the X-ray to mass scaling relations derived for the Representative
+XMM-Newton Cluster Structure Survey (REXCESS) in
+\cite{2009A&A...498..361P}:
+\begin{equation}
+\lx=1.18\times 10^{44}\,\rmn{erg\,s}^{-1}
+\left(\frac{M_{200}}{10^{14}\msun}\right)^{1.81}\,,
+\end{equation}
+where we have used that $M_\rmn{200} \approx 1.58\,M_\rmn{500}$ for a
+small cluster \footnote{We derive the factor 1.58 using
+  $M_\rmn{200}/M_\rmn{500}$ for the clusters in the HIFLUGCS catalogue
+  with a mass similar to $\mvir=4.0\times10^{13}\msun$ that we use to
+  derive the luminosity from dust.}. (2) From the IR to X-ray scaling
+relation in Eq.~(\ref{eq:SD-X}) we can now estimate calculate the
+luminosity from the dust for a $\mvir=4.0\times10^{13}\msun$ cluster;
+$L_\dust=4.7\times10^{44}\,\rmn{erg\,s}^{-1}$. (3) We generalize
+Eq.~(\ref{eq:L_star}) to an arbitrary cluster mass using
+Eq.~(\ref{eq:SD-X}) together with the cluster X-ray luminosities in
+the extended HIFLUGCS catalogue. (4) The normalization constant for
+the dust can now be determined from from the above steps together with
+Eq.~(\ref{eq:E_SD}) where we integrate over the cluster volume and
+spectral distribution of the dust. It is given by
+\begin{equation}
+ N_\dust(\lx) = 1.4\times10^{-9}\,
+\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,.
+\label{eq:N_stars}
+\end{equation}
+Note that since the luminosities include the contribution from
+galaxies, we have integrated the spatial distribution including
+galaxies to derive the normalization. Once the normalization is fixed,
+the SD energy densities are derived from the spatial distribution
+where galaxies have been excluded.
+
+{\it Energy density}\\ The energy density from starlight and dust in
+a galaxy cluster is given by
+\begin{eqnarray}
+\label{eq:U_SD}
+u_\sd(r) &=& \int \dd \eph \frac{\dd^2 N_\ph}{\dd \eph \dd V}\,\eph
+=\int \dd \eph \frac{u_\sd(\eph, r)}{\eph}
 \nonumber \\
-&=&  N\frac{j(r)}{j(0)} \int \dd \eph \frac{u_\iruv^\gal(\eph)}{\eph}\,. \nonumber \\
+&=&  \frac{j(r)}{j(0)} \int \dd \eph \sum_i 
+N_i(\lx) u_i^\gal(\eph)\,. \nonumber \\
 \end{eqnarray}
+In Fig.~\ref{fig:SD_Edens} we compare the energy densities from
+different radiation fields in a galaxy cluster with the mass
+$\mvir=4.0\times10^{13}\msun$. We use two different profiles for the
+SD energy density, where the total includes the ICL, the BCG and all
+the galaxies, while the galaxies are excluded in the smooth
+contribution. We find that even for a cluster with a relative small
+mass the energy density of the SD components dominates over the CMB
+and the magnetic fields (with a central B field of 3~$\mu G$) within
+about 10\% of $\rvir$. Outside this radius the CMB is dominating the
+energy density of the cluster, hence the density of the magnetic
+fields are always subdominant in the cluster and can safely be removed
+from cluster IC calculations for reasonable central densities and
+spectral index. Although, in this work we keep its contribution to the
+total energy density for consistency.
+
+\begin{figure}%[t]
+ \includegraphics[width=0.99\columnwidth]{figures/ucool.eps}
+ \caption{\it Spatial dependence of the energy density of radiation
+   fields in a cluster of galaxies. The energy density of the CMB,
+   shown by the blue dotted line, is isotropic throughout the cluster,
+   hence represented by a flat profile with
+   $u_\rmn{cmb}=0.26\,\rmn{eV}\,\rmn{cm}^{-3}$. The energy density of
+   the light from stars and dust (SD) is denoted by the red dashed
+   line and the solid purple line for the total SD light and the
+   smooth SD light, respectively. The SD light has been renormalized
+   to a cluster with the mass $\mvir=4.0\,10^{13}\msun$. Finally we
+   show the energy density two magnetic field models with a central
+   magnetic field of 3~$\mu G$. The magnetic field scales with the gas
+   density to the power $\alpha_\rmn{B}$; green dash-dotted line
+   ($\alpha_\rmn{B}=0.5$) and orange dash-dotted line
+   ($\alpha_\rmn{B}=0.7$). Note that the SD radiation is dominating
+   the energy density inside $\sim0.1\,\rvir$.}
+ \label{fig:SD_Edens}
+\end{figure}
 
@@
 
-\section{Surface brightness profiles}
-
-\section{Population studies}
-Model predictions
-
-%-) Consider having one figure where we compare the Einasto profile, to
-%NFW, NFW w/ beta 0.6, and also the effect of a different concentration
-%mass-scaling relation
-%
-%-) also, plot BM flux vs. psf, for models w/ and w/o substructures
-
-%***********************************************
-
-\begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/SB.photon.eps}
-\caption{\it Spatial dependence of light from dust and stars. We show
-  2D surface brightness profiles obtained from stacked clusters in the
-  Sloan Digital Sky Survey (SDSS) at the redshift $z \sim 0.25$
-  \cite{2005MNRAS.358..949Z}. The brightness profiles have been
-  weighted with the $\rvir$ normalized area inside radius $r$, and
-  trace the radial dependence of the luminosity from stars and
-  galaxies. The crosses show the total observed light including the
-  diffuse intracluster (ICL), the galaxies, and the brightest cluster
-  galaxy (BCG) in the center of the cluster. The diamonds denote the
-  observed light from the ICL and the BCG. The solid line show the fit
-  to the data of the total light including the ICL, the BCG, and the
-  galaxies, while the smooth component is represented by the dashed
-  line that is fitted to only the ICL and the BCG.}
- \label{fig3}
-\end{figure}
-
-\begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/fit.porter.v2.eps}
-\caption{\it Spectral dependence of radiation fields in a cluster of
-  galaxies. The black dotted line in the left peak show the spectrum
-  of CMB photons using a black body with a temperature of 2.7 K. The
-  crosses in the middle and right peaks represent the measured spectra
-  from dust and stars (SD), respectively, and are derived in
-  \cite{2006ApJ...648L..29P} for a galaxy. We normalize the individual
-  spectra from SD separately using the observed luminosity from SD in
-  clusters. The SD luminosity is related to the cluster mass through
-  Eq, where we use have used the mass $\mvir=4.0\,10^{13}\msun$ in this
-  figure. Finally we renormalize the SD spectra to the radius
-  $r=0.071\rvir$, where the smooth energy density of the SD light (see
-  fig~\ref{fig3}) equals the energy density of the CMB. The red dashed
-  lines show the fitted SD spectral model.}
- \label{fig4}
-\end{figure}
-
-\begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/ucool.eps}
-\caption{\it Spatial dependence of the energy density of radiation
-  fields in a cluster of galaxies. The energy density of the CMB, shown
-  by the blue dotted line, is isotropic throughout the cluster, hence
-  represented by a flat profile with
-  $u_\rmn{cmb}=0.26\,\rmn{eV}\,\rmn{cm}^{-3}$. The energy density of
-  the light from dust and stars (SD) is denoted by the red dashed line
-  and the solid purple line for the total SD light and the smooth SD
-  light, respectively. The SD light has been renormalized to a cluster
-  with the mass $\mvir=4.0\,10^{13}\msun$. Finally we show the energy density
-  two magnetic field models with a central magnetic field of 3~$\mu
-  G$. The magnetic field scales with the gas density to the power
-  $\alpha_\rmn{B}$; green dash-dotted line ($\alpha_\rmn{B}=0.5$) and
-  orange dash-dotted line ($\alpha_\rmn{B}=0.7$). Note that the SD
-  radiation is dominating the energy density inside $\sim0.1\,\rvir$.}
- \label{fig5}
-\end{figure}
-
 \begin{figure*}
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v8.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v8.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v8.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v8.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v9.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v9.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v9.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v9.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
 \caption{\it Comparing the differential flux from different models: we
@@
 \begin{minipage}{2.0\columnwidth}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v8.0.1deg.1.6T.SubMass.elmu.SF300.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv8.0.1deg.SubMass.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v9.0.1deg.1.6T.SubMass.elmu.SF300.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv9.0.1deg.SubMass.noMW.woGal.eps}
 \caption{\it Comparing the differential flux from different inverse
   Compton upscattered radiation fields in the Fornax cluster. We show
-  the inverse Compton emissin induced by leptophilic DM in the left
+  the inverse Compton emission induced by leptophilic DM in the left
   panel and by the $\Km$ benchmark model in the right panel. The
@@
   shown with the orange solid line. The black dotted line represents
-  the upscattered CMB photons without any cooling from dust and
-  stars. The red solid line show the CR induced gamma-ray flux. The
+  the upscattered CMB photons without any cooling from stars and
+  dust. The red solid line show the CR induced gamma-ray flux. The
   black arrow show the differential upper limit from Fermi ADD
@@
 \begin{figure}
- \includegraphics[width=0.99\columnwidth]{figures/flux.int.v8.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/flux.int.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
 \caption{\it Comparing the energy integrated flux from different
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v8.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v8.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v8.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v8.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
 
@@
 
+\section{Surface brightness profiles}
+
 \begin{figure}
- \includegraphics[width=0.99\columnwidth]{figures/SB.v8.1GeV.SF300.SubMass.elmu.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.v9.1GeV.SF300.SubMass.elmu.eps}
 \caption{\it Comparing the surface brightness from different
   clusters. We show the surface brightness above the energy 1~GeV. The
-  boost from substructures is included and we usie a point spread
+  boost from substructures is included and we use a point spread
   function of $0.1\deg$.}
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v8.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
 \caption{\it Constraining leptophilic boost factors using flux upper
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v8.1GeV.SF300.noSuB.vs.SubMass.elmu.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v9.1GeV.SF300.noSuB.vs.SubMass.elmu.eps}
 \caption{\it The impact of substructures on surface brightness. We
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.v8.1GeV.SF300.noSuB.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v8.1GeV.SF300.noSuB.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.v9.1GeV.SF300.noSuB.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v9.1GeV.SF300.noSuB.elmu.eps}
 \caption{\it The surface brightness without substructures. We show the
@@
   the inverse Compton (IC) upscattered CMB photons, dashed lines show
-  the IC upscattered photons from dust and stars, and blue solid line
+  the IC upscattered photons from stars and dust, and blue solid line
   show the continuum emission from the $\Km$ benchmark
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v8.SF300.SubMass.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v8.SF300.SubMass.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v9.SF300.SubMass.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v9.SF300.SubMass.elmu.eps}
 \caption{\it Surface brightness predicted for Cherenkov telescopes. We
@@
 \end{figure*}
+
+\section{Population studies}
+Model predictions
 
@@
     gamma-ray emission from CR induced $\pi^0$\:s decaying, where the
-    upper bound shows the estimates for an optemistic model and the
+    upper bound shows the estimates for an optimistic model and the
     lower bound a more conservative model excluding point sources (the
@@
 We wish to thank...
+
+%-) Consider having one figure where we compare the Einasto profile, to
+%NFW, NFW w/ beta 0.6, and also the effect of a different concentration
+%mass-scaling relation
+%
+%-) also, plot BM flux vs. psf, for models w/ and w/o substructures
 
@@
   $\Jm$ (blue). RIGHT PANEL: number of electron and positron per DM
-  annihilation above the electron energy $E_\e$ for different dark
+  annihilation above the electron energy $\ee$ for different dark
   matter models; $\Imm$ BM model (red), $\Jmm$ BM model (orange),

### 2011-03-30 paper.tex
updated figures+theory

@@
 \newcommand{\s}{\rmn{s}}
+\newcommand{\Kp}{\rmn{K}`}
+\newcommand{\Ip}{\rmn{I}`}
+\newcommand{\Js}{\rmn{J}^*}
+\newcommand{\Jp}{\rmn{J}`}
 
@@
 \newcommand{\ir}{\rmn{ir}}
-\newcommand{\Km}{\rmn{K}`}
-\newcommand{\Imm}{\rmn{I}`}
-\newcommand{\Jm}{\rmn{J}^*}
-\newcommand{\Jmm}{\rmn{J}`}
 
@@
 \begin{equation}
-\rho(r) = \frac{\rho_\s}{\left(r/r_\s+\right)^\gamma
+\rho(r) = \frac{\rhos}{\left(r/r_\s+\right)^\gamma
   \left[1+\left(r/r_\s\right)^\alpha\right]^\delta}\,,\quad
@@
 $(\alpha,\beta,\gamma)=(1,3,1)$. The scaling radius is given by $r_\s$
-and the characteristic density by $\rhos=(\Delta\rhoc/3)\,
-c^3/(\log(1+c)-(c/(1+c)))$, where the halo mass dependent
-concentration parameter $c$ is derived from a power-law fit to
-cosmological simulations with $\mvir \gtrsim 10^{10} \msun$
-\cite{2008MNRAS.391.1940M},
+and the characteristic density by 
+\begin{equation}
+\rhos(c)=\frac{\Delta\,\rhoc}{3}\,\frac{c^3}
+{\log\left(1+c\right)-c/(1+c)}\,,
+\label{eq:rho_s}
+\end{equation}
+ where the halo mass dependent concentration parameter $c$ is derived
+ from a power-law fit to cosmological simulations with $\mvir \gtrsim
+ 10^{10} \msun$ \cite{2008MNRAS.391.1940M},
 \begin{equation}
@@
 $\rvir$. This difference is build up within 10\% of $\rvir$
-(i.e. close to $r_\rmn{s}$). The emission from an Einasto density
+(i.e. close to $r_\s$). The emission from an Einasto density
 profile is about 50\% larger than the cuspy NFW profile in the
@@
 through radio, X-ray, and gamma-ray emission. On larger scales of the
-order of few 100 kpc up to Mpc, there are a vast number of
+order of few 100~kpc up to Mpc, there are a vast number of
 observations of radio emission coming from radio mini halos in the
@@
 of the IC gamma-ray spectrum. In the low energy Thomson regime the IC
-spectrum is given by $E_\gamma^{-(\alpha_\e-1)/2}$, however when
+spectrum $F_\gamma\sim E_\gamma^{-(\alpha_\e-1)/2}$, however when
 $\Gamma_\e \gg 1$ the IC spectrum steepens due to the KN suppression
-to $\eg^{-\alpha_\e}\log(\eg)$ .
+to $\eg^{-\alpha_\e}\log(\eg)$. Here we denote the steady
+state electon spectrum by $\alpha_\e$.
 
@@
   luminosity from stars and galaxies. The crosses show the total
-  observed star light including the diffuse intracluster (ICL), the
+  observed starlight including the diffuse intracluster (ICL), the
   galaxies, and the brightest cluster galaxy (BCG) in the center of
-  the cluster. The diamonds denote the observed star light from the
+  the cluster. The diamonds denote the observed starlight from the
   ICL and the BCG. The solid line show the fit to the data of the
@@
 
-The normalization constant for the star light [$N_\stars(\lx)$] is derived
+The normalization constant for the starlight $N_\stars(\lx)$ is derived
 in the following three steps: (1) We use the average apparent magnitude
@@
 
-The normalization constant for the dust [$N_\dust(\lx)$] is derived in the
+The normalization constant for the dust $N_\dust(\lx)$ is derived in the
 following four steps: (1) We use a cluster with the the average mass
@@
 \section{Spectral gamma-ray distribution}
+Spectrally resolved indirect DM searches have the advantage of probing
+different DM models through their characteristic spectral
+distributions. In this section we focus on the gamma-ray flux from
+clusters its spectral distribution. We use both a leptophilic model
+that give rise to substantial amounts of electrons and positrons that
+IC upscatter background radiation fields to high energies as well as a
+few supersymmetric DM models with a high gamma-ray yield in the form of
+continuum emission. In addition to the annihilating DM, we estimate
+the gamma-ray flux induced by shock accelerated CR protons.
+
+In Fig.~\ref{fig:diff_BM} we show the differential flux from the
+Fornax cluster which is one of the best clusters for inderect DM
+serches due to its relative high DM fluxes. We derive the flux from
+four different supersymmetric BM models and compare the flux to both
+the emission induced by CRs as well as to the differential gamma-ray
+upper limits set by Fermi-LAT after 18 months of observations
+\cite{2010ApJ...717L..71A}. The upper limits are not violated,
+although the predicted DM flux that is dominated by the continuum
+emission from $\Kp$ and $\Ip$ (shown in the left panels) are close to
+the upper limits and can potentially be probed by the Fermi 3 year
+data. Furthermore, the expected masking gamma-ray signal induced by
+CRs is about a factor 10 below the DM continuum flux from the $\Kp$
+and $\Ip$ BM models aound 10~GeV. It is also important to note that IC
+emission from upscattered CMB and SD photons is at least a factor 10
+lower than the expected flux from CRs above 100~MeV, making it very
+hard to distinguish such a signal from the foreground due to the
+similar spectral index. Below the pion bump, however, we expect the IC
+emission coming from shock accelerated electrons to be dominating
+\cite{2010MNRAS.409..449P}. Hence the IC emission from SUSY DM in
+clusters can for most applications safeley be neglected compared to
+the CRs and continuum emission.
 
@@
 \caption{\it Comparing the differential flux from different models: we
-  show the continuum emission from DM benchmark (BM) models
-  (blue), electrons and positrons from DM BM models that inverse
-  Compton upscattered both CMB photons (orange) as well as dust and
-  star photons (green), and CR induced gamma-ray emission (red
-  solid). The various linestyles are associated with individual DM BM
-  models; $\Imm$ (dotted), $\Km$ (dashed), and $\Jm$
-  (dash-dotted). The emission is calculated for the Fornax cluster
+  show the continuum emission from DM benchmark (BM) models (blue
+  dashed), electrons and positrons from DM BM models that inverse
+  Compton upscattere both CMB photons (orange dash-dotted) as well as
+  dust and star photons (green dotted), and CR induced gamma-ray
+  emission (red solid). Each panel is associated with an individual DM
+  BM model; upper left $\Ip$, lower left $\Kp$, upper right $\Jp$, and
+  lower right $\Js$. The emission is calculated for the Fornax cluster
   using a point spread function of $0.1\deg$ and a boost from
@@
   continuum emission that is dominating the total emission in the GeV
-  energy range. Also note that, above 100 MeV the total inverse
+  energy range. Also note that, above 100~MeV the total inverse
   Compton emission is at least a factor 10 smaller than the emission
@@
   from CRs.}
- \label{fig7}
+ \label{fig:diff_BM}
 \end{minipage}
 \end{figure*}
+
+In Fig.~\ref{fig:IR_comp} we show the total IC emission as well as its
+individual contributions from different IC upscattered radiation
+fields. The left panel show the gamma-ray emission from the LP model
+and the right panel from the $\Kp$ BM model, for comparison we
+overplot the emission expected from the CRs. We find that the IC
+upscattered CMB pfortons for the LP model overproduce the upper
+gamma-ray limits set by Fermi. This puts tight constraints on the
+boost from substructures as well as the Sommerfeld enhancement.
+
+.........
+Fermi can put tight limits on IC-CMB, much harder for IACTs to
+constrain the flux due to the relative small SD flux and the lack of
+substructures in the central cluster region
+
+PHYSICS
+100 MeV photons requre 30 GeV electrons, which are supressed from dust
+(dust require higher electron energies to upscatter photons to he same
+energy, these are KN supressed.), also discuss spectral index
 
@@
 \includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv9.0.1deg.SubMass.noMW.woGal.eps}
-\caption{\it Comparing the differential flux from different inverse
-  Compton upscattered radiation fields in the Fornax cluster. We show
-  the inverse Compton emission induced by leptophilic DM in the left
-  panel and by the $\Km$ benchmark model in the right panel. The
-  contribution from each individual radiation field from top line to
-  bottom line; CMB (green dashed-double-dotted), dust (blue dashed),
-  stars (purple dashed-dotted). The sum of the three components are
-  shown with the orange solid line. The black dotted line represents
-  the upscattered CMB photons without any cooling from stars and
-  dust. The red solid line show the CR induced gamma-ray flux. The
-  black arrow show the differential upper limit from Fermi ADD
-  REF. All fluxes are calculated within $\rvir$ with a point spread
-  function of $0.1\deg$. The boost from Sommerfeld is ..., and from
-  substructures is .}
- \label{fig6}
+\caption{\it Comparing the flux from different inverse Compton
+  upscattered radiation fields. We show the differential inverse
+  Compton emission induced by leptophilic DM in the left panel and by
+  the $\Kp$ benchmark model in the right panel. The contribution from
+  each individual radiation field from top line to bottom line; CMB
+  (green dashed-double-dotted), dust (blue dashed), stars (purple
+  dashed-dotted). The sum of the three components are shown with the
+  orange solid line. The black dotted line represents the upscattered
+  CMB photons without any cooling from stars and dust. The red solid
+  line show the CR induced gamma-ray flux. The black arrow show the
+  differential upper limit from Fermi \cite{2010ApJ...717L..71A}. All
+  fluxes are calculated for the Fornax cluster within $\rvir$ using a
+  point spread function of $0.1\deg$. The boost from Sommerfeld is
+  ..., and from substructures is .}
+ \label{fig:IR_comp}
 \end{minipage}
@@
   models: we show the emission from leptophilic (LP) models with green
-  lines, $\Km$ benchmark model (BM) with blue lines, and the CR
+  lines, $\Kp$ benchmark model (BM) with blue lines, and the CR
   induced emission with a red line. The dotted and dashed lines show
@@
 \end{figure}
+Fornax is a great target for indirect DM studies because the relative
+ low flux from CRs and high flux from DM
 
@@
   leptophilic models (LP) include both final state radiation and IC
-  upscattered CMB, dust and star light (dotted), and benchmark $\Km$
+  upscattered CMB, dust and starlight (dotted), and benchmark $\Kp$
   models (BM) include continuum emission, and IC upscattered CMB, dust
-  and star light (dashed). The arrows have colors matching each
+  and starlight (dashed). The arrows have colors matching each
   cluster and show the differential upper limits set by Fermi in the
@@
 \end{figure*}
+Fornax is a great target for indirect DM studies because the relative
+ low flux from CRs and high flux from DM
+
+How are ul calculated, Fermy sees M87 (Virgo), NGC 1275 (Perseus), no improvment of the 5 GeV limit
 
@@
 \end{figure}
+flat surface brightness profiles with substructures
+
+boost at small r due to projection from outer halo
 
@@
 \end{figure}
+ Fermi 3 year data will constrain the smallest mass of substructures
+ using the benchmark models
+
+How can we explain the difference between the clusters, 
+\begin{eqnarray}
+B_\rmn{LP}=B_\sfe B_\sub \propto M^{-1/3}M^{0.23} \propto M^{-0.1}\nonumber\\
+B_\rmn{BM}=B_\sub \propto M^{0.23}
+\end{eqnarray}
+
+\begin{eqnarray}
+L_\gamma \propto \int \dd V \rho(r)^2 \propto \frac{c^3}
+{\left[\log\left(1+c\right)-c/(1+c)\right]} \propto M^{0.83}\nonumber\\
+L_{\gamma,\rmn{sub tot}} \propto N\,L_{\gamma,\sub} \propto N\,M_\sub 
+ \propto M_\sub^{\left(A+1\right)}\,\frac{\dd N_\sub}{\dd M} \propto  M^{A-0.9}
+\end{eqnarray}
+Assuming that the concentration $c$ decrease for increasing mass as it
+does for the mass range $10^{12}-10^{14}\,\msun$ where
+$L_{\gamma,\sub} \propto N\,M_\sub^A$, where $A<1$.
 
@@
   denoted by the red solid line, the leptophilic models by green
-  lines, and the DM $\Km$ benchmark model by blue lines. The dashed
+  lines, and the DM $\Kp$ benchmark model by blue lines. The dashed
   and dotted lines include and exclude substructures,
@@
   CR induced emission (red), leptophilic emission (green), and
-  emission from the $\Km$ benchmark model (blue). The surface
+  emission from the $\Kp$ benchmark model (blue). The surface
   brightness above 1~GeV is derived using a very small point spread
@@
   the IC upscattered photons from stars and dust, and blue solid line
-  show the continuum emission from the $\Km$ benchmark
+  show the continuum emission from the $\Kp$ benchmark
   model. \del{Since cooling is dominated by IR and UV processes in the
@@
   emission is derived for the following components; CRs (red solid),
-  continuum emission from the DM $\Km$ benchmark model (blue
+  continuum emission from the DM $\Kp$ benchmark model (blue
   dash-dotted), as well as final state radiation (green dashed) and
-  inverse Compton upscattered dust and star light (green dotted) from
+  inverse Compton upscattered dust and starlight (green dotted) from
   leptophilic DM. \del{GeV energies give rise to small BM model fluxes
@@
     upscattered CMB photons (red), and the continuum emission from the
-    DM $\Km$ benchmark model (blue). The leptophilic fluxes are ruled
+    DM $\Kp$ benchmark model (blue). The leptophilic fluxes are ruled
     out by 14 of the clusters, with the strongest constraints set by
@@
 \end{figure*}
+ difficult to detect DM without a Sommerfeld boost with Cherenkov
+ telescopes since the boost from substructures is extended while the
+ sensitivity of Cherenkov telescopes drops linearly with radius
+ outside the point spread function (CHECK)
+
+we rule out the leptophilic models in present form in 14 clusters,
+ and limit the boost from Sommerfeld enhancement in the MW to less
+ than 10
+
+mention prime cluster candidates, LP under pressure, Fornax start
+being constraining, since only few clusters close to UL stacking will
+not increase the DM limits much
 
@@
 
+the tightest limits on DM and CRs from Fermi are in the 1-10 GeV
+ regime, where Fornax, M49, and NGC4636 are the most constraining
+ "clusters" for the DM and Virgo, Coma and Norma are very close to the
+ predictions for the CRs
+
+using beta brofiles, discrapency with Norma cluster in Ackermann gone,
+Integrated flux similar
+
+AGN M87, effective area better in 1 GeV range
+
+CONCLUSIONS
+
+Some of the results (should discuss what we want to emphasize):
+--) the flux from annihilating DM is boosted by about a factor 1000 in
+ clusters
+--) flat surface brightness profiles with substructures
+--) Fornax is a great target for indirect DM studies because the relative
+ low flux from CRs and high flux from DM
+--) the IC upscattered photons from stars and dust are dominated in the
+ relevant energy regimes by the continuum emission for our DM
+ benchmark models
+--) Fermi 3 year data will constrain the smallest mass of substructures
+ using the benchmark models
+--) difficult to detect DM without a Sommerfeld boost with Cherenkov
+ telescopes since the boost from substructures is extended while the
+ sensitivity of Cherenkov telescopes drops linearly with radius
+ outside the point spread function (CHECK)
+--) we rule out the leptophilic models in present form in 14 clusters,
+ and limit the boost from Sommerfeld enhancement in the MW to less
+ than 10
+--) the tightest limits on DM and CRs from Fermi are in the 1-10 GeV
+ regime, where Fornax, M49, and NGC4636 are the most constraining
+ "clusters" for the DM and Virgo, Coma and Norma are very close to the
+ predictions for the CRs
+--) we provide a rather simple model to calculate the spatial and spectral
+ distribution of dust and stars in cluster (might be used for
+ galaxies? with different spatial profile)
+
 %------------------------------------------------------------------
@@
   differential continuum spectra for four different DM benchmark (BM)
-  models; $\Imm$ model (red), $\Jmm$ (orange), $\Km$ (green), and
-  $\Jm$ (blue). RIGHT PANEL: number of electron and positron per DM
+  models; $\Ip$ model (red), $\Jp$ (orange), $\Kp$ (green), and
+  $\Js$ (blue). RIGHT PANEL: number of electron and positron per DM
   annihilation above the electron energy $\ee$ for different dark
-  matter models; $\Imm$ BM model (red), $\Jmm$ BM model (orange),
-  $\Km$ BM model (green), and $\Jm$ BM model (blue), leptophilic (LP)
+  matter models; $\Ip$ BM model (red), $\Jp$ BM model (orange),
+  $\Kp$ BM model (green), and $\Js$ BM model (blue), leptophilic (LP)
   DM annihilating into electrons and positrons (purple), and LP DM
@@
 \end{figure*}
+Only LP models have energetic enough CRe such that IC emission
+powerfull to either constrain or be detected
+
+similar shape for BM continuum models
 
@@
   mass-luminosity scaling relations compared to the flux computed
-  using the semi-analytically model CITE The name of the
-  clusters with the largest offset are printed out, which correlate
-  with cool core clusters.}
+  using the semi-analytically model \cite{2010MNRAS.409..449P}. The
+  name of the clusters with the largest offset are printed out, which
+  correlate with cool core clusters.}
  \label{fig19}
@@
 \end{figure*}
+if CC, then skewed torwards large X-ray fluxes; X-ray emission good
+proxies for gamam-ray emission --) The dust turns up at about a factor
+100 lower than the stars --) The other figure show the spectral shape
+of the IC-star with the same spectral shape as the dust, it shows the
+same gamma-ray slope as the dust --) The reason why there is only a
+factor 10 difference in the break in the gamma-ray emission between
+the star and dust is related to the KN. In our CR paper, the last
+figure shows that at $\eg=100\,\tev$, the spectra is suppressed with
+about a factor 10 (also depends on $\alpha_\e$). Since the dust
+photons have a factor 10 higher energy, I expect this suppression at
+about 10~TeV. For star photons the suppression should be at
+100~GeV. So the star photons are definitely KN suppressed, which
+explains the earlier break and the steeper slope.
 
@@
   from both leptophilic DM that result in inverse Compton upscattered
-  CMB photons (red), and the continuum emission from the DM $\Km$
+  CMB photons (red), and the continuum emission from the DM $\Kp$
   benchmark model (blue). The fluxes are calculated within $\rvir$

### 2011-04-04 paper.tex
theory+results updated

@@
 \newcommand{\Jp}{\rmn{J}`}
+\newcommand{\B}{\rmn{B}}
+\newcommand{\bsub}{\B_\rmn{sub}}
+\newcommand{\qCR}{q_{\rmn{CR}-\ensuremath{\pi^0}}}
 
@@
 \newcommand{\eeq}{\end{equation}}
-\newcommand{\gev}{\rm{GeV}}
-\newcommand{\tev}{\rm{TeV}}
-\newcommand{\ev}{\rm{eV}}
+\newcommand{\gev}{\rmn{GeV}}
+\newcommand{\tev}{\rmn{TeV}}
+\newcommand{\ev}{\rmn{eV}}
 \newcommand{\dd}{\rmn{d}}
@@
 \newcommand{\rhoc}{\ensuremath{\rho_c}}
-\newcommand{\B}{\rmn{B}}
 \newcommand{\e}{\rmn{e}}
@@
 and also the accompanying bremsstrahlung and inverse Compton
-components coming from charged particles produce in the annihilations)
+components coming from charged particles produced in the annihilations)
 are basically three:
@@
   this paper are scaled to the currently favored value of Hubble's
-  constant, $H_0 = 70\, \rm{km~s}^{-1}\,\rm{Mpc}^{-1}$. We define the
+  constant, $H_0 = 70\, \rmn{km~s}^{-1}\,\rmn{Mpc}^{-1}$. We define the
   virial mass $\mvir$ and virial radius $\rvir$ as the mass and radius
   of a sphere enclosing a mean density that is 200 times the critical
-  density of the Universe $\rho_{\rm{cr}}$.}.
+  density of the Universe $\rho_{\rmn{cr}}$.}.
 
@@
 
+\del{In this work we define the virial radius $\rvir$ of a halo to be
+  the radius at which the mean density within is a factor $\Delta=200$
+  times the critical density $\rhoc$ of the universe.}
+
 % --- section:  --- %
@@
 direction $\psi$ that the detector is pointing, is parameterized such
-that the radius of the source $r=\sqrt{l^2+D^2-2Dl\cos\Psi}$, where
+that the radius of the source $r=\sqrt{l^2+D^2-2 D l\cos\Psi}$, where
 $D$ is the distance to the source from the galactic center and
@@
 \end{equation}
-We denote the total source function by $q_{\rm sum}(\eg,r)$, where we
-include contributions from five main processes; leptophilic DM
-annihilating to $\mu^+/\mu^-$ decaying to $\rm{e}^+/\rm{e}^-$ pairs
-that up-scatter background photons (IC), leptophilic DM emitting final
-state radiation (FSR), DM benchmark models where neutralino
-annihilations generate electrons that up-scatter background photons
-(BM-IC) and emit a continuum as well as final state radiation
-(BM-Cont), and CR induced $\pi^0$:s decaying into gamma-rays. The
-source function is given by
-\begin{equation}
-q_\rmn{sum} (\eg,r) = q_{\pi^0-\gamma}(\eg,r)+
+We denote the total differential source function by $q_{\rm
+  sum}(\eg,r)$, where we include contributions from five main
+processes; leptophilic DM annihilating either indirectly through
+$\mu^+/\mu^-$ to $\rmn{e}^+/\rmn{e}^-$ or directly to
+$\rmn{e}^+/\rmn{e}^-$ pairs that inverse Compton upscatter background
+photons (LP-IC), leptophilic DM emitting final state radiation
+(LP-FSR), supersymmetric DM benchmark models where annihilating
+neutralinos generate $\rmn{e}^+/\rmn{e}^-$ pairs that upscatter
+background photons (BM-IC) and emit a continuum as well as final state
+radiation (BM-Cont), and CR proton induced $\pi^0$:s decaying into
+gamma-rays (CR-$\pi^0$). The source function is given by
+\begin{equation}
+q_\rmn{sum} (\eg,r) = \qCR(\eg,r)+
 \sum_i \,q_{\rmn{sm},i}(\eg,r)\,\B_{\rmn{tot},i}(\sigv,r)
 \end{equation}
-where the subscript $i$ runs over the gamma-ray producing DM
-channels. The differential CR to gamma-ray source function is denoted
-by $q_{\pi^0-\gamma}(\eg,r)$, where we refer the reader to
-Sect.~\ref{sect:CRs} and \cite{2010MNRAS.409..449P} for further
-details. The total differential boost factor for DM is the product of
-enhancement factors from SFE $\B_\sfe(\sigv)$ (see
-Sect.~\ref{sect:LP}) and from substructure enhancement over the smooth
-halo contribution $\B_{\sub,i}(r) = 1+q_\sub(r)/q_{\rmn{sm},i}(r)$
-(see Sect.~\ref{sect:subst}) and is denoted by
-$\B_{\rmn{tot},i}(r,\sigv) = \B_\sfe(\sigv)\,\B_{\sub,i}(r)$. The DM
-source function from the smooth halo for each process is written on
-the form:
+the differential CR to gamma-ray source function is denoted by
+$\qCR(\eg,r)$ (see Sect.~\ref{sect:CRs} and \cite{2010MNRAS.409..449P}
+for further details). The subscript $i$ runs over the gamma-ray
+producing DM channels and the total differential boost factor for DM
+is given by $\B_{\rmn{tot},i}(r,\sigv) =
+\B_\sfe(\sigv)\,\B_{\sub,i}(r)$. It is the product of enhancement factors
+from SFE $\B_\sfe(\sigv)$ (see Sect.~\ref{sect:LP}) and from
+substructure enhancement over the smooth halo contribution
+$\B_{\sub,i}(r) = 1+q_\sub(r)/q_{\rmn{sm},i}(r)$ (see
+Sect.~\ref{sect:subst}). The DM source function from the smooth halo
+for each process is written on the form:
 \begin{equation}
@@
 q_{\rmn{sm},i} (\egamma,r) = \sum_j
-\frac{\dd \ngammaj}{\dd E_\gamma} \Gamma_j(r)\,.
-\end{equation}
-Here the annihilation rate density is given by 
+\frac{\dd \ngammaj}{\dd E_\gamma} \Gamma_j(r)\,,
+\end{equation}
+where the annihilation rate density is given by 
 \begin{equation}
 \label{eq:ann_rate}
-\Gamma_j(r) = \frac{1}{2} \left(\frac{\rho(r)}{\mx}\right)^2 
-\, \sigmaannv_j\,
-\end{equation}
-where the subscript $j$ runs over all kinematically allowed gamma-ray
+\Gamma_j(r) = \frac{1}{2} \left[\frac{\rho(r)}{\mx}\right]^2 
+\, \sigmaannv_j\,.
+\end{equation}
+Here the subscript $j$ runs over all kinematically allowed gamma-ray
 producing channels each with the spectrum $\frac{\dd
@@
 profile provide a good fit to both the observed and simulated
-clusters. It can be considered as a special case of the 5-parameter profile:
+clusters. It can be considered as a special case of the more general
+5-parameter profile:
 \begin{equation}
@@
 $(\alpha,\beta,\gamma)=(1,3,1)$. The scaling radius is given by $r_\s$
-and the characteristic density by 
+and the characteristic overdensity by 
 \begin{equation}
@@
 \begin{equation}
+\label{eq:dens_ein}
 \rho_{\rm ein}(r) = \rho_{-2}\,\exp\left\{-\frac{2}{\alpha}
@@
 that is slightly shallower in the center than the conventional
-Navarro-Frenk-White (NFW) profile, but provide a better fit to
-simulated DM halos \cite{2010MNRAS.402...21N}. We denote the density
-where the profile has a slope of $-2$ by $\rho_{-2}$, and the radius
-by $r_{-2}$. Assuming that all the flux from an NFW profile originate
-from within the scale radius $\rs=\rvir/c$, and all the flux from an
-Einasto profile originate within $r_{-2}=\rvir/c$, it follows that
-$\rho_{-2} = \rhos/4$. The virial radius $\rvir$ of a halo is defined
-to be the radius at which the mean density within is a factor
-$\Delta=200$ times the critical density $\rhoc$ of the universe.
+Navarro-Frenk-White (NFW) profile, but provide a better fit to recent
+simulated high resolution DM halos \cite{2010MNRAS.402...21N}. It
+should also be noted that recent detailed galaxy cluster observations
+find a core like density profile with an inner slope of $\beta=0.6$,
+where $\beta\gtrsim 1$ can be ruled out to a $>95$\% confidence
+\cite{2011ApJ...728L..39N}. In Eq.~(\ref{eq:dens_ein}) we denote the
+density where the profile has a slope of $-2$ by $\rho_{-2}$, and the
+radius by $r_{-2}$. Assuming that all the flux from an NFW profile
+originate from within the scale radius $\rs=\rvir/c$, and all the flux
+from an Einasto profile originate within $r_{-2}=\rvir/c$, it follows
+that $\rho_{-2} = \rhos/4$.
+
+%However, this finding is hard to reconcile with simulations that
+%typically prefere a steeper central profile.
 
@@
 disruption. Since the rate of which DM is annihilating depends on the
-density squared, the resulting flux is boosted compared to the smooth
-density distribution. Recent simulations suggest a flux enhancement
-from substructures of the order of ten up to a few 100
-\cite{2008MNRAS.391.1685S, 2008JPhCS.125a2008K} for a MW size
-halo. Using the Aquarius simulations \cite{2008Natur.456...73S}, we
+density squared, the resulting flux from substructures is boosted
+compared to the smooth density distribution. Recent high resolution
+simulations suggest a flux enhancement from substructures of the order
+of ten up to a few 100 \cite{2008MNRAS.391.1685S, 2008JPhCS.125a2008K}
+for a MW size halo. We use a double power-law function to
 fit \footnote{Our approach of fitting the scaling behavior of
@@
   self-consistently accounts for the radial dependence of the
-  substructure concentration \cite{2008MNRAS.391.1685S}.} to the
-luminosity from smooth substructures (i.e. substructures within
-substructures are not included) inside radius $r$. The best fit is
-given by
+  substructure concentration \cite{2008MNRAS.391.1685S}.} the
+luminosity from the smooth component of substructures
+(i.e. substructures within substructures are not included) inside
+radius $r$ which is determined for the Aquarius simulations
+\cite{2008MNRAS.391.1685S,2008Natur.456...73S}. Our best fit is given
+by
 \begin{equation}
@@
 \end{equation}
-where $M_{\rm res,sim}=10^5\msun$ is the minimum subhalo mass in the
-MW simulation, and $M_{\rm lim}$ the free streaming mass. Here we
-assume that the power-law scaling relation in Eq.~(\ref{eq:C1}) is
-valid down to the minimum mass of DM halos, which is conventionally in
-the cold dark matter universe
+where $M_{\rm res,sim}=10^5\msun$ is the mass of the smallest resolved
+subhalos in the MW simulation, and $M_{\rm lim}$ is the theoretical
+smallest mass of subhalos determined from free streaming length of DM
+(CHECK). Here we assume that the power-law scaling relation in
+Eq.~(\ref{eq:C1}) is valid down to the free streaming mass of DM
+halos, which is conventionally in the cold dark matter universe
 \cite{2001PhRvD..64h3507H,2005JCAP...08..003G} taken to be
@@
 
-Recent detailed galaxy cluster observations find a core like density
-profile with an inner slope of $\beta=0.6$, where $\beta\gtrsim 1$ can
-be ruled out to a $>95$\% confidence \cite{2011ApJ...728L..39N}. This
-finding is hard to reconcile with simulations that typically prefere a
-steeper central profile. The different density profiles have a large
-impact on the luminosity from annihilating DM, although the details of
-the density profile can be neglected compared to the dominating boost
-from substructures. In Fig.~\ref{fig:radial_lum} we compare the radial
-dependence of the accumulative luminosity from different smooth
-cluster density profiles to the substructure boosted luminosity at
-different mass scales. We recalculate the density contrast for the
-core like density profile $\rhos$ and rescale the concentration
-parameter in Eq.~(\ref{eq:cfit}) with $300/160$
-\cite{2011ApJ...728L..39N} to account for the more centralized scale
-radius in a core like cluster. The emission coming from the core
-compared to a cuspy like density profile is about 30\% larger within
-$\rvir$. This difference is build up within 10\% of $\rvir$
-(i.e. close to $r_\s$). The emission from an Einasto density
-profile is about 50\% larger than the cuspy NFW profile in the
+The different density profiles have a large impact on the luminosity
+from annihilating DM, although the details of the density profile can
+be neglected compared to the dominating boost from substructures. In
+Fig.~\ref{fig:radial_lum} we compare the radial dependence of the
+accumulative luminosity from different smooth cluster density profiles
+to the substructure boosted luminosity at different mass scales. We
+recalculate the density contrast for the core like NFW density profile
+$\rhos$ and rescale the concentration parameter in Eq.~(\ref{eq:cfit})
+with $300/160$ \cite{2011ApJ...728L..39N} to account for the more
+centralized scale radius in cluster with a softer cusp. The emission
+coming from the core like NFW density profile ($\beta=0.6$) compared
+to a cuspy ($\beta=1.0$) is about 30\% larger within $\rvir$. This
+difference is build up within 10\% of $\rvir$ (i.e. close to
+$r_\s$). Hence the slope of the central part of a cluster is
+unimportant for the DM luminosity inside $\rvir$, instead the
+important factor is the scale radius. The emission from an Einasto
+density profile is about 50\% larger than the cuspy NFW profile in the
 periphery of the cluster, where the difference is mainly build up at a
@@
   profile. We have assumed the standard value for the limiting
-  substructure mass of $10^{-6}\,\msun$. Note the large expected
-  boost from substructures in clusters ($\sim1000$), and the relative
-  small boost in dwarf galaxies ($\sim20$).}
+  substructure mass of $M_\rmn{lim}=10^{-6}\,\msun$. Note the large
+  expected boost from substructures in clusters ($\sim1000$), and the
+  relative small boost in dwarf galaxies ($\sim20$).}
  \label{fig:radial_lum}
@@
 $\rvir$. In Fig.~\ref{fig:radial_emis} we show the luminosity
-dominating radius for substructures and smooth density profiles, both
+dominated radius for substructures and smooth density profiles, both
 for three different mass scales. It clearly shows how that the main
@@
 DM halos, while the main contribution from the smooth density profiles
-peaks around the scale radius. NOT QUITE, ALSO FIGURE IS SHOWING DIFF
-VOLUME, FAC 3 DIFFERENCE, WHAT DO WE REALLY LEARN FROM THE FIGURE
+peaks around the scale radius. SHOW WHERE THE FLUX PEEKS WITH EQUATION
+SEC DERIV
 \begin{figure}
   \includegraphics[width=0.99\columnwidth]{figures/emissiv.sub.eps}
-  \caption{\it Radial dependence of differential luminosity at
-    different mass scales. The solid lines show the emissivity from a
-    cuspy $\beta=1.0$ NFW density profile for three different mass
-    scales; an $\mvir=10^{15}\,\msun$ galaxy cluster (red), an
+  \caption{\it Luminosity dominated radius for different mass
+    scales. The solid lines show the emissivity from a cuspy
+    $\beta=1.0$ NFW density profile for three different mass scales;
+    an $\mvir=10^{15}\,\msun$ galaxy cluster (red), an
     $\mvir=10^{12}\,\msun$ galaxy (orange), and an
@@
     standard value for the limiting substructure mass of
-    $10^{-6}\,\msun$.}
+    $M_\rmn{lim}=10^{-6}\,\msun$.}
   \label{fig:radial_emis}
@@
 \label{sect:CRs}
-The formation process of a galaxy cluster is a very energetic
-processes that induces both turbulence as well as frequently occurring
-merging and accretion shocks. These processes are thought to
-accelerate large quantities of relativistic non-thermal electrons and
-protons to high energies. On smaller scales, such as galaxies, there
-is convincing evidence of such non-thermal populations. Especially, in
-the MW, the cosmic rays are observed directly as well as indirectly
-through radio, X-ray, and gamma-ray emission. On larger scales of the
-order of few 100~kpc up to Mpc, there are a vast number of
-observations of radio emission coming from radio mini halos in the
-center of cooling flow clusters, radio relics in the periphery of
-clusters \cite{2004rcfg.proc..335K} as well smooth giant radio halos
-that have been observed in more than 50 clusters
-\cite{2003ASPC..301..143F,2008SSRv..134...93F}. Most of this observed
-radio emission is expected to emerge from synchrotron emitting
-cosmic-ray electrons whose precise origin in especially relics and
-giant radio halos is still not settled. However, due to the smoothness
-of the extended emission and the observed power-law slope it seems
-quite natural that they are of hadronic origin. Especially since the
-long cooling time of cosmic ray protons (CRs) allows for both an
-extended and large population of CRs to build up over the cluster
-history \cite{1997ApJ...487..529B}.
-
-When the CRs interact with ambient gas protons, it results in the
+On small astrophysical scales, such as supernovae remnants and
+galaxies, there are convincing evidences of non-thermal
+populations. Especially, in the MW, the cosmic rays are observed
+directly as well as indirectly through radio, X-ray, and gamma-ray
+emission. On larger scales of the order of few 100~kpc up to Mpc,
+there are currently a vast number of observations of radio emission
+coming from radio mini halos in the center of cooling flow clusters,
+radio relics in the periphery of clusters \cite{2004rcfg.proc..335K}
+as well as smooth giant radio halos that have been observed in more
+than 50 clusters \cite{2003ASPC..301..143F,2008SSRv..134...93F}. This
+type of emission is expected in clusters since the formation process
+of a galaxy cluster is a very energetic processes that induces both
+turbulence as well as frequently occurring merging and accretion
+shocks which both are thought to accelerate large quantities of
+relativistic non-thermal protons and radio emitting electrons to high
+energies. Thus most of the observed radio emission in clusters is
+expected to emerge from cosmic-ray electron induced radio synchrotron
+emission. The precise origin of these electrons, in especially relics
+and giant radio halos, is still not settled. However, due to the
+smoothness of the extended emission and the observed power-law slope
+it seems quite natural that they are of hadronic origin. Especially
+since the long cooling time of cosmic ray protons (CRps) allows for
+both an extended and large population of CRps to build up over the
+cluster history \cite{1997ApJ...487..529B}.
+
+When the CRps interact with ambient gas protons, it results in the
 production of both charged and neutral pions that decay into
 electrons, neutrinos, and gamma-rays. The production of these
-secondaries depend both on the gas and CR densities in the cluster,
-where the CR density roughly trace the gas outside the core regime and
-is slightly enhance in the center. This density scaling implies that
+secondaries depend both on the gas and CRp densities in the cluster,
+where the CRp density roughly trace the gas outside the core regime and
+is slightly enhanced in the center. This density scaling implies that
 clusters are great targets for Cherenkov telescopes with a high
@@
 cluster gamma-ray emission is crucial in this respect as it
-potentially provides the unique and unambiguous evidence of CR
+potentially provides the unique and unambiguous evidence of CRp
 populations in clusters through observing the $\pi^0$ bump at about
@@
 simulations of clusters of galaxies that included radiative
-hydrodynamics, star formation, supernova feedback, and followed CR
+hydrodynamics, star formation, supernova feedback, and followed CRp
 physics using a novel formulation that trace the most important
 injection and loss processes self-consistently while accounting for
-the CR pressure in the equation of motion
+the CRp pressure in the equation of motion
 \cite{2008A&A...481...33J,2007A&A...473...41E,2006MNRAS.367..113P}.
-We note that the overall normalization of the CR and gamma-ray
+We note that the overall normalization of the CRp and gamma-ray
 distribution scales with the maximum acceleration efficiency at
@@
 parameter and assume that 50\% of the dissipated energy at strong
-shocks is injected into CRs while this efficiency rapidly decreases
+shocks is injected into CRps while this efficiency rapidly decreases
 for weaker shocks \cite{2007A&A...473...41E}.
@@
 background (CMB) photons, and the light from stars and dust (SD). We
-derive a semi-analytic model from which we can estimate the SD
-spectral and spatial distributions as a simple function of cluster
-mass.
+derive a semi-analytic model from which we can estimate the spectral
+and spatial distributions of SD as a simple function of cluster mass.
 
@@
 to $\eg^{-\alpha_\e}\log(\eg)$. Here we denote the steady
-state electon spectrum by $\alpha_\e$.
+state electron spectrum by $\alpha_\e$.
 
 We account for two major contributions to the number density of
-radiative background fields $n_\ph$; the cosmic microwave background
-(CMB) photons and the infra-red (IR) to ultra-violet (UV) light
-emitted by starlight and dust (SD). The number density for the SD is
-given by $n_\ph\equiv\frac{\dd^2 N_\ph}{\dd V \,\dd
-  \eph}(\eph,r)= \frac{u_\sd(\eph,r)}{\eph^2}$ where the SD
-energy density $u_\sd(\eph,r)$ is given in Eq.~(\ref{eq:U_SD}). We
-model the CMB photon spectrum as a photon gas that is isotropically
-distributed and follows a black body spectrum with the temperature
-$T=2.73\,$~K:
+radiative background fields $n_\ph$; the CMB photons and the infra-red
+(IR) to ultra-violet (UV) light emitted by SD. The number density for
+the SD is given by $n_\ph\equiv\frac{\dd^2 N_\ph}{\dd V \,\dd
+  \eph}(\eph,r)= \frac{u_\sd(\eph,r)}{\eph^2}$ where the SD energy
+density $u_\sd(\eph,r)$ is given in Eq.~(\ref{eq:U_SD}). We model the
+CMB photon spectrum as a photon gas that is isotropically distributed
+and follows a black body spectrum with the temperature $T=2.73\,$~K:
 \begin{equation}
@@
 models where a fraction of the annihilating neutralinos is converted
-into electrons and positrons (see Sect.~\ref{sect:PF} for further
-details).
+into electrons and positrons (see Sect.~\ref{sect:PF} and
+Fig.~\ref{fig:q_DM} for further details).
 %(see \cite{2009JCAP...01..016B} and references therein,
@@
 equivalent field strength of the CMB is denoted by $B_{\rm
-  CMB}=3.24(1+z)^2\mu\rmn{G}$. (2) Synchrotron losses on ambient
+  CMB}=3.24\mu\rmn{G}$. (2) Synchrotron losses on ambient
 magnetic fields where we parameterize the magnetic field in the galaxy
@@
 {\it Spatial distribution -- stars and dust}\\ Our goal in this
-section is to derive a simple spatial model for the distribution of
-stars and dust in galaxy clusters. For this reason we use stacked
-cluster observations by Sloan in the $r$-band that trace the stars. We
-assume that the dust trace the stars in the clusters, which should be
+section is to derive a simple spatial model for the distribution of SD
+in galaxy clusters. For this reason we use stacked cluster
+observations by Sloan in the $r$-band that trace the stars. We assume
+that the dust trace the stars in the clusters, which should be
 accurate to the order of magnitude estimate that we are interested in
@@
 {\it Spectral distribution -- stars and dust} \\ Our goal in this
-section is to derive a simple spectral model for stars and dust in
-galaxy clusters. Since the radiation from galaxies are expected to
-leak out into the ICM, we expect similar spectral distributions, at
-least to the order of magnitude that we are interested in here. Hence, we
-use the IR to UV spectrum derived in \cite{2006ApJ...648L..29P} for a
-MW type galaxy to characterize the spectral distribution of dust and
-starlight in a cluster. Note, however, that we only keep the spectral
-shape, and renormalize the spectral distribution using the luminosity
-from stars and dust.
-
-In Fig.~\ref{fig:SD_spectra} we show the SD spectral distribution
-together with the CMB black-body distribution in a galaxy cluster,
-both at the radius $r=0.071\rvir$ where the smooth energy density of
-the SD light (see Fig.~\ref{fig:SD_Edens}) equals the energy density
-of the CMB. We have renormalized both the spectral SD data and the
-fitted SD spectra using the luminosity from stars and dust
+section is to derive a simple spectral model for SD in galaxy
+clusters. Since the radiation from galaxies are expected to leak out
+into the ICM, we expect similar spectral distributions, at least to
+the order of magnitude that we are interested in here. Hence, we use
+the IR to UV spectrum derived in \cite{2006ApJ...648L..29P} for a MW
+type galaxy to characterize the spectral distribution of light from SD
+in a cluster. Note, however, that we only keep the spectral shape, and
+renormalize the spectral distribution using the luminosity from SD.
+
+In Fig.~\ref{fig:SD_spectra} we show the spectral distribution of the
+light from SD together with the CMB black-body distribution in a
+galaxy cluster, both at the radius $r=0.071\rvir$ where the smooth
+energy density of the SD light (see Fig.~\ref{fig:SD_Edens}) equals
+the energy density of the CMB. We have renormalized both the spectral
+data and the fitted spectra using the luminosity from stars and dust
 individually (see below for further details about the
@@
   galaxies. The black dotted line in the left peak show the spectrum
-  of CMB photons using a black body with a temperature of 2.73 K. The
-  crosses in the middle and right peaks represent the measured spectra
-  from stars and dust (SD), respectively, and are derived in
-  \cite{2006ApJ...648L..29P} for a galaxy. We normalize the individual
-  SD spectrum separately using the observed luminosity from SD in
-  clusters. The SD luminosity is related to the cluster mass through
-  Eq, where we use have used the mass $\mvir=4.0\,10^{13}\msun$ in
-  this figure. Finally we renormalize the SD spectra to the radius
-  $r=0.071\rvir$, where the smooth energy density of the SD light (see
-  fig~\ref{fig:SD_Edens}) equals the energy density of the CMB. The
-  red dashed lines show the fitted SD spectral model.}
+  of CMB photons using a black body with a temperature of
+  $2.73$~K. The crosses in the middle and right peaks represent the
+  measured spectra from stars and dust (SD), respectively, and are
+  derived in \cite{2006ApJ...648L..29P} for a galaxy. We normalize the
+  individual SD spectrum separately using the observed luminosity from
+  SD in clusters. The SD luminosity is related to the cluster mass
+  through Eq, where we use have used the mass
+  $\mvir=4.0\times10^{13}\msun$ in this figure. Finally we renormalize
+  the SD spectra to the radius $r=0.071\rvir$, where the smooth energy
+  density of the SD light (see Fig.~\ref{fig:SD_Edens}) equals the
+  energy density of the CMB. The red dashed lines show the fitted SD
+  spectral model.}
  \label{fig:SD_spectra}
@@
 
-{\it Normalization}\\ HARD TO READ, TO MUCH DETAIL, MOVE TO APPENDIX?,
-MABEY KEEP NORM CONSTATS AND A VERY SHORT SUMMARY?? The spatial and
-spectral distribution functions of the light from stars and dust in a
-cluster are both normalized with a constant determined from the
-luminosity in each respective wavelength. The specific energy density
-is given by
+{\it Normalization}\\ HARD TO READ FIRST PART The spatial and spectral
+distribution functions of the light from SD in a cluster are both
+normalized with a constant determined from the luminosity in each
+respective wavelength. The specific energy density is given by
 \begin{eqnarray} 
@@
 where we fix the unitless normalization $N_i(\lx)$ using the total
-energy of the light in stars and dust ($E_{i,\vir}$) within $\rvir$:
+energy of the light in SD ($E_{i,\vir}$) within $\rvir$:
 \begin{eqnarray} 
@@
   \frac{u_i^\gal(\eph)}{\eph}\,\dd V\dd \eph\,,\nonumber \\
- &\rmn{for}&\qquad i=\{\rmn{stars,dust}\}\,.
+ \rmn{for}\quad i&=&\{\rmn{stars,dust}\}\,.
 \label{eq:E_SD}
@@
 timescale it takes for a photon to propagate through the cluster (we
-assume that the cluster is optically thin). Once we estimated the SD
+assume that the cluster is optically thin). Once we derived the SD
 luminosities for a well representative cluster, we use a IR to X-ray
-scaling relation to estimate the luminosity from an arbitrary cluster
-with mass $\mvir$:
-\begin{equation}
-L=1.05\times10^{45}\,\rmn{erg\,s}^{-1}\,
+scaling relation to estimate the luminosity from an arbitrary cluster:
+\begin{equation}
+L_\ir=1.05\times10^{45}\,\rmn{erg\,s}^{-1}\,
 \left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,,
@@
 L_\stars=10^{\frac{m_\odot-m_{(r+i),0.25}}{2.5}}
-\left(\frac{d_\clu}{d_\odot}\right)^2 L_\odot
+\left(\frac{D_\clu}{D_\odot}\right)^2 L_\odot
 \approx 7.1\times10^{44}\,\rmn{erg}\,\rmn{s}^{-1}\,,
@@
 where the apparent magnitude of the sun $m_\odot\approx -27.1$, the
-distance to the sun $d_\odot=4.85\times10^{-6}\,\rmn{pc}$, the
+distance to the sun $D_\odot=4.85\times10^{-6}\,\rmn{pc}$, the
 luminosity of the sun $L_\odot=3.85\times10^{34}\,\rmn{erg\,s}^{-1}$,
-and the distance to the cluster $d_\clu=1.26\times10^9\,\rmn{pc}$. (2)
-We use the IR to X-ray scaling relation in Eq.~(\ref{eq:SD-X}) to find
+and the distance to the cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. (2)
+We use the IR to X-ray scaling relation in Eq.~(\ref{eq:SD-X}) to derive
 a more general form of the luminosity from stars in
@@
 
-{\it Energy density}\\ The energy density from starlight and dust in
-a galaxy cluster is given by
+{\it Energy density}\\ The spatial distribution of the SD energy
+density is an important quantity since it impacts the steady state
+electron and positron spectra through cooling. A higher density of SD
+in a cluster suppresses the spectra of the upscattering particles. With
+the formalism presented above, we can now derive the energy density
+from starlight and dust in a galaxy cluster through
 \begin{eqnarray}
@@
 $\mvir=4.0\times10^{13}\msun$. We use two different profiles for the
-SD energy density, where the total includes the ICL, the BCG and all
-the galaxies, while the galaxies are excluded in the smooth
-contribution. We find that even for a cluster with a relative small
-mass the energy density of the SD components dominates over the CMB
-and the magnetic fields (with a central B field of 3~$\mu G$) within
-about 10\% of $\rvir$. Outside this radius the CMB is dominating the
-energy density of the cluster, hence the density of the magnetic
+SD energy density, where the total profile includes the contribution
+from the ICL, the BCG and all the galaxies, while the galaxies are
+excluded in the smooth profile. We find that even for a cluster with a
+relative small mass the energy density of the SD components dominates
+over the CMB and the magnetic fields (with a central B field of 3~$\mu
+G$) within about 10\% of $\rvir$. Outside this radius the CMB is
+dominating the energy density of the cluster, hence the magnetic
 fields are always subdominant in the cluster and can safely be removed
-from cluster IC calculations for reasonable central densities and
-spectral index. Although, in this work we keep its contribution to the
-total energy density for consistency.
+from cluster IC calculations for a reasonable central density and
+spectral index. Although, in this work we keep the contribution from
+B-fields to the total energy density for consistency.
 
@@
    smooth SD light, respectively. The SD light has been renormalized
-   to a cluster with the mass $\mvir=4.0\,10^{13}\msun$. Finally we
+   to a cluster with the mass $\mvir=4.0\times10^{13}\msun$. Finally we
    show the energy density two magnetic field models with a central
@@
 \section{Spectral gamma-ray distribution}
+\label{sect:spectral}
 Spectrally resolved indirect DM searches have the advantage of probing
 different DM models through their characteristic spectral
-distributions. In this section we focus on the gamma-ray flux from
-clusters its spectral distribution. We use both a leptophilic model
-that give rise to substantial amounts of electrons and positrons that
-IC upscatter background radiation fields to high energies as well as a
-few supersymmetric DM models with a high gamma-ray yield in the form of
-continuum emission. In addition to the annihilating DM, we estimate
-the gamma-ray flux induced by shock accelerated CR protons.
+distributions. To make current and future DM searches more effective it
+is important to know in which energy band to focus the efforts in
+order to maximize the potential DM signal over the expected
+background. We dedicate this section to the spectral distribution of
+gamma-ray flux from clusters. The flux emerge from a DM LP model that
+emit final state radiation and give rise to substantial amounts of
+electrons and positrons that IC upscatter background radiation fields
+to high energies. We also consider a few supersymmetric DM models with
+a high gamma-ray yield in the form of continuum emission and IC
+induced emission. In addition to the annihilating DM, we estimate the
+gamma-ray flux induced by shock accelerated CRps.
 
 In Fig.~\ref{fig:diff_BM} we show the differential flux from the
-Fornax cluster which is one of the best clusters for inderect DM
-serches due to its relative high DM fluxes. We derive the flux from
-four different supersymmetric BM models and compare the flux to both
-the emission induced by CRs as well as to the differential gamma-ray
-upper limits set by Fermi-LAT after 18 months of observations
-\cite{2010ApJ...717L..71A}. The upper limits are not violated,
-although the predicted DM flux that is dominated by the continuum
-emission from $\Kp$ and $\Ip$ (shown in the left panels) are close to
-the upper limits and can potentially be probed by the Fermi 3 year
-data. Furthermore, the expected masking gamma-ray signal induced by
-CRs is about a factor 10 below the DM continuum flux from the $\Kp$
-and $\Ip$ BM models aound 10~GeV. It is also important to note that IC
-emission from upscattered CMB and SD photons is at least a factor 10
-lower than the expected flux from CRs above 100~MeV, making it very
-hard to distinguish such a signal from the foreground due to the
-similar spectral index. Below the pion bump, however, we expect the IC
-emission coming from shock accelerated electrons to be dominating
+Fornax cluster which is one of the best clusters for indirect DM
+searches due to its relative high DM induced fluxes and low CR induced
+fluxes. We derive the emission from four different supersymmetric BM
+models and compare the flux to both the emission induced by CRps as
+well as to the differential gamma-ray upper limits set by Fermi-LAT
+after 18 months of observations \cite{2010ApJ...717L..71A}. We find
+that the upper limits are not violated, although the predicted DM flux
+that is dominated by the continuum emission from $\Kp$ and $\Ip$ models
+(shown in the left panels) are close to the upper limits and can
+potentially be probed by the Fermi 3 year data. Furthermore, the
+expected masking gamma-ray signal induced by CRps is about a factor 10
+below the DM continuum flux from the $\Kp$ and $\Ip$ BM models around
+10~GeV. It is also important to note that IC emission from upscattered
+CMB and SD photons is at least a factor 10 lower than the expected
+flux from CRps above 100~MeV, making it very hard to distinguish such
+a signal from the foreground due to the similar spectral
+index. Furthermore, below the pion bump we expect the IC emission
+coming from shock accelerated electrons to be dominating
 \cite{2010MNRAS.409..449P}. Hence the IC emission from SUSY DM in
-clusters can for most applications safeley be neglected compared to
-the CRs and continuum emission.
+clusters can for most applications safely be neglected compared to the
+CRps and DM continuum emission.
 
@@
   dashed), electrons and positrons from DM BM models that inverse
-  Compton upscattere both CMB photons (orange dash-dotted) as well as
-  dust and star photons (green dotted), and CR induced gamma-ray
+  Compton upscattered both CMB photons (orange dash-dotted) as well as
+  dust and star photons (green dotted), and CRp induced gamma-ray
   emission (red solid). Each panel is associated with an individual DM
@@
   using a point spread function of $0.1\deg$ and a boost from
-  substructures of ...  We find bright prospects for detecting the
+  substructures of 570. We find bright prospects for detecting the
   continuum emission that is dominating the total emission in the GeV
@@
   expected from both the continuum emission and the emission coming
-  from CRs.}
+  from CRps.}
  \label{fig:diff_BM}
@@
 
+CONSIDER REWRITING, START WITH PHYSICS, THEN DISCUSS DOMINATING
+CONTRIBUTIONS, PEAKS, AND SPECTRAL INDICES
+
 In Fig.~\ref{fig:IR_comp} we show the total IC emission as well as its
@@
 fields. The left panel show the gamma-ray emission from the LP model
-and the right panel from the $\Kp$ BM model, for comparison we
-overplot the emission expected from the CRs. We find that the IC
-upscattered CMB pfortons for the LP model overproduce the upper
-gamma-ray limits set by Fermi. This puts tight constraints on the
-boost from substructures as well as the Sommerfeld enhancement.
-
-.........
-Fermi can put tight limits on IC-CMB, much harder for IACTs to
-constrain the flux due to the relative small SD flux and the lack of
-substructures in the central cluster region
-
-PHYSICS
-100 MeV photons requre 30 GeV electrons, which are supressed from dust
-(dust require higher electron energies to upscatter photons to he same
-energy, these are KN supressed.), also discuss spectral index
+and the right panel from the $\Kp$ BM model, and for comparison we
+overplot the emission expected from the CRps. Due to the flat electron
+and positron spectrum resulting from the DM LP model and the relative
+smaller energy density of the CMB compared to the SD, we find that the
+upscattered CMB photons dominate the total DM IC emission in the
+energy regime below 100~GeV, while the SD dominate above this
+energy. For the BM models this transition is shifted towards a smaller
+energy since the electron and positron spectrum has a steep spectral
+distribution that suppresses low energy photon fields. This
+suppression is also seen in the relative normalization of the flux
+where the IC from both CMB and dust photons are lower compared to the
+starlight simply because the starlight has a higher energy, hence it
+is upscattered by more abundant low energy electrons and positrons
+(c.f. Fig.~\ref{fig:q_DM}). At the highest gamma-ray energies of about
+100~GeV and above, the IC from starlight steepens because it both
+probes the high energy tail of the electrons as well as suffer from
+the KN suppression. Even though the SD component seems to be
+suppressed compared to the CMB at energies around 100~MeV, it has a
+relative large impact on the steady state electron spectrum. If we
+remove the SD cooling, we find a factor two larger IC flux at low
+energies for a cluster of the size of Fornax. For more massive
+clusters we expect a larger IC flux from the SD component, but a
+smaller contribution from the CMB because of the more effective
+cooling.
+
+Because of the large boost factor for the LP model ($\sim 10^4$), we
+overproduce the upper gamma-ray limit in the $1-10$~GeV energy
+interval set by Fermi-LAT by about a factor 100. This imposes tight
+constraints on both the boost from substructures and the Sommerfeld
+enhancement. These constraints might improve with future more
+sensitive Cherenkov telescopes. However considering that an indirect
+detection of DM in clusters relies on the boost from substructures
+whose main contribution comes from the periphery, we conclude that the
+wide angular extent of clusters in gamma-rays on the sky suggest that
+these sources are not ideal for Cherenkov telescopes due to the loss
+of sensitivity outside the small PSF (BETTER CHECK THIS WITH SOME
+EXPERT).
 
@@
   CMB photons without any cooling from stars and dust. The red solid
-  line show the CR induced gamma-ray flux. The black arrow show the
+  line show the CRp induced gamma-ray flux. The black arrow show the
   differential upper limit from Fermi \cite{2010ApJ...717L..71A}. All
   fluxes are calculated for the Fornax cluster within $\rvir$ using a
-  point spread function of $0.1\deg$. The boost from Sommerfeld is
-  ..., and from substructures is .}
+  point spread function of $0.1\deg$. The boost from Sommerfeld and
+  substructures is about 130 and 570, respectively.}
  \label{fig:IR_comp}
@@
 
+It is also interesting to compare the total contribution from the LP
+model, the brightest BM model, and the CRp induced emission. In
+Fig.~\ref{fig:flux_int} we show the integrated flux from Fornax for
+our different gamma-ray models and compare it to the unresolved
+integrated flux upper limit on Fornax set by Fermi-LAT where they
+averaged the flux over the energy range $0.2-100\,\gev$ assuming a
+spectral index of 2. Again we are overproducing the upper limits,
+although only with a factor 10 which is about a order magnitude less
+constraining than the differential flux in the energy range
+$1-10$~GeV. From the figure one clearly see that the LP model is
+dominating the entire gamma-ray energy range up to the DM mass of this
+model of about 1~TeV. In addition it is interesting to note that the
+flux the DM BM $\Kp$ model is above the predicted emission from the
+CRps in the $1-100$~GeV energy regime accessible both to Fermi and
+Cherenkov telescopes.
+
 \begin{figure}
@@
 \caption{\it Comparing the energy integrated flux from different
-  models: we show the emission from leptophilic (LP) models with green
-  lines, $\Kp$ benchmark model (BM) with blue lines, and the CR
-  induced emission with a red line. The dotted and dashed lines show
-  the inverse Compton (IC) upscattered CMB photons and star and dust
-  photons, respectively. The green solid line show the final state
-  radiation from the LP model, and the solid blue line show the
-  continuum emission from the DM. The black arrow show the integrated
-  flux upper limit set by Fermi.  The emission is calculated for the
-  Fornax cluster using a point spread function of $0.1\deg$ and a
-  boost from substructures of ...  We find that LP models are
-  dominating the total flux in the entire energy range, where the IC
-  upscattered CMB photons overproduce the upper limit by a factor 3.}
- \label{fig8}
+  models. We show the emission from; CRp induced emission (red solid),
+  leptophilic models (LP) that include both final state radiation and
+  IC upscattered CMB, dust and starlight (green dash-dotted), and
+  benchmark $\Kp$ models (BM) include continuum emission, and IC
+  upscattered CMB, dust and starlight (blue dashed). The black arrow
+  show the integrated flux upper limit set by Fermi-LAT. The emission
+  is calculated for the Fornax cluster using a point spread function
+  of $0.1\deg$. The boost from Sommerfeld and substructures is about
+  130 and 570, respectively. We find that LP models are dominating the
+  total flux in the entire energy range, where the IC upscattered CMB
+  photons overproduce the upper limit by a factor 3.}
+ \label{fig:flux_int}
 \end{figure}
-Fornax is a great target for indirect DM studies because the relative
- low flux from CRs and high flux from DM
+
+We continue by comparing how the estimated differential flux from
+Fornax to three other clusters in Fig.~\ref{fig:clu_comp}; the close
+by well studied Virgo cluster, the X-ray bright Perseus clusters, and
+the massive merging Coma cluster. We find high DM induced gamma-ray
+fluxes from both the Fornax and Virgo clusters, which highlight them
+as promising targets for indirect DM searches. Note, however, that we
+have used spatially unresolved upper limits, which is quite optimistic
+for the angular extended Virgo cluster. It is quite striking how
+constraining the upper limits for the Fornax cluster is compared to
+the other clusters, especially in the $1-10$~GeV energy regime where
+Fermi-LAT is most sensitive due to the maximized effective area. The
+upper limits for Virgo and Perseus are background contaminated by AGN
+activity from M87 and NGC 1267, respectively, and do not gain much
+from the increased sensitivity. One should also note that the high CRp
+induced flux from both Coma and Perseus is of the same magnitude as
+the DM flux from LP models, making it difficult for indirect DM
+searches in those clusters. Conversely is the Fornax cluster a great
+target for indirect DM studies because the relative low gamma-ray flux
+from CRps, absents of an active AGN, and high DM gamma-ray
+flux. Actually, the Fermi-LAT 3 year data will be able to constrain
+constrain the smallest mass of substructures using the DM BM
+models. We have also learned that close by clusters are superior to
+far away clusters, even though close by clusters have a mass that is
+much smaller. In fact, we can understand this by looking at the
+luminosity-to-mass scaling relations. The gamma-ray luminosity from
+the smooth density profile is given by
+\begin{equation}
+L_\rmn{sm} \propto \int \dd V \rho(r)^2 \propto \frac{c^3}
+{\left[\log\left(1+c\right)-c/(1+c)\right]} \propto \mvir^{0.83}\,,
+\end{equation}
+and the total luminosity including boostfactors for the DM LP and BM
+models is given by
+\begin{eqnarray}
+L_\rmn{tot,LP} &=& L_\rmn{sm,LP} \B_\rmn{LP} \propto \mvir^{0.73}\qquad
+\,\,\,\,\,\,\rmn{and}\\
+L_\rmn{tot,BM} &=& L_\rmn{sm,BM} \B_\rmn{BM} \propto  \mvir^{1.06}\,,\qquad
+\rmn{where} \\
+B_\rmn{LP}&=&B_\sfe B_\sub \propto \mvir^{-1/3}\mvir^{0.23} \propto
+ \mvir^{-0.1}\,,\\
+B_\rmn{BM}&=&B_\sub \propto \mvir^{0.23}\,.
+\end{eqnarray}
+Hence increasing the mass with a factor two doubles the luminosity,
+but increasing the distance by a factor two decrease the flux with a
+factor four.
+\del{
+\begin{eqnarray}
+L_{\gamma,\rmn{sub tot}} \propto N\,L_{\gamma,\sub} \propto N\,M_\sub 
+ \propto M_\sub^{\left(A+1\right)}\,\frac{\dd N_\sub}{\dd M} \propto  M^{A-0.9}
+\end{eqnarray}
+Assuming that the concentration $c$ decrease for increasing mass as it
+does for the mass range $10^{12}-10^{14}\,\msun$ where
+$L_{\gamma,\sub} \propto N\,M_\sub^A$, where $A<1$.
+}
 
@@
 \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-
-\caption{\it Comparing the emission from different clusters. The
-  emission from the clusters is calculated using a point spread
-  function of $0.1\deg$ and includes the boost from substructures. We
-  show the differential flux from four clusters; Fornax (upper left),
-  Coma (upper right), Virgo (lower left), and Perseus (lower
-  right). The different linestyles show; CR induced emission (solid),
-  leptophilic models (LP) include both final state radiation and IC
-  upscattered CMB, dust and starlight (dotted), and benchmark $\Kp$
+\caption{\it Comparing the emission from different clusters. We show
+  the differential flux from four clusters; Fornax (upper left), Coma
+  (upper right), Virgo (lower left), and Perseus (lower right). The
+  different flux models; CRp induced emission (red solid), leptophilic
+  models (LP) include both final state radiation and IC upscattered
+  CMB, dust and starlight (green dash-dotted), and benchmark $\Kp$
   models (BM) include continuum emission, and IC upscattered CMB, dust
-  and starlight (dashed). The arrows have colors matching each
-  cluster and show the differential upper limits set by Fermi in the
-  energy ranges $0.2-1$~GeV, $1-10$~GeV, and $10-100$~GeV from left to
-  right. For visualization we offset the arrows by increasing the mean
-  energy by 30 percent in the opposite order as they appear in the
-  figure, i.e. starting with Perseus. All fluxes are calculated within
-  $\rvir$. We find that the lower GeV energy regime is most
-  constraining, and induce upper limits on boost factors.}
- \label{fig9}
+  and starlight (blue dashed). The arrows have colors matching each
+  cluster and show the differential upper limits set by Fermi-LAT in
+  the energy ranges $0.2-1$~GeV, $1-10$~GeV, and $10-100$~GeV from
+  left to right. For visualization we offset the arrows by increasing
+  the mean energy by 30\% in the opposite order as they appear in the
+  figure, i.e. starting with Perseus. The flux from the clusters is
+  integrated out to $\rvir$ using a point spread function of $0.1\deg$
+  and includes the boost from substructures. We find that the lower
+  GeV energy regime is most constraining, and induce upper limits on
+  boost factors.}
+ \label{fig:clu_comp}
 \end{minipage}
 \end{figure*}
-Fornax is a great target for indirect DM studies because the relative
- low flux from CRs and high flux from DM
-
-How are ul calculated, Fermy sees M87 (Virgo), NGC 1275 (Perseus), no improvment of the 5 GeV limit
+
+As we have seen in this section the LP models overproduce both the
+differential and integrated flux upper limits set by the Fermi-LAT for
+several clusters. We can use these upper limits to enforce constraints
+on the SFE and boost from substructures. As more sensitive experiments
+and better upper limits emerge, we can start ruling out models giving
+rise to these type of boost factors that are manifested in the
+gamma-ray flux. Especially interesting is to constrain the SFE, where
+a boost of 300 is required to explain the excess of electrons and
+positrons observed in the vicinity of Earth by PAMELA/Fermi/HESS.  In
+Fig.~\ref{fig:clu_comp} we use the estimated flux from four clusters
+to constrain the minimum mass of substructures where
+$M_\rmn{lim}\propto\mvir^{0.226}$, as well as the SFE. As expected,
+the Fornax cluster is the most constraining cluster by far, although
+the current upper limits are not good enough to rule out either the
+boost from substructures or SFE. Assuming that the electron and
+positron excess is due to SFE DM matter, then in order not to
+overproduce the differential upper limits set by Fermi-LAT in the
+energy range $1-10$~GeV \footnote{We average the LP DM flux in the
+  energy range $1-10$~GeV before we compare it to the upper limits.}
+we can constrain the smallest mass of substructures to
+$M_\rmn{lim}\gtrsim 10\,\msun$. Instead assuming the standard mass of
+the smallest substructures of $M_\rmn{lim}\gtrsim 10^{-6}\,\msun$, we
+can constrain the boost from SFE to about 4 in Fornax, corresponding
+to a maximum SFE in the MW of about 10.
+
+\begin{figure}%[t]
+ \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\caption{\it Constraining boost factors using flux upper limits. The
+  leptophilic (LP) gamma-ray emission is derived within $\rvir$ using
+  a point spread function of $0.1\deg$. In order not to overproduce
+  the Fermi-LAT differential flux upper limits in the energy interval
+  $1-10$~GeV the boost from substructures and Sommerfeld enhancement
+  (SFE) is constrained for four clusters; Fornax (red), Virgo
+  (orange), M49 (green), and NGC4636 (Blue). The SFE has been rescaled
+  from 300 (refer to equation) that is required to explain the
+  electron and positron excess observed at Earth with LP DM (black
+  arrow). If the DM interpretation is correct, we can constrain the
+  smallest size of halos to be larger than $10\,\msun$. However, if
+  the smallest size of DM halos is $10^{-6}\,\msun$, we can constrain
+  the SFE to about 4 in Fornax, corresponding to a maximum SFE in the
+  MW of about 10.}
+ \label{fig:boost_const}
+\end{figure}
+HOW ARE UL CALCULATED?
 
 \section{Surface brightness profiles}
+\label{sect:spatial}
+The large angular extent of clusters on the sky in combination with
+the small PSF of most gamma-ray probes ($\sim 0.1$~deg) suggest that
+we would be able to probe the different spatial regimes of a
+cluster. Especially important is the spatial distribution of the
+gamma-ray emission as it bias upper limits derived for spatially
+extended clusters where a simple density profile is often assumed. In
+fact when DM substructures are included the total brightness profile
+is almost flat and very different from the smooth halo distribution
+with a steep outer brightness slope of $-5$.
+
+In this section we investigate the gamma-ray surface brightness
+profiles induced by both DM and CRps. We start by comparing the
+substructure included brightness from different clusters in
+Fig.~\ref{fig:SB_clu}. As expected, we find that the DM flux in all
+clusters follow the same smooth shape imposed by the
+substructures. Even as far in as 1\% of $\rvir$ we are dominated by
+the substructures, which is due to the projection of the outer cluster
+halo (see Sect.~\ref{sect:subst} for a longer discussion). This
+implies that the spatial distribution of annihilating DM induced
+emission is independent of the type of DM model, and can not be used
+to separate different models. The normalization for the BM model
+determined by $\bsub L_\rmn{BM}^{1/3} \propto \mvir^{0.50}$, which
+explains the factor three difference in normalization. The flux from
+the LP model show a smaller spread in the normalization which is due
+to the additional contribution from SFE with a negative mass trend,
+hence a normalization with a softer mass-scaling of
+$\sim\mvir^{0.17}$. The surface brightness induced by CRps mainly
+trace the gas profile of each cluster with an additional enhancement
+in the center due to the expected large population of CRps, hence we
+see a much larger spread in these profiles. It is noticeable that
+Fornax show such a small surface brightness. However, it is explained
+by the low gas density outside the BCG and the less abundant CRp
+population in the relative small cluster compared to a more massive
+cluster \cite{2010MNRAS.409..449P}. In fact, only the very inner part
+of Fornax is dominated by a large gamma-ray flux from CRps, which
+however, is neglible compared to the flux withing $\rvir$. This is the
+reason why Fornax is such a good target for indirect DM searches, and
+competitive to DM searches in dwarf galaxies. Although, it might be a
+problem for Cherenkov telescopes looking for a DM in the center of
+Fornax.
 
@@
 \caption{\it Comparing the surface brightness from different
-  clusters. We show the surface brightness above the energy 1~GeV. The
-  boost from substructures is included and we use a point spread
-  function of $0.1\deg$.}
- \label{fig20}
+  clusters. We show the CRp induced emission (red), leptophilic
+  emission (green), and emission from the $\Kp$ benchmark model
+  (blue). The surface brightness above 1~GeV is derived using a very
+  small point spread function ($\theta_\rmn{psf}=10^{-5}\deg$). The
+  different linestyles each represent a cluster; Fornax (solid), Coma
+  (dotted), Virgo (dashed), and Perseus (dash-dotted). The boost from
+  Sommerfeld and substructures is about 130 and 570,
+  respectively. Notice the very similar shape and normalization of the DM
+  models, while the CRps have a much larger scatter in the profiles.}
+ \label{fig:SB_clu}
 \end{figure}
-flat surface brightness profiles with substructures
-
-boost at small r due to projection from outer halo
-
-\begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\caption{\it Constraining leptophilic boost factors using flux upper
-  limits. The emission is derived within $\rvir$ using a point spread
-  function of $0.1\deg$. In order not to overproduce the Fermi
-  differential flux upper limits in the energy interval $1-10$~GeV the
-  boost from substructures and Sommerfeld enhancement (SFE) is
-  constrained for four clusters; Fornax (red), Virgo (orange), M49
-  (green), and NGC4636 (Blue). The arrows have colors matching each
-  cluster and indicate the SFE in each cluster. The SFE has been
-  rescaled from 300 that is required to explain the electron and
-  positron excess observed in the Milky Way (MW) with leptophilic dark
-  matter (refer to equation). If the DM interpretation is correct, we
-  can constrain the smallest size of halos to be larger than
-  $10\,\msun$. However, if the smallest size of DM halos is
-  $10^{-6}\,\msun$, we can constrain the SFE to about 4 in Fornax,
-  corresponding to a maximum SFE in the MW of about 10.}
- \label{fig10}
-\end{figure}
- Fermi 3 year data will constrain the smallest mass of substructures
- using the benchmark models
-
-How can we explain the difference between the clusters, 
-\begin{eqnarray}
-B_\rmn{LP}=B_\sfe B_\sub \propto M^{-1/3}M^{0.23} \propto M^{-0.1}\nonumber\\
-B_\rmn{BM}=B_\sub \propto M^{0.23}
-\end{eqnarray}
-
-\begin{eqnarray}
-L_\gamma \propto \int \dd V \rho(r)^2 \propto \frac{c^3}
-{\left[\log\left(1+c\right)-c/(1+c)\right]} \propto M^{0.83}\nonumber\\
-L_{\gamma,\rmn{sub tot}} \propto N\,L_{\gamma,\sub} \propto N\,M_\sub 
- \propto M_\sub^{\left(A+1\right)}\,\frac{\dd N_\sub}{\dd M} \propto  M^{A-0.9}
-\end{eqnarray}
-Assuming that the concentration $c$ decrease for increasing mass as it
-does for the mass range $10^{12}-10^{14}\,\msun$ where
-$L_{\gamma,\sub} \propto N\,M_\sub^A$, where $A<1$.
+
+To quantify the impact of substructures on the spatial profiles in
+more detail we again turn to the Fornax clusters and show in
+Fig.~\ref{fig:SB_sub} a comparison of surface brightness profiles with
+and without substructures. It is quite remarkable how flat the
+profiles including substructures are compared to the ones
+without. This implies that the relative flux within the PSF in the
+center is comparable to the outer parts, which should increase the
+signal-to-noise significantly. If we assume that substructures for
+some reason are suppressed in the Fornax cluster, then the expected
+signal from DM is swamped by astrophysical backgrounds over the entire
+extent of the cluster, even though Fornax has one of the highest
+ratios of DM/CRp gamma-ray brightness.
 
@@
   very small point spread function of $10^{-5}\deg$ that reveals the
-  details of the spatial profiles. The emission induced by CRs is
+  details of the spatial profiles. The emission induced by CRps is
   denoted by the red solid line, the leptophilic models by green
   lines, and the DM $\Kp$ benchmark model by blue lines. The dashed
-  and dotted lines include and exclude substructures,
-  respectively. Notice the nearly flat profiles when substructures are
-  included, and the relative large boost at a percent of $\rvir$.}
- \label{fig11}
+  line show the brightness where the boost from substructures is
+  included while the substructures are excluded in the dotted
+  line. The boost from Sommerfeld and substructures is about 130 and
+  570, respectively. Notice the nearly flat profiles when
+  substructures are included, and the relative large boost at a
+  percent of $\rvir$.}
+ \label{fig:SB_sub}
 \end{figure}
+
+In order to learn about the spatial distribution of the DM flux in
+various clusters for different DM models and associated gamma-ray
+components, we show in the left panel of Fig.~\ref{fig:SB_clu_nosub}
+the brightness profiles for the smooth DM distribution for the same
+four representative clusters that was shown previously in
+Fig.~\ref{fig:SB_clu}. In addition, we show the spatial dependence of
+the individual gamma-ray components for the Fornax cluster in the
+right panel. We find that the spatial distribution of the DM emission
+at 1~GeV in the outer parts of the all clusters have the same
+shape. The shape trace the underlying density slope of $-3$, which is
+expected for IC upscattered CMB photons. This picture is confirmed by
+the components study in the right panel that show the neglible
+contribution from the IC upscattered light from stars and dust at this
+energy. Since the surface brightness from BM models are dominated by
+the continuum emission at each radius in all clusters, we see that
+this component follows the projected density profile over the entire
+clusters. The LP model, however, show a much flatter profile in the
+central parts of the clusters, which is due to the efficient IC cooling
+of the electrons and positrons on the SD component. There is also some
+variation in the profiles for the different clusters in the central
+parts. Especially in the Fornax cluster, where we find a factor two
+larger flux compared to the other clusters. This is due to more
+efficient SD cooling of the dominating IC upscattered CMB photons in
+Fornax; a low X-ray luminous cluster has a low energy density in
+starlight and dust in our semi-analytic SD model. However, note that
+the surface brightness from the SD component is suppresses at the
+relative low energy of 1~GeV.  Since there is no enhancement from the
+substructures, the overall mass normalization of the LP DM model has a
+marginally negative trend $\sim\mvir^{-0.06}$. Hence, we only see a
+very small difference in outer parts of the different clusters from
+these type of models. The BM DM models have a normalization of
+$\sim\mvir^{0.27}$, hence more massive clusters show a slightly higher
+surface brightness. As also noticed in previous figure, the flux from
+DM is dominated by the CRp induced emission for all clusters.
+
+Might want to mention that the IC-SD spectra for both DM models follow
+the projected density contribution due to the cancellation in the
+radial dependence of the SD spectra and the SD cooling that dominates
+he cooling in the center.
 
@@
 \caption{\it The surface brightness without substructures. We show the
-  CR induced emission (red), leptophilic emission (green), and
+  CRp induced emission (red), leptophilic emission (green), and
   emission from the $\Kp$ benchmark model (blue). The surface
@@
   show the continuum emission from the $\Kp$ benchmark
-  model. \del{Since cooling is dominated by IR and UV processes in the
-    center, the spatial dependence of the equilibrium electron spectra
-    cancels the spatial dependence on the upscattered IR photon,
-    resulting in a smooth halo dependence (density square) in the
-    center. The spatial profile for the upscattered CMB photons is
-    flatter in the center since the strong spatial dependence inferred
-    from cooling counteracts the smooth halo contribution. Cluster
-    outskirts dominated by the emission from DM, although large
-    uncertainty in the gas density profile.}}
- \label{fig12}
+  model.}
+ \label{fig:SB_clu_nosub}
 \end{minipage}
 \end{figure*}
+
+In Sect.~\ref{sect:spatial} we saw that the spectral distribution of
+the gamma-ray flux from the LP model were dominated at high energies
+of $100\,$~GeV by final state radiation and the IC upscattered
+starlight and dust, while the BM models were mainly dominated by the
+continuum emission. These high energies are reachable by both Fermi-LAT
+and Cherenkov telescopes, thus important observationally. We therefore
+show in Fig.~\ref{fig:SB_IACTs} the surface brightness above
+$100\,$~GeV for a realistic PSF of $0.1\deg$ where we include the
+boost from substructures. We look at both the relative small Fornax
+cluster and the massive close by Virgo cluster Both clusters show a
+very flat brightness profile within about 10\% of $\rvir$, due to both
+the effect from substructures and the smoothening over the PSF. The CRp
+induced emission also show a smoothing in the central parts due to the
+PSF. In the outer part of the Fornax cluster the CRp flux is suppressed
+compared to the substructure boosted DM flux, where the LP model is
+over three orders of magnitude larger. Although, it should be noted
+that there are large uncertainties in the gas density profile used to
+estimate the CRp surface brightness (see Fig.~\ref{fig:dens_fornax} for
+more details).
 
@@
   \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v9.SF300.SubMass.elmu.eps}
-\caption{\it Surface brightness predicted for Cherenkov telescopes. We
-  show the emission above $\eg=100$~GeV, include the boost from
-  substructures and use a point spread function of $0.1\deg$. Left
-  panel show the Fornax cluster and right panel the Virgo cluster. The
-  emission is derived for the following components; CRs (red solid),
-  continuum emission from the DM $\Kp$ benchmark model (blue
-  dash-dotted), as well as final state radiation (green dashed) and
-  inverse Compton upscattered dust and starlight (green dotted) from
-  leptophilic DM. \del{GeV energies give rise to small BM model fluxes
-    but high LP fluxes, other words BM models good for Cerenkov
-    telescopes and LP good for Fermi (although the flat LP spectra
-    give rise to high fluxes at high energies as well).}}
- \label{fig13}
+\caption{\it Surface brightness predicted for Cherenkov telescopes at
+  high energies. We show the emission above $100$~GeV and include the
+  boost from substructures. We use a point spread function of
+  $0.1\deg$ that is typical for both Cherenkov telescopes as well as
+  the Fermi-LAT at this energy. Left panel show the Fornax cluster
+  and right panel the Virgo cluster. The gamma-ray emission is derived
+  for the following components; CRps (red solid), continuum emission
+  from the DM $\Kp$ benchmark model (blue dash-dotted), as well as
+  final state radiation (green dashed) and inverse Compton upscattered
+  dust and starlight (green dotted) from leptophilic DM.}
+ \label{fig:SB_IACTs}
 \end{minipage}
@@
 
-\section{Population studies}
+\section{Predictions and observational limits}
 Model predictions
+
+\begin{figure}
+  \includegraphics[width=0.99\columnwidth]{figures/MLscaling.eps}
+  \caption{\it Lum-scaling relations, mass dependence of SD cooling
+    have been neglected, actually a factor few difference for
+    groups. factor 2 for Fornax, and small difference for large
+    clusters}
+ \label{fig:lum_mass_scaling}
+\end{figure}
 
@@
     gamma-ray flux. We show the mean differential flux in the energy
-    range $E_\gamma=1-10$~GeV for 32 clusters. The Fermi upper limits
-    are shown with black arrows. The predicted fluxes are derived from
-    both a leptophilic DM model that result in inverse Compton
-    upscattered CMB photons (red), and the continuum emission from the
-    DM $\Kp$ benchmark model (blue). The leptophilic fluxes are ruled
-    out by 14 of the clusters, with the strongest constraints set by
-    Fornax and M49. We can not constrain the benchmark models,
-    although our predictions are approaching the upper limits.}
+    range $E_\gamma=1-10$~GeV for 32 clusters. The Fermi-LAT upper
+    limits are shown with black arrows. The predicted fluxes are
+    derived from both a leptophilic DM model that result in inverse
+    Compton upscattered CMB photons (red), and the continuum emission
+    from the DM $\Kp$ benchmark model (blue). The leptophilic fluxes
+    are ruled out by 14 of the clusters, with the strongest
+    constraints set by Fornax and M49. We can not constrain the
+    benchmark models, although our predictions are approaching the
+    upper limits.}
  \label{fig14}
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.CR.diff.eps}
-  \caption{\it Fermi flux upper limits contrasted to the predictions
-    by the semi-analytic Pinzke and Pfrommer model for CR induced
-    gamma-ray emission. We show the mean differential flux in the
-    energy range $E_\gamma=1-10$~GeV for 32 clusters. The Fermi upper
-    limits are shown with black arrows. The blue boxes show the
-    gamma-ray emission from CR induced $\pi^0$\:s decaying, where the
+  \caption{\it Fermi-LAT flux upper limits contrasted to the
+    predictions by the semi-analytic Pinzke and Pfrommer model for CRp
+    induced gamma-ray emission. We show the mean differential flux in
+    the energy range $E_\gamma=1-10$~GeV for 32 clusters. The Fermi
+    upper limits are shown with black arrows. The blue boxes show the
+    gamma-ray emission from CRp induced $\pi^0$\:s decaying, where the
     upper bound shows the estimates for an optimistic model and the
@@
 
-the tightest limits on DM and CRs from Fermi are in the 1-10 GeV
+the tightest limits on DM and CRps from Fermi are in the 1-10 GeV
  regime, where Fornax, M49, and NGC4636 are the most constraining
  "clusters" for the DM and Virgo, Coma and Norma are very close to the
- predictions for the CRs
-
-using beta brofiles, discrapency with Norma cluster in Ackermann gone,
+ predictions for the CRps
+
+using beta profiles, discrepancy with Norma cluster in Ackermann gone,
 Integrated flux similar
@@
 
-CONCLUSIONS
+%-) Consider having one figure where we compare the Einasto profile, to
+%NFW, NFW w/ beta 0.6, and also the effect of a different concentration
+%mass-scaling relation
+%
+%-) also, plot BM flux vs. psf, for models w/ and w/o substructures
+
+\section{Conclusions}
 
@@
 --) Fornax is a great target for indirect DM studies because the relative
- low flux from CRs and high flux from DM
+ low flux from CRps and high flux from DM
 --) the IC upscattered photons from stars and dust are dominated in the
@@
  than 10
---) the tightest limits on DM and CRs from Fermi are in the 1-10 GeV
+--) the tightest limits on DM and CRps from Fermi are in the 1-10 GeV
  regime, where Fornax, M49, and NGC4636 are the most constraining
  "clusters" for the DM and Virgo, Coma and Norma are very close to the
- predictions for the CRs
+ predictions for the CRps
 --) we provide a rather simple model to calculate the spatial and spectral
@@
   annihilating into muons (black).}
- \label{fig17}
+ \label{fig:q_DM}
 \end{minipage}
@@
 Only LP models have energetic enough CRe such that IC emission
-powerfull to either constrain or be detected
+powerful to either constrain or be detected
 
@@
   catalogue.}
- \label{fig18}
+ \label{fig:dens_fornax}
 \end{figure}
@@
   catalogue. We show the energy integrated gamma-ray flux induced by
-  CRs for the 106 clusters included in the extended HIFLUGCS
+  CRps for the 106 clusters included in the extended HIFLUGCS
   catalogue. The fluxes are calculated within $\rvir$, and are derived
@@
 \end{figure*}
-if CC, then skewed torwards large X-ray fluxes; X-ray emission good
-proxies for gamam-ray emission --) The dust turns up at about a factor
+if CC, then skewed towards large X-ray fluxes; X-ray emission good
+proxies for gamma-ray emission --) The dust turns up at about a factor
 100 lower than the stars --) The other figure show the spectral shape
@@
 factor 10 difference in the break in the gamma-ray emission between
-the star and dust is related to the KN. In our CR paper, the last
+the star and dust is related to the KN. In our CRp paper, the last
 figure shows that at $\eg=100\,\tev$, the spectra is suppressed with

### 2011-04-05 paper.tex
new fig

@@
 
-Even though the bulk of substructures have been erased in the central
-regions of DM halos, a cluster in projection has a significant
-enhancement due to substructures at a radius of just a few percent of
-$\rvir$. In Fig.~\ref{fig:radial_emis} we show the luminosity
-dominated radius for substructures and smooth density profiles, both
-for three different mass scales. It clearly shows how that the main
-contribution from the substructures is coming from outer parts of the
-DM halos, while the main contribution from the smooth density profiles
-peaks around the scale radius. SHOW WHERE THE FLUX PEEKS WITH EQUATION
-SEC DERIV
+In Fig.~\ref{fig:radial_emis} we show the radius with the maximum
+luminosity for substructures and smooth density profiles, both for
+three different mass scales. We find that the smooth luminosity per
+logaritmic radial bin peaks at $x \dd^2 L/\dd x^2+\dd L/\dd x == 0
+\rightarrow r \propto \rvir/3c$. Hence the main contribition to the
+luminosity for large mass scales, which are usually assosiated with a
+low concentrated DM halos, is focused to the regime around 10\% of
+$\rvir$.  It clearly shows how that the main contribution from the
+substructures is coming from outer parts of the DM halos, while the
+main contribution from the smooth density profiles peaks around the
+scale radius. Not that, even though the bulk of substructures have
+been erased in the central regions of DM halos, a cluster in
+projection has a significant enhancement due to substructures at a
+radius of just a few percent of $\rvir$.
 \begin{figure}
@@
 \left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,.
-\label{eq:N_stars}
+\label{eq:N_dust}
 \end{equation}
@@
 \smallskip
-We wish to thank...
+Anders Pinzke acknowledges NSF grant AST 0908480 for support.
 

### 2011-04-05 paper.tex
updated text

@@
 redshift $\sim 0.25$ \cite{2005MNRAS.358..949Z}. Finally, we fix the
-normalization for the light from stars and dust in an galaxy cluster
-individually using using the IR to X-ray luminosity scaling relation
+normalization for the light from stars and dust individually in a
+galaxy cluster using using the IR to X-ray luminosity scaling relation
 found in \cite{2008A&A...490..547G}. The X-ray luminosities for the
@@
   luminosity of the sun by $L_\odot=3.85\,10^{33}
-  \rmn{erg}\,\rmn{s}^{-1}$.}. Our benchmark spatial model are show
-with the solid black line, and include the contribution from the ICL
-and BCG.
+  \rmn{erg}\,\rmn{s}^{-1}$.}, both scaled with the unitless $\rvir$
+normalized area to resembele the expected luminosity at radius
+$r$. Our benchmark spatial model is shown with the solid black line,
+and include the contribution from the ICL and BCG.
 
@@
 light from SD together with the CMB black-body distribution in a
-galaxy cluster, both at the radius $r=0.071\rvir$ where the smooth
-energy density of the SD light (see Fig.~\ref{fig:SD_Edens}) equals
-the energy density of the CMB. We have renormalized both the spectral
-data and the fitted spectra using the luminosity from stars and dust
-individually (see below for further details about the
-renormalization).
+galaxy cluster, both at the radius $r=0.071\rvir$ where the energy
+density of the smooth light from SD (see Fig.~\ref{fig:SD_Edens})
+equals the energy density of the CMB. We have renormalized both the
+spectral data and the fitted spectra using the luminosity from stars
+and dust individually (see the normalization section below for further
+details).
 \begin{figure}%[t]
@@
 
-{\it Normalization}\\ HARD TO READ FIRST PART The spatial and spectral
-distribution functions of the light from SD in a cluster are both
-normalized with a constant determined from the luminosity in each
-respective wavelength. The specific energy density is given by
+{\it Normalization}\\ The spatial and spectral distribution functions
+of the light from SD in a cluster are both normalized with a constant
+determined from the luminosity in each respective wavelength. The
+specific energy density is given by
 \begin{eqnarray} 
@@
 where we fix the unitless normalization $N_i(\lx)$ using the total
-energy of the light in SD ($E_{i,\vir}$) within $\rvir$:
+energy of the light in SD  within $\rvir$:
 \begin{eqnarray} 
@@
 Here we approximate the total energy of the photons within $\rvir$
-with the luminosity $L_i$ \cite{2008A&A...490..547G} times the typical
-timescale it takes for a photon to propagate through the cluster (we
-assume that the cluster is optically thin). Once we derived the SD
-luminosities for a well representative cluster, we use a IR to X-ray
-scaling relation to estimate the luminosity from an arbitrary cluster:
+($E_{i,\vir}$) with the luminosity $L_i$ \cite{2008A&A...490..547G}
+times the typical timescale it takes for a photon to propagate through
+the cluster (we assume that the cluster is optically thin). Once we
+derived the SD luminosities for a well representative cluster, we use
+a IR to X-ray scaling relation to estimate the luminosity from an
+arbitrary cluster:
 \begin{equation}
@@
 &=&  \frac{j(r)}{j(0)}  \int \dd \eph \sum_i 
-N_i(\lx) u_i^\gal(\eph)\,. \nonumber \\
+N_i(\lx) \frac{u_i^\gal(\eph)}{\eph}\,. \nonumber \\
 \end{eqnarray}
@@
 fields are always subdominant in the cluster and can safely be removed
-from cluster IC calculations for a reasonable central density and
-spectral index. Although, in this work we keep the contribution from
-B-fields to the total energy density for consistency.
+from cluster IC calculations for a reasonable central B-field and
+spectral index. Note that in this work we keep the contribution
+from B-fields to the total energy density for consistency.
 
@@
 different DM models through their characteristic spectral
-distributions. To make current and future DM searches more effective it
-is important to know in which energy band to focus the efforts in
-order to maximize the potential DM signal over the expected
-background. We dedicate this section to the spectral distribution of
-gamma-ray flux from clusters. The flux emerge from a DM LP model that
+distributions. To make current and future DM searches more effective
+it is important to know in which energy band to focus the efforts in
+order to maximize potential DM signal over expected background.
+
+We dedicate this section to the spectral distribution of gamma-ray
+flux from clusters. The flux emerge from a leptophilic DM model that
 emit final state radiation and give rise to substantial amounts of
@@
 that the upper limits are not violated, although the predicted DM flux
-that is dominated by the continuum emission from $\Kp$ and $\Ip$ models
-(shown in the left panels) are close to the upper limits and can
-potentially be probed by the Fermi 3 year data. Furthermore, the
+that is dominated by the continuum emission from $\Kp$ and $\Ip$
+models (shown in the left panels) are close to the upper limits and
+can potentially be probed by the Fermi 3 year data. Furthermore, the
 expected masking gamma-ray signal induced by CRps is about a factor 10
 below the DM continuum flux from the $\Kp$ and $\Ip$ BM models around
-10~GeV. It is also important to note that IC emission from upscattered
-CMB and SD photons is at least a factor 10 lower than the expected
-flux from CRps above 100~MeV, making it very hard to distinguish such
-a signal from the foreground due to the similar spectral
-index. Furthermore, below the pion bump we expect the IC emission
-coming from shock accelerated electrons to be dominating
-\cite{2010MNRAS.409..449P}. Hence the IC emission from SUSY DM in
+10~GeV. However, the IC emission from upscattered CMB and SD photons
+is at least a factor 10 lower than the expected flux from CRps above
+100~MeV, making it very hard to distinguish such a signal from the
+foreground due to the similar spectral index. For energies below
+100~MeV we expect shock accelerated electrons and positrons to be
+dominating \cite{2010MNRAS.409..449P} over the supersymmetric DM
+induced leptons. Hence the IC emission from supersymmetric DM in
 clusters can for most applications safely be neglected compared to the
@@
 
-CONSIDER REWRITING, START WITH PHYSICS, THEN DISCUSS DOMINATING
-CONTRIBUTIONS, PEAKS, AND SPECTRAL INDICES
+\del{CONSIDER REWRITING, START WITH PHYSICS, THEN DISCUSS DOMINATING
+CONTRIBUTIONS, PEAKS, AND SPECTRAL INDICES}
 
@@
 overplot the emission expected from the CRps. Due to the flat electron
-and positron spectrum resulting from the DM LP model and the relative
-smaller energy density of the CMB compared to the SD, we find that the
+and positron spectrum resulting from the LP DM model and the smaller
+mean energy of the CMB compared to the SD, we find that the
 upscattered CMB photons dominate the total DM IC emission in the
@@
 It is also interesting to compare the total contribution from the LP
-model, the brightest BM model, and the CRp induced emission. In
+model, the brightest BM model ($\Kp$), and the CRp induced emission. In
 Fig.~\ref{fig:flux_int} we show the integrated flux from Fornax for
@@
 
-We continue by comparing how the estimated differential flux from
-Fornax to three other clusters in Fig.~\ref{fig:clu_comp}; the close
-by well studied Virgo cluster, the X-ray bright Perseus clusters, and
-the massive merging Coma cluster. We find high DM induced gamma-ray
-fluxes from both the Fornax and Virgo clusters, which highlight them
-as promising targets for indirect DM searches. Note, however, that we
+We continue by comparing the estimated differential flux from Fornax
+to three other clusters in Fig.~\ref{fig:clu_comp}; the close by well
+studied Virgo cluster, the X-ray bright Perseus clusters, and the
+massive merging Coma cluster. We find high DM induced gamma-ray fluxes
+from both the Fornax and Virgo clusters, which highlight them as
+promising targets for indirect DM searches. Note, however, that we
 have used spatially unresolved upper limits, which is quite optimistic
@@
 flux. Actually, the Fermi-LAT 3 year data will be able to constrain
-constrain the smallest mass of substructures using the DM BM
-models. We have also learned that close by clusters are superior to
-far away clusters, even though close by clusters have a mass that is
-much smaller. In fact, we can understand this by looking at the
-luminosity-to-mass scaling relations. The gamma-ray luminosity from
-the smooth density profile is given by
-\begin{equation}
-L_\rmn{sm} \propto \int \dd V \rho(r)^2 \propto \frac{c^3}
+the smallest mass of substructures using the DM BM models. We have
+also learned that the closest clusters are superior for DM searches
+compared to further away clusters, even though the close by clusters
+have a mass that is smaller. In fact, we can understand this by
+looking at the luminosity-to-mass scaling relations. The gamma-ray
+luminosity from the smooth density profile is given by
+\begin{equation}
+L_{\gamma,\rmn{sm}} \propto \int \dd V \rho(r)^2 \propto \frac{c^3}
 {\left[\log\left(1+c\right)-c/(1+c)\right]} \propto \mvir^{0.83}\,,
 \end{equation}
-and the total luminosity including boostfactors for the DM LP and BM
-models is given by
+and the total DM luminosity including boost factors for the LP and
+the BM models are given by
 \begin{eqnarray}
-L_\rmn{tot,LP} &=& L_\rmn{sm,LP} \B_\rmn{LP} \propto \mvir^{0.73}\qquad
+L_{\gamma,\rmn{LP}} &=& L_{\gamma,\rmn{smLP}} \B_\rmn{LP} \propto \mvir^{0.73}\qquad
 \,\,\,\,\,\,\rmn{and}\\
-L_\rmn{tot,BM} &=& L_\rmn{sm,BM} \B_\rmn{BM} \propto  \mvir^{1.06}\,,\qquad
+L_{\gamma,\rmn{BM}} &=& L_{\gamma,\rmn{smBM}} \B_\rmn{BM} \propto  \mvir^{1.06}\,,\qquad
 \rmn{where} \\
@@
 on the SFE and boost from substructures. As more sensitive experiments
-and better upper limits emerge, we can start ruling out models giving
-rise to these type of boost factors that are manifested in the
-gamma-ray flux. Especially interesting is to constrain the SFE, where
-a boost of 300 is required to explain the excess of electrons and
+and better upper limits emerge, we can start ruling out models that
+give rise to boost factors that are manifested in the gamma-ray
+flux. It is especially interesting is to constrain the SFE, where a
+boost of 300 is required to explain the excess of electrons and
 positrons observed in the vicinity of Earth by PAMELA/Fermi/HESS.  In
 Fig.~\ref{fig:clu_comp} we use the estimated flux from four clusters
-to constrain the minimum mass of substructures where
-$M_\rmn{lim}\propto\mvir^{0.226}$, as well as the SFE. As expected,
-the Fornax cluster is the most constraining cluster by far, although
-the current upper limits are not good enough to rule out either the
-boost from substructures or SFE. Assuming that the electron and
-positron excess is due to SFE DM matter, then in order not to
-overproduce the differential upper limits set by Fermi-LAT in the
-energy range $1-10$~GeV \footnote{We average the LP DM flux in the
-  energy range $1-10$~GeV before we compare it to the upper limits.}
-we can constrain the smallest mass of substructures to
-$M_\rmn{lim}\gtrsim 10\,\msun$. Instead assuming the standard mass of
-the smallest substructures of $M_\rmn{lim}\gtrsim 10^{-6}\,\msun$, we
-can constrain the boost from SFE to about 4 in Fornax, corresponding
-to a maximum SFE in the MW of about 10.
+to constrain the SFE as well as the minimum mass of substructures
+where $M_\rmn{lim}\propto\mvir^{0.226}$. As expected, the Fornax
+cluster is the most constraining cluster by far, although the current
+upper limits are not good enough to rule out the boost from
+substructures or SFE. Assuming that the electron and positron excess
+is due to SFE DM matter, then in order not to overproduce the
+differential upper limits set by Fermi-LAT in the energy range
+$1-10$~GeV \footnote{We average the LP DM flux in the energy range
+  $1-10$~GeV before we compare it to the upper limits.}  we can
+constrain the smallest mass of substructures to $M_\rmn{lim}\gtrsim
+10\,\msun$. Instead assuming the standard mass of the smallest
+substructures of $M_\rmn{lim}\gtrsim 10^{-6}\,\msun$, we can constrain
+the boost from SFE to about 4 in Fornax, corresponding to a maximum
+SFE in the MW of about 10.
 
@@
 \end{figure}
-HOW ARE UL CALCULATED?
 
@@
 In this section we investigate the gamma-ray surface brightness
-profiles induced by both DM and CRps. We start by comparing the
-substructure included brightness from different clusters in
-Fig.~\ref{fig:SB_clu}. As expected, we find that the DM flux in all
-clusters follow the same smooth shape imposed by the
-substructures. Even as far in as 1\% of $\rvir$ we are dominated by
-the substructures, which is due to the projection of the outer cluster
-halo (see Sect.~\ref{sect:subst} for a longer discussion). This
-implies that the spatial distribution of annihilating DM induced
-emission is independent of the type of DM model, and can not be used
-to separate different models. The normalization for the BM model
-determined by $\bsub L_\rmn{BM}^{1/3} \propto \mvir^{0.50}$, which
-explains the factor three difference in normalization. The flux from
-the LP model show a smaller spread in the normalization which is due
-to the additional contribution from SFE with a negative mass trend,
-hence a normalization with a softer mass-scaling of
-$\sim\mvir^{0.17}$. The surface brightness induced by CRps mainly
-trace the gas profile of each cluster with an additional enhancement
-in the center due to the expected large population of CRps, hence we
-see a much larger spread in these profiles. It is noticeable that
-Fornax show such a small surface brightness. However, it is explained
-by the low gas density outside the BCG and the less abundant CRp
-population in the relative small cluster compared to a more massive
-cluster \cite{2010MNRAS.409..449P}. In fact, only the very inner part
-of Fornax is dominated by a large gamma-ray flux from CRps, which
-however, is neglible compared to the flux withing $\rvir$. This is the
-reason why Fornax is such a good target for indirect DM searches, and
-competitive to DM searches in dwarf galaxies. Although, it might be a
-problem for Cherenkov telescopes looking for a DM in the center of
-Fornax.
+profiles induced by both CRps and different models of DM in more
+detail. We start by comparing the substructure included brightness
+from different clusters in Fig.~\ref{fig:SB_clu}. As expected, we find
+that the DM flux in all clusters follow the same smooth universal
+shape imposed by the substructures. Even as far in as 1\% of $\rvir$
+we are dominated by the substructures, which is due to the projection
+of the outer cluster halo (see Sect.~\ref{sect:subst} for a longer
+discussion). This implies that the spatial distribution of
+annihilating DM induced emission is independent of the type of DM
+model, and can not be used to separate different models. The
+normalization for the BM model is determined by $\bsub
+L_{\gamma,\rmn{BM}}^{1/3} \propto \mvir^{0.5}$, which explains the
+factor three difference in normalization between the most massive
+cluster Coma and the least massive cluster Fornax with a mass ratio of
+about 10. The flux from the LP model show a smaller spread in the
+normalization which is due to the additional contribution from SFE
+with a negative mass trend, hence a normalization with a softer
+mass-scaling of $\sim\mvir^{0.17}$. The surface brightness induced by
+CRps mainly trace the gas profile of each cluster with an additional
+enhancement in the center due to the expected large population of
+CRps, hence we see a much larger spread in these profiles. It is
+noticeable that Fornax show such a small surface brightness. However,
+it is explained by the low gas density outside the BCG and the less
+abundant CRp population in the relative small cluster compared to a
+more massive cluster \cite{2010MNRAS.409..449P}. In fact, only the
+very inner part of Fornax is dominated by a large gamma-ray flux from
+CRps, which however, is neglible compared to the flux withing
+$\rvir$. This is the reason why Fornax is such a good target for
+indirect DM searches, and competitive to DM searches in dwarf
+galaxies. Although, it might be a problem for Cherenkov telescopes
+looking for a DM in the center of Fornax.
 
@@
   (blue). The surface brightness above 1~GeV is derived using a very
-  small point spread function ($\theta_\rmn{psf}=10^{-5}\deg$). The
+  small point spread function ($\psf=10^{-5}\deg$). The
   different linestyles each represent a cluster; Fornax (solid), Coma
@@
 
-In order to learn about the spatial distribution of the DM flux in
-various clusters for different DM models and associated gamma-ray
-components, we show in the left panel of Fig.~\ref{fig:SB_clu_nosub}
-the brightness profiles for the smooth DM distribution for the same
-four representative clusters that was shown previously in
+NEED TO REWRITE, JUMPING BACK AND FORTH BETWEEN PANELS In order to
+learn about the spatial distribution of the DM flux in various
+clusters for different DM models and associated gamma-ray components,
+we show in the left panel of Fig.~\ref{fig:SB_clu_nosub} the
+brightness profiles for the smooth DM distribution for the same four
+representative clusters that was shown previously in
 Fig.~\ref{fig:SB_clu}. In addition, we show the spatial dependence of
@@
 the components study in the right panel that show the neglible
-contribution from the IC upscattered light from stars and dust at this
+contribution from the IC upscattered light from SD at this
 energy. Since the surface brightness from BM models are dominated by
-the continuum emission at each radius in all clusters, we see that
-this component follows the projected density profile over the entire
-clusters. The LP model, however, show a much flatter profile in the
-central parts of the clusters, which is due to the efficient IC cooling
-of the electrons and positrons on the SD component. There is also some
+the continuum emission at each radial bin in all clusters, we see that
+the total DM emission follows the projected density profile over the
+entire clusters. The LP model, however, give rise to a much flatter
+profile in the central parts of the clusters. This is due to the IC
+upscattered CMB photons that are upscattered on an electron and
+positron population that suffers from efficent cooling on light from
+SD. The IC emission from SD photons have a rather steep spectrum in
+the center that follows the projected density profile which is
+explained by the SD dominated cooling that cancels the spatial
+dependece from the SD spectrum. In the left panel we also find some
 variation in the profiles for the different clusters in the central
@@
 surface brightness. As also noticed in previous figure, the flux from
-DM is dominated by the CRp induced emission for all clusters.
-
-Might want to mention that the IC-SD spectra for both DM models follow
-the projected density contribution due to the cancellation in the
-radial dependence of the SD spectra and the SD cooling that dominates
-he cooling in the center.
+DM without substructures is dominated by the CRp induced emission for
+all clusters.
 
@@
   brightness above 1~GeV is derived using a very small point spread
-  function ($\theta_\rmn{psf}=10^{-5}\deg$). LEFT PANEL: compare the
+  function ($\psf=10^{-5}\deg$). LEFT PANEL: compare the
   surface brightness for different clusters; Fornax (solid), Coma
@@
 starlight and dust, while the BM models were mainly dominated by the
-continuum emission. These high energies are reachable by both Fermi-LAT
-and Cherenkov telescopes, thus important observationally. We therefore
-show in Fig.~\ref{fig:SB_IACTs} the surface brightness above
+continuum emission. These high energies are reachable by both
+Fermi-LAT and Cherenkov telescopes, thus important observationally. We
+therefore show in Fig.~\ref{fig:SB_IACTs} the surface brightness above
 $100\,$~GeV for a realistic PSF of $0.1\deg$ where we include the
-boost from substructures. We look at both the relative small Fornax
-cluster and the massive close by Virgo cluster Both clusters show a
-very flat brightness profile within about 10\% of $\rvir$, due to both
-the effect from substructures and the smoothening over the PSF. The CRp
-induced emission also show a smoothing in the central parts due to the
-PSF. In the outer part of the Fornax cluster the CRp flux is suppressed
+boost from substructures. We look at two clusters with an expected
+high DM signal; the relative small Fornax cluster and the massive
+close by Virgo cluster Both clusters show a very flat brightness
+profile within about 10\% of $\rvir$, due to both the effect from
+substructures and the smoothening over the PSF. The CRp induced
+emission also show a smoothing in the central parts due to the PSF. In
+the outer part of the Fornax cluster the CRp flux is suppressed
 compared to the substructure boosted DM flux, where the LP model is
@@
 that there are large uncertainties in the gas density profile used to
-estimate the CRp surface brightness (see Fig.~\ref{fig:dens_fornax} for
-more details).
+estimate the CRp surface brightness (see Fig.~\ref{fig:dens_fornax}
+for more details).
 
@@
   boost from substructures. We use a point spread function of
-  $0.1\deg$ that is typical for both Cherenkov telescopes as well as
-  the Fermi-LAT at this energy. Left panel show the Fornax cluster
-  and right panel the Virgo cluster. The gamma-ray emission is derived
-  for the following components; CRps (red solid), continuum emission
-  from the DM $\Kp$ benchmark model (blue dash-dotted), as well as
-  final state radiation (green dashed) and inverse Compton upscattered
-  dust and starlight (green dotted) from leptophilic DM.}
+  $\psf=0.1\deg$ that is typical for both Cherenkov
+  telescopes as well as the Fermi-LAT at this energy. Left panel show
+  the Fornax cluster and right panel the Virgo cluster. The gamma-ray
+  emission is derived for the following components; CRps (red solid),
+  continuum emission from the DM $\Kp$ benchmark model (blue
+  dash-dotted), as well as final state radiation (green dashed) and
+  inverse Compton upscattered dust and starlight (green dotted) from
+  leptophilic DM.}
  \label{fig:SB_IACTs}

### 2011-04-05 paper.tex
conclusion added

--- 2011-04-05 paper.tex
@@
 
-%\def\del#1{{}}
-\def\del#1{{\bf (DELETED TEXT)}}
-%\def\C#1{#1}
-\def\C#1{{\bf #1}}
+\def\del#1{{}}
+%\def\del#1{{\bf (DELETED TEXT)}}
+\def\C#1{#1}
+%\def\C#1{{\bf #1}}
 
@@
 This yields Fornax ($\mvir=10^{14}\,\msun$) and Virgo
-($\mvir=2.1\times10^{14}\,\msun$) \cite{} as the prime targets for DM
+($\mvir=2.1\times10^{14}\,\msun$) \del{\cite{}} as the prime targets for DM
 observations, Perseus ($\mvir=7.7\times10^{14}\,\msun$) for CR induced
@@
 
+\clearpage
+
 \section{Conclusions}
 
+In this paper, we study the possibility for detecting $\gamma$-ray emission in
+galaxy clusters. We consider benchmark and leptophilic models of supersymmetric
+dark matter as well as cosmic ray induced pion decay which is thought to
+dominate the astrophysical signal from clusters. Once supersymmetric cold dark
+matter decouples from the expanding universe it streams freely and smooths over
+any potentially present smaller scales. This imprints as a characteristic
+minimum halo mass $M_\mathrm{min}$ into the hierarchy of structure formation and
+should still survive until the present time as substructure within larger
+halos. It turns out that the boost due to substructures dominates over the
+smooth component for halo masses $M>10^3 \msun$ and contributes a constant
+luminosity for each decade in halo mass. The ratio of halo-to-minimum subhalo
+mass $M_{200}/M_\mathrm{min}$ is maximized for the largest systems that had time
+to collapse and virialize since the Big Bang -- galaxy clusters. The
+corresponding substructure boost can reach values exceeding $10^3$ which should
+make nearby clusters the brightest DM annihilation sources after the Milky May
+center and hypothetical very close-by DM substructures. Since the substructures
+are distributed according to an Einasto profile, the contribution to the
+annihilation emission from substructures peaks around the virial radius. This
+implies an almost flat surface brightness profile of the annihilation emission
+which makes it necessary to have the entire cluster in the field-of-view to take
+advantage of the entire substructure boost.  This property makes it difficult to
+detect DM annihilation emission without an enhancement of the particle physics
+cross section over its standard value of $\sigma v\sim 3\times 10^{-26}
+~\mathrm{cm}^3~\mathrm{s}^{-1}$ with imaging air Cherenkov telescopes due to the
+spatially extended boost from substructures of angular extend $\sim
+0.5-1\deg$. In contrast, the sensitivity of Cherenkov telescopes drops linearly
+with radius outside the point spread function $\sim0.1\deg$.
+
+We identify Fornax to be the best cluster/group candidate for indirect DM
+studies as it is expected to emit the brightest annihilation flux and more
+importantly, has a comparably low CR induced $\gamma$-ray flux.  This in
+principle should allow to detect or constrain some benchmark models that have
+been chosen for the large $\gamma$-ray flux yield with three-year Fermi data
+(or constrain the substructure boost factor). Other nearby bright sources of the
+extended HIFLUCGS sample of nearby bright X-ray cluster/groups are M49,
+Centaurus, and NGC~4636.  The non-detection of $\gamma$-ray emission by Fermi in
+a total of 14 clusters/groups (the mentioned clusters as well as Virgo, Coma,
+Hydra, and Norma among others) considerably constrains leptophilic models for DM
+annihilation which were introduced to explain the increasing positron-to-lepton
+ratio beyond 10 GeV. Assuming that the minimum DM substructure mass extends down
+to an Earth mass, we can rule out these leptophilic models based on the
+non-observation of $\gamma$-rays in any of the fore-mentioned
+clusters/groups. Alternatively, assuming the leptophilic models to be correct,
+we limit the minimum substructure mass to $4~\msun$ in Fornax. Assuming
+universality of the DM model, this corresponds to a minimum substructure mass of
+$10~\msun$ in the Milky Way due to the larger Sommerfeld boost factor in smaller
+mass halos which have a lower circular velocity which enhances the particle
+cross section.
+
+In this work, we thoroughly study the spectral emission characteristics of the
+DM emission. In general there are different radiation mechanism that emit in the
+$\gamma$-ray regime, namely (i) continuum emission following the hadronization
+of the annihilating neutralinos in benchmark models which leads to the
+production of charged and neutral mesons which decay finally into electrons,
+neutrinos, and gammas, and (ii) inverse Compton (IC) emission by the leptons in
+the final state which up-scatter radiation fields from the cosmic microwave
+background, dust, and starlight, and (iii) final state radiation or internal
+bremsstrahlung which dominates the highest energy emission close to the rest
+mass of the self-annihilating neutralinos (if present in the model under
+consideration). We construct a rather simple semi-analytic model for the spatial
+and spectral distribution of dust and starlight in clusters which can be used
+for the annihilation emission in galaxies with a different spatial profile.  We
+find that in benchmark models, the continuum emission dominates over the IC
+emission of any available radiation field. In the leptophilic models, where the
+continuum emission is absent, the IC up-scattering of the CMB dominate below 30
+GeV. For energies $30~\mathrm{GeV} \lesssim E_\gamma \lesssim 300~\mathrm{GeV}$,
+the IC up-scattering of the dust emission dominates and is followed by the final
+state radiation for energies up to $m_\chi c^2 \sim 1$~TeV. The IC emission of
+starlight remains always subdominant. We stress, that the inclusion of the dust
+and starlight radiation fields are important in the cooling function for the
+leptons and a failure to do so biases the inferred CMB IC flux high by a factor
+of two.
+
+We substantially improve the modelling of the expected $\gamma$-ray signal from
+pion-decay resulting from hadronic CR interactions with gas protons. We employ
+the semi-analytic model of the CR spectrum and spatial distribution, recently
+developed by \citet{2010MNRAS.409..449P} that is based on cosmological
+hydrodynamical simulations that self-consistently follow the evolution of CRs in
+cosmic structure formation. Adopting the model for all clusters in the HIFLUGCS
+sample of flux-limited X-ray clusters, we compare the expected $\gamma$-ray
+emission to that inferred from using $L_\gamma$-cluster mass scaling
+relation. We note that the predictions of our ``optimistic'' model are perfectly
+in agreement with Fermi upper limits for all clusters.  The hint of a tension
+that the scaling relation modeling showed for Norma \citep{2010ApJ...717L..71A}
+could not be confirmed due to the apparently lower gas density of this cluster
+relative to the average.  As expected, the semi-analytic model adds ``scatter''
+to the scaling relation and biases the $\gamma$-ray flux high for prominent cool
+core clusters by up to a factor of 3.5 relative to the expectation from the
+scaling relation. This is due to the high target gas densities and associated CR
+densities in those cool cores that shape the spatial emission characteristic to
+be very similar to that observed in thermal X-rays. We caution that these
+predictions only apply for the case of negligible CR transport such as streaming
+and diffusion relative to the gas and might be considerably modified in those
+cluster that do not show an extended diffuse radio(-mini) halo that might point
+to a centrally concentrated CR distribution \citep{2011A&A...527A..99E}. The CR
+spectrum $E^2 dN/dE$ shows the characteristic pion bump at energies around
+1~GeV. It is expected to dominate the DM annihilation signal in the benchmark
+models for all clusters/groups but Fornax. We conclude that it will be possible
+to rule out the leptophilic model with eight-years of Fermi data and start to
+constrain some benchmark DM models. Hence this should nicely complement direct
+and accelerator searches for the nature of dark matter.
+
+\del{
 Some of the results (should discuss what we want to emphasize):
---) the flux from annihilating DM is boosted by about a factor 1000 in
+O) the flux from annihilating DM is boosted by about a factor 1000 in
  clusters
---) flat surface brightness profiles with substructures
---) Fornax is a great target for indirect DM studies because the relative
+O) flat surface brightness profiles with substructures
+O) Fornax is a great target for indirect DM studies because the relative
  low flux from CRps and high flux from DM
---) the IC upscattered photons from stars and dust are dominated in the
+O) the IC upscattered photons from stars and dust are dominated in the
  relevant energy regimes by the continuum emission for our DM
  benchmark models
---) Fermi 3 year data will constrain the smallest mass of substructures
+O) Fermi 3 year data will constrain the smallest mass of substructures
  using the benchmark models
---) difficult to detect DM without a Sommerfeld boost with Cherenkov
+O) difficult to detect DM without a Sommerfeld boost with Cherenkov
  telescopes since the boost from substructures is extended while the
@@
  outside the point spread function (CHECK)
---) we rule out the leptophilic models in present form in 14 clusters,
+O) we rule out the leptophilic models in present form in 14 clusters,
  and limit the boost from Sommerfeld enhancement in the MW to less
@@
  predictions for the CRps
---) we provide a rather simple model to calculate the spatial and spectral
+O) we provide a rather simple model to calculate the spatial and spectral
  distribution of dust and stars in cluster (might be used for
  galaxies? with different spatial profile)
+}
 

### 2011-04-06 paper.tex
minor changes

@@
 \newcommand{\s}{\rmn{s}}
-\newcommand{\Kp}{\rmn{K}`}
-\newcommand{\Ip}{\rmn{I}`}
+\newcommand{\Kp}{\rmn{K}^\prime}
+\newcommand{\Ip}{\rmn{I}^\prime}
 \newcommand{\Js}{\rmn{J}^*}
-\newcommand{\Jp}{\rmn{J}`}
+\newcommand{\Jp}{\rmn{J}^\prime}
 \newcommand{\B}{\rmn{B}}
@@
 \newcommand{\qCR}{q_{\rmn{CR}-\ensuremath{\pi^0}}}
+\newcommand{\ds}{{\sc DarkSUSY}}
 
@@
 
-\subsection{Particle physics}
+\subsection{Detecting Particle Dark Matter}
 \label{sect:PF}
+Besides the intrinsic interest in the gamma-ray flux from galaxy
+clusters generated by conventional hadronic and electromagnetic
+process - which should be close to observability with the Fermi-LAT
+data \cite{Berezinsky:1996wx,2007A&A...473...41E,2010MNRAS.409..449P}
+- the possible contribution from WIMP dark matter is of greatest
+interest. A WIMP (Weakly Interactive Massive Particle) which fulfils
+the WMAP bounds on the relic density of cold dark matter (CDM) of
+\cite{Komatsu:2010fb}
+$$\Omega_{CDM}h^2=0.112\pm 0.0056,$$ will in many cases naturally give
+a $\gamma$ yield which may be observable. In addition, there are
+possible enhancement effects known, such as the astrophysical boost
+from dense substructure of dark matter halos, or the particle physics
+boost from the Sommerfeld effect, which may increase the chances of
+detection further.
+
+There are three methods for detecting dark matter candidates which are
+presently employed: First, at particle physics accelerators such as
+CERN's LHC, one is now entering into a new energy regime which may
+allow the production of the heavy, electrically neutral and long-lived
+particles which may constitute dark matter. From these experiments one
+may get the first glimpse of the mass scale beyond the standard model
+where dark matter may reside. However, to really show that any of the
+hypothetical, new particles created at the LHC is actually the dark
+matter, one has to rely on the two other methods available for the
+dark matter search, namely direct and indirect detection. Direct
+detection methods, which are presently evolving rapidly use the feeble
+interaction between that dark matter particles of the galactic halo
+and nuclei such as Germanium, Sodium, Iodine, Argon or Xenon to infer
+the scattering cross section and a rough estimate of the mass of the
+dark matter particle (for the currently most sensitive search, see
+\cite{Aprile:2010um}). A characteristic of this method is that it
+basically only depends on the local dark matter density (which is
+rather well determined to be around $0.4$ GeV/cm$^3$) and the basic
+cross section for dark matter - nucleus scattering. A disadvantage is
+that it does benefit from the two enhancement mechanisms mentioned
+above, boost from substructure and/or the Sommerfeld effect. Also, it
+cannot be excluded - although it seems at present improbable - that
+the local halo structure is such that the solar system happens to be
+in an underdense region.
+
+In indirect detection, on the other hand, in particular in the photon
+channel, one searches for products of dark matter annihilation in the
+galactic halo and beyond. Particularly interesting targets are the
+galactic center (for a recent possible indication of a signal, see
+\cite{Hooper:2010mq}), the dwarf galaxies surrounding the Milky Way
+\cite{Strigari:2006rd,Essig:2009jx,2010JCAP...01..031S}, galaxy
+clusters (the focus of this work)
+\cite{Ghigna:1998vn,Lewis:2002mfa,Boyarsky:2006kc,2006A&A...455...21C,2009PhRvL.103r1302P},
+and even the cosmological large scale structure
+\cite{Bergstrom:2001jj,Ullio:2002pj,Taylor:2002zd,Elsaesser:2004ap,Cuoco:2010jb,Abazajian:2010sq,Abdo:2010dk,Zavala:2011tt}.
+
+There is also a possiblity to search for dark matter annihilation
+indirectly in antimatter channels, like antiprotons or positrons. Here
+diffusion is, however, very efficient which means that the directional
+signature which is so important for gamma-rays, is completely
+erased. This method has, however, recently been much in focus due to
+the surprising rise with energy of the electron to proton ratio
+measured by the PAMELA satellite experiment \cite{Adriani:2008zr} and
+the ``bump'' in the total electron plus positron spectrum detected by
+Fermi \cite{Abdo:2009zk}. The viable particle physics models
+describing these results contain some non-trivial, or even unnatural
+elements, however. First of all, annhilation to quarks has to be very
+much suppressed, due to the non-observation of an enhanced antiproton
+flux by PAMELA \cite{Adriani:2010rc}. This means that only so-called
+{\em leptophilic} models, where the annihilation only goes to leptons
+have to be considered. Here, one has to have a sizeable fraction going
+to muons and tau leptons, as the shape of the spectrum disfavours
+direct annihilation into electrons and positrons. To get agreement
+with the measured absolute rates, one also has to have a large boost
+factor (of the order of at least several hundred), which is difficult
+to achieve with substrucutre alone. An additional enhancement of the
+annihilation rate has to be invoked, for example given by the {\em
+  Sommerfeld effect}. This basically means that the usual connection
+between annihilation rate at decoupling (when relative velocities $v$
+were of order $0.2 - 0.3$), which gives the relic density, and
+present-day annihilation in the halo (with velocities $v\sim 10^{-3}$)
+is broken. This would come about because the dark matter sector
+contains additional light particles which mediates an interaction with
+almost bound states which enhance the wave function at the relative
+origin, and therefore the annihilation rate (for a pedagogical review
+of viable scenarios, see \cite{ArkaniHamed:2008qn}). As a final
+difficulty of these models, the lack of an inverse-compton signature
+from the galactic center means that only shallow density profiles can
+describe the galactic dark matter density distribution
+\cite{Bertone:2008xr,Cirelli:2008pk,Bergstrom:2008ag}. (For a review
+of the dark matter modelling of these effects, see
+\cite{Bergstrom:2009ib}. For a recent treatment, showing still viable
+models, see \cite{Finkbeiner:2010sm}.)
+
+A more standard explanation of the PAMELA/Fermi excess would be
+pulsars or other supernova remnants (e.g.,
+\cite{Hooper:2008kg,Ahlers:2009ae}). In that case, dark matter would
+more likely be explained by the standard scenario of a WIMP, for
+example the thoroughly studied lightest supersymmertric neutralino
+(for reviews, see
+\cite{Jungman:1995df,Bergstrom:2000pn,Bertone:2004pz}). We note that
+the soon to be launched AMS-02 experiment on the International Space
+Station \cite{ams02} may gave interesting clues to the origin of the
+antimatter excess.
 
@@
 \label{sect:LP}
-Sommerfeld enhancement, electron spectra
-
-\subsubsection{Supersymmetric dark matter}
-neutralino, benchmark models, continuum emission, electron spectra
+The results of PAMELA \cite{Adriani:2008zr} and Fermi-LAT
+\cite{Abdo:2009zk} (and to some extent ATIC
+\cite{2008Natur.456..362C}, although the bump seen there at 600 GeV
+has not been reproduced by other experiments) has caused intense
+activity in the theoretical dark matter community. At first, there was
+skepticism whether such a large signal could be compatible with a
+WIMP. However, the possibility of an enhanced annihilation rate due to
+dark matter halo substructure has been realised for a long time
+\cite{1993ApJ...411..439S,Bergstrom:1998zs,Moore:1999nt}, although it
+is difficult to achieive the boost factor of the order of a few
+hundred to a thousand in the solar neighbourhood, as substructure
+according to numerical simulations is most important in the outer
+portions of the halo, due to tidal stripping of subhaloes in the inner
+part. Another potentially very important effect which may explain the
+large boost had been found a few years earlier, namely the Sommerfeld
+enhancement. This effect, was computed for electromagnetism by Arnold
+Sommerfeld may years ago \cite{sommerfeld} and recently rediscovered
+in the quantum field theory of dark matter
+\cite{2005PhRvD..71f3528H,2007NuPhB.787..152C,2009PhRvD..79a5014A}.
+In quantum mechanics describing electron scattering and electron
+positron annihilation, it is caused by the distortion of the plane
+wave describing the relative motion of the annihilating particle pair,
+due to the near formation of a bound state caused by photon
+exchange. In the ladder approximation for QED, one reproduces the
+Sommerfeld effect, and the square of the relative wave function at the
+origin (which enters into the probablity for the short-distance
+process of annihilation) is increased by the factor
+\cite{2009PhRvD..79a5014A}
+$$
+S_{QED}=\frac{|\psi(0)|^2}{|\psi^{(0)}(0)|^2}=|\frac{\frac{\pi\alpha}{v}}{1-e^{-\frac{\pi\alpha}{v}}}|,
+$$ with $\alpha =e^2/\hbar c$ the fine-structure constant, and $v$ the
+realtive velocity. This amounts to $S_{QED}=\pi\alpha/v$ for small
+velocities. For a Yukawa-like particle of mass $m_\phi$, mediating a
+weak attractive force with coupling contant $\alpha_Y$ between dark
+matter particles $\chi$ with mass $m_\chi$, the small-velocity limit
+of the enhancement becomes instead
+$$
+S_Y\sim\frac{\alpha_Y m_\chi}{m_\phi}.
+$$ In the general case, with mediators that may also excite virtual
+charged particles in the dark matter sector, one has to solve
+numerically a coupled system of differential equations using
+appropriate boundary conditions
+\cite{2005PhRvD..71f3528H,2007NuPhB.787..152C,2009PhRvD..79a5014A}. In
+some cases, the enhancement factor $S$ can be as high as several
+hundred to a few thousand, depnding however on the exact parameters of
+the theory. The effect is usually strongly velocity-dependent,
+depending on velicity as $1/v$ or, in the fine-tuning case of being
+very near resonance, as $1/v^2$. This means that in a virialised
+system (such a a galaxy cluster) with large velocity dispersion
+$v_{\rm cl}$ the Sommerfeld enhancement will be smaller than the one
+expected in a single galaxy such as the Milky Way, roughly by a factor
+$v_{\rm MW}/v_{\rm cl}$.
+
+As leptophilic models, apart from being slightly contrived from the
+particle physics point of view, are also rather limited by several
+sets of astrophysical data, we take advantage of the recent reanalysis
+\cite{Finkbeiner:2010sm} to define a benchmark leptophilic model that
+is still viable.  It is found that the bounds from WMAP5 approximately
+imply a Sommerfeld boost factor $S$ which has to satisfy $S(v\to
+0)\lesssim 200/f\ (m_Y/1$ GeV$)$, where $f$ is the fraction of energy
+from dark matter annihilation that ionizes the intergalactic medium,
+$f\sim 0.7$ for annihilation to electrons and a factor a a few smaller
+for all other standard model final states.
+
+Taking into account the whole cosmic history of leptophilic models,
+also utilizing limit on spectral and polarization distorsions of the
+CMB, the maximal value for the boost factor for a 1 to 2 TeV particle
+and sub-GeV force carriers is found to be \cite{Finkbeiner:2010sm}
+between 400 and 800. Although lower than the first estimates (e.g.,
+\cite{Bergstrom:2009fa,Meade:2009iu}) this is still enough to explain
+the PAMELA and Fermi excess, given other astrophysical uncertainties.
+
+To connect easily to our previous work \cite{2009PhRvL.103r1302P}, we
+choose as our benchmark leptophilic model one with mass $1.6$ TeV and
+Sommerfeld boost $S=300$.
+
+\subsubsection{Supersymetric dark matter}
+The most studied models for dark matter are supersymmetric ones,
+especially models where the lightest supersymmetric particle, in most
+models the lightest neutralino, is stable. The stability is assured in
+viable SUSY models due to a discrete symmetry, $R$-parity. This
+symmetry is needed from the particle physics point of view to avoid
+fast proton decay, and automatically makes the lightest supersymmetric
+particle stable, and therefore a good candidate for dark matter. In
+addition, as the coupling to ordinary matter is given by gauge
+couplings, the neutralino is automatically a WIMP
+candidate. Unfortunately, the breaking of supersymmetry (which has to
+be there since otherwise, e.g., there would exist a scalar electron
+with the same mass as the electron) means that a large number of
+essentially free parameters enter actual calculations.  The neutralino
+is then a linear combination of the supersymmetric partners of the
+U(1) gauge boson, one of the SU(2) gauge bosons, and the two Higgs
+doublets in the Minimal Supersymmetric extension of the Standard Model
+(the MSSM) with mixing coefficients which depend on the SUSY breaking
+parameters \cite{1984NuPhB.238..453E}. The parameter space is very
+large, too large in general to scan efficiently even with the most
+powerful computers. Therefore, often simplifying assumptions are made
+to limit the number of free parameters. Even then, a large number of
+viable models is found which give a relic density consistent with the
+WMAP data. This means that they are indeed very good templates for
+WIMP dark matter, something that explains their popularity besides the
+subjective statement that few more plausible models for dark matter
+have been put forward so far.
+
+The the wave function of the lightest neutralino can be written
+$$
+\tilde\chi_1=a_1\tilde B+a_2\tilde W_3+a_3 \tilde H_1^0+a_4\tilde H_2^0,
+$$
+with 
+$$
+\sum_{i=1}^4 |a_i|^2=1.
+$$
+the gaugino fraction of a given neutralino is $|a_1|^2+|a_2|^2$ whereas $|a_3|^2+|a_4|^2$ is the higgsino fraction.
+
+We use the \ds package \cite{ds} to compute the mass, couplings and
+relic density for a given set of parameters.  Actually, we take
+advantage of so-called benchmark models, which have been proposed in
+different contexts (in particular in \cite{Bringmann:2008kj} giving
+predictions for the MAGIC experiment), and which give a good
+representation of models with high enough gamma-ray rates to become
+the first candidates for dark matter indirect detection in imaging air
+Cherenkov telescopes. We use the following supersymmetric benchmark
+models:
+
+\begin{itemize}
+\item
+ $I′$: This model was introduced in \cite{2004EPJC...33..273B}, where
+  its phenomenology at colliders was studied. Annihilation directly
+  into lepton pairs is suppressed for neutralinos due to their
+  Majorana nature and therefore helicity suppression for annihilation
+  in the galactic halo \cite{1983PhRvL..50.1419G}. The higher order
+  process (inner bremsstrahlung, IB) $\tilde\chi_1\tilde\chi_1\to
+  \ell^+\ell^-\gamma$, which does not suffer from helicity suppression
+  \cite{1989PhLB..225..372B,2008JHEP...01..049B}, gives a considerable
+  contribution due to light sleptons in this model.
+
+\item $J′$: This model, also from \cite{2004EPJC...33..273B} is in the
+  so-called coannihilation tail. The sleptons are nearly degenerate
+  with the neutralino, which causes the large IB from the leptonic
+  final states to give a high enhancement of the flux.
+
+\item $K′$: A representative model for the funnel region, where the
+  annihilation dominantly occurs in the $s$-channel through exchange
+  of the pseudoscalar Higgs boson \cite{2004EPJC...33..273B}. Here IB
+  contributions are not important.
+
+\item $J^*$: Annihilation in the so-called coannihilation region,
+  introduced in \cite{2008JHEP...01..049B} as BM3, with a particularly
+  large IB contribution.
+
+\end{itemize}
 
 \subsubsection{Final state radiation}
-The photon spectrum from resulting from FSR is universal with only a
+There are two types of radiative processes which are important for our
+benchmark models, first the usual QED final state radiation (FSR) for
+both the leptophilic model and for supersymmetric models with charged
+final states. In addition, there may be direct emission from a
+virtual, charged, exchanged particle (such as a spin-0 slepton or
+squark), internal bremsstrahlung, IB. The latter is essentially only
+important when there is a helicity suppression for the lowest order
+annihilation process, which is the case for neutralinos, whose
+Majorana nature make the annihilation rate in the $s$ wave
+proportional to $m_f^2$, for final state fermion $f$. Interestingly,
+both the gamma-ray and fermion energy spectra are peaked at the
+highest energy for this process, which can in some models cause a
+rather spectacular bump in the spectra for these models.
+
+The photon spectrum resulting from FSR is universal with only a
 weak dependence of the underlying particle physics model. The photon
@@
 \end{equation}
-Here, the normalized photon energy $x=\eg/m_\chi c^2$, $\alpha =
-e^2/\hbar c$ is the fine-structure constant, $Q_X^2$ and $m_X$ the
+Here, the normalized photon energy $x=\eg/m_\chi c^2$, 
+$\alpha =e^2/\hbar c$ is the fine-structure constant, 
+$Q_X^2$ and $m_X$ the
 charge and mass of the particle $X$, respectively. The function
@@
 for fermions.
+
+The differential energy spectrum for the IB process is more
+complicated (see \cite{1989PhLB..225..372B,2008JHEP...01..049B}), but
+can be computed using {\sc DarkSUSY}. The differential photon energy
+spectra for all our benchmark models are shown in
+Fig.~\ref{fig:bmspectra}.  The peaking at high photon energy and the
+resulting bump caused by inner bremsstrahlung is clearly seen for
+benchmark models $I´$, $J´$, and $J^*$.
 
@@
 but increasing the distance by a factor two decrease the flux with a
-factor four.
+factor four. It is also usefull to relate the luminosities to a more
+model independent variable as the maximum circular velocity given by
+\begin{eqnarray}
+V_\rmn{max} &=& V_\rmn{circ}(r_\rmn{max})\qquad\,\,\,\,\,\,\,\,\,\rmn{where}\nonumber\\
+V_\rmn{circ}(r)&=& \sqrt{\frac{G_\rmn{N}\,M(<r)}{r}}\qquad\rmn{and}\nonumber\\
+\frac{\dd V_\rmn{circ}(r)}{\dd r} &=& 0\quad \Longrightarrow\quad r_\rmn{max}\,.
+\end{eqnarray}
+We find that $V_\rmn{max}=650\,\rmn{km/s}$ of a large $10^{15}\,\msun$
+cluster, and $V_\rmn{max}=420\,\rmn{km/s}$ of a small
+$4\times10^{13}\,\msun$ group.
+
 \del{

### 2011-04-07 paper.tex
figures,bib,txt

@@
 
-{\it Spatial distribution -- stars and dust}\\ Our goal in this
-section is to derive a simple spatial model for the distribution of SD
-in galaxy clusters. For this reason we use stacked cluster
-observations by Sloan in the $r$-band that trace the stars. We assume
-that the dust trace the stars in the clusters, which should be
-accurate to the order of magnitude estimate that we are interested in
-here. The stacked surface brightness profiles in
-\cite{2005MNRAS.358..949Z} are measured at redshift $z \sim 0.25$ with
-an average mass of the clusters of $4.0\times10^{13}\,\msun$. The
-profiles are build up out of three components; diffuse intracluster
-light (ICL), galaxies, and the brightest cluster galaxy (BCG) in the
-center of clusters. However, the total volume overlap of the ISM to
-the cluster is very small compared to the ICL- and BCG overlap with
-the cluster, thus the relative contribution of the galaxies to the IC
-emission is suppressed. To remove this bias we cut out the galaxies
-that have been smoothed over the cluster in the stacked analysis. In
-Fig.~\ref{fig:SD_spatial} we show the SDSS stacked brightness profiles
-as well as the fitted profiles\footnote{The measured brightness is
-  converted into units of $\rmn{erg}\,\rmn{s}^{-1}$ using
-  \cite{2010...book} $S(\rmn{mag}\,''^{-2}) =
-  \mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})$,
-  where the sun's absolute magnitude in the $r$-band is given by
-  $\mathcal{M}_\odot=27.1$ \cite{2000asqu.book..339L} and the
-  luminosity of the sun by $L_\odot=3.85\,10^{33}
-  \rmn{erg}\,\rmn{s}^{-1}$.}, both scaled with the unitless $\rvir$
-normalized area to resembele the expected luminosity at radius
-$r$. Our benchmark spatial model is shown with the solid black line,
-and include the contribution from the ICL and BCG.
-
 \begin{figure}%[t]
@@
 \end{figure}
-
-Instead of modelling the surface brightness with a de Vaucouleur
-profile with the addition of a power-law, we use a double beta profile
-model for simplicity of deprojection given by:
-\begin{equation}
-S_\sd (r_\bot)= \sum_{i=1}^2 \,S_i\, 
-\left[1 + \left( \frac{r_\bot}{r_{\mathrm{c}_i}}\right)^2\right]
-^{-3\beta_i + 1/2}\,,
-\label{double_beta}
-\end{equation}
-where we found the following best fitted central brightness ($S_i$),
-core radius ($r_{\mathrm{c}_i}$), and slope ($\beta_i$):
-\begin{eqnarray}
- S_1&=&1.4\times10^{-5}\,\rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1},\,
-r_{\mathrm{c}_1}=210\,\rmn{kpc},\,
-\beta_1=0.44\nonumber\\
- S_2&=&6.0\times10^{-3}\,\rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1},\,
-r_{\mathrm{c}_2}=2.8\,\rmn{kpc},\,
-\beta_2=0.45\,.\nonumber\\
-\label{fit_spatial_IR}
-\end{eqnarray}
-The 3D spatial profile is derived by deprojecting the surface
-brightness in Eq.~(\ref{double_beta}) (see
-e.g. \cite{2004A&A...413...17P} for details about the deprojection):
-\begin{eqnarray}
-  j(r)  = \sum_{i=1}^2 \frac{S_i}{2\pi\,r_{\mathrm{c}_i}}\,
-  \frac{6 \beta_i - 1}{\left(1 + r^2/r^2_{\mathrm{c}_i}\right)^{3\beta_i}}\,
-  \mathcal{B}\left(\frac{1}{2},3\beta_i\right)\,,
-\end{eqnarray}
-where $\mathcal{B}(a,b)$ denotes the beta-function
-\cite{1965hmfw.book.....A}.
-
-{\it Spectral distribution -- stars and dust} \\ Our goal in this
-section is to derive a simple spectral model for SD in galaxy
-clusters. Since the radiation from galaxies are expected to leak out
-into the ICM, we expect similar spectral distributions, at least to
-the order of magnitude that we are interested in here. Hence, we use
-the IR to UV spectrum derived in \cite{2006ApJ...648L..29P} for a MW
-type galaxy to characterize the spectral distribution of light from SD
-in a cluster. Note, however, that we only keep the spectral shape, and
-renormalize the spectral distribution using the luminosity from SD.
-
-In Fig.~\ref{fig:SD_spectra} we show the spectral distribution of the
-light from SD together with the CMB black-body distribution in a
-galaxy cluster, both at the radius $r=0.071\rvir$ where the energy
-density of the smooth light from SD (see Fig.~\ref{fig:SD_Edens})
-equals the energy density of the CMB. We have renormalized both the
-spectral data and the fitted spectra using the luminosity from stars
-and dust individually (see the normalization section below for further
-details).
 \begin{figure}%[t]
@@
 \end{figure}
-We choose to fit the spectrum of the dust that peaks at about
-$10^{-2}\,\ev$ with a double power-law, and the slightly wider
-spectral distribution of the stars that peaks at about $1\,\ev$ with a
-tipple power-law. We find the best fit spectra for the SD in a
-cluster through:
-\begin{eqnarray}
-  \eph^2\frac{\dd^2 N_\ph}{\dd \eph \dd V}
-  &\equiv& u_\sd(\eph) =  \sum_i N_i(\lx) u_i^\gal(\eph)\,,\nonumber \\ 
-\rmn{where}\quad i&=&\{\rmn{stars,dust}\} \qquad \rmn{and}\\ 
-% &=&  N_\dust(\lx) u_\dust^\gal(\eph) + N_\stars(\lx) u_\stars^\gal(\eph)  \nonumber \\ 
-%  \\
-  u_\stars^\gal(\eph) &=& \frac{23\,\rmn{eV}}{\rmn{cm}^3} 
-  \left(\frac{1.23\,\rmn{eV}}{\eph}\right)^{1.9} \nonumber \\
-  &\times&\left[1+\left(\frac{2.04\,\rmn{eV}}{\eph}\right)^{20}\right]
-  ^{-\frac{1.9}{20}}\nonumber \\
-  &\times& \left[1+\left(\frac{0.78\,\rmn{eV}}{\eph}\right)^{20}\right]^{-\frac{2.6}{20}}\,, \\
-  u_\dust^\gal(\eph) &=& 
-  \frac{40\,\rmn{eV}}{\rmn{cm}^3} 
-  \left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{4.9}\nonumber \\
-  &\times& \left[1+\left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{1.9}\right]^{-4.9}\,.
-\end{eqnarray}
-
-{\it Normalization}\\ The spatial and spectral distribution functions
-of the light from SD in a cluster are both normalized with a constant
-determined from the luminosity in each respective wavelength. The
-specific energy density is given by
-\begin{eqnarray} 
-u_\sd(\eph, r) &=& \frac{j(r)}{j(0)}\,u_\sd(\eph) \nonumber\\
-&=& \frac{j(r)}{j(0)}\,\sum_i N_i(\lx) u_i^\gal(\eph)\,,
-\end{eqnarray}
-where we fix the unitless normalization $N_i(\lx)$ using the total
-energy of the light in SD  within $\rvir$:
-\begin{eqnarray} 
-  E_{i,\vir} &=& L_i \frac{\rvir}{c} \nonumber \\
-  &=&N_i(\lx)\int_{\rvir} \int_i \,\frac{j(r)}{j(0)} 
-  \frac{u_i^\gal(\eph)}{\eph}\,\dd V\dd \eph\,,\nonumber \\
- \rmn{for}\quad i&=&\{\rmn{stars,dust}\}\,.
-\label{eq:E_SD}
-\end{eqnarray}
-Here we approximate the total energy of the photons within $\rvir$
-($E_{i,\vir}$) with the luminosity $L_i$ \cite{2008A&A...490..547G}
-times the typical timescale it takes for a photon to propagate through
-the cluster (we assume that the cluster is optically thin). Once we
-derived the SD luminosities for a well representative cluster, we use
-a IR to X-ray scaling relation to estimate the luminosity from an
-arbitrary cluster:
-\begin{equation}
-L_\ir=1.05\times10^{45}\,\rmn{erg\,s}^{-1}\,
-\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,,
-\label{eq:SD-X}
-\end{equation}
-where $\lx$ is the luminosity of the X-ray emitting gas within
-$\rvir$.
-
-The normalization constant for the starlight $N_\stars(\lx)$ is derived
-in the following three steps: (1) We use the average apparent magnitude
-in the $(r+i)$-band $m_{(r+i),0.25}\approx 15.5$
-\cite{2005MNRAS.358..949Z} of a cluster with the average mass
-$\mvir=4.0\times10^{13}\msun$ at a redshift $z=0.25$ to derive the
-luminosity from the stars:
-\begin{equation}
-L_\stars=10^{\frac{m_\odot-m_{(r+i),0.25}}{2.5}}
-\left(\frac{D_\clu}{D_\odot}\right)^2 L_\odot
-\approx 7.1\times10^{44}\,\rmn{erg}\,\rmn{s}^{-1}\,,
-\label{eq:L_star}
-\end{equation}
-where the apparent magnitude of the sun $m_\odot\approx -27.1$, the
-distance to the sun $D_\odot=4.85\times10^{-6}\,\rmn{pc}$, the
-luminosity of the sun $L_\odot=3.85\times10^{34}\,\rmn{erg\,s}^{-1}$,
-and the distance to the cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. (2)
-We use the IR to X-ray scaling relation in Eq.~(\ref{eq:SD-X}) to derive
-a more general form of the luminosity from stars in
-Eq.~(\ref{eq:L_star}) that is valid for an arbitrary cluster mass. The
-cluster X-ray luminosities are found in the extended HIFLUGCS
-catalogue \cite{2002ApJ...567..716R} to which we have added the Virgo
-cluster. (3) The normalization constant for the stars is
-determined from the above steps together with Eq.~(\ref{eq:E_SD})
-where we integrate over the cluster volume and spectral distribution
-of the stars. It is given by
-\begin{equation}
- N_\stars(\lx) = 1.2\times10^{-9}\,
-\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,.
-\label{eq:N_stars}
-\end{equation}
-Note that since the luminosities include the contribution from
-galaxies, we have integrated the spatial distribution including
-galaxies to derive the normalization. Once the normalization is fixed,
-the SD energy densities are derived from the spatial distribution
-where galaxies have been excluded.
-
-The normalization constant for the dust $N_\dust(\lx)$ is derived in the
-following four steps: (1) We use a cluster with the the average mass
-$\mvir=4.0\times10^{13}\msun$ and estimate the X-ray luminosity from
-the X-ray to mass scaling relations derived for the Representative
-XMM-Newton Cluster Structure Survey (REXCESS) in
-\cite{2009A&A...498..361P}:
-\begin{equation}
-\lx=1.18\times 10^{44}\,\rmn{erg\,s}^{-1}
-\left(\frac{M_{200}}{10^{14}\msun}\right)^{1.81}\,,
-\end{equation}
-where we have used that $M_\rmn{200} \approx 1.58\,M_\rmn{500}$ for a
-small cluster \footnote{We derive the factor 1.58 using
-  $M_\rmn{200}/M_\rmn{500}$ for the clusters in the HIFLUGCS catalogue
-  with a mass similar to $\mvir=4.0\times10^{13}\msun$ that we use to
-  derive the luminosity from dust.}. (2) From the IR to X-ray scaling
-relation in Eq.~(\ref{eq:SD-X}) we can now estimate calculate the
-luminosity from the dust for a $\mvir=4.0\times10^{13}\msun$ cluster;
-$L_\dust=4.7\times10^{44}\,\rmn{erg\,s}^{-1}$. (3) We generalize
-Eq.~(\ref{eq:L_star}) to an arbitrary cluster mass using
-Eq.~(\ref{eq:SD-X}) together with the cluster X-ray luminosities in
-the extended HIFLUGCS catalogue. (4) The normalization constant for
-the dust can now be determined from from the above steps together with
-Eq.~(\ref{eq:E_SD}) where we integrate over the cluster volume and
-spectral distribution of the dust. It is given by
-\begin{equation}
- N_\dust(\lx) = 1.4\times10^{-9}\,
-\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,.
-\label{eq:N_dust}
-\end{equation}
-Note that since the luminosities include the contribution from
-galaxies, we have integrated the spatial distribution including
-galaxies to derive the normalization. Once the normalization is fixed,
-the SD energy densities are derived from the spatial distribution
-where galaxies have been excluded.
-
-{\it Energy density}\\ The spatial distribution of the SD energy
-density is an important quantity since it impacts the steady state
-electron and positron spectra through cooling. A higher density of SD
-in a cluster suppresses the spectra of the upscattering particles. With
-the formalism presented above, we can now derive the energy density
-from starlight and dust in a galaxy cluster through
-\begin{eqnarray}
-\label{eq:U_SD}
-u_\sd(r) &=& \int \dd \eph \frac{\dd^2 N_\ph}{\dd \eph \dd V}\,\eph
-=\int \dd \eph \frac{u_\sd(\eph, r)}{\eph}
-\nonumber \\
-&=&  \frac{j(r)}{j(0)}  \int \dd \eph \sum_i 
-N_i(\lx) \frac{u_i^\gal(\eph)}{\eph}\,. \nonumber \\
-\end{eqnarray}
-In Fig.~\ref{fig:SD_Edens} we compare the energy densities from
-different radiation fields in a galaxy cluster with the mass
-$\mvir=4.0\times10^{13}\msun$. We use two different profiles for the
-SD energy density, where the total profile includes the contribution
-from the ICL, the BCG and all the galaxies, while the galaxies are
-excluded in the smooth profile. We find that even for a cluster with a
-relative small mass the energy density of the SD components dominates
-over the CMB and the magnetic fields (with a central B field of 3~$\mu
-G$) within about 10\% of $\rvir$. Outside this radius the CMB is
-dominating the energy density of the cluster, hence the magnetic
-fields are always subdominant in the cluster and can safely be removed
-from cluster IC calculations for a reasonable central B-field and
-spectral index. Note that in this work we keep the contribution
-from B-fields to the total energy density for consistency.
-
 \begin{figure}%[t]
@@
 \end{figure}
-
-\del{In this section we present the formalism for the different
-galaxy cluster emission components and show their contribution to the
-total dark matter gamma-ray spectrum. We account for the emission
-radiated both by final state radiation and inverse Compton where we
-allow for upscattering through CMB, starlight, and dust.}
-
-%Using a typical
-%X-ray luminosity of $L_\rmn{X}=10^{44}\,\rmn{erg\,s}^{-1}$ results in a
-%IR energy density
-%$N\,E_\IR\,f_\rmn{tot}(E_\IR)\,j(20\,\rmn{kpc})=u_\IR\simeq 4\,\rmn{erg\,
-%  cm}^{-1}$ in the region around 20~kpc from the cluster center at the
-%energy of the maximum IR energy density $E_\IR=0.011\,\rmn{eV}$.
 
@@
   \includegraphics[width=0.99\columnwidth]{figures/MLscaling.eps}
-  \caption{\it Lum-scaling relations, mass dependence of SD cooling
-    have been neglected, actually a factor few difference for
-    groups. factor 2 for Fornax, and small difference for large
-    clusters}
+  \caption{\it Luminosity to mass scaling relations. We show the
+    luminosity from; CRp induced emission (red solid), a leptophilic
+    model that IC upscatter CMB photons (green dash-dotted), mass
+    dependence of SD cooling have been neglected, actually a factor
+    few difference for groups. factor 2 for Fornax, and small
+    difference for large clusters}
  \label{fig:lum_mass_scaling}
@@
 \appendix
+
+{\it Spatial distribution -- stars and dust}\\ Our goal in this
+section is to derive a simple spatial model for the distribution of SD
+in galaxy clusters. For this reason we use stacked cluster
+observations by Sloan in the $r$-band that trace the stars. We assume
+that the dust trace the stars in the clusters, which should be
+accurate to the order of magnitude estimate that we are interested in
+here. The stacked surface brightness profiles in
+\cite{2005MNRAS.358..949Z} are measured at redshift $z \sim 0.25$ with
+an average mass of the clusters of $4.0\times10^{13}\,\msun$. The
+profiles are build up out of three components; diffuse intracluster
+light (ICL), galaxies, and the brightest cluster galaxy (BCG) in the
+center of clusters. However, the total volume overlap of the ISM to
+the cluster is very small compared to the ICL- and BCG overlap with
+the cluster, thus the relative contribution of the galaxies to the IC
+emission is suppressed. To remove this bias we cut out the galaxies
+that have been smoothed over the cluster in the stacked analysis. In
+Fig.~\ref{fig:SD_spatial} we show the SDSS stacked brightness profiles
+as well as the fitted profiles\footnote{The measured brightness is
+  converted into units of $\rmn{erg}\,\rmn{s}^{-1}$ using
+  \cite{2010...book} $S(\rmn{mag}\,''^{-2}) =
+  \mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})$,
+  where the sun's absolute magnitude in the $r$-band is given by
+  $\mathcal{M}_\odot=27.1$ \cite{1998gaas.book.....B} and the
+  luminosity of the sun by $L_\odot=3.85\,10^{33}
+  \rmn{erg}\,\rmn{s}^{-1}$.}, both scaled with the unitless $\rvir$
+normalized area to resembele the expected luminosity at radius
+$r$. Our benchmark spatial model is shown with the solid black line,
+and include the contribution from the ICL and BCG.
+
+Instead of modelling the surface brightness with a de Vaucouleur
+profile with the addition of a power-law, we use a double beta profile
+model for simplicity of deprojection given by:
+\begin{equation}
+S_\sd (r_\bot)= \sum_{i=1}^2 \,S_i\, 
+\left[1 + \left( \frac{r_\bot}{r_{\mathrm{c}_i}}\right)^2\right]
+^{-3\beta_i + 1/2}\,,
+\label{double_beta}
+\end{equation}
+where we found the following best fitted central brightness ($S_i$),
+core radius ($r_{\mathrm{c}_i}$), and slope ($\beta_i$):
+\begin{eqnarray}
+ S_1&=&5.0\times10^{-6}\,\rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1},\,
+r_{\mathrm{c}_1}=130\,\rmn{kpc},\,
+\beta_1=0.54\nonumber\\
+ S_2&=&3.9\times10^{-3}\,\rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1},\,
+r_{\mathrm{c}_2}=2.8\,\rmn{kpc},\,
+\beta_2=0.53\,.\nonumber\\
+\label{fit_spatial_IR}
+\end{eqnarray}
+The 3D spatial profile is derived by deprojecting the surface
+brightness in Eq.~(\ref{double_beta}) (see
+e.g. \cite{2004A&A...413...17P} for details about the deprojection):
+\begin{eqnarray}
+  j(r)  = \sum_{i=1}^2 \frac{S_i}{2\pi\,r_{\mathrm{c}_i}}\,
+  \frac{6 \beta_i - 1}{\left(1 + r^2/r^2_{\mathrm{c}_i}\right)^{3\beta_i}}\,
+  \mathcal{B}\left(\frac{1}{2},3\beta_i\right)\,,
+\end{eqnarray}
+where $\mathcal{B}(a,b)$ denotes the beta-function
+\cite{1965hmfw.book.....A}.
+
+{\it Spectral distribution -- stars and dust} \\ Our goal in this
+section is to derive a simple spectral model for SD in galaxy
+clusters. Since the radiation from galaxies are expected to leak out
+into the ICM, we expect similar spectral distributions, at least to
+the order of magnitude that we are interested in here. Hence, we use
+the IR to UV spectrum derived in \cite{2006ApJ...648L..29P} for a MW
+type galaxy to characterize the spectral distribution of light from SD
+in a cluster. Note, however, that we only keep the spectral shape, and
+renormalize the spectral distribution using the luminosity from SD.
+
+In Fig.~\ref{fig:SD_spectra} we show the spectral distribution of the
+light from SD together with the CMB black-body distribution in a
+galaxy cluster, both at the radius $r=0.071\rvir$ where the energy
+density of the smooth light from SD (see Fig.~\ref{fig:SD_Edens})
+equals the energy density of the CMB. We have renormalized both the
+spectral data and the fitted spectra using the luminosity from stars
+and dust individually (see the normalization section below for further
+details).
+
+We choose to fit the spectrum of the dust that peaks at about
+$10^{-2}\,\ev$ with a double power-law, and the slightly wider
+spectral distribution of the stars that peaks at about $1\,\ev$ with a
+tipple power-law. We find the best fit spectra for the SD in a
+cluster through:
+\begin{eqnarray}
+  \eph^2\frac{\dd^2 N_\ph}{\dd \eph \dd V}
+  &\equiv& u_\sd(\eph) =  \sum_i N_i(\lx) u_i^\gal(\eph)\,,\nonumber \\ 
+\rmn{where}\quad i&=&\{\rmn{stars,dust}\} \qquad \rmn{and}\\ 
+% &=&  N_\dust(\lx) u_\dust^\gal(\eph) + N_\stars(\lx) u_\stars^\gal(\eph)  \nonumber \\ 
+%  \\
+  u_\stars^\gal(\eph) &=& \frac{23\,\rmn{eV}}{\rmn{cm}^3} 
+  \left(\frac{1.23\,\rmn{eV}}{\eph}\right)^{1.9} \nonumber \\
+  &\times&\left[1+\left(\frac{2.04\,\rmn{eV}}{\eph}\right)^{20}\right]
+  ^{-\frac{1.9}{20}}\nonumber \\
+  &\times& \left[1+\left(\frac{0.78\,\rmn{eV}}{\eph}\right)^{20}\right]^{-\frac{2.6}{20}}\,, \\
+  u_\dust^\gal(\eph) &=& 
+  \frac{40\,\rmn{eV}}{\rmn{cm}^3} 
+  \left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{4.9}\nonumber \\
+  &\times& \left[1+\left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{1.9}\right]^{-4.9}\,.
+\end{eqnarray}
+
+{\it Normalization}\\ The spatial and spectral distribution functions
+of the light from SD in a cluster are both normalized with a constant
+determined from the luminosity in each respective wavelength. The
+specific energy density is given by
+\begin{eqnarray} 
+u_\sd(\eph, r) &=& \frac{j(r)}{j(0)}\,u_\sd(\eph) \nonumber\\
+&=& \frac{j(r)}{j(0)}\,\sum_i N_i(\lx) u_i^\gal(\eph)\,,
+\end{eqnarray}
+where we fix the unitless normalization $N_i(\lx)$ using the total
+energy of the light in SD  within $\rvir$:
+\begin{eqnarray} 
+  E_{i,\vir} &=& L_i \frac{\rvir}{c} \nonumber \\
+  &=&N_i(\lx)\int_{\rvir} \int_i \,\frac{j(r)}{j(0)} 
+  \frac{u_i^\gal(\eph)}{\eph}\,\dd V\dd \eph\,,\nonumber \\
+ \rmn{for}\quad i&=&\{\rmn{stars,dust}\}\,.
+\label{eq:E_SD}
+\end{eqnarray}
+Here we approximate the total energy of the photons within $\rvir$
+($E_{i,\vir}$) with the luminosity $L_i$ \cite{2008A&A...490..547G}
+times the typical timescale it takes for a photon to propagate through
+the cluster (we assume that the cluster is optically thin). Once we
+derived the SD luminosities for a well representative cluster, we use
+a IR to X-ray scaling relation to estimate the luminosity from an
+arbitrary cluster:
+\begin{equation}
+L_\ir=1.05\times10^{45}\,\rmn{erg\,s}^{-1}\,
+\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,,
+\label{eq:SD-X}
+\end{equation}
+where $\lx$ is the luminosity of the X-ray emitting gas within
+$\rvir$.
+
+The normalization constant for the starlight $N_\stars(\lx)$ is derived
+in the following three steps: (1) We use the average apparent magnitude
+in the $(r+i)$-band $m_{(r+i),0.25}\approx 15.5$
+\cite{2005MNRAS.358..949Z} of a cluster with the average mass
+$\mvir=4.0\times10^{13}\msun$ at a redshift $z=0.25$ to derive the
+luminosity from the stars:
+\begin{equation}
+L_\stars=10^{\frac{m_\odot-m_{(r+i),0.25}}{2.5}}
+\left(\frac{D_\clu}{D_\odot}\right)^2 L_\odot
+\approx 7.1\times10^{44}\,\rmn{erg}\,\rmn{s}^{-1}\,,
+\label{eq:L_star}
+\end{equation}
+where the apparent magnitude of the sun $m_\odot\approx -27.1$, the
+distance to the sun $D_\odot=4.85\times10^{-6}\,\rmn{pc}$, the
+luminosity of the sun $L_\odot=3.85\times10^{33}\,\rmn{erg\,s}^{-1}$,
+and the distance to the cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. (2)
+We use the IR to X-ray scaling relation in Eq.~(\ref{eq:SD-X}) to derive
+a more general form of the luminosity from stars in
+Eq.~(\ref{eq:L_star}) that is valid for an arbitrary cluster mass. The
+cluster X-ray luminosities are found in the extended HIFLUGCS
+catalogue \cite{2002ApJ...567..716R} to which we have added the Virgo
+cluster. (3) The normalization constant for the stars is
+determined from the above steps together with Eq.~(\ref{eq:E_SD})
+where we integrate over the cluster volume and spectral distribution
+of the stars. It is given by
+\begin{equation}
+ N_\stars(\lx) = 1.2\times10^{-9}\,
+\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,.
+\label{eq:N_stars}
+\end{equation}
+Note that since the luminosities include the contribution from
+galaxies, we have integrated the spatial distribution including
+galaxies to derive the normalization. Once the normalization is fixed,
+the SD energy densities are derived from the spatial distribution
+where galaxies have been excluded.
+
+The normalization constant for the dust $N_\dust(\lx)$ is derived in the
+following four steps: (1) We use a cluster with the the average mass
+$\mvir=4.0\times10^{13}\msun$ and estimate the X-ray luminosity from
+the X-ray to mass scaling relations derived for the Representative
+XMM-Newton Cluster Structure Survey (REXCESS) in
+\cite{2009A&A...498..361P}:
+\begin{equation}
+\lx=1.18\times 10^{44}\,\rmn{erg\,s}^{-1}
+\left(\frac{M_{200}}{10^{14}\msun}\right)^{1.81}\,,
+\end{equation}
+where we have used that $M_\rmn{200} \approx 1.58\,M_\rmn{500}$ for a
+small cluster \footnote{We derive the factor 1.58 using
+  $M_\rmn{200}/M_\rmn{500}$ for the clusters in the HIFLUGCS catalogue
+  with a mass similar to $\mvir=4.0\times10^{13}\msun$ that we use to
+  derive the luminosity from dust.}. (2) From the IR to X-ray scaling
+relation in Eq.~(\ref{eq:SD-X}) we can now estimate calculate the
+luminosity from the dust for a $\mvir=4.0\times10^{13}\msun$ cluster;
+$L_\dust=4.7\times10^{44}\,\rmn{erg\,s}^{-1}$. (3) We generalize
+Eq.~(\ref{eq:L_star}) to an arbitrary cluster mass using
+Eq.~(\ref{eq:SD-X}) together with the cluster X-ray luminosities in
+the extended HIFLUGCS catalogue. (4) The normalization constant for
+the dust can now be determined from from the above steps together with
+Eq.~(\ref{eq:E_SD}) where we integrate over the cluster volume and
+spectral distribution of the dust. It is given by
+\begin{equation}
+ N_\dust(\lx) = 1.4\times10^{-9}\,
+\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,.
+\label{eq:N_dust}
+\end{equation}
+Note that since the luminosities include the contribution from
+galaxies, we have integrated the spatial distribution including
+galaxies to derive the normalization. Once the normalization is fixed,
+the SD energy densities are derived from the spatial distribution
+where galaxies have been excluded.
+
+{\it Energy density}\\ The spatial distribution of the SD energy
+density is an important quantity since it impacts the steady state
+electron and positron spectra through cooling. A higher density of SD
+in a cluster suppresses the spectra of the upscattering particles. With
+the formalism presented above, we can now derive the energy density
+from starlight and dust in a galaxy cluster through
+\begin{eqnarray}
+\label{eq:U_SD}
+u_\sd(r) &=& \int \dd \eph \frac{\dd^2 N_\ph}{\dd \eph \dd V}\,\eph
+=\int \dd \eph \frac{u_\sd(\eph, r)}{\eph}
+\nonumber \\
+&=&  \frac{j(r)}{j(0)}  \int \dd \eph \sum_i 
+N_i(\lx) \frac{u_i^\gal(\eph)}{\eph}\,. \nonumber \\
+\end{eqnarray}
+In Fig.~\ref{fig:SD_Edens} we compare the energy densities from
+different radiation fields in a galaxy cluster with the mass
+$\mvir=4.0\times10^{13}\msun$. We use two different profiles for the
+SD energy density, where the total profile includes the contribution
+from the ICL, the BCG and all the galaxies, while the galaxies are
+excluded in the smooth profile. We find that even for a cluster with a
+relative small mass the energy density of the SD components dominates
+over the CMB and the magnetic fields (with a central B field of 3~$\mu
+G$) within about 10\% of $\rvir$. Outside this radius the CMB is
+dominating the energy density of the cluster, hence the magnetic
+fields are always subdominant in the cluster and can safely be removed
+from cluster IC calculations for a reasonable central B-field and
+spectral index. Note that in this work we keep the contribution
+from B-fields to the total energy density for consistency.
+
+%***********************************************
 

### 2011-04-07 paper.tex
population studies almost finished

--- 2011-04-06 paper.tex
@@
 \begin{eqnarray}
+\label{eq:LP_scaling}
 L_{\gamma,\rmn{LP}} &=& L_{\gamma,\rmn{smLP}} \B_\rmn{LP} \propto \mvir^{0.73}\qquad
 \,\,\,\,\,\,\rmn{and}\\
+\label{eq:BM_scaling}
 L_{\gamma,\rmn{BM}} &=& L_{\gamma,\rmn{smBM}} \B_\rmn{BM} \propto  \mvir^{1.06}\,,\qquad
@@
 \section{Predictions and observational limits}
-Model predictions
-
-\begin{figure}
-  \includegraphics[width=0.99\columnwidth]{figures/MLscaling.eps}
-  \caption{\it Lum-scaling relations, mass dependence of SD cooling
-    have been neglected, actually a factor few difference for
-    groups. factor 2 for Fornax, and small difference for large
-    clusters}
+
+In this section, we compute the expected $\gamma$-ray fluxes from DM
+annihilation and CR interactions of the brightest clusters of the X-ray flux
+complete sample in the local universe. We confront these predictions to upper
+limits obtained by Fermi 1.5-year data and conclude on the viability of the
+underlying models and perspectives for the next years of Fermi observations.
+
+\begin{figure*}
+  \includegraphics[width=0.99\columnwidth]{figures/MLscaling.100M.eps}
+  \includegraphics[width=0.99\columnwidth]{figures/MLscaling.10G.eps}
+  \caption{\it Scaling relations of the cluster's virial mass $M_{200}$ and the
+    $\gamma$-ray luminosity for energies $E_\gamma>100$~MeV (left) and
+    $E_\gamma>10$~GeV (right).  Shown are the relations for the CR-induced
+    emission that is dominated by pion decay resulting from hadronic CR
+    interactions (solid), the leptophilic model of DM annihilations that
+    includes the scaling of the substructure and Sommerfeld boost factors with
+    custer mass from Equation~(\ref{eq:LP_scaling}) (dash-dotted) as well as the
+    benchmark model $K'$ of DM annihilation that includes the scaling of the
+    substructure boost with cluster mass of Equation~(\ref{eq:BM_scaling})
+    (dashed). Note that the scaling of this particular benchmark model is
+    indicative for all (non-Sommerfeld enhanced) DM annihilation models while
+    the normalization depends on the particular cross-section and neyralino
+    masses.}
 \label{fig:lum_mass_scaling}
-\end{figure}
+\end{figure*}
+
+First we focus on $\gamma$-ray flux-cluster mass scaling relations for DM
+annihilation and CR induced emission in Fig.~\ref{fig:lum_mass_scaling}.  The
+mass scaling of the substructure boost steepens the intrinsically shallower DM
+annihilation relation of benchmark models (Equation~(\ref{eq:BM_scaling})) while
+this steepening is in fact over-compensated by the inverse mass scaling of the
+Sommerfeld boost in leptophilic models that prefers smaller halos with a larger
+ratio of $c/v_\mathrm{circ}$ (Equation~(\ref{eq:LP_scaling})). In contrast, the
+CR scaling relation is considerably steeper as shown by reference
+\cite{2010MNRAS.409..449P}. [ANDERS: add CR scaling formula] This implies
+already a general strategy to minimize the CR-induced foreground for DM
+annihilation and argues for very nearby groups. We note that these simulations
+do not include AGn feedback that is thought to furthermore reduce the baryon
+fraction in groups relative to that in clusters \cite{2008ApJ...687L..53P}. The
+resulting smaller target density for hadronic CR interactions will furthermore
+steepen the $L_\gamma-M$ relation of CR induced emission, making the case for
+groups even stronger.
 
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.DM.eps}
-  \caption{\it Fermi flux upper limits contrasted to the predicted DM
-    gamma-ray flux. We show the mean differential flux in the energy
-    range $E_\gamma=1-10$~GeV for 32 clusters. The Fermi-LAT upper
-    limits are shown with black arrows. The predicted fluxes are
-    derived from both a leptophilic DM model that result in inverse
-    Compton upscattered CMB photons (red), and the continuum emission
-    from the DM $\Kp$ benchmark model (blue). The leptophilic fluxes
-    are ruled out by 14 of the clusters, with the strongest
-    constraints set by Fornax and M49. We can not constrain the
-    benchmark models, although our predictions are approaching the
-    upper limits.}
+  \caption{\it Fermi flux upper limits are contrasted to the predicted DM
+    gamma-ray flux. We show the mean differential flux in the energy range
+    $E_\gamma=1-10$~GeV for 32 clusters. The Fermi-LAT upper limits are shown
+    with black arrows. The predicted fluxes are derived from the dominant
+    inverse Compton-scattering of CMB photons in a leptophilic DM model (red),
+    and the continuum emission from the DM $\Kp$ benchmark model
+    (blue). Assuming a boost factor due to substructures that has a mass
+    spectrum extending down to Earth masses, the expected leptophilic fluxes are
+    ruled out by lower upper limits in 14 of the clusters, with the strongest
+    constraints set by Fornax and M49. We can not yet constrain the benchmark
+    models, although our predictions are approaching the upper limits and will
+    allow to test these in the upcoming years with better data.}
  \label{fig14}
@@
 \end{figure*}
- difficult to detect DM without a Sommerfeld boost with Cherenkov
- telescopes since the boost from substructures is extended while the
- sensitivity of Cherenkov telescopes drops linearly with radius
- outside the point spread function (CHECK)
-
-we rule out the leptophilic models in present form in 14 clusters,
- and limit the boost from Sommerfeld enhancement in the MW to less
- than 10
-
-mention prime cluster candidates, LP under pressure, Fornax start
-being constraining, since only few clusters close to UL stacking will
-not increase the DM limits much
+
+Figure~\ref{fig14} compares Fermi upper limits on the $\gamma$-ray flux with
+predictions of DM annihilation fluxes in the leptophilic and benchmark models.
+To obtain the $\gamma$-ray fluxes, we scale the virial mass of clusters in the
+extended HIFLUGCS catalogue \cite{2002ApJ...567..716R} with our scaling
+relations of Equations~(\ref{eq:BM_scaling}) and (\ref{eq:LP_scaling}).  We
+assume a boost factor due to substructures that has a constant contribution per
+decade in substructure mass and has a mass spectrum extending down to Earth
+masses. Fermi limits rule out the leptophilic models in their present form with
+the mentioned assumptions in 14 clusters, and limit the boost from Sommerfeld
+enhancement to less than 4 [?] in Fornax. Assuming universality, this limits the
+Sommerfeld boost in the MW to less than 10 (see Fig.~\ref{fig:boost_const}).
+The flux level of the Fermi limits are an indirect measure of the ambient
+background flux in the $\gamma$-ray sky and/or the presence of strong point
+sources such as AGN in the immediate vicinity of the cluster position. Hence, the ratio of
+the Fermi upper limits to the predicted annihilation fluxes,
+$F_{\mathrm{UL}}/F_{\mathrm{scal}}$, is a good indication of the best cluster
+candidates for indirect DM experiments. We identify Fornax, M49, NGC4636, and
+Virgo to be prime candidates. Note however, that Virgo extends of $7\deg$ over
+the sky which implies a lower surface brightness and lower signal-to-noise.
+Fermi limits on individual clusters are expected to improve as $\sqrt{T/1.5
+  \mathrm{yr}}$, where $T$ is the total elapsed time of the Fermi mission. We
+emphasize that the very inhomogeneous distribution of $F_{\mathrm{UL}}/
+F_{\mathrm{scal}}$ makes it unlikely to dramatically improve the limits through
+a stacking analysis as the weak signal will dilute the average constraints.
+Assuming the projected sensitivity of the future Cherenkov telescope array (CTA)
+of [ANDERS: value?], we note that it will be difficult to detect the DM
+annihilation signal from clusters without a Sommerfeld boost by Cherenkov
+telescopes. This is because the boost from substructures is extended while the
+sensitivity of Cherenkov telescopes drops linearly with radius outside the point
+spread function.
 
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.CR.diff.eps}
-  \caption{\it Fermi-LAT flux upper limits contrasted to the
-    predictions by the semi-analytic Pinzke and Pfrommer model for CRp
-    induced gamma-ray emission. We show the mean differential flux in
-    the energy range $E_\gamma=1-10$~GeV for 32 clusters. The Fermi
-    upper limits are shown with black arrows. The blue boxes show the
-    gamma-ray emission from CRp induced $\pi^0$\:s decaying, where the
-    upper bound shows the estimates for an optimistic model and the
-    lower bound a more conservative model excluding point sources (the
-    realistic case is more likely in between, see
-    \cite{2010MNRAS.409..449P} for details). Note that there is
-    currently no tension between our predictions and upper limits from
-    Fermi, although Virgo, Norma, and Coma are close and will in the
-    coming years enforce constraints on the hadronic models.}
+  \caption{\it Fermi-LAT flux upper limits are contrasted to the predictions by
+    the semi-analytic Pinzke and Pfrommer model for CRp induced gamma-ray
+    emission. We show the mean differential flux in the energy range
+    $E_\gamma=1-10$~GeV for 32 clusters. The Fermi upper limits are shown with
+    black arrows. The blue boxes show the gamma-ray emission from CRp induced
+    $\pi^0$-decay, where the upper bound shows the estimates for an optimistic
+    model and the lower bound a more conservative model excluding point sources
+    (note that both models assume the maximally allowed acceleration efficiency
+    for strong shocks and most likely will have to be corrected down, see
+    \cite{2010MNRAS.409..449P} for details). Note that there is currently no
+    tension between our predictions and upper limits from Fermi, although Virgo,
+    Norma, and Coma are coming close and will enforce constraints on the
+    hadronic models in the coming years.}
  \label{fig15}
@@
 AGN M87, effective area better in 1 GeV range
+
+\begin{figure*}%[t]
+\begin{minipage}{2.0\columnwidth}
+ \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.CR.eps}
+ \caption{\it Comparison of the gamma-ray flux induced by CRps for the 106
+   clusters included in the extended HIFLUGCS catalogue. The fluxes are
+   calculated within $\rvir$, and are derived using a single beta profile for
+   each cluster's gas density profile as obtained by ROSAT X-ray
+   observations. The CR distribution follows the semi-analytically model derived
+   by hydrodynamical cosmological cluster simulations \cite{2010MNRAS.409..449P}
+   (see text for details). The upper panel shows the energy integrated flux
+   above 100~MeV (left side) and above 100~GeV (right side), both as a function
+   of HIFLUGCS cluster ID. The eight brightest clusters are labelled. The lower
+   panel shows the relative difference between the gamma-ray flux predicted by
+   the mass-luminosity scaling relation and to the flux computed using the
+   semi-analytical model \cite{2010MNRAS.409..449P}. The name of the clusters
+   with the largest offset are printed out, which correlate with cool core
+   clusters.}
+ \label{fig19}
+\end{minipage}
+\end{figure*}
+ best clusters, stacking unlikely to improve
+
+if CC, then skewed towards large X-ray fluxes; X-ray emission good
+proxies for gamma-ray emission --) The dust turns up at about a factor
+100 lower than the stars --) The other figure show the spectral shape
+of the IC-star with the same spectral shape as the dust, it shows the
+same gamma-ray slope as the dust --) The reason why there is only a
+factor 10 difference in the break in the gamma-ray emission between
+the star and dust is related to the KN. In our CRp paper, the last
+figure shows that at $\eg=100\,\tev$, the spectra is suppressed with
+about a factor 10 (also depends on $\alpha_\e$). Since the dust
+photons have a factor 10 higher energy, I expect this suppression at
+about 10~TeV. For star photons the suppression should be at
+100~GeV. So the star photons are definitely KN suppressed, which
+explains the earlier break and the steeper slope.
 
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.CR.eps}
-\caption{\it Comparing the flux from clusters in the extended HIFLUGCS
-  catalogue. We show the energy integrated gamma-ray flux induced by
-  CRps for the 106 clusters included in the extended HIFLUGCS
-  catalogue. The fluxes are calculated within $\rvir$, and are derived
-  using a single beta profile for each cluster's gas density profile
-  (see text for details). The upper panel show the energy integrated
-  flux above 100~MeV (left side) and above 100~GeV (right side), both
-  as a function of HIFLUGCS cluster ID. The name of the eight
-  brightest clusters are written out. The lower panel show the
-  relative difference between the gamma-ray flux predicted by
-  mass-luminosity scaling relations compared to the flux computed
-  using the semi-analytically model \cite{2010MNRAS.409..449P}. The
-  name of the clusters with the largest offset are printed out, which
-  correlate with cool core clusters.}
- \label{fig19}
-\end{minipage}
-\end{figure*}
-if CC, then skewed towards large X-ray fluxes; X-ray emission good
-proxies for gamma-ray emission --) The dust turns up at about a factor
-100 lower than the stars --) The other figure show the spectral shape
-of the IC-star with the same spectral shape as the dust, it shows the
-same gamma-ray slope as the dust --) The reason why there is only a
-factor 10 difference in the break in the gamma-ray emission between
-the star and dust is related to the KN. In our CRp paper, the last
-figure shows that at $\eg=100\,\tev$, the spectra is suppressed with
-about a factor 10 (also depends on $\alpha_\e$). Since the dust
-photons have a factor 10 higher energy, I expect this suppression at
-about 10~TeV. For star photons the suppression should be at
-100~GeV. So the star photons are definitely KN suppressed, which
-explains the earlier break and the steeper slope.
-
-\begin{figure*}%[t]
-\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.DM.eps}

### 2011-04-07 paper.tex

@@
 
+{\it Spatial distribution -- stars and dust}\\ Our goal in this
+section is to derive a simple spatial model for the distribution of SD
+in galaxy clusters. For this reason we use stacked cluster
+observations by Sloan in the $r$-band that trace the stars. We assume
+that the dust trace the stars in the clusters, which should be
+accurate to the order of magnitude estimate that we are interested in
+here. The stacked surface brightness profiles in
+\cite{2005MNRAS.358..949Z} are measured at redshift $z \sim 0.25$ with
+an average mass of the clusters of $4.0\times10^{13}\,\msun$. The
+profiles are build up out of three components; diffuse intracluster
+light (ICL), galaxies, and the brightest cluster galaxy (BCG) in the
+center of clusters. However, the total volume overlap of the ISM to
+the cluster is very small compared to the ICL- and BCG overlap with
+the cluster, thus the relative contribution of the galaxies to the IC
+emission is suppressed. To remove this bias we cut out the galaxies
+that have been smoothed over the cluster in the stacked analysis. In
+Fig.~\ref{fig:SD_spatial} we show the SDSS stacked brightness profiles
+as well as the fitted profiles\footnote{The measured brightness is
+  converted into units of $\rmn{erg}\,\rmn{s}^{-1}$ using
+  \cite{2010...book} $S(\rmn{mag}\,''^{-2}) =
+  \mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})$,
+  where the sun's absolute magnitude in the $r$-band is given by
+  $\mathcal{M}_\odot=27.1$ \cite{1998gaas.book.....B} and the
+  luminosity of the sun by $L_\odot=3.85\,10^{33}
+  \rmn{erg}\,\rmn{s}^{-1}$.}, both scaled with the unitless $\rvir$
+normalized area to resembele the expected luminosity at radius
+$r$. Our benchmark spatial model is shown with the solid black line,
+and include the contribution from the ICL and BCG.
+
+Instead of modelling the surface brightness with a de Vaucouleur
+profile with the addition of a power-law, we use a double beta profile
+model for simplicity of deprojection given by:
+\begin{equation}
+S_\sd (r_\bot)= \sum_{i=1}^2 \,S_i\, 
+\left[1 + \left( \frac{r_\bot}{r_{\mathrm{c}_i}}\right)^2\right]
+^{-3\beta_i + 1/2}\,,
+\label{double_beta}
+\end{equation}
+where we found the following best fitted central brightness ($S_i$),
+core radius ($r_{\mathrm{c}_i}$), and slope ($\beta_i$):
+\begin{eqnarray}
+ S_1&=&5.0\times10^{-6}\,\rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1},\,
+r_{\mathrm{c}_1}=130\,\rmn{kpc},\,
+\beta_1=0.54\nonumber\\
+ S_2&=&3.9\times10^{-3}\,\rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1},\,
+r_{\mathrm{c}_2}=2.8\,\rmn{kpc},\,
+\beta_2=0.53\,.\nonumber\\
+\label{fit_spatial_IR}
+\end{eqnarray}
+The 3D spatial profile is derived by deprojecting the surface
+brightness in Eq.~(\ref{double_beta}) (see
+e.g. \cite{2004A&A...413...17P} for details about the deprojection):
+\begin{eqnarray}
+  j(r)  = \sum_{i=1}^2 \frac{S_i}{2\pi\,r_{\mathrm{c}_i}}\,
+  \frac{6 \beta_i - 1}{\left(1 + r^2/r^2_{\mathrm{c}_i}\right)^{3\beta_i}}\,
+  \mathcal{B}\left(\frac{1}{2},3\beta_i\right)\,,
+\end{eqnarray}
+where $\mathcal{B}(a,b)$ denotes the beta-function
+\cite{1965hmfw.book.....A}.
+
+{\it Spectral distribution -- stars and dust} \\ Our goal in this
+section is to derive a simple spectral model for SD in galaxy
+clusters. Since the radiation from galaxies are expected to leak out
+into the ICM, we expect similar spectral distributions, at least to
+the order of magnitude that we are interested in here. Hence, we use
+the IR to UV spectrum derived in \cite{2006ApJ...648L..29P} for a MW
+type galaxy to characterize the spectral distribution of light from SD
+in a cluster. Note, however, that we only keep the spectral shape, and
+renormalize the spectral distribution using the luminosity from SD.
+
+In Fig.~\ref{fig:SD_spectra} we show the spectral distribution of the
+light from SD together with the CMB black-body distribution in a
+galaxy cluster, both at the radius $r=0.071\rvir$ where the energy
+density of the smooth light from SD (see Fig.~\ref{fig:SD_Edens})
+equals the energy density of the CMB. We have renormalized both the
+spectral data and the fitted spectra using the luminosity from stars
+and dust individually (see the normalization section below for further
+details).
+
+We choose to fit the spectrum of the dust that peaks at about
+$10^{-2}\,\ev$ with a double power-law, and the slightly wider
+spectral distribution of the stars that peaks at about $1\,\ev$ with a
+tipple power-law. We find the best fit spectra for the SD in a
+cluster through:
+\begin{eqnarray}
+  \eph^2\frac{\dd^2 N_\ph}{\dd \eph \dd V}
+  &\equiv& u_\sd(\eph) =  \sum_i N_i(\lx) u_i^\gal(\eph)\,,\nonumber \\ 
+\rmn{where}\quad i&=&\{\rmn{stars,dust}\} \qquad \rmn{and}\\ 
+% &=&  N_\dust(\lx) u_\dust^\gal(\eph) + N_\stars(\lx) u_\stars^\gal(\eph)  \nonumber \\ 
+%  \\
+  u_\stars^\gal(\eph) &=& \frac{23\,\rmn{eV}}{\rmn{cm}^3} 
+  \left(\frac{1.23\,\rmn{eV}}{\eph}\right)^{1.9} \nonumber \\
+  &\times&\left[1+\left(\frac{2.04\,\rmn{eV}}{\eph}\right)^{20}\right]
+  ^{-\frac{1.9}{20}}\nonumber \\
+  &\times& \left[1+\left(\frac{0.78\,\rmn{eV}}{\eph}\right)^{20}\right]^{-\frac{2.6}{20}}\,, \\
+  u_\dust^\gal(\eph) &=& 
+  \frac{40\,\rmn{eV}}{\rmn{cm}^3} 
+  \left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{4.9}\nonumber \\
+  &\times& \left[1+\left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{1.9}\right]^{-4.9}\,.
+\end{eqnarray}
+
+{\it Normalization}\\ The spatial and spectral distribution functions
+of the light from SD in a cluster are both normalized with a constant
+determined from the luminosity in each respective wavelength. The
+specific energy density is given by
+\begin{eqnarray} 
+u_\sd(\eph, r) &=& \frac{j(r)}{j(0)}\,u_\sd(\eph) \nonumber\\
+&=& \frac{j(r)}{j(0)}\,\sum_i N_i(\lx) u_i^\gal(\eph)\,,
+\end{eqnarray}
+where we fix the unitless normalization $N_i(\lx)$ using the total
+energy of the light in SD  within $\rvir$:
+\begin{eqnarray} 
+  E_{i,\vir} &=& L_i \frac{\rvir}{c} \nonumber \\
+  &=&N_i(\lx)\int_{\rvir} \int_i \,\frac{j(r)}{j(0)} 
+  \frac{u_i^\gal(\eph)}{\eph}\,\dd V\dd \eph\,,\nonumber \\
+ \rmn{for}\quad i&=&\{\rmn{stars,dust}\}\,.
+\label{eq:E_SD}
+\end{eqnarray}
+Here we approximate the total energy of the photons within $\rvir$
+($E_{i,\vir}$) with the luminosity $L_i$ \cite{2008A&A...490..547G}
+times the typical timescale it takes for a photon to propagate through
+the cluster (we assume that the cluster is optically thin). Once we
+derived the SD luminosities for a well representative cluster, we use
+a IR to X-ray scaling relation to estimate the luminosity from an
+arbitrary cluster:
+\begin{equation}
+L_\ir=1.05\times10^{45}\,\rmn{erg\,s}^{-1}\,
+\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,,
+\label{eq:SD-X}
+\end{equation}
+where $\lx$ is the luminosity of the X-ray emitting gas within
+$\rvir$.
+
+The normalization constant for the starlight $N_\stars(\lx)$ is derived
+in the following three steps: (1) We use the average apparent magnitude
+in the $(r+i)$-band $m_{(r+i),0.25}\approx 15.5$
+\cite{2005MNRAS.358..949Z} of a cluster with the average mass
+$\mvir=4.0\times10^{13}\msun$ at a redshift $z=0.25$ to derive the
+luminosity from the stars:
+\begin{equation}
+L_\stars=10^{\frac{m_\odot-m_{(r+i),0.25}}{2.5}}
+\left(\frac{D_\clu}{D_\odot}\right)^2 L_\odot
+\approx 7.1\times10^{44}\,\rmn{erg}\,\rmn{s}^{-1}\,,
+\label{eq:L_star}
+\end{equation}
+where the apparent magnitude of the sun $m_\odot\approx -27.1$, the
+distance to the sun $D_\odot=4.85\times10^{-6}\,\rmn{pc}$, the
+luminosity of the sun $L_\odot=3.85\times10^{33}\,\rmn{erg\,s}^{-1}$,
+and the distance to the cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. (2)
+We use the IR to X-ray scaling relation in Eq.~(\ref{eq:SD-X}) to derive
+a more general form of the luminosity from stars in
+Eq.~(\ref{eq:L_star}) that is valid for an arbitrary cluster mass. The
+cluster X-ray luminosities are found in the extended HIFLUGCS
+catalogue \cite{2002ApJ...567..716R} to which we have added the Virgo
+cluster. (3) The normalization constant for the stars is
+determined from the above steps together with Eq.~(\ref{eq:E_SD})
+where we integrate over the cluster volume and spectral distribution
+of the stars. It is given by
+\begin{equation}
+ N_\stars(\lx) = 1.2\times10^{-9}\,
+\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,.
+\label{eq:N_stars}
+\end{equation}
+Note that since the luminosities include the contribution from
+galaxies, we have integrated the spatial distribution including
+galaxies to derive the normalization. Once the normalization is fixed,
+the SD energy densities are derived from the spatial distribution
+where galaxies have been excluded.
+
+The normalization constant for the dust $N_\dust(\lx)$ is derived in the
+following four steps: (1) We use a cluster with the the average mass
+$\mvir=4.0\times10^{13}\msun$ and estimate the X-ray luminosity from
+the X-ray to mass scaling relations derived for the Representative
+XMM-Newton Cluster Structure Survey (REXCESS) in
+\cite{2009A&A...498..361P}:
+\begin{equation}
+\lx=1.18\times 10^{44}\,\rmn{erg\,s}^{-1}
+\left(\frac{M_{200}}{10^{14}\msun}\right)^{1.81}\,,
+\end{equation}
+where we have used that $M_\rmn{200} \approx 1.58\,M_\rmn{500}$ for a
+small cluster \footnote{We derive the factor 1.58 using
+  $M_\rmn{200}/M_\rmn{500}$ for the clusters in the HIFLUGCS catalogue
+  with a mass similar to $\mvir=4.0\times10^{13}\msun$ that we use to
+  derive the luminosity from dust.}. (2) From the IR to X-ray scaling
+relation in Eq.~(\ref{eq:SD-X}) we can now estimate calculate the
+luminosity from the dust for a $\mvir=4.0\times10^{13}\msun$ cluster;
+$L_\dust=4.7\times10^{44}\,\rmn{erg\,s}^{-1}$. (3) We generalize
+Eq.~(\ref{eq:L_star}) to an arbitrary cluster mass using
+Eq.~(\ref{eq:SD-X}) together with the cluster X-ray luminosities in
+the extended HIFLUGCS catalogue. (4) The normalization constant for
+the dust can now be determined from from the above steps together with
+Eq.~(\ref{eq:E_SD}) where we integrate over the cluster volume and
+spectral distribution of the dust. It is given by
+\begin{equation}
+ N_\dust(\lx) = 1.4\times10^{-9}\,
+\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,.
+\label{eq:N_dust}
+\end{equation}
+Note that since the luminosities include the contribution from
+galaxies, we have integrated the spatial distribution including
+galaxies to derive the normalization. Once the normalization is fixed,
+the SD energy densities are derived from the spatial distribution
+where galaxies have been excluded.
+
+{\it Energy density}\\ The spatial distribution of the SD energy
+density is an important quantity since it impacts the steady state
+electron and positron spectra through cooling. A higher density of SD
+in a cluster suppresses the spectra of the upscattering particles. With
+the formalism presented above, we can now derive the energy density
+from starlight and dust in a galaxy cluster through
+\begin{eqnarray}
+\label{eq:U_SD}
+u_\sd(r) &=& \int \dd \eph \frac{\dd^2 N_\ph}{\dd \eph \dd V}\,\eph
+=\int \dd \eph \frac{u_\sd(\eph, r)}{\eph}
+\nonumber \\
+&=&  \frac{j(r)}{j(0)}  \int \dd \eph \sum_i 
+N_i(\lx) \frac{u_i^\gal(\eph)}{\eph}\,. \nonumber \\
+\end{eqnarray}
+In Fig.~\ref{fig:SD_Edens} we compare the energy densities from
+different radiation fields in a galaxy cluster with the mass
+$\mvir=4.0\times10^{13}\msun$. We use two different profiles for the
+SD energy density, where the total profile includes the contribution
+from the ICL, the BCG and all the galaxies, while the galaxies are
+excluded in the smooth profile. We find that even for a cluster with a
+relative small mass the energy density of the SD components dominates
+over the CMB and the magnetic fields (with a central B field of 3~$\mu
+G$) within about 10\% of $\rvir$. Outside this radius the CMB is
+dominating the energy density of the cluster, hence the magnetic
+fields are always subdominant in the cluster and can safely be removed
+from cluster IC calculations for a reasonable central B-field and
+spectral index. Note that in this work we keep the contribution
+from B-fields to the total energy density for consistency.
+
+%***********************************************
+
 \begin{figure*}

### 2011-04-08 paper.tex
pop studies improved

@@
     $E_\gamma=1-10$~GeV for 32 clusters. The Fermi upper limits are shown with
-    black arrows. The blue boxes show the gamma-ray emission from CRp induced
+    black arrows. The blue boxes show the gamma-ray emission from CRp-induced
     $\pi^0$-decay, where the upper bound shows the estimates for an optimistic
     model and the lower bound a more conservative model excluding point sources
-    (note that both models assume the maximally allowed acceleration efficiency
-    for strong shocks and most likely will have to be corrected down, see
-    \cite{2010MNRAS.409..449P} for details). Note that there is currently no
-    tension between our predictions and upper limits from Fermi, although Virgo,
-    Norma, and Coma are coming close and will enforce constraints on the
-    hadronic models in the coming years.}
+    (see \cite{2010MNRAS.409..449P} for details). Note that our models are in
+    perfect agreement with the derived upper limits from Fermi. Interestingly,
+    the limits of Virgo, Norma, and Coma are closing in on our predictions and
+    will enforce constraints on the hadronic models in the coming years.}
  \label{fig15}
@@
 
-the tightest limits on DM and CRps from Fermi are in the 1-10 GeV
- regime, where Fornax, M49, and NGC4636 are the most constraining
- "clusters" for the DM and Virgo, Coma and Norma are very close to the
- predictions for the CRps
-
-using beta profiles, discrepancy with Norma cluster in Ackermann gone,
-Integrated flux similar
-
-AGN M87, effective area better in 1 GeV range
+In Fig.~\ref{fig15}, we compare Fermi-LAT flux upper limits to the flux
+predictions by the semi-analytical Pinzke and Pfrommer model
+\cite{2010MNRAS.409..449P} for CRp induced $\gamma$-rays that uses the
+X-ray-inferred density profiles of clusters as an input. For consistency, we use
+beta-model fits to ROSAT data of X-ray bright clusters for our $\gamma$-ray flux
+estimates \cite{2002ApJ...567..71}). Hence these predictions are superior to
+those that use luminosity-mass scaling relation to infer the expected
+$\gamma$-ray flux---a method used by reference \cite{2010ApJ...717L..71A} to
+compare to Fermi limits.  In this semi-analytic model, we employ the fact that
+CRs accelerated at structure formation shocks and transported over cosmic time
+exhibit a universal spectral form and an almost universal spatial
+distribution. Depending on whether or not we account for the bias of
+``artificial galaxies'' in cosmological simulations, we derive an optimistic or
+conservative limit of the expected $\gamma$-ray emission from decaying pions
+(bracketing our ignorance of the contribution of cluster galaxies to the overall
+$\gamma$-ray flux from a cluster). Note that both models assume the maximally
+allowed acceleration efficiency for strong shocks that transfer 50\% of the
+shock kinetic energy to CRs and most likely will have to be corrected down if
+this number is not realized at structure formation shocks. Secondly, these
+simulations neglect active CR transport such as streaming and diffusion relative
+to the gas, i.e. we assume that advective transport is the dominant one and CRs
+are tightly coupled to the gas via flux-frozen magnetic fields tangled on
+sufficiently small scales. Evidence from the statistics of radio halos suggests
+that this might not be the case for relaxed clusters, arguing that CR streaming
+in those objects could be responsible for a decrease in the central CR number
+density. This effect would also reduce the expected $\gamma$-ray flux by up to a
+factor of five \cite{2011A&A...527A..99E}. We note that the tightest Fermi
+limits are obtained in the 1-10 GeV regime due to the largest effective area of
+LAT there. In this energy band, the Fermi limits come close to the flux
+predictions of Virgo, Coma and Norma. Using integrated flux limits from Fermi,
+we arrive at very similar results.  We emphasize that by using our semi-analytic
+modeling, the slight discrepancy of the scaling relation-based prediction with
+the Fermi limit on Norma \cite{2010ApJ...717L..71A} is resolved: Norma simply
+seems to be less bright than an average cluster of the same mass as Norma. The
+insenstitive limit on Perseus comes about since the central AGN in NGC1275 has
+turned on over the last years, making it hard to determine a comparable
+limit as obtained from teh other clusters.
 
@@
 \end{figure*}
- best clusters, stacking unlikely to improve
 

### 2011-04-08 paper.tex
further editing to App, pop studies

@@
 
+\begin{figure*}%[t]
+\begin{minipage}{2.0\columnwidth}
+ \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.DM.eps}
+\caption{\it Comparing the flux from clusters in the extended HIFLUGCS
+  catalogue. We show the energy integrated gamma-ray fluxes derived
+  from both leptophilic DM that result in inverse Compton upscattered
+  CMB photons (red), and the continuum emission from the DM $\Kp$
+  benchmark model (blue). The fluxes are calculated within $\rvir$
+  for each of the 106 clusters included in the extended HIFLUGCS
+  catalogue, and are derived using a single beta profile for each
+  cluster's gas density profile (see text for details). The upper
+  panel show the energy integrated flux above 100~MeV and the lower
+  panel above 10~GeV, both as a function of HIFLUGCS cluster ID. The
+  name of the four brightest clusters are written out, where Fornax
+  and M49 are the brightest targets.}
+ \label{fig21}
+\end{minipage}
+\end{figure*}
+
 Figure~\ref{fig14} compares Fermi upper limits on the $\gamma$-ray flux with
@@
 extended HIFLUGCS catalogue \cite{2002ApJ...567..716R} with our scaling
-relations of Equations~(\ref{eq:BM_scaling}) and (\ref{eq:LP_scaling}).  We
-assume a boost factor due to substructures that has a constant contribution per
-decade in substructure mass and has a mass spectrum extending down to Earth
-masses. Fermi limits rule out the leptophilic models in their present form with
-the mentioned assumptions in 14 clusters, and limit the boost from Sommerfeld
-enhancement to less than 4 [?] in Fornax. Assuming universality, this limits the
-Sommerfeld boost in the MW to less than 10 (see Fig.~\ref{fig:boost_const}).
-The flux level of the Fermi limits are an indirect measure of the ambient
-background flux in the $\gamma$-ray sky and/or the presence of strong point
-sources such as AGN in the immediate vicinity of the cluster position. Hence, the ratio of
-the Fermi upper limits to the predicted annihilation fluxes,
+relations of Equations~(\ref{eq:BM_scaling}) and (\ref{eq:LP_scaling}). In
+Figure~\ref{fig14}, we compare only those clusters of the HIFLUGCS sample with
+Fermi limits to our predictions and show the DM flux predictions of the entire
+sample in Fig.~\ref{fig21}.  We assume a boost factor due to substructures that
+has a constant contribution per decade in substructure mass and has a mass
+spectrum extending down to Earth masses. Fermi limits rule out the leptophilic
+models in their present form with the mentioned assumptions in 14 clusters, and
+limit the boost from Sommerfeld enhancement to less than 4 [?] in
+Fornax. Assuming universality, this limits the Sommerfeld boost in the MW to
+less than 10 (see Fig.~\ref{fig:boost_const}).  The flux level of the Fermi
+limits are an indirect measure of the ambient background flux in the
+$\gamma$-ray sky and/or the presence of strong point sources such as AGN in the
+immediate vicinity of the cluster position. Hence, the ratio of the Fermi upper
+limits to the predicted annihilation fluxes,
 $F_{\mathrm{UL}}/F_{\mathrm{scal}}$, is a good indication of the best cluster
@@
 turned on over the last years, making it hard to determine a comparable
-limit as obtained from teh other clusters.
+limit as obtained from the other clusters.
 
@@
    of HIFLUGCS cluster ID. The eight brightest clusters are labelled. The lower
-   panel shows the relative difference between the gamma-ray flux predicted by
+   panel shows the relative difference between the $\gamma$-ray flux predicted by
    the mass-luminosity scaling relation and to the flux computed using the
    semi-analytical model \cite{2010MNRAS.409..449P}. The name of the clusters
-   with the largest offset are printed out, which correlate with cool core
-   clusters.}
+   with the largest positive offset are printed out; as expected, they all
+   correspond to cool core clusters.}
  \label{fig19}
@@
 \end{figure*}
+
+To complete this section
 
@@
 %-) also, plot BM flux vs. psf, for models w/ and w/o substructures
-
-\clearpage
 
@@
 
-\del{
-Some of the results (should discuss what we want to emphasize):
-O) the flux from annihilating DM is boosted by about a factor 1000 in
- clusters
-O) flat surface brightness profiles with substructures
-O) Fornax is a great target for indirect DM studies because the relative
- low flux from CRps and high flux from DM
-O) the IC upscattered photons from stars and dust are dominated in the
- relevant energy regimes by the continuum emission for our DM
- benchmark models
-O) Fermi 3 year data will constrain the smallest mass of substructures
- using the benchmark models
-O) difficult to detect DM without a Sommerfeld boost with Cherenkov
- telescopes since the boost from substructures is extended while the
- sensitivity of Cherenkov telescopes drops linearly with radius
- outside the point spread function (CHECK)
-O) we rule out the leptophilic models in present form in 14 clusters,
- and limit the boost from Sommerfeld enhancement in the MW to less
- than 10
---) the tightest limits on DM and CRps from Fermi are in the 1-10 GeV
- regime, where Fornax, M49, and NGC4636 are the most constraining
- "clusters" for the DM and Virgo, Coma and Norma are very close to the
- predictions for the CRps
-O) we provide a rather simple model to calculate the spatial and spectral
- distribution of dust and stars in cluster (might be used for
- galaxies? with different spatial profile)
-}
-
 %------------------------------------------------------------------
@@
 
-\clearpage
 \appendix
 
-{\it Spatial distribution -- stars and dust}\\ Our goal in this
-section is to derive a simple spatial model for the distribution of SD
-in galaxy clusters. For this reason we use stacked cluster
-observations by Sloan in the $r$-band that trace the stars. We assume
-that the dust trace the stars in the clusters, which should be
-accurate to the order of magnitude estimate that we are interested in
-here. The stacked surface brightness profiles in
-\cite{2005MNRAS.358..949Z} are measured at redshift $z \sim 0.25$ with
-an average mass of the clusters of $4.0\times10^{13}\,\msun$. The
-profiles are build up out of three components; diffuse intracluster
-light (ICL), galaxies, and the brightest cluster galaxy (BCG) in the
-center of clusters. However, the total volume overlap of the ISM to
-the cluster is very small compared to the ICL- and BCG overlap with
-the cluster, thus the relative contribution of the galaxies to the IC
-emission is suppressed. To remove this bias we cut out the galaxies
-that have been smoothed over the cluster in the stacked analysis. In
-Fig.~\ref{fig:SD_spatial} we show the SDSS stacked brightness profiles
-as well as the fitted profiles\footnote{The measured brightness is
-  converted into units of $\rmn{erg}\,\rmn{s}^{-1}$ using
+\section{Detailed modelling of  starlight and dust in clusters}
+
+\subsection{Radial profiles}
+
+Our goal in this section is to derive a simple spatial model for the
+distribution of SD in galaxy clusters. For this reason we use stacked cluster
+observations by Sloan in the $r$-band that trace the stars. We assume that the
+dust trace the stars in the clusters, which should be accurate to the order of
+magnitude estimate that we are interested in here. The stacked surface
+brightness profiles in \cite{2005MNRAS.358..949Z} are measured at redshift $z
+\sim 0.25$ with an average mass of the clusters of
+$4.0\times10^{13}\,\msun$. The profiles are build up out of three components;
+diffuse intracluster light (ICL), galaxies, and the brightest cluster galaxy
+(BCG) in the center of clusters. However, the total volume overlap of the ISM to
+the cluster is very small compared to the ICL- and BCG overlap with the cluster,
+thus the relative contribution of the galaxies to the IC emission is
+suppressed. To remove this bias we cut out the galaxies that have been smoothed
+over the cluster in the stacked analysis. In Fig.~\ref{fig:SD_spatial} we show
+the SDSS stacked brightness profiles as well as the fitted profiles\footnote{The
+  measured brightness is converted into units of $\rmn{erg}\,\rmn{s}^{-1}$ using
   \cite{2010...book} $S(\rmn{mag}\,''^{-2}) =
-  \mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})$,
-  where the sun's absolute magnitude in the $r$-band is given by
-  $\mathcal{M}_\odot=27.1$ \cite{1998gaas.book.....B} and the
-  luminosity of the sun by $L_\odot=3.85\,10^{33}
-  \rmn{erg}\,\rmn{s}^{-1}$.}, both scaled with the unitless $\rvir$
-normalized area to resembele the expected luminosity at radius
-$r$. Our benchmark spatial model is shown with the solid black line,
-and include the contribution from the ICL and BCG.
+  \mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})$, where
+  the sun's absolute magnitude in the $r$-band is given by
+  $\mathcal{M}_\odot=27.1$ \cite{1998gaas.book.....B} and the luminosity of the
+  sun by $L_\odot=3.85\,10^{33} \rmn{erg}\,\rmn{s}^{-1}$.}, both scaled with the
+unitless $\rvir$ normalized area to resembele the expected luminosity at radius
+$r$. Our benchmark spatial model is shown with the solid black line, and include
+the contribution from the ICL and BCG.
 
@@
 
-{\it Spectral distribution -- stars and dust} \\ Our goal in this
-section is to derive a simple spectral model for SD in galaxy
-clusters. Since the radiation from galaxies are expected to leak out
-into the ICM, we expect similar spectral distributions, at least to
-the order of magnitude that we are interested in here. Hence, we use
-the IR to UV spectrum derived in \cite{2006ApJ...648L..29P} for a MW
-type galaxy to characterize the spectral distribution of light from SD
-in a cluster. Note, however, that we only keep the spectral shape, and
-renormalize the spectral distribution using the luminosity from SD.
+\subsection{Energy spectrum}
+
+Our goal in this section is to derive a simple spectral model for SD in galaxy
+clusters. Since the radiation from galaxies are expected to leak out into the
+ICM, we expect similar spectral distributions, at least to the order of
+magnitude that we are interested in here. Hence, we use the IR to UV spectrum
+derived in \cite{2006ApJ...648L..29P} for a MW type galaxy to characterize the
+spectral distribution of light from SD in a cluster. Note, however, that we only
+keep the spectral shape, and renormalize the spectral distribution using the
+luminosity from SD.
 
@@
 
-{\it Normalization}\\ The spatial and spectral distribution functions
+The spatial and spectral distribution functions
 of the light from SD in a cluster are both normalized with a constant
@@
 
-{\it Energy density}\\ The spatial distribution of the SD energy
-density is an important quantity since it impacts the steady state
-electron and positron spectra through cooling. A higher density of SD
-in a cluster suppresses the spectra of the upscattering particles. With
-the formalism presented above, we can now derive the energy density
-from starlight and dust in a galaxy cluster through
+The spatial distribution of the SD energy density is an important quantity since
+it impacts the steady state electron and positron spectra through cooling. A
+higher density of SD in a cluster suppresses the spectra of the upscattering
+particles. With the formalism presented above, we can now derive the energy
+density from starlight and dust in a galaxy cluster through
 \begin{eqnarray}
@@
 
+\section{Source functions of different DM models}
+
 \begin{figure*}
@@
 
+\section{Gas density profile of Fornax}
+
 \begin{figure}%[t]
@@
 
-\begin{figure*}%[t]
-\begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.DM.eps}
-\caption{\it Comparing the flux from clusters in the extended HIFLUGCS
-  catalogue. We show the energy integrated gamma-ray fluxes derived
-  from both leptophilic DM that result in inverse Compton upscattered
-  CMB photons (red), and the continuum emission from the DM $\Kp$
-  benchmark model (blue). The fluxes are calculated within $\rvir$
-  for each of the 106 clusters included in the extended HIFLUGCS
-  catalogue, and are derived using a single beta profile for each
-  cluster's gas density profile (see text for details). The upper
-  panel show the energy integrated flux above 100~MeV and the lower
-  panel above 10~GeV, both as a function of HIFLUGCS cluster ID. The
-  name of the four brightest clusters are written out, where Fornax
-  and M49 are the brightest targets.}
- \label{fig21}
-\end{minipage}
-\end{figure*}
-
 \end{document}

### 2011-04-08 paper.tex
pop studies finished

@@
 
-\section{Predictions and observational limits}
+\section{Population studies: flux predictions and observational limits}
 
@@
 underlying models and perspectives for the next years of Fermi observations.
+
+\subsection{Scaling relations}
 
@@
 groups even stronger.
+
+\subsection{DM annihilation}
 
@@
 spread function.
+
+\subsection{CR-induced emission}
 
@@
 
-To complete this section
-
-if CC, then skewed towards large X-ray fluxes; X-ray emission good
-proxies for gamma-ray emission --) The dust turns up at about a factor
-100 lower than the stars --) The other figure show the spectral shape
-of the IC-star with the same spectral shape as the dust, it shows the
-same gamma-ray slope as the dust --) The reason why there is only a
-factor 10 difference in the break in the gamma-ray emission between
-the star and dust is related to the KN. In our CRp paper, the last
-figure shows that at $\eg=100\,\tev$, the spectra is suppressed with
-about a factor 10 (also depends on $\alpha_\e$). Since the dust
-photons have a factor 10 higher energy, I expect this suppression at
-about 10~TeV. For star photons the suppression should be at
-100~GeV. So the star photons are definitely KN suppressed, which
-explains the earlier break and the steeper slope.
+To complete this section, we present our semi-analytical model predictions for
+the CR-induced $\gamma$-ray flux for all clusters in the extended HIFLUGCS
+sample in Fig.~\ref{fig19}. In the lower panel of this figure, we show the
+relative difference between the $\gamma$-ray flux predicted by the
+mass-luminosity scaling relation and to the flux computed using the
+semi-analytical model. Using our semi-analytic modelling results in a scatter of
+the expected $\gamma$-ray flux at a given mass. Cool core clusters have a denser
+core which increases the target density of gas protons for the hadronic reaction
+which in turn biases the expected $\gamma$-ray fluxes systematically higher. We
+confirm this effect as all our outliers with increased fux in our semi-analytic
+model relative to the scaling relation expectation are in fact cool core
+clusters suggesting that teh X-ray emission should be a good proxy for the
+expected $\gamma$-ray emission. Note however that there could be the
+counter-acting effect of CR streaming in relaxed clusters which would tend to
+decrease the $\gamma$-ray luminosity \cite{2011A&A...527A..99E}. Future careful
+modelling is needed to quatify this effect.
+
+\del{
+ANDERS: do you need this?
+--) The dust turns up at about a factor 100 lower than the stars
+--) The other figure show the spectral shape of the IC-star with the same
+spectral shape as the dust, it shows the same gamma-ray slope as the dust
+--) The reason why there is only a factor 10 difference in the break in the
+gamma-ray emission between the star and dust is related to the KN. In our CRp
+paper, the last figure shows that at $\eg=100\,\tev$, the spectra is suppressed
+with about a factor 10 (also depends on $\alpha_\e$). Since the dust photons
+have a factor 10 higher energy, I expect this suppression at about 10~TeV. For
+star photons the suppression should be at 100~GeV. So the star photons are
+definitely KN suppressed, which explains the earlier break and the steeper
+slope.
+}
 
@@
 dominate the astrophysical signal from clusters. Once supersymmetric cold dark
-matter decouples from the expanding universe it streams freely and smooths over
-any potentially present smaller scales. This imprints as a characteristic
+matter decouples from the expanding universe it streams and erases any
+potentially present smaller scales. Once gravitational instabilities causes
+halos to collapse, this free-streaming scale imprints as a characteristic
 minimum halo mass $M_\mathrm{min}$ into the hierarchy of structure formation and
@@
 halos. It turns out that the boost due to substructures dominates over the
-smooth component for halo masses $M>10^3 \msun$ and contributes a constant
+smooth component for halo masses $M>10^3 \msun$ [Anders?] and contributes a constant
 luminosity for each decade in halo mass. The ratio of halo-to-minimum subhalo

### 2011-04-09 paper.tex
updated

--- 2011-04-08 paper.tex
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v9.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v9.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v9.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v9.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v10.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v10.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v10.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v10.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
 \caption{\it Comparing the differential flux from different models: we
@@
 \begin{minipage}{2.0\columnwidth}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v9.0.1deg.1.6T.SubMass.elmu.SF300.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv9.0.1deg.SubMass.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v10.0.1deg.1.6T.SubMass.elmu.SF300.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv10.0.1deg.SubMass.noMW.woGal.eps}
 \caption{\it Comparing the flux from different inverse Compton
@@
 \begin{eqnarray}
-\label{eq:LP_scaling}
 L_{\gamma,\rmn{LP}} &=& L_{\gamma,\rmn{smLP}} \B_\rmn{LP} \propto \mvir^{0.73}\qquad
 \,\,\,\,\,\,\rmn{and}\\
-\label{eq:BM_scaling}
 L_{\gamma,\rmn{BM}} &=& L_{\gamma,\rmn{smBM}} \B_\rmn{BM} \propto  \mvir^{1.06}\,,\qquad
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
 \caption{\it Comparing the emission from different clusters. We show
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
 \caption{\it Constraining boost factors using flux upper limits. The
@@
 \begin{figure}
- \includegraphics[width=0.99\columnwidth]{figures/SB.v9.1GeV.SF300.SubMass.elmu.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.v10.1GeV.SF300.SubMass.elmu.eps}
 \caption{\it Comparing the surface brightness from different
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v9.1GeV.SF300.noSuB.vs.SubMass.elmu.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v10.1GeV.SF300.noSuB.vs.SubMass.elmu.eps}
 \caption{\it The impact of substructures on surface brightness. We
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.v9.1GeV.SF300.noSuB.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v9.1GeV.SF300.noSuB.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.v10.1GeV.SF300.noSuB.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v10.1GeV.SF300.noSuB.elmu.eps}
 \caption{\it The surface brightness without substructures. We show the
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v9.SF300.SubMass.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v9.SF300.SubMass.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v10.SF300.SubMass.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v10.SF300.SubMass.elmu.eps}
 \caption{\it Surface brightness predicted for Cherenkov telescopes at
@@
 \section{Predictions and observational limits}
-
-In this section, we compute the expected $\gamma$-ray fluxes from DM
-annihilation and CR interactions of the brightest clusters of the X-ray flux
-complete sample in the local universe. We confront these predictions to upper
-limits obtained by Fermi 1.5-year data and conclude on the viability of the
-underlying models and perspectives for the next years of Fermi observations.
-
-\begin{figure*}
-  \includegraphics[width=0.99\columnwidth]{figures/MLscaling.100M.eps}
-  \includegraphics[width=0.99\columnwidth]{figures/MLscaling.10G.eps}
-  \caption{\it Scaling relations of the cluster's virial mass $M_{200}$ and the
-    $\gamma$-ray luminosity for energies $E_\gamma>100$~MeV (left) and
-    $E_\gamma>10$~GeV (right).  Shown are the relations for the CR-induced
-    emission that is dominated by pion decay resulting from hadronic CR
-    interactions (solid), the leptophilic model of DM annihilations that
-    includes the scaling of the substructure and Sommerfeld boost factors with
-    custer mass from Equation~(\ref{eq:LP_scaling}) (dash-dotted) as well as the
-    benchmark model $K'$ of DM annihilation that includes the scaling of the
-    substructure boost with cluster mass of Equation~(\ref{eq:BM_scaling})
-    (dashed). Note that the scaling of this particular benchmark model is
-    indicative for all (non-Sommerfeld enhanced) DM annihilation models while
-    the normalization depends on the particular cross-section and neyralino
-    masses.}
+Model predictions
+
+\begin{figure}
+  \includegraphics[width=0.99\columnwidth]{figures/MLscaling.eps}
+  \caption{\it Luminosity to mass scaling relations. We show the
+    luminosity from; CRp induced emission (red solid), a leptophilic
+    model that IC upscatter CMB photons (green dash-dotted), mass
+    dependence of SD cooling have been neglected, actually a factor
+    few difference for groups. factor 2 for Fornax, and small
+    difference for large clusters}
  \label{fig:lum_mass_scaling}
-\end{figure*}
-
-First we focus on $\gamma$-ray flux-cluster mass scaling relations for DM
-annihilation and CR induced emission in Fig.~\ref{fig:lum_mass_scaling}.  The
-mass scaling of the substructure boost steepens the intrinsically shallower DM
-annihilation relation of benchmark models (Equation~(\ref{eq:BM_scaling})) while
-this steepening is in fact over-compensated by the inverse mass scaling of the
-Sommerfeld boost in leptophilic models that prefers smaller halos with a larger
-ratio of $c/v_\mathrm{circ}$ (Equation~(\ref{eq:LP_scaling})). In contrast, the
-CR scaling relation is considerably steeper as shown by reference
-\cite{2010MNRAS.409..449P}. [ANDERS: add CR scaling formula] This implies
-already a general strategy to minimize the CR-induced foreground for DM
-annihilation and argues for very nearby groups. We note that these simulations
-do not include AGn feedback that is thought to furthermore reduce the baryon
-fraction in groups relative to that in clusters \cite{2008ApJ...687L..53P}. The
-resulting smaller target density for hadronic CR interactions will furthermore
-steepen the $L_\gamma-M$ relation of CR induced emission, making the case for
-groups even stronger.
+\end{figure}
 
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.DM.eps}
-  \caption{\it Fermi flux upper limits are contrasted to the predicted DM
-    gamma-ray flux. We show the mean differential flux in the energy range
-    $E_\gamma=1-10$~GeV for 32 clusters. The Fermi-LAT upper limits are shown
-    with black arrows. The predicted fluxes are derived from the dominant
-    inverse Compton-scattering of CMB photons in a leptophilic DM model (red),
-    and the continuum emission from the DM $\Kp$ benchmark model
-    (blue). Assuming a boost factor due to substructures that has a mass
-    spectrum extending down to Earth masses, the expected leptophilic fluxes are
-    ruled out by lower upper limits in 14 of the clusters, with the strongest
-    constraints set by Fornax and M49. We can not yet constrain the benchmark
-    models, although our predictions are approaching the upper limits and will
-    allow to test these in the upcoming years with better data.}
+  \caption{\it Fermi flux upper limits contrasted to the predicted DM
+    gamma-ray flux. We show the mean differential flux in the energy
+    range $E_\gamma=1-10$~GeV for 32 clusters. The Fermi-LAT upper
+    limits are shown with black arrows. The predicted fluxes are
+    derived from both a leptophilic DM model that result in inverse
+    Compton upscattered CMB photons (red), and the continuum emission
+    from the DM $\Kp$ benchmark model (blue). The leptophilic fluxes
+    are ruled out by 14 of the clusters, with the strongest
+    constraints set by Fornax and M49. We can not constrain the
+    benchmark models, although our predictions are approaching the
+    upper limits.}
  \label{fig14}
@@
 \end{figure*}
-
-Figure~\ref{fig14} compares Fermi upper limits on the $\gamma$-ray flux with
-predictions of DM annihilation fluxes in the leptophilic and benchmark models.
-To obtain the $\gamma$-ray fluxes, we scale the virial mass of clusters in the
-extended HIFLUGCS catalogue \cite{2002ApJ...567..716R} with our scaling
-relations of Equations~(\ref{eq:BM_scaling}) and (\ref{eq:LP_scaling}).  We
-assume a boost factor due to substructures that has a constant contribution per
-decade in substructure mass and has a mass spectrum extending down to Earth
-masses. Fermi limits rule out the leptophilic models in their present form with
-the mentioned assumptions in 14 clusters, and limit the boost from Sommerfeld
-enhancement to less than 4 [?] in Fornax. Assuming universality, this limits the
-Sommerfeld boost in the MW to less than 10 (see Fig.~\ref{fig:boost_const}).
-The flux level of the Fermi limits are an indirect measure of the ambient
-background flux in the $\gamma$-ray sky and/or the presence of strong point
-sources such as AGN in the immediate vicinity of the cluster position. Hence, the ratio of
-the Fermi upper limits to the predicted annihilation fluxes,
-$F_{\mathrm{UL}}/F_{\mathrm{scal}}$, is a good indication of the best cluster
-candidates for indirect DM experiments. We identify Fornax, M49, NGC4636, and
-Virgo to be prime candidates. Note however, that Virgo extends of $7\deg$ over
-the sky which implies a lower surface brightness and lower signal-to-noise.
-Fermi limits on individual clusters are expected to improve as $\sqrt{T/1.5
-  \mathrm{yr}}$, where $T$ is the total elapsed time of the Fermi mission. We
-emphasize that the very inhomogeneous distribution of $F_{\mathrm{UL}}/
-F_{\mathrm{scal}}$ makes it unlikely to dramatically improve the limits through
-a stacking analysis as the weak signal will dilute the average constraints.
-Assuming the projected sensitivity of the future Cherenkov telescope array (CTA)
-of [ANDERS: value?], we note that it will be difficult to detect the DM
-annihilation signal from clusters without a Sommerfeld boost by Cherenkov
-telescopes. This is because the boost from substructures is extended while the
-sensitivity of Cherenkov telescopes drops linearly with radius outside the point
-spread function.
+ difficult to detect DM without a Sommerfeld boost with Cherenkov
+ telescopes since the boost from substructures is extended while the
+ sensitivity of Cherenkov telescopes drops linearly with radius
+ outside the point spread function (CHECK)
+
+we rule out the leptophilic models in present form in 14 clusters,
+ and limit the boost from Sommerfeld enhancement in the MW to less
+ than 10
+
+mention prime cluster candidates, LP under pressure, Fornax start
+being constraining, since only few clusters close to UL stacking will
+not increase the DM limits much
 
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.CR.diff.eps}
-  \caption{\it Fermi-LAT flux upper limits are contrasted to the predictions by
-    the semi-analytic Pinzke and Pfrommer model for CRp induced gamma-ray
-    emission. We show the mean differential flux in the energy range
-    $E_\gamma=1-10$~GeV for 32 clusters. The Fermi upper limits are shown with
-    black arrows. The blue boxes show the gamma-ray emission from CRp-induced
-    $\pi^0$-decay, where the upper bound shows the estimates for an optimistic
-    model and the lower bound a more conservative model excluding point sources
-    (see \cite{2010MNRAS.409..449P} for details). Note that our models are in
-    perfect agreement with the derived upper limits from Fermi. Interestingly,
-    the limits of Virgo, Norma, and Coma are closing in on our predictions and
-    will enforce constraints on the hadronic models in the coming years.}
+  \caption{\it Fermi-LAT flux upper limits contrasted to the
+    predictions by the semi-analytic Pinzke and Pfrommer model for CRp
+    induced gamma-ray emission. We show the mean differential flux in
+    the energy range $E_\gamma=1-10$~GeV for 32 clusters. The Fermi
+    upper limits are shown with black arrows. The blue boxes show the
+    gamma-ray emission from CRp induced $\pi^0$\:s decaying, where the
+    upper bound shows the estimates for an optimistic model and the
+    lower bound a more conservative model excluding point sources (the
+    realistic case is more likely in between, see
+    \cite{2010MNRAS.409..449P} for details). Note that there is
+    currently no tension between our predictions and upper limits from
+    Fermi, although Virgo, Norma, and Coma are close and will in the
+    coming years enforce constraints on the hadronic models.}
  \label{fig15}
@@
 
-In Fig.~\ref{fig15}, we compare Fermi-LAT flux upper limits to the flux
-predictions by the semi-analytical Pinzke and Pfrommer model
-\cite{2010MNRAS.409..449P} for CRp induced $\gamma$-rays that uses the
-X-ray-inferred density profiles of clusters as an input. For consistency, we use
-beta-model fits to ROSAT data of X-ray bright clusters for our $\gamma$-ray flux
-estimates \cite{2002ApJ...567..71}). Hence these predictions are superior to
-those that use luminosity-mass scaling relation to infer the expected
-$\gamma$-ray flux---a method used by reference \cite{2010ApJ...717L..71A} to
-compare to Fermi limits.  In this semi-analytic model, we employ the fact that
-CRs accelerated at structure formation shocks and transported over cosmic time
-exhibit a universal spectral form and an almost universal spatial
-distribution. Depending on whether or not we account for the bias of
-``artificial galaxies'' in cosmological simulations, we derive an optimistic or
-conservative limit of the expected $\gamma$-ray emission from decaying pions
-(bracketing our ignorance of the contribution of cluster galaxies to the overall
-$\gamma$-ray flux from a cluster). Note that both models assume the maximally
-allowed acceleration efficiency for strong shocks that transfer 50\% of the
-shock kinetic energy to CRs and most likely will have to be corrected down if
-this number is not realized at structure formation shocks. Secondly, these
-simulations neglect active CR transport such as streaming and diffusion relative
-to the gas, i.e. we assume that advective transport is the dominant one and CRs
-are tightly coupled to the gas via flux-frozen magnetic fields tangled on
-sufficiently small scales. Evidence from the statistics of radio halos suggests
-that this might not be the case for relaxed clusters, arguing that CR streaming
-in those objects could be responsible for a decrease in the central CR number
-density. This effect would also reduce the expected $\gamma$-ray flux by up to a
-factor of five \cite{2011A&A...527A..99E}. We note that the tightest Fermi
-limits are obtained in the 1-10 GeV regime due to the largest effective area of
-LAT there. In this energy band, the Fermi limits come close to the flux
-predictions of Virgo, Coma and Norma. Using integrated flux limits from Fermi,
-we arrive at very similar results.  We emphasize that by using our semi-analytic
-modeling, the slight discrepancy of the scaling relation-based prediction with
-the Fermi limit on Norma \cite{2010ApJ...717L..71A} is resolved: Norma simply
-seems to be less bright than an average cluster of the same mass as Norma. The
-insenstitive limit on Perseus comes about since the central AGN in NGC1275 has
-turned on over the last years, making it hard to determine a comparable
-limit as obtained from teh other clusters.
-
-\begin{figure*}%[t]
-\begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.CR.eps}
- \caption{\it Comparison of the gamma-ray flux induced by CRps for the 106
-   clusters included in the extended HIFLUGCS catalogue. The fluxes are
-   calculated within $\rvir$, and are derived using a single beta profile for
-   each cluster's gas density profile as obtained by ROSAT X-ray
-   observations. The CR distribution follows the semi-analytically model derived
-   by hydrodynamical cosmological cluster simulations \cite{2010MNRAS.409..449P}
-   (see text for details). The upper panel shows the energy integrated flux
-   above 100~MeV (left side) and above 100~GeV (right side), both as a function
-   of HIFLUGCS cluster ID. The eight brightest clusters are labelled. The lower
-   panel shows the relative difference between the gamma-ray flux predicted by
-   the mass-luminosity scaling relation and to the flux computed using the
-   semi-analytical model \cite{2010MNRAS.409..449P}. The name of the clusters
-   with the largest offset are printed out, which correlate with cool core
-   clusters.}
- \label{fig19}
-\end{minipage}
-\end{figure*}
-
-if CC, then skewed towards large X-ray fluxes; X-ray emission good
-proxies for gamma-ray emission --) The dust turns up at about a factor
-100 lower than the stars --) The other figure show the spectral shape
-of the IC-star with the same spectral shape as the dust, it shows the
-same gamma-ray slope as the dust --) The reason why there is only a
-factor 10 difference in the break in the gamma-ray emission between
-the star and dust is related to the KN. In our CRp paper, the last
-figure shows that at $\eg=100\,\tev$, the spectra is suppressed with
-about a factor 10 (also depends on $\alpha_\e$). Since the dust
-photons have a factor 10 higher energy, I expect this suppression at
-about 10~TeV. For star photons the suppression should be at
-100~GeV. So the star photons are definitely KN suppressed, which
-explains the earlier break and the steeper slope.
+the tightest limits on DM and CRps from Fermi are in the 1-10 GeV
+ regime, where Fornax, M49, and NGC4636 are the most constraining
+ "clusters" for the DM and Virgo, Coma and Norma are very close to the
+ predictions for the CRps
+
+using beta profiles, discrepancy with Norma cluster in Ackermann gone,
+Integrated flux similar
+
+AGN M87, effective area better in 1 GeV range
 
@@
 \begin{minipage}{2.0\columnwidth}
+ \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.CR.eps}
+\caption{\it Comparing the flux from clusters in the extended HIFLUGCS
+  catalogue. We show the energy integrated gamma-ray flux induced by
+  CRps for the 106 clusters included in the extended HIFLUGCS
+  catalogue. The fluxes are calculated within $\rvir$, and are derived
+  using a single beta profile for each cluster's gas density profile
+  (see text for details). The upper panel show the energy integrated
+  flux above 100~MeV (left side) and above 100~GeV (right side), both
+  as a function of HIFLUGCS cluster ID. The name of the eight
+  brightest clusters are written out. The lower panel show the
+  relative difference between the gamma-ray flux predicted by
+  mass-luminosity scaling relations compared to the flux computed
+  using the semi-analytically model \cite{2010MNRAS.409..449P}. The
+  name of the clusters with the largest offset are printed out, which
+  correlate with cool core clusters.}
+ \label{fig19}
+\end{minipage}
+\end{figure*}
+if CC, then skewed towards large X-ray fluxes; X-ray emission good
+proxies for gamma-ray emission --) The dust turns up at about a factor
+100 lower than the stars --) The other figure show the spectral shape
+of the IC-star with the same spectral shape as the dust, it shows the
+same gamma-ray slope as the dust --) The reason why there is only a
+factor 10 difference in the break in the gamma-ray emission between
+the star and dust is related to the KN. In our CRp paper, the last
+figure shows that at $\eg=100\,\tev$, the spectra is suppressed with
+about a factor 10 (also depends on $\alpha_\e$). Since the dust
+photons have a factor 10 higher energy, I expect this suppression at
+about 10~TeV. For star photons the suppression should be at
+100~GeV. So the star photons are definitely KN suppressed, which
+explains the earlier break and the steeper slope.
+
+\begin{figure*}%[t]
+\begin{minipage}{2.0\columnwidth}
  \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.DM.eps}

### 2011-04-10 paper.tex
figures+text

@@
 
-\subsection{Radial profiles}
-
-Our goal in this section is to derive a simple spatial model for the
-distribution of SD in galaxy clusters. For this reason we use stacked cluster
-observations by Sloan in the $r$-band that trace the stars. We assume that the
-dust trace the stars in the clusters, which should be accurate to the order of
-magnitude estimate that we are interested in here. The stacked surface
-brightness profiles in \cite{2005MNRAS.358..949Z} are measured at redshift $z
-\sim 0.25$ with an average mass of the clusters of
-$4.0\times10^{13}\,\msun$. The profiles are build up out of three components;
-diffuse intracluster light (ICL), galaxies, and the brightest cluster galaxy
-(BCG) in the center of clusters. However, the total volume overlap of the ISM to
-the cluster is very small compared to the ICL- and BCG overlap with the cluster,
-thus the relative contribution of the galaxies to the IC emission is
-suppressed. To remove this bias we cut out the galaxies that have been smoothed
-over the cluster in the stacked analysis. In Fig.~\ref{fig:SD_spatial} we show
-the SDSS stacked brightness profiles as well as the fitted profiles\footnote{The
-  measured brightness is converted into units of $\rmn{erg}\,\rmn{s}^{-1}$ using
-  \cite{2010...book} $S(\rmn{mag}\,''^{-2}) =
-  \mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})$, where
-  the sun's absolute magnitude in the $r$-band is given by
-  $\mathcal{M}_\odot=27.1$ \cite{1998gaas.book.....B} and the luminosity of the
-  sun by $L_\odot=3.85\,10^{33} \rmn{erg}\,\rmn{s}^{-1}$.}, both scaled with the
-unitless $\rvir$ normalized area to resembele the expected luminosity at radius
-$r$. Our benchmark spatial model is shown with the solid black line, and include
-the contribution from the ICL and BCG.
-
-Instead of modelling the surface brightness with a de Vaucouleur
-profile with the addition of a power-law, we use a double beta profile
-model for simplicity of deprojection given by:
-\begin{equation}
-S_\sd (r_\bot)= \sum_{i=1}^2 \,S_i\, 
-\left[1 + \left( \frac{r_\bot}{r_{\mathrm{c}_i}}\right)^2\right]
-^{-3\beta_i + 1/2}\,,
-\label{double_beta}
-\end{equation}
-where we found the following best fitted central brightness ($S_i$),
-core radius ($r_{\mathrm{c}_i}$), and slope ($\beta_i$):
-\begin{eqnarray}
- S_1&=&5.0\times10^{-6}\,\rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1},\,
-r_{\mathrm{c}_1}=130\,\rmn{kpc},\,
-\beta_1=0.54\nonumber\\
- S_2&=&3.9\times10^{-3}\,\rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1},\,
-r_{\mathrm{c}_2}=2.8\,\rmn{kpc},\,
-\beta_2=0.53\,.\nonumber\\
-\label{fit_spatial_IR}
-\end{eqnarray}
-The 3D spatial profile is derived by deprojecting the surface
-brightness in Eq.~(\ref{double_beta}) (see
-e.g. \cite{2004A&A...413...17P} for details about the deprojection):
-\begin{eqnarray}
-  j(r)  = \sum_{i=1}^2 \frac{S_i}{2\pi\,r_{\mathrm{c}_i}}\,
-  \frac{6 \beta_i - 1}{\left(1 + r^2/r^2_{\mathrm{c}_i}\right)^{3\beta_i}}\,
-  \mathcal{B}\left(\frac{1}{2},3\beta_i\right)\,,
-\end{eqnarray}
-where $\mathcal{B}(a,b)$ denotes the beta-function
-\cite{1965hmfw.book.....A}.
-
 \subsection{Energy spectrum}
 
-Our goal in this section is to derive a simple spectral model for SD in galaxy
-clusters. Since the radiation from galaxies are expected to leak out into the
-ICM, we expect similar spectral distributions, at least to the order of
-magnitude that we are interested in here. Hence, we use the IR to UV spectrum
-derived in \cite{2006ApJ...648L..29P} for a MW type galaxy to characterize the
-spectral distribution of light from SD in a cluster. Note, however, that we only
-keep the spectral shape, and renormalize the spectral distribution using the
-luminosity from SD.
+Our goal in this section is to derive a simple spectral model for SD
+in galaxy clusters. The SD light from clusters is dominated by the
+emission from galaxies. This radiation is expected to leak out into
+the much larger volume of the ICM, hence we approximate the spectral
+distribution of the ICL with the light from galaxies. We use the far
+infrared to ultraviolet spectrum derived in \cite{2006ApJ...648L..29P}
+for a MW type galaxy to characterize the SD spectral distribution of a
+cluster. Note that we only keep the spectral shape, and renormalize
+the spectral distribution using the luminosity from SD.
 
@@
 light from SD together with the CMB black-body distribution in a
-galaxy cluster, both at the radius $r=0.071\rvir$ where the energy
+galaxy cluster, both at the radius $r=0.02\rvir$ where the energy
 density of the smooth light from SD (see Fig.~\ref{fig:SD_Edens})
@@
 spectral data and the fitted spectra using the luminosity from stars
-and dust individually (see the normalization section below for further
-details).
+and dust individually.
 
@@
   \eph^2\frac{\dd^2 N_\ph}{\dd \eph \dd V}
-  &\equiv& u_\sd(\eph) =  \sum_i N_i(\lx) u_i^\gal(\eph)\,,\nonumber \\ 
+  &\equiv& u_\sd(\eph) =  \sum_i N_i(\mvir) u_i^\gal(\eph)\,,\nonumber \\ 
 \rmn{where}\quad i&=&\{\rmn{stars,dust}\} \qquad \rmn{and}\\ 
@@
 
-The spatial and spectral distribution functions
-of the light from SD in a cluster are both normalized with a constant
-determined from the luminosity in each respective wavelength. The
+The spatial and spectral distribution functions of the light from SD
+in a cluster are both normalized with a mass dependent function
+determined from the luminosity in each respective wavelength band. The
 specific energy density is given by
 \begin{eqnarray} 
-u_\sd(\eph, r) &=& \frac{j(r)}{j(0)}\,u_\sd(\eph) \nonumber\\
-&=& \frac{j(r)}{j(0)}\,\sum_i N_i(\lx) u_i^\gal(\eph)\,,
+u_\sd(\eph, r) &=& j(r)\,u_\sd(\eph) \nonumber\\
+&=& j(r)\,\sum_i N_i(\mvir) u_i^\gal(\eph)\,,
 \end{eqnarray}
-where we fix the unitless normalization $N_i(\lx)$ using the total
-energy of the light in SD  within $\rvir$:
+where $j(r)$ describes the spatial distribution. We fix the unitless
+normalization $N_i(\mvir)$ using the total energy of the light in SD
+within $\rvir$:
 \begin{eqnarray} 
   E_{i,\vir} &=& L_i \frac{\rvir}{c} \nonumber \\
-  &=&N_i(\lx)\int_{\rvir} \int_i \,\frac{j(r)}{j(0)} 
+  &=&N_i(\mvir)\int_{\rvir} \int_i \,j(r) 
   \frac{u_i^\gal(\eph)}{\eph}\,\dd V\dd \eph\,,\nonumber \\
@@
 times the typical timescale it takes for a photon to propagate through
-the cluster (we assume that the cluster is optically thin). Once we
-derived the SD luminosities for a well representative cluster, we use
-a IR to X-ray scaling relation to estimate the luminosity from an
-arbitrary cluster:
-\begin{equation}
-L_\ir=1.05\times10^{45}\,\rmn{erg\,s}^{-1}\,
-\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,,
-\label{eq:SD-X}
-\end{equation}
-where $\lx$ is the luminosity of the X-ray emitting gas within
-$\rvir$.
-
-The normalization constant for the starlight $N_\stars(\lx)$ is derived
-in the following three steps: (1) We use the average apparent magnitude
-in the $(r+i)$-band $m_{(r+i),0.25}\approx 15.5$
-\cite{2005MNRAS.358..949Z} of a cluster with the average mass
-$\mvir=4.0\times10^{13}\msun$ at a redshift $z=0.25$ to derive the
-luminosity from the stars:
-\begin{equation}
-L_\stars=10^{\frac{m_\odot-m_{(r+i),0.25}}{2.5}}
-\left(\frac{D_\clu}{D_\odot}\right)^2 L_\odot
-\approx 7.1\times10^{44}\,\rmn{erg}\,\rmn{s}^{-1}\,,
+the cluster (we assume that the cluster is optically thin). We derive
+the luminostity from the stars using
+\begin{eqnarray}
+L_\stars(M_{200\rmn{av}})&=&10^{\frac{m_\odot-m_\rmn{cl}-2.5\log\left(1+z\right)}{2.5}}
+\left(\frac{D_\clu}{D_\odot}\right)^2 L_\odot\nonumber\\
+&\approx& 5.3\times10^{44}\,\rmn{erg}\,\rmn{s}^{-1}\,,
 \label{eq:L_star}
-\end{equation}
-where the apparent magnitude of the sun $m_\odot\approx -27.1$, the
-distance to the sun $D_\odot=4.85\times10^{-6}\,\rmn{pc}$, the
-luminosity of the sun $L_\odot=3.85\times10^{33}\,\rmn{erg\,s}^{-1}$,
-and the distance to the cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. (2)
-We use the IR to X-ray scaling relation in Eq.~(\ref{eq:SD-X}) to derive
-a more general form of the luminosity from stars in
-Eq.~(\ref{eq:L_star}) that is valid for an arbitrary cluster mass. The
-cluster X-ray luminosities are found in the extended HIFLUGCS
-catalogue \cite{2002ApJ...567..716R} to which we have added the Virgo
-cluster. (3) The normalization constant for the stars is
-determined from the above steps together with Eq.~(\ref{eq:E_SD})
-where we integrate over the cluster volume and spectral distribution
-of the stars. It is given by
-\begin{equation}
- N_\stars(\lx) = 1.2\times10^{-9}\,
-\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,.
+\end{eqnarray}
+where the average apparent magnitude of a cluster at $z\approx 0.25$
+in the $(r+i)$-band is given by $m_\rmn{cl}\approx 15.5$
+\cite{2005MNRAS.358..949Z}. This magnitude is derived from stacking
+clusters observed by the SDSS with the average mass
+$M_{200\rmn{av}}=4.0\times10^{13}\msun$ and redshift close to
+$z=0.25$. We also use an apparent magnitude of the sun $m_\odot\approx
+-27.7$, distance to the sun $D_\odot=4.85\times10^{-6}\,\rmn{pc}$,
+luminosity of the sun $L_\odot=1.17\times10^{33}\,\rmn{erg\,s}^{-1}$,
+and distance to the cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. To
+account for different cluster masses in our analisys we adopt a simple
+mass scaling of the luminosity from the stars in clusters. Since a
+large contribution of the total starlight in a cluster comes from the
+brightest central galaxy (BCG), we assume that the total starlight has
+the same halo mass scaling as the BCG \cite{2010ApJ...713.1037H}
+\begin{equation}
+L_\stars(\mvir)=L_\stars(M_{200\rmn{av}})\,
+\left(\frac{\mvir}{M_{200\rmn{av}}}\right)^{0.18}\,.
+\end{equation} 
+We can now fix the normalization constant for the stars in
+Eq.~(\ref{eq:E_SD}) by integrating over the cluster volume and
+spectral distribution of the stars. It is given by
+\begin{equation}
+ N_\stars(\mvir) = 2.1\times10^{33}\,
+\left(\frac{\mvir}{M_{200\rmn{av}}}\right)^{0.18}\,
+\frac{\rvir}{\int_{\rvir} j(r) \,\dd V}\,.
 \label{eq:N_stars}
 \end{equation}
-Note that since the luminosities include the contribution from
+\del{Note that since the luminosities include the contribution from
 galaxies, we have integrated the spatial distribution including
@@
 the SD energy densities are derived from the spatial distribution
-where galaxies have been excluded.
-
-The normalization constant for the dust $N_\dust(\lx)$ is derived in the
-following four steps: (1) We use a cluster with the the average mass
-$\mvir=4.0\times10^{13}\msun$ and estimate the X-ray luminosity from
-the X-ray to mass scaling relations derived for the Representative
-XMM-Newton Cluster Structure Survey (REXCESS) in
-\cite{2009A&A...498..361P}:
-\begin{equation}
-\lx=1.18\times 10^{44}\,\rmn{erg\,s}^{-1}
-\left(\frac{M_{200}}{10^{14}\msun}\right)^{1.81}\,,
-\end{equation}
-where we have used that $M_\rmn{200} \approx 1.58\,M_\rmn{500}$ for a
-small cluster \footnote{We derive the factor 1.58 using
-  $M_\rmn{200}/M_\rmn{500}$ for the clusters in the HIFLUGCS catalogue
-  with a mass similar to $\mvir=4.0\times10^{13}\msun$ that we use to
-  derive the luminosity from dust.}. (2) From the IR to X-ray scaling
-relation in Eq.~(\ref{eq:SD-X}) we can now estimate calculate the
-luminosity from the dust for a $\mvir=4.0\times10^{13}\msun$ cluster;
-$L_\dust=4.7\times10^{44}\,\rmn{erg\,s}^{-1}$. (3) We generalize
-Eq.~(\ref{eq:L_star}) to an arbitrary cluster mass using
-Eq.~(\ref{eq:SD-X}) together with the cluster X-ray luminosities in
-the extended HIFLUGCS catalogue. (4) The normalization constant for
-the dust can now be determined from from the above steps together with
-Eq.~(\ref{eq:E_SD}) where we integrate over the cluster volume and
-spectral distribution of the dust. It is given by
-\begin{equation}
- N_\dust(\lx) = 1.4\times10^{-9}\,
-\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,.
+where galaxies have been excluded.}
+
+The luminosity from the dust is derived from the the luminosity to
+richness scaling relation found in \cite{2008A&A...490..547G}
+$L_\dust=10^{44.8}\left(\frac{N_{200}}{10}\right)^{0.8}$. We pic a high
+richness $N_{200}=82$ cluster to normalize the luminosity since they
+are less likely biased by chance coincidences. This richness roughly
+correspond to $\mvir=6.0\times10^{14}\,\msun$
+\cite{2010ApJ...713.1037H}. Assuming that the dust scales with halo
+mass in the same way as the stars, we get
+\begin{equation}
+L_\stars(\mvir)=L_\stars(M_{200\rmn{av}})\,
+\left(\frac{\mvir}{M_{200\rmn{av}}}\right)^{0.18}\,.
+\end{equation} 
+The normalization constant for the dust in Eq.~(\ref{eq:E_SD}) can now
+be determined:
+\begin{equation}
+ N_\dust(\mvir) =\,
+\left(\frac{\mvir}{M_{200\rmn{av}}}\right)^{0.18}\,
+\frac{\rvir}{\int_{\rvir} j(r) \,\dd V}\,.
 \label{eq:N_dust}
 \end{equation}
-Note that since the luminosities include the contribution from
-galaxies, we have integrated the spatial distribution including
-galaxies to derive the normalization. Once the normalization is fixed,
-the SD energy densities are derived from the spatial distribution
-where galaxies have been excluded.
 
@@
 \nonumber \\
-&=&  \frac{j(r)}{j(0)}  \int \dd \eph \sum_i 
-N_i(\lx) \frac{u_i^\gal(\eph)}{\eph}\,. \nonumber \\
+&=&  j(r)  \int \dd \eph \sum_i 
+N_i(\mvir) \frac{u_i^\gal(\eph)}{\eph}\,. \nonumber \\
 \end{eqnarray}
@@
 from B-fields to the total energy density for consistency.
+
+\subsection{Radial profiles}
+
+Our goal in this section is to derive a simple spatial model for the
+distribution of SD in galaxy clusters. For this reason we use stacked
+cluster observations by Sloan in the $r$ and $i$-band that trace the
+stars. For simplicity we assume that the dust trace the stars in the
+clusters [WHY IS THIS A GOOD APPROXIMATION]. The stacked surface
+brightness profiles in \cite{2005MNRAS.358..949Z} are measured at
+redshift $z \sim 0.25$ with an average mass of the clusters of
+$4.0\times10^{13}\,\msun$. The profiles are build up out of three
+components; diffuse intracluster light (ICL), galaxies, and the
+brightest cluster galaxy (BCG) in the center of clusters. However, the
+total volume overlap of the ISM to the cluster is very small compared
+to the ICL- and BCG overlap with the cluster, thus the relative
+contribution of the galaxies to the IC emission is suppressed. To
+remove this bias we cut out the galaxies that have been smoothed over
+the cluster in the stacked analysis. In Fig.~\ref{fig:SD_spatial} we
+show the SDSS stacked brightness profiles as well as the fitted
+profiles\footnote{The measured brightness is converted into units of
+  $\rmn{erg}\,\rmn{s}^{-1}$ using \cite{2010...book}
+  $S(\rmn{mag}\,''^{-2}) =
+  \mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})$,
+  where the sun's absolute magnitude in the $r$-band is given by
+  $\mathcal{M}_\odot=27.1$ \cite{1998gaas.book.....B} and the
+  luminosity of the sun by $L_\odot=3.85\,10^{33}
+  \rmn{erg}\,\rmn{s}^{-1}$.}, both scaled with the unitless $\rvir$
+normalized area to resembele the expected luminosity at radius
+$r$. Our benchmark spatial model is shown with the solid black line,
+and include the contribution from the ICL and BCG.
+
+Instead of modelling the surface brightness with a de Vaucouleur
+profile with the addition of a power-law, we use a double beta profile
+model for simplicity of deprojection given by:
+\begin{equation}
+\tilde{S}_\sd (r_\bot) = \frac{S_\sd (r_\bot)}{S_\rmn{SD}^\rmn{tot}(0)} = 
+\sum_{i=1}^2 \,S_i\, 
+\left[1 + \left( \frac{r_\bot}{r_{\mathrm{c}_i}}\right)^2\right]
+^{-3\beta_i + 1/2}\,,
+\label{double_beta}
+\end{equation}
+where we found the following best fitted normalized central brightness
+($S_i$), core radius ($r_{\mathrm{c}_i}$), and slope ($\beta_i$) for
+the total model:
+\begin{align}
+&\tilde{S}_1^\rmn{tot} = 1.0\,,
+&&r_{\mathrm{c}_1}^\rmn{tot} = 1.8\,\rmn{kpc}\,,
+&&&\beta_1^\rmn{tot} = 0.45\, \nonumber\\
+&\tilde{S}_2^\rmn{tot} = 2.3\times10^{-3}\,,
+&&r_{\mathrm{c}_2}^\rmn{tot} = 0.19\,\rvir\,,
+&&&\beta_2^\rmn{tot} = 0.44\,.\nonumber\\
+& && &&&
+\label{fit_spatial_IR}
+\end{align}
+and for the smooth model
+\begin{align}
+&\tilde{S}_1^\rmn{sm}=0.47,\,
+&&r_{\mathrm{c}_1}^\rmn{sm}=3.9\,\rmn{kpc}\,,
+&&&\beta_1^\rmn{sm}=0.53 \,\nonumber\\
+&\tilde{S}_2^\rmn{sm}=8.3\times10^{-4}\,,
+&&r_{\mathrm{c}_2}^\rmn{sm}=0.19\,\rvir\,,
+&&&\beta_2^\rmn{sm}=0.54\,.\nonumber\\
+& && &&&
+\label{fit_spatial_IR}
+\end{align}
+The 3D spatial profile is derived by deprojecting the surface
+brightness in Eq.~(\ref{double_beta}) (see
+e.g. \cite{2004A&A...413...17P} for details about the deprojection):
+\begin{eqnarray}
+  j(r)  = \sum_{i=1}^2 \frac{\tilde{S}_i}{2\pi\,r_{\mathrm{c}_i}}\,
+  \frac{6 \beta_i - 1}{\left(1 + r^2/r^2_{\mathrm{c}_i}\right)^{3\beta_i}}\,
+  \mathcal{B}\left(\frac{1}{2},3\beta_i\right)\,,
+\end{eqnarray}
+where $\mathcal{B}(a,b)$ denotes the beta-function
+\cite{1965hmfw.book.....A}.
 

### 2011-04-10 paper.tex
update

@@
 three different mass scales. We find that the smooth luminosity per
-logaritmic radial bin peaks at $x \dd^2 L/\dd x^2+\dd L/\dd x == 0
-\rightarrow r \propto \rvir/3c$. Hence the main contribition to the
-luminosity for large mass scales, which are usually assosiated with a
+logarithmic radial bin peaks at $x \dd^2 L/\dd x^2+\dd L/\dd x == 0
+\rightarrow r \propto \rvir/3c$. Hence the main contribution to the
+luminosity for large mass scales, which are usually associated with a
 low concentrated DM halos, is focused to the regime around 10\% of
@@
 
-There is also a possiblity to search for dark matter annihilation
+There is also a possibility to search for dark matter annihilation
 indirectly in antimatter channels, like antiprotons or positrons. Here
@@
 describing these results contain some non-trivial, or even unnatural
-elements, however. First of all, annhilation to quarks has to be very
+elements, however. First of all, annihilation to quarks has to be very
 much suppressed, due to the non-observation of an enhanced antiproton
@@
 factor (of the order of at least several hundred), which is difficult
-to achieve with substrucutre alone. An additional enhancement of the
+to achieve with substructure alone. An additional enhancement of the
 annihilation rate has to be invoked, for example given by the {\em
@@
 of viable scenarios, see \cite{ArkaniHamed:2008qn}). As a final
-difficulty of these models, the lack of an inverse-compton signature
+difficulty of these models, the lack of an inverse-Compton signature
 from the galactic center means that only shallow density profiles can
@@
 more likely be explained by the standard scenario of a WIMP, for
-example the thoroughly studied lightest supersymmertric neutralino
+example the thoroughly studied lightest supersymmetric neutralino
 (for reviews, see
@@
 WIMP. However, the possibility of an enhanced annihilation rate due to
-dark matter halo substructure has been realised for a long time
+dark matter halo substructure has been realized for a long time
 \cite{1993ApJ...411..439S,Bergstrom:1998zs,Moore:1999nt}, although it
-is difficult to achieive the boost factor of the order of a few
-hundred to a thousand in the solar neighbourhood, as substructure
+is difficult to achieve the boost factor of the order of a few
+hundred to a thousand in the solar neighborhood, as substructure
 according to numerical simulations is most important in the outer
@@
 Sommerfeld effect, and the square of the relative wave function at the
-origin (which enters into the probablity for the short-distance
+origin (which enters into the probability for the short-distance
 process of annihilation) is increased by the factor
@@
 $$ with $\alpha =e^2/\hbar c$ the fine-structure constant, and $v$ the
-realtive velocity. This amounts to $S_{QED}=\pi\alpha/v$ for small
+relative velocity. This amounts to $S_{QED}=\pi\alpha/v$ for small
 velocities. For a Yukawa-like particle of mass $m_\phi$, mediating a
-weak attractive force with coupling contant $\alpha_Y$ between dark
+weak attractive force with coupling constant $\alpha_Y$ between dark
 matter particles $\chi$ with mass $m_\chi$, the small-velocity limit
@@
 some cases, the enhancement factor $S$ can be as high as several
-hundred to a few thousand, depnding however on the exact parameters of
+hundred to a few thousand, depending however on the exact parameters of
 the theory. The effect is usually strongly velocity-dependent,
-depending on velicity as $1/v$ or, in the fine-tuning case of being
+depending on velocity as $1/v$ or, in the fine-tuning case of being
 very near resonance, as $1/v^2$. This means that in a virialised
@@
 
-\subsubsection{Supersymetric dark matter}
+\subsubsection{Supersymmetric dark matter}
 The most studied models for dark matter are supersymmetric ones,
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/SB.photon.eps}
-\caption{\it Spatial dependence of light from stars and dust. We show
-  2D surface brightness profiles in the $r$-band ($\sim 1\,\ev$)
-  obtained from stacked clusters in the Sloan Digital Sky Survey
-  (SDSS) at the redshift $z \sim 0.25$ \cite{2005MNRAS.358..949Z}. The
-  brightness profiles have been weighted with the $\rvir$ normalized
-  area inside radius $r$, and trace the radial dependence of the
-  luminosity from stars and galaxies. The crosses show the total
-  observed starlight including the diffuse intracluster (ICL), the
-  galaxies, and the brightest cluster galaxy (BCG) in the center of
-  the cluster. The diamonds denote the observed starlight from the
-  ICL and the BCG. The solid line show the fit to the data of the
-  total light including the ICL, the BCG, and the galaxies, while the
-  smooth component is represented by the dashed line that is fitted to
-  only the ICL and the BCG.}
- \label{fig:SD_spatial}
+ \includegraphics[width=0.99\columnwidth]{figures/lum.stars.eps}
+\caption{\it accumulative luminosity}
+ \label{fig:SD_lum}
 \end{figure}
@@
 but increasing the distance by a factor two decrease the flux with a
-factor four. It is also usefull to relate the luminosities to a more
+factor four. It is also useful to relate the luminosities to a more
 model independent variable as the maximum circular velocity given by
@@
 upscattered CMB photons that are upscattered on an electron and
-positron population that suffers from efficent cooling on light from
+positron population that suffers from efficient cooling on light from
 SD. The IC emission from SD photons have a rather steep spectrum in
@@
 explained by the SD dominated cooling that cancels the spatial
-dependece from the SD spectrum. In the left panel we also find some
+dependence from the SD spectrum. In the left panel we also find some
 variation in the profiles for the different clusters in the central
@@
     includes the scaling of the substructure and Sommerfeld boost factors with
-    custer mass from Equation~(\ref{eq:LP_scaling}) (dash-dotted) as well as the
+    cluster mass from Equation~(\ref{eq:LP_scaling}) (dash-dotted) as well as the
     benchmark model $K'$ of DM annihilation that includes the scaling of the
@@
     indicative for all (non-Sommerfeld enhanced) DM annihilation models while
-    the normalization depends on the particular cross-section and neyralino
+    the normalization depends on the particular cross-section and neutralino
     masses.}
@@
 annihilation and argues for very nearby groups. We note that these simulations
-do not include AGn feedback that is thought to furthermore reduce the baryon
+do not include AGN feedback that is thought to furthermore reduce the baryon
 fraction in groups relative to that in clusters \cite{2008ApJ...687L..53P}. The
@@
 seems to be less bright than an average cluster of the same mass as Norma. The
-insenstitive limit on Perseus comes about since the central AGN in NGC1275 has
+insensitive limit on Perseus comes about since the central AGN in NGC1275 has
 turned on over the last years, making it hard to determine a comparable
@@
 which in turn biases the expected $\gamma$-ray fluxes systematically higher. We
-confirm this effect as all our outliers with increased fux in our semi-analytic
+confirm this effect as all our outliers with increased flux in our semi-analytic
 model relative to the scaling relation expectation are in fact cool core
-clusters suggesting that teh X-ray emission should be a good proxy for the
+clusters suggesting that the X-ray emission should be a good proxy for the
 expected $\gamma$-ray emission. Note however that there could be the
@@
 decrease the $\gamma$-ray luminosity \cite{2011A&A...527A..99E}. Future careful
-modelling is needed to quatify this effect.
+modelling is needed to quantify this effect.
 
@@
 (or constrain the substructure boost factor). Other nearby bright sources of the
-extended HIFLUCGS sample of nearby bright X-ray cluster/groups are M49,
+extended HIFLUGCS sample of nearby bright X-ray cluster/groups are M49,
 Centaurus, and NGC~4636.  The non-detection of $\gamma$-ray emission by Fermi in
@@
 the cluster (we assume that the cluster is optically thin). We derive
-the luminostity from the stars using
+the luminosity from the stars using
 \begin{eqnarray}
@@
 and distance to the cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. To
-account for different cluster masses in our analisys we adopt a simple
+account for different cluster masses in our analysis we adopt a simple
 mass scaling of the luminosity from the stars in clusters. Since a
@@
 richness scaling relation found in \cite{2008A&A...490..547G}
-$L_\dust=10^{44.8}\left(\frac{N_{200}}{10}\right)^{0.8}$. We pic a high
+$L_\dust=10^{44.8}\left(\frac{N_{200}}{10}\right)^{0.8}$. We pick a high
 richness $N_{200}=82$ cluster to normalize the luminosity since they
@@
 
+\begin{figure}%[t]
+ \includegraphics[width=0.99\columnwidth]{figures/SB.photon.eps}
+\caption{\it Spatial dependence of light from stars and dust. We show
+  2D surface brightness profiles in the $r$-band ($\sim 1\,\ev$)
+  obtained from stacked clusters in the Sloan Digital Sky Survey
+  (SDSS) at the redshift $z \sim 0.25$ \cite{2005MNRAS.358..949Z}. The
+  brightness profiles have been weighted with the $\rvir$ normalized
+  area inside radius $r$, and trace the radial dependence of the
+  luminosity from stars and galaxies. The crosses show the total
+  observed starlight including the diffuse intracluster (ICL), the
+  galaxies, and the brightest cluster galaxy (BCG) in the center of
+  the cluster. The diamonds denote the observed starlight from the
+  ICL and the BCG. The solid line show the fit to the data of the
+  total light including the ICL, the BCG, and the galaxies, while the
+  smooth component is represented by the dashed line that is fitted to
+  only the ICL and the BCG.}
+ \label{fig:SD_spatial}
+\end{figure}
 Our goal in this section is to derive a simple spatial model for the
@@
   \rmn{erg}\,\rmn{s}^{-1}$.}, both scaled with the unitless $\rvir$
-normalized area to resembele the expected luminosity at radius
+normalized area to resemble the expected luminosity at radius
 $r$. Our benchmark spatial model is shown with the solid black line,

### 2011-04-12 paper.tex
update
small changes

--- 2011-04-09 paper.tex
@@
 crowded region with many gamma-ray sources like pulsars and other
-supernova recants, which have to be subtracted from the data to
+supernova remnants, which have to be subtracted from the data to
 extract the dark matter induced signal. In fact, there is a recent
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v10.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v10.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v10.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v10.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v9.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v9.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v9.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v9.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
 \caption{\it Comparing the differential flux from different models: we
@@
 \begin{minipage}{2.0\columnwidth}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v10.0.1deg.1.6T.SubMass.elmu.SF300.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv10.0.1deg.SubMass.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v9.0.1deg.1.6T.SubMass.elmu.SF300.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv9.0.1deg.SubMass.noMW.woGal.eps}
 \caption{\it Comparing the flux from different inverse Compton
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
 \caption{\it Comparing the emission from different clusters. We show
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
 \caption{\it Constraining boost factors using flux upper limits. The
@@
 \begin{figure}
- \includegraphics[width=0.99\columnwidth]{figures/SB.v10.1GeV.SF300.SubMass.elmu.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.v9.1GeV.SF300.SubMass.elmu.eps}
 \caption{\it Comparing the surface brightness from different
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v10.1GeV.SF300.noSuB.vs.SubMass.elmu.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v9.1GeV.SF300.noSuB.vs.SubMass.elmu.eps}
 \caption{\it The impact of substructures on surface brightness. We
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.v10.1GeV.SF300.noSuB.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v10.1GeV.SF300.noSuB.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.v9.1GeV.SF300.noSuB.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v9.1GeV.SF300.noSuB.elmu.eps}
 \caption{\it The surface brightness without substructures. We show the
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v10.SF300.SubMass.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v10.SF300.SubMass.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v9.SF300.SubMass.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v9.SF300.SubMass.elmu.eps}
 \caption{\it Surface brightness predicted for Cherenkov telescopes at

### 2011-04-12 paper.tex

--- 2011-04-10 paper.tex
@@
 \begin{figure}
- \includegraphics[width=0.99\columnwidth]{figures/flux.int.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/flux.int.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
 \caption{\it Comparing the energy integrated flux from different

### 2011-04-20 paper.tex
update

--- 2011-04-10 paper.tex
@@
 direction $\psi$ that the detector is pointing, is parameterized such
-that the radius of the source $r=\sqrt{l^2+D^2-2 D l\cos\Psi}$, where
-$D$ is the distance to the source from the galactic center and
+that the radius of the source $r=\sqrt{l^2+D_\clu^2-2 D_\clu
+  l\cos\Psi}$, where $D_\clu$ is the distance to the source from the
+galactic center and
 $\cos\Psi\equiv\cos\theta\cos\psi-\cos\varphi\sin\theta\sin\psi$. The
@@
 by
-\begin{equation}
-  {\rm L_{sub}}(<r)= 0.76\,C_1\,C_2(\mvir)\,{\rm L_{200sm}}\,x^{0.95
-    \displaystyle{x}^{-0.27}}\,,
+\begin{eqnarray}
+  {\rm L_{sub}}(<r) &=& 0.76\,C_1\,C_2(\mvir)\,{\rm L_{200sm}}\,x^{a_0
+    \displaystyle{x}^{a_1}}\quad\rmn{where} \nonumber\\
+  a_0 = 0.95\,,\quad  a_1 = -0.27 \qquad \rmn{and} \nonumber\\
+  C(\mvir) = C_1\left(\frac{\mvir}{M_{\rm lim}}\right)^{0.226}\,.
+C_1  
 \label{eq:LSub}
-\end{equation}
+\end{eqnarray}
+Here
+
 where ${\rm L_{200sm}}$ is the luminosity from the smooth halo without
@@
 three different mass scales. We find that the smooth luminosity per
-logarithmic radial bin peaks at $x \dd^2 L/\dd x^2+\dd L/\dd x == 0
+logarithmic radial bin peaks at $x \dd^2 L/\dd x^2+\dd L/\dd x = 0
 \rightarrow r \propto \rvir/3c$. Hence the main contribution to the
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v10.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v10.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v10.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v10.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
 \caption{\it Comparing the differential flux from different models: we
@@
 \begin{minipage}{2.0\columnwidth}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v10.0.1deg.1.6T.SubMass.elmu.SF300.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv10.0.1deg.SubMass.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v11.0.1deg.1.6T.SubMass.elmu.SF300.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv11.0.1deg.SubMass.noMW.woGal.eps}
 \caption{\it Comparing the flux from different inverse Compton
@@
 \begin{figure}
- \includegraphics[width=0.99\columnwidth]{figures/flux.int.v9.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/flux.int.v11.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
 \caption{\it Comparing the energy integrated flux from different
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v11.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v11.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v11.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v11.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
 \caption{\it Comparing the emission from different clusters. We show
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v10.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v11.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
 \caption{\it Constraining boost factors using flux upper limits. The
@@
 \begin{figure}
- \includegraphics[width=0.99\columnwidth]{figures/SB.v10.1GeV.SF300.SubMass.elmu.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.v11.1GeV.SF300.SubMass.elmu.eps}
 \caption{\it Comparing the surface brightness from different
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v10.1GeV.SF300.noSuB.vs.SubMass.elmu.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v11.1GeV.SF300.noSuB.vs.SubMass.elmu.eps}
 \caption{\it The impact of substructures on surface brightness. We
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.v10.1GeV.SF300.noSuB.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v10.1GeV.SF300.noSuB.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.v11.1GeV.SF300.noSuB.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v11.1GeV.SF300.noSuB.elmu.eps}
 \caption{\it The surface brightness without substructures. We show the
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v10.SF300.SubMass.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v10.SF300.SubMass.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v11.SF300.SubMass.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v11.SF300.SubMass.elmu.eps}
 \caption{\it Surface brightness predicted for Cherenkov telescopes at

### 2011-04-22 paper.tex
update

--- 2011-04-20 paper.tex
@@
 \newcommand{\ds}{{\sc DarkSUSY}}
+\newcommand{\mlim}{M_\rmn{lim}}
 
@@
 \begin{abstract}
-... to be written...
+... to be written...  if $\mlim \approx 10^{-6}\,\msun$ then the boost
+  from SFE is smaller than about a factor 5 in the MW and 2 in Fornax, or
+  alternatively if SFE corrext then $\mlim > 10^2\,\msun$.
 \end{abstract}
@@
 
+This work studies the prospects for detecting extended gamma-ray
+emission from galaxy clusters induced by both DM as well as CR
+protons. In section two we discuss the theory of DM and gamma-rays. In
+particular, we focus one the leptophilic and supersymmetric DM models
+used in this work, and outline the framework for estimating the
+gamma-ray emission from various radiative processes. In section three
+we calculate the gamma-ray fluxes and spectral distributions from four
+clusters and compare it to upper limits set by Fermi-LAT. For the same
+clusters we derive the gamma-ray surface brightness profiles in
+section four. To extend the analysis to more clusters and find
+promesing targets we estimate the fluxes from DM and CRs of all
+clusters in the extended HIFLUGCS sample in section five. In section
+six we conclude and discuss our results.
+
 % --- section:  --- %
@@
 \label{sect:theory}
-
-\subsection{Astrophysics}
-\label{sect:AP}
-
-The differential photon flux within a given solid angle $\Delta
-\Omega$ along a line-of-sight (los) is given by
-\begin{equation}
-\label{eq:dflux}
-\frac{\dd \fg}{\dd \eg} \equiv \frac{\dd^3 \ngamma}{\dd A \,\dd t\, \dd
-  \egamma} = \frac{1}{2}\int_{\Delta\Omega} \dd\psi \sin\psi \frac{\dd \sg}{\dd \eg}(\psi,\eg)\,,
-\end{equation}
-where
-\begin{equation}
-\label{eq:dtildeflux}
-\frac{\dd \sg}{\dd \eg}(\psi,\eg) = \int_{\Delta\Omega} \dd\Omega \int_{\rm los}
-\dd l\, q_{\rm sum}\left(\eg,r\right)\Lambda(\theta)\,,
-\end{equation}
-and $\sg(\psi, >\eg)$ denotes the surface brightness above the photon
-energy $\eg$.  The integration along the line-of-sight $l$, in the
-direction $\psi$ that the detector is pointing, is parameterized such
-that the radius of the source $r=\sqrt{l^2+D_\clu^2-2 D_\clu
-  l\cos\Psi}$, where $D_\clu$ is the distance to the source from the
-galactic center and
-$\cos\Psi\equiv\cos\theta\cos\psi-\cos\varphi\sin\theta\sin\psi$. The
-angular integration $\dd \Omega= \sin\theta\dd \theta \,\dd \varphi$
-is performed over a cone centered around $\psi$ and the opening angle
-$\Delta \Omega$ is typically taken to be a few times the point spread
-function (PSF) $\psf$. The limited angular resolution results in a
-probability that a photon coming from a direction $\psi$' is instead
-reconstructed to a direction $\psi$, where the underlying probability
-distribution follow a Gaussian:
-\begin{equation}
-\Lambda(\theta)=\frac{1}{2\pi\psf^2}
-\,\rmn{exp}\left[-\frac{\theta^2}{2\psf^2}\right]\,,
-\quad \rmn{where}\quad \theta=\psi'-\psi \,.
-\end{equation}
-We denote the total differential source function by $q_{\rm
-  sum}(\eg,r)$, where we include contributions from five main
-processes; leptophilic DM annihilating either indirectly through
-$\mu^+/\mu^-$ to $\rmn{e}^+/\rmn{e}^-$ or directly to
-$\rmn{e}^+/\rmn{e}^-$ pairs that inverse Compton upscatter background
-photons (LP-IC), leptophilic DM emitting final state radiation
-(LP-FSR), supersymmetric DM benchmark models where annihilating
-neutralinos generate $\rmn{e}^+/\rmn{e}^-$ pairs that upscatter
-background photons (BM-IC) and emit a continuum as well as final state
-radiation (BM-Cont), and CR proton induced $\pi^0$:s decaying into
-gamma-rays (CR-$\pi^0$). The source function is given by
-\begin{equation}
-q_\rmn{sum} (\eg,r) = \qCR(\eg,r)+
-\sum_i \,q_{\rmn{sm},i}(\eg,r)\,\B_{\rmn{tot},i}(\sigv,r)
-\end{equation}
-the differential CR to gamma-ray source function is denoted by
-$\qCR(\eg,r)$ (see Sect.~\ref{sect:CRs} and \cite{2010MNRAS.409..449P}
-for further details). The subscript $i$ runs over the gamma-ray
-producing DM channels and the total differential boost factor for DM
-is given by $\B_{\rmn{tot},i}(r,\sigv) =
-\B_\sfe(\sigv)\,\B_{\sub,i}(r)$. It is the product of enhancement factors
-from SFE $\B_\sfe(\sigv)$ (see Sect.~\ref{sect:LP}) and from
-substructure enhancement over the smooth halo contribution
-$\B_{\sub,i}(r) = 1+q_\sub(r)/q_{\rmn{sm},i}(r)$ (see
-Sect.~\ref{sect:subst}). The DM source function from the smooth halo
-for each process is written on the form:
-\begin{equation}
-\label{eq:q_sm}
-q_{\rmn{sm},i} (\egamma,r) = \sum_j
-\frac{\dd \ngammaj}{\dd E_\gamma} \Gamma_j(r)\,,
-\end{equation}
-where the annihilation rate density is given by 
-\begin{equation}
-\label{eq:ann_rate}
-\Gamma_j(r) = \frac{1}{2} \left[\frac{\rho(r)}{\mx}\right]^2 
-\, \sigmaannv_j\,.
-\end{equation}
-Here the subscript $j$ runs over all kinematically allowed gamma-ray
-producing channels each with the spectrum $\frac{\dd
-  \ngammaj}{\dd\eg}$ and annihilation cross-section $\sigmaannv_j$. We
-denote the DM mass with $\mx$ and the DM density profile with
-$\rho(r)$. Typically the universal Navarro-Frenk-White (NFW) density
-profile provide a good fit to both the observed and simulated
-clusters. It can be considered as a special case of the more general
-5-parameter profile:
-\begin{equation}
-\rho(r) = \frac{\rhos}{\left(r/r_\s+\right)^\gamma
-  \left[1+\left(r/r_\s\right)^\alpha\right]^\delta}\,,\quad
-\delta=\frac{\beta-\gamma}{\alpha}\,,
-\label{eq:rho_nfw}
-\end{equation}
-where a cuspy NFW profile is given by
-$(\alpha,\beta,\gamma)=(1,3,1)$. The scaling radius is given by $r_\s$
-and the characteristic overdensity by 
-\begin{equation}
-\rhos(c)=\frac{\Delta\,\rhoc}{3}\,\frac{c^3}
-{\log\left(1+c\right)-c/(1+c)}\,,
-\label{eq:rho_s}
-\end{equation}
- where the halo mass dependent concentration parameter $c$ is derived
- from a power-law fit to cosmological simulations with $\mvir \gtrsim
- 10^{10} \msun$ \cite{2008MNRAS.391.1940M},
-\begin{equation}
-\label{eq:cfit}
-  c=3.56 \times \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-0.098}\,.
-\end{equation}
-This mass scaling agrees well with \cite{2009ApJ...707..354Z} for
-cluster-mass halos after converting the concentration definitions
-according to \cite{2003ApJ...584..702H}. In this work we choose to
-model the DM density by an Einasto density profile
-\begin{equation}
-\label{eq:dens_ein}
-\rho_{\rm ein}(r) = \rho_{-2}\,\exp\left\{-\frac{2}{\alpha}
-  \left[\left(\frac{r}{r_{-2}}\right)^\alpha -1 \right] \right\},\,
-\alpha=0.17 \,,
-\end{equation}
-that is slightly shallower in the center than the conventional
-Navarro-Frenk-White (NFW) profile, but provide a better fit to recent
-simulated high resolution DM halos \cite{2010MNRAS.402...21N}. It
-should also be noted that recent detailed galaxy cluster observations
-find a core like density profile with an inner slope of $\beta=0.6$,
-where $\beta\gtrsim 1$ can be ruled out to a $>95$\% confidence
-\cite{2011ApJ...728L..39N}. In Eq.~(\ref{eq:dens_ein}) we denote the
-density where the profile has a slope of $-2$ by $\rho_{-2}$, and the
-radius by $r_{-2}$. Assuming that all the flux from an NFW profile
-originate from within the scale radius $\rs=\rvir/c$, and all the flux
-from an Einasto profile originate within $r_{-2}=\rvir/c$, it follows
-that $\rho_{-2} = \rhos/4$.
-
-%However, this finding is hard to reconcile with simulations that
-%typically prefere a steeper central profile.
-
-\subsubsection{Substructures}
-\label{sect:subst}
-High-resolution DM only simulations of Milky Way (MW) type halos find
-substantial amount of substructures in the periphery of DM halos,
-while the substructures in the center are erased due to dynamical
-disruption. Since the rate of which DM is annihilating depends on the
-density squared, the resulting flux from substructures is boosted
-compared to the smooth density distribution. Recent high resolution
-simulations suggest a flux enhancement from substructures of the order
-of ten up to a few 100 \cite{2008MNRAS.391.1685S, 2008JPhCS.125a2008K}
-for a MW size halo. We use a double power-law function to
-fit \footnote{Our approach of fitting the scaling behavior of
-  $\rmn{L_{sub}}(<r)$ directly from numerical simulations
-  self-consistently accounts for the radial dependence of the
-  substructure concentration \cite{2008MNRAS.391.1685S}.} the
-luminosity from the smooth component of substructures
-(i.e. substructures within substructures are not included) inside
-radius $r$ which is determined for the Aquarius simulations
-\cite{2008MNRAS.391.1685S,2008Natur.456...73S}. Our best fit is given
-by
-\begin{eqnarray}
-  {\rm L_{sub}}(<r) &=& 0.76\,C_1\,C_2(\mvir)\,{\rm L_{200sm}}\,x^{a_0
-    \displaystyle{x}^{a_1}}\quad\rmn{where} \nonumber\\
-  a_0 = 0.95\,,\quad  a_1 = -0.27 \qquad \rmn{and} \nonumber\\
-  C(\mvir) = C_1\left(\frac{\mvir}{M_{\rm lim}}\right)^{0.226}\,.
-C_1  
-\label{eq:LSub}
-\end{eqnarray}
-Here
-
-where ${\rm L_{200sm}}$ is the luminosity from the smooth halo without
-substructures within $\rvir$ and $x=
-\left(\frac{r}{\rvir}\right)$. The first normalization constant is
-derived from the simulations:
-\begin{equation}
-  C_1=\left(\frac{M_{\rm res,sim}}{M_{\rm lim}}\right)^{0.226}\,,
-   \label{eq:C1}
-\end{equation}
-where $M_{\rm res,sim}=10^5\msun$ is the mass of the smallest resolved
-subhalos in the MW simulation, and $M_{\rm lim}$ is the theoretical
-smallest mass of subhalos determined from free streaming length of DM
-(CHECK). Here we assume that the power-law scaling relation in
-Eq.~(\ref{eq:C1}) is valid down to the free streaming mass of DM
-halos, which is conventionally in the cold dark matter universe
-\cite{2001PhRvD..64h3507H,2005JCAP...08..003G} taken to be
-$10^{-6}\msun$. Note that potentially the power-law could flatten
-towards smaller mass scales although current simulations show no hits
-of such a behavior and in addition we are approaching the asymptotic
-behavior in the power spectrum on these scales(CHECK). For DM halos
-more (less) massive than the MW we expect a larger (smaller) boost
-from substructures, simply because of the larger (smaller) mass range
-down to the minimum mass $M_\rmn{lim}$. We capture this halo mass
-dependence with the second normalization in Eq.~(\ref{eq:LSub}):
-\begin{equation}
-C_2(\mvir)=\left(\frac{\mvir}{M_{\rm 200sim}}\right)^{0.226}\,,
- \label{eq:C2}
-\end{equation}
-where $M_{\rm 200sim}=1.9\times10^{12}\msun$ is the mass of the MW
-halo in the simulation \cite{2008Natur.456...73S}.
-
-The different density profiles have a large impact on the luminosity
-from annihilating DM, although the details of the density profile can
-be neglected compared to the dominating boost from substructures. In
-Fig.~\ref{fig:radial_lum} we compare the radial dependence of the
-accumulative luminosity from different smooth cluster density profiles
-to the substructure boosted luminosity at different mass scales. We
-recalculate the density contrast for the core like NFW density profile
-$\rhos$ and rescale the concentration parameter in Eq.~(\ref{eq:cfit})
-with $300/160$ \cite{2011ApJ...728L..39N} to account for the more
-centralized scale radius in cluster with a softer cusp. The emission
-coming from the core like NFW density profile ($\beta=0.6$) compared
-to a cuspy ($\beta=1.0$) is about 30\% larger within $\rvir$. This
-difference is build up within 10\% of $\rvir$ (i.e. close to
-$r_\s$). Hence the slope of the central part of a cluster is
-unimportant for the DM luminosity inside $\rvir$, instead the
-important factor is the scale radius. The emission from an Einasto
-density profile is about 50\% larger than the cuspy NFW profile in the
-periphery of the cluster, where the difference is mainly build up at a
-few percent of $\rvir$. The substructure boosted luminosities is
-neglible in the center of halos, but integrated out to $\rvir$ the
-boost is about; 10 for dwarf galaxies, $10^2$ for galaxies, and $10^3$
-for galaxy clusters.
-\begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/dens.prof.eps}
-\caption{\it Radial dependence of various luminosity
-  contributions. The solid lines show the accumulative smooth
-  luminosity from a cluster with the mass $\mvir=10^{15}\,\msun$ for
-  three different density profiles; an Einasto profile with
-  $\alpha=0.17$ (light blue), a cuspy NFW profile with $\beta=1.0$
-  (dark blue), and a core NFW profile with $\beta=0.6$ (purple). The
-  dashed lines show the accumulative luminosity from substructures for
-  three different mass scales; an $\mvir=10^{15}\,\msun$ galaxy
-  cluster (red), an $\mvir=10^{12}\,\msun$ galaxy (orange), and an
-  $\mvir=10^{8}\,\msun$ dwarf galaxy (green). All luminosities have
-  been normalized with the luminosity within $\rvir$ from a cuspy NFW
-  profile. We have assumed the standard value for the limiting
-  substructure mass of $M_\rmn{lim}=10^{-6}\,\msun$. Note the large
-  expected boost from substructures in clusters ($\sim1000$), and the
-  relative small boost in dwarf galaxies ($\sim20$).}
- \label{fig:radial_lum}
-\end{figure}
-
-In Fig.~\ref{fig:radial_emis} we show the radius with the maximum
-luminosity for substructures and smooth density profiles, both for
-three different mass scales. We find that the smooth luminosity per
-logarithmic radial bin peaks at $x \dd^2 L/\dd x^2+\dd L/\dd x = 0
-\rightarrow r \propto \rvir/3c$. Hence the main contribution to the
-luminosity for large mass scales, which are usually associated with a
-low concentrated DM halos, is focused to the regime around 10\% of
-$\rvir$.  It clearly shows how that the main contribution from the
-substructures is coming from outer parts of the DM halos, while the
-main contribution from the smooth density profiles peaks around the
-scale radius. Not that, even though the bulk of substructures have
-been erased in the central regions of DM halos, a cluster in
-projection has a significant enhancement due to substructures at a
-radius of just a few percent of $\rvir$.
-\begin{figure}
-  \includegraphics[width=0.99\columnwidth]{figures/emissiv.sub.eps}
-  \caption{\it Luminosity dominated radius for different mass
-    scales. The solid lines show the emissivity from a cuspy
-    $\beta=1.0$ NFW density profile for three different mass scales;
-    an $\mvir=10^{15}\,\msun$ galaxy cluster (red), an
-    $\mvir=10^{12}\,\msun$ galaxy (orange), and an
-    $\mvir=10^{8}\,\msun$ dwarf galaxy (green). The dashed lines show
-    the emissivity from substructures for the same three mass
-    scales. All emissivities have been normalized with the luminosity
-    within $\rvir$ from a cuspy NFW profile. We have assumed the
-    standard value for the limiting substructure mass of
-    $M_\rmn{lim}=10^{-6}\,\msun$.}
-  \label{fig:radial_emis}
-\end{figure}
-
-\subsubsection{Cosmic-ray induced gamma-ray emission}
-\label{sect:CRs}
-On small astrophysical scales, such as supernovae remnants and
-galaxies, there are convincing evidences of non-thermal
-populations. Especially, in the MW, the cosmic rays are observed
-directly as well as indirectly through radio, X-ray, and gamma-ray
-emission. On larger scales of the order of few 100~kpc up to Mpc,
-there are currently a vast number of observations of radio emission
-coming from radio mini halos in the center of cooling flow clusters,
-radio relics in the periphery of clusters \cite{2004rcfg.proc..335K}
-as well as smooth giant radio halos that have been observed in more
-than 50 clusters \cite{2003ASPC..301..143F,2008SSRv..134...93F}. This
-type of emission is expected in clusters since the formation process
-of a galaxy cluster is a very energetic processes that induces both
-turbulence as well as frequently occurring merging and accretion
-shocks which both are thought to accelerate large quantities of
-relativistic non-thermal protons and radio emitting electrons to high
-energies. Thus most of the observed radio emission in clusters is
-expected to emerge from cosmic-ray electron induced radio synchrotron
-emission. The precise origin of these electrons, in especially relics
-and giant radio halos, is still not settled. However, due to the
-smoothness of the extended emission and the observed power-law slope
-it seems quite natural that they are of hadronic origin. Especially
-since the long cooling time of cosmic ray protons (CRps) allows for
-both an extended and large population of CRps to build up over the
-cluster history \cite{1997ApJ...487..529B}.
-
-When the CRps interact with ambient gas protons, it results in the
-production of both charged and neutral pions that decay into
-electrons, neutrinos, and gamma-rays. The production of these
-secondaries depend both on the gas and CRp densities in the cluster,
-where the CRp density roughly trace the gas outside the core regime and
-is slightly enhanced in the center. This density scaling implies that
-clusters are great targets for Cherenkov telescopes with a high
-sensitivity for the central parts of close by clusters. Detecting the
-cluster gamma-ray emission is crucial in this respect as it
-potentially provides the unique and unambiguous evidence of CRp
-populations in clusters through observing the $\pi^0$ bump at about
-100~MeV in the spectra.
-
-We adopt the spectrally and spatially universal gamma-ray model
-developed by Pinzke \& Pfrommer \cite{2010MNRAS.409..449P} to estimate
-the emission from decaying $\pi^0$:s that dominates over the inverse
-Compton emission from primary and secondary electrons above 100~MeV in
-clusters. The gamma-ray formalism was derived from high resolution
-simulations of clusters of galaxies that included radiative
-hydrodynamics, star formation, supernova feedback, and followed CRp
-physics using a novel formulation that trace the most important
-injection and loss processes self-consistently while accounting for
-the CRp pressure in the equation of motion
-\cite{2008A&A...481...33J,2007A&A...473...41E,2006MNRAS.367..113P}.
-We note that the overall normalization of the CRp and gamma-ray
-distribution scales with the maximum acceleration efficiency at
-structure formation shock waves. Following recent observations at
-supernova remnants \cite{2009Sci...325..719H} as well as theoretical
-studies \cite{2005ApJ...620...44K}, we adopt a realistic value of this
-parameter and assume that 50\% of the dissipated energy at strong
-shocks is injected into CRps while this efficiency rapidly decreases
-for weaker shocks \cite{2007A&A...473...41E}.
+We start the section by discussing two different, but well motivated DM
+models; leptophilic and supersymmetric DM. In addition we present the
+gamma-ray framework that is used to calculate the emission for these DM
+models using an Einasto DM density profile and the expected
+enhancement from DM substructures. In the end of this sections we
+outline the framework of inverse Compton emission on both CMB photons
+as well as photons from stars and dust.
 
@@
 process - which should be close to observability with the Fermi-LAT
-data \cite{Berezinsky:1996wx,2007A&A...473...41E,2010MNRAS.409..449P}
+data \cite{1997ApJ...487..529B,2007A&A...473...41E,2010MNRAS.409..449P}
 - the possible contribution from WIMP dark matter is of greatest
@@
 
+\subsection{Astrophysics}
+\label{sect:AP}
+
+The differential photon flux within a given solid angle $\Delta
+\Omega$ along a line-of-sight (los) is given by
+\begin{equation}
+\label{eq:dflux}
+\frac{\dd \fg}{\dd \eg} \equiv \frac{\dd^3 \ngamma}{\dd A \,\dd t\, \dd
+  \egamma} = \frac{1}{2}\int_{\Delta\Omega} \dd\psi \sin\psi \frac{\dd \sg}{\dd \eg}(\psi,\eg)\,,
+\end{equation}
+where
+\begin{equation}
+\label{eq:dtildeflux}
+\frac{\dd \sg}{\dd \eg}(\psi,>\eg) = \int_{\Delta\Omega} \dd\Omega \int_{\rm los}
+\dd l\, q_{\rm sum}\left(\eg,r\right)\Lambda(\theta)\,,
+\end{equation}
+and $\sg(\psi, >\eg)$ denotes the surface brightness above the photon
+energy $\eg$.  The integration along the line-of-sight $l$, in the
+direction $\psi$ that the detector is pointing, is parameterized such
+that the radius of the source $r=\sqrt{l^2+D_\clu^2-2 D_\clu
+  l\cos\Psi}$, where $D_\clu$ is the distance to the source from the
+galactic center and
+$\cos\Psi\equiv\cos\theta\cos\psi-\cos\varphi\sin\theta\sin\psi$. The
+angular integration $\dd \Omega= \sin\theta\dd \theta \,\dd \varphi$
+is performed over a cone centered around $\psi$ and the opening angle
+$\Delta \Omega$ is typically taken to be a few times the point spread
+function (PSF) $\psf$. The limited angular resolution results in a
+probability that a photon coming from a direction $\psi$' is instead
+reconstructed to a direction $\psi$, where the underlying probability
+distribution follow a Gaussian:
+\begin{equation}
+\Lambda(\theta)=\frac{1}{2\pi\psf^2}
+\,\rmn{exp}\left[-\frac{\theta^2}{2\psf^2}\right]\,,
+\quad \rmn{where}\quad \theta=\psi'-\psi \,.
+\end{equation}
+We denote the total differential source function by $q_{\rm
+  sum}(\eg,r)$, where we include contributions from five main
+processes; leptophilic DM annihilating either indirectly through
+$\mu^+/\mu^-$ to $\rmn{e}^+/\rmn{e}^-$ or directly to
+$\rmn{e}^+/\rmn{e}^-$ pairs that inverse Compton upscatter background
+photons (LP-IC), leptophilic DM emitting final state radiation
+(LP-FSR), supersymmetric DM benchmark models where annihilating
+neutralinos generate $\rmn{e}^+/\rmn{e}^-$ pairs that upscatter
+background photons (BM-IC) and emit a continuum as well as final state
+radiation (BM-Cont), and CR proton induced $\pi^0$ that decays into
+gamma-rays (CR-$\pi^0$). The source function is given by
+\begin{equation}
+q_\rmn{sum} (\eg,r) = \qCR(\eg,r)+
+\sum_i \,q_{\rmn{sm},i}(\eg,r)\,\B_{\rmn{tot},i}(\sigv,r)
+\end{equation}
+the differential CR to gamma-ray source function is denoted by
+$\qCR(\eg,r)$ (see Sect.~\ref{sect:CRs} and \cite{2010MNRAS.409..449P}
+for further details). The subscript $i$ runs over the gamma-ray
+producing DM channels and the total differential boost factor for DM
+is given by:
+\begin{eqnarray}
+\B_{\rmn{tot},i}(r,\sigv) = \left\{\begin{array}{cc}
+\B_\sfe(\sigv)\,\B_{\sub,i}(r) &\rmn{for\,\,LP}\\
+\B_{\sub,i}(r) &\rmn{for\,\,BM\,.}\end{array}\right.
+\end{eqnarray}
+It is the product of enhancement factors from SFE $\B_\sfe(\sigv)$
+(see Sect.~\ref{sect:LP}) and from substructure enhancement over the
+smooth halo contribution $\B_{\sub,i}(r) =
+1+\rho_{\sub,i}^2(r)/\rho^2(r)$ (see Sect.~\ref{sect:subst}). The DM
+source function from the smooth halo for each process is written in
+the form:
+\begin{equation}
+\label{eq:q_sm}
+q_{\rmn{sm},i} (\egamma,r) = \sum_j
+\frac{\dd \ngammaj}{\dd E_\gamma} \Gamma_j(r)\,,
+\end{equation}
+where the annihilation rate density is given by 
+\begin{equation}
+\label{eq:ann_rate}
+\Gamma_j(r) = \frac{1}{2} \left[\frac{\rho(r)}{\mx}\right]^2 
+\, \sigmaannv_j\,.
+\end{equation}
+Here runs the subscript $j$ over all kinematically allowed gamma-ray
+producing channels, each with the spectrum $\frac{\dd
+  \ngammaj}{\dd\eg}$ and annihilation cross-section $\sigmaannv_j$. We
+denote the DM mass with $\mx$ and the DM density profile with
+$\rho(r)$. Typically the universal Navarro-Frenk-White (NFW) density
+profile provides a good fit to both the observed and simulated
+clusters. It can be considered as a special case of the more general
+5-parameter profile:
+\begin{equation}
+\rho(r) = \frac{\rhos}{\left(r/r_\s+\right)^\gamma
+  \left[1+\left(r/r_\s\right)^\alpha\right]^\delta}\,,\quad
+\delta=\frac{\beta-\gamma}{\alpha}\,,
+\label{eq:rho_nfw}
+\end{equation}
+where a cuspy NFW profile is given by
+$(\alpha,\beta,\gamma)=(1,3,1)$. The scaling radius is given by $r_\s$
+and the characteristic overdensity by 
+\begin{equation}
+\rhos(c)=\frac{\Delta\,\rhoc}{3}\,\frac{c^3}
+{\log\left(1+c\right)-c/(1+c)}\,,
+\label{eq:rho_s}
+\end{equation}
+ where the halo mass dependent concentration parameter $c$ is derived
+ from a power-law fit to cosmological simulations with $\mvir \gtrsim
+ 10^{10} \msun$ \cite{2008MNRAS.391.1940M},
+\begin{equation}
+\label{eq:cfit}
+  c=3.56 \times \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-0.098}\,.
+\end{equation}
+This mass scaling agrees well with \cite{2009ApJ...707..354Z} for
+cluster-mass halos after converting the concentration definitions
+according to \cite{2003ApJ...584..702H}. In this work we choose to
+model the DM density by an Einasto density profile
+\begin{equation}
+\label{eq:dens_ein}
+\rho_{\rm ein}(r) = \rho_{-2}\,\exp\left\{-\frac{2}{\alpha}
+  \left[\left(\frac{r}{r_{-2}}\right)^\alpha -1 \right] \right\},\,
+\alpha=0.17 \,,
+\end{equation}
+that is slightly shallower in the center than the conventional
+Navarro-Frenk-White (NFW) profile, but provide a better fit to recent
+simulated high resolution DM halos \cite{2010MNRAS.402...21N}. It
+should also be noted that a recent observations of the Abell 383
+galaxy cluster finds a core like density profile with an inner slope
+of $\beta=0.6$, where $\beta\gtrsim 1$ can be ruled out to a $>95$\%
+confidence \cite{2011ApJ...728L..39N}. These observations are based on
+lensing and X-ray measurements as well as the stellar velocity
+dispersion of the central galaxy. In Eq.~(\ref{eq:dens_ein}) we denote
+the density where the profile has a slope of $-2$ by $\rho_{-2}$, and
+the radius by $r_{-2}$.  Assuming that all the flux from an NFW profile
+originate from within the scale radius $\rs=\rvir/c$, and all the flux
+from an Einasto profile originate within $r_{-2}=\rvir/c$, it follows
+that $\rho_{-2} = \rhos/4$. [MIGHT REMOVE THIS, COULD NOT REPRODUCE IT, CAN
+MOTIVATE THE FACTOR 4 FROM MATCHING THE MASSES FROM THE EINSASTO WITH
+THE NFW INSTEAD] SHOW INTEGRATION, COMPUTE RMAX, DISCUSS
+FIG 1+2 SMOOTH COMPONENT
+
+%However, this finding is hard to reconcile with simulations that
+%typically prefere a steeper central profile.
+
+\subsubsection{Substructures}
+\label{sect:subst}
+High-resolution DM only simulations of Milky Way (MW) type halos find
+substantial amount of substructures in the periphery of DM halos,
+while the substructures in the center suffer from dynamical friction
+and tidal effects depleating their central number densities. Since
+the rate of which DM is annihilating depends on the density squared,
+the resulting flux from substructures is boosted compared to the
+smooth density distribution. Recent high resolution simulations
+suggest a flux enhancement from substructures of the order of ten up
+to a few 100 \cite{2008MNRAS.391.1685S, 2008JPhCS.125a2008K} for a MW
+size halo. We use a double power-law function to fit \footnote{Our
+  approach of fitting the scaling behavior of $\rmn{L_{sub}}(<r)$
+  directly from numerical simulations self-consistently accounts for
+  the radial dependence of the substructure concentration
+  \cite{2008MNRAS.391.1685S}.} the luminosity from the smooth
+component of substructures (i.e. substructures within substructures
+are not included) inside radius $r$ which is determined for the
+Aquarius simulations
+\cite{2008MNRAS.391.1685S,2008Natur.456...73S}. Our best fit is given
+by
+\begin{eqnarray}
+  {\rm L_{sub}}(<x) &=& a_0\,C(\mvir)\,{\rm L_{200sm}}(\mvir)\,x^{a_1
+    \displaystyle{x}^{a_2}}\,,\quad\rmn{where} \nonumber\\
+   a_0 &=& 0.76\,,\quad a_1 = 0.95\,,\quad  a_2 = -0.27\,, \quad 
+\rmn{and} \nonumber\\
+\label{eq:LSub} \\
+  C(\mvir) &=& 0.023\,\left(\frac{\mvir}{M_{\rm lim}}\right)^{0.226}\,.
+\label{eq:Csub}
+\end{eqnarray}
+Here $a_i$ denote our fitted variables, ${\rm L_{200sm}}$ is the
+luminosity from the smooth halo without substructures within $\rvir$
+and $x= \left(\frac{r}{\rvir}\right)$. The theoretical smallest mass
+of subhalos $M_{\rm lim}$ is determined from free streaming length of
+DM (CHECK), where we assume that the mass power-law scaling relation
+in Eq.~(\ref{eq:Csub}) is valid down to the free streaming mass of DM
+halos. This is conventionally in the cold dark matter universe
+\cite{2001PhRvD..64h3507H,2005JCAP...08..003G} taken to be
+$10^{-6}\msun$. Note that potentially the power-law could flatten
+towards smaller mass scales although current simulations show no hits
+of such a behavior and in addition we are approaching the asymptotic
+behavior in the power spectrum on these scales(CHECK). We derive the
+normalization function $C(\mvir)$ in Eq.~(\ref{eq:Csub}) from the
+simulations in \cite{2008Natur.456...73S}:
+\begin{equation}
+\left(\frac{\mvir\,M_{\rm res,sim}}
+{M_{\rm 200sim}\,M_{\rm lim}}\right)^{0.226}\,.
+ \label{eq:C2}
+\end{equation}
+Here $M_{\rm 200sim}=1.9\times10^{12}\msun$ is the mass of the MW halo
+in the simulation and $M_{\rm res,sim}=10^5\msun$ is the mass of the
+smallest resolved subhalos in the MW simulation. For DM halos more
+(less) massive than the MW we expect a larger (smaller) boost from
+substructures, simply because of the larger (smaller) mass range down
+to the minimum mass $M_\rmn{lim}$.
+
+Finally we derive the squared density profile for the substructures
+using
+\begin{eqnarray}
+\rho_\rmn{sub}^2(r) &=& \frac{\dd \rmn{L_{sub}}}{\dd V} \frac{1}{\rmn{L_{200sm}}}
+\int_{\rvir} \dd r' 4\pi r'^2 \rho^2(r')\qquad\rmn{where}\nonumber\\
+ \frac{\dd \rmn{L_{sub}}}{\dd V} &=& a_0\,a_1\,C(\mvir)\,x^{a_2+a_1\,x^{a_2}}\,
+\left[\frac{1+a_2\log(x)}{4\pi\,r^3}\right]\quad\rmn{and}\nonumber\\
+x &=& r/\rvir\,.
+\end{eqnarray}
+
+The different density profiles have a large impact on the luminosity
+from annihilating DM, although the details of the density profile can
+be neglected compared to the dominating boost from substructures. In
+Fig.~\ref{fig:radial_lum} we compare the radial dependence of the
+accumulative luminosity from different smooth cluster density profiles
+to the substructure boosted luminosity at different mass scales. We
+recalculate the density contrast for the core like NFW density profile
+$\rhos$ and rescale the concentration parameter in Eq.~(\ref{eq:cfit})
+with $300/160$ \cite{2011ApJ...728L..39N} to account for the more
+centralized scale radius in cluster with a softer cusp. The emission
+coming from the core like NFW density profile ($\beta=0.6$) compared
+to a cuspy ($\beta=1.0$) is about 30\% larger within $\rvir$. This
+difference is build up within 10\% of $\rvir$ (i.e. close to
+$r_\s$). Hence the slope of the central part of a cluster is
+unimportant for the DM luminosity inside $\rvir$, instead the
+important factor is the scale radius. The emission from an Einasto
+density profile is about 50\% larger than the cuspy NFW profile in the
+periphery of the cluster, where the difference is mainly build up at a
+few percent of $\rvir$. The substructure boosted luminosities is
+neglible in the center of halos, but integrated out to $\rvir$ the
+boost is about; 10 for dwarf galaxies, $10^2$ for galaxies, and $10^3$
+for galaxy clusters.
+\begin{figure}%[t]
+ \includegraphics[width=0.99\columnwidth]{figures/dens.prof.eps}
+\caption{\it Radial dependence of various luminosity
+  contributions. The solid lines show the accumulative smooth
+  luminosity from a cluster with the mass $\mvir=10^{15}\,\msun$ for
+  three different density profiles; an Einasto profile with
+  $\alpha=0.17$ (light blue), a cuspy NFW profile with $\beta=1.0$
+  (dark blue), and a core NFW profile with $\beta=0.6$ (purple). The
+  dashed lines show the accumulative luminosity from substructures for
+  three different mass scales; an $\mvir=10^{15}\,\msun$ galaxy
+  cluster (red), an $\mvir=10^{12}\,\msun$ galaxy (orange), and an
+  $\mvir=10^{8}\,\msun$ dwarf galaxy (green). All luminosities have
+  been normalized with the luminosity within $\rvir$ from a cuspy NFW
+  profile. We have assumed the standard value for the limiting
+  substructure mass of $M_\rmn{lim}=10^{-6}\,\msun$. Note the large
+  expected boost from substructures in clusters ($\sim1000$), and the
+  relative small boost in dwarf galaxies ($\sim20$).}
+ \label{fig:radial_lum}
+\end{figure}
+
+In Fig.~\ref{fig:radial_emis} we show the radius with the maximum
+luminosity for substructures and smooth density profiles, both for
+three different mass scales. We find that the smooth luminosity per
+logarithmic radial bin peaks at $x \dd^2 L/\dd x^2+\dd L/\dd x = 0
+\rightarrow r \propto \rvir/3c$. Hence the main contribution to the
+luminosity for large mass scales, which are usually associated with a
+low concentrated DM halos, is focused to the regime around 10\% of
+$\rvir$.  It clearly shows how that the main contribution from the
+substructures is coming from outer parts of the DM halos, while the
+main contribution from the smooth density profiles peaks around the
+scale radius. Not that, even though the bulk of substructures have
+been erased in the central regions of DM halos, a cluster in
+projection has a significant enhancement due to substructures at a
+radius of just a few percent of $\rvir$.
+\begin{figure}
+  \includegraphics[width=0.99\columnwidth]{figures/emissiv.sub.eps}
+  \caption{\it Luminosity dominated radius for different mass
+    scales. We show the normalized luminosity per logaritmic radial
+    bin which corresponds to $x^3\rho^2/\rho^2_{200}$ where
+    $\rho_{200}$ is the density at $\rvir$. The solid lines represents
+    cuspy $\beta=1.0$ NFW density profiles for three different mass
+    scales; an $\mvir=10^{15}\,\msun$ galaxy cluster (red), an
+    $\mvir=10^{12}\,\msun$ galaxy (orange), and an
+    $\mvir=10^{8}\,\msun$ dwarf galaxy (green). The dashed lines show
+    the contribution from substructures for the same three mass
+    scales. All luminosities have been normalized with the luminosity
+    within $\rvir$ from a cuspy NFW profile. We have assumed the
+    standard value for the limiting substructure mass of
+    $M_\rmn{lim}=10^{-6}\,\msun$. The peaks show that the flux is not
+    dominated by the center of the halos, but instead by the core
+    region for the smooth density profile and by the outer parts for
+    the substructures.}
+  \label{fig:radial_emis}
+\end{figure}
+
+\subsubsection{Cosmic-ray induced gamma-ray emission}
+\label{sect:CRs}
+On small astrophysical scales, such as supernovae remnants and
+galaxies, there are convincing evidences of non-thermal
+populations. Especially, in the MW, the cosmic rays are observed
+directly as well as indirectly through radio, X-ray, and gamma-ray
+emission. On larger scales of the order of few 100~kpc up to Mpc,
+there are currently a vast number of observations of radio emission
+coming from radio mini halos in the center of cooling flow clusters,
+radio relics in the periphery of clusters \cite{2004rcfg.proc..335K}
+as well as smooth giant radio halos that have been observed in more
+than 50 clusters \cite{2003ASPC..301..143F,2008SSRv..134...93F}. This
+type of emission is expected in clusters since the formation process
+of a galaxy cluster is a very energetic processes that induces both
+turbulence as well as frequently occurring merging and accretion
+shocks which both are thought to accelerate large quantities of
+relativistic non-thermal protons and radio emitting electrons to high
+energies. Thus most of the observed radio emission in clusters is
+expected to emerge from cosmic-ray electron induced radio synchrotron
+emission. The precise origin of these electrons, in especially relics
+and giant radio halos, is still not settled. However, due to the
+smoothness of the extended emission and the observed power-law slope
+it seems quite natural that they are of hadronic origin. Especially
+since the long cooling time of cosmic ray protons (CRps) allows for
+both an extended and large population of CRps to build up over the
+cluster history \cite{1997ApJ...487..529B}.
+
+When the CRps interact with ambient gas protons, it results in the
+production of both charged and neutral pions that decay into
+electrons, neutrinos, and gamma-rays. The production of these
+secondaries depend both on the gas and CRp densities in the cluster,
+where the CRp density roughly trace the gas outside the core regime and
+is slightly enhanced in the center. This density scaling implies that
+clusters are great targets for Cherenkov telescopes with a high
+sensitivity for the central parts of close by clusters. Detecting the
+cluster gamma-ray emission is crucial in this respect as it
+potentially provides the unique and unambiguous evidence of CRp
+populations in clusters through observing the $\pi^0$ bump at about
+100~MeV in the spectra.
+
+We adopt the universal spectral and spatial gamma-ray model developed
+by Pinzke \& Pfrommer \cite{2010MNRAS.409..449P} to estimate the
+emission from decaying $\pi^0$:s that dominates over the inverse
+Compton emission from primary and secondary electrons above 100~MeV in
+clusters. The gamma-ray formalism was derived from high resolution
+simulations of clusters of galaxies that included radiative
+hydrodynamics, star formation, supernova feedback, and followed CRp
+physics using a novel formulation that trace the most important
+injection and loss processes self-consistently while accounting for
+the CRp pressure in the equation of motion
+\cite{2008A&A...481...33J,2007A&A...473...41E,2006MNRAS.367..113P}.
+We note that the overall normalization of the CRp and gamma-ray
+distribution scales with the maximum acceleration efficiency at
+structure formation shock waves. Following recent observations at
+supernova remnants \cite{2009Sci...325..719H} as well as theoretical
+studies \cite{2005ApJ...620...44K}, we adopt a realistic value of this
+parameter and assume that 50\% of the dissipated energy at strong
+shocks is injected into CRps while this efficiency rapidly decreases
+for weaker shocks \cite{2007A&A...473...41E}.
+
 \subsection{Radiative processes}
@@
 for the galaxies and the ICM in these wavelengths. Hence, we use the
-accurately measured light from galactic dust and starlight for the ISM
-to model the ICM. We characterize the spectra through a fit to the
-galactic spectra presented in \cite{2006ApJ...648L..29P}. The spatial
-distribution of the SD light in clusters is extracted from a stacked
-emission analysis of Sloan Digital Sky Survey (SDSS) data at the
-redshift $\sim 0.25$ \cite{2005MNRAS.358..949Z}. Finally, we fix the
-normalization for the light from stars and dust individually in a
-galaxy cluster using using the IR to X-ray luminosity scaling relation
-found in \cite{2008A&A...490..547G}. The X-ray luminosities for the
-clusters used in this work are listed in the extended HIghest X-ray
-FLUx Galaxy Cluster Sample (HIFLUGCS) \cite{2002ApJ...567..716R} from
-the Rosat all-sky survey. Note that we have added the Virgo cluster to
-the sample that we nevertheless refer to as extended HIFLUGCS
-catalogue in the following.
-
-\begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/lum.stars.eps}
-\caption{\it accumulative luminosity}
- \label{fig:SD_lum}
-\end{figure}
+accurately measured light from galactic dust and starlight in the ISM
+to model the ICM. In Fig.~\ref{fig:SD_spectra} we characterize the
+spectral shape through a fit to the galactic spectra presented in
+\cite{2006ApJ...648L..29P}. We fix the normalization for the energy
+density of light from stars and dust in a galaxy cluster individually
+using observed luminosities from SD. In addition, we attach a mass
+scaling to the normalization which we adopt from a simple
+mass-to-starlight luminosity scaling relation derived from
+observations of the brightest cluster galaxy
+\cite{2010ApJ...713.1037H}. The figure is showing the spectra at
+$r=0.03\rvir$, which is the radius there the SD energy density equals
+the energy density of the CMB black-body distribution in a galaxy
+cluster. Inside this central radius the SD component is dominating,
+which is shown in Fig.~\ref{fig:SD_Edens} where we compare the energy
+densities from different radiation fields in a galaxy cluster with the
+mass $\mvir=10^{15}\msun$. For this figure we use two different
+profiles for the SD energy density, where the total profile includes
+the contribution from the ICL, the BCG and all the galaxies, while the
+galaxies are excluded in the smooth profile. We find that even for a
+cluster with a relative small mass the energy density of the SD
+components dominates over the CMB and the magnetic fields (with a
+central B field of 3~$\mu G$) within about 10\% of $\rvir$. Outside
+this radius the CMB is dominating the energy density of the cluster,
+hence the magnetic fields are always subdominant in the cluster and
+can safely be removed from cluster IC calculations for a reasonable
+central B-field and spectral index. Note that in this work we keep the
+contribution from B-fields to the total energy density for
+consistency. Also note that we extract the spatial distribution of the
+SD light in clusters from a stacked emission analysis of Sloan Digital
+Sky Survey (SDSS) data at the redshift $\sim 0.25$
+\cite{2005MNRAS.358..949Z} (c.f. Fig.~\ref{fig:SD_spatial}).
+
+ADD DISCUSSION ABOUT ACCUMILATIVE LUMINOSITY
+
+\del{
+found the IR to X-ray luminosity scaling relation found in
+\cite{2008A&A...490..547G}. The X-ray luminosities for the clusters
+used in this work are listed in the extended HIghest X-ray FLUx Galaxy
+Cluster Sample (HIFLUGCS) \cite{2002ApJ...567..716R} from the Rosat
+all-sky survey. Note that we have added the Virgo cluster to the
+sample that we nevertheless refer to as extended HIFLUGCS catalogue in
+the following.
+}
+
 \begin{figure}%[t]
@@
   SD in clusters. The SD luminosity is related to the cluster mass
-  through Eq, where we use have used the mass
-  $\mvir=4.0\times10^{13}\msun$ in this figure. Finally we renormalize
-  the SD spectra to the radius $r=0.071\rvir$, where the smooth energy
-  density of the SD light (see Fig.~\ref{fig:SD_Edens}) equals the
-  energy density of the CMB. The red dashed lines show the fitted SD
-  spectral model.}
+  through Eqns.~(\ref{eq:N_stars}-\ref{eq:u_SD}), where we use have
+  used the mass $\mvir=10^{15}\msun$ in this figure. Finally we
+  renormalize the SD spectra to the radius $r=0.03\rvir$, where the
+  smooth energy density of the SD light (see Fig.~\ref{fig:SD_Edens})
+  equals the energy density of the CMB. The red dashed lines show the
+  fitted SD spectral model.}
  \label{fig:SD_spectra}
@@
    line and the solid purple line for the total SD light and the
-   smooth SD light, respectively. The SD light has been renormalized
-   to a cluster with the mass $\mvir=4.0\times10^{13}\msun$. Finally we
-   show the energy density two magnetic field models with a central
-   magnetic field of 3~$\mu G$. The magnetic field scales with the gas
-   density to the power $\alpha_\rmn{B}$; green dash-dotted line
-   ($\alpha_\rmn{B}=0.5$) and orange dash-dotted line
-   ($\alpha_\rmn{B}=0.7$). Note that the SD radiation is dominating
-   the energy density inside $\sim0.1\,\rvir$.}
+   smooth SD light, respectively. For comparison we show the energy
+   density of the stars and a low dust model (SLD) with the light blue
+   line. The SD light has been renormalized to a cluster with the mass
+   $\mvir=10^{15}\msun$. Finally we show the energy density two
+   magnetic field models with a central magnetic field of 3~$\mu
+   G$. The magnetic field scales with the gas density to the power
+   $\alpha_\rmn{B}$; green dash-dotted line ($\alpha_\rmn{B}=0.5$) and
+   orange dash-dotted line ($\alpha_\rmn{B}=0.7$). Note that the SD
+   radiation is dominating the energy density inside
+   $\sim0.1\,\rvir$.}
  \label{fig:SD_Edens}
+\end{figure}
+
+\begin{figure}%[t]
+ \includegraphics[width=0.99\columnwidth]{figures/lum.stars.eps}
+\caption{\it Accumulative luminosity as a function of radius. We show
+  the luminosity without substructures inside radius $r$. The solid
+  line show the emission from stars and dust (SD) and the IC
+  upscattered SD light is shown by the dashed lines. The red lines
+  show the total emission including the brightest cluster galaxy, the
+  intra cluster light and the additional intra cluster galaxies, while
+  these galaxies have been cut out in the smooth component shown by
+  the orange lines. We normalize the SD light and the IC upscattered
+  SD light with the luminosity from the smooth component within
+  $\rvir$ for each component. We find that the gamma-ray IC
+  luminosities are dominated by the central regime, while the SD light
+  is mainly build up in the outer parts of the cluster. In addition we
+  show that the SD light trace the cuspy NFW density profile (blue)
+  outside 10\% of $\rvir$.}
+ \label{fig:SD_lum}
 \end{figure}
@@
 it is important to know in which energy band to focus the efforts in
-order to maximize potential DM signal over expected background.
+order to maximize potential DM signals over expected background.
 
@@
 
+One of the main contributions to the expected extended gamma-ray is
+coming from the IC upscattered photons on various photon background
+fields. Depending on the spatial and spectral distribution of
+electrons and positrons as well as the photon background field, the
+resulting spectral distributions of gamma-ray can differ
+greatly. Hence it is interesting to understand which spectral features
+and energy regimes that are dominating for the different DM models.
+
+If the substructure boost in clusters is significant, then the total
+electron and positron distribution is dominated by its radial profile
+outside the very center where the smooth density profile dominates
+over the substructures and the cooling from SD dominates over the
+CMB. Especially since the SD distribution is centrally peaked and the
+substructure distribution peaks in the outskirts around $\rvir$, the
+overlap is small. This results in a suppression of the IC upscattered
+SD photons relative to the IC upscattered CMB, the FSR and the
+continuum emission. However if substructures are only marginally
+dominating over the smooth distribution in a cluster, the SD component
+becomes more important, especially in the 100~GeV to 1~TeV energy
+regime where the IC on CMB photons is small.
+
 In Fig.~\ref{fig:IR_comp} we show the total IC emission as well as its
@@
 energy since the electron and positron spectrum has a steep spectral
-distribution that suppresses low energy photon fields. This
+distribution that suppresses low energy photon fields. \del{This
   suppression is also seen in the relative normalization of the flux
-where the IC from both CMB and dust photons are lower compared to the
-starlight simply because the starlight has a higher energy, hence it
-is upscattered by more abundant low energy electrons and positrons
-(c.f. Fig.~\ref{fig:q_DM}). At the highest gamma-ray energies of about
-100~GeV and above, the IC from starlight steepens because it both
-probes the high energy tail of the electrons as well as suffer from
-the KN suppression. Even though the SD component seems to be
-suppressed compared to the CMB at energies around 100~MeV, it has a
-relative large impact on the steady state electron spectrum. If we
-remove the SD cooling, we find a factor two larger IC flux at low
-energies for a cluster of the size of Fornax. For more massive
-clusters we expect a larger IC flux from the SD component, but a
-smaller contribution from the CMB because of the more effective
-cooling.
+  where the IC from both CMB and dust photons are lower compared to
+  the starlight simply because the starlight has a higher energy,
+  hence it is upscattered by more abundant low energy electrons and
+  positrons (c.f. Fig.~\ref{fig:q_DM}).} At the highest gamma-ray
+energies of about 100~GeV and above, the IC from starlight steepens
+because it both probes the high energy tail of the electrons as well
+as suffer from the KN suppression. It should be noted that if we
+remove the boost from substructures, the density profile of electrons
+and prositrons is more centrally peaked, and the relative importance
+of the IC upscattered SD increases. In addition the IC upscattered CMB
+light would suffer more from SD cooling in the center. \del{Even though
+the SD component seems to be suppressed compared to the CMB at
+energies around 100~MeV, it has a relative large impact on the steady
+state electron spectrum. If we remove the SD cooling, we find a factor
+two larger IC flux at low energies for a cluster of the size of
+Fornax. For more massive clusters we expect a larger IC flux from the
+SD component, but a smaller contribution from the CMB because of the
+more effective cooling.} EXPAND DISCUSSION
 
@@
 We continue by comparing the estimated differential flux from Fornax
-to three other clusters in Fig.~\ref{fig:clu_comp}; the close by well
-studied Virgo cluster, the X-ray bright Perseus clusters, and the
+to three other clusters in Fig.~\ref{fig:clu_comp}; the close by and
+well studied Virgo cluster, the X-ray bright Perseus clusters, and the
 massive merging Coma cluster. We find high DM induced gamma-ray fluxes
@@
 but increasing the distance by a factor two decrease the flux with a
-factor four. It is also useful to relate the luminosities to a more
-model independent variable as the maximum circular velocity given by
+factor four. One should also note that the IC on SD photons scales
+slightly softer with mass, hence giving rise to a larger fraction of
+gamma-rays in low mass clusters compared to the total gamma-ray
+flux. In addition, considering that the brightest cluster galaxy
+constitute a relative larger contribution to the SD luminosity in low
+mass clusters which increase the importance of the SD component in low mass
+clusters even more (c.f. Fig.~\ref{fig:IR_comp}).
+
+It is also useful to relate the luminosities to a more model
+independent variable as the maximum circular velocity given by
 \begin{eqnarray}
@@
   models (BM) include continuum emission, and IC upscattered CMB, dust
-  and starlight (blue dashed). The arrows have colors matching each
-  cluster and show the differential upper limits set by Fermi-LAT in
-  the energy ranges $0.2-1$~GeV, $1-10$~GeV, and $10-100$~GeV from
-  left to right. For visualization we offset the arrows by increasing
-  the mean energy by 30\% in the opposite order as they appear in the
-  figure, i.e. starting with Perseus. The flux from the clusters is
-  integrated out to $\rvir$ using a point spread function of $0.1\deg$
-  and includes the boost from substructures. We find that the lower
-  GeV energy regime is most constraining, and induce upper limits on
-  boost factors.}
+  and starlight (blue dashed). The arrows show the differential upper
+  limits set by Fermi-LAT in the energy ranges $0.2-1$~GeV,
+  $1-10$~GeV, and $10-100$~GeV from left to right. We show the
+  individual components for the BM model and LP model for Virgo and
+  Perseus, respectively. The flux from the clusters is integrated out
+  to $\rvir$ using a point spread function of $0.1\deg$ and includes
+  the boost from substructures. We find that the lower GeV energy
+  regime is most constraining, and impose upper limits on boost
+  factors.}
  \label{fig:clu_comp}
@@
 constrain the smallest mass of substructures to $M_\rmn{lim}\gtrsim
-10\,\msun$. Instead assuming the standard mass of the smallest
+100\,\msun$. Instead assuming the standard mass of the smallest
 substructures of $M_\rmn{lim}\gtrsim 10^{-6}\,\msun$, we can constrain
-the boost from SFE to about 4 in Fornax, corresponding to a maximum
-SFE in the MW of about 10.
+the boost from SFE to about 2 in Fornax, corresponding to a maximum
+SFE in the MW of about 5.
 
@@
   arrow). If the DM interpretation is correct, we can constrain the
-  smallest size of halos to be larger than $10\,\msun$. However, if
+  smallest size of halos to be larger than $100\,\msun$. However, if
   the smallest size of DM halos is $10^{-6}\,\msun$, we can constrain
-  the SFE to about 4 in Fornax, corresponding to a maximum SFE in the
-  MW of about 10.}
+  the SFE to about 2 in Fornax, corresponding to a maximum SFE in the
+  MW of about 5.}
  \label{fig:boost_const}
@@
 \label{sect:spatial}
-The large angular extent of clusters on the sky in combination with
-the small PSF of most gamma-ray probes ($\sim 0.1$~deg) suggest that
-we would be able to probe the different spatial regimes of a
-cluster. Especially important is the spatial distribution of the
-gamma-ray emission as it bias upper limits derived for spatially
-extended clusters where a simple density profile is often assumed. In
-fact when DM substructures are included the total brightness profile
-is almost flat and very different from the smooth halo distribution
-with a steep outer brightness slope of $-5$.
+[ADD DUSTY STAR FORMING GALAXIES IN OUTERPARTS (LITTLE OVERLAP), DUST
+  WOULD NOT SURVIVE. IF DUST RAMPRESSURE STRIPPED, SPATIALLIATION
+  PROCESS IN THE HOT ICM FOR DYNAMICAL TIME] The large angular extent
+of clusters on the sky in combination with the small PSF of most
+gamma-ray probes ($\sim 0.1$~deg) suggest that we would be able to
+probe the different spatial regimes of a cluster. Especially important
+is the spatial distribution of the gamma-ray emission as it bias upper
+limits derived for spatially extended clusters where a simple density
+profile is often assumed. In fact when DM substructures are included
+the total brightness profile is almost flat and very different from
+the smooth halo distribution with a steep outer brightness slope of
+$-5$.
 
@@
 
-In Fig.~\ref{fig15}, we compare Fermi-LAT flux upper limits to the flux
-predictions by the semi-analytical Pinzke and Pfrommer model
+In Fig.~\ref{fig15}, we compare Fermi-LAT flux upper limits to the
+flux predictions by the semi-analytical Pinzke and Pfrommer model
 \cite{2010MNRAS.409..449P} for CRp induced $\gamma$-rays that uses the
-X-ray-inferred density profiles of clusters as an input. For consistency, we use
-beta-model fits to ROSAT data of X-ray bright clusters for our $\gamma$-ray flux
-estimates \cite{2002ApJ...567..71}). Hence these predictions are superior to
-those that use luminosity-mass scaling relation to infer the expected
-$\gamma$-ray flux---a method used by reference \cite{2010ApJ...717L..71A} to
-compare to Fermi limits.  In this semi-analytic model, we employ the fact that
-CRs accelerated at structure formation shocks and transported over cosmic time
-exhibit a universal spectral form and an almost universal spatial
+X-ray-inferred density profiles of clusters as an input. For
+consistency, we use beta-model fits to ROSAT data of X-ray bright
+clusters for our $\gamma$-ray flux estimates
+\cite{2002ApJ...567..716R}). We derive the central gas densites for
+each cluster by following the approach outlined in
+\cite{1999ApJ...517..627M} which assumes that the ICM is
+isothermal. The central gas density is found by combining X-ray
+temperature with X-ray luminosity, X-ray detection radius, density
+core radius and density slope for each cluster. These predictions are
+superior to those that use luminosity-mass scaling relation to infer
+the expected $\gamma$-ray flux---a method used by reference
+\cite{2010ApJ...717L..71A} to compare to Fermi limits.  In this
+semi-analytic model, we employ the fact that CRs accelerated at
+structure formation shocks and transported over cosmic time exhibit a
+universal spectral form and an almost universal spatial
 distribution. Depending on whether or not we account for the bias of
-``artificial galaxies'' in cosmological simulations, we derive an optimistic or
-conservative limit of the expected $\gamma$-ray emission from decaying pions
-(bracketing our ignorance of the contribution of cluster galaxies to the overall
-$\gamma$-ray flux from a cluster). Note that both models assume the maximally
-allowed acceleration efficiency for strong shocks that transfer 50\% of the
-shock kinetic energy to CRs and most likely will have to be corrected down if
-this number is not realized at structure formation shocks. Secondly, these
-simulations neglect active CR transport such as streaming and diffusion relative
-to the gas, i.e. we assume that advective transport is the dominant one and CRs
-are tightly coupled to the gas via flux-frozen magnetic fields tangled on
-sufficiently small scales. Evidence from the statistics of radio halos suggests
-that this might not be the case for relaxed clusters, arguing that CR streaming
-in those objects could be responsible for a decrease in the central CR number
-density. This effect would also reduce the expected $\gamma$-ray flux by up to a
-factor of five \cite{2011A&A...527A..99E}. We note that the tightest Fermi
-limits are obtained in the 1-10 GeV regime due to the largest effective area of
-LAT there. In this energy band, the Fermi limits come close to the flux
-predictions of Virgo, Coma and Norma. Using integrated flux limits from Fermi,
-we arrive at very similar results.  We emphasize that by using our semi-analytic
-modeling, the slight discrepancy of the scaling relation-based prediction with
-the Fermi limit on Norma \cite{2010ApJ...717L..71A} is resolved: Norma simply
-seems to be less bright than an average cluster of the same mass as Norma. The
-insensitive limit on Perseus comes about since the central AGN in NGC1275 has
-turned on over the last years, making it hard to determine a comparable
-limit as obtained from the other clusters.
+``artificial galaxies'' in cosmological simulations, we derive an
+optimistic or conservative limit of the expected $\gamma$-ray emission
+from decaying pions (bracketing our ignorance of the contribution of
+cluster galaxies to the overall $\gamma$-ray flux from a
+cluster). Note that both models assume the maximally allowed
+acceleration efficiency for strong shocks that transfer 50\% of the
+shock kinetic energy to CRs and most likely will have to be corrected
+down if this number is not realized at structure formation
+shocks. Secondly, these simulations neglect active CR transport such
+as streaming and diffusion relative to the gas, i.e. we assume that
+advective transport is the dominant one and CRs are tightly coupled to
+the gas via flux-frozen magnetic fields tangled on sufficiently small
+scales. Evidence from the statistics of radio halos suggests that this
+might not be the case for relaxed clusters, arguing that CR streaming
+in those objects could be responsible for a decrease in the central CR
+number density. This effect would also reduce the expected
+$\gamma$-ray flux by up to a factor of five
+\cite{2011A&A...527A..99E}. We note that the tightest Fermi limits are
+obtained in the 1-10 GeV regime due to the largest effective area of
+LAT there. In this energy band, the Fermi limits come close to the
+flux predictions of Virgo, Coma and Norma. Using integrated flux
+limits from Fermi, we arrive at very similar results.  We emphasize
+that by using our semi-analytic modeling, the slight discrepancy of
+the scaling relation-based prediction with the Fermi limit on Norma
+\cite{2010ApJ...717L..71A} is resolved: Norma simply seems to be less
+bright than an average cluster of the same mass as Norma. The
+insensitive limit on Perseus comes about since the central AGN in
+NGC1275 has turned on over the last years, making it hard to determine
+a comparable limit as obtained from the other clusters.
 
@@
  \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.CR.eps}
- \caption{\it Comparison of the gamma-ray flux induced by CRps for the 106
-   clusters included in the extended HIFLUGCS catalogue. The fluxes are
-   calculated within $\rvir$, and are derived using a single beta profile for
-   each cluster's gas density profile as obtained by ROSAT X-ray
-   observations. The CR distribution follows the semi-analytically model derived
-   by hydrodynamical cosmological cluster simulations \cite{2010MNRAS.409..449P}
-   (see text for details). The upper panel shows the energy integrated flux
-   above 100~MeV (left side) and above 100~GeV (right side), both as a function
-   of HIFLUGCS cluster ID. The eight brightest clusters are labelled. The lower
-   panel shows the relative difference between the $\gamma$-ray flux predicted by
-   the mass-luminosity scaling relation and to the flux computed using the
-   semi-analytical model \cite{2010MNRAS.409..449P}. The name of the clusters
-   with the largest positive offset are printed out; as expected, they all
+ \caption{\it Comparison of the gamma-ray flux induced by CRps for the
+   106 clusters included in the extended HIFLUGCS catalogue. The
+   fluxes are calculated within $\rvir$, and are derived using a
+   single beta profile for each cluster's gas density profile as
+   obtained by ROSAT X-ray observations. The CR distribution follows
+   the semi-analytically model derived by hydrodynamical cosmological
+   cluster simulations \cite{2010MNRAS.409..449P} (see text for
+   details). The upper panel shows the energy integrated flux above
+   100~MeV (left side) and above 100~GeV (right side), both as a
+   function of HIFLUGCS cluster ID. The eight brightest clusters are
+   labelled. The lower panel shows the relative difference between the
+   $\gamma$-ray flux predicted by the mass-luminosity scaling relation
+   and to the flux computed using the semi-analytical model
+   \cite{2010MNRAS.409..449P}. The name of the clusters with the
+   largest positive offset are printed out; as expected, they all
    correspond to cool core clusters.}
@@
 
-To complete this section, we present our semi-analytical model predictions for
-the CR-induced $\gamma$-ray flux for all clusters in the extended HIFLUGCS
-sample in Fig.~\ref{fig19}. In the lower panel of this figure, we show the
-relative difference between the $\gamma$-ray flux predicted by the
-mass-luminosity scaling relation and to the flux computed using the
-semi-analytical model. Using our semi-analytic modelling results in a scatter of
-the expected $\gamma$-ray flux at a given mass. Cool core clusters have a denser
-core which increases the target density of gas protons for the hadronic reaction
-which in turn biases the expected $\gamma$-ray fluxes systematically higher. We
-confirm this effect as all our outliers with increased flux in our semi-analytic
-model relative to the scaling relation expectation are in fact cool core
-clusters suggesting that the X-ray emission should be a good proxy for the
+To complete this section, we present our semi-analytical model
+predictions for the CR-induced $\gamma$-ray flux for all clusters in
+the extended HIFLUGCS sample in Fig.~\ref{fig19}. In the lower panel
+of this figure, we show the relative difference between the
+$\gamma$-ray flux predicted by the mass-luminosity scaling relation
+and to the flux computed using the semi-analytical model. Using our
+semi-analytic modelling results in a scatter of the expected
+$\gamma$-ray flux at a given mass. Cool core clusters have a denser
+core which increases the target density of gas protons for the
+hadronic reaction which in turn biases the expected $\gamma$-ray
+fluxes systematically higher. We confirm this effect as all our
+outliers with increased flux in our semi-analytic model relative to
+the scaling relation expectation are in fact cool core clusters
+suggesting that the X-ray emission should be a good proxy for the
 expected $\gamma$-ray emission. Note however that there could be the
-counter-acting effect of CR streaming in relaxed clusters which would tend to
-decrease the $\gamma$-ray luminosity \cite{2011A&A...527A..99E}. Future careful
-modelling is needed to quantify this effect.
+counter-acting effect of CR streaming in relaxed clusters which would
+tend to decrease the $\gamma$-ray luminosity
+\cite{2011A&A...527A..99E}. Future careful modelling is needed to
+quantify this effect.
 
@@
 &=& j(r)\,\sum_i N_i(\mvir) u_i^\gal(\eph)\,,
+\label{eq:u_SD}
 \end{eqnarray}
@@
 large contribution of the total starlight in a cluster comes from the
-brightest central galaxy (BCG), we assume that the total starlight has
+brightest cluster galaxy (BCG), we assume that the total starlight has
 the same halo mass scaling as the BCG \cite{2010ApJ...713.1037H}
@@
 \subsection{Radial profiles}
-
+ADD CALCULATION ABOUT GALAXY OVERLAP WITH THE ICM
 \begin{figure}%[t]

### 2011-04-22 paper.tex
update

@@
   SD in clusters. The SD luminosity is related to the cluster mass
-  through Eqns.~(\ref{eq:N_stars}-\ref{eq:u_SD}), where we use have
+  through Eqns.~(\ref{eq:u_SD}-\ref{eq:N_stars}), where we use have
   used the mass $\mvir=10^{15}\msun$ in this figure. Finally we
@@
   using a point spread function of $0.1\deg$ and a boost from
-  substructures of 570. We find bright prospects for detecting the
-  continuum emission that is dominating the total emission in the GeV
-  energy range. Also note that, above 100~MeV the total inverse
-  Compton emission is at least a factor 10 smaller than the emission
-  expected from both the continuum emission and the emission coming
-  from CRps.}
+  substructures of 570 (ADD SUBBOOST ON SD MODEL, SHOULD BE ONLY FACTOR
+  FEW). We find bright prospects for detecting the continuum emission
+  that is dominating the total emission in the GeV energy range. Also
+  note that, above 100~MeV the total inverse Compton emission is at
+  least a factor 10 smaller than the emission expected from both the
+  continuum emission and the emission coming from CRps.}
  \label{fig:diff_BM}

### 2011-05-07 paper.tex
corrected text, minor restructuring

@@
 \author{Anders Pinzke$^{1}$} \email{apinzke@physics.ucsb.edu} 
-\author{Christoph Pfrommer$^{2}$}\email{pfrommer@cita.utoronto.ca}
+\author{Christoph Pfrommer$^{2}$}\email{christoph.pfrommer@h-its.org}
 \author{Lars Bergstr\"om$^{3}$}\email{lbe@fysik.su.se}
@@
   from SFE is smaller than about a factor 5 in the MW and 2 in Fornax, or
-  alternatively if SFE corrext then $\mlim > 10^2\,\msun$.
+  alternatively if SFE correct then $\mlim > 10^2\,\msun$.
 \end{abstract}
@@
 3. Galaxy clusters. This possibility has been less studied, however we
-noted in a previous Letter \cite{2009PhRvL.103r1302P} that the are
+noted in a previous Letter \cite{2009PhRvL.103r1302P} that there are
 certain advantages that work in favour of this possible target for
@@
 ($\mvir=2.1\times10^{14}\,\msun$) \del{\cite{}} as the prime targets for DM
-observations, Perseus ($\mvir=7.7\times10^{14}\,\msun$) for CR induced
-emission and we additionally decide in favor of the well studied
-cluster Coma ($\mvir=1.4\times10^{15}\,\msun$) for comparison.
+observations, Perseus ($\mvir=7.7\times10^{14}\,\msun$) for CR induced emission
+and we additionally decide in favor of the well studied cluster Coma
+($\mvir=1.4\times10^{15}\,\msun$) for comparison. While studying these four
+clusters in great detail, we complement the analysis by calculating the expected
+gamma-ray fluxes of a nearby X-ray flux complete sample of galaxy clusters
+(HIFLUGCS, \citealt{2002ApJ...567..716R})
 
@@
 emission from galaxy clusters induced by both DM as well as CR
-protons. In section two we discuss the theory of DM and gamma-rays. In
+protons. In Section 2 we discuss the theory of DM and gamma-rays. In
 particular, we focus one the leptophilic and supersymmetric DM models
 used in this work, and outline the framework for estimating the
-gamma-ray emission from various radiative processes. In section three
+gamma-ray emission from various radiative processes. In Section 3
 we calculate the gamma-ray fluxes and spectral distributions from four
@@
 clusters we derive the gamma-ray surface brightness profiles in
-section four. To extend the analysis to more clusters and find
-promesing targets we estimate the fluxes from DM and CRs of all
-clusters in the extended HIFLUGCS sample in section five. In section
-six we conclude and discuss our results.
+Section 4. To extend the analysis to more clusters and find
+promising targets we estimate the fluxes from DM and CRs of all
+clusters in the extended HIFLUGCS sample in Section 5. In Section
+6 we conclude and discuss our results.
 
@@
 \label{sect:theory}
-We start the section by discussing two different, but well motivated DM
-models; leptophilic and supersymmetric DM. In addition we present the
-gamma-ray framework that is used to calculate the emission for these DM
-models using an Einasto DM density profile and the expected
-enhancement from DM substructures. In the end of this sections we
-outline the framework of inverse Compton emission on both CMB photons
-as well as photons from stars and dust.
+We start the section by discussing two different, but well motivated DM models;
+leptophilic and supersymmetric DM. We then present the framework that is used to
+calculate the gamma-ray emission for these DM models using an Einasto DM density
+profile and the expected enhancement from DM substructures. This is followed by
+an outline of the framework of inverse Compton emission where we take into
+account photon fields of the cosmic microwave background (CMB), dust, and
+starlight. We end by summarizing our formalism of calculating the CR-induced
+pion decay gamma-ray emission which is thought to dominate the astrophysical
+gamma-ray signal.
 
@@
 clusters generated by conventional hadronic and electromagnetic
-process - which should be close to observability with the Fermi-LAT
+processes - which should be close to observability with the Fermi-LAT
 data \cite{1997ApJ...487..529B,2007A&A...473...41E,2010MNRAS.409..449P}
@@
 $$\Omega_{CDM}h^2=0.112\pm 0.0056,$$ will in many cases naturally give
-a $\gamma$ yield which may be observable. In addition, there are
+a gamma-yield which may be observable. In addition, there are
 possible enhancement effects known, such as the astrophysical boost
@@
 detection methods, which are presently evolving rapidly use the feeble
-interaction between that dark matter particles of the galactic halo
+interaction between dark matter particles of the galactic halo
 and nuclei such as Germanium, Sodium, Iodine, Argon or Xenon to infer
@@
 
-There is also a possibility to search for dark matter annihilation
-indirectly in antimatter channels, like antiprotons or positrons. Here
-diffusion is, however, very efficient which means that the directional
-signature which is so important for gamma-rays, is completely
-erased. This method has, however, recently been much in focus due to
-the surprising rise with energy of the electron to proton ratio
-measured by the PAMELA satellite experiment \cite{Adriani:2008zr} and
-the ``bump'' in the total electron plus positron spectrum detected by
-Fermi \cite{Abdo:2009zk}. The viable particle physics models
-describing these results contain some non-trivial, or even unnatural
-elements, however. First of all, annihilation to quarks has to be very
-much suppressed, due to the non-observation of an enhanced antiproton
-flux by PAMELA \cite{Adriani:2010rc}. This means that only so-called
-{\em leptophilic} models, where the annihilation only goes to leptons
-have to be considered. Here, one has to have a sizeable fraction going
-to muons and tau leptons, as the shape of the spectrum disfavours
-direct annihilation into electrons and positrons. To get agreement
-with the measured absolute rates, one also has to have a large boost
-factor (of the order of at least several hundred), which is difficult
-to achieve with substructure alone. An additional enhancement of the
-annihilation rate has to be invoked, for example given by the {\em
-  Sommerfeld effect}. This basically means that the usual connection
-between annihilation rate at decoupling (when relative velocities $v$
-were of order $0.2 - 0.3$), which gives the relic density, and
-present-day annihilation in the halo (with velocities $v\sim 10^{-3}$)
-is broken. This would come about because the dark matter sector
-contains additional light particles which mediates an interaction with
-almost bound states which enhance the wave function at the relative
-origin, and therefore the annihilation rate (for a pedagogical review
-of viable scenarios, see \cite{ArkaniHamed:2008qn}). As a final
-difficulty of these models, the lack of an inverse-Compton signature
-from the galactic center means that only shallow density profiles can
-describe the galactic dark matter density distribution
-\cite{Bertone:2008xr,Cirelli:2008pk,Bergstrom:2008ag}. (For a review
-of the dark matter modelling of these effects, see
-\cite{Bergstrom:2009ib}. For a recent treatment, showing still viable
-models, see \cite{Finkbeiner:2010sm}.)
+There is also a possibility to search for dark matter annihilation indirectly in
+antimatter channels, like antiprotons or positrons. Here diffusion is, however,
+very efficient which means that the directional signature which is so important
+for gamma-rays, is completely erased. This method has, however, recently been
+much in focus due to the surprising rise with energy of the positron-to-total
+lepton ratio measured by the PAMELA satellite experiment \cite{Adriani:2008zr}
+and the ``bump'' in the total electron plus positron spectrum detected by Fermi
+\cite{Abdo:2009zk}. The viable particle physics models describing these results
+contain some non-trivial, or even unnatural elements, however. First of all,
+annihilation to quarks has to be very much suppressed, due to the
+non-observation of an enhanced antiproton flux by PAMELA
+\cite{Adriani:2010rc}. This means that only so-called {\em leptophilic} models,
+where the annihilation only goes to leptons have to be considered. Here, one has
+to have a sizeable fraction going to muons and tau leptons, as the shape of the
+spectrum disfavours direct annihilation into electrons and positrons. To get
+agreement with the measured absolute rates, one also has to have a large boost
+factor (of the order of at least several hundred), which is difficult to achieve
+with substructure alone. An additional enhancement of the annihilation rate has
+to be invoked, for example given by the {\em Sommerfeld effect}. This basically
+means that the usual connection between annihilation rate at decoupling (when
+relative velocities $v/c$ were of order $0.2 - 0.3$), which gives the relic
+density, and present-day annihilation in the halo (with velocities $v/c\sim
+10^{-3}$) is broken. This would come about because the dark matter sector
+contains additional light particles which mediates an interaction with almost
+bound states which enhance the wave function at the relative origin, and
+therefore the annihilation rate (for a pedagogical review of viable scenarios,
+see \cite{ArkaniHamed:2008qn}). As a final difficulty of these models, the lack
+of an inverse-Compton signature from the galactic center means that only shallow
+density profiles can describe the galactic dark matter density distribution
+\cite{Bertone:2008xr,Cirelli:2008pk,Bergstrom:2008ag}. (For a review of the dark
+matter modelling of these effects, see \cite{Bergstrom:2009ib}. For a recent
+treatment, showing still viable models, see \cite{Finkbeiner:2010sm}.)
 
@@
 the soon to be launched AMS-02 experiment on the International Space
-Station \cite{ams02} may gave interesting clues to the origin of the
+Station \cite{ams02} may give interesting clues to the origin of the
 antimatter excess.
@@
 enhancement. This effect, was computed for electromagnetism by Arnold
-Sommerfeld may years ago \cite{sommerfeld} and recently rediscovered
+Sommerfeld many years ago \cite{sommerfeld} and recently rediscovered
 in the quantum field theory of dark matter
@@
 $$
-S_{QED}=\frac{|\psi(0)|^2}{|\psi^{(0)}(0)|^2}=|\frac{\frac{\pi\alpha}{v}}{1-e^{-\frac{\pi\alpha}{v}}}|,
-$$ with $\alpha =e^2/\hbar c$ the fine-structure constant, and $v$ the
-relative velocity. This amounts to $S_{QED}=\pi\alpha/v$ for small
-velocities. For a Yukawa-like particle of mass $m_\phi$, mediating a
-weak attractive force with coupling constant $\alpha_Y$ between dark
-matter particles $\chi$ with mass $m_\chi$, the small-velocity limit
-of the enhancement becomes instead
+S_{QED}=\frac{|\psi(0)|^2}{|\psi^{(0)}(0)|^2}=
+\left|\frac{\frac{\pi\alpha}{v}}{1-e^{-\frac{\pi\alpha}{v}}}\right|,
+$$ 
+with $\alpha =e^2/\hbar c$ the fine-structure constant, and $v$ the relative
+velocity. This amounts to $S_{QED}=\pi\alpha/v$ for small velocities. For a
+Yukawa-like particle of mass $m_\phi$, mediating a weak attractive force with
+coupling constant $\alpha_Y$ between dark matter particles $\chi$ with mass
+$m_\chi$, the small-velocity limit of the enhancement becomes instead
 $$
@@
 very near resonance, as $1/v^2$. This means that in a virialised
-system (such a a galaxy cluster) with large velocity dispersion
+system (such as a galaxy cluster) with large velocity dispersion
 $v_{\rm cl}$ the Sommerfeld enhancement will be smaller than the one
@@
 from dark matter annihilation that ionizes the intergalactic medium,
-$f\sim 0.7$ for annihilation to electrons and a factor a a few smaller
+$f\sim 0.7$ for annihilation to electrons and a factor of a few smaller
 for all other standard model final states.
@@
 
-To connect easily to our previous work \cite{2009PhRvL.103r1302P}, we
-choose as our benchmark leptophilic model one with mass $1.6$ TeV and
-Sommerfeld boost $S=300$.
+To connect easily to our previous work \cite{2009PhRvL.103r1302P}, we choose as
+our benchmark leptophilic model one with mass $1.6$ TeV and Sommerfeld boost
+$S=300$ for a Milky Way halo and scale this appropriately down for cluster halos, using
+
+{\bf Anders: insert Sommerfeld boost formula as a function of halo mass}
+
+Clusters have a larger velocity dispersion and an accordingly smaller Sommerfeld
+boost factor.
 
 \subsubsection{Supersymmetric dark matter}
-The most studied models for dark matter are supersymmetric ones,
-especially models where the lightest supersymmetric particle, in most
-models the lightest neutralino, is stable. The stability is assured in
-viable SUSY models due to a discrete symmetry, $R$-parity. This
-symmetry is needed from the particle physics point of view to avoid
-fast proton decay, and automatically makes the lightest supersymmetric
-particle stable, and therefore a good candidate for dark matter. In
-addition, as the coupling to ordinary matter is given by gauge
-couplings, the neutralino is automatically a WIMP
-candidate. Unfortunately, the breaking of supersymmetry (which has to
-be there since otherwise, e.g., there would exist a scalar electron
-with the same mass as the electron) means that a large number of
-essentially free parameters enter actual calculations.  The neutralino
-is then a linear combination of the supersymmetric partners of the
-U(1) gauge boson, one of the SU(2) gauge bosons, and the two Higgs
-doublets in the Minimal Supersymmetric extension of the Standard Model
-(the MSSM) with mixing coefficients which depend on the SUSY breaking
-parameters \cite{1984NuPhB.238..453E}. The parameter space is very
-large, too large in general to scan efficiently even with the most
-powerful computers. Therefore, often simplifying assumptions are made
-to limit the number of free parameters. Even then, a large number of
-viable models is found which give a relic density consistent with the
-WMAP data. This means that they are indeed very good templates for
-WIMP dark matter, something that explains their popularity besides the
-subjective statement that few more plausible models for dark matter
-have been put forward so far.
+The most studied models for dark matter are supersymmetric ones, especially
+models where the lightest supersymmetric particle, in most models the lightest
+neutralino, is stable. The stability is assured in viable SUSY models due to a
+discrete symmetry, $R$-parity. This symmetry is needed from the particle physics
+point of view to avoid fast proton decay, and automatically makes the lightest
+supersymmetric particle stable, and therefore a good candidate for dark
+matter. In addition, as the coupling to ordinary matter is given by gauge
+couplings, the neutralino is automatically a WIMP candidate. Unfortunately, the
+breaking of supersymmetry (which has to be there since otherwise, e.g., there
+would exist a scalar electron with the same mass as the electron) means that a
+large number of essentially free parameters enter actual calculations.  The
+neutralino is then a linear combination of the supersymmetric partners of the
+U(1) gauge boson, $\tilde B$, one of the SU(2) gauge bosons, $\tilde W_3$, and
+the two Higgs doublets in the Minimal Supersymmetric extension of the Standard
+Model (the MSSM), $\tilde H_1^0$ and $\tilde H_2^0$, with mixing coefficients
+which depend on the SUSY breaking parameters \cite{1984NuPhB.238..453E}. The
+parameter space is very large, too large in general to scan efficiently even
+with the most powerful computers. Therefore, often simplifying assumptions are
+made to limit the number of free parameters. Even then, a large number of viable
+models is found which give a relic density consistent with the WMAP data. This
+means that they are indeed very good templates for WIMP dark matter, something
+that explains their popularity besides the subjective statement that few more
+plausible models for dark matter have been put forward so far.
 
@@
 \end{itemize}
+
+{\bf Anders: add DM particle mass and cross section to all these 4 models}
 
@@
 $Q_X^2$ and $m_X$ the
-charge and mass of the particle $X$, respectively. The function
+charge and mass of the final state particle $X$, respectively. The function
 $\mathcal{F}_X(x)$ depends on the spin of the final state and is given
@@
 can be computed using {\sc DarkSUSY}. The differential photon energy
-spectra for all our benchmark models are shown in
-Fig.~\ref{fig:bmspectra}.  The peaking at high photon energy and the
-resulting bump caused by inner bremsstrahlung is clearly seen for
-benchmark models $I´$, $J´$, and $J^*$.
-
-\subsection{Astrophysics}
+spectra for all our benchmark models are shown in Fig.~\ref{fig:q_DM}.
+The peaking at high photon energy and the resulting bump caused by
+inner bremsstrahlung is clearly seen for benchmark models $I´$, $J´$,
+and $J^*$. Despite the different particle masses and cross sections,
+the spectrum of the continuums emission shows a remarkably similar
+shape which suggests that a simple rescaling of particle masses
+(responsible for the exponential cutoff in the spectrum) and cross
+sections (spectral amplitude) should yield a roughly scale-invariant
+contiuums emission spectrum except for the presence of the final state
+emission feature which depends on the details of the specific decay
+channels. The right panel of Fig.~\ref{fig:q_DM} shows the cumuative
+number of leptons (electrons and positrons) above a given energy for
+our different DM models which is of interested for the high-energy
+inverse Compton emission of those leptons.  Only leptophilic (LP)
+models have energetic enough electrons such that the IC emission is
+powerful enough to either be constrained or detected at GeV energies
+and higher.
+
+\begin{figure*}
+\begin{minipage}{2.0\columnwidth}
+ \includegraphics[width=0.49\columnwidth]{figures/fit.ds.flux.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/fit.epflux.int.eps}
+ \caption{\it Source functions for different DM models. Crosses show
+   the simulated data from DarkSUSY and the solid lines show the fit
+   to the data using Eq.... LEFT PANEL: normalized differential
+   continuum spectra for four different DM benchmark (BM) models;
+   $\Ip$ model (red), $\Jp$ (orange), $\Kp$ (green), and $\Js$
+   (blue). RIGHT PANEL: number of electron and positron per DM
+   annihilation above the electron energy $\ee$ for different dark
+   matter models; $\Ip$ BM model (red), $\Jp$ BM model (orange), $\Kp$
+   BM model (green), and $\Js$ BM model (blue), leptophilic (LP) DM
+   annihilating into electrons and positrons (purple), and LP DM
+   annihilating into muons (black) without considering Sommerfeld
+   boosts.}
+ \label{fig:q_DM}
+\end{minipage}
+\end{figure*}
+
+\subsection{Astrophysical modeling of DM induced emission}
 \label{sect:AP}
+
+We now turn to the detailed modeling of the surface brightness
+profiles of DM annihilation emission and discuss the DM profiles for
+the smooth distribution and substructures.
+
+\subsubsection{General equations}
 
@@
 galactic center and
-$\cos\Psi\equiv\cos\theta\cos\psi-\cos\varphi\sin\theta\sin\psi$. The
-angular integration $\dd \Omega= \sin\theta\dd \theta \,\dd \varphi$
-is performed over a cone centered around $\psi$ and the opening angle
-$\Delta \Omega$ is typically taken to be a few times the point spread
-function (PSF) $\psf$. The limited angular resolution results in a
-probability that a photon coming from a direction $\psi$' is instead
-reconstructed to a direction $\psi$, where the underlying probability
-distribution follow a Gaussian:
+$\cos\Psi\equiv\cos\theta\cos\psi-\cos\varphi\sin\theta\sin\psi$ {\bf
+  Anders: I do not understand this equation: why galactic
+  center?}. The angular integration $\dd \Omega= \sin\theta\dd \theta
+\,\dd \varphi$ is performed over a cone centered around $\psi$ and the
+opening angle $\Delta \Omega$ is typically taken to be a few times the
+point spread function (PSF) $\psf$. The limited angular resolution
+results in a probability that a photon coming from a direction $\psi$'
+is instead reconstructed to a direction $\psi$, where the underlying
+probability distribution follow a Gaussian:
 \begin{equation}
@@
 smooth halo contribution $\B_{\sub,i}(r) =
-1+\rho_{\sub,i}^2(r)/\rho^2(r)$ (see Sect.~\ref{sect:subst}). The DM
-source function from the smooth halo for each process is written in
-the form:
+1+\rho_{\sub,i}^2(r)/\rho^2(r)$ (see Sect.~\ref{sect:subst}). {\bf
+  Anders: please add equation for $\B_{\sub,i}(M_{halo})$ here and
+  reference $B_{sfe}$ equation.} The DM source function from the
+smooth halo for each process is written in the form:
 \begin{equation}
@@
 producing channels, each with the spectrum $\frac{\dd
-  \ngammaj}{\dd\eg}$ and annihilation cross-section $\sigmaannv_j$. We
-denote the DM mass with $\mx$ and the DM density profile with
-$\rho(r)$. Typically the universal Navarro-Frenk-White (NFW) density
+  \ngammaj}{\dd\eg}$ and annihilation cross-section $\sigmaannv_j$.
+We denote the DM mass with $\mx$ and the smooth DM density profile
+with $\rho(r)$.
+
+\subsubsection{The smooth DM density profile}
+\label{sect:smooth}
+
+ Typically the universal Navarro-Frenk-White (NFW) density
 profile provides a good fit to both the observed and simulated
@@
 \begin{equation}
-\rho(r) = \frac{\rhos}{\left(r/r_\s+\right)^\gamma
+\rho(r) = \frac{\rhos}{\left(r/r_\s\right)^\beta
   \left[1+\left(r/r_\s\right)^\alpha\right]^\delta}\,,\quad
-\delta=\frac{\beta-\gamma}{\alpha}\,,
+\delta=\frac{\gamma - \beta}{\alpha}\,.
 \label{eq:rho_nfw}
 \end{equation}
-where a cuspy NFW profile is given by
-$(\alpha,\beta,\gamma)=(1,3,1)$. The scaling radius is given by $r_\s$
-and the characteristic overdensity by 
+Here, $\beta$ denotes the inner slope, $\gamma$ is the outer slope,
+and $\alpha$ is the shape parameter that determines the profile shape
+at the scaling radius $r_\s$ that characterizes the transition between
+the different power-law slopes. A cuspy NFW profile is given by
+$(\alpha,\beta,\gamma)=(1,1,3)$. The characteristic overdensity for an
+NFW profile is given by
 \begin{equation}
@@
 from an Einasto profile originate within $r_{-2}=\rvir/c$, it follows
-that $\rho_{-2} = \rhos/4$. [MIGHT REMOVE THIS, COULD NOT REPRODUCE IT, CAN
+that $\rho_{-2} = \rhos/4$. {\bf Anders: MIGHT REMOVE THIS, COULD NOT REPRODUCE IT, CAN
 MOTIVATE THE FACTOR 4 FROM MATCHING THE MASSES FROM THE EINSASTO WITH
-THE NFW INSTEAD] SHOW INTEGRATION, COMPUTE RMAX, DISCUSS
-FIG 1+2 SMOOTH COMPONENT
+THE NFW INSTEAD] SHOW INTEGRATION, COMPUTE RMAX}
 
@@
 while the substructures in the center suffer from dynamical friction
-and tidal effects depleating their central number densities. Since
-the rate of which DM is annihilating depends on the density squared,
-the resulting flux from substructures is boosted compared to the
-smooth density distribution. Recent high resolution simulations
-suggest a flux enhancement from substructures of the order of ten up
-to a few 100 \cite{2008MNRAS.391.1685S, 2008JPhCS.125a2008K} for a MW
-size halo. We use a double power-law function to fit \footnote{Our
-  approach of fitting the scaling behavior of $\rmn{L_{sub}}(<r)$
-  directly from numerical simulations self-consistently accounts for
-  the radial dependence of the substructure concentration
-  \cite{2008MNRAS.391.1685S}.} the luminosity from the smooth
-component of substructures (i.e. substructures within substructures
-are not included) inside radius $r$ which is determined for the
-Aquarius simulations
+and tidal effects depleating their central number densities. Since the
+DM annihilation rate depends on the density squared, the resulting
+flux from substructures is boosted compared to the smooth density
+distribution. Recent high resolution simulations suggest a flux
+enhancement from substructures of the order of ten up to a few 100
+\cite{2008MNRAS.391.1685S, 2008JPhCS.125a2008K} for a MW size
+halo. {\bf Anders: motivate why we take 200; is there a reference that
+  shows that Kuhlen now also get 100-200?}  We use a double power-law
+function to fit \footnote{Our approach of fitting the scaling behavior
+  of $\rmn{L_{sub}}(<r)$ directly from numerical simulations
+  self-consistently accounts for the radial dependence of the
+  substructure concentration \cite{2008MNRAS.391.1685S}.} the
+luminosity from the smooth component of substructures
+(i.e. substructures within substructures are not included) inside
+radius $r$ which is determined for the Aquarius simulations
 \cite{2008MNRAS.391.1685S,2008Natur.456...73S}. Our best fit is given
@@
   {\rm L_{sub}}(<x) &=& a_0\,C(\mvir)\,{\rm L_{200sm}}(\mvir)\,x^{a_1
-    \displaystyle{x}^{a_2}}\,,\quad\rmn{where} \nonumber\\
+    \displaystyle{x}^{a_2}}\,,\label{eq:LSub}\\
    a_0 &=& 0.76\,,\quad a_1 = 0.95\,,\quad  a_2 = -0.27\,, \quad 
-\rmn{and} \nonumber\\
-\label{eq:LSub} \\
-  C(\mvir) &=& 0.023\,\left(\frac{\mvir}{M_{\rm lim}}\right)^{0.226}\,.
+ \nonumber\\
+  C(\mvir) &=& \left(\frac{\mvir\,M_{\rm res,sim}}
+{M_{\rm 200sim}\,M_{\rm lim}}\right)^{\alpha_C}
+=0.023\,\left(\frac{\mvir}{M_{\rm lim}}\right)^{\alpha_C}.\nonumber\\
 \label{eq:Csub}
 \end{eqnarray}
-Here $a_i$ denote our fitted variables, ${\rm L_{200sm}}$ is the
-luminosity from the smooth halo without substructures within $\rvir$
-and $x= \left(\frac{r}{\rvir}\right)$. The theoretical smallest mass
-of subhalos $M_{\rm lim}$ is determined from free streaming length of
-DM (CHECK), where we assume that the mass power-law scaling relation
-in Eq.~(\ref{eq:Csub}) is valid down to the free streaming mass of DM
-halos. This is conventionally in the cold dark matter universe
-\cite{2001PhRvD..64h3507H,2005JCAP...08..003G} taken to be
-$10^{-6}\msun$. Note that potentially the power-law could flatten
-towards smaller mass scales although current simulations show no hits
-of such a behavior and in addition we are approaching the asymptotic
-behavior in the power spectrum on these scales(CHECK). We derive the
+Here, $\alpha_C=0.226$, $a_i$ denote our fit variables, ${\rm
+  L_{200sm}}$ is the luminosity from the smooth halo without
+substructures within $\rvir$ and $x= r/\rvir$.  We derive the
 normalization function $C(\mvir)$ in Eq.~(\ref{eq:Csub}) from the
-simulations in \cite{2008Natur.456...73S}:
-\begin{equation}
-\left(\frac{\mvir\,M_{\rm res,sim}}
-{M_{\rm 200sim}\,M_{\rm lim}}\right)^{0.226}\,.
- \label{eq:C2}
-\end{equation}
-Here $M_{\rm 200sim}=1.9\times10^{12}\msun$ is the mass of the MW halo
-in the simulation and $M_{\rm res,sim}=10^5\msun$ is the mass of the
-smallest resolved subhalos in the MW simulation. For DM halos more
-(less) massive than the MW we expect a larger (smaller) boost from
-substructures, simply because of the larger (smaller) mass range down
-to the minimum mass $M_\rmn{lim}$.
-
-Finally we derive the squared density profile for the substructures
+simulations in reference \cite{2008Natur.456...73S} using a value of
+$M_{\rm 200sim}=1.9\times10^{12}\msun$ for the mass of the MW halo in
+the simulation and $M_{\rm res,sim}=10^5\msun$ for the mass of the
+smallest resolved subhalos in the MW simulation.  The smallest mass of
+subhalos in reality, $M_{\rm lim}$, is determined from the free
+streaming length of DM at decoupling---an effect that erases structure
+on scales smaller than the free streaming length. In applying
+Eq.~(\ref{eq:Csub}), we implicitely assume that the mass power-law
+scaling relation is valid down to the free streaming mass of DM
+halos. In the cold dark matter universe, this is conventionally taken
+to be $10^{-6}\msun$ \cite{2001PhRvD..64h3507H,
+  2005JCAP...08..003G}. Note that potentially the power-law could
+flatten towards smaller mass scales although current simulations show
+no hits of such a behavior and since Einstein's gravity is a
+scale-free theory, we do not expect such a behavior on theoretical
+grounds either.  For DM halos more (less) massive than the MW we
+expect a larger (smaller) boost from substructures, simply because of
+the larger (smaller) mass range down to the minimum mass
+$M_\rmn{lim}$.
+
+We now derive the squared density profile for the substructures
 using
 \begin{eqnarray}
-\rho_\rmn{sub}^2(r) &=& \frac{\dd \rmn{L_{sub}}}{\dd V} \frac{1}{\rmn{L_{200sm}}}
-\int_{\rvir} \dd r' 4\pi r'^2 \rho^2(r')\qquad\rmn{where}\nonumber\\
+\rho_\rmn{sub}^2(r) &=& \frac{\dd \rmn{L_{sub}}}{\dd V} \frac{1}{A_{\rmn{dm}}},\\
+\rmn{L_{200sm}} &=&  A_{\rmn{dm}} \int_{\rvir} \dd r' 4\pi r'^2 \rho^2(r'),\label{eq:Lsm}\\
  \frac{\dd \rmn{L_{sub}}}{\dd V} &=& a_0\,a_1\,C(\mvir)\,x^{a_2+a_1\,x^{a_2}}\,
-\left[\frac{1+a_2\log(x)}{4\pi\,r^3}\right]\quad\rmn{and}\nonumber\\
+\left[\frac{1+a_2\log(x)}{4\pi\,r^3}\right],\\
 x &=& r/\rvir\,.
@@
 
-The different density profiles have a large impact on the luminosity
-from annihilating DM, although the details of the density profile can
-be neglected compared to the dominating boost from substructures. In
-Fig.~\ref{fig:radial_lum} we compare the radial dependence of the
-accumulative luminosity from different smooth cluster density profiles
-to the substructure boosted luminosity at different mass scales. We
-recalculate the density contrast for the core like NFW density profile
-$\rhos$ and rescale the concentration parameter in Eq.~(\ref{eq:cfit})
-with $300/160$ \cite{2011ApJ...728L..39N} to account for the more
+The different density profiles have some impact on the luminosity from
+annihilating DM, although the details of the density profile can be
+neglected compared to the dominating boost from substructures
+(assuming dark matter to be cold). In Fig.~\ref{fig:radial_lum} we
+compare the radial dependence of the accumulative luminosity from
+different smooth cluster density profiles to the boosted luminosity
+due to substructure for different mass scales. We recalculate the
+density contrast for the core like NFW density profile $\rhos$ and
+rescale the concentration parameter in Eq.~(\ref{eq:cfit}) with
+$300/160$ \cite{2011ApJ...728L..39N} to account for the more
 centralized scale radius in cluster with a softer cusp. The emission
-coming from the core like NFW density profile ($\beta=0.6$) compared
-to a cuspy ($\beta=1.0$) is about 30\% larger within $\rvir$. This
-difference is build up within 10\% of $\rvir$ (i.e. close to
-$r_\s$). Hence the slope of the central part of a cluster is
-unimportant for the DM luminosity inside $\rvir$, instead the
-important factor is the scale radius. The emission from an Einasto
+coming from the density profile with a shallower inner slope
+($\beta=0.6$) as obtained by recent lensing and velocity dispersion
+measurements of the central galaxy \cite{2011ApJ...728L..39N} compared
+to a cuspy NFW ($\beta=1.0$) is about 30\% larger within $\rvir$. This
+difference is build up within $0.1\rvir$ (i.e. close to $r_\s$). Hence
+the slope of the central part of a cluster has little influence for
+the DM luminosity within $\rvir$ as long as the degeneracy in the
+lensing mass measurements with $r_\s$ (which decreases for decreasing
+inner slope) has been taken into account. The emission from an Einasto
 density profile is about 50\% larger than the cuspy NFW profile in the
 periphery of the cluster, where the difference is mainly build up at a
-few percent of $\rvir$. The substructure boosted luminosities is
-neglible in the center of halos, but integrated out to $\rvir$ the
-boost is about; 10 for dwarf galaxies, $10^2$ for galaxies, and $10^3$
-for galaxy clusters.
+few percent of $\rvir$. The increase in luminosity due to substructure
+is neglible in the center of halos, but integrated out to $\rvir$ the
+boost relative to the smooth emission profile amounts to approximately
+10 for dwarf galaxies, $10^2$ for galaxies, and $10^3$ for galaxy
+clusters.
 \begin{figure}%[t]
  \includegraphics[width=0.99\columnwidth]{figures/dens.prof.eps}
-\caption{\it Radial dependence of various luminosity
-  contributions. The solid lines show the accumulative smooth
-  luminosity from a cluster with the mass $\mvir=10^{15}\,\msun$ for
-  three different density profiles; an Einasto profile with
-  $\alpha=0.17$ (light blue), a cuspy NFW profile with $\beta=1.0$
-  (dark blue), and a core NFW profile with $\beta=0.6$ (purple). The
-  dashed lines show the accumulative luminosity from substructures for
-  three different mass scales; an $\mvir=10^{15}\,\msun$ galaxy
-  cluster (red), an $\mvir=10^{12}\,\msun$ galaxy (orange), and an
+ \caption{\it Radial dependence of DM annihilation luminosity of
+   smooth halo and substructures. The solid lines show the
+   accumulative smooth luminosity from a cluster with the mass
+   $\mvir=10^{15}\,\msun$ for three different density profiles; an
+   Einasto profile with $\alpha=0.17$ (light blue), a cuspy NFW
+   profile with $\beta=1.0$ (dark blue), and a core NFW profile with
+   $\beta=0.6$ (purple). The dashed lines show the accumulative
+   luminosity from substructures for three different mass scales; an
+   $\mvir=10^{15}\,\msun$ galaxy cluster (red), an
+   $\mvir=10^{12}\,\msun$ galaxy (orange), and an
    $\mvir=10^{8}\,\msun$ dwarf galaxy (green). All luminosities have
@@
 
-In Fig.~\ref{fig:radial_emis} we show the radius with the maximum
-luminosity for substructures and smooth density profiles, both for
-three different mass scales. We find that the smooth luminosity per
-logarithmic radial bin peaks at $x \dd^2 L/\dd x^2+\dd L/\dd x = 0
-\rightarrow r \propto \rvir/3c$. Hence the main contribution to the
-luminosity for large mass scales, which are usually associated with a
-low concentrated DM halos, is focused to the regime around 10\% of
-$\rvir$.  It clearly shows how that the main contribution from the
-substructures is coming from outer parts of the DM halos, while the
-main contribution from the smooth density profiles peaks around the
-scale radius. Not that, even though the bulk of substructures have
+In Fig.~\ref{fig:radial_emis} we show the radial regions that dominate
+the DM annihilation luminosity, in particular we show the differential
+contribution to the DM luminosity per logarithmic interval in radius
+for three different mass scales. Solving for the maximum of this
+curve, $\dd^2L_{200sm}/\dd (\log x)^2=0$ in combination with
+Eqn.~\ref{eq:Lsm}, we find that the luminosity from the smooth NFW
+profile peaks at $r \simeq \rvir/3c$. Despite the cuspy nature of the
+density profile, the luminosity is not dominated by the central region
+but by the transition region where the profile steepens because of the
+larger volume available there. For large clusters with typical
+concentrations of $c = r_{200}/r_\s \simeq 4$, the luminosity from the
+smooth profile is focused to the regime around 10\% of $\rvir$. In
+contrast, emission from substructures is mainly contributed by the
+outer parts of DM halos where the number density of subhalos steepens
+considerably.  Note that, even though most of the substructures have
 been erased in the central regions of DM halos, a cluster in
@@
   \includegraphics[width=0.99\columnwidth]{figures/emissiv.sub.eps}
-  \caption{\it Luminosity dominated radius for different mass
-    scales. We show the normalized luminosity per logaritmic radial
-    bin which corresponds to $x^3\rho^2/\rho^2_{200}$ where
-    $\rho_{200}$ is the density at $\rvir$. The solid lines represents
-    cuspy $\beta=1.0$ NFW density profiles for three different mass
-    scales; an $\mvir=10^{15}\,\msun$ galaxy cluster (red), an
-    $\mvir=10^{12}\,\msun$ galaxy (orange), and an
+  \caption{\it Plot that shows where most of the DM annihilation
+    luminosity comes from for different halo masses.  Differential
+    contribution to the DM annihilation luminosity per logarithmic
+    interval in radius which corresponds to $x^3\rho^2/\rho^2_{200}$
+    where $\rho_{200}$ is the density at $\rvir$. The solid lines
+    represents cuspy $\beta=1.0$ NFW density profiles for three
+    different mass scales; an $\mvir=10^{15}\,\msun$ galaxy cluster
+    (red), an $\mvir=10^{12}\,\msun$ galaxy (orange), and an
     $\mvir=10^{8}\,\msun$ dwarf galaxy (green). The dashed lines show
@@
     standard value for the limiting substructure mass of
-    $M_\rmn{lim}=10^{-6}\,\msun$. The peaks show that the flux is not
-    dominated by the center of the halos, but instead by the core
-    region for the smooth density profile and by the outer parts for
-    the substructures.}
+    $M_\rmn{lim}=10^{-6}\,\msun$. For the smooth profile, the majority
+    of the flux is delivered by a region around $r_\s/3$ as indicated
+    by the maximum value of the curves. In contrast, for substructures
+    the emission is dominated by regions around $r_{200}$.}
   \label{fig:radial_emis}
@@
 
-\subsubsection{Cosmic-ray induced gamma-ray emission}
-\label{sect:CRs}
-On small astrophysical scales, such as supernovae remnants and
-galaxies, there are convincing evidences of non-thermal
-populations. Especially, in the MW, the cosmic rays are observed
-directly as well as indirectly through radio, X-ray, and gamma-ray
-emission. On larger scales of the order of few 100~kpc up to Mpc,
-there are currently a vast number of observations of radio emission
-coming from radio mini halos in the center of cooling flow clusters,
-radio relics in the periphery of clusters \cite{2004rcfg.proc..335K}
-as well as smooth giant radio halos that have been observed in more
-than 50 clusters \cite{2003ASPC..301..143F,2008SSRv..134...93F}. This
-type of emission is expected in clusters since the formation process
-of a galaxy cluster is a very energetic processes that induces both
-turbulence as well as frequently occurring merging and accretion
-shocks which both are thought to accelerate large quantities of
-relativistic non-thermal protons and radio emitting electrons to high
-energies. Thus most of the observed radio emission in clusters is
-expected to emerge from cosmic-ray electron induced radio synchrotron
-emission. The precise origin of these electrons, in especially relics
-and giant radio halos, is still not settled. However, due to the
-smoothness of the extended emission and the observed power-law slope
-it seems quite natural that they are of hadronic origin. Especially
-since the long cooling time of cosmic ray protons (CRps) allows for
-both an extended and large population of CRps to build up over the
-cluster history \cite{1997ApJ...487..529B}.
-
-When the CRps interact with ambient gas protons, it results in the
-production of both charged and neutral pions that decay into
-electrons, neutrinos, and gamma-rays. The production of these
-secondaries depend both on the gas and CRp densities in the cluster,
-where the CRp density roughly trace the gas outside the core regime and
-is slightly enhanced in the center. This density scaling implies that
-clusters are great targets for Cherenkov telescopes with a high
-sensitivity for the central parts of close by clusters. Detecting the
-cluster gamma-ray emission is crucial in this respect as it
-potentially provides the unique and unambiguous evidence of CRp
-populations in clusters through observing the $\pi^0$ bump at about
-100~MeV in the spectra.
-
-We adopt the universal spectral and spatial gamma-ray model developed
-by Pinzke \& Pfrommer \cite{2010MNRAS.409..449P} to estimate the
-emission from decaying $\pi^0$:s that dominates over the inverse
-Compton emission from primary and secondary electrons above 100~MeV in
-clusters. The gamma-ray formalism was derived from high resolution
-simulations of clusters of galaxies that included radiative
-hydrodynamics, star formation, supernova feedback, and followed CRp
-physics using a novel formulation that trace the most important
-injection and loss processes self-consistently while accounting for
-the CRp pressure in the equation of motion
-\cite{2008A&A...481...33J,2007A&A...473...41E,2006MNRAS.367..113P}.
-We note that the overall normalization of the CRp and gamma-ray
-distribution scales with the maximum acceleration efficiency at
-structure formation shock waves. Following recent observations at
-supernova remnants \cite{2009Sci...325..719H} as well as theoretical
-studies \cite{2005ApJ...620...44K}, we adopt a realistic value of this
-parameter and assume that 50\% of the dissipated energy at strong
-shocks is injected into CRps while this efficiency rapidly decreases
-for weaker shocks \cite{2007A&A...473...41E}.
-
-\subsection{Radiative processes}
+\subsection{Inverse Compton emission}
+\label{sect:IC}
+
 In this section we outline the basics of inverse Compton (IC)
-emission. As target radiation fields we consider both cosmic microwave
+emission. As target radiation fields we consider  cosmic microwave
 background (CMB) photons, and the light from stars and dust (SD). We
@@
 
-\subsubsection{Inverse Compton}
-\label{sect:IC}
 The standard IC source function is given by
@@
 The full KN cross-section accounts for the less efficient energy
-transfer between the photon and electron and results in a steepening
-of the IC gamma-ray spectrum. In the low energy Thomson regime the IC
-spectrum $F_\gamma\sim E_\gamma^{-(\alpha_\e-1)/2}$, however when
-$\Gamma_\e \gg 1$ the IC spectrum steepens due to the KN suppression
-to $\eg^{-\alpha_\e}\log(\eg)$. Here we denote the steady
-state electron spectrum by $\alpha_\e$.
+transfer between the photon and electron once the energy of the
+Lorentz-boosted photon in the electron rest frame comes close to $m_\e
+c^2$ such that the scattering electrons experiences a significant
+recoil. This results in a steepening of the IC gamma-ray spectrum. In
+the low energy Thomson regime the IC spectrum $F_\gamma\sim
+E_\gamma^{-(\alpha_\e-1)/2}$, however when $\Gamma_\e \gg 1$ the IC
+spectrum steepens due to the KN suppression to
+$\eg^{-\alpha_\e}\log(\eg)$. Here we denote the steady state electron
+spectrum by $\alpha_\e$.
 
@@
   \eph}(\eph,r)= \frac{u_\sd(\eph,r)}{\eph^2}$ where the SD energy
-density $u_\sd(\eph,r)$ is given in Eq.~(\ref{eq:U_SD}). We model the
+density $u_\sd(\eph,r)$ is given in the Appendix, Eq.~(\ref{eq:U_SD}). We model the
 CMB photon spectrum as a photon gas that is isotropically distributed
@@
 Note that the typical energy of a black body photon before scattering
-is given by $<\eph>=\epsilon_\ph/\tilde{n}_\ph\approx\,2.70 k_\B T$,
+is given by $\langle\eph\rangle=\epsilon_\ph/\tilde{n}_\ph\approx\,2.7\, k_\B T$,
 where $\tilde{n}_\ph$ and $\epsilon_\ph$ are the number- and
@@
 shorter than the diffusive timescale in the ICM of galaxy clusters for
-CR electrons with $\ee \gtrsim\,$~MeV (CHECK). Hence, we neglect the
+CR electrons with $\ee \gtrsim\,$~MeV {\bf Anders: CHECK}. Hence, we neglect the
 first term of the r.h.s. in Eq.~(\ref{eq:CRdiffusion}), and derive an
@@
 equivalent field strength of the CMB is denoted by $B_{\rm
-  CMB}=3.24\mu\rmn{G}$. (2) Synchrotron losses on ambient
-magnetic fields where we parameterize the magnetic field in the galaxy
-cluster by $B(r) = 3\mu\rmn{G} \,[n_{\rm e}(r)/n_{\rm
-    e}(0)]^{\alpha_\B}$, which follows from flux frozen magnetic
-fields. We adopt a magnetic decline of $\alpha_\B=0.7$ in this
-work. (3) IC losses on starlight and dust with an energy density
-$u_\sd(r)$ given by Eq.~(\ref{eq:U_SD}), which we derive in the
-following subsection.
-
-{\it IC -- dust and starlight}\\ Galaxy clusters are typically
-characterized by the hot gas in the ICM and the collection of
-gravitationally bound galaxies. The emission in the IR and UV
-wavelengths emerge from dust and starlight in both the galaxies and
-the ICM (e.g. \cite{2006ApJ...648L..29P} and
-\cite{2009MNRAS.399.1694G}). Much of the radiation leaks out from the
-galaxy into the ICM, which give rise to similar spectral distributions
-for the galaxies and the ICM in these wavelengths. Hence, we use the
-accurately measured light from galactic dust and starlight in the ISM
-to model the ICM. In Fig.~\ref{fig:SD_spectra} we characterize the
-spectral shape through a fit to the galactic spectra presented in
-\cite{2006ApJ...648L..29P}. We fix the normalization for the energy
-density of light from stars and dust in a galaxy cluster individually
-using observed luminosities from SD. In addition, we attach a mass
-scaling to the normalization which we adopt from a simple
-mass-to-starlight luminosity scaling relation derived from
+  CMB}=3.24\mu\rmn{G}\,(1+z)^2$, where $z$ is the cosmological
+redshift. (2) Synchrotron losses on ambient magnetic fields where we
+parameterize the magnetic field in the galaxy cluster by $B(r) =
+3\mu\rmn{G} \,[n_{\rm e}(r)/n_{\rm e}(0)]^{\alpha_\B}$. We adopt a
+magnetic decline of $\alpha_\B=0.7$ in this work which follows from
+flux frozen magnetic fields. (3) IC losses on starlight and dust with
+an energy density $u_\sd(r)$ given by Eq.~(\ref{eq:U_SD}), which we
+derive in the following.
+
+The emission of galaxy clusters at infra-red (IR) and ultra-violet
+(UV) wavelengths emerges from dust and starlight in both the galaxies
+and the ICM (e.g. \cite{2006ApJ...648L..29P} and
+\cite{2009MNRAS.399.1694G}). Three distinctive components dominate
+these wavelengths: a central galaxy, the intra-cluster light, and
+individual cluster galaxies. We decided to use the accurately measured
+spectral shape of dust and starlight in the interstellar medium of our
+Galaxy to model the emmission from clusters. We then normalize the two
+spectral components -- far IR dust and starlight at wavelengths ranging
+from the near IR to UV -- individually by using stacked cluster data and employ a
+measured mass-to-starlight luminosity scaling relation derived from
 observations of the brightest cluster galaxy
-\cite{2010ApJ...713.1037H}. The figure is showing the spectra at
-$r=0.03\rvir$, which is the radius there the SD energy density equals
-the energy density of the CMB black-body distribution in a galaxy
-cluster. Inside this central radius the SD component is dominating,
-which is shown in Fig.~\ref{fig:SD_Edens} where we compare the energy
-densities from different radiation fields in a galaxy cluster with the
-mass $\mvir=10^{15}\msun$. For this figure we use two different
-profiles for the SD energy density, where the total profile includes
-the contribution from the ICL, the BCG and all the galaxies, while the
-galaxies are excluded in the smooth profile. We find that even for a
-cluster with a relative small mass the energy density of the SD
-components dominates over the CMB and the magnetic fields (with a
-central B field of 3~$\mu G$) within about 10\% of $\rvir$. Outside
-this radius the CMB is dominating the energy density of the cluster,
-hence the magnetic fields are always subdominant in the cluster and
-can safely be removed from cluster IC calculations for a reasonable
-central B-field and spectral index. Note that in this work we keep the
-contribution from B-fields to the total energy density for
-consistency. Also note that we extract the spatial distribution of the
-SD light in clusters from a stacked emission analysis of Sloan Digital
-Sky Survey (SDSS) data at the redshift $\sim 0.25$
-\cite{2005MNRAS.358..949Z} (c.f. Fig.~\ref{fig:SD_spatial}).
-
-ADD DISCUSSION ABOUT ACCUMILATIVE LUMINOSITY
+\cite{2010ApJ...713.1037H}.
+
+In Fig.~\ref{fig:SD_spectra} we characterize the spectral shape
+through a fit to the galactic spectra presented in
+\cite{2006ApJ...648L..29P}.  The figure is showing the spectra at
+$r=0.03\rvir$, which is the radius there the SD energy density of a
+galaxy cluster equals the energy density of the CMB black-body
+distribution. Inside this central radius the SD component is
+dominating, which is shown in Fig.~\ref{fig:SD_Edens} where we compare
+the energy densities from different radiation fields in a galaxy
+cluster with the mass $\mvir=10^{15}\msun$. For this figure we use two
+different profiles for the SD energy density, where the total profile
+includes the contribution from the ICL, the BCG and all the galaxies,
+while the galaxies are excluded in the smooth profile. {\bf Anders:
+  add the order of magnitude calculation that the overlap of galaxies
+  with smooth profile or substructures is minor, 1e-4 if I remember
+  correctly, motivating that we go along with the smooth SD profile.}
+We find that even for a cluster with a relative small mass the energy
+density of the SD components dominates over the CMB and the magnetic
+fields (with a central B field of 3~$\mu G$) within about 10\% of
+$\rvir$. Outside this radius the CMB is dominating the energy density
+of the cluster.  Note that while the magnetic field is always
+subdominant in the cluster for our assumptions, we keep its
+contribution to the total energy density for consistency. Also note
+that we extract the spatial distribution of the SD light in clusters
+from a stacked emission analysis of Sloan Digital Sky Survey (SDSS)
+data at the redshift $\sim 0.25$ \cite{2005MNRAS.358..949Z} and do not
+attempt to correct for a potential evolution in this component
+(c.f. Fig.~\ref{fig:SD_spatial}).
+
+{\bf Anders: ADD DISCUSSION ABOUT ACCUMILATIVE LUMINOSITY}
 
@@
    $2.73$~K. The crosses in the middle and right peaks represent the
-  measured spectra from stars and dust (SD), respectively, and are
-  derived in \cite{2006ApJ...648L..29P} for a galaxy. We normalize the
-  individual SD spectrum separately using the observed luminosity from
-  SD in clusters. The SD luminosity is related to the cluster mass
-  through Eqns.~(\ref{eq:u_SD}-\ref{eq:N_stars}), where we use have
-  used the mass $\mvir=10^{15}\msun$ in this figure. Finally we
+   measured spectra from stars extending from the near IR to UV and
+   dust at far IR wavelengths (SD), respectively, and are derived in
+   \cite{2006ApJ...648L..29P} for a galaxy. We normalize the
+   individual SD spectrum separately using the observed luminosity
+   from SD in clusters. The SD luminosity is related to the cluster
+   mass through Eqns.~(\ref{eq:u_SD}-\ref{eq:N_stars}), where we use
+   have used the mass $\mvir=10^{15}\msun$ in this figure. We
    renormalize the SD spectra to the radius $r=0.03\rvir$, where the
@@
  \caption{\it Spatial dependence of the energy density of radiation
-   fields in a cluster of galaxies. The energy density of the CMB,
-   shown by the blue dotted line, is isotropic throughout the cluster,
-   hence represented by a flat profile with
+   fields in a cluster of galaxies. The energy density of the CMB
+   (blue dotted line) is isotropic with
    $u_\rmn{cmb}=0.26\,\rmn{eV}\,\rmn{cm}^{-3}$. The energy density of
@@
    the luminosity without substructures inside radius $r$. The solid
-  line show the emission from stars and dust (SD) and the IC
-  upscattered SD light is shown by the dashed lines. The red lines
+   lines show the optical/IR emission from stars and dust (SD) and the
+   IC upscattered SD light is shown by the dashed lines. The red lines
    show the total emission including the brightest cluster galaxy, the
-  intra cluster light and the additional intra cluster galaxies, while
-  these galaxies have been cut out in the smooth component shown by
-  the orange lines. We normalize the SD light and the IC upscattered
-  SD light with the luminosity from the smooth component within
-  $\rvir$ for each component. We find that the gamma-ray IC
-  luminosities are dominated by the central regime, while the SD light
-  is mainly build up in the outer parts of the cluster. In addition we
-  show that the SD light trace the cuspy NFW density profile (blue)
-  outside 10\% of $\rvir$.}
+   intra cluster light and the additional intra cluster galaxies,
+   while these galaxies have been cut out in the smooth component
+   shown by the orange lines. We normalize the SD light and the IC
+   upscattered SD light with the luminosity from the smooth component
+   within $\rvir$ for each component. We find that the gamma-ray IC
+   luminosities are dominated by the central regime, while the SD
+   light is mainly build up in the outer parts of the cluster. For
+   comparison, we show that the SD light traces the NFW mass profile
+   (blue) outside  $0.1\rvir$.}
  \label{fig:SD_lum}
@@
 
-\section{Spectral gamma-ray distribution}
+\subsection{Cosmic-ray induced gamma-ray emission}
+\label{sect:CRs}
+
+In supernovae remnants and on scales of galaxies, there are convincing
+evidences of non-thermal populations. Especially, in the MW, the
+cosmic rays are observed directly as well as indirectly through radio,
+X-ray, and gamma-ray emission. On larger scales of the order of few
+100~kpc up to Mpc, there are currently a vast number of observations
+of radio emission coming from radio mini halos in the center of
+cooling flow clusters, radio relics in the periphery of clusters
+\cite{2004rcfg.proc..335K} as well as smooth giant radio halos that
+have been observed in more than 50 clusters
+\cite{2003ASPC..301..143F,2008SSRv..134...93F}. This type of emission
+is expected in clusters since the formation process of a galaxy
+cluster is a very energetic processes that induces both turbulence as
+well as frequently occurring merging and accretion shocks which both
+are thought to accelerate relativistic non-thermal protons and radio
+emitting electrons to high energies. Thus most of the observed radio
+emission in clusters is expected to emerge from cosmic-ray electron
+induced radio synchrotron emission. The precise origin of these
+electrons, in especially relics and giant radio halos, is still not
+settled. One possible scenario for the production of these electrons
+are hadronic CR interactions with ambient gas protons which results in
+the production of both charged and neutral pions that decay into
+electrons, neutrinos, and gamma-rays. \footnote{An alternative
+  scenario is the second order turbulent re-acceleration through the
+  interaction of a previously injected relativistic population of
+  electrons by supernova driven winds or active galactic nuclei with
+  plasma waves and magneto-turbulence.} {\bf Anders: please add
+  references for the hadronic/re-acceleration scenario; look them up
+  from our Ensslin-transport paper.} Supporting evidence comes from
+the smoothness of the extended radio emission that often resembles
+that observed in thermal X-rays. Especially since the long cooling
+time of cosmic ray protons (CRps) allows for an extended and large
+population of CRps to build up over the cluster history
+\cite{1997ApJ...487..529B}.  The production of these secondaries
+depend both on the gas and CRp densities in the cluster, where the CRp
+density roughly traces the gas outside the core regime and is slightly
+enhanced in the center.  This density scaling implies that clusters
+are great targets for Cherenkov telescopes with a high sensitivity for
+the central parts of nearby clusters. Detecting the cluster gamma-ray
+emission is crucial in this respect as it potentially provides the
+unique and unambiguous evidence of CRp populations in clusters through
+observing the $\pi^0$ bump at about 100~MeV in the spectra.
+
+We adopt the universal spectral and spatial gamma-ray model developed
+by Pinzke \& Pfrommer \cite{2010MNRAS.409..449P} to estimate the
+emission from decaying $\pi^0$:s that dominates over the inverse
+Compton emission from primary and secondary electrons above 100~MeV in
+clusters. The gamma-ray formalism was derived from high resolution
+simulations of clusters of galaxies that included radiative
+hydrodynamics, star formation, supernova feedback, and followed CRp
+physics using a novel formulation that trace the most important
+injection and loss processes self-consistently while accounting for
+the CRp pressure in the equation of motion
+\cite{2008A&A...481...33J,2007A&A...473...41E,2006MNRAS.367..113P}.
+We note that the overall normalization of the CRp and gamma-ray
+distribution scales with the maximum acceleration efficiency at
+structure formation shock waves. Following recent observations at
+supernova remnants \cite{2009Sci...325..719H} as well as theoretical
+studies \cite{2005ApJ...620...44K}, we adopt a realistic value of this
+parameter and assume that 50\% of the dissipated energy at strong
+shocks is injected into CRps while this efficiency rapidly decreases
+for weaker shocks \cite{2007A&A...473...41E}. As a caviat we note that
+the semi-analytic odel is based on simulations that only considered
+advective transport of CRs by turbulent gas motions which produces
+centrally enhanced profiles. However active CR transport such as CR
+diffusion and streaming tends to drive the CR radial profiles towards
+being flat, with equal CR number density everywhere. While the CR
+streaming is then usually larger than typical advection velocities and
+becomes comparable or lower than this only for periods with trans- and
+supersonic cluster turbulence during a cluster merger. As a
+consequence a bimodality of the CR spatial distribution results with
+merging (relaxed) clusters showing a centrally concentrated (flat) CR
+energy density profile \cite{2011A&A...527A..99E}.  This translates
+into a bimodality of the expected diffuse radio and gamma-ray emission
+of clusters, since more centrally concentrated CR will find higher
+target densities for hadronic CR proton interactions
+\cite{2011A&A...527A..99E}. As a result of this, relaxed clusters
+could have a reduced gamma-ray luminosity by up to a factor of five.
+
+\section{Gamma-ray spectra}
 \label{sect:spectral}
@@
 it is important to know in which energy band to focus the efforts in
-order to maximize potential DM signals over expected background.
-
-We dedicate this section to the spectral distribution of gamma-ray
-flux from clusters. The flux emerge from a leptophilic DM model that
-emit final state radiation and give rise to substantial amounts of
+order to maximize potential DM signals over the expected background.
+
+We focus in this section on the spectral distribution of gamma-rays
+from clusters.  In the leptophilic model, DM annihilation radiation
+includes final state radiation and give rise to substantial amounts of
 electrons and positrons that IC upscatter background radiation fields
@@
 fluxes. We derive the emission from four different supersymmetric BM
-models and compare the flux to both the emission induced by CRps as
-well as to the differential gamma-ray upper limits set by Fermi-LAT
-after 18 months of observations \cite{2010ApJ...717L..71A}. We find
-that the upper limits are not violated, although the predicted DM flux
-that is dominated by the continuum emission from $\Kp$ and $\Ip$
-models (shown in the left panels) are close to the upper limits and
-can potentially be probed by the Fermi 3 year data. Furthermore, the
-expected masking gamma-ray signal induced by CRps is about a factor 10
-below the DM continuum flux from the $\Kp$ and $\Ip$ BM models around
+models and the emission induced by CRps. Comparing this emission to
+the differential gamma-ray upper limits set by Fermi-LAT after 18
+months of observations \cite{2010ApJ...717L..71A}, we find that the
+upper limits are not violated. The predicted DM flux that is dominated
+by the continuum emission from $\Kp$ and $\Ip$ models (shown in the
+left panels) are close to the upper limits and can potentially be
+probed by the Fermi 3 year data. Furthermore, the gamma-ray signal
+induced by CRps is expected to be about a factor 10 below the DM
+continuum flux from the $\Kp$ and $\Ip$ BM models around
 10~GeV. However, the IC emission from upscattered CMB and SD photons
@@
 foreground due to the similar spectral index. For energies below
-100~MeV we expect shock accelerated electrons and positrons to be
-dominating \cite{2010MNRAS.409..449P} over the supersymmetric DM
-induced leptons. Hence the IC emission from supersymmetric DM in
-clusters can for most applications safely be neglected compared to the
-CRps and DM continuum emission.
+100~MeV we expect inverse Compton emission by primary shock
+accelerated electrons to be dominating \cite{2010MNRAS.409..449P} over
+the supersymmetric DM induced leptons. Hence the IC emission from
+supersymmetric DM in clusters can for DM benchmark models be safely
+neglected compared to the CRps and DM continuum emission.
 
@@
   dashed), electrons and positrons from DM BM models that inverse
-  Compton upscattered both CMB photons (orange dash-dotted) as well as
-  dust and star photons (green dotted), and CRp induced gamma-ray
+  Compton upscattered both CMB photons (green dotted) as well as dust
+  and star photons (orange dash-dotted), and CRp induced gamma-ray
   emission (red solid). Each panel is associated with an individual DM
@@
   using a point spread function of $0.1\deg$ and a boost from
-  substructures of 570 (ADD SUBBOOST ON SD MODEL, SHOULD BE ONLY FACTOR
-  FEW). We find bright prospects for detecting the continuum emission
-  that is dominating the total emission in the GeV energy range. Also
-  note that, above 100~MeV the total inverse Compton emission is at
-  least a factor 10 smaller than the emission expected from both the
-  continuum emission and the emission coming from CRps.}
+  substructures of 570 (ADD SUBBOOST ON SD MODEL, SHOULD BE ONLY
+  FACTOR FEW). We find bright prospects for detecting the continuum
+  emission, that is dominating the total emission in the GeV energy
+  range, in the models $\Ip$ and $\Kp$. }
  \label{fig:diff_BM}
@@
 \end{figure*}
+
+{\bf Ander: I got that far with the results, please polish the reminder up to population studies!}
 
@@
   each individual radiation field from top line to bottom line; CMB
-  (green dashed-double-dotted), dust (blue dashed), stars (purple
+  (green dashed-tripple-dotted), dust (purple dashed), stars (blue
   dashed-dotted). The sum of the three components are shown with the
-  orange solid line. The black dotted line represents the upscattered
-  CMB photons without any cooling from stars and dust. The red solid
-  line show the CRp induced gamma-ray flux. The black arrow show the
-  differential upper limit from Fermi \cite{2010ApJ...717L..71A}. All
-  fluxes are calculated for the Fornax cluster within $\rvir$ using a
-  point spread function of $0.1\deg$. The boost from Sommerfeld and
+  orange solid line.  The red solid line show the CRp induced
+  gamma-ray flux. The black arrow shows the differential upper limit
+  from Fermi \cite{2010ApJ...717L..71A} indicating that the model
+  assumptions such as Sommerfeld and/or substructure boost are in
+  conflict with the upper limit. All fluxes are calculated for the
+  Fornax cluster within $\rvir$ using a point spread function of
+  $0.1\deg$. For this cluster, the boost from Sommerfeld and
   substructures is about 130 and 570, respectively.}
@@
  \caption{\it Comparing the energy integrated flux from different
-  models. We show the emission from; CRp induced emission (red solid),
-  leptophilic models (LP) that include both final state radiation and
-  IC upscattered CMB, dust and starlight (green dash-dotted), and
-  benchmark $\Kp$ models (BM) include continuum emission, and IC
-  upscattered CMB, dust and starlight (blue dashed). The black arrow
-  show the integrated flux upper limit set by Fermi-LAT. The emission
-  is calculated for the Fornax cluster using a point spread function
-  of $0.1\deg$. The boost from Sommerfeld and substructures is about
-  130 and 570, respectively. We find that LP models are dominating the
-  total flux in the entire energy range, where the IC upscattered CMB
-  photons overproduce the upper limit by a factor 3.}
+   models. We show the emission from; CRp induced emission (red
+   solid), leptophilic models (LP) that include both final state
+   radiation and IC upscattered CMB, dust and starlight (green
+   dash-dotted), and benchmark $\Kp$ models (BM) include continuum
+   emission, and IC upscattered CMB, dust and starlight (blue
+   dashed). The black arrow show the integrated flux upper limit set
+   by Fermi-LAT again indicating challenges for the assumptions
+   underlying the LP model. The emission is calculated for the Fornax
+   cluster using a point spread function of $0.1\deg$. The boost from
+   Sommerfeld and substructures is about 130 and 570, respectively. }
  \label{fig:flux_int}
@@
 \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v11.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\caption{\it Comparing the emission from different clusters. We show
-  the differential flux from four clusters; Fornax (upper left), Coma
-  (upper right), Virgo (lower left), and Perseus (lower right). The
-  different flux models; CRp induced emission (red solid), leptophilic
+\caption{\it Comparing the gamma-ray emission from different
+  clusters. We show the differential flux from four clusters; Fornax
+  (upper left), Coma (upper right), Virgo (lower left), and Perseus
+  (lower right). We show CRp induced emission (red solid), leptophilic
   models (LP) include both final state radiation and IC upscattered
@@
   the boost from substructures. We find that the lower GeV energy
-  regime is most constraining, and impose upper limits on boost
+  regime is most constraining due to the peak sensitivity of Fermi at
+  these energies and use this regime to get upper limits on boost
   factors.}
@@
 \end{figure*}
+
+peak sensitivity of Fermi at these energies due to a combination of effective area background and source spectra...
 
@@
    (SFE) is constrained for four clusters; Fornax (red), Virgo
-  (orange), M49 (green), and NGC4636 (Blue). The SFE has been rescaled
-  from 300 (refer to equation) that is required to explain the
-  electron and positron excess observed at Earth with LP DM (black
-  arrow). If the DM interpretation is correct, we can constrain the
-  smallest size of halos to be larger than $100\,\msun$. However, if
-  the smallest size of DM halos is $10^{-6}\,\msun$, we can constrain
-  the SFE to about 2 in Fornax, corresponding to a maximum SFE in the
-  MW of about 5.}
+   (orange), M49 (green), and NGC4636 (blue). The SFE has been
+   rescaled from the MW value of 300 {\bf Anders (refer to equation)}
+   that is required to explain the electron and positron excess
+   observed at Earth with LP DM (black arrow). If the DM
+   interpretation is correct, we can constrain the smallest size of
+   halos to be larger than $100\,\msun$. Contrarily, if the smallest
+   size of DM halos is $10^{-6}\,\msun$, we can constrain the SFE to
+   about 2 in Fornax, corresponding to a maximum SFE in the MW of
+   about 5 which would be too small to support the DM annihilation
+   hypothesis for the Pamela/Fermi excess.}
  \label{fig:boost_const}
@@
  \includegraphics[width=0.99\columnwidth]{figures/SB.v11.1GeV.SF300.SubMass.elmu.eps}
-\caption{\it Comparing the surface brightness from different
-  clusters. We show the CRp induced emission (red), leptophilic
-  emission (green), and emission from the $\Kp$ benchmark model
-  (blue). The surface brightness above 1~GeV is derived using a very
-  small point spread function ($\psf=10^{-5}\deg$). The
-  different linestyles each represent a cluster; Fornax (solid), Coma
-  (dotted), Virgo (dashed), and Perseus (dash-dotted). The boost from
-  Sommerfeld and substructures is about 130 and 570,
-  respectively. Notice the very similar shape and normalization of the DM
-  models, while the CRps have a much larger scatter in the profiles.}
+ \caption{\it Comparing the intrinsic surface brightness from
+   different clusters without taking PSF effects into account. We show
+   the CRp induced emission (red), leptophilic emission (green), and
+   emission from the $\Kp$ benchmark model (blue). The different
+   linestyles each represent a cluster; Fornax (solid), Coma (dotted),
+   Virgo (dashed), and Perseus (dash-dotted). The boost from
+   Sommerfeld effect and substructures is about 130 and 570,
+   respectively. Notice the very similar shape and normalization of
+   the DM models, while the CRps have a much larger scatter in the
+   profiles due to the large variation of the gas fraction in these clusters.}
  \label{fig:SB_clu}
@@
  \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v11.1GeV.SF300.noSuB.vs.SubMass.elmu.eps}
-\caption{\it The impact of substructures on surface brightness. We
-  show the surface brightness at 1~GeV for the Fornax cluster using a
-  very small point spread function of $10^{-5}\deg$ that reveals the
-  details of the spatial profiles. The emission induced by CRps is
-  denoted by the red solid line, the leptophilic models by green
-  lines, and the DM $\Kp$ benchmark model by blue lines. The dashed
-  line show the brightness where the boost from substructures is
-  included while the substructures are excluded in the dotted
-  line. The boost from Sommerfeld and substructures is about 130 and
-  570, respectively. Notice the nearly flat profiles when
-  substructures are included, and the relative large boost at a
-  percent of $\rvir$.}
+ \caption{\it The impact of substructures on the intrinsic surface
+   brightness profile of the Fornax cluster at 1~GeV. The emission
+   induced by CRps is denoted by the red solid line, the leptophilic
+   models by green lines, and the DM $\Kp$ benchmark model by blue
+   lines. The dashed line show the brightness where the boost from
+   substructures is included while the substructures are excluded in
+   the dotted line. The boost from Sommerfeld and substructures is
+   about 130 and 570, respectively. Notice the nearly flat profiles
+   when substructures are included, and the relative large boost at
+   $0.01\rvir$ that is due to projection of peripheral substructures
+   onto the cluster center.}
  \label{fig:SB_sub}
@@
   \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v11.1GeV.SF300.noSuB.elmu.eps}
-\caption{\it The surface brightness without substructures. We show the
-  CRp induced emission (red), leptophilic emission (green), and
-  emission from the $\Kp$ benchmark model (blue). The surface
-  brightness above 1~GeV is derived using a very small point spread
-  function ($\psf=10^{-5}\deg$). LEFT PANEL: compare the
-  surface brightness for different clusters; Fornax (solid), Coma
-  (dotted), Virgo (dashed), and Perseus (dash-dotted). RIGHT PANEL:
-  compare different emission components in Fornax; dotted lines show
-  the inverse Compton (IC) upscattered CMB photons, dashed lines show
-  the IC upscattered photons from stars and dust, and blue solid line
-  show the continuum emission from the $\Kp$ benchmark
-  model.}
+  \caption{\it The intrinsic surface brightness profiles without
+    substructures at energies $E>1 GeV$. We show the CRp induced
+    emission (red), leptophilic emission (green), and emission from
+    the $\Kp$ benchmark model (blue).  LEFT PANEL: comparison of the surface
+    brightness of different clusters; Fornax (solid), Coma (dotted),
+    Virgo (dashed), and Perseus (dash-dotted). RIGHT PANEL: comparison of
+    different emission components in Fornax; dotted lines show the
+    inverse Compton (IC) upscattered CMB photons, dashed lines show
+    the IC upscattered photons from stars and dust, and blue solid
+    line show the continuum emission from the $\Kp$ benchmark model.}
  \label{fig:SB_clu_nosub}
@@
   boost from substructures. We use a point spread function of
-  $\psf=0.1\deg$ that is typical for both Cherenkov
-  telescopes as well as the Fermi-LAT at this energy. Left panel show
+  $\psf=0.1\deg$ that is typical for Cherenkov
+  telescopes as well as the Fermi-LAT at this energy. Left panel shows
   the Fornax cluster and right panel the Virgo cluster. The gamma-ray
@@
     the normalization depends on the particular cross-section and neutralino
-    masses.}
+    mass.}
 \label{fig:lum_mass_scaling}
@@
 CR scaling relation is considerably steeper as shown by reference
-\cite{2010MNRAS.409..449P}. [ANDERS: add CR scaling formula] This implies
+\cite{2010MNRAS.409..449P}. {\bf Anders: add CR scaling formula} This implies
 already a general strategy to minimize the CR-induced foreground for DM
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.DM.eps}
-  \caption{\it Fermi flux upper limits are contrasted to the predicted DM
+  \caption{\it Fermi gamma-ray flux upper limits are contrasted to the predicted DM
     gamma-ray flux. We show the mean differential flux in the energy range
@@
     spectrum extending down to Earth masses, the expected leptophilic fluxes are
-    ruled out by lower upper limits in 14 of the clusters, with the strongest
+    ruled out by upper limits in 14 of the clusters, with the strongest
     constraints set by Fornax and M49. We can not yet constrain the benchmark
@@
  \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.DM.eps}
-\caption{\it Comparing the flux from clusters in the extended HIFLUGCS
+\caption{\it Comparing the DM annihilation flux from clusters in the extended HIFLUGCS
   catalogue. We show the energy integrated gamma-ray fluxes derived
@@
   for each of the 106 clusters included in the extended HIFLUGCS
-  catalogue, and are derived using a single beta profile for each
+  catalogue. The CR emission is derived using a single beta profile for each
   cluster's gas density profile (see text for details). The upper
-  panel show the energy integrated flux above 100~MeV and the lower
-  panel above 10~GeV, both as a function of HIFLUGCS cluster ID. The
-  name of the four brightest clusters are written out, where Fornax
-  and M49 are the brightest targets.}
+  panel shows the energy integrated flux above 100~MeV and the lower
+  panel that above 10~GeV, both as a function of HIFLUGCS cluster ID. The
+  name of the four brightest clusters are written out. This yields Fornax
+  and M49 as the brightest targets. {\bf Anders: what is the dashed line?}}
  \label{fig21}
@@
 Assuming the projected sensitivity of the future Cherenkov telescope array (CTA)
-of [ANDERS: value?], we note that it will be difficult to detect the DM
+of {\bf Anders: value?}, we note that it will be difficult to detect the DM
 annihilation signal from clusters without a Sommerfeld boost by Cherenkov
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.CR.diff.eps}
-  \caption{\it Fermi-LAT flux upper limits are contrasted to the predictions by
-    the semi-analytic Pinzke and Pfrommer model for CRp induced gamma-ray
-    emission. We show the mean differential flux in the energy range
-    $E_\gamma=1-10$~GeV for 32 clusters. The Fermi upper limits are shown with
-    black arrows. The blue boxes show the gamma-ray emission from CRp-induced
-    $\pi^0$-decay, where the upper bound shows the estimates for an optimistic
-    model and the lower bound a more conservative model excluding point sources
-    (see \cite{2010MNRAS.409..449P} for details). Note that our models are in
-    perfect agreement with the derived upper limits from Fermi. Interestingly,
-    the limits of Virgo, Norma, and Coma are closing in on our predictions and
-    will enforce constraints on the hadronic models in the coming years.}
+  \caption{\it We contrast predictions of the CRp induced gamma-ray
+    emission using the semi-analytic Pinzke \& Pfrommer model
+    \cite{2010MNRAS.409..449P} to Fermi-LAT flux upper limits. We show
+    the mean differential flux in the energy range $E_\gamma=1-10$~GeV
+    for 32 clusters. The Fermi upper limits are shown with black
+    arrows. The blue boxes show the gamma-ray emission from
+    CRp-induced $\pi^0$-decay, where the upper bound shows the
+    estimates for an optimistic model and the lower bound a more
+    conservative model excluding point sources (see
+    \cite{2010MNRAS.409..449P} for details). Note that our models are
+    in perfect agreement with the derived upper limits from
+    Fermi. Interestingly, the limits of Virgo, Norma, and Coma are
+    closing in on our predictions and will enforce constraints on the
+    parameters of hadronic models such as shock acceleration
+    efficiencies or CR transport properties in the coming years.}
  \label{fig15}
@@
  \caption{\it Comparison of the gamma-ray flux induced by CRps for the
-   106 clusters included in the extended HIFLUGCS catalogue. The
-   fluxes are calculated within $\rvir$, and are derived using a
-   single beta profile for each cluster's gas density profile as
-   obtained by ROSAT X-ray observations. The CR distribution follows
-   the semi-analytically model derived by hydrodynamical cosmological
-   cluster simulations \cite{2010MNRAS.409..449P} (see text for
-   details). The upper panel shows the energy integrated flux above
-   100~MeV (left side) and above 100~GeV (right side), both as a
-   function of HIFLUGCS cluster ID. The eight brightest clusters are
-   labelled. The lower panel shows the relative difference between the
-   $\gamma$-ray flux predicted by the mass-luminosity scaling relation
-   and to the flux computed using the semi-analytical model
-   \cite{2010MNRAS.409..449P}. The name of the clusters with the
-   largest positive offset are printed out; as expected, they all
-   correspond to cool core clusters.}
+   106 clusters included in the extended HIFLUGCS catalogue.  The CR
+   distribution follows the semi-analytical Pinzke \& Pfrommer model
+   derived through hydrodynamical cosmological cluster simulations
+   \cite{2010MNRAS.409..449P} (see text for details).  Gamma-ray
+   fluxes are calculated within $\rvir$ and are derived using a single
+   beta profile for each cluster's gas density profile as obtained by
+   ROSAT X-ray observations. The upper panel shows the energy
+   integrated flux above 100~MeV (left side) and above 100~GeV (right
+   side), both as a function of HIFLUGCS cluster ID. The eight
+   brightest clusters are labelled. The lower panel shows the relative
+   difference between the the flux computed using the semi-analytical
+   Pinzke \& Pfrommer model and the $\gamma$-ray flux predicted by the
+   mass-luminosity scaling relation \cite{2010MNRAS.409..449P}. The
+   name of the clusters with the largest positive offset are printed
+   out; as expected, they all correspond to cool core clusters.}
  \label{fig19}
@@
 
-In this paper, we study the possibility for detecting $\gamma$-ray emission in
+In this paper, we study the possibility for detecting gamma-ray emission in
 galaxy clusters. We consider benchmark and leptophilic models of supersymmetric
@@
 halos. It turns out that the boost due to substructures dominates over the
-smooth component for halo masses $M>10^3 \msun$ [Anders?] and contributes a constant
-luminosity for each decade in halo mass. The ratio of halo-to-minimum subhalo
-mass $M_{200}/M_\mathrm{min}$ is maximized for the largest systems that had time
-to collapse and virialize since the Big Bang -- galaxy clusters. The
-corresponding substructure boost can reach values exceeding $10^3$ which should
-make nearby clusters the brightest DM annihilation sources after the Milky May
-center and hypothetical very close-by DM substructures. Since the substructures
-are distributed according to an Einasto profile, the contribution to the
-annihilation emission from substructures peaks around the virial radius. This
+smooth component for halo masses $M>10^3 \msun$ {\bf Anders: check?} and
+contributes a constant luminosity for each decade in halo mass. The ratio of
+halo-to-minimum subhalo mass $M_{200}/M_\mathrm{min}$ is maximized for the
+largest systems that had time to collapse and virialize since the Big Bang --
+galaxy clusters. The corresponding substructure boost can reach values exceeding
+$10^3$ which should make nearby clusters the brightest DM annihilation sources
+after the Milky May center and hypothetical very close-by DM
+substructures. Since the number density of substructures are distributed
+according to an Einasto profile, the contribution to the annihilation emission
+from substructures is dominated from radii close to the virial radius. This
 implies an almost flat surface brightness profile of the annihilation emission
@@
 ~\mathrm{cm}^3~\mathrm{s}^{-1}$ with imaging air Cherenkov telescopes due to the
-spatially extended boost from substructures of angular extend $\sim
-0.5-1\deg$. In contrast, the sensitivity of Cherenkov telescopes drops linearly
-with radius outside the point spread function $\sim0.1\deg$.
+spatially extended boost from substructures of angular extend $\sim 0.5-1\deg$
+(as independently found by reference \cite{2011arXiv1104.3530S}). In contrast,
+the sensitivity of Cherenkov telescopes drops linearly with radius outside the
+point spread function $\sim0.1\deg$.
 
@@
 studies as it is expected to emit the brightest annihilation flux and more
-importantly, has a comparably low CR induced $\gamma$-ray flux.  This in
-principle should allow to detect or constrain some benchmark models that have
-been chosen for the large $\gamma$-ray flux yield with three-year Fermi data
-(or constrain the substructure boost factor). Other nearby bright sources of the
-extended HIFLUGCS sample of nearby bright X-ray cluster/groups are M49,
-Centaurus, and NGC~4636.  The non-detection of $\gamma$-ray emission by Fermi in
-a total of 14 clusters/groups (the mentioned clusters as well as Virgo, Coma,
-Hydra, and Norma among others) considerably constrains leptophilic models for DM
-annihilation which were introduced to explain the increasing positron-to-lepton
-ratio beyond 10 GeV. Assuming that the minimum DM substructure mass extends down
-to an Earth mass, we can rule out these leptophilic models based on the
-non-observation of $\gamma$-rays in any of the fore-mentioned
-clusters/groups. Alternatively, assuming the leptophilic models to be correct,
-we limit the minimum substructure mass to $4~\msun$ in Fornax. Assuming
-universality of the DM model, this corresponds to a minimum substructure mass of
-$10~\msun$ in the Milky Way due to the larger Sommerfeld boost factor in smaller
-mass halos which have a lower circular velocity which enhances the particle
-cross section.
+importantly, has a comparably low CR induced gamma-ray flux.  This in principle
+should allow to detect or constrain some benchmark models that have been chosen
+for the large gamma-ray flux yield with three-year Fermi data (or constrain the
+substructure boost factor). Other nearby bright sources of the extended HIFLUGCS
+sample of nearby bright X-ray cluster/groups are M49, Centaurus, and NGC~4636.
+The non-detection of gamma-ray emission by Fermi in a total of 14
+clusters/groups (the mentioned clusters as well as Virgo, Coma, Hydra, and Norma
+among others) considerably constrains leptophilic models for DM annihilation
+which were introduced to explain the increasing positron-to-lepton ratio beyond
+10 GeV. Assuming that the minimum DM substructure mass extends down to an Earth
+mass, we can rule out these leptophilic models based on the non-observation of
+gamma-rays in any of the fore-mentioned clusters/groups. Alternatively, assuming
+the leptophilic models to be correct, we limit the minimum substructure mass to
+$>100~\msun$ in Fornax. Assuming universality of the DM model, this corresponds
+to a minimum substructure mass of $5\times 10^4~\msun$ {\bf Anders: check value} in
+the Milky Way due to the larger Sommerfeld boost factor in smaller mass halos
+which have a lower circular velocity which enhances the particle cross section.
 
@@
 DM emission. In general there are different radiation mechanism that emit in the
-$\gamma$-ray regime, namely (i) continuum emission following the hadronization
-of the annihilating neutralinos in benchmark models which leads to the
-production of charged and neutral mesons which decay finally into electrons,
-neutrinos, and gammas, and (ii) inverse Compton (IC) emission by the leptons in
-the final state which up-scatter radiation fields from the cosmic microwave
-background, dust, and starlight, and (iii) final state radiation or internal
-bremsstrahlung which dominates the highest energy emission close to the rest
-mass of the self-annihilating neutralinos (if present in the model under
-consideration). We construct a rather simple semi-analytic model for the spatial
-and spectral distribution of dust and starlight in clusters which can be used
-for the annihilation emission in galaxies with a different spatial profile.  We
-find that in benchmark models, the continuum emission dominates over the IC
-emission of any available radiation field. In the leptophilic models, where the
-continuum emission is absent, the IC up-scattering of the CMB dominate below 30
-GeV. For energies $30~\mathrm{GeV} \lesssim E_\gamma \lesssim 300~\mathrm{GeV}$,
-the IC up-scattering of the dust emission dominates and is followed by the final
-state radiation for energies up to $m_\chi c^2 \sim 1$~TeV. The IC emission of
-starlight remains always subdominant. We stress, that the inclusion of the dust
-and starlight radiation fields are important in the cooling function for the
-leptons and a failure to do so biases the inferred CMB IC flux high by a factor
-of two.
-
-We substantially improve the modelling of the expected $\gamma$-ray signal from
-pion-decay resulting from hadronic CR interactions with gas protons. We employ
-the semi-analytic model of the CR spectrum and spatial distribution, recently
-developed by \citet{2010MNRAS.409..449P} that is based on cosmological
-hydrodynamical simulations that self-consistently follow the evolution of CRs in
-cosmic structure formation. Adopting the model for all clusters in the HIFLUGCS
-sample of flux-limited X-ray clusters, we compare the expected $\gamma$-ray
-emission to that inferred from using $L_\gamma$-cluster mass scaling
-relation. We note that the predictions of our ``optimistic'' model are perfectly
-in agreement with Fermi upper limits for all clusters.  The hint of a tension
-that the scaling relation modeling showed for Norma \citep{2010ApJ...717L..71A}
-could not be confirmed due to the apparently lower gas density of this cluster
-relative to the average.  As expected, the semi-analytic model adds ``scatter''
-to the scaling relation and biases the $\gamma$-ray flux high for prominent cool
-core clusters by up to a factor of 3.5 relative to the expectation from the
-scaling relation. This is due to the high target gas densities and associated CR
+gamma-ray regime, namely (i) continuum emission following the hadronization of
+the annihilating neutralinos in benchmark models which leads to the production
+of charged and neutral mesons which decay finally into electrons, neutrinos, and
+gammas, (ii) inverse Compton (IC) emission by the leptons in the final state
+which up-scatter radiation fields from the cosmic microwave background, dust,
+and starlight, and (iii) final state radiation or internal bremsstrahlung which
+dominates the highest energy emission close to the rest mass of the
+self-annihilating neutralinos (if present in the model under
+consideration). While this final state radiation is sometimes not distinguished
+from the continuums emission contribution, we keep it separate as it dominates
+the very high-energy tail of the gamma-ray spectrum in leptophilic models while
+there the continuums emission is negligibly low.
+
+For the first time we compute the inverse Compton emission component not only
+from the upscattered CMB photons but also from a realistically modeled photon
+field due to dust and starlight extending from infra red to optical
+wavelengths. To this end, we construct a rather simple semi-analytic model for
+the spatial and spectral distribution of dust and starlight in clusters which
+can be used for the annihilation emission in galaxies with a different spatial
+profile.  We find that in benchmark models, the continuum emission dominates
+over the IC emission of any available radiation field. In the leptophilic
+models, where the continuum emission is low, the IC up-scattering of the CMB
+dominates below 60 GeV. For large clusters, the final state radiation takes then
+over for energies up to the cutoff at $m_\chi c^2 \sim 1$~TeV. In small
+clusters, there is a window around $E_\gamma \sim 100~\mathrm{GeV}$ where the IC
+up-scattering of the dust emission dominates over the CMB IC emission and the
+final state radiation. The IC emission of starlight remains always subdominant.
+We stress, that the inclusion of the dust and starlight radiation fields are
+negligible in the cooling function for the leptons.  The main reason why the IC
+emission from starlight and dust remains subdominant is the small overlap of
+this component with the peripherally peaked substructure mass density
+profiles. If for some reason, dark matter has less substructure, the relative
+importance of this inverse Compton component increases considerably.
+
+We substantially improve the modelling of the expected gamma-ray signal from
+pion-decay resulting from hadronic CR interactions with gas protons over
+previous work \citep{2010ApJ...717L..71A}. We employ the semi-analytic model of
+the CR spectrum and spatial distribution, recently developed by
+\citet{2010MNRAS.409..449P} that is based on cosmological hydrodynamical
+simulations that self-consistently follow the evolution of CRs in cosmic
+structure formation. Adopting the model for all clusters in the HIFLUGCS sample
+of flux-limited X-ray clusters, we compare the expected gamma-ray emission to
+that inferred from using $L_\gamma$-cluster mass scaling relation. We note that
+the predictions of our ``optimistic'' model are perfectly in agreement with
+Fermi upper limits for all clusters.  The hint of a tension that the scaling
+relation modeling showed for Norma \citep{2010ApJ...717L..71A} could not be
+confirmed due to the apparently lower gas density of this cluster relative to
+the average.  As expected, the semi-analytic model adds ``scatter'' to the
+scaling relation and biases the gamma-ray flux high for prominent cool core
+clusters by up to a factor of 3.5 relative to the expectation from the scaling
+relation. This is due to the high target gas densities and associated CR
 densities in those cool cores that shape the spatial emission characteristic to
 be very similar to that observed in thermal X-rays. We caution that these
-predictions only apply for the case of negligible CR transport such as streaming
-and diffusion relative to the gas and might be considerably modified in those
-cluster that do not show an extended diffuse radio(-mini) halo that might point
-to a centrally concentrated CR distribution \citep{2011A&A...527A..99E}. The CR
-spectrum $E^2 dN/dE$ shows the characteristic pion bump at energies around
-1~GeV. It is expected to dominate the DM annihilation signal in the benchmark
-models for all clusters/groups but Fornax. We conclude that it will be possible
-to rule out the leptophilic model with eight-years of Fermi data and start to
-constrain some benchmark DM models. Hence this should nicely complement direct
-and accelerator searches for the nature of dark matter.
+predictions only apply for the case of negligible active CR transport such as
+streaming and diffusion relative to the gas and might be considerably modified
+in those cluster that do not show an extended diffuse radio(-mini) halo that
+might point to a centrally concentrated CR distribution
+\citep{2011A&A...527A..99E}. The CR spectrum $E^2 dN/dE$ shows the
+characteristic pion bump at energies around 1~GeV. It is expected to dominate
+the DM annihilation signal in the benchmark models for all clusters/groups but
+Fornax. We conclude that it will be possible to rule out the leptophilic model
+with eight-years of Fermi data {\bf Anders: check} and start to constrain some
+benchmark DM models. Hence this should nicely complement direct and accelerator
+searches for the nature of dark matter.
 
@@
 
-\smallskip
-Anders Pinzke acknowledges NSF grant AST 0908480 for support.
+\smallskip Anders Pinzke acknowledges NSF grant AST 0908480 for
+support. We would furthermore like to thank KITP for their hospitality
+during the galaxy cluster workshop.  This research was supported in
+part by the National Science Foundation under Grant No. NSF
+PHY05-51164.
 
@@
  \includegraphics[width=0.99\columnwidth]{figures/SB.photon.eps}
-\caption{\it Spatial dependence of light from stars and dust. We show
-  2D surface brightness profiles in the $r$-band ($\sim 1\,\ev$)
-  obtained from stacked clusters in the Sloan Digital Sky Survey
-  (SDSS) at the redshift $z \sim 0.25$ \cite{2005MNRAS.358..949Z}. The
-  brightness profiles have been weighted with the $\rvir$ normalized
-  area inside radius $r$, and trace the radial dependence of the
-  luminosity from stars and galaxies. The crosses show the total
-  observed starlight including the diffuse intracluster (ICL), the
-  galaxies, and the brightest cluster galaxy (BCG) in the center of
-  the cluster. The diamonds denote the observed starlight from the
-  ICL and the BCG. The solid line show the fit to the data of the
-  total light including the ICL, the BCG, and the galaxies, while the
-  smooth component is represented by the dashed line that is fitted to
-  only the ICL and the BCG.}
+ \caption{\it Surface brightness profiles of the $r$-band ($h\nu\sim
+   1\,\ev$) obtained from stacked clusters in the Sloan Digital Sky
+   Survey (SDSS) at the redshift $z \sim 0.25$
+   \cite{2005MNRAS.358..949Z}. {\bf Anders, this is not clear: The
+     brightness profiles have been weighted with the $\rvir$
+     normalized area inside radius $r$, and trace the radial
+     dependence of the luminosity from stars and galaxies.}  The
+   crosses show the total observed starlight including the diffuse
+   intracluster (ICL), the galaxies, and the brightest cluster galaxy
+   (BCG) in the center of the cluster. The diamonds denote the smooth
+   part of the observed starlight from the ICL and the BCG. The solid
+   line show the fit to the data of the total light including the ICL,
+   the BCG, and the galaxies, while the smooth component is
+   represented by the dashed line that is fitted to only the ICL and
+   the BCG.}
  \label{fig:SD_spatial}
@@
 
-\begin{figure*}
-\begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/fit.ds.flux.eps}
- \includegraphics[width=0.49\columnwidth]{figures/fit.epflux.int.eps}
-\caption{\it The underlying source functions for different DM
-  models. Crosses show the simulated data from DarkSUSY and the solid
-  lines show the fit to the data using Eq.... LEFT PANEL: normalized
-  differential continuum spectra for four different DM benchmark (BM)
-  models; $\Ip$ model (red), $\Jp$ (orange), $\Kp$ (green), and
-  $\Js$ (blue). RIGHT PANEL: number of electron and positron per DM
-  annihilation above the electron energy $\ee$ for different dark
-  matter models; $\Ip$ BM model (red), $\Jp$ BM model (orange),
-  $\Kp$ BM model (green), and $\Js$ BM model (blue), leptophilic (LP)
-  DM annihilating into electrons and positrons (purple), and LP DM
-  annihilating into muons (black).}
- \label{fig:q_DM}
-\end{minipage}
-\end{figure*}
-Only LP models have energetic enough CRe such that IC emission
-powerful to either constrain or be detected
-
-similar shape for BM continuum models
+{\bf Anders: add your fit functions for the 4 BM and the LP models }
 
@@
    from deprojected Chandra and Rosat X-ray surface brightness
-  observations CITE. The total hybrid profile shown by the red solid
-  line represent the best fit to the data, where the fitted individual
-  density components are shown by the black dotted lines. The blue
-  solid line show the single beta density profile inferred from the
-  HIFLUGCS catalogue. Due to insufficient sensitivity to the outer part
-  in the plotted data, we infer the outer slope found in the HIFLUGCS
-  catalogue.}
+   observations {\bf Anders: CITE}. The total hybrid profile shown by
+   the red solid line represent the best fit to the data, where the
+   fitted individual density components are shown by the black dotted
+   lines. The blue solid line shows the single beta density profile
+   inferred from the HIFLUGCS catalogue. Due to insufficient
+   sensitivity of teh data to the outer cluster part, we use the outer
+   slope from the HIFLUGCS catalogue that is very similar to that of
+   the Coma cluster.}
  \label{fig:dens_fornax}

### 2011-05-07 paper.tex
abstract commited

@@
 \begin{abstract}
+  We study the possibility for detecting gamma-ray emission in galaxy clusters. We consider 1)
+  cosmic ray (CR) induced pion decay which is thought to dominate the astrophysical signal from
+  clusters, 2) different representative benchmark models of supersymmetric DM, and 3) leptophilic
+  models of dark matter (DM) annihilation that recently have been proposed to explain the positron
+  excess seen by PAMELA and include a Sommerfeld enhancement of the particle physics cross section
+  over its standard value. To model DM annihilation, we consider continuum emission as a result of
+  the hadronization the annihilating neutralinos, internal bremsstrahlung, and inverse Compton
+  emission from the cosmic microwave background as well as a realistic spatial and spectral
+  distribution of dust and stellar light.  After the galactic center which hosts many astrophysical
+  sources, galaxy clusters are the best known target class to detect DM annihilation. We predict
+  Virgo and Fornax to be the brightest DM sources and find a particularly low CR induced background
+  for Fornax. Because for a given minimum substructure mass as given by the DM free-streaming scale,
+  galaxy clusters are the largest collapsed objects which maximizes the boost of the smoothly
+  distributed annihilation flux by a factor of more than 1000. Since the annihilation flux of
+  substructures is mostly contributed by the regions around the virial radius, the resulting surface
+  brightness profiles are almost flat. This makes it very challenging to detect this flux with
+  imaging air Cherenkov telescopes since their sensitivity drops linearly with radius and they
+  typically encounter have $5-10$ linear resolution elements across a cluster. Assuming cold dark
+  matter with a substructure mass distribution down to an Earth mass, we rule out the leptophilic
+  models in present form in 14 clusters, and limit the boost from Sommerfeld enhancement in Fornax
+  to be less than 2 which corresponds to a value in the Milky Way of less than 5. Alternatively, if
+  the Sommerfeld enhancement factor is realized in Nature, this would imply limiting substructure
+  mass in Fornax of $\mlim > 10^2\,\msun$ corresponding to a Milky Way value of $\mlim > 5\times
+  10^3\,\msun$ which would be evidence for an unknown form of warm dark matter. We find that Fermi
+  three-year data will be able to constrain the smallest mass of substructures using the
+  supersymmetric benchmark models or alternatively their cross sections for a given substructure
+  boost. Although the Perseus and Ophiuchus clusters are expected to have the largest CR induced
+  flux according to our semi-analytic model that is derived from cosmological hydrodynamical cluster
+  simulations, their central active galactic nucleus as well as the Galactic foreground makes it
+  hard to detect this flux in the Fermi band. The next to best targets to detect the CR flux are the
+  Virgo, Coma, and Norma clusters -- the Fermi upper limits are closing in on our predictions and
+  will soon start to constraining the underlying CR physics such as shock acceleration efficiencies
+  or CR transport properties.
+\end{abstract}
+
+\del{
+--) the flux from annihilating DM is boosted by about a factor 1000 in
+  clusters
+--) flat surface brightness profiles with substructures
+--) Fornax is a great target for indirect DM studies because the relative
+  low flux from CRs and high flux from DM
+--) difficult to detect DM without a Sommerfeld boost with Cherenkov
+  telescopes since the boost from substructures is extended while the
+  sensitivity of Cherenkov telescopes drops linearly with radius
+  outside the point spread function (CHECK)
+--) the IC upscattered photons from stars and dust are dominated in the
+  relevant energy regimes by the continuum emission for our DM
+  benchmark models
+--) we provide a rather simple model to calculate the spatial and spectral
+  distribution of dust and stars in cluster (might be used for
+  galaxies? with different spatial profile)
+--) we rule out the leptophilic models in present form in 14 clusters,
+  and limit the boost from Sommerfeld enhancement in the MW to less
+  than 10
+--) the tightest limits on DM and CRs from Fermi are in the 1-10 GeV
+  regime, where Fornax, M49, and NGC4636 are the most constraining
+  "clusters" for the DM and 
 ... to be written...  if $\mlim \approx 10^{-6}\,\msun$ then the boost
@@
   alternatively if SFE correct then  $\mlim > 10^2\,\msun$.
-\end{abstract}
+}
 

### 2011-05-07 paper.tex
abstract 2nd draft

--- 2011-05-07 paper.tex
@@
 \begin{abstract}
+  We study the possibility for detecting gamma-ray emission in galaxy clusters. We consider 1)
+  cosmic ray (CR) induced pion decay which is thought to dominate the astrophysical signal from
+  clusters, 2) different representative benchmark models of supersymmetric dark matter (DM), and 3)
+  leptophilic models of DM annihilation that recently have been proposed to explain the positron
+  excess seen by PAMELA and include a Sommerfeld enhancement of the particle physics cross section
+  over its standard value. To model DM annihilation, we consider continuum emission as a result of
+  the hadronization of annihilating neutralinos, internal bremsstrahlung, and inverse Compton
+  emission from the cosmic microwave background as well as from a realistic spatial and spectral
+  distribution of dust and stellar light.  After the galactic center, which hosts many astrophysical
+  sources, galaxy clusters are the best known target class to detect DM annihilation. We predict
+  Virgo and Fornax to be the brightest DM sources and find a particularly low CR induced background
+  for Fornax. For a given minimum substructure mass as given by the DM free-streaming scale, one
+  needs the largest DM halo mass to maximize the substructure boost over the smoothly distributed
+  annihilation flux: for galaxy clusters as the largest collapsed objects, we find a boost factor of
+  more than 1000. Since the annihilation flux of substructures is mostly contributed by the regions
+  around the virial radius, the resulting surface brightness profiles are almost flat. This makes it
+  very challenging to detect this flux with imaging air Cherenkov telescopes since their sensitivity
+  drops linearly with radius and they typically encounter have $5-10$ linear resolution elements
+  across a cluster; the gamma-ray satellite Fermi is better suited. Assuming cold dark matter with a
+  substructure mass distribution down to an Earth mass and using Fermi upper limits, we rule out the
+  leptophilic models in their present form in 14 clusters, and limit the boost from Sommerfeld
+  enhancement in Fornax to be less than 2 which corresponds to a value in the Milky Way of less than
+  5. Alternatively, if the Sommerfeld enhancement factor is realized in Nature, this would imply a
+  limiting substructure mass in Fornax of $\mlim > 10^2\,\msun$ corresponding to a Milky Way value
+  of $\mlim > 5\times 10^3\,\msun$ which would be a hint for an unknown form of warm dark matter. We
+  find that Fermi three-year data will be able to constrain the smallest mass of substructures for
+  supersymmetric benchmark models or alternatively constrain their cross sections for a given
+  substructure boost. Although the Perseus and Ophiuchus clusters are expected to have the largest
+  CR induced flux according to our semi-analytic model that is derived from cosmological
+  hydrodynamical cluster simulations, their central active galactic nucleus as well as the Galactic
+  foreground makes it hard to detect this flux in the Fermi band. The next to best targets to detect
+  the CR flux are Virgo, Coma, and Norma -- the Fermi upper limits are closing in on our predictions
+  and will soon start to constrain the underlying CR physics such as shock acceleration efficiencies
+  or CR transport properties.
+\end{abstract}
+
+\del{
+--) the flux from annihilating DM is boosted by about a factor 1000 in
+  clusters
+--) flat surface brightness profiles with substructures
+--) Fornax is a great target for indirect DM studies because the relative
+  low flux from CRs and high flux from DM
+--) difficult to detect DM without a Sommerfeld boost with Cherenkov
+  telescopes since the boost from substructures is extended while the
+  sensitivity of Cherenkov telescopes drops linearly with radius
+  outside the point spread function (CHECK)
+--) the IC upscattered photons from stars and dust are dominated in the
+  relevant energy regimes by the continuum emission for our DM
+  benchmark models
+--) we provide a rather simple model to calculate the spatial and spectral
+  distribution of dust and stars in cluster (might be used for
+  galaxies? with different spatial profile)
+--) we rule out the leptophilic models in present form in 14 clusters,
+  and limit the boost from Sommerfeld enhancement in the MW to less
+  than 10
+--) the tightest limits on DM and CRs from Fermi are in the 1-10 GeV
+  regime, where Fornax, M49, and NGC4636 are the most constraining
+  "clusters" for the DM and 
 ... to be written...  if $\mlim \approx 10^{-6}\,\msun$ then the boost

### 2011-05-09 paper.tex
text and figures updated

@@
-\documentclass[10pt,aps,pra,reprint,amsmath,amsfonts,amssymb,showpacs]{revtex4-1}
+\documentclass[10pt,aps,pra,reprint,amsmath,amsfonts,amssymb,showpacs,nofootinbib,floatfix]{revtex4-1}
 \usepackage{epsfig,psfrag,graphicx,bm,color}
@@
 \newcommand{\mlim}{M_\rmn{lim}}
-
+\newcommand{\sm}{\rmn{sm}}
+\newcommand{\mpc}{\rmn{Mpc}}
+\newcommand{\kpc}{\rmn{kpc}}
+\newcommand{\mev}{\rmn{MeV}}
+\newcommand{\cm}{\rmn{cm}}
 %OLD
@@
 \begin{abstract}
-  We study the possibility for detecting gamma-ray emission in galaxy clusters. We consider 1)
-  cosmic ray (CR) induced pion decay which is thought to dominate the astrophysical signal from
-  clusters, 2) different representative benchmark models of supersymmetric dark matter (DM), and 3)
-  leptophilic models of DM annihilation that recently have been proposed to explain the positron
-  excess seen by PAMELA and include a Sommerfeld enhancement of the particle physics cross section
-  over its standard value. To model DM annihilation, we consider continuum emission as a result of
-  the hadronization of annihilating neutralinos, internal bremsstrahlung, and inverse Compton
-  emission from the cosmic microwave background as well as from a realistic spatial and spectral
-  distribution of dust and stellar light.  After the galactic center, which hosts many astrophysical
-  sources, galaxy clusters are the best known target class to detect DM annihilation. We predict
-  Virgo and Fornax to be the brightest DM sources and find a particularly low CR induced background
-  for Fornax. For a given minimum substructure mass as given by the DM free-streaming scale, one
-  needs the largest DM halo mass to maximize the substructure boost over the smoothly distributed
-  annihilation flux: for galaxy clusters as the largest collapsed objects, we find a boost factor of
-  more than 1000. Since the annihilation flux of substructures is mostly contributed by the regions
-  around the virial radius, the resulting surface brightness profiles are almost flat. This makes it
-  very challenging to detect this flux with imaging air Cherenkov telescopes since their sensitivity
-  drops linearly with radius and they typically encounter have $5-10$ linear resolution elements
-  across a cluster; the gamma-ray satellite Fermi is better suited. Assuming cold dark matter with a
-  substructure mass distribution down to an Earth mass and using Fermi upper limits, we rule out the
-  leptophilic models in their present form in 14 clusters, and limit the boost from Sommerfeld
-  enhancement in Fornax to be less than 2 which corresponds to a value in the Milky Way of less than
-  5. Alternatively, if the Sommerfeld enhancement factor is realized in Nature, this would imply a
-  limiting substructure mass in Fornax of $\mlim > 10^2\,\msun$ corresponding to a Milky Way value
-  of $\mlim > 5\times 10^3\,\msun$ which would be a hint for an unknown form of warm dark matter. We
-  find that Fermi three-year data will be able to constrain the smallest mass of substructures for
-  supersymmetric benchmark models or alternatively constrain their cross sections for a given
-  substructure boost. Although the Perseus and Ophiuchus clusters are expected to have the largest
-  CR induced flux according to our semi-analytic model that is derived from cosmological
-  hydrodynamical cluster simulations, their central active galactic nucleus as well as the Galactic
-  foreground makes it hard to detect this flux in the Fermi band. The next to best targets to detect
-  the CR flux are Virgo, Coma, and Norma -- the Fermi upper limits are closing in on our predictions
-  and will soon start to constrain the underlying CR physics such as shock acceleration efficiencies
-  or CR transport properties.
+We study the possibility for detecting gamma-ray emission in galaxy
+clusters. We consider 1) cosmic ray (CR) induced pion decay which is
+thought to dominate the astrophysical signal from clusters, 2)
+different representative benchmark models of supersymmetric dark
+matter (DM), and 3) leptophilic models of DM annihilation that
+recently have been proposed to explain the positron excess seen by
+PAMELA and include a Sommerfeld enhancement of the particle physics
+cross section over its standard value. To model DM annihilation, we
+consider continuum emission as a result of the hadronization of
+annihilating neutralinos, internal bremsstrahlung, and inverse Compton
+emission from the cosmic microwave background as well as from a
+realistic spatial and spectral distribution of dust and stellar light.
+After the galactic center, which hosts many astrophysical sources,
+galaxy clusters are the best known target class to detect DM
+annihilation. We predict Virgo and Fornax to be the brightest DM
+sources and find a particularly low CR induced background for
+Fornax. For a given minimum substructure mass as given by the DM
+free-streaming scale, one needs the largest DM halo mass to maximize
+the substructure boost over the smoothly distributed annihilation
+flux: for galaxy clusters as the largest collapsed objects, we find a
+boost factor of more than 1000. Since the annihilation flux of
+substructures is mostly contributed by the regions around the virial
+radius, the resulting surface brightness profiles are almost
+flat. This makes it very challenging to detect this flux with imaging
+air Cherenkov telescopes since their sensitivity drops linearly with
+radius and they typically encounter have $5-10$ linear resolution
+elements across a cluster; the gamma-ray satellite Fermi is better
+suited. Assuming cold dark matter with a substructure mass
+distribution down to an Earth mass and using Fermi upper limits, we
+rule out the leptophilic models in their present form in 14 clusters,
+and limit the boost from Sommerfeld enhancement in Fornax to be less
+than 2 which corresponds to a value in the Milky Way of less than
+5. Alternatively, if the Sommerfeld enhancement factor is realized in
+Nature, this would imply a limiting substructure mass in Fornax of
+$\mlim > 10^2\,\msun$ corresponding to a Milky Way value of $\mlim >
+5\times 10^3\,\msun$ which would be a hint for an unknown form of warm
+dark matter. We find that Fermi three-year data will be able to
+constrain the smallest mass of substructures for supersymmetric
+benchmark models or alternatively constrain their cross sections for a
+given substructure boost. Although the Perseus and Ophiuchus clusters
+are expected to have the largest CR induced flux according to our
+semi-analytic model that is derived from cosmological hydrodynamical
+cluster simulations, their central active galactic nucleus as well as
+the Galactic foreground makes it hard to detect this flux in the Fermi
+band. The next to best targets to detect the CR flux are Virgo, Coma,
+and Norma -- the Fermi upper limits are closing in on our predictions
+and will soon start to constrain the underlying CR physics such as
+shock acceleration efficiencies or CR transport properties.
 \end{abstract}
@@
 
-Dark matter has been searched for in direct detection experiments
+Dark matter (DM) has been searched for in direct detection experiments
 \cite{Pato:2010zk}, at accelerators
@@
 the other methods, depending on presently unknown parameters in the
-particle physics models for dark matter.
+particle physics models for DM.
 
@@
 gamma-ray annihilation signal (from the annihilation process itself,
-and also the accompanying bremsstrahlung and inverse Compton
+and also the accompanying bremsstrahlung and inverse Compton (IC)
 components coming from charged particles produced in the annihilations)
@@
 
-1. The galactic centre (g.c.). This is where all numerical simulations
-of cold dark matter predict the highest density. However, the detailed
-dark matter density in the very central part is difficult to predict,
-due a to a possibly very complicated interplay between baryons, dark
-matter, and the central galactic black hole. Also, it is a very
-crowded region with many gamma-ray sources like pulsars and other
-supernova remnants, which have to be subtracted from the data to
-extract the dark matter induced signal. In fact, there is a recent
-claim of an indication of a relatively light dark matter particle
-contribution to the gamma-ray flux from the
-g.c. \cite{2010arXiv1010.2752H}, but other hypotheses seem to work at
-least as well \cite{2010arXiv1012.5839B}.
+1. The galactic center (g.c.). This is where all numerical simulations
+of cold dark matter (CDM) predict the highest density. However, the
+detailed DM density in the very central part is difficult to predict,
+due a to a possibly very complicated interplay between baryons, DM,
+and the central galactic black hole. Also, it is a very crowded region
+with many gamma-ray sources like pulsars and other supernova remnants,
+which have to be subtracted from the data to extract the DM induced
+signal. In fact, there is a recent claim of an indication of a
+relatively light DM particle contribution to the gamma-ray flux from
+the g.c. \cite{2010arXiv1010.2752H}, but other hypotheses seem to work
+at least as well \cite{2010arXiv1012.5839B}.
 
@@
 disruption and confusion with star clusters are other
-complications. Thus the dark matter density profile is very uncertain
-for most of them. Nonetheless, by stacking the data together from many
-dwarf spheroidals these uncertainties can be made less severe, and
+complications. Thus the DM density profile is very uncertain for most
+of them. Nonetheless, by stacking the data together from many dwarf
+spheroidals these uncertainties can be made less severe, and
 preliminary results from Fermi-LAT shows this method to give quite
@@
 noted in a previous Letter \cite{2009PhRvL.103r1302P} that there are
-certain advantages that work in favour of this possible target for
-gamma-ray detection of dark matter annihilation.  Galaxy clusters
-constitute the most massive objects in our Universe that are forming
-today. This causes their DM subhalo mass function to be less affected
-by tidal stripping compared to galaxy sized halos that formed long
-ago.  The annihilation luminosities of the DM halo component for
-e.g. the Virgo cluster and the Draco dwarf scales in a way (see
+certain advantages that work in Cavour of this possible target for
+gamma-ray detection of DM annihilation.  Galaxy clusters constitute
+the most massive objects in our Universe that are forming today. This
+causes their DM subhalo mass function to be less affected by tidal
+stripping compared to galaxy sized halos that formed long ago.  The
+annihilation luminosities of the DM halo component for e.g. the Virgo
+cluster and the Draco dwarf scales in a way (see
 \cite{2009PhRvL.103r1302P}) that the ratio of gamma-ray luminosities
-from the smooth components is around 4, in favour of Virgo. In
+from the smooth components is around 4, in Cavour of Virgo. In
 addition, there may be a further enhancement due to substructure,
@@
   this paper are scaled to the currently favored value of Hubble's
-  constant, $H_0 = 70\, \rmn{km~s}^{-1}\,\rmn{Mpc}^{-1}$. We define the
-  virial mass $\mvir$ and virial radius $\rvir$ as the mass and radius
-  of a sphere enclosing a mean density that is 200 times the critical
-  density of the Universe $\rho_{\rmn{cr}}$.}.
+  constant, $H_0 = 70\, \rmn{km~s}^{-1}\,\rmn{Mpc}^{-1}$. We define
+  the virial mass $\mvir$ and virial radius $\rvir$ as the mass and
+  radius of a sphere enclosing a mean density that is 200 times the
+  critical density of the Universe $\rho_{\rmn{cr}}$.}.
 
@@
 
+{\bf Anders, insert your flux table for various clusters, and discuss it, DONE}
+
 In this paper, we will investigate in some more detail the potential
@@
 annihilation gamma-ray yield which could be observable with present
-and planned gamma-ray detectors.
-
-For previous work related to dark matter in clusters, see, e.g.,
-\cite{2006A&A...455...21C,2009PhRvD..80b3005J}.
-
-%***********************************************
-{\bf Anders, insert your flux table for various clusters, and discuss it}
-
-This yields Fornax ($\mvir=10^{14}\,\msun$) and Virgo
-($\mvir=2.1\times10^{14}\,\msun$) \del{\cite{}} as the prime targets for DM
-observations, Perseus ($\mvir=7.7\times10^{14}\,\msun$) for CR induced emission
-and we additionally decide in favor of the well studied cluster Coma
-($\mvir=1.4\times10^{15}\,\msun$) for comparison. While studying these four
-clusters in great detail, we complement the analysis by calculating the expected
-gamma-ray fluxes of a nearby X-ray flux complete sample of galaxy clusters
-(HIFLUGCS, \citealt{2002ApJ...567..716R})
+and planned gamma-ray detectors. In Table~\ref{tab:flux_tab} we show
+the gamma-ray flux from four clusters, which are all targets with a
+high gamma-ray yield. We derive the emission from two different DM
+models and a hadronic CR model and find that Virgo has the highest
+gamma-ray flux which emerge from annihilating DM. If the boost from
+Sommerfeld enhancement is small, however, then the gamma-ray emission
+induced by CRs is dominating most clusters with the exception of a few
+clusters where Fornax had the highest flux from DM. In particular, we
+find Fornax ($\mvir=10^{14}\,\msun$) and Virgo
+($\mvir=2.1\times10^{14}\,\msun$) \del{\cite{}} as the prime targets
+for DM observations, Perseus ($\mvir=7.7\times10^{14}\,\msun$) for CR
+induced emission and we additionally decide in favor of the well
+studied cluster Coma ($\mvir=1.4\times10^{15}\,\msun$) for
+comparison. While studying these four clusters in great detail, we
+complement the analysis by calculating the expected gamma-ray fluxes
+of a nearby X-ray flux complete sample of galaxy clusters (HIFLUGCS,
+\citealt{2002ApJ...567..716R}). For previous work related to DM in
+clusters, see, e.g., \cite{2006A&A...455...21C,2009PhRvD..80b3005J}.
+
+\begin{table*}
+\begin{minipage}{2.0\columnwidth}
+  \caption{Gamma-ray flux from various clusters.}
+\begin{tabular}{c  c c c  c  c c c}
+\hline
+\hline
+ Cluster &
+\multicolumn{3}{c}{$F_{\gamma}(>100\,\rmn{MeV})$ $[\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}]$:} & &
+\multicolumn{3}{c}{$F_{\gamma}(>100\,\rmn{GeV})$ $[\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}]$:} \\
+         & DM-LP $^{(1)}$ & DM-BM-$\Kp$ $^{(2)}$ & CR-$\pi^0$ $^{(3)}$ 
+         & & DM-LP $^{(1)}$ & DM-BM-$\Kp$ $^{(2)}$ & CR-$\pi^0$ $^{(3)}$ \\
+ \hline
+Fornax               & $4.8\times10^{-8}$ & $1.3\times10^{-10}$ &  $2.2\times10^{-10}$ 
+& \,\,\,\,\, & $5.6\times10^{-12}$  & $3.6\times10^{-13}$ & $8.3\times10^{-14}$ \\
+Coma                 & $1.3\times10^{-8}$ & $8.3\times10^{-11}$ &  $4.0\times10^{-9}$  
+& \,\,\,\,\, & $1.4\times10^{-12}$  & $2.3\times10^{-13}$ & $1.5\times10^{-12}$ \\
+Virgo                & $1.2\times10^{-7}$ & $4.0\times10^{-10}$ &  $8.7\times10^{-9}$  
+& \,\,\,\,\, & $1.3\times10^{-11}$  & $1.1\times10^{-12}$ & $3.2\times10^{-12}$ \\
+Perseus \,\,\,\,\,\, & $1.4\times10^{-8}$ & $7.1\times10^{-11}$ &  $1.4\times10^{-8}$  
+& \,\,\,\,\, & $1.4\times10^{-12}$  & $2.0\times10^{-13}$ & $5.2\times10^{-12}$ \\
+\hline
+\hline
+\end{tabular}
+\begin{quote}
+ Notes: \\ 
+ (1) The total gamma-ray flux from leptophilic (LP) DM where both the boost 
+ from substructures and Sommerfeld enhancement are included.\\
+ (2) The total gamma-ray flux from the supersymmetric $\Kp$ benchmark (BM) 
+ model where the boost from substructures is included.\\
+ (3) Gamma-ray flux induced by CR protons.
+ \label{tab:flux_tab}
+  \end{quote}
+\end{minipage}
+\end{table*}
 
@@
 \label{sect:theory}
-We start the section by discussing two different, but well motivated DM models;
-leptophilic and supersymmetric DM. We then present the framework that is used to
-calculate the gamma-ray emission for these DM models using an Einasto DM density
-profile and the expected enhancement from DM substructures. This is followed by
-an outline of the framework of inverse Compton emission where we take into
-account photon fields of the cosmic microwave background (CMB), dust, and
-starlight. We end by summarizing our formalism of calculating the CR-induced
-pion decay gamma-ray emission which is thought to dominate the astrophysical
+We start the section by discussing two different, but well motivated
+DM models; leptophilic and supersymmetric DM. We then present the
+framework that is used to calculate the gamma-ray emission for these
+DM models using an Einasto DM density profile and the expected
+enhancement from DM substructures. This is followed by an outline of
+the framework of IC emission where we take into account photon fields
+of the cosmic microwave background (CMB), dust, and starlight. We end
+by summarizing our formalism of calculating the CR-induced pion decay
+gamma-ray emission which is thought to dominate the astrophysical
 gamma-ray signal.
@@
 processes - which should be close to observability with the Fermi-LAT
-data \cite{1997ApJ...487..529B,2007A&A...473...41E,2010MNRAS.409..449P}
-- the possible contribution from WIMP dark matter is of greatest
-interest. A WIMP (Weakly Interactive Massive Particle) which fulfils
-the WMAP bounds on the relic density of cold dark matter (CDM) of
-\cite{Komatsu:2010fb}
+data
+\cite{1997ApJ...487..529B,2007A&A...473...41E,2010MNRAS.409..449P} -
+the possible contribution from WIMP DM is of greatest interest. A WIMP
+(Weakly Interactive Massive Particle) which fulfils the WMAP bounds on
+the relic density of CDM of \cite{Komatsu:2010fb}
 $$\Omega_{CDM}h^2=0.112\pm 0.0056,$$ will in many cases naturally give
-a gamma-yield which may be observable. In addition, there are
-possible enhancement effects known, such as the astrophysical boost
-from dense substructure of dark matter halos, or the particle physics
-boost from the Sommerfeld effect, which may increase the chances of
-detection further.
-
-There are three methods for detecting dark matter candidates which are
+a gamma-yield which may be observable. In addition, there are possible
+enhancement effects known, such as the astrophysical boost from dense
+substructure of DM halos, or the particle physics boost from the
+Sommerfeld effect, which may increase the chances of detection
+further.
+
+There are three methods for detecting DM candidates which are
 presently employed: First, at particle physics accelerators such as
@@
 allow the production of the heavy, electrically neutral and long-lived
-particles which may constitute dark matter. From these experiments one
-may get the first glimpse of the mass scale beyond the standard model
-where dark matter may reside. However, to really show that any of the
-hypothetical, new particles created at the LHC is actually the dark
-matter, one has to rely on the two other methods available for the
-dark matter search, namely direct and indirect detection. Direct
-detection methods, which are presently evolving rapidly use the feeble
-interaction between dark matter particles of the galactic halo
-and nuclei such as Germanium, Sodium, Iodine, Argon or Xenon to infer
-the scattering cross section and a rough estimate of the mass of the
-dark matter particle (for the currently most sensitive search, see
-\cite{Aprile:2010um}). A characteristic of this method is that it
-basically only depends on the local dark matter density (which is
-rather well determined to be around $0.4$ GeV/cm$^3$) and the basic
-cross section for dark matter - nucleus scattering. A disadvantage is
-that it does benefit from the two enhancement mechanisms mentioned
-above, boost from substructure and/or the Sommerfeld effect. Also, it
-cannot be excluded - although it seems at present improbable - that
-the local halo structure is such that the solar system happens to be
-in an underdense region.
+particles which may constitute DM. From these experiments one may get
+the first glimpse of the mass scale beyond the standard model where DM
+may reside. However, to really show that any of the hypothetical, new
+particles created at the LHC is actually the DM, one has to rely on
+the two other methods available for the DM search, namely direct and
+indirect detection. Direct detection methods, which are presently
+evolving rapidly use the feeble interaction between DM particles of
+the galactic halo and nuclei such as Germanium, Sodium, Iodine, Argon
+or Xenon to infer the scattering cross section and a rough estimate of
+the mass of the DM particle (for the currently most sensitive search,
+see \cite{Aprile:2010um}). A characteristic of this method is that it
+basically only depends on the local DM density (which is rather well
+determined to be around $0.4$ GeV/cm$^3$) and the basic cross section
+for DM - nucleus scattering. A disadvantage is that it does benefit
+from the two enhancement mechanisms mentioned above, boost from
+substructure and/or the Sommerfeld effect. Also, it cannot be excluded
+- although it seems at present improbable - that the local halo
+structure is such that the solar system happens to be in an underdense
+region.
 
 In indirect detection, on the other hand, in particular in the photon
-channel, one searches for products of dark matter annihilation in the
-galactic halo and beyond. Particularly interesting targets are the
-galactic center (for a recent possible indication of a signal, see
+channel, one searches for products of DM annihilation in the galactic
+halo and beyond. Particularly interesting targets are the galactic
+center (for a recent possible indication of a signal, see
 \cite{Hooper:2010mq}), the dwarf galaxies surrounding the Milky Way
@@
 
-There is also a possibility to search for dark matter annihilation indirectly in
-antimatter channels, like antiprotons or positrons. Here diffusion is, however,
-very efficient which means that the directional signature which is so important
-for gamma-rays, is completely erased. This method has, however, recently been
-much in focus due to the surprising rise with energy of the positron-to-total
-lepton ratio measured by the PAMELA satellite experiment \cite{Adriani:2008zr}
-and the ``bump'' in the total electron plus positron spectrum detected by Fermi
-\cite{Abdo:2009zk}. The viable particle physics models describing these results
-contain some non-trivial, or even unnatural elements, however. First of all,
-annihilation to quarks has to be very much suppressed, due to the
-non-observation of an enhanced antiproton flux by PAMELA
-\cite{Adriani:2010rc}. This means that only so-called {\em leptophilic} models,
-where the annihilation only goes to leptons have to be considered. Here, one has
-to have a sizeable fraction going to muons and tau leptons, as the shape of the
-spectrum disfavours direct annihilation into electrons and positrons. To get
-agreement with the measured absolute rates, one also has to have a large boost
-factor (of the order of at least several hundred), which is difficult to achieve
-with substructure alone. An additional enhancement of the annihilation rate has
-to be invoked, for example given by the {\em Sommerfeld effect}. This basically
-means that the usual connection between annihilation rate at decoupling (when
-relative velocities $v/c$ were of order $0.2 - 0.3$), which gives the relic
-density, and present-day annihilation in the halo (with velocities $v/c\sim
-10^{-3}$) is broken. This would come about because the dark matter sector
-contains additional light particles which mediates an interaction with almost
-bound states which enhance the wave function at the relative origin, and
-therefore the annihilation rate (for a pedagogical review of viable scenarios,
-see \cite{ArkaniHamed:2008qn}). As a final difficulty of these models, the lack
-of an inverse-Compton signature from the galactic center means that only shallow
-density profiles can describe the galactic dark matter density distribution
-\cite{Bertone:2008xr,Cirelli:2008pk,Bergstrom:2008ag}. (For a review of the dark
-matter modelling of these effects, see \cite{Bergstrom:2009ib}. For a recent
-treatment, showing still viable models, see \cite{Finkbeiner:2010sm}.)
+There is also a possibility to search for DM annihilation indirectly
+in antimatter channels, like antiprotons or positrons. Here diffusion
+is, however, very efficient which means that the directional signature
+which is so important for gamma-rays, is completely erased. This
+method has, however, recently been much in focus due to the surprising
+rise with energy of the positron-to-total lepton ratio measured by the
+PAMELA satellite experiment \cite{Adriani:2008zr} and the ``bump'' in
+the total electron plus positron spectrum detected by Fermi
+\cite{Abdo:2009zk}. The viable particle physics models describing
+these results contain some non-trivial, or even unnatural elements,
+however. First of all, annihilation to quarks has to be very much
+suppressed, due to the non-observation of an enhanced antiproton flux
+by PAMELA \cite{Adriani:2010rc}. This means that only so-called {\em
+  leptophilic} models, where the annihilation only goes to leptons
+have to be considered. Here, one has to have a sizeable fraction going
+to muons and tau leptons, as the shape of the spectrum disfavors
+direct annihilation into electrons and positrons. To get agreement
+with the measured absolute rates, one also has to have a large boost
+factor (of the order of at least several hundred), which is difficult
+to achieve with substructure alone. An additional enhancement of the
+annihilation rate has to be invoked, for example given by the {\em
+  Sommerfeld effect}. This basically means that the usual connection
+between annihilation rate at decoupling (when relative velocities
+$v/c$ were of order $0.2 - 0.3$), which gives the relic density, and
+present-day annihilation in the halo (with velocities $v/c\sim
+10^{-3}$) is broken. This would come about because the DM sector
+contains additional light particles which mediates an interaction with
+almost bound states which enhance the wave function at the relative
+origin, and therefore the annihilation rate (for a pedagogical review
+of viable scenarios, see \cite{ArkaniHamed:2008qn}). As a final
+difficulty of these models, the lack of an IC signature from the
+galactic center means that only shallow density profiles can describe
+the galactic DM density distribution
+\cite{Bertone:2008xr,Cirelli:2008pk,Bergstrom:2008ag}. (For a review
+of the DM modelling of these effects, see \cite{Bergstrom:2009ib}. For
+a recent treatment, showing still viable models, see
+\cite{Finkbeiner:2010sm}.)
 
@@
 pulsars or other supernova remnants (e.g.,
-\cite{Hooper:2008kg,Ahlers:2009ae}). In that case, dark matter would
-more likely be explained by the standard scenario of a WIMP, for
-example the thoroughly studied lightest supersymmetric neutralino
-(for reviews, see
+\cite{Hooper:2008kg,Ahlers:2009ae}). In that case, DM would more
+likely be explained by the standard scenario of a WIMP, for example
+the thoroughly studied lightest supersymmetric neutralino (for
+reviews, see
 \cite{Jungman:1995df,Bergstrom:2000pn,Bertone:2004pz}). We note that
@@
 has not been reproduced by other experiments) has caused intense
-activity in the theoretical dark matter community. At first, there was
+activity in the theoretical DM community. At first, there was
 skepticism whether such a large signal could be compatible with a
 WIMP. However, the possibility of an enhanced annihilation rate due to
-dark matter halo substructure has been realized for a long time
+DM halo substructure has been realized for a long time
 \cite{1993ApJ...411..439S,Bergstrom:1998zs,Moore:1999nt}, although it
-is difficult to achieve the boost factor of the order of a few
-hundred to a thousand in the solar neighborhood, as substructure
-according to numerical simulations is most important in the outer
-portions of the halo, due to tidal stripping of subhaloes in the inner
-part. Another potentially very important effect which may explain the
-large boost had been found a few years earlier, namely the Sommerfeld
+is difficult to achieve the boost factor of the order of a few hundred
+to a thousand in the solar neighborhood, as substructure according to
+numerical simulations is most important in the outer portions of the
+halo, due to tidal stripping of subhalos in the inner part. Another
+potentially very important effect which may explain the large boost
+had been found a few years earlier, namely the Sommerfeld
 enhancement. This effect, was computed for electromagnetism by Arnold
 Sommerfeld many years ago \cite{sommerfeld} and recently rediscovered
-in the quantum field theory of dark matter
+in the quantum field theory of DM
 \cite{2005PhRvD..71f3528H,2007NuPhB.787..152C,2009PhRvD..79a5014A}.
@@
 Yukawa-like particle of mass $m_\phi$, mediating a weak attractive force with
-coupling constant $\alpha_Y$ between dark matter particles $\chi$ with mass
+coupling constant $\alpha_Y$ between DM particles $\chi$ with mass
 $m_\chi$, the small-velocity limit of the enhancement becomes instead
@@
 $$ In the general case, with mediators that may also excite virtual
-charged particles in the dark matter sector, one has to solve
-numerically a coupled system of differential equations using
-appropriate boundary conditions
+charged particles in the DM sector, one has to solve numerically a
+coupled system of differential equations using appropriate boundary
+conditions
 \cite{2005PhRvD..71f3528H,2007NuPhB.787..152C,2009PhRvD..79a5014A}. In
 some cases, the enhancement factor $S$ can be as high as several
-hundred to a few thousand, depending however on the exact parameters of
-the theory. The effect is usually strongly velocity-dependent,
+hundred to a few thousand, depending however on the exact parameters
+of the theory. The effect is usually strongly velocity-dependent,
 depending on velocity as $1/v$ or, in the fine-tuning case of being
@@
 0)\lesssim 200/f\ (m_Y/1$ GeV$)$, where $f$ is the fraction of energy
-from dark matter annihilation that ionizes the intergalactic medium,
+from DM annihilation that ionizes the intergalactic medium,
 $f\sim 0.7$ for annihilation to electrons and a factor of a few smaller
@@
 Taking into account the whole cosmic history of leptophilic models,
-also utilizing limit on spectral and polarization distorsions of the
+also utilizing limit on spectral and polarization distortions of the
 CMB, the maximal value for the boost factor for a 1 to 2 TeV particle
@@
 
-To connect easily to our previous work \cite{2009PhRvL.103r1302P}, we choose as
-our benchmark leptophilic model one with mass $1.6$ TeV and Sommerfeld boost
-$S=300$ for a Milky Way halo and scale this appropriately down for cluster halos, using
-
-{\bf Anders: insert Sommerfeld boost formula as a function of halo mass}
-
-Clusters have a larger velocity dispersion and an accordingly smaller Sommerfeld
-boost factor.
+To connect easily to our previous work \cite{2009PhRvL.103r1302P}, we
+choose as our benchmark leptophilic model one with mass $1.6$~TeV and
+Sommerfeld boost $\B_\sfe(\sigv=200\,km/s)\approx 300$ for a Milky Way
+halo and scale this appropriately down for cluster halos, using {\bf
+  Anders: insert Sommerfeld boost formula as a function of halo mass, done}
+\begin{equation}
+\B_\sfe(\sigv) = 0.2\, \frac{c}{\sigv} = 
+49.4 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{1/3}\,,
+\label{eq:B_sfe}
+\end{equation}
+where the velocity dispersion $\sigv$ for clusters is derived in
+\cite{2005RvMP...77..207V}. Clusters have a larger velocity
+dispersion and an accordingly smaller Sommerfeld boost factor.
 
 \subsubsection{Supersymmetric dark matter}
-The most studied models for dark matter are supersymmetric ones, especially
-models where the lightest supersymmetric particle, in most models the lightest
-neutralino, is stable. The stability is assured in viable SUSY models due to a
-discrete symmetry, $R$-parity. This symmetry is needed from the particle physics
-point of view to avoid fast proton decay, and automatically makes the lightest
-supersymmetric particle stable, and therefore a good candidate for dark
-matter. In addition, as the coupling to ordinary matter is given by gauge
-couplings, the neutralino is automatically a WIMP candidate. Unfortunately, the
-breaking of supersymmetry (which has to be there since otherwise, e.g., there
-would exist a scalar electron with the same mass as the electron) means that a
-large number of essentially free parameters enter actual calculations.  The
-neutralino is then a linear combination of the supersymmetric partners of the
-U(1) gauge boson, $\tilde B$, one of the SU(2) gauge bosons, $\tilde W_3$, and
-the two Higgs doublets in the Minimal Supersymmetric extension of the Standard
-Model (the MSSM), $\tilde H_1^0$ and $\tilde H_2^0$, with mixing coefficients
-which depend on the SUSY breaking parameters \cite{1984NuPhB.238..453E}. The
-parameter space is very large, too large in general to scan efficiently even
-with the most powerful computers. Therefore, often simplifying assumptions are
-made to limit the number of free parameters. Even then, a large number of viable
-models is found which give a relic density consistent with the WMAP data. This
-means that they are indeed very good templates for WIMP dark matter, something
-that explains their popularity besides the subjective statement that few more
-plausible models for dark matter have been put forward so far.
+The most studied models for DM are supersymmetric ones, especially
+models where the lightest supersymmetric particle, in most models the
+lightest neutralino, is stable. The stability is assured in viable
+SUSY models due to a discrete symmetry, $R$-parity. This symmetry is
+needed from the particle physics point of view to avoid fast proton
+decay, and automatically makes the lightest supersymmetric particle
+stable, and therefore a good candidate for DM. In addition, as the
+coupling to ordinary matter is given by gauge couplings, the
+neutralino is automatically a WIMP candidate. Unfortunately, the
+breaking of supersymmetry (which has to be there since otherwise,
+e.g., there would exist a scalar electron with the same mass as the
+electron) means that a large number of essentially free parameters
+enter actual calculations.  The neutralino is then a linear
+combination of the supersymmetric partners of the U(1) gauge boson,
+$\tilde B$, one of the SU(2) gauge bosons, $\tilde W_3$, and the two
+Higgs doublets in the Minimal Supersymmetric extension of the Standard
+Model (the MSSM), $\tilde H_1^0$ and $\tilde H_2^0$, with mixing
+coefficients which depend on the SUSY breaking parameters
+\cite{1984NuPhB.238..453E}. The parameter space is very large, too
+large in general to scan efficiently even with the most powerful
+computers. Therefore, often simplifying assumptions are made to limit
+the number of free parameters. Even then, a large number of viable
+models is found which give a relic density consistent with the WMAP
+data. This means that they are indeed very good templates for WIMP DM,
+something that explains their popularity besides the subjective
+statement that few more plausible models for DM have been put forward
+so far.
 
@@
 representation of models with high enough gamma-ray rates to become
-the first candidates for dark matter indirect detection in imaging air
+the first candidates for DM indirect detection in imaging air
 Cherenkov telescopes. We use the following supersymmetric benchmark
@@
 
-{\bf Anders: add DM particle mass and cross section to all these 4 models}
+The details for the DM BM models are summarized in Table~\ref{tab:BMpara}.
+
+\begin{table}
+\begin{tabular}{cccc}
+\hline\hline
+      BM &  $m_{\chi}$     & $\Omega_{\chi} h^2$ & $\sigmaannv$\\
+         &  $[\rmn{GeV}]$ &                    & $[\rmn{cm}^3\,s^{-1}]$\\
+\hline
+$\Ip$  & 140 & 0.09 & $4.0\times 10^{-27}$ \\
+$\Jp$  & 315 & 0.12 & $3.3\times 10^{-28}$ \\
+$\Kp$  & 570 & 0.10 & $4.4\times 10^{-26}$ \\
+$\Js$  & 234 & 0.09 & $8.9\times 10^{-29}$ \\
+\hline\hline
+\end{tabular}
+ \caption{Relevant parameters for the four benchmark models. The mass
+   of the DM particles are given denoted by $m_{\chi}$, the relic
+   density by $\Omega_{\chi} h^2$ and the annihilation rate today by
+   $\sigmaannv$.\label{tab:BMpara}}
+\end{table}
+{\bf Anders: add DM particle mass and cross section to all these 4
+  models, done, might consider adding the detailed particle physics
+  info as well }
 
@@
 sections (spectral amplitude) should yield a roughly scale-invariant
-contiuums emission spectrum except for the presence of the final state
+continuum emission spectrum except for the presence of the final state
 emission feature which depends on the details of the specific decay
-channels. The right panel of Fig.~\ref{fig:q_DM} shows the cumuative
+channels. The right panel of Fig.~\ref{fig:q_DM} shows the cumulative
 number of leptons (electrons and positrons) above a given energy for
-our different DM models which is of interested for the high-energy
-inverse Compton emission of those leptons.  Only leptophilic (LP)
-models have energetic enough electrons such that the IC emission is
-powerful enough to either be constrained or detected at GeV energies
-and higher.
+our different DM models which is of interested for the high-energy IC
+emission of those leptons.  Only leptophilic (LP) models have
+energetic enough electrons such that the IC emission is powerful
+enough to either be constrained or detected at GeV energies and
+higher.
 
@@
  \includegraphics[width=0.49\columnwidth]{figures/fit.epflux.int.eps}
- \caption{\it Source functions for different DM models. Crosses show
-   the simulated data from DarkSUSY and the solid lines show the fit
-   to the data using Eq.... LEFT PANEL: normalized differential
+ \caption{\it Source functions for different dark matter (DM)
+   models. Crosses show the simulated data from DarkSUSY and the solid
+   lines show the fit to the data. LEFT PANEL: normalized differential
    continuum spectra for four different DM benchmark (BM) models;
    $\Ip$ model (red), $\Jp$ (orange), $\Kp$ (green), and $\Js$
-   (blue). RIGHT PANEL: number of electron and positron per DM
-   annihilation above the electron energy $\ee$ for different dark
-   matter models; $\Ip$ BM model (red), $\Jp$ BM model (orange), $\Kp$
-   BM model (green), and $\Js$ BM model (blue), leptophilic (LP) DM
+   (blue). We use Eq.~(\ref{eq:bm_cont}) to fit the continuum
+   spectra. RIGHT PANEL: number of electron and positron per DM
+   annihilation above the electron energy $\ee$ for different DM
+   models; $\Ip$ BM model (red), $\Jp$ BM model (orange), $\Kp$ BM
+   model (green), and $\Js$ BM model (blue), leptophilic (LP) DM
    annihilating into electrons and positrons (purple), and LP DM
    annihilating into muons (black) without considering Sommerfeld
-   boosts.}
+   boosts. We use Eq.~(\ref{eq:bm_elec}) to fit the spectra of
+   electrons and positrons.}
  \label{fig:q_DM}
@@
 that the radius of the source $r=\sqrt{l^2+D_\clu^2-2 D_\clu
-  l\cos\Psi}$, where $D_\clu$ is the distance to the source from the
-galactic center and
+  l\cos\Psi}$, where $D_\clu$ is the distance from the Earth to the
+center of the cluster halo and
 $\cos\Psi\equiv\cos\theta\cos\psi-\cos\varphi\sin\theta\sin\psi$ {\bf
-  Anders: I do not understand this equation: why galactic
-  center?}. The angular integration $\dd \Omega= \sin\theta\dd \theta
-\,\dd \varphi$ is performed over a cone centered around $\psi$ and the
-opening angle $\Delta \Omega$ is typically taken to be a few times the
-point spread function (PSF) $\psf$. The limited angular resolution
-results in a probability that a photon coming from a direction $\psi$'
-is instead reconstructed to a direction $\psi$, where the underlying
-probability distribution follow a Gaussian:
+  Anders: I do not understand this equation: why galactic center?
+  changed to earth, doen not really matter}. The angular integration
+$\dd \Omega= \sin\theta\dd \theta \,\dd \varphi$ is performed over a
+cone centered around $\psi$ and the opening angle $\Delta \Omega$ is
+typically taken to be a few times the point spread function (PSF)
+$\psf$. The limited angular resolution results in a probability that a
+photon coming from a direction $\psi$' is instead reconstructed to a
+direction $\psi$, where the underlying probability distribution follow
+a Gaussian:
 \begin{equation}
@@
 $\mu^+/\mu^-$ to $\rmn{e}^+/\rmn{e}^-$ or directly to
-$\rmn{e}^+/\rmn{e}^-$ pairs that inverse Compton upscatter background
-photons (LP-IC), leptophilic DM emitting final state radiation
-(LP-FSR), supersymmetric DM benchmark models where annihilating
-neutralinos generate $\rmn{e}^+/\rmn{e}^-$ pairs that upscatter
-background photons (BM-IC) and emit a continuum as well as final state
-radiation (BM-Cont), and CR proton induced $\pi^0$ that decays into
-gamma-rays (CR-$\pi^0$). The source function is given by
+$\rmn{e}^+/\rmn{e}^-$ pairs that IC upscatter background photons
+(LP-IC), leptophilic DM emitting final state radiation (LP-FSR),
+supersymmetric DM benchmark models where annihilating neutralinos
+generate $\rmn{e}^+/\rmn{e}^-$ pairs that upscatter background photons
+(BM-IC) and emit a continuum as well as final state radiation
+(BM-Cont), and CR proton induced $\pi^0$ that decays into gamma-rays
+(CR-$\pi^0$). The source function is given by
 \begin{equation}
@@
 It is the product of enhancement factors from SFE $\B_\sfe(\sigv)$
-(see Sect.~\ref{sect:LP}) and from substructure enhancement over the
-smooth halo contribution $\B_{\sub,i}(r) =
-1+\rho_{\sub,i}^2(r)/\rho^2(r)$ (see Sect.~\ref{sect:subst}). {\bf
+(see Eq.~\ref{eq:B_sfe} and Sect.~\ref{sect:LP}) and from substructure
+enhancement over the smooth halo contribution $\B_{\sub,i}(r) =
+1+\rho_{\sub,i}^2(r)/\rho^2(r)$ (see
+Eqs.~\ref{eq:rho_sub}-\ref{eq:xvir} and Sect.~\ref{sect:subst}). {\bf
   Anders: please add equation for $\B_{\sub,i}(M_{halo})$ here and
-  reference $B_{sfe}$ equation.} The DM source function from the
-smooth halo for each process is written in the form:
+  reference $B_{sfe}$ equation. added reference to both eqns} The DM
+source function from the smooth halo for each process is written in
+the form:
 \begin{equation}
@@
 and $\alpha$ is the shape parameter that determines the profile shape
-at the scaling radius $r_\s$ that characterizes the transition between
-the different power-law slopes. A cuspy NFW profile is given by
-$(\alpha,\beta,\gamma)=(1,1,3)$. The characteristic overdensity for an
-NFW profile is given by
+at the scaling radius $r_\s=\rvir/c$ that characterizes the transition
+between the different power-law slopes. A cuspy NFW profile is given
+by $(\alpha,\beta,\gamma)=(1,1,3)$. The characteristic overdensity for
+an NFW profile is given by
 \begin{equation}
-\rhos(c)=\frac{\Delta\,\rhoc}{3}\,\frac{c^3}
+\rhos(c)=\frac{200\,\rhoc}{3}\,\frac{c^3}
 {\log\left(1+c\right)-c/(1+c)}\,,
@@
 the density where the profile has a slope of $-2$ by $\rho_{-2}$, and
-the radius by $r_{-2}$.  Assuming that all the flux from an NFW profile
-originate from within the scale radius $\rs=\rvir/c$, and all the flux
-from an Einasto profile originate within $r_{-2}=\rvir/c$, it follows
-that $\rho_{-2} = \rhos/4$. {\bf Anders: MIGHT REMOVE THIS, COULD NOT REPRODUCE IT, CAN
-MOTIVATE THE FACTOR 4 FROM MATCHING THE MASSES FROM THE EINSASTO WITH
-THE NFW INSTEAD] SHOW INTEGRATION, COMPUTE RMAX}
+the radius by $r_{-2}=\rvir/c$. We use that the density
+$\rho_{-2}(c)=\rho_\s(c)/a(c)$ and determine $a(c)$ through $\mvir$:
+\begin{equation}
+\int_0^{\rvir}\dd V \rho_{\rm ein} = \mvir = 
+200\,\rho_{\rmn{cr}} \frac{4\pi\,\rvir^3}{3} \,.
+\end{equation}
+Here $a=(4.16-4.30)$ for $c=(3-10)$ and since $a$ is a slowly
+increasing function with $c$, we fix it for simplicity to $a(c)\approx
+a \approx 4$.
+
+{\bf Christoph: not sure where we are going with this}
+It is also useful to relate the masses to a more model independent
+variable as the maximum circular velocity given by
+\begin{eqnarray}
+V_\rmn{max} &=& V_\rmn{circ}(\rvir) 
+\left[\frac{0.216\,c}{\log(1+c)-c/(1+c)}\right]^{0.5}\propto \mvir^{0.32}\,,
+\end{eqnarray}
+where the circular velocity at radius $r$ is given by
+$V_\rmn{circ}(r)=(GM(<r)/r)^{0.5}$. We find that
+($V_\rmn{max}=1480\,\rmn{km/s}$, $R_\rmn{max}=0.61\,\rvir$) for a large
+$10^{15}\,\msun$ cluster of galaxies, and
+($V_\rmn{max}=520\,\rmn{km/s}$, $R_\rmn{max}=0.44\,\rvir$) for a small
+$4\times10^{13}\,\msun$ galaxy group.
+
+\del{
+\begin{eqnarray}
+V_\rmn{max} &=& V_\rmn{circ}(r_\rmn{max})\qquad\,\,\,\,\,\,\,\,\,\rmn{where}\nonumber\\
+V_\rmn{circ}(r)&=& \sqrt{\frac{G_\rmn{N}\,M(<r)}{r}}\qquad\rmn{and}\nonumber\\
+\frac{\dd V_\rmn{circ}(r)}{\dd r} &=& 0\quad \Longrightarrow\quad r_\rmn{max}\,.
+\end{eqnarray}
+}
+
+\del{Assuming that all the flux from an NFW profile originate from
+  within the scale radius $\rs=\rvir/c$, and all the flux from an
+  Einasto profile originate within $r_{-2}=\rvir/c$, it follows that
+  $\rho_{-2} = \rhos/4$.} {\bf Anders: SHOW INTEGRATION, COMPUTE RMAX}
 
@@
 while the substructures in the center suffer from dynamical friction
-and tidal effects depleating their central number densities. Since the
+and tidal effects depleting their central number densities. Since the
 DM annihilation rate depends on the density squared, the resulting
@@
 enhancement from substructures of the order of ten up to a few 100
-\cite{2008MNRAS.391.1685S, 2008JPhCS.125a2008K} for a MW size
-halo. {\bf Anders: motivate why we take 200; is there a reference that
-  shows that Kuhlen now also get 100-200?}  We use a double power-law
-function to fit \footnote{Our approach of fitting the scaling behavior
-  of $\rmn{L_{sub}}(<r)$ directly from numerical simulations
+\cite{2008MNRAS.391.1685S, 2008JPhCS.125a2008K} for a MW size halo. We
+adopt a boost from substructures of 230 which is the enhancement
+found in one of the highest resolved MW halos ever simulated, in
+addition, this model induce gamma-ray fluxes that allows the smallest
+mass of substructures to be constrained. {\bf Anders: motivate why we
+  take 200 DONE; is there a reference that shows that Kuhlen now also get
+  100-200? Have not found any.}  We use a double power-law function to
+fit \footnote{Our approach of fitting the scaling behavior of
+  $L_\rmn{sub}(<r)$ directly from numerical simulations
   self-consistently accounts for the radial dependence of the
@@
 \begin{eqnarray}
-  {\rm L_{sub}}(<x) &=& a_0\,C(\mvir)\,{\rm L_{200sm}}(\mvir)\,x^{a_1
+  L_\rmn{sub}(<x) &=& a_0\,C(\mvir)\,L_{200\sm}(\mvir)\,x^{a_1
     \displaystyle{x}^{a_2}}\,,\label{eq:LSub}\\
@@
 \end{eqnarray}
-Here, $\alpha_C=0.226$, $a_i$ denote our fit variables, ${\rm
-  L_{200sm}}$ is the luminosity from the smooth halo without
-substructures within $\rvir$ and $x= r/\rvir$.  We derive the
-normalization function $C(\mvir)$ in Eq.~(\ref{eq:Csub}) from the
-simulations in reference \cite{2008Natur.456...73S} using a value of
-$M_{\rm 200sim}=1.9\times10^{12}\msun$ for the mass of the MW halo in
-the simulation and $M_{\rm res,sim}=10^5\msun$ for the mass of the
+Here, $\alpha_C=0.226$, $a_i$ denote our fit variables, $L_{200\sm}$
+is the luminosity from the smooth halo without substructures within
+$\rvir$ and $x= r/\rvir$.  We derive the normalization function
+$C(\mvir)$ in Eq.~(\ref{eq:Csub}) from the simulations in reference
+\cite{2008Natur.456...73S} using a value of $M_{\rm
+  200sim}=1.9\times10^{12}\msun$ for the mass of the MW halo in the
+simulation and $M_{\rm res,sim}=10^5\msun$ for the mass of the
 smallest resolved subhalos in the MW simulation.  The smallest mass of
@@
 on scales smaller than the free streaming length. In applying
-Eq.~(\ref{eq:Csub}), we implicitely assume that the mass power-law
+Eq.~(\ref{eq:Csub}), we implicitly assume that the mass power-law
 scaling relation is valid down to the free streaming mass of DM
-halos. In the cold dark matter universe, this is conventionally taken
-to be $10^{-6}\msun$ \cite{2001PhRvD..64h3507H,
-  2005JCAP...08..003G}. Note that potentially the power-law could
-flatten towards smaller mass scales although current simulations show
-no hits of such a behavior and since Einstein's gravity is a
-scale-free theory, we do not expect such a behavior on theoretical
-grounds either.  For DM halos more (less) massive than the MW we
-expect a larger (smaller) boost from substructures, simply because of
-the larger (smaller) mass range down to the minimum mass
-$M_\rmn{lim}$.
+halos. In the CDM universe, this is conventionally taken to be
+$10^{-6}\msun$ \cite{2001PhRvD..64h3507H, 2005JCAP...08..003G}. Note
+that potentially the power-law could flatten towards smaller mass
+scales although current simulations show no hits of such a behavior
+and since Einstein's gravity is a scale-free theory, we do not expect
+such a behavior on theoretical grounds either.  For DM halos more
+(less) massive than the MW we expect a larger (smaller) boost from
+substructures, simply because of the larger (smaller) mass range down
+to the minimum mass $M_\rmn{lim}$.
 
@@
 \begin{eqnarray}
-\rho_\rmn{sub}^2(r) &=& \frac{\dd \rmn{L_{sub}}}{\dd V} \frac{1}{A_{\rmn{dm}}},\\
-\rmn{L_{200sm}} &=&  A_{\rmn{dm}} \int_{\rvir} \dd r' 4\pi r'^2 \rho^2(r'),\label{eq:Lsm}\\
- \frac{\dd \rmn{L_{sub}}}{\dd V} &=& a_0\,a_1\,C(\mvir)\,x^{a_2+a_1\,x^{a_2}}\,
-\left[\frac{1+a_2\log(x)}{4\pi\,r^3}\right],\\
-x &=& r/\rvir\,.
+\rho_\rmn{sub}^2(r) &=& \frac{\dd L_\rmn{sub}}{\dd V} \frac{1}{A_{\rmn{dm}}}\,,\label{eq:rho_sub}\\
+L_{200\sm} &=&  A_{\rmn{dm}} \int_{\rvir} \dd r' 4\pi r'^2 \rho^2(r')\,,\label{eq:Lsm}\\
+ \frac{\dd L_\rmn{sub}}{\dd V} &=& a_0\,a_1\,C(\mvir)\,x^{a_2+a_1\,x^{a_2}}\,
+\left[\frac{1+a_2\log(x)}{4\pi\,r^3}\right]\,,\\
+x &=& r/\rvir\,.\label{eq:xvir}
 \end{eqnarray}
@@
 neglected compared to the dominating boost from substructures
-(assuming dark matter to be cold). In Fig.~\ref{fig:radial_lum} we
-compare the radial dependence of the accumulative luminosity from
-different smooth cluster density profiles to the boosted luminosity
-due to substructure for different mass scales. We recalculate the
-density contrast for the core like NFW density profile $\rhos$ and
-rescale the concentration parameter in Eq.~(\ref{eq:cfit}) with
-$300/160$ \cite{2011ApJ...728L..39N} to account for the more
-centralized scale radius in cluster with a softer cusp. The emission
-coming from the density profile with a shallower inner slope
-($\beta=0.6$) as obtained by recent lensing and velocity dispersion
-measurements of the central galaxy \cite{2011ApJ...728L..39N} compared
-to a cuspy NFW ($\beta=1.0$) is about 30\% larger within $\rvir$. This
-difference is build up within $0.1\rvir$ (i.e. close to $r_\s$). Hence
-the slope of the central part of a cluster has little influence for
-the DM luminosity within $\rvir$ as long as the degeneracy in the
-lensing mass measurements with $r_\s$ (which decreases for decreasing
-inner slope) has been taken into account. The emission from an Einasto
+(assuming DM to be cold). In Fig.~\ref{fig:radial_lum} we compare the
+radial dependence of the accumulative luminosity from different smooth
+cluster density profiles to the boosted luminosity due to substructure
+for different mass scales. We recalculate the density contrast for the
+core like NFW density profile $\rhos$ and rescale the concentration
+parameter in Eq.~(\ref{eq:cfit}) with $300/160$
+\cite{2011ApJ...728L..39N} to account for the more centralized scale
+radius in cluster with a softer cusp. The emission coming from the
+density profile with a shallower inner slope ($\beta=0.6$) as obtained
+by recent lensing and velocity dispersion measurements of the central
+galaxy \cite{2011ApJ...728L..39N} compared to a cuspy NFW
+($\beta=1.0$) is about 30\% larger within $\rvir$. This difference is
+build up within $0.1\rvir$ (i.e. close to $r_\s$). Hence the slope of
+the central part of a cluster has little influence for the DM
+luminosity within $\rvir$ as long as the degeneracy in the lensing
+mass measurements with $r_\s$ (which decreases for decreasing inner
+slope) has been taken into account. The emission from an Einasto
 density profile is about 50\% larger than the cuspy NFW profile in the
@@
 for three different mass scales. Solving for the maximum of this
-curve, $\dd^2L_{200sm}/\dd (\log x)^2=0$ in combination with
-Eqn.~\ref{eq:Lsm}, we find that the luminosity from the smooth NFW
+curve, $\dd^2L_{200\sm}/\dd (\log x)^2=0$ in combination with
+Eq.~(\ref{eq:Lsm}), we find that the luminosity from the smooth NFW
 profile peaks at $r \simeq \rvir/3c$. Despite the cuspy nature of the
@@
 concentrations of $c = r_{200}/r_\s \simeq 4$, the luminosity from the
-smooth profile is focused to the regime around 10\% of $\rvir$. In
-contrast, emission from substructures is mainly contributed by the
-outer parts of DM halos where the number density of subhalos steepens
+smooth profile is focused to the regime around 10\% of $\rvir$. {\bf
+  Christoph: why is the number density of subhalos relevant here?} In contrast,
+emission from substructures is mainly contributed by the outer parts
+of DM halos where the number density of subhalos steepens
 considerably.  Note that, even though most of the substructures have
@@
   \eph}(\eph,r)= \frac{u_\sd(\eph,r)}{\eph^2}$ where the SD energy
-density $u_\sd(\eph,r)$ is given in the Appendix, Eq.~(\ref{eq:U_SD}). We model the
-CMB photon spectrum as a photon gas that is isotropically distributed
-and follows a black body spectrum with the temperature $T=2.73\,$~K:
+density $u_\sd(\eph,r)$ is given in the Appendix,
+Eq.~(\ref{eq:U_SD}). We model the CMB photon spectrum as a photon gas
+that is isotropically distributed and follows a black body spectrum
+with the temperature $T=2.73\,$~K:
 \begin{equation}
@@
 shorter than the diffusive timescale in the ICM of galaxy clusters for
-CR electrons with $\ee \gtrsim\,$~MeV {\bf Anders: CHECK}. Hence, we neglect the
-first term of the r.h.s. in Eq.~(\ref{eq:CRdiffusion}), and derive an
-expression for the equilibrium number density:
+CR electrons with \del{$\ee \gtrsim\,$~MeV}
+\cite{1997ApJ...487..529B,2011A&A...527A..99E} {\bf Anders: CHECK,
+  seems like the diffusive timescale is larger than hubble time in our
+  energy range.}. Hence, we neglect the first term of the r.h.s. in
+Eq.~(\ref{eq:CRdiffusion}), and derive an expression for the
+equilibrium number density:
 \begin{eqnarray}
@@
 spectral shape of dust and starlight in the interstellar medium of our
-Galaxy to model the emmission from clusters. We then normalize the two
+Galaxy to model the emission from clusters. We then normalize the two
 spectral components -- far IR dust and starlight at wavelengths ranging
@@
 includes the contribution from the ICL, the BCG and all the galaxies,
-while the galaxies are excluded in the smooth profile. {\bf Anders:
-  add the order of magnitude calculation that the overlap of galaxies
-  with smooth profile or substructures is minor, 1e-4 if I remember
-  correctly, motivating that we go along with the smooth SD profile.}
-We find that even for a cluster with a relative small mass the energy
-density of the SD components dominates over the CMB and the magnetic
-fields (with a central B field of 3~$\mu G$) within about 10\% of
+while the galaxies are excluded in the smooth profile. In fact, one
+can with a simple order of magnitude calculation show that the overlap
+of the SD dominated regimes in galaxies with the DM halo including
+substructures is marginal, hence we can neglect the IC upscattered SD
+photons contribution from galaxies:
+\begin{eqnarray}
+V_\rmn{icm} \approx (2\,\mpc)^3\approx 10\,\mpc^3\nonumber\\
+V_\rmn{SD,gal} \approx 0.1^3\times(0.1\,\mpc)^3 = 10^{-6}\,\mpc^3\nonumber\\
+V_\rmn{SD,sum} = N_\rmn{gal}\,V_\rmn{SD,gal} \approx 10^{-3}\,\mpc^3
+\quad\rmn{and}\nonumber\\
+V_\rmn{icm}/V_\rmn{SD,sum} \sim 10^4 \nonumber\,.
+\end{eqnarray}
+Here $V_\rmn{icm}$ denotes the total volume of the ICM of a typical
+cluster, $V_\rmn{SD,gal}$ is the volume dominated by SD in a typical
+galaxy (we have assumed that most of the SD are located inside
+$0.1\rvir$ of the galaxy), and $_\rmn{SD,sum}$ is the total volume of
+the SD in galaxies within the ICM where the number of galaxies is
+given by $ N_\rmn{gal}=10^3$.
+
+ {\bf Anders: add the order of
+  magnitude calculation that the overlap of galaxies with smooth
+  profile or substructures is minor, 1e-4 if I remember correctly,
+  motivating that we go along with the smooth SD profile. DONE}  We find
+that even for a cluster with a relative small mass the energy density
+of the SD components dominates over the CMB and the magnetic fields
+(with a central B field of 3~$\mu G$) within about 10\% of
 $\rvir$. Outside this radius the CMB is dominating the energy density
@@
 
-{\bf Anders: ADD DISCUSSION ABOUT ACCUMILATIVE LUMINOSITY}
+The spatial distribution of light emitted by SD is quite different
+from what is expected from the IC upscattered SD photons. We
+illustrate this in Fig.~\ref{fig:SD_lum}, where the accumulative
+luminosity from SD is compared to the IC SD photons for a
+$\mvir=6.0\times10^{14}\,\msun$ cluster where the boost from
+substructures is excluded. We find that the accumulative SD luminosity
+follow a flat distribution outside a few percent of $\rvir$, while the
+luminosity from IC upscattered SD photons is marginal inside
+$0.1\rvir$ and instead dominated by the outer parts of the cluster
+where the distribution follows an NFW mass profile. In the center, the
+electrons and positrons mainly cool by IC upscattering SD photons,
+hence the spatial dependence of the cooling cancels the distribution
+of the SD source function, which results in a distribution that
+approaches a density square profile in the center. We also find that
+the luminosity within $\rvir$ from the total SD model is a factor
+three larger compared to the more realistic smooth SD model. {\bf
+  Anders: ADD DISCUSSION ABOUT ACCUMULATIVE LUMINOSITY, DONE}
 
@@
    from SD in clusters. The SD luminosity is related to the cluster
-   mass through Eqns.~(\ref{eq:u_SD}-\ref{eq:N_stars}), where we use
+   mass through Eqs.~(\ref{eq:u_SD}-\ref{eq:N_stars}), where we use
    have used the mass $\mvir=10^{15}\msun$ in this figure. We
@@
 the production of both charged and neutral pions that decay into
-electrons, neutrinos, and gamma-rays. \footnote{An alternative
-  scenario is the second order turbulent re-acceleration through the
-  interaction of a previously injected relativistic population of
-  electrons by supernova driven winds or active galactic nuclei with
-  plasma waves and magneto-turbulence.} {\bf Anders: please add
-  references for the hadronic/re-acceleration scenario; look them up
-  from our Ensslin-transport paper.} Supporting evidence comes from
-the smoothness of the extended radio emission that often resembles
-that observed in thermal X-rays. Especially since the long cooling
-time of cosmic ray protons (CRps) allows for an extended and large
-population of CRps to build up over the cluster history
-\cite{1997ApJ...487..529B}.  The production of these secondaries
-depend both on the gas and CRp densities in the cluster, where the CRp
-density roughly traces the gas outside the core regime and is slightly
-enhanced in the center.  This density scaling implies that clusters
-are great targets for Cherenkov telescopes with a high sensitivity for
-the central parts of nearby clusters. Detecting the cluster gamma-ray
-emission is crucial in this respect as it potentially provides the
-unique and unambiguous evidence of CRp populations in clusters through
+electrons, neutrinos, and gamma-rays (see
+\cite{1980ApJ...239L..93D,1982AJ.....87.1266V,1999APh....12..169B,2000A&A...362..151D,2001ApJ...559...59M,2003MNRAS.342.1009M,2004A&A...413...17P,2004MNRAS.352...76P,2008MNRAS.385.1211P,2008MNRAS.385.1242P,2009JCAP...09..024K,2010MNRAS.401...47D,2010MNRAS.407.1565D,2010ApJ...722..737K,2010arXiv1011.0729K,2011A&A...527A..99E}
+). \footnote{An alternative scenario is the second order turbulent
+  re-acceleration through the interaction of a previously injected
+  relativistic population of electrons by supernova driven winds or
+  active galactic nuclei with plasma waves and
+  magneto-turbulence.\cite{1987A&A...182...21S,1993ApJ...406..399G,2004MNRAS.350.1174B,2005MNRAS.363.1173B,2007MNRAS.378..245B,2011MNRAS.410..127B,2009A&A...507..661B}}
+     {\bf Anders: please add references for the
+       hadronic/re-acceleration scenario; look them up from our
+       Ensslin-transport paper. DONE} Supporting evidence comes from
+     the smoothness of the extended radio emission that often
+     resembles that observed in thermal X-rays. Especially since the
+     long cooling time of cosmic ray protons (CRps) allows for an
+     extended and large population of CRps to build up over the
+     cluster history \citep{1996SSRv...75..279V, 1997ApJ...477..560E,
+       1997ApJ...487..529B}. The production of these secondaries
+     depend both on the gas and CRp densities in the cluster, where
+     the CRp density roughly traces the gas outside the core regime
+     and is slightly enhanced in the center.  This density scaling
+     implies that clusters are great targets for Cherenkov telescopes
+     with a high sensitivity for the central parts of nearby
+     clusters. Detecting the cluster gamma-ray emission is crucial in
+     this respect as it potentially provides the unique and
+     unambiguous evidence of CRp populations in clusters through
      observing the $\pi^0$ bump at about 100~MeV in the spectra.
@@
 by Pinzke \& Pfrommer \cite{2010MNRAS.409..449P} to estimate the
-emission from decaying $\pi^0$:s that dominates over the inverse
-Compton emission from primary and secondary electrons above 100~MeV in
-clusters. The gamma-ray formalism was derived from high resolution
-simulations of clusters of galaxies that included radiative
-hydrodynamics, star formation, supernova feedback, and followed CRp
-physics using a novel formulation that trace the most important
-injection and loss processes self-consistently while accounting for
-the CRp pressure in the equation of motion
+emission from decaying $\pi^0$:s that dominates over the IC emission
+from primary and secondary electrons above 100~MeV in clusters. The
+gamma-ray formalism was derived from high resolution simulations of
+clusters of galaxies that included radiative hydrodynamics, star
+formation, supernova feedback, and followed CRp physics using a novel
+formulation that trace the most important injection and loss processes
+self-consistently while accounting for the CRp pressure in the
+equation of motion
 \cite{2008A&A...481...33J,2007A&A...473...41E,2006MNRAS.367..113P}.
@@
 shocks is injected into CRps while this efficiency rapidly decreases
-for weaker shocks \cite{2007A&A...473...41E}. As a caviat we note that
-the semi-analytic odel is based on simulations that only considered
+for weaker shocks \cite{2007A&A...473...41E}. As a caveat we note that
+the semi-analytic model is based on simulations that only considered
 advective transport of CRs by turbulent gas motions which produces
@@
 foreground due to the similar spectral index. For energies below
-100~MeV we expect inverse Compton emission by primary shock
-accelerated electrons to be dominating \cite{2010MNRAS.409..449P} over
-the supersymmetric DM induced leptons. Hence the IC emission from
-supersymmetric DM in clusters can for DM benchmark models be safely
-neglected compared to the CRps and DM continuum emission.
+100~MeV we expect IC emission by primary shock accelerated electrons
+to be dominating \cite{2010MNRAS.409..449P} over the supersymmetric DM
+induced leptons. Hence the IC emission from supersymmetric DM in
+clusters can for DM benchmark models be safely neglected compared to
+the CRps and DM continuum emission.
 
@@
   lower right $\Js$. The emission is calculated for the Fornax cluster
-  using a point spread function of $0.1\deg$ and a boost from
-  substructures of 570 (ADD SUBBOOST ON SD MODEL, SHOULD BE ONLY
-  FACTOR FEW). We find bright prospects for detecting the continuum
-  emission, that is dominating the total emission in the GeV energy
-  range, in the models $\Ip$ and $\Kp$. }
+  using a point spread function of $0.1\deg$. The substructures boost
+  the gamma-ray flux from IC upscattered CMB and continuum emission by
+  570 while the IC upscattered SD photons is boosted by 20. We find
+  bright prospects for detecting the continuum emission, that is
+  dominating the total emission in the GeV energy range, in the models
+  $\Ip$ and $\Kp$.}
  \label{fig:diff_BM}
@@
 
-{\bf Ander: I got that far with the results, please polish the reminder up to population studies!}
+{\bf Anders: I got that far with the results, please polish the reminder up to population studies!}
 
@@
 
-One of the main contributions to the expected extended gamma-ray is
-coming from the IC upscattered photons on various photon background
+One of the main contributions to the expected extended gamma-ray flux
+is coming from the IC upscattered photons on various photon background
 fields. Depending on the spatial and spectral distribution of
@@
 
-If the substructure boost in clusters is significant, then the total
-electron and positron distribution is dominated by its radial profile
-outside the very center where the smooth density profile dominates
-over the substructures and the cooling from SD dominates over the
-CMB. Especially since the SD distribution is centrally peaked and the
-substructure distribution peaks in the outskirts around $\rvir$, the
-overlap is small. This results in a suppression of the IC upscattered
-SD photons relative to the IC upscattered CMB, the FSR and the
-continuum emission. However if substructures are only marginally
-dominating over the smooth distribution in a cluster, the SD component
-becomes more important, especially in the 100~GeV to 1~TeV energy
-regime where the IC on CMB photons is small.
+If the enhancement due to substructures in clusters is significant,
+then the distribution of electrons and positrons follows the radial
+profile of substructures outside the cluster center where the smooth
+DM density profile is dominating. In addition, the cooling of the
+steady state electron and positron distribution is dominated by SD
+photons in the center. Especially since the SD distribution is
+centrally peaked and the substructure distribution peaks in the
+outskirts around $\rvir$, the overlap between electrons/positrons and
+SD photons is small. This results in a suppression of the IC
+upscattered SD photons relative to the IC upscattered CMB photons, the
+FSR, and the continuum emission. However, if substructures are only
+marginally dominating over the smooth distribution in a cluster, the
+SD component becomes more important, especially the flux from IC
+upscattered CMB photons is small for LP models in the 100~GeV to 1~TeV
+energy regime and in the 1~GeV to 100~GeV energy regime for BM models.
 
@@
 remove the boost from substructures, the density profile of electrons
-and prositrons is more centrally peaked, and the relative importance
-of the IC upscattered SD increases. In addition the IC upscattered CMB
-light would suffer more from SD cooling in the center. \del{Even though
-the SD component seems to be suppressed compared to the CMB at
-energies around 100~MeV, it has a relative large impact on the steady
-state electron spectrum. If we remove the SD cooling, we find a factor
-two larger IC flux at low energies for a cluster of the size of
-Fornax. For more massive clusters we expect a larger IC flux from the
-SD component, but a smaller contribution from the CMB because of the
-more effective cooling.} EXPAND DISCUSSION
+and positrons is more centrally peaked, and the relative importance
+of the IC upscattered SD increases by a factor $\sim 30$. In
+addition, the IC upscattered CMB light would suffer more from SD
+cooling in the center as most of its flux resides from the outer parts
+when substructures are included. For comparison, we include the
+contribution of IC upscattered SD photons and to bracket the
+uncertainty in the SD model, with a small amount of dust. In this low
+dust model we have reduced the energy in dust by a factor 10. However,
+we find that the IC SD flux only decreases by a factor 3 since the
+cooling of the electrons and positrons also decreases. Note that for a
+smaller boost from substructures, the effect from cooling is smaller.
+\del{Even though the SD component seems to be suppressed compared to
+  the CMB at energies around 100~MeV, it has a relative large impact
+  on the steady state electron spectrum. If we remove the SD cooling,
+  we find a factor two larger IC flux at low energies for a cluster of
+  the size of Fornax. For more massive clusters we expect a larger IC
+  flux from the SD component, but a smaller contribution from the CMB
+  because of the more effective cooling.}
 
@@
 overproduce the upper gamma-ray limit in the $1-10$~GeV energy
-interval set by Fermi-LAT by about a factor 100. This imposes tight
-constraints on both the boost from substructures and the Sommerfeld
-enhancement. These constraints might improve with future more
-sensitive Cherenkov telescopes. However considering that an indirect
-detection of DM in clusters relies on the boost from substructures
-whose main contribution comes from the periphery, we conclude that the
-wide angular extent of clusters in gamma-rays on the sky suggest that
-these sources are not ideal for Cherenkov telescopes due to the loss
-of sensitivity outside the small PSF (BETTER CHECK THIS WITH SOME
-EXPERT).
+interval set by Fermi-LAT by about a factor 100. This strongly
+constrain the boost from both substructures and the Sommerfeld
+enhancement. Additional, these constraints might improve with future
+more sensitive Cherenkov telescopes such as CTA. However, considering
+that an indirect detection of DM in clusters relies on the boost from
+substructures whose main contribution comes from the periphery, we
+conclude that the wide angular extent of clusters on the sky in
+gamma-rays suggest that these sources are not ideal for Cherenkov
+telescopes due to the loss of sensitivity outside the small PSF
+{\bf BETTER CHECK THIS WITH SOME EXPERT}.
 
@@
   each individual radiation field from top line to bottom line; CMB
-  (green dashed-tripple-dotted), dust (purple dashed), stars (blue
+  (green dashed-triple-dotted), dust (purple dashed), stars (blue
   dashed-dotted). The sum of the three components are shown with the
@@
   Fornax cluster within $\rvir$ using a point spread function of
-  $0.1\deg$. For this cluster, the boost from Sommerfeld and
-  substructures is about 130 and 570, respectively.}
+  $0.1\deg$. For this cluster, the boost from Sommerfeld is about 130
+  and the enhancement due to substructures from IC upscattered CMB and
+  SD photons is 570 and 20, respectively.}
  \label{fig:IR_comp}
@@
 It is also interesting to compare the total contribution from the LP
-model, the brightest BM model ($\Kp$), and the CRp induced emission. In
-Fig.~\ref{fig:flux_int} we show the integrated flux from Fornax for
-our different gamma-ray models and compare it to the unresolved
-integrated flux upper limit on Fornax set by Fermi-LAT where they
-averaged the flux over the energy range $0.2-100\,\gev$ assuming a
-spectral index of 2. Again we are overproducing the upper limits,
-although only with a factor 10 which is about a order magnitude less
-constraining than the differential flux in the energy range
-$1-10$~GeV. From the figure one clearly see that the LP model is
+model, the brightest BM model ($\Kp$), and the CRp induced
+emission. In Fig.~\ref{fig:flux_int} we show the integrated flux from
+Fornax for our different gamma-ray models and compare it to the
+unresolved integrated flux upper limit on Fornax set by Fermi-LAT
+where they averaged the flux over the energy range $0.2-100\,\gev$
+assuming a spectral index of 2. Again we are overproducing the upper
+limits, although only with a factor 10 which is about a order
+magnitude less constraining than the differential flux in the energy
+range $1-10$~GeV. From the figure one clearly see that the LP model is
 dominating the entire gamma-ray energy range up to the DM mass of this
-model of about 1~TeV. In addition it is interesting to note that the
-flux the DM BM $\Kp$ model is above the predicted emission from the
-CRps in the $1-100$~GeV energy regime accessible both to Fermi and
-Cherenkov telescopes.
+model of about 1~TeV. Finally, we note that the flux the DM BM $\Kp$
+model is above the predicted emission from the CRps in the $1-100$~GeV
+energy regime accessible both to Fermi and Cherenkov
+telescopes. Hence, in the absence of LP DM the prospects for detecting
+the $\Kp$ BM model over the expected gamma-ray background induced by
+CRps look promising.
 
@@
 for the angular extended Virgo cluster. It is quite striking how
-constraining the upper limits for the Fornax cluster is compared to
+constraining the upper limits for the Fornax cluster are compared to
 the other clusters, especially in the $1-10$~GeV energy regime where
 Fermi-LAT is most sensitive due to the maximized effective area. The
-upper limits for Virgo and Perseus are background contaminated by AGN
-activity from M87 and NGC 1267, respectively, and do not gain much
-from the increased sensitivity. One should also note that the high CRp
-induced flux from both Coma and Perseus is of the same magnitude as
-the DM flux from LP models, making it difficult for indirect DM
-searches in those clusters. Conversely is the Fornax cluster a great
-target for indirect DM studies because the relative low gamma-ray flux
-from CRps, absents of an active AGN, and high DM gamma-ray
-flux. Actually, the Fermi-LAT 3 year data will be able to constrain
-the smallest mass of substructures using the DM BM models. We have
-also learned that the closest clusters are superior for DM searches
-compared to further away clusters, even though the close by clusters
-have a mass that is smaller. In fact, we can understand this by
-looking at the luminosity-to-mass scaling relations. The gamma-ray
-luminosity from the smooth density profile is given by
+upper limits for Virgo and Perseus are unfortunately background
+contaminated by AGN activity from M87 and NGC 1267, respectively, and
+do not gain much from the increased sensitivity. One should also note
+that the high CRp induced flux from both Coma and Perseus is of the
+same magnitude as the DM flux from LP models, making it difficult for
+indirect DM searches in those clusters. Conversely is the Fornax
+cluster a great target for indirect DM studies because the relative
+low gamma-ray flux from CRps, absents of an active AGN, and high DM
+gamma-ray flux. Actually, the Fermi-LAT 3 year data will be able to
+constrain the smallest mass of substructures using the DM BM
+models. We have also learned that the closest clusters are superior
+for DM searches compared to further away clusters, even though the
+close by clusters have a mass that is much smaller. In fact, we can
+understand this by looking at the luminosity-to-mass scaling
+relations. The gamma-ray luminosity from the smooth density profile is
+given by \cite{2009PhRvL.103r1302P}
 \begin{equation}
-L_{\gamma,\rmn{sm}} \propto \int \dd V \rho(r)^2 \propto \frac{c^3}
+L_{\gamma,\sm} \propto \int \dd V \rho(r)^2 \propto \frac{c^3}
 {\left[\log\left(1+c\right)-c/(1+c)\right]} \propto \mvir^{0.83}\,,
@@
 \rmn{where} \\
-B_\rmn{LP}&=&B_\sfe B_\sub \propto \mvir^{-1/3}\mvir^{0.23} \propto
+\B_\rmn{LP}&=&\B_\sfe \B_\sub \propto \mvir^{-1/3}\mvir^{0.23} \propto
  \mvir^{-0.1}\,,\\
-B_\rmn{BM}&=&B_\sub \propto \mvir^{0.23}\,.
+\B_\rmn{BM}&=&\B_\sub \propto \mvir^{0.23}\,.
 \end{eqnarray}
@@
 but increasing the distance by a factor two decrease the flux with a
-factor four. One should also note that the IC on SD photons scales
-slightly softer with mass, hence giving rise to a larger fraction of
-gamma-rays in low mass clusters compared to the total gamma-ray
-flux. In addition, considering that the brightest cluster galaxy
-constitute a relative larger contribution to the SD luminosity in low
-mass clusters which increase the importance of the SD component in low mass
-clusters even more (c.f. Fig.~\ref{fig:IR_comp}).
-
-It is also useful to relate the luminosities to a more model
-independent variable as the maximum circular velocity given by
-\begin{eqnarray}
-V_\rmn{max} &=& V_\rmn{circ}(r_\rmn{max})\qquad\,\,\,\,\,\,\,\,\,\rmn{where}\nonumber\\
-V_\rmn{circ}(r)&=& \sqrt{\frac{G_\rmn{N}\,M(<r)}{r}}\qquad\rmn{and}\nonumber\\
-\frac{\dd V_\rmn{circ}(r)}{\dd r} &=& 0\quad \Longrightarrow\quad r_\rmn{max}\,.
-\end{eqnarray}
-We find that $V_\rmn{max}=650\,\rmn{km/s}$ of a large $10^{15}\,\msun$
-cluster, and $V_\rmn{max}=420\,\rmn{km/s}$ of a small
-$4\times10^{13}\,\msun$ group.
+factor four. One should also note that the IC upscattered SD photons
+scales slightly softer with mass, hence giving rise to a larger
+fraction of gamma-rays in low mass clusters compared to the total
+gamma-ray flux. \del{Furthermore, the low mass clusters have a higher flux
+from IC upscattered SD photons than high mass clusters which increase
+the importance of the SD component in low mass clusters even more
+(c.f. Fig.~\ref{fig:IR_comp}).}
 
@@
 
-peak sensitivity of Fermi at these energies due to a combination of effective area background and source spectra...
-
-As we have seen in this section the LP models overproduce both the
-differential and integrated flux upper limits set by the Fermi-LAT for
-several clusters. We can use these upper limits to enforce constraints
-on the SFE and boost from substructures. As more sensitive experiments
-and better upper limits emerge, we can start ruling out models that
-give rise to boost factors that are manifested in the gamma-ray
-flux. It is especially interesting is to constrain the SFE, where a
-boost of 300 is required to explain the excess of electrons and
-positrons observed in the vicinity of Earth by PAMELA/Fermi/HESS.  In
-Fig.~\ref{fig:clu_comp} we use the estimated flux from four clusters
-to constrain the SFE as well as the minimum mass of substructures
-where $M_\rmn{lim}\propto\mvir^{0.226}$. As expected, the Fornax
-cluster is the most constraining cluster by far, although the current
-upper limits are not good enough to rule out the boost from
-substructures or SFE. Assuming that the electron and positron excess
-is due to SFE DM matter, then in order not to overproduce the
+\del{
+peak sensitivity of Fermi at these energies due to a combination of effective area background and source spectra...}
+
+In this section we have found that the LP DM models overproduce both
+the differential and integrated gamma-ray flux upper limits set by the
+Fermi-LAT 18 month data for several clusters. We can use these upper
+limits to constrain both the SFE and boost from
+substructures. Furthermore, as more sensitive experiments and better
+upper limits emerge, we can start ruling out models that give rise to
+boost factors that are manifested in the gamma-ray flux. It is
+especially interesting is to constrain the SFE, where a boost of 300
+is required to explain the excess of electrons and positrons observed
+in the vicinity of Earth by PAMELA/Fermi/HESS. In
+Fig.~\ref{fig:boost_const} we use the estimated flux from four
+clusters to constrain the SFE as well as the minimum mass of
+substructures where $M_\rmn{lim}\propto\mvir^{0.226}$. As expected,
+the Fornax cluster is the most constraining cluster by far, although
+the current upper limits are not good enough to rule out the boost
+from substructures or SFE. Assuming that the electron and positron
+excess is due to SFE DM, then in order not to overproduce the
 differential upper limits set by Fermi-LAT in the energy range
 $1-10$~GeV \footnote{We average the LP DM flux in the energy range
-  $1-10$~GeV before we compare it to the upper limits.}  we can
+  $1-10$~GeV before we compare it to the upper limits.}, we can
 constrain the smallest mass of substructures to $M_\rmn{lim}\gtrsim
 100\,\msun$. Instead assuming the standard mass of the smallest
-substructures of $M_\rmn{lim}\gtrsim 10^{-6}\,\msun$, we can constrain
-the boost from SFE to about 2 in Fornax, corresponding to a maximum
-SFE in the MW of about 5.
+substructures of $M_\rmn{lim}\approx 10^{-6}\,\msun$, we can constrain
+the boost from SFE to about 2 in Fornax, which corresponds to a
+maximum SFE in the MW of about 5. Note that after about six years of
+observations with Fermi-LAT, we will be able to rule out the LP model
+assuming a substructure boost with a smallest mass of $M_\rmn{lim} =
+10^{-6}\,\msun$.
 
@@
    (orange), M49 (green), and NGC4636 (blue). The SFE has been
-   rescaled from the MW value of 300 {\bf Anders (refer to equation)}
-   that is required to explain the electron and positron excess
-   observed at Earth with LP DM (black arrow). If the DM
-   interpretation is correct, we can constrain the smallest size of
-   halos to be larger than $100\,\msun$. Contrarily, if the smallest
-   size of DM halos is $10^{-6}\,\msun$, we can constrain the SFE to
-   about 2 in Fornax, corresponding to a maximum SFE in the MW of
-   about 5 which would be too small to support the DM annihilation
-   hypothesis for the Pamela/Fermi excess.}
+   rescaled from the MW value of 300 (c.f. Eq.~\ref{eq:B_sfe}) {\bf
+     Anders (refer to equation), DONE} that is required to explain the
+   electron and positron excess observed at Earth with LP DM (black
+   arrow). If the DM interpretation is correct, we can constrain the
+   smallest size of halos to be larger than $100\,\msun$. Contrarily,
+   if the smallest size of DM halos is $10^{-6}\,\msun$, we can
+   constrain the SFE to about 2 in Fornax, corresponding to a maximum
+   SFE in the MW of about 5 which would be too small to support the DM
+   annihilation hypothesis for the Pamela/Fermi excess.}
  \label{fig:boost_const}
@@
 \label{sect:spatial}
-[ADD DUSTY STAR FORMING GALAXIES IN OUTERPARTS (LITTLE OVERLAP), DUST
-  WOULD NOT SURVIVE. IF DUST RAMPRESSURE STRIPPED, SPATIALLIATION
-  PROCESS IN THE HOT ICM FOR DYNAMICAL TIME] The large angular extent
-of clusters on the sky in combination with the small PSF of most
-gamma-ray probes ($\sim 0.1$~deg) suggest that we would be able to
-probe the different spatial regimes of a cluster. Especially important
-is the spatial distribution of the gamma-ray emission as it bias upper
-limits derived for spatially extended clusters where a simple density
-profile is often assumed. In fact when DM substructures are included
-the total brightness profile is almost flat and very different from
-the smooth halo distribution with a steep outer brightness slope of
-$-5$.
+{\bf should probably be integrated into text; DUSTY STAR FORMING
+  GALAXIES IN OUTER PARTS (LITTLE OVERLAP), DUST WOULD NOT SURVIVE. IF
+  DUST RAMPRESSURE STRIPPED, SPATIALLIATION PROCESS IN THE HOT ICM FOR
+  DYNAMICAL TIME} The large angular extent of clusters on the sky in
+combination with the small PSF of most gamma-ray probes ($\sim
+0.1$~deg) suggest that we would be able to probe the different spatial
+regimes of a cluster. Especially important is the spatial distribution
+of the gamma-ray emission as it bias upper limits derived for
+spatially extended clusters where a simple profile is often
+assumed. In fact when DM substructures are included, the gamma-ray
+brightness profile is almost flat and very different from the
+gamma-ray distribution following a smooth density profile with a steep
+outer brightness slope of $-5$.
 
@@
 from different clusters in Fig.~\ref{fig:SB_clu}. As expected, we find
-that the DM flux in all clusters follow the same smooth universal
-shape imposed by the substructures. Even as far in as 1\% of $\rvir$
-we are dominated by the substructures, which is due to the projection
-of the outer cluster halo (see Sect.~\ref{sect:subst} for a longer
+that the DM flux in all clusters follow the same universal shape
+imposed by the substructures. Even as far in as 1\% of $\rvir$ we are
+dominated by the substructures, which is due to the projection of the
+outer cluster halo (see Sect.~\ref{sect:subst} for a longer
 discussion). This implies that the spatial distribution of
 annihilating DM induced emission is independent of the type of DM
-model, and can not be used to separate different models. The
+model, and can not be used to separate different models {\bf
+  Christoph, include this finding in conclusions, abstract?}. The
 normalization for the BM model is determined by $\bsub
@@
 normalization which is due to the additional contribution from SFE
-with a negative mass trend, hence a normalization with a softer
+with a negative mass trend, hence a flux normalization with a softer
 mass-scaling of $\sim\mvir^{0.17}$. The surface brightness induced by
@@
 very inner part of Fornax is dominated by a large gamma-ray flux from
-CRps, which however, is neglible compared to the flux withing
+CRps, which is however, neglible compared to the flux withing
 $\rvir$. This is the reason why Fornax is such a good target for
@@
 galaxies. Although, it might be a problem for Cherenkov telescopes
-looking for a DM in the center of Fornax.
+searching for DM in the center of Fornax.
 
@@
 extent of the cluster, even though Fornax has one of the highest
-ratios of DM/CRp gamma-ray brightness.
+ratios of DM to CRp induced gamma-ray brightness.
 
@@
 
-NEED TO REWRITE, JUMPING BACK AND FORTH BETWEEN PANELS In order to
-learn about the spatial distribution of the DM flux in various
+\del{NEED TO REWRITE, JUMPING BACK AND FORTH BETWEEN PANELS} In order
+to learn about the spatial distribution of the DM flux in various
 clusters for different DM models and associated gamma-ray components,
@@
 the components study in the right panel that show the neglible
-contribution from the IC upscattered light from SD at this
-energy. Since the surface brightness from BM models are dominated by
-the continuum emission at each radial bin in all clusters, we see that
-the total DM emission follows the projected density profile over the
-entire clusters. The LP model, however, give rise to a much flatter
-profile in the central parts of the clusters. This is due to the IC
-upscattered CMB photons that are upscattered on an electron and
-positron population that suffers from efficient cooling on light from
-SD. The IC emission from SD photons have a rather steep spectrum in
-the center that follows the projected density profile which is
-explained by the SD dominated cooling that cancels the spatial
-dependence from the SD spectrum. In the left panel we also find some
-variation in the profiles for the different clusters in the central
+contribution at this energy from the IC upscattered SD photons that
+follow a steeper distribution in the outer parts because of the
+decreasing energy density of SD photons with radius. Since the surface
+brightness from BM models are dominated by the continuum emission at
+each radial bin in all clusters, we find that the total DM BM emission
+follows the projected density profile over the entire clusters. In
+addition, the sum of the IC upscattered photons for the LP model
+approximately trace the same distribution, although with the exception
+in the core regime where we find a transition from centrally
+dominating IC SD light to the IC CMB light. The transition is due to
+the IC upscattered CMB photons that trace the smooth profile in the
+core and outer parts of the cluster, while the electron and positron
+population suffers from efficient cooling on light from SD in the
+center which flatten the IC CMB profile. Conversely trace the LP IC
+emission from SD photons a steeper distribution in the center that
+follows the projected density profile. This is explained by the SD
+dominated cooling that cancels the spatial dependence from the SD
+source function. \del{In the left panel we also find some variation in
+  the profiles for the different clusters in the central
   parts. Especially in the Fornax cluster, where we find a factor two
@@
   Fornax; a low X-ray luminous cluster has a low energy density in
-starlight and dust in our semi-analytic SD model. However, note that
-the surface brightness from the SD component is suppresses at the
-relative low energy of 1~GeV.  Since there is no enhancement from the
-substructures, the overall mass normalization of the LP DM model has a
-marginally negative trend $\sim\mvir^{-0.06}$. Hence, we only see a
-very small difference in outer parts of the different clusters from
-these type of models. The BM DM models have a normalization of
-$\sim\mvir^{0.27}$, hence more massive clusters show a slightly higher
-surface brightness. As also noticed in previous figure, the flux from
-DM without substructures is dominated by the CRp induced emission for
-all clusters.
+  starlight and dust in our semi-analytic SD model.} It should be
+noted that the surface brightness due to SD upscattered photons is
+suppressed at the relative low energy of 1~GeV. Furthermore, since
+there is no enhancement from substructures, the overall mass
+normalization of the LP DM model has a marginally negative trend
+$\sim\mvir^{-0.06}$. Hence, we only see a very small difference in
+outer parts of the different clusters from these type of models. The
+DM BM models have a normalization of $\sim\mvir^{0.27}$, hence more
+massive clusters show a slightly higher surface brightness. Finally,
+we note that the flux from DM without substructures is dominated by
+the CRp induced emission for all clusters.
 
@@
 In Sect.~\ref{sect:spatial} we saw that the spectral distribution of
-the gamma-ray flux from the LP model were dominated at high energies
-of $100\,$~GeV by final state radiation and the IC upscattered
-starlight and dust, while the BM models were mainly dominated by the
-continuum emission. These high energies are reachable by both
-Fermi-LAT and Cherenkov telescopes, thus important observationally. We
-therefore show in Fig.~\ref{fig:SB_IACTs} the surface brightness above
-$100\,$~GeV for a realistic PSF of $0.1\deg$ where we include the
-boost from substructures. We look at two clusters with an expected
-high DM signal; the relative small Fornax cluster and the massive
-close by Virgo cluster Both clusters show a very flat brightness
-profile within about 10\% of $\rvir$, due to both the effect from
+gamma-ray flux from the LP model was dominated at high energies of
+about $100\,$~GeV by FSR and IC upscattered starlight and dust, while
+the BM models were mainly dominated by the continuum emission. These
+high energies are reachable by both Fermi-LAT and Cherenkov
+telescopes, thus important observationally. We therefore show in
+Fig.~\ref{fig:SB_IACTs} the surface brightness above $100\,$~GeV for a
+realistic PSF of $0.1\deg$ where we include the boost from
+substructures. We investigate two clusters with an expected high DM
+signal; the relative small Fornax cluster and the massive close by
+Virgo cluster. Both clusters show a very flat brightness profile
+within about 10\% of $\rvir$, due to both the effect from
 substructures and the smoothening over the PSF. The CRp induced
@@
 the outer part of the Fornax cluster the CRp flux is suppressed
-compared to the substructure boosted DM flux, where the LP model is
-over three orders of magnitude larger. Although, it should be noted
-that there are large uncertainties in the gas density profile used to
-estimate the CRp surface brightness (see Fig.~\ref{fig:dens_fornax}
-for more details).
+compared to the substructure boosted DM flux, where the LP model give
+rise to a gamma-ray flux that is more than three orders of magnitude
+larger. Although, it should be noted that there are large
+uncertainties in the gas density profile which we use to estimate the
+CRp induced gamma-ray surface brightness (see
+Fig.~\ref{fig:dens_fornax} for more details).
 
@@
   \includegraphics[width=0.99\columnwidth]{figures/MLscaling.10G.eps}
-  \caption{\it Scaling relations of the cluster's virial mass $M_{200}$ and the
+  \caption{\it Scaling relations of the cluster's virial mass $\mvir$ and the
     $\gamma$-ray luminosity for energies $E_\gamma>100$~MeV (left) and
@@
     includes the scaling of the substructure and Sommerfeld boost factors with
-    cluster mass from Equation~(\ref{eq:LP_scaling}) (dash-dotted) as well as the
+    cluster mass from Eq.~(\ref{eq:LP_scaling}) (dash-dotted) as well as the
     benchmark model $K'$ of DM annihilation that includes the scaling of the
-    substructure boost with cluster mass of Equation~(\ref{eq:BM_scaling})
+    substructure boost with cluster mass of Eq.~(\ref{eq:BM_scaling})
     (dashed). Note that the scaling of this particular benchmark model is
@@
 mass scaling of the substructure boost steepens the intrinsically shallower DM
-annihilation relation of benchmark models (Equation~(\ref{eq:BM_scaling})) while
+annihilation relation of benchmark models (Eq.~\ref{eq:BM_scaling}) while
 this steepening is in fact over-compensated by the inverse mass scaling of the
 Sommerfeld boost in leptophilic models that prefers smaller halos with a larger
-ratio of $c/v_\mathrm{circ}$ (Equation~(\ref{eq:LP_scaling})). In contrast, the
+ratio of $c/v_\mathrm{circ}$ (Eq.~\ref{eq:LP_scaling}). In contrast, the
 CR scaling relation is considerably steeper as shown by reference
-\cite{2010MNRAS.409..449P}. {\bf Anders: add CR scaling formula} This implies
+\cite{2010MNRAS.409..449P}: 
+\begin{eqnarray}
+L_{\rmn{CR}-\ensuremath{\pi^0}}(>100\,\mev) = 3.13\times10^{45}
+\left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.46}\nonumber\\
+L_{\rmn{CR}-\ensuremath{\pi^0}}(>10\,\gev)  = 2.23\times10^{43}
+\left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.34}\nonumber\\
+\end{eqnarray}
+{\bf Anders: add CR scaling formula, DONE} This implies
 already a general strategy to minimize the CR-induced foreground for DM
@@
  \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.DM.eps}
-\caption{\it Comparing the DM annihilation flux from clusters in the extended HIFLUGCS
-  catalogue. We show the energy integrated gamma-ray fluxes derived
-  from both leptophilic DM that result in inverse Compton upscattered
-  CMB photons (red), and the continuum emission from the DM $\Kp$
-  benchmark model (blue). The fluxes are calculated within $\rvir$
-  for each of the 106 clusters included in the extended HIFLUGCS
-  catalogue. The CR emission is derived using a single beta profile for each
-  cluster's gas density profile (see text for details). The upper
-  panel shows the energy integrated flux above 100~MeV and the lower
-  panel that above 10~GeV, both as a function of HIFLUGCS cluster ID. The
-  name of the four brightest clusters are written out. This yields Fornax
-  and M49 as the brightest targets. {\bf Anders: what is the dashed line?}}
+\caption{\it Comparing the DM annihilation flux from clusters in the
+  extended HIFLUGCS catalogue. We show the energy integrated gamma-ray
+  fluxes derived from both leptophilic DM that result in inverse
+  Compton upscattered CMB photons (red), and the continuum emission
+  from the DM $\Kp$ benchmark model (blue). The fluxes are calculated
+  within $\rvir$ for each of the 106 clusters included in the extended
+  HIFLUGCS catalogue. The CR emission is derived using a single beta
+  profile for each cluster's gas density profile (see text for
+  details). The upper panel shows the energy integrated flux above
+  100~MeV and the lower panel that above 10~GeV, both as a function of
+  HIFLUGCS cluster ID. For comparison we show with a dashed line the
+  estimated point source sensitivity of the Fermi-LAT after two years
+  of data taking $\sim
+  2\times10^{-9}\,\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$ . The name of
+  the four brightest clusters are written out. This yields Fornax and
+  M49 as the brightest targets. {\bf Anders: what is the dashed
+    line? DONE}}
  \label{fig21}
@@
 
-Figure~\ref{fig14} compares Fermi upper limits on the $\gamma$-ray flux with
-predictions of DM annihilation fluxes in the leptophilic and benchmark models.
-To obtain the $\gamma$-ray fluxes, we scale the virial mass of clusters in the
-extended HIFLUGCS catalogue \cite{2002ApJ...567..716R} with our scaling
-relations of Equations~(\ref{eq:BM_scaling}) and (\ref{eq:LP_scaling}). In
-Figure~\ref{fig14}, we compare only those clusters of the HIFLUGCS sample with
-Fermi limits to our predictions and show the DM flux predictions of the entire
-sample in Fig.~\ref{fig21}.  We assume a boost factor due to substructures that
-has a constant contribution per decade in substructure mass and has a mass
-spectrum extending down to Earth masses. Fermi limits rule out the leptophilic
-models in their present form with the mentioned assumptions in 14 clusters, and
-limit the boost from Sommerfeld enhancement to less than 4 [?] in
-Fornax. Assuming universality, this limits the Sommerfeld boost in the MW to
-less than 10 (see Fig.~\ref{fig:boost_const}).  The flux level of the Fermi
-limits are an indirect measure of the ambient background flux in the
-$\gamma$-ray sky and/or the presence of strong point sources such as AGN in the
-immediate vicinity of the cluster position. Hence, the ratio of the Fermi upper
-limits to the predicted annihilation fluxes,
-$F_{\mathrm{UL}}/F_{\mathrm{scal}}$, is a good indication of the best cluster
-candidates for indirect DM experiments. We identify Fornax, M49, NGC4636, and
-Virgo to be prime candidates. Note however, that Virgo extends of $7\deg$ over
-the sky which implies a lower surface brightness and lower signal-to-noise.
-Fermi limits on individual clusters are expected to improve as $\sqrt{T/1.5
-  \mathrm{yr}}$, where $T$ is the total elapsed time of the Fermi mission. We
-emphasize that the very inhomogeneous distribution of $F_{\mathrm{UL}}/
-F_{\mathrm{scal}}$ makes it unlikely to dramatically improve the limits through
-a stacking analysis as the weak signal will dilute the average constraints.
-Assuming the projected sensitivity of the future Cherenkov telescope array (CTA)
-of {\bf Anders: value?}, we note that it will be difficult to detect the DM
-annihilation signal from clusters without a Sommerfeld boost by Cherenkov
-telescopes. This is because the boost from substructures is extended while the
-sensitivity of Cherenkov telescopes drops linearly with radius outside the point
+Figure~\ref{fig14} compares Fermi upper limits on the $\gamma$-ray
+flux with predictions of DM annihilation fluxes in the leptophilic and
+benchmark models.  To obtain the $\gamma$-ray fluxes, we scale the
+virial mass of clusters in the extended HIFLUGCS catalogue
+\cite{2002ApJ...567..716R} with our scaling relations of
+Eqs.~(\ref{eq:BM_scaling}) and (\ref{eq:LP_scaling}). In
+Figure~\ref{fig14}, we compare only those clusters of the HIFLUGCS
+sample with Fermi limits to our predictions and show the DM flux
+predictions of the entire sample in Fig.~\ref{fig21}.  We assume a
+boost factor due to substructures that has a constant contribution per
+decade in substructure mass and has a mass spectrum extending down to
+Earth masses. Fermi limits rule out the leptophilic models in their
+present form with the mentioned assumptions in 14 clusters, and limit
+the boost from Sommerfeld enhancement to less than 4 [?] in
+Fornax. Assuming universality, this limits the Sommerfeld boost in the
+MW to less than 10 (see Fig.~\ref{fig:boost_const}).  The flux level
+of the Fermi limits are an indirect measure of the ambient background
+flux in the $\gamma$-ray sky and/or the presence of strong point
+sources such as AGN in the immediate vicinity of the cluster
+position. Hence, the ratio of the Fermi upper limits to the predicted
+annihilation fluxes, $F_{\mathrm{UL}}/F_{\mathrm{scal}}$, is a good
+indication of the best cluster candidates for indirect DM
+experiments. We identify Fornax, M49, NGC4636, and Virgo to be prime
+candidates. Note however, that Virgo extends of $7\deg$ over the sky
+which implies a lower surface brightness and lower signal-to-noise.
+Fermi limits on individual clusters are expected to improve as
+$\sqrt{T/1.5 \mathrm{yr}}$, where $T$ is the total elapsed time of the
+Fermi mission. We emphasize that the very inhomogeneous distribution
+of $F_{\mathrm{UL}}/ F_{\mathrm{scal}}$ makes it unlikely to
+dramatically improve the limits through a stacking analysis as the
+weak signal will dilute the average constraints.  Assuming the
+projected sensitivity of the future Cherenkov telescope array (CTA) of
+$2\times10^{-14} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$
+\cite{2009arXiv0908.1410D} {\bf Anders: value?, DONE}, we note that it
+will be difficult to detect the DM annihilation signal from clusters
+without a Sommerfeld boost by Cherenkov telescopes. This is because
+the boost from substructures is extended while the sensitivity of
+Cherenkov telescopes drops linearly with radius outside the point
 spread function.
@@
 clusters for our $\gamma$-ray flux estimates
-\cite{2002ApJ...567..716R}). We derive the central gas densites for
+\cite{2002ApJ...567..716R}). We derive the central gas densities for
 each cluster by following the approach outlined in
@@
 
-In this paper, we study the possibility for detecting gamma-ray emission in
-galaxy clusters. We consider benchmark and leptophilic models of supersymmetric
-dark matter as well as cosmic ray induced pion decay which is thought to
-dominate the astrophysical signal from clusters. Once supersymmetric cold dark
-matter decouples from the expanding universe it streams and erases any
-potentially present smaller scales. Once gravitational instabilities causes
-halos to collapse, this free-streaming scale imprints as a characteristic
-minimum halo mass $M_\mathrm{min}$ into the hierarchy of structure formation and
-should still survive until the present time as substructure within larger
-halos. It turns out that the boost due to substructures dominates over the
-smooth component for halo masses $M>10^3 \msun$ {\bf Anders: check?} and
-contributes a constant luminosity for each decade in halo mass. The ratio of
-halo-to-minimum subhalo mass $M_{200}/M_\mathrm{min}$ is maximized for the
-largest systems that had time to collapse and virialize since the Big Bang --
-galaxy clusters. The corresponding substructure boost can reach values exceeding
-$10^3$ which should make nearby clusters the brightest DM annihilation sources
-after the Milky May center and hypothetical very close-by DM
-substructures. Since the number density of substructures are distributed
-according to an Einasto profile, the contribution to the annihilation emission
-from substructures is dominated from radii close to the virial radius. This
-implies an almost flat surface brightness profile of the annihilation emission
-which makes it necessary to have the entire cluster in the field-of-view to take
-advantage of the entire substructure boost.  This property makes it difficult to
-detect DM annihilation emission without an enhancement of the particle physics
-cross section over its standard value of $\sigma v\sim 3\times 10^{-26}
-~\mathrm{cm}^3~\mathrm{s}^{-1}$ with imaging air Cherenkov telescopes due to the
-spatially extended boost from substructures of angular extend $\sim 0.5-1\deg$
-(as independently found by reference \cite{2011arXiv1104.3530S}). In contrast,
-the sensitivity of Cherenkov telescopes drops linearly with radius outside the
-point spread function $\sim0.1\deg$.
-
-We identify Fornax to be the best cluster/group candidate for indirect DM
-studies as it is expected to emit the brightest annihilation flux and more
-importantly, has a comparably low CR induced gamma-ray flux.  This in principle
-should allow to detect or constrain some benchmark models that have been chosen
-for the large gamma-ray flux yield with three-year Fermi data (or constrain the
-substructure boost factor). Other nearby bright sources of the extended HIFLUGCS
-sample of nearby bright X-ray cluster/groups are M49, Centaurus, and NGC~4636.
-The non-detection of gamma-ray emission by Fermi in a total of 14
-clusters/groups (the mentioned clusters as well as Virgo, Coma, Hydra, and Norma
-among others) considerably constrains leptophilic models for DM annihilation
-which were introduced to explain the increasing positron-to-lepton ratio beyond
-10 GeV. Assuming that the minimum DM substructure mass extends down to an Earth
-mass, we can rule out these leptophilic models based on the non-observation of
-gamma-rays in any of the fore-mentioned clusters/groups. Alternatively, assuming
-the leptophilic models to be correct, we limit the minimum substructure mass to
-$>100~\msun$ in Fornax. Assuming universality of the DM model, this corresponds
-to a minimum substructure mass of $5\times 10^4~\msun$ {\bf Anders: check value} in
-the Milky Way due to the larger Sommerfeld boost factor in smaller mass halos
-which have a lower circular velocity which enhances the particle cross section.
-
-In this work, we thoroughly study the spectral emission characteristics of the
-DM emission. In general there are different radiation mechanism that emit in the
-gamma-ray regime, namely (i) continuum emission following the hadronization of
-the annihilating neutralinos in benchmark models which leads to the production
-of charged and neutral mesons which decay finally into electrons, neutrinos, and
-gammas, (ii) inverse Compton (IC) emission by the leptons in the final state
-which up-scatter radiation fields from the cosmic microwave background, dust,
-and starlight, and (iii) final state radiation or internal bremsstrahlung which
-dominates the highest energy emission close to the rest mass of the
-self-annihilating neutralinos (if present in the model under
-consideration). While this final state radiation is sometimes not distinguished
-from the continuums emission contribution, we keep it separate as it dominates
-the very high-energy tail of the gamma-ray spectrum in leptophilic models while
-there the continuums emission is negligibly low.
-
-For the first time we compute the inverse Compton emission component not only
-from the upscattered CMB photons but also from a realistically modeled photon
-field due to dust and starlight extending from infra red to optical
-wavelengths. To this end, we construct a rather simple semi-analytic model for
-the spatial and spectral distribution of dust and starlight in clusters which
-can be used for the annihilation emission in galaxies with a different spatial
-profile.  We find that in benchmark models, the continuum emission dominates
-over the IC emission of any available radiation field. In the leptophilic
-models, where the continuum emission is low, the IC up-scattering of the CMB
-dominates below 60 GeV. For large clusters, the final state radiation takes then
-over for energies up to the cutoff at $m_\chi c^2 \sim 1$~TeV. In small
-clusters, there is a window around $E_\gamma \sim 100~\mathrm{GeV}$ where the IC
-up-scattering of the dust emission dominates over the CMB IC emission and the
-final state radiation. The IC emission of starlight remains always subdominant.
-We stress, that the inclusion of the dust and starlight radiation fields are
-negligible in the cooling function for the leptons.  The main reason why the IC
-emission from starlight and dust remains subdominant is the small overlap of
-this component with the peripherally peaked substructure mass density
-profiles. If for some reason, dark matter has less substructure, the relative
-importance of this inverse Compton component increases considerably.
-
-We substantially improve the modelling of the expected gamma-ray signal from
-pion-decay resulting from hadronic CR interactions with gas protons over
-previous work \citep{2010ApJ...717L..71A}. We employ the semi-analytic model of
-the CR spectrum and spatial distribution, recently developed by
-\citet{2010MNRAS.409..449P} that is based on cosmological hydrodynamical
-simulations that self-consistently follow the evolution of CRs in cosmic
-structure formation. Adopting the model for all clusters in the HIFLUGCS sample
-of flux-limited X-ray clusters, we compare the expected gamma-ray emission to
-that inferred from using $L_\gamma$-cluster mass scaling relation. We note that
-the predictions of our ``optimistic'' model are perfectly in agreement with
-Fermi upper limits for all clusters.  The hint of a tension that the scaling
-relation modeling showed for Norma \citep{2010ApJ...717L..71A} could not be
-confirmed due to the apparently lower gas density of this cluster relative to
-the average.  As expected, the semi-analytic model adds ``scatter'' to the
-scaling relation and biases the gamma-ray flux high for prominent cool core
-clusters by up to a factor of 3.5 relative to the expectation from the scaling
-relation. This is due to the high target gas densities and associated CR
-densities in those cool cores that shape the spatial emission characteristic to
-be very similar to that observed in thermal X-rays. We caution that these
-predictions only apply for the case of negligible active CR transport such as
-streaming and diffusion relative to the gas and might be considerably modified
-in those cluster that do not show an extended diffuse radio(-mini) halo that
+In this paper, we study the possibility for detecting gamma-ray
+emission in galaxy clusters. We consider benchmark and leptophilic
+models of supersymmetric dark matter (DM) as well as cosmic ray
+induced pion decay which is thought to dominate the astrophysical
+signal from clusters. Once supersymmetric cold dark matter decouples
+from the expanding universe it streams and erases any potentially
+present smaller scales. Once gravitational instabilities causes halos
+to collapse, this free-streaming scale imprints as a characteristic
+minimum halo mass $M_\mathrm{min}$ into the hierarchy of structure
+formation and should still survive until the present time as
+substructure within larger halos. It turns out that the boost due to
+substructures dominates over the smooth component for halo masses
+$\mvir>10^3 \msun$ {\bf Anders: check?OK} and contributes a constant
+luminosity for each decade in halo mass. The ratio of halo-to-minimum
+subhalo mass $\mvir/M_\mathrm{min}$ is maximized for the largest
+systems that had time to collapse and virialise since the Big Bang --
+galaxy clusters. The corresponding substructure boost can reach values
+exceeding $10^3$ which should make nearby clusters the brightest DM
+annihilation sources after the Milky May center and hypothetical very
+close-by DM substructures. Since the number density of substructures
+are distributed according to an Einasto profile, the contribution to
+the annihilation emission from substructures is dominated from radii
+close to the virial radius. This implies an almost flat surface
+brightness profile of the annihilation emission which makes it
+necessary to have the entire cluster in the field-of-view to take
+advantage of the entire substructure boost.  This property makes it
+difficult to detect DM annihilation emission without an enhancement of
+the particle physics cross section over its standard value of $\sigma
+v\sim 3\times 10^{-26} ~\mathrm{cm}^3~\mathrm{s}^{-1}$ with imaging
+air Cherenkov telescopes due to the spatially extended boost from
+substructures of angular extend $\sim 0.5-1\deg$ (as independently
+found by reference \cite{2011arXiv1104.3530S}). In contrast, the
+sensitivity of Cherenkov telescopes drops linearly with radius outside
+the point spread function $\sim0.1\deg$.
+
+We identify Fornax to be the best cluster/group candidate for indirect
+DM studies as it is expected to emit the brightest annihilation flux
+and more importantly, has a comparably low CR induced gamma-ray flux.
+This in principle should allow to detect or constrain some benchmark
+models that have been chosen for the large gamma-ray flux yield with
+three-year Fermi data (or constrain the substructure boost
+factor). Other nearby bright sources of the extended HIFLUGCS sample
+of nearby bright X-ray cluster/groups are M49, Centaurus, and
+NGC~4636.  The non-detection of gamma-ray emission by Fermi in a total
+of 14 clusters/groups (the mentioned clusters as well as Virgo, Coma,
+Hydra, and Norma among others) considerably constrains leptophilic
+models for DM annihilation which were introduced to explain the
+increasing positron-to-lepton ratio beyond 10 GeV. Assuming that the
+minimum DM substructure mass extends down to an Earth mass, we can
+rule out these leptophilic models based on the non-observation of
+gamma-rays in any of the fore-mentioned
+clusters/groups. Alternatively, assuming the leptophilic models to be
+correct, we limit the minimum substructure mass to $>100~\msun$ in
+Fornax. Assuming universality of the DM model, this corresponds to a
+minimum substructure mass of $5\times 10^4~\msun$ {\bf Anders: check
+  value, DO not understand what you mean by universality, or how you
+  get the minimum mass} in the Milky Way due to the larger Sommerfeld
+boost factor in smaller mass halos which have a lower circular
+velocity which enhances the particle cross section.
+
+In this work, we thoroughly study the spectral emission
+characteristics of the DM emission. In general there are different
+radiation mechanism that emit in the gamma-ray regime, namely (i)
+continuum emission following the hadronization of the annihilating
+neutralinos in benchmark models which leads to the production of
+charged and neutral mesons which decay finally into electrons,
+neutrinos, and gammas, (ii) inverse Compton (IC) emission by the
+leptons in the final state which up-scatter radiation fields from the
+cosmic microwave background, dust, and starlight, and (iii) final
+state radiation or internal bremsstrahlung which dominates the highest
+energy emission close to the rest mass of the self-annihilating
+neutralinos (if present in the model under consideration). While this
+final state radiation is sometimes not distinguished from the
+continuums emission contribution, we keep it separate as it dominates
+the very high-energy tail of the gamma-ray spectrum in leptophilic
+models while there the continuums emission is negligibly low.
+
+For the first time we compute the IC emission component not only from
+the upscattered cosmic microwave (CMB) photons but also from a
+realistically modeled photon field due to dust and starlight extending
+from infra red to optical wavelengths. To this end, we construct a
+rather simple semi-analytic model for the spatial and spectral
+distribution of dust and starlight in clusters which can be used for
+the annihilation emission in galaxies with a different spatial
+profile.  We find that in benchmark models, the continuum emission
+dominates over the IC emission of any available radiation field. In
+the leptophilic models, where the continuum emission is low, the IC
+up-scattering of the CMB dominates below 60 GeV. For large clusters,
+the final state radiation takes then over for energies up to the
+cutoff at $m_\chi c^2 \sim 1$~TeV. In small clusters, there is a
+window around $E_\gamma \sim 100~\mathrm{GeV}$ where the IC
+up-scattering of the dust emission dominates over the CMB IC emission
+and the final state radiation. The IC emission of starlight remains
+always subdominant.  We stress, that the inclusion of the dust and
+starlight radiation fields are negligible in the cooling function for
+the leptons.  The main reason why the IC emission from starlight and
+dust remains subdominant is the small overlap of this component with
+the peripherally peaked substructure mass density profiles. If for
+some reason, DM has less substructure, the relative importance of this
+IC component increases considerably.
+
+We substantially improve the modelling of the expected gamma-ray
+signal from pion-decay resulting from hadronic CR interactions with
+gas protons over previous work \citep{2010ApJ...717L..71A}. We employ
+the semi-analytic model of the CR spectrum and spatial distribution,
+recently developed by \citet{2010MNRAS.409..449P} that is based on
+cosmological hydrodynamical simulations that self-consistently follow
+the evolution of CRs in cosmic structure formation. Adopting the model
+for all clusters in the HIFLUGCS sample of flux-limited X-ray
+clusters, we compare the expected gamma-ray emission to that inferred
+from using $L_\gamma$-cluster mass scaling relation. We note that the
+predictions of our ``optimistic'' model are perfectly in agreement
+with Fermi upper limits for all clusters.  The hint of a tension that
+the scaling relation modeling showed for Norma
+\citep{2010ApJ...717L..71A} could not be confirmed due to the
+apparently lower gas density of this cluster relative to the average.
+As expected, the semi-analytic model adds ``scatter'' to the scaling
+relation and biases the gamma-ray flux high for prominent cool core
+clusters by up to a factor of 3.5 relative to the expectation from the
+scaling relation. This is due to the high target gas densities and
+associated CR densities in those cool cores that shape the spatial
+emission characteristic to be very similar to that observed in thermal
+X-rays. We caution that these predictions only apply for the case of
+negligible active CR transport such as streaming and diffusion
+relative to the gas and might be considerably modified in those
+cluster that do not show an extended diffuse radio(-mini) halo that
 might point to a centrally concentrated CR distribution
 \citep{2011A&A...527A..99E}. The CR spectrum $E^2 dN/dE$ shows the
-characteristic pion bump at energies around 1~GeV. It is expected to dominate
-the DM annihilation signal in the benchmark models for all clusters/groups but
-Fornax. We conclude that it will be possible to rule out the leptophilic model
-with eight-years of Fermi data {\bf Anders: check} and start to constrain some
-benchmark DM models. Hence this should nicely complement direct and accelerator
-searches for the nature of dark matter.
+characteristic pion bump at energies around 1~GeV. It is expected to
+dominate the DM annihilation signal in the benchmark models for all
+clusters/groups but Fornax. We conclude that it will be possible to
+rule out the leptophilic model with eight-years of Fermi data {\bf
+  Anders: check, I would say six years data since in fig 11 we can
+  constrain $B_sfe < 2$ in Fornax, -> $2**2*1.5 = 6$ years} and start
+to constrain some benchmark DM models. Hence this should nicely
+complement direct and accelerator searches for the nature of DM.
 
@@
 \subsection{Radial profiles}
-ADD CALCULATION ABOUT GALAXY OVERLAP WITH THE ICM
+
 \begin{figure}%[t]
@@
      normalized area inside radius $r$, and trace the radial
-     dependence of the luminosity from stars and galaxies.}  The
-   crosses show the total observed starlight including the diffuse
-   intracluster (ICL), the galaxies, and the brightest cluster galaxy
-   (BCG) in the center of the cluster. The diamonds denote the smooth
-   part of the observed starlight from the ICL and the BCG. The solid
-   line show the fit to the data of the total light including the ICL,
-   the BCG, and the galaxies, while the smooth component is
-   represented by the dashed line that is fitted to only the ICL and
-   the BCG.}
+     dependence of the luminosity from stars and galaxies. REMOVE,
+     OLD, ADDED SENTENCE IN END} The crosses show the total observed
+   starlight including the diffuse intracluster (ICL), the galaxies,
+   and the brightest cluster galaxy (BCG) in the center of the
+   cluster. The diamonds denote the smooth part of the observed
+   starlight from the ICL and the BCG. The solid line show the fit to
+   the data of the total light including the ICL, the BCG, and the
+   galaxies, while the smooth component is represented by the dashed
+   line that is fitted to only the ICL and the BCG. Note that, we use
+   total SD brightness in the cluster center to normalize the SD
+   surface brightness profiles.}
  \label{fig:SD_spatial}
@@
 & && &&&
-\label{fit_spatial_IR}
+\label{fit_spatial_IR_sm}
 \end{align}
@@
 
-{\bf Anders: add your fit functions for the 4 BM and the LP models }
+{\bf Anders: add your fit functions for the 4 BM and the LP models. NEED MORE WORK}
+\begin{eqnarray}
+q_\rmn{BM}&=&\left(\frac{\rho\,c^2}{\gev\,\cm^{-3}}\right)^2\times
+\left(\frac{10^{33}}{\eg1.6e-3}\right) \nonumber\\
+&\times&\left\{a_1\frac{\exp\left(-\eg^{-a_2}\right)}{1+\exp\left(\eg^{a_3}\right)}+a_5^{\left(4-\beta_1\right)}\,a_4\,\eg^{\beta_1}
+\exp\left[-\left(\frac{\eg}{a_5}\right)^{\beta_2}\right]\right\} \nonumber\\
+ \label{eq:bm_cont}
+\end{eqnarray}
+
+\del{      egn = eg/GeV
+diffBM=(p1*dexp(-egn**(-p2))/(1.+dexp(egn**p3))+
+     1     p5**(4.-pow1)*p4*egn**pow1*dexp(-(egn/p5)**pow2))
+     2     /(egn)/GeV}
+
+where the common parameters $\beta_1 = 4.5,\,\beta_2 = 15$, and the
+model specific parameters:
+\begin{table}
+\begin{tabular}{c c c c c c }
+\hline
+\hline
+ BM model & $a_1$ & $a_2$  & $a_3$ & $a_4$  & $a_5$ \\
+ \hline
+$\Ip$ & $3.2\times10^{18}$ & $0.36$ & $0.51$ & $5.8\times10^6$ & $135$ \\
+$\Jp$ & $6.6\times10^{16}$ & $0.40$ & $0.43$ & $1.8\times10^4$ & $308$ \\
+$\Kp$ & $2.7\times10^{18}$ & $0.42$ & $0.37$ & $0.0$           & $123$ \\
+$\Js$ & $3.4\times10^{16}$ & $0.34$ & $0.51$ & $4.0\times10^5$ & $221$ \\
+\hline
+\hline
+\end{tabular}
+\begin{quote}
+ \label{tab:bm_cont}
+  \end{quote}
+\end{table}
+
+\begin{equation}
+N_\rmn{el} = a_1\frac{\ee^{-a_2}}
+{\left[1+\left(\frac{\ee}{a_3}\right)^{a_4}\right]^{a_5}}
+\times\left[1+\left(\frac{\ee}{a_6}\right)^{a_7}\right]^{a_8}
+\label{eq:bm_elec}
+\end{equation}
+
+\begin{table}
+\begin{tabular}{c c c c c c c c c}
+\hline
+\hline
+ BM model & $a_1$ & $a_2$ & $a_3$ & $a_4$ & $a_5$ & $a_6$ & $a_7$ & $a_8$ \\
+ \hline
+$\Ip$ & $14$ & $0.06$ & $1.8$ & $0.9$  & $2.0$ & $60$  & $5$ & $-1$     \\
+$\Jp$ & $17$ & $0.08$ & $5.5$ & $0.8$  & $2.6$ & $250$ & $5$ & $-1$     \\
+$\Kp$ & $22$ & $0.05$ & $1.7$ & $0.85$ & $2.1$ & $10$  & $2$ & $0.62$ \\
+$\Js$ & $15$ & $0.14$ & $5.0$ & $1.0$  & $1.5$ & $300$ & $5$ & $-1$     \\
+\hline
+\hline
+\end{tabular}
+\begin{quote}
+ \label{tab:bm_elec}
+  \end{quote}
+\end{table}
+
+%  een = ee/GeV
+%  
+%  if(BMmodel.eq.0) then
+%  gmu = 14.d0*een**(-0.06)/(1.d0+(een/1.8d0)**0.9 )**2.0/
+%  &           (1.d0+(een/60.d0)**5 ) !0
+%  c            write(*,*) gmu,een
+%  endif
+%  if(BMmodel.eq.1) then
+%  gmu = 17.d0*een**(-0.08)/(1.d0+(een/5.5d0)**0.8 )**2.6/
+%  &           (1.d0+(een/250.d0)**5) !1
+%  endif
+%  if(BMmodel.eq.2) then
+%  gmu =(22.d0*een**(-0.05)/(1.d0+(een/1.7d0)**0.85)**2.1*
+%  &           (1.d0+(een/10.d0)**2 )**0.62*dexp(-(een/230.d0)**7)) !2 &3
+%  endif
+%  if(BMmodel.eq.3) then
+%  gmu = 15.d0*een**(-0.14)/(1.d0+(een/5.0d0)      )**1.5/
+%  &           (1.d0+(een/300.d0)**5) !4
+%  endif
+%  gmu = gmu*2d0! acounting for the electrons as well
+%
+%LP
+%      gmu=0.71894+2.27161*dlog(1.-(ee/mX))+
+%     &           0.199579*(dlog(1.-(ee/mX)))**2
+%            gmu = dexp(gmu)/2.d0+1.d0
 
 \section{Gas density profile of Fornax}
+
+\begin{equation}
+n_\e(r) = \sum_i n_i\left[1+\left(\frac{r}{r_{c,i}}\right)^2\right]^{-3\beta_i+0.5}
+\end{equation}
+where
+\begin{align}
+&n_1 = 0.35\, \rmn{el}\,\rmn{cm}^{-3}\,,
+&&r_{c,1} = 0.36\,\kpc\,,\,\,\,
+\beta_1 = 0.54\,, \nonumber\\
+&n_2 = 2.2\times10^{-3}\,\rmn{el}\,\rmn{cm}^{-3}\,,
+&&r_{c,2} = 190\,\kpc\,,\,\,\,\,
+\beta_2 = 41\,, \nonumber\\
+&n_3 = 5.7\times10^{-4}\,\rmn{el}\,\rmn{cm}^{-3}\,,
+&&r_{c,3} = 830\,\kpc\,,\,\,\,\,
+\beta_3 = 24\,. \nonumber\\
+& &&
+\label{fit_fornax}
+\end{align}
+Note that we remove the contribution of the flat central component
+($i=1$) in the outer parts of the cluster, hence we cut it at about
+$40\,\kpc$.
 
@@
    from deprojected Chandra and Rosat X-ray surface brightness
-   observations {\bf Anders: CITE}. The total hybrid profile shown by
-   the red solid line represent the best fit to the data, where the
-   fitted individual density components are shown by the black dotted
-   lines. The blue solid line shows the single beta density profile
-   inferred from the HIFLUGCS catalogue. Due to insufficient
-   sensitivity of teh data to the outer cluster part, we use the outer
-   slope from the HIFLUGCS catalogue that is very similar to that of
-   the Coma cluster.}
+   observations \cite{2002ApJ...565..883P} {\bf Anders: CITE, DONE}. The
+   total hybrid profile shown by the red solid line represent the best
+   fit to the data, where the fitted individual density components are
+   shown by the black dotted lines. The blue solid line shows the
+   single beta density profile inferred from the HIFLUGCS
+   catalogue. Due to insufficient sensitivity of the data to the outer
+   cluster part, we use the outer slope from the HIFLUGCS catalogue
+   that is very similar to that of the Coma cluster.}
  \label{fig:dens_fornax}

### 2011-05-10 paper.tex
corrections

@@
   consider continuum emission as a result of the hadronization of
-annihilating neutralinos, internal bremsstrahlung, and inverse Compton
-emission from the cosmic microwave background as well as from a
-realistic spatial and spectral distribution of dust and stellar light.
-After the galactic center, which hosts many astrophysical sources,
-galaxy clusters are the best known target class to detect DM
-annihilation. We predict Virgo and Fornax to be the brightest DM
-sources and find a particularly low CR induced background for
-Fornax. For a given minimum substructure mass as given by the DM
-free-streaming scale, one needs the largest DM halo mass to maximize
-the substructure boost over the smoothly distributed annihilation
-flux: for galaxy clusters as the largest collapsed objects, we find a
-boost factor of more than 1000. Since the annihilation flux of
-substructures is mostly contributed by the regions around the virial
-radius, the resulting surface brightness profiles are almost
-flat. This makes it very challenging to detect this flux with imaging
-air Cherenkov telescopes since their sensitivity drops linearly with
-radius and they typically encounter have $5-10$ linear resolution
-elements across a cluster; the gamma-ray satellite Fermi is better
-suited. Assuming cold dark matter with a substructure mass
-distribution down to an Earth mass and using Fermi upper limits, we
-rule out the leptophilic models in their present form in 14 clusters,
-and limit the boost from Sommerfeld enhancement in Fornax to be less
-than 2 which corresponds to a value in the Milky Way of less than
-5. Alternatively, if the Sommerfeld enhancement factor is realized in
-Nature, this would imply a limiting substructure mass in Fornax of
-$\mlim > 10^2\,\msun$ corresponding to a Milky Way value of $\mlim >
-5\times 10^3\,\msun$ which would be a hint for an unknown form of warm
-dark matter. We find that Fermi three-year data will be able to
-constrain the smallest mass of substructures for supersymmetric
-benchmark models or alternatively constrain their cross sections for a
-given substructure boost. Although the Perseus and Ophiuchus clusters
-are expected to have the largest CR induced flux according to our
-semi-analytic model that is derived from cosmological hydrodynamical
-cluster simulations, their central active galactic nucleus as well as
-the Galactic foreground makes it hard to detect this flux in the Fermi
-band. The next to best targets to detect the CR flux are Virgo, Coma,
-and Norma -- the Fermi upper limits are closing in on our predictions
-and will soon start to constrain the underlying CR physics such as
-shock acceleration efficiencies or CR transport properties.
+  annihilating neutralinos, internal bremsstrahlung, and inverse
+  Compton emission from the cosmic microwave background as well as
+  from a realistic spatial and spectral distribution of dust and
+  stellar light.  After the galactic center, which hosts many
+  astrophysical sources, galaxy clusters are the best known target
+  class to detect DM annihilation. We predict Virgo and Fornax to be
+  the brightest DM sources and find a particularly low CR induced
+  background for Fornax. For a given minimum substructure mass as
+  given by the DM free-streaming scale, one needs the largest DM halo
+  mass to maximize the substructure boost over the smoothly
+  distributed annihilation flux: for galaxy clusters as the largest
+  collapsed objects, we find a boost factor of more than 1000. Since
+  the annihilation flux of substructures is mostly contributed by the
+  regions around the virial radius, the resulting surface brightness
+  profiles are almost flat. This makes it very challenging to detect
+  this flux with imaging air Cherenkov telescopes since their
+  sensitivity drops linearly with radius and they typically encounter
+  have $5-10$ linear resolution elements across a cluster; the
+  gamma-ray satellite Fermi is better suited. Assuming cold dark
+  matter with a substructure mass distribution down to an Earth mass
+  and using Fermi upper limits, we rule out the leptophilic models in
+  their present form in 14 clusters, and limit the boost from
+  Sommerfeld enhancement in Fornax to be less than 2 which corresponds
+  to a value in the Milky Way of less than 5. Alternatively, if the
+  Sommerfeld enhancement factor is realized in Nature, this would
+  imply a limiting substructure mass in Fornax of $\mlim >
+  10^2\,\msun$ which would be a hint for an unknown form of warm dark
+  matter. We find that Fermi three-year data will be able to constrain
+  the smallest mass of substructures for supersymmetric benchmark
+  models or alternatively constrain their cross sections for a given
+  substructure boost. Although the Perseus and Ophiuchus clusters are
+  expected to have the largest CR induced flux according to our
+  analytic model that is derived from cosmological hydrodynamical
+  cluster simulations, their central active galactic nucleus as well
+  as the Galactic foreground makes it hard to detect this flux in the
+  Fermi band. The next to best targets to detect the CR flux are
+  Virgo, Coma, and Norma -- the Fermi upper limits are closing in on
+  our predictions and will soon start to constrain the underlying CR
+  physics such as shock acceleration efficiencies or CR transport
+  properties.
 \end{abstract}
-
-\del{
---) the flux from annihilating DM is boosted by about a factor 1000 in
-  clusters
---) flat surface brightness profiles with substructures
---) Fornax is a great target for indirect DM studies because the relative
-  low flux from CRs and high flux from DM
---) difficult to detect DM without a Sommerfeld boost with Cherenkov
-  telescopes since the boost from substructures is extended while the
-  sensitivity of Cherenkov telescopes drops linearly with radius
-  outside the point spread function (CHECK)
---) the IC upscattered photons from stars and dust are dominated in the
-  relevant energy regimes by the continuum emission for our DM
-  benchmark models
---) we provide a rather simple model to calculate the spatial and spectral
-  distribution of dust and stars in cluster (might be used for
-  galaxies? with different spatial profile)
---) we rule out the leptophilic models in present form in 14 clusters,
-  and limit the boost from Sommerfeld enhancement in the MW to less
-  than 10
---) the tightest limits on DM and CRs from Fermi are in the 1-10 GeV
-  regime, where Fornax, M49, and NGC4636 are the most constraining
-  "clusters" for the DM and 
-... to be written...  if $\mlim \approx 10^{-6}\,\msun$ then the boost
-  from SFE is smaller than about a factor 5 in the MW and 2 in Fornax, or
-  alternatively if SFE correct then  $\mlim > 10^2\,\msun$.
-}
 
@@
 
-{\bf Anders, insert your flux table for various clusters, and discuss it, DONE}
-
 In this paper, we will investigate in some more detail the potential
@@
 and planned gamma-ray detectors. In Table~\ref{tab:flux_tab} we show
-the gamma-ray flux from four clusters, which are all targets with a
-high gamma-ray yield. We derive the emission from two different DM
-models and a hadronic CR model and find that Virgo has the highest
-gamma-ray flux which emerge from annihilating DM. If the boost from
-Sommerfeld enhancement is small, however, then the gamma-ray emission
-induced by CRs is dominating most clusters with the exception of a few
-clusters where Fornax had the highest flux from DM. In particular, we
-find Fornax ($\mvir=10^{14}\,\msun$) and Virgo
-($\mvir=2.1\times10^{14}\,\msun$) \del{\cite{}} as the prime targets
-for DM observations, Perseus ($\mvir=7.7\times10^{14}\,\msun$) for CR
-induced emission and we additionally decide in favor of the well
-studied cluster Coma ($\mvir=1.4\times10^{15}\,\msun$) for
-comparison. While studying these four clusters in great detail, we
-complement the analysis by calculating the expected gamma-ray fluxes
-of a nearby X-ray flux complete sample of galaxy clusters (HIFLUGCS,
-\citealt{2002ApJ...567..716R}). For previous work related to DM in
-clusters, see, e.g., \cite{2006A&A...455...21C,2009PhRvD..80b3005J}.
+the gamma-ray flux from four promising clusters with a high gamma-ray
+yield. We derive the emission from two different DM models and a
+hadronic CR model and find that Virgo has the highest gamma-ray flux
+from annihilating DM. If the boost from Sommerfeld enhancement is
+small, however, then the gamma-ray emission induced by CRs is
+dominating most clusters with the exception of a few clusters where
+Fornax had the highest flux from DM. In particular, we find Fornax
+($\mvir=10^{14}\,\msun$) and Virgo ($\mvir=2.1\times10^{14}\,\msun$)
+\del{\cite{}} as the prime targets for DM observations, Perseus
+($\mvir=7.7\times10^{14}\,\msun$) for CR induced emission and we
+additionally decide in favor of the well studied cluster Coma
+($\mvir=1.4\times10^{15}\,\msun$) for comparison. While studying these
+four clusters in great detail, we complement the analysis by
+calculating the expected gamma-ray fluxes of a nearby X-ray flux
+complete sample of galaxy clusters from the Rosat all-sky survey
+(extended HIghest X-ray FLUx Galaxy Cluster Sample, HIFLUGCS,
+\citealt{2002ApJ...567..716R}).\footnote{Note that we have added the
+  Virgo cluster to the sample that we nevertheless refer to as
+  extended HIFLUGCS catalogue in the following.}  For previous work
+related to DM in clusters, see, e.g.,
+\cite{2006A&A...455...21C,2009PhRvD..80b3005J}.
 
@@
   Notes: \\
- (1) The total gamma-ray flux from leptophilic (LP) DM where both the boost 
- from substructures and Sommerfeld enhancement are included.\\
+  (1) The total gamma-ray flux from leptophilic (LP) DM where both the
+  boost from substructures and Sommerfeld enhancement are
+  included. Note that all these values are in conflict with upper limits from
+  Fermi (see the following sections for detail).\\
  (2) The total gamma-ray flux from the supersymmetric $\Kp$ benchmark (BM) 
@@
 \end{table*}
-
-\del{In this work we define the virial radius $\rvir$ of a halo to be
-  the radius at which the mean density within is a factor $\Delta=200$
-  times the critical density $\rhoc$ of the universe.}
 
@@
 \cite{2009PhRvD..79a5014A}
-$$
+\begin{equation}
 S_{QED}=\frac{|\psi(0)|^2}{|\psi^{(0)}(0)|^2}=
 \left|\frac{\frac{\pi\alpha}{v}}{1-e^{-\frac{\pi\alpha}{v}}}\right|,
-$$ 
+\end{equation}
 with $\alpha =e^2/\hbar c$ the fine-structure constant, and $v$ the relative
@@
 $m_\chi$, the small-velocity limit of the enhancement becomes instead
-$$
+\begin{equation}
 S_Y\sim\frac{\alpha_Y m_\chi}{m_\phi}.
-$$ In the general case, with mediators that may also excite virtual
+\label{eq:saturation}
+\end{equation}
+In the general case, with mediators that may also excite virtual
 charged particles in the DM sector, one has to solve numerically a
@@
 Sommerfeld boost $\B_\sfe(\sigv=200\,km/s)\approx 300$ for a Milky Way
-halo and scale this appropriately down for cluster halos, using {\bf
-  Anders: insert Sommerfeld boost formula as a function of halo mass, done}
+halo and scale this appropriately down for cluster halos, using
 \begin{equation}
 \B_\sfe(\sigv) = 0.2\, \frac{c}{\sigv} = 
-49.4 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{1/3}\,,
+49.4 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-1/3}\,,
 \label{eq:B_sfe}
@@
 where the velocity dispersion $\sigv$ for clusters is derived in
-\cite{2005RvMP...77..207V}. Clusters have a larger velocity
-dispersion and an accordingly smaller Sommerfeld boost factor.
+\cite{2005RvMP...77..207V}. Clusters have a larger velocity dispersion
+and an accordingly smaller Sommerfeld boost factor. Note that this
+$1/v$-scaling is valid only for $(v/c) \gtrsim (m_\phi/m_\chi)$; at
+smaller velocities and outside resonances, the $1/v$-enhancement
+saturates at $m_\phi/m_\chi$ \cite{2008PhRvL.101z1301K}.
 
@@
 The the wave function of the lightest neutralino can be written
-$$
+\begin{equation}
 \tilde\chi_1=a_1\tilde B+a_2\tilde W_3+a_3 \tilde H_1^0+a_4\tilde H_2^0,
-$$
+\end{equation}
 with 
-$$
+\begin{equation}
 \sum_{i=1}^4 |a_i|^2=1.
-$$
+\end{equation}
 the gaugino fraction of a given neutralino is $|a_1|^2+|a_2|^2$ whereas $|a_3|^2+|a_4|^2$ is the higgsino fraction.
@@
 \end{table}
-{\bf Anders: add DM particle mass and cross section to all these 4
-  models, done, might consider adding the detailed particle physics
-  info as well }
 
@@
 center of the cluster halo and
-$\cos\Psi\equiv\cos\theta\cos\psi-\cos\varphi\sin\theta\sin\psi$ {\bf
-  Anders: I do not understand this equation: why galactic center?
-  changed to earth, doen not really matter}. The angular integration
-$\dd \Omega= \sin\theta\dd \theta \,\dd \varphi$ is performed over a
-cone centered around $\psi$ and the opening angle $\Delta \Omega$ is
-typically taken to be a few times the point spread function (PSF)
-$\psf$. The limited angular resolution results in a probability that a
-photon coming from a direction $\psi$' is instead reconstructed to a
-direction $\psi$, where the underlying probability distribution follow
-a Gaussian:
+$\cos\Psi\equiv\cos\theta\cos\psi-\cos\varphi\sin\theta\sin\psi$. The
+angular integration $\dd \Omega= \sin\theta\dd \theta \,\dd \varphi$
+is performed over a cone centered around $\psi$ and the opening angle
+$\Delta \Omega$ is typically taken to be a few times the point spread
+function (PSF) $\psf$. The limited angular resolution results in a
+probability that a photon coming from a direction $\psi$' is instead
+reconstructed to a direction $\psi$, where the underlying probability
+distribution follow a Gaussian:
 \begin{equation}
@@
 1+\rho_{\sub,i}^2(r)/\rho^2(r)$ (see
-Eqs.~\ref{eq:rho_sub}-\ref{eq:xvir} and Sect.~\ref{sect:subst}). {\bf
-  Anders: please add equation for $\B_{\sub,i}(M_{halo})$ here and
-  reference $B_{sfe}$ equation. added reference to both eqns} The DM
-source function from the smooth halo for each process is written in
+Eqs.~\ref{eq:rho_sub}-\ref{eq:xvir} and Sect.~\ref{sect:subst}).  The
+DM source function from the smooth halo for each process is written in
 the form:
@@
 
-{\bf Christoph: not sure where we are going with this}
-It is also useful to relate the masses to a more model independent
-variable as the maximum circular velocity given by
+In the recent dark matter simulation literature, it has become
+standard to characterize halos by the value, $V_\rmn{max}$, where the
+circular velocity $V_\rmn{circ}(r)=\sqrt{GM(<r)/r}$ attains its
+maximum:
 \begin{eqnarray}
 V_\rmn{max} &=& V_\rmn{circ}(\rvir) 
-\left[\frac{0.216\,c}{\log(1+c)-c/(1+c)}\right]^{0.5}\propto \mvir^{0.32}\,,
+\left[\frac{0.216\,c}{\log(1+c)-c/(1+c)}\right]^{0.5}\propto \mvir^{0.32}.\nonumber\\
 \end{eqnarray}
-where the circular velocity at radius $r$ is given by
-$V_\rmn{circ}(r)=(GM(<r)/r)^{0.5}$. We find that
-($V_\rmn{max}=1480\,\rmn{km/s}$, $R_\rmn{max}=0.61\,\rvir$) for a large
-$10^{15}\,\msun$ cluster of galaxies, and
-($V_\rmn{max}=520\,\rmn{km/s}$, $R_\rmn{max}=0.44\,\rvir$) for a small
-$4\times10^{13}\,\msun$ galaxy group.
-
-\del{
+Especially for subhalos, this quantity seems to be more stable
+compared to the virial mass that is subject to tidal stripping. For
+comparison, we quote typical values for a large galaxy clusters and a galaxy group:
 \begin{eqnarray}
-V_\rmn{max} &=& V_\rmn{circ}(r_\rmn{max})\qquad\,\,\,\,\,\,\,\,\,\rmn{where}\nonumber\\
-V_\rmn{circ}(r)&=& \sqrt{\frac{G_\rmn{N}\,M(<r)}{r}}\qquad\rmn{and}\nonumber\\
-\frac{\dd V_\rmn{circ}(r)}{\dd r} &=& 0\quad \Longrightarrow\quad r_\rmn{max}\,.
+M_{200} = 1\times10^{15}\,\msun:\quad &&V_\rmn{max}=1480\,\rmn{km/s}, \nonumber\\
+                                     &&R_\rmn{max}=0.61\,\rvir, \\
+M_{200} = 4\times10^{13}\,\msun:\quad &&V_\rmn{max}=~520\,\rmn{km/s}, \nonumber\\
+                                     &&R_\rmn{max}=0.44\,\rvir.
 \end{eqnarray}
-}
-
-\del{Assuming that all the flux from an NFW profile originate from
-  within the scale radius $\rs=\rvir/c$, and all the flux from an
-  Einasto profile originate within $r_{-2}=\rvir/c$, it follows that
-  $\rho_{-2} = \rhos/4$.} {\bf Anders: SHOW INTEGRATION, COMPUTE RMAX}
-
-%However, this finding is hard to reconcile with simulations that
-%typically prefere a steeper central profile.
 
@@
 distribution. Recent high resolution simulations suggest a flux
-enhancement from substructures of the order of ten up to a few 100
-\cite{2008MNRAS.391.1685S, 2008JPhCS.125a2008K} for a MW size halo. We
-adopt a boost from substructures of 230 which is the enhancement
-found in one of the highest resolved MW halos ever simulated, in
-addition, this model induce gamma-ray fluxes that allows the smallest
-mass of substructures to be constrained. {\bf Anders: motivate why we
-  take 200 DONE; is there a reference that shows that Kuhlen now also get
-  100-200? Have not found any.}  We use a double power-law function to
-fit \footnote{Our approach of fitting the scaling behavior of
-  $L_\rmn{sub}(<r)$ directly from numerical simulations
-  self-consistently accounts for the radial dependence of the
-  substructure concentration \cite{2008MNRAS.391.1685S}.} the
+enhancement from substructures of more than 100
+\cite{2008MNRAS.391.1685S, 2010ApJ...718..899A} for a MW size halo. We
+adopt a boost from substructures of 230 which is the enhancement found
+in one of the highest resolved MW halos ever simulated.\footnote{Note
+  that these high values for boost factors are now consistently found
+  in high-resolution simulations of dark matter halos
+  \cite{2008MNRAS.391.1685S, 2010ApJ...718..899A} after accounting for
+  the tidal mass loss of subhalos. This effect causes a significantly
+  flatter subhalo distribution compared to the smooth distribution and
+  errornously assuming an identical mass density distribution of
+  smooth DM and substructure biases the subhalo boost factor too low
+  \cite{2008JPhCS.125a2008K, 2008JPhCS.125a2008K}.} We use a double
+power-law function to fit \footnote{Our approach of fitting the
+  scaling behavior of $L_\rmn{sub}(<r)$ directly from numerical
+  simulations self-consistently accounts for the radial dependence of
+  the substructure concentration \cite{2008MNRAS.391.1685S}.} the
 luminosity from the smooth component of substructures
@@
 larger volume available there. For large clusters with typical
-concentrations of $c = r_{200}/r_\s \simeq 4$, the luminosity from the
-smooth profile is focused to the regime around 10\% of $\rvir$. {\bf
-  Christoph: why is the number density of subhalos relevant here?} In contrast,
-emission from substructures is mainly contributed by the outer parts
-of DM halos where the number density of subhalos steepens
-considerably.  Note that, even though most of the substructures have
-been erased in the central regions of DM halos, a cluster in
-projection has a significant enhancement due to substructures at a
-radius of just a few percent of $\rvir$.
+concentrations of $c = \rvir/r_\s \simeq 4$, the luminosity from the
+smooth profile is focused to the regime around 10\% of $\rvir$.  In
+contrast, emission from substructures is mainly contributed by the
+outer parts of DM halos. As shown in Fig.~\ref{fig:radial_emis}, the
+product of annihilation emissivity and emission volume increases
+towards $\rvir$ and only starts to drop outside this radius.  Note
+that, even though most of the substructure mass density has been
+erased in the central regions of DM halos, a cluster in projection has
+a significant enhancement due to substructures at a radius of just a
+few percent of $\rvir$.
 \begin{figure}
@@
 background (CMB) photons, and the light from stars and dust (SD). We
-derive a semi-analytic model from which we can estimate the spectral
+derive a analytic model from which we can estimate the spectral
 and spatial distributions of SD as a simple function of cluster mass.
@@
 shorter than the diffusive timescale in the ICM of galaxy clusters for
-CR electrons with \del{$\ee \gtrsim\,$~MeV}
-\cite{1997ApJ...487..529B,2011A&A...527A..99E} {\bf Anders: CHECK,
-  seems like the diffusive timescale is larger than hubble time in our
-  energy range.}. Hence, we neglect the first term of the r.h.s. in
-Eq.~(\ref{eq:CRdiffusion}), and derive an expression for the
-equilibrium number density:
+CR electrons which is larger than the hubble time in our energy range
+\cite{1997ApJ...487..529B,2011A&A...527A..99E}. Hence, we neglect the
+first term of the r.h.s. in Eq.~(\ref{eq:CRdiffusion}), and derive an
+expression for the equilibrium number density:
 \begin{eqnarray}
@@
 includes the contribution from the ICL, the BCG and all the galaxies,
-while the galaxies are excluded in the smooth profile. In fact, one
-can with a simple order of magnitude calculation show that the overlap
-of the SD dominated regimes in galaxies with the DM halo including
-substructures is marginal, hence we can neglect the IC upscattered SD
-photons contribution from galaxies:
+while the galaxies are excluded in the smooth profile. To compute the
+IC emission from SD, we require a non-negligible overlap of the
+relativistic lepton distribution resulting form DM annihilation and
+SD.  In fact, one can show with a simple order of magnitude
+calculation that the overlap, $f_\rmn{IC-ol}$, of the photon field of individual
+galaxies (starlight and dust emission) and the smooth DM density is
+very small so that we can neglect the starlight contribution from
+galaxies to the IC emission for the reminder of this work,
 \begin{eqnarray}
-V_\rmn{icm} \approx (2\,\mpc)^3\approx 10\,\mpc^3\nonumber\\
-V_\rmn{SD,gal} \approx 0.1^3\times(0.1\,\mpc)^3 = 10^{-6}\,\mpc^3\nonumber\\
-V_\rmn{SD,sum} = N_\rmn{gal}\,V_\rmn{SD,gal} \approx 10^{-3}\,\mpc^3
-\quad\rmn{and}\nonumber\\
-V_\rmn{icm}/V_\rmn{SD,sum} \sim 10^4 \nonumber\,.
+f_\rmn{IC-ol} = \frac{N_\rmn{gal} V_\rmn{gal} f_\rmn{light}}{V_\rmn{clu}}
+\lesssim  \frac{N_\rmn{gal} M_\rmn{gal}}{M_\rmn{clu}\,c_\rmn{gal}^{3}}=10^{-4}.
 \end{eqnarray}
-Here $V_\rmn{icm}$ denotes the total volume of the ICM of a typical
-cluster, $V_\rmn{SD,gal}$ is the volume dominated by SD in a typical
-galaxy (we have assumed that most of the SD are located inside
-$0.1\rvir$ of the galaxy), and $_\rmn{SD,sum}$ is the total volume of
-the SD in galaxies within the ICM where the number of galaxies is
-given by $ N_\rmn{gal}=10^3$.
-
- {\bf Anders: add the order of
-  magnitude calculation that the overlap of galaxies with smooth
-  profile or substructures is minor, 1e-4 if I remember correctly,
-  motivating that we go along with the smooth SD profile. DONE}  We find
-that even for a cluster with a relative small mass the energy density
-of the SD components dominates over the CMB and the magnetic fields
-(with a central B field of 3~$\mu G$) within about 10\% of
+Here we assume that the exponential scale height of the stellar light
+is less than the scale radius of the galaxy halo, $f_\rmn{light}
+\lesssim (r_\rmn{s} / r_{200,~\rmn{gal}})^3 \sim c_\rmn{gal}^{-3} \sim
+10^{-3}$ and $N_\rmn{gal} M_\rmn{gal} \sim 0.1 M_\rmn{clu}$.
+
+We find that even for a cluster with a relative small mass the energy
+density of the SD components dominates over the CMB and the magnetic
+fields (with a central B field of 3~$\mu G$) within about 10\% of
 $\rvir$. Outside this radius the CMB is dominating the energy density
@@
 The spatial distribution of light emitted by SD is quite different
-from what is expected from the IC upscattered SD photons. We
-illustrate this in Fig.~\ref{fig:SD_lum}, where the accumulative
-luminosity from SD is compared to the IC SD photons for a
+from what is expected for the IC upscattered SD photons. We illustrate
+this in Fig.~\ref{fig:SD_lum}, where the accumulative luminosity from
+SD is compared to the IC SD photons for a
 $\mvir=6.0\times10^{14}\,\msun$ cluster where the boost from
-substructures is excluded. We find that the accumulative SD luminosity
-follow a flat distribution outside a few percent of $\rvir$, while the
-luminosity from IC upscattered SD photons is marginal inside
-$0.1\rvir$ and instead dominated by the outer parts of the cluster
-where the distribution follows an NFW mass profile. In the center, the
-electrons and positrons mainly cool by IC upscattering SD photons,
-hence the spatial dependence of the cooling cancels the distribution
-of the SD source function, which results in a distribution that
-approaches a density square profile in the center. We also find that
-the luminosity within $\rvir$ from the total SD model is a factor
-three larger compared to the more realistic smooth SD model. {\bf
-  Anders: ADD DISCUSSION ABOUT ACCUMULATIVE LUMINOSITY, DONE}
+substructures is excluded. The gamma-ray luminosity from IC
+upscattered SD photons is dominated from the inner parts where there
+is the largest overlap of the cuspy DM profile and the peaked SD
+distribution. This is in marked contrast to the accumulative SD
+luminosity in the optical that is dominated by the outer parts of the
+cluster. Interestingly, it rises as a function of radius and follows
+the distribution of an NFW mass profile outside $0.1\rvir$.  In the
+center, the electrons and positrons mainly cool by IC upscattering SD
+photons, hence the spatial dependence of the cooling cancels the
+distribution of the SD source function, which results in a
+distribution that approaches a density square profile in the center.
+We also find that the luminosity within $\rvir$ from the total SD
+model is a factor three larger compared to the more realistic smooth
+SD model.
 
@@
 found the IR to X-ray luminosity scaling relation found in
-\cite{2008A&A...490..547G}. The X-ray luminosities for the clusters
-used in this work are listed in the extended HIghest X-ray FLUx Galaxy
-Cluster Sample (HIFLUGCS) \cite{2002ApJ...567..716R} from the Rosat
-all-sky survey. Note that we have added the Virgo cluster to the
-sample that we nevertheless refer to as extended HIFLUGCS catalogue in
-the following.
+\cite{2008A&A...490..547G}. 
 }
@@
   magneto-turbulence.\cite{1987A&A...182...21S,1993ApJ...406..399G,2004MNRAS.350.1174B,2005MNRAS.363.1173B,2007MNRAS.378..245B,2011MNRAS.410..127B,2009A&A...507..661B}}
-     {\bf Anders: please add references for the
-       hadronic/re-acceleration scenario; look them up from our
-       Ensslin-transport paper. DONE} Supporting evidence comes from
-     the smoothness of the extended radio emission that often
-     resembles that observed in thermal X-rays. Especially since the
-     long cooling time of cosmic ray protons (CRps) allows for an
-     extended and large population of CRps to build up over the
-     cluster history \citep{1996SSRv...75..279V, 1997ApJ...477..560E,
-       1997ApJ...487..529B}. The production of these secondaries
-     depend both on the gas and CRp densities in the cluster, where
-     the CRp density roughly traces the gas outside the core regime
-     and is slightly enhanced in the center.  This density scaling
-     implies that clusters are great targets for Cherenkov telescopes
-     with a high sensitivity for the central parts of nearby
-     clusters. Detecting the cluster gamma-ray emission is crucial in
-     this respect as it potentially provides the unique and
-     unambiguous evidence of CRp populations in clusters through
-     observing the $\pi^0$ bump at about 100~MeV in the spectra.
+Supporting evidence comes from the smoothness of the extended radio
+emission that often resembles that observed in thermal
+X-rays. Especially since the long cooling time of cosmic ray protons
+(CRps) allows for an extended and large population of CRps to build up
+over the cluster history \citep{1996SSRv...75..279V,
+  1997ApJ...477..560E, 1997ApJ...487..529B}. The production of these
+secondaries depend both on the gas and CRp densities in the cluster,
+where the CRp density roughly traces the gas outside the core regime
+and is slightly enhanced in the center.  This density scaling implies
+that clusters are great targets for Cherenkov telescopes with a high
+sensitivity for the central parts of nearby clusters. Detecting the
+cluster gamma-ray emission is crucial in this respect as it
+potentially provides the unique and unambiguous evidence of CRp
+populations in clusters through observing the $\pi^0$ bump at about
+100~MeV in the spectra.
 
@@
 for weaker shocks \cite{2007A&A...473...41E}. As a caveat we note that
-the semi-analytic model is based on simulations that only considered
+the analytic model is based on simulations that only considered
 advective transport of CRs by turbulent gas motions which produces
@@
 
-\del{
+{\bf
 peak sensitivity of Fermi at these energies due to a combination of effective area background and source spectra...}
@@
    (orange), M49 (green), and NGC4636 (blue). The SFE has been
-   rescaled from the MW value of 300 (c.f. Eq.~\ref{eq:B_sfe}) {\bf
-     Anders (refer to equation), DONE} that is required to explain the
-   electron and positron excess observed at Earth with LP DM (black
-   arrow). If the DM interpretation is correct, we can constrain the
-   smallest size of halos to be larger than $100\,\msun$. Contrarily,
-   if the smallest size of DM halos is $10^{-6}\,\msun$, we can
-   constrain the SFE to about 2 in Fornax, corresponding to a maximum
-   SFE in the MW of about 5 which would be too small to support the DM
-   annihilation hypothesis for the Pamela/Fermi excess.}
+   rescaled from the MW value of 300 (c.f. Eq.~\ref{eq:B_sfe}) that is
+   required to explain the electron and positron excess observed at
+   Earth with LP DM (black arrow). If the DM interpretation is
+   correct, we can constrain the smallest size of halos to be larger
+   than $100\,\msun$. Contrarily, if the smallest size of DM halos is
+   $10^{-6}\,\msun$, we can constrain the SFE to about 2 in Fornax,
+   corresponding to a maximum SFE in the MW of about 5 which would be
+   too small to support the DM annihilation hypothesis for the
+   Pamela/Fermi excess.}
  \label{fig:boost_const}
@@
   Fornax; a low X-ray luminous cluster has a low energy density in
-  starlight and dust in our semi-analytic SD model.} It should be
+  starlight and dust in our analytic SD model.} It should be
 noted that the surface brightness due to SD upscattered photons is
@@
 
-In this section, we compute the expected $\gamma$-ray fluxes from DM
-annihilation and CR interactions of the brightest clusters of the X-ray flux
-complete sample in the local universe. We confront these predictions to upper
-limits obtained by Fermi 1.5-year data and conclude on the viability of the
-underlying models and perspectives for the next years of Fermi observations.
+In this section, we compute the expected gamma-ray fluxes from DM
+annihilation and CR interactions of the brightest clusters of the
+X-ray flux-complete sample in the local universe. We confront these
+predictions to upper limits obtained by Fermi 1.5-year data and
+conclude on the viability of the underlying models and perspectives
+for the next years of Fermi observations.
 
@@
   \caption{\it Scaling relations of the cluster's virial mass $\mvir$ and the
-    $\gamma$-ray luminosity for energies $E_\gamma>100$~MeV (left) and
+    gamma-ray luminosity for energies $E_\gamma>100$~MeV (left) and
     $E_\gamma>10$~GeV (right).  Shown are the relations for the CR-induced
@@
 
-First we focus on $\gamma$-ray flux-cluster mass scaling relations for DM
+First we focus on gamma-ray flux-cluster mass scaling relations for DM
 annihilation and CR induced emission in Fig.~\ref{fig:lum_mass_scaling}.  The
@@
 \begin{eqnarray}
-L_{\rmn{CR}-\ensuremath{\pi^0}}(>100\,\mev) = 3.13\times10^{45}
-\left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.46}\nonumber\\
-L_{\rmn{CR}-\ensuremath{\pi^0}}(>10\,\gev)  = 2.23\times10^{43}
-\left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.34}\nonumber\\
+L_{\rmn{CR}-\ensuremath{\pi^0}}(>100\,\mev) = 3.1\times10^{45}
+\left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.46}\mbox{erg~s}^{-1}\nonumber\\
+L_{\rmn{CR}-\ensuremath{\pi^0}}(>10\,\gev)  = 2.2\times10^{43}
+\left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.34}\mbox{erg~s}^{-1}\nonumber\\
 \end{eqnarray}
-{\bf Anders: add CR scaling formula, DONE} This implies
-already a general strategy to minimize the CR-induced foreground for DM
-annihilation and argues for very nearby groups. We note that these simulations
-do not include AGN feedback that is thought to furthermore reduce the baryon
-fraction in groups relative to that in clusters \cite{2008ApJ...687L..53P}. The
-resulting smaller target density for hadronic CR interactions will furthermore
-steepen the $L_\gamma-M$ relation of CR induced emission, making the case for
+This implies already a general strategy to minimize the CR-induced
+foreground for DM annihilation and argues for very nearby groups. We
+note that these simulations do not include AGN feedback that is
+thought to furthermore reduce the baryon fraction in groups relative
+to that in clusters \cite{2008ApJ...687L..53P}. The resulting smaller
+target density for hadronic CR interactions will furthermore steepen
+the $L_\gamma-M$ relation of CR induced emission, making the case for
 groups even stronger.
@@
   of data taking $\sim
-  2\times10^{-9}\,\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$ . The name of
+  2\times10^{-9}\,\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$. The name of
   the four brightest clusters are written out. This yields Fornax and
-  M49 as the brightest targets. {\bf Anders: what is the dashed
-    line? DONE}}
+  M49 as the brightest targets.}
  \label{fig21}
@@
 
-Figure~\ref{fig14} compares Fermi upper limits on the $\gamma$-ray
-flux with predictions of DM annihilation fluxes in the leptophilic and
-benchmark models.  To obtain the $\gamma$-ray fluxes, we scale the
-virial mass of clusters in the extended HIFLUGCS catalogue
+Figure~\ref{fig14} compares Fermi upper limits on the gamma-ray flux
+with predictions of DM annihilation fluxes in the leptophilic and
+benchmark models.  To obtain the gamma-ray fluxes, we scale the virial
+mass of clusters in the extended HIFLUGCS catalogue
 \cite{2002ApJ...567..716R} with our scaling relations of
-Eqs.~(\ref{eq:BM_scaling}) and (\ref{eq:LP_scaling}). In
-Figure~\ref{fig14}, we compare only those clusters of the HIFLUGCS
-sample with Fermi limits to our predictions and show the DM flux
-predictions of the entire sample in Fig.~\ref{fig21}.  We assume a
-boost factor due to substructures that has a constant contribution per
-decade in substructure mass and has a mass spectrum extending down to
-Earth masses. Fermi limits rule out the leptophilic models in their
-present form with the mentioned assumptions in 14 clusters, and limit
-the boost from Sommerfeld enhancement to less than 4 [?] in
-Fornax. Assuming universality, this limits the Sommerfeld boost in the
-MW to less than 10 (see Fig.~\ref{fig:boost_const}).  The flux level
-of the Fermi limits are an indirect measure of the ambient background
-flux in the $\gamma$-ray sky and/or the presence of strong point
-sources such as AGN in the immediate vicinity of the cluster
+Eqs.~(\ref{eq:BM_scaling}) and (\ref{eq:LP_scaling}). In those, we
+assume a boost factor due to substructures that has a constant
+contribution per decade in substructure mass and has a mass spectrum
+extending down to Earth masses for our LP and BM DM annihilation
+models. In the LP models we additionally assume a cluster-mass
+dependent bost due to SFE. Fermi limits rule out the leptophilic
+models in their present form with the mentioned assumptions in 14
+clusters, and limit the boost from Sommerfeld enhancement to less than
+2 in Fornax. Assuming universality, this limits the Sommerfeld boost
+in the MW to less than 5 (see Fig.~\ref{fig:boost_const}).  The flux
+level of the Fermi limits are an indirect measure of the ambient
+background flux in the gamma-ray sky and/or the presence of strong
+point sources such as AGN in the immediate vicinity of the cluster
 position. Hence, the ratio of the Fermi upper limits to the predicted
@@
 experiments. We identify Fornax, M49, NGC4636, and Virgo to be prime
-candidates. Note however, that Virgo extends of $7\deg$ over the sky
+candidates. Note however, that Virgo extends of 7 degree over the sky
 which implies a lower surface brightness and lower signal-to-noise.
@@
 dramatically improve the limits through a stacking analysis as the
-weak signal will dilute the average constraints.  Assuming the
-projected sensitivity of the future Cherenkov telescope array (CTA) of
-$2\times10^{-14} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$
-\cite{2009arXiv0908.1410D} {\bf Anders: value?, DONE}, we note that it
-will be difficult to detect the DM annihilation signal from clusters
-without a Sommerfeld boost by Cherenkov telescopes. This is because
-the boost from substructures is extended while the sensitivity of
-Cherenkov telescopes drops linearly with radius outside the point
-spread function.
+weak signal will dilute the average constraints.
+
+In Figure~\ref{fig21}, we show the DM annihilation flux predictions of
+the entire sample in Fig.~\ref{fig21}.  Assuming the projected point
+source sensitivity ($5\sigma$, 50h) of the future Cherenkov telescope
+array (CTA) of $F_\gamma(>E_\gamma) = \{4\times10^{-11},
+2\times10^{-12}, 2\times10^{-14}\}
+\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$ at energies of
+$E_\gamma=\{10~\rmn{GeV}, 100~\rmn{GeV}, 1~\rmn{TeV}\}$
+\cite{2009arXiv0908.1410D}, we note that it will be difficult to
+detect the DM annihilation signal from clusters without a Sommerfeld
+boost by Cherenkov telescopes.  This is because the boost from
+substructures is extended while the sensitivity of Cherenkov
+telescopes drops linearly with radius outside the point spread
+function. Hence the fluxes quoted in Fig.~\ref{fig21} will have to be
+compared to a sensitivity that is scaled down by the ratio of cluster
+diameter to angular resolution of 0.1 degree so that even a large
+increase in observational time would make it highly improbable to
+probe the presented class of BM models.
 
@@
   \caption{\it We contrast predictions of the CRp induced gamma-ray
-    emission using the semi-analytic Pinzke \& Pfrommer model
+    emission using the analytical  model
     \cite{2010MNRAS.409..449P} to Fermi-LAT flux upper limits. We show
@@
 In Fig.~\ref{fig15}, we compare Fermi-LAT flux upper limits to the
-flux predictions by the semi-analytical Pinzke and Pfrommer model
-\cite{2010MNRAS.409..449P} for CRp induced $\gamma$-rays that uses the
-X-ray-inferred density profiles of clusters as an input. For
-consistency, we use beta-model fits to ROSAT data of X-ray bright
-clusters for our $\gamma$-ray flux estimates
-\cite{2002ApJ...567..716R}). We derive the central gas densities for
-each cluster by following the approach outlined in
+flux predictions by the analytical model \cite{2010MNRAS.409..449P}
+for CRp induced gamma-rays. For consistency, we use beta-model fits to
+ROSAT data of X-ray bright clusters for our gamma-ray flux estimates
+as an input \cite{2002ApJ...567..716R}). We derive the central gas
+densities for each cluster by following the approach outlined in
 \cite{1999ApJ...517..627M} which assumes that the ICM is
@@
 superior to those that use luminosity-mass scaling relation to infer
-the expected $\gamma$-ray flux---a method used by reference
+the expected gamma-ray flux---a method used by reference
 \cite{2010ApJ...717L..71A} to compare to Fermi limits.  In this
-semi-analytic model, we employ the fact that CRs accelerated at
-structure formation shocks and transported over cosmic time exhibit a
-universal spectral form and an almost universal spatial
-distribution. Depending on whether or not we account for the bias of
-``artificial galaxies'' in cosmological simulations, we derive an
-optimistic or conservative limit of the expected $\gamma$-ray emission
+analytic model, we employ the fact that CRs accelerated at structure
+formation shocks and transported over cosmic time. This leads to a CR
+distribution with a universal spectral form and an almost universal
+spatial distribution. Depending on whether or not we account for the
+bias of ``artificial galaxies'' in cosmological simulations, we derive
+an optimistic or conservative limit of the expected gamma-ray emission
 from decaying pions (bracketing our ignorance of the contribution of
-cluster galaxies to the overall $\gamma$-ray flux from a
-cluster). Note that both models assume the maximally allowed
-acceleration efficiency for strong shocks that transfer 50\% of the
-shock kinetic energy to CRs and most likely will have to be corrected
-down if this number is not realized at structure formation
-shocks. Secondly, these simulations neglect active CR transport such
-as streaming and diffusion relative to the gas, i.e. we assume that
-advective transport is the dominant one and CRs are tightly coupled to
-the gas via flux-frozen magnetic fields tangled on sufficiently small
+cluster galaxies to the overall gamma-ray flux from a cluster). Note
+that both models assume the maximally allowed acceleration efficiency
+for strong shocks that transfers 50\% of the shock-dissipated energy
+(kinetic energy corrected for adiabatic compressional heating at the
+shock) to CRs and most likely will have to be corrected down if this
+number is not realized at structure formation shocks. Secondly, these
+simulations neglect active CR transport such as streaming and
+diffusion relative to the gas, i.e. we assume that advective transport
+is the dominant one and CRs are tightly coupled to the gas via
+flux-frozen magnetic fields tangled on sufficiently small
 scales. Evidence from the statistics of radio halos suggests that this
@@
 in those objects could be responsible for a decrease in the central CR
-number density. This effect would also reduce the expected
-$\gamma$-ray flux by up to a factor of five
-\cite{2011A&A...527A..99E}. We note that the tightest Fermi limits are
-obtained in the 1-10 GeV regime due to the largest effective area of
-LAT there. In this energy band, the Fermi limits come close to the
-flux predictions of Virgo, Coma and Norma. Using integrated flux
-limits from Fermi, we arrive at very similar results.  We emphasize
-that by using our semi-analytic modeling, the slight discrepancy of
-the scaling relation-based prediction with the Fermi limit on Norma
-\cite{2010ApJ...717L..71A} is resolved: Norma simply seems to be less
-bright than an average cluster of the same mass as Norma. The
-insensitive limit on Perseus comes about since the central AGN in
-NGC1275 has turned on over the last years, making it hard to determine
-a comparable limit as obtained from the other clusters.
+number density. This effect would also reduce the expected gamma-ray
+flux by up to a factor of five \cite{2011A&A...527A..99E}. We note
+that the tightest Fermi limits are obtained in the 1-10 GeV regime due
+to the highest sensitivity of Fermi-LAT there. While the effective
+area of Fermi-LAT increases up to these energies, the typical photon
+spectra decrease as a function of energy: combining those effects
+selects this energy range to be most sensitive.  In this energy band,
+the Fermi limits come close to the flux predictions of Virgo, Coma and
+Norma. Using integrated flux limits from Fermi, we arrive at very
+similar results.  We emphasize that by using our analytic modeling,
+the slight discrepancy of the scaling relation-based prediction with
+the Fermi limit on Norma \cite{2010ApJ...717L..71A} is resolved: Norma
+simply seems to be less bright than an average cluster of the same
+mass as Norma. The insensitive limit on Perseus comes about since the
+central AGN in NGC1275 has turned on over the last years, making it
+hard to determine a comparable limit as obtained for the other
+clusters.
 
@@
    106 clusters included in the extended HIFLUGCS catalogue.  The CR
-   distribution follows the semi-analytical Pinzke \& Pfrommer model
-   derived through hydrodynamical cosmological cluster simulations
+   distribution follows the analytical model derived through
+   hydrodynamical cosmological cluster simulations
    \cite{2010MNRAS.409..449P} (see text for details).  Gamma-ray
@@
    brightest clusters are labelled. The lower panel shows the relative
-   difference between the the flux computed using the semi-analytical
-   Pinzke \& Pfrommer model and the $\gamma$-ray flux predicted by the
-   mass-luminosity scaling relation \cite{2010MNRAS.409..449P}. The
-   name of the clusters with the largest positive offset are printed
-   out; as expected, they all correspond to cool core clusters.}
+   difference between the the flux computed using the analytical model
+   and the gamma-ray flux predicted by the mass-luminosity scaling
+   relation \cite{2010MNRAS.409..449P}. The name of the clusters with
+   the largest positive offset are printed out; as expected, they all
+   correspond to cool core clusters.}
  \label{fig19}
@@
 
-To complete this section, we present our semi-analytical model
-predictions for the CR-induced $\gamma$-ray flux for all clusters in
-the extended HIFLUGCS sample in Fig.~\ref{fig19}. In the lower panel
-of this figure, we show the relative difference between the
-$\gamma$-ray flux predicted by the mass-luminosity scaling relation
-and to the flux computed using the semi-analytical model. Using our
-semi-analytic modelling results in a scatter of the expected
-$\gamma$-ray flux at a given mass. Cool core clusters have a denser
-core which increases the target density of gas protons for the
-hadronic reaction which in turn biases the expected $\gamma$-ray
-fluxes systematically higher. We confirm this effect as all our
-outliers with increased flux in our semi-analytic model relative to
-the scaling relation expectation are in fact cool core clusters
-suggesting that the X-ray emission should be a good proxy for the
-expected $\gamma$-ray emission. Note however that there could be the
-counter-acting effect of CR streaming in relaxed clusters which would
-tend to decrease the $\gamma$-ray luminosity
-\cite{2011A&A...527A..99E}. Future careful modelling is needed to
-quantify this effect.
+To complete this section, we present our analytical model predictions
+for the CR-induced gamma-ray flux for all clusters in the extended
+HIFLUGCS sample in Fig.~\ref{fig19}. In the lower panel of this
+figure, we show the relative difference between the gamma-ray flux
+predicted by the mass-luminosity scaling relation and to the flux
+computed using the analytical model. Statistically, one can view the
+analytical modeling as comtributing to the scatter of the expected
+gamma-ray flux at a given mass. Cool core clusters have a denser core
+which increases the target density of gas protons for the hadronic
+reaction which in turn leads to a systematic increase of the expected
+gamma-ray fluxes. We confirm this effect as all our outliers with
+increased flux in our analytic model relative to the scaling relation
+expectation are in fact cool core clusters suggesting that the X-ray
+emission should be a good proxy for the expected gamma-ray
+emission. Note however that there could be the counter-acting effect
+of CR streaming in relaxed clusters which would tend to decrease the
+gamma-ray luminosity \cite{2011A&A...527A..99E}. Future careful
+modelling is needed to quantify this effect.
 
@@
 substructures dominates over the smooth component for halo masses
-$\mvir>10^3 \msun$ {\bf Anders: check?OK} and contributes a constant
+$\mvir>10^3 \msun$  and contributes a constant
 luminosity for each decade in halo mass. The ratio of halo-to-minimum
@@
 increasing positron-to-lepton ratio beyond 10 GeV. Assuming that the
-minimum DM substructure mass extends down to an Earth mass, we can
-rule out these leptophilic models based on the non-observation of
-gamma-rays in any of the fore-mentioned
+minimum DM substructure mass extends down to an Earth mass, we limit
+the Sommerfeld enhancement factor in the Fornax galaxy cluster to be
+less than 2. This corresponds to a value in the Milky Way of less than
+5 due to the larger Sommerfeld boost factor in smaller mass halos
+which have a lower circular velocity that enhances the particle cross
+section (while assuming universality of the DM model). This would rule
+out leptophilic models in their current form based on the
+non-observation of gamma-rays in any of the fore-mentioned
 clusters/groups. Alternatively, assuming the leptophilic models to be
 correct, we limit the minimum substructure mass to $>100~\msun$ in
-Fornax. Assuming universality of the DM model, this corresponds to a
-minimum substructure mass of $5\times 10^4~\msun$ {\bf Anders: check
-  value, DO not understand what you mean by universality, or how you
-  get the minimum mass} in the Milky Way due to the larger Sommerfeld
-boost factor in smaller mass halos which have a lower circular
-velocity which enhances the particle cross section.
+Fornax.
 
@@
 from infra red to optical wavelengths. To this end, we construct a
-rather simple semi-analytic model for the spatial and spectral
+rather simple analytic model for the spatial and spectral
 distribution of dust and starlight in clusters which can be used for
@@
 gas protons over previous work \citep{2010ApJ...717L..71A}. We employ
-the semi-analytic model of the CR spectrum and spatial distribution,
+the analytic model of the CR spectrum and spatial distribution,
 recently developed by \citet{2010MNRAS.409..449P} that is based on
@@
 apparently lower gas density of this cluster relative to the average.
-As expected, the semi-analytic model adds ``scatter'' to the scaling
+As expected, the analytic model adds ``scatter'' to the scaling
 relation and biases the gamma-ray flux high for prominent cool core
@@
 clusters/groups but Fornax. We conclude that it will be possible to
-rule out the leptophilic model with eight-years of Fermi data {\bf
-  Anders: check, I would say six years data since in fig 11 we can
-  constrain $B_sfe < 2$ in Fornax, -> $2**2*1.5 = 6$ years} and start
+rule out the leptophilic model with six years of Fermi data and start
 to constrain some benchmark DM models. Hence this should nicely
@@
 
-\smallskip Anders Pinzke acknowledges NSF grant AST 0908480 for
+\smallskip We would like to thank Volker Sprigel for helpful comments.
+Anders Pinzke acknowledges NSF grant AST 0908480 for
 support. We would furthermore like to thank KITP for their hospitality

### 2011-05-10 paper.tex
<Enter short summary of changes>

@@
 \newcommand{\cm}{\rmn{cm}}
+\newcommand{\egt}{\tilde{E}_\gamma}
+\newcommand{\eet}{\tilde{E}_\rmn{e}}
 %OLD
@@
 protons. In Section 2 we discuss the theory of DM and gamma-rays. In
-particular, we focus one the leptophilic and supersymmetric DM models
+particular, we focus one the LP and supersymmetric DM models
 used in this work, and outline the framework for estimating the
@@
 We start the section by discussing two different, but well motivated
-DM models; leptophilic and supersymmetric DM. We then present the
-framework that is used to calculate the gamma-ray emission for these
-DM models using an Einasto DM density profile and the expected
-enhancement from DM substructures. This is followed by an outline of
-the framework of IC emission where we take into account photon fields
-of the cosmic microwave background (CMB), dust, and starlight. We end
-by summarizing our formalism of calculating the CR-induced pion decay
-gamma-ray emission which is thought to dominate the astrophysical
-gamma-ray signal.
+DM models; LP and supersymmetric DM. We then present the framework
+that is used to calculate the gamma-ray emission for these DM models
+using an Einasto DM density profile and the expected enhancement from
+DM substructures. This is followed by an outline of the framework of
+IC emission where we take into account photon fields of the cosmic
+microwave background (CMB), dust, and starlight. We end by summarizing
+our formalism of calculating the CR-induced pion decay gamma-ray
+emission which is thought to dominate the astrophysical gamma-ray
+signal.
 
@@
 sets of astrophysical data, we take advantage of the recent reanalysis
-\cite{Finkbeiner:2010sm} to define a benchmark leptophilic model that
+\cite{Finkbeiner:2010sm} to define a benchmark LP model that
 is still viable.  It is found that the bounds from WMAP5 approximately
@@
 
-Taking into account the whole cosmic history of leptophilic models,
-also utilizing limit on spectral and polarization distortions of the
-CMB, the maximal value for the boost factor for a 1 to 2 TeV particle
-and sub-GeV force carriers is found to be \cite{Finkbeiner:2010sm}
-between 400 and 800. Although lower than the first estimates (e.g.,
+Taking into account the whole cosmic history of LP models, also
+utilizing limit on spectral and polarization distortions of the CMB,
+the maximal value for the boost factor for a 1 to 2~TeV particle and
+sub-GeV force carriers is found to be \cite{Finkbeiner:2010sm} between
+400 and 800. Although lower than the first estimates (e.g.,
 \cite{Bergstrom:2009fa,Meade:2009iu}) this is still enough to explain
@@
 
-To connect easily to our previous work \cite{2009PhRvL.103r1302P}, we
-choose as our benchmark leptophilic model one with mass $1.6$~TeV and
-Sommerfeld boost $\B_\sfe(\sigv=200\,km/s)\approx 300$ for a Milky Way
-halo and scale this appropriately down for cluster halos, using
+We adopt our benchmark LP model from \cite{Finkbeiner:2010sm} where we
+use a DM mass $m_\chi=1.6$~TeV and a branching ratio of ($1/2,\,1/2$)
+into ($\mu^+/\mu^-,\,\e^+/\e^-$) \footnote{This is an approximation to
+  the model found in \cite{Finkbeiner:2010sm} that has a branching
+  ratio of ($1/3,\,1/3,\,1/3$) into
+  ($\mu^+/\mu^-,\,\e^+/\e^-,\,\pi^+/\pi^-$).}. The Sommerfeld boost
+$S=\B_\sfe(\sigv=200\,km/s)\approx 300$ for a Milky Way halo in our LP
+model, which we appropriately scale down for cluster halos, using
+\del{To connect easily to our previous work
+  \cite{2009PhRvL.103r1302P}, we choose as our benchmark LP model one
+  with mass $1.6$~TeV and Sommerfeld boost
+  $S=\B_\sfe(\sigv=200\,km/s)\approx 300$ for a Milky Way halo and
+  scale this appropriately down for cluster halos, using} {\bf Anders:
+  insert Sommerfeld boost formula as a function of halo mass, done}
 \begin{equation}
@@
 benchmark models, first the usual QED final state radiation (FSR) for
-both the leptophilic model and for supersymmetric models with charged
-final states. In addition, there may be direct emission from a
-virtual, charged, exchanged particle (such as a spin-0 slepton or
-squark), internal bremsstrahlung, IB. The latter is essentially only
-important when there is a helicity suppression for the lowest order
-annihilation process, which is the case for neutralinos, whose
-Majorana nature make the annihilation rate in the $s$ wave
-proportional to $m_f^2$, for final state fermion $f$. Interestingly,
-both the gamma-ray and fermion energy spectra are peaked at the
-highest energy for this process, which can in some models cause a
-rather spectacular bump in the spectra for these models.
+both the LP model and for supersymmetric models with charged final
+states. In addition, there may be direct emission from a virtual,
+charged, exchanged particle (such as a spin-0 slepton or squark),
+internal bremsstrahlung, IB. The latter is essentially only important
+when there is a helicity suppression for the lowest order annihilation
+process, which is the case for neutralinos, whose Majorana nature make
+the annihilation rate in the $s$ wave proportional to $m_f^2$, for
+final state fermion $f$. Interestingly, both the gamma-ray and fermion
+energy spectra are peaked at the highest energy for this process,
+which can in some models cause a rather spectacular bump in the
+spectra for these models.
 
@@
 our different DM models which is of interested for the high-energy IC
-emission of those leptons.  Only leptophilic (LP) models have
-energetic enough electrons such that the IC emission is powerful
-enough to either be constrained or detected at GeV energies and
-higher.
+emission of those leptons. Only LP models have energetic enough
+electrons such that the IC emission is powerful enough to either be
+constrained or detected at GeV energies and higher.
 
@@
  \caption{\it Source functions for different dark matter (DM)
-   models. Crosses show the simulated data from DarkSUSY and the solid
-   lines show the fit to the data. LEFT PANEL: normalized differential
-   continuum spectra for four different DM benchmark (BM) models;
-   $\Ip$ model (red), $\Jp$ (orange), $\Kp$ (green), and $\Js$
+   models. Crosses show the simulated data from {\sc DarkSUSY} and the
+   solid lines show the fit to the data. LEFT PANEL: normalized
+   differential continuum spectra for four different DM benchmark (BM)
+   models; $\Ip$ model (red), $\Jp$ (orange), $\Kp$ (green), and $\Js$
    (blue). We use Eq.~(\ref{eq:bm_cont}) to fit the continuum
@@
 the energy densities from different radiation fields in a galaxy
-cluster with the mass $\mvir=10^{15}\msun$. For this figure we use two
-different profiles for the SD energy density, where the total profile
-includes the contribution from the ICL, the BCG and all the galaxies,
-while the galaxies are excluded in the smooth profile. To compute the
-IC emission from SD, we require a non-negligible overlap of the
-relativistic lepton distribution resulting form DM annihilation and
-SD.  In fact, one can show with a simple order of magnitude
-calculation that the overlap, $f_\rmn{IC-ol}$, of the photon field of individual
-galaxies (starlight and dust emission) and the smooth DM density is
-very small so that we can neglect the starlight contribution from
-galaxies to the IC emission for the reminder of this work,
+cluster with the mass $\mvir=6\times10^{14}\msun$. For this figure we
+use two different profiles for the SD energy density, where the total
+profile includes the contribution from the ICL, the BCG and all the
+galaxies, while the galaxies are excluded in the smooth profile. To
+compute the IC emission from SD, we require a non-negligible overlap
+of the relativistic lepton distribution resulting form DM annihilation
+and SD.  In fact, one can show with a simple order of magnitude
+calculation that the overlap, $f_\rmn{IC-ol}$, of the photon field of
+individual galaxies (starlight and dust emission) and the smooth DM
+density is very small so that we can neglect the starlight
+contribution from galaxies to the IC emission for the reminder of this
+work,
 \begin{eqnarray}
@@
    from SD in clusters. The SD luminosity is related to the cluster
-   mass through Eqs.~(\ref{eq:u_SD}-\ref{eq:N_stars}), where we use
-   have used the mass $\mvir=10^{15}\msun$ in this figure. We
+   mass through Eqs.~(\ref{eq:E_SD}-\ref{eq:N_dust}), where we use
+   have used the mass $\mvir=6\times10^{14}\msun$ in this figure. We
    renormalize the SD spectra to the radius $r=0.03\rvir$, where the
@@
    line. The SD light has been renormalized to a cluster with the mass
-   $\mvir=10^{15}\msun$. Finally we show the energy density two
+   $\mvir=6\times10^{14}\msun$. Finally we show the energy density two
    magnetic field models with a central magnetic field of 3~$\mu
@@
 \begin{eqnarray}
-L_{\rmn{CR}-\ensuremath{\pi^0}}(>100\,\mev) = 3.1\times10^{45}
+L_{\gamma}(>100\,\mev) = 3.1\times10^{45}
 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.46}\mbox{erg~s}^{-1}\nonumber\\
-L_{\rmn{CR}-\ensuremath{\pi^0}}(>10\,\gev)  = 2.2\times10^{43}
-\left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.34}\mbox{erg~s}^{-1}\nonumber\\
+L_{\gamma}(>10\,\gev)  = 2.2\times10^{43}
+\left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.34}\mbox{erg~s}^{-1}\,.\nonumber\\
 \end{eqnarray}
-This implies already a general strategy to minimize the CR-induced
+Note that the CR luminosity scaling relations include the IC gamma-ray
+contribution from shock accelerated electrons as well as secondary
+electrons created through CRp-proton interactions. The gamma-ray flux
+from the electrons is, however, dominated by the decaying $\pi^0$ and
+only show up as a small flattening of the scaling relation at energies
+around $100\,\gev$. The steeper mass scaling of the CR compared to the
+DM implies already a general strategy to minimize the CR-induced
 foreground for DM annihilation and argues for very nearby groups. We
@@
 \section{Detailed modelling of starlight and dust in clusters}
+\label{sect:SD}
+In this section we show the details of our model of stars and dust
+(SD) in clusters of galaxies. In the first part we use the spectral
+distribution of the SD light in galaxies to derive a simple spectral
+model for SD in galaxy clusters. This is done by renormalizing the
+galactic SD light to match the conditions for a cluster. In the second
+part we derive the spatial distirbution of the SD light.
 
 \subsection{Energy spectrum}
-
-Our goal in this section is to derive a simple spectral model for SD
-in galaxy clusters. The SD light from clusters is dominated by the
-emission from galaxies. This radiation is expected to leak out into
-the much larger volume of the ICM, hence we approximate the spectral
-distribution of the ICL with the light from galaxies. We use the far
-infrared to ultraviolet spectrum derived in \cite{2006ApJ...648L..29P}
-for a MW type galaxy to characterize the SD spectral distribution of a
+The SD light from clusters is dominated by the emission from
+galaxies. This radiation is expected to leak out into the much larger
+volume of the ICM, hence we approximate the spectral distribution of
+the ICL with the light from galaxies. We use the far infrared to
+ultraviolet spectrum derived in \cite{2006ApJ...648L..29P} for a MW
+type galaxy to characterize the SD spectral distribution of a
 cluster. Note that we only keep the spectral shape, and renormalize
@@
 light from SD together with the CMB black-body distribution in a
-galaxy cluster, both at the radius $r=0.02\rvir$ where the energy
-density of the smooth light from SD (see Fig.~\ref{fig:SD_Edens})
-equals the energy density of the CMB. We have renormalized both the
-spectral data and the fitted spectra using the luminosity from stars
-and dust individually.
-
-We choose to fit the spectrum of the dust that peaks at about
-$10^{-2}\,\ev$ with a double power-law, and the slightly wider
-spectral distribution of the stars that peaks at about $1\,\ev$ with a
-tipple power-law. We find the best fit spectra for the SD in a
-cluster through:
+$6\times10^{14}\,\msun$ galaxy cluster. We fit the spectral shape of
+SD individually; the dust that peaks at about $10^{-2}\,\ev$ is fitted
+using a double power-law, while the broader spectral distribution of
+the stars that peaks at about $1\,\ev$ is fitted using a tipple
+power-law. The best fitted SD spectra are given by: \del{both at the
+  radius $r=0.03\rvir$ where the energy density of the smooth light
+  from SD (see Fig.~\ref{fig:SD_Edens}) equals the energy density of
+  the CMB. We have renormalized both the spectral data and the fitted
+  spectra using the luminosity from stars and dust individually.}
 \begin{eqnarray}
-  \eph^2\frac{\dd^2 N_\ph}{\dd \eph \dd V}
-  &\equiv& u_\sd(\eph) =  \sum_i N_i(\mvir) u_i^\gal(\eph)\,,\nonumber \\ 
-\rmn{where}\quad i&=&\{\rmn{stars,dust}\} \qquad \rmn{and}\\ 
-% &=&  N_\dust(\lx) u_\dust^\gal(\eph) + N_\stars(\lx) u_\stars^\gal(\eph)  \nonumber \\ 
-%  \\
   u_\stars^\gal(\eph) &=& \frac{23\,\rmn{eV}}{\rmn{cm}^3} 
@@
 \end{eqnarray}
-
-The spatial and spectral distribution functions of the light from SD
-in a cluster are both normalized with a mass dependent function
-determined from the luminosity in each respective wavelength band. The
-specific energy density is given by
+The specific energy density of SD light in a cluster can now be
+derived from 
 \begin{eqnarray} 
-u_\sd(\eph, r) &=& j(r)\,u_\sd(\eph) \nonumber\\
-&=& j(r)\,\sum_i N_i(\mvir) u_i^\gal(\eph)\,,
-\label{eq:u_SD}
+u_\sd(\eph, r) &=& j(r)\,u_\sd(\eph)\,,
+\label{eq:u_SD_re}
 \end{eqnarray}
-where $j(r)$ describes the spatial distribution. We fix the unitless
-normalization $N_i(\mvir)$ using the total energy of the light in SD
-within $\rvir$:
+where the SD spectrum is given by 
+\begin{eqnarray}
+  u_\sd(\eph) &\equiv& \eph^2\frac{\dd^2 N_\ph}{\dd \eph \dd V}
+  =  \sum_i N_i(\mvir) u_i^\gal(\eph)\,,\nonumber \\ 
+\rmn{where}\quad i&=&\{\rmn{stars,dust}\}\,.
+\end{eqnarray}
+Here $\eph$ denotes the energy of the SD photons, $j(r)$ describes the
+unitless spatial distribution which we derive in
+sect.~\ref{sect:SD_radial}, and $N_i(\mvir)$ denotes the mass
+dependent normalization for the SD. This function is determined using
+the total energy of the light in SD within $\rvir$ denoted by
+$E_{i,\vir}$. We relate this energy to the luminosity $L_i$ of each
+respective wavelength band (optical and IR light for the dust, and UV
+light for the stars) using
 \begin{eqnarray} 
@@
 \end{eqnarray}
-Here we approximate the total energy of the photons within $\rvir$
-($E_{i,\vir}$) with the luminosity $L_i$ \cite{2008A&A...490..547G}
-times the typical timescale it takes for a photon to propagate through
-the cluster (we assume that the cluster is optically thin). We derive
-the luminosity from the stars using
+We approximate the total energy of the photons within $\rvir$ with the
+luminosity \cite{2008A&A...490..547G} times the typical timescale it
+takes for a photon to propagate through the cluster (we assume that
+the cluster is optically thin).
+
+We derive the luminosity from the stars using
 \begin{eqnarray}
@@
 &\approx& 5.3\times10^{44}\,\rmn{erg}\,\rmn{s}^{-1}\,,
-\label{eq:L_star}
+\label{eq:L_stars}
 \end{eqnarray}
@@
 in the $(r+i)$-band is given by $m_\rmn{cl}\approx 15.5$
-\cite{2005MNRAS.358..949Z}. This magnitude is derived from stacking
+\cite{2005MNRAS.358..949Z}. This magnitude is derived from stacked
 clusters observed by the SDSS with the average mass
@@
 and distance to the cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. To
-account for different cluster masses in our analysis we adopt a simple
-mass scaling of the luminosity from the stars in clusters. Since a
-large contribution of the total starlight in a cluster comes from the
-brightest cluster galaxy (BCG), we assume that the total starlight has
-the same halo mass scaling as the BCG \cite{2010ApJ...713.1037H}
+account for different cluster masses, we attach a simple mass scaling
+to the luminosity from the stars in clusters in Eq.~(\ref{eq:L_stars}).
+Since a large contribution of the total starlight in a cluster comes
+from the brightest cluster galaxy (BCG), we assume that the total
+starlight has the same halo mass scaling as the BCG
+\cite{2010ApJ...713.1037H}
 \begin{equation}
@@
 \left(\frac{\mvir}{M_{200\rmn{av}}}\right)^{0.18}\,.
+\label{eq:L_stars_m}
 \end{equation} 
-We can now fix the normalization constant for the stars in
+We can now fix the unitless normalization constant for the stars in
 Eq.~(\ref{eq:E_SD}) by integrating over the cluster volume and
@@
 \begin{equation}
- N_\stars(\mvir) = 2.1\times10^{33}\,
+ N_\stars(\mvir) = 6.0\times10^{-9}\,\kpc^2\,
 \left(\frac{\mvir}{M_{200\rmn{av}}}\right)^{0.18}\,
@@
 
-The luminosity from the dust is derived from the the luminosity to
-richness scaling relation found in \cite{2008A&A...490..547G}
-$L_\dust=10^{44.8}\left(\frac{N_{200}}{10}\right)^{0.8}$. We pick a high
-richness $N_{200}=82$ cluster to normalize the luminosity since they
-are less likely biased by chance coincidences. This richness roughly
-correspond to $\mvir=6.0\times10^{14}\,\msun$
+The luminosity from the dust is derived from the luminosity-richness
+scaling relation found in \cite{2008A&A...490..547G}
+$L_\dust=10^{44.8}\left(\frac{N_{200}}{10}\right)^{0.8}$. We pick a
+high richness cluster with $N_{200}=82$ to normalize the luminosity
+since these clusters are less likely biased by chance
+coincidences. This richness roughly correspond to a mass
+$M_\rmn{200dust}=6.0\times10^{14}\,\msun$
 \cite{2010ApJ...713.1037H}. Assuming that the dust scales with halo
@@
 \begin{equation}
-L_\stars(\mvir)=L_\stars(M_{200\rmn{av}})\,
-\left(\frac{\mvir}{M_{200\rmn{av}}}\right)^{0.18}\,.
+L_\dust(\mvir)=L_\dust(M_\rmn{200dust})\,
+\left(\frac{\mvir}{M_\rmn{200dust}}\right)^{0.18}\,.
+\label{eq:L_dust_scale}
 \end{equation} 
@@
 \begin{equation}
- N_\dust(\mvir) =\,
-\left(\frac{\mvir}{M_{200\rmn{av}}}\right)^{0.18}\,
+ N_\stars(\mvir) = 4.0\times10^{-7}\,\kpc^2\,
+\left(\frac{\mvir}{M_\rmn{200dust}}\right)^{0.18}\,
 \frac{\rvir}{\int_{\rvir} j(r) \,\dd V}\,.
@@
 
-The spatial distribution of the SD energy density is an important quantity since
-it impacts the steady state electron and positron spectra through cooling. A
-higher density of SD in a cluster suppresses the spectra of the upscattering
-particles. With the formalism presented above, we can now derive the energy
-density from starlight and dust in a galaxy cluster through
-\begin{eqnarray}
-\label{eq:U_SD}
-u_\sd(r) &=& \int \dd \eph \frac{\dd^2 N_\ph}{\dd \eph \dd V}\,\eph
-=\int \dd \eph \frac{u_\sd(\eph, r)}{\eph}
-\nonumber \\
-&=&  j(r)  \int \dd \eph \sum_i 
-N_i(\mvir) \frac{u_i^\gal(\eph)}{\eph}\,. \nonumber \\
-\end{eqnarray}
-In Fig.~\ref{fig:SD_Edens} we compare the energy densities from
-different radiation fields in a galaxy cluster with the mass
-$\mvir=4.0\times10^{13}\msun$. We use two different profiles for the
-SD energy density, where the total profile includes the contribution
-from the ICL, the BCG and all the galaxies, while the galaxies are
-excluded in the smooth profile. We find that even for a cluster with a
-relative small mass the energy density of the SD components dominates
-over the CMB and the magnetic fields (with a central B field of 3~$\mu
-G$) within about 10\% of $\rvir$. Outside this radius the CMB is
-dominating the energy density of the cluster, hence the magnetic
-fields are always subdominant in the cluster and can safely be removed
-from cluster IC calculations for a reasonable central B-field and
-spectral index. Note that in this work we keep the contribution
-from B-fields to the total energy density for consistency.
-
 \subsection{Radial profiles}
+\label{sect:SD_radial}
+Our goal in this section is to derive a simple spatial model for the
+distribution of SD in galaxy clusters. For this reason we use stacked
+cluster observations by Sloan in the $r$ and $i$-band that trace the
+stars. For simplicity we assume that the dust trace the stars in the
+clusters {\bf WHY IS THIS A GOOD APPROXIMATION}. The stacked surface
+brightness profiles in \cite{2005MNRAS.358..949Z} are measured at
+redshift $z \sim 0.25$ with an average mass of the clusters of
+$4.0\times10^{13}\,\msun$. The profiles are build up out of three
+components; diffuse intracluster light (ICL), galaxies, and the
+brightest cluster galaxy (BCG) in the center of clusters. However, the
+total volume overlap of the ISM to the cluster is very small compared
+to the ICL- and BCG overlap with the cluster, thus the relative
+contribution of the galaxies to the IC emission is suppressed
+(c.f. Eq.~\ref{eq:SD_overlap}). To remove this bias we cut out the
+galaxies that have been smoothed over the cluster in the stacked
+analysis. In Fig.~\ref{fig:SD_spatial} we show the SDSS stacked
+brightness profiles as well as the fitted profiles\footnote{The
+  measured brightness is converted into units of
+  $\rmn{erg}\,\rmn{s}^{-1}$ using \cite{2010...book}
+  $S(\rmn{mag}\,''^{-2}) =
+  \mathcal{M}_\odot+21.6-2.5\log_{10}[S(L_\odot\,\rmn{pc}^{-2})]$,
+  where the sun's absolute magnitude in the $r$-band is given by
+  $\mathcal{M}_\odot=27.1$ \cite{1998gaas.book.....B} and the
+  luminosity of the sun by $L_\odot=3.85\times10^{33}\,
+  \rmn{erg}\,\rmn{s}^{-1}$.}, where both the data and fits are
+normalized with the central surface brightness of the total SD
+component ($S_\sd^\rmn{tot}(0)$). Our benchmark spatial model is shown
+with the solid black line, and include the contribution from the ICL
+and BCG.
 
@@
    line that is fitted to only the ICL and the BCG. Note that, we use
-   total SD brightness in the cluster center to normalize the SD
-   surface brightness profiles.}
+   total SD brightness in the cluster center ($S_\sd^\rmn{tot}(0)$) to
+   normalize the SD surface brightness profiles.}
  \label{fig:SD_spatial}
 \end{figure}
-Our goal in this section is to derive a simple spatial model for the
-distribution of SD in galaxy clusters. For this reason we use stacked
-cluster observations by Sloan in the $r$ and $i$-band that trace the
-stars. For simplicity we assume that the dust trace the stars in the
-clusters [WHY IS THIS A GOOD APPROXIMATION]. The stacked surface
-brightness profiles in \cite{2005MNRAS.358..949Z} are measured at
-redshift $z \sim 0.25$ with an average mass of the clusters of
-$4.0\times10^{13}\,\msun$. The profiles are build up out of three
-components; diffuse intracluster light (ICL), galaxies, and the
-brightest cluster galaxy (BCG) in the center of clusters. However, the
-total volume overlap of the ISM to the cluster is very small compared
-to the ICL- and BCG overlap with the cluster, thus the relative
-contribution of the galaxies to the IC emission is suppressed. To
-remove this bias we cut out the galaxies that have been smoothed over
-the cluster in the stacked analysis. In Fig.~\ref{fig:SD_spatial} we
-show the SDSS stacked brightness profiles as well as the fitted
-profiles\footnote{The measured brightness is converted into units of
-  $\rmn{erg}\,\rmn{s}^{-1}$ using \cite{2010...book}
-  $S(\rmn{mag}\,''^{-2}) =
-  \mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})$,
-  where the sun's absolute magnitude in the $r$-band is given by
-  $\mathcal{M}_\odot=27.1$ \cite{1998gaas.book.....B} and the
-  luminosity of the sun by $L_\odot=3.85\,10^{33}
-  \rmn{erg}\,\rmn{s}^{-1}$.}, both scaled with the unitless $\rvir$
-normalized area to resemble the expected luminosity at radius
-$r$. Our benchmark spatial model is shown with the solid black line,
-and include the contribution from the ICL and BCG.
 
@@
 profile with the addition of a power-law, we use a double beta profile
-model for simplicity of deprojection given by:
+model for simplicity of deprojection. It is given by
 \begin{equation}
 \tilde{S}_\sd (r_\bot) = \frac{S_\sd (r_\bot)}{S_\rmn{SD}^\rmn{tot}(0)} = 
-\sum_{i=1}^2 \,S_i\, 
+\sum_{i=1}^2 \,\tilde{S}_i\, 
 \left[1 + \left( \frac{r_\bot}{r_{\mathrm{c}_i}}\right)^2\right]
@@
 \end{align}
-The 3D spatial profile is derived by deprojecting the surface
-brightness in Eq.~(\ref{double_beta}) (see
+The three dimensional spatial profile is derived by deprojecting the
+surface brightness in Eq.~(\ref{double_beta}) (see
 e.g. \cite{2004A&A...413...17P} for details about the deprojection):
@@
   \frac{6 \beta_i - 1}{\left(1 + r^2/r^2_{\mathrm{c}_i}\right)^{3\beta_i}}\,
-  \mathcal{B}\left(\frac{1}{2},3\beta_i\right)\,,
+  \mathcal{B}\left(\frac{1}{2},3\beta_i\right)\,,\nonumber\\
 \end{eqnarray}
@@
 
+The spatial distribution of the SD energy density is an important
+quantity since it impacts the steady state electron and positron
+distribution through cooling. A higher energy density of SD photons in
+a cluster suppresses the gamma-ray flux from IC upscattered
+photons. We derive the energy density from starlight and dust in a
+galaxy cluster through
+\begin{eqnarray}
+\label{eq:U_SD_r}
+u_\sd(r) &=& \int \dd \eph \frac{\dd^2 N_\ph}{\dd \eph \dd V}\,\eph
+=\int \dd \eph \frac{u_\sd(\eph, r)}{\eph}
+\nonumber \\
+&=&  j(r)  \int \dd \eph \sum_i 
+N_i(\mvir) \frac{u_i^\gal(\eph)}{\eph}\,, \nonumber \\
+\end{eqnarray}
+where we have used that specific energy density of the SD light given
+by Eq.~(\ref{eq:u_SD_re}). Note that we compare the energy density
+$u_\sd(r)$ to other radiation background fields in
+Fig.~\ref{fig:SD_Edens} for a galaxy cluster with the mass
+$\mvir=6\times10^{14}\msun$.
+
+\del{ we compare the energy densities from different radiation fields
+  in a galaxy cluster with the mass $\mvir=6\times10^{14}\msun$. We
+  use two different profiles for the SD energy density, where the
+  total profile includes the contribution from the ICL, the BCG and
+  all the galaxies, while the galaxies are excluded in the smooth
+  profile. We find that even for a cluster with a relative small mass
+  the energy density of the SD components dominates over the CMB and
+  the magnetic fields (with a central B field of 3~$\mu G$) within
+  about 10\% of $\rvir$. Outside this radius the CMB is dominating the
+  energy density of the cluster, hence the magnetic fields are always
+  subdominant in the cluster and can safely be removed from cluster IC
+  calculations for a reasonable central B-field and spectral
+  index. Note that in this work we keep the contribution from B-fields
+  to the total energy density for consistency.}
+
 %***********************************************
@@
 \section{Source functions of different DM models}
-
-{\bf Anders: add your fit functions for the 4 BM and the LP models. NEED MORE WORK}
+{\bf Anders: add your fit functions for the 4 BM and the LP models. DONE}
+
+We use {\sc DarkSUSY} to derive the spectra for the continuum emision
+from the DM BM models. These spectra is shown in the left panel of
+Fig.~\ref{fig:q_DM}. We fit the source function using the following
+functional form
 \begin{eqnarray}
-q_\rmn{BM}&=&\left(\frac{\rho\,c^2}{\gev\,\cm^{-3}}\right)^2\times
-\left(\frac{10^{33}}{\eg1.6e-3}\right) \nonumber\\
-&\times&\left\{a_1\frac{\exp\left(-\eg^{-a_2}\right)}{1+\exp\left(\eg^{a_3}\right)}+a_5^{\left(4-\beta_1\right)}\,a_4\,\eg^{\beta_1}
-\exp\left[-\left(\frac{\eg}{a_5}\right)^{\beta_2}\right]\right\} \nonumber\\
+q_\rmn{BM} (\eg,r)&=&\left[\frac{\rho(r)}{10^{-29}\rmn{g}\,\cm^{-3}}\right]^2
+\times\frac{a_1}{\egt}\times\theta(\eg-m_\chi\,c^2)\nonumber\\
+&\times&\left[\frac{\exp\left(-\egt^{-a_2}\right)}{1+\exp\left(\egt^{a_3}\right)}
++\left(\frac{\egt}{a_4}\right)^{4.5}\right]\,, \nonumber\\
+&&\rmn{where}\quad \egt = \frac{\eg}{\gev}\,,
  \label{eq:bm_cont}
 \end{eqnarray}
-
-\del{      egn = eg/GeV
-diffBM=(p1*dexp(-egn**(-p2))/(1.+dexp(egn**p3))+
-     1     p5**(4.-pow1)*p4*egn**pow1*dexp(-(egn/p5)**pow2))
-     2     /(egn)/GeV}
-
-where the common parameters $\beta_1 = 4.5,\,\beta_2 = 15$, and the
-model specific parameters:
+where the model specific parameters are given by:
+
+%     egn    = eg/GeV
+%     diffBM = (p1*dexp(-egn**(-p2))/(1.+dexp(egn**p3))
+%     1      + p5**(4.-pow1)*p4*egn**pow1*dexp(-(egn/p5)**pow2))
+%     2      / (egn*GeV)
+
 \begin{table}
-\begin{tabular}{c c c c c c }
+\begin{tabular}{c c c c c }
 \hline
 \hline
- BM model & $a_1$ & $a_2$  & $a_3$ & $a_4$  & $a_5$ \\
+ BM model & $a_1$ & $a_2$  & $a_3$ & $a_4$ \\
+          & $[\gev^{-1}\,\cm^{-2}\,\rmn{s}^{-1}]$ & & & \\
  \hline
-$\Ip$ & $3.2\times10^{18}$ & $0.36$ & $0.51$ & $5.8\times10^6$ & $135$ \\
-$\Jp$ & $6.6\times10^{16}$ & $0.40$ & $0.43$ & $1.8\times10^4$ & $308$ \\
-$\Kp$ & $2.7\times10^{18}$ & $0.42$ & $0.37$ & $0.0$           & $123$ \\
-$\Js$ & $3.4\times10^{16}$ & $0.34$ & $0.51$ & $4.0\times10^5$ & $221$ \\
+$\Ip$ & $2.0\times10^{-4}$ & $0.36$ & $0.51$ & $701$  \\
+$\Jp$ & $4.1\times10^{-6}$ & $0.40$ & $0.43$ & $1178$ \\
+$\Kp$ & $1.7\times10^{-4}$ & $0.42$ & $0.37$ & $-$    \\
+$\Js$ & $2.1\times10^{-6}$ & $0.34$ & $0.51$ & $490$  \\
 \hline
@@
 \begin{quote}
+The best fit parameters to the continuum emision from our
+supersymmetric BM models.
  \label{tab:bm_cont}
@@
 \end{table} 
-
-\begin{equation}
-N_\rmn{el} = a_1\frac{\ee^{-a_2}}
-{\left[1+\left(\frac{\ee}{a_3}\right)^{a_4}\right]^{a_5}}
-\times\left[1+\left(\frac{\ee}{a_6}\right)^{a_7}\right]^{a_8}
+Again we use {\sc DarkSUSY} to derive the number of electrons amd
+positons resulting from each annihilating pair. This spectra is shown
+in the right panel of Fig.~\ref{fig:q_DM}. The electron and positon
+yield resulting from our supersymmetric BM model is fitted using
+\begin{eqnarray}
+N_{\e,\rmn{BM}}(>\ee) &=& \frac{a_1}{\eet^{a_2}}\times
+\frac{\left[1+\left(\frac{\eet}{a_6}\right)^{a_7}\right]^{a_8}}
+{\left[1+\left(\frac{\eet}{a_3}\right)^{a_4}\right]^{a_5}}
+\times\theta(\ee-m_\chi\,c^2)\,,\nonumber\\
+& &\rmn{where}\quad\eet=\frac{\ee}{\gev}\,.
 \label{eq:bm_elec}
-\end{equation}
-
+\end{eqnarray}
+We find the following best fit parameters.
 \begin{table}
@@
  \hline
-$\Ip$ & $14$ & $0.06$ & $1.8$ & $0.9$  & $2.0$ & $60$  & $5$ & $-1$     \\
-$\Jp$ & $17$ & $0.08$ & $5.5$ & $0.8$  & $2.6$ & $250$ & $5$ & $-1$     \\
-$\Kp$ & $22$ & $0.05$ & $1.7$ & $0.85$ & $2.1$ & $10$  & $2$ & $0.62$ \\
-$\Js$ & $15$ & $0.14$ & $5.0$ & $1.0$  & $1.5$ & $300$ & $5$ & $-1$     \\
+$\Ip$ & $28$ & $0.06$ & $1.8$ & $0.9$  & $2.0$ & $60$  & $5$ & $-1$     \\
+$\Jp$ & $34$ & $0.08$ & $5.5$ & $0.8$  & $2.6$ & $250$ & $5$ & $-1$     \\
+$\Kp$ & $44$ & $0.05$ & $1.7$ & $0.85$ & $2.1$ & $10$  & $2$ & $0.62$   \\
+$\Js$ & $30$ & $0.14$ & $5.0$ & $1.0$  & $1.5$ & $300$ & $5$ & $-1$     \\
 \hline
@@
 \begin{quote}
+The best fit parameters to the electron and positron yield from the DM
+BM models above the electron energy $\ee$.
  \label{tab:bm_elec}
@@
 \end{table} 
-
+Once again, we use {\sc DarkSUSY} to derive the electron and positron
+yield resulting from LP DM annihilating into decaying muons. We find
+the following best fit:
+\begin{eqnarray}
+N_{\e,\rmn{LP}\mu}(>\ee) &=& \exp\left\{a_1+\log\left(1-x\right)+
+a_3\left[\log\left(1-x\right)\right]^2\right\}
+\,,\nonumber\\
+\rmn{where}\quad a_1&=&0.719,\,a_2=2.27,\,a_3=0.200,\,\quad\rmn{and}\nonumber\\
+x&=&\frac{\ee}{m_\chi\,c^2}\,.
+\label{eq:bm_elec}
+\end{eqnarray}
+It should be noted that the LP model we are using has a branching
+factor branching ratio of ($1/2,\,1/2$) into
+($\mu^+/\mu^-,\,\e^+/\e^-$). Hence the resulting electron and positron
+yield for the LP model is given by $N_{\e,\rmn{LP}}(>\ee) =
+1+N_{\e,\rmn{LP}\mu}(>\ee)/2$.
+
+% BM
 %  een = ee/GeV
-%  
-%  if(BMmodel.eq.0) then
 %  gmu = 14.d0*een**(-0.06)/(1.d0+(een/1.8d0)**0.9 )**2.0/
 %  &           (1.d0+(een/60.d0)**5 ) !0
-%  c            write(*,*) gmu,een
-%  endif
-%  if(BMmodel.eq.1) then
 %  gmu = 17.d0*een**(-0.08)/(1.d0+(een/5.5d0)**0.8 )**2.6/
 %  &           (1.d0+(een/250.d0)**5) !1
-%  endif
-%  if(BMmodel.eq.2) then
 %  gmu =(22.d0*een**(-0.05)/(1.d0+(een/1.7d0)**0.85)**2.1*
 %  &           (1.d0+(een/10.d0)**2 )**0.62*dexp(-(een/230.d0)**7)) !2 &3
-%  endif
-%  if(BMmodel.eq.3) then
 %  gmu = 15.d0*een**(-0.14)/(1.d0+(een/5.0d0)      )**1.5/
 %  &           (1.d0+(een/300.d0)**5) !4
-%  endif
 %  gmu = gmu*2d0! acounting for the electrons as well
-%
+
 %LP
-%      gmu=0.71894+2.27161*dlog(1.-(ee/mX))+
+%  gmu = 0.71894+2.27161*dlog(1.-(ee/mX))+
 %  &           0.199579*(dlog(1.-(ee/mX)))**2
@@
 
+\section{Flux tables for the HIFLUGCS catalouge}
+
 \end{document}

### 2011-05-11 paper.tex
correction of main part finished

@@
 X-rays. Especially since the long cooling time of cosmic ray protons
-(CRps) allows for an extended and large population of CRps to build up
+(CRs) allows for an extended and large population of CRs to build up
 over the cluster history \citep{1996SSRv...75..279V,
@@
 parameter and assume that 50\% of the dissipated energy at strong
-shocks is injected into CRps while this efficiency rapidly decreases
+shocks is injected into CRs while this efficiency rapidly decreases
 for weaker shocks \cite{2007A&A...473...41E}. As a caveat we note that
@@
 from clusters.  In the leptophilic model, DM annihilation radiation
-includes final state radiation and give rise to substantial amounts of
+includes final state radiation and gives rise to substantial amounts of
 electrons and positrons that IC upscatter background radiation fields
@@
 induced emission. In addition to the annihilating DM, we estimate the
-gamma-ray flux induced by shock accelerated CRps.
+gamma-ray flux induced by shock accelerated CRs.
 
@@
 searches due to its relative high DM induced fluxes and low CR induced
-fluxes. We derive the emission from four different supersymmetric BM
-models and the emission induced by CRps. Comparing this emission to
-the differential gamma-ray upper limits set by Fermi-LAT after 18
-months of observations \cite{2010ApJ...717L..71A}, we find that the
-upper limits are not violated. The predicted DM flux that is dominated
-by the continuum emission from $\Kp$ and $\Ip$ models (shown in the
-left panels) are close to the upper limits and can potentially be
-probed by the Fermi 3 year data. Furthermore, the gamma-ray signal
-induced by CRps is expected to be about a factor 10 below the DM
-continuum flux from the $\Kp$ and $\Ip$ BM models around
+fluxes. We show the emission for four different supersymmetric BM
+models and contrast it to the emission induced by CRs. Comparing this
+emission to the differential gamma-ray upper limits set by Fermi-LAT
+after 18 months of observations \cite{2010ApJ...717L..71A}, we find
+that the upper limits are not violated. The predicted DM flux that is
+dominated by the continuum emission from $\Kp$ and $\Ip$ models (shown
+in the left panels) are close to the upper limits and can potentially
+be probed by the Fermi three-year data. Furthermore, the gamma-ray
+signal induced by CRs is expected to be about a factor 5--10 below
+the DM continuum flux from the $\Kp$ and $\Ip$ BM models at
 10~GeV. However, the IC emission from upscattered CMB and SD photons
-is at least a factor 10 lower than the expected flux from CRps above
+is at least a factor 10 lower than the expected flux from CRs above
 100~MeV, making it very hard to distinguish such a signal from the
@@
 to be dominating \cite{2010MNRAS.409..449P} over the supersymmetric DM
-induced leptons. Hence the IC emission from supersymmetric DM in
-clusters can for DM benchmark models be safely neglected compared to
-the CRps and DM continuum emission.
+induced leptons. Hence in clusters, the IC emission from
+supersymmetric DM benchmark models be  neglected compared to the
+CR pion and DM continuum emission.
 
@@
 
-{\bf Anders: I got that far with the results, please polish the reminder up to population studies!}
-
-\del{CONSIDER REWRITING, START WITH PHYSICS, THEN DISCUSS DOMINATING
-CONTRIBUTIONS, PEAKS, AND SPECTRAL INDICES}
-
 One of the main contributions to the expected extended gamma-ray flux
@@
 greatly. Hence it is interesting to understand which spectral features
-and energy regimes that are dominating for the different DM models.
+and energy regimes  are dominating for the different DM models.
 
@@
 marginally dominating over the smooth distribution in a cluster, the
-SD component becomes more important, especially the flux from IC
-upscattered CMB photons is small for LP models in the 100~GeV to 1~TeV
-energy regime and in the 1~GeV to 100~GeV energy regime for BM models.
+SD component becomes relatively more important.
 
@@
 individual contributions from different IC upscattered radiation
-fields. The left panel show the gamma-ray emission from the LP model
+fields. The left panel shows the gamma-ray emission from the LP model
 and the right panel from the $\Kp$ BM model, and for comparison we
-overplot the emission expected from the CRps. Due to the flat electron
+overplot the emission expected from the CRs. Due to the flat electron
 and positron spectrum resulting from the LP DM model and the smaller
@@
 energy regime below 100~GeV, while the SD dominate above this
-energy. For the BM models this transition is shifted towards a smaller
-energy since the electron and positron spectrum has a steep spectral
-distribution that suppresses low energy photon fields. \del{This
+energy. For the BM models this transition energy is shifted towards
+smaller energies since the electron and positron spectrum has a
+steeper spectral distribution (see Fig.~\ref{fig:q_DM}). At the
+highest gamma-ray energies of about 100~GeV and above, the IC from
+starlight steepens because it probes the high energy tail of the
+electrons and more importantly, it suffers from the Klein-Nishina
+suppression. When substructures are present, most of their flux
+resides in the outer parts of clusters. However, if we remove the
+boost from substructures, the density profile of electrons and
+positrons is more centrally peaked, and the relative importance of the
+IC upscattered SD increases by a factor $\sim 30$.  A larger fraction
+of electrons (in the core) will now also cool by Compton-upscattering
+SD photons which suppresses the IC-upscattered CMB light.  For
+comparison, we include the contribution of IC upscattered SD photons
+and to bracket the uncertainty in the SD model, with a smaller amount of
+dust. In this low-dust model, we have reduced the energy in dust by a
+factor 10. However, we find that the IC SD flux only decreases by a
+factor 3 since the IC cooling of the electrons and positrons also
+decreases. Note that for a smaller boost from substructures, the
+effect from cooling is smaller.
+
+ \del{This
   suppression is also seen in the relative normalization of the flux
@@
   hence it is upscattered by more abundant low energy electrons and
-  positrons (c.f. Fig.~\ref{fig:q_DM}).} At the highest gamma-ray
-energies of about 100~GeV and above, the IC from starlight steepens
-because it both probes the high energy tail of the electrons as well
-as suffer from the KN suppression. It should be noted that if we
-remove the boost from substructures, the density profile of electrons
-and positrons is more centrally peaked, and the relative importance
-of the IC upscattered SD increases by a factor $\sim 30$. In
-addition, the IC upscattered CMB light would suffer more from SD
-cooling in the center as most of its flux resides from the outer parts
-when substructures are included. For comparison, we include the
-contribution of IC upscattered SD photons and to bracket the
-uncertainty in the SD model, with a small amount of dust. In this low
-dust model we have reduced the energy in dust by a factor 10. However,
-we find that the IC SD flux only decreases by a factor 3 since the
-cooling of the electrons and positrons also decreases. Note that for a
-smaller boost from substructures, the effect from cooling is smaller.
+  positrons (c.f. Fig.~\ref{fig:q_DM}).}
 \del{Even though the SD component seems to be suppressed compared to
@@
 
-Because of the large boost factor for the LP model ($\sim 10^4$), we
-overproduce the upper gamma-ray limit in the $1-10$~GeV energy
-interval set by Fermi-LAT by about a factor 100. This strongly
-constrain the boost from both substructures and the Sommerfeld
-enhancement. Additional, these constraints might improve with future
+Because of the large total boost factor for the LP model ($\sim
+10^4$), we overproduce the upper gamma-ray limit in the $1-10$~GeV
+energy interval set by Fermi-LAT by about a factor 100. This strongly
+constrains the boost from both substructures and the Sommerfeld
+enhancement. Additionally, these constraints might improve with future
 more sensitive Cherenkov telescopes such as CTA. However, considering
@@
 conclude that the wide angular extent of clusters on the sky in
-gamma-rays suggest that these sources are not ideal for Cherenkov
-telescopes due to the loss of sensitivity outside the small PSF
-{\bf BETTER CHECK THIS WITH SOME EXPERT}.
+gamma-rays suggest that these sources are not ideal for IACTs since
+their sensitivity drops linearly with source extension.
 
@@
 where they averaged the flux over the energy range $0.2-100\,\gev$
-assuming a spectral index of 2. Again we are overproducing the upper
-limits, although only with a factor 10 which is about a order
-magnitude less constraining than the differential flux in the energy
-range $1-10$~GeV. From the figure one clearly see that the LP model is
-dominating the entire gamma-ray energy range up to the DM mass of this
-model of about 1~TeV. Finally, we note that the flux the DM BM $\Kp$
-model is above the predicted emission from the CRps in the $1-100$~GeV
-energy regime accessible both to Fermi and Cherenkov
-telescopes. Hence, in the absence of LP DM the prospects for detecting
-the $\Kp$ BM model over the expected gamma-ray background induced by
-CRps look promising.
+assuming a spectral index of 2. Again, the annihilation flux in the LP
+model is in conflict with the upper limits by Fermi-LAT, although only
+by a factor of 10 which is about a order magnitude less constraining
+than the differential flux in the energy range $1-10$~GeV. As shown in
+this figure, the LP model is dominating the entire gamma-ray energy
+range up to the DM rest mass energy in this model of about
+1~TeV. Finally, we note that the flux the DM BM $\Kp$ model is above
+the predicted emission from the CRs in the $1-100$~GeV energy
+regime. Hence, the prospects for detecting the $\Kp$ BM model over the
+expected gamma-ray background induced by CRs looks promising.
 
@@
 have used spatially unresolved upper limits, which is quite optimistic
-for the angular extended Virgo cluster. It is quite striking how
-constraining the upper limits for the Fornax cluster are compared to
-the other clusters, especially in the $1-10$~GeV energy regime where
-Fermi-LAT is most sensitive due to the maximized effective area. The
-upper limits for Virgo and Perseus are unfortunately background
-contaminated by AGN activity from M87 and NGC 1267, respectively, and
-do not gain much from the increased sensitivity. One should also note
-that the high CRp induced flux from both Coma and Perseus is of the
-same magnitude as the DM flux from LP models, making it difficult for
-indirect DM searches in those clusters. Conversely is the Fornax
-cluster a great target for indirect DM studies because the relative
-low gamma-ray flux from CRps, absents of an active AGN, and high DM
-gamma-ray flux. Actually, the Fermi-LAT 3 year data will be able to
-constrain the smallest mass of substructures using the DM BM
-models. We have also learned that the closest clusters are superior
-for DM searches compared to further away clusters, even though the
-close by clusters have a mass that is much smaller. In fact, we can
-understand this by looking at the luminosity-to-mass scaling
-relations. The gamma-ray luminosity from the smooth density profile is
-given by \cite{2009PhRvL.103r1302P}
+for the Virgo cluster which has an angular extended of 7 degrees. It
+is quite striking how constraining the upper limits for the Fornax
+cluster are compared to the other clusters, especially in the
+$1-10$~GeV energy regime. At these energies, Fermi-LAT has its peak
+sensitivity due to a combination of increasing effective area and
+decreasing source spectra as a function of energy. The upper limits
+for Virgo and Perseus are unfortunately background contaminated by AGN
+activity from M87 and NGC 1267, respectively, and do not gain much
+from the increased sensitivity. Note that the high CR-induced flux in
+Coma and Perseus is of the same magnitude as the DM flux from LP
+models, making it difficult for indirect DM searches in those
+clusters. Conversely is the Fornax cluster a great target for indirect
+DM studies because the relative low gamma-ray flux from CRs, absents
+of an active AGN, and high DM gamma-ray flux. The Fermi-LAT three-year
+data will be able to constrain the smallest mass of substructures
+using the DM BM models.
+
+What is the figure of merit for selecting the most promising cluster
+targets for indirect DM searches? To this end, we employ the
+luminosity-to-mass scaling relations. The gamma-ray luminosity from
+the smooth density profile is given by \cite{2009PhRvL.103r1302P}
 \begin{equation}
-L_{\gamma,\sm} \propto \int \dd V \rho(r)^2 \propto \frac{c^3}
-{\left[\log\left(1+c\right)-c/(1+c)\right]} \propto \mvir^{0.83}\,,
+L_{\gamma,\sm} \propto \int \dd V \rho(r)^2 \propto \frac{M_{200}\,c^3}
+{\left[\log\left(1+c\right)-c/(1+c)\right]^2} \propto \mvir^{0.83}\,,
 \end{equation}
-and the total DM luminosity including boost factors for the LP and
+and the total DM luminosity that includes boost factors for the LP and
 the BM models are given by
@@
 \label{eq:LP_scaling}
-L_{\gamma,\rmn{LP}} &=& L_{\gamma,\rmn{smLP}} \B_\rmn{LP} \propto \mvir^{0.73}\qquad
-\,\,\,\,\,\,\rmn{and}\\
+L_{\gamma,\rmn{LP}} &=& L_{\gamma,\rmn{smLP}} \B_\rmn{LP} \propto \frac{\mvir^{0.73}}{D_\rmn{lum}^2},\\
 \label{eq:BM_scaling}
-L_{\gamma,\rmn{BM}} &=& L_{\gamma,\rmn{smBM}} \B_\rmn{BM} \propto  \mvir^{1.06}\,,\qquad
-\rmn{where} \\
+L_{\gamma,\rmn{BM}} &=& L_{\gamma,\rmn{smBM}} \B_\rmn{BM} \propto  \frac{\mvir^{1.06}}{D_\rmn{lum}^2},\\
 \B_\rmn{LP}&=&\B_\sfe \B_\sub \propto \mvir^{-1/3}\mvir^{0.23} \propto
@@
 \end{eqnarray}
-Hence increasing the mass with a factor two doubles the luminosity,
-but increasing the distance by a factor two decrease the flux with a
-factor four. One should also note that the IC upscattered SD photons
-scales slightly softer with mass, hence giving rise to a larger
-fraction of gamma-rays in low mass clusters compared to the total
-gamma-ray flux. \del{Furthermore, the low mass clusters have a higher flux
-from IC upscattered SD photons than high mass clusters which increase
-the importance of the SD component in low mass clusters even more
+Hence increasing the cluster mass in the BM model by a factor two more
+than doubles the luminosity, but increasing the luminosity distance,
+$D_\rmn{lum}$, by a factor two decrease the flux by a factor four. One
+should also note that the IC upscattered SD photons scales slightly
+softer with mass, hence giving rise to a larger fraction of gamma-rays
+in low mass clusters compared to the total gamma-ray flux.
+
+\del{Furthermore, the low mass clusters have a higher flux from IC
+  upscattered SD photons than high mass clusters which increase the
+  importance of the SD component in low mass clusters even more
   (c.f. Fig.~\ref{fig:IR_comp}).}
@@
 
-{\bf
-peak sensitivity of Fermi at these energies due to a combination of effective area background and source spectra...}
-
-In this section we have found that the LP DM models overproduce both
+In this section we have found that the LP DM models overproduces both
 the differential and integrated gamma-ray flux upper limits set by the
 Fermi-LAT 18 month data for several clusters. We can use these upper
-limits to constrain both the SFE and boost from
+limits to constrain the boosts due to SFE and
 substructures. Furthermore, as more sensitive experiments and better
@@
 boost factors that are manifested in the gamma-ray flux. It is
-especially interesting is to constrain the SFE, where a boost of 300
-is required to explain the excess of electrons and positrons observed
-in the vicinity of Earth by PAMELA/Fermi/HESS. In
-Fig.~\ref{fig:boost_const} we use the estimated flux from four
-clusters to constrain the SFE as well as the minimum mass of
-substructures where $M_\rmn{lim}\propto\mvir^{0.226}$. As expected,
-the Fornax cluster is the most constraining cluster by far, although
+especially interesting is to constrain the SFE, where a boost of the
+particle physics cross section of 300 is required to explain the
+excess of electrons and positrons observed in the vicinity of Earth by
+PAMELA/Fermi/HESS. In Fig.~\ref{fig:boost_const} we use the estimated
+flux of four clusters to constrain the SFE as well as the minimum mass
+of substructures where $M_\rmn{lim}\propto\mvir^{0.226}$. As expected,
+the Fornax cluster is by far the most constraining cluster, although
 the current upper limits are not good enough to rule out the boost
-from substructures or SFE. Assuming that the electron and positron
-excess is due to SFE DM, then in order not to overproduce the
-differential upper limits set by Fermi-LAT in the energy range
-$1-10$~GeV \footnote{We average the LP DM flux in the energy range
-  $1-10$~GeV before we compare it to the upper limits.}, we can
-constrain the smallest mass of substructures to $M_\rmn{lim}\gtrsim
-100\,\msun$. Instead assuming the standard mass of the smallest
-substructures of $M_\rmn{lim}\approx 10^{-6}\,\msun$, we can constrain
-the boost from SFE to about 2 in Fornax, which corresponds to a
-maximum SFE in the MW of about 5. Note that after about six years of
-observations with Fermi-LAT, we will be able to rule out the LP model
-assuming a substructure boost with a smallest mass of $M_\rmn{lim} =
-10^{-6}\,\msun$.
+from substructures or SFE. Assuming that the PAMELA positron excess is
+due to SFE DM, then in order not to overproduce the differential upper
+limits set by Fermi-LAT in the energy range $1-10$~GeV \footnote{We
+  average the LP DM flux in the energy range $1-10$~GeV before we
+  compare it to the upper limits.}, we can constrain the smallest mass
+of substructures to $M_\rmn{lim}\gtrsim 100\,\msun$. Instead assuming
+the standard mass of the smallest substructures of $M_\rmn{lim}\approx
+10^{-6}\,\msun$, we can constrain the boost from SFE to about 2 in
+Fornax, which corresponds to a maximum SFE in the MW of about 5. Note
+that after about six years of observations with Fermi-LAT, we will be
+able to rule out the LP model assuming a substructure boost with a
+smallest mass of $M_\rmn{lim} = 10^{-6}\,\msun$.
 
@@
 \label{sect:spatial}
-{\bf should probably be integrated into text; DUSTY STAR FORMING
+
+\del{\bf should probably be integrated into text; DUSTY STAR FORMING
   GALAXIES IN OUTER PARTS (LITTLE OVERLAP), DUST WOULD NOT SURVIVE. IF
   DUST RAMPRESSURE STRIPPED, SPATIALLIATION PROCESS IN THE HOT ICM FOR
-  DYNAMICAL TIME} The large angular extent of clusters on the sky in
-combination with the small PSF of most gamma-ray probes ($\sim
-0.1$~deg) suggest that we would be able to probe the different spatial
-regimes of a cluster. Especially important is the spatial distribution
-of the gamma-ray emission as it bias upper limits derived for
-spatially extended clusters where a simple profile is often
-assumed. In fact when DM substructures are included, the gamma-ray
+  DYNAMICAL TIME}
+
+The large angular extent of clusters on the sky in combination with
+the small PSF of most gamma-ray probes ($\sim 0.1$~deg) suggest that
+we would be able to probe the different spatial regimes of a
+cluster. Especially important is the spatial distribution of the
+gamma-ray emission as it bias upper limits derived for spatially
+extended clusters where a simple profile is often assumed. In fact, we
+will show that if DM substructures are present, the gamma-ray
 brightness profile is almost flat and very different from the
 gamma-ray distribution following a smooth density profile with a steep
-outer brightness slope of $-5$.
+outer surface brightness slope of $-5$.
 
 In this section we investigate the gamma-ray surface brightness
-profiles induced by both CRps and different models of DM in more
-detail. We start by comparing the substructure included brightness
-from different clusters in Fig.~\ref{fig:SB_clu}. As expected, we find
-that the DM flux in all clusters follow the same universal shape
-imposed by the substructures. Even as far in as 1\% of $\rvir$ we are
-dominated by the substructures, which is due to the projection of the
-outer cluster halo (see Sect.~\ref{sect:subst} for a longer
+profiles induced by both CRs and different models of DM in more
+detail. We start by comparing the intrinsic surface brightness that
+includes substructures from different clusters in
+Fig.~\ref{fig:SB_clu}. As expected, we find that the DM flux in all
+clusters follows the same universal shape imposed by the
+substructures. Already at $0.01\rvir$, we are dominated by the
+substructures due to the projection of their peaked distribution the
+outer cluster regions (see Sect.~\ref{sect:subst} for a longer
 discussion). This implies that the spatial distribution of
-annihilating DM induced emission is independent of the type of DM
-model, and can not be used to separate different models {\bf
-  Christoph, include this finding in conclusions, abstract?}. The
-normalization for the BM model is determined by $\bsub
+annihilating DM is independent of the type of DM model, and can not be
+used to separate different models. The surface brightness, $S_\gamma$,
+of the BM model scales as $S_\gamma\propto\bsub
 L_{\gamma,\rmn{BM}}^{1/3} \propto \mvir^{0.5}$, which explains the
@@
 with a negative mass trend, hence a flux normalization with a softer
-mass-scaling of $\sim\mvir^{0.17}$. The surface brightness induced by
-CRps mainly trace the gas profile of each cluster with an additional
-enhancement in the center due to the expected large population of
-CRps, hence we see a much larger spread in these profiles. It is
-noticeable that Fornax show such a small surface brightness. However,
-it is explained by the low gas density outside the BCG and the less
-abundant CRp population in the relative small cluster compared to a
-more massive cluster \cite{2010MNRAS.409..449P}. In fact, only the
-very inner part of Fornax is dominated by a large gamma-ray flux from
-CRps, which is however, neglible compared to the flux withing
-$\rvir$. This is the reason why Fornax is such a good target for
-indirect DM searches, and competitive to DM searches in dwarf
-galaxies. Although, it might be a problem for Cherenkov telescopes
-searching for DM in the center of Fornax.
+mass-scaling of $S_\gamma\propto\mvir^{0.17}$. The surface brightness
+induced by CRs is proportional to the projected squared the gas
+profile with an additional enhancement in the center of cool core
+clusters due to the adiabatic compression of CRs during the formation
+of the cool core. Hence, we see a much larger variation in these
+profiles driven by the large variation of the gas mass fraction. It is
+noticeable that Fornax shows such a small surface brightness. This is
+explained by the low gas density outside the BCG and the less abundant
+CRp population in the relative small cluster compared to a more
+massive cluster \cite{2010MNRAS.409..449P}.  This is the reason why
+Fornax is such a good target for indirect DM searches, and superior
+to DM searches in dwarf galaxies.
 
@@
    emission from the $\Kp$ benchmark model (blue). The different
-   linestyles each represent a cluster; Fornax (solid), Coma (dotted),
+   line styles each represent a cluster; Fornax (solid), Coma (dotted),
    Virgo (dashed), and Perseus (dash-dotted). The boost from
@@
    respectively. Notice the very similar shape and normalization of
-   the DM models, while the CRps have a much larger scatter in the
+   the DM models, while the CRs have a much larger scatter in the
    profiles due to the large variation of the gas fraction in these clusters.}
@@
 and without substructures. It is quite remarkable how flat the
-profiles including substructures are compared to the ones
+profiles becomes when substructures are present compared to the case
 without. This implies that the relative flux within the PSF in the
@@
    brightness profile of the Fornax cluster at 1~GeV. The emission
-   induced by CRps is denoted by the red solid line, the leptophilic
+   induced by CRs is denoted by the red solid line, the leptophilic
    models by green lines, and the DM $\Kp$ benchmark model by blue
@@
 
-\del{NEED TO REWRITE, JUMPING BACK AND FORTH BETWEEN PANELS} In order
-to learn about the spatial distribution of the DM flux in various
-clusters for different DM models and associated gamma-ray components,
-we show in the left panel of Fig.~\ref{fig:SB_clu_nosub} the
-brightness profiles for the smooth DM distribution for the same four
-representative clusters that was shown previously in
-Fig.~\ref{fig:SB_clu}. In addition, we show the spatial dependence of
-the individual gamma-ray components for the Fornax cluster in the
-right panel. We find that the spatial distribution of the DM emission
-at 1~GeV in the outer parts of the all clusters have the same
-shape. The shape trace the underlying density slope of $-3$, which is
-expected for IC upscattered CMB photons. This picture is confirmed by
-the components study in the right panel that show the neglible
+In order to learn about the spatial distribution of the DM flux in
+various clusters for different DM models and associated gamma-ray
+components, we show in the left panel of Fig.~\ref{fig:SB_clu_nosub}
+the brightness profiles for the smooth DM distribution for the same
+four representative clusters that was shown previously in
+Fig.~\ref{fig:SB_clu}.  We find that the surface brightness,
+$S_\gamma$ of the DM emission above 1~GeV in the outer parts of all
+clusters have the same shape. In addition, we show the spatial
+dependence of the individual gamma-ray components for the Fornax
+cluster in the right panel. We see that in the BM model, the emission
+is dominated by the continuum emission. In the LP model, the emission
+at intermediate and large radii is dominated by IC-upscattered CMB
+photons while at small radii, IC-upscattered SD photons dominate the
+emission. The fact that the sum of both IC components resembles the
+profile of the BM model is not surprising: in this energy range, all
+the energy of the annihilation is imparted on leptons which radiate
+all the energy away and the sum of the IC components represents a
+calorimeter for these radiating leptons.  We note that the surface
+brightness due to SD upscattered photons dominates over larger central
+regions for energies $E_\gamma>1$~GeV (cf. Fig.~\ref{fig:IR_comp}).
+Furthermore, since there is no enhancement from substructures, the
+overall mass normalization of the LP DM model has a marginally
+negative trend $\sim\mvir^{-0.06}$. Hence, we only see a very small
+difference in outer parts of the different clusters from these type of
+models. The DM BM models scale as $S_\gamma\sim\mvir^{0.27}$,
+hence more massive clusters show a slightly higher surface
+brightness. Finally, we note that the flux from DM without
+substructures is dominated by the CRp induced emission for all
+clusters.
+
+\del{The shape trace the underlying density slope of $-3$, which is
+  expected for IC upscattered CMB photons. This picture is confirmed
+  by the components study in the right panel that show the negligible
   contribution at this energy from the IC upscattered SD photons that
   follow a steeper distribution in the outer parts because of the
-decreasing energy density of SD photons with radius. Since the surface
-brightness from BM models are dominated by the continuum emission at
-each radial bin in all clusters, we find that the total DM BM emission
-follows the projected density profile over the entire clusters. In
-addition, the sum of the IC upscattered photons for the LP model
-approximately trace the same distribution, although with the exception
-in the core regime where we find a transition from centrally
-dominating IC SD light to the IC CMB light. The transition is due to
-the IC upscattered CMB photons that trace the smooth profile in the
-core and outer parts of the cluster, while the electron and positron
-population suffers from efficient cooling on light from SD in the
-center which flatten the IC CMB profile. Conversely trace the LP IC
-emission from SD photons a steeper distribution in the center that
-follows the projected density profile. This is explained by the SD
-dominated cooling that cancels the spatial dependence from the SD
-source function. \del{In the left panel we also find some variation in
-  the profiles for the different clusters in the central
-  parts. Especially in the Fornax cluster, where we find a factor two
-  larger flux compared to the other clusters. This is due to more
-  efficient SD cooling of the dominating IC upscattered CMB photons in
-  Fornax; a low X-ray luminous cluster has a low energy density in
-  starlight and dust in our analytic SD model.} It should be
-noted that the surface brightness due to SD upscattered photons is
-suppressed at the relative low energy of 1~GeV. Furthermore, since
-there is no enhancement from substructures, the overall mass
-normalization of the LP DM model has a marginally negative trend
-$\sim\mvir^{-0.06}$. Hence, we only see a very small difference in
-outer parts of the different clusters from these type of models. The
-DM BM models have a normalization of $\sim\mvir^{0.27}$, hence more
-massive clusters show a slightly higher surface brightness. Finally,
-we note that the flux from DM without substructures is dominated by
-the CRp induced emission for all clusters.
+  decreasing energy density of SD photons with radius. Since the
+  surface brightness from BM models are dominated by the continuum
+  emission at each radial bin in all clusters, we find that the total
+  DM BM emission follows the projected density profile over the entire
+  clusters. In addition, the sum of the IC upscattered photons for the
+  LP model approximately trace the same distribution, although with
+  the exception in the core regime where we find a transition from
+  centrally dominating IC SD light to the IC CMB light. The transition
+  is due to the IC upscattered CMB photons that trace the smooth
+  profile in the core and outer parts of the cluster, while the
+  electron and positron population suffers from efficient cooling on
+  light from SD in the center which flatten the IC CMB
+  profile. Conversely trace the LP IC emission from SD photons a
+  steeper distribution in the center that follows the projected
+  density profile. This is explained by the SD dominated cooling that
+  cancels the spatial dependence from the SD source function.
+%
+  In the left panel we also find some variation in the profiles for
+  the different clusters in the central parts. Especially in the
+  Fornax cluster, where we find a factor two larger flux compared to
+  the other clusters. This is due to more efficient SD cooling of the
+  dominating IC upscattered CMB photons in Fornax; a low X-ray
+  luminous cluster has a low energy density in starlight and dust in
+  our analytic SD model.}
 
@@
 the BM models were mainly dominated by the continuum emission. These
-high energies are reachable by both Fermi-LAT and Cherenkov
-telescopes, thus important observationally. We therefore show in
-Fig.~\ref{fig:SB_IACTs} the surface brightness above $100\,$~GeV for a
-realistic PSF of $0.1\deg$ where we include the boost from
-substructures. We investigate two clusters with an expected high DM
-signal; the relative small Fornax cluster and the massive close by
-Virgo cluster. Both clusters show a very flat brightness profile
-within about 10\% of $\rvir$, due to both the effect from
-substructures and the smoothening over the PSF. The CRp induced
-emission also show a smoothing in the central parts due to the PSF. In
-the outer part of the Fornax cluster the CRp flux is suppressed
-compared to the substructure boosted DM flux, where the LP model give
-rise to a gamma-ray flux that is more than three orders of magnitude
-larger. Although, it should be noted that there are large
-uncertainties in the gas density profile which we use to estimate the
-CRp induced gamma-ray surface brightness (see
-Fig.~\ref{fig:dens_fornax} for more details).
+high energies are observationally important for both Fermi-LAT and
+Cherenkov telescopes. In Fig.~\ref{fig:SB_IACTs}, we thus show the
+surface brightness above $100\,$~GeV for a realistic PSF of $0.1\deg$
+where we include the boost from substructures. We investigate two
+clusters with an expected high DM signal; the Fornax and Virgo
+cluster. Both clusters show a very flat brightness profile
+$r<0.1\rvir$, due to both the effect from substructures and the
+smoothing over the PSF. The CRp induced emission also show a
+smoothing in the central parts due to the PSF. In the outer part of
+the Fornax cluster the CRp flux is suppressed compared to the DM flux
+boosted by substructures, where the LP model gives rise to a gamma-ray
+flux that is more than three orders of magnitude larger. Although, it
+should be noted that there are large uncertainties in the gas density
+profile which we use to estimate the CRp induced gamma-ray surface
+brightness (see Fig.~\ref{fig:dens_fornax} for more details).
 
@@
   the Fornax cluster and right panel the Virgo cluster. The gamma-ray
-  emission is derived for the following components; CRps (red solid),
+  emission is derived for the following components; CRs (red solid),
   continuum emission from the DM $\Kp$ benchmark model (blue
@@
  \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.CR.eps}
- \caption{\it Comparison of the gamma-ray flux induced by CRps for the
+ \caption{\it Comparison of the gamma-ray flux induced by CRs for the
    106 clusters included in the extended HIFLUGCS catalogue.  The CR

### 2011-05-11 paper.tex
text updated

@@
 
-2. The dwarf spheroidal galaxies orbiting the Milky Way, like Segue-1,
-Ursa Minor, Draco, Sagittarius, Sculptor, Carina or Willman-1
+2. The dwarf spheroidal galaxies orbiting the Milky Way (MW), like
+Segue-1, Ursa Minor, Draco, Sagittarius, Sculptor, Carina or Willman-1
 \cite{2009JCAP...01..016B,2010ApJ...720.1174A,2010JCAP...01..031S,2010JCAP...01..031S}. The
@@
 
-For a satellite dwarf galaxy, however, once it is accreted by the
-Milky Way, the outer regions are severely affected by tidal
-stripping. The longer a satellite has been part of our Galaxy, and the
-closer it comes to the center during its pericentral passage, the more
-material is removed \cite{2004MNRAS.355..819G}.
+For a satellite dwarf galaxy, however, once it is accreted by the MW,
+the outer regions are severely affected by tidal stripping. The longer
+a satellite has been part of our Galaxy, and the closer it comes to
+the center during its pericentral passage, the more material is
+removed \cite{2004MNRAS.355..819G}.
 
@@
 hadronic CR model and find that Virgo has the highest gamma-ray flux
-from annihilating DM. If the boost from Sommerfeld enhancement is
-small, however, then the gamma-ray emission induced by CRs is
+from annihilating DM. If the boost from Sommerfeld enhancement (SFE)
+is small, however, then the gamma-ray emission induced by CRs is
 dominating most clusters with the exception of a few clusters where
-Fornax had the highest flux from DM. In particular, we find Fornax
-($\mvir=10^{14}\,\msun$) and Virgo ($\mvir=2.1\times10^{14}\,\msun$)
-\del{\cite{}} as the prime targets for DM observations, Perseus
-($\mvir=7.7\times10^{14}\,\msun$) for CR induced emission and we
-additionally decide in favor of the well studied cluster Coma
-($\mvir=1.4\times10^{15}\,\msun$) for comparison. While studying these
-four clusters in great detail, we complement the analysis by
-calculating the expected gamma-ray fluxes of a nearby X-ray flux
-complete sample of galaxy clusters from the Rosat all-sky survey
-(extended HIghest X-ray FLUx Galaxy Cluster Sample, HIFLUGCS,
+Fornax had the highest flux from DM. In particular, we find Fornax and
+Virgo \del{\cite{}} as the prime targets for DM observations, Perseus
+for CR induced emission and we additionally decide in favor of the
+well studied cluster Coma for comparison. While studying these four
+clusters in great detail, we complement the analysis by calculating
+the expected gamma-ray fluxes of a nearby X-ray flux complete sample
+of galaxy clusters from the Rosat all-sky survey (extended HIghest
+X-ray FLUx Galaxy Cluster Sample, HIFLUGCS,
 \citealt{2002ApJ...567..716R}).\footnote{Note that we have added the
@@
   \caption{Gamma-ray flux from various clusters.}
-\begin{tabular}{c  c c c  c  c c c}
+\begin{tabular}{c  c c c  c  c c c c c c}
 \hline
@@
 \multicolumn{3}{c}{$F_{\gamma}(>100\,\rmn{MeV})$ $[\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}]$:} & &
-\multicolumn{3}{c}{$F_{\gamma}(>100\,\rmn{GeV})$ $[\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}]$:} \\
-         & DM-LP $^{(1)}$ & DM-BM-$\Kp$ $^{(2)}$ & CR-$\pi^0$ $^{(3)}$ 
-         & & DM-LP $^{(1)}$ & DM-BM-$\Kp$ $^{(2)}$ & CR-$\pi^0$ $^{(3)}$ \\
+\multicolumn{3}{c}{$F_{\gamma}(>100\,\rmn{GeV})$ $[\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}]$:} & 
+$\mvir$ & $\B_\rmn{sfe} $$^{(1)}$ &  $\B_\rmn{sub} $$^{(2)}$ \\
+         & DM-LP $^{(3)}$ & DM-BM-$\Kp$ $^{(4)}$ & CR-$\pi^0$ $^{(5)}$ 
+         & & DM-LP $^{(3)}$ & DM-BM-$\Kp$ $^{(4)}$ & CR-$\pi^0$ $^{(5)}$ & $[10^{14}\,\msun]$ &&  \\
  \hline
  Fornax               & $4.8\times10^{-8}$  & $1.3\times10^{-10}$ & $2.2\times10^{-10}$ 
-& \,\,\,\,\, & $5.6\times10^{-12}$  & $3.6\times10^{-13}$ & $8.3\times10^{-14}$ \\
+ & \,\,\,\,\,         & $5.6\times10^{-12}$ & $3.6\times10^{-13}$ & $8.3\times10^{-14}$ 
+ & $1.0$  & $106$ & $730$  \\
  Coma                 & $1.3\times10^{-8}$  & $8.3\times10^{-11}$ & $4.0\times10^{-9}$  
-& \,\,\,\,\, & $1.4\times10^{-12}$  & $2.3\times10^{-13}$ & $1.5\times10^{-12}$ \\
+ & \,\,\,\,\,         & $1.4\times10^{-12}$ & $2.3\times10^{-13}$ & $1.5\times10^{-12}$ 
+ & $13.8$ & $44$  & $1310$ \\
  Virgo                & $1.2\times10^{-7}$  & $4.0\times10^{-10}$ & $8.7\times10^{-9}$  
-& \,\,\,\,\, & $1.3\times10^{-11}$  & $1.1\times10^{-12}$ & $3.2\times10^{-12}$ \\
+ & \,\,\,\,\,         & $1.3\times10^{-11}$ & $1.1\times10^{-12}$ & $3.2\times10^{-12}$ 
+ & $2.1$  & $83$  & $870$  \\
  Perseus \,\,\,\,\,\, & $1.4\times10^{-8}$  & $7.1\times10^{-11}$ & $1.4\times10^{-8}$  
-& \,\,\,\,\, & $1.4\times10^{-12}$  & $2.0\times10^{-13}$ & $5.2\times10^{-12}$ \\
+ & \,\,\,\,\,         & $1.4\times10^{-12}$ & $2.0\times10^{-13}$ & $5.2\times10^{-12}$ 
+ & $7.71$ & $54$  & $1280$ \\
 \hline
@@
   Notes: \\
-  (1) The total gamma-ray flux from leptophilic (LP) DM where both the
+  (1) The boost due to Sommerfeld enhancement.\\
+  (2) The boost from substructures have been intergated out to $\rvir$.\\
+  (3) The total gamma-ray flux from leptophilic (LP) DM where both the
   boost from substructures and Sommerfeld enhancement are
@@
   Fermi (see the following sections for detail).\\
- (2) The total gamma-ray flux from the supersymmetric $\Kp$ benchmark (BM) 
+  (4) The total gamma-ray flux from the supersymmetric $\Kp$ benchmark (BM) 
   model where the boost from substructures is included.\\
- (3) Gamma-ray flux induced by CR protons.
+  (5) Gamma-ray flux induced by CR protons.
  \label{tab:flux_tab}
@@
 center (for a recent possible indication of a signal, see
-\cite{Hooper:2010mq}), the dwarf galaxies surrounding the Milky Way
+\cite{Hooper:2010mq}), the dwarf galaxies surrounding the MW
 \cite{Strigari:2006rd,Essig:2009jx,2010JCAP...01..031S}, galaxy
@@
 potentially very important effect which may explain the large boost
-had been found a few years earlier, namely the Sommerfeld
-enhancement. This effect, was computed for electromagnetism by Arnold
+had been found a few years earlier, namely the Sommerfeld enhancement
+(SFE). This effect, was computed for electromagnetism by Arnold
 Sommerfeld many years ago \cite{sommerfeld} and recently rediscovered
@@
 system (such as a galaxy cluster) with large velocity dispersion
-$v_{\rm cl}$ the Sommerfeld enhancement will be smaller than the one
-expected in a single galaxy such as the Milky Way, roughly by a factor
-$v_{\rm MW}/v_{\rm cl}$.
-
-As leptophilic models, apart from being slightly contrived from the
+$v_{\rm cl}$ the SFE will be smaller than the one expected in a single
+galaxy such as the MW, roughly by a factor $v_{\rm MW}/v_{\rm
+  cl}$.
+
+As LP models, apart from being slightly contrived from the
 particle physics point of view, are also rather limited by several
@@
   ratio of ($1/3,\,1/3,\,1/3$) into
-  ($\mu^+/\mu^-,\,\e^+/\e^-,\,\pi^+/\pi^-$).}. The Sommerfeld boost
-$S=\B_\sfe(\sigv=200\,km/s)\approx 300$ for a Milky Way halo in our LP
-model, which we appropriately scale down for cluster halos, using
-\del{To connect easily to our previous work
-  \cite{2009PhRvL.103r1302P}, we choose as our benchmark LP model one
-  with mass $1.6$~TeV and Sommerfeld boost
-  $S=\B_\sfe(\sigv=200\,km/s)\approx 300$ for a Milky Way halo and
-  scale this appropriately down for cluster halos, using} {\bf Anders:
-  insert Sommerfeld boost formula as a function of halo mass, done}
+  ($\mu^+/\mu^-,\,\e^+/\e^-,\,\pi^+/\pi^-$).}. The SFE
+$S=\B_\sfe(\sigv=200\,km/s)\approx 300$ for a MW halo in our LP model,
+which we appropriately scale down for cluster halos, using \del{To
+  connect easily to our previous work \cite{2009PhRvL.103r1302P}, we
+  choose as our benchmark LP model one with mass $1.6$~TeV and
+  Sommerfeld boost $S=\B_\sfe(\sigv=200\,km/s)\approx 300$ for a MW
+  halo and scale this appropriately down for cluster halos, using}
 \begin{equation}
@@
 lightest neutralino, is stable. The stability is assured in viable
-SUSY models due to a discrete symmetry, $R$-parity. This symmetry is
-needed from the particle physics point of view to avoid fast proton
-decay, and automatically makes the lightest supersymmetric particle
-stable, and therefore a good candidate for DM. In addition, as the
-coupling to ordinary matter is given by gauge couplings, the
+supersymmetric models due to a discrete symmetry, $R$-parity. This
+symmetry is needed from the particle physics point of view to avoid
+fast proton decay, and automatically makes the lightest supersymmetric
+particle stable, and therefore a good candidate for DM. In addition,
+as the coupling to ordinary matter is given by gauge couplings, the
 neutralino is automatically a WIMP candidate. Unfortunately, the
@@
 Model (the MSSM), $\tilde H_1^0$ and $\tilde H_2^0$, with mixing
-coefficients which depend on the SUSY breaking parameters
+coefficients which depend on the supersymmetric breaking parameters
 \cite{1984NuPhB.238..453E}. The parameter space is very large, too
@@
 \end{equation}
-the gaugino fraction of a given neutralino is $|a_1|^2+|a_2|^2$ whereas $|a_3|^2+|a_4|^2$ is the higgsino fraction.
+the gaugino fraction of a given neutralino is $|a_1|^2+|a_2|^2$
+whereas $|a_3|^2+|a_4|^2$ is the higgsino fraction.
 
@@
 \label{sect:subst}
-High-resolution DM only simulations of Milky Way (MW) type halos find
-substantial amount of substructures in the periphery of DM halos,
-while the substructures in the center suffer from dynamical friction
-and tidal effects depleting their central number densities. Since the
-DM annihilation rate depends on the density squared, the resulting
-flux from substructures is boosted compared to the smooth density
+High-resolution DM only simulations of MW type halos find substantial
+amount of substructures in the periphery of DM halos, while the
+substructures in the center suffer from dynamical friction and tidal
+effects depleting their central number densities. Since the DM
+annihilation rate depends on the density squared, the resulting flux
+from substructures is boosted compared to the smooth density
 distribution. Recent high resolution simulations suggest a flux
@@
 density $u_\sd(\eph,r)$ is given in the Appendix,
-Eq.~(\ref{eq:U_SD}). We model the CMB photon spectrum as a photon gas
-that is isotropically distributed and follows a black body spectrum
-with the temperature $T=2.73\,$~K:
+Eq.~(\ref{eq:u_SD_er}). We model the CMB photon spectrum as a photon
+gas that is isotropically distributed and follows a black body
+spectrum with the temperature $T=2.73\,$~K:
 \begin{equation}
@@
 positrons we model the spectral distribution with $\frac{\dd
-  N_\e^f}{\dd \ee}= 2\delta(\ee-m_\chi c^2)$. We use DarkSUSY to
+  N_\e^f}{\dd \ee}= 2\delta(\ee-m_\chi c^2)$. We use {\sc DarkSUSY} to
 compute both the spectra when neutralinos annihilate directly into a
-$\mu^+$ and $\mu^-$ in the leptophilic model as well as in the four BM
-models where a fraction of the annihilating neutralinos is converted
-into electrons and positrons (see Sect.~\ref{sect:PF} and
+$\mu^+$ and $\mu^-$ in the LP model as well as in the four BM models
+where a fraction of the annihilating neutralinos is converted into
+electrons and positrons (see Sect.~\ref{sect:PF} and
 Fig.~\ref{fig:q_DM} for further details).
@@
  \frac{1}{b(\ee, r)} \int_{\ee}^{\mx c^2} \dd \ee' \, 
-  Q(\ee', r),
+  q_\e(\ee', r),
 \label{eq:nds}\\
@@
 flux frozen magnetic fields. (3) IC losses on starlight and dust with
-an energy density $u_\sd(r)$ given by Eq.~(\ref{eq:U_SD}), which we
+an energy density $u_\sd(r)$ given by Eq.~(\ref{eq:u_SD_r}), which we
 derive in the following.
@@
 Galaxy to model the emission from clusters. We then normalize the two
-spectral components -- far IR dust and starlight at wavelengths ranging
-from the near IR to UV -- individually by using stacked cluster data and employ a
-measured mass-to-starlight luminosity scaling relation derived from
-observations of the brightest cluster galaxy
-\cite{2010ApJ...713.1037H}.
+spectral components -- far IR dust and starlight at wavelengths
+ranging from the near IR to UV -- individually by using stacked
+cluster data and employ a measured mass-to-starlight luminosity
+scaling relation derived from observations of the brightest cluster
+galaxy \cite{2010ApJ...713.1037H}.
 
@@
 \begin{eqnarray}
+\label{eq:SD_overlap}
 f_\rmn{IC-ol} = \frac{N_\rmn{gal} V_\rmn{gal} f_\rmn{light}}{V_\rmn{clu}}
@@
 We focus in this section on the spectral distribution of gamma-rays
-from clusters.  In the leptophilic model, DM annihilation radiation
-includes final state radiation and gives rise to substantial amounts of
+from clusters.  In the LP model, DM annihilation radiation includes
+final state radiation and gives rise to substantial amounts of
 electrons and positrons that IC upscatter background radiation fields
@@
 energy interval set by Fermi-LAT by about a factor 100. This strongly
-constrains the boost from both substructures and the Sommerfeld
-enhancement. Additionally, these constraints might improve with future
-more sensitive Cherenkov telescopes such as CTA. However, considering
-that an indirect detection of DM in clusters relies on the boost from
+constrains the boost from both substructures and the
+SFE. Additionally, these constraints might improve with future more
+sensitive Cherenkov telescopes such as CTA. However, considering that
+an indirect detection of DM in clusters relies on the boost from
 substructures whose main contribution comes from the periphery, we
@@
    models. We show the emission from; CRp induced emission (red
-   solid), leptophilic models (LP) that include both final state
+   solid), leptophilic (LP) models that include both final state
    radiation and IC upscattered CMB, dust and starlight (green
@@
   (lower right). We show CRp induced emission (red solid), leptophilic
-  models (LP) include both final state radiation and IC upscattered
+  (LP) models include both final state radiation and IC upscattered
   CMB, dust and starlight (green dash-dotted), and benchmark $\Kp$
@@
 First we focus on gamma-ray flux-cluster mass scaling relations for DM
-annihilation and CR induced emission in Fig.~\ref{fig:lum_mass_scaling}.  The
-mass scaling of the substructure boost steepens the intrinsically shallower DM
-annihilation relation of benchmark models (Eq.~\ref{eq:BM_scaling}) while
-this steepening is in fact over-compensated by the inverse mass scaling of the
-Sommerfeld boost in leptophilic models that prefers smaller halos with a larger
-ratio of $c/v_\mathrm{circ}$ (Eq.~\ref{eq:LP_scaling}). In contrast, the
-CR scaling relation is considerably steeper as shown by reference
+annihilation and CR induced emission in
+Fig.~\ref{fig:lum_mass_scaling}.  The mass scaling of the substructure
+boost steepens the intrinsically shallower DM annihilation relation of
+benchmark models (Eq.~\ref{eq:BM_scaling}) while this steepening is in
+fact over-compensated by the inverse mass scaling of the Sommerfeld
+boost in LP models that prefers smaller halos with a larger ratio of
+$c/v_\mathrm{circ}$ (Eq.~\ref{eq:LP_scaling}). In contrast, the CR
+scaling relation is considerably steeper as shown by reference
 \cite{2010MNRAS.409..449P}:
 \begin{eqnarray}
-L_{\gamma}(>100\,\mev) = 3.1\times10^{45}
+L_{\gamma}(>100\,\mev) = 1.8\times10^{45}
 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.46}\mbox{erg~s}^{-1}\nonumber\\
-L_{\gamma}(>10\,\gev)  = 2.2\times10^{43}
+L_{\gamma}(>10\,\gev)  = 1.4\times10^{43}
 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.34}\mbox{erg~s}^{-1}\,.\nonumber\\
 \end{eqnarray}
-Note that the CR luminosity scaling relations include the IC gamma-ray
-contribution from shock accelerated electrons as well as secondary
-electrons created through CRp-proton interactions. The gamma-ray flux
-from the electrons is, however, dominated by the decaying $\pi^0$ and
-only show up as a small flattening of the scaling relation at energies
-around $100\,\gev$. The steeper mass scaling of the CR compared to the
-DM implies already a general strategy to minimize the CR-induced
-foreground for DM annihilation and argues for very nearby groups. We
-note that these simulations do not include AGN feedback that is
-thought to furthermore reduce the baryon fraction in groups relative
-to that in clusters \cite{2008ApJ...687L..53P}. The resulting smaller
-target density for hadronic CR interactions will furthermore steepen
-the $L_\gamma-M$ relation of CR induced emission, making the case for
-groups even stronger.
+Note that the CR luminosity scaling relations \footnote{The scaling
+  relations show the flux inside $\rvir$ and do not include the
+  contribution from galaxies. Also note that in this paper the scaling
+  relations are normalized with $10^{15}/h_{70}\,\msun$, in contrast
+  to $10^{15}/h\,\msun$ that was used in \cite{2010MNRAS.409..449P}.}
+include the IC gamma-ray contribution from shock accelerated electrons
+as well as secondary electrons created through CRp-proton
+interactions. The gamma-ray flux from the electrons is, however,
+dominated by the decaying $\pi^0$ and only show up as a small
+flattening of the scaling relation at energies around $100\,\gev$. The
+steeper mass scaling of the CR compared to the DM implies already a
+general strategy to minimize the CR-induced foreground for DM
+annihilation and argues for very nearby groups. We note that these
+simulations do not include AGN feedback that is thought to furthermore
+reduce the baryon fraction in groups relative to that in clusters
+\cite{2008ApJ...687L..53P}. The resulting smaller target density for
+hadronic CR interactions will furthermore steepen the $L_\gamma-M$
+relation of CR induced emission, making the case for groups even
+stronger.
 
@@
 Figure~\ref{fig14} compares Fermi upper limits on the gamma-ray flux
-with predictions of DM annihilation fluxes in the leptophilic and
-benchmark models.  To obtain the gamma-ray fluxes, we scale the virial
-mass of clusters in the extended HIFLUGCS catalogue
-\cite{2002ApJ...567..716R} with our scaling relations of
-Eqs.~(\ref{eq:BM_scaling}) and (\ref{eq:LP_scaling}). In those, we
-assume a boost factor due to substructures that has a constant
-contribution per decade in substructure mass and has a mass spectrum
-extending down to Earth masses for our LP and BM DM annihilation
-models. In the LP models we additionally assume a cluster-mass
-dependent bost due to SFE. Fermi limits rule out the leptophilic
-models in their present form with the mentioned assumptions in 14
-clusters, and limit the boost from Sommerfeld enhancement to less than
+with predictions of DM annihilation fluxes in the LP and benchmark
+models.  To obtain the gamma-ray fluxes, we scale the virial mass of
+clusters in the extended HIFLUGCS catalogue \cite{2002ApJ...567..716R}
+with our scaling relations of Eqs.~(\ref{eq:BM_scaling}) and
+(\ref{eq:LP_scaling}). In those, we assume a boost factor due to
+substructures that has a constant contribution per decade in
+substructure mass and has a mass spectrum extending down to Earth
+masses for our LP and BM DM annihilation models. In the LP models we
+additionally assume a cluster-mass dependent bost due to SFE. Fermi
+limits rule out the LP models in their present form with the mentioned
+assumptions in 14 clusters, and limit the boost from SFE to less than
 2 in Fornax. Assuming universality, this limits the Sommerfeld boost
@@
 emission in galaxy clusters. We consider benchmark and leptophilic
-models of supersymmetric dark matter (DM) as well as cosmic ray
+(LP) models of supersymmetric dark matter (DM) as well as cosmic ray
 induced pion decay which is thought to dominate the astrophysical
@@
 substructures dominates over the smooth component for halo masses
-$\mvir>10^3 \msun$  and contributes a constant
-luminosity for each decade in halo mass. The ratio of halo-to-minimum
-subhalo mass $\mvir/M_\mathrm{min}$ is maximized for the largest
-systems that had time to collapse and virialise since the Big Bang --
-galaxy clusters. The corresponding substructure boost can reach values
+$\mvir>10^3 \msun$ and contributes a constant luminosity for each
+decade in halo mass. The ratio of halo-to-minimum subhalo mass
+$\mvir/M_\mathrm{min}$ is maximized for the largest systems that had
+time to collapse and virialise since the Big Bang -- galaxy
+clusters. The corresponding substructure boost can reach values
 exceeding $10^3$ which should make nearby clusters the brightest DM
-annihilation sources after the Milky May center and hypothetical very
+annihilation sources after the MM center and hypothetical very
 close-by DM substructures. Since the number density of substructures
@@
 of 14 clusters/groups (the mentioned clusters as well as Virgo, Coma,
-Hydra, and Norma among others) considerably constrains leptophilic
-models for DM annihilation which were introduced to explain the
-increasing positron-to-lepton ratio beyond 10 GeV. Assuming that the
-minimum DM substructure mass extends down to an Earth mass, we limit
-the Sommerfeld enhancement factor in the Fornax galaxy cluster to be
-less than 2. This corresponds to a value in the Milky Way of less than
+Hydra, and Norma among others) considerably constrains LP models for
+DM annihilation which were introduced to explain the increasing
+positron-to-lepton ratio beyond 10 GeV. Assuming that the minimum DM
+substructure mass extends down to an Earth mass, we limit the
+Sommerfeld enhancement factor in the Fornax galaxy cluster to be less
+than 2. This corresponds to a value in the Milky Way (MW) of less than
 5 due to the larger Sommerfeld boost factor in smaller mass halos
@@
 section (while assuming universality of the DM model). This would rule
-out leptophilic models in their current form based on the
-non-observation of gamma-rays in any of the fore-mentioned
-clusters/groups. Alternatively, assuming the leptophilic models to be
-correct, we limit the minimum substructure mass to $>100~\msun$ in
-Fornax.
+out LP models in their current form based on the non-observation of
+gamma-rays in any of the fore-mentioned
+clusters/groups. Alternatively, assuming the LP models to be correct,
+we limit the minimum substructure mass to $>100~\msun$ in Fornax.
 
@@
 continuums emission contribution, we keep it separate as it dominates
-the very high-energy tail of the gamma-ray spectrum in leptophilic
-models while there the continuums emission is negligibly low.
+the very high-energy tail of the gamma-ray spectrum in LP models while
+there the continuums emission is negligibly low.
 
@@
 from infra red to optical wavelengths. To this end, we construct a
-rather simple analytic model for the spatial and spectral
-distribution of dust and starlight in clusters which can be used for
-the annihilation emission in galaxies with a different spatial
-profile.  We find that in benchmark models, the continuum emission
-dominates over the IC emission of any available radiation field. In
-the leptophilic models, where the continuum emission is low, the IC
-up-scattering of the CMB dominates below 60 GeV. For large clusters,
-the final state radiation takes then over for energies up to the
-cutoff at $m_\chi c^2 \sim 1$~TeV. In small clusters, there is a
-window around $E_\gamma \sim 100~\mathrm{GeV}$ where the IC
-up-scattering of the dust emission dominates over the CMB IC emission
-and the final state radiation. The IC emission of starlight remains
-always subdominant.  We stress, that the inclusion of the dust and
-starlight radiation fields are negligible in the cooling function for
-the leptons.  The main reason why the IC emission from starlight and
-dust remains subdominant is the small overlap of this component with
-the peripherally peaked substructure mass density profiles. If for
-some reason, DM has less substructure, the relative importance of this
-IC component increases considerably.
+rather simple analytic model for the spatial and spectral distribution
+of dust and starlight in clusters which can be used for the
+annihilation emission in galaxies with a different spatial profile.
+We find that in benchmark models, the continuum emission dominates
+over the IC emission of any available radiation field. In the LP
+models, where the continuum emission is low, the IC up-scattering of
+the CMB dominates below 60 GeV. For large clusters, the final state
+radiation takes then over for energies up to the cutoff at $m_\chi c^2
+\sim 1$~TeV. In small clusters, there is a window around $E_\gamma
+\sim 100~\mathrm{GeV}$ where the IC up-scattering of the dust emission
+dominates over the CMB IC emission and the final state radiation. The
+IC emission of starlight remains always subdominant.  We stress, that
+the inclusion of the dust and starlight radiation fields are
+negligible in the cooling function for the leptons.  The main reason
+why the IC emission from starlight and dust remains subdominant is the
+small overlap of this component with the peripherally peaked
+substructure mass density profiles. If for some reason, DM has less
+substructure, the relative importance of this IC component increases
+considerably.
 
@@
 clusters/groups but Fornax. We conclude that it will be possible to
-rule out the leptophilic model with six years of Fermi data and start
-to constrain some benchmark DM models. Hence this should nicely
+rule out the LP model with six years of Fermi data and start to
+constrain some benchmark DM models. Hence this should nicely
 complement direct and accelerator searches for the nature of DM.
@@
 u_\sd(\eph, r) &=& j(r)\,u_\sd(\eph)\,,
-\label{eq:u_SD_re}
+\label{eq:u_SD_er}
 \end{eqnarray}
@@
 cluster observations by Sloan in the $r$ and $i$-band that trace the
-stars. For simplicity we assume that the dust trace the stars in the
-clusters {\bf WHY IS THIS A GOOD APPROXIMATION}. The stacked surface
-brightness profiles in \cite{2005MNRAS.358..949Z} are measured at
-redshift $z \sim 0.25$ with an average mass of the clusters of
+stars and for simplicity we assume that the dust trace the stars in
+the clusters \del{\bf WHY IS THIS A GOOD APPROXIMATION}. The stacked
+surface brightness profiles in \cite{2005MNRAS.358..949Z} are measured
+at redshift $z \sim 0.25$ with an average mass of the clusters of
 $4.0\times10^{13}\,\msun$. The profiles are build up out of three
@@
    Survey (SDSS) at the redshift $z \sim 0.25$
-   \cite{2005MNRAS.358..949Z}. {\bf Anders, this is not clear: The
-     brightness profiles have been weighted with the $\rvir$
-     normalized area inside radius $r$, and trace the radial
-     dependence of the luminosity from stars and galaxies. REMOVE,
-     OLD, ADDED SENTENCE IN END} The crosses show the total observed
+   \cite{2005MNRAS.358..949Z}. The crosses show the total observed
    starlight including the diffuse intracluster (ICL), the galaxies,
@@
 \begin{eqnarray}
-\label{eq:U_SD_r}
+\label{eq:u_SD_r}
 u_\sd(r) &=& \int \dd \eph \frac{\dd^2 N_\ph}{\dd \eph \dd V}\,\eph
@@
 where we have used that specific energy density of the SD light given
-by Eq.~(\ref{eq:u_SD_re}). Note that we compare the energy density
+by Eq.~(\ref{eq:u_SD_er}). Note that we compare the energy density
 $u_\sd(r)$ to other radiation background fields in
@@
 \section{Source functions of different DM models}
-{\bf Anders: add your fit functions for the 4 BM and the LP models. DONE}
-
 We use {\sc DarkSUSY} to derive the spectra for the continuum emision
@@
    from deprojected Chandra and Rosat X-ray surface brightness
-   observations \cite{2002ApJ...565..883P} {\bf Anders: CITE, DONE}. The
-   total hybrid profile shown by the red solid line represent the best
-   fit to the data, where the fitted individual density components are
-   shown by the black dotted lines. The blue solid line shows the
-   single beta density profile inferred from the HIFLUGCS
-   catalogue. Due to insufficient sensitivity of the data to the outer
-   cluster part, we use the outer slope from the HIFLUGCS catalogue
-   that is very similar to that of the Coma cluster.}
+   observations \cite{2002ApJ...565..883P}. The total hybrid profile
+   shown by the red solid line represent the best fit to the data,
+   where the fitted individual density components are shown by the
+   black dotted lines. The blue solid line shows the single beta
+   density profile inferred from the HIFLUGCS catalogue. Due to
+   insufficient sensitivity of the data to the outer cluster part, we
+   use the outer slope from the HIFLUGCS catalogue that is very
+   similar to that of the Coma cluster.}
  \label{fig:dens_fornax}
@@
 \section{Flux tables for the HIFLUGCS catalouge}
+TO BE WRITTEN
 

### 2011-05-12 paper.tex
updated with lars version

@@
   from a realistic spatial and spectral distribution of dust and
-  stellar light.  After the galactic center, which hosts many
-  astrophysical sources, galaxy clusters are the best known target
-  class to detect DM annihilation. We predict Virgo and Fornax to be
-  the brightest DM sources and find a particularly low CR induced
+  stellar light. We predict the Virgo and Fornax clusters to be the
+  brightest DM sources and find a particularly low CR induced
   background for Fornax. For a given minimum substructure mass as
@@
   this flux with imaging air Cherenkov telescopes since their
-  sensitivity drops linearly with radius and they typically encounter
-  have $5-10$ linear resolution elements across a cluster; the
-  gamma-ray satellite Fermi is better suited. Assuming cold dark
-  matter with a substructure mass distribution down to an Earth mass
-  and using Fermi upper limits, we rule out the leptophilic models in
-  their present form in 14 clusters, and limit the boost from
-  Sommerfeld enhancement in Fornax to be less than 2 which corresponds
-  to a value in the Milky Way of less than 5. Alternatively, if the
-  Sommerfeld enhancement factor is realized in Nature, this would
-  imply a limiting substructure mass in Fornax of $\mlim >
-  10^2\,\msun$ which would be a hint for an unknown form of warm dark
-  matter. We find that Fermi three-year data will be able to constrain
-  the smallest mass of substructures for supersymmetric benchmark
-  models or alternatively constrain their cross sections for a given
-  substructure boost. Although the Perseus and Ophiuchus clusters are
-  expected to have the largest CR induced flux according to our
-  analytic model that is derived from cosmological hydrodynamical
-  cluster simulations, their central active galactic nucleus as well
-  as the Galactic foreground makes it hard to detect this flux in the
-  Fermi band. The next to best targets to detect the CR flux are
-  Virgo, Coma, and Norma -- the Fermi upper limits are closing in on
-  our predictions and will soon start to constrain the underlying CR
+  sensitivity drops linearly with radius and they typically have
+  $5-10$ linear resolution elements across a cluster; the gamma-ray
+  satellite Fermi is better suited. Assuming cold dark matter with a
+  substructure mass distribution down to an Earth mass and using Fermi
+  upper limits, we rule out the leptophilic models in their present
+  form in 14 clusters, and limit the boost from Sommerfeld enhancement
+  in Fornax to be less than 2 which corresponds to a value in the
+  Milky Way of less than 5. Alternatively, if the Sommerfeld
+  enhancement factor is realized in Nature, this would imply a
+  limiting substructure mass in Fornax of $\mlim > 10^2\,\msun$ which
+  would be a challenge for structure formation. We find that Fermi
+  three-year data will be able to constrain the smallest mass of
+  substructures for supersymmetric benchmark models or alternatively
+  constrain their cross sections for a given substructure boost. The
+  Fermi upper limits are closing in on our predictions for the CR flux
+  using an analytic model based on cosmological hydrodynamical cluster
+  simulations. We will soon start to constrain the underlying CR
   physics such as shock acceleration efficiencies or CR transport
@@
 relatively light DM particle contribution to the gamma-ray flux from
-the g.c. \cite{2010arXiv1010.2752H}, but other hypotheses seem to work
+the g.c. \cite{2010arXiv1010.2752H}, 
+but other hypotheses seem to work
 at least as well \cite{2010arXiv1012.5839B}.
@@
 noted in a previous Letter \cite{2009PhRvL.103r1302P} that there are
-certain advantages that work in Cavour of this possible target for
+certain advantages that work in favour of this possible target for
 gamma-ray detection of DM annihilation.  Galaxy clusters constitute
@@
 \cite{2009PhRvL.103r1302P}) that the ratio of gamma-ray luminosities
-from the smooth components is around 4, in Cavour of Virgo. In
+from the smooth components is around 4, in favour of Virgo. In
 addition, there may be a further enhancement due to substructure,
@@
 fractional mass larger than $10^{-5}$, which is 25 per cent higher
-than galactic haloes \footnote{All halo masses and length scales in
+than for galactic haloes.\footnote{All halo masses and length scales in
   this paper are scaled to the currently favored value of Hubble's
@@
   radius of a sphere enclosing a mean density that is 200 times the
-  critical density of the Universe $\rho_{\rmn{cr}}$.}.
+  critical density of the Universe $\rho_{\rmn{cr}}$.}
 
@@
 annihilation gamma-ray yield which could be observable with present
-and planned gamma-ray detectors. In Table~\ref{tab:flux_tab} we show
-the gamma-ray flux from four promising clusters with a high gamma-ray
-yield. We derive the emission from two different DM models and a
-hadronic CR model and find that Virgo has the highest gamma-ray flux
+and planned gamma-ray detectors. For convenience, we summarize already
+in Table~\ref{tab:flux_tab} our results for the gamma-ray flux from
+four promising clusters with a high gamma-ray yield. We will in the
+following derive the emission from two different DM models and a
+hadronic CR model to show that Virgo has the highest gamma-ray flux
 from annihilating DM. If the boost from Sommerfeld enhancement (SFE)
@@
 Fornax had the highest flux from DM. In particular, we find Fornax and
-Virgo \del{\cite{}} as the prime targets for DM observations, Perseus
-for CR induced emission and we additionally decide in favor of the
-well studied cluster Coma for comparison. While studying these four
-clusters in great detail, we complement the analysis by calculating
-the expected gamma-ray fluxes of a nearby X-ray flux complete sample
-of galaxy clusters from the Rosat all-sky survey (extended HIghest
-X-ray FLUx Galaxy Cluster Sample, HIFLUGCS,
+Virgo as the prime targets for DM observations, Perseus for CR induced
+emission and we additionally decide in favor of the well studied
+cluster Coma for comparison. While studying these four clusters in
+great detail, we complement the analysis by calculating the expected
+gamma-ray fluxes of a nearby X-ray flux complete sample of galaxy
+clusters from the Rosat all-sky survey (extended HIghest X-ray FLUx
+Galaxy Cluster Sample, HIFLUGCS,
 \citealt{2002ApJ...567..716R}).\footnote{Note that we have added the
@@
   Notes: \\
-  (1) The boost due to Sommerfeld enhancement.\\
-  (2) The boost from substructures have been intergated out to $\rvir$.\\
+  (1) The boost due to Sommerfeld enhancement. See Section II A 1.\\
+  (2) The boost from substructures have been integrated out to $\rvir$.\\
   (3) The total gamma-ray flux from leptophilic (LP) DM where both the
@@
   (4) The total gamma-ray flux from the supersymmetric $\Kp$ benchmark (BM) 
-  model where the boost from substructures is included.\\
-  (5) Gamma-ray flux induced by CR protons.
+  model where the boost from substructures is included. See Sections II A 2 and II B 3.\\
+  (5) Gamma-ray flux induced by CR protons. See Section V C. 
  \label{tab:flux_tab}
@@
 the mass of the DM particle (for the currently most sensitive search,
-see \cite{Aprile:2010um}). A characteristic of this method is that it
+see \cite{Aprile:2010um,Aprile:2011ts}). A characteristic of this method is that it
 basically only depends on the local DM density (which is rather well
 determined to be around $0.4$ GeV/cm$^3$) and the basic cross section
-for DM - nucleus scattering. A disadvantage is that it does benefit
+for DM - nucleus scattering. A disadvantage is that it does not benefit
 from the two enhancement mechanisms mentioned above, boost from
@@
 center (for a recent possible indication of a signal, see
-\cite{Hooper:2010mq}), the dwarf galaxies surrounding the MW
+\cite{2010arXiv1010.2752H}, however, see also \cite{2010arXiv1012.5839B}.), the dwarf galaxies surrounding the MW
 \cite{Strigari:2006rd,Essig:2009jx,2010JCAP...01..031S}, galaxy
@@
 pulsars or other supernova remnants (e.g.,
-\cite{Hooper:2008kg,Ahlers:2009ae}). In that case, DM would more
-likely be explained by the standard scenario of a WIMP, for example
-the thoroughly studied lightest supersymmetric neutralino (for
-reviews, see
+\cite{1995PhRvD..52.3265A,Hooper:2008kg,Ahlers:2009ae}). In that case,
+DM would more likely be explained by the standard scenario of a WIMP,
+for example the thoroughly studied lightest supersymmetric neutralino
+(for reviews, see
 \cite{Jungman:1995df,Bergstrom:2000pn,Bertone:2004pz}). We note that
@@
 \cite{2008Natur.456..362C}, although the bump seen there at 600 GeV
-has not been reproduced by other experiments) has caused intense
+has not been reproduced by other experiments) caused intense
 activity in the theoretical DM community. At first, there was
-skepticism whether such a large signal could be compatible with a
+scepticism whether such a large signal could be compatible with a
 WIMP. However, the possibility of an enhanced annihilation rate due to
@@
 something that explains their popularity besides the subjective
-statement that few more plausible models for DM have been put forward
+statement that few more well-motivated models for DM have been put forward
 so far.
@@
 different contexts (in particular in \cite{Bringmann:2008kj} giving
-predictions for the MAGIC experiment), and which give a good
+predictions for imaging air Cherenkov telescopes, like  MAGIC II and CTA), They give a good
 representation of models with high enough gamma-ray rates to become
@@
 and $J^*$. Despite the different particle masses and cross sections,
-the spectrum of the continuums emission shows a remarkably similar
+the spectrum of the continuum emission shows a remarkably similar
 shape which suggests that a simple rescaling of particle masses
@@
    annihilating into muons (black) without considering Sommerfeld
-   boosts. We use Eq.~(\ref{eq:bm_elec}) to fit the spectra of
-   electrons and positrons.}
+   boosts. We use Eq.~(\ref{eq:bm_elec}) and Eq.~(\ref{eq:lp_elec}) to
+   fit the spectra of electrons and positrons from BM and LP models,
+   respectively.}
  \label{fig:q_DM}
@@
   that these high values for boost factors are now consistently found
-  in high-resolution simulations of dark matter halos
+  in high-resolution simulations of dark matter halos \protect
   \cite{2008MNRAS.391.1685S, 2010ApJ...718..899A} after accounting for
@@
   flatter subhalo distribution compared to the smooth distribution and
-  errornously assuming an identical mass density distribution of
-  smooth DM and substructure biases the subhalo boost factor too low
+  errorously assuming an identical mass density distribution of smooth
+  DM and substructure biases the subhalo boost factor too low
   \cite{2008JPhCS.125a2008K, 2008JPhCS.125a2008K}.} We use a double
@@
   simulations self-consistently accounts for the radial dependence of
-  the substructure concentration \cite{2008MNRAS.391.1685S}.} the
-luminosity from the smooth component of substructures
+  the substructure concentration \protect \cite{2008MNRAS.391.1685S}.}
+the luminosity from the smooth component of substructures
 (i.e. substructures within substructures are not included) inside
@@
 halos. In the CDM universe, this is conventionally taken to be
-$10^{-6}\msun$ \cite{2001PhRvD..64h3507H, 2005JCAP...08..003G}. Note
-that potentially the power-law could flatten towards smaller mass
-scales although current simulations show no hits of such a behavior
-and since Einstein's gravity is a scale-free theory, we do not expect
-such a behavior on theoretical grounds either.  For DM halos more
-(less) massive than the MW we expect a larger (smaller) boost from
-substructures, simply because of the larger (smaller) mass range down
-to the minimum mass $M_\rmn{lim}$.
+$10^{-6}\msun$ \cite{2001PhRvD..64h3507H, 2005JCAP...08..003G} (see
+\cite{2009NJPh...11j5027B} for a discussion of the range expected in
+various DM models). Note that potentially the power-law could flatten
+towards smaller mass scales although current simulations show no hits
+of such a behavior and since Einstein's gravity is a scale-free
+theory, we do not expect such a behavior on theoretical grounds
+either.  For DM halos more (less) massive than the MW we expect a
+larger (smaller) boost from substructures, simply because of the
+larger (smaller) mass range down to the minimum mass $M_\rmn{lim}$.
 
@@
 ($\beta=1.0$) is about 30\% larger within $\rvir$. This difference is
-build up within $0.1\rvir$ (i.e. close to $r_\s$). Hence the slope of
+built up within $0.1\rvir$ (i.e. close to $r_\s$). Hence the slope of
 the central part of a cluster has little influence for the DM
@@
 density profile is about 50\% larger than the cuspy NFW profile in the
-periphery of the cluster, where the difference is mainly build up at a
+periphery of the cluster, where the difference is mainly built up at a
 few percent of $\rvir$. The increase in luminosity due to substructure
@@
    dust at far IR wavelengths (SD), respectively, and are derived in
-   \cite{2006ApJ...648L..29P} for a galaxy. We normalize the
+   \protect \cite{2006ApJ...648L..29P} for a galaxy. We normalize the
    individual SD spectrum separately using the observed luminosity
@@
 \cite{1980ApJ...239L..93D,1982AJ.....87.1266V,1999APh....12..169B,2000A&A...362..151D,2001ApJ...559...59M,2003MNRAS.342.1009M,2004A&A...413...17P,2004MNRAS.352...76P,2008MNRAS.385.1211P,2008MNRAS.385.1242P,2009JCAP...09..024K,2010MNRAS.401...47D,2010MNRAS.407.1565D,2010ApJ...722..737K,2010arXiv1011.0729K,2011A&A...527A..99E}
-). \footnote{An alternative scenario is the second order turbulent
+).\footnote{An alternative scenario is the second order turbulent
   re-acceleration through the interaction of a previously injected
@@
   active galactic nuclei with plasma waves and
-  magneto-turbulence.\cite{1987A&A...182...21S,1993ApJ...406..399G,2004MNRAS.350.1174B,2005MNRAS.363.1173B,2007MNRAS.378..245B,2011MNRAS.410..127B,2009A&A...507..661B}}
+  magneto-turbulence. \protect
+  \cite{1987A&A...182...21S,1993ApJ...406..399G,2004MNRAS.350.1174B,2005MNRAS.363.1173B,2007MNRAS.378..245B,2011MNRAS.410..127B,2009A&A...507..661B}}
 Supporting evidence comes from the smoothness of the extended radio
@@
 emission to the differential gamma-ray upper limits set by Fermi-LAT
-after 18 months of observations \cite{2010ApJ...717L..71A}, we find
+after 18 months of observations \cite{2010ApJ...717L..71A}, 
+we find
 that the upper limits are not violated. The predicted DM flux that is
@@
   the gamma-ray flux from IC upscattered CMB and continuum emission by
-  570 while the IC upscattered SD photons is boosted by 20. We find
+  570 while the IC upscattered SD photons is boosted by 20. Upper limits
+from Fermi-LAT after 18 months 
+ \protect \cite{2010ApJ...717L..71A} are also shown. We find
   bright prospects for detecting the continuum emission, that is
@@
   gamma-ray flux. The black arrow shows the differential upper limit
-  from Fermi \cite{2010ApJ...717L..71A} indicating that the model
+  from Fermi \protect \cite{2010ApJ...717L..71A} indicating that the model
   assumptions such as Sommerfeld and/or substructure boost are in
@@
 \label{sect:spatial}
-
-\del{\bf should probably be integrated into text; DUSTY STAR FORMING
-  GALAXIES IN OUTER PARTS (LITTLE OVERLAP), DUST WOULD NOT SURVIVE. IF
-  DUST RAMPRESSURE STRIPPED, SPATIALLIATION PROCESS IN THE HOT ICM FOR
-  DYNAMICAL TIME}
 
@@
   \caption{\it The intrinsic surface brightness profiles without
-    substructures at energies $E>1 GeV$. We show the CRp induced
+    substructures at energies $E>1\ GeV$. We show the CRp induced
     emission (red), leptophilic emission (green), and emission from
@@
 boosted by substructures, where the LP model gives rise to a gamma-ray
-flux that is more than three orders of magnitude larger. Although, it
+flux that is more than three orders of magnitude larger. However, it
 should be noted that there are large uncertainties in the gas density
@@
 \subsection{Scaling relations}
-
+First we focus on gamma-ray flux-cluster mass scaling relations for DM
+annihilation and CR induced emission in
+Fig.~\ref{fig:lum_mass_scaling}.  
 \begin{figure*}
@@
 \end{figure*}
-
-First we focus on gamma-ray flux-cluster mass scaling relations for DM
-annihilation and CR induced emission in
-Fig.~\ref{fig:lum_mass_scaling}.  The mass scaling of the substructure
+The mass scaling of the substructure
 boost steepens the intrinsically shallower DM annihilation relation of
@@
 In Figure~\ref{fig21}, we show the DM annihilation flux predictions of
-the entire sample in Fig.~\ref{fig21}.  Assuming the projected point
+the entire sample.  Assuming the projected point
 source sensitivity ($5\sigma$, 50h) of the future Cherenkov telescope
@@
 
+{\bf Christoph, are you sure about this? CTA will be able to collect data in survey mode with a large angular acceptance (6-8 degrees). From the Concept paper that they put on the arXiv last fall:
+``CTA will also have the potential to deliver for the first time significant results on the
+extragalactic diffuse emission at VHE, with the possibility to probe the integrated emission
+from all sources at these energies. While well measured at GeV energies with the EGRET
+and Fermi instruments, the diffuse emission at VHE is extremely challenging to measure
+due to its faintness and the difficulty to adequately subtract the background. Here, the
+improved sensitivity coupled with the large field of view puts detection in reach of CTA.'' So, maybe we should instead say that we want encourage the development of new methods to detect very extended sources?}
+
 \subsection{CR-induced emission}
@@
   \caption{\it We contrast predictions of the CRp induced gamma-ray
-    emission using the analytical  model
+    emission using the analytical model \protect
     \cite{2010MNRAS.409..449P} to Fermi-LAT flux upper limits. We show
@@
    distribution follows the analytical model derived through
-   hydrodynamical cosmological cluster simulations
+   hydrodynamical cosmological cluster simulations \protect
    \cite{2010MNRAS.409..449P} (see text for details).  Gamma-ray
@@
 exceeding $10^3$ which should make nearby clusters the brightest DM
-annihilation sources after the MM center and hypothetical very
+annihilation sources after the MW center and hypothetical very
 close-by DM substructures. Since the number density of substructures
@@
 air Cherenkov telescopes due to the spatially extended boost from
-substructures of angular extend $\sim 0.5-1\deg$ (as independently
+substructures of angular extent $\sim 0.5-1\deg$ (as independently
 found by reference \cite{2011arXiv1104.3530S}). In contrast, the
 sensitivity of Cherenkov telescopes drops linearly with radius outside
-the point spread function $\sim0.1\deg$.
+the point spread function $\sim 0.1\deg$, unless new background subtraction schemes can be found, e.g., for the survey mode of CTA. {\bf Note new last part of this senstence!}
 
@@
 final state radiation is sometimes not distinguished from the
-continuums emission contribution, we keep it separate as it dominates
+continuum emission contribution, we keep it separate as it dominates
 the very high-energy tail of the gamma-ray spectrum in LP models while
-there the continuums emission is negligibly low.
+there the continuum  emission is negligibly low.
 
@@
 
-\smallskip We would like to thank Volker Sprigel for helpful comments.
-Anders Pinzke acknowledges NSF grant AST 0908480 for
+\smallskip We would like to thank Volker Springel for helpful comments.
+A.P. acknowledges NSF grant AST 0908480 for
 support. We would furthermore like to thank KITP for their hospitality
@@
 part by the National Science Foundation under Grant No. NSF
-PHY05-51164.
+PHY05-51164. The work of L.B. was supported by the Swedish Research Council (VR), under contracts no. 621-2009-3915 and 349-2007-8709 (the Oskar Klein Centre).
 
@@
    1\,\ev$) obtained from stacked clusters in the Sloan Digital Sky
-   Survey (SDSS) at the redshift $z \sim 0.25$
+   Survey (SDSS) at the redshift $z \sim 0.25$ \protect
    \cite{2005MNRAS.358..949Z}. The crosses show the total observed
@@
 x&=&\frac{\ee}{m_\chi\,c^2}\,.
-\label{eq:bm_elec}
+\label{eq:lp_elec}
 \end{eqnarray}
@@
    from deprojected Chandra and Rosat X-ray surface brightness
-   observations \cite{2002ApJ...565..883P}. The total hybrid profile
-   shown by the red solid line represent the best fit to the data,
-   where the fitted individual density components are shown by the
-   black dotted lines. The blue solid line shows the single beta
+   observations \protect \cite{2002ApJ...565..883P}. The total hybrid
+   profile shown by the red solid line represent the best fit to the
+   data, where the fitted individual density components are shown by
+   the black dotted lines. The blue solid line shows the single beta
    density profile inferred from the HIFLUGCS catalogue. Due to

### 2011-05-13 paper.tex
corrections to text

@@
 In this paper, we will investigate in some more detail the potential
-of several of the most promising galaxy clusters to yield an
+of several of the most promising galaxy clusters to produce an
 annihilation gamma-ray yield which could be observable with present
@@
 \begin{minipage}{2.0\columnwidth}
-  \caption{Gamma-ray flux from various clusters.}
-\begin{tabular}{c  c c c  c  c c c c c c}
+  \caption{Gamma-ray flux from various clusters within $\rvir$.}
+\begin{tabular}{l  c c c  c  c c c c c c}
 \hline
@@
  \hline
+ Coma                 & $1.3\times10^{-8}$  & $8.3\times10^{-11}$ & $4.0\times10^{-9}$  
+ & \,\,\,\,\,         & $1.4\times10^{-12}$ & $2.3\times10^{-13}$ & $1.5\times10^{-12}$ 
+ & $13.8$ & $44$  & $1310$ \\
+ Perseus \,\,\,\,\,\, & $1.4\times10^{-8}$  & $7.1\times10^{-11}$ & $1.4\times10^{-8}$  
+ & \,\,\,\,\,         & $1.4\times10^{-12}$ & $2.0\times10^{-13}$ & $5.2\times10^{-12}$ 
+ & $7.71$ & $54$  & $1280$ \\
+ Virgo                & $1.2\times10^{-7}$  & $4.0\times10^{-10}$ & $8.7\times10^{-9}$  
+ & \,\,\,\,\,         & $1.3\times10^{-11}$ & $1.1\times10^{-12}$ & $3.2\times10^{-12}$ 
+ & $2.1$  & $83$  & $870$  \\
  Fornax               & $4.8\times10^{-8}$  & $1.3\times10^{-10}$ & $2.2\times10^{-10}$ 
@@
  & $1.0$  & $106$ & $730$  \\
- Coma                 & $1.3\times10^{-8}$  & $8.3\times10^{-11}$ & $4.0\times10^{-9}$  
- & \,\,\,\,\,         & $1.4\times10^{-12}$ & $2.3\times10^{-13}$ & $1.5\times10^{-12}$ 
- & $13.8$ & $44$  & $1310$ \\
- Virgo                & $1.2\times10^{-7}$  & $4.0\times10^{-10}$ & $8.7\times10^{-9}$  
- & \,\,\,\,\,         & $1.3\times10^{-11}$ & $1.1\times10^{-12}$ & $3.2\times10^{-12}$ 
- & $2.1$  & $83$  & $870$  \\
- Perseus \,\,\,\,\,\, & $1.4\times10^{-8}$  & $7.1\times10^{-11}$ & $1.4\times10^{-8}$  
- & \,\,\,\,\,         & $1.4\times10^{-12}$ & $2.0\times10^{-13}$ & $5.2\times10^{-12}$ 
- & $7.71$ & $54$  & $1280$ \\
 \hline
@@
 protons. In Section 2 we discuss the theory of DM and gamma-rays. In
-particular, we focus one the LP and supersymmetric DM models
+particular, we focus on the LP and supersymmetric DM models
 used in this work, and outline the framework for estimating the
@@
 center (for a recent possible indication of a signal, see
-\cite{2010arXiv1010.2752H}, however, see also \cite{2010arXiv1012.5839B}.), the dwarf galaxies surrounding the MW
+\cite{2010arXiv1010.2752H}, however, see also \cite{2010arXiv1012.5839B}), the dwarf galaxies surrounding the MW
 \cite{Strigari:2006rd,Essig:2009jx,2010JCAP...01..031S}, galaxy
@@
   Sommerfeld effect}. This basically means that the usual connection
-between annihilation rate at decoupling (when relative velocities
-$v/c$ were of order $0.2 - 0.3$), which gives the relic density, and
-present-day annihilation in the halo (with velocities $v/c\sim
-10^{-3}$) is broken. This would come about because the DM sector
-contains additional light particles which mediates an interaction with
-almost bound states which enhance the wave function at the relative
-origin, and therefore the annihilation rate (for a pedagogical review
-of viable scenarios, see \cite{ArkaniHamed:2008qn}). As a final
-difficulty of these models, the lack of an IC signature from the
-galactic center means that only shallow density profiles can describe
-the galactic DM density distribution
+between annihilation rate at decoupling (when velocities $v$ relative
+to the speed of light were of order $0.2 - 0.3$), which gives the
+relic density, and present-day annihilation in the halo (with relative
+velocities $v\sim 10^{-3}$) is broken. This would come about because
+the DM sector contains additional light particles which mediates an
+interaction with almost bound states which enhance the wave function
+at the relative origin, and therefore the annihilation rate (for a
+pedagogical review of viable scenarios, see
+\cite{ArkaniHamed:2008qn}). As a final difficulty of these models, the
+lack of an IC signature from the galactic center means that only
+shallow density profiles can describe the galactic DM density
+distribution
 \cite{Bertone:2008xr,Cirelli:2008pk,Bergstrom:2008ag}. (For a review
@@
 particle physics point of view, are also rather limited by several
-sets of astrophysical data, we take advantage of the recent reanalysis
+sets of astrophysical data. We take advantage of the recent reanalysis
 \cite{Finkbeiner:2010sm} to define a benchmark LP model that
@@
 use a DM mass $m_\chi=1.6$~TeV and a branching ratio of ($1/2,\,1/2$)
-into ($\mu^+/\mu^-,\,\e^+/\e^-$) \footnote{This is an approximation to
+into ($\mu^+/\mu^-,\,\e^+/\e^-$).\footnote{This is an approximation to
   the model found in \cite{Finkbeiner:2010sm} that has a branching
   ratio of ($1/3,\,1/3,\,1/3$) into
-  ($\mu^+/\mu^-,\,\e^+/\e^-,\,\pi^+/\pi^-$).}. The SFE
+  ($\mu^+/\mu^-,\,\e^+/\e^-,\,\pi^+/\pi^-$).} The SFE
 $S=\B_\sfe(\sigv=200\,km/s)\approx 300$ for a MW halo in our LP model,
@@
 different contexts (in particular in \cite{Bringmann:2008kj} giving
-predictions for imaging air Cherenkov telescopes, like  MAGIC II and CTA), They give a good
+predictions for imaging air Cherenkov telescopes, like  MAGIC II and CTA). They give a good
 representation of models with high enough gamma-ray rates to become
@@
 \end{equation}
-Here runs the subscript $j$ over all kinematically allowed gamma-ray
-producing channels, each with the spectrum $\frac{\dd
-  \ngammaj}{\dd\eg}$ and annihilation cross-section $\sigmaannv_j$.
+Here,  the subscript $j$ runs over all kinematically allowed gamma-ray
+producing channels, each with the spectrum $\dd
+  \ngammaj /\dd\eg$ and annihilation cross-section $\sigmaannv_j$.
 We denote the DM mass with $\mx$ and the smooth DM density profile
@@
 that is slightly shallower in the center than the conventional
-Navarro-Frenk-White (NFW) profile, but provide a better fit to recent
+Navarro-Frenk-White (NFW) profile, but provides a better fit to recent
 simulated high resolution DM halos \cite{2010MNRAS.402...21N}. It
-should also be noted that a recent observations of the Abell 383
-galaxy cluster finds a core like density profile with an inner slope
-of $\beta=0.6$, where $\beta\gtrsim 1$ can be ruled out to a $>95$\%
-confidence \cite{2011ApJ...728L..39N}. These observations are based on
-lensing and X-ray measurements as well as the stellar velocity
-dispersion of the central galaxy. In Eq.~(\ref{eq:dens_ein}) we denote
-the density where the profile has a slope of $-2$ by $\rho_{-2}$, and
-the radius by $r_{-2}=\rvir/c$. We use that the density
-$\rho_{-2}(c)=\rho_\s(c)/a(c)$ and determine $a(c)$ through $\mvir$:
+should also be noted that recent observations of the Abell 383 galaxy
+cluster find a density profile with a shallower inner slope of
+$\beta=0.6$ compared to an NFW profile, and $\beta\gtrsim 1$ can be
+ruled out with $>95$\% confidence \cite{2011ApJ...728L..39N}. These
+observations are based on lensing and X-ray measurements as well as
+the stellar velocity dispersion of the central galaxy. In
+Eq.~(\ref{eq:dens_ein}) we denote the density where the profile has a
+slope of $-2$ by $\rho_{-2}$, and the radius by $r_{-2}=\rvir/c$. We
+use that the density $\rho_{-2}(c)=\rho_\s(c)/a(c)$ and determine
+$a(c)$ through $\mvir$:
 \begin{equation}
@@
 compared to the virial mass that is subject to tidal stripping. For
-comparison, we quote typical values for a large galaxy clusters and a galaxy group:
+comparison, we quote typical values for a large galaxy cluster and a galaxy group:
 \begin{eqnarray}
@@
 \label{sect:subst}
-High-resolution DM only simulations of MW type halos find substantial
+High-resolution dissipationless DM simulations of MW type halos find substantial
 amount of substructures in the periphery of DM halos, while the
@@
   \cite{2008JPhCS.125a2008K, 2008JPhCS.125a2008K}.} We use a double
-power-law function to fit \footnote{Our approach of fitting the
+power-law function to fit\footnote{Our approach of fitting the
   scaling behavior of $L_\rmn{sub}(<r)$ directly from numerical
@@
 various DM models). Note that potentially the power-law could flatten
-towards smaller mass scales although current simulations show no hits
+towards smaller mass scales although current simulations show no hints
 of such a behavior and since Einstein's gravity is a scale-free
@@
 cluster density profiles to the boosted luminosity due to substructure
-for different mass scales. We recalculate the density contrast for the
-core like NFW density profile $\rhos$ and rescale the concentration
-parameter in Eq.~(\ref{eq:cfit}) with $300/160$
+for different mass scales. We recalculate the overdensity, $\rhos$,
+for the shallower density profile with $\beta=0.6$ and rescale the
+concentration parameter in Eq.~(\ref{eq:cfit}) with $300/160$
 \cite{2011ApJ...728L..39N} to account for the more centralized scale
-radius in cluster with a softer cusp. The emission coming from the
-density profile with a shallower inner slope ($\beta=0.6$) as obtained
-by recent lensing and velocity dispersion measurements of the central
-galaxy \cite{2011ApJ...728L..39N} compared to a cuspy NFW
-($\beta=1.0$) is about 30\% larger within $\rvir$. This difference is
-built up within $0.1\rvir$ (i.e. close to $r_\s$). Hence the slope of
-the central part of a cluster has little influence for the DM
-luminosity within $\rvir$ as long as the degeneracy in the lensing
-mass measurements with $r_\s$ (which decreases for decreasing inner
-slope) has been taken into account. The emission from an Einasto
-density profile is about 50\% larger than the cuspy NFW profile in the
-periphery of the cluster, where the difference is mainly built up at a
-few percent of $\rvir$. The increase in luminosity due to substructure
-is neglible in the center of halos, but integrated out to $\rvir$ the
-boost relative to the smooth emission profile amounts to approximately
-10 for dwarf galaxies, $10^2$ for galaxies, and $10^3$ for galaxy
-clusters.
+radius in cluster with a shallow inner slope. The emission of this
+profile with $\beta=0.6$ is about 30\% larger within $\rvir$ compared
+to a cuspy NFW ($\beta=1.0$).  This difference is built up within
+$0.1\rvir$ (i.e. close to $r_\s$). Hence the slope of the central part
+of a cluster has little influence for the DM luminosity within $\rvir$
+as long as the degeneracy in the lensing mass measurements with $r_\s$
+(which decreases for decreasing inner slope) has been taken into
+account. The emission from an Einasto density profile is about 50\%
+larger than the cuspy NFW profile in the periphery of the cluster,
+where the difference is mainly built up at a few percent of
+$\rvir$. The increase in luminosity due to substructure is neglible in
+the center of halos, but integrated out to $\rvir$ the boost relative
+to the smooth emission profile amounts to approximately 20 for dwarf
+galaxies, $200$ for galaxies, and $10^3$ for galaxy clusters.
 \begin{figure}%[t]
@@
   \caption{\it Plot that shows where most of the DM annihilation
-    luminosity comes from for different halo masses.  Differential
-    contribution to the DM annihilation luminosity per logarithmic
-    interval in radius which corresponds to $x^3\rho^2/\rho^2_{200}$
-    where $\rho_{200}$ is the density at $\rvir$. The solid lines
-    represents cuspy $\beta=1.0$ NFW density profiles for three
-    different mass scales; an $\mvir=10^{15}\,\msun$ galaxy cluster
-    (red), an $\mvir=10^{12}\,\msun$ galaxy (orange), and an
+    luminosity originates.  We show the differential contribution to
+    the DM annihilation luminosity per logarithmic interval in radius
+    which corresponds to $x^3\rho^2/\rho^2_{200}$ where $\rho_{200}$
+    is the density at $\rvir$. The solid lines represent cuspy
+    $\beta=1.0$ NFW density profiles for three different mass scales;
+    an $\mvir=10^{15}\,\msun$ galaxy cluster (red), an
+    $\mvir=10^{12}\,\msun$ galaxy (orange), and an
     $\mvir=10^{8}\,\msun$ dwarf galaxy (green). The dashed lines show
@@
 background (CMB) photons, and the light from stars and dust (SD). We
-derive a analytic model from which we can estimate the spectral
+derive an analytic model from which we can estimate the spectral
 and spatial distributions of SD as a simple function of cluster mass.
@@
 Lorentz-boosted photon in the electron rest frame comes close to $m_\e
-c^2$ such that the scattering electrons experiences a significant
+c^2$ such that the scattering electron experiences a significant
 recoil. This results in a steepening of the IC gamma-ray spectrum. In
@@
 (IR) to ultra-violet (UV) light emitted by SD. The number density for
-the SD is given by $n_\ph\equiv\frac{\dd^2 N_\ph}{\dd V \,\dd
-  \eph}(\eph,r)= \frac{u_\sd(\eph,r)}{\eph^2}$ where the SD energy
-density $u_\sd(\eph,r)$ is given in the Appendix,
-Eq.~(\ref{eq:u_SD_er}). We model the CMB photon spectrum as a photon
-gas that is isotropically distributed and follows a black body
-spectrum with the temperature $T=2.73\,$~K:
+the SD is given by $n_\ph\equiv\dd^2 N_\ph/ (\dd V \,\dd \eph) (\eph,r)=
+u_\sd(\eph,r) /\eph^2$ where the SD energy density $u_\sd(\eph,r)$ is
+given in the Appendix, Eq.~(\ref{eq:u_SD_er}). We model the CMB photon
+spectrum as a photon gas that is isotropically distributed and follows
+a black body spectrum with the temperature $T=2.73\,$~K:
 \begin{equation}
@@
 and radiative losses. Hence we have to calculate the equilibrium
-spectrum of the electrons plus positrons denoted by $\frac{\dd
-  n_\e}{\dd \ee}$ in Eq.~(\ref{eq:ICemiss}). We derive this stationary
-solution using the CR transport equation (neglecting convection and
-re-acceleration effects):
+spectrum of the electrons plus positrons denoted by $\dd n_\e/\dd \ee$
+in Eq.~(\ref{eq:ICemiss}). We derive this stationary solution using
+the CR transport equation (neglecting convection and re-acceleration
+effects):
 \begin{eqnarray}
@@
 annihilation final states $f$, each with a branching ratio $B_f$ and a
-differential spectrum $\frac{\dd N_\e^f}{\dd \ee}$ that represents the
+differential spectrum $\dd N_\e^f/\dd \ee$ that represents the
 number of electrons plus positrons resulting from an annihilation
 event. For neutralinos annihilating directly into electrons and
-positrons we model the spectral distribution with $\frac{\dd
-  N_\e^f}{\dd \ee}= 2\delta(\ee-m_\chi c^2)$. We use {\sc DarkSUSY} to
+positrons we model the spectral distribution with $\dd
+  N_\e^f/\dd \ee= 2\delta(\ee-m_\chi c^2)$. We use {\sc DarkSUSY} to
 compute both the spectra when neutralinos annihilate directly into a
@@
 shorter than the diffusive timescale in the ICM of galaxy clusters for
-CR electrons which is larger than the hubble time in our energy range
+CR electrons which is larger than the Hubble time in our energy range
 \cite{1997ApJ...487..529B,2011A&A...527A..99E}. Hence, we neglect the
@@
 Here we include the three main radiative loss processes for the CR
-electrons and positrons: (1) IC losses on CMB photons where the
-equivalent field strength of the CMB is denoted by $B_{\rm
+electrons and positrons: (1) IC losses on CMB photons with the
+equivalent field strength of the CMB of $B_{\rm
   CMB}=3.24\mu\rmn{G}\,(1+z)^2$, where $z$ is the cosmological
@@
 compute the IC emission from SD, we require a non-negligible overlap
-of the relativistic lepton distribution resulting form DM annihilation
+of the relativistic lepton distribution resulting from DM annihilation
 and SD.  In fact, one can show with a simple order of magnitude
@@
  \caption{\it Spectral dependence of radiation fields in a cluster of
-   galaxies. The black dotted line in the left peak show the spectrum
+   galaxies. The black dotted line of the left peak show the spectrum
    of CMB photons using a black body with a temperature of
-   $2.73$~K. The crosses in the middle and right peaks represent the
+   $2.73$~K. The crosses of the middle and right peaks represent the
    measured spectra from stars extending from the near IR to UV and
@@
    smooth SD light, respectively. For comparison we show the energy
-   density of the stars and a low dust model (SLD) with the light blue
+   density of the stars and a low dust model (SLD) with the light grey
    line. The SD light has been renormalized to a cluster with the mass
-   $\mvir=6\times10^{14}\msun$. Finally we show the energy density two
+   $\mvir=6\times10^{14}\msun$. Finally we show the energy density of two
    magnetic field models with a central magnetic field of 3~$\mu
@@
    radiation is dominating the energy density inside
-   $\sim0.1\,\rvir$.}
+   $\sim0.03\,\rvir$.}
  \label{fig:SD_Edens}
@@
    shown by the orange lines. We normalize the SD light and the IC
-   upscattered SD light with the luminosity from the smooth component
-   within $\rvir$ for each component. We find that the gamma-ray IC
-   luminosities are dominated by the central regime, while the SD
-   light is mainly build up in the outer parts of the cluster. For
-   comparison, we show that the SD light traces the NFW mass profile
-   (blue) outside  $0.1\rvir$.}
+   upscattered SD with the smooth luminosity within $\rvir$ for each
+   component. We find that the gamma-ray IC luminosities are dominated
+   by the central regime, while the SD light is mainly build up in the
+   outer parts of the cluster. For comparison, we show that the SD
+   light traces the NFW mass profile (blue) outside $0.1\rvir$.}
  \label{fig:SD_lum}
@@
 electrons, neutrinos, and gamma-rays (see
-\cite{1980ApJ...239L..93D,1982AJ.....87.1266V,1999APh....12..169B,2000A&A...362..151D,2001ApJ...559...59M,2003MNRAS.342.1009M,2004A&A...413...17P,2004MNRAS.352...76P,2008MNRAS.385.1211P,2008MNRAS.385.1242P,2009JCAP...09..024K,2010MNRAS.401...47D,2010MNRAS.407.1565D,2010ApJ...722..737K,2010arXiv1011.0729K,2011A&A...527A..99E}
+\cite{1980ApJ...239L..93D,1982AJ.....87.1266V,1999APh....12..169B,2000A&A...362..151D,2001ApJ...559...59M,2003MNRAS.342.1009M,2004A&A...413...17P,2004MNRAS.352...76P,2008MNRAS.385.1211P,2008MNRAS.385.1242P,2009JCAP...09..024K,2010MNRAS.401...47D,2010MNRAS.407.1565D,2010ApJ...722..737K,2011A&A...527A..99E}
 ).\footnote{An alternative scenario is the second order turbulent
@@
 Supporting evidence comes from the smoothness of the extended radio
-emission that often resembles that observed in thermal
-X-rays. Especially since the long cooling time of cosmic ray protons
-(CRs) allows for an extended and large population of CRs to build up
-over the cluster history \citep{1996SSRv...75..279V,
-  1997ApJ...477..560E, 1997ApJ...487..529B}. The production of these
-secondaries depend both on the gas and CRp densities in the cluster,
-where the CRp density roughly traces the gas outside the core regime
-and is slightly enhanced in the center.  This density scaling implies
-that clusters are great targets for Cherenkov telescopes with a high
-sensitivity for the central parts of nearby clusters. Detecting the
-cluster gamma-ray emission is crucial in this respect as it
-potentially provides the unique and unambiguous evidence of CRp
-populations in clusters through observing the $\pi^0$ bump at about
-100~MeV in the spectra.
+emission that often resembles that observed in thermal X-rays. This
+can be easily achievd in the hadronic model since the long cooling
+time of cosmic ray protons (CRs) allows for an extended and large
+population of CRs to build up over the cluster history
+\citep{1996SSRv...75..279V, 1997ApJ...477..560E,
+  1997ApJ...487..529B}. The production of these secondaries depend
+both on the gas and CR densities in the cluster, where the CR
+density roughly traces the gas outside the core regime and is slightly
+enhanced in the center.  This density scaling implies that clusters
+are great targets for Cherenkov telescopes with a high sensitivity for
+the central parts of nearby clusters. Detecting the cluster gamma-ray
+emission is crucial in this respect as it potentially provides the
+unique and unambiguous evidence of CR populations in clusters through
+observing the $\pi^0$ bump at about 100~MeV in the spectra.
 
@@
 clusters of galaxies that included radiative hydrodynamics, star
-formation, supernova feedback, and followed CRp physics using a novel
+formation, supernova feedback, and followed CR physics using a novel
 formulation that trace the most important injection and loss processes
-self-consistently while accounting for the CRp pressure in the
+self-consistently while accounting for the CR pressure in the
 equation of motion
 \cite{2008A&A...481...33J,2007A&A...473...41E,2006MNRAS.367..113P}.
-We note that the overall normalization of the CRp and gamma-ray
+We note that the overall normalization of the CR and gamma-ray
 distribution scales with the maximum acceleration efficiency at
@@
   Compton upscattered both CMB photons (green dotted) as well as dust
-  and star photons (orange dash-dotted), and CRp induced gamma-ray
+  and star photons (orange dash-dotted), and CR induced gamma-ray
   emission (red solid). Each panel is associated with an individual DM
@@
   dashed-dotted). The sum of the three components are shown with the
-  orange solid line.  The red solid line show the CRp induced
+  orange solid line.  The red solid line show the CR induced
   gamma-ray flux. The black arrow shows the differential upper limit
@@
 It is also interesting to compare the total contribution from the LP
-model, the brightest BM model ($\Kp$), and the CRp induced
-emission. In Fig.~\ref{fig:flux_int} we show the integrated flux from
-Fornax for our different gamma-ray models and compare it to the
-unresolved integrated flux upper limit on Fornax set by Fermi-LAT
-where they averaged the flux over the energy range $0.2-100\,\gev$
-assuming a spectral index of 2. Again, the annihilation flux in the LP
-model is in conflict with the upper limits by Fermi-LAT, although only
-by a factor of 10 which is about a order magnitude less constraining
-than the differential flux in the energy range $1-10$~GeV. As shown in
-this figure, the LP model is dominating the entire gamma-ray energy
-range up to the DM rest mass energy in this model of about
-1~TeV. Finally, we note that the flux the DM BM $\Kp$ model is above
-the predicted emission from the CRs in the $1-100$~GeV energy
-regime. Hence, the prospects for detecting the $\Kp$ BM model over the
-expected gamma-ray background induced by CRs looks promising.
+model, the brightest BM model ($\Kp$), and the CR induced emission. In
+Fig.~\ref{fig:flux_int} we show the integrated flux from Fornax for
+our different gamma-ray models and compare it to the unresolved
+integrated flux upper limit on Fornax set by Fermi-LAT where they
+averaged the flux over the energy range $0.2-100\,\gev$ assuming a
+spectral index of 2. Again, the annihilation flux in the LP model is
+in conflict with the upper limits by Fermi-LAT, although only by a
+factor of 10 which is about a order magnitude less constraining than
+the differential flux in the energy range $1-10$~GeV. As shown in this
+figure, the LP model is dominating the entire gamma-ray energy range
+up to the DM rest mass energy in this model of about 1~TeV. Finally,
+we note that the flux the DM BM $\Kp$ model is above the predicted
+emission from the CRs in the $1-100$~GeV energy regime. Hence, the
+prospects for detecting the $\Kp$ BM model over the expected gamma-ray
+background induced by CRs looks promising. The projected CTA point
+source sensitivity ($5\sigma$, 50h) shows the potential of this
+experiment in also constraining leptophilic models as well as BM
+models with a very large neutralino mass $m_\chi c^2 \gtrsim
+1$~TeV. To this end, analysis techniques have to be developed that
+enable the detection of extended sources without too much degradation
+of sensitivity.
 
@@
  \caption{\it Comparing the energy integrated flux from different
-   models. We show the emission from; CRp induced emission (red
+   models. We show the emission from; CR induced emission (red
    solid), leptophilic (LP) models that include both final state
@@
   (upper left), Coma (upper right), Virgo (lower left), and Perseus
-  (lower right). We show CRp induced emission (red solid), leptophilic
+  (lower right). We show CR induced emission (red solid), leptophilic
   (LP) models include both final state radiation and IC upscattered
@@
 explained by the low gas density outside the BCG and the less abundant
-CRp population in the relative small cluster compared to a more
+CR population in the relative small cluster compared to a more
 massive cluster \cite{2010MNRAS.409..449P}.  This is the reason why
@@
    different clusters without taking PSF effects into account. We show
-   the CRp induced emission (red), leptophilic emission (green), and
+   the CR induced emission (red), leptophilic emission (green), and
    emission from the $\Kp$ benchmark model (blue). The different
@@
 extent of the cluster, even though Fornax has one of the highest
-ratios of DM to CRp induced gamma-ray brightness.
+ratios of DM to CR induced gamma-ray brightness.
 
@@
 brightness. Finally, we note that the flux from DM without
-substructures is dominated by the CRp induced emission for all
+substructures is dominated by the CR induced emission for all
 clusters.
@@
   \caption{\it The intrinsic surface brightness profiles without
-    substructures at energies $E>1\ GeV$. We show the CRp induced
+    substructures at energies $E>1\ GeV$. We show the CR induced
     emission (red), leptophilic emission (green), and emission from
@@
 $r<0.1\rvir$, due to both the effect from substructures and the
-smoothing over the PSF. The CRp induced emission also show a
+smoothing over the PSF. The CR induced emission also show a
 smoothing in the central parts due to the PSF. In the outer part of
-the Fornax cluster the CRp flux is suppressed compared to the DM flux
+the Fornax cluster the CR flux is suppressed compared to the DM flux
 boosted by substructures, where the LP model gives rise to a gamma-ray
@@
 should be noted that there are large uncertainties in the gas density
-profile which we use to estimate the CRp induced gamma-ray surface
+profile which we use to estimate the CR induced gamma-ray surface
 brightness (see Fig.~\ref{fig:dens_fornax} for more details).
@@
 include the IC gamma-ray contribution from shock accelerated electrons
-as well as secondary electrons created through CRp-proton
+as well as secondary electrons created through CR-proton
 interactions. The gamma-ray flux from the electrons is, however,
@@
 In Figure~\ref{fig21}, we show the DM annihilation flux predictions of
-the entire sample.  Assuming the projected point
-source sensitivity ($5\sigma$, 50h) of the future Cherenkov telescope
-array (CTA) of $F_\gamma(>E_\gamma) = \{4\times10^{-11},
-2\times10^{-12}, 2\times10^{-14}\}
-\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$ at energies of
-$E_\gamma=\{10~\rmn{GeV}, 100~\rmn{GeV}, 1~\rmn{TeV}\}$
-\cite{2009arXiv0908.1410D}, we note that it will be difficult to
-detect the DM annihilation signal from clusters without a Sommerfeld
-boost by Cherenkov telescopes.  This is because the boost from
-substructures is extended while the sensitivity of Cherenkov
+the entire sample.  Assuming the projected point source sensitivity
+($5\sigma$, 50h) of the future Cherenkov telescope array (CTA) of
+$F_\gamma(>E_\gamma) = \{4\times10^{-11}, 2\times10^{-12},
+2\times10^{-14}\} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$ at energies
+of $E_\gamma=\{10~\rmn{GeV}, 100~\rmn{GeV}, 1~\rmn{TeV}\}$
+\cite{2009arXiv0908.1410D}, we note that it will be very challenging
+to detect the DM annihilation signal from clusters without a
+Sommerfeld boost by Cherenkov telescopes.  This is because the boost
+from substructures is extended while the sensitivity of Cherenkov
 telescopes drops linearly with radius outside the point spread
@@
 compared to a sensitivity that is scaled down by the ratio of cluster
-diameter to angular resolution of 0.1 degree so that even a large
-increase in observational time would make it highly improbable to
-probe the presented class of BM models.
-
-{\bf Christoph, are you sure about this? CTA will be able to collect data in survey mode with a large angular acceptance (6-8 degrees). From the Concept paper that they put on the arXiv last fall:
-``CTA will also have the potential to deliver for the first time significant results on the
-extragalactic diffuse emission at VHE, with the possibility to probe the integrated emission
-from all sources at these energies. While well measured at GeV energies with the EGRET
-and Fermi instruments, the diffuse emission at VHE is extremely challenging to measure
-due to its faintness and the difficulty to adequately subtract the background. Here, the
-improved sensitivity coupled with the large field of view puts detection in reach of CTA.'' So, maybe we should instead say that we want encourage the development of new methods to detect very extended sources?}
+radius to angular resolution of 0.1 degree assuming current background
+subtraction techniques of IACTs.  This important finding should
+encourage the development of new methods to overcome the degradation
+of sensitivity for diffuse and very extended sources. Such a
+break-through would be needed to probe and potentially detect the
+presented class of BM models with a large investment of observational
+time.
 
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.CR.diff.eps}
-  \caption{\it We contrast predictions of the CRp induced gamma-ray
+  \caption{\it We contrast predictions of the CR induced gamma-ray
     emission using the analytical model \protect
@@
     arrows. The blue boxes show the gamma-ray emission from
-    CRp-induced $\pi^0$-decay, where the upper bound shows the
+    CR-induced $\pi^0$-decay, where the upper bound shows the
     estimates for an optimistic model and the lower bound a more
@@
 flux predictions by the analytical model \cite{2010MNRAS.409..449P}
-for CRp induced gamma-rays. For consistency, we use beta-model fits to
+for CR induced gamma-rays. For consistency, we use beta-model fits to
 ROSAT data of X-ray bright clusters for our gamma-ray flux estimates
@@
 --) The reason why there is only a factor 10 difference in the break in the
-gamma-ray emission between the star and dust is related to the KN. In our CRp
+gamma-ray emission between the star and dust is related to the KN. In our CR
 paper, the last figure shows that at $\eg=100\,\tev$, the spectra is suppressed
@@
 sensitivity of Cherenkov telescopes drops linearly with radius outside
-the point spread function $\sim 0.1\deg$, unless new background subtraction schemes can be found, e.g., for the survey mode of CTA. {\bf Note new last part of this senstence!}
+the point spread function $\sim 0.1\deg$, unless new background
+subtraction schemes can be found, e.g., for the survey mode of CTA.
 

### 2011-05-13 paper.tex
corrections to text

@@
   dashed-dotted). The sum of the three components are shown with the
-  orange solid line.  The red solid line show the CR induced
-  gamma-ray flux. The black arrow shows the differential upper limit
-  from Fermi \protect \cite{2010ApJ...717L..71A} indicating that the model
+  orange solid line.  The red solid line show the CR induced gamma-ray
+  flux. The black arrow shows the differential upper limit from Fermi
+  \protect \cite{2010ApJ...717L..71A} indicating that the model
   assumptions such as Sommerfeld and/or substructure boost are in
-  conflict with the upper limit. All fluxes are calculated for the
-  Fornax cluster within $\rvir$ using a point spread function of
-  $0.1\deg$. For this cluster, the boost from Sommerfeld is about 130
-  and the enhancement due to substructures from IC upscattered CMB and
-  SD photons is 570 and 20, respectively.}
+  conflict with the upper limit. We also show projected CTA point
+  source sensitivities ($5\sigma$, 50h).  All fluxes are calculated
+  for the Fornax cluster within $\rvir$ using a point spread function
+  of $0.1\deg$. For this cluster, the boost from Sommerfeld is about
+  130 and the enhancement due to substructures from IC upscattered CMB
+  and SD photons is 570 and 20, respectively.}
  \label{fig:IR_comp}

### 2011-05-13 paper.tex
minor changes

@@
 and even the cosmological large scale structure
-\cite{Bergstrom:2001jj,Ullio:2002pj,Taylor:2002zd,Elsaesser:2004ap,Cuoco:2010jb,Abazajian:2010sq,Abdo:2010dk,Zavala:2011tt}.
+\cite{Bergstrom:2001jj,Ullio:2002pj,Taylor:2002zd,Elsaesser:2004ap,2011MNRAS.tmp..503C,Abazajian:2010sq,Abdo:2010dk,Zavala:2011tt}.
 
@@
 in Eq.~(\ref{eq:ICemiss}). We derive this stationary solution using
-the CR transport equation (neglecting convection and re-acceleration
-effects):
+the cosmic ray transport equation (neglecting convection and
+re-acceleration effects):
 \begin{eqnarray}
@@
 shorter than the diffusive timescale in the ICM of galaxy clusters for
-CR electrons which is larger than the Hubble time in our energy range
-\cite{1997ApJ...487..529B,2011A&A...527A..99E}. Hence, we neglect the
-first term of the r.h.s. in Eq.~(\ref{eq:CRdiffusion}), and derive an
-expression for the equilibrium number density:
+cosmic ray electrons which is larger than the Hubble time in our
+energy range \cite{1997ApJ...487..529B,2011A&A...527A..99E}. Hence, we
+neglect the first term of the r.h.s. in Eq.~(\ref{eq:CRdiffusion}),
+and derive an expression for the equilibrium number density:
 \begin{eqnarray}
@@
 \end{eqnarray}
-Here we include the three main radiative loss processes for the CR
-electrons and positrons: (1) IC losses on CMB photons with the
+Here we include the three main radiative loss processes for the cosmic
+ray electrons and positrons: (1) IC losses on CMB photons with the
 equivalent field strength of the CMB of $B_{\rm

### 2011-05-14 paper.tex
updated appendix

@@
    show the total emission including the brightest cluster galaxy, the
-   intra cluster light and the additional intra cluster galaxies,
+   intra-cluster light and the additional intra-cluster galaxies,
    while these galaxies have been cut out in the smooth component
@@
 leptons in the final state which up-scatter radiation fields from the
-cosmic microwave background, dust, and starlight, and (iii) final
+cosmic microwave background (CMB), dust, and starlight, and (iii) final
 state radiation or internal bremsstrahlung which dominates the highest
@@
 For the first time we compute the IC emission component not only from
-the upscattered cosmic microwave (CMB) photons but also from a
-realistically modeled photon field due to dust and starlight extending
-from infra red to optical wavelengths. To this end, we construct a
-rather simple analytic model for the spatial and spectral distribution
-of dust and starlight in clusters which can be used for the
-annihilation emission in galaxies with a different spatial profile.
-We find that in benchmark models, the continuum emission dominates
-over the IC emission of any available radiation field. In the LP
-models, where the continuum emission is low, the IC up-scattering of
-the CMB dominates below 60 GeV. For large clusters, the final state
-radiation takes then over for energies up to the cutoff at $m_\chi c^2
-\sim 1$~TeV. In small clusters, there is a window around $E_\gamma
-\sim 100~\mathrm{GeV}$ where the IC up-scattering of the dust emission
+the upscattered CMB photons but also from a realistically modeled
+photon field due to dust and starlight extending from infra red to
+optical wavelengths. To this end, we construct a rather simple
+analytic model for the spatial and spectral distribution of dust and
+starlight in clusters which can be used for the annihilation emission
+in galaxies with a different spatial profile.  We find that in
+benchmark models, the continuum emission dominates over the IC
+emission of any available radiation field. In the LP models, where the
+continuum emission is low, the IC up-scattering of the CMB dominates
+below 60 GeV. For large clusters, the final state radiation takes then
+over for energies up to the cutoff at $m_\chi c^2 \sim 1$~TeV. In
+small clusters, there is a window around $E_\gamma \sim
+100~\mathrm{GeV}$ where the IC up-scattering of the dust emission
 dominates over the CMB IC emission and the final state radiation. The
@@
 \label{sect:SD}
-In this section we show the details of our model of stars and dust
-(SD) in clusters of galaxies. In the first part we use the spectral
-distribution of the SD light in galaxies to derive a simple spectral
-model for SD in galaxy clusters. This is done by renormalizing the
-galactic SD light to match the conditions for a cluster. In the second
-part we derive the spatial distirbution of the SD light.
+In this section we present the details of our model of stars and dust
+(SD) in clusters of galaxies. In the first part we the measured
+spectral distribution of light from SD in a typical galaxy to derive a
+simple spectral model for SD in galaxy clusters. This is done by
+renormalizing the galactic SD light to match the observed luminosity
+from a cluster in the far infrared (IR) and ultraviolet (UV) bands. In
+the second part we derive the spatial distribution of the SD light
+from a stacked sample of clusters.
 
@@
 galaxies. This radiation is expected to leak out into the much larger
-volume of the ICM, hence we approximate the spectral distribution of
-the ICL with the light from galaxies. We use the far infrared to
-ultraviolet spectrum derived in \cite{2006ApJ...648L..29P} for a MW
-type galaxy to characterize the SD spectral distribution of a
-cluster. Note that we only keep the spectral shape, and renormalize
-the spectral distribution using the luminosity from SD.
+volume of the intra-cluster medium, hence we approximate the spectral
+distribution of the intra-cluster light (ICL) with the light from
+galaxies. We use the far IR to UV spectrum derived in reference
+\cite{2006ApJ...648L..29P} for a Milky Way (MW) type galaxy to
+characterize the spectral distribution of SD in a cluster. Note that
+we only keep the spectral shape, and renormalize the spectral
+distribution using the luminosity from SD in clusters.
 
 In Fig.~\ref{fig:SD_spectra} we show the spectral distribution of the
-light from SD together with the CMB black-body distribution in a
-$6\times10^{14}\,\msun$ galaxy cluster. We fit the spectral shape of
-SD individually; the dust that peaks at about $10^{-2}\,\ev$ is fitted
-using a double power-law, while the broader spectral distribution of
-the stars that peaks at about $1\,\ev$ is fitted using a tipple
-power-law. The best fitted SD spectra are given by: \del{both at the
-  radius $r=0.03\rvir$ where the energy density of the smooth light
-  from SD (see Fig.~\ref{fig:SD_Edens}) equals the energy density of
-  the CMB. We have renormalized both the spectral data and the fitted
-  spectra using the luminosity from stars and dust individually.}
+light from SD together with the cosmic microwave background (CMB)
+black-body distribution in a $6\times10^{14}\,\msun$ galaxy
+cluster. We fit the spectral shape of SD individually; the dust that
+peaks at about $10^{-2}\,\ev$ is fitted using a double power-law,
+while the broader spectral distribution of the stars that peaks at
+about $1\,\ev$ is fitted using a tipple power-law. The best fit to the
+galactic spectrum is given by:
 \begin{eqnarray}
@@
 \end{eqnarray}
-The specific energy density of SD light in a cluster can now be
-derived from 
+The specific energy density of the light from SD in a cluster can now
+be derived from
 \begin{eqnarray} 
@@
 \end{eqnarray}
-where the SD spectrum is given by 
+where the spectral distribution of SD is given by
 \begin{eqnarray}
@@
   =  \sum_i N_i(\mvir) u_i^\gal(\eph)\,,\nonumber \\ 
-\rmn{where}\quad i&=&\{\rmn{stars,dust}\}\,.
+\rmn{for}\quad i&=&\{\rmn{stars,dust}\}\,.
 \end{eqnarray}
 Here $\eph$ denotes the energy of the SD photons, $j(r)$ describes the
-unitless spatial distribution which we derive in
-sect.~\ref{sect:SD_radial}, and $N_i(\mvir)$ denotes the mass
+unitless spatial distribution of SD (derived in
+sect.~\ref{sect:SD_radial}), and $N_i(\mvir)$ denotes the mass
 dependent normalization for the SD. This function is determined using
-the total energy of the light in SD within $\rvir$ denoted by
-$E_{i,\vir}$. We relate this energy to the luminosity $L_i$ of each
-respective wavelength band (optical and IR light for the dust, and UV
-light for the stars) using
+the total energy of the light from SD within $\rvir$ which is
+represented by $E_{i,\vir}$. We relate this energy to the luminosity
+$L_i$ of each respective wavelength band (optical and IR light for the
+dust, and UV light for the stars) using
 \begin{eqnarray} 
@@
 \end{eqnarray}
-We approximate the total energy of the photons within $\rvir$ with the
-luminosity \cite{2008A&A...490..547G} times the typical timescale it
-takes for a photon to propagate through the cluster (we assume that
-the cluster is optically thin).
-
-We derive the luminosity from the stars using
+Here we approximate the total energy of the photons within $\rvir$
+with the luminosity \cite{2008A&A...490..547G} multiplied the typical
+timescale it takes for a photon to propagate through the cluster (we
+assume that the cluster is optically thin).
+
+We derive the {\em luminosity from the stars} using
 \begin{eqnarray}
@@
 clusters observed by the SDSS with the average mass
-$M_{200\rmn{av}}=4.0\times10^{13}\msun$ and redshift close to
-$z=0.25$. We also use an apparent magnitude of the sun $m_\odot\approx
--27.7$, distance to the sun $D_\odot=4.85\times10^{-6}\,\rmn{pc}$,
-luminosity of the sun $L_\odot=1.17\times10^{33}\,\rmn{erg\,s}^{-1}$,
-and distance to the cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. To
-account for different cluster masses, we attach a simple mass scaling
-to the luminosity from the stars in clusters in Eq.~(\ref{eq:L_stars}).
-Since a large contribution of the total starlight in a cluster comes
-from the brightest cluster galaxy (BCG), we assume that the total
-starlight has the same halo mass scaling as the BCG
-\cite{2010ApJ...713.1037H}
+$M_{200\rmn{av}}=4.0\times10^{13}\msun$. We also use an apparent
+magnitude of the sun $m_\odot\approx -27.7$, distance to the sun
+$D_\odot=4.85\times10^{-6}\,\rmn{pc}$, luminosity of the sun
+$L_\odot=1.17\times10^{33}\,\rmn{erg\,s}^{-1}$, and distance to the
+cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. To account for different
+cluster masses, we attach a simple mass scaling to the luminosity from
+the stars in clusters in Eq.~(\ref{eq:L_stars}).  Since a large
+contribution of the total starlight in a cluster comes from the
+brightest cluster galaxy (BCG), we assume that the total starlight has
+the same halo mass scaling as the BCG \cite{2010ApJ...713.1037H}
 \begin{equation}
@@
 Eq.~(\ref{eq:E_SD}) by integrating over the cluster volume and
-spectral distribution of the stars. It is given by
+spectral distribution of the stars:
 \begin{equation}
- N_\stars(\mvir) = 6.0\times10^{-9}\,\kpc^2\,
+ N_\stars(\mvir) = 
 \left(\frac{\mvir}{M_{200\rmn{av}}}\right)^{0.18}\,
-\frac{\rvir}{\int_{\rvir} j(r) \,\dd V}\,.
+\frac{6.0\,\rvir\times10^{-9}\,\kpc^2}{\int_{\rvir} j(r) \,\dd V}\,.
 \label{eq:N_stars}
 \end{equation}
-\del{Note that since the luminosities include the contribution from
-galaxies, we have integrated the spatial distribution including
-galaxies to derive the normalization. Once the normalization is fixed,
-the SD energy densities are derived from the spatial distribution
-where galaxies have been excluded.}
-
-The luminosity from the dust is derived from the luminosity-richness
-scaling relation found in \cite{2008A&A...490..547G}
+
+The {\em luminosity from the dust} is derived from the
+luminosity-richness scaling relation found in
+\cite{2008A&A...490..547G}
 $L_\dust=10^{44.8}\left(\frac{N_{200}}{10}\right)^{0.8}$. We pick a
@@
 $M_\rmn{200dust}=6.0\times10^{14}\,\msun$
-\cite{2010ApJ...713.1037H}. Assuming that the dust scales with halo
-mass in the same way as the stars, we get
+\cite{2010ApJ...713.1037H}. We assume that the dust scales with halo
+mass in the same way as the stars, and determine the normalization
+constant for the dust in Eq.~(\ref{eq:E_SD}) to
 \begin{equation}
-L_\dust(\mvir)=L_\dust(M_\rmn{200dust})\,
-\left(\frac{\mvir}{M_\rmn{200dust}}\right)^{0.18}\,.
-\label{eq:L_dust_scale}
-\end{equation} 
-The normalization constant for the dust in Eq.~(\ref{eq:E_SD}) can now
-be determined:
-\begin{equation}
- N_\stars(\mvir) = 4.0\times10^{-7}\,\kpc^2\,
+ N_\stars(\mvir) = 
 \left(\frac{\mvir}{M_\rmn{200dust}}\right)^{0.18}\,
-\frac{\rvir}{\int_{\rvir} j(r) \,\dd V}\,.
+\frac{4.0\,\rvir\times10^{-7}\,\kpc^2}{\int_{\rvir} j(r) \,\dd V}\,.
 \label{eq:N_dust}
@@
 Our goal in this section is to derive a simple spatial model for the
-distribution of SD in galaxy clusters. For this reason we use stacked
-cluster observations by Sloan in the $r$ and $i$-band that trace the
-stars and for simplicity we assume that the dust trace the stars in
-the clusters \del{\bf WHY IS THIS A GOOD APPROXIMATION}. The stacked
-surface brightness profiles in \cite{2005MNRAS.358..949Z} are measured
-at redshift $z \sim 0.25$ with an average mass of the clusters of
-$4.0\times10^{13}\,\msun$. The profiles are build up out of three
-components; diffuse intracluster light (ICL), galaxies, and the
-brightest cluster galaxy (BCG) in the center of clusters. However, the
-total volume overlap of the ISM to the cluster is very small compared
-to the ICL- and BCG overlap with the cluster, thus the relative
-contribution of the galaxies to the IC emission is suppressed
-(c.f. Eq.~\ref{eq:SD_overlap}). To remove this bias we cut out the
-galaxies that have been smoothed over the cluster in the stacked
-analysis. In Fig.~\ref{fig:SD_spatial} we show the SDSS stacked
-brightness profiles as well as the fitted profiles\footnote{The
-  measured brightness is converted into units of
-  $\rmn{erg}\,\rmn{s}^{-1}$ using \cite{2010...book}
-  $S(\rmn{mag}\,''^{-2}) =
+distribution of the light from SD in galaxy clusters. For this reason
+we use stacked cluster observations by Sloan in the $r$ and $i$-band
+that trace the stars and for simplicity we assume that the dust trace
+the stars in the clusters {\bf Christoph, why is this a valid
+  approximation?}. The stacked surface brightness profiles in
+\cite{2005MNRAS.358..949Z} are measured at redshift $z \approx 0.25$
+with an average mass of the clusters of $4.0\times10^{13}\,\msun$. The
+profiles are build up out of three components; diffuse ICL, galaxies,
+and the BCG in the center of clusters. However, the total volume
+overlap of the inter-stellar medium with a cluster is very small
+compared to the total overlap of the ICL- and BCG with a cluster, thus
+the relative contribution of the galaxies to the IC emission is
+suppressed (c.f. Eq.~\ref{eq:SD_overlap}). We remove this bias in our
+benchmark model for SD by cutting out the galaxies which roughly
+corresponds to $70$ percent of the total SD light. In
+Fig.~\ref{fig:SD_spatial} we show the SDSS stacked brightness profiles
+as well as the fitted profiles\footnote{The measured brightness is
+  converted into units of $\rmn{erg}\,\rmn{s}^{-1}$ using
+  \cite{2010...book} $S(\rmn{mag}\,''^{-2}) =
   \mathcal{M}_\odot+21.6-2.5\log_{10}[S(L_\odot\,\rmn{pc}^{-2})]$,
@@
  \includegraphics[width=0.99\columnwidth]{figures/SB.photon.eps}
- \caption{\it Surface brightness profiles of the $r$-band ($h\nu\sim
-   1\,\ev$) obtained from stacked clusters in the Sloan Digital Sky
+ \caption{\it Surface brightness profiles of the $r$-band $(h\nu\sim
+   1\,\ev)$ obtained from stacked clusters in the Sloan Digital Sky
    Survey (SDSS) at the redshift $z \sim 0.25$ \protect
@@
    line that is fitted to only the ICL and the BCG. Note that, we use
-   total SD brightness in the cluster center ($S_\sd^\rmn{tot}(0)$) to
-   normalize the SD surface brightness profiles.}
+   total SD brightness in the cluster center
+   $(S_\sd^\rmn{tot}(0))$ to normalize the SD surface
+   brightness profiles.}
  \label{fig:SD_spatial}
@@
 \end{align}
-and for the smooth model
+For the smooth model, which is also our benchmark SD model, we find:
 \begin{align}
@@
 
-The spatial distribution of the SD energy density is an important
+The spatial distribution of the energy density of SD is an important
 quantity since it impacts the steady state electron and positron
-distribution through cooling. A higher energy density of SD photons in
+distribution through cooling; a high energy density of SD photons in
 a cluster suppresses the gamma-ray flux from IC upscattered
@@
 Fig.~\ref{fig:SD_Edens} for a galaxy cluster with the mass
-$\mvir=6\times10^{14}\msun$.
-
-\del{ we compare the energy densities from different radiation fields
-  in a galaxy cluster with the mass $\mvir=6\times10^{14}\msun$. We
-  use two different profiles for the SD energy density, where the
-  total profile includes the contribution from the ICL, the BCG and
-  all the galaxies, while the galaxies are excluded in the smooth
-  profile. We find that even for a cluster with a relative small mass
-  the energy density of the SD components dominates over the CMB and
-  the magnetic fields (with a central B field of 3~$\mu G$) within
-  about 10\% of $\rvir$. Outside this radius the CMB is dominating the
-  energy density of the cluster, hence the magnetic fields are always
-  subdominant in the cluster and can safely be removed from cluster IC
-  calculations for a reasonable central B-field and spectral
-  index. Note that in this work we keep the contribution from B-fields
-  to the total energy density for consistency.}
+$\mvir=6\times10^{14}\msun$. We find that inside a few percent of of
+$\rvir$ the total energy density is dominated by the light from SD,
+while the CMB is dominating elsewhere. This implies that if the boost
+from dark matter (DM) substructures is significant then the overlap of
+light from SD with the electron and positron distribution that trace
+the substructures is small. Hence the resulting flux from inverse
+Compton (IC) upscattered SD photons is suppressed compared to the IC
+upscattered CMB photons.
 
@@
 \section{Source functions of different DM models}
-We use {\sc DarkSUSY} to derive the spectra for the continuum emision
-from the DM BM models. These spectra is shown in the left panel of
-Fig.~\ref{fig:q_DM}. We fit the source function using the following
-functional form
+We use {\sc DarkSUSY} to derive the spectra for the continuum emission
+from our four DM benchmark (BM) models. These spectra are shown in the
+left panel of Fig.~\ref{fig:q_DM}. We choose to fit the source
+function using the following functional form
 \begin{eqnarray}
@@
 \end{eqnarray}
-where the model specific parameters are given by:
-
-%     egn    = eg/GeV
-%     diffBM = (p1*dexp(-egn**(-p2))/(1.+dexp(egn**p3))
-%     1      + p5**(4.-pow1)*p4*egn**pow1*dexp(-(egn/p5)**pow2))
-%     2      / (egn*GeV)
-
-\begin{table}
+where the model specific parameters are given in
+Tab.~\ref{tab:bm_cont}.
+
+\begin{table}[h]
 \begin{tabular}{c c c c c }
@@
 \begin{quote}
-The best fit parameters to the continuum emision from our
+The best fit parameters to the continuum emission from our
 supersymmetric BM models.
@@
 \end{table}
-Again we use {\sc DarkSUSY} to derive the number of electrons amd
-positons resulting from each annihilating pair. This spectra is shown
-in the right panel of Fig.~\ref{fig:q_DM}. The electron and positon
+
+Again we use {\sc DarkSUSY} to derive the number of electrons and
+positrons resulting from each annihilating pair. This spectra is shown
+in the right panel of Fig.~\ref{fig:q_DM}. The electron and positron
 yield resulting from our supersymmetric BM model is fitted using
 \begin{eqnarray}
-N_{\e,\rmn{BM}}(>\ee) &=& \frac{a_1}{\eet^{a_2}}\times
-\frac{\left[1+\left(\frac{\eet}{a_6}\right)^{a_7}\right]^{a_8}}
-{\left[1+\left(\frac{\eet}{a_3}\right)^{a_4}\right]^{a_5}}
+N_{\e,\rmn{BM}}(>\ee) &=& \frac{b_1}{\eet^{b_2}}\times
+\frac{\left[1+\left(\frac{\eet}{b_6}\right)^{b_7}\right]^{b_8}}
+{\left[1+\left(\frac{\eet}{b_3}\right)^{b_4}\right]^{b_5}}
 \times\theta(\ee-m_\chi\,c^2)\,,\nonumber\\
@@
 \end{eqnarray}
-We find the following best fit parameters.
-\begin{table}
+The best fit parameters are given in Tab.~\ref{tab:bm_elec}.
+\begin{table}[h]
 \begin{tabular}{c c c c c c c c c}
@@
 \hline
- BM model & $a_1$ & $a_2$ & $a_3$ & $a_4$ & $a_5$ & $a_6$ & $a_7$ & $a_8$ \\
+ BM model & $b_1$ & $b_2$ & $b_3$ & $b_4$ & $b_5$ & $b_6$ & $b_7$ & $b_8$ \\
  \hline
@@
 \end{table}
+
 Once again, we use {\sc DarkSUSY} to derive the electron and positron
@@
 \begin{eqnarray}
-N_{\e,\rmn{LP}\mu}(>\ee) &=& \exp\left\{a_1+\log\left(1-x\right)+
-a_3\left[\log\left(1-x\right)\right]^2\right\}
+N_{\e,\rmn{LP}\mu}(>\ee) &=& \exp\left(c_1+c_2\,y+c_3\,y^2\right)
 \,,\nonumber\\
-\rmn{where}\quad a_1&=&0.719,\,a_2=2.27,\,a_3=0.200,\,\quad\rmn{and}\nonumber\\
-x&=&\frac{\ee}{m_\chi\,c^2}\,.
+\rmn{where}\quad y&=&\,\log\left(1-x\right)\,,\quad 
+x=\frac{\ee}{m_\chi\,c^2}\,\quad\rmn{and}\nonumber\\
+c_1&=&0.719,\,c_2=2.27,\,c_3=0.200\,.
 \label{eq:lp_elec}
@@
 ($\mu^+/\mu^-,\,\e^+/\e^-$). Hence the resulting electron and positron
-yield for the LP model is given by $N_{\e,\rmn{LP}}(>\ee) =
-1+N_{\e,\rmn{LP}\mu}(>\ee)/2$.
-
-% BM
-%  een = ee/GeV
-%  gmu = 14.d0*een**(-0.06)/(1.d0+(een/1.8d0)**0.9 )**2.0/
-%  &           (1.d0+(een/60.d0)**5 ) !0
-%  gmu = 17.d0*een**(-0.08)/(1.d0+(een/5.5d0)**0.8 )**2.6/
-%  &           (1.d0+(een/250.d0)**5) !1
-%  gmu =(22.d0*een**(-0.05)/(1.d0+(een/1.7d0)**0.85)**2.1*
-%  &           (1.d0+(een/10.d0)**2 )**0.62*dexp(-(een/230.d0)**7)) !2 &3
-%  gmu = 15.d0*een**(-0.14)/(1.d0+(een/5.0d0)      )**1.5/
-%  &           (1.d0+(een/300.d0)**5) !4
-%  gmu = gmu*2d0! acounting for the electrons as well
-
-%LP
-%  gmu = 0.71894+2.27161*dlog(1.-(ee/mX))+
-%  &           0.199579*(dlog(1.-(ee/mX)))**2
-%  gmu = dexp(gmu)/2.d0+1.d0
+yield for the LP model is given by 
+\begin{equation}
+N_{\e,\rmn{LP}}(>\ee) =
+1+N_{\e,\rmn{LP}\mu}(>\ee)/2\,.
+\end{equation}
 
 \section{Gas density profile of Fornax}
-
+The X-ray emitting gas in Fornax does not follow a simple
+$\beta$-profile. Instead, based on deep Rosat data and supported by
+Chandra data, it is best modeled by a multicomponent bidimensional
+model \cite{2002ApJ...565..883P}, consisting of: (1) a central
+component ($r<5\,\kpc$); (2) a ``galactic'' component
+($5\,\kpc<r<40\,\kpc$); and (3) an elliptical ICM component
+($r>40\,\kpc$).
+
+In Fig.~\ref{fig:dens_fornax} we show the data points for the electron
+number density ($n_\e$) in Fornax, derived from the deep Rosat data
+presented in reference \cite{2002ApJ...565..883P}, and the the best
+fit density profile together with the individual components. The total
+$n_\e$ profile is derived from their fitted central and galactic
+surface brightness components while we re-fit the ICM component. The
+reason for the re-fitted outer component is the large uncertainty in
+the data points outside $0.2-0.3\rvir$ which we exclude in our
+fit. Instead we assume that the outer slop of $n_\e$ follows the outer
+slope of Fornax in the HIFLUGCS catalogue that is very similar to that
+of the Coma cluster. Deprojecting the fitted surface brightness
+components yields the following electron number density profile:
 \begin{equation}
-n_\e(r) = \sum_i n_i\left[1+\left(\frac{r}{r_{c,i}}\right)^2\right]^{-3\beta_i+0.5}
+n_\e(r) = \left[\sum_i n_i^2\left[1+\left(\frac{r}{r_{c,i}}\right)^2\right]^{-3\beta_i}\right]^{1/2}
 \end{equation}
@@
 \beta_2 = 41\,, \nonumber\\
-&n_3 = 5.7\times10^{-4}\,\rmn{el}\,\rmn{cm}^{-3}\,,
-&&r_{c,3} = 830\,\kpc\,,\,\,\,\,
-\beta_3 = 24\,. \nonumber\\
+&n_3 = 5.4\times10^{-4}\,\rmn{el}\,\rmn{cm}^{-3}\,,
+&&r_{c,3} = 183\,\kpc\,,\,\,\,\,
+\beta_3 = 0.8\,. \nonumber\\
 & &&
@@
 \end{align}
-Note that we remove the contribution of the flat central component
-($i=1$) in the outer parts of the cluster, hence we cut it at about
-$40\,\kpc$.
+Note that we remove the contribution of the flat central component of
+the fit ($i=1$) in the outer parts of the cluster, thus we cut it at
+about $40\,\kpc$.
 
@@
    the Fornax cluster. Black crosses show the density profile inferred
-   from deprojected Chandra and Rosat X-ray surface brightness
-   observations \protect \cite{2002ApJ...565..883P}. The total hybrid
-   profile shown by the red solid line represent the best fit to the
-   data, where the fitted individual density components are shown by
-   the black dotted lines. The blue solid line shows the single beta
-   density profile inferred from the HIFLUGCS catalogue. Due to
-   insufficient sensitivity of the data to the outer cluster part, we
-   use the outer slope from the HIFLUGCS catalogue that is very
-   similar to that of the Coma cluster.}
+   from deprojected deep Rosat X-ray surface brightness observations
+   \protect \cite{2002ApJ...565..883P}. The total hybrid profile shown
+   by the red solid line represent the best fit to the data, where the
+   fitted individual density components are shown by the black dotted
+   lines. The blue solid line shows the single beta density profile
+   inferred from the HIFLUGCS catalogue. Due to insufficient
+   sensitivity of the data to the outer cluster part, we use the outer
+   slope from the HIFLUGCS catalogue that is very similar to that of
+   the Coma cluster.}
  \label{fig:dens_fornax}
@@
 
+\del{
 \section{Flux tables for the HIFLUGCS catalouge}
 TO BE WRITTEN
-
+}
 \end{document}

### 2011-05-14 paper.tex
appendix

@@
 
-\smallskip We would like to thank Volker Springel for helpful comments.
-A.P. acknowledges NSF grant AST 0908480 for
-support. We would furthermore like to thank KITP for their hospitality
-during the galaxy cluster workshop.  This research was supported in
-part by the National Science Foundation under Grant No. NSF
-PHY05-51164. The work of L.B. was supported by the Swedish Research Council (VR), under contracts no. 621-2009-3915 and 349-2007-8709 (the Oskar Klein Centre).
+\smallskip We would like to thank Volker Springel for helpful
+comments.  A.P. acknowledges NSF grant AST 0908480 for support. We
+would furthermore like to thank KITP for their hospitality during the
+galaxy cluster workshop.  This research was supported in part by the
+National Science Foundation under Grant No. NSF PHY05-51164. The work
+of L.B. was supported by the Swedish Research Council (VR), under
+contracts no. 621-2009-3915 and 349-2007-8709 (the Oskar Klein
+Centre).
 
@@
 In this section we present the details of our model of stars and dust
-(SD) in clusters of galaxies. In the first part we the measured
+(SD) in clusters of galaxies. In the first part we use the measured
 spectral distribution of light from SD in a typical galaxy to derive a
@@
 \subsection{Energy spectrum}
-The SD light from clusters is dominated by the emission from
+The light from SD in clusters is dominated by the emission from
 galaxies. This radiation is expected to leak out into the much larger
-volume of the intra-cluster medium, hence we approximate the spectral
-distribution of the intra-cluster light (ICL) with the light from
-galaxies. We use the far IR to UV spectrum derived in reference
+volume of the intra-cluster medium (ICM), hence we approximate the
+spectral distribution of the intra-cluster light (ICL) with the light
+from galaxies. We use the far IR to UV spectrum derived in reference
 \cite{2006ApJ...648L..29P} for a Milky Way (MW) type galaxy to
@@
 represented by $E_{i,\vir}$. We relate this energy to the luminosity
-$L_i$ of each respective wavelength band (optical and IR light for the
+$L_i$ in each respective wavelength band (optical and IR light for the
 dust, and UV light for the stars) using
@@
 Here we approximate the total energy of the photons within $\rvir$
-with the luminosity \cite{2008A&A...490..547G} multiplied the typical
-timescale it takes for a photon to propagate through the cluster (we
-assume that the cluster is optically thin).
+with the SD luminosity multiplied the typical timescale it takes for a
+photon to propagate through the cluster (we assume that the cluster is
+optically thin).
 
@@
 $L_\odot=1.17\times10^{33}\,\rmn{erg\,s}^{-1}$, and distance to the
-cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. To account for different
-cluster masses, we attach a simple mass scaling to the luminosity from
-the stars in clusters in Eq.~(\ref{eq:L_stars}).  Since a large
-contribution of the total starlight in a cluster comes from the
-brightest cluster galaxy (BCG), we assume that the total starlight has
-the same halo mass scaling as the BCG \cite{2010ApJ...713.1037H}
+cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. Furthermore, to account for
+different cluster masses, we attach a simple mass scaling to the
+luminosity from the stars in Eq.~(\ref{eq:L_stars}). Here we assume
+that the total starlight has the same halo mass scaling as the
+brightest cluster galaxy (BCG) \cite{2010ApJ...713.1037H}, which is a
+reasonable assumption since a large contribution of the total
+starlight in a cluster comes from the BCG. The starlight luminosity as
+a function of mass is given by
 \begin{equation}
@@
 normalized with the central surface brightness of the total SD
-component ($S_\sd^\rmn{tot}(0)$). Our benchmark spatial model is shown
+component ($S_\sd^\rmn{tot}(0)$). Our spatial benchmark model is shown
 with the solid black line, and include the contribution from the ICL
@@
 where we found the following best fitted normalized central brightness
-($S_i$), core radius ($r_{\mathrm{c}_i}$), and slope ($\beta_i$) for
-the total model:
+($\tilde{S}_i$), core radius ($r_{\mathrm{c}_i}$), and slope
+($\beta_i$) for the total model:
 \begin{align}
@@
 \end{eqnarray}
-where we have used that specific energy density of the SD light given
-by Eq.~(\ref{eq:u_SD_er}). Note that we compare the energy density
-$u_\sd(r)$ to other radiation background fields in
+where we have used the specific energy density of the light from SD
+given by Eq.~(\ref{eq:u_SD_er}). Note that we compare the energy
+density $u_\sd(r)$ to other radiation background fields in
 Fig.~\ref{fig:SD_Edens} for a galaxy cluster with the mass
@@
 while the CMB is dominating elsewhere. This implies that if the boost
-from dark matter (DM) substructures is significant then the overlap of
+from dark matter (DM) substructures is significant, then the overlap of
 light from SD with the electron and positron distribution that trace
@@
 \section{Source functions of different DM models}
-We use {\sc DarkSUSY} to derive the spectra for the continuum emission
-from our four DM benchmark (BM) models. These spectra are shown in the
-left panel of Fig.~\ref{fig:q_DM}. We choose to fit the source
-function using the following functional form
+We use {\sc DarkSUSY} to derive the spectral distribution of the
+continuum emission from our four DM benchmark (BM) models. These
+spectra are shown in the left panel of Fig.~\ref{fig:q_DM}. We choose
+to fit the source function using the following functional form
 \begin{eqnarray}
@@
 \end{tabular}
-\begin{quote}
-The best fit parameters to the continuum emission from our
-supersymmetric BM models.
- \label{tab:bm_cont}
-  \end{quote}
+\caption{The best fit parameters to the continuum emission from our
+  supersymmetric benchmark models.
+ \label{tab:bm_cont}}
 \end{table}
 
-Again we use {\sc DarkSUSY} to derive the number of electrons and
-positrons resulting from each annihilating pair. This spectra is shown
-in the right panel of Fig.~\ref{fig:q_DM}. The electron and positron
+Once again we use {\sc DarkSUSY} to derive the number of electrons and
+positrons resulting from each annihilation. This spectra is shown in
+the right panel of Fig.~\ref{fig:q_DM}. The electron and positron
 yield resulting from our supersymmetric BM model is fitted using
@@
 \end{tabular}
-\begin{quote}
-The best fit parameters to the electron and positron yield from the DM
-BM models above the electron energy $\ee$.
- \label{tab:bm_elec}
-  \end{quote}
+\caption{The best fit parameters to the electron and positron yield
+  above the electron energy $\ee$ from the dark matter benchmark
+  models.
+ \label{tab:bm_elec}}
 \end{table}
 
-Once again, we use {\sc DarkSUSY} to derive the electron and positron
+Finally, we use {\sc DarkSUSY} to derive the electron and positron
 yield resulting from LP DM annihilating into decaying muons. We find
@@
 \end{eqnarray}
-It should be noted that the LP model we are using has a branching
-factor branching ratio of ($1/2,\,1/2$) into
+It should be noted that the LP model that we are using in this work
+has a branching factor branching ratio of ($1/2,\,1/2$) into
 ($\mu^+/\mu^-,\,\e^+/\e^-$). Hence the resulting electron and positron
@@
 number density ($n_\e$) in Fornax, derived from the deep Rosat data
-presented in reference \cite{2002ApJ...565..883P}, and the the best
-fit density profile together with the individual components. The total
+presented in reference \cite{2002ApJ...565..883P}, and the best fit
+density profile together with the individual components. The total
 $n_\e$ profile is derived from their fitted central and galactic

### 2011-05-14 paper.tex
updated figures

@@
 
-\affiliation{$^{2}$Heidelberg Institute for Theoretical Studies (HITS), Schloss-Wolfsbrunnenweg 33, DE - 69118 Heidelberg, Germany}
-
-\affiliation{$^{3}$The Oskar Klein Centre for Cosmoparticle Physics, Department
-  of Physics, Stockholm University, AlbaNova University Center, SE - 106 91
-  Stockholm, Sweden}
+\affiliation{$^{2}$Heidelberg Institute for Theoretical Studies
+  (HITS), Schloss-Wolfsbrunnenweg 33, DE - 69118 Heidelberg, Germany}
+
+\affiliation{$^{3}$The Oskar Klein Centre for Cosmoparticle Physics,
+  Department of Physics, Stockholm University, AlbaNova University
+  Center, SE - 106 91 Stockholm, Sweden}
 
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v11.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v12.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v12.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v12.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v12.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
 \caption{\it Comparing the differential flux from different models: we
@@
 \begin{minipage}{2.0\columnwidth}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v11.0.1deg.1.6T.SubMass.elmu.SF300.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv11.0.1deg.SubMass.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v12.0.1deg.1.6T.SubMass.elmu.SF300.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv12.0.1deg.SubMass.noMW.woGal.eps}
 \caption{\it Comparing the flux from different inverse Compton
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v11.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v11.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v11.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v11.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v12.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v12.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v12.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v12.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
 \caption{\it Comparing the gamma-ray emission from different
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v11.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v12.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
  \caption{\it Constraining boost factors using flux upper limits. The
@@
 \begin{figure}
- \includegraphics[width=0.99\columnwidth]{figures/SB.v11.1GeV.SF300.SubMass.elmu.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.v12.1GeV.SF300.SubMass.elmu.eps}
  \caption{\it Comparing the intrinsic surface brightness from
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v11.1GeV.SF300.noSuB.vs.SubMass.elmu.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v12.1GeV.SF300.noSuB.vs.SubMass.elmu.eps}
  \caption{\it The impact of substructures on the intrinsic surface
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.v11.1GeV.SF300.noSuB.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v11.1GeV.SF300.noSuB.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.v12.1GeV.SF300.noSuB.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v12.1GeV.SF300.noSuB.elmu.eps}
   \caption{\it The intrinsic surface brightness profiles without
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v11.SF300.SubMass.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v11.SF300.SubMass.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v12.SF300.SubMass.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v12.SF300.SubMass.elmu.eps}
 \caption{\it Surface brightness predicted for Cherenkov telescopes at

### 2011-05-15 paper.tex
figures updated

@@
  & \,\,\,\,\,         & $1.4\times10^{-12}$ & $2.3\times10^{-13}$ & $1.5\times10^{-12}$ 
- & $13.8$ & $44$  & $1310$ \\
+ & $13.8$ & $60$  & $1040$ \\
  Perseus \,\,\,\,\,\, & $1.4\times10^{-8}$  & $7.1\times10^{-11}$ & $1.4\times10^{-8}$  
  & \,\,\,\,\,         & $1.4\times10^{-12}$ & $2.0\times10^{-13}$ & $5.2\times10^{-12}$ 
- & $7.71$ & $54$  & $1280$ \\
+ & $7.71$ & $70$  & $910$ \\
  Virgo                & $1.2\times10^{-7}$  & $4.0\times10^{-10}$ & $8.7\times10^{-9}$  
  & \,\,\,\,\,         & $1.3\times10^{-11}$ & $1.1\times10^{-12}$ & $3.2\times10^{-12}$ 
- & $2.1$  & $83$  & $870$  \\
+ & $2.1$  & $105$  & $680$  \\
  Fornax               & $4.8\times10^{-8}$  & $1.3\times10^{-10}$ & $2.2\times10^{-10}$ 
  & \,\,\,\,\,         & $5.6\times10^{-12}$ & $3.6\times10^{-13}$ & $8.3\times10^{-14}$ 
- & $1.0$  & $106$ & $730$  \\
+ & $1.0$  & $130$  & $580$  \\
 \hline
@@
 protons. In Section 2 we discuss the theory of DM and gamma-rays. In
-particular, we focus on the LP and supersymmetric DM models
-used in this work, and outline the framework for estimating the
-gamma-ray emission from various radiative processes. In Section 3
-we calculate the gamma-ray fluxes and spectral distributions from four
+particular, we focus on the leptophilic (LP) and supersymmetric DM
+models used in this work, and outline the framework for estimating the
+gamma-ray emission from various radiative processes. In Section 3 we
+calculate the gamma-ray fluxes and spectral distributions from four
 clusters and compare it to upper limits set by Fermi-LAT. For the same
 clusters we derive the gamma-ray surface brightness profiles in
-Section 4. To extend the analysis to more clusters and find
-promising targets we estimate the fluxes from DM and CRs of all
-clusters in the extended HIFLUGCS sample in Section 5. In Section
-6 we conclude and discuss our results.
+Section 4. To extend the analysis to more clusters and find promising
+targets we estimate the fluxes from DM and CRs of all clusters in the
+extended HIFLUGCS sample in Section 5. In Section 6 we conclude and
+discuss our results.
 
@@
   the gamma-ray flux from IC upscattered CMB and continuum emission by
-  570 while the IC upscattered SD photons is boosted by 20. Upper limits
-from Fermi-LAT after 18 months 
- \protect \cite{2010ApJ...717L..71A} are also shown. We find
-  bright prospects for detecting the continuum emission, that is
-  dominating the total emission in the GeV energy range, in the models
-  $\Ip$ and $\Kp$.}
+  730 while the IC upscattered SD photons is boosted by 20. Upper
+  limits from Fermi-LAT after 18 months \protect
+  \cite{2010ApJ...717L..71A} are also shown. We find bright prospects
+  for detecting the continuum emission, that is dominating the total
+  emission in the GeV energy range, in the models $\Ip$ and $\Kp$.}
  \label{fig:diff_BM}
@@
   130 and the enhancement due to substructures from IC upscattered CMB
-  and SD photons is 570 and 20, respectively.}
+  and SD photons is 730 and 20, respectively.}
  \label{fig:IR_comp}
@@
 \begin{figure}
- \includegraphics[width=0.99\columnwidth]{figures/flux.int.v11.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/flux.int.v12.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
  \caption{\it Comparing the energy integrated flux from different
@@
    cluster using a point spread function of $0.1\deg$. The boost from
-   Sommerfeld and substructures is about 130 and 570, respectively. }
+   Sommerfeld and substructures is about 130 and 730, respectively. }
  \label{fig:flux_int}
@@
    the CR induced emission (red), leptophilic emission (green), and
-   emission from the $\Kp$ benchmark model (blue). The different
-   line styles each represent a cluster; Fornax (solid), Coma (dotted),
-   Virgo (dashed), and Perseus (dash-dotted). The boost from
-   Sommerfeld effect and substructures is about 130 and 570,
-   respectively. Notice the very similar shape and normalization of
-   the DM models, while the CRs have a much larger scatter in the
-   profiles due to the large variation of the gas fraction in these clusters.}
+   emission from the $\Kp$ benchmark model (blue). The different line
+   styles each represent a cluster; Fornax (solid), Coma (dotted),
+   Virgo (dashed), and Perseus (dash-dotted). \C{We include the boost
+   from both substructures and Sommerfeld effect.} Notice the very
+   similar shape and normalization of the DM models, while the CRs
+   have a much larger scatter in the profiles due to the large
+   variation of the gas fraction in these clusters.}
  \label{fig:SB_clu}
@@
    the dotted line. The boost from Sommerfeld and substructures is
-   about 130 and 570, respectively. Notice the nearly flat profiles
+   about 130 and 730, respectively. Notice the nearly flat profiles
    when substructures are included, and the relative large boost at

### 2011-05-16 paper.tex
updated text

@@
 %\def\del#1{{\bf (DELETED TEXT)}}
-\def\C#1{#1}
-%\def\C#1{{\bf #1}}
+%\def\C#1{#1}
+\def\C#1{{\bf #1}}
 
@@
 \newcommand{\sigmaannv}{\ensuremath{\langle\sigma v\rangle}}
-\newcommand{\sigv}{\ensuremath{\sigma_v}}
+\newcommand{\sigv}{v_\rmn{cl}}
 \newcommand{\ic}{\rmn{IC}}
@@
   brightest DM sources and find a particularly low CR induced
-  background for Fornax. For a given minimum substructure mass as
-  given by the DM free-streaming scale, one needs the largest DM halo
-  mass to maximize the substructure boost over the smoothly
-  distributed annihilation flux: for galaxy clusters as the largest
-  collapsed objects, we find a boost factor of more than 1000. Since
-  the annihilation flux of substructures is mostly contributed by the
-  regions around the virial radius, the resulting surface brightness
-  profiles are almost flat. This makes it very challenging to detect
-  this flux with imaging air Cherenkov telescopes since their
-  sensitivity drops linearly with radius and they typically have
-  $5-10$ linear resolution elements across a cluster; the gamma-ray
-  satellite Fermi is better suited. Assuming cold dark matter with a
-  substructure mass distribution down to an Earth mass and using Fermi
-  upper limits, we rule out the leptophilic models in their present
-  form in 14 clusters, and limit the boost from Sommerfeld enhancement
-  in Fornax to be less than 2 which corresponds to a value in the
-  Milky Way of less than 5. Alternatively, if the Sommerfeld
-  enhancement factor is realized in Nature, this would imply a
-  limiting substructure mass in Fornax of $\mlim > 10^2\,\msun$ which
-  would be a challenge for structure formation. We find that Fermi
-  three-year data will be able to constrain the smallest mass of
-  substructures for supersymmetric benchmark models or alternatively
-  constrain their cross sections for a given substructure boost. The
-  Fermi upper limits are closing in on our predictions for the CR flux
-  using an analytic model based on cosmological hydrodynamical cluster
-  simulations. We will soon start to constrain the underlying CR
-  physics such as shock acceleration efficiencies or CR transport
-  properties.
+  background for Fornax. \C{For a minimum substructure mass given by
+    the DM free-streaming scale, the largest DM halo mass maximizes
+    the substructure boost over the smoothly distributed annihilation
+    flux: for galaxy clusters as the largest collapsed objects, we
+    find a boost factor of more than 1000.} \del{For a given minimum
+    substructure mass as given by the DM free-streaming scale, one
+    needs the largest DM halo mass to maximize the substructure boost
+    over the smoothly distributed annihilation flux: for galaxy
+    clusters as the largest collapsed objects, we find a boost factor
+    of more than 1000.} Since the annihilation flux of substructures
+  is mostly contributed by the regions around the virial radius, the
+  resulting surface brightness profiles are almost flat. This makes it
+  very challenging to detect this flux with imaging air Cherenkov
+  telescopes since their sensitivity drops linearly with radius and
+  they typically have $5-10$ linear resolution elements across a
+  cluster; the gamma-ray satellite Fermi is better suited. Assuming
+  cold dark matter with a substructure mass distribution down to an
+  Earth mass and using Fermi upper limits, we rule out the leptophilic
+  models in their present form in 14 clusters, and limit the boost
+  from Sommerfeld enhancement in Fornax to be less than 2 which
+  corresponds to a value in the Milky Way of less than
+  5. Alternatively, if the Sommerfeld enhancement factor is realized
+  in Nature, this would imply a limiting substructure mass in Fornax
+  of $\mlim > 10^2\,\msun$ which would be a challenge for structure
+  formation. \C{In addition, we} \del{We} find that Fermi three-year
+  data will be able to constrain the smallest mass of substructures
+  for supersymmetric benchmark models or alternatively constrain their
+  cross sections for a given substructure boost. The Fermi upper
+  limits are closing in on our predictions for the CR flux using an
+  analytic model based on cosmological hydrodynamical cluster
+  simulations. \C{Thus we} \del{We} will soon start to constrain the
+  underlying CR physics such as shock acceleration efficiencies or CR
+  transport properties.
 \end{abstract}
@@
 spectra of antiprotons, positrons, neutrinos and all of the
-electromagnetic spectrum from radio waves to gamma rays
+electromagnetic spectrum from radio waves to gamma-rays
 \cite{Bergstrom:2009ib}. So far, the improvements in direct detection
@@
 system (such as a galaxy cluster) with large velocity dispersion
-$v_{\rm cl}$ the SFE will be smaller than the one expected in a single
-galaxy such as the MW, roughly by a factor $v_{\rm MW}/v_{\rm
-  cl}$.
+$\sigv$ the SFE will be smaller than the one expected in a single
+galaxy such as the MW, roughly by a factor $v_{\rm MW}/\sigv$.
 
@@
 We adopt our benchmark LP model from \cite{Finkbeiner:2010sm} where we
-use a DM mass $m_\chi=1.6$~TeV and a branching ratio of ($1/2,\,1/2$)
-into ($\mu^+/\mu^-,\,\e^+/\e^-$).\footnote{This is an approximation to
-  the model found in \cite{Finkbeiner:2010sm} that has a branching
-  ratio of ($1/3,\,1/3,\,1/3$) into
-  ($\mu^+/\mu^-,\,\e^+/\e^-,\,\pi^+/\pi^-$).} The SFE
-$S=\B_\sfe(\sigv=200\,km/s)\approx 300$ for a MW halo in our LP model,
-which we appropriately scale down for cluster halos, using \del{To
-  connect easily to our previous work \cite{2009PhRvL.103r1302P}, we
-  choose as our benchmark LP model one with mass $1.6$~TeV and
-  Sommerfeld boost $S=\B_\sfe(\sigv=200\,km/s)\approx 300$ for a MW
-  halo and scale this appropriately down for cluster halos, using}
+use a DM mass $m_\chi=1.6$~TeV and a branching ratio of ($1/2:1/2$)
+into ($\mu^+\mu^-:\e^+e^-$).\footnote{This is an approximation to the
+  model found in \cite{Finkbeiner:2010sm} that has a branching ratio
+  of ($1/4:1/4:1/2$) into ($\mu^+\mu^-:\e^+\e^-:\pi^+\pi^-$).}  The
+SFE $S=\B_\sfe(\sigv=200\,\rmn{km}/\rmn{s})\approx 300$ for a MW halo
+in our LP model, which we appropriately scale down for cluster halos,
+using
 \begin{equation}
 \B_\sfe(\sigv) = 0.2\, \frac{c}{\sigv} = 
-49.4 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-1/3}\,,
+62.6 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-1/3}\,,
 \label{eq:B_sfe}
@@
 relic density for a given set of parameters.  Actually, we take
-advantage of so-called benchmark models, which have been proposed in
-different contexts (in particular in \cite{Bringmann:2008kj} giving
-predictions for imaging air Cherenkov telescopes, like  MAGIC II and CTA). They give a good
-representation of models with high enough gamma-ray rates to become
-the first candidates for DM indirect detection in imaging air
-Cherenkov telescopes. We use the following supersymmetric benchmark
-models:
+advantage of so-called benchmark (BM) models, which have been proposed
+in different contexts (in particular in \cite{Bringmann:2008kj} giving
+predictions for imaging air Cherenkov telescopes, like MAGIC II and
+CTA). They give a good representation of models with high enough
+gamma-ray rates to become the first candidates for DM indirect
+detection in imaging air Cherenkov telescopes. We use the following
+supersymmetric BM models:
 
@@
 \item
- $I′$: This model was introduced in \cite{2004EPJC...33..273B}, where
+ $\Ip$: This model was introduced in \cite{2004EPJC...33..273B}, where
   its phenomenology at colliders was studied. Annihilation directly
@@
 
-\item $J′$: This model, also from \cite{2004EPJC...33..273B} is in the
+\item $\Jp$: This model, also from \cite{2004EPJC...33..273B} is in the
   so-called coannihilation tail. The sleptons are nearly degenerate
@@
 
-\item $K′$: A representative model for the funnel region, where the
+\item $\Kp$: A representative model for the funnel region, where the
   annihilation dominantly occurs in the $s$-channel through exchange
@@
 
-\item $J^*$: Annihilation in the so-called coannihilation region,
+\item $\Js$: Annihilation in the so-called coannihilation region,
   introduced in \cite{2008JHEP...01..049B} as BM3, with a particularly
@@
 There are two types of radiative processes which are important for our
-benchmark models, first the usual QED final state radiation (FSR) for
-both the LP model and for supersymmetric models with charged final
-states. In addition, there may be direct emission from a virtual,
-charged, exchanged particle (such as a spin-0 slepton or squark),
-internal bremsstrahlung, IB. The latter is essentially only important
-when there is a helicity suppression for the lowest order annihilation
+BM models, first the usual QED final state radiation for both the LP
+model and for supersymmetric models with charged final states. In
+addition, there may be direct emission from a virtual, charged,
+exchanged particle (such as a spin-0 slepton or squark), internal
+bremsstrahlung, IB. The latter is essentially only important when
+there is a helicity suppression for the lowest order annihilation
 process, which is the case for neutralinos, whose Majorana nature make
@@
 
-The photon spectrum resulting from FSR is universal with only a
-weak dependence of the underlying particle physics model. The photon
-yield from this process is given by (see
+The photon spectrum resulting from final state radiation is universal
+with only a weak dependence of the underlying particle physics
+model. The photon yield from this process is given by (see
 e.g. \cite{2008JHEP...01..049B})
@@
 can be computed using {\sc DarkSUSY}. The differential photon energy
-spectra for all our benchmark models are shown in Fig.~\ref{fig:q_DM}.
-The peaking at high photon energy and the resulting bump caused by
-inner bremsstrahlung is clearly seen for benchmark models $I´$, $J´$,
-and $J^*$. Despite the different particle masses and cross sections,
-the spectrum of the continuum emission shows a remarkably similar
-shape which suggests that a simple rescaling of particle masses
-(responsible for the exponential cutoff in the spectrum) and cross
-sections (spectral amplitude) should yield a roughly scale-invariant
-continuum emission spectrum except for the presence of the final state
-emission feature which depends on the details of the specific decay
+spectra for all our BM models are shown in Fig.~\ref{fig:q_DM}.  The
+peaking at high photon energy and the resulting bump caused by inner
+bremsstrahlung is clearly seen for BM models $\Ip$, $\Jp$, and
+$\Js$. Despite the different particle masses and cross sections, the
+spectrum of the continuum emission shows a remarkably similar shape
+which suggests that a simple rescaling of particle masses (responsible
+for the exponential cutoff in the spectrum) and cross sections
+(spectral amplitude) should yield a roughly scale-invariant continuum
+emission spectrum except for the presence of the final state emission
+feature which depends on the details of the specific decay
 channels. The right panel of Fig.~\ref{fig:q_DM} shows the cumulative
@@
 (LP-IC), leptophilic DM emitting final state radiation (LP-FSR),
-supersymmetric DM benchmark models where annihilating neutralinos
-generate $\rmn{e}^+/\rmn{e}^-$ pairs that upscatter background photons
-(BM-IC) and emit a continuum as well as final state radiation
-(BM-Cont), and CR proton induced $\pi^0$ that decays into gamma-rays
+supersymmetric DM BM models where annihilating neutralinos generate
+$\rmn{e}^+/\rmn{e}^-$ pairs that upscatter background photons (BM-IC)
+and emit a continuum as well as final state radiation (BM-Cont), and
+CR proton induced $\pi^0$ that decays into gamma-rays
 (CR-$\pi^0$). The source function is given by
@@
 \end{equation}
-the differential CR to gamma-ray source function is denoted by
-$\qCR(\eg,r)$ (see Sect.~\ref{sect:CRs} and \cite{2010MNRAS.409..449P}
-for further details). The subscript $i$ runs over the gamma-ray
-producing DM channels and the total differential boost factor for DM
-is given by:
+\C{where} the differential CR to gamma-ray source function is denoted
+by $\qCR(\eg,r)$ (see Sect.~\ref{sect:CRs} and
+\cite{2010MNRAS.409..449P} for further details). The subscript $i$
+runs over the gamma-ray producing DM channels and the total
+differential boost factor for DM is given by:
 \begin{eqnarray}
@@
 producing channels, each with the spectrum $\dd
-  \ngammaj /\dd\eg$ and annihilation cross-section $\sigmaannv_j$.
+  \ngammaj /\dd\eg$ and annihilation cross section $\sigmaannv_j$.
 We denote the DM mass with $\mx$ and the smooth DM density profile
@@
 where the difference is mainly built up at a few percent of
-$\rvir$. The increase in luminosity due to substructure is neglible in
+$\rvir$. The increase in luminosity due to substructures is neglible in
 the center of halos, but integrated out to $\rvir$ the boost relative
@@
 the energy of the background photon field. We represent the Thomson
-cross-section with $\sigma_\rmn{T}$ and the full differential
-Klein-Nishina (KN) cross-section is captured by
+cross section with $\sigma_\rmn{T}$ and the full differential
+Klein-Nishina (KN) cross section is captured by
 \cite{1970RvMP...42..237B}:
@@
 \end{equation}
-The full KN cross-section accounts for the less efficient energy
+The full KN cross section accounts for the less efficient energy
 transfer between the photon and electron once the energy of the
@@
 (IR) to ultra-violet (UV) light emitted by SD. The number density for
-the SD is given by $n_\ph\equiv\dd^2 N_\ph/ (\dd V \,\dd \eph) (\eph,r)=
-u_\sd(\eph,r) /\eph^2$ where the SD energy density $u_\sd(\eph,r)$ is
-given in the Appendix, Eq.~(\ref{eq:u_SD_er}). We model the CMB photon
-spectrum as a photon gas that is isotropically distributed and follows
-a black body spectrum with the temperature $T=2.73\,$~K:
+the SD is given by $n_\ph\equiv\dd^2 N_\ph/ (\dd V \,\dd \eph)
+(\eph,r)= u_\sd(\eph,r) /\eph^2$ where the \C{specific} SD energy
+density $u_\sd(\eph,r)$ is given in the Appendix,
+Eq.~(\ref{eq:u_SD_er}). We model the CMB photon spectrum as a photon
+gas that is isotropically distributed and follows a black body
+spectrum with the temperature $T=2.73\,$~K:
 \begin{equation}
@@
 flux frozen magnetic fields. (3) IC losses on starlight and dust with
-an energy density $u_\sd(r)$ given by Eq.~(\ref{eq:u_SD_r}), which we
-derive in the following.
+an energy density $u_\sd(r)$ given by Eq.~(\ref{eq:u_SD_r}), \C{where
+  we outline the derivation} \del{which we derive} in the following.
 
@@
 \cite{2009MNRAS.399.1694G}). Three distinctive components dominate
-these wavelengths: a central galaxy, the intra-cluster light, and
-individual cluster galaxies. We decided to use the accurately measured
-spectral shape of dust and starlight in the interstellar medium of our
-Galaxy to model the emission from clusters. We then normalize the two
-spectral components -- far IR dust and starlight at wavelengths
-ranging from the near IR to UV -- individually by using stacked
-cluster data and employ a measured mass-to-starlight luminosity
-scaling relation derived from observations of the brightest cluster
-galaxy \cite{2010ApJ...713.1037H}.
+these wavelengths: a central galaxy, the intra-cluster light (ICL),
+and individual cluster galaxies. We decided to use the accurately
+measured spectral shape of dust and starlight in the interstellar
+medium of our Galaxy to model the emission from clusters. We then
+normalize the two spectral components -- far IR dust and starlight at
+wavelengths ranging from the near IR to UV -- individually by using
+stacked cluster data and employ a measured mass-to-starlight
+luminosity scaling relation derived from observations of the brightest
+cluster galaxy (BCG) \cite{2010ApJ...713.1037H}.
 
@@
 \lesssim (r_\rmn{s} / r_{200,~\rmn{gal}})^3 \sim c_\rmn{gal}^{-3} \sim
-10^{-3}$ and $N_\rmn{gal} M_\rmn{gal} \sim 0.1 M_\rmn{clu}$.
+10^{-3}$ and $N_\rmn{gal} M_\rmn{gal} \sim 0.1 M_\rmn{clu}$. \C{We
+  denote the number of galaxies within $\rvir$ with $N_\rmn{gal}$ and
+  the concentration of a galaxy with $c_\rmn{gal}$.}
 
@@
 SD model.
-
-\del{
-found the IR to X-ray luminosity scaling relation found in
-\cite{2008A&A...490..547G}. 
-}
 
@@
 emission that often resembles that observed in thermal X-rays. This
-can be easily achievd in the hadronic model since the long cooling
+can be easily achieve in the hadronic model since the long cooling
 time of cosmic ray protons (CRs) allows for an extended and large
@@
 electrons and positrons that IC upscatter background radiation fields
-to high energies. We also consider a few supersymmetric DM models with
+to high energies. We also consider a four supersymmetric DM models with
 a high gamma-ray yield in the form of continuum emission and IC
@@
 emission to the differential gamma-ray upper limits set by Fermi-LAT
-after 18 months of observations \cite{2010ApJ...717L..71A}, 
-we find
+after 18 months of observations \cite{2010ApJ...717L..71A}, we find
 that the upper limits are not violated. The predicted DM flux that is
@@
 be probed by the Fermi three-year data. Furthermore, the gamma-ray
-signal induced by CRs is expected to be about a factor 5--10 below
-the DM continuum flux from the $\Kp$ and $\Ip$ BM models at
+signal induced by CRs is expected to be about a factor 5--10 below the
+DM continuum flux from the $\Kp$ and $\Ip$ BM models at
 10~GeV. However, the IC emission from upscattered CMB and SD photons
-is at least a factor 10 lower than the expected flux from CRs above
-100~MeV, making it very hard to distinguish such a signal from the
-foreground due to the similar spectral index. For energies below
+is at least a factor \C{few lower for $\Kp$ and a factor 1000 lower
+  for $\Ip,\Jp,\Js$,} \del{10 lower} than the expected flux from CRs
+above 100~MeV, making it very hard to distinguish such a signal from
+the foreground due to the similar spectral index. For energies below
 100~MeV we expect IC emission by primary shock accelerated electrons
@@
 induced leptons. Hence in clusters, the IC emission from
-supersymmetric DM benchmark models be  neglected compared to the
-CR pion and DM continuum emission.
+supersymmetric DM BM models be neglected compared to the CR pion and
+DM continuum emission.
 
@@
 
-One of the main contributions to the expected extended gamma-ray flux
-is coming from the IC upscattered photons on various photon background
-fields. Depending on the spatial and spectral distribution of
-electrons and positrons as well as the photon background field, the
-resulting spectral distributions of gamma-ray can differ
-greatly. Hence it is interesting to understand which spectral features
-and energy regimes  are dominating for the different DM models.
+\C{For the LP DM models, however,}\del{One of} the main contributions
+to the expected extended gamma-ray flux is coming from the IC
+upscattered photons on various photon background fields. Depending on
+the spatial and spectral distribution of electrons and positrons as
+well as the photon background field, the resulting spectral
+distributions of gamma-ray can differ greatly. Hence it is interesting
+to understand which spectral features and energy regimes are
+dominating.\del{for the different DM models.}
 
@@
 upscattered SD photons relative to the IC upscattered CMB photons, the
-FSR, and the continuum emission. However, if substructures are only
-marginally dominating over the smooth distribution in a cluster, the
-SD component becomes relatively more important.
+final state radiation, and the continuum emission. However, if
+substructures are only marginally dominating over the smooth
+distribution in a cluster, the SD component becomes relatively more
+important.
 
@@
 comparison, we include the contribution of IC upscattered SD photons
-and to bracket the uncertainty in the SD model, with a smaller amount of
-dust. In this low-dust model, we have reduced the energy in dust by a
-factor 10. However, we find that the IC SD flux only decreases by a
-factor 3 since the IC cooling of the electrons and positrons also
-decreases. Note that for a smaller boost from substructures, the
-effect from cooling is smaller.
-
- \del{This
-  suppression is also seen in the relative normalization of the flux
-  where the IC from both CMB and dust photons are lower compared to
-  the starlight simply because the starlight has a higher energy,
-  hence it is upscattered by more abundant low energy electrons and
-  positrons (c.f. Fig.~\ref{fig:q_DM}).}
-\del{Even though the SD component seems to be suppressed compared to
-  the CMB at energies around 100~MeV, it has a relative large impact
-  on the steady state electron spectrum. If we remove the SD cooling,
-  we find a factor two larger IC flux at low energies for a cluster of
-  the size of Fornax. For more massive clusters we expect a larger IC
-  flux from the SD component, but a smaller contribution from the CMB
-  because of the more effective cooling.}
+and to bracket the uncertainty in the SD model, with a smaller amount
+of dust. In this low-dust model, we have reduced the energy in dust by
+a factor 10. \C{However, the resulting flux from the IC upscattered
+  dust in this model only decreases with a factor that is slightly
+  smaller than 10 since the IC cooling of the electrons and positrons
+  also decreases.}\del{However, we find that the IC
+  SD flux only decreases by a factor 3 since the IC cooling of the
+  electrons and positrons also decreases. Note that for a smaller
+  boost from substructures, the effect from cooling is smaller.}
 
@@
   assumptions such as Sommerfeld and/or substructure boost are in
-  conflict with the upper limit. We also show projected CTA point
-  source sensitivities ($5\sigma$, 50h).  All fluxes are calculated
+  conflict with the upper limit. \del{We also show projected CTA point
+  source sensitivities ($5\sigma$, 50h).}  All fluxes are calculated
   for the Fornax cluster within $\rvir$ using a point spread function
@@
  \caption{\it Comparing the energy integrated flux from different
-   models. We show the emission from; CR induced emission (red
-   solid), leptophilic (LP) models that include both final state
-   radiation and IC upscattered CMB, dust and starlight (green
-   dash-dotted), and benchmark $\Kp$ models (BM) include continuum
-   emission, and IC upscattered CMB, dust and starlight (blue
-   dashed). The black arrow show the integrated flux upper limit set
-   by Fermi-LAT again indicating challenges for the assumptions
-   underlying the LP model. The emission is calculated for the Fornax
+   models. We show the emission from; CR induced emission (red solid),
+   leptophilic (LP) models that include both final state radiation and
+   IC upscattered CMB, dust and starlight (green dash-dotted), and
+   benchmark $\Kp$ models (BM) include continuum emission, and IC
+   upscattered CMB, dust and starlight (blue dashed). The black arrow
+   show the integrated flux upper limit set by Fermi-LAT again
+   indicating challenges for the assumptions underlying the LP
+   model. \C{We also show projected CTA point source sensitivities
+     ($5\sigma$, 50h).} The emission is calculated for the Fornax
    cluster using a point spread function of $0.1\deg$. The boost from
-   Sommerfeld and substructures is about 130 and 730, respectively. }
+   Sommerfeld and substructures is about 130 and 730, respectively.}
  \label{fig:flux_int}
@@
 in low mass clusters compared to the total gamma-ray flux.
-
-\del{Furthermore, the low mass clusters have a higher flux from IC
-  upscattered SD photons than high mass clusters which increase the
-  importance of the SD component in low mass clusters even more
-  (c.f. Fig.~\ref{fig:IR_comp}).}
-
-\del{
-\begin{eqnarray}
-L_{\gamma,\rmn{sub tot}} \propto N\,L_{\gamma,\sub} \propto N\,M_\sub 
- \propto M_\sub^{\left(A+1\right)}\,\frac{\dd N_\sub}{\dd M} \propto  M^{A-0.9}
-\end{eqnarray}
-Assuming that the concentration $c$ decrease for increasing mass as it
-does for the mass range $10^{12}-10^{14}\,\msun$ where
-$L_{\gamma,\sub} \propto N\,M_\sub^A$, where $A<1$.
-}
 
@@
    too small to support the DM annihilation hypothesis for the
-   Pamela/Fermi excess.}
+   PAMELA/Fermi excess.}
  \label{fig:boost_const}
@@
 
-\del{The shape trace the underlying density slope of $-3$, which is
-  expected for IC upscattered CMB photons. This picture is confirmed
-  by the components study in the right panel that show the negligible
-  contribution at this energy from the IC upscattered SD photons that
-  follow a steeper distribution in the outer parts because of the
-  decreasing energy density of SD photons with radius. Since the
-  surface brightness from BM models are dominated by the continuum
-  emission at each radial bin in all clusters, we find that the total
-  DM BM emission follows the projected density profile over the entire
-  clusters. In addition, the sum of the IC upscattered photons for the
-  LP model approximately trace the same distribution, although with
-  the exception in the core regime where we find a transition from
-  centrally dominating IC SD light to the IC CMB light. The transition
-  is due to the IC upscattered CMB photons that trace the smooth
-  profile in the core and outer parts of the cluster, while the
-  electron and positron population suffers from efficient cooling on
-  light from SD in the center which flatten the IC CMB
-  profile. Conversely trace the LP IC emission from SD photons a
-  steeper distribution in the center that follows the projected
-  density profile. This is explained by the SD dominated cooling that
-  cancels the spatial dependence from the SD source function.
-%
-  In the left panel we also find some variation in the profiles for
-  the different clusters in the central parts. Especially in the
-  Fornax cluster, where we find a factor two larger flux compared to
-  the other clusters. This is due to more efficient SD cooling of the
-  dominating IC upscattered CMB photons in Fornax; a low X-ray
-  luminous cluster has a low energy density in starlight and dust in
-  our analytic SD model.}
-
 \begin{figure*}
@@
 gamma-ray flux from the LP model was dominated at high energies of
-about $100\,$~GeV by FSR and IC upscattered starlight and dust, while
-the BM models were mainly dominated by the continuum emission. These
-high energies are observationally important for both Fermi-LAT and
-Cherenkov telescopes. In Fig.~\ref{fig:SB_IACTs}, we thus show the
-surface brightness above $100\,$~GeV for a realistic PSF of $0.1\deg$
-where we include the boost from substructures. We investigate two
-clusters with an expected high DM signal; the Fornax and Virgo
-cluster. Both clusters show a very flat brightness profile
-$r<0.1\rvir$, due to both the effect from substructures and the
-smoothing over the PSF. The CR induced emission also show a
-smoothing in the central parts due to the PSF. In the outer part of
-the Fornax cluster the CR flux is suppressed compared to the DM flux
-boosted by substructures, where the LP model gives rise to a gamma-ray
-flux that is more than three orders of magnitude larger. However, it
-should be noted that there are large uncertainties in the gas density
-profile which we use to estimate the CR induced gamma-ray surface
-brightness (see Fig.~\ref{fig:dens_fornax} for more details).
+about $100\,$~GeV by final state radiation and IC upscattered
+starlight and dust, while the BM models were mainly dominated by the
+continuum emission. These high energies are observationally important
+for both Fermi-LAT and Cherenkov telescopes. In
+Fig.~\ref{fig:SB_IACTs}, we thus show the surface brightness above
+$100\,$~GeV for a realistic PSF of $0.1\deg$ where we include the
+boost from substructures. We investigate two clusters with an expected
+high DM signal; the Fornax and Virgo cluster. Both clusters show a
+very flat brightness profile $r<0.1\rvir$, due to both the effect from
+substructures and the smoothing over the PSF. The CR induced emission
+also show a smoothing in the central parts due to the PSF. In the
+outer part of the Fornax cluster the CR flux is suppressed compared to
+the DM flux boosted by substructures, where the LP model gives rise to
+a gamma-ray flux that is more than three orders of magnitude
+larger. However, it should be noted that there are large uncertainties
+in the gas density profile which we use to estimate the CR induced
+gamma-ray surface brightness (see Fig.~\ref{fig:dens_fornax} for more
+details).
 
@@
     indicative for all (non-Sommerfeld enhanced) DM annihilation models while
-    the normalization depends on the particular cross-section and neutralino
+    the normalization depends on the particular cross section and neutralino
     mass.}
@@
 \end{figure*}
-The mass scaling of the substructure
-boost steepens the intrinsically shallower DM annihilation relation of
-benchmark models (Eq.~\ref{eq:BM_scaling}) while this steepening is in
-fact over-compensated by the inverse mass scaling of the Sommerfeld
-boost in LP models that prefers smaller halos with a larger ratio of
+The mass scaling of the substructure boost steepens the intrinsically
+shallower DM annihilation relation of BM models
+(Eq.~\ref{eq:BM_scaling}) while this steepening is in fact
+over-compensated by the inverse mass scaling of the Sommerfeld boost
+in LP models that prefers smaller halos with a larger ratio of
 $c/v_\mathrm{circ}$ (Eq.~\ref{eq:LP_scaling}). In contrast, the CR
@@
 dominated by the decaying $\pi^0$ and only show up as a small
-flattening of the scaling relation at energies around $100\,\gev$. The
-steeper mass scaling of the CR compared to the DM implies already a
-general strategy to minimize the CR-induced foreground for DM
-annihilation and argues for very nearby groups. We note that these
-simulations do not include AGN feedback that is thought to furthermore
-reduce the baryon fraction in groups relative to that in clusters
-\cite{2008ApJ...687L..53P}. The resulting smaller target density for
-hadronic CR interactions will furthermore steepen the $L_\gamma-M$
-relation of CR induced emission, making the case for groups even
-stronger.
+flattening of the scaling relation at energies around
+$10-100\,\gev$. The steeper mass scaling of the CR compared to the DM
+implies already a general strategy to minimize the CR-induced
+foreground for DM annihilation and argues for very nearby groups. We
+note that these simulations do not include AGN feedback that is
+thought to furthermore reduce the baryon fraction in groups relative
+to that in clusters \cite{2008ApJ...687L..53P}. The resulting smaller
+target density for hadronic CR interactions will furthermore steepen
+the $L_\gamma-M$ relation of CR induced emission, making the case for
+groups even stronger.
 
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.DM.eps}
-  \caption{\it Fermi gamma-ray flux upper limits are contrasted to the predicted DM
-    gamma-ray flux. We show the mean differential flux in the energy range
-    $E_\gamma=1-10$~GeV for 32 clusters. The Fermi-LAT upper limits are shown
-    with black arrows. The predicted fluxes are derived from the dominant
-    inverse Compton-scattering of CMB photons in a leptophilic DM model (red),
-    and the continuum emission from the DM $\Kp$ benchmark model
-    (blue). Assuming a boost factor due to substructures that has a mass
-    spectrum extending down to Earth masses, the expected leptophilic fluxes are
-    ruled out by upper limits in 14 of the clusters, with the strongest
-    constraints set by Fornax and M49. We can not yet constrain the benchmark
-    models, although our predictions are approaching the upper limits and will
-    allow to test these in the upcoming years with better data.}
+  \caption{\it Fermi gamma-ray flux upper limits are contrasted to the
+    predicted DM gamma-ray flux. We show the mean differential flux in
+    the energy range $E_\gamma=1-10$~GeV for 32 clusters. The
+    Fermi-LAT upper limits are shown with black arrows. The predicted
+    fluxes are derived from the dominant inverse Compton-scattering of
+    CMB photons in a leptophilic DM model (red), and the continuum
+    emission from the DM $\Kp$ benchmark model (blue). Assuming a
+    boost factor due to substructures that has a mass spectrum
+    extending down to Earth masses, the expected leptophilic fluxes
+    are ruled out by upper limits in 14 of the clusters, with the
+    strongest constraints set by Fornax and M49. We can not yet
+    constrain the benchmark models, although our predictions are
+    approaching the upper limits and will allow to test these in the
+    upcoming years with better data.}
  \label{fig14}
@@
 Figure~\ref{fig14} compares Fermi upper limits on the gamma-ray flux
-with predictions of DM annihilation fluxes in the LP and benchmark
-models.  To obtain the gamma-ray fluxes, we scale the virial mass of
-clusters in the extended HIFLUGCS catalogue \cite{2002ApJ...567..716R}
-with our scaling relations of Eqs.~(\ref{eq:BM_scaling}) and
+with predictions of DM annihilation fluxes in the LP and BM models.
+To obtain the gamma-ray fluxes, we scale the virial mass of clusters
+in the extended HIFLUGCS catalogue \cite{2002ApJ...567..716R} with our
+scaling relations of Eqs.~(\ref{eq:BM_scaling}) and
 (\ref{eq:LP_scaling}). In those, we assume a boost factor due to
@@
 masses for our LP and BM DM annihilation models. In the LP models we
-additionally assume a cluster-mass dependent bost due to SFE. Fermi
+additionally assume a cluster-mass dependent boost due to SFE. Fermi
 limits rule out the LP models in their present form with the mentioned
@@
 computed using the analytical model. Statistically, one can view the
-analytical modeling as comtributing to the scatter of the expected
+analytical modeling as contributing to the scatter of the expected
 gamma-ray flux at a given mass. Cool core clusters have a denser core
@@
 
-\del{
-ANDERS: do you need this?
---) The dust turns up at about a factor 100 lower than the stars
---) The other figure show the spectral shape of the IC-star with the same
-spectral shape as the dust, it shows the same gamma-ray slope as the dust
---) The reason why there is only a factor 10 difference in the break in the
-gamma-ray emission between the star and dust is related to the KN. In our CR
-paper, the last figure shows that at $\eg=100\,\tev$, the spectra is suppressed
-with about a factor 10 (also depends on $\alpha_\e$). Since the dust photons
-have a factor 10 higher energy, I expect this suppression at about 10~TeV. For
-star photons the suppression should be at 100~GeV. So the star photons are
-definitely KN suppressed, which explains the earlier break and the steeper
-slope.
-}
-
-%-) Consider having one figure where we compare the Einasto profile, to
-%NFW, NFW w/ beta 0.6, and also the effect of a different concentration
-%mass-scaling relation
-%
-%-) also, plot BM flux vs. psf, for models w/ and w/o substructures
-
 \section{Conclusions}
@@
 In this paper, we study the possibility for detecting gamma-ray
-emission in galaxy clusters. We consider benchmark and leptophilic
-(LP) models of supersymmetric dark matter (DM) as well as cosmic ray
-induced pion decay which is thought to dominate the astrophysical
-signal from clusters. Once supersymmetric cold dark matter decouples
-from the expanding universe it streams and erases any potentially
-present smaller scales. Once gravitational instabilities causes halos
-to collapse, this free-streaming scale imprints as a characteristic
-minimum halo mass $M_\mathrm{min}$ into the hierarchy of structure
-formation and should still survive until the present time as
-substructure within larger halos. It turns out that the boost due to
-substructures dominates over the smooth component for halo masses
-$\mvir>10^3 \msun$ and contributes a constant luminosity for each
-decade in halo mass. The ratio of halo-to-minimum subhalo mass
-$\mvir/M_\mathrm{min}$ is maximized for the largest systems that had
-time to collapse and virialise since the Big Bang -- galaxy
-clusters. The corresponding substructure boost can reach values
-exceeding $10^3$ which should make nearby clusters the brightest DM
-annihilation sources after the MW center and hypothetical very
-close-by DM substructures. Since the number density of substructures
-are distributed according to an Einasto profile, the contribution to
-the annihilation emission from substructures is dominated from radii
-close to the virial radius. This implies an almost flat surface
-brightness profile of the annihilation emission which makes it
-necessary to have the entire cluster in the field-of-view to take
-advantage of the entire substructure boost.  This property makes it
-difficult to detect DM annihilation emission without an enhancement of
-the particle physics cross section over its standard value of $\sigma
-v\sim 3\times 10^{-26} ~\mathrm{cm}^3~\mathrm{s}^{-1}$ with imaging
-air Cherenkov telescopes due to the spatially extended boost from
-substructures of angular extent $\sim 0.5-1\deg$ (as independently
-found by reference \cite{2011arXiv1104.3530S}). In contrast, the
-sensitivity of Cherenkov telescopes drops linearly with radius outside
-the point spread function $\sim 0.1\deg$, unless new background
-subtraction schemes can be found, e.g., for the survey mode of CTA.
+emission in galaxy clusters. We consider benchmark (BM) and
+leptophilic (LP) models of supersymmetric dark matter (DM) as well as
+cosmic ray induced pion decay which is thought to dominate the
+astrophysical signal from clusters. Once supersymmetric cold dark
+matter decouples from the expanding universe it streams and erases any
+potentially present smaller scales. \C{When} \del{Once} gravitational
+instabilities causes halos to collapse, this free-streaming scale
+imprints as a characteristic minimum halo mass $M_\mathrm{min}$ into
+the hierarchy of structure formation and should still survive until
+the present time as substructure within larger halos. It turns out
+that the boost due to substructures dominates over the smooth
+component for halo masses $\mvir>10^3 \msun$ and contributes a
+constant luminosity for each decade in halo mass. The ratio of
+halo-to-minimum subhalo mass $\mvir/M_\mathrm{min}$ is maximized for
+the largest systems that had time to collapse and virialise since the
+Big Bang -- galaxy clusters. The corresponding substructure boost can
+reach values exceeding $10^3$ which should make nearby clusters the
+brightest DM annihilation sources after the MW center and hypothetical
+very close-by DM substructures. \C{CHRISTOPH, I DO NOT THINK THAT AN
+  EINASTO PROFILE IMPLIES THAT THE FLUX IS DOMINATED AROUND RVIR?!?
+  Since the number density of substructures are distributed according
+  to an Einasto profile, the contribution to the annihilation emission
+  from substructures is dominated from radii close to the virial
+  radius.}  This implies an almost flat surface brightness profile of
+the annihilation emission which makes it necessary to have the entire
+cluster in the field-of-view to take advantage of the \C{total}
+\del{entire} substructure boost. This property makes it difficult to
+detect DM annihilation emission without an enhancement of the particle
+physics cross section over its standard value of $\sigma v\sim 3\times
+10^{-26} ~\mathrm{cm}^3~\mathrm{s}^{-1}$ with imaging air Cherenkov
+telescopes due to the spatially extended boost from substructures of
+angular extent $\sim 0.5-1\deg$ (as independently found by reference
+\cite{2011arXiv1104.3530S}). In contrast, the sensitivity of Cherenkov
+telescopes drops linearly with radius outside the point spread
+function $\sim 0.1\deg$, unless new background subtraction schemes can
+be found, e.g., for the survey mode of CTA.
 
@@
 and more importantly, has a comparably low CR induced gamma-ray flux.
-This in principle should allow to detect or constrain some benchmark
-models that have been chosen for the large gamma-ray flux yield with
+This in principle should allow to detect or constrain some BM models
+that have been chosen for the large gamma-ray flux yield with
 three-year Fermi data (or constrain the substructure boost
@@
 continuum emission following the hadronization of the annihilating
-neutralinos in benchmark models which leads to the production of
-charged and neutral mesons which decay finally into electrons,
-neutrinos, and gammas, (ii) inverse Compton (IC) emission by the
-leptons in the final state which up-scatter radiation fields from the
-cosmic microwave background (CMB), dust, and starlight, and (iii) final
-state radiation or internal bremsstrahlung which dominates the highest
-energy emission close to the rest mass of the self-annihilating
-neutralinos (if present in the model under consideration). While this
-final state radiation is sometimes not distinguished from the
-continuum emission contribution, we keep it separate as it dominates
-the very high-energy tail of the gamma-ray spectrum in LP models while
-there the continuum  emission is negligibly low.
+neutralinos in BM models which leads to the production of charged and
+neutral mesons which decay finally into electrons, neutrinos, and
+gammas, (ii) inverse Compton (IC) emission by the leptons in the final
+state which up-scatter radiation fields from the cosmic microwave
+background (CMB), dust, and starlight, and (iii) final state radiation
+or internal bremsstrahlung which dominates the highest energy emission
+close to the rest mass of the self-annihilating neutralinos (if
+present in the model under consideration). While this final state
+radiation is sometimes not distinguished from the continuum emission
+contribution, we keep it separate as it dominates the very high-energy
+tail of the gamma-ray spectrum in LP models while there the continuum
+emission is negligibly low.
 
@@
 the upscattered CMB photons but also from a realistically modeled
-photon field due to dust and starlight extending from infra red to
+photon field due to dust and starlight extending from infra-red to
 optical wavelengths. To this end, we construct a rather simple
@@
 starlight in clusters which can be used for the annihilation emission
-in galaxies with a different spatial profile.  We find that in
-benchmark models, the continuum emission dominates over the IC
-emission of any available radiation field. In the LP models, where the
-continuum emission is low, the IC up-scattering of the CMB dominates
-below 60 GeV. For large clusters, the final state radiation takes then
-over for energies up to the cutoff at $m_\chi c^2 \sim 1$~TeV. In
-small clusters, there is a window around $E_\gamma \sim
-100~\mathrm{GeV}$ where the IC up-scattering of the dust emission
+in galaxies with a different spatial profile.  We find that in BM
+models, the continuum emission dominates over the IC emission of any
+available radiation field. In the LP models, where the continuum
+emission is low, the IC up-scattering of the CMB dominates below 60
+GeV. For large clusters, the final state radiation \C{then takes}
+\del{takes then} over for energies up to the cutoff at $m_\chi c^2
+\sim 1$~TeV. In small clusters, there is a window around $E_\gamma
+\sim 100~\mathrm{GeV}$ where the IC up-scattering of the dust emission
 dominates over the CMB IC emission and the final state radiation. The
@@
 characteristic pion bump at energies around 1~GeV. It is expected to
-dominate the DM annihilation signal in the benchmark models for all
+dominate the DM annihilation signal in the BM models for all
 clusters/groups but Fornax. We conclude that it will be possible to
 rule out the LP model with six years of Fermi data and start to
-constrain some benchmark DM models. Hence this should nicely
-complement direct and accelerator searches for the nature of DM.
+constrain some BM DM models. Hence this should nicely complement
+direct and accelerator searches for the nature of DM.
 
@@
 renormalizing the galactic SD light to match the observed luminosity
-from a cluster in the far infrared (IR) and ultraviolet (UV) bands. In
+from a cluster in the far infra-red (IR) and ultra-violet (UV) bands. In
 the second part we derive the spatial distribution of the SD light
@@
 unitless spatial distribution of SD (derived in
-sect.~\ref{sect:SD_radial}), and $N_i(\mvir)$ denotes the mass
+Sect.~\ref{sect:SD_radial}), and $N_i(\mvir)$ denotes the mass
 dependent normalization for the SD. This function is determined using
@@
 \caption{The best fit parameters to the electron and positron yield
-  above the electron energy $\ee$ from the dark matter benchmark
+  above the electron energy $\ee$ from the supersymmetric benchmark
   models.
@@
 It should be noted that the LP model that we are using in this work
-has a branching factor branching ratio of ($1/2,\,1/2$) into
-($\mu^+/\mu^-,\,\e^+/\e^-$). Hence the resulting electron and positron
+has a branching factor branching ratio of ($1/2:1/2$) into
+($\mu^+\mu^-:\e^+\e^-$). Hence the resulting electron and positron
 yield for the LP model is given by
@@
 \del{
-\section{Flux tables for the HIFLUGCS catalouge}
+\section{Flux tables for the HIFLUGCS catalogue}
 TO BE WRITTEN

### 2011-05-16 paper.tex
text

@@
 in LP models that prefers smaller halos with a larger ratio of
-$c/v_\mathrm{circ}$ (Eq.~\ref{eq:LP_scaling}). In contrast, the CR
-scaling relation is considerably steeper as shown by reference
-\cite{2010MNRAS.409..449P}:
+\C{CHRISTOPH, Should it not be $\sigv$ here instead of
+  $v_\mathrm{circ}$?}  $c/v_\mathrm{circ}$
+(Eq.~\ref{eq:LP_scaling}). In contrast, the CR scaling relation is
+considerably steeper as shown by reference \cite{2010MNRAS.409..449P}:
 \begin{eqnarray}

### 2011-05-16 paper.tex
corrections main part finished

--- 2011-05-16 paper.tex
@@
   brightest DM sources and find a particularly low CR induced
-  background for Fornax. \C{For a minimum substructure mass given by
-    the DM free-streaming scale, the largest DM halo mass maximizes
-    the substructure boost over the smoothly distributed annihilation
-    flux: for galaxy clusters as the largest collapsed objects, we
-    find a boost factor of more than 1000.} \del{For a given minimum
-    substructure mass as given by the DM free-streaming scale, one
-    needs the largest DM halo mass to maximize the substructure boost
-    over the smoothly distributed annihilation flux: for galaxy
-    clusters as the largest collapsed objects, we find a boost factor
-    of more than 1000.} Since the annihilation flux of substructures
-  is mostly contributed by the regions around the virial radius, the
-  resulting surface brightness profiles are almost flat. This makes it
-  very challenging to detect this flux with imaging air Cherenkov
-  telescopes since their sensitivity drops linearly with radius and
-  they typically have $5-10$ linear resolution elements across a
-  cluster; the gamma-ray satellite Fermi is better suited. Assuming
-  cold dark matter with a substructure mass distribution down to an
-  Earth mass and using Fermi upper limits, we rule out the leptophilic
-  models in their present form in 14 clusters, and limit the boost
-  from Sommerfeld enhancement in Fornax to be less than 2 which
-  corresponds to a value in the Milky Way of less than
-  5. Alternatively, if the Sommerfeld enhancement factor is realized
-  in Nature, this would imply a limiting substructure mass in Fornax
-  of $\mlim > 10^2\,\msun$ which would be a challenge for structure
-  formation. \C{In addition, we} \del{We} find that Fermi three-year
-  data will be able to constrain the smallest mass of substructures
-  for supersymmetric benchmark models or alternatively constrain their
+  background for Fornax. For a minimum substructure mass given by the
+  DM free-streaming scale, the largest DM halo mass maximizes the
+  substructure boost over the smoothly distributed annihilation flux:
+  for galaxy clusters as the largest collapsed objects, we find a
+  boost factor of more than 1000. Since the annihilation flux of
+  substructures is mostly contributed by the regions around the virial
+  radius, the resulting surface brightness profiles are almost
+  flat. This makes it very challenging to detect this flux with
+  imaging air Cherenkov telescopes since their sensitivity drops
+  linearly with radius and they typically have $5-10$ linear
+  resolution elements across a cluster; the gamma-ray satellite Fermi
+  is better suited. Assuming cold dark matter with a substructure mass
+  distribution down to an Earth mass and using Fermi upper limits, we
+  rule out the leptophilic models in their present form in 14
+  clusters, and limit the boost from Sommerfeld enhancement in Fornax
+  to be less than 2 which corresponds to a value in the Milky Way of
+  less than 5. Alternatively, if the Sommerfeld enhancement factor is
+  realized in Nature, this would imply a limiting substructure mass in
+  Fornax of $\mlim > 10^2\,\msun$ which would be a challenge for
+  structure formation. In addition, we find that Fermi three-year data
+  will be able to constrain the smallest mass of substructures for
+  supersymmetric benchmark models or alternatively constrain their
   cross sections for a given substructure boost. The Fermi upper
@@
   analytic model based on cosmological hydrodynamical cluster
-  simulations. \C{Thus we} \del{We} will soon start to constrain the
-  underlying CR physics such as shock acceleration efficiencies or CR
-  transport properties.
+  simulations. Thus we will soon start to constrain the underlying CR
+  physics such as shock acceleration efficiencies or CR transport
+  properties.
 \end{abstract}
@@
 \end{equation}
-\C{where} the differential CR to gamma-ray source function is denoted
+where the differential CR to gamma-ray source function is denoted
 by $\qCR(\eg,r)$ (see Sect.~\ref{sect:CRs} and
@@
 where the difference is mainly built up at a few percent of
-$\rvir$. The increase in luminosity due to substructures is neglible in
-the center of halos, but integrated out to $\rvir$ the boost relative
-to the smooth emission profile amounts to approximately 20 for dwarf
-galaxies, $200$ for galaxies, and $10^3$ for galaxy clusters.
+$\rvir$. The increase in luminosity due to substructures is neglible
+in the center of halos, but integrated out to $\rvir$ the boost
+relative to the smooth emission profile amounts to approximately 20
+for dwarf galaxies, $200$ for galaxies, and $10^3$ for galaxy
+clusters. These boost factors are only realized for direct
+annihilation emission (continuum emission or final state radiation) or
+IC scattering off homogeneous seed photon fields (CMB). For IC
+scattering of SD photons, the overlap of final state leptons and SD
+photons is smaller which causes the substructure boost over the smooth
+emission to be reduced by roughly two orders of magnitudes.
+
 \begin{figure}%[t]
@@
 the SD is given by $n_\ph\equiv\dd^2 N_\ph/ (\dd V \,\dd \eph)
-(\eph,r)= u_\sd(\eph,r) /\eph^2$ where the \C{specific} SD energy
+(\eph,r)= u_\sd(\eph,r) /\eph^2$ where the specific SD energy
 density $u_\sd(\eph,r)$ is given in the Appendix,
@@
 flux frozen magnetic fields. (3) IC losses on starlight and dust with
-an energy density $u_\sd(r)$ given by Eq.~(\ref{eq:u_SD_r}), \C{where
-  we outline the derivation} \del{which we derive} in the following.
+an energy density $u_\sd(r)$ given by Eq.~(\ref{eq:u_SD_r}), where
+  we outline the derivation in the following.
 
@@
 \lesssim (r_\rmn{s} / r_{200,~\rmn{gal}})^3 \sim c_\rmn{gal}^{-3} \sim
-10^{-3}$ and $N_\rmn{gal} M_\rmn{gal} \sim 0.1 M_\rmn{clu}$. \C{We
-  denote the number of galaxies within $\rvir$ with $N_\rmn{gal}$ and
-  the concentration of a galaxy with $c_\rmn{gal}$.}
+10^{-3}$ and $N_\rmn{gal} M_\rmn{gal} \sim 0.1 M_\rmn{clu}$. We denote
+the number of galaxies within $\rvir$ with $N_\rmn{gal}$ and the
+concentration of a galaxy DM halo with $c_\rmn{gal}$.
 
@@
 Fornax cluster which is one of the best clusters for indirect DM
-searches due to its relative high DM induced fluxes and low CR induced
-fluxes. We show the emission for four different supersymmetric BM
+searches due to its relative high DM annihilation fluxes and low CR induced
+fluxes. We show the emission of four different supersymmetric BM
 models and contrast it to the emission induced by CRs. Comparing this
@@
 10~GeV. However, the IC emission from upscattered CMB and SD photons
-is at least a factor \C{few lower for $\Kp$ and a factor 1000 lower
-  for $\Ip,\Jp,\Js$,} \del{10 lower} than the expected flux from CRs
-above 100~MeV, making it very hard to distinguish such a signal from
-the foreground due to the similar spectral index. For energies below
-100~MeV we expect IC emission by primary shock accelerated electrons
-to be dominating \cite{2010MNRAS.409..449P} over the supersymmetric DM
+is at least a factor of a few lower for $\Kp$ and a factor 1000 lower
+for $\Ip,\Jp,\Js$, than the expected flux from CRs above 100~MeV,
+making it very hard to distinguish such a signal from the foreground
+due to the similar spectral index. For energies below 100~MeV we
+expect IC emission by primary shock accelerated electrons to be
+dominating \cite{2010MNRAS.409..449P} over the supersymmetric DM
 induced leptons. Hence in clusters, the IC emission from
@@
   show the continuum emission from DM benchmark (BM) models (blue
-  dashed), electrons and positrons from DM BM models that inverse
-  Compton upscattered both CMB photons (green dotted) as well as dust
-  and star photons (orange dash-dotted), and CR induced gamma-ray
-  emission (red solid). Each panel is associated with an individual DM
-  BM model; upper left $\Ip$, lower left $\Kp$, upper right $\Jp$, and
+  dashed), electrons and positrons from DM BM models that
+  Compton-upscatter CMB photons (green dotted) as well as dust and
+  star photons (orange dash-dotted), and CR induced gamma-ray emission
+  (red solid). Each panel is associated with an individual DM BM
+  model; upper left $\Ip$, lower left $\Kp$, upper right $\Jp$, and
   lower right $\Js$. The emission is calculated for the Fornax cluster
@@
   the gamma-ray flux from IC upscattered CMB and continuum emission by
-  730 while the IC upscattered SD photons is boosted by 20. Upper
-  limits from Fermi-LAT after 18 months \protect
+  a factor of 730 while the IC upscattered SD photons are only boosted
+  by 20. Upper limits from Fermi-LAT after 18 months \protect
   \cite{2010ApJ...717L..71A} are also shown. We find bright prospects
@@
 
-\C{For the LP DM models, however,}\del{One of} the main contributions
+For the LP DM models, however, the main contributions
 to the expected extended gamma-ray flux is coming from the IC
@@
 the spatial and spectral distribution of electrons and positrons as
-well as the photon background field, the resulting spectral
-distributions of gamma-ray can differ greatly. Hence it is interesting
+well as the photon background fields, the resulting spectral
+distributions of gamma-rays can differ greatly. Hence it is interesting
 to understand which spectral features and energy regimes are
-dominating.\del{for the different DM models.}
+dominating.
 
@@
 energy regime below 100~GeV, while the SD dominate above this
-energy. For the BM models this transition energy is shifted towards
+energy. For the BM models, this transition energy is shifted towards
 smaller energies since the electron and positron spectrum has a
@@
 of dust. In this low-dust model, we have reduced the energy in dust by
-a factor 10. \C{However, the resulting flux from the IC upscattered
-  dust in this model only decreases with a factor that is slightly
-  smaller than 10 since the IC cooling of the electrons and positrons
-  also decreases.}\del{However, we find that the IC
-  SD flux only decreases by a factor 3 since the IC cooling of the
-  electrons and positrons also decreases. Note that for a smaller
-  boost from substructures, the effect from cooling is smaller.}
-
-Because of the large total boost factor for the LP model ($\sim
+a factor 10. However, the resulting flux from the IC upscattered dust
+in this model only decreases with a factor that is slightly smaller
+than 10 since the IC cooling of the electrons and positrons also
+decreases.
+
+Because of the large total boost factor for the LP model ($\sim5\times
 10^4$), we overproduce the upper gamma-ray limit in the $1-10$~GeV
@@
   dashed-dotted). The sum of the three components are shown with the
-  orange solid line.  The red solid line show the CR induced gamma-ray
+  orange solid line.  The red solid lines show the CR induced gamma-ray
   flux. The black arrow shows the differential upper limit from Fermi
-  \protect \cite{2010ApJ...717L..71A} indicating that the model
+  \protect \cite{2010ApJ...717L..71A} indicating that the LP model
   assumptions such as Sommerfeld and/or substructure boost are in
@@
 up to the DM rest mass energy in this model of about 1~TeV. Finally,
-we note that the flux the DM BM $\Kp$ model is above the predicted
+we note that the flux the DM BM $\Kp$ model is larger than the predicted
 emission from the CRs in the $1-100$~GeV energy regime. Hence, the
@@
  \caption{\it Comparing the energy integrated flux from different
-   models. We show the emission from; CR induced emission (red solid),
-   leptophilic (LP) models that include both final state radiation and
-   IC upscattered CMB, dust and starlight (green dash-dotted), and
-   benchmark $\Kp$ models (BM) include continuum emission, and IC
-   upscattered CMB, dust and starlight (blue dashed). The black arrow
-   show the integrated flux upper limit set by Fermi-LAT again
+   models. We show the emission from CR induced emission (red solid),
+   a leptophilic (LP) model that includes both final state radiation
+   and IC upscattered CMB, dust and starlight (green dash-dotted), and
+   the benchmark $\Kp$ model (BM) that includes continuum emission, and
+   IC upscattered CMB, dust and starlight (blue dashed). The black
+   arrow shows the integrated flux upper limit set by Fermi-LAT again
    indicating challenges for the assumptions underlying the LP
-   model. \C{We also show projected CTA point source sensitivities
-     ($5\sigma$, 50h).} The emission is calculated for the Fornax
-   cluster using a point spread function of $0.1\deg$. The boost from
+   model. We also show projected CTA point source sensitivities
+   ($5\sigma$, 50h). The emission is calculated for the Fornax cluster
+   using a point spread function of $0.1\deg$. The boost from
    Sommerfeld and substructures is about 130 and 730, respectively.}
@@
 We continue by comparing the estimated differential flux from Fornax
-to three other clusters in Fig.~\ref{fig:clu_comp}; the close by and
+to three other clusters in Fig.~\ref{fig:clu_comp}; the close-by and
 well studied Virgo cluster, the X-ray bright Perseus clusters, and the
 massive merging Coma cluster. We find high DM induced gamma-ray fluxes
-from both the Fornax and Virgo clusters, which highlight them as
+from the Fornax and Virgo clusters, which highlight them as
 promising targets for indirect DM searches. Note, however, that we
@@
 models, making it difficult for indirect DM searches in those
-clusters. Conversely is the Fornax cluster a great target for indirect
+clusters. Conversely, the Fornax cluster is a great target for indirect
 DM studies because the relative low gamma-ray flux from CRs, absents
@@
 \end{eqnarray}
-Hence increasing the cluster mass in the BM model by a factor two more
-than doubles the luminosity, but increasing the luminosity distance,
-$D_\rmn{lum}$, by a factor two decrease the flux by a factor four. One
-should also note that the IC upscattered SD photons scales slightly
-softer with mass, hence giving rise to a larger fraction of gamma-rays
+Hence, increasing the cluster mass in the BM model by a factor two
+more than doubles the luminosity, but increasing the luminosity
+distance, $D_\rmn{lum}$, by a factor two decrease the flux by a factor
+four. We note that the IC from upscattered SD photons scales slightly
+softer with mass, hence gives rise to a larger fraction of gamma-rays
 in low mass clusters compared to the total gamma-ray flux.
@@
 \caption{\it Comparing the gamma-ray emission from different
-  clusters. We show the differential flux from four clusters; Fornax
+  clusters. We show the differential flux from of clusters: Fornax
   (upper left), Coma (upper right), Virgo (lower left), and Perseus
-  (lower right). We show CR induced emission (red solid), leptophilic
-  (LP) models include both final state radiation and IC upscattered
-  CMB, dust and starlight (green dash-dotted), and benchmark $\Kp$
-  models (BM) include continuum emission, and IC upscattered CMB, dust
+  (lower right). We show CR induced emission (red solid), a leptophilic
+  (LP) model that includes both final state radiation and IC upscattered
+  CMB, dust and starlight (green dash-dotted), and the benchmark $\Kp$
+  model (BM) that includes continuum emission, and IC upscattered CMB, dust
   and starlight (blue dashed). The arrows show the differential upper
@@
 
-In this section we have found that the LP DM models overproduces both
+In this section, we have found that the LP DM models overproduces both
 the differential and integrated gamma-ray flux upper limits set by the
@@
 boost factors that are manifested in the gamma-ray flux. It is
-especially interesting is to constrain the SFE, where a boost of the
+especially interesting to constrain the SFE, where a boost of the
 particle physics cross section of 300 is required to explain the
@@
 due to SFE DM, then in order not to overproduce the differential upper
-limits set by Fermi-LAT in the energy range $1-10$~GeV \footnote{We
+limits set by Fermi-LAT in the energy range\footnote{We
   average the LP DM flux in the energy range $1-10$~GeV before we
-  compare it to the upper limits.}, we can constrain the smallest mass
+  compare it to the upper limits.}  $1-10$~GeV, we can constrain the smallest mass
 of substructures to $M_\rmn{lim}\gtrsim 100\,\msun$. Instead assuming
@@
 able to rule out the LP model assuming a substructure boost with a
-smallest mass of $M_\rmn{lim} = 10^{-6}\,\msun$.
+smallest mass of $M_\rmn{lim} \approx 10^{-6}\,\msun$.
 
@@
 cluster. Especially important is the spatial distribution of the
-gamma-ray emission as it bias upper limits derived for spatially
+gamma-ray emission as it biases upper limits derived for spatially
 extended clusters where a simple profile is often assumed. In fact, we
-will show that if DM substructures are present, the gamma-ray
-brightness profile is almost flat and very different from the
-gamma-ray distribution following a smooth density profile with a steep
-outer surface brightness slope of $-5$.
+will show that if DM substructures are present with the discussed
+abundances, the gamma-ray brightness profile is almost flat and very
+different from the gamma-ray distribution following a smooth density
+profile with a steep outer surface brightness slope of $-5$.
 
@@
 of the BM model scales as $S_\gamma\propto\bsub
-L_{\gamma,\rmn{BM}}^{1/3} \propto \mvir^{0.5}$, which explains the
+L_{\gamma,\rmn{BM}}  \mvir^{-2/3} \propto \mvir^{0.59}$, which explains the
 factor three difference in normalization between the most massive
 cluster Coma and the least massive cluster Fornax with a mass ratio of
-about 10. The flux from the LP model show a smaller spread in the
+about 10. The flux from the LP model shows a smaller spread in the
 normalization which is due to the additional contribution from SFE
 with a negative mass trend, hence a flux normalization with a softer
-mass-scaling of $S_\gamma\propto\mvir^{0.17}$. The surface brightness
+mass-scaling of $S_\gamma\propto\mvir^{0.06}$. The surface brightness
 induced by CRs is proportional to the projected squared the gas
@@
 explained by the low gas density outside the BCG and the less abundant
-CR population in the relative small cluster compared to a more
+CR population in a small cluster compared to a
 massive cluster \cite{2010MNRAS.409..449P}.  This is the reason why
@@
    styles each represent a cluster; Fornax (solid), Coma (dotted),
-   Virgo (dashed), and Perseus (dash-dotted). \C{We include the boost
-   from both substructures and Sommerfeld effect.} Notice the very
+   Virgo (dashed), and Perseus (dash-dotted). We include the boost
+   from both substructures and Sommerfeld effect. Notice the very
    similar shape and normalization of the DM models, while the CRs
@@
 To quantify the impact of substructures on the spatial profiles in
-more detail we again turn to the Fornax clusters and show in
+more detail we again turn to the Fornax cluster and show in
 Fig.~\ref{fig:SB_sub} a comparison of surface brightness profiles with
 and without substructures. It is quite remarkable how flat the
-profiles becomes when substructures are present compared to the case
+profiles become when substructures are present compared to the case
 without. This implies that the relative flux within the PSF in the
 center is comparable to the outer parts, which should increase the
-signal-to-noise significantly. If we assume that substructures for
-some reason are suppressed in the Fornax cluster, then the expected
+signal-to-noise significantly. If we assume that -- for
+some reason -- substructures are suppressed in the Fornax cluster, then the expected
 signal from DM is swamped by astrophysical backgrounds over the entire
@@
  \caption{\it The impact of substructures on the intrinsic surface
-   brightness profile of the Fornax cluster at 1~GeV. The emission
+   brightness profile o the Fornax cluster at 1~GeV. The emission
    induced by CRs is denoted by the red solid line, the leptophilic
-   models by green lines, and the DM $\Kp$ benchmark model by blue
-   lines. The dashed line show the brightness where the boost from
-   substructures is included while the substructures are excluded in
-   the dotted line. The boost from Sommerfeld and substructures is
-   about 130 and 730, respectively. Notice the nearly flat profiles
-   when substructures are included, and the relative large boost at
-   $0.01\rvir$ that is due to projection of peripheral substructures
-   onto the cluster center.}
+   model by green lines, and the DM $\Kp$ benchmark model by blue
+   lines. The dashed lines show the brightness profiles where the
+   boost from substructures is included while the substructures are
+   excluded for the dotted lines. The boost from Sommerfeld and
+   substructures is about 130 and 730, respectively. Notice the nearly
+   flat profiles when substructures are included, and the relative
+   large boost at $0.01\rvir$ that is due to projection of peripheral
+   substructures onto the cluster center.}
  \label{fig:SB_sub}
@@
 In order to learn about the spatial distribution of the DM flux in
-various clusters for different DM models and associated gamma-ray
+various clusters for different DM models and the associated gamma-ray
 components, we show in the left panel of Fig.~\ref{fig:SB_clu_nosub}
 the brightness profiles for the smooth DM distribution for the same
-four representative clusters that was shown previously in
+four representative clusters that were shown previously in
 Fig.~\ref{fig:SB_clu}.  We find that the surface brightness,
@@
 the energy of the annihilation is imparted on leptons which radiate
-all the energy away and the sum of the IC components represents a
+all their energy away through IC emission and the sum of the IC components represents a
 calorimeter for these radiating leptons.  We note that the surface
@@
 overall mass normalization of the LP DM model has a marginally
-negative trend $\sim\mvir^{-0.06}$. Hence, we only see a very small
+negative trend $\sim\mvir^{-0.17}$. Hence, we only see a very small
 difference in outer parts of the different clusters from these type of
-models. The DM BM models scale as $S_\gamma\sim\mvir^{0.27}$,
+models. The DM BM models scale as $S_\gamma\sim\mvir^{0.16}$,
 hence more massive clusters show a slightly higher surface
@@
     the IC upscattered photons from stars and dust, and blue solid
-    line show the continuum emission from the $\Kp$ benchmark model.}
+    lines show the continuum emission from the $\Kp$ benchmark model.}
  \label{fig:SB_clu_nosub}
@@
 
-In Sect.~\ref{sect:spatial} we saw that the spectral distribution of
+In Sect.~\ref{sect:spectral} we saw that the spectral distribution of
 gamma-ray flux from the LP model was dominated at high energies of
-about $100\,$~GeV by final state radiation and IC upscattered
+$E_\gamma\gtrsim 100\,$~GeV by final state radiation and IC upscattered
 starlight and dust, while the BM models were mainly dominated by the
@@
 in LP models that prefers smaller halos with a larger ratio of
-$c/v_\mathrm{circ}$ (Eq.~\ref{eq:LP_scaling}). In contrast, the CR
-scaling relation is considerably steeper as shown by reference
+$c/\sigv$ (Eq.~\ref{eq:LP_scaling}). In contrast, the CR scaling
+relation is considerably steeper as shown by reference
 \cite{2010MNRAS.409..449P}:
@@
 \end{eqnarray}
-Note that the CR luminosity scaling relations \footnote{The scaling
+Note that the CR luminosity scaling relations\footnote{The scaling
   relations show the flux inside $\rvir$ and do not include the
@@
   to $10^{15}/h\,\msun$ that was used in \cite{2010MNRAS.409..449P}.}
-include the IC gamma-ray contribution from shock accelerated electrons
-as well as secondary electrons created through CR-proton
-interactions. The gamma-ray flux from the electrons is, however,
-dominated by the decaying $\pi^0$ and only show up as a small
-flattening of the scaling relation at energies around
-$10-100\,\gev$. The steeper mass scaling of the CR compared to the DM
-implies already a general strategy to minimize the CR-induced
-foreground for DM annihilation and argues for very nearby groups. We
-note that these simulations do not include AGN feedback that is
-thought to furthermore reduce the baryon fraction in groups relative
-to that in clusters \cite{2008ApJ...687L..53P}. The resulting smaller
-target density for hadronic CR interactions will furthermore steepen
-the $L_\gamma-M$ relation of CR induced emission, making the case for
-groups even stronger.
+include the IC gamma-ray contribution from shock-accelerated electrons
+as well as secondary electrons created in CR-proton interactions. The
+gamma-ray flux from the electrons is, however, dominated by the
+decaying neutral pions and only show up as a small flattening of the
+scaling relation at energies around $10-100\,\gev$. The steeper mass
+scaling of CR emission compared to DM annihilation already implies a
+general strategy to minimize the CR-induced foreground for DM
+annihilation and argues for very nearby groups. We note that these
+simulations do not include AGN feedback that is thought to furthermore
+reduce the baryon fraction in groups relative to that in clusters
+\cite{2008ApJ...687L..53P}. The resulting smaller target density for
+hadronic CR interactions will furthermore steepen the $L_\gamma-M$
+relation of CR induced emission, making the case for groups even
+stronger.
 
@@
     boost factor due to substructures that has a mass spectrum
-    extending down to Earth masses, the expected leptophilic fluxes
+    extending down to an Earth mass, the expected leptophilic fluxes
     are ruled out by upper limits in 14 of the clusters, with the
@@
  \caption{\it Comparing the DM annihilation flux from clusters in the
-  extended HIFLUGCS catalogue. We show the energy integrated gamma-ray
-  fluxes derived from both leptophilic DM that result in inverse
-  Compton upscattered CMB photons (red), and the continuum emission
-  from the DM $\Kp$ benchmark model (blue). The fluxes are calculated
-  within $\rvir$ for each of the 106 clusters included in the extended
-  HIFLUGCS catalogue. The CR emission is derived using a single beta
-  profile for each cluster's gas density profile (see text for
-  details). The upper panel shows the energy integrated flux above
-  100~MeV and the lower panel that above 10~GeV, both as a function of
-  HIFLUGCS cluster ID. For comparison we show with a dashed line the
+   extended HIFLUGCS catalogue. We show the energy integrated
+   gamma-ray fluxes derived from both leptophilic DM that result in
+   inverse Compton upscattered CMB photons (red), and the continuum
+   emission from the DM $\Kp$ benchmark model (blue). The fluxes are
+   calculated within $\rvir$ for each of the 106 clusters included in
+   the extended HIFLUGCS catalogue. The CR emission is derived using a
+   single beta profile for each cluster's gas density profile (see
+   text for details). The upper panel shows the energy integrated flux
+   above 100~MeV and the lower panel that above 10~GeV, both as a
+   function of HIFLUGCS cluster ID. For comparison we show the
    estimated point source sensitivity of the Fermi-LAT after two years
-  of data taking $\sim
-  2\times10^{-9}\,\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$. The name of
-  the four brightest clusters are written out. This yields Fornax and
-  M49 as the brightest targets.}
+   of data taking $F_\gamma\sim 2\times10^{-9}\,\rmn{ph}\,
+   \rmn{cm}^{-2}\,\rmn{s}^{-1}$ (dashed line). The four brightest
+   clusters are labelled yielding Fornax and M49 as the brightest
+   targets.}
  \label{fig21}
@@
 position. Hence, the ratio of the Fermi upper limits to the predicted
-annihilation fluxes, $F_{\mathrm{UL}}/F_{\mathrm{scal}}$, is a good
+annihilation fluxes, $F_{\mathrm{UL}}/F_{\mathrm{DM}}$, is a good
 indication of the best cluster candidates for indirect DM
@@
 Fermi mission. We emphasize that the very inhomogeneous distribution
-of $F_{\mathrm{UL}}/ F_{\mathrm{scal}}$ makes it unlikely to
+of $F_{\mathrm{UL}}/ F_{\mathrm{DM}}$ makes it unlikely to
 dramatically improve the limits through a stacking analysis as the
@@
 \subsection{CR-induced emission}
-
+\label{sec:CRemission} 
 \begin{figure*}
@@
   \caption{\it We contrast predictions of the CR induced gamma-ray
-    emission using the analytical model \protect
+    emission using an analytical CR model \protect
     \cite{2010MNRAS.409..449P} to Fermi-LAT flux upper limits. We show
@@
     for 32 clusters. The Fermi upper limits are shown with black
-    arrows. The blue boxes show the gamma-ray emission from
-    CR-induced $\pi^0$-decay, where the upper bound shows the
-    estimates for an optimistic model and the lower bound a more
-    conservative model excluding point sources (see
-    \cite{2010MNRAS.409..449P} for details). Note that our models are
-    in perfect agreement with the derived upper limits from
-    Fermi. Interestingly, the limits of Virgo, Norma, and Coma are
-    closing in on our predictions and will enforce constraints on the
-    parameters of hadronic models such as shock acceleration
-    efficiencies or CR transport properties in the coming years.}
+    arrows. The blue boxes show the gamma-ray emission from CR-induced
+    $\pi^0$-decay, where the upper (lower) bounds show the estimates
+    for an optimistic (conservative) model (see
+    Sect.~\ref{sec:CRemission} and \cite{2010MNRAS.409..449P} for
+    details). Note that our models are in perfect agreement with the
+    derived upper limits from Fermi. Interestingly, the limits of
+    Virgo, Norma, and Coma are closing in on our predictions and will
+    enforce constraints on the parameters of hadronic models such as
+    shock acceleration efficiencies or CR transport properties in the
+    coming years.}
  \label{fig15}
@@
 In Fig.~\ref{fig15}, we compare Fermi-LAT flux upper limits to the
-flux predictions by the analytical model \cite{2010MNRAS.409..449P}
+flux predictions by an analytical CR model \cite{2010MNRAS.409..449P}
 for CR induced gamma-rays. For consistency, we use beta-model fits to
@@
 (kinetic energy corrected for adiabatic compressional heating at the
-shock) to CRs and most likely will have to be corrected down if this
-number is not realized at structure formation shocks. Secondly, these
-simulations neglect active CR transport such as streaming and
-diffusion relative to the gas, i.e. we assume that advective transport
-is the dominant one and CRs are tightly coupled to the gas via
-flux-frozen magnetic fields tangled on sufficiently small
-scales. Evidence from the statistics of radio halos suggests that this
-might not be the case for relaxed clusters, arguing that CR streaming
-in those objects could be responsible for a decrease in the central CR
-number density. This effect would also reduce the expected gamma-ray
-flux by up to a factor of five \cite{2011A&A...527A..99E}. We note
-that the tightest Fermi limits are obtained in the 1-10 GeV regime due
-to the highest sensitivity of Fermi-LAT there. While the effective
-area of Fermi-LAT increases up to these energies, the typical photon
-spectra decrease as a function of energy: combining those effects
-selects this energy range to be most sensitive.  In this energy band,
-the Fermi limits come close to the flux predictions of Virgo, Coma and
-Norma. Using integrated flux limits from Fermi, we arrive at very
-similar results.  We emphasize that by using our analytic modeling,
-the slight discrepancy of the scaling relation-based prediction with
-the Fermi limit on Norma \cite{2010ApJ...717L..71A} is resolved: Norma
-simply seems to be less bright than an average cluster of the same
-mass as Norma. The insensitive limit on Perseus comes about since the
-central AGN in NGC1275 has turned on over the last years, making it
-hard to determine a comparable limit as obtained for the other
-clusters.
+shock) to CRs. These efficiencies drop quickly for weaker shocks
+\cite{2007A&A...473...41E} which dominate the gravitational energy
+dissipation inside galaxy clusters \cite{2006MNRAS.367..113}. These
+efficiencies will have to be corrected down if this value is not
+realized at structure formation shocks. Secondly, these simulations
+neglect active CR transport such as streaming and diffusion relative
+to the gas, i.e. we assume that advective transport is the dominant
+one and CRs are tightly coupled to the gas via flux-frozen magnetic
+fields tangled on sufficiently small scales. Evidence from the
+statistics of radio halos suggests that this might not be the case for
+relaxed clusters, arguing that CR streaming in those objects could be
+responsible for a decrease in the central CR number density. This
+effect would also reduce the expected gamma-ray flux by up to a factor
+of five \cite{2011A&A...527A..99E}. We note that the tightest Fermi
+limits are obtained in the 1-10 GeV regime due to the highest
+sensitivity of Fermi-LAT there. While the effective area of Fermi-LAT
+increases up to these energies, the typical photon spectra decrease as
+a function of energy: combining those effects selects this energy
+range to be most sensitive.  In this energy band, the Fermi limits
+come close to the flux predictions of Virgo, Coma and Norma. Using
+integrated flux limits from Fermi, we arrive at very similar results.
+We emphasize that by using our analytic modeling, the slight
+discrepancy of the scaling relation-based prediction with the Fermi
+limit on Norma \cite{2010ApJ...717L..71A} is resolved: Norma simply
+seems to be less bright than an average cluster of the same mass as
+Norma. The insensitive limit on Perseus comes about since the central
+AGN in NGC1275 has turned on over the last years, making it hard to
+determine a comparable limit as obtained for the other clusters.
 
@@
    and the gamma-ray flux predicted by the mass-luminosity scaling
-   relation \cite{2010MNRAS.409..449P}. The name of the clusters with
-   the largest positive offset are printed out; as expected, they all
-   correspond to cool core clusters.}
+   relation \cite{2010MNRAS.409..449P}. The clusters with the largest
+   positive offset are labelled. As expected, they all are cool core
+   clusters.}
  \label{fig19}
@@
 figure, we show the relative difference between the gamma-ray flux
-predicted by the mass-luminosity scaling relation and to the flux
-computed using the analytical model. Statistically, one can view the
-analytical modeling as contributing to the scatter of the expected
+computed using the analytical CR model to the flux predicted by the
+mass-luminosity scaling relation. Statistically, one can view the
+analytical modeling as explicitely accounting for the scatter of the expected
 gamma-ray flux at a given mass. Cool core clusters have a denser core
@@
 reaction which in turn leads to a systematic increase of the expected
-gamma-ray fluxes. We confirm this effect as all our outliers with
-increased flux in our analytic model relative to the scaling relation
-expectation are in fact cool core clusters suggesting that the X-ray
+gamma-ray fluxes. We confirm this effect since all clusters with
+increased flux ratio of our analytical CR model relative to the scaling relation
+expectation are in fact cool core clusters. This suggests that the X-ray
 emission should be a good proxy for the expected gamma-ray
@@
 matter decouples from the expanding universe it streams and erases any
-potentially present smaller scales. \C{When} \del{Once} gravitational
-instabilities causes halos to collapse, this free-streaming scale
-imprints as a characteristic minimum halo mass $M_\mathrm{min}$ into
-the hierarchy of structure formation and should still survive until
-the present time as substructure within larger halos. It turns out
-that the boost due to substructures dominates over the smooth
-component for halo masses $\mvir>10^3 \msun$ and contributes a
-constant luminosity for each decade in halo mass. The ratio of
-halo-to-minimum subhalo mass $\mvir/M_\mathrm{min}$ is maximized for
-the largest systems that had time to collapse and virialise since the
-Big Bang -- galaxy clusters. The corresponding substructure boost can
-reach values exceeding $10^3$ which should make nearby clusters the
-brightest DM annihilation sources after the MW center and hypothetical
-very close-by DM substructures. \C{CHRISTOPH, I DO NOT THINK THAT AN
-  EINASTO PROFILE IMPLIES THAT THE FLUX IS DOMINATED AROUND RVIR?!?
-  Since the number density of substructures are distributed according
-  to an Einasto profile, the contribution to the annihilation emission
-  from substructures is dominated from radii close to the virial
-  radius.}  This implies an almost flat surface brightness profile of
+potentially present smaller scales. When gravitational instabilities
+causes halos to collapse, this free-streaming scale imprints as a
+characteristic minimum halo mass $M_\mathrm{min}$ into the hierarchy
+of structure formation and should still survive until the present time
+as substructure within larger halos. It turns out that the boost due
+to substructures dominates over the smooth component for halo masses
+$\mvir>10^3 \msun$ and contributes a constant luminosity for each
+decade in halo mass. The ratio of halo-to-minimum subhalo mass
+$\mvir/M_\mathrm{min}$ is maximized for the largest systems that had
+time to collapse and virialise since the Big Bang -- galaxy
+clusters. The corresponding substructure boost can reach values
+exceeding $10^3$ which should make nearby clusters the brightest DM
+annihilation sources after the MW center and hypothetical very
+close-by DM substructures.  Since the mass density of substructures
+peaks at radii close to $\rvir$, the contribution to the annihilation
+emission from substructures is also dominated from these outer cluster
+regions.  This implies an almost flat surface brightness profile of
 the annihilation emission which makes it necessary to have the entire
-cluster in the field-of-view to take advantage of the \C{total}
-\del{entire} substructure boost. This property makes it difficult to
-detect DM annihilation emission without an enhancement of the particle
-physics cross section over its standard value of $\sigma v\sim 3\times
+cluster in the field-of-view to take advantage of the total
+substructure boost. This property makes it difficult to detect DM
+annihilation emission without an enhancement of the particle physics
+cross section over its standard value of $\sigma v\sim 3\times
 10^{-26} ~\mathrm{cm}^3~\mathrm{s}^{-1}$ with imaging air Cherenkov
@@
 5 due to the larger Sommerfeld boost factor in smaller mass halos
-which have a lower circular velocity that enhances the particle cross
-section (while assuming universality of the DM model). This would rule
-out LP models in their current form based on the non-observation of
-gamma-rays in any of the fore-mentioned
+which have a lower velocity dispersion that enhances the particle
+cross section (while assuming universality of the DM model). This
+would rule out LP models in their current form based on the
+non-observation of gamma-rays in any of the fore-mentioned
 clusters/groups. Alternatively, assuming the LP models to be correct,
@@
 
-For the first time we compute the IC emission component not only from
+For the first time, we compute the IC emission component not only from
 the upscattered CMB photons but also from a realistically modeled
@@
 emission is low, the IC up-scattering of the CMB dominates below 60
-GeV. For large clusters, the final state radiation \C{then takes}
-\del{takes then} over for energies up to the cutoff at $m_\chi c^2
-\sim 1$~TeV. In small clusters, there is a window around $E_\gamma
-\sim 100~\mathrm{GeV}$ where the IC up-scattering of the dust emission
-dominates over the CMB IC emission and the final state radiation. The
-IC emission of starlight remains always subdominant.  We stress, that
-the inclusion of the dust and starlight radiation fields are
-negligible in the cooling function for the leptons.  The main reason
-why the IC emission from starlight and dust remains subdominant is the
-small overlap of this component with the peripherally peaked
-substructure mass density profiles. If for some reason, DM has less
-substructure, the relative importance of this IC component increases
-considerably.
+GeV. For large clusters, the final state radiation then takes over for
+energies up to the cutoff at $m_\chi c^2 \sim 1$~TeV. In small
+clusters, there is a window around $E_\gamma \sim 100~\mathrm{GeV}$
+where the IC up-scattering of the dust emission dominates over the CMB
+IC emission and the final state radiation. The IC emission of
+starlight remains always subdominant.  We stress, that the inclusion
+of the dust and starlight radiation fields are negligible in the
+cooling function for the leptons.  The main reason why the IC emission
+from starlight and dust remains subdominant is the small overlap of
+this component with the peripherally peaked substructure mass density
+profiles. If for some reason, DM has less substructure, the relative
+importance of this IC component increases considerably.
 
@@
 recently developed by \citet{2010MNRAS.409..449P} that is based on
-cosmological hydrodynamical simulations that self-consistently follow
+cosmological hydrodynamical simulations of galaxy clusters that self-consistently follow
 the evolution of CRs in cosmic structure formation. Adopting the model
@@
 \citep{2010ApJ...717L..71A} could not be confirmed due to the
-apparently lower gas density of this cluster relative to the average.
-As expected, the analytic model adds ``scatter'' to the scaling
+ lower gas density of this cluster relative to the average.
+As expected, the analytical CR model accounts for the ``scatter'' to the scaling
 relation and biases the gamma-ray flux high for prominent cool core
-clusters by up to a factor of 3.5 relative to the expectation from the
+clusters by up to a factor of 6 relative to the expectation from the
 scaling relation. This is due to the high target gas densities and
@@
 X-rays. We caution that these predictions only apply for the case of
-negligible active CR transport such as streaming and diffusion
-relative to the gas and might be considerably modified in those
+negligible active CR transport such as CR streaming and diffusion
+relative to the gas. Gamma-ray fluxes might be considerably smaller in those
 cluster that do not show an extended diffuse radio(-mini) halo that
@@
 characteristic pion bump at energies around 1~GeV. It is expected to
-dominate the DM annihilation signal in the BM models for all
+dominate the DM annihilation signal of BM models for all
 clusters/groups but Fornax. We conclude that it will be possible to
@@
 that trace the stars and for simplicity we assume that the dust trace
-the stars in the clusters {\bf Christoph, why is this a valid
-  approximation?}. The stacked surface brightness profiles in
-\cite{2005MNRAS.358..949Z} are measured at redshift $z \approx 0.25$
-with an average mass of the clusters of $4.0\times10^{13}\,\msun$. The
-profiles are build up out of three components; diffuse ICL, galaxies,
-and the BCG in the center of clusters. However, the total volume
-overlap of the inter-stellar medium with a cluster is very small
-compared to the total overlap of the ICL- and BCG with a cluster, thus
-the relative contribution of the galaxies to the IC emission is
-suppressed (c.f. Eq.~\ref{eq:SD_overlap}). We remove this bias in our
-benchmark model for SD by cutting out the galaxies which roughly
-corresponds to $70$ percent of the total SD light. In
-Fig.~\ref{fig:SD_spatial} we show the SDSS stacked brightness profiles
-as well as the fitted profiles\footnote{The measured brightness is
-  converted into units of $\rmn{erg}\,\rmn{s}^{-1}$ using
-  \cite{2010...book} $S(\rmn{mag}\,''^{-2}) =
+the stars in the clusters. This is justified if the dust is delivered
+alongside the stars in the same stripping process and got not
+destroyed by spallation thereafter. The stacked surface brightness
+profiles in \cite{2005MNRAS.358..949Z} are measured at redshift $z
+\approx 0.25$ with an average mass of the clusters of
+$4.0\times10^{13}\,\msun$. The profiles are build up out of three
+components; diffuse ICL, galaxies, and the BCG in the center of
+clusters. However, the total volume overlap of the inter-stellar
+medium with a cluster is very small compared to the total overlap of
+the ICL- and BCG with a cluster, thus the relative contribution of the
+galaxies to the IC emission is suppressed
+(c.f. Eq.~\ref{eq:SD_overlap}). We remove this bias in our benchmark
+model for SD by cutting out the galaxies which roughly corresponds to
+$70$ percent of the total SD light. In Fig.~\ref{fig:SD_spatial} we
+show the SDSS stacked brightness profiles as well as the fitted
+profiles\footnote{The measured brightness is converted into units of
+  $\rmn{erg}\,\rmn{s}^{-1}$ using \cite{2010...book}
+  $S(\rmn{mag}\,''^{-2}) =
   \mathcal{M}_\odot+21.6-2.5\log_{10}[S(L_\odot\,\rmn{pc}^{-2})]$,

### 2011-05-16 paper.tex
minor update text

@@
 \caption{\it Comparing the gamma-ray emission from different
-  clusters. We show the differential flux from of clusters: Fornax
+  clusters. We show the differential flux of clusters: Fornax
   (upper left), Coma (upper right), Virgo (lower left), and Perseus
@@
 \cite{2007A&A...473...41E} which dominate the gravitational energy
-dissipation inside galaxy clusters \cite{2006MNRAS.367..113}. These
+dissipation inside galaxy clusters \cite{2006MNRAS.367..113P}. These
 efficiencies will have to be corrected down if this value is not

### 2011-05-16 paper.tex
final correction

--- 2011-05-16 paper.tex
@@
 energy $\eg$.  The integration along the line-of-sight $l$, in the
-direction $\psi$ that the detector is pointing, is parameterized such
+direction $\psi$ that the detector is pointing, is parametrized such
 that the radius of the source $r=\sqrt{l^2+D_\clu^2-2 D_\clu
@@
   flatter subhalo distribution compared to the smooth distribution and
-  errorously assuming an identical mass density distribution of smooth
+  erroneously assuming an identical mass density distribution of smooth
   DM and substructure biases the subhalo boost factor too low
@@
 \label{sect:SD}
-In this section we present the details of our model of stars and dust
-(SD) in clusters of galaxies. In the first part we use the measured
+In this section, we present the details of our model of stars and dust
+(SD) in clusters of galaxies. In the first part, we use the measured
 spectral distribution of light from SD in a typical galaxy to derive a
 simple spectral model for SD in galaxy clusters. This is done by
-renormalizing the galactic SD light to match the observed luminosity
-from a cluster in the far infra-red (IR) and ultra-violet (UV) bands. In
-the second part we derive the spatial distribution of the SD light
-from a stacked sample of clusters.
+renormalizing the galactic SD distribution to match the observed luminosity
+from a cluster in the far infra-red (IR) and ultra-violet (UV) bands
+separately. In the second part, we derive the spatial distribution of
+the SD light from a stacked sample of clusters.
 
 \subsection{Energy spectrum}
-The light from SD in clusters is dominated by the emission from
-galaxies. This radiation is expected to leak out into the much larger
-volume of the intra-cluster medium (ICM), hence we approximate the
-spectral distribution of the intra-cluster light (ICL) with the light
-from galaxies. We use the far IR to UV spectrum derived in reference
-\cite{2006ApJ...648L..29P} for a Milky Way (MW) type galaxy to
-characterize the spectral distribution of SD in a cluster. Note that
-we only keep the spectral shape, and renormalize the spectral
-distribution using the luminosity from SD in clusters.
-
-In Fig.~\ref{fig:SD_spectra} we show the spectral distribution of the
-light from SD together with the cosmic microwave background (CMB)
-black-body distribution in a $6\times10^{14}\,\msun$ galaxy
-cluster. We fit the spectral shape of SD individually; the dust that
-peaks at about $10^{-2}\,\ev$ is fitted using a double power-law,
-while the broader spectral distribution of the stars that peaks at
-about $1\,\ev$ is fitted using a tipple power-law. The best fit to the
-galactic spectrum is given by:
+The cluster emission from far-IR to optical/UV is due to dust emission
+and stellar light, respectively. We distiguish three components: the
+brightest cluster galaxy (BCG), the intra-cluster light (ICL) and
+individual galaxies. While the latter distribution is highly clumped,
+the first two components are smoothly distributed.  We use the far-IR
+to UV spectrum derived in reference \cite{2006ApJ...648L..29P} for a
+Milky Way (MW)-type galaxy to characterize the spectral distribution
+of SD in a cluster. Note that we only keep the spectral shape, and
+renormalize the amplitude of the spectral distribution using the
+luminosity from SD in clusters.
+
+In Fig.~\ref{fig:SD_spectra}, we show the cosmic microwave background
+(CMB) black-body distribution together with the spectral distribution
+of SD light of a $6\times10^{14}\,\msun$ galaxy cluster. We fit the
+spectral shape of SD individually; the dust that peaks at about
+$10^{-2}\,\ev$ is fitted using a double power-law, while the broader
+spectral distribution of the stars that peaks at about $1\,\ev$ is
+fitted using a tripple power-law. The best fit to the galactic spectrum
+is given by:
 \begin{eqnarray}
@@
 represented by $E_{i,\vir}$. We relate this energy to the luminosity
-$L_i$ in each respective wavelength band (optical and IR light for the
-dust, and UV light for the stars) using
+$L_i$ in each respective wavelength band (far-IR light for the
+dust, and optical/UV light for the stars) using
 \begin{eqnarray} 
@@
 Here we approximate the total energy of the photons within $\rvir$
-with the SD luminosity multiplied the typical timescale it takes for a
-photon to propagate through the cluster (we assume that the cluster is
-optically thin).
-
-We derive the {\em luminosity from the stars} using
+with the SD luminosity multiplied with the typical timescale that it
+takes for a photon to propagate through the cluster (we assume that
+the cluster is optically thin).
+
+The {\em luminosity from star light} is given by
 \begin{eqnarray}
@@
 $L_\odot=1.17\times10^{33}\,\rmn{erg\,s}^{-1}$, and distance to the
-cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. Furthermore, to account for
-different cluster masses, we attach a simple mass scaling to the
-luminosity from the stars in Eq.~(\ref{eq:L_stars}). Here we assume
+cluster average of $D_\clu=1.26\times10^9\,\rmn{pc}$. Furthermore, to account for
+different cluster masses, we employ a simple mass scaling for the
+luminosity from  stars in Eq.~(\ref{eq:L_stars}). Here we assume
 that the total starlight has the same halo mass scaling as the
 brightest cluster galaxy (BCG) \cite{2010ApJ...713.1037H}, which is a
-reasonable assumption since a large contribution of the total
+reasonable assumption since a large contribution of the smoothly distributed
 starlight in a cluster comes from the BCG. The starlight luminosity as
@@
 \left(\frac{\mvir}{M_{200\rmn{av}}}\right)^{0.18}\,
-\frac{6.0\,\rvir\times10^{-9}\,\kpc^2}{\int_{\rvir} j(r) \,\dd V}\,.
+\frac{\rvir\, 6.0\times10^{-9}\,\kpc^2}{\int_{\rvir} j(r) \,\dd V}\,.
 \label{eq:N_stars}
@@
 
-The {\em luminosity from the dust} is derived from the
+The {\em luminosity from  dust} is derived from the
 luminosity-richness scaling relation found in
@@
 since these clusters are less likely biased by chance
-coincidences. This richness roughly correspond to a mass
+coincidences. This richness  corresponds to a virial mass of approximately
 $M_\rmn{200dust}=6.0\times10^{14}\,\msun$
@@
 \begin{equation}
- N_\stars(\mvir) = 
+ N_\dust(\mvir) = 
 \left(\frac{\mvir}{M_\rmn{200dust}}\right)^{0.18}\,
-\frac{4.0\,\rvir\times10^{-7}\,\kpc^2}{\int_{\rvir} j(r) \,\dd V}\,.
+\frac{\rvir\,4.0\times10^{-7}\,\kpc^2}{\int_{\rvir} j(r) \,\dd V}\,.
 \label{eq:N_dust}
@@
 distribution of the light from SD in galaxy clusters. For this reason
-we use stacked cluster observations by Sloan in the $r$ and $i$-band
-that trace the stars and for simplicity we assume that the dust trace
-the stars in the clusters. This is justified if the dust is delivered
-alongside the stars in the same stripping process and got not
-destroyed by spallation thereafter. The stacked surface brightness
+we use stacked cluster observations from the Sloan Digital Sky Survey
+(SDSS) in the $r$ and $i$-band that trace the starlight. For
+simplicity we assume that the dust traces the stars in the
+clusters. This is justified for sufficiently young stellar populations
+(blue BCG and spiral galaxies) or, in the case of the ICL, if the dust
+got stripped alongside the stars without having been destroyed by
+spallation processes thereafter. The stacked surface brightness
 profiles in \cite{2005MNRAS.358..949Z} are measured at redshift $z
 \approx 0.25$ with an average mass of the clusters of
-$4.0\times10^{13}\,\msun$. The profiles are build up out of three
-components; diffuse ICL, galaxies, and the BCG in the center of
-clusters. However, the total volume overlap of the inter-stellar
-medium with a cluster is very small compared to the total overlap of
-the ICL- and BCG with a cluster, thus the relative contribution of the
-galaxies to the IC emission is suppressed
-(c.f. Eq.~\ref{eq:SD_overlap}). We remove this bias in our benchmark
-model for SD by cutting out the galaxies which roughly corresponds to
-$70$ percent of the total SD light. In Fig.~\ref{fig:SD_spatial} we
-show the SDSS stacked brightness profiles as well as the fitted
-profiles\footnote{The measured brightness is converted into units of
-  $\rmn{erg}\,\rmn{s}^{-1}$ using \cite{2010...book}
-  $S(\rmn{mag}\,''^{-2}) =
+$4.0\times10^{13}\,\msun$. As already mentioned, three components
+contribute to the SD: diffuse ICL, galaxies, and the BCG in the center
+of clusters.  However, the overlapping volume of the galactic light
+with the DM distribution of a cluster is very small compared to the
+overlaping volume of ICL- and BCG-light with the DM distribution;
+thus, the relative contribution of the galaxies to the IC emission is
+suppressed (c.f. Eq.~\ref{eq:SD_overlap}). In our benchmark model for
+SD, we remove the contribution from galaxies which corresponds to
+roughly $70$ percent of the total SD light. In
+Fig.~\ref{fig:SD_spatial} we show the SDSS stacked brightness profiles
+as well as the fitted profiles\footnote{The measured brightness is
+  converted into units of $\rmn{erg}\,\rmn{s}^{-1}$ using
+  \cite{2010...book} $S(\rmn{mag}\,''^{-2}) =
   \mathcal{M}_\odot+21.6-2.5\log_{10}[S(L_\odot\,\rmn{pc}^{-2})]$,
@@
 normalized with the central surface brightness of the total SD
-component ($S_\sd^\rmn{tot}(0)$). Our spatial benchmark model is shown
-with the solid black line, and include the contribution from the ICL
-and BCG.
+component, $S_\sd^\rmn{tot}(0)$. Our spatial benchmark model is shown
+with the solid black line.
 
@@
    \cite{2005MNRAS.358..949Z}. The crosses show the total observed
-   starlight including the diffuse intracluster (ICL), the galaxies,
+   starlight including the diffuse intracluster light (ICL), galaxies,
    and the brightest cluster galaxy (BCG) in the center of the
    cluster. The diamonds denote the smooth part of the observed
-   starlight from the ICL and the BCG. The solid line show the fit to
-   the data of the total light including the ICL, the BCG, and the
-   galaxies, while the smooth component is represented by the dashed
-   line that is fitted to only the ICL and the BCG. Note that, we use
-   total SD brightness in the cluster center
-   $(S_\sd^\rmn{tot}(0))$ to normalize the SD surface
-   brightness profiles.}
+   starlight of the ICL and the BCG. The solid line shows the fit to
+   the data of the total light, while the smooth component is
+   represented by the dashed line. Note that we use total SD
+   brightness in the cluster center, $S_\sd^\rmn{tot}(0)$, to
+   normalize the SD surface brightness profiles.}
  \label{fig:SD_spatial}
@@
 Instead of modelling the surface brightness with a de Vaucouleur
-profile with the addition of a power-law, we use a double beta profile
-model for simplicity of deprojection. It is given by
+profile and a power-law, we use a double beta profile model to
+simplify deprojection. It is given by
 \begin{equation}
@@
 \left[1 + \left( \frac{r_\bot}{r_{\mathrm{c}_i}}\right)^2\right]
-^{-3\beta_i + 1/2}\,,
+^{-3\beta_i + 1/2}.
 \label{double_beta}
 \end{equation}
-where we found the following best fitted normalized central brightness
-($\tilde{S}_i$), core radius ($r_{\mathrm{c}_i}$), and slope
-($\beta_i$) for the total model:
+Our fit parameters for the normalized central brightness,
+$\tilde{S}_i$, the core radius, $r_{\mathrm{c}_i}$, and slope
+$\beta_i$ are given for the total model by
 \begin{align}
@@
 \end{align}
-For the smooth model, which is also our benchmark SD model, we find:
+For the smooth model (our benchmark SD model), we find:
 \begin{align}
@@
 
-The spatial distribution of the energy density of SD is an important
-quantity since it impacts the steady state electron and positron
-distribution through cooling; a high energy density of SD photons in
-a cluster suppresses the gamma-ray flux from IC upscattered
-photons. We derive the energy density from starlight and dust in a
-galaxy cluster through
+The radial distribution of the energy density of SD governs the seed
+photon distribution for IC emission (together with the CMB).  The
+energy density from starlight and dust in a galaxy cluster is given by
 \begin{eqnarray}
@@
 where we have used the specific energy density of the light from SD
-given by Eq.~(\ref{eq:u_SD_er}). Note that we compare the energy
+given by Eq.~(\ref{eq:u_SD_er}). We compare the energy
 density $u_\sd(r)$ to other radiation background fields in
@@
 $\mvir=6\times10^{14}\msun$. We find that inside a few percent of of
-$\rvir$ the total energy density is dominated by the light from SD,
+$\rvir$, the total energy density is dominated by the light from SD
 while the CMB is dominating elsewhere. This implies that if the boost
@@
 \end{tabular}
-\caption{The best fit parameters to the continuum emission from our
+\caption{Fit parameters to the continuum emission from our
   supersymmetric benchmark models.
@@
 
-Once again we use {\sc DarkSUSY} to derive the number of electrons and
-positrons resulting from each annihilation. This spectra is shown in
+We also use {\sc DarkSUSY} to derive the number of electrons and
+positrons resulting from each annihilation. These spectra are shown in
 the right panel of Fig.~\ref{fig:q_DM}. The electron and positron
@@
 \end{eqnarray}
-The best fit parameters are given in Tab.~\ref{tab:bm_elec}.
+Fit parameters are given in Tab.~\ref{tab:bm_elec}.
 \begin{table}[h]
@@
 \end{tabular}
-\caption{The best fit parameters to the electron and positron yield
+\caption{Fit parameters to the electron and positron yield
   above the electron energy $\ee$ from the supersymmetric benchmark
@@
 \end{eqnarray}
-It should be noted that the LP model that we are using in this work
+The LP model, that we are using in this work,
 has a branching factor branching ratio of ($1/2:1/2$) into
-($\mu^+\mu^-:\e^+\e^-$). Hence the resulting electron and positron
+($\mu^+\mu^-:\e^+\e^-$). Hence, the resulting electron and positron
 yield for the LP model is given by
@@
 Note that we remove the contribution of the flat central component of
-the fit ($i=1$) in the outer parts of the cluster, thus we cut it at
-about $40\,\kpc$.
+the fit ($i=1$) in the outer parts of the cluster, thus we neglect the
+central contribution for $r>40\,\kpc$.
 

### 2011-06-03 paper.tex
small changes
<Enter short summary of changes>

@@
 power-law function to fit\footnote{Our approach of fitting the
-  scaling behavior of $L_\rmn{sub}(<r)$ directly from numerical
+  scaling behavior of $L_\sub(<r)$ directly from numerical
   simulations self-consistently accounts for the radial dependence of
@@
 \begin{eqnarray}
-  L_\rmn{sub}(<x) &=& a_0\,C(\mvir)\,L_{200\sm}(\mvir)\,x^{a_1
+  L_\sub(<x) &=& a_0\,C(\mvir)\,L_{200\sm}(\mvir)\,x^{a_1
     \displaystyle{x}^{a_2}}\,,\label{eq:LSub}\\
@@
 
+\C{To further motivate the scaling of the substructure boost with
+  limiting substructure mass in Eqs.~(\ref{eq:LSub}-\ref{eq:CSub}), we
+  show how it relates to the substructure mass function, $\dd
+  N_\sub/\dd M \propto M^{-1.9}$ \cite{2008MNRAS.391.1685S}. Adopting
+  a mass dependence of the concentration parameter of $c\,(M)\propto
+  M$, as it is measured for dwarf halos \cite{}, the substructure
+  luminosity scales as $L_\sub\propto M^A$, where $A=0.674$. Hence we
+  find that the total luminosity of substructures scales as
+\begin{eqnarray}
+  L_\rmn{sub,tot} &=& L_\sub\,N_\sub = L_\sub 
+\int \dd M \frac{\dd N_\sub}{\dd M} \nonumber\\
+ &\propto& M^{A-0.9} \propto M^{-0.226}\,,
+\end{eqnarray}
+which is the result found by \cite{2008Natur.456...73S}.}
+
 We now derive the squared density profile for the substructures
@@
  \frac{\dd L_\rmn{sub}}{\dd V} &=& a_0\,a_1\,C(\mvir)\,x^{a_2+a_1\,x^{a_2}}\,
-\left[\frac{1+a_2\log(x)}{4\pi\,r^3}\right]\,,\\
+\left[\frac{1+a_2\log(x)}{4\pi\,r^3}\right]\,,\nonumber\\
+\\
 x &=& r/\rvir\,.\label{eq:xvir}
@@
   contribution from galaxies. Also note that in this paper the scaling
-  relations are normalized with $10^{15}/h_{70}\,\msun$, in contrast
-  to $10^{15}/h\,\msun$ that was used in \cite{2010MNRAS.409..449P}.}
+  relations are normalized with $10^{15}/h_{70}\,\msun$. \C{In
+    contrast, is the corresponding scaling relations in Table 5 in
+    \cite{2010MNRAS.409..449P} normalized with $10^{15}/h\,\msun$
+    instead of the mentioned $10^{15}/h_{70}\,\msun$. However, all
+    figures/tables/equations including the scaling relation figures
+    are derived for masses in units of $10^{15}/h_{70}\,\msun$.}}
 include the IC gamma-ray contribution from shock-accelerated electrons
@@
 mass-luminosity scaling relation. Statistically, one can view the
-analytical modeling as explicitely accounting for the scatter of the expected
+analytical modeling as explicitly accounting for the scatter of the expected
 gamma-ray flux at a given mass. Cool core clusters have a denser core
@@
 
-\smallskip We would like to thank Volker Springel for helpful
-comments.  A.P. acknowledges NSF grant AST 0908480 for support. We
-would furthermore like to thank KITP for their hospitality during the
-galaxy cluster workshop.  This research was supported in part by the
-National Science Foundation under Grant No. NSF PHY05-51164. The work
-of L.B. was supported by the Swedish Research Council (VR), under
+\smallskip We would like to thank Volker Springel, Megan Donahue,
+Stefano Profumo, and Tesla Jeltema for helpful discussions.  In
+addition we thank Neal Weiner ans Tracy Slatyer for many comments and
+suggestions for improvements of a previous version of this
+paper. A.P. acknowledges NSF grant AST 0908480 for support. We would
+furthermore like to thank KITP for their hospitality during the galaxy
+cluster workshop.  This research was supported in part by the National
+Science Foundation under Grant No. NSF PHY05-51164.  C.P. gratefully
+acknowledges financial support of the Klaus Tschira Foundation. The
+work of L.B. was supported by the Swedish Research Council (VR), under
 contracts no. 621-2009-3915 and 349-2007-8709 (the Oskar Klein
@@
 The cluster emission from far-IR to optical/UV is due to dust emission
-and stellar light, respectively. We distiguish three components: the
+and stellar light, respectively. We distinguish three components: the
 brightest cluster galaxy (BCG), the intra-cluster light (ICL) and
@@
 spectral distribution of the stars that peaks at about $1\,\ev$ is
-fitted using a tripple power-law. The best fit to the galactic spectrum
+fitted using a triple power-law. The best fit to the galactic spectrum
 is given by:
@@
 with the DM distribution of a cluster is very small compared to the
-overlaping volume of ICL- and BCG-light with the DM distribution;
+overlapping volume of ICL- and BCG-light with the DM distribution;
 thus, the relative contribution of the galaxies to the IC emission is
@@
 where the model specific parameters are given in
-Tab.~\ref{tab:bm_cont}.
+Table~\ref{tab:bm_cont}.
 
@@
 \end{eqnarray}
-Fit parameters are given in Tab.~\ref{tab:bm_elec}.
+Fit parameters are given in Table~\ref{tab:bm_elec}.
 \begin{table}[h]
@@
 Finally, we use {\sc DarkSUSY} to derive the electron and positron
-yield resulting from LP DM annihilating into decaying muons. We find
-the following best fit:
+yield resulting from leptophilic (LP) DM annihilating into decaying
+muons. We find the following best fit:
 \begin{eqnarray}
@@
 
-\del{
 \section{Flux tables for the HIFLUGCS catalogue}
-TO BE WRITTEN
-}
+
+\C{In this section we present the gamma-ray flux predictions using the
+clusters in the extended HIFLUGCS catalogue. We show the brightest 50
+clusters in descending order; CR proton induced $\pi^0$ that decays
+into gamma-rays in Table~\ref{tab:flux_tab_CRs}, the supersymmetric DM
+BM-$\Kp$ model where the Neutralino emit a continuum as well as final
+state radiation in Table~\ref{tab:flux_tab_BM}, and LP DM that emit
+final state radiation and annihilate either indirectly through
+$\mu^+/\mu^-$ to $\rmn{e}^+/\rmn{e}^-$ or directly to
+$\rmn{e}^+/\rmn{e}^-$ that IC upscatter CMB photons in
+Table~\ref{tab:flux_tab_LP}. The flux from DM has been boosted by the
+substructures, where we in addition include the Sommerfeld enhancement
+for the LP model.  
+For completeness, we show in Table~\ref{tab:flux_tab_CLp} the
+parameters that we use to derive the fluxes for the clusters in the
+HIFLUGCS sample.}
+
+\begin{table*}
+\begin{minipage}{2.0\columnwidth}
+  \caption{Gamma-ray CR-$\pi^0$ flux within $\rvir$ from brightest 50 clusters in HIFLUGCS catalogue.}
+\begin{tabular}{l  c c c c c c c}
+\hline
+\hline
+ Cluster & ID$^{(1)}$ & $F_{\gamma}$$^{(2)}$ & $F_{\gamma}$$^{(3)}$& 
+ $F_{\gamma}$$^{(4)}$ & $\eg^2\,\dd F_{\gamma}/\dd \eg$$^{(5)}$ &
+ $\eg^2\,\dd F_{\gamma,0.1}/\dd \eg$$^{(5,6)}$ & 
+ $\eg^2\,\dd F_{\gamma,1.0}/\dd \eg$$^{(5,7)}$\\
+  & & $(>100\,\rmn{MeV})$ & $(>1\,\rmn{GeV})$ & $(>100\,\rmn{GeV})$ & 
+ $(5\,\rmn{GeV})$ & $(5\,\rmn{GeV})$ &  $(5\,\rmn{GeV})$\\
+ \hline
+PERSEUS  &  68 &  56.14 &  75.31 &  20.64 &  63.95 &  13.92 &  24.52 \\
+OPHIUCHUS &  96 &  23.31 &  31.27 &   8.57 &  26.55 &   5.88 &  10.28 \\
+COMA     &  34 &  17.50 &  23.48 &   6.43 &  19.94 &   2.62 &   7.56 \\
+NORMA    &  94 &  13.39 &  17.97 &   4.92 &  15.26 &   1.16 &   5.57 \\
+CENTAURUS &  30 &  12.06 &  16.17 &   4.43 &  13.73 &   2.45 &   5.04 \\
+AWM7     &  67 &   8.24 &  11.05 &   3.03 &   9.38 &   1.85 &   3.63 \\
+A3571    &  39 &   6.10 &   8.19 &   2.24 &   6.95 &   1.80 &   2.83 \\
+TRIANGULUM &  95 &   5.92 &   7.95 &   2.18 &   6.75 &   1.61 &   2.81 \\
+A2319    &  98 &   5.58 &   7.48 &   2.05 &   6.35 &   1.54 &   2.74 \\
+A2199    &  51 &   5.18 &   6.94 &   1.90 &   5.90 &   1.68 &   2.35 \\
+3C129    &  70 &   5.15 &   6.91 &   1.89 &   5.87 &   0.71 &   2.30 \\
+HYDRA    &  25 &   5.15 &   6.91 &   1.89 &   5.86 &   1.11 &   2.22 \\
+2A0335   &  11 &   4.91 &   6.59 &   1.81 &   5.59 &   1.94 &   2.33 \\
+FORNAX   &  10 &   4.09 &   5.48 &   1.50 &   4.66 &   0.33 &   1.65 \\
+A2029    &  43 &   3.73 &   5.00 &   1.37 &   4.25 &   1.45 &   1.80 \\
+A0496    &  18 &   3.59 &   4.81 &   1.32 &   4.09 &   1.13 &   1.84 \\
+A0085    &   1 &   3.54 &   4.75 &   1.30 &   4.04 &   1.20 &   1.79 \\
+A1795    &  40 &   3.52 &   4.73 &   1.29 &   4.01 &   1.37 &   1.66 \\
+A2256    &  54 &   3.45 &   4.63 &   1.27 &   3.93 &   1.11 &   1.55 \\
+PKS0745  &  77 &   3.28 &   4.40 &   1.20 &   3.73 &   1.39 &   1.57 \\
+A3266    &  17 &   3.18 &   4.27 &   1.17 &   3.63 &   0.92 &   1.45 \\
+A2142    &  48 &   3.09 &   4.14 &   1.13 &   3.52 &   1.16 &   1.50 \\
+NGC5044  &  35 &   2.97 &   3.98 &   1.09 &   3.38 &   1.01 &   1.34 \\
+A3558    &  37 &   2.89 &   3.88 &   1.06 &   3.29 &   0.82 &   1.44 \\
+A3667    &  56 &   2.85 &   3.82 &   1.05 &   3.25 &   0.73 &   1.55 \\
+A0262    &   5 &   2.76 &   3.70 &   1.01 &   3.14 &   0.57 &   1.41 \\
+A0478    &  14 &   2.72 &   3.64 &   1.00 &   3.09 &   1.11 &   1.30 \\
+A1367    &  26 &   2.65 &   3.55 &   0.97 &   3.02 &   0.40 &   1.19 \\
+A4038    &  62 &   2.56 &   3.43 &   0.94 &   2.91 &   0.83 &   1.22 \\
+HYDRA-A  &  24 &   2.46 &   3.30 &   0.90 &   2.80 &   0.98 &   1.19 \\
+A0401    &   8 &   2.39 &   3.21 &   0.88 &   2.72 &   0.82 &   1.16 \\
+A2052    &  44 &   2.25 &   3.02 &   0.83 &   2.57 &   0.81 &   1.11 \\
+A0644    &  78 &   2.17 &   2.91 &   0.80 &   2.47 &   0.84 &   0.98 \\
+NGC1550  &  15 &   2.06 &   2.76 &   0.76 &   2.35 &   0.59 &   0.93 \\
+NGC4636  &  29 &   2.06 &   2.76 &   0.76 &   2.34 &   0.55 &   0.86 \\
+A0754    &  23 &   2.03 &   2.73 &   0.75 &   2.32 &   0.69 &   0.92 \\
+ANTLIA   &  79 &   1.87 &   2.50 &   0.69 &   2.13 &   0.19 &   0.82 \\
+A3158    &  13 &   1.83 &   2.45 &   0.67 &   2.08 &   0.61 &   0.86 \\
+A2147    &  49 &   1.80 &   2.41 &   0.66 &   2.05 &   0.29 &   1.19 \\
+A0119    &   2 &   1.75 &   2.35 &   0.65 &   2.00 &   0.38 &   0.84 \\
+A2063    &  47 &   1.70 &   2.28 &   0.63 &   1.94 &   0.53 &   0.82 \\
+A3581    &  41 &   1.66 &   2.22 &   0.61 &   1.89 &   0.58 &   0.78 \\
+A1644    &  31 &   1.63 &   2.19 &   0.60 &   1.86 &   0.42 &   0.85 \\
+MKW3S    &  45 &   1.62 &   2.18 &   0.60 &   1.85 &   0.62 &   0.77 \\
+A2065    &  46 &   1.56 &   2.09 &   0.57 &   1.78 &   0.58 &   0.70 \\
+A0399    &   7 &   1.55 &   2.07 &   0.57 &   1.76 &   0.50 &   0.73 \\
+A3112    &   9 &   1.54 &   2.07 &   0.57 &   1.76 &   0.63 &   0.76 \\
+EXO0422  &  16 &   1.53 &   2.05 &   0.56 &   1.74 &   0.58 &   0.69 \\
+A4059    &  63 &   1.51 &   2.02 &   0.55 &   1.72 &   0.54 &   0.72 \\
+A0576    &  22 &   1.47 &   1.97 &   0.54 &   1.68 &   0.42 &   0.66 \\
+\hline
+\hline
+\end{tabular}
+\begin{quote}
+  Notes: 
+   (1) The HIFLUGCS cluster ID.
+   (2) In units of  $10^{-10} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (3) In units of  $10^{-11} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (4) In units of  $10^{-13} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (5) In units of  $10^{-11} \rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (6) The flux within $0.1$ degree. In addition, we smooth the flux with a point spread function of $0.1$ degree. 
+   (7) The flux within $1.0$ degree. In addition, we smooth the flux with a point spread function of $1.0$ degree. 
+ \label{tab:flux_tab_CRs}
+  \end{quote}
+\end{minipage}
+\end{table*}
+
+\begin{table*}
+\begin{minipage}{2.0\columnwidth}
+  \caption{Gamma-ray BM-$\Kp$ Continuum flux within $\rvir$ from brightest 50 clusters in HIFLUGCS catalogue.}
+\begin{tabular}{l  c c c c c c c}
+\hline
+\hline
+ Cluster & ID$^{(1)}$ & $F_{\gamma}$$^{(2)}$ & $F_{\gamma}$$^{(3)}$& 
+ $F_{\gamma}$$^{(4)}$ & $\eg^2\,\dd F_{\gamma}/\dd \eg$$^{(5)}$ &
+ $\eg^2\,\dd F_{\gamma,0.1}/\dd \eg$$^{(5,6)}$ & 
+ $\eg^2\,\dd F_{\gamma,1.0}/\dd \eg$$^{(5,7)}$\\
+  & & $(>100\,\rmn{MeV})$ & $(>1\,\rmn{GeV})$ & $(>100\,\rmn{GeV})$ & 
+ $(5\,\rmn{GeV})$ & $(5\,\rmn{GeV})$ &  $(5\,\rmn{GeV})$\\
+ \hline
+FORNAX   &  10 &  12.71 &  80.57 &  44.45 &  12.76 &   0.09 &   2.61 \\
+OPHIUCHUS &  96 &   9.95 &  63.10 &  34.81 &   9.99 &   0.27 &   3.90 \\
+COMA     &  34 &   8.26 &  52.38 &  28.89 &   8.29 &   0.22 &   3.20 \\
+NORMA    &  94 &   7.48 &  47.43 &  26.16 &   7.51 &   0.17 &   2.68 \\
+CENTAURUS &  30 &   7.24 &  45.87 &  25.31 &   7.26 &   0.12 &   2.28 \\
+PERSEUS  &  68 &   7.15 &  45.30 &  24.99 &   7.17 &   0.18 &   2.67 \\
+HYDRA    &  25 &   6.75 &  42.81 &  23.61 &   6.78 &   0.12 &   2.23 \\
+M49      &  81 &   5.98 &  37.93 &  20.92 &   6.00 &   0.06 &   1.51 \\
+NGC4636  &  29 &   4.42 &  28.01 &  15.45 &   4.44 &   0.05 &   1.14 \\
+AWM7     &  67 &   4.30 &  27.24 &  15.03 &   4.31 &   0.13 &   1.76 \\
+3C129    &  70 &   4.06 &  25.74 &  14.20 &   4.08 &   0.15 &   1.79 \\
+A1367    &  26 &   2.51 &  15.92 &   8.78 &   2.52 &   0.11 &   1.20 \\
+NGC5846  &  92 &   2.48 &  15.73 &   8.68 &   2.49 &   0.05 &   0.86 \\
+A0754    &  23 &   2.14 &  13.57 &   7.49 &   2.15 &   0.17 &   1.26 \\
+TRIANGULUM &  95 &   1.85 &  11.72 &   6.47 &   1.86 &   0.16 &   1.10 \\
+A3571    &  39 &   1.84 &  11.68 &   6.45 &   1.85 &   0.14 &   1.05 \\
+NGC5813  &  91 &   1.59 &  10.06 &   5.55 &   1.59 &   0.04 &   0.62 \\
+ANTLIA   &  79 &   1.58 &  10.03 &   5.53 &   1.59 &   0.06 &   0.71 \\
+A2199    &  51 &   1.54 &   9.73 &   5.37 &   1.54 &   0.11 &   0.85 \\
+A3266    &  17 &   1.50 &   9.49 &   5.24 &   1.50 &   0.15 &   0.94 \\
+A2877    &  65 &   1.48 &   9.40 &   5.18 &   1.49 &   0.09 &   0.79 \\
+NGC5044  &  35 &   1.42 &   9.00 &   4.97 &   1.43 &   0.05 &   0.61 \\
+A3395n   &  75 &   1.35 &   8.57 &   4.73 &   1.36 &   0.13 &   0.83 \\
+A3395s   &  21 &   1.35 &   8.56 &   4.72 &   1.36 &   0.13 &   0.83 \\
+A2256    &  54 &   1.34 &   8.49 &   4.68 &   1.34 &   0.14 &   0.85 \\
+A0576    &  22 &   1.31 &   8.28 &   4.57 &   1.31 &   0.11 &   0.77 \\
+NGC1550  &  15 &   1.30 &   8.25 &   4.55 &   1.31 &   0.06 &   0.62 \\
+A2319    &  98 &   1.25 &   7.92 &   4.37 &   1.25 &   0.13 &   0.80 \\
+A3376    &  19 &   1.24 &   7.85 &   4.33 &   1.24 &   0.12 &   0.76 \\
+A0119    &   2 &   1.19 &   7.54 &   4.16 &   1.19 &   0.11 &   0.73 \\
+A2634    &  60 &   1.11 &   7.07 &   3.90 &   1.12 &   0.09 &   0.65 \\
+A0262    &   5 &   1.02 &   6.46 &   3.57 &   1.02 &   0.06 &   0.53 \\
+A2065    &  46 &   0.98 &   6.21 &   3.42 &   0.98 &   0.13 &   0.67 \\
+A0539    &  71 &   0.90 &   5.70 &   3.14 &   0.90 &   0.08 &   0.53 \\
+MKW8     &  42 &   0.89 &   5.65 &   3.12 &   0.89 &   0.07 &   0.52 \\
+A1795    &  40 &   0.87 &   5.50 &   3.03 &   0.87 &   0.11 &   0.58 \\
+A0644    &  78 &   0.85 &   5.42 &   2.99 &   0.86 &   0.11 &   0.59 \\
+A4038    &  62 &   0.82 &   5.23 &   2.88 &   0.83 &   0.07 &   0.49 \\
+A0496    &  18 &   0.80 &   5.09 &   2.81 &   0.81 &   0.08 &   0.49 \\
+IIIZw54  &  12 &   0.80 &   5.05 &   2.79 &   0.80 &   0.07 &   0.49 \\
+A2147    &  49 &   0.78 &   4.97 &   2.74 &   0.79 &   0.08 &   0.49 \\
+A3558    &  37 &   0.77 &   4.88 &   2.69 &   0.77 &   0.09 &   0.51 \\
+A3667    &  56 &   0.75 &   4.74 &   2.62 &   0.75 &   0.09 &   0.51 \\
+A0085    &   1 &   0.73 &   4.64 &   2.56 &   0.73 &   0.09 &   0.50 \\
+A2063    &  47 &   0.72 &   4.58 &   2.52 &   0.72 &   0.07 &   0.46 \\
+A0399    &   7 &   0.69 &   4.39 &   2.42 &   0.69 &   0.10 &   0.49 \\
+UGC03957 &  76 &   0.69 &   4.35 &   2.40 &   0.69 &   0.07 &   0.43 \\
+A2029    &  43 &   0.68 &   4.34 &   2.39 &   0.69 &   0.10 &   0.49 \\
+A0400    &   6 &   0.68 &   4.31 &   2.38 &   0.68 &   0.06 &   0.41 \\
+A3158    &  13 &   0.67 &   4.26 &   2.35 &   0.67 &   0.09 &   0.46 \\
+\hline
+\hline
+\end{tabular}
+\begin{quote}
+  Notes: 
+   (1) The HIFLUGCS cluster ID.
+   (2) In units of  $10^{-11} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (3) In units of  $10^{-12} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (4) In units of  $10^{-14} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (5) In units of  $10^{-11} \rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (6) The flux within $0.1$ degree. In addition, we smooth the flux with a point spread function of $0.1$ degree. 
+   (7) The flux within $1.0$ degree. In addition, we smooth the flux with a point spread function of $1.0$ degree. 
+  \label{tab:flux_tab_BM}
+  \end{quote}
+\end{minipage}
+\end{table*}
+
+\begin{table*}
+\begin{minipage}{2.0\columnwidth}
+  \caption{Gamma-ray LP-IC-CMB and LP-BS flux within $\rvir$ from brightest 50 clusters in HIFLUGCS catalogue.}
+\begin{tabular}{l  c c c c c c c}
+\hline
+\hline
+ Cluster & ID$^{(1)}$ & $F_{\gamma}$$^{(2)}$ & $F_{\gamma}$$^{(2)}$& 
+ $F_{\gamma}$$^{(3)}$ & $\eg^2\,\dd F_{\gamma}/\dd \eg$$^{(4)}$ &
+ $\eg^2\,\dd F_{\gamma,0.1}/\dd \eg$$^{(4,5)}$ & 
+ $\eg^2\,\dd F_{\gamma,1.0}/\dd \eg$$^{(4,6)}$\\
+  & & $(>100\,\rmn{MeV})$ & $(>1\,\rmn{GeV})$ & $(>100\,\rmn{GeV})$ & 
+ $(5\,\rmn{GeV})$ & $(5\,\rmn{GeV})$ &  $(5\,\rmn{GeV})$\\
+ \hline
+FORNAX   &  10 &  50.40 &  93.76 &  50.96 &  11.56 &   0.06 &   2.30 \\
+M49      &  81 &  31.16 &  57.97 &  31.12 &   7.15 &   0.06 &   1.77 \\
+NGC4636  &  29 &  28.06 &  52.20 &  28.26 &   6.44 &   0.05 &   1.63 \\
+CENTAURUS &  30 &  21.23 &  39.50 &  20.93 &   4.87 &   0.07 &   1.53 \\
+HYDRA    &  25 &  19.00 &  35.36 &  18.80 &   4.36 &   0.07 &   1.43 \\
+NORMA    &  94 &  15.74 &  29.28 &  16.09 &   3.61 &   0.07 &   1.29 \\
+PERSEUS  &  68 &  14.84 &  27.60 &  14.57 &   3.40 &   0.08 &   1.27 \\
+OPHIUCHUS &  96 &  14.27 &  26.54 &  14.07 &   3.27 &   0.08 &   1.28 \\
+COMA     &  34 &  13.81 &  25.70 &  13.86 &   3.17 &   0.07 &   1.22 \\
+NGC5846  &  92 &  13.80 &  25.67 &  13.82 &   3.16 &   0.05 &   1.09 \\
+AWM7     &  67 &  10.67 &  19.84 &  10.61 &   2.45 &   0.07 &   1.00 \\
+NGC5813  &  91 &   9.81 &  18.25 &   9.87 &   2.25 &   0.05 &   0.87 \\
+3C129    &  70 &   8.54 &  15.88 &   8.70 &   1.96 &   0.06 &   0.86 \\
+NGC5044  &  35 &   7.40 &  13.76 &   7.39 &   1.70 &   0.05 &   0.73 \\
+ANTLIA   &  79 &   6.28 &  11.68 &   6.79 &   1.44 &   0.04 &   0.66 \\
+A1367    &  26 &   6.12 &  11.39 &   6.34 &   1.40 &   0.05 &   0.68 \\
+NGC1550  &  15 &   5.72 &  10.63 &   5.70 &   1.31 &   0.05 &   0.62 \\
+A0262    &   5 &   4.10 &   7.62 &   4.09 &   0.94 &   0.05 &   0.49 \\
+A2877    &  65 &   4.08 &   7.59 &   4.13 &   0.94 &   0.05 &   0.50 \\
+A2199    &  51 &   3.70 &   6.89 &   3.67 &   0.85 &   0.06 &   0.47 \\
+A3571    &  39 &   3.54 &   6.59 &   3.50 &   0.81 &   0.06 &   0.46 \\
+A0754    &  23 &   3.29 &   6.13 &   3.25 &   0.76 &   0.06 &   0.44 \\
+TRIANGULUM &  95 &   3.00 &   5.59 &   2.99 &   0.69 &   0.06 &   0.41 \\
+A0576    &  22 &   2.80 &   5.21 &   2.83 &   0.64 &   0.05 &   0.38 \\
+A2634    &  60 &   2.76 &   5.14 &   2.87 &   0.63 &   0.04 &   0.38 \\
+MKW8     &  42 &   2.69 &   5.00 &   2.69 &   0.62 &   0.05 &   0.36 \\
+A0539    &  71 &   2.60 &   4.84 &   2.61 &   0.60 &   0.05 &   0.36 \\
+NGC499   &  66 &   2.51 &   4.67 &   2.51 &   0.58 &   0.04 &   0.33 \\
+A4038    &  62 &   2.50 &   4.65 &   2.47 &   0.57 &   0.05 &   0.34 \\
+A3581    &  41 &   2.43 &   4.52 &   2.41 &   0.56 &   0.04 &   0.33 \\
+A3395s   &  21 &   2.40 &   4.47 &   2.45 &   0.55 &   0.05 &   0.35 \\
+A3395n   &  75 &   2.38 &   4.43 &   2.44 &   0.55 &   0.05 &   0.34 \\
+A0400    &   6 &   2.36 &   4.38 &   2.41 &   0.54 &   0.04 &   0.33 \\
+A3376    &  19 &   2.35 &   4.37 &   2.44 &   0.54 &   0.04 &   0.34 \\
+A0119    &   2 &   2.33 &   4.34 &   2.43 &   0.53 &   0.04 &   0.34 \\
+A3266    &  17 &   2.31 &   4.30 &   2.35 &   0.53 &   0.05 &   0.34 \\
+IIIZw54  &  12 &   2.25 &   4.19 &   2.28 &   0.52 &   0.04 &   0.32 \\
+A0496    &  18 &   2.25 &   4.19 &   2.22 &   0.52 &   0.05 &   0.32 \\
+NGC507   &   4 &   2.18 &   4.05 &   2.18 &   0.50 &   0.04 &   0.30 \\
+A2319    &  98 &   2.14 &   3.99 &   2.15 &   0.49 &   0.05 &   0.32 \\
+A2256    &  54 &   2.14 &   3.97 &   2.16 &   0.49 &   0.05 &   0.32 \\
+MKW4     &  27 &   2.03 &   3.78 &   2.02 &   0.47 &   0.04 &   0.29 \\
+A2147    &  49 &   2.00 &   3.72 &   2.09 &   0.46 &   0.04 &   0.29 \\
+A2063    &  47 &   1.98 &   3.68 &   1.96 &   0.45 &   0.04 &   0.29 \\
+UGC03957 &  76 &   1.96 &   3.65 &   1.95 &   0.45 &   0.04 &   0.29 \\
+2A0335   &  11 &   1.70 &   3.17 &   1.68 &   0.39 &   0.04 &   0.25 \\
+A3558    &  37 &   1.68 &   3.13 &   1.69 &   0.39 &   0.04 &   0.26 \\
+EXO0422  &  16 &   1.64 &   3.05 &   1.63 &   0.38 &   0.04 &   0.25 \\
+A1795    &  40 &   1.60 &   2.98 &   1.57 &   0.37 &   0.05 &   0.25 \\
+A2052    &  44 &   1.54 &   2.87 &   1.52 &   0.35 &   0.04 &   0.23 \\
+\hline
+\hline
+\end{tabular}
+\begin{quote}
+  Notes: 
+   (1) The HIFLUGCS cluster ID.
+   (2) In units of  $10^{-9} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (3) In units of  $10^{-13} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (4) In units of  $10^{-13} \rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (5) The flux within $0.1$ degree that have in addition been smoothed over with a point spread function of $0.1$ degree. 
+   (6) The flux within $1.0$ degree that have in addition been smoothed over with a point spread function of $1.0$ degree. 
+ \label{tab:flux_tab_LP}
+  \end{quote}
+\end{minipage}
+\end{table*}
+
+\begin{table*}
+\begin{minipage}{2.0\columnwidth}
+  \caption{Galaxy cluster parameters for to all clusters in the HIFLUGCS catalogue.}
+\begin{tabular}{l  c c c c c c c c c c c}
+\hline
+\hline
+Cluster & ID$^{(1)}$ & $D_\clu$$^{(1)}$ & $\rvir$$^{(1)}$ & $\rvir$ & 
+$\mvir$$^{(1)}$ & $\rho_\rmn{gas}(0)$$^{(2)}$ & $r_\rmn{core}$$^{(2)}$ & 
+$\beta$$^{(2)}$ & $r_\rmn{hlr,CR}$$^{(3)}$ & $r_\rmn{hlr,DM}$  $^{(4)}$ \\
+& & [Mpc] & [Mpc] & [deg] & [$10^{14}\,\msun$] & 
+[$10^{-27}\,\rmn{g}\,\rmn{cm}^{-3}$] & [kpc] &  & [deg] & [deg] \\
+ \hline
+A0085    &   1 & 248.29 &   1.90 &   0.44 &   7.71 &  24.54 &  59.29 &   0.53 &   0.04 &   0.20 \\
+A0119    &   2 & 194.82 &   1.90 &   0.56 &   7.69 &   1.93 & 357.86 &   0.68 &   0.13 &   0.26 \\
+A0133    &   3 & 254.34 &   1.41 &   0.32 &   3.15 &  35.76 &  32.14 &   0.53 &   0.02 &   0.15 \\
+NGC507   &   4 &  71.57 &   0.74 &   0.59 &   0.46 &  23.05 &  13.57 &   0.44 &   0.07 &   0.28 \\
+A0262    &   5 &  69.81 &   0.96 &   0.79 &   1.01 &  14.38 &  30.00 &   0.44 &   0.14 &   0.37 \\
+A0400    &   6 & 104.69 &   1.09 &   0.60 &   1.48 &   3.40 & 110.00 &   0.53 &   0.12 &   0.28 \\
+A0399    &   7 & 323.00 &   2.19 &   0.39 &  11.89 &   3.40 & 321.43 &   0.71 &   0.07 &   0.18 \\
+A0401    &   8 & 338.70 &   2.19 &   0.37 &  11.85 &   7.84 & 175.71 &   0.61 &   0.05 &   0.17 \\
+A3112    &   9 & 339.66 &   1.74 &   0.29 &   5.87 &  43.07 &  43.57 &   0.58 &   0.02 &   0.14 \\
+FORNAX   &  10 &  19.77 &   0.96 &   2.79 &   1.01 &   2.48 & 124.29 &   0.80 &   0.31 &   1.30 \\
+2A0335   &  11 & 153.49 &   1.31 &   0.49 &   2.51 &  93.06 &  23.57 &   0.57 &   0.02 &   0.23 \\
+IIIZw54  &  12 & 136.39 &   1.35 &   0.57 &   2.81 &   3.86 & 206.43 &   0.89 &   0.07 &   0.26 \\
+A3158    &  13 & 264.13 &   1.92 &   0.42 &   8.06 &   5.96 & 192.14 &   0.66 &   0.06 &   0.19 \\
+A0478    &  14 & 411.96 &   2.24 &   0.31 &  12.78 &  35.47 &  70.00 &   0.61 &   0.02 &   0.14 \\
+NGC1550  &  15 &  53.18 &   0.88 &   0.95 &   0.78 &  15.86 &  32.14 &   0.55 &   0.07 &   0.44 \\
+EXO0422  &  16 & 172.04 &   1.43 &   0.48 &   3.31 &  11.91 & 101.43 &   0.72 &   0.04 &   0.22 \\
+A3266    &  17 & 266.00 &   2.46 &   0.53 &  16.97 &   3.17 & 402.86 &   0.80 &   0.08 &   0.25 \\
+A0496    &  18 & 144.03 &   1.40 &   0.56 &   3.11 &  51.30 &  21.43 &   0.48 &   0.05 &   0.26 \\
+A3376    &  19 & 201.69 &   1.96 &   0.56 &   8.54 &   1.70 & 539.29 &   1.05 &   0.10 &   0.26 \\
+A3391    &  20 & 236.69 &   1.74 &   0.42 &   6.01 &   3.93 & 167.14 &   0.58 &   0.07 &   0.20 \\
+A3395s   &  21 & 221.45 &   2.14 &   0.55 &  10.96 &   2.07 & 431.43 &   0.96 &   0.08 &   0.26 \\
+A0576    &  22 & 167.96 &   1.79 &   0.61 &   6.40 &   2.97 & 281.43 &   0.82 &   0.08 &   0.28 \\
+A0754    &  23 & 235.31 &   2.55 &   0.62 &  18.71 &   5.98 & 170.71 &   0.70 &   0.05 &   0.29 \\
+HYDRA-A  &  24 & 239.94 &   1.55 &   0.37 &   4.24 &  53.04 &  35.71 &   0.57 &   0.02 &   0.17 \\
+HYDRA    &  25 &  49.25 &   1.39 &   1.62 &   3.03 &   8.20 &  67.14 &   0.61 &   0.13 &   0.75 \\
+A1367    &  26 &  94.05 &   1.53 &   0.93 &   4.06 &   2.02 & 273.57 &   0.69 &   0.19 &   0.43 \\
+MKW4     &  27 &  86.98 &   0.86 &   0.56 &   0.71 &  50.43 &   7.86 &   0.44 &   0.06 &   0.26 \\
+ZwCl1215 &  28 & 339.66 &   2.09 &   0.35 &  10.37 &   4.07 & 307.86 &   0.82 &   0.05 &   0.16 \\
+NGC4636  &  29 &  15.89 &   0.61 &   2.19 &   0.25 &  55.18 &   4.29 &   0.49 &   0.07 &   1.02 \\
+CENTAURU &  30 &  44.46 &   1.34 &   1.72 &   2.70 &  24.45 &  26.43 &   0.49 &   0.14 &   0.80 \\
+A1644    &  31 & 210.40 &   1.62 &   0.44 &   4.81 &   3.49 & 214.29 &   0.58 &   0.10 &   0.21 \\
+A1650    &  32 & 385.28 &   2.15 &   0.32 &  11.14 &   6.77 & 200.71 &   0.70 &   0.04 &   0.15 \\
+A1651    &  33 & 392.54 &   1.96 &   0.29 &   8.51 &  11.72 & 129.29 &   0.64 &   0.03 &   0.13 \\
+COMA     &  34 & 101.14 &   2.30 &   1.30 &  13.84 &   4.34 & 245.71 &   0.65 &   0.20 &   0.60 \\
+NGC5044  &  35 &  38.81 &   0.74 &   1.10 &   0.46 &  81.77 &   7.86 &   0.52 &   0.03 &   0.51 \\
+A1736    &  36 & 204.44 &   1.34 &   0.37 &   2.70 &   2.10 & 267.14 &   0.54 &   0.12 &   0.17 \\
+A3558    &  37 & 213.16 &   1.76 &   0.47 &   6.17 &   6.51 & 160.00 &   0.58 &   0.08 &   0.22 \\
+A3562    &  38 & 221.91 &   1.54 &   0.40 &   4.16 &   8.30 &  70.71 &   0.47 &   0.08 &   0.18 \\
+A3571    &  39 & 175.22 &   2.04 &   0.67 &   9.51 &  10.39 & 129.29 &   0.61 &   0.07 &   0.31 \\
+A1795    &  40 & 276.29 &   2.14 &   0.44 &  10.99 &  35.96 &  55.71 &   0.60 &   0.02 &   0.21 \\
+A3581    &  41 &  93.17 &   0.99 &   0.61 &   1.09 &  31.10 &  25.00 &   0.54 &   0.03 &   0.28 \\
+MKW8     &  42 & 118.04 &   1.28 &   0.62 &   2.38 &   5.06 &  76.43 &   0.51 &   0.10 &   0.29 \\
+A2029    &  43 & 347.78 &   2.29 &   0.38 &  13.42 &  38.80 &  59.29 &   0.58 &   0.02 &   0.17 \\
+A2052    &  44 & 153.04 &   1.25 &   0.47 &   2.21 &  44.71 &  26.43 &   0.53 &   0.03 &   0.22 \\
+MKW3S    &  45 & 199.40 &   1.45 &   0.42 &   3.46 &  26.57 &  47.14 &   0.58 &   0.02 &   0.19 \\
+A2065    &  46 & 325.85 &   2.45 &   0.43 &  16.69 &   3.31 & 492.86 &   1.16 &   0.05 &   0.20 \\
+A2063    &  47 & 155.75 &   1.42 &   0.52 &   3.24 &  10.17 &  78.57 &   0.56 &   0.06 &   0.24 \\
+A2142    &  48 & 411.47 &   2.36 &   0.33 &  15.03 &  18.05 & 110.00 &   0.59 &   0.03 &   0.15 \\
+A2147    &  49 & 154.39 &   1.45 &   0.54 &   3.46 &   2.41 & 170.00 &   0.44 &   0.18 &   0.25 \\
+A2163    &  50 & 990.91 &   3.21 &   0.19 &  37.14 &   6.43 & 370.71 &   0.80 &   0.02 &   0.09 \\
+A2199    &  51 & 132.35 &   1.62 &   0.70 &   4.81 &  13.66 &  99.29 &   0.66 &   0.06 &   0.33 \\
+A2204    &  52 & 727.47 &   2.06 &   0.16 &   9.85 &  73.26 &  47.86 &   0.60 &   0.01 &   0.08 \\
+A2244    &  53 & 446.19 &   2.06 &   0.27 &   9.84 &  17.26 &  90.00 &   0.61 &   0.02 &   0.12 \\
+A2256    &  54 & 269.27 &   2.40 &   0.51 &  15.58 &   3.90 & 419.29 &   0.91 &   0.07 &   0.24 \\
+A2255    &  55 & 363.60 &   2.27 &   0.36 &  13.32 &   2.40 & 423.57 &   0.80 &   0.06 &   0.17 \\
+\end{tabular}
+\end{minipage}
+\end{table*} 
+\newpage
+\begin{table}
+\begin{minipage}{2.0\columnwidth}
+\begin{tabular}{l  c c c c c c c c c c c}
+\hline
+\hline
+Cluster & ID$^{(1)}$ & $D_\clu$$^{(1)}$ & $\rvir$$^{(1)}$ & $\rvir$ & 
+$\mvir$$^{(1)}$ & $\rho_\rmn{gas}(0)$$^{(2)}$ & $r_\rmn{core}$$^{(2)}$ & 
+$\beta$$^{(2)}$ & $r_\rmn{hlr,CR}$$^{(3)}$ & $r_\rmn{hlr,DM}$  $^{(4)}$ \\
+& & [Mpc] & [Mpc] & [deg] & [$10^{14}\,\msun$] & 
+[$10^{-27}\,\rmn{g}\,\rmn{cm}^{-3}$] & [kpc] &  & [deg] & [deg] \\
+ \hline
+A3667    &  56 & 250.15 &   1.92 &   0.44 &   7.99 &   4.64 & 199.29 &   0.54 &   0.10 &   0.20 \\
+S1101    &  57 & 259.46 &   1.37 &   0.30 &   2.91 &  48.52 &  40.00 &   0.64 &   0.01 &   0.14 \\
+A2589    &  58 & 183.87 &   1.47 &   0.46 &   3.58 &  10.07 &  84.29 &   0.60 &   0.04 &   0.21 \\
+A2597    &  59 & 388.66 &   1.65 &   0.24 &   5.10 &  59.06 &  41.43 &   0.63 &   0.01 &   0.11 \\
+A2634    &  60 & 136.84 &   1.50 &   0.63 &   3.82 &   1.70 & 260.00 &   0.64 &   0.14 &   0.29 \\
+A2657    &  61 & 178.41 &   1.42 &   0.46 &   3.23 &   8.16 &  85.00 &   0.56 &   0.06 &   0.21 \\
+A4038    &  62 & 123.85 &   1.29 &   0.59 &   2.44 &  22.03 &  42.14 &   0.54 &   0.05 &   0.28 \\
+A4059    &  63 & 203.98 &   1.59 &   0.45 &   4.50 &  16.44 &  64.29 &   0.58 &   0.03 &   0.21 \\
+A2734    &  64 & 278.16 &   1.53 &   0.31 &   4.05 &   5.24 & 151.43 &   0.62 &   0.05 &   0.15 \\
+A2877    &  65 & 105.13 &   1.39 &   0.76 &   3.03 &   2.30 & 135.71 &   0.57 &   0.13 &   0.35 \\
+NGC499   &  66 &  63.67 &   0.71 &   0.64 &   0.41 &  28.76 &  17.14 &   0.72 &   0.02 &   0.30 \\
+AWM7     &  67 &  74.64 &   1.56 &   1.20 &   4.34 &   7.70 & 123.57 &   0.67 &   0.12 &   0.56 \\
+PERSEUS  &  68 &  79.48 &   1.90 &   1.37 &   7.71 &  45.94 &  45.71 &   0.54 &   0.10 &   0.64 \\
+S405     &  69 & 274.88 &   1.62 &   0.34 &   4.82 &   2.13 & 327.86 &   0.66 &   0.08 &   0.16 \\
+3C129    &  70 &  97.15 &   1.81 &   1.07 &   6.64 &   2.61 & 227.14 &   0.60 &   0.21 &   0.49 \\
+A0539    &  71 & 126.08 &   1.34 &   0.61 &   2.67 &   5.11 & 105.71 &   0.56 &   0.09 &   0.28 \\
+S540     &  72 & 157.55 &   1.23 &   0.45 &   2.09 &   7.70 &  92.86 &   0.64 &   0.04 &   0.21 \\
+A0548w   &  73 & 187.52 &   0.88 &   0.27 &   0.76 &   2.30 & 141.43 &   0.67 &   0.05 &   0.12 \\
+A0548e   &  74 & 181.14 &   1.20 &   0.38 &   1.98 &   4.44 &  84.29 &   0.48 &   0.08 &   0.18 \\
+A3395n   &  75 & 221.45 &   2.14 &   0.55 &  11.05 &   1.61 & 480.00 &   0.98 &   0.09 &   0.26 \\
+UGC03957 &  76 & 149.43 &   1.36 &   0.52 &   2.87 &   8.93 & 101.43 &   0.74 &   0.04 &   0.24 \\
+PKS0745  &  77 & 474.79 &   2.08 &   0.25 &  10.09 &  72.11 &  50.71 &   0.61 &   0.01 &   0.12 \\
+A0644    &  78 & 317.77 &   2.31 &   0.42 &  14.16 &  11.21 & 145.00 &   0.70 &   0.03 &   0.19 \\
+ANTLIA   &  79 &  50.13 &   0.90 &   1.03 &   0.83 &   1.64 & 245.71 &   0.75 &   0.26 &   0.48 \\
+A1413    &  80 & 677.27 &   2.18 &   0.18 &  11.64 &  14.19 & 127.86 &   0.66 &   0.02 &   0.09 \\
+M49      &  81 &  18.91 &   0.74 &   2.25 &   0.46 &  34.18 &   7.86 &   0.59 &   0.04 &   1.04 \\
+A3528n   &  82 & 240.86 &   1.43 &   0.34 &   3.32 &   5.61 & 127.14 &   0.62 &   0.04 &   0.16 \\
+A3528s   &  83 & 245.97 &   1.19 &   0.28 &   1.93 &   7.70 &  72.14 &   0.46 &   0.06 &   0.13 \\
+A3530    &  84 & 242.72 &   1.69 &   0.40 &   5.46 &   2.07 & 300.71 &   0.77 &   0.07 &   0.18 \\
+A3532    &  85 & 240.40 &   1.70 &   0.41 &   5.56 &   3.63 & 201.43 &   0.65 &   0.06 &   0.19 \\
+A1689    &  86 & 897.29 &   2.50 &   0.16 &  17.63 &  23.21 & 116.43 &   0.69 &   0.01 &   0.07 \\
+A3560    &  87 & 220.07 &   1.31 &   0.34 &   2.56 &   2.80 & 182.86 &   0.57 &   0.08 &   0.16 \\
+A1775    &  88 & 343.00 &   1.55 &   0.26 &   4.22 &   5.19 & 185.71 &   0.67 &   0.04 &   0.12 \\
+A1800    &  89 & 338.70 &   1.71 &   0.29 &   5.69 &   3.32 & 280.00 &   0.77 &   0.05 &   0.13 \\
+A1914    &  90 & 827.98 &   2.77 &   0.19 &  24.28 &  14.68 & 165.00 &   0.75 &   0.01 &   0.09 \\
+NGC5813  &  91 &  27.55 &   0.62 &   1.29 &   0.27 &  22.37 &  17.86 &   0.77 &   0.03 &   0.60 \\
+NGC5846  &  92 &  26.25 &   0.69 &   1.51 &   0.38 &  66.64 &   5.00 &   0.60 &   0.02 &   0.70 \\
+A2151w   &  93 & 162.53 &   1.15 &   0.41 &   1.73 &  14.20 &  48.57 &   0.56 &   0.03 &   0.19 \\
+NORMA    &  94 &  70.69 &   1.79 &   1.45 &   6.57 &   2.88 & 213.57 &   0.56 &   0.33 &   0.67 \\
+TRIANGUL &  95 & 226.98 &   2.39 &   0.60 &  15.39 &   6.47 & 199.29 &   0.61 &   0.09 &   0.28 \\
+OPHIUCHU &  96 & 122.51 &   2.74 &   1.28 &  23.16 &   9.08 & 199.29 &   0.75 &   0.10 &   0.59 \\
+ZwCl1742 &  97 & 343.00 &   1.91 &   0.32 &   7.89 &   7.76 & 165.71 &   0.72 &   0.03 &   0.15 \\
+A2319    &  98 & 252.01 &   2.26 &   0.51 &  12.91 &   6.66 & 203.57 &   0.59 &   0.09 &   0.24 \\
+A3695    &  99 & 407.09 &   1.81 &   0.25 &   6.66 &   3.28 & 285.00 &   0.64 &   0.05 &   0.12 \\
+IIZw108  & 100 & 219.60 &   1.47 &   0.38 &   3.60 &   2.47 & 260.71 &   0.66 &   0.08 &   0.18 \\
+A3822    & 101 & 344.43 &   1.74 &   0.29 &   5.90 &   3.48 & 250.71 &   0.64 &   0.06 &   0.13 \\
+A3827    & 102 & 451.10 &   2.59 &   0.33 &  19.60 &   3.95 & 423.57 &   0.99 &   0.04 &   0.15 \\
+A3888    & 103 & 720.64 &   2.83 &   0.22 &  25.53 &   7.16 & 286.43 &   0.93 &   0.02 &   0.10 \\
+A3921    & 104 & 429.52 &   2.06 &   0.28 &   9.86 &   5.23 & 234.29 &   0.76 &   0.03 &   0.13 \\
+HCG94    & 105 & 184.32 &   1.31 &   0.41 &   2.59 &   8.77 &  61.43 &   0.51 &   0.06 &   0.19 \\
+RXJ2344  & 106 & 356.88 &   1.92 &   0.31 &   8.05 &   5.89 & 215.00 &   0.81 &   0.03 &   0.14 \\
+\hline
+\hline
+\end{tabular}
+\begin{quote}
+  Notes: 
+  (1) The HIFLUGCS cluster ID, luminosity distance
+  ($D_\rmn{lum}$), virial radius ($\rvir$), and virial mass ($\mvir$),
+  are taken from \cite{2002ApJ...567..716R}.
+  (2) We parametrize the
+  gas density profile of each cluster with a single beta profile;
+  $\rho_\rmn{gas}=\rho_\rmn{gas}(0)(1+r^2/r_\rmn{c}^2)^{3\beta/2}$
+  where the core radius $r_\rmn{c}$ and the slop of the surface
+  brightness profile $\beta$ are taken from
+  \cite{2002ApJ...567..716R}. The central gas density
+  $\rho_\rmn{gas}(0)$ is determined through he procedure outlined in
+  \cite{1999ApJ...517..627M}.
+   (3) Half light radius ($r_\rmn{hlr,CR}$) of the flux from CR-$\pi^0$.
+   (4) Half light radius ($r_\rmn{hlr,DM}$) of the flux from the BM-$\Kp$ 
+  continuum and LP-IC-CMB emission. The flux has been
+  boosted by substructures and in addition include the
+  Sommerfeld enhancement for the LP model. 
+ \label{tab:flux_tab_CLp}
+  \end{quote}
+\end{minipage}
+\end{table}
+
 \end{document}

### 2011-06-13 paper.tex
updated text and figures

@@
   distribution down to an Earth mass and using Fermi upper limits, we
-  rule out the leptophilic models in their present form in 14
-  clusters, and limit the boost from Sommerfeld enhancement in Fornax
-  to be less than 2 which corresponds to a value in the Milky Way of
-  less than 5. Alternatively, if the Sommerfeld enhancement factor is
-  realized in Nature, this would imply a limiting substructure mass in
-  Fornax of $\mlim > 10^2\,\msun$ which would be a challenge for
-  structure formation. In addition, we find that Fermi three-year data
-  will be able to constrain the smallest mass of substructures for
-  supersymmetric benchmark models or alternatively constrain their
-  cross sections for a given substructure boost. The Fermi upper
-  limits are closing in on our predictions for the CR flux using an
-  analytic model based on cosmological hydrodynamical cluster
-  simulations. Thus we will soon start to constrain the underlying CR
-  physics such as shock acceleration efficiencies or CR transport
-  properties.
+  rule out the leptophilic models in their present form in 26
+  clusters, and limit the boost from Sommerfeld enhancement in the
+  most constraining cluster M49 to be less than 14. This corresponds
+  to a Sommerfeld enhancement in the Milky Way of less than
+  8. Alternatively, if the Sommerfeld enhancement factor is realized
+  in Nature, this would imply a limiting substructure mass in M49 of
+  $\mlim > 10\,\msun$ which would be a challenge for structure
+  formation. \C{Furthermore, we find it challenging for Fermi to
+    constrain our selection of DM benchmark models using clusters
+    without improved modelling of extended sources in addition to a
+    stacked likelihood analysis.} The Fermi upper limits are, however,
+  closing in on our predictions for the CR flux using an analytic
+  model based on cosmological hydrodynamical cluster simulations. Thus
+  we will soon start to constrain the underlying CR physics such as
+  shock acceleration efficiencies or CR transport properties.
 \end{abstract}
@@
 Segue-1, Ursa Minor, Draco, Sagittarius, Sculptor, Carina or Willman-1
-\cite{2009JCAP...01..016B,2010ApJ...720.1174A,2010JCAP...01..031S,2010JCAP...01..031S}. The
+\cite{2009JCAP...01..016B,2010ApJ...720.1174A,2010JCAP...01..031S,2010JCAP...01..031S,2011arXiv1103.0477T,2011APh....34..608H}. The
 problem here is that the nature of many of these small, dark
@@
 
-3. Galaxy clusters. This possibility has been less studied, however we
-noted in a previous Letter \cite{2009PhRvL.103r1302P} that there are
-certain advantages that work in favour of this possible target for
-gamma-ray detection of DM annihilation.  Galaxy clusters constitute
-the most massive objects in our Universe that are forming today. This
-causes their DM subhalo mass function to be less affected by tidal
-stripping compared to galaxy sized halos that formed long ago.  The
-annihilation luminosities of the DM halo component for e.g. the Virgo
-cluster and the Draco dwarf scales in a way (see
-\cite{2009PhRvL.103r1302P}) that the ratio of gamma-ray luminosities
-from the smooth components is around 4, in favour of Virgo. In
-addition, there may be a further enhancement due to substructure,
-which to a large extent should be unaffected by tidal disruption, at
-least in the outer regions.  According to a recent estimate
-\cite{2011MNRAS.410.2309G}, more massive haloes tend to have a larger
-mass fraction in subhalos.  For example, cluster size haloes typically
-have 7.5 per cent of the mass within $r_{200}$ in substructures of
-fractional mass larger than $10^{-5}$, which is 25 per cent higher
-than for galactic haloes.\footnote{All halo masses and length scales in
-  this paper are scaled to the currently favored value of Hubble's
-  constant, $H_0 = 70\, \rmn{km~s}^{-1}\,\rmn{Mpc}^{-1}$. We define
-  the virial mass $\mvir$ and virial radius $\rvir$ as the mass and
-  radius of a sphere enclosing a mean density that is 200 times the
-  critical density of the Universe $\rho_{\rmn{cr}}$.}
+3. Galaxy clusters. This possibility has been less studied, however
+\C{currently there is an ongoing observational campaign to detect
+  gamma-ray emission from galaxy clusters
+  \cite{2010ApJ...710..634A,2010JCAP...05..025A,2009A&A...495...27A,2009IJMPD..18.1627D,2009A&A...502..437A,2009arXiv0907.5000G,2009ApJ...704..240K,2009ApJ...706L.275A,2010ApJ...717L..71A}.
+In fact, we noted} in a previous Letter
+\cite{2009PhRvL.103r1302P} that there are certain advantages that work
+in favour of this possible target for gamma-ray detection of DM
+annihilation. Galaxy clusters constitute the most massive objects in
+our Universe that are forming today. This causes their DM subhalo mass
+function to be less affected by tidal stripping compared to galaxy
+sized halos that formed long ago.  The annihilation luminosities of
+the DM halo component for e.g. the Virgo cluster and the Draco dwarf
+scales in a way (see \cite{2009PhRvL.103r1302P}) that the ratio of
+gamma-ray luminosities from the smooth components is around 4, in
+favour of Virgo. In addition, there may be a further enhancement due
+to substructure, which to a large extent should be unaffected by tidal
+disruption, at least in the outer regions.  According to a recent
+estimate \cite{2011MNRAS.410.2309G}, more massive haloes tend to have
+a larger mass fraction in subhalos.  For example, cluster size haloes
+typically have 7.5 per cent of the mass within $r_{200}$ in
+substructures of fractional mass larger than $10^{-5}$, which is 25
+per cent higher than for galactic haloes.\footnote{All halo masses and
+  length scales in this paper are scaled to the currently favored
+  value of Hubble's constant, $H_0 = 70\,
+  \rmn{km~s}^{-1}\,\rmn{Mpc}^{-1}$. We define the virial mass $\mvir$
+  and virial radius $\rvir$ as the mass and radius of a sphere
+  enclosing a mean density that is 200 times the critical density of
+  the Universe $\rho_{\rmn{cr}}$.}
 
@@
 related to DM in clusters, see, e.g.,
-\cite{2006A&A...455...21C,2009PhRvD..80b3005J}.
+\cite{2006A&A...455...21C,2009PhRvD..80b3005J,2011arXiv1104.3530S,2011ApJ...726L...6C,2010JCAP...05..025A}.
 
@@
 \multicolumn{3}{c}{$F_{\gamma}(>100\,\rmn{GeV})$ $[\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}]$:} & 
-$\mvir$ & $\B_\rmn{sfe} $$^{(1)}$ &  $\B_\rmn{sub} $$^{(2)}$ \\
-         & DM-LP $^{(3)}$ & DM-BM-$\Kp$ $^{(4)}$ & CR-$\pi^0$ $^{(5)}$ 
-         & & DM-LP $^{(3)}$ & DM-BM-$\Kp$ $^{(4)}$ & CR-$\pi^0$ $^{(5)}$ & $[10^{14}\,\msun]$ &&  \\
- \hline
- Coma                 & $1.3\times10^{-8}$  & $8.3\times10^{-11}$ & $4.0\times10^{-9}$  
- & \,\,\,\,\,         & $1.4\times10^{-12}$ & $2.3\times10^{-13}$ & $1.5\times10^{-12}$ 
- & $13.8$ & $60$  & $1040$ \\
- Perseus \,\,\,\,\,\, & $1.4\times10^{-8}$  & $7.1\times10^{-11}$ & $1.4\times10^{-8}$  
- & \,\,\,\,\,         & $1.4\times10^{-12}$ & $2.0\times10^{-13}$ & $5.2\times10^{-12}$ 
- & $7.71$ & $70$  & $910$ \\
- Virgo                & $1.2\times10^{-7}$  & $4.0\times10^{-10}$ & $8.7\times10^{-9}$  
- & \,\,\,\,\,         & $1.3\times10^{-11}$ & $1.1\times10^{-12}$ & $3.2\times10^{-12}$ 
- & $2.1$  & $105$  & $680$  \\
- Fornax               & $4.8\times10^{-8}$  & $1.3\times10^{-10}$ & $2.2\times10^{-10}$ 
- & \,\,\,\,\,         & $5.6\times10^{-12}$ & $3.6\times10^{-13}$ & $8.3\times10^{-14}$ 
- & $1.0$  & $130$  & $580$  \\
+$\mvir$ $^{(1)}$ & $\B_\rmn{sfe} $$^{(2)}$ &  $\B_\rmn{sub} $$^{(3)}$ \\
+         & DM-LP $^{(4)}$ & DM-BM-$\Kp$ $^{(5)}$ & CR-$\pi^0$ $^{(6)}$ 
+         & & DM-LP $^{(4)}$ & DM-BM-$\Kp$ $^{(5)}$ & CR-$\pi^0$ $^{(6)}$ & $[10^{14}\,\msun]$ &&  \\
+ \hline
+ Coma                 & $5.1\times10^{-8}$  & $8.2\times10^{-11}$ & $4.0\times10^{-9}$  
+ & \,\,\,\,\,         & $7.4\times10^{-12}$ & $3.0\times10^{-13}$ & $1.5\times10^{-12}$ 
+ & $13.8$ & $530/60$  & $1290$ \\
+ Perseus \,\,\,\,\,\, & $4.4\times10^{-8}$  & $7.1\times10^{-11}$ & $1.4\times10^{-8}$  
+ & \,\,\,\,\,         & $6.4\times10^{-12}$ & $2.6\times10^{-13}$ & $5.2\times10^{-12}$ 
+ & $7.71$ & $530/70$  & $1210$ \\
+ Virgo                & $9.2\times10^{-7}$  & $1.4\times10^{-9}$ & $1.1\times10^{-8}$  
+ & \,\,\,\,\,         & $1.3\times10^{-10}$ & $5.4\times10^{-12}$ & $3.9\times10^{-12}$ 
+ & $6.9$  & $530/105$  & $1110$  \\
+ Fornax               & $7.9\times10^{-8}$  & $1.3\times10^{-10}$ & $2.2\times10^{-10}$ 
+ & \,\,\,\,\,         & $1.1\times10^{-11}$ & $4.6\times10^{-13}$ & $8.3\times10^{-14}$ 
+ & $1.0$  & $530/130$  & $730$  \\
 \hline
@@
   Notes: \\
-  (1) The boost due to Sommerfeld enhancement. See Section II A 1.\\
-  (2) The boost from substructures have been integrated out to $\rvir$.\\
-  (3) The total gamma-ray flux from leptophilic (LP) DM where both the
+  (1) \C{The mass of Fornax, Coma, and Perseus are taken from \cite{2002ApJ...567..716R}, 
+  while the mass of Virgo is derived from \cite{1984ApJ...281...31T}.}\\
+  (2) \C{The boost due to Sommerfeld enhancement. The first value shows the saturated 
+  Sommerfeld boost realized when substructures are present, the latter is the Sommerfeld 
+  boost without substructures. See Section II A 1.}\\
+  (3) \C{The boost from substructures along the line of sight has been integrated 
+    out to an angular size corresponding to $\rvir$.}\\
+  (4) The total gamma-ray flux from leptophilic (LP) DM where both the
   boost from substructures and Sommerfeld enhancement are
@@
   Fermi (see the following sections for detail).\\
-  (4) The total gamma-ray flux from the supersymmetric $\Kp$ benchmark (BM) 
+  (5) The total gamma-ray flux from the supersymmetric $\Kp$ benchmark (BM) 
   model where the boost from substructures is included. See Sections II A 2 and II B 3.\\
-  (5) Gamma-ray flux induced by CR protons. See Section V C. 
+  (6) Gamma-ray flux induced by CR protons. See Section V C. 
  \label{tab:flux_tab}
@@
 protons. In Section 2 we discuss the theory of DM and gamma-rays. In
-particular, we focus on the leptophilic (LP) and supersymmetric DM
-models used in this work, and outline the framework for estimating the
-gamma-ray emission from various radiative processes. In Section 3 we
-calculate the gamma-ray fluxes and spectral distributions from four
-clusters and compare it to upper limits set by Fermi-LAT. For the same
-clusters we derive the gamma-ray surface brightness profiles in
-Section 4. To extend the analysis to more clusters and find promising
-targets we estimate the fluxes from DM and CRs of all clusters in the
-extended HIFLUGCS sample in Section 5. In Section 6 we conclude and
-discuss our results.
+particular, we focus on the leptophilic (LP) and supersymmetric
+benchmark (BM) DM models in this work, and outline the framework
+for estimating the gamma-ray emission from various radiative
+processes. In Section 3 we calculate the gamma-ray fluxes and spectral
+distributions from four clusters and compare it to upper limits set by
+Fermi-LAT. For the same clusters we derive the gamma-ray surface
+brightness profiles in Section 4. To extend the analysis to more
+clusters and find promising targets we estimate the fluxes from DM and
+CRs of all clusters in the extended HIFLUGCS sample in Section 5. In
+Section 6 we conclude and discuss our results.
 
@@
 the mass of the DM particle (for the currently most sensitive search,
-see \cite{Aprile:2010um,Aprile:2011ts}). A characteristic of this method is that it
-basically only depends on the local DM density (which is rather well
-determined to be around $0.4$ GeV/cm$^3$) and the basic cross section
-for DM - nucleus scattering. A disadvantage is that it does not benefit
-from the two enhancement mechanisms mentioned above, boost from
-substructure and/or the Sommerfeld effect. Also, it cannot be excluded
-- although it seems at present improbable - that the local halo
-structure is such that the solar system happens to be in an underdense
-region.
+see \cite{Aprile:2010um,Aprile:2011hi}). A characteristic of this
+method is that it basically only depends on the local DM density
+(which is rather well determined to be around $0.4$ GeV/cm$^3$) and
+the basic cross section for DM - nucleus scattering. A disadvantage is
+that it does not benefit from the two enhancement mechanisms mentioned
+above, boost from substructure and/or the Sommerfeld effect. Also, it
+cannot be excluded - although it seems at present improbable - that
+the local halo structure is such that the solar system happens to be
+in an underdense region.
 
@@
 \cite{1995PhRvD..52.3265A,Hooper:2008kg,Ahlers:2009ae}). In that case,
-DM would more likely be explained by the standard scenario of a WIMP,
+DM would more likely be explained by the conventional scenario of a WIMP,
 for example the thoroughly studied lightest supersymmetric neutralino
@@
 $\sigv$ the SFE will be smaller than the one expected in a single
-galaxy such as the MW, roughly by a factor $v_{\rm MW}/\sigv$.
-
-As LP models, apart from being slightly contrived from the
-particle physics point of view, are also rather limited by several
-sets of astrophysical data. We take advantage of the recent reanalysis
-\cite{Finkbeiner:2010sm} to define a benchmark LP model that
-is still viable.  It is found that the bounds from WMAP5 approximately
-imply a Sommerfeld boost factor $S$ which has to satisfy $S(v\to
-0)\lesssim 200/f\ (m_Y/1$ GeV$)$, where $f$ is the fraction of energy
-from DM annihilation that ionizes the intergalactic medium,
-$f\sim 0.7$ for annihilation to electrons and a factor of a few smaller
-for all other standard model final states.
+galaxy such as the MW, roughly by a factor $v_{\rm MW}/\sigv$. \C{Note
+  that the $1/v$-scaling is valid only for $(v/c) \gtrsim
+  (m_\phi/m_\chi)$; at smaller velocities and outside resonances, the
+  $1/v$-enhancement saturates at $m_\phi/m_\chi$
+  \cite{2008PhRvL.101z1301K}.}
+
+As LP models, apart from being slightly contrived from the particle
+physics point of view, are also rather limited by several sets of
+astrophysical data. We take advantage of the recent reanalysis
+\cite{Finkbeiner:2010sm} to define a benchmark LP model that is still
+viable.  It is found that the bounds from WMAP5 approximately imply a
+Sommerfeld boost factor $S$ which has to satisfy $S(v\to
+150\,\rmn{km}/\rmn{s})\lesssim 250/f\ (m_\phi/1$ GeV$)$, where $f$ is
+the fraction of energy from DM annihilation that ionizes the
+intergalactic medium, $f\sim 0.7$ for annihilation to electrons and a
+factor of a few smaller for all other standard model final states.
 
@@
 We adopt our benchmark LP model from \cite{Finkbeiner:2010sm} where we
-use a DM mass $m_\chi=1.6$~TeV and a branching ratio of ($1/2:1/2$)
-into ($\mu^+\mu^-:\e^+e^-$).\footnote{This is an approximation to the
-  model found in \cite{Finkbeiner:2010sm} that has a branching ratio
-  of ($1/4:1/4:1/2$) into ($\mu^+\mu^-:\e^+\e^-:\pi^+\pi^-$).}  The
-SFE $S=\B_\sfe(\sigv=200\,\rmn{km}/\rmn{s})\approx 300$ for a MW halo
-in our LP model, which we appropriately scale down for cluster halos,
-using
+use a DM mass $m_\chi=1.6$~TeV and a branching ratio of
+($1/4:1/4:1/2$) into
+($\mu^+\mu^-:\e^+\e^-:\pi^+\pi^-$). \del{\footnote{This is an
+    approximation to the model found in \cite{Finkbeiner:2010sm} that
+    has a branching ratio of ($1/4:1/4:1/2$) into
+    ($\mu^+\mu^-:\e^+\e^-:\pi^+\pi^-$).}} \C{Furthermore, since most
+  of gamma-ray flux is expected from come from dense subhalos at which
+  the velocity dispersion is close to the velocity limit $v_\rmn{sat}$
+  where the SFE saturates, we use $S=\B_\sfe(\sigv=v_\rmn{sat})\approx
+  530$ \footnote{Note that, $S$ is strictly speaking the Sommerfeld
+    enhanced annihilation cross-section, but here we have in addition
+    included the order unity constraint that make sure that the relic
+    density is not over-depleted at freeze-out.} for the cluster
+  halos. However, for those cluster halos without a boost from
+  substructures, we adopt a velocity dependent SFE that is normalized
+  to fit the electron and positron excess at Earth observed by the
+  PAMELA and Fermi satellites,}
 \begin{equation}
-\B_\sfe(\sigv) = 0.2\, \frac{c}{\sigv} = 
-62.6 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-1/3}\,,
+\B_\sfe(\sigv) = 0.266\, \frac{c}{v_\rmn{sat}}\, \frac{v_\rmn{MW}}{\sigv} = 
+121 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-1/3}\,.
 \label{eq:B_sfe}
 \end{equation}
-where the velocity dispersion $\sigv$ for clusters is derived in
-\cite{2005RvMP...77..207V}. Clusters have a larger velocity dispersion
-and an accordingly smaller Sommerfeld boost factor. Note that this
-$1/v$-scaling is valid only for $(v/c) \gtrsim (m_\phi/m_\chi)$; at
-smaller velocities and outside resonances, the $1/v$-enhancement
-saturates at $m_\phi/m_\chi$ \cite{2008PhRvL.101z1301K}.
+Here the velocity dispersion for the MW $v_\rmn{MW} \approx
+220\,$~km/s and the velocity dispersion $\sigv$ for clusters is
+derived in \cite{2005RvMP...77..207V}. Clusters have a larger velocity
+dispersion and an accordingly smaller Sommerfeld boost factor.
 
@@
  \caption{\it Source functions for different dark matter (DM)
-   models. Crosses show the simulated data from {\sc DarkSUSY} and the
+   models. Crosses show the simulated data from {\sc DarkSUSY}
+   \cite{ds}, \C{$\times$ show the data generated by
+     \protect\cite{2011JCAP...03..019C,2011JCAP...03..051C}} and the
    solid lines show the fit to the data. LEFT PANEL: normalized
@@
    models; $\Ip$ BM model (red), $\Jp$ BM model (orange), $\Kp$ BM
-   model (green), and $\Js$ BM model (blue), leptophilic (LP) DM
-   annihilating into electrons and positrons (purple), and LP DM
-   annihilating into muons (black) without considering Sommerfeld
-   boosts. We use Eq.~(\ref{eq:bm_elec}) and Eq.~(\ref{eq:lp_elec}) to
+   model (green), and $\Js$ BM model (blue), \C{leptophilic (LP) DM
+   annihilating indirectly into electrons and positrons (purple) and
+   into muons (black) without considering Sommerfeld boosts.} We use
+   Eq.~(\ref{eq:bm_elec}) and Eqs.~(\ref{eq:lp_mu}-\ref{eq:lp_ep}) to
    fit the spectra of electrons and positrons from BM and LP models,
@@
   sum}(\eg,r)$, where we include contributions from five main
-processes; leptophilic DM annihilating either indirectly through
-$\mu^+/\mu^-$ to $\rmn{e}^+/\rmn{e}^-$ or directly to
-$\rmn{e}^+/\rmn{e}^-$ pairs that IC upscatter background photons
+processes; leptophilic DM annihilating \C{through
+  $\chi\,\chi\to\phi\,\phi\to\{4\mu\to4e,\,4e,\,4\pi\to4e\}$ where the
+  $\rmn{e}^+/\rmn{e}^-$ pairs} IC upscatter background photons
 (LP-IC), leptophilic DM emitting final state radiation (LP-FSR),
@@
 Navarro-Frenk-White (NFW) profile, but provides a better fit to recent
-simulated high resolution DM halos \cite{2010MNRAS.402...21N}. It
-should also be noted that recent observations of the Abell 383 galaxy
-cluster find a density profile with a shallower inner slope of
-$\beta=0.6$ compared to an NFW profile, and $\beta\gtrsim 1$ can be
-ruled out with $>95$\% confidence \cite{2011ApJ...728L..39N}. These
-observations are based on lensing and X-ray measurements as well as
-the stellar velocity dispersion of the central galaxy. In
-Eq.~(\ref{eq:dens_ein}) we denote the density where the profile has a
-slope of $-2$ by $\rho_{-2}$, and the radius by $r_{-2}=\rvir/c$. We
-use that the density $\rho_{-2}(c)=\rho_\s(c)/a(c)$ and determine
-$a(c)$ through $\mvir$:
+simulated high resolution DM halos
+\cite{2006AJ....132.2685M,2010MNRAS.402...21N}. It should also be
+noted that recent observations of the Abell 383 galaxy cluster find a
+density profile with a shallower inner slope of $\beta=0.6$ compared
+to an NFW profile, and $\beta\gtrsim 1$ can be ruled out with $>95$\%
+confidence \cite{2011ApJ...728L..39N}. These observations are based on
+lensing and X-ray measurements as well as the stellar velocity
+dispersion of the central galaxy. In Eq.~(\ref{eq:dens_ein}) we denote
+the density where the profile has a slope of $-2$ by $\rho_{-2}$, and
+the radius by $r_{-2}=\rvir/c$. We use that the density
+$\rho_{-2}(c)=\rho_\s(c)/a(c)$ and determine $a(c)$ through $\mvir$:
 \begin{equation}
@@
 Here $a=(4.16-4.30)$ for $c=(3-10)$ and since $a$ is a slowly
-increasing function with $c$, we fix it for simplicity to $a(c)\approx
-a \approx 4$.
+increasing function with concentration $c$, we fix it for simplicity
+to $a(c)\approx a \approx 4$.
 
@@
   L_\sub(<x) &=& a_0\,C(\mvir)\,L_{200\sm}(\mvir)\,x^{a_1
-    \displaystyle{x}^{a_2}}\,,\label{eq:LSub}\\
+    \displaystyle{x}^{a_2}}\,,\label{eq:Lsub}\\
    a_0 &=& 0.76\,,\quad a_1 = 0.95\,,\quad  a_2 = -0.27\,, \quad 
@@
 
-\C{To further motivate the scaling of the substructure boost with
-  limiting substructure mass in Eqs.~(\ref{eq:LSub}-\ref{eq:CSub}), we
-  show how it relates to the substructure mass function, $\dd
-  N_\sub/\dd M \propto M^{-1.9}$ \cite{2008MNRAS.391.1685S}. Adopting
-  a mass dependence of the concentration parameter of $c\,(M)\propto
-  M$, as it is measured for dwarf halos \cite{}, the substructure
-  luminosity scales as $L_\sub\propto M^A$, where $A=0.674$. Hence we
-  find that the total luminosity of substructures scales as
+\C{To motivate the scaling of the substructure luminosity boost with
+  limiting substructure mass in Eqs.~(\ref{eq:Lsub}-\ref{eq:Csub}),
+  we show how it derives from the substructure mass function, $\dd
+  N_\sub/\dd M \propto M^{-1.9}$
+  \cite{2008MNRAS.391.1685S,2008Natur.456...73S} and substructure
+  luminosity scaling, $L_\sub \propto M^A$. The total luminosity of
+  substructures scales as
 \begin{eqnarray}
@@
 \int \dd M \frac{\dd N_\sub}{\dd M} \nonumber\\
- &\propto& M^{A-0.9} \propto M^{-0.226}\,,
+ &\propto& M^{A-0.9} \propto M^{-0.226}\,,\quad
+\rmn{for}\quad A=0.674\,. \nonumber\\
+&&
 \end{eqnarray}
-which is the result found by \cite{2008Natur.456...73S}.}
+Tidal truncation is responsible in shaping the substructure luminosity
+scaling parameter $A$. Here we only sketch out qualitative arguments
+and leave the details to future work. First, tidal effects truncate
+the subhalo profile primarily in the outer regions. As a result of
+this, the subhalo acquires a steeper logarithmic slope than the
+canonical 3 from the NFW-profile. Second, tidal stripping imposes a
+mass-dependency and should be stronger for smaller substructure. While
+the stripping efficiency (for an effective cross section $\sigma$)
+only depends on the density since the mean free path scales as
+$x_\rmn{mfp} \propto 1/(n_\rmn{dm} \sigma)$, there is less mass at any
+given density for smaller substructures. Hence, modest density
+inhomogeneities in the host halo seen by the orbiting substructures
+cause a stronger mass loss of these smaller satellites. Third, the
+tidal truncation radius should be a function of host halo radius due
+to the increasing smooth density profile for smaller radii.  If we
+pick an effective host halo radius which dominates the luminosity
+contribution of the substructures and were to fit the tidally
+truncated subhalo density profile with an NFW-profile, the resulting
+$\rs$ would be biased toward lower values implying a higher
+concentration compared to an isolated halo. In order to reproduce our
+value of $A$, we would need a concentration mass relation of $c\propto
+M^{-0.14}$.  As expected, this is steeper than the concentration-mass
+relation found for isolated halos on dwarf galaxy scales, $c \propto
+M^{-0.06}$ \cite{2011arXiv1101.2020I}, as well as galaxy and cluster
+scales, $c \propto M^{-0.098}$ \cite{2008MNRAS.391.1940M}.}
 
@@
 photons is smaller which causes the substructure boost over the smooth
-emission to be reduced by roughly two orders of magnitudes.
+emission to be reduced by roughly two orders of magnitudes. \C{It
+  should also be noted that the substructure boosted fluxes from
+  clusters are much more extended than for dwarf galaxies, hence more
+  difficult to detect with Cherenkov telescopes. In fact, it was shown
+  in Sanchez-Conde et al. \cite{2011arXiv1104.3530S} that inside
+  $0.1$~deg, where the sensitivity of Cherenkov telescopes is
+  maximized, the expected DM flux including substructures from the
+  brightest dwarf galaxy is about an order magnitude higher than the
+  brightest cluster. However, that work assumed a substructure boost
+  of about 50 in the most massive cluster halos which is more than an
+  order magnitude smaller than what we use in this work, hence in
+  projection we expect this difference to be a factor few smaller.}
 
@@
 \begin{equation}
-q_\e(\ee,r)=\sum_f\frac{\dd N_{\e,f}}{\dd \ee}(\ee) B_f \Gamma_f(r) \,,
+q_\e(\ee,r)=\sum_f\frac{\dd N_\e^f}{\dd \ee}(\ee) B_f \Gamma_f(r) \,,
 \end{equation}
@@
 annihilation final states $f$, each with a branching ratio $B_f$ and a
-differential spectrum $\dd N_\e^f/\dd \ee$ that represents the
-number of electrons plus positrons resulting from an annihilation
-event. For neutralinos annihilating directly into electrons and
-positrons we model the spectral distribution with $\dd
-  N_\e^f/\dd \ee= 2\delta(\ee-m_\chi c^2)$. We use {\sc DarkSUSY} to
-compute both the spectra when neutralinos annihilate directly into a
-$\mu^+$ and $\mu^-$ in the LP model as well as in the four BM models
-where a fraction of the annihilating neutralinos is converted into
-electrons and positrons (see Sect.~\ref{sect:PF} and
-Fig.~\ref{fig:q_DM} for further details).
+differential spectrum $\dd N_\e^f/\dd \ee$ that represents the number
+of electrons plus positrons resulting from an annihilation
+event. \del{For neutralinos annihilating directly into electrons and
+  positrons we model the spectral distribution with $\dd N_\e^f/\dd
+  \ee= 2\delta(\ee-m_\chi c^2)$.} \C{We use the data from
+  \cite{2011JCAP...03..019C,2011JCAP...03..051C} to compute the
+spectra when neutralinos annihilate indirectly into $e^+/e^-$ pairs as
+well as $\mu^+/\mu^-$ pairs in the LP model. We use \ds to compute the
+$e^+/e^-$ spectra from our four BM models where only a fraction of the
+annihilating neutralinos is converted into electrons and positrons
+(see Sect.~\ref{sect:PF} and Fig.~\ref{fig:q_DM} for further details).}
 %(see \cite{2009JCAP...01..016B} and references therein,
@@
 
+\C{We compare the calculated fluxes to gamma-ray upper limits set by
+  Fermi-LAT after 18 months of observations
+  \cite{2010ApJ...717L..71A}. In particular, to achieve a more
+  reliable comparison we adopt the maximal spatially extended limits
+  (if nothing else is stated) since the gamma-ray flux from our
+  brightest clusters all have an angular extent above 1 degree on the
+  sky when the boost from substructures is included. In fact, current
+  Fermi flux upper limits are not derived for the kind of extended
+  emission that we get with our treatment of substructures, hence the
+  Fermi limits may not be adequate for some of these clusters. This and
+  other recent work highlights that the improved substructure models
+  imply that Fermi limits will have to be re-calculated to accommodate
+  for the large source extensions. Note, however, that for most
+  clusters the assumption of a point source is well justified.}
+
+ \C{Also note that the flux upper limits that we compare to are in
+   reality a function of spectral indices $\alpha$. However, in the
+   relevant energy range $0.1-100$~GeV these spectral indices are
+   approximately $1.5 < \alpha < 3.0$, where the change in photon flux
+   upper limits is less than 50\%, with the Fermi-LAT being more
+   sensitive to the hard spectrum \cite{2010ApJ...717L..71A}. For
+   simplicity of the analysis in our paper we adopt the upper limits
+   calculated for a spectral index $\alpha=2$.  For consistency we
+   estimate the change in the differential upper limits for each
+   gamma-ray model and energy range using:
+\begin{eqnarray}
+\frac{\dd F_\gamma}{\dd \eg} &=& K\,\eg^{-\alpha}\,,\quad F_\gamma = 
+K\,\eg^{1-\alpha}\,,\nonumber\\
+<\eg \,F_\gamma> &=& K\,\frac{\sum \dd \eg^{2-\alpha}}{\sum \dd \eg}
+= K\,\frac{\sum \dd \eg^{2-\alpha}}{E_{\gamma,2}-E_{\gamma,1}}\,,\nonumber
+\end{eqnarray}
+where $E_{\gamma,1}$ and $E_{\gamma,2}$ are the upper and lower energy
+limits, respectively. In the 1-10~GeV energy range we find that the
+upper limits for $($LP,BM,CR$)$ change by a factor
+$(1.10,\,0.71,\,1.15)$ where we have used the spectral indices
+$(2.20,\,1.22,\,2.24)$, respectively. See Fig.~\ref{fig:clu_comp} for
+additional spectral indices.}
+
 In Fig.~\ref{fig:diff_BM} we show the differential flux from the
 Fornax cluster which is one of the best clusters for indirect DM
-searches due to its relative high DM annihilation fluxes and low CR induced
+searches due to its high DM annihilation fluxes and low CR induced
 fluxes. We show the emission of four different supersymmetric BM
@@
 emission to the differential gamma-ray upper limits set by Fermi-LAT
-after 18 months of observations \cite{2010ApJ...717L..71A}, we find
-that the upper limits are not violated. The predicted DM flux that is
-dominated by the continuum emission from $\Kp$ and $\Ip$ models (shown
-in the left panels) are close to the upper limits and can potentially
-be probed by the Fermi three-year data. Furthermore, the gamma-ray
-signal induced by CRs is expected to be about a factor 5--10 below the
-DM continuum flux from the $\Kp$ and $\Ip$ BM models at
-10~GeV. However, the IC emission from upscattered CMB and SD photons
-is at least a factor of a few lower for $\Kp$ and a factor 1000 lower
-for $\Ip,\Jp,\Js$, than the expected flux from CRs above 100~MeV,
-making it very hard to distinguish such a signal from the foreground
-due to the similar spectral index. For energies below 100~MeV we
-expect IC emission by primary shock accelerated electrons to be
-dominating \cite{2010MNRAS.409..449P} over the supersymmetric DM
-induced leptons. Hence in clusters, the IC emission from
-supersymmetric DM BM models be neglected compared to the CR pion and
-DM continuum emission.
+\del{after 18 months of observations \cite{2010ApJ...717L..71A}}, we
+find that the upper limits are not violated. The predicted DM flux
+that is dominated by the continuum emission from $\Kp$ and $\Ip$
+models (shown in the left panels) \C{are about an order of magnitude
+  below the upper limits, making it hard for Fermi to probe these kind
+  of DM models without a significant improvement in the analysis from
+  e.g. stacking of clusters and improved methods for analyzing
+  extended sources.}  Furthermore, the gamma-ray signal induced by CRs
+is expected to be about a factor 5--10 below the DM continuum flux
+from the $\Kp$ and $\Ip$ BM models at 10~GeV. However, the IC emission
+from upscattered CMB and SD photons is at least a factor of a few
+lower for $\Kp$ and a factor 1000 lower for $\Ip,\Jp,\Js$, than the
+expected flux from CRs above 100~MeV, making it very hard to
+distinguish such a signal from the foreground due to the similar
+spectral index. For energies below 100~MeV we expect IC emission by
+primary shock accelerated electrons to be dominating
+\cite{2010MNRAS.409..449P} over the supersymmetric DM induced
+leptons. Hence in clusters, the IC emission from supersymmetric DM BM
+models can be neglected compared to the CR pion and DM continuum emission.
 
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v12.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v12.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v12.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v12.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v13.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v13.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v13.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v13.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
 \caption{\it Comparing the differential flux from different models: we
@@
   a factor of 730 while the IC upscattered SD photons are only boosted
-  by 20. Upper limits from Fermi-LAT after 18 months \protect
-  \cite{2010ApJ...717L..71A} are also shown. We find bright prospects
-  for detecting the continuum emission, that is dominating the total
-  emission in the GeV energy range, in the models $\Ip$ and $\Kp$.}
+  by 20. Extended upper limits from Fermi-LAT after 18 months \protect
+  \cite{2010ApJ...717L..71A} are also shown. \C{We find it hard to
+    detect even the brightest BM models, $\Ip$ and $\Kp$, where the
+    continuum emission is dominating the total emission in the
+    GeV energy range.}}
  \label{fig:diff_BM}
@@
 positrons is more centrally peaked, and the relative importance of the
-IC upscattered SD increases by a factor $\sim 30$.  A larger fraction
-of electrons (in the core) will now also cool by Compton-upscattering
-SD photons which suppresses the IC-upscattered CMB light.  For
-comparison, we include the contribution of IC upscattered SD photons
-and to bracket the uncertainty in the SD model, with a smaller amount
-of dust. In this low-dust model, we have reduced the energy in dust by
-a factor 10. However, the resulting flux from the IC upscattered dust
-in this model only decreases with a factor that is slightly smaller
-than 10 since the IC cooling of the electrons and positrons also
-decreases.
+IC upscattered SD increases by a factor $\sim 30$ \footnote{\C{Note
+    that for the leptophilic DM model this increase is much smaller
+    since Sommerfeld enhancement is no longer dominated by the low
+    velocity DM particles living in the subhalos.}}.  A larger
+fraction of electrons (in the core) will now also cool by
+Compton-upscattering SD photons which suppresses the IC-upscattered
+CMB light.  For comparison, we include the contribution of IC
+upscattered SD photons and to bracket the uncertainty in the SD model,
+with a smaller amount of dust. In this low-dust model, we have reduced
+the energy in dust by a factor 10. However, the resulting flux from
+the IC upscattered dust in this model only decreases with a factor
+that is slightly smaller than 10 since the IC cooling of the electrons
+and positrons also decreases.
 
 Because of the large total boost factor for the LP model ($\sim5\times
-10^4$), we overproduce the upper gamma-ray limit in the $1-10$~GeV
-energy interval set by Fermi-LAT by about a factor 100. This strongly
+10^5$), we overproduce the upper gamma-ray limit in the $1-10$~GeV
+energy interval set by Fermi-LAT by about a factor 50. This strongly
 constrains the boost from both substructures and the
@@
 conclude that the wide angular extent of clusters on the sky in
-gamma-rays suggest that these sources are not ideal for IACTs since
-their sensitivity drops linearly with source extension.
+gamma-rays suggest that these sources are not ideal for Cherenkov
+telescopes since their sensitivity drops linearly with source
+extension.
 
@@
 \begin{minipage}{2.0\columnwidth}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v12.0.1deg.1.6T.SubMass.elmu.SF300.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv12.0.1deg.SubMass.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v13.0.1deg.1.6T.SubMass.elmu.SF700.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv13.0.1deg.SubMass.noMW.woGal.eps}
 \caption{\it Comparing the flux from different inverse Compton
@@
   dashed-dotted). The sum of the three components are shown with the
-  orange solid line.  The red solid lines show the CR induced gamma-ray
-  flux. The black arrow shows the differential upper limit from Fermi
-  \protect \cite{2010ApJ...717L..71A} indicating that the LP model
-  assumptions such as Sommerfeld and/or substructure boost are in
-  conflict with the upper limit. \del{We also show projected CTA point
-  source sensitivities ($5\sigma$, 50h).}  All fluxes are calculated
-  for the Fornax cluster within $\rvir$ using a point spread function
-  of $0.1\deg$. For this cluster, the boost from Sommerfeld is about
-  130 and the enhancement due to substructures from IC upscattered CMB
-  and SD photons is 730 and 20, respectively.}
+  orange solid line.  The red solid lines show the CR induced
+  gamma-ray flux. The black arrow shows the differential upper limit
+  from Fermi \protect \cite{2010ApJ...717L..71A} indicating that the
+  LP model assumptions such as Sommerfeld and/or substructure boost
+  are in conflict with the upper limit. \del{We also show projected
+    CTA point source sensitivities ($5\sigma$, 50h).}  All fluxes are
+  calculated for the Fornax cluster within $\rvir$ using a point
+  spread function of $0.1\deg$.\C{ For this cluster, the enhancement
+    due to substructures from IC upscattered CMB and SD photons is
+    730. The Sommerfeld boost is 530.}}
  \label{fig:IR_comp}
@@
 up to the DM rest mass energy in this model of about 1~TeV. Finally,
-we note that the flux the DM BM $\Kp$ model is larger than the predicted
-emission from the CRs in the $1-100$~GeV energy regime. Hence, the
-prospects for detecting the $\Kp$ BM model over the expected gamma-ray
-background induced by CRs looks promising. The projected CTA point
-source sensitivity ($5\sigma$, 50h) shows the potential of this
-experiment in also constraining leptophilic models as well as BM
-models with a very large neutralino mass $m_\chi c^2 \gtrsim
-1$~TeV. To this end, analysis techniques have to be developed that
-enable the detection of extended sources without too much degradation
-of sensitivity.
+we note that the flux the DM BM $\Kp$ model is larger than the
+predicted emission from the CRs in the $1-100$~GeV energy
+regime. \C{Hence, for an experiment with a high sensitivity even for
+  for extended sources, the prospects for detecting the $\Kp$ BM model
+  over the expected gamma-ray background induced by CRs looks
+  promising in clusters. Present day Cherenkov telescopes, however,
+  have a trigger region that is smaller than the size of clusters,
+  hence it has to be increased to several degrees to overcome problems
+  with background estimation. In addition, even though the projected
+  CTA point source sensitivity ($5\sigma$, 50h) shows the potential of
+  this experiment in constraining leptophilic models as well as BM
+  models with a very large neutralino mass $m_\chi c^2 \gtrsim 1$~TeV,
+  we find that analysis techniques have to be developed that enable
+  the detection of extended sources without too much degradation of
+  sensitivity.}
 
 \begin{figure}
- \includegraphics[width=0.99\columnwidth]{figures/flux.int.v12.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/flux.int.v13.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
  \caption{\it Comparing the energy integrated flux from different
@@
    using a point spread function of $0.1\deg$. The boost from
-   Sommerfeld and substructures is about 130 and 730, respectively.}
+   Sommerfeld and substructures is about 530 and 730, respectively.}
  \label{fig:flux_int}
@@
 massive merging Coma cluster. We find high DM induced gamma-ray fluxes
-from the Fornax and Virgo clusters, which highlight them as
-promising targets for indirect DM searches. Note, however, that we
-have used spatially unresolved upper limits, which is quite optimistic
-for the Virgo cluster which has an angular extended of 7 degrees. It
-is quite striking how constraining the upper limits for the Fornax
-cluster are compared to the other clusters, especially in the
-$1-10$~GeV energy regime. At these energies, Fermi-LAT has its peak
-sensitivity due to a combination of increasing effective area and
-decreasing source spectra as a function of energy. The upper limits
-for Virgo and Perseus are unfortunately background contaminated by AGN
-activity from M87 and NGC 1267, respectively, and do not gain much
-from the increased sensitivity. Note that the high CR-induced flux in
-Coma and Perseus is of the same magnitude as the DM flux from LP
+from the Fornax and Virgo clusters, which highlight them as promising
+targets for indirect DM searches. \C{Note, however, that the angular
+  extended of Virgo is 7 degrees, while the extended upper limit from
+  Fermi-LAT is calculated assuming a $\sigma=1.2$ degree extension. In
+  fact, the ratio of the virial radius to the assumed extension for
+  the upper limits $\rvir/\sigma$ for $($Fornax, Coma, Virgo$)$ are
+  $(2.79,\,1.3,\,5.8)$, respectively. Similarly, it is interesting to
+  compare the radius that contain 68\% of the flux to the assumed
+  extension, $r_\sigma/\sigma$, which is given by $(,\,,\,)$ for
+  $($Fornax,Coma,Virgo$)$, respectively. It is quite striking how
+  constraining the upper limits are for some of the clusters.}
+\del{Note, however, that we have used spatially unresolved upper
+  limits, which is quite optimistic for the Virgo cluster which has an
+  angular extended of 7 degrees.  It is quite striking how
+  constraining the upper limits are for the Fornax cluster are
+  compared to the other clusters, especially in the $1-10$~GeV energy
+  regime.} At these energies, Fermi-LAT has its peak sensitivity due
+to a combination of increasing effective area and decreasing source
+spectra as a function of energy. The upper limits for Virgo and
+Perseus are unfortunately background contaminated by AGN activity from
+M87 and NGC 1267, respectively, and do not gain much from the
+increased sensitivity. Note the high CR-induced flux in Coma and
+Perseus \C{is making it difficult for indirect DM searches in
+  those clusters if the boost factors are much lower than assumed in
+  this work.} \del{is of the same magnitude as the DM flux from LP
   models, making it difficult for indirect DM searches in those
-clusters. Conversely, the Fornax cluster is a great target for indirect
-DM studies because the relative low gamma-ray flux from CRs, absents
-of an active AGN, and high DM gamma-ray flux. The Fermi-LAT three-year
-data will be able to constrain the smallest mass of substructures
-using the DM BM models.
+  clusters.} Conversely, the Fornax cluster is a great target for
+indirect DM studies because the relative low gamma-ray flux from CRs,
+absents of an active AGN, and high DM gamma-ray flux. \del{The
+  Fermi-LAT three-year data will be able to constrain the smallest
+  mass of substructures using the DM BM models.}
 
@@
 \end{equation}
-and the total DM luminosity that includes boost factors for the LP and
-the BM models are given by
-\begin{eqnarray}
-\label{eq:LP_scaling}
-L_{\gamma,\rmn{LP}} &=& L_{\gamma,\rmn{smLP}} \B_\rmn{LP} \propto \frac{\mvir^{0.73}}{D_\rmn{lum}^2},\\
-\label{eq:BM_scaling}
-L_{\gamma,\rmn{BM}} &=& L_{\gamma,\rmn{smBM}} \B_\rmn{BM} \propto  \frac{\mvir^{1.06}}{D_\rmn{lum}^2},\\
-\B_\rmn{LP}&=&\B_\sfe \B_\sub \propto \mvir^{-1/3}\mvir^{0.23} \propto
- \mvir^{-0.1}\,,\\
-\B_\rmn{BM}&=&\B_\sub \propto \mvir^{0.23}\,.
-\end{eqnarray}
-Hence, increasing the cluster mass in the BM model by a factor two
+\del{and the total DM luminosity that includes boost factors for the LP and
+the BM models are given by}
+%\begin{eqnarray}
+%\label{eq:LP_scaling}
+%L_{\gamma,\rmn{LP}} &=& L_{\gamma,\rmn{smLP}} \B_\rmn{LP} \propto \frac{\mvir^{0.73}}{D_\rmn{lum}^2},\\
+%\label{eq:BM_scaling}
+%L_{\gamma,\rmn{BM}} &=& L_{\gamma,\rmn{smBM}} \B_\rmn{BM} \propto  \frac{\mvir^{1.06}}{D_\rmn{lum}^2},\\
+%\B_\rmn{LP}&=&\B_\sfe \B_\sub \propto \mvir^{-1/3}\mvir^{0.23} \propto
+% \mvir^{-0.1}\,,\\
+%\B_\rmn{BM}&=&\B_\sub \propto \mvir^{0.23}\,.
+%\end{eqnarray}
+\del{Hence, increasing the cluster mass in the BM model by a factor two
 more than doubles the luminosity, but increasing the luminosity
@@
 softer with mass, hence gives rise to a larger fraction of gamma-rays
-in low mass clusters compared to the total gamma-ray flux.
+in low mass clusters compared to the total gamma-ray flux.}
+\C{and the total DM luminosity that includes boost factors for the LP and
+the BM models is given by
+\begin{eqnarray}
+\label{eq:DM_scaling}
+L_{\gamma} &=& L_{\gamma,\rmn{sm}} \B_\rmn{sub} \propto \frac{\mvir^{1.06}}{D_\rmn{lum}^2},\\
+\rmn{where} & &\B_\sub \propto \mvir^{0.23}\,.
+\end{eqnarray}
+Hence, increasing the cluster mass by a factor two more than doubles
+the DM luminosity, but increasing the luminosity distance,
+$D_\rmn{lum}$, by a factor two decrease the flux by a factor four. We
+note that the IC from upscattered SD photons scales slightly softer
+with mass, hence gives rise to a larger fraction of gamma-rays in low
+mass clusters compared to the total gamma-ray flux. Also note that we
+have not included the SFE for the LP model in
+Eq.~(\ref{eq:DM_scaling}) since it is a constant when substructures
+are included. If only a small fraction of the DM resides in the
+subhalos, the scaling of the LP DM becomes slightly steeper due to the
+mass dependence inferred from the velocity dispersion:
+\begin{eqnarray}
+L_{\gamma,LPnosub} &=& L_{\gamma,\rmn{sm}} \B_\rmn{sfe} 
+\propto \frac{\mvir^{0.5}}{D_\rmn{lum}^2},\\
+\rmn{where} &\quad&\B_\rmn{sfe} \propto \mvir^{-1/3}.
+\end{eqnarray}}
 
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v12.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v12.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v12.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v12.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v13.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v13.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v13.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v13.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
 \caption{\it Comparing the gamma-ray emission from different
@@
 PAMELA/Fermi/HESS. In Fig.~\ref{fig:boost_const} we use the estimated
-flux of four clusters to constrain the SFE as well as the minimum mass
-of substructures where $M_\rmn{lim}\propto\mvir^{0.226}$. As expected,
-the Fornax cluster is by far the most constraining cluster, although
-the current upper limits are not good enough to rule out the boost
-from substructures or SFE. Assuming that the PAMELA positron excess is
-due to SFE DM, then in order not to overproduce the differential upper
-limits set by Fermi-LAT in the energy range\footnote{We
-  average the LP DM flux in the energy range $1-10$~GeV before we
-  compare it to the upper limits.}  $1-10$~GeV, we can constrain the smallest mass
-of substructures to $M_\rmn{lim}\gtrsim 100\,\msun$. Instead assuming
-the standard mass of the smallest substructures of $M_\rmn{lim}\approx
-10^{-6}\,\msun$, we can constrain the boost from SFE to about 2 in
-Fornax, which corresponds to a maximum SFE in the MW of about 5. Note
-that after about six years of observations with Fermi-LAT, we will be
-able to rule out the LP model assuming a substructure boost with a
-smallest mass of $M_\rmn{lim} \approx 10^{-6}\,\msun$.
+flux \C{within $\rvir$ of four bright and maximal constraining
+  clusters (Fornax, M49, Norma, and Coma, where we have excluded Virgo
+  due to its large angular extent) to limit} the SFE as well as the
+minimum mass of substructures where
+$M_\rmn{lim}\propto\mvir^{0.226}$. We find that M49 and the Fornax
+cluster are the most constraining clusters, although the current upper
+limits are not good enough to rule out the boost from substructures or
+SFE. Assuming that the PAMELA positron excess is due to SFE DM, then
+in order not to overproduce the differential upper limits set by
+Fermi-LAT in the energy range\footnote{We average the LP DM flux in
+  the energy range $1-10$~GeV before we compare it to the upper
+  limits.}  $1-10$~GeV, we can constrain the smallest mass of
+substructures to $M_\rmn{lim}\gtrsim 10\,\msun$. Instead assuming the
+standard mass of the smallest substructures of $M_\rmn{lim}\approx
+10^{-6}\,\msun$, we can constrain the \C{saturated boost from SFE to
+  about 14 in M49 and 22 in Fornax, which corresponds to a maximum SFE
+  in the MW of about 8 and 13, respectively. Hence, we conclude that
+  without substantial improvement in the modelling of these extended
+  sources, Fermi-LAT will not be able to rule out LP models in their
+  current form using clusters.} \del{Note that after about six years
+  of observations with Fermi-LAT, we will be able to rule out the LP
+  model assuming a substructure boost with a smallest mass of
+  $M_\rmn{lim} \approx 10^{-6}\,\msun$.}
 
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v12.0.1deg.1.6T.SubMass.SF300.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v13.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
  \caption{\it Constraining boost factors using flux upper limits. The
@@
    $1-10$~GeV the boost from substructures and Sommerfeld enhancement
-   (SFE) is constrained for four clusters; Fornax (red), Virgo
-   (orange), M49 (green), and NGC4636 (blue). The SFE has been
-   rescaled from the MW value of 300 (c.f. Eq.~\ref{eq:B_sfe}) that is
+   (SFE) is constrained for four clusters; Fornax (red), Norma
+   (orange), M49 (green), and Coma (blue). \C{We indicate both the
+     saturated SFE of 530 (right black arrow) as well as the the local
+     boost in the Milky Way of 300 (c.f. Eq.~\ref{eq:B_sfe}) that is
      required to explain the electron and positron excess observed at
-   Earth with LP DM (black arrow). If the DM interpretation is
+     Earth with LP DM (left black arrow). If the DM interpretation is
      correct, we can constrain the smallest size of halos to be larger
-   than $100\,\msun$. Contrarily, if the smallest size of DM halos is
-   $10^{-6}\,\msun$, we can constrain the SFE to about 2 in Fornax,
-   corresponding to a maximum SFE in the MW of about 5 which would be
-   too small to support the DM annihilation hypothesis for the
-   PAMELA/Fermi excess.}
+     than $10\,\msun$. Contrarily, if the smallest size of DM halos is
+     $10^{-6}\,\msun$, we can constrain the SFE to about 14 in M49 and
+     22 in Fornax. This corresponds to a maximum SFE in the MW of
+     about 8 and 13, respectively, which would be too small to support
+     the DM annihilation hypothesis for the PAMELA/Fermi excess.}}
  \label{fig:boost_const}
@@
 used to separate different models. The surface brightness, $S_\gamma$,
-of the BM model scales as $S_\gamma\propto\bsub
-L_{\gamma,\rmn{BM}}  \mvir^{-2/3} \propto \mvir^{0.59}$, which explains the
-factor three difference in normalization between the most massive
-cluster Coma and the least massive cluster Fornax with a mass ratio of
-about 10. The flux from the LP model shows a smaller spread in the
-normalization which is due to the additional contribution from SFE
-with a negative mass trend, hence a flux normalization with a softer
-mass-scaling of $S_\gamma\propto\mvir^{0.06}$. The surface brightness
-induced by CRs is proportional to the projected squared the gas
-profile with an additional enhancement in the center of cool core
-clusters due to the adiabatic compression of CRs during the formation
-of the cool core. Hence, we see a much larger variation in these
-profiles driven by the large variation of the gas mass fraction. It is
-noticeable that Fornax shows such a small surface brightness. This is
-explained by the low gas density outside the BCG and the less abundant
-CR population in a small cluster compared to a
-massive cluster \cite{2010MNRAS.409..449P}.  This is the reason why
-Fornax is such a good target for indirect DM searches, and superior
-to DM searches in dwarf galaxies.
+of the DM scales as $S_\gamma\propto\bsub L_{\gamma} \mvir^{-2/3}
+\propto \mvir^{0.59}$, which explains the factor three difference in
+normalization between the most massive cluster Coma and the least
+massive cluster Fornax with a mass ratio of about 10. \del{The flux
+  from the LP model shows a smaller spread in the normalization which
+  is due to the additional contribution from SFE with a negative mass
+  trend, hence a flux normalization with a softer mass-scaling of
+  $S_\gamma\propto\mvir^{0.06}$.} The surface brightness induced by
+CRs is proportional to the projected squared the gas profile with an
+additional enhancement in the center of cool core clusters due to the
+adiabatic compression of CRs during the formation of the cool
+core. Hence, we see a much larger variation in these profiles driven
+by the large variation of the gas mass fraction. It is noticeable that
+Fornax shows such a small surface brightness. This is explained by the
+low gas density outside the BCG and the less abundant CR population in
+a small cluster compared to a massive cluster
+\cite{2010MNRAS.409..449P}.  This is the reason why Fornax is such a
+good target for indirect DM searches, and superior to DM searches in
+dwarf galaxies.
 
 \begin{figure}
- \includegraphics[width=0.99\columnwidth]{figures/SB.v12.1GeV.SF300.SubMass.elmu.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.v13.1GeV.SF700.SubMass.elmu.eps}
  \caption{\it Comparing the intrinsic surface brightness from
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v12.1GeV.SF300.noSuB.vs.SubMass.elmu.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v13.1GeV.SF700.noSuB.vs.SubMass.elmu.eps}
  \caption{\it The impact of substructures on the intrinsic surface
@@
    boost from substructures is included while the substructures are
-   excluded for the dotted lines. The boost from Sommerfeld and
-   substructures is about 130 and 730, respectively. Notice the nearly
-   flat profiles when substructures are included, and the relative
-   large boost at $0.01\rvir$ that is due to projection of peripheral
-   substructures onto the cluster center.}
+   excluded for the dotted lines. The boost from Sommerfeld
+   \C{enhancement with and without substructures is 130 and 530
+     respectively, where in addition the boost due to substructures is
+     about 730.} Notice the nearly flat profiles when substructures
+   are included, and the relative large boost at $0.01\rvir$ that is
+   due to projection of peripheral substructures onto the cluster
+   center.}
  \label{fig:SB_sub}
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.v12.1GeV.SF300.noSuB.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v12.1GeV.SF300.noSuB.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.v13.1GeV.SF700.noSuB.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v13.1GeV.SF700.noSuB.elmu.eps}
   \caption{\it The intrinsic surface brightness profiles without
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v12.SF300.SubMass.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v12.SF300.SubMass.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v13.SF700.SubMass.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v13.SF700.SubMass.elmu.eps}
 \caption{\it Surface brightness predicted for Cherenkov telescopes at
@@
   \includegraphics[width=0.99\columnwidth]{figures/MLscaling.10G.eps}
-  \caption{\it Scaling relations of the cluster's virial mass $\mvir$ and the
-    gamma-ray luminosity for energies $E_\gamma>100$~MeV (left) and
-    $E_\gamma>10$~GeV (right).  Shown are the relations for the CR-induced
-    emission that is dominated by pion decay resulting from hadronic CR
-    interactions (solid), the leptophilic model of DM annihilations that
-    includes the scaling of the substructure and Sommerfeld boost factors with
-    cluster mass from Eq.~(\ref{eq:LP_scaling}) (dash-dotted) as well as the
-    benchmark model $K'$ of DM annihilation that includes the scaling of the
-    substructure boost with cluster mass of Eq.~(\ref{eq:BM_scaling})
-    (dashed). Note that the scaling of this particular benchmark model is
-    indicative for all (non-Sommerfeld enhanced) DM annihilation models while
-    the normalization depends on the particular cross section and neutralino
-    mass.}
+  \caption{\it Scaling relations of the cluster's virial mass $\mvir$
+    and the gamma-ray luminosity for energies $E_\gamma>100$~MeV
+    (left) and $E_\gamma>10$~GeV (right).  Shown are the relations for
+    the CR-induced emission that is dominated by pion decay resulting
+    from hadronic CR interactions (solid), the leptophilic model of DM
+    annihilations \C{(dash-dotted) as well as the benchmark model $K'$
+      of DM annihilation. Both DM models include the scaling of the
+      substructure boost with cluster mass of
+      Eq.~(\ref{eq:DM_scaling}) (dashed). Note that the scaling of the
+      DM models are indicative for all (non-Sommerfeld enhanced)
+      DM annihilation models while the normalization depends on the
+      particular cross section and neutralino mass.}}
 \label{fig:lum_mass_scaling}
 \end{figure*}
-The mass scaling of the substructure boost steepens the intrinsically
-shallower DM annihilation relation of BM models
-(Eq.~\ref{eq:BM_scaling}) while this steepening is in fact
-over-compensated by the inverse mass scaling of the Sommerfeld boost
-in LP models that prefers smaller halos with a larger ratio of
-$c/\sigv$ (Eq.~\ref{eq:LP_scaling}). In contrast, the CR scaling
-relation is considerably steeper as shown by reference
-\cite{2010MNRAS.409..449P}:
+\C{The mass scaling of the substructure boost steepens the
+  intrinsically shallower DM annihilation relation in
+  Eq.~(\ref{eq:DM_scaling}) to $L_\gamma\propto \mvir^{1.06}$.
+  However, the CR scaling relation is still considerably steeper as
+  shown by reference} \cite{2010MNRAS.409..449P}:
 \begin{eqnarray}
@@
     the energy range $E_\gamma=1-10$~GeV for 32 clusters. The
-    Fermi-LAT upper limits are shown with black arrows. The predicted
-    fluxes are derived from the dominant inverse Compton-scattering of
-    CMB photons in a leptophilic DM model (red), and the continuum
-    emission from the DM $\Kp$ benchmark model (blue). Assuming a
-    boost factor due to substructures that has a mass spectrum
-    extending down to an Earth mass, the expected leptophilic fluxes
-    are ruled out by upper limits in 14 of the clusters, with the
-    strongest constraints set by Fornax and M49. We can not yet
-    constrain the benchmark models, although our predictions are
-    approaching the upper limits and will allow to test these in the
-    upcoming years with better data.}
+    \C{maximal extended Fermi-LAT upper limits are shown with black
+      arrows, while the point source limits are shown in grey.} The
+    predicted fluxes are derived from the dominant inverse
+    Compton-scattering of CMB photons in a leptophilic DM model (red),
+    and the continuum emission from the DM $\Kp$ benchmark model
+    (blue). Assuming a boost factor due to substructures that has a
+    mass spectrum extending down to an Earth mass, the expected
+    leptophilic fluxes are ruled out by upper limits in 26 of the
+    clusters, with the strongest constraints set by Fornax and
+    Ophiuchus. We can not yet constrain the benchmark models,
+    although improved modelling of extended sources as well as
+    stacking of clusters will allow to test these in the upcoming
+    years with better data.}
  \label{fig14}
@@
    estimated point source sensitivity of the Fermi-LAT after two years
-   of data taking $F_\gamma\sim 2\times10^{-9}\,\rmn{ph}\,
-   \rmn{cm}^{-2}\,\rmn{s}^{-1}$ (dashed line). The four brightest
-   clusters are labelled yielding Fornax and M49 as the brightest
-   targets.}
+   of data taking $F_\gamma(>100\,\rmn{MeV})\sim
+   2\times10^{-9}\,\rmn{ph}\, \rmn{cm}^{-2}\,\rmn{s}^{-1}$ and
+   $F_\gamma(>10\,\rmn{GeV})\sim 9\times10^{-11}\,\rmn{ph}\,
+   \rmn{cm}^{-2}\,\rmn{s}^{-1}$ (dashed lines). The four brightest
+   clusters are labelled yielding Fornax and Ophiuchus as the
+   brightest targets.}
  \label{fig21}
@@
 in the extended HIFLUGCS catalogue \cite{2002ApJ...567..716R} with our
-scaling relations of Eqs.~(\ref{eq:BM_scaling}) and
-(\ref{eq:LP_scaling}). In those, we assume a boost factor due to
-substructures that has a constant contribution per decade in
-substructure mass and has a mass spectrum extending down to Earth
-masses for our LP and BM DM annihilation models. In the LP models we
-additionally assume a cluster-mass dependent boost due to SFE. Fermi
-limits rule out the LP models in their present form with the mentioned
-assumptions in 14 clusters, and limit the boost from SFE to less than
-2 in Fornax. Assuming universality, this limits the Sommerfeld boost
-in the MW to less than 5 (see Fig.~\ref{fig:boost_const}).  The flux
-level of the Fermi limits are an indirect measure of the ambient
-background flux in the gamma-ray sky and/or the presence of strong
-point sources such as AGN in the immediate vicinity of the cluster
-position. Hence, the ratio of the Fermi upper limits to the predicted
-annihilation fluxes, $F_{\mathrm{UL}}/F_{\mathrm{DM}}$, is a good
-indication of the best cluster candidates for indirect DM
-experiments. We identify Fornax, M49, NGC4636, and Virgo to be prime
-candidates. Note however, that Virgo extends of 7 degree over the sky
-which implies a lower surface brightness and lower signal-to-noise.
-Fermi limits on individual clusters are expected to improve as
-$\sqrt{T/1.5 \mathrm{yr}}$, where $T$ is the total elapsed time of the
-Fermi mission. We emphasize that the very inhomogeneous distribution
-of $F_{\mathrm{UL}}/ F_{\mathrm{DM}}$ makes it unlikely to
-dramatically improve the limits through a stacking analysis as the
-weak signal will dilute the average constraints.
+scaling relation of Eq.~(\ref{eq:DM_scaling}). In those, we assume a
+boost factor due to substructures that has a constant contribution per
+decade in substructure mass and has a mass spectrum extending down to
+Earth masses for our LP and BM DM annihilation models. In the LP
+models we additionally assume a cluster-mass dependent boost due to
+SFE. Fermi limits rule out the LP models in their present form with
+the mentioned assumptions in 26 clusters, and limit the boost from SFE
+to less than 14 in M49. Assuming universality, this limits the
+Sommerfeld boost in the MW to less than 8 (see
+Fig.~\ref{fig:boost_const}).  The flux level of the Fermi limits are
+an indirect measure of the ambient background flux in the gamma-ray
+sky and/or the presence of strong point sources such as AGN in the
+immediate vicinity of the cluster position. Hence, the ratio of the
+Fermi upper limits to the predicted annihilation fluxes,
+$F_{\mathrm{UL}}/F_{\mathrm{DM}}$, is a good indication of the best
+cluster candidates for indirect DM experiments. We identify Fornax,
+M49, Norma, Coma, and Virgo to be prime candidates. Note however, that
+Virgo extends of 7 degree over the sky which implies a lower surface
+brightness and lower signal-to-noise.  Fermi limits on individual
+clusters are expected to improve as $\sqrt{T/1.5 \mathrm{yr}}$, where
+$T$ is the total elapsed time of the Fermi mission. We emphasize that
+the very inhomogeneous distribution of $F_{\mathrm{UL}}/
+F_{\mathrm{DM}}$ makes it unlikely to dramatically improve the limits
+through a stacking analysis as the weak signal will dilute the average
+constraints.
 
@@
 $F_\gamma(>E_\gamma) = \{4\times10^{-11}, 2\times10^{-12},
-2\times10^{-14}\} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$ at energies
+2\times10^{-14}\}\,\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$ at energies
 of $E_\gamma=\{10~\rmn{GeV}, 100~\rmn{GeV}, 1~\rmn{TeV}\}$
-\cite{2009arXiv0908.1410D}, we note that it will be very challenging
-to detect the DM annihilation signal from clusters without a
-Sommerfeld boost by Cherenkov telescopes.  This is because the boost
-from substructures is extended while the sensitivity of Cherenkov
-telescopes drops linearly with radius outside the point spread
-function. Hence the fluxes quoted in Fig.~\ref{fig21} will have to be
-compared to a sensitivity that is scaled down by the ratio of cluster
-radius to angular resolution of 0.1 degree assuming current background
-subtraction techniques of IACTs.  This important finding should
+\cite{Doro:2009qs}, we note that it will be very challenging to detect
+the DM annihilation signal from clusters without a Sommerfeld boost by
+Cherenkov telescopes.  This is because the boost from substructures is
+extended while the sensitivity of Cherenkov telescopes scales
+\C{approximately linearly with source extension}. Hence the fluxes
+quoted in Fig.~\ref{fig21} will have to be compared to a sensitivity
+that is scaled down by the ratio of cluster radius to angular
+resolution of 0.1 degree assuming current background subtraction
+techniques of Cherenkov telescopes. This important finding should
 encourage the development of new methods to overcome the degradation
@@
     the mean differential flux in the energy range $E_\gamma=1-10$~GeV
-    for 32 clusters. The Fermi upper limits are shown with black
-    arrows. The blue boxes show the gamma-ray emission from CR-induced
-    $\pi^0$-decay, where the upper (lower) bounds show the estimates
-    for an optimistic (conservative) model (see
+    for 32 clusters. \C{The maximal extended Fermi upper limits are
+      shown with black arrows, while the point source limits are
+      show with grey arrows.} The blue boxes show the gamma-ray emission from
+    CR-induced $\pi^0$-decay, where the upper (lower) bounds show the
+    estimates for an optimistic (conservative) model (see
     Sect.~\ref{sec:CRemission} and \cite{2010MNRAS.409..449P} for
@@
 seems to be less bright than an average cluster of the same mass as
-Norma. The insensitive limit on Perseus comes about since the central
-AGN in NGC1275 has turned on over the last years, making it hard to
-determine a comparable limit as obtained for the other clusters.
+Norma. The insensitive limit on Perseus \C{is due to the bright
+  central source NGC1275 with an AGN in the center
+  \cite{2010ATel.2916....1M} making it hard to determine a comparable
+  limit as obtained for the other clusters. In addition, there are
+recent gamma-ray observations of the head-tail radio galaxy IC310 in
+the cluster outskirts \cite{2010ApJ...723L.207A,2010A&A...519L...6N}.}
+
+\begin{figure*}
+\begin{minipage}{2.0\columnwidth}
+  \includegraphics[width=0.99\columnwidth]{figures/XCR.Fermi.eps}
+  \caption{\it }
+ \label{fig:XCR}
+\end{minipage}
+\end{figure*}
+
+To complete this section, we present our analytical model predictions
+for the CR-induced gamma-ray flux for all clusters in the extended
+HIFLUGCS sample in Fig.~\ref{fig19}. In the lower panel of this
+figure, we show the relative difference between the gamma-ray flux
+computed using the analytical CR model to the flux predicted by the
+mass-luminosity scaling relation. Statistically, one can view the
+analytical modeling as explicitly accounting for the scatter of the expected
+gamma-ray flux at a given mass. Cool core clusters have a denser core
+which increases the target density of gas protons for the hadronic
+reaction which in turn leads to a systematic increase of the expected
+gamma-ray fluxes. We confirm this effect since all clusters with
+increased flux ratio of our analytical CR model relative to the scaling relation
+expectation are in fact cool core clusters. This suggests that the X-ray
+emission should be a good proxy for the expected gamma-ray
+emission. Note however that there could be the counter-acting effect
+of CR streaming in relaxed clusters which would tend to decrease the
+gamma-ray luminosity \cite{2011A&A...527A..99E}. Future careful
+modelling is needed to quantify this effect.
 
@@
 
-To complete this section, we present our analytical model predictions
-for the CR-induced gamma-ray flux for all clusters in the extended
-HIFLUGCS sample in Fig.~\ref{fig19}. In the lower panel of this
-figure, we show the relative difference between the gamma-ray flux
-computed using the analytical CR model to the flux predicted by the
-mass-luminosity scaling relation. Statistically, one can view the
-analytical modeling as explicitly accounting for the scatter of the expected
-gamma-ray flux at a given mass. Cool core clusters have a denser core
-which increases the target density of gas protons for the hadronic
-reaction which in turn leads to a systematic increase of the expected
-gamma-ray fluxes. We confirm this effect since all clusters with
-increased flux ratio of our analytical CR model relative to the scaling relation
-expectation are in fact cool core clusters. This suggests that the X-ray
-emission should be a good proxy for the expected gamma-ray
-emission. Note however that there could be the counter-acting effect
-of CR streaming in relaxed clusters which would tend to decrease the
-gamma-ray luminosity \cite{2011A&A...527A..99E}. Future careful
-modelling is needed to quantify this effect.
-
 \section{Conclusions}
@@
 leptophilic (LP) models of supersymmetric dark matter (DM) as well as
-cosmic ray induced pion decay which is thought to dominate the
+cosmic ray (CR) induced pion decay which is thought to dominate the
 astrophysical signal from clusters. Once supersymmetric cold dark
@@
 and more importantly, has a comparably low CR induced gamma-ray flux.
-This in principle should allow to detect or constrain some BM models
-that have been chosen for the large gamma-ray flux yield with
-three-year Fermi data (or constrain the substructure boost
-factor). Other nearby bright sources of the extended HIFLUGCS sample
-of nearby bright X-ray cluster/groups are M49, Centaurus, and
-NGC~4636.  The non-detection of gamma-ray emission by Fermi in a total
-of 14 clusters/groups (the mentioned clusters as well as Virgo, Coma,
-Hydra, and Norma among others) considerably constrains LP models for
-DM annihilation which were introduced to explain the increasing
-positron-to-lepton ratio beyond 10 GeV. Assuming that the minimum DM
-substructure mass extends down to an Earth mass, we limit the
-Sommerfeld enhancement factor in the Fornax galaxy cluster to be less
-than 2. This corresponds to a value in the Milky Way (MW) of less than
-5 due to the larger Sommerfeld boost factor in smaller mass halos
-which have a lower velocity dispersion that enhances the particle
-cross section (while assuming universality of the DM model). This
-would rule out LP models in their current form based on the
-non-observation of gamma-rays in any of the fore-mentioned
-clusters/groups. Alternatively, assuming the LP models to be correct,
-we limit the minimum substructure mass to $>100~\msun$ in Fornax.
+\del{This in principle should allow to detect or constrain some BM
+  models that have been chosen for the large gamma-ray flux yield with
+  three-year Fermi data (or constrain the substructure boost factor).}
+Other nearby bright sources of the extended HIFLUGCS sample of nearby
+bright X-ray cluster/groups are M49, Centaurus, and NGC~4636.  The
+non-detection of gamma-ray emission by Fermi in a total of 26
+clusters/groups (the mentioned clusters as well as Virgo, Coma, Hydra,
+and Norma among others) considerably constrains LP models for DM
+annihilation which were introduced to explain the increasing
+positron-to-lepton ratio beyond 10 GeV. \C{Assuming that the minimum
+  DM substructure mass extends down to an Earth mass, we limit the
+  saturated Sommerfeld enhancement factor in M49 and Fornax to about
+  14 and 22, respectively. This corresponds to a value in the Milky
+  Way (MW) of less than 8 and 13 due to the larger Sommerfeld boost
+  factor in smaller mass halos which have a lower velocity dispersion
+  that enhances the particle cross section (while assuming
+  universality of the DM model).} This would rule out LP models in
+  their current form based on the non-observation of gamma-rays in any
+  of the fore-mentioned clusters/groups. Alternatively, assuming the
+  LP models to be correct, we limit the minimum substructure mass to
+  $>10~\msun$ in M49.
 
@@
 recently developed by \citet{2010MNRAS.409..449P} that is based on
-cosmological hydrodynamical simulations of galaxy clusters that self-consistently follow
-the evolution of CRs in cosmic structure formation. Adopting the model
-for all clusters in the HIFLUGCS sample of flux-limited X-ray
-clusters, we compare the expected gamma-ray emission to that inferred
-from using $L_\gamma$-cluster mass scaling relation. We note that the
-predictions of our ``optimistic'' model are perfectly in agreement
-with Fermi upper limits for all clusters.  The hint of a tension that
-the scaling relation modeling showed for Norma
-\citep{2010ApJ...717L..71A} could not be confirmed due to the
- lower gas density of this cluster relative to the average.
-As expected, the analytical CR model accounts for the ``scatter'' to the scaling
+cosmological hydrodynamical simulations of galaxy clusters that
+self-consistently follow the evolution of CRs in cosmic structure
+formation. Adopting the model for all clusters in the HIFLUGCS sample
+of flux-limited X-ray clusters, we compare the expected gamma-ray
+emission to that inferred from using $L_\gamma$-cluster mass scaling
+relation. We note that the predictions of our ``optimistic'' model are
+perfectly in agreement with Fermi upper limits for all clusters.  The
+hint of a tension that the scaling relation modeling showed for Norma
+\citep{2010ApJ...717L..71A} could not be confirmed due to the lower
+gas density of this cluster relative to the average.  As expected, the
+analytical CR model accounts for the ``scatter'' to the scaling
 relation and biases the gamma-ray flux high for prominent cool core
@@
 negligible active CR transport such as CR streaming and diffusion
-relative to the gas. Gamma-ray fluxes might be considerably smaller in those
-cluster that do not show an extended diffuse radio(-mini) halo that
-might point to a centrally concentrated CR distribution
+relative to the gas. Gamma-ray fluxes might be considerably smaller in
+those cluster that do not show an extended diffuse radio(-mini) halo
+that might point to a centrally concentrated CR distribution
 \citep{2011A&A...527A..99E}. The CR spectrum $E^2 dN/dE$ shows the
@@
 \smallskip We would like to thank Volker Springel, Megan Donahue,
-Stefano Profumo, and Tesla Jeltema for helpful discussions.  In
-addition we thank Neal Weiner ans Tracy Slatyer for many comments and
-suggestions for improvements of a previous version of this
-paper. A.P. acknowledges NSF grant AST 0908480 for support. We would
-furthermore like to thank KITP for their hospitality during the galaxy
-cluster workshop.  This research was supported in part by the National
-Science Foundation under Grant No. NSF PHY05-51164.  C.P. gratefully
-acknowledges financial support of the Klaus Tschira Foundation. The
-work of L.B. was supported by the Swedish Research Council (VR), under
-contracts no. 621-2009-3915 and 349-2007-8709 (the Oskar Klein
-Centre).
+Stefano Profumo, Tesla Jeltema and Fabio Zandanel for helpful
+discussions.  In addition we thank Neal Weiner and Tracy Slatyer for
+many comments and suggestions for improvements of a previous version
+of this paper. A.P. acknowledges NSF grant AST 0908480 for support. We
+would furthermore like to thank KITP for their hospitality during the
+galaxy cluster workshop.  This research was supported in part by the
+National Science Foundation under Grant No. NSF PHY05-51164.
+C.P. gratefully acknowledges financial support of the Klaus Tschira
+Foundation. The work of L.B. was supported by the Swedish Research
+Council (VR), under contracts no. 621-2009-3915 and 349-2007-8709 (the
+Oskar Klein Centre).
 
@@
 spectra are shown in the left panel of Fig.~\ref{fig:q_DM}. We choose
-to fit the source function using the following functional form
+to fit the source function in the energy regime $30\,\rmn{MeV}<\eg<
+m_\chi c^2$ using the following functional form
 \begin{eqnarray}
 q_\rmn{BM} (\eg,r)&=&\left[\frac{\rho(r)}{10^{-29}\rmn{g}\,\cm^{-3}}\right]^2
-\times\frac{a_1}{\egt}\times\theta(\eg-m_\chi\,c^2)\nonumber\\
+\times\frac{a_1}{\egt}\times\nonumber\\
 &\times&\left[\frac{\exp\left(-\egt^{-a_2}\right)}{1+\exp\left(\egt^{a_3}\right)}
 +\left(\frac{\egt}{a_4}\right)^{4.5}\right]\,, \nonumber\\
-&&\rmn{where}\quad \egt = \frac{\eg}{\gev}\,,
+\rmn{where}&\quad& \egt = \frac{\eg}{\gev}\,,
  \label{eq:bm_cont}
@@
 the right panel of Fig.~\ref{fig:q_DM}. The electron and positron
-yield resulting from our supersymmetric BM model is fitted using
+yield resulting from our supersymmetric BM model is fitted in the
+regime $30\,\rmn{MeV}<\ee< m_\chi c^2$ using
 \begin{eqnarray}
@@
 \frac{\left[1+\left(\frac{\eet}{b_6}\right)^{b_7}\right]^{b_8}}
-{\left[1+\left(\frac{\eet}{b_3}\right)^{b_4}\right]^{b_5}}
-\times\theta(\ee-m_\chi\,c^2)\,,\nonumber\\
-& &\rmn{where}\quad\eet=\frac{\ee}{\gev}\,.
+{\left[1+\left(\frac{\eet}{b_3}\right)^{b_4}\right]^{b_5}}\,,\nonumber\\
+\rmn{where}&\quad&\eet=\frac{\ee}{\gev}\,.
 \label{eq:bm_elec}
@@
 
-Finally, we use {\sc DarkSUSY} to derive the electron and positron
-yield resulting from leptophilic (LP) DM annihilating into decaying
-muons. We find the following best fit:
+\C{Finally, we use the data from
+  \cite{2011JCAP...03..019C,2011JCAP...03..051C} to derive the
+  electron and positron yield resulting from leptophilic (LP) DM
+  annihilating indirectly into decaying muons or electrons and
+  positrons. In the energy regime $30\,\rmn{MeV}<\ee< m_\chi c^2$ we
+  find the following best fit for the annihilation into muons:}
 \begin{eqnarray}
-N_{\e,\rmn{LP}\mu}(>\ee) &=& \exp\left(c_1+c_2\,y+c_3\,y^2\right)
+N_{\e,\rmn{LP}\mu}(>\ee) &=& \exp\left[c_1+c_2\,x+c_3\,(2-x)^{c_4}\right]
+\,,\nonumber\\
+\rmn{where}\quad x&=&\frac{\ee}{m_\chi\,c^2}\,\quad\rmn{and}\nonumber\\
+c_1=0.802,\,c_2&=&-5.00,\,c_3=-2.46,\,c_4=-4.40\,.\nonumber\\
+\label{eq:lp_mu}
+\end{eqnarray}
+Similarly, for the annihilation into electrons and positrons we find the following best fit:
+\begin{eqnarray}
+N_{\e,\rmn{LP}\e}(>\ee) &=& \exp\left(c_1+c_2\,y+c_3\,y^2\right)
 \,,\nonumber\\
@@
 x=\frac{\ee}{m_\chi\,c^2}\,\quad\rmn{and}\nonumber\\
-c_1&=&0.719,\,c_2=2.27,\,c_3=0.200\,.
-\label{eq:lp_elec}
+c_1&=&0.709,\,c_2=1.11,\,c_3=0.058\,.
+\label{eq:lp_ep}
 \end{eqnarray}
-The LP model, that we are using in this work,
-has a branching factor branching ratio of ($1/2:1/2$) into
-($\mu^+\mu^-:\e^+\e^-$). Hence, the resulting electron and positron
-yield for the LP model is given by
+
+The LP model, that we are using in this work has a branching factor
+branching ratio of ($1/4:1/4:1/2$) into
+($\mu^+\mu^-:\e^+\e^-:\pi^+\pi^-$). The contribution from the
+electrons from the decaying pions is relative small, hence the
+resulting electron and positron yield for the LP model is
+approximately given by
 \begin{equation}
 N_{\e,\rmn{LP}}(>\ee) =
-1+N_{\e,\rmn{LP}\mu}(>\ee)/2\,.
+N_{\e,\rmn{LP}\e}(>\ee)/4+N_{\e,\rmn{LP}\mu}(>\ee)/4\,.
 \end{equation}
@@
 reason for the re-fitted outer component is the large uncertainty in
-the data points outside $0.2-0.3\rvir$ which we exclude in our
+the data points outside $(0.2-0.3)\rvir$ which we exclude in our
 fit. Instead we assume that the outer slop of $n_\e$ follows the outer
@@
 \C{In this section we present the gamma-ray flux predictions using the
-clusters in the extended HIFLUGCS catalogue. We show the brightest 50
-clusters in descending order; CR proton induced $\pi^0$ that decays
-into gamma-rays in Table~\ref{tab:flux_tab_CRs}, the supersymmetric DM
-BM-$\Kp$ model where the Neutralino emit a continuum as well as final
-state radiation in Table~\ref{tab:flux_tab_BM}, and LP DM that emit
-final state radiation and annihilate either indirectly through
-$\mu^+/\mu^-$ to $\rmn{e}^+/\rmn{e}^-$ or directly to
-$\rmn{e}^+/\rmn{e}^-$ that IC upscatter CMB photons in
-Table~\ref{tab:flux_tab_LP}. The flux from DM has been boosted by the
-substructures, where we in addition include the Sommerfeld enhancement
-for the LP model.  
-For completeness, we show in Table~\ref{tab:flux_tab_CLp} the
-parameters that we use to derive the fluxes for the clusters in the
-HIFLUGCS sample.}
+  clusters in the extended HIFLUGCS catalogue. We show the brightest
+  50 clusters in descending order; CR proton induced $\pi^0$ that
+  decays into gamma-rays in Table~\ref{tab:flux_tab_CRs}, the
+  supersymmetric DM BM-$\Kp$ model where the Neutralino emit a
+  continuum as well as final state radiation in
+  Table~\ref{tab:flux_tab_BM}, and LP DM that emit final state
+  radiation and annihilate either indirectly to $\rmn{e}^+/\rmn{e}^-$
+  or through $\mu^+/\mu^-$ to $\rmn{e}^+/\rmn{e}^-$ that IC upscatter
+  CMB photons in Table~\ref{tab:flux_tab_LP}. The flux from DM has
+  been boosted by the substructures, where we in addition include the
+  Sommerfeld enhancement for the LP model. For completeness, we show
+  in Table~\ref{tab:flux_tab_CLp} the parameters that we use to derive
+  the fluxes for the clusters in the HIFLUGCS sample.}
 
@@
 \hline
- Cluster & ID$^{(1)}$ & $F_{\gamma}$$^{(2)}$ & $F_{\gamma}$$^{(2)}$& 
- $F_{\gamma}$$^{(3)}$ & $\eg^2\,\dd F_{\gamma}/\dd \eg$$^{(4)}$ &
- $\eg^2\,\dd F_{\gamma,0.1}/\dd \eg$$^{(4,5)}$ & 
- $\eg^2\,\dd F_{\gamma,1.0}/\dd \eg$$^{(4,6)}$\\
+ Cluster & ID$^{(1)}$ & $F_{\gamma}$$^{(2)}$ & $F_{\gamma}$$^{(3)}$& 
+ $F_{\gamma}$$^{(4)}$ & $\eg^2\,\dd F_{\gamma}/\dd \eg$$^{(5)}$ &
+ $\eg^2\,\dd F_{\gamma,0.1}/\dd \eg$$^{(5,6)}$ & 
+ $\eg^2\,\dd F_{\gamma,1.0}/\dd \eg$$^{(5,7)}$\\
   & & $(>100\,\rmn{MeV})$ & $(>1\,\rmn{GeV})$ & $(>100\,\rmn{GeV})$ & 
@@
  \hline
-FORNAX   &  10 &  50.40 &  93.76 &  50.96 &  11.56 &   0.06 &   2.30 \\
-M49      &  81 &  31.16 &  57.97 &  31.12 &   7.15 &   0.06 &   1.77 \\
-NGC4636  &  29 &  28.06 &  52.20 &  28.26 &   6.44 &   0.05 &   1.63 \\
-CENTAURUS &  30 &  21.23 &  39.50 &  20.93 &   4.87 &   0.07 &   1.53 \\
-HYDRA    &  25 &  19.00 &  35.36 &  18.80 &   4.36 &   0.07 &   1.43 \\
-NORMA    &  94 &  15.74 &  29.28 &  16.09 &   3.61 &   0.07 &   1.29 \\
-PERSEUS  &  68 &  14.84 &  27.60 &  14.57 &   3.40 &   0.08 &   1.27 \\
-OPHIUCHUS &  96 &  14.27 &  26.54 &  14.07 &   3.27 &   0.08 &   1.28 \\
-COMA     &  34 &  13.81 &  25.70 &  13.86 &   3.17 &   0.07 &   1.22 \\
-NGC5846  &  92 &  13.80 &  25.67 &  13.82 &   3.16 &   0.05 &   1.09 \\
-AWM7     &  67 &  10.67 &  19.84 &  10.61 &   2.45 &   0.07 &   1.00 \\
-NGC5813  &  91 &   9.81 &  18.25 &   9.87 &   2.25 &   0.05 &   0.87 \\
-3C129    &  70 &   8.54 &  15.88 &   8.70 &   1.96 &   0.06 &   0.86 \\
-NGC5044  &  35 &   7.40 &  13.76 &   7.39 &   1.70 &   0.05 &   0.73 \\
-ANTLIA   &  79 &   6.28 &  11.68 &   6.79 &   1.44 &   0.04 &   0.66 \\
-A1367    &  26 &   6.12 &  11.39 &   6.34 &   1.40 &   0.05 &   0.68 \\
-NGC1550  &  15 &   5.72 &  10.63 &   5.70 &   1.31 &   0.05 &   0.62 \\
-A0262    &   5 &   4.10 &   7.62 &   4.09 &   0.94 &   0.05 &   0.49 \\
-A2877    &  65 &   4.08 &   7.59 &   4.13 &   0.94 &   0.05 &   0.50 \\
-A2199    &  51 &   3.70 &   6.89 &   3.67 &   0.85 &   0.06 &   0.47 \\
-A3571    &  39 &   3.54 &   6.59 &   3.50 &   0.81 &   0.06 &   0.46 \\
-A0754    &  23 &   3.29 &   6.13 &   3.25 &   0.76 &   0.06 &   0.44 \\
-TRIANGULUM &  95 &   3.00 &   5.59 &   2.99 &   0.69 &   0.06 &   0.41 \\
-A0576    &  22 &   2.80 &   5.21 &   2.83 &   0.64 &   0.05 &   0.38 \\
-A2634    &  60 &   2.76 &   5.14 &   2.87 &   0.63 &   0.04 &   0.38 \\
-MKW8     &  42 &   2.69 &   5.00 &   2.69 &   0.62 &   0.05 &   0.36 \\
-A0539    &  71 &   2.60 &   4.84 &   2.61 &   0.60 &   0.05 &   0.36 \\
-NGC499   &  66 &   2.51 &   4.67 &   2.51 &   0.58 &   0.04 &   0.33 \\
-A4038    &  62 &   2.50 &   4.65 &   2.47 &   0.57 &   0.05 &   0.34 \\
-A3581    &  41 &   2.43 &   4.52 &   2.41 &   0.56 &   0.04 &   0.33 \\
-A3395s   &  21 &   2.40 &   4.47 &   2.45 &   0.55 &   0.05 &   0.35 \\
-A3395n   &  75 &   2.38 &   4.43 &   2.44 &   0.55 &   0.05 &   0.34 \\
-A0400    &   6 &   2.36 &   4.38 &   2.41 &   0.54 &   0.04 &   0.33 \\
-A3376    &  19 &   2.35 &   4.37 &   2.44 &   0.54 &   0.04 &   0.34 \\
-A0119    &   2 &   2.33 &   4.34 &   2.43 &   0.53 &   0.04 &   0.34 \\
-A3266    &  17 &   2.31 &   4.30 &   2.35 &   0.53 &   0.05 &   0.34 \\
-IIIZw54  &  12 &   2.25 &   4.19 &   2.28 &   0.52 &   0.04 &   0.32 \\
-A0496    &  18 &   2.25 &   4.19 &   2.22 &   0.52 &   0.05 &   0.32 \\
-NGC507   &   4 &   2.18 &   4.05 &   2.18 &   0.50 &   0.04 &   0.30 \\
-A2319    &  98 &   2.14 &   3.99 &   2.15 &   0.49 &   0.05 &   0.32 \\
-A2256    &  54 &   2.14 &   3.97 &   2.16 &   0.49 &   0.05 &   0.32 \\
-MKW4     &  27 &   2.03 &   3.78 &   2.02 &   0.47 &   0.04 &   0.29 \\
-A2147    &  49 &   2.00 &   3.72 &   2.09 &   0.46 &   0.04 &   0.29 \\
-A2063    &  47 &   1.98 &   3.68 &   1.96 &   0.45 &   0.04 &   0.29 \\
-UGC03957 &  76 &   1.96 &   3.65 &   1.95 &   0.45 &   0.04 &   0.29 \\
-2A0335   &  11 &   1.70 &   3.17 &   1.68 &   0.39 &   0.04 &   0.25 \\
-A3558    &  37 &   1.68 &   3.13 &   1.69 &   0.39 &   0.04 &   0.26 \\
-EXO0422  &  16 &   1.64 &   3.05 &   1.63 &   0.38 &   0.04 &   0.25 \\
-A1795    &  40 &   1.60 &   2.98 &   1.57 &   0.37 &   0.05 &   0.25 \\
-A2052    &  44 &   1.54 &   2.87 &   1.52 &   0.35 &   0.04 &   0.23 \\
+FORNAX   &  10 &  13.70 &  17.37 &  20.12 &  16.99 &   0.05 &   1.91 \\
+OPHIUCHU &  96 &  11.00 &  13.95 &  15.76 &  13.64 &   0.20 &   3.01 \\
+COMA     &  34 &   8.97 &  11.38 &  13.08 &  11.13 &   0.15 &   2.42 \\
+CENTAURU &  30 &   8.00 &  10.14 &  11.46 &   9.92 &   0.08 &   1.75 \\
+NORMA    &  94 &   7.98 &  10.11 &  11.85 &   9.89 &   0.10 &   1.99 \\
+PERSEUS  &  68 &   7.93 &  10.06 &  11.31 &   9.83 &   0.13 &   2.07 \\
+HYDRA    &  25 &   7.44 &   9.43 &  10.69 &   9.22 &   0.09 &   1.71 \\
+M49      &  81 &   6.53 &   8.28 &   9.47 &   8.10 &   0.04 &   1.13 \\
+NGC4636  &  29 &   4.78 &   6.06 &   7.00 &   5.93 &   0.03 &   0.85 \\
+AWM7     &  67 &   4.71 &   5.97 &   6.80 &   5.84 &   0.09 &   1.34 \\
+3C129    &  70 &   4.34 &   5.51 &   6.43 &   5.38 &   0.10 &   1.34 \\
+NGC5846  &  92 &   2.70 &   3.42 &   3.93 &   3.35 &   0.03 &   0.65 \\
+A1367    &  26 &   2.64 &   3.35 &   3.98 &   3.28 &   0.07 &   0.89 \\
+A0754    &  23 &   2.37 &   3.00 &   3.39 &   2.93 &   0.13 &   0.97 \\
+A3571    &  39 &   2.03 &   2.57 &   2.92 &   2.52 &   0.10 &   0.81 \\
+TRIANGUL &  95 &   2.02 &   2.56 &   2.93 &   2.51 &   0.11 &   0.85 \\
+NGC5813  &  91 &   1.72 &   2.18 &   2.51 &   2.13 &   0.03 &   0.47 \\
+A2199    &  51 &   1.69 &   2.14 &   2.43 &   2.10 &   0.08 &   0.66 \\
+A3266    &  17 &   1.61 &   2.04 &   2.37 &   1.99 &   0.10 &   0.72 \\
+A2877    &  65 &   1.60 &   2.03 &   2.35 &   1.98 &   0.06 &   0.60 \\
+ANTLIA   &  79 &   1.60 &   2.02 &   2.51 &   1.98 &   0.03 &   0.51 \\
+NGC5044  &  35 &   1.55 &   1.96 &   2.25 &   1.92 &   0.03 &   0.47 \\
+A3395s   &  21 &   1.45 &   1.83 &   2.14 &   1.79 &   0.09 &   0.63 \\
+A2256    &  54 &   1.44 &   1.83 &   2.12 &   1.79 &   0.10 &   0.65 \\
+A3395n   &  75 &   1.44 &   1.82 &   2.14 &   1.78 &   0.09 &   0.63 \\
+NGC1550  &  15 &   1.42 &   1.80 &   2.06 &   1.76 &   0.04 &   0.47 \\
+A0576    &  22 &   1.41 &   1.78 &   2.07 &   1.74 &   0.08 &   0.59 \\
+A2319    &  98 &   1.36 &   1.72 &   1.98 &   1.69 &   0.09 &   0.61 \\
+A3376    &  19 &   1.30 &   1.65 &   1.96 &   1.61 &   0.08 &   0.57 \\
+A0119    &   2 &   1.24 &   1.58 &   1.88 &   1.54 &   0.07 &   0.55 \\
+A2634    &  60 &   1.17 &   1.48 &   1.77 &   1.45 &   0.06 &   0.49 \\
+A0262    &   5 &   1.11 &   1.41 &   1.61 &   1.38 &   0.04 &   0.41 \\
+A2065    &  46 &   1.06 &   1.34 &   1.55 &   1.31 &   0.09 &   0.51 \\
+A0539    &  71 &   0.98 &   1.24 &   1.42 &   1.21 &   0.05 &   0.41 \\
+MKW8     &  42 &   0.97 &   1.23 &   1.41 &   1.20 &   0.05 &   0.40 \\
+A1795    &  40 &   0.96 &   1.22 &   1.37 &   1.20 &   0.08 &   0.45 \\
+A0644    &  78 &   0.94 &   1.20 &   1.35 &   1.17 &   0.09 &   0.46 \\
+A4038    &  62 &   0.91 &   1.15 &   1.31 &   1.13 &   0.05 &   0.38 \\
+A0496    &  18 &   0.89 &   1.13 &   1.27 &   1.10 &   0.06 &   0.38 \\
+IIIZw54  &  12 &   0.86 &   1.09 &   1.26 &   1.07 &   0.05 &   0.37 \\
+A3558    &  37 &   0.84 &   1.06 &   1.22 &   1.04 &   0.06 &   0.39 \\
+A2147    &  49 &   0.82 &   1.04 &   1.24 &   1.01 &   0.05 &   0.37 \\
+A0085    &   1 &   0.81 &   1.03 &   1.16 &   1.01 &   0.07 &   0.38 \\
+A3667    &  56 &   0.80 &   1.02 &   1.19 &   1.00 &   0.07 &   0.38 \\
+A2063    &  47 &   0.79 &   1.00 &   1.14 &   0.98 &   0.05 &   0.35 \\
+A2029    &  43 &   0.76 &   0.96 &   1.08 &   0.94 &   0.08 &   0.38 \\
+UGC03957 &  76 &   0.75 &   0.96 &   1.09 &   0.93 &   0.05 &   0.33 \\
+A0399    &   7 &   0.74 &   0.94 &   1.10 &   0.92 &   0.07 &   0.37 \\
+A3158    &  13 &   0.73 &   0.93 &   1.06 &   0.91 &   0.07 &   0.36 \\
+A0400    &   6 &   0.73 &   0.92 &   1.08 &   0.90 &   0.04 &   0.31 \\
 \hline
@@
    (1) The HIFLUGCS cluster ID.
-   (2) In units of  $10^{-9} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
-   (3) In units of  $10^{-13} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
-   (4) In units of  $10^{-13} \rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
-   (5) The flux within $0.1$ degree that have in addition been smoothed over with a point spread function of $0.1$ degree. 
-   (6) The flux within $1.0$ degree that have in addition been smoothed over with a point spread function of $1.0$ degree. 
+   (2) In units of  $10^{-8} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (3) In units of  $10^{-9} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (4) In units of  $10^{-12} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (5) In units of  $10^{-9} \rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (6) The flux within $0.1$ degree that have in addition been smoothed over with a point spread function of $0.1$ degree. 
+   (7) The flux within $1.0$ degree that have in addition been smoothed over with a point spread function of $1.0$ degree. 
  \label{tab:flux_tab_LP}

### 2011-06-13 paper.tex
text

@@
 
+\begin{figure*}
+\begin{minipage}{2.0\columnwidth}
+  \includegraphics[width=0.99\columnwidth]{figures/XCR.Fermi.eps}
+  \caption{\it Limits on the relative CR pressure, $\bra X_\rmn{CR}\ket = \bra
+    P_\rmn{CR} \ket / \bra P_\rmn{th}\ket$ averaged across the cluster. Our
+    constraints are obtained with the extended Fermi-LAT limits in the energy
+    range $E_\gamma=1-10$~GeV that assume a King profile which matches the
+    extension of the thermal X-ray emission (black) and for comparison with
+    Fermi-LAT point-source limits (grey) \cite{2010ApJ...717L..71A}. In
+    computing those limits, we adopted our (conservative) analytic model
+    \cite{2010MNRAS.409..449P} and a averaged relative CR flux as obtained from
+    our simulations.}
+ \label{fig:XCR}
+\end{minipage}
+\end{figure*}
+
 In Fig.~\ref{fig15}, we compare Fermi-LAT flux upper limits to the
@@
 the cluster outskirts \cite{2010ApJ...723L.207A,2010A&A...519L...6N}.}
-
-\begin{figure*}
-\begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.99\columnwidth]{figures/XCR.Fermi.eps}
-  \caption{\it }
- \label{fig:XCR}
-\end{minipage}
-\end{figure*}
 

### 2011-06-13 paper.tex
update
updated fluxes, and XCR

--- 2011-06-13 paper.tex
@@
   the upper limits $\rvir/\sigma$ for $($Fornax, Coma, Virgo$)$ are
-  $(2.79,\,1.3,\,5.8)$, respectively. Similarly, it is interesting to
+  $(2.8,\,1.6,\,5.3)$, respectively. Similarly, it is interesting to
   compare the radius that contain 68\% of the flux to the assumed
-  extension, $r_\sigma/\sigma$, which is given by $(,\,,\,)$ for
+  extension, $r_\sigma/\sigma$, which is given by $(1.7,\,1.0,\,3.3)$ for
   $($Fornax,Coma,Virgo$)$, respectively. It is quite striking how
@@
 
-\begin{figure*}
-\begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.99\columnwidth]{figures/XCR.Fermi.eps}
-  \caption{\it Limits on the relative CR pressure, $\bra X_\rmn{CR}\ket = \bra
-    P_\rmn{CR} \ket / \bra P_\rmn{th}\ket$ averaged across the cluster. Our
-    constraints are obtained with the extended Fermi-LAT limits in the energy
-    range $E_\gamma=1-10$~GeV that assume a King profile which matches the
-    extension of the thermal X-ray emission (black) and for comparison with
-    Fermi-LAT point-source limits (grey) \cite{2010ApJ...717L..71A}. In
-    computing those limits, we adopted our (conservative) analytic model
-    \cite{2010MNRAS.409..449P} and a averaged relative CR flux as obtained from
-    our simulations.}
- \label{fig:XCR}
-\end{minipage}
-\end{figure*}
-
 In Fig.~\ref{fig15}, we compare Fermi-LAT flux upper limits to the
@@
 the cluster outskirts \cite{2010ApJ...723L.207A,2010A&A...519L...6N}.}
+
+\C{A quantity that is of great scientific interest is the CR pressure
+  ($P_\CR$) relative to the thermal pressure ($P_\rmn{th}$), $X_\CR =
+  P_\CR/P_\rmn{th}$, as it directly bias galaxy cluster observables
+  and the resulting cosmological constraints, such as the hydrostatic
+  mass bias or the Sunyaev-Zel’dovich signal measured by Planck, South
+  Pole Telescope, or Atacama Cosmology Telescope. In the following we
+  estimate the mass scaling of the relative CR pressure using the CR
+  formalism outlined in
+  \cite{2007A&A...473...41E,2010MNRAS.409..449P}.  First we calculate
+  the CR distribution function $f = C\,p^{-\alpha}$, where $C$ is the
+  normalization of each power-law, $p=P/m_\rmn{p} c$ is the normalized
+  CR proton momentum, and $\alpha$ is the spectral index. The CR
+  pressure $P_\CR \propto C=\tilde{C}/\rho_\rmn{gas}$, where
+  $\tilde{C}\propto M^{0.44}$ for clusters with a mass $\mvir\gtrsim
+  10^{14}\,\msun$. We determine the mass scaling of the gas density
+  through its relation to the enclosed gas fraction $f_\rmn{gas}$, and
+  find that $\rho_\rmn{gas}\propto f_\rmn{gas} \propto M^{0.135}$
+  \cite{2009ApJ...693.1142S}. The thermal pressure is derived from the
+  temperature in virial equilibrium, and scales as $P_\rmn{th}\propto
+  k_\B T \propto G M/R \propto M^{0.67}$. Finally we can derive the
+  mass scaling of the relative CR pressure from,
+\begin{equation}
+ X_\CR = \frac{P_\CR}{P_\rmn{th}} \propto \frac{\rho_\rmn{gas}\,
+   \tilde{C}}{k_\B T} \propto M^{-0.06}\,,
+\end{equation}
+which is roughly a constant, i.e. almost independent on mass. Since
+the CRs that build up the bulk of the CR pressure also give rise to
+gamma-ray emission through the production of decaying pions, we can
+use gamma-ray upper limits from Fermi-LAT to constrain $X_\CR$. These
+upper limits are 95 percent confidence limits and assume a spectral
+index of 2. EXPAND DISCUSSION, ADD VOLUME WEIGHT, HOW TO GO FROM
+GAMMA->XCR.}
+
+\C{In Fig.~\ref{fig:XCR} we show the volume weighted relative CR
+  pressure for 32 clusters, for which Fermi-LAT gamma-ray upper limits
+  are derived. We find that the most constraining clusters are the
+  Norma and Coma clusters of $X_\CR < 0.07$.}
+
+\begin{figure*}
+\begin{minipage}{2.0\columnwidth}
+  \includegraphics[width=0.99\columnwidth]{figures/XCR.Fermi.eps}
+  \caption{\it Limits on the relative CR pressure, $< X_\rmn{CR}> = <
+    P_\rmn{CR} > / < P_\rmn{th}>$ averaged across the cluster. Our
+    constraints are obtained with the extended Fermi-LAT limits in the energy
+    range $E_\gamma=1-10$~GeV that assume a King profile which matches the
+    extension of the thermal X-ray emission (black) and for comparison with
+    Fermi-LAT point-source limits (grey) \cite{2010ApJ...717L..71A}. In
+    computing those limits, we adopted our (conservative) analytic model
+    \cite{2010MNRAS.409..449P} and an averaged relative CR flux as obtained from
+    our simulations.}
+ \label{fig:XCR}
+\end{minipage}
+\end{figure*}
 

### 2011-06-15 paper.tex
minor corrections, scaling fig updated

@@
   Virgo cluster to the sample that we nevertheless refer to as
-  extended HIFLUGCS catalogue in the following.}  For previous work
+  extended HIFLUGCS catalogue in the following.}  \C{For previous work
   related to DM in clusters, see, e.g.,
-\cite{2006A&A...455...21C,2009PhRvD..80b3005J,2011arXiv1104.3530S,2011ApJ...726L...6C,2010JCAP...05..025A}.
+  \cite{2006A&A...455...21C,2009PhRvD..80b3005J,2011arXiv1104.3530S,2011ApJ...726L...6C,2010JCAP...05..025A}
+  and for recent work on CRs in clusters see
+  \cite{2010MNRAS.409..449P,2011MNRAS.410..127B,2008MNRAS.385.1211P,2009JCAP...08..002K,2010MNRAS.407.1565D}.}
 
@@
 center (for a recent possible indication of a signal, see
-\cite{2010arXiv1010.2752H}, however, see also \cite{2010arXiv1012.5839B}), the dwarf galaxies surrounding the MW
+\cite{2010arXiv1010.2752H}, however, see also
+\cite{2010arXiv1012.5839B}), the dwarf galaxies surrounding the MW
 \cite{Strigari:2006rd,Essig:2009jx,2010JCAP...01..031S}, galaxy
@@
 
-The the wave function of the lightest neutralino can be written
+The wave function of the lightest neutralino can be written
 \begin{equation}
-\tilde\chi_1=a_1\tilde B+a_2\tilde W_3+a_3 \tilde H_1^0+a_4\tilde H_2^0,
+\tilde\chi_1=a_1\tilde B+a_2\tilde W_3+a_3 \tilde H_1^0+a_4\tilde H_2^0\,,
 \end{equation}
@@
 \begin{equation}
-\sum_{i=1}^4 |a_i|^2=1.
+\sum_{i=1}^4 |a_i|^2=1\,,
 \end{equation}
-the gaugino fraction of a given neutralino is $|a_1|^2+|a_2|^2$
+where the gaugino fraction of a given neutralino is $|a_1|^2+|a_2|^2$
 whereas $|a_3|^2+|a_4|^2$ is the higgsino fraction.
@@
 processes; leptophilic DM annihilating \C{through
-  $\chi\,\chi\to\phi\,\phi\to\{4\mu\to4e,\,4e,\,4\pi\to4e\}$ where the
+  $\chi\,\chi\to\phi\,\phi\to\{4e,\,4\mu\to4e,\,4\pi\to4e\}$ where the
   $\rmn{e}^+/\rmn{e}^-$ pairs} IC upscatter background photons
@@
 enhancement over the smooth halo contribution $\B_{\sub,i}(r) =
-1+\rho_{\sub,i}^2(r)/\rho^2(r)$ (see
+1+\rho_{\sub,i}^2(r)/\rho^2(r)$ \C{\footnote{Note that if the boost
+    from substructures is $\gg 1$, then the Sommerfeld enhancement
+    approaches the constant saturated boost of 530.}} (see
 Eqs.~\ref{eq:rho_sub}-\ref{eq:xvir} and Sect.~\ref{sect:subst}).  The
@@
   positrons we model the spectral distribution with $\dd N_\e^f/\dd
-  \ee= 2\delta(\ee-m_\chi c^2)$.} \C{We use the data from
+  \ee= 2\delta(\ee-m_\chi c^2)$.} \C{We use the differential spectra
+  derived from high-statistics simulations in
   \cite{2011JCAP...03..019C,2011JCAP...03..051C} to compute the
-spectra when neutralinos annihilate indirectly into $e^+/e^-$ pairs as
-well as $\mu^+/\mu^-$ pairs in the LP model. We use \ds to compute the
-$e^+/e^-$ spectra from our four BM models where only a fraction of the
-annihilating neutralinos is converted into electrons and positrons
-(see Sect.~\ref{sect:PF} and Fig.~\ref{fig:q_DM} for further details).}
+  cumulative number of electrons and positrons resulting from
+  neutralinos annihilate indirectly into $e^+/e^-$ pairs as well as
+  $\mu^+/\mu^-$ pairs in the LP model. We use \ds to compute the
+  $e^+/e^-$ spectra from our four BM models where only a fraction of
+  the annihilating neutralinos is converted into electrons and
+  positrons (see Sect.~\ref{sect:PF} and Fig.~\ref{fig:q_DM} for
+  further details).}
 %(see \cite{2009JCAP...01..016B} and references therein,
@@
 the energy densities from different radiation fields in a galaxy
-cluster with the mass $\mvir=6\times10^{14}\msun$. For this figure we
+cluster with the mass $\mvir=6.0\times10^{14}\msun$. For this figure we
 use two different profiles for the SD energy density, where the total
@@
    mass through Eqs.~(\ref{eq:E_SD}-\ref{eq:N_dust}), where we use
-   have used the mass $\mvir=6\times10^{14}\msun$ in this figure. We
+   have used the mass $\mvir=6.0\times10^{14}\msun$ in this figure. We
    renormalize the SD spectra to the radius $r=0.03\rvir$, where the
@@
    line. The SD light has been renormalized to a cluster with the mass
-   $\mvir=6\times10^{14}\msun$. Finally we show the energy density of two
+   $\mvir=6.0\times10^{14}\msun$. Finally we show the energy density of two
    magnetic field models with a central magnetic field of 3~$\mu
@@
 
-\C{We compare the calculated fluxes to gamma-ray upper limits set by
-  Fermi-LAT after 18 months of observations
+\C{We compare the calculated fluxes to 95\% c.l. gamma-ray upper
+  limits set by Fermi-LAT after 18 months of observations
   \cite{2010ApJ...717L..71A}. In particular, to achieve a more
@@
   emission that we get with our treatment of substructures, hence the
-  Fermi limits may not be adequate for some of these clusters. This and
-  other recent work highlights that the improved substructure models
-  imply that Fermi limits will have to be re-calculated to accommodate
-  for the large source extensions. Note, however, that for most
-  clusters the assumption of a point source is well justified.}
+  Fermi limits may not be adequate for some of these clusters. This
+  and other recent work highlights that the improved substructure
+  models imply that Fermi limits will have to be re-calculated to
+  accommodate for the large source extensions. Note, however, that for
+  most clusters the assumption of a point source is well justified.}
 
@@
     since Sommerfeld enhancement is no longer dominated by the low
-    velocity DM particles living in the subhalos.}}.  A larger
-fraction of electrons (in the core) will now also cool by
-Compton-upscattering SD photons which suppresses the IC-upscattered
-CMB light.  For comparison, we include the contribution of IC
-upscattered SD photons and to bracket the uncertainty in the SD model,
-with a smaller amount of dust. In this low-dust model, we have reduced
-the energy in dust by a factor 10. However, the resulting flux from
-the IC upscattered dust in this model only decreases with a factor
-that is slightly smaller than 10 since the IC cooling of the electrons
-and positrons also decreases.
+    velocity DM particles living in the subhalos (see
+    Sect.~\ref{sect:LP} for more details.}}.  A larger fraction of
+electrons (in the core) will now also cool by Compton-upscattering SD
+photons which suppresses the IC-upscattered CMB light.  For
+comparison, we include the contribution of IC upscattered SD photons
+and to bracket the uncertainty in the SD model, with a smaller amount
+of dust. In this low-dust model, we have reduced the energy in dust by
+a factor 10. However, the resulting flux from the IC upscattered dust
+in this model only decreases with a factor that is slightly smaller
+than 10 since the IC cooling of the electrons and positrons also
+decreases.
 
@@
   dashed-dotted). The sum of the three components are shown with the
-  orange solid line.  The red solid lines show the CR induced
-  gamma-ray flux. The black arrow shows the differential upper limit
-  from Fermi \protect \cite{2010ApJ...717L..71A} indicating that the
-  LP model assumptions such as Sommerfeld and/or substructure boost
-  are in conflict with the upper limit. \del{We also show projected
-    CTA point source sensitivities ($5\sigma$, 50h).}  All fluxes are
-  calculated for the Fornax cluster within $\rvir$ using a point
-  spread function of $0.1\deg$.\C{ For this cluster, the enhancement
-    due to substructures from IC upscattered CMB and SD photons is
-    730. The Sommerfeld boost is 530.}}
+  orange solid line. The red solid lines show the CR induced gamma-ray
+  flux. The black arrow shows the spatially extended differential
+  upper limit from Fermi \protect \cite{2010ApJ...717L..71A}
+  indicating that the LP model assumptions such as Sommerfeld and/or
+  substructure boost are in conflict with the upper limit. \del{We
+    also show projected CTA point source sensitivities ($5\sigma$,
+    50h).}  All fluxes are calculated for the Fornax cluster within
+  $\rvir$ using a point spread function of $0.1\deg$. \C{For this
+    cluster, the enhancement due to substructures from IC upscattered
+    CMB and SD photons is 730. The Sommerfeld boost is 530.}}
  \label{fig:IR_comp}
@@
    and IC upscattered CMB, dust and starlight (green dash-dotted), and
-   the benchmark $\Kp$ model (BM) that includes continuum emission, and
-   IC upscattered CMB, dust and starlight (blue dashed). The black
-   arrow shows the integrated flux upper limit set by Fermi-LAT again
-   indicating challenges for the assumptions underlying the LP
-   model. We also show projected CTA point source sensitivities
-   ($5\sigma$, 50h). The emission is calculated for the Fornax cluster
-   using a point spread function of $0.1\deg$. The boost from
-   Sommerfeld and substructures is about 530 and 730, respectively.}
+   the benchmark $\Kp$ model (BM) that includes continuum emission,
+   and IC upscattered CMB, dust and starlight (blue dashed). The black
+   arrow shows the spatially extended integrated flux upper limit set
+   by Fermi-LAT again indicating challenges for the assumptions
+   underlying the LP model. We also show projected CTA point source
+   sensitivities ($5\sigma$, 50h). The emission is calculated for the
+   Fornax cluster using a point spread function of $0.1\deg$. The
+   boost from Sommerfeld and substructures is about 530 and 730,
+   respectively.}
  \label{fig:flux_int}
@@
 from the Fornax and Virgo clusters, which highlight them as promising
-targets for indirect DM searches. \C{Note, however, that the angular
-  extended of Virgo is 7 degrees, while the extended upper limit from
-  Fermi-LAT is calculated assuming a $\sigma=1.2$ degree extension. In
-  fact, the ratio of the virial radius to the assumed extension for
-  the upper limits $\rvir/\sigma$ for $($Fornax, Coma, Virgo$)$ are
-  $(2.8,\,1.6,\,5.3)$, respectively. Similarly, it is interesting to
-  compare the radius that contain 68\% of the flux to the assumed
-  extension, $r_\sigma/\sigma$, which is given by $(1.7,\,1.0,\,3.3)$ for
-  $($Fornax,Coma,Virgo$)$, respectively. It is quite striking how
-  constraining the upper limits are for some of the clusters.}
-\del{Note, however, that we have used spatially unresolved upper
-  limits, which is quite optimistic for the Virgo cluster which has an
-  angular extended of 7 degrees.  It is quite striking how
-  constraining the upper limits are for the Fornax cluster are
-  compared to the other clusters, especially in the $1-10$~GeV energy
-  regime.} At these energies, Fermi-LAT has its peak sensitivity due
-to a combination of increasing effective area and decreasing source
-spectra as a function of energy. The upper limits for Virgo and
-Perseus are unfortunately background contaminated by AGN activity from
-M87 and NGC 1267, respectively, and do not gain much from the
-increased sensitivity. Note the high CR-induced flux in Coma and
-Perseus \C{is making it difficult for indirect DM searches in
-  those clusters if the boost factors are much lower than assumed in
-  this work.} \del{is of the same magnitude as the DM flux from LP
-  models, making it difficult for indirect DM searches in those
-  clusters.} Conversely, the Fornax cluster is a great target for
-indirect DM studies because the relative low gamma-ray flux from CRs,
-absents of an active AGN, and high DM gamma-ray flux. \del{The
-  Fermi-LAT three-year data will be able to constrain the smallest
-  mass of substructures using the DM BM models.}
+targets for indirect DM searches. \C{Especially in the $1-10$~GeV
+  energy range it is quite striking how constraining the upper limits
+  are for some of the clusters. At these energies, Fermi-LAT has its
+  peak sensitivity due to a combination of increasing effective area
+  and decreasing source spectra as a function of energy. The upper
+  limits for Virgo and Perseus are unfortunately background
+  contaminated by AGN activity from M87 and NGC 1267, respectively,
+  and do not gain much from the increased sensitivity. In addition,
+  the angular radius of Virgo is about 6 degrees, while the extended
+  upper limit from Fermi-LAT is calculated assuming a $\sigma=1.2$
+  degree radius. In fact, the ratio of the virial radius to the
+  assumed extension for the upper limits $\rvir/\sigma$ for $($Fornax,
+  Coma, Virgo$)$ are $(2.8,\,1.6,\,5.3)$, respectively. Similarly, it
+  is interesting to compare the radius that contain 68\% of the flux
+  to the assumed extension, $r_{68}/\sigma$, which is given by
+  $(1.7,\,1.0,\,3.3)$ for $($Fornax,Coma,Virgo$)$, respectively. This
+  further motivates a re-calculation of the Fermi upper limits to
+  account for the full extension of the galaxy clusters.}  \del{Note,
+  however, that we have used spatially unresolved upper limits, which
+  is quite optimistic for the Virgo cluster which has an angular
+  extended of 7 degrees.  It is quite striking how constraining the
+  upper limits are for the Fornax cluster are compared to the other
+  clusters, especially in the $1-10$~GeV energy regime.}  \C{We also
+  find that the high CR-induced flux in Coma and Perseus is making it
+  difficult for indirect DM searches in those clusters if the boost
+  factors are much lower than assumed in this work.} \del{is of the
+  same magnitude as the DM flux from LP models, making it difficult
+  for indirect DM searches in those clusters.} Conversely, the Fornax
+cluster is a great target for indirect DM studies because the relative
+low gamma-ray flux from CRs, absents of an active AGN, and high DM
+gamma-ray flux. \del{The Fermi-LAT three-year data will be able to
+  constrain the smallest mass of substructures using the DM BM
+  models.}
 
@@
 \caption{\it Comparing the gamma-ray emission from different
-  clusters. We show the differential flux of clusters: Fornax
-  (upper left), Coma (upper right), Virgo (lower left), and Perseus
-  (lower right). We show CR induced emission (red solid), a leptophilic
-  (LP) model that includes both final state radiation and IC upscattered
+  clusters. We show the differential flux of clusters: Fornax (upper
+  left), Coma (upper right), Virgo (lower left), and Perseus (lower
+  right). We show CR induced emission (red solid), a leptophilic (LP)
+  model that includes both final state radiation and IC upscattered
   CMB, dust and starlight (green dash-dotted), and the benchmark $\Kp$
-  model (BM) that includes continuum emission, and IC upscattered CMB, dust
-  and starlight (blue dashed). The arrows show the differential upper
-  limits set by Fermi-LAT in the energy ranges $0.2-1$~GeV,
-  $1-10$~GeV, and $10-100$~GeV from left to right. We show the
-  individual components for the BM model and LP model for Virgo and
-  Perseus, respectively. The flux from the clusters is integrated out
-  to $\rvir$ using a point spread function of $0.1\deg$ and includes
-  the boost from substructures. We find that the lower GeV energy
-  regime is most constraining due to the peak sensitivity of Fermi at
-  these energies and use this regime to get upper limits on boost
-  factors.}
+  model (BM) that includes continuum emission, and IC upscattered CMB,
+  dust and starlight (blue dashed). The arrows show the spatially
+  extended differential upper limits set by Fermi-LAT in the energy
+  ranges $0.2-1$~GeV, $1-10$~GeV, and $10-100$~GeV from left to
+  right. We show the individual components for the BM model and LP
+  model for Virgo and Perseus, respectively. The flux from the
+  clusters is integrated out to $\rvir$ using a point spread function
+  of $0.1\deg$ and includes the boost from substructures. We find that
+  the lower GeV energy regime is most constraining due to the peak
+  sensitivity of Fermi at these energies and use this regime to get
+  upper limits on boost factors.}
  \label{fig:clu_comp}
@@
 In this section, we have found that the LP DM models overproduces both
-the differential and integrated gamma-ray flux upper limits set by the
-Fermi-LAT 18 month data for several clusters. We can use these upper
-limits to constrain the boosts due to SFE and
-substructures. Furthermore, as more sensitive experiments and better
-upper limits emerge, we can start ruling out models that give rise to
-boost factors that are manifested in the gamma-ray flux. It is
+the spatially extended differential and integrated gamma-ray flux
+upper limits set by the Fermi-LAT 18 month data for several
+clusters. We can use these upper limits to constrain the boosts due to
+SFE and substructures. Furthermore, as more sensitive experiments and
+better upper limits emerge, we can start ruling out models that give
+rise to boost factors that are manifested in the gamma-ray flux. It is
 especially interesting to constrain the SFE, where a boost of the
@@
   $S_\gamma\propto\mvir^{0.06}$.} The surface brightness induced by
-CRs is proportional to the projected squared the gas profile with an
+CRs is proportional to the projected squared gas profile with an
 additional enhancement in the center of cool core clusters due to the
@@
 M49, Norma, Coma, and Virgo to be prime candidates. Note however, that
-Virgo extends of 7 degree over the sky which implies a lower surface
+Virgo extends of 12 degree over the sky which implies a lower surface
 brightness and lower signal-to-noise.  Fermi limits on individual
@@
     the mean differential flux in the energy range $E_\gamma=1-10$~GeV
-    for 32 clusters. \C{The maximal extended Fermi upper limits are
-      shown with black arrows, while the point source limits are
-      show with grey arrows.} The blue boxes show the gamma-ray emission from
-    CR-induced $\pi^0$-decay, where the upper (lower) bounds show the
-    estimates for an optimistic (conservative) model (see
-    Sect.~\ref{sec:CRemission} and \cite{2010MNRAS.409..449P} for
-    details). Note that our models are in perfect agreement with the
-    derived upper limits from Fermi. Interestingly, the limits of
-    Virgo, Norma, and Coma are closing in on our predictions and will
-    enforce constraints on the parameters of hadronic models such as
-    shock acceleration efficiencies or CR transport properties in the
-    coming years.}
+    for 32 clusters. \C{The extended Fermi upper limits assume King
+      profiles and are shown with black arrows, while the point source
+      limits are show with grey arrows.} The blue boxes show the
+    gamma-ray emission from CR-induced $\pi^0$-decay, where the upper
+    (lower) bounds show the estimates for an optimistic (conservative)
+    model (see Sect.~\ref{sec:CRemission} and
+    \cite{2010MNRAS.409..449P} for details). Note that our models are
+    in perfect agreement with the derived upper limits from
+    Fermi. Interestingly, the limits of Virgo, Norma, and Coma are
+    closing in on our predictions and will enforce constraints on the
+    parameters of hadronic models such as shock acceleration
+    efficiencies or CR transport properties in the coming years.}
  \label{fig15}
@@
 
-In Fig.~\ref{fig15}, we compare Fermi-LAT flux upper limits to the
-flux predictions by an analytical CR model \cite{2010MNRAS.409..449P}
-for CR induced gamma-rays. For consistency, we use beta-model fits to
-ROSAT data of X-ray bright clusters for our gamma-ray flux estimates
-as an input \cite{2002ApJ...567..716R}). We derive the central gas
-densities for each cluster by following the approach outlined in
+\C{In Fig.~\ref{fig15}, we show the extended Fermi-LAT flux upper
+  limits that assume King profiles that trace the X-ray emitting gas
+  compared to the flux predictions by an analytical CR model
+  \cite{2010MNRAS.409..449P} for CR induced gamma-rays.} For
+consistency, we use beta-model fits to ROSAT data of X-ray bright
+clusters for our gamma-ray flux estimates as an input
+\cite{2002ApJ...567..716R}). We derive the central gas densities for
+each cluster by following the approach outlined in
 \cite{1999ApJ...517..627M} which assumes that the ICM is
@@
   recent gamma-ray observations of the head-tail radio galaxy IC310 in
-the cluster outskirts \cite{2010ApJ...723L.207A,2010A&A...519L...6N}.}
+  the cluster outskirts
+  \cite{2010ApJ...723L.207A,2010A&A...519L...6N}.}
 
@@
   k_\B T \propto G M/R \propto M^{0.67}$. Finally we can derive the
-  mass scaling of the relative CR pressure from,
+  mass scaling of the volume weighted relative CR pressure from
 \begin{equation}
- X_\CR = \frac{P_\CR}{P_\rmn{th}} \propto \frac{\rho_\rmn{gas}\,
-   \tilde{C}}{k_\B T} \propto M^{-0.06}\,,
+ <X_\CR> = \frac{<P_\CR>}{<P_\rmn{th}>} \propto \frac{<\rho_\rmn{gas}\,
+   \tilde{C}>}{<k_\B T>} \propto M^{-0.06}\,,
 \end{equation}
-which is roughly a constant, i.e. almost independent on mass. Since
-the CRs that build up the bulk of the CR pressure also give rise to
-gamma-ray emission through the production of decaying pions, we can
-use gamma-ray upper limits from Fermi-LAT to constrain $X_\CR$. These
-upper limits are 95 percent confidence limits and assume a spectral
-index of 2. EXPAND DISCUSSION, ADD VOLUME WEIGHT, HOW TO GO FROM
-GAMMA->XCR.}
-
-\C{In Fig.~\ref{fig:XCR} we show the volume weighted relative CR
-  pressure for 32 clusters, for which Fermi-LAT gamma-ray upper limits
-  are derived. We find that the most constraining clusters are the
-  Norma and Coma clusters of $X_\CR < 0.07$.}
+which is roughly a constant, i.e. almost independent on mass. Hence we
+adopt a constant $<X_\CR>\approx 0.02$ derived from a representative
+simulated cluster \cite{2008MNRAS.385.1211P}.  Since the CRs that
+build up the bulk of the CR pressure also give rise to gamma-ray
+emission through the production of decaying pions, we use gamma-ray
+upper limits from Fermi-LAT to constrain $X_\CR$. In
+Fig.~\ref{fig:XCR} we show the volume weighted relative CR pressure
+for 32 clusters, for which LAT upper limits that assume King profiles
+are derived. We find that the most constraining clusters are the Norma
+and Coma clusters of $<X_\CR> < 0.07$.}
 
@@
 emission is low, the IC up-scattering of the CMB dominates below 60
-GeV. For large clusters, the final state radiation then takes over for
+GeV. \C{The final state radiation then takes over for energies up to
+  the cutoff at $m_\chi c^2 \sim 1$~TeV. The IC up-scattering of the
+  dust and starlight is always subdominant compared to the upscattered
+  CMB (below 60~GeV) and the final state radiation (above 60~GeV).}
+\del{For large clusters, the final state radiation then takes over for
   energies up to the cutoff at $m_\chi c^2 \sim 1$~TeV. In small
   clusters, there is a window around $E_\gamma \sim 100~\mathrm{GeV}$
-where the IC up-scattering of the dust emission dominates over the CMB
-IC emission and the final state radiation. The IC emission of
-starlight remains always subdominant.  We stress, that the inclusion
-of the dust and starlight radiation fields are negligible in the
-cooling function for the leptons.  The main reason why the IC emission
-from starlight and dust remains subdominant is the small overlap of
-this component with the peripherally peaked substructure mass density
-profiles. If for some reason, DM has less substructure, the relative
-importance of this IC component increases considerably.
+  where the IC up-scattering of the dust emission dominates over the
+  CMB IC emission and the final state radiation. The IC emission of
+  starlight remains always subdominant.}  We stress, that the
+inclusion of the dust and starlight radiation fields are negligible in
+the cooling function for the leptons.  The main reason why the IC
+emission from starlight and dust remains subdominant is the small
+overlap of this component with the peripherally peaked substructure
+mass density profiles. If for some reason, DM has less substructure,
+the relative importance of this IC component increases considerably.
 
@@
 dominate the DM annihilation signal of BM models for all
-clusters/groups but Fornax. We conclude that it will be possible to
-rule out the LP model with six years of Fermi data and start to
-constrain some BM DM models. Hence this should nicely complement
-direct and accelerator searches for the nature of DM.
+clusters/groups but Fornax. \C{We conclude that due to the large
+  spatial extension of the brightest clusters it is not possible for
+  Fermi to rule out the LP model nor to constrain the BM DM models
+  without improved modelling. However, we can put tight constrints on
+  the boost from substructures and Sommerfeld enhancement using the LP
+  model. Hence, clusters are a nice complement to direct and
+  accelerator searches for the nature of DM.}\del{We conclude that it
+  will be possible to rule out the LP model with six years of Fermi
+  data and start to constrain some BM DM models. Hence this should
+  nicely complement direct and accelerator searches for the nature of
+  DM.}
 
@@
 (CMB) black-body distribution together with the spectral distribution
-of SD light of a $6\times10^{14}\,\msun$ galaxy cluster. We fit the
+of SD light of a $6.0\times10^{14}\,\msun$ galaxy cluster. We fit the
 spectral shape of SD individually; the dust that peaks at about
@@
 Fig.~\ref{fig:SD_Edens} for a galaxy cluster with the mass
-$\mvir=6\times10^{14}\msun$. We find that inside a few percent of of
+$\mvir=6.0\times10^{14}\msun$. We find that inside a few percent of of
 $\rvir$, the total energy density is dominated by the light from SD
@@
 \rmn{where}\quad x&=&\frac{\ee}{m_\chi\,c^2}\,\quad\rmn{and}\nonumber\\
-c_1=0.802,\,c_2&=&-5.00,\,c_3=-2.46,\,c_4=-4.40\,.\nonumber\\
+c_1=1.49,\,c_2&=&-5.00,\,c_3=-2.46,\,c_4=-4.40\,.\nonumber\\
 \label{eq:lp_mu}
@@
 x=\frac{\ee}{m_\chi\,c^2}\,\quad\rmn{and}\nonumber\\
-c_1&=&0.709,\,c_2=1.11,\,c_3=0.058\,.
+c_1&=&1.40,\,c_2=1.11,\,c_3=0.058\,.
 \label{eq:lp_ep}
@@
 \end{tabular}
+ \label{tab:flux_tab_CLp}
 \end{minipage}
@@
   Sommerfeld enhancement for the LP model. 
- \label{tab:flux_tab_CLp}
   \end{quote}

### 2011-06-17 paper.tex
minor corrections text

@@
 \def\C#1{{\bf #1}}
+
+%\voffset-.6in 
+\voffset.3in
 
@@
 <\eg \,F_\gamma> &=& K\,\frac{\sum \dd \eg^{2-\alpha}}{\sum \dd \eg}
-= K\,\frac{\sum \dd \eg^{2-\alpha}}{E_{\gamma,2}-E_{\gamma,1}}\,,\nonumber
+= K\,\frac{\sum \dd \eg^{2-\alpha}}{E_{\gamma,2}-E_{\gamma,1}}\,,\nonumber\\
+\label{eq:spec_ind_UL}
 \end{eqnarray}
@@
 $(1.10,\,0.71,\,1.15)$ where we have used the spectral indices
-$(2.20,\,1.22,\,2.24)$, respectively. See Fig.~\ref{fig:clu_comp} for
-additional spectral indices.}
+$(2.20,\,1.22,\,2.24)$, respectively. See
+Tab.~\ref{tab:spectral_index} for additional spectral indices.}
 
@@
 have not included the SFE for the LP model in
-Eq.~(\ref{eq:DM_scaling}) since it is a constant when substructures
-are included. If only a small fraction of the DM resides in the
-subhalos, the scaling of the LP DM becomes slightly steeper due to the
-mass dependence inferred from the velocity dispersion:
+Eq.~(\ref{eq:DM_scaling}) since it saturates to a constant value in
+the substructures. However, if only a small fraction of the DM resides
+in the subhalos, the scaling of the LP DM becomes slightly steeper due
+to the mass dependence inferred from the velocity dispersion:
 \begin{eqnarray}
@@
 \caption{\it Comparing the gamma-ray emission from different
-  clusters. We show the differential flux of clusters: Fornax (upper
-  left), Coma (upper right), Virgo (lower left), and Perseus (lower
-  right). We show CR induced emission (red solid), a leptophilic (LP)
-  model that includes both final state radiation and IC upscattered
-  CMB, dust and starlight (green dash-dotted), and the benchmark $\Kp$
-  model (BM) that includes continuum emission, and IC upscattered CMB,
-  dust and starlight (blue dashed). The arrows show the spatially
-  extended differential upper limits set by Fermi-LAT in the energy
-  ranges $0.2-1$~GeV, $1-10$~GeV, and $10-100$~GeV from left to
-  right. We show the individual components for the BM model and LP
-  model for Virgo and Perseus, respectively. The flux from the
+  clusters. We show the differential flux of clusters \C{in the upper
+    panel of each figure}: Fornax (upper left), Coma (upper right),
+  Virgo (lower left), and Perseus (lower right). We show CR induced
+  emission (red solid), a leptophilic (LP) model that includes both
+  final state radiation and IC upscattered CMB, dust and starlight
+  (green dash-dotted), and the benchmark $\Kp$ model (BM) that
+  includes continuum emission, and IC upscattered CMB, dust and
+  starlight (blue dashed). The arrows show the spatially extended
+  differential upper limits set by Fermi-LAT in the energy ranges
+  $0.2-1$~GeV, $1-10$~GeV, and $10-100$~GeV from left to right. We
+  show the individual components for the BM model and LP model for
+  Virgo and Perseus, respectively. \C{In the lower panel of each
+    figure we show differential spectral index where $\dd F_\gamma/\dd
+    E_\gamma \sim E_\gamma^{-\alpha_\gamma}$.} The flux from the
   clusters is integrated out to $\rvir$ using a point spread function
@@
 \end{figure*}
+
+\C{For consistency we provide in addition the differential spectral
+  indices $\alpha_\gamma=-\frac{\dd \log(\dd F/\dd E)}{\dd \log(E)}$
+  for the different emission models in the lower panels of
+  Fig.~\ref{fig:clu_comp}. We find very similar spectral indices for
+  different clusters when the boost from substructures is substantial,
+  while for models without substructures the relative contribution
+  from the upscattered dust and starlight breaks the spectral
+  universality for the DM models. In the $1~\gev-1~\tev$ energy regime
+  the CR spectral index is approximately constant $\sim (2.1-2.3)$,
+  while the spectral index for the LP model has a large spread and
+  varies between $1.2-4.0$, hence implying that gamma-ray upper limits
+  are more sensitive to the specific energy regime for these
+  models. Similarly, the index for the BM $\Kp$ model is about 1.0 at
+  1~GeV and increases monotonically for higher energies, which also
+  suggests that the flux upper limits contrasted to this model are
+  sensitive to the specific energy range, and where a small energy
+  range would be preferred. In experiments is the spectral index often
+  fixed over an energy range, hence we show in
+  Tab.~\ref{tab:spectral_index} the indices for our emission models in
+  four different energy bands. We find that these spectral indices
+  have a much smaller spread, hence reducing the importance of the
+  specific energy regimes. For further discussion about the impact of
+  different spectral indices on the gamma-ray upper limits see
+  Eq.~(\ref{sect:spectral}) and related text.}
+
+\begin{table}
+\begin{tabular}{ccccc}
+\hline\hline
+      Model & $\alpha_{100\,\rmn{MeV}}^{1\,\rmn{GeV}}$  & 
+              $\alpha_{1\,\rmn{GeV}}^{10\,\rmn{GeV}}$   & 
+              $\alpha_{10\,\rmn{GeV}}^{100\,\rmn{GeV}}$ &
+              $\alpha_{100\,\rmn{GeV}}^{1\,\rmn{TeV}}$  \\
+\hline
+CR-$\pi^0$      & 1.44 & 2.24 & 2.30 & 2.26 \\
+DM-LP Sum       & 1.74 & 2.20 & 3.06 & 1.30 \\
+DM-BM-$\Kp$ Sum  & 1.28 & 1.22 & 2.23 & -    \\
+\hline\hline
+\end{tabular}
+ \caption{\C{Gamma-ray spectral indices $\alpha_{E_1}^{E_2}$ between
+     energies $E_1$ and $E_2$. We show the spectral index for three
+     different emission models where the boost from substructures is
+     included; the CR induced emission, the leptophilic (LP) model
+     that includes both final state radiation and IC upscattered CMB,
+     dust and starlight, and the benchmark (BM) $\Kp$ model that
+     includes continuum emission, and IC upscattered CMB, dust and
+     starlight. The indices are derived for the Fornax cluster,
+     although the variance between clusters is very small when the
+     enhancement from substructures is included which suppresses the
+     relative contribution from the upscattered dust and starlight
+     component that is cluster dependent. \label{tab:spectral_index}}}
+\end{table}
 
@@
 limits are obtained in the 1-10 GeV regime due to the highest
-sensitivity of Fermi-LAT there. While the effective area of Fermi-LAT
+sensitivity of Fermi-LAT there. While the effective area of LAT
 increases up to these energies, the typical photon spectra decrease as
@@
 \C{A quantity that is of great scientific interest is the CR pressure
-  ($P_\CR$) relative to the thermal pressure ($P_\rmn{th}$), $X_\CR =
-  P_\CR/P_\rmn{th}$, as it directly bias galaxy cluster observables
-  and the resulting cosmological constraints, such as the hydrostatic
-  mass bias or the Sunyaev-Zel’dovich signal measured by Planck, South
-  Pole Telescope, or Atacama Cosmology Telescope. In the following we
-  estimate the mass scaling of the relative CR pressure using the CR
-  formalism outlined in
+  ($P_\CR$) relative to the thermal pressure ($P_\rmn{th}$) as it
+  directly bias galaxy cluster observables and the resulting
+  cosmological constraints, such as the hydrostatic mass bias or the
+  Sunyaev-Zel’dovich signal measured by Planck, South Pole Telescope,
+  or Atacama Cosmology Telescope. In the following we estimate the
+  mass scaling of the relative CR pressure, $X_\CR =
+  P_\CR/P_\rmn{th}$, using the CR formalism outlined in
   \cite{2007A&A...473...41E,2010MNRAS.409..449P}.  First we calculate
@@
   $\tilde{C}\propto M^{0.44}$ for clusters with a mass $\mvir\gtrsim
-  10^{14}\,\msun$. We determine the mass scaling of the gas density
-  through its relation to the enclosed gas fraction $f_\rmn{gas}$, and
-  find that $\rho_\rmn{gas}\propto f_\rmn{gas} \propto M^{0.135}$
-  \cite{2009ApJ...693.1142S}. The thermal pressure is derived from the
-  temperature in virial equilibrium, and scales as $P_\rmn{th}\propto
-  k_\B T \propto G M/R \propto M^{0.67}$. Finally we can derive the
-  mass scaling of the volume weighted relative CR pressure from
+  10^{14}\,\msun$ \cite{2010MNRAS.409..449P}. We determine the
+  mass scaling of the gas density through its relation to the enclosed
+  gas fraction $f_\rmn{gas}$, and find that $\rho_\rmn{gas}\propto
+  f_\rmn{gas} \propto M^{0.135}$ \cite{2009ApJ...693.1142S}. The
+  thermal pressure is derived from the temperature in virial
+  equilibrium, and scales as $P_\rmn{th}\propto k_\B T \propto G M/R
+  \propto M^{0.67}$. Finally we can derive the mass scaling of the
+  volume weighted relative CR pressure from
 \begin{equation}
@@
 adopt a constant $<X_\CR>\approx 0.02$ derived from a representative
-simulated cluster \cite{2008MNRAS.385.1211P}.  Since the CRs that
-build up the bulk of the CR pressure also give rise to gamma-ray
-emission through the production of decaying pions, we use gamma-ray
-upper limits from Fermi-LAT to constrain $X_\CR$. In
+simulated cluster \cite{2008MNRAS.385.1211P}. Since the CRs that build
+up the bulk of the CR pressure also give rise to gamma-ray emission
+through the production of decaying pions, we use gamma-ray upper
+limits from Fermi-LAT to constrain the volume weighted $X_\CR$. In
 Fig.~\ref{fig:XCR} we show the volume weighted relative CR pressure
 for 32 clusters, for which LAT upper limits that assume King profiles
-are derived. We find that the most constraining clusters are the Norma
-and Coma clusters of $<X_\CR> < 0.07$.}
+are derived. For most of the clusters in the sample we can constrain
+$X_\CR < (0.1-0.2)$ using the extended gamma-ray upper limits, where
+the most constraining clusters are Norma and Coma with $X_\CR <
+0.07$. Most of the 32 clusters have $X_\CR$ upper limits within a
+factor few from the best constraining clusters, which suggests that
+stacking of clusters will be able to improve these limits. This might
+even be improved further using a scaled stacking with our model as a
+prior. In previous work \cite{2010ApJ...717L..71A} where the 1.5 year
+Fermi data was used to derive limits on $X_\CR$ they found on average
+more constraining limits on the most massive clusters, while we find
+better limits on the low mass clusters. This difference is explained
+by the different modelling of $P_\CR$; they assumed a mass
+independent CR pressure while we assume that $P_\CR\sim
+M^{0.44}$. Furthermore, the gamma-ray flux predictions that we use in
+this work to constrain $X_\CR$ assumes the true gas density
+distribution for each cluster \footnote{Derived from the parameters in
+  the extended HIFLUGCS catalogue.} that accounts for
+cluster-to-cluster scatter, in contrast to the mass-to-luminosity
+scaling relations that was used in previous works.}
 
@@
   Fermi to rule out the LP model nor to constrain the BM DM models
-  without improved modelling. However, we can put tight constrints on
+  without improved modelling. However, we can put tight constraints on
   the boost from substructures and Sommerfeld enhancement using the LP

### 2011-06-20 paper.tex
XCR update

@@
 
-\C{We compare the calculated fluxes to 95\% c.l. gamma-ray upper
-  limits set by Fermi-LAT after 18 months of observations
+\C{We compare the calculated fluxes to gamma-ray upper limits (95\%
+  c.l.) set by Fermi-LAT after 18 months of observations
   \cite{2010ApJ...717L..71A}. In particular, to achieve a more
-  reliable comparison we adopt the maximal spatially extended limits
-  (if nothing else is stated) since the gamma-ray flux from our
+  reliable comparison we adopt, if nothing else is stated, the maximal
+  spatially extended limits since the gamma-ray flux from our
   brightest clusters all have an angular extent above 1 degree on the
@@
   Virgo and Perseus, respectively. \C{In the lower panel of each
-    figure we show differential spectral index where $\dd F_\gamma/\dd
-    E_\gamma \sim E_\gamma^{-\alpha_\gamma}$.} The flux from the
-  clusters is integrated out to $\rvir$ using a point spread function
-  of $0.1\deg$ and includes the boost from substructures. We find that
-  the lower GeV energy regime is most constraining due to the peak
-  sensitivity of Fermi at these energies and use this regime to get
-  upper limits on boost factors.}
+    figure we show differential spectral indices, $\alpha_\gamma$,
+    where $\dd F_\gamma/\dd E_\gamma \sim E_\gamma^{-\alpha_\gamma}$.}
+  The flux from the clusters is integrated out to $\rvir$ using a
+  point spread function of $0.1\deg$ and includes the boost from
+  substructures. We find that the lower GeV energy regime is most
+  constraining due to the peak sensitivity of Fermi at these energies
+  and use this regime to get upper limits on boost factors.}
  \label{fig:clu_comp}
@@
   P_\CR/P_\rmn{th}$, using the CR formalism outlined in
-  \cite{2007A&A...473...41E,2010MNRAS.409..449P}.  First we calculate
-  the CR distribution function $f = C\,p^{-\alpha}$, where $C$ is the
-  normalization of each power-law, $p=P/m_\rmn{p} c$ is the normalized
-  CR proton momentum, and $\alpha$ is the spectral index. The CR
-  pressure $P_\CR \propto C=\tilde{C}/\rho_\rmn{gas}$, where
-  $\tilde{C}\propto M^{0.44}$ for clusters with a mass $\mvir\gtrsim
-  10^{14}\,\msun$ \cite{2010MNRAS.409..449P}. We determine the
-  mass scaling of the gas density through its relation to the enclosed
-  gas fraction $f_\rmn{gas}$, and find that $\rho_\rmn{gas}\propto
-  f_\rmn{gas} \propto M^{0.135}$ \cite{2009ApJ...693.1142S}. The
-  thermal pressure is derived from the temperature in virial
-  equilibrium, and scales as $P_\rmn{th}\propto k_\B T \propto G M/R
-  \propto M^{0.67}$. Finally we can derive the mass scaling of the
-  volume weighted relative CR pressure from
+  \cite{2007A&A...473...41E,2010MNRAS.409..449P}. We derive the CR
+  pressure from the CR distribution function $f = C\,p^{-\alpha}$,
+  where $C$ is the normalization of each power-law, $p=P/m_\rmn{p} c$
+  is the normalized CR proton momentum, and $\alpha$ is the CR
+  spectral index. The pressure is given by $P_\CR \propto
+  C=\tilde{C} \,\rho_\rmn{gas}$, where $\tilde{C}\propto M^{0.44}$ for
+  clusters with a mass $\mvir\gtrsim 10^{14}\,\msun$
+  \cite{2010MNRAS.409..449P}. We determine the mass scaling of the gas
+  density through its relation to the enclosed gas fraction
+  $f_\rmn{gas}$, and find that $\rho_\rmn{gas}\propto f_\rmn{gas}
+  \propto M^{0.135}$ \cite{2009ApJ...693.1142S}. The thermal pressure
+  is derived from the temperature in virial equilibrium, and scales as
+  $P_\rmn{th}\propto k_\B T \propto G M/R \propto M^{0.67}$. Finally
+  we can derive the mass scaling of the volume weighted relative CR
+  pressure from
 \begin{equation}
  <X_\CR> = \frac{<P_\CR>}{<P_\rmn{th}>} \propto \frac{<\rho_\rmn{gas}\,
-   \tilde{C}>}{<k_\B T>} \propto M^{-0.06}\,,
+   \tilde{C}>}{<k_\B T>} \propto M^{-0.1}\,,
 \end{equation}
@@
 even be improved further using a scaled stacking with our model as a
-prior. In previous work \cite{2010ApJ...717L..71A} where the 1.5 year
-Fermi data was used to derive limits on $X_\CR$ they found on average
-more constraining limits on the most massive clusters, while we find
-better limits on the low mass clusters. This difference is explained
-by the different modelling of $P_\CR$; they assumed a mass
-independent CR pressure while we assume that $P_\CR\sim
+prior. In the recent work \cite{2010ApJ...717L..71A} where the 1.5
+year Fermi data was used to derive limits on $X_\CR$, they found that
+the most massive clusters are on average more constraining, while we
+find better limits on the low mass clusters. This difference is
+explained by the different priors of $P_\CR$; they assumed a mass
+independent CR pressure derived from a single CR power-law
+distribution function, while we adopt a prior infered from cosmological
+simulations that dynamically trace the CRs during cluster assembly and
+allow for a varyning spectral index where $P_\CR\sim
 M^{0.44}$. Furthermore, the gamma-ray flux predictions that we use in
@@
 cluster-to-cluster scatter, in contrast to the mass-to-luminosity
-scaling relations that was used in previous works.}
+scaling relations that was used in previous work.}
 
@@
   spatial extension of the brightest clusters it is not possible for
-  Fermi to rule out the LP model nor to constrain the BM DM models
+  Fermi to rule out the LP model or to constrain the BM DM models
   without improved modelling. However, we can put tight constraints on

### 2011-06-20 paper.tex
XCR update

@@
 \end{equation}
-which is roughly a constant, i.e. almost independent on mass. Hence we
-adopt a constant $<X_\CR>\approx 0.02$ derived from a representative
-simulated cluster \cite{2008MNRAS.385.1211P}. Since the CRs that build
-up the bulk of the CR pressure also give rise to gamma-ray emission
+which is roughly a constant, i.e. almost independent on halo
+mass. This suggests that CRs are acclerated at the strongest shocks,
+in the early universe or between voids and pre-collapsed IGM, and then
+experience a similar transport history in the form of adiabatic
+compression or similarily weaker shocks. Since the CRs that build up
+the bulk of the CR pressure also give rise to gamma-ray emission
 through the production of decaying pions, we use gamma-ray upper
-limits from Fermi-LAT to constrain the volume weighted $X_\CR$. In
-Fig.~\ref{fig:XCR} we show the volume weighted relative CR pressure
-for 32 clusters, for which LAT upper limits that assume King profiles
-are derived. For most of the clusters in the sample we can constrain
-$X_\CR < (0.1-0.2)$ using the extended gamma-ray upper limits, where
-the most constraining clusters are Norma and Coma with $X_\CR <
-0.07$. Most of the 32 clusters have $X_\CR$ upper limits within a
-factor few from the best constraining clusters, which suggests that
-stacking of clusters will be able to improve these limits. This might
-even be improved further using a scaled stacking with our model as a
-prior. In the recent work \cite{2010ApJ...717L..71A} where the 1.5
-year Fermi data was used to derive limits on $X_\CR$, they found that
-the most massive clusters are on average more constraining, while we
-find better limits on the low mass clusters. This difference is
-explained by the different priors of $P_\CR$; they assumed a mass
-independent CR pressure derived from a single CR power-law
-distribution function, while we adopt a prior infered from cosmological
-simulations that dynamically trace the CRs during cluster assembly and
-allow for a varyning spectral index where $P_\CR\sim
-M^{0.44}$. Furthermore, the gamma-ray flux predictions that we use in
-this work to constrain $X_\CR$ assumes the true gas density
-distribution for each cluster \footnote{Derived from the parameters in
-  the extended HIFLUGCS catalogue.} that accounts for
-cluster-to-cluster scatter, in contrast to the mass-to-luminosity
+limits from Fermi-LAT to constrain $X_\CR$. In Fig.~\ref{fig:XCR} we
+show the volume weighted relative CR pressure for 32 clusters, for
+which LAT upper limits that assume King profiles are derived. We adopt
+a constant $<X_\CR>\approx 0.02$ derived from a representative
+simulated cluster \cite{2008MNRAS.385.1211P} and find that for most of
+the clusters in the sample we can constrain $X_\CR < (0.1-0.2)$ using
+the extended gamma-ray upper limits, where the most constraining
+clusters are Norma and Coma with $X_\CR < 0.07$. Most of the 32
+clusters have $X_\CR$ upper limits within a factor few from the best
+constraining clusters, which suggests that stacking of clusters will
+be able to improve these limits. This might even be improved further
+using a scaled stacking with our model as a prior. In a recent work
+\cite{2010ApJ...717L..71A}, where the 1.5 year Fermi data was used to
+derive limits on $X_\CR$, they found that the most massive clusters
+are on average more constraining, while we find better limits on the
+low mass clusters. This difference is explained by the different
+priors on $P_\CR$; they assumed a mass independent CR pressure derived
+from a single CR power-law distribution function, while we adopt a
+prior inferred from cosmological simulations that dynamically trace the
+CRs during cluster assembly and allow for a varying spectral index
+where $P_\CR\sim M^{0.44}$. Furthermore, the gamma-ray flux
+predictions that we use in this work to constrain $X_\CR$ assumes the
+true gas density distribution for each cluster \footnote{Derived from
+  the parameters in the extended HIFLUGCS catalogue.} that accounts
+for cluster-to-cluster scatter, in contrast to the mass-to-luminosity
 scaling relations that was used in previous work.}

### 2011-06-21 paper.tex
half-ways through with the corrections

@@
 \usepackage{epsfig,psfrag,graphicx,bm,color}
+\usepackage{xspace}
 
@@
 \newcommand{\jcap}{JCAP}
+
+\newcommand{\Fermi}{{\em Fermi}\xspace}
 
@@
 \newcommand{\eet}{\tilde{E}_\rmn{e}}
+\newcommand{\bra}{\langle}
+\newcommand{\ket}{\rangle}
 %OLD
@@
 
+\voffset.8in
+
 \begin{document}
@@
   linearly with radius and they typically have $5-10$ linear
-  resolution elements across a cluster; the gamma-ray satellite Fermi
+  resolution elements across a cluster; the gamma-ray satellite \Fermi
   is better suited. Assuming cold dark matter with a substructure mass
-  distribution down to an Earth mass and using Fermi upper limits, we
+  distribution down to an Earth mass and using \Fermi upper limits, we
   rule out the leptophilic models in their present form in 26
@@
   $\mlim > 10\,\msun$ which would be a challenge for structure
-  formation. \C{Furthermore, we find it challenging for Fermi to
+  formation. \C{We find it challenging for \Fermi to
     constrain our selection of DM benchmark models using clusters
     without improved modelling of extended sources in addition to a
-    stacked likelihood analysis.} The Fermi upper limits are, however,
+    stacked likelihood analysis.} The \Fermi upper limits are, however,
   closing in on our predictions for the CR flux using an analytic
@@
 
-Among the astrophysical systems which will be very interesting to
-detect, and study, with coming gamma-ray detectors (Fermi, HESS,
-MAGIC, VERITAS, and eventually large detectors like CTA) belong galaxy
-clusters. The most promising directions in which to search for a
-gamma-ray annihilation signal (from the annihilation process itself,
-and also the accompanying bremsstrahlung and inverse Compton (IC)
-components coming from charged particles produced in the annihilations)
-are basically three:
+Among the astrophysical systems which will be very interesting to detect, and
+study, with coming gamma-ray detectors (\Fermi, H.E.S.S., MAGIC, VERITAS, and
+eventually large detectors like CTA)\footnote{{High Energy Stereoscopic System,
+    Major Atmospheric Gamma Imaging Cerenkov Telescope, Very Energetic Radiation
+    Imaging Telescope Array System, Cerenkov Telescope Array.}} belong galaxy
+clusters. The most promising directions in which to search for a gamma-ray
+annihilation signal (from the annihilation process itself, and also the
+accompanying bremsstrahlung and inverse Compton (IC) components coming from
+charged particles produced in the annihilations) are basically three:
 
@@
 spheroidals these uncertainties can be made less severe, and
-preliminary results from Fermi-LAT shows this method to give quite
+preliminary results from \Fermi-LAT shows this method to give quite
 promising results \cite{garde}.
 
-3. Galaxy clusters. This possibility has been less studied, however
+3. Galaxy clusters. This possibility has been less studied \C{theoretically}, however
 \C{currently there is an ongoing observational campaign to detect
@@
   boost without substructures. See Section II A 1.}\\
-  (3) \C{The boost from substructures along the line of sight has been integrated 
-    out to an angular size corresponding to $\rvir$.}\\
+  (3) \C{We integrate the emission in a cylinder with a radial extent of $2.5
+  R_{200}$ along the line-of-sight and an angular size corresponding to $\rvir$
+  (both measured from the cluster center).}\\
   (4) The total gamma-ray flux from leptophilic (LP) DM where both the
@@
   included. Note that all these values are in conflict with upper limits from
-  Fermi (see the following sections for detail).\\
+  \Fermi (see the following sections for detail).\\
   (5) The total gamma-ray flux from the supersymmetric $\Kp$ benchmark (BM) 
@@
 distributions from four clusters and compare it to upper limits set by
-Fermi-LAT. For the same clusters we derive the gamma-ray surface
+\Fermi-LAT. For the same clusters we derive the gamma-ray surface
 brightness profiles in Section 4. To extend the analysis to more
@@
 clusters generated by conventional hadronic and electromagnetic
-processes - which should be close to observability with the Fermi-LAT
+processes - which should be close to observability with the \Fermi-LAT
 data
@@
 PAMELA satellite experiment \cite{Adriani:2008zr} and the ``bump'' in
-the total electron plus positron spectrum detected by Fermi
+the total electron plus positron spectrum detected by \Fermi
 \cite{Abdo:2009zk}. The viable particle physics models describing
@@
 
-A more standard explanation of the PAMELA/Fermi excess would be
+A more standard explanation of the PAMELA/\Fermi excess would be
 pulsars or other supernova remnants (e.g.,
@@
 \label{sect:LP}
-The results of PAMELA \cite{Adriani:2008zr} and Fermi-LAT
+The results of PAMELA \cite{Adriani:2008zr} and \Fermi-LAT
 \cite{Abdo:2009zk} (and to some extent ATIC
@@
 \cite{Bergstrom:2009fa,Meade:2009iu}) this is still enough to explain
-the PAMELA and Fermi excess, given other astrophysical uncertainties.
+the PAMELA and \Fermi excess, given other astrophysical uncertainties.
 
@@
   where the SFE saturates, we use $S=\B_\sfe(\sigv=v_\rmn{sat})\approx
-  530$ \footnote{Note that, $S$ is strictly speaking the Sommerfeld
-    enhanced annihilation cross-section, but here we have in addition
-    included the order unity constraint that make sure that the relic
-    density is not over-depleted at freeze-out.} for the cluster
-  halos. However, for those cluster halos without a boost from
-  substructures, we adopt a velocity dependent SFE that is normalized
-  to fit the electron and positron excess at Earth observed by the
-  PAMELA and Fermi satellites,}
+  530$ for the cluster halos.\footnote{Note that, $S$ is strictly
+    speaking the Sommerfeld enhanced annihilation cross-section, but
+    here we have in addition included the order unity constraint that
+    make sure that the relic density is not over-depleted at
+    freeze-out.} However, for figures where we neglect the
+  substructure boost, we adopt a velocity dependent SFE that is
+  normalized to fit the electron and positron excess at Earth observed
+  by the PAMELA and \Fermi satellites,}
 \begin{equation}
@@
  \caption{\it Source functions for different dark matter (DM)
-   models. Crosses show the simulated data from {\sc DarkSUSY}
-   \cite{ds}, \C{$\times$ show the data generated by
-     \protect\cite{2011JCAP...03..019C,2011JCAP...03..051C}} and the
-   solid lines show the fit to the data. LEFT PANEL: normalized
-   differential continuum spectra for four different DM benchmark (BM)
-   models; $\Ip$ model (red), $\Jp$ (orange), $\Kp$ (green), and $\Js$
-   (blue). We use Eq.~(\ref{eq:bm_cont}) to fit the continuum
-   spectra. RIGHT PANEL: number of electron and positron per DM
-   annihilation above the electron energy $\ee$ for different DM
+   models. We show the simulated data from {\sc DarkSUSY} \cite{ds}
+   ($+$), \C{and that generated by
+     \protect\cite{2011JCAP...03..019C,2011JCAP...03..051C}}
+   ($\times$); the solid lines show the fit to the data. LEFT PANEL:
+   normalized differential continuum spectra for four different DM
+   benchmark (BM) models; $\Ip$ model (red), $\Jp$ (orange), $\Kp$
+   (green), and $\Js$ (blue). We use Eq.~(\ref{eq:bm_cont}) to fit the
+   continuum spectra. RIGHT PANEL: number of electron and positron per
+   DM annihilation above the electron energy $\ee$ for different DM
    models; $\Ip$ BM model (red), $\Jp$ BM model (orange), $\Kp$ BM
@@
 processes; leptophilic DM annihilating \C{through
-  $\chi\,\chi\to\phi\,\phi\to\{4e,\,4\mu\to4e,\,4\pi\to4e\}$ where the
-  $\rmn{e}^+/\rmn{e}^-$ pairs} IC upscatter background photons
+  $\chi\,\chi\to\phi\,\phi\to\{4e\mbox{~or~}4\mu\to4e
+  \mbox{~or~}4\pi\to4e\}$ (neglecting the produced neutrinos) where
+  the $\rmn{e}^+/\rmn{e}^-$ pairs} IC upscatter background photons
 (LP-IC), leptophilic DM emitting final state radiation (LP-FSR),
@@
 High-resolution dissipationless DM simulations of MW type halos find substantial
-amount of substructures in the periphery of DM halos, while the
-substructures in the center suffer from dynamical friction and tidal
-effects depleting their central number densities. Since the DM
-annihilation rate depends on the density squared, the resulting flux
-from substructures is boosted compared to the smooth density
-distribution. Recent high resolution simulations suggest a flux
-enhancement from substructures of more than 100
-\cite{2008MNRAS.391.1685S, 2010ApJ...718..899A} for a MW size halo. We
-adopt a boost from substructures of 230 which is the enhancement found
-in one of the highest resolved MW halos ever simulated.\footnote{Note
-  that these high values for boost factors are now consistently found
-  in high-resolution simulations of dark matter halos \protect
-  \cite{2008MNRAS.391.1685S, 2010ApJ...718..899A} after accounting for
-  the tidal mass loss of subhalos. This effect causes a significantly
-  flatter subhalo distribution compared to the smooth distribution and
-  erroneously assuming an identical mass density distribution of smooth
-  DM and substructure biases the subhalo boost factor too low
-  \cite{2008JPhCS.125a2008K, 2008JPhCS.125a2008K}.} We use a double
-power-law function to fit\footnote{Our approach of fitting the
-  scaling behavior of $L_\sub(<r)$ directly from numerical
-  simulations self-consistently accounts for the radial dependence of
-  the substructure concentration \protect \cite{2008MNRAS.391.1685S}.}
-the luminosity from the smooth component of substructures
-(i.e. substructures within substructures are not included) inside
-radius $r$ which is determined for the Aquarius simulations
-\cite{2008MNRAS.391.1685S,2008Natur.456...73S}. Our best fit is given
-by
+amount of substructures in the periphery of DM halos, while the substructures in
+the center suffer from dynamical friction and tidal effects depleting their
+central number densities. Since the DM annihilation rate depends on the density
+squared, the resulting flux from substructures is boosted compared to the smooth
+density distribution. Recent high resolution simulations suggest a flux
+enhancement from substructures of more than 100 \cite{2008MNRAS.391.1685S,
+  2010ApJ...718..899A} for a MW size halo. We adopt a boost from substructures
+of 230 which is the enhancement found in one of the highest resolved MW halos
+ever simulated.\footnote{\C{While there is still a discrepancy in the literature
+    of the exact value of the predicted boost factor of the DM annihilation
+    luminosity from substructures in DM halos, this inconsistency starts to
+    become resolved, apparently converging toward predictions at the high end,
+    e.g. those by the Aquarius simulations \protect \cite{2008MNRAS.391.1685S,
+      2008Natur.456...73S}. The initial suggestions of a small {\em total} boost
+    ($<R_{200}$) of order unity by the Via Lactea simulations
+    \cite{2008JPhCS.125a2008K} made assumptions of computing the boost assuming
+    that the substructure luminosity follows that of the smooth DM
+    distribution. Physically, this would imply substructure to follow the smooth
+    DM distribution and a radially independent concentration parameter of
+    substructures; both following from neglecting tidal mass loss of
+    satellites. Tidal losses, however, are at work in simulations and cause the
+    radial number density to be anti-biased with respect to the host's mass
+    density profile yielding a significantly flatter subhalo distribution
+    compared to the smooth DM distribution \cite{2010ApJ...718..899A}. This
+    increases the substructure boost preferentially in the outer parts of DM
+    halos with a factor that ranges between 20 and 1000 (for dwarfs and galaxy
+    clusters), hence depending sensitively on the host halo mass (see
+    Figure~\ref{fig:radial_lum}).}}  We use a double power-law function to fit
+the luminosity from the smooth component of substructures (i.e. substructures
+within substructures are not included) inside radius $r$ which is determined for
+the Aquarius simulations
+\cite{2008MNRAS.391.1685S,2008Natur.456...73S}.\footnote{Our approach of fitting
+  the scaling behavior of $L_\sub(<r)$ directly from numerical simulations
+  self-consistently accounts for the radial dependence of the substructure
+  concentration \C{due to tidal mass losses} \protect
+  \cite{2008MNRAS.391.1685S}.} Our best fit is given by
 \begin{eqnarray}
@@
 
-\C{To motivate the scaling of the substructure luminosity boost with
-  limiting substructure mass in Eqs.~(\ref{eq:Lsub}-\ref{eq:Csub}),
-  we show how it derives from the substructure mass function, $\dd
-  N_\sub/\dd M \propto M^{-1.9}$
-  \cite{2008MNRAS.391.1685S,2008Natur.456...73S} and substructure
-  luminosity scaling, $L_\sub \propto M^A$. The total luminosity of
-  substructures scales as
+\C{To motivate the scaling of the substructure luminosity boost with limiting
+  substructure mass in Eqs.~(\ref{eq:Lsub}-\ref{eq:Csub}), we show how it
+  derives from the substructure mass function, $\dd N_\sub/\dd M_\rmn{sub}
+  \propto M_\rmn{sub}^{-1.9}$ \cite{2008MNRAS.391.1685S,2008Natur.456...73S} and
+  substructure luminosity scaling with the limiting mass of satellites, $L_\sub
+  \propto M_\rmn{lim}^A$. The total luminosity of substructures scales as
 \begin{eqnarray}
-  L_\rmn{sub,tot} &=& L_\sub\,N_\sub = L_\sub 
-\int \dd M \frac{\dd N_\sub}{\dd M} \nonumber\\
- &\propto& M^{A-0.9} \propto M^{-0.226}\,,\quad
+  L_\rmn{sub,tot} &\simeq& L_\sub\,N_\sub \simeq L_\sub 
+\int_{M_\rmn{lim}} \dd M_\rmn{sub} \frac{\dd N_\sub}{\dd M_\rmn{sub}} \nonumber\\
+ &\propto& M_\rmn{lim}^{A-0.9} \propto M_\rmn{lim}^{-0.226}\,,\quad
 \rmn{for}\quad A=0.674\,. \nonumber\\
@@
 \end{eqnarray}
-Tidal truncation is responsible in shaping the substructure luminosity
-scaling parameter $A$. Here we only sketch out qualitative arguments
-and leave the details to future work. First, tidal effects truncate
-the subhalo profile primarily in the outer regions. As a result of
-this, the subhalo acquires a steeper logarithmic slope than the
-canonical 3 from the NFW-profile. Second, tidal stripping imposes a
-mass-dependency and should be stronger for smaller substructure. While
-the stripping efficiency (for an effective cross section $\sigma$)
-only depends on the density since the mean free path scales as
-$x_\rmn{mfp} \propto 1/(n_\rmn{dm} \sigma)$, there is less mass at any
-given density for smaller substructures. Hence, modest density
-inhomogeneities in the host halo seen by the orbiting substructures
-cause a stronger mass loss of these smaller satellites. Third, the
-tidal truncation radius should be a function of host halo radius due
-to the increasing smooth density profile for smaller radii.  If we
-pick an effective host halo radius which dominates the luminosity
-contribution of the substructures and were to fit the tidally
-truncated subhalo density profile with an NFW-profile, the resulting
-$\rs$ would be biased toward lower values implying a higher
-concentration compared to an isolated halo. In order to reproduce our
-value of $A$, we would need a concentration mass relation of $c\propto
-M^{-0.14}$.  As expected, this is steeper than the concentration-mass
-relation found for isolated halos on dwarf galaxy scales, $c \propto
-M^{-0.06}$ \cite{2011arXiv1101.2020I}, as well as galaxy and cluster
-scales, $c \propto M^{-0.098}$ \cite{2008MNRAS.391.1940M}.}
+Tidal truncation is responsible in shaping the substructure luminosity scaling
+parameter $A$. Here we only sketch out qualitative arguments and leave details
+and comparison to numerical simulations to future work. First, tidal effects
+truncate the subhalo profile primarily in the outer regions. As a result of
+this, the subhalo acquires a steeper logarithmic slope than the canonical 3 from
+the NFW-profile. Second, tidal stripping imposes a mass-dependency and should be
+stronger for smaller substructure.  The stripping efficiency (for an effective
+cross section $\sigma$) only depends on the ambient DM density of the host halo,
+$n_\rmn{dm}$, which implies a scaling of the mean free path of a subhalo of
+$x_\rmn{mfp} \propto 1/(n_\rmn{dm} \sigma)$. Since there is less mass at any
+given density for smaller substructures, modest density inhomogeneities within
+the host halo seen by the orbiting substructures cause a stronger mass loss of
+these smaller satellites. Third, the tidal truncation radius should be a
+function of host halo radius due to the increasing smooth density profile for
+smaller radii.  If we pick an effective host halo radius which dominates the
+luminosity contribution of the substructures and were to fit the tidally
+truncated subhalo density profile with an NFW-profile, the resulting $\rs$ would
+be biased toward lower values implying a higher concentration compared to an
+isolated halo. In order to reproduce our value of $A$, we would need a
+concentration mass relation of $c\propto M_\rmn{sub}^{-0.14}$ (employing the
+$L(M_{200},c)$ formula derived by reference \cite{2009PhRvL.103r1302P}).  As expected,
+this is steeper than the concentration-mass relation found for isolated halos on
+dwarf galaxy scales, $c \propto M_\rmn{vir}^{-0.06}$ \cite{2011arXiv1101.2020I},
+as well as galaxy and cluster scales, $c \propto M_\rmn{vir}^{-0.098}$
+\cite{2008MNRAS.391.1940M}.}
 
@@
 
+\C{Here, $A_{\rmn{dm}}$ is the particle physics factor and implicitely defined by Equation~\ref{eq:dflux}.}
 The different density profiles have some impact on the luminosity from
@@
 electrons and positrons that IC upscatter background radiation fields
-to high energies. We also consider a four supersymmetric DM models with
+to high energies. We also consider four supersymmetric DM models with
 a high gamma-ray yield in the form of continuum emission and IC
 induced emission. In addition to the annihilating DM, we estimate the
-gamma-ray flux induced by shock accelerated CRs.
+gamma-ray flux induced by shock-accelerated CRs.
 
 \C{We compare the calculated fluxes to gamma-ray upper limits (95\%
-  c.l.) set by Fermi-LAT after 18 months of observations
+  c.l.) set by \Fermi-LAT after 18 months of observations
   \cite{2010ApJ...717L..71A}. In particular, to achieve a more
@@
   spatially extended limits since the gamma-ray flux from our
-  brightest clusters all have an angular extent above 1 degree on the
-  sky when the boost from substructures is included. In fact, current
-  Fermi flux upper limits are not derived for the kind of extended
-  emission that we get with our treatment of substructures, hence the
-  Fermi limits may not be adequate for some of these clusters. This
+  brightest clusters all have an angular extent $>1^\circ$ on the
+  sky when the boost from substructures is included. In fact, published
+  \Fermi  upper limits are not derived for the kind of extended
+  emission that we find with our treatment of substructures, hence these
+  \Fermi limits may not be adequate for some of these clusters. This
   and other recent work highlights that the improved substructure
-  models imply that Fermi limits will have to be re-calculated to
+  models imply that \Fermi limits will have to be re-calculated to
   accommodate for the large source extensions. Note, however, that for
@@
 
- \C{Also note that the flux upper limits that we compare to are in
-   reality a function of spectral indices $\alpha$. However, in the
-   relevant energy range $0.1-100$~GeV these spectral indices are
-   approximately $1.5 < \alpha < 3.0$, where the change in photon flux
-   upper limits is less than 50\%, with the Fermi-LAT being more
-   sensitive to the hard spectrum \cite{2010ApJ...717L..71A}. For
-   simplicity of the analysis in our paper we adopt the upper limits
-   calculated for a spectral index $\alpha=2$.  For consistency we
-   estimate the change in the differential upper limits for each
-   gamma-ray model and energy range using:
+\C{The flux upper limits, that we compare to, are a function of spectral index
+  $\alpha$. However, in the relevant energy range, $0.1-100$~GeV, the spectral
+  index varies within $1.5 < \alpha < 3.0$. This changes the photon flux upper
+  limits by $<50\%$, with \Fermi-LAT being more sensitive to a hard
+  spectrum \cite{2010ApJ...717L..71A}. For simplicity, we adopt the upper limits
+  calculated for a spectral index $\alpha=2$ and estimate the change in the
+  differential upper limits for each gamma-ray model and energy range using:
 \begin{eqnarray}
@@
 K\,\eg^{1-\alpha}\,,\nonumber\\
-<\eg \,F_\gamma> &=& K\,\frac{\sum \dd \eg^{2-\alpha}}{\sum \dd \eg}
-= K\,\frac{\sum \dd \eg^{2-\alpha}}{E_{\gamma,2}-E_{\gamma,1}}\,,\nonumber\\
+\bra\eg \,F_\gamma\ket &=& K\,
+\frac{\displaystyle\int \dd E\, \eg^{1-\alpha}}{\displaystyle\int \dd \eg}
+= \frac{K}{2-\alpha}\,
+\frac{E_{\gamma,2}^{2-\alpha}-E_{\gamma,1}^{2-\alpha}}{E_{\gamma,2}-E_{\gamma,1}}\,,\nonumber\\
+%\bra\eg \,F_\gamma\ket &=& K\,\frac{\sum \dd \eg^{2-\alpha}}{\sum \dd \eg}
+%= K\,\frac{\sum \dd \eg^{2-\alpha}}{E_{\gamma,2}-E_{\gamma,1}}\,,\nonumber\\
 \label{eq:spec_ind_UL}
@@
 $(2.20,\,1.22,\,2.24)$, respectively. See
-Tab.~\ref{tab:spectral_index} for additional spectral indices.}
+Table~\ref{tab:spectral_index} for additional spectral indices.}
 
@@
 models and contrast it to the emission induced by CRs. Comparing this
-emission to the differential gamma-ray upper limits set by Fermi-LAT
+emission to the differential gamma-ray upper limits set by \Fermi-LAT
 \del{after 18 months of observations \cite{2010ApJ...717L..71A}}, we
@@
 models (shown in the left panels) \C{are about an order of magnitude
-  below the upper limits, making it hard for Fermi to probe these kind
+  below the upper limits, making it hard for \Fermi to probe these kind
   of DM models without a significant improvement in the analysis from
@@
   a factor of 730 while the IC upscattered SD photons are only boosted
-  by 20. Extended upper limits from Fermi-LAT after 18 months \protect
+  by 20. Extended upper limits ($<1^\circ$) from \Fermi-LAT after 18 months \protect
   \cite{2010ApJ...717L..71A} are also shown. \C{We find it hard to
@@
 positrons is more centrally peaked, and the relative importance of the
-IC upscattered SD increases by a factor $\sim 30$ \footnote{\C{Note
-    that for the leptophilic DM model this increase is much smaller
-    since Sommerfeld enhancement is no longer dominated by the low
-    velocity DM particles living in the subhalos (see
-    Sect.~\ref{sect:LP} for more details.}}.  A larger fraction of
-electrons (in the core) will now also cool by Compton-upscattering SD
-photons which suppresses the IC-upscattered CMB light.  For
-comparison, we include the contribution of IC upscattered SD photons
-and to bracket the uncertainty in the SD model, with a smaller amount
-of dust. In this low-dust model, we have reduced the energy in dust by
-a factor 10. However, the resulting flux from the IC upscattered dust
-in this model only decreases with a factor that is slightly smaller
-than 10 since the IC cooling of the electrons and positrons also
-decreases.
+IC upscattered SD increases by a factor $\sim 30$ (see
+Fig.~\ref{fig:IR_comp})\footnote{\C{Note that for the leptophilic DM
+    model this increase is much smaller since Sommerfeld enhancement
+    is no longer dominated by the low velocity DM particles living in
+    the subhalos (see Sect.~\ref{sect:LP} for more details).}}.  A
+larger fraction of electrons (in the core) will now also cool by
+Compton-upscattering SD photons which suppresses the IC-upscattered
+CMB light.  For comparison, we include the contribution of IC
+upscattered SD photons and to bracket the uncertainty in the SD model,
+with a smaller amount of dust. In this low-dust model, we have reduced
+the energy in dust by a factor 10. However, the resulting flux from
+the IC upscattered dust in this model only decreases with a factor
+that is slightly smaller than 10 since the IC cooling of the electrons
+and positrons also decreases.
 
@@
 10^5$), we overproduce the upper gamma-ray limit in the $1-10$~GeV
-energy interval set by Fermi-LAT by about a factor 50. This strongly
+energy interval set by \Fermi-LAT by about a factor 50. This strongly
 constrains the boost from both substructures and the
@@
   flux. The black arrow shows the spatially extended differential
-  upper limit from Fermi \protect \cite{2010ApJ...717L..71A}
+  upper limit from \Fermi \protect \cite{2010ApJ...717L..71A}
   indicating that the LP model assumptions such as Sommerfeld and/or
@@
     cluster, the enhancement due to substructures from IC upscattered
-    CMB and SD photons is 730. The Sommerfeld boost is 530.}}
+    CMB and SD photons is 730. The saturated Sommerfeld boost is 530.}}
  \label{fig:IR_comp}
@@
 our different gamma-ray models and compare it to the unresolved
-integrated flux upper limit on Fornax set by Fermi-LAT where they
+integrated flux upper limit on Fornax set by \Fermi-LAT where they
 averaged the flux over the energy range $0.2-100\,\gev$ assuming a
 spectral index of 2. Again, the annihilation flux in the LP model is
-in conflict with the upper limits by Fermi-LAT, although only by a
+in conflict with the upper limits by \Fermi-LAT, although only by a
 factor of 10 which is about a order magnitude less constraining than
@@
 predicted emission from the CRs in the $1-100$~GeV energy
-regime. \C{Hence, for an experiment with a high sensitivity even for
+regime. \C{Hence, for an experiment with a high sensitivity even
   for extended sources, the prospects for detecting the $\Kp$ BM model
@@
    arrow shows the spatially extended integrated flux upper limit set
-   by Fermi-LAT again indicating challenges for the assumptions
+   by \Fermi-LAT again indicating challenges for the assumptions
    underlying the LP model. We also show projected CTA point source
@@
 massive merging Coma cluster. We find high DM induced gamma-ray fluxes
-from the Fornax and Virgo clusters, which highlight them as promising
+from the Fornax and Virgo clusters, which confirms them as promising
 targets for indirect DM searches. \C{Especially in the $1-10$~GeV
   energy range it is quite striking how constraining the upper limits
-  are for some of the clusters. At these energies, Fermi-LAT has its
+  are for some of the clusters. At these energies, \Fermi-LAT has its
   peak sensitivity due to a combination of increasing effective area
@@
   and do not gain much from the increased sensitivity. In addition,
-  the angular radius of Virgo is about 6 degrees, while the extended
-  upper limit from Fermi-LAT is calculated assuming a $\sigma=1.2$
-  degree radius. In fact, the ratio of the virial radius to the
-  assumed extension for the upper limits $\rvir/\sigma$ for $($Fornax,
-  Coma, Virgo$)$ are $(2.8,\,1.6,\,5.3)$, respectively. Similarly, it
-  is interesting to compare the radius that contain 68\% of the flux
-  to the assumed extension, $r_{68}/\sigma$, which is given by
-  $(1.7,\,1.0,\,3.3)$ for $($Fornax,Coma,Virgo$)$, respectively. This
-  further motivates a re-calculation of the Fermi upper limits to
-  account for the full extension of the galaxy clusters.}  \del{Note,
-  however, that we have used spatially unresolved upper limits, which
-  is quite optimistic for the Virgo cluster which has an angular
-  extended of 7 degrees. It is quite striking how constraining the
-  upper limits are for the Fornax cluster are compared to the other
-  clusters, especially in the $1-10$~GeV energy regime.}  \C{We also
-  find that the high CR-induced flux in Coma and Perseus is making it
-  difficult for indirect DM searches in those clusters if the boost
-  factors are much lower than assumed in this work.} \del{is of the
-  same magnitude as the DM flux from LP models, making it difficult
-  for indirect DM searches in those clusters.} Conversely, the Fornax
-cluster is a great target for indirect DM studies because the relative
-low gamma-ray flux from CRs, absents of an active AGN, and high DM
-gamma-ray flux. \del{The Fermi-LAT three-year data will be able to
-  constrain the smallest mass of substructures using the DM BM
-  models.}
+  the angular radius of Virgo is about $6^\circ$, while the extended
+  upper limit from \Fermi-LAT is calculated assuming a
+  $\sigma=1.2^\circ$ radius. In fact, the ratio of the virial radius
+  to the assumed extension for the upper limits $\rvir/\sigma$ for
+  $($Fornax, Coma, Virgo$)$ are $(2.8,\,1.6,\,5.3)$,
+  respectively. Similarly, it is interesting to compare the radius
+  that contains 68\% of the flux to the assumed extension,
+  $r_{68}/\sigma$, which is given by $(1.7,\,1.0,\,3.3)$ for
+  $($Fornax, Coma, Virgo$)$, respectively. This further motivates a
+  re-calculation of the \Fermi upper limits to account for the full
+  extension of the galaxy clusters.}  \del{Note, however, that we have
+  used spatially unresolved upper limits, which is quite optimistic
+  for the Virgo cluster which has an angular extended of $7^\circ$. It
+  is quite striking how constraining the upper limits are for the
+  Fornax cluster are compared to the other clusters, especially in the
+  $1-10$~GeV energy regime.}  \C{We also find that the theoretical
+  expectation of a high CR-induced flux in Coma and Perseus may
+  significantly complicate indirect DM searches in those clusters if
+  the boost factors are much lower than assumed in this work.} \del{is
+  of the same magnitude as the DM flux from LP models, making it
+  difficult for indirect DM searches in those clusters.
+  The Fornax cluster, however,} is a great target for indirect DM
+studies because the relative low gamma-ray flux from CRs, absents of
+an active AGN, and high DM gamma-ray flux. \del{The \Fermi-LAT
+  three-year data will be able to constrain the smallest mass of
+  substructures using the DM BM models.}
 
@@
 \end{eqnarray}
-Hence, increasing the cluster mass by a factor two more than doubles
-the DM luminosity, but increasing the luminosity distance,
-$D_\rmn{lum}$, by a factor two decrease the flux by a factor four. We
-note that the IC from upscattered SD photons scales slightly softer
+We note that the IC from upscattered SD photons scales slightly softer
 with mass, hence gives rise to a larger fraction of gamma-rays in low
@@
 the substructures. However, if only a small fraction of the DM resides
-in the subhalos, the scaling of the LP DM becomes slightly steeper due
+in the subhalos, i.e. the scaling of the LP DM becomes shallower due
 to the mass dependence inferred from the velocity dispersion:
 \begin{eqnarray}
-L_{\gamma,LPnosub} &=& L_{\gamma,\rmn{sm}} \B_\rmn{sfe} 
+L_{\gamma,LP~nosub} &=& L_{\gamma,\rmn{sm}} \B_\rmn{sfe} 
 \propto \frac{\mvir^{0.5}}{D_\rmn{lum}^2},\\
@@
   starlight (blue dashed). The arrows show the spatially extended
-  differential upper limits set by Fermi-LAT in the energy ranges
+  differential upper limits set by \Fermi-LAT in the energy ranges
   $0.2-1$~GeV, $1-10$~GeV, and $10-100$~GeV from left to right. We
@@
   substructures. We find that the lower GeV energy regime is most
-  constraining due to the peak sensitivity of Fermi at these energies
+  constraining due to the peak sensitivity of \Fermi at these energies
   and use this regime to get upper limits on boost factors.}
@@
 
-\C{For consistency we provide in addition the differential spectral
+\C{In the lower panels of Fig.~\ref
+
+For consistency we provide in addition the differential spectral
   indices $\alpha_\gamma=-\frac{\dd \log(\dd F/\dd E)}{\dd \log(E)}$
@@
 the spatially extended differential and integrated gamma-ray flux
-upper limits set by the Fermi-LAT 18 month data for several
+upper limits set by the \Fermi-LAT 18 month data for several
 clusters. We can use these upper limits to constrain the boosts due to
@@
 excess of electrons and positrons observed in the vicinity of Earth by
-PAMELA/Fermi/HESS. In Fig.~\ref{fig:boost_const} we use the estimated
+PAMELA/\Fermi/H.E.S.S. In Fig.~\ref{fig:boost_const} we use the estimated
 flux \C{within $\rvir$ of four bright and maximal constraining
@@
 in order not to overproduce the differential upper limits set by
-Fermi-LAT in the energy range\footnote{We average the LP DM flux in
+\Fermi-LAT in the energy range\footnote{We average the LP DM flux in
   the energy range $1-10$~GeV before we compare it to the upper
@@
   without substantial improvement in the modelling of these extended
-  sources, Fermi-LAT will not be able to rule out LP models in their
+  sources, \Fermi-LAT will not be able to rule out LP models in their
   current form using clusters.} \del{Note that after about six years
-  of observations with Fermi-LAT, we will be able to rule out the LP
+  of observations with \Fermi-LAT, we will be able to rule out the LP
   model assuming a substructure boost with a smallest mass of
@@
    a point spread function of $0.1\deg$. In order not to overproduce
-   the Fermi-LAT differential flux upper limits in the energy interval
+   the \Fermi-LAT differential flux upper limits in the energy interval
    $1-10$~GeV the boost from substructures and Sommerfeld enhancement
@@
      about 8 and 13, respectively, which would be too small to support
-     the DM annihilation hypothesis for the PAMELA/Fermi excess.}}
+     the DM annihilation hypothesis for the PAMELA/\Fermi excess.}}
  \label{fig:boost_const}
@@
 continuum emission. These high energies are observationally important
-for both Fermi-LAT and Cherenkov telescopes. In
+for both \Fermi-LAT and Cherenkov telescopes. In
 Fig.~\ref{fig:SB_IACTs}, we thus show the surface brightness above
@@
   $\psf=0.1\deg$ that is typical for Cherenkov
-  telescopes as well as the Fermi-LAT at this energy. Left panel shows
+  telescopes as well as the \Fermi-LAT at this energy. Left panel shows
   the Fornax cluster and right panel the Virgo cluster. The gamma-ray
@@
 X-ray flux-complete sample in the local universe. We confront these
-predictions to upper limits obtained by Fermi 1.5-year data and
+predictions to upper limits obtained by \Fermi 1.5-year data and
 conclude on the viability of the underlying models and perspectives
-for the next years of Fermi observations.
+for the next years of \Fermi observations.
 
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.DM.eps}
-  \caption{\it Fermi gamma-ray flux upper limits are contrasted to the
+  \caption{\it \Fermi gamma-ray flux upper limits are contrasted to the
     predicted DM gamma-ray flux. We show the mean differential flux in
     the energy range $E_\gamma=1-10$~GeV for 32 clusters. The
-    \C{maximal extended Fermi-LAT upper limits are shown with black
+    \C{maximal extended \Fermi-LAT upper limits are shown with black
       arrows, while the point source limits are shown in grey.} The
@@
    function of HIFLUGCS cluster ID. For comparison we show the
-   estimated point source sensitivity of the Fermi-LAT after two years
+   estimated point source sensitivity of the \Fermi-LAT after two years
    of data taking $F_\gamma(>100\,\rmn{MeV})\sim
@@
 
-Figure~\ref{fig14} compares Fermi upper limits on the gamma-ray flux
+Figure~\ref{fig14} compares \Fermi upper limits on the gamma-ray flux
 with predictions of DM annihilation fluxes in the LP and BM models.
@@
 models we additionally assume a cluster-mass dependent boost due to
-SFE. Fermi limits rule out the LP models in their present form with
+SFE. \Fermi limits rule out the LP models in their present form with
 the mentioned assumptions in 26 clusters, and limit the boost from SFE
@@
 Sommerfeld boost in the MW to less than 8 (see
-Fig.~\ref{fig:boost_const}).  The flux level of the Fermi limits are
+Fig.~\ref{fig:boost_const}).  The flux level of the \Fermi limits are
 an indirect measure of the ambient background flux in the gamma-ray
@@
 immediate vicinity of the cluster position. Hence, the ratio of the
-Fermi upper limits to the predicted annihilation fluxes,
+\Fermi upper limits to the predicted annihilation fluxes,
 $F_{\mathrm{UL}}/F_{\mathrm{DM}}$, is a good indication of the best
@@
 M49, Norma, Coma, and Virgo to be prime candidates. Note however, that
-Virgo extends of 12 degree over the sky which implies a lower surface
-brightness and lower signal-to-noise.  Fermi limits on individual
+Virgo extends of $12^\circ$ over the sky which implies a lower surface
+brightness and lower signal-to-noise.  \Fermi limits on individual
 clusters are expected to improve as $\sqrt{T/1.5 \mathrm{yr}}$, where
-$T$ is the total elapsed time of the Fermi mission. We emphasize that
+$T$ is the total elapsed time of the \Fermi mission. We emphasize that
 the very inhomogeneous distribution of $F_{\mathrm{UL}}/
@@
 that is scaled down by the ratio of cluster radius to angular
-resolution of 0.1 degree assuming current background subtraction
+resolution of $0.1^\circ$ assuming current background subtraction
 techniques of Cherenkov telescopes. This important finding should
@@
     emission using an analytical CR model \protect
-    \cite{2010MNRAS.409..449P} to Fermi-LAT flux upper limits. We show
+    \cite{2010MNRAS.409..449P} to \Fermi-LAT flux upper limits. We show
     the mean differential flux in the energy range $E_\gamma=1-10$~GeV
-    for 32 clusters. \C{The extended Fermi upper limits assume King
+    for 32 clusters. \C{The extended \Fermi upper limits assume King
       profiles and are shown with black arrows, while the point source
@@
     in perfect agreement with the derived upper limits from
-    Fermi. Interestingly, the limits of Virgo, Norma, and Coma are
+    \Fermi. Interestingly, the limits of Virgo, Norma, and Coma are
     closing in on our predictions and will enforce constraints on the
@@
 
-\C{In Fig.~\ref{fig15}, we show the extended Fermi-LAT flux upper
+\C{In Fig.~\ref{fig15}, we show the extended \Fermi-LAT flux upper
   limits that assume King profiles that trace the X-ray emitting gas
@@
 the expected gamma-ray flux---a method used by reference
-\cite{2010ApJ...717L..71A} to compare to Fermi limits.  In this
+\cite{2010ApJ...717L..71A} to compare to \Fermi limits.  In this
 analytic model, we employ the fact that CRs accelerated at structure
@@
 effect would also reduce the expected gamma-ray flux by up to a factor
-of five \cite{2011A&A...527A..99E}. We note that the tightest Fermi
+of five \cite{2011A&A...527A..99E}. We note that the tightest \Fermi
 limits are obtained in the 1-10 GeV regime due to the highest
-sensitivity of Fermi-LAT there. While the effective area of LAT
+sensitivity of \Fermi-LAT there. While the effective area of LAT
 increases up to these energies, the typical photon spectra decrease as
 a function of energy: combining those effects selects this energy
-range to be most sensitive.  In this energy band, the Fermi limits
+range to be most sensitive.  In this energy band, the \Fermi limits
 come close to the flux predictions of Virgo, Coma and Norma. Using
-integrated flux limits from Fermi, we arrive at very similar results.
+integrated flux limits from \Fermi, we arrive at very similar results.
 We emphasize that by using our analytic modeling, the slight
-discrepancy of the scaling relation-based prediction with the Fermi
+discrepancy of the scaling relation-based prediction with the \Fermi
 limit on Norma \cite{2010ApJ...717L..71A} is resolved: Norma simply
@@
 through the production of decaying pions, we use gamma-ray upper
-limits from Fermi-LAT to constrain $X_\CR$. In Fig.~\ref{fig:XCR} we
+limits from \Fermi-LAT to constrain $X_\CR$. In Fig.~\ref{fig:XCR} we
 show the volume weighted relative CR pressure for 32 clusters, for
@@
 using a scaled stacking with our model as a prior. In a recent work
-\cite{2010ApJ...717L..71A}, where the 1.5 year Fermi data was used to
+\cite{2010ApJ...717L..71A}, where the 1.5 year \Fermi data was used to
 derive limits on $X_\CR$, they found that the most massive clusters
@@
     P_\rmn{CR} > / < P_\rmn{th}>$ averaged across the cluster. Our
-    constraints are obtained with the extended Fermi-LAT limits in the energy
+    constraints are obtained with the extended \Fermi-LAT limits in the energy
     range $E_\gamma=1-10$~GeV that assume a King profile which matches the
     extension of the thermal X-ray emission (black) and for comparison with
-    Fermi-LAT point-source limits (grey) \cite{2010ApJ...717L..71A}. In
+    \Fermi-LAT point-source limits (grey) \cite{2010ApJ...717L..71A}. In
     computing those limits, we adopted our (conservative) analytic model
@@
   models that have been chosen for the large gamma-ray flux yield with
-  three-year Fermi data (or constrain the substructure boost factor).}
+  three-year \Fermi data (or constrain the substructure boost factor).}
 Other nearby bright sources of the extended HIFLUGCS sample of nearby
 bright X-ray cluster/groups are M49, Centaurus, and NGC~4636.  The
-non-detection of gamma-ray emission by Fermi in a total of 26
+non-detection of gamma-ray emission by \Fermi in a total of 26
 clusters/groups (the mentioned clusters as well as Virgo, Coma, Hydra,
@@
 relation. We note that the predictions of our ``optimistic'' model are
-perfectly in agreement with Fermi upper limits for all clusters.  The
+perfectly in agreement with \Fermi upper limits for all clusters.  The
 hint of a tension that the scaling relation modeling showed for Norma
@@
   spatial extension of the brightest clusters it is not possible for
-  Fermi to rule out the LP model or to constrain the BM DM models
+  \Fermi to rule out the LP model or to constrain the BM DM models
   without improved modelling. However, we can put tight constraints on
@@
   accelerator searches for the nature of DM.}\del{We conclude that it
-  will be possible to rule out the LP model with six years of Fermi
+  will be possible to rule out the LP model with six years of \Fermi
   data and start to constrain some BM DM models. Hence this should
@@
    (5) In units of  $10^{-11} \rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
-   (6) The flux within $0.1$ degree. In addition, we smooth the flux with a point spread function of $0.1$ degree. 
-   (7) The flux within $1.0$ degree. In addition, we smooth the flux with a point spread function of $1.0$ degree. 
+   (6) The flux within $0.1^\circ$, smoothed with a point spread function of $0.1^\circ$. 
+   (7) The flux within $0.1^\circ$, smoothed with a point spread function of $0.1^\circ$. 
  \label{tab:flux_tab_CRs}
@@
    (5) In units of  $10^{-11} \rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
-   (6) The flux within $0.1$ degree. In addition, we smooth the flux with a point spread function of $0.1$ degree. 
-   (7) The flux within $1.0$ degree. In addition, we smooth the flux with a point spread function of $1.0$ degree. 
+   (6) The flux within $0.1^\circ$, smoothed with a point spread function of $0.1^\circ$. 
+   (7) The flux within $0.1^\circ$, smoothed with a point spread function of $0.1^\circ$. 
   \label{tab:flux_tab_BM}
@@
    (5) In units of  $10^{-9} \rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
-   (6) The flux within $0.1$ degree that have in addition been smoothed over with a point spread function of $0.1$ degree. 
-   (7) The flux within $1.0$ degree that have in addition been smoothed over with a point spread function of $1.0$ degree. 
+   (6) The flux within $0.1^\circ$, smoothed with a point spread function of $0.1^\circ$. 
+   (7) The flux within $0.1^\circ$, smoothed with a point spread function of $0.1^\circ$. 
  \label{tab:flux_tab_LP}
@@
   $\rho_\rmn{gas}=\rho_\rmn{gas}(0)(1+r^2/r_\rmn{c}^2)^{3\beta/2}$
-  where the core radius $r_\rmn{c}$ and the slop of the surface
-  brightness profile $\beta$ are taken from
+  where the core radius, $r_\rmn{c}$, and the slope, $\beta$, are taken from
   \cite{2002ApJ...567..716R}. The central gas density
@@
   continuum and LP-IC-CMB emission. The flux has been
-  boosted by substructures and in addition include the
+  boosted by substructures and includes the
   Sommerfeld enhancement for the LP model. 

### 2011-06-22 paper.tex

@@
 
-\C{Here, $A_{\rmn{dm}}$ is the particle physics factor and implicitely defined by Equation~\ref{eq:dflux}.}
+\C{Here, $A_{\rmn{dm}}$ is the particle physics factor and implicitly defined by Equation~\ref{eq:dflux}.}
 The different density profiles have some impact on the luminosity from
@@
 where the difference is mainly built up at a few percent of
-$\rvir$. The increase in luminosity due to substructures is neglible
+$\rvir$. The increase in luminosity due to substructures is negligible
 in the center of halos, but integrated out to $\rvir$ the boost
@@
 redshift. (2) Synchrotron losses on ambient magnetic fields where we
-parameterize the magnetic field in the galaxy cluster by $B(r) =
+parametrize the magnetic field in the galaxy cluster by $B(r) =
 3\mu\rmn{G} \,[n_{\rm e}(r)/n_{\rm e}(0)]^{\alpha_\B}$. We adopt a
@@
   spatially extended limits since the gamma-ray flux from our
-  brightest clusters all have an angular extent $>1^\circ$ on the
-  sky when the boost from substructures is included. In fact, published
+  brightest clusters all have an angular extent $>1^\circ$ on the sky
+  when the boost from substructures is included. In fact, published
   \Fermi upper limits are not derived for the kind of extended
-  emission that we find with our treatment of substructures, hence these
-  \Fermi limits may not be adequate for some of these clusters. This
-  and other recent work highlights that the improved substructure
-  models imply that \Fermi limits will have to be re-calculated to
-  accommodate for the large source extensions. Note, however, that for
-  most clusters the assumption of a point source is well justified.}
-
-\C{The flux upper limits, that we compare to, are a function of spectral index
-  $\alpha$. However, in the relevant energy range, $0.1-100$~GeV, the spectral
-  index varies within $1.5 < \alpha < 3.0$. This changes the photon flux upper
-  limits by $<50\%$, with \Fermi-LAT being more sensitive to a hard
-  spectrum \cite{2010ApJ...717L..71A}. For simplicity, we adopt the upper limits
+  emission that we find with our treatment of substructures, hence
+  these \Fermi limits may not be adequate for some of these
+  clusters. This and other recent work highlights that the improved
+  substructure models imply that \Fermi limits will have to be
+  re-calculated to accommodate for the large source extensions. Note,
+  however, that for most clusters the assumption of a point source is
+  well justified.  The flux upper limits, that we compare to, are a
+  function of spectral index $\alpha$. However, in the relevant energy
+  range, $0.1-100$~GeV, the spectral index varies within $1.5 < \alpha
+  < 3.0$. This changes the photon flux upper limits by $<50\%$, with
+  \Fermi-LAT being more sensitive to a hard spectrum
+  \cite{2010ApJ...717L..71A}.}
+
+\del{For simplicity, we adopt the upper limits
   calculated for a spectral index $\alpha=2$ and estimate the change in the
@@
   differential upper limits set by \Fermi-LAT in the energy ranges
-  $0.2-1$~GeV, $1-10$~GeV, and $10-100$~GeV from left to right. We
-  show the individual components for the BM model and LP model for
-  Virgo and Perseus, respectively. \C{In the lower panel of each
-    figure we show differential spectral indices, $\alpha_\gamma$,
-    where $\dd F_\gamma/\dd E_\gamma \sim E_\gamma^{-\alpha_\gamma}$.}
-  The flux from the clusters is integrated out to $\rvir$ using a
-  point spread function of $0.1\deg$ and includes the boost from
-  substructures. We find that the lower GeV energy regime is most
-  constraining due to the peak sensitivity of \Fermi at these energies
-  and use this regime to get upper limits on boost factors.}
+  $0.2-1$~GeV, $1-10$~GeV, and $10-100$~GeV from left to right
+  \C{(using Gau{\ss} profiles for the source extension with
+    $\sigma=\{1.2,1.0,0.8\}$ for \{Virgo, Coma, Fornax\} and an
+    X-ray-inferred King profile for Perseus)
+    \cite{2010ApJ...717L..71A}}. We show the individual components for
+  the BM model and LP model for Virgo and Perseus, respectively. \C{In
+    the lower panel of each figure we show differential spectral
+    indices, $\alpha_\gamma$, where $\dd F_\gamma/\dd E_\gamma \sim
+    E_\gamma^{-\alpha_\gamma}$.}  The flux from the clusters is
+  integrated out to $\rvir$ using a point spread function of $0.1\deg$
+  and includes the boost from substructures. We find that the lower
+  GeV energy regime is most constraining due to the peak sensitivity
+  of \Fermi at these energies and use this regime to get upper limits
+  on boost factors.}
  \label{fig:clu_comp}
@@
 
-\C{In the lower panels of Fig.~\ref
-
-For consistency we provide in addition the differential spectral
-  indices $\alpha_\gamma=-\frac{\dd \log(\dd F/\dd E)}{\dd \log(E)}$
-  for the different emission models in the lower panels of
-  Fig.~\ref{fig:clu_comp}. We find very similar spectral indices for
-  different clusters when the boost from substructures is substantial,
-  while for models without substructures the relative contribution
-  from the upscattered dust and starlight breaks the spectral
-  universality for the DM models. In the $1~\gev-1~\tev$ energy regime
-  the CR spectral index is approximately constant $\sim (2.1-2.3)$,
-  while the spectral index for the LP model has a large spread and
-  varies between $1.2-4.0$, hence implying that gamma-ray upper limits
-  are more sensitive to the specific energy regime for these
-  models. Similarly, the index for the BM $\Kp$ model is about 1.0 at
-  1~GeV and increases monotonically for higher energies, which also
-  suggests that the flux upper limits contrasted to this model are
-  sensitive to the specific energy range, and where a small energy
-  range would be preferred. In experiments is the spectral index often
-  fixed over an energy range, hence we show in
-  Tab.~\ref{tab:spectral_index} the indices for our emission models in
-  four different energy bands. We find that these spectral indices
-  have a much smaller spread, hence reducing the importance of the
-  specific energy regimes. For further discussion about the impact of
-  different spectral indices on the gamma-ray upper limits see
+\C{In the lower panels of Fig.~\ref{fig:clu_comp}, we also provide the
+  differential spectral index, $\alpha_\gamma=-\dd \log(\dd F/\dd
+  E)/\dd \log(E)$, for the different emission models. We find very
+  similar spectral indices for different clusters assuming a
+  substantial boost from substructures, while for models without
+  substructures the relative contribution from the upscattered dust
+  and starlight breaks the spectral universality for the DM models. In
+  the $1~\gev-1~\tev$ energy regime the CR spectral index is
+  approximately constant $\sim (2.1-2.3)$, while the spectral index
+  for the LP model varies substantially between $1.2-4.0$, hence
+  implying that gamma-ray upper limits are more sensitive to the
+  specific energy regime for these models. Similarly, the index for
+  the BM $\Kp$ model is about 1.0 at 1~GeV and increases monotonically
+  toward higher energies. To maximize photon count statistics,
+  experiments calculate band-integrated fluxes which implies a fixed
+  spectral index over that energy range. Hence, we show $\alpha_\gamma$ in
+  Table~\ref{tab:spectral_index} for our emission models in four
+  different energy bands. We find smaller variations for the banded
+  $\alpha_\gamma$-values, hence reducing the importance of the specific
+  energy regimes.}
+
+\del{ For further discussion about the impact of different
+  spectral indices on the gamma-ray upper limits see
   Eq.~(\ref{sect:spectral}) and related text.}
@@
 \end{tabular}
- \caption{\C{Gamma-ray spectral indices $\alpha_{E_1}^{E_2}$ between
+\caption{\C{Banded gamma-ray spectral index $\alpha_{E_1}^{E_2}$ between
     energies $E_1$ and $E_2$. We show the spectral index for three
@@
     includes continuum emission, and IC upscattered CMB, dust and
-     starlight. The indices are derived for the Fornax cluster,
-     although the variance between clusters is very small when the
-     enhancement from substructures is included which suppresses the
+    starlight. $\alpha_\gamma$-values are derived for the Fornax cluster,
+    although the variance between clusters is very small when we account for the
+    enhancement from substructures. This  suppresses the
     relative contribution from the upscattered dust and starlight
-     component that is cluster dependent. \label{tab:spectral_index}}}
+    component that depends on  cluster mass. \label{tab:spectral_index}}}
 \end{table}
@@
 especially interesting to constrain the SFE, where a boost of the
-particle physics cross section of 300 is required to explain the
+particle physics cross section of $\sim$300 is required to explain the
 excess of electrons and positrons observed in the vicinity of Earth by
@@
   limits.}  $1-10$~GeV, we can constrain the smallest mass of
-substructures to $M_\rmn{lim}\gtrsim 10\,\msun$. Instead assuming the
+substructures to $M_\rmn{lim}\gtrsim 10\,\msun$. Instead, assuming the
 standard mass of the smallest substructures of $M_\rmn{lim}\approx
@@
    \C{enhancement with and without substructures is 130 and 530
-     respectively, where in addition the boost due to substructures is
+     respectively. The boost due to substructures is
      about 730.} Notice the nearly flat profiles when substructures
@@
   \includegraphics[width=0.99\columnwidth]{figures/MLscaling.10G.eps}
-  \caption{\it Scaling relations of the cluster's virial mass $\mvir$
-    and the gamma-ray luminosity for energies $E_\gamma>100$~MeV
-    (left) and $E_\gamma>10$~GeV (right).  Shown are the relations for
-    the CR-induced emission that is dominated by pion decay resulting
-    from hadronic CR interactions (solid), the leptophilic model of DM
-    annihilations \C{(dash-dotted) as well as the benchmark model $K'$
-      of DM annihilation. Both DM models include the scaling of the
-      substructure boost with cluster mass of
-      Eq.~(\ref{eq:DM_scaling}) (dashed). Note that the scaling of the
-      DM models are indicative for all (non-Sommerfeld enhanced)
-      DM annihilation models while the normalization depends on the
-      particular cross section and neutralino mass.}}
+  \caption{\it Scaling relations of the cluster's virial mass $\mvir$ and the
+    gamma-ray luminosity for energies $E_\gamma>100$~MeV (left) and
+    $E_\gamma>10$~GeV (right).  Shown are the relations for the CR-induced
+    emission that is dominated by pion decay resulting from hadronic CR
+    interactions (solid), the leptophilic model of DM annihilations
+    \C{(dash-dotted) as well as the benchmark model $K'$ of DM
+      annihilation. Both DM models include the scaling of the substructure boost
+      with cluster mass of Eq.~(\ref{eq:DM_scaling}) (dashed). Note that the
+      scaling of the DM models are indicative for all DM annihilation models (as
+      long as there is no additional mass scaling from, e.g., non-saturated SFE
+      models) while the normalization depends on the particular cross section
+      and neutralino mass.}}
 \label{fig:lum_mass_scaling}
@@
 \end{eqnarray}
-Note that the CR luminosity scaling relations\footnote{The scaling
-  relations show the flux inside $\rvir$ and do not include the
-  contribution from galaxies. Also note that in this paper the scaling
-  relations are normalized with $10^{15}/h_{70}\,\msun$. \C{In
-    contrast, is the corresponding scaling relations in Table 5 in
-    \cite{2010MNRAS.409..449P} normalized with $10^{15}/h\,\msun$
-    instead of the mentioned $10^{15}/h_{70}\,\msun$. However, all
-    figures/tables/equations including the scaling relation figures
-    are derived for masses in units of $10^{15}/h_{70}\,\msun$.}}
-include the IC gamma-ray contribution from shock-accelerated electrons
-as well as secondary electrons created in CR-proton interactions. The
-gamma-ray flux from the electrons is, however, dominated by the
-decaying neutral pions and only show up as a small flattening of the
-scaling relation at energies around $10-100\,\gev$. The steeper mass
-scaling of CR emission compared to DM annihilation already implies a
-general strategy to minimize the CR-induced foreground for DM
-annihilation and argues for very nearby groups. We note that these
-simulations do not include AGN feedback that is thought to furthermore
+Note that the CR luminosity scaling relations\footnote{The scaling relations
+  show the flux inside $\rvir$ and do not include the contribution from
+  galaxies. Also note that in this paper the scaling relations are normalized at
+  $10^{15}\,h_{70}^{-1}\,\msun$. \C{In contrast, the corresponding scaling
+    relations in Table 5 in \cite{2010MNRAS.409..449P} are normalized at
+    $10^{15}\,h^{-1}\,\msun$ instead of the mentioned
+    $10^{15}\,h_{70}^{-1}\,\msun$ in the caption. However, all
+    figures/tables/equations including the scaling relation figures are derived
+    for masses in units of $10^{15}\,h_{70}^{-1}\,\msun$.}}  include the IC
+gamma-ray contribution from shock-accelerated electrons as well as secondary
+electrons created in CR-proton interactions. The gamma-ray flux from the
+electrons is, however, dominated by the decaying neutral pions and only shows up
+as a small flattening of the scaling relation at energies around
+$10-100\,\gev$. The steeper mass scaling of CR emission compared to DM
+annihilation already implies a general strategy to minimize the CR-induced
+foreground for DM annihilation and argues for very nearby groups. We note that
+these simulations do not include AGN feedback that is thought to furthermore
 reduce the baryon fraction in groups relative to that in clusters
-\cite{2008ApJ...687L..53P}. The resulting smaller target density for
-hadronic CR interactions will furthermore steepen the $L_\gamma-M$
-relation of CR induced emission, making the case for groups even
-stronger.
+\cite{2008ApJ...687L..53P}. The resulting smaller target density for hadronic CR
+interactions steepens the $L_\gamma-M$ relation of CR induced emission, making
+the case for groups even stronger.
 
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.DM.eps}
-  \caption{\it \Fermi gamma-ray flux upper limits are contrasted to the
-    predicted DM gamma-ray flux. We show the mean differential flux in
+  \caption{\it \Fermi gamma-ray flux upper limits are contrasted to 
+    predicted DM gamma-ray fluxes. We show the mean differential flux in
     the energy range $E_\gamma=1-10$~GeV for 32 clusters. The
-    \C{maximal extended \Fermi-LAT upper limits are shown with black
+    \C{maximally extended \Fermi-LAT upper limits are shown with black
       arrows, while the point source limits are shown in grey.} The
@@
 
-\C{In Fig.~\ref{fig15}, we show the extended \Fermi-LAT flux upper
-  limits that assume King profiles that trace the X-ray emitting gas
-  compared to the flux predictions by an analytical CR model
-  \cite{2010MNRAS.409..449P} for CR induced gamma-rays.} For
-consistency, we use beta-model fits to ROSAT data of X-ray bright
-clusters for our gamma-ray flux estimates as an input
-\cite{2002ApJ...567..716R}). We derive the central gas densities for
-each cluster by following the approach outlined in
-\cite{1999ApJ...517..627M} which assumes that the ICM is
-isothermal. The central gas density is found by combining X-ray
-temperature with X-ray luminosity, X-ray detection radius, density
-core radius and density slope for each cluster. These predictions are
-superior to those that use luminosity-mass scaling relation to infer
-the expected gamma-ray flux---a method used by reference
-\cite{2010ApJ...717L..71A} to compare to \Fermi limits.  In this
-analytic model, we employ the fact that CRs accelerated at structure
-formation shocks and transported over cosmic time. This leads to a CR
-distribution with a universal spectral form and an almost universal
-spatial distribution. Depending on whether or not we account for the
-bias of ``artificial galaxies'' in cosmological simulations, we derive
-an optimistic or conservative limit of the expected gamma-ray emission
-from decaying pions (bracketing our ignorance of the contribution of
-cluster galaxies to the overall gamma-ray flux from a cluster). Note
-that both models assume the maximally allowed acceleration efficiency
-for strong shocks that transfers 50\% of the shock-dissipated energy
-(kinetic energy corrected for adiabatic compressional heating at the
-shock) to CRs. These efficiencies drop quickly for weaker shocks
-\cite{2007A&A...473...41E} which dominate the gravitational energy
+\C{In Fig.~\ref{fig15}, we show flux predictions by an analytical CR model
+  \cite{2010MNRAS.409..449P} for CR induced gamma-rays and compare those to the
+  extended \Fermi-LAT flux upper limits that assume King profiles which trace
+  the X-ray emitting gas.}  For consistency, we use beta-model fits to ROSAT
+data of X-ray bright clusters for our gamma-ray flux estimates as an input
+\cite{2002ApJ...567..716R}). We derive the central gas densities for each
+cluster by following the approach outlined in \cite{1999ApJ...517..627M} which
+assumes that the ICM is isothermal. The central gas density is found by
+combining X-ray temperature with X-ray luminosity, X-ray detection radius,
+density core radius and density slope for each cluster. These predictions are
+superior to those that use luminosity-mass scaling relation to infer the
+expected gamma-ray flux---a method used by reference \cite{2010ApJ...717L..71A}
+to compare to \Fermi limits.  In this analytic model, we employ the fact that
+CRs accelerated at structure formation shocks and transported over cosmic
+time. This leads to a CR distribution with a universal spectral form and an
+almost universal spatial distribution. Depending on whether or not we account
+for the bias of ``artificial galaxies'' in cosmological simulations, we derive
+an optimistic or conservative limit of the expected gamma-ray emission from
+decaying pions (bracketing our ignorance of the contribution of cluster galaxies
+to the overall gamma-ray flux from a cluster). Note that both models assume the
+maximally allowed acceleration efficiency for strong shocks that transfers 50\%
+of the shock-dissipated energy (kinetic energy corrected for adiabatic
+compressional heating at the shock) to CRs. These efficiencies drop quickly for
+weaker shocks \cite{2007A&A...473...41E} which dominate the gravitational energy
 dissipation inside galaxy clusters \cite{2006MNRAS.367..113P}. These
-efficiencies will have to be corrected down if this value is not
-realized at structure formation shocks. Secondly, these simulations
-neglect active CR transport such as streaming and diffusion relative
-to the gas, i.e. we assume that advective transport is the dominant
-one and CRs are tightly coupled to the gas via flux-frozen magnetic
-fields tangled on sufficiently small scales. Evidence from the
-statistics of radio halos suggests that this might not be the case for
-relaxed clusters, arguing that CR streaming in those objects could be
-responsible for a decrease in the central CR number density. This
-effect would also reduce the expected gamma-ray flux by up to a factor
-of five \cite{2011A&A...527A..99E}. We note that the tightest \Fermi
-limits are obtained in the 1-10 GeV regime due to the highest
-sensitivity of \Fermi-LAT there. While the effective area of LAT
-increases up to these energies, the typical photon spectra decrease as
-a function of energy: combining those effects selects this energy
-range to be most sensitive.  In this energy band, the \Fermi limits
-come close to the flux predictions of Virgo, Coma and Norma. Using
-integrated flux limits from \Fermi, we arrive at very similar results.
-We emphasize that by using our analytic modeling, the slight
-discrepancy of the scaling relation-based prediction with the \Fermi
-limit on Norma \cite{2010ApJ...717L..71A} is resolved: Norma simply
-seems to be less bright than an average cluster of the same mass as
-Norma. The insensitive limit on Perseus \C{is due to the bright
-  central source NGC1275 with an AGN in the center
-  \cite{2010ATel.2916....1M} making it hard to determine a comparable
-  limit as obtained for the other clusters. In addition, there are
-  recent gamma-ray observations of the head-tail radio galaxy IC310 in
-  the cluster outskirts
+efficiencies will have to be corrected down if this value is not realized at
+structure formation shocks. Secondly, these simulations neglect active CR
+transport such as streaming and diffusion relative to the gas, i.e. we assume
+that advective transport is the dominant one and CRs are tightly coupled to the
+gas via flux-frozen magnetic fields tangled on sufficiently small
+scales. Evidence from the statistics of radio halos suggests that this might not
+be the case for relaxed clusters, arguing that CR streaming in those objects
+could be responsible for a decrease in the central CR number density. This
+effect would also reduce the expected gamma-ray flux by up to a factor of five
+\cite{2011A&A...527A..99E}. We note that the tightest \Fermi limits are obtained
+in the 1-10 GeV regime due to the highest sensitivity of \Fermi-LAT there. While
+the effective area of LAT increases up to these energies, the typical photon
+spectra decrease as a function of energy: combining those effects selects this
+energy range to be most sensitive.  In this energy band, the \Fermi limits come
+close to the flux predictions of Virgo, Coma and Norma. Using integrated flux
+limits from \Fermi, we arrive at very similar results.  We emphasize that by
+using our analytic modeling, the slight discrepancy of the scaling
+relation-based prediction with the \Fermi limit on Norma
+\cite{2010ApJ...717L..71A} is resolved: Norma simply seems to be less bright
+than an average cluster of the same mass as Norma. The insensitive limit on
+Perseus \C{is due to the bright central source NGC1275 with an AGN in the center
+  \cite{2010ATel.2916....1M} making it hard to determine a comparable limit as
+  obtained for the other clusters. In addition, there are recent gamma-ray
+  observations of the head-tail radio galaxy IC310 in the cluster outskirts
   \cite{2010ApJ...723L.207A,2010A&A...519L...6N}.}
@@
 which is roughly a constant, i.e. almost independent on halo
-mass. This suggests that CRs are acclerated at the strongest shocks,
+mass. This suggests that CRs are accelerated at the strongest shocks,
 in the early universe or between voids and pre-collapsed IGM, and then
 experience a similar transport history in the form of adiabatic
-compression or similarily weaker shocks. Since the CRs that build up
+compression or similarly weaker shocks. Since the CRs that build up
 the bulk of the CR pressure also give rise to gamma-ray emission
@@
   \includegraphics[width=0.99\columnwidth]{figures/XCR.Fermi.eps}
-  \caption{\it Limits on the relative CR pressure, $< X_\rmn{CR}> = <
-    P_\rmn{CR} > / < P_\rmn{th}>$ averaged across the cluster. Our
+  \caption{\it Limits on the relative CR pressure, $\bra X_\rmn{CR}\ket = \bra
+    P_\rmn{CR} \ket / \bra P_\rmn{th}\ket$ averaged across the cluster. Our
     constraints are obtained with the extended \Fermi-LAT limits in the energy
@@
   models that have been chosen for the large gamma-ray flux yield with
-  three-year \Fermi data (or constrain the substructure boost factor).}
-Other nearby bright sources of the extended HIFLUGCS sample of nearby
-bright X-ray cluster/groups are M49, Centaurus, and NGC~4636.  The
-non-detection of gamma-ray emission by \Fermi in a total of 26
-clusters/groups (the mentioned clusters as well as Virgo, Coma, Hydra,
-and Norma among others) considerably constrains LP models for DM
-annihilation which were introduced to explain the increasing
+  three-year \Fermi data (or constrain the substructure boost
+  factor).}  Other nearby bright sources of the extended HIFLUGCS
+sample of nearby bright X-ray cluster/groups are M49, Centaurus, and
+NGC~4636.  The non-detection of gamma-ray emission by \Fermi in a
+total of 26 clusters/groups (the mentioned clusters as well as Virgo,
+Coma, Hydra, and Norma among others) considerably constrains LP models
+for DM annihilation which were introduced to explain the increasing
 positron-to-lepton ratio beyond 10 GeV. \C{Assuming that the minimum
-  DM substructure mass extends down to an Earth mass, we limit the
-  saturated Sommerfeld enhancement factor in M49 and Fornax to about
-  14 and 22, respectively. This corresponds to a value in the Milky
-  Way (MW) of less than 8 and 13 due to the larger Sommerfeld boost
-  factor in smaller mass halos which have a lower velocity dispersion
-  that enhances the particle cross section (while assuming
+  DM substructure mass extends down to an Earth mass and that the DM
+  annihilation flux is dominated by small scale substructure, we limit
+  the saturated Sommerfeld enhancement factor in M49 and Fornax to
+  about 14 and 22, respectively. This corresponds to a value in the
+  Milky Way (MW) of less than 8 and 13, respectively, due to the larger Sommerfeld
+  boost factor in smaller mass halos which have a lower velocity
+  dispersion that enhances the particle cross section (while assuming
   universality of the DM model).} This would rule out LP models in
 their current form based on the non-observation of gamma-rays in any
-  of the fore-mentioned clusters/groups. Alternatively, assuming the
-  LP models to be correct, we limit the minimum substructure mass to
+of the fore-mentioned clusters/groups. Alternatively, assuming the LP
+models to be correct, we limit the minimum substructure mass to
 $>10~\msun$ in M49.
@@
 analytic model for the spatial and spectral distribution of dust and
-starlight in clusters which can be used for the annihilation emission
-in galaxies with a different spatial profile.  We find that in BM
-models, the continuum emission dominates over the IC emission of any
-available radiation field. In the LP models, where the continuum
-emission is low, the IC up-scattering of the CMB dominates below 60
-GeV. \C{The final state radiation then takes over for energies up to
-  the cutoff at $m_\chi c^2 \sim 1$~TeV. The IC up-scattering of the
-  dust and starlight is always subdominant compared to the upscattered
-  CMB (below 60~GeV) and the final state radiation (above 60~GeV).}
-\del{For large clusters, the final state radiation then takes over for
-  energies up to the cutoff at $m_\chi c^2 \sim 1$~TeV. In small
-  clusters, there is a window around $E_\gamma \sim 100~\mathrm{GeV}$
-  where the IC up-scattering of the dust emission dominates over the
-  CMB IC emission and the final state radiation. The IC emission of
-  starlight remains always subdominant.}  We stress, that the
-inclusion of the dust and starlight radiation fields are negligible in
-the cooling function for the leptons.  The main reason why the IC
-emission from starlight and dust remains subdominant is the small
-overlap of this component with the peripherally peaked substructure
-mass density profiles. If for some reason, DM has less substructure,
-the relative importance of this IC component increases considerably.
+starlight in clusters (which can also be used for the annihilation
+emission in galaxies after adopting a different spatial profile).  We
+find that in BM models, the continuum emission dominates over the IC
+emission of any available radiation field. In the LP models, where the
+continuum emission is low, the IC up-scattering of the CMB dominates
+below 60 GeV. \C{For larger energies, the final state radiation
+  dominates the emission up to the cutoff at $m_\chi c^2 \sim
+  1$~TeV. The IC up-scattering of the dust and starlight is always
+  subdominant compared to the upscattered CMB (below 60~GeV) and the
+  final state radiation (above 60~GeV).}  \del{For large clusters, the
+  final state radiation then takes over for energies up to the cutoff
+  at $m_\chi c^2 \sim 1$~TeV. In small clusters, there is a window
+  around $E_\gamma \sim 100~\mathrm{GeV}$ where the IC up-scattering
+  of the dust emission dominates over the CMB IC emission and the
+  final state radiation. The IC emission of starlight remains always
+  subdominant.}  We stress, that the inclusion of the dust and
+starlight radiation fields are negligible in the cooling function for
+the leptons.  The main reason why the IC emission from starlight and
+dust remains subdominant is the small overlap of this component with
+the peripherally peaked substructure mass density profiles. If for
+some reason, DM has less substructure, the relative importance of this
+IC component increases considerably.
 
@@
   the boost from substructures and Sommerfeld enhancement using the LP
-  model. Hence, clusters are a nice complement to direct and
+  model. Hence, clusters are a valuable complement to direct and
   accelerator searches for the nature of DM.}\del{We conclude that it
@@
 Stefano Profumo, Tesla Jeltema and Fabio Zandanel for helpful
-discussions.  In addition we thank Neal Weiner and Tracy Slatyer for
-many comments and suggestions for improvements of a previous version
-of this paper. A.P. acknowledges NSF grant AST 0908480 for support. We
-would furthermore like to thank KITP for their hospitality during the
-galaxy cluster workshop.  This research was supported in part by the
-National Science Foundation under Grant No. NSF PHY05-51164.
-C.P. gratefully acknowledges financial support of the Klaus Tschira
-Foundation. The work of L.B. was supported by the Swedish Research
-Council (VR), under contracts no. 621-2009-3915 and 349-2007-8709 (the
-Oskar Klein Centre).
+discussions.  We express our thanks to Neal Weiner and Tracy Slayter
+for many comments and suggestions that improved an earlier version of
+this manuscript. A.P. acknowledges NSF grant AST 0908480 for
+support. We would furthermore like to thank KITP for their hospitality
+during the galaxy cluster workshop.  This research was supported in
+part by the National Science Foundation under Grant No. NSF
+PHY05-51164.  C.P. gratefully acknowledges financial support of the
+Klaus Tschira Foundation. The work of L.B. was supported by the
+Swedish Research Council (VR), under contracts no. 621-2009-3915 and
+349-2007-8709 (the Oskar Klein Centre).
 

### 2011-06-22 paper.tex
corrections finished

@@
 
-\C{In Fig.~\ref{fig15}, we show flux predictions by an analytical CR model
-  \cite{2010MNRAS.409..449P} for CR induced gamma-rays and compare those to the
-  extended \Fermi-LAT flux upper limits that assume King profiles which trace
-  the X-ray emitting gas.}  For consistency, we use beta-model fits to ROSAT
-data of X-ray bright clusters for our gamma-ray flux estimates as an input
-\cite{2002ApJ...567..716R}). We derive the central gas densities for each
-cluster by following the approach outlined in \cite{1999ApJ...517..627M} which
-assumes that the ICM is isothermal. The central gas density is found by
-combining X-ray temperature with X-ray luminosity, X-ray detection radius,
-density core radius and density slope for each cluster. These predictions are
-superior to those that use luminosity-mass scaling relation to infer the
-expected gamma-ray flux---a method used by reference \cite{2010ApJ...717L..71A}
-to compare to \Fermi limits.  In this analytic model, we employ the fact that
-CRs accelerated at structure formation shocks and transported over cosmic
-time. This leads to a CR distribution with a universal spectral form and an
-almost universal spatial distribution. Depending on whether or not we account
-for the bias of ``artificial galaxies'' in cosmological simulations, we derive
-an optimistic or conservative limit of the expected gamma-ray emission from
-decaying pions (bracketing our ignorance of the contribution of cluster galaxies
-to the overall gamma-ray flux from a cluster). Note that both models assume the
-maximally allowed acceleration efficiency for strong shocks that transfers 50\%
-of the shock-dissipated energy (kinetic energy corrected for adiabatic
-compressional heating at the shock) to CRs. These efficiencies drop quickly for
-weaker shocks \cite{2007A&A...473...41E} which dominate the gravitational energy
-dissipation inside galaxy clusters \cite{2006MNRAS.367..113P}. These
-efficiencies will have to be corrected down if this value is not realized at
-structure formation shocks. Secondly, these simulations neglect active CR
-transport such as streaming and diffusion relative to the gas, i.e. we assume
-that advective transport is the dominant one and CRs are tightly coupled to the
-gas via flux-frozen magnetic fields tangled on sufficiently small
-scales. Evidence from the statistics of radio halos suggests that this might not
-be the case for relaxed clusters, arguing that CR streaming in those objects
-could be responsible for a decrease in the central CR number density. This
-effect would also reduce the expected gamma-ray flux by up to a factor of five
-\cite{2011A&A...527A..99E}. We note that the tightest \Fermi limits are obtained
-in the 1-10 GeV regime due to the highest sensitivity of \Fermi-LAT there. While
-the effective area of LAT increases up to these energies, the typical photon
-spectra decrease as a function of energy: combining those effects selects this
-energy range to be most sensitive.  In this energy band, the \Fermi limits come
-close to the flux predictions of Virgo, Coma and Norma. Using integrated flux
-limits from \Fermi, we arrive at very similar results.  We emphasize that by
-using our analytic modeling, the slight discrepancy of the scaling
-relation-based prediction with the \Fermi limit on Norma
-\cite{2010ApJ...717L..71A} is resolved: Norma simply seems to be less bright
-than an average cluster of the same mass as Norma. The insensitive limit on
-Perseus \C{is due to the bright central source NGC1275 with an AGN in the center
-  \cite{2010ATel.2916....1M} making it hard to determine a comparable limit as
-  obtained for the other clusters. In addition, there are recent gamma-ray
-  observations of the head-tail radio galaxy IC310 in the cluster outskirts
-  \cite{2010ApJ...723L.207A,2010A&A...519L...6N}.}
-
-\C{A quantity that is of great scientific interest is the CR pressure
-  ($P_\CR$) relative to the thermal pressure ($P_\rmn{th}$) as it
-  directly bias galaxy cluster observables and the resulting
-  cosmological constraints, such as the hydrostatic mass bias or the
-  Sunyaev-Zel’dovich signal measured by Planck, South Pole Telescope,
-  or Atacama Cosmology Telescope. In the following we estimate the
-  mass scaling of the relative CR pressure, $X_\CR =
-  P_\CR/P_\rmn{th}$, using the CR formalism outlined in
-  \cite{2007A&A...473...41E,2010MNRAS.409..449P}. We derive the CR
-  pressure from the CR distribution function $f = C\,p^{-\alpha}$,
-  where $C$ is the normalization of each power-law, $p=P/m_\rmn{p} c$
-  is the normalized CR proton momentum, and $\alpha$ is the CR
-  spectral index. The pressure is given by $P_\CR \propto
-  C=\tilde{C} \,\rho_\rmn{gas}$, where $\tilde{C}\propto M^{0.44}$ for
-  clusters with a mass $\mvir\gtrsim 10^{14}\,\msun$
-  \cite{2010MNRAS.409..449P}. We determine the mass scaling of the gas
-  density through its relation to the enclosed gas fraction
-  $f_\rmn{gas}$, and find that $\rho_\rmn{gas}\propto f_\rmn{gas}
-  \propto M^{0.135}$ \cite{2009ApJ...693.1142S}. The thermal pressure
-  is derived from the temperature in virial equilibrium, and scales as
-  $P_\rmn{th}\propto k_\B T \propto G M/R \propto M^{0.67}$. Finally
-  we can derive the mass scaling of the volume weighted relative CR
-  pressure from
-\begin{equation}
- <X_\CR> = \frac{<P_\CR>}{<P_\rmn{th}>} \propto \frac{<\rho_\rmn{gas}\,
-   \tilde{C}>}{<k_\B T>} \propto M^{-0.1}\,,
-\end{equation}
-which is roughly a constant, i.e. almost independent on halo
-mass. This suggests that CRs are accelerated at the strongest shocks,
-in the early universe or between voids and pre-collapsed IGM, and then
-experience a similar transport history in the form of adiabatic
-compression or similarly weaker shocks. Since the CRs that build up
-the bulk of the CR pressure also give rise to gamma-ray emission
-through the production of decaying pions, we use gamma-ray upper
-limits from \Fermi-LAT to constrain $X_\CR$. In Fig.~\ref{fig:XCR} we
-show the volume weighted relative CR pressure for 32 clusters, for
-which LAT upper limits that assume King profiles are derived. We adopt
-a constant $<X_\CR>\approx 0.02$ derived from a representative
-simulated cluster \cite{2008MNRAS.385.1211P} and find that for most of
-the clusters in the sample we can constrain $X_\CR < (0.1-0.2)$ using
-the extended gamma-ray upper limits, where the most constraining
-clusters are Norma and Coma with $X_\CR < 0.07$. Most of the 32
-clusters have $X_\CR$ upper limits within a factor few from the best
-constraining clusters, which suggests that stacking of clusters will
-be able to improve these limits. This might even be improved further
-using a scaled stacking with our model as a prior. In a recent work
-\cite{2010ApJ...717L..71A}, where the 1.5 year \Fermi data was used to
-derive limits on $X_\CR$, they found that the most massive clusters
-are on average more constraining, while we find better limits on the
-low mass clusters. This difference is explained by the different
-priors on $P_\CR$; they assumed a mass independent CR pressure derived
-from a single CR power-law distribution function, while we adopt a
-prior inferred from cosmological simulations that dynamically trace the
-CRs during cluster assembly and allow for a varying spectral index
-where $P_\CR\sim M^{0.44}$. Furthermore, the gamma-ray flux
-predictions that we use in this work to constrain $X_\CR$ assumes the
-true gas density distribution for each cluster \footnote{Derived from
-  the parameters in the extended HIFLUGCS catalogue.} that accounts
-for cluster-to-cluster scatter, in contrast to the mass-to-luminosity
-scaling relations that was used in previous work.}
-
 \begin{figure*}
@@
 \end{figure*}
-
-To complete this section, we present our analytical model predictions
-for the CR-induced gamma-ray flux for all clusters in the extended
-HIFLUGCS sample in Fig.~\ref{fig19}. In the lower panel of this
-figure, we show the relative difference between the gamma-ray flux
-computed using the analytical CR model to the flux predicted by the
-mass-luminosity scaling relation. Statistically, one can view the
-analytical modeling as explicitly accounting for the scatter of the expected
-gamma-ray flux at a given mass. Cool core clusters have a denser core
-which increases the target density of gas protons for the hadronic
-reaction which in turn leads to a systematic increase of the expected
-gamma-ray fluxes. We confirm this effect since all clusters with
-increased flux ratio of our analytical CR model relative to the scaling relation
-expectation are in fact cool core clusters. This suggests that the X-ray
-emission should be a good proxy for the expected gamma-ray
-emission. Note however that there could be the counter-acting effect
-of CR streaming in relaxed clusters which would tend to decrease the
-gamma-ray luminosity \cite{2011A&A...527A..99E}. Future careful
-modelling is needed to quantify this effect.
 
@@
 
+\C{Figure~\ref{fig15} shows flux predictions by an analytical CR model
+  \cite{2010MNRAS.409..449P} for CR induced gamma-rays and compare those to the
+  extended \Fermi-LAT flux upper limits that assume King profiles which trace
+  the X-ray emitting gas.}  For consistency, we use beta-model fits to ROSAT
+data of X-ray bright clusters for our gamma-ray flux estimates as an input
+\cite{2002ApJ...567..716R}). We derive the central gas densities for each
+cluster by following the approach outlined in \cite{1999ApJ...517..627M} which
+assumes that the ICM is isothermal. The central gas density is found by
+combining X-ray temperature with X-ray luminosity, X-ray detection radius,
+density core radius and density slope for each cluster. These predictions are
+superior to those that use luminosity-mass scaling relation to infer the
+expected gamma-ray flux---a method used by reference \cite{2010ApJ...717L..71A}
+to compare to \Fermi limits.  In this CR analytic model, we model
+CR-acceleration at structure formation shocks and their transport over cosmic
+time. This leads to a CR distribution with a universal spectral form and an
+almost universal spatial distribution. Depending on whether or not we account
+for the bias of ``artificial galaxies'' in cosmological simulations, we derive
+an optimistic or conservative limit of the expected gamma-ray emission from
+decaying pions (bracketing our ignorance of the contribution of cluster galaxies
+to the overall gamma-ray flux from a cluster).
+
+\C{We highlight two main uncertainties of the models, namely the acceleration
+  efficiency at formation shocks and CR transport parameters. First, we note}
+that both models assume the maximally allowed acceleration efficiency for {\em
+  strong} shocks that transfers 50\% of the shock-dissipated energy (kinetic
+energy corrected for adiabatic compressional heating at the shock) to CRs. These
+efficiencies drop quickly for weaker shocks \cite{2007A&A...473...41E} which
+dominate the gravitational energy dissipation inside galaxy clusters
+\cite{2006MNRAS.367..113P}. These efficiencies will have to be corrected down if
+this value is not realized at structure formation shocks. Second, these
+simulations \C{(and by extension the analytic model)} neglect active CR
+transport such as streaming and diffusion relative to the gas, i.e., we assume
+that advective transport dominates and CRs are tightly coupled to the gas via
+flux-frozen magnetic fields tangled on sufficiently small scales. Evidence from
+the statistics of radio halos suggests that this might not be the case for
+relaxed clusters, arguing that CR streaming \C{(and diffusion)} in those objects
+could be responsible for a decrease in the central CR number density. This
+effect would also reduce the expected gamma-ray flux by up to a factor of five
+\cite{2011A&A...527A..99E}.
+
+We note that the tightest \Fermi limits are obtained in the 1-10 GeV regime due
+to the highest sensitivity of \Fermi-LAT there. While the effective area of LAT
+increases up to these energies, the typical photon spectra decrease as a
+function of energy: combining those effects selects this energy range to be most
+sensitive.  In this energy band, the \Fermi limits come close to the flux
+predictions of Virgo, Coma and Norma. Using integrated flux limits from \Fermi,
+we arrive at very similar results.  We emphasize that by using our analytic
+modeling, the slight discrepancy of the scaling relation-based prediction with
+the \Fermi limit on Norma \cite{2010ApJ...717L..71A} is resolved: Norma simply
+seems to be less bright than an average cluster of the same mass as Norma. The
+insensitive limit on Perseus \C{is due to the bright central source NGC1275 with
+  an AGN in the center \cite{2010ATel.2916....1M} making it hard to determine a
+  comparable limit as obtained for the other clusters. In addition, there are
+  recent gamma-ray observations of the head-tail radio galaxy IC310 in the
+  cluster outskirts \cite{2010ApJ...723L.207A,2010A&A...519L...6N}.}
+
+\C{A quantity that is of great scientific interest is the CR pressure ($P_\CR$)
+  relative to the thermal pressure ($P_\rmn{th}$) as it may bias galaxy cluster
+  observables, e.g., the Sunyaev-Zel’dovich signal or hydrostatic mass
+  estimates, and the resulting cosmological constraints if the analyses do not
+  marginalize over a potential pressure contribution from CRs. Before we turn to
+  the newly derived constraints on the relative CR pressure, $X_\CR =
+  P_\CR/P_\rmn{th}$, we study the Bayesian prior that different models (a
+  simulation based and a simple analytic model) impose on the scaling of $X_\CR$
+  with cluster mass.}
+
+\C{In the simulation based analytic CR model \cite{2010MNRAS.409..449P}, the CR
+  pressure derives from the CR distribution function, $f\dd p =
+  C\,p^{-\alpha}\dd p$, where $C$ is the normalization, $p=P/m_\rmn{p} c$ is the
+  normalized CR proton momentum, and $\alpha$ is the CR spectral index. The
+  pressure is given by $P_\CR \propto C\propto \tilde{C} \,\rho_\rmn{gas}$,
+  where the volume weighted, dimensionless normalization,
+  $\bra\tilde{C}\ket\propto \mvir^{0.44}$ for clusters with a mass $\mvir\gtrsim
+  10^{14}\,\msun$ \cite{2010MNRAS.409..449P}. The thermal pressure is derived
+  from the temperature in virial equilibrium, and scales as $P_\rmn{th}= n k_\B
+  T \propto G \mvir/R_{200} \propto \mvir^{2/3}$. Hence, the volume weighted
+  relative CR pressure scales as
+  \begin{equation}
+    \bra X_{\CR,\,\rmn{sim}}\ket = \frac{\bra P_\CR\ket}{\bra P_\rmn{th}\ket} 
+    \propto \frac{\bra\tilde{C}\ket}{\bra k_\B T\ket} \propto M^{-0.22}\,,
+  \end{equation}
+  which depends only weakly on cluster virial mass. This suggests that
+  CRs are accelerated at the strongest formation shocks, i.e. during
+  proto-cluster formation at high$-z$ or in between voids and
+  pre-collapsed IGM. These CRs experience then a similar transport
+  history in the form of adiabatic compression or encounter shocks of
+  similar (weak) strength.}
+
+\C{In contrast, the analytic (isobaric) CR model \cite{2004A&A...413...17}, that
+  was used by the \Fermi collaboration to derive CR pressure constraints
+  \cite{2010ApJ...717L..71A}, assumes $P_\CR = X_\CR P_\rmn{th}$ and constrains
+  $X_\CR$ by assuming no intrinsic cluster mass dependence of the CR pressure.
+  While apparently very natural, this implies a strong cluster mass dependence
+  of $X_\CR$ as the following estimate shows:
+  \begin{equation}
+    \bra X_{\CR,\,\rmn{iso}}\ket = \frac{\bra P_\CR\ket}{\bra P_\rmn{th}\ket} 
+    \propto \frac{C}{\bra n k_\B T\ket} \propto M^{-0.8}\,.
+  \end{equation}
+  Here, we determine the mass scaling of the average gas density
+  through its relation to the enclosed gas fraction, $f_\rmn{gas}$, and find that
+  $n_\rmn{gas}\propto f_\rmn{gas} \propto M^{0.135}$
+  \cite{2009ApJ...693.1142S}.}
+
+\C{Figure~\ref{fig:XCR} shows the volume weighted relative CR pressure for 32
+  clusters, for which extended \Fermi-LAT upper limits are derived (that assume
+  King profiles). We adopt a constant $\bra X_\CR\ket\approx 0.02$ derived from
+  the average of the large clusters in our simulation sample
+  \cite{2008MNRAS.385.1211P, 2010MNRAS.409..449P}. We can constrain $X_\CR <
+  (0.1-0.2)$ using the extended gamma-ray upper limits on most of the clusters
+  in the \Fermi sample. The most constraining clusters are Norma and Coma with
+  $X_\CR < 0.07$. Most of the 32 clusters have limits on $X_\CR$ within a factor
+  few from the best constraining clusters suggesting that stacking of clusters
+  will be able to improve these limits.  These limits may improved upon by using
+  a stacking approach that adopts our simulation-based analytic model as a
+  prior.}
+
+\C{In a recent work by the \Fermi collaboration \cite{2010ApJ...717L..71A},
+  where the 1.5 year \Fermi data was used to derive limits on $X_\CR$, they
+  found that the most massive clusters are on average more constraining yielding
+  the best constraints of the order of 5\% (by adopting, however, point-like
+  upper limits). In contrast, we find better limits on the low mass
+  clusters. This difference is explained by the different priors on $P_\CR$.  We
+  adopt a prior inferred from cosmological simulations that dynamically trace
+  the CRs during cluster assembly suggesting that adiabatic transport is
+  dominant in shaping the CR population in clusters and implying a weak mass
+  dependence of $X_\CR$. Their analysis assumes a CR pressure that is
+  independent of cluster mass, i.e., constraints on $X_\CR$ inherit the inverse
+  mass dependence of the thermal pressure, $X_\CR\propto 1/P_\rmn{th}\propto
+  M^{-0.8}$. While it is not clear which mass scaling of $X_\CR$ is realized in
+  Nature, these considerations suggest that it will be critical for future work
+  to account for the Bayesian prior in deriving limits on their pressure.}
+
+ %%%%%
+\del{ In the following we
+  estimate the mass scaling of the relative CR pressure, $X_\CR =
+  P_\CR/P_\rmn{th}$, using the CR formalism outlined in
+  \cite{2007A&A...473...41E,2010MNRAS.409..449P}. We derive the CR pressure from
+  the CR distribution function $f = C\,p^{-\alpha}$, where $C$ is the
+  normalization of each power-law, $p=P/m_\rmn{p} c$ is the normalized CR proton
+  momentum, and $\alpha$ is the CR spectral index. The pressure is given by
+  $P_\CR \propto C=\tilde{C} \,\rho_\rmn{gas}$, where $\tilde{C}\propto
+  M^{0.44}$ for clusters with a mass $\mvir\gtrsim 10^{14}\,\msun$
+  \cite{2010MNRAS.409..449P}. We determine the mass scaling of the gas density
+  through its relation to the enclosed gas fraction $f_\rmn{gas}$, and find that
+  $\rho_\rmn{gas}\propto f_\rmn{gas} \propto M^{0.135}$
+  \cite{2009ApJ...693.1142S}. The thermal pressure is derived from the
+  temperature in virial equilibrium, and scales as $P_\rmn{th}\propto k_\B T
+  \propto G M/R \propto M^{0.67}$. Finally we can derive the mass scaling of the
+  volume weighted relative CR pressure from
+  \begin{equation}
+    <X_\CR> = \frac{<P_\CR>}{<P_\rmn{th}>} \propto \frac{<\rho_\rmn{gas}\,
+      \tilde{C}>}{<k_\B T>} \propto M^{-0.1}\,,
+  \end{equation}
+  which is roughly a constant, i.e. almost independent on halo
+  mass. This suggests that CRs are accelerated at the strongest
+  shocks, in the early universe or between voids and pre-collapsed
+  IGM, and then experience a similar transport history in the form of
+  adiabatic compression or similarly weaker shocks. Since the CRs that
+  build up the bulk of the CR pressure also give rise to gamma-ray
+  emission through the production of decaying pions, we use gamma-ray
+  upper limits from \Fermi-LAT to constrain $X_\CR$. In
+  Fig.~\ref{fig:XCR} we show the volume weighted relative CR pressure
+  for 32 clusters, for which LAT upper limits that assume King
+  profiles are derived. We adopt a constant $<X_\CR>\approx 0.02$
+  derived from a representative simulated cluster
+  \cite{2008MNRAS.385.1211P} and find that for most of the clusters in
+  the sample we can constrain $X_\CR < (0.1-0.2)$ using the extended
+  gamma-ray upper limits, where the most constraining clusters are
+  Norma and Coma with $X_\CR < 0.07$. Most of the 32 clusters have
+  $X_\CR$ upper limits within a factor few from the best constraining
+  clusters, which suggests that stacking of clusters will be able to
+  improve these limits. This might even be improved further using a
+  scaled stacking with our model as a prior. In a recent work
+  \cite{2010ApJ...717L..71A}, where the 1.5 year \Fermi data was used
+  to derive limits on $X_\CR$, they found that the most massive
+  clusters are on average more constraining, while we find better
+  limits on the low mass clusters. This difference is explained by the
+  different priors on $P_\CR$; they assumed a mass independent CR
+  pressure derived from a single CR power-law distribution function,
+  while we adopt a prior inferred from cosmological simulations that
+  dynamically trace the CRs during cluster assembly and allow for a
+  varying spectral index where $P_\CR\sim M^{0.44}$. Furthermore, the
+  gamma-ray flux predictions that we use in this work to constrain
+  $X_\CR$ assumes the true gas density distribution for each cluster
+  \footnote{Derived from the parameters in the extended HIFLUGCS
+    catalogue.} that accounts for cluster-to-cluster scatter, in
+  contrast to the mass-to-luminosity scaling relations that was used
+  in previous work.}
+
+To complete this section, we present our analytical model predictions
+for the CR-induced gamma-ray flux for all clusters in the extended
+HIFLUGCS sample in Fig.~\ref{fig19}. In the lower panel of this
+figure, we show the relative difference between the gamma-ray flux
+computed using the analytical CR model to the flux predicted by the
+mass-luminosity scaling relation. Statistically, one can view the
+analytical modeling as explicitly accounting for the scatter of the expected
+gamma-ray flux at a given mass. Cool core clusters have a denser core
+which increases the target density of gas protons for the hadronic
+reaction which in turn leads to a systematic increase of the expected
+gamma-ray fluxes. We confirm this effect since all clusters with
+increased flux ratio of our analytical CR model relative to the scaling relation
+expectation are in fact cool core clusters. This suggests that the X-ray
+emission should be a good proxy for the expected gamma-ray
+emission. Note however that there could be the counter-acting effect
+of CR streaming in relaxed clusters which would tend to decrease the
+gamma-ray luminosity \cite{2011A&A...527A..99E}. Future careful
+modelling is needed to quantify this effect.
+
 \section{Conclusions}
@@
 cosmic ray (CR) induced pion decay which is thought to dominate the
-astrophysical signal from clusters. Once supersymmetric cold dark
-matter decouples from the expanding universe it streams and erases any
-potentially present smaller scales. When gravitational instabilities
-causes halos to collapse, this free-streaming scale imprints as a
-characteristic minimum halo mass $M_\mathrm{min}$ into the hierarchy
-of structure formation and should still survive until the present time
-as substructure within larger halos. It turns out that the boost due
-to substructures dominates over the smooth component for halo masses
-$\mvir>10^3 \msun$ and contributes a constant luminosity for each
-decade in halo mass. The ratio of halo-to-minimum subhalo mass
-$\mvir/M_\mathrm{min}$ is maximized for the largest systems that had
-time to collapse and virialise since the Big Bang -- galaxy
-clusters. The corresponding substructure boost can reach values
-exceeding $10^3$ which should make nearby clusters the brightest DM
-annihilation sources after the MW center and hypothetical very
-close-by DM substructures.  Since the mass density of substructures
-peaks at radii close to $\rvir$, the contribution to the annihilation
-emission from substructures is also dominated from these outer cluster
-regions.  This implies an almost flat surface brightness profile of
-the annihilation emission which makes it necessary to have the entire
+astrophysical signal from clusters.
+
+{\em Dark matter annihilation.} Once supersymmetric cold dark matter decouples
+from the expanding universe it streams and erases any potentially present
+smaller scales. When gravitational instability causes halos to collapse, this
+free-streaming scale imprints as a characteristic minimum halo mass
+$M_\mathrm{min}$ into the hierarchy of structure formation and should still
+survive until the present time as substructure within larger halos. We show that
+the boost due to substructures dominates over the smooth component for halo
+masses $\mvir>10^3 \msun$ and contributes a constant luminosity for each decade
+in halo mass. The ratio of halo-to-minimum subhalo mass $\mvir/M_\mathrm{min}$
+is maximized for the largest virialized systems in the Universe -- galaxy
+clusters. The corresponding substructure boost can reach values exceeding $10^3$
+which should make nearby clusters the brightest DM annihilation sources after
+the MW center and hypothetical very close-by DM substructures. \C{We stress that
+  this conclusion relies on two hypotheses that are still open problems in
+  particle physics and numerical cosmology. We assume (i) the existence of cold
+  DM, i.e., the density fluctuation power spectrum extends down to the DM free
+  streaming scale of about an Earth mass, and (ii) assume that structure
+  formation at scales smaller than currently resolved ones ($\sim 10^5\,\msun$)
+  proceeds scale-invariant, i.e., there is no non-linear mode coupling between
+  different scales that could potentially erase structure smaller than a
+  characteristic one as the linear power spectrum approaches $\Delta^2(k)
+  \propto k^3 P(k)=\rmn{const.}$ and structure on different scales forms not any
+  more hierarchically, but collapses at the same time.}
+
+Since the mass density of substructures peaks at radii close to
+$\rvir$, the contribution to the annihilation emission from
+substructures is also dominated from these outer cluster regions.
+This implies an almost flat surface brightness profile of the
+annihilation emission which makes it necessary to have the entire
 cluster in the field-of-view to take advantage of the total
@@
 
-We identify Fornax to be the best cluster/group candidate for indirect
-DM studies as it is expected to emit the brightest annihilation flux
-and more importantly, has a comparably low CR induced gamma-ray flux.
-\del{This in principle should allow to detect or constrain some BM
-  models that have been chosen for the large gamma-ray flux yield with
-  three-year \Fermi data (or constrain the substructure boost
-  factor).}  Other nearby bright sources of the extended HIFLUGCS
-sample of nearby bright X-ray cluster/groups are M49, Centaurus, and
-NGC~4636.  The non-detection of gamma-ray emission by \Fermi in a
-total of 26 clusters/groups (the mentioned clusters as well as Virgo,
-Coma, Hydra, and Norma among others) considerably constrains LP models
-for DM annihilation which were introduced to explain the increasing
-positron-to-lepton ratio beyond 10 GeV. \C{Assuming that the minimum
-  DM substructure mass extends down to an Earth mass and that the DM
-  annihilation flux is dominated by small scale substructure, we limit
-  the saturated Sommerfeld enhancement factor in M49 and Fornax to
-  about 14 and 22, respectively. This corresponds to a value in the
-  Milky Way (MW) of less than 8 and 13, respectively, due to the larger Sommerfeld
-  boost factor in smaller mass halos which have a lower velocity
-  dispersion that enhances the particle cross section (while assuming
-  universality of the DM model).} This would rule out LP models in
-their current form based on the non-observation of gamma-rays in any
-of the fore-mentioned clusters/groups. Alternatively, assuming the LP
-models to be correct, we limit the minimum substructure mass to
-$>10~\msun$ in M49.
-
 In this work, we thoroughly study the spectral emission
@@
 close to the rest mass of the self-annihilating neutralinos (if
-present in the model under consideration). While this final state
-radiation is sometimes not distinguished from the continuum emission
-contribution, we keep it separate as it dominates the very high-energy
-tail of the gamma-ray spectrum in LP models while there the continuum
-emission is negligibly low.
+present in the model under consideration).\footnote{While this final
+  state radiation is sometimes not distinguished from the continuum
+  emission contribution, we keep it separate as it dominates the very
+  high-energy tail of the gamma-ray spectrum in LP models while there
+  the continuum emission is negligibly low.}
 
@@
   subdominant compared to the upscattered CMB (below 60~GeV) and the
-  final state radiation (above 60~GeV).}  \del{For large clusters, the
-  final state radiation then takes over for energies up to the cutoff
-  at $m_\chi c^2 \sim 1$~TeV. In small clusters, there is a window
-  around $E_\gamma \sim 100~\mathrm{GeV}$ where the IC up-scattering
-  of the dust emission dominates over the CMB IC emission and the
-  final state radiation. The IC emission of starlight remains always
-  subdominant.}  We stress, that the inclusion of the dust and
-starlight radiation fields are negligible in the cooling function for
-the leptons.  The main reason why the IC emission from starlight and
-dust remains subdominant is the small overlap of this component with
-the peripherally peaked substructure mass density profiles. If for
-some reason, DM has less substructure, the relative importance of this
-IC component increases considerably.
-
-We substantially improve the modelling of the expected gamma-ray
-signal from pion-decay resulting from hadronic CR interactions with
-gas protons over previous work \citep{2010ApJ...717L..71A}. We employ
-the analytic model of the CR spectrum and spatial distribution,
-recently developed by \citet{2010MNRAS.409..449P} that is based on
-cosmological hydrodynamical simulations of galaxy clusters that
-self-consistently follow the evolution of CRs in cosmic structure
-formation. Adopting the model for all clusters in the HIFLUGCS sample
-of flux-limited X-ray clusters, we compare the expected gamma-ray
-emission to that inferred from using $L_\gamma$-cluster mass scaling
-relation. We note that the predictions of our ``optimistic'' model are
-perfectly in agreement with \Fermi upper limits for all clusters.  The
-hint of a tension that the scaling relation modeling showed for Norma
-\citep{2010ApJ...717L..71A} could not be confirmed due to the lower
-gas density of this cluster relative to the average.  As expected, the
-analytical CR model accounts for the ``scatter'' to the scaling
-relation and biases the gamma-ray flux high for prominent cool core
-clusters by up to a factor of 6 relative to the expectation from the
-scaling relation. This is due to the high target gas densities and
-associated CR densities in those cool cores that shape the spatial
-emission characteristic to be very similar to that observed in thermal
-X-rays. We caution that these predictions only apply for the case of
-negligible active CR transport such as CR streaming and diffusion
-relative to the gas. Gamma-ray fluxes might be considerably smaller in
-those cluster that do not show an extended diffuse radio(-mini) halo
-that might point to a centrally concentrated CR distribution
-\citep{2011A&A...527A..99E}. The CR spectrum $E^2 dN/dE$ shows the
-characteristic pion bump at energies around 1~GeV. It is expected to
-dominate the DM annihilation signal of BM models for all
-clusters/groups but Fornax. \C{We conclude that due to the large
-  spatial extension of the brightest clusters it is not possible for
-  \Fermi to rule out the LP model or to constrain the BM DM models
-  without improved modelling. However, we can put tight constraints on
-  the boost from substructures and Sommerfeld enhancement using the LP
-  model. Hence, clusters are a valuable complement to direct and
-  accelerator searches for the nature of DM.}\del{We conclude that it
-  will be possible to rule out the LP model with six years of \Fermi
-  data and start to constrain some BM DM models. Hence this should
-  nicely complement direct and accelerator searches for the nature of
-  DM.}
+  final state radiation (above 60~GeV).}  We stress, that the
+inclusion of the dust and starlight radiation fields are negligible in
+the cooling function for the leptons.  The main reason why the IC
+emission from starlight and dust remains subdominant is the small
+overlap of this component with the peripherally peaked substructure
+mass density profiles. If for some reason, DM has less substructure,
+the relative importance of this IC component increases considerably.
+
+\C{We identify Virgo and Fornax to be the best cluster/group
+  candidates for indirect DM studies as they are expected to emit the
+  brightest annihilation flux.\footnote{\C{We excluded Virgo from our
+    further analysis due to its large angular extent that needs a
+    separate treatment.}}  More importantly, Fornax has a comparably
+  low CR induced gamma-ray flux which may enable an indirect DM
+  detection or a particularly tight limit on DM properties}.  Other
+nearby bright sources of the extended HIFLUGCS sample of nearby bright
+X-ray cluster/groups are \C{Ophiuchus, Coma, and Centaurus}.
+
+The non-detection of gamma-ray emission by \Fermi in a total of 26
+clusters/groups considerably constrains LP models for DM annihilation
+which were introduced to explain the increasing positron-to-lepton
+ratio beyond 10 GeV. \C{Assuming that the minimum DM substructure mass
+  extends down to an Earth mass and that the DM annihilation flux is
+  dominated by small scale substructure, we limit the saturated
+  Sommerfeld enhancement factor in M49 (that has a particularly tight
+  upper limit) and Fornax to about 14 and 22, respectively. This
+  corresponds to a value in the Milky Way (MW) of less than 8 and 13,
+  respectively, due to the larger Sommerfeld boost factor in smaller
+  mass halos which have a lower velocity dispersion that enhances the
+  particle cross section (while assuming universality of the DM
+  model).} This would rule out LP models in their current form based
+on the non-observation of gamma-rays in any of the fore-mentioned
+clusters/groups. Alternatively, assuming the LP models to be correct,
+we limit the minimum substructure mass to $>10~\msun$ in M49.
+
+{\em Cosmic ray induced emission.} We substantially improve the
+modelling of the expected gamma-ray signal from pion-decay resulting
+from hadronic CR interactions with gas protons over previous work
+\citep{2010ApJ...717L..71A}. We employ the analytic model of the CR
+spectrum and spatial distribution that is based on cosmological
+hydrodynamical simulations of galaxy clusters that self-consistently
+follow the evolution of CRs in cosmic structure formation
+\citet{2010MNRAS.409..449P}. Adopting the model for all clusters in
+the HIFLUGCS sample of flux-limited X-ray clusters, we compare the
+expected gamma-ray emission to that inferred from using
+$L_\gamma$-cluster mass scaling relation. We note that the predictions
+of our ``optimistic'' model are perfectly in agreement with \Fermi
+upper limits for all clusters.  The hint of a tension that the scaling
+relation modeling showed for Norma \citep{2010ApJ...717L..71A} could
+not be confirmed due to the lower gas density of this cluster relative
+to the average.
+
+As expected, the analytical CR model accounts for the ``scatter'' to
+the scaling relation and biases the gamma-ray flux high for prominent
+cool core clusters by up to a factor of 6 relative to the expectation
+from the scaling relation. This is due to the high target gas
+densities and associated CR densities in those cool cores that shape
+the spatial emission characteristic to be very similar to that
+observed in thermal X-rays. We caution that these predictions only
+apply for the case of negligible active CR transport such as CR
+streaming and diffusion relative to the gas. Gamma-ray fluxes might be
+considerably smaller in those cluster that do not show an extended
+diffuse radio(-mini) halo that might point to a centrally concentrated
+CR distribution \citep{2011A&A...527A..99E}. The CR spectrum $E^2
+dN/dE$ shows the characteristic pion bump at energies around 1~GeV. It
+is expected to dominate the DM annihilation signal of BM models for
+all clusters/groups but Fornax.
+
+\C{Combining extended \Fermi upper limits and our model flux predictions, we
+  limit the relative CR pressure, $X_\CR = P_\CR/P_\rmn{th}$, in 32 nearby
+  bright galaxy clusters of the \Fermi sample. The best limits are found in
+  Norma and Coma of the order of 7\%, with typical limits ranging between 10\%
+  to 30\%. This is somewhat larger that those inferred by the \Fermi
+  collaboration \citep{2010ApJ...717L..71A} and due to the differently assumed
+  Bayesian prior on the CR pressure which implies a different cluster mass
+  dependence of the resulting limits on $X_\CR$. }
+
+\C{We conclude that due to the large spatial extension of the
+  brightest clusters it is not possible for \Fermi to rule out the LP
+  model or to constrain the BM DM models without improved
+  modelling. However, we can put tight constraints on the boost from
+  substructures and Sommerfeld enhancement using the LP model. Hence,
+  clusters are a valuable complement to direct and accelerator
+  searches for the nature of DM.}
 

### 2011-06-22 paper.tex
big footnote moved to text

@@
 of 230 which is the enhancement found in one of the highest resolved MW halos
-ever simulated.\footnote{\C{While there is still a discrepancy in the literature
-    of the exact value of the predicted boost factor of the DM annihilation
-    luminosity from substructures in DM halos, this inconsistency starts to
-    become resolved, apparently converging toward predictions at the high end,
-    e.g. those by the Aquarius simulations \protect \cite{2008MNRAS.391.1685S,
+ever simulated. \C{While there is still a discrepancy in the literature of the
+  exact value of the predicted boost factor of the DM annihilation luminosity
+  from substructures in DM halos, this inconsistency starts to become resolved,
+  apparently converging toward predictions at the high end, e.g. those by the
+  Aquarius simulations \protect \cite{2008MNRAS.391.1685S,
     2008Natur.456...73S}. The initial suggestions of a small {\em total} boost
@@
   radial number density to be anti-biased with respect to the host's mass
-    density profile yielding a significantly flatter subhalo distribution
-    compared to the smooth DM distribution \cite{2010ApJ...718..899A}. This
-    increases the substructure boost preferentially in the outer parts of DM
-    halos with a factor that ranges between 20 and 1000 (for dwarfs and galaxy
-    clusters), hence depending sensitively on the host halo mass (see
-    Figure~\ref{fig:radial_lum}).}}  We use a double power-law function to fit
-the luminosity from the smooth component of substructures (i.e. substructures
-within substructures are not included) inside radius $r$ which is determined for
-the Aquarius simulations
+  density profile yielding a significantly flatter subhalo distribution compared
+  to the smooth DM distribution \cite{2010ApJ...718..899A}. This increases the
+  substructure boost preferentially in the outer parts of DM halos with a factor
+  that ranges between 20 and 1000 (for dwarfs and galaxy clusters), hence
+  depending sensitively on the host halo mass (see
+  Figure~\ref{fig:radial_lum}).}
+
+We use a double power-law function to fit the luminosity from the smooth
+component of substructures (i.e. substructures within substructures are not
+included) inside radius $r$ which is determined for the Aquarius simulations
 \cite{2008MNRAS.391.1685S,2008Natur.456...73S}.\footnote{Our approach of fitting

### 2011-08-01 paper.tex
minor cgange
updated figures and text, new masses

@@
 %\voffset-.6in 
-\voffset.3in
+%\voffset.3in
 
@@
 \newcommand{\ket}{\rangle}
+\newcommand{\vst}{\vspace{-0.14mm}}
+\newcommand{\el}{\rmn{el}}
+
 %OLD
@@
 
-\voffset.8in
+%\voffset.8in
+\voffset.4in
 
@@
   from a realistic spatial and spectral distribution of dust and
-  stellar light. We predict the Virgo and Fornax clusters to be the
-  brightest DM sources and find a particularly low CR induced
+  stellar light. We predict the Virgo, Fornax and \C{M49} clusters to
+  be the brightest DM sources and find a particularly low CR induced
   background for Fornax. For a minimum substructure mass given by the
@@
   distribution down to an Earth mass and using \Fermi upper limits, we
-  rule out the leptophilic models in their present form in 26
+  rule out the leptophilic models in their present form in 28
   clusters, and limit the boost from Sommerfeld enhancement in the
-  most constraining cluster M49 to be less than 14. This corresponds
-  to a Sommerfeld enhancement in the Milky Way of less than
-  8. Alternatively, if the Sommerfeld enhancement factor is realized
-  in Nature, this would imply a limiting substructure mass in M49 of
-  $\mlim > 10\,\msun$ which would be a challenge for structure
-  formation. \C{We find it challenging for \Fermi to
-    constrain our selection of DM benchmark models using clusters
+  most constraining clusters, \C{M49 and Fornax, } to be less than 5. This
+  corresponds to a Sommerfeld enhancement in the Milky Way of less
+  than 5. Alternatively, if the Sommerfeld enhancement factor is
+  realized in Nature, this would imply a limiting substructure mass of
+  $\mlim > 10^4\,\msun$ which would be a challenge for structure
+  formation. We find it challenging for \Fermi to constrain our
+  selection of DM benchmark models in the \C{near future} using clusters
   without improved modelling of extended sources in addition to a
-    stacked likelihood analysis.} The \Fermi upper limits are, however,
+  stacked likelihood analysis. The \Fermi upper limits are, however,
   closing in on our predictions for the CR flux using an analytic
@@
 
-3. Galaxy clusters. This possibility has been less studied \C{theoretically}, however
-\C{currently there is an ongoing observational campaign to detect
-  gamma-ray emission from galaxy clusters
-  \cite{2010ApJ...710..634A,2010JCAP...05..025A,2009A&A...495...27A,2009IJMPD..18.1627D,2009A&A...502..437A,2009arXiv0907.5000G,2009ApJ...704..240K,2009ApJ...706L.275A,2010ApJ...717L..71A}.
-In fact, we noted} in a previous Letter
-\cite{2009PhRvL.103r1302P} that there are certain advantages that work
-in favour of this possible target for gamma-ray detection of DM
-annihilation. Galaxy clusters constitute the most massive objects in
-our Universe that are forming today. This causes their DM subhalo mass
-function to be less affected by tidal stripping compared to galaxy
-sized halos that formed long ago.  The annihilation luminosities of
-the DM halo component for e.g. the Virgo cluster and the Draco dwarf
-scales in a way (see \cite{2009PhRvL.103r1302P}) that the ratio of
-gamma-ray luminosities from the smooth components is around 4, in
-favour of Virgo. In addition, there may be a further enhancement due
-to substructure, which to a large extent should be unaffected by tidal
-disruption, at least in the outer regions.  According to a recent
-estimate \cite{2011MNRAS.410.2309G}, more massive haloes tend to have
-a larger mass fraction in subhalos.  For example, cluster size haloes
-typically have 7.5 per cent of the mass within $r_{200}$ in
-substructures of fractional mass larger than $10^{-5}$, which is 25
-per cent higher than for galactic haloes.\footnote{All halo masses and
-  length scales in this paper are scaled to the currently favored
-  value of Hubble's constant, $H_0 = 70\,
-  \rmn{km~s}^{-1}\,\rmn{Mpc}^{-1}$. We define the virial mass $\mvir$
-  and virial radius $\rvir$ as the mass and radius of a sphere
-  enclosing a mean density that is 200 times the critical density of
-  the Universe $\rho_{\rmn{cr}}$.}
+3. Galaxy clusters. This possibility has been less studied
+theoretically, however currently there is an ongoing observational
+campaign to detect gamma-ray emission from galaxy clusters
+\cite{2010ApJ...710..634A,2010JCAP...05..025A,2009A&A...495...27A,2009IJMPD..18.1627D,2009A&A...502..437A,2009arXiv0907.5000G,2009ApJ...704..240K,2009ApJ...706L.275A,2010ApJ...717L..71A}. In
+fact, we noted in a previous Letter \cite{2009PhRvL.103r1302P} that
+there are certain advantages that work in favour of this possible
+target for gamma-ray detection of DM annihilation. Galaxy clusters
+constitute the most massive objects in our Universe that are forming
+today. This causes their DM subhalo mass function to be less affected
+by tidal stripping compared to galaxy sized halos that formed long
+ago.  The annihilation luminosities of the DM halo component for
+e.g. the Virgo cluster and the Draco dwarf scales in a way (see
+\cite{2009PhRvL.103r1302P}) that the ratio of gamma-ray luminosities
+from the smooth components is around 4, in favour of Virgo. In
+addition, there may be a further enhancement due to substructure,
+which to a large extent should be unaffected by tidal disruption, at
+least in the outer regions.  According to a recent estimate
+\cite{2011MNRAS.410.2309G}, more massive haloes tend to have a larger
+mass fraction in subhalos.  For example, cluster size haloes typically
+have 7.5 per cent of the mass within $r_{200}$ in substructures of
+fractional mass larger than $10^{-5}$, which is 25 per cent higher
+than for galactic haloes.\footnote{All halo masses and length scales
+  in this paper are scaled to the currently favored value of Hubble's
+  constant, $H_0 = 70\, \rmn{km~s}^{-1}\,\rmn{Mpc}^{-1}$. We define
+  the virial mass $\mvir$ and virial radius $\rvir$ as the mass and
+  radius of a sphere enclosing a mean density that is 200 times the
+  critical density of the Universe $\rho_{\rmn{cr}}$.}
 
@@
 Galaxy Cluster Sample, HIFLUGCS,
-\citealt{2002ApJ...567..716R}).\footnote{Note that we have added the
-  Virgo cluster to the sample that we nevertheless refer to as
-  extended HIFLUGCS catalogue in the following.}  \C{For previous work
-  related to DM in clusters, see, e.g.,
+\citealt{2002ApJ...567..716R,2007A&A...466..805C}).\footnote{Note that
+  we have added the Virgo cluster to the sample that we nevertheless
+  refer to as extended HIFLUGCS catalogue in the following.}  For
+previous work related to DM in clusters, see, e.g.,
 \cite{2006A&A...455...21C,2009PhRvD..80b3005J,2011arXiv1104.3530S,2011ApJ...726L...6C,2010JCAP...05..025A}
 and for recent work on CRs in clusters see
-  \cite{2010MNRAS.409..449P,2011MNRAS.410..127B,2008MNRAS.385.1211P,2009JCAP...08..002K,2010MNRAS.407.1565D}.}
+\cite{2010MNRAS.409..449P,2011MNRAS.410..127B,2008MNRAS.385.1211P,2009JCAP...08..002K,2010MNRAS.407.1565D}.
 
@@
  \hline
- Coma                 & $5.1\times10^{-8}$  & $8.2\times10^{-11}$ & $4.0\times10^{-9}$  
- & \,\,\,\,\,         & $7.4\times10^{-12}$ & $3.0\times10^{-13}$ & $1.5\times10^{-12}$ 
- & $13.8$ & $530/60$  & $1290$ \\
- Perseus \,\,\,\,\,\, & $4.4\times10^{-8}$  & $7.1\times10^{-11}$ & $1.4\times10^{-8}$  
- & \,\,\,\,\,         & $6.4\times10^{-12}$ & $2.6\times10^{-13}$ & $5.2\times10^{-12}$ 
- & $7.71$ & $530/70$  & $1210$ \\
- Virgo                & $9.2\times10^{-7}$  & $1.4\times10^{-9}$ & $1.1\times10^{-8}$  
- & \,\,\,\,\,         & $1.3\times10^{-10}$ & $5.4\times10^{-12}$ & $3.9\times10^{-12}$ 
- & $6.9$  & $530/105$  & $1110$  \\
- Fornax               & $7.9\times10^{-8}$  & $1.3\times10^{-10}$ & $2.2\times10^{-10}$ 
- & \,\,\,\,\,         & $1.1\times10^{-11}$ & $4.6\times10^{-13}$ & $8.3\times10^{-14}$ 
- & $1.0$  & $530/130$  & $730$  \\
+ Coma                 & $8.2\times10^{-8}$  & $7.6\times10^{-11}$ & $4.1\times10^{-9}$  
+ & \,\,\,\,\,         & $1.2\times10^{-11}$ & $2.8\times10^{-13}$ & $1.5\times10^{-12}$ 
+ & $12.9$ & $530/65$  & $1290$ \\
+ Perseus \,\,\,\,\,\, & $8.6\times10^{-8}$  & $7.8\times10^{-11}$ & $1.5\times10^{-8}$  
+ & \,\,\,\,\,         & $1.2\times10^{-11}$ & $2.9\times10^{-13}$ & $5.5\times10^{-12}$ 
+ & $8.6$ & $530/75$  & $1190$ \\
+ Virgo                & $1.6\times10^{-6}$  & $1.5\times10^{-9}$ & $1.5\times10^{-8}$  
+ & \,\,\,\,\,         & $2.3\times10^{-10}$ & $5.4\times10^{-12}$ & $5.7\times10^{-12}$ 
+ & $6.9$  & $530/80$  & $1120$  \\
+ Fornax               & $3.5\times10^{-7}$  & $3.2\times10^{-10}$ & $3.1\times10^{-10}$ 
+ & \,\,\,\,\,         & $5.1\times10^{-11}$ & $1.2\times10^{-12}$ & $1.1\times10^{-13}$ 
+ & $2.4$  & $530/110$  & $890$  \\
 \hline
@@
   Notes: \\
-  (1) \C{The mass of Fornax, Coma, and Perseus are taken from \cite{2002ApJ...567..716R}, 
-  while the mass of Virgo is derived from \cite{1984ApJ...281...31T}.}\\
-  (2) \C{The boost due to Sommerfeld enhancement. The first value shows the saturated 
+  (1) The mass of Fornax, Coma, and Perseus are derived from \cite{2007A&A...466..805C}, 
+  while the mass of Virgo is derived from \cite{1984ApJ...281...31T}.\\
+  (2) The boost due to Sommerfeld enhancement. The first value shows the saturated 
   Sommerfeld boost realized when substructures are present, the latter is the Sommerfeld 
-  boost without substructures. See Section II A 1.}\\
-  (3) \C{We integrate the emission in a cylinder with a radial extent of $2.5
+  boost without substructures. See Section II A 1.\\
+  (3) We integrate the emission in a cylinder with a radial extent of $2.5
   R_{200}$ along the line-of-sight and an angular size corresponding to $\rvir$
-  (both measured from the cluster center).}\\
+  (both measured from the cluster center).\\
   (4) The total gamma-ray flux from leptophilic (LP) DM where both the
@@
 $\sigv$ the SFE will be smaller than the one expected in a single
-galaxy such as the MW, roughly by a factor $v_{\rm MW}/\sigv$. \C{Note
+galaxy such as the MW, roughly by a factor $v_{\rm MW}/\sigv$. Note
 that the $1/v$-scaling is valid only for $(v/c) \gtrsim
@@
 $1/v$-enhancement saturates at $m_\phi/m_\chi$
-  \cite{2008PhRvL.101z1301K}.}
+\cite{2008PhRvL.101z1301K}.
 
@@
 use a DM mass $m_\chi=1.6$~TeV and a branching ratio of
-($1/4:1/4:1/2$) into
-($\mu^+\mu^-:\e^+\e^-:\pi^+\pi^-$). \del{\footnote{This is an
-    approximation to the model found in \cite{Finkbeiner:2010sm} that
-    has a branching ratio of ($1/4:1/4:1/2$) into
-    ($\mu^+\mu^-:\e^+\e^-:\pi^+\pi^-$).}} \C{Furthermore, since most
-  of gamma-ray flux is expected from come from dense subhalos at which
-  the velocity dispersion is close to the velocity limit $v_\rmn{sat}$
-  where the SFE saturates, we use $S=\B_\sfe(\sigv=v_\rmn{sat})\approx
-  530$ for the cluster halos.\footnote{Note that, $S$ is strictly
-    speaking the Sommerfeld enhanced annihilation cross-section, but
-    here we have in addition included the order unity constraint that
-    make sure that the relic density is not over-depleted at
-    freeze-out.} However, for figures where we neglect the
-  substructure boost, we adopt a velocity dependent SFE that is
-  normalized to fit the electron and positron excess at Earth observed
-  by the PAMELA and \Fermi satellites,}
+($1/4:1/4:1/2$) into ($\mu^+\mu^-:\e^+\e^-:\pi^+\pi^-$). Furthermore,
+since most of gamma-ray flux is expected from come from dense subhalos
+at which the velocity dispersion is close to the velocity limit
+$v_\rmn{sat}$ where the SFE saturates, we use
+$S=\B_\sfe(\sigv=v_\rmn{sat})\approx 530$ for the cluster
+halos.\footnote{Note that, $S$ is strictly speaking the Sommerfeld
+  enhanced annihilation cross-section, but here we have in addition
+  included the order unity constraint that make sure that the relic
+  density is not over-depleted at freeze-out.} However, for figures
+where we neglect the substructure boost, we adopt a velocity dependent
+SFE that is normalized to fit the electron and positron excess at
+Earth observed by the PAMELA and \Fermi satellites,
 \begin{equation}
-\B_\sfe(\sigv) = 0.266\, \frac{c}{v_\rmn{sat}}\, \frac{v_\rmn{MW}}{\sigv} = 
-121 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-1/3}\,.
+%\B_\sfe(\sigv) = 0.266\, \frac{c}{v_\rmn{sat}}\, \frac{v_\rmn{MW}}{\sigv} = 
+%121 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-1/3}\,.
+\C{\B_\sfe(\sigv) = \B_\rmn{sfe,MW} \frac{v_\rmn{MW}}{\sigv} = 
+70 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-1/3}\,.}
 \label{eq:B_sfe}
 \end{equation}
-Here the velocity dispersion for the MW $v_\rmn{MW} \approx
-220\,$~km/s and the velocity dispersion $\sigv$ for clusters is
-derived in \cite{2005RvMP...77..207V}. Clusters have a larger velocity
+\C{Here the boost factor needed to explain the PAMELA/\Fermi excess of
+  electrons and positrons $\B_\rmn{sfe,MW}=300$, the velocity
+  dispersion for the MW $v_\rmn{MW} \approx 220\,$~km/s and the
+  velocity dispersion $\sigv$ for clusters is derived in
+  \cite{2005RvMP...77..207V}.} Clusters have a larger velocity
 dispersion and an accordingly smaller Sommerfeld boost factor.
@@
    models. We show the simulated data from {\sc DarkSUSY} \cite{ds}
-   ($+$), \C{and that generated by
-     \protect\cite{2011JCAP...03..019C,2011JCAP...03..051C}}
-   ($\times$); the solid lines show the fit to the data. LEFT PANEL:
-   normalized differential continuum spectra for four different DM
-   benchmark (BM) models; $\Ip$ model (red), $\Jp$ (orange), $\Kp$
-   (green), and $\Js$ (blue). We use Eq.~(\ref{eq:bm_cont}) to fit the
-   continuum spectra. RIGHT PANEL: number of electron and positron per
-   DM annihilation above the electron energy $\ee$ for different DM
+   ($+$), and that generated by
+   \protect\cite{2011JCAP...03..019C,2011JCAP...03..051C} ($\times$);
+   the solid lines show the fit to the data. LEFT PANEL: normalized
+   differential continuum spectra for four different DM benchmark (BM)
+   models; $\Ip$ model (red), $\Jp$ (orange), $\Kp$ (green), and $\Js$
+   (blue). We use Eq.~(\ref{eq:bm_cont}) to fit the continuum
+   spectra. RIGHT PANEL: number of electron and positron per DM
+   annihilation above the electron energy $\ee$ for different DM
    models; $\Ip$ BM model (red), $\Jp$ BM model (orange), $\Kp$ BM
-   model (green), and $\Js$ BM model (blue), \C{leptophilic (LP) DM
+   model (green), and $\Js$ BM model (blue), leptophilic (LP) DM
      annihilating indirectly into electrons and positrons (purple) and
-     into muons (black) without considering Sommerfeld boosts.} We use
+     into muons (black) without considering Sommerfeld boosts. We use
    Eq.~(\ref{eq:bm_elec}) and Eqs.~(\ref{eq:lp_mu}-\ref{eq:lp_ep}) to
@@
   sum}(\eg,r)$, where we include contributions from five main
-processes; leptophilic DM annihilating \C{through
+processes; leptophilic DM annihilating through
 $\chi\,\chi\to\phi\,\phi\to\{4e\mbox{~or~}4\mu\to4e
-  \mbox{~or~}4\pi\to4e\}$ (neglecting the produced neutrinos) where
-  the $\rmn{e}^+/\rmn{e}^-$ pairs} IC upscatter background photons
-(LP-IC), leptophilic DM emitting final state radiation (LP-FSR),
-supersymmetric DM BM models where annihilating neutralinos generate
+\mbox{~or~}4\pi\to4e\}$ (neglecting the produced neutrinos) where the
+$\rmn{e}^+/\rmn{e}^-$ pairs IC upscatter background photons (LP-IC),
+leptophilic DM emitting final state radiation (LP-FSR), supersymmetric
+DM BM models where annihilating neutralinos generate
 $\rmn{e}^+/\rmn{e}^-$ pairs that upscatter background photons (BM-IC)
@@
 enhancement over the smooth halo contribution $\B_{\sub,i}(r) =
-1+\rho_{\sub,i}^2(r)/\rho^2(r)$ \C{\footnote{Note that if the boost
+1+\rho_{\sub,i}^2(r)/\rho^2(r)$ \footnote{Note that if the boost
     from substructures is $\gg 1$, then the Sommerfeld enhancement
-    approaches the constant saturated boost of 530.}} (see
+    approaches the constant saturated boost of 530.} (see
 Eqs.~\ref{eq:rho_sub}-\ref{eq:xvir} and Sect.~\ref{sect:subst}).  The
@@
 \label{sect:subst}
-High-resolution dissipationless DM simulations of MW type halos find substantial
-amount of substructures in the periphery of DM halos, while the substructures in
-the center suffer from dynamical friction and tidal effects depleting their
-central number densities. Since the DM annihilation rate depends on the density
-squared, the resulting flux from substructures is boosted compared to the smooth
-density distribution. Recent high resolution simulations suggest a flux
-enhancement from substructures of more than 100 \cite{2008MNRAS.391.1685S,
-  2010ApJ...718..899A} for a MW size halo. We adopt a boost from substructures
-of 230 which is the enhancement found in one of the highest resolved MW halos
-ever simulated. \C{While there is still a discrepancy in the literature of the
-  exact value of the predicted boost factor of the DM annihilation luminosity
-  from substructures in DM halos, this inconsistency starts to become resolved,
-  apparently converging toward predictions at the high end, e.g. those by the
-  Aquarius simulations \protect \cite{2008MNRAS.391.1685S,
-    2008Natur.456...73S}. The initial suggestions of a small {\em total} boost
-  ($<R_{200}$) of order unity by the Via Lactea simulations
-  \cite{2008JPhCS.125a2008K} made assumptions of computing the boost assuming
-  that the substructure luminosity follows that of the smooth DM
-  distribution. Physically, this would imply substructure to follow the smooth
-  DM distribution and a radially independent concentration parameter of
-  substructures; both following from neglecting tidal mass loss of
-  satellites. Tidal losses, however, are at work in simulations and cause the
-  radial number density to be anti-biased with respect to the host's mass
-  density profile yielding a significantly flatter subhalo distribution compared
-  to the smooth DM distribution \cite{2010ApJ...718..899A}. This increases the
-  substructure boost preferentially in the outer parts of DM halos with a factor
-  that ranges between 20 and 1000 (for dwarfs and galaxy clusters), hence
-  depending sensitively on the host halo mass (see
-  Figure~\ref{fig:radial_lum}).}
-
-We use a double power-law function to fit the luminosity from the smooth
-component of substructures (i.e. substructures within substructures are not
-included) inside radius $r$ which is determined for the Aquarius simulations
-\cite{2008MNRAS.391.1685S,2008Natur.456...73S}.\footnote{Our approach of fitting
-  the scaling behavior of $L_\sub(<r)$ directly from numerical simulations
-  self-consistently accounts for the radial dependence of the substructure
-  concentration \C{due to tidal mass losses} \protect
-  \cite{2008MNRAS.391.1685S}.} Our best fit is given by
+High-resolution dissipationless DM simulations of MW type halos find
+substantial amount of substructures in the periphery of DM halos,
+while the substructures in the center suffer from dynamical friction
+and tidal effects depleting their central number densities. Since the
+DM annihilation rate depends on the density squared, the resulting
+flux from substructures is boosted compared to the smooth density
+distribution. Recent high resolution simulations suggest a flux
+enhancement from substructures of more than 100
+\cite{2008MNRAS.391.1685S, 2010ApJ...718..899A} for a MW size halo.
+We adopt a boost from substructures of 230 which is the enhancement
+found in one of the highest resolved MW halos ever simulated. While
+there is still a discrepancy in the literature of the exact value of
+the predicted boost factor of the DM annihilation luminosity from
+substructures in DM halos, this inconsistency starts to become
+resolved, apparently converging toward predictions at the high end,
+e.g. those by the Aquarius simulations \protect
+\cite{2008MNRAS.391.1685S, 2008Natur.456...73S}. The initial
+suggestions of a small {\em total} boost ($<R_{200}$) of order unity
+by the Via Lactea simulations \cite{2008JPhCS.125a2008K} made
+assumptions of computing the boost assuming that the substructure
+luminosity follows that of the smooth DM distribution. Physically,
+this would imply substructure to follow the smooth DM distribution and
+a radially independent concentration parameter of substructures; both
+following from neglecting tidal mass loss of satellites. Tidal losses,
+however, are at work in simulations and cause the radial number
+density to be anti-biased with respect to the host's mass density
+profile yielding a significantly flatter subhalo distribution compared
+to the smooth DM distribution \cite{2010ApJ...718..899A}. This
+increases the substructure boost preferentially in the outer parts of
+DM halos with a factor that ranges between 20 and 1000 (for dwarfs and
+galaxy clusters), hence depending sensitively on the host halo mass
+(see Figure~\ref{fig:radial_lum}). \C{It should be noted that the very
+  recent {\it Phoenix} simulations by Chen et
+  al. \cite{2011arXiv1107.1916G} confirms the large enhancement due to
+  substructures in clusters. In fact they find a boost of 1125 for a
+  Coma like cluster which agrees within 10\% with our estimated boost
+  (see e.g. Table~\ref{tab:flux_tab}).}
+
+We use a double power-law function to fit the luminosity from the
+smooth component of substructures (i.e. substructures within
+substructures are not included) inside radius $r$ which is determined
+for the Aquarius simulations
+\cite{2008MNRAS.391.1685S,2008Natur.456...73S}.\footnote{Our approach
+  of fitting the scaling behavior of $L_\sub(<r)$ directly from
+  numerical simulations self-consistently accounts for the radial
+  dependence of the substructure concentration due to tidal mass
+  losses \protect \cite{2008MNRAS.391.1685S}.} Our best fit is given
+by
 \begin{eqnarray}
-  L_\sub(<x) &=& a_0\,C(\mvir)\,L_{200\sm}(\mvir)\,x^{a_1
-    \displaystyle{x}^{a_2}}\,,\label{eq:Lsub}\\
+  L_\sub(<x) &=& a_0\,C(\mvir)\,L_{200\sm}(\mvir)\,x^{f(x)}\,,\label{eq:Lsub}\\
+   f(x)&=&a_1\,x^{a_2}\,, \nonumber\\
  a_0 &=& 0.76\,,\quad a_1 = 0.95\,,\quad  a_2 = -0.27\,, \quad 
@@
 
-\C{To motivate the scaling of the substructure luminosity boost with limiting
-  substructure mass in Eqs.~(\ref{eq:Lsub}-\ref{eq:Csub}), we show how it
-  derives from the substructure mass function, $\dd N_\sub/\dd M_\rmn{sub}
-  \propto M_\rmn{sub}^{-1.9}$ \cite{2008MNRAS.391.1685S,2008Natur.456...73S} and
-  substructure luminosity scaling with the limiting mass of satellites, $L_\sub
-  \propto M_\rmn{lim}^A$. The total luminosity of substructures scales as
+To motivate the scaling of the substructure luminosity boost with
+limiting substructure mass in Eqs.~(\ref{eq:Lsub}-\ref{eq:Csub}), we
+show how it derives from the substructure mass function, $\dd
+N_\sub/\dd M_\rmn{sub} \propto M_\rmn{sub}^{-1.9}$
+\cite{2008MNRAS.391.1685S,2008Natur.456...73S} and substructure
+luminosity scaling with the limiting mass of satellites, $L_\sub
+\propto M_\rmn{lim}^\delta$. The total luminosity of substructures scales
+as
 \begin{eqnarray}
@@
 \int_{M_\rmn{lim}} \dd M_\rmn{sub} \frac{\dd N_\sub}{\dd M_\rmn{sub}} \nonumber\\
- &\propto& M_\rmn{lim}^{A-0.9} \propto M_\rmn{lim}^{-0.226}\,,\quad
-\rmn{for}\quad A=0.674\,. \nonumber\\
+ &\propto& M_\rmn{lim}^{\delta-0.9} \propto M_\rmn{lim}^{-0.226}\,,\quad
+\rmn{for}\quad \delta=0.674\,. \nonumber\\
 &&
 \end{eqnarray}
-Tidal truncation is responsible in shaping the substructure luminosity scaling
-parameter $A$. Here we only sketch out qualitative arguments and leave details
-and comparison to numerical simulations to future work. First, tidal effects
-truncate the subhalo profile primarily in the outer regions. As a result of
-this, the subhalo acquires a steeper logarithmic slope than the canonical 3 from
-the NFW-profile. Second, tidal stripping imposes a mass-dependency and should be
-stronger for smaller substructure.  The stripping efficiency (for an effective
-cross section $\sigma$) only depends on the ambient DM density of the host halo,
-$n_\rmn{dm}$, which implies a scaling of the mean free path of a subhalo of
-$x_\rmn{mfp} \propto 1/(n_\rmn{dm} \sigma)$. Since there is less mass at any
-given density for smaller substructures, modest density inhomogeneities within
-the host halo seen by the orbiting substructures cause a stronger mass loss of
-these smaller satellites. Third, the tidal truncation radius should be a
-function of host halo radius due to the increasing smooth density profile for
-smaller radii.  If we pick an effective host halo radius which dominates the
-luminosity contribution of the substructures and were to fit the tidally
-truncated subhalo density profile with an NFW-profile, the resulting $\rs$ would
-be biased toward lower values implying a higher concentration compared to an
-isolated halo. In order to reproduce our value of $A$, we would need a
-concentration mass relation of $c\propto M_\rmn{sub}^{-0.14}$ (employing the
-$L(M_{200},c)$ formula derived by reference \cite{2009PhRvL.103r1302P}).  As expected,
-this is steeper than the concentration-mass relation found for isolated halos on
-dwarf galaxy scales, $c \propto M_\rmn{vir}^{-0.06}$ \cite{2011arXiv1101.2020I},
-as well as galaxy and cluster scales, $c \propto M_\rmn{vir}^{-0.098}$
-\cite{2008MNRAS.391.1940M}.}
+Tidal truncation is responsible in shaping the substructure luminosity
+scaling parameter $\delta$. Here we only sketch out qualitative
+arguments and leave details and comparison to numerical simulations to
+future work. First, tidal effects truncate the subhalo profile
+primarily in the outer regions. As a result of this, the subhalo
+acquires a steeper logarithmic slope than the canonical 3 from the
+NFW-profile. Second, tidal stripping imposes a mass-dependency and
+should be stronger for smaller substructure.  The stripping efficiency
+(for an effective cross section $\sigma$) only depends on the ambient
+DM density of the host halo, $n_\rmn{dm}$, which implies a scaling of
+the mean free path of a subhalo of $x_\rmn{mfp} \propto 1/(n_\rmn{dm}
+\sigma)$. Since there is less mass at any given density for smaller
+substructures, modest density inhomogeneities within the host halo
+seen by the orbiting substructures cause a stronger mass loss of these
+smaller satellites. Third, the tidal truncation radius should be a
+function of host halo radius due to the increasing smooth density
+profile for smaller radii.  If we pick an effective host halo radius
+which dominates the luminosity contribution of the substructures and
+were to fit the tidally truncated subhalo density profile with an
+NFW-profile, the resulting $\rs$ would be biased toward lower values
+implying a higher concentration compared to an isolated halo. In order
+to reproduce our value of $\delta$, we would need a concentration mass
+relation of $c\propto M_\rmn{sub}^{-0.14}$ (employing the
+$L(M_{200},c)$ formula derived by reference
+\cite{2009PhRvL.103r1302P}).  As expected, this is steeper than the
+concentration-mass relation found for isolated halos on dwarf galaxy
+scales, $c \propto M_\rmn{vir}^{-0.06}$ \cite{2011arXiv1101.2020I}, as
+well as galaxy and cluster scales, $c \propto M_\rmn{vir}^{-0.098}$
+\cite{2008MNRAS.391.1940M}.
 
@@
 L_{200\sm} &=&  A_{\rmn{dm}} \int_{\rvir} \dd r' 4\pi r'^2 \rho^2(r')\,,\label{eq:Lsm}\\
- \frac{\dd L_\rmn{sub}}{\dd V} &=& a_0\,a_1\,C(\mvir)\,x^{a_2+a_1\,x^{a_2}}\,
+ \frac{\dd L_\rmn{sub}}{\dd V} &=& a_0\,a_1\,C(\mvir)\,x^{g(x)}\,
 \left[\frac{1+a_2\log(x)}{4\pi\,r^3}\right]\,,\nonumber\\
 \\
-x &=& r/\rvir\,.\label{eq:xvir}
+x &=& r/\rvir\,,\quad g(x) = a_2+a_1\,x^{a_2}\,.\label{eq:xvir}
 \end{eqnarray} 
-
-\C{Here, $A_{\rmn{dm}}$ is the particle physics factor and implicitly defined by Equation~\ref{eq:dflux}.}
-The different density profiles have some impact on the luminosity from
-annihilating DM, although the details of the density profile can be
-neglected compared to the dominating boost from substructures
-(assuming DM to be cold). In Fig.~\ref{fig:radial_lum} we compare the
-radial dependence of the accumulative luminosity from different smooth
-cluster density profiles to the boosted luminosity due to substructure
-for different mass scales. We recalculate the overdensity, $\rhos$,
-for the shallower density profile with $\beta=0.6$ and rescale the
-concentration parameter in Eq.~(\ref{eq:cfit}) with $300/160$
-\cite{2011ApJ...728L..39N} to account for the more centralized scale
-radius in cluster with a shallow inner slope. The emission of this
-profile with $\beta=0.6$ is about 30\% larger within $\rvir$ compared
-to a cuspy NFW ($\beta=1.0$).  This difference is built up within
-$0.1\rvir$ (i.e. close to $r_\s$). Hence the slope of the central part
-of a cluster has little influence for the DM luminosity within $\rvir$
-as long as the degeneracy in the lensing mass measurements with $r_\s$
+Here, $A_{\rmn{dm}} = q_{\rmn{sm},i}(\eg,R) / \rho(R)^2$ represents
+the particle physics, where $q_{\rmn{sm},i}(\eg,R)$ is defined by
+Eq.~(\ref{eq:q_sm}). The different density profiles have some impact
+on the luminosity from annihilating DM, although the details of the
+density profile can be neglected compared to the dominating boost from
+substructures (assuming DM to be cold). In Fig.~\ref{fig:radial_lum}
+we compare the radial dependence of the accumulative luminosity from
+different smooth cluster density profiles to the boosted luminosity
+due to substructure for different mass scales. We recalculate the
+overdensity, $\rhos$, for the shallower density profile with
+$\beta=0.6$ and rescale the concentration parameter in
+Eq.~(\ref{eq:cfit}) with $300/160$ \cite{2011ApJ...728L..39N} to
+account for the more centralized scale radius in cluster with a
+shallow inner slope. The emission of this profile with $\beta=0.6$ is
+about 30\% larger within $\rvir$ compared to a cuspy NFW
+($\beta=1.0$).  This difference is built up within $0.1\rvir$
+(i.e. close to $r_\s$). Hence the slope of the central part of a
+cluster has little influence for the DM luminosity within $\rvir$ as
+long as the degeneracy in the lensing mass measurements with $r_\s$
 (which decreases for decreasing inner slope) has been taken into
@@
 photons is smaller which causes the substructure boost over the smooth
-emission to be reduced by roughly two orders of magnitudes. \C{It
-  should also be noted that the substructure boosted fluxes from
-  clusters are much more extended than for dwarf galaxies, hence more
-  difficult to detect with Cherenkov telescopes. In fact, it was shown
-  in Sanchez-Conde et al. \cite{2011arXiv1104.3530S} that inside
-  $0.1$~deg, where the sensitivity of Cherenkov telescopes is
-  maximized, the expected DM flux including substructures from the
-  brightest dwarf galaxy is about an order magnitude higher than the
-  brightest cluster. However, that work assumed a substructure boost
-  of about 50 in the most massive cluster halos which is more than an
-  order magnitude smaller than what we use in this work, hence in
-  projection we expect this difference to be a factor few smaller.}
+emission to be reduced by roughly two orders of magnitudes. It should
+also be noted that the substructure boosted fluxes from clusters are
+much more extended than for dwarf galaxies, hence more difficult to
+detect with Cherenkov telescopes. In fact, it was shown in
+Sanchez-Conde et al. \cite{2011arXiv1104.3530S} that inside $0.1$~deg,
+where the sensitivity of Cherenkov telescopes is maximized, the
+expected DM flux including substructures from the brightest dwarf
+galaxy is about an order magnitude higher than the brightest
+cluster. However, that work assumed a substructure boost of about 50
+in the most massive cluster halos which is more than an order
+magnitude smaller than what we use in this work, hence in projection
+we expect this difference to be a factor few smaller.
 
@@
 differential spectrum $\dd N_\e^f/\dd \ee$ that represents the number
-of electrons plus positrons resulting from an annihilation
-event. \del{For neutralinos annihilating directly into electrons and
-  positrons we model the spectral distribution with $\dd N_\e^f/\dd
-  \ee= 2\delta(\ee-m_\chi c^2)$.} \C{We use the differential spectra
-  derived from high-statistics simulations in
-  \cite{2011JCAP...03..019C,2011JCAP...03..051C} to compute the
+of electrons plus positrons resulting from an annihilation event. We
+use the differential spectra derived from high-statistics simulations
+in \cite{2011JCAP...03..019C,2011JCAP...03..051C} to compute the
 cumulative number of electrons and positrons resulting from
@@
 $\mu^+/\mu^-$ pairs in the LP model. We use \ds to compute the
-  $e^+/e^-$ spectra from our four BM models where only a fraction of
-  the annihilating neutralinos is converted into electrons and
-  positrons (see Sect.~\ref{sect:PF} and Fig.~\ref{fig:q_DM} for
-  further details).}
+$e^+/e^-$ spectra from our four BM models where only a fraction of the
+annihilating neutralinos is converted into electrons and positrons
+(see Sect.~\ref{sect:PF} and Fig.~\ref{fig:q_DM} for further details).
 %(see \cite{2009JCAP...01..016B} and references therein,
@@
 
-\C{We compare the calculated fluxes to gamma-ray upper limits (95\%
-  c.l.) set by \Fermi-LAT after 18 months of observations
-  \cite{2010ApJ...717L..71A}. In particular, to achieve a more
-  reliable comparison we adopt, if nothing else is stated, the maximal
-  spatially extended limits since the gamma-ray flux from our
-  brightest clusters all have an angular extent $>1^\circ$ on the sky
-  when the boost from substructures is included. In fact, published
-  \Fermi upper limits are not derived for the kind of extended
-  emission that we find with our treatment of substructures, hence
-  these \Fermi limits may not be adequate for some of these
-  clusters. This and other recent work highlights that the improved
-  substructure models imply that \Fermi limits will have to be
-  re-calculated to accommodate for the large source extensions. Note,
-  however, that for most clusters the assumption of a point source is
-  well justified.  The flux upper limits, that we compare to, are a
-  function of spectral index $\alpha$. However, in the relevant energy
-  range, $0.1-100$~GeV, the spectral index varies within $1.5 < \alpha
-  < 3.0$. This changes the photon flux upper limits by $<50\%$, with
-  \Fermi-LAT being more sensitive to a hard spectrum
-  \cite{2010ApJ...717L..71A}.}
-
-\del{For simplicity, we adopt the upper limits
-  calculated for a spectral index $\alpha=2$ and estimate the change in the
-  differential upper limits for each gamma-ray model and energy range using:
-\begin{eqnarray}
-\frac{\dd F_\gamma}{\dd \eg} &=& K\,\eg^{-\alpha}\,,\quad F_\gamma = 
-K\,\eg^{1-\alpha}\,,\nonumber\\
-\bra\eg \,F_\gamma\ket &=& K\,
-\frac{\displaystyle\int \dd E\, \eg^{1-\alpha}}{\displaystyle\int \dd \eg}
-= \frac{K}{2-\alpha}\,
-\frac{E_{\gamma,2}^{2-\alpha}-E_{\gamma,1}^{2-\alpha}}{E_{\gamma,2}-E_{\gamma,1}}\,,\nonumber\\
-%\bra\eg \,F_\gamma\ket &=& K\,\frac{\sum \dd \eg^{2-\alpha}}{\sum \dd \eg}
-%= K\,\frac{\sum \dd \eg^{2-\alpha}}{E_{\gamma,2}-E_{\gamma,1}}\,,\nonumber\\
-\label{eq:spec_ind_UL}
-\end{eqnarray}
-where $E_{\gamma,1}$ and $E_{\gamma,2}$ are the upper and lower energy
-limits, respectively. In the 1-10~GeV energy range we find that the
-upper limits for $($LP,BM,CR$)$ change by a factor
-$(1.10,\,0.71,\,1.15)$ where we have used the spectral indices
-$(2.20,\,1.22,\,2.24)$, respectively. See
-Table~\ref{tab:spectral_index} for additional spectral indices.}
+We compare the calculated fluxes to gamma-ray upper limits (95\% c.l.)
+set by \Fermi-LAT after 18 months of observations
+\cite{2010ApJ...717L..71A}. In particular, to achieve a more reliable
+comparison we adopt, if nothing else is stated, the maximal spatially
+extended limits since the gamma-ray flux from our brightest clusters
+all have an angular extent $>1^\circ$ on the sky when the boost from
+substructures is included. In fact, published \Fermi upper limits are
+not derived for the kind of extended emission that we find with our
+treatment of substructures, hence these \Fermi limits may not be
+adequate for some of these clusters. This and other recent work
+highlights that the improved substructure models imply that \Fermi
+limits will have to be re-calculated to accommodate for the large
+source extensions. Note, however, that for most clusters the
+assumption of a point source is well justified.  The flux upper
+limits, that we compare to, are a function of spectral index
+$\alpha$. However, in the relevant energy range, $0.1-100$~GeV, the
+spectral index varies within $1.5 < \alpha < 3.0$. This changes the
+photon flux upper limits by $<50\%$, with \Fermi-LAT being more
+sensitive to a hard spectrum \cite{2010ApJ...717L..71A}.
 
@@
 models and contrast it to the emission induced by CRs. Comparing this
-emission to the differential gamma-ray upper limits set by \Fermi-LAT
-\del{after 18 months of observations \cite{2010ApJ...717L..71A}}, we
-find that the upper limits are not violated. The predicted DM flux
+emission to the differential gamma-ray upper limits set by \Fermi-LAT,
+we find that the upper limits are not violated. The predicted DM flux
 that is dominated by the continuum emission from $\Kp$ and $\Ip$
-models (shown in the left panels) \C{are about an order of magnitude
-  below the upper limits, making it hard for \Fermi to probe these kind
-  of DM models without a significant improvement in the analysis from
-  e.g. stacking of clusters and improved methods for analyzing
-  extended sources.}  Furthermore, the gamma-ray signal induced by CRs
-is expected to be about a factor 5--10 below the DM continuum flux
-from the $\Kp$ and $\Ip$ BM models at 10~GeV. However, the IC emission
-from upscattered CMB and SD photons is at least a factor of a few
-lower for $\Kp$ and a factor 1000 lower for $\Ip,\Jp,\Js$, than the
-expected flux from CRs above 100~MeV, making it very hard to
+models (shown in the left panels) are about \C{a factor few} below the
+upper limits, making it hard for \Fermi to probe these kind of DM
+models \C{in the near future} without a significant improvement in the
+analysis from e.g. stacking of clusters and improved methods for
+analyzing extended sources. Furthermore, the gamma-ray signal induced
+by CRs is expected to be about a factor 10 below the DM continuum
+flux from the $\Kp$ and $\Ip$ BM models at 10~GeV. However, the IC
+emission from upscattered CMB and SD photons is at least a factor of a
+few lower for $\Kp$ and a factor 1000 lower for $\Ip,\Jp,\Js$, than
+the expected flux from CRs above 100~MeV, making it very hard to
 distinguish such a signal from the foreground due to the similar
@@
 leptons. Hence in clusters, the IC emission from supersymmetric DM BM
-models can be neglected compared to the CR pion and DM continuum emission.
+models can be neglected compared to the CR pion and DM continuum
+emission.
 
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v13.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v13.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v13.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v13.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompI.v14.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJ.v14.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompK.v14.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v14.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
 \caption{\it Comparing the differential flux from different models: we
@@
   the gamma-ray flux from IC upscattered CMB and continuum emission by
-  a factor of 730 while the IC upscattered SD photons are only boosted
-  by 20. Extended upper limits ($<1^\circ$) from \Fermi-LAT after 18 months \protect
-  \cite{2010ApJ...717L..71A} are also shown. \C{We find it hard to
-    detect even the brightest BM models, $\Ip$ and $\Kp$, where the
-    continuum emission is dominating the total emission in the
-    GeV energy range.}}
+  a factor of 890 while the IC upscattered SD photons are only boosted
+  by 20. Extended upper limits ($<1^\circ$) from \Fermi-LAT after 18
+  months \protect \cite{2010ApJ...717L..71A} are also shown. \C{In the
+    near future} we find it hard to detect even the brightest BM
+  models, $\Ip$ and $\Kp$, where the continuum emission is dominating
+  the total emission in the GeV energy range.}
  \label{fig:diff_BM}
@@
 IC upscattered SD increases by a factor $\sim 30$ (see
-Fig.~\ref{fig:IR_comp})\footnote{\C{Note that for the leptophilic DM
-    model this increase is much smaller since Sommerfeld enhancement
-    is no longer dominated by the low velocity DM particles living in
-    the subhalos (see Sect.~\ref{sect:LP} for more details).}}.  A
-larger fraction of electrons (in the core) will now also cool by
+Fig.~\ref{fig:IR_comp})\footnote{Note that for the leptophilic DM
+  model this increase is much smaller since Sommerfeld enhancement is
+  no longer dominated by the low velocity DM particles living in the
+  subhalos (see Sect.~\ref{sect:LP} for more details).}.  A larger
+fraction of electrons (in the core) will now also cool by
 Compton-upscattering SD photons which suppresses the IC-upscattered
@@
 10^5$), we overproduce the upper gamma-ray limit in the $1-10$~GeV
-energy interval set by \Fermi-LAT by about a factor 50. This strongly
+energy interval set by \Fermi-LAT by about a factor 100. This strongly
 constrains the boost from both substructures and the
@@
 \begin{minipage}{2.0\columnwidth}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v13.0.1deg.1.6T.SubMass.elmu.SF700.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv13.0.1deg.SubMass.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v14.0.1deg.1.6T.SubMass.elmu.SF700.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv14.0.1deg.SubMass.noMW.woGal.eps}
 \caption{\it Comparing the flux from different inverse Compton
@@
   indicating that the LP model assumptions such as Sommerfeld and/or
-  substructure boost are in conflict with the upper limit. \del{We
-    also show projected CTA point source sensitivities ($5\sigma$,
-    50h).}  All fluxes are calculated for the Fornax cluster within
-  $\rvir$ using a point spread function of $0.1\deg$. \C{For this
-    cluster, the enhancement due to substructures from IC upscattered
-    CMB and SD photons is 730. The saturated Sommerfeld boost is 530.}}
+  substructure boost are in conflict with the upper limit. All fluxes
+  are calculated for the Fornax cluster within $\rvir$ using a point
+  spread function of $0.1\deg$. For this cluster, the enhancement due
+  to substructures from IC upscattered CMB and SD photons is 890. The
+  saturated Sommerfeld boost is 530.}
  \label{fig:IR_comp}
@@
 in conflict with the upper limits by \Fermi-LAT, although only by a
-factor of 10 which is about a order magnitude less constraining than
-the differential flux in the energy range $1-10$~GeV. As shown in this
+factor of 30 which is \C{a factor few} less constraining than the
+differential flux in the energy range $1-10$~GeV. As shown in this
 figure, the LP model is dominating the entire gamma-ray energy range
@@
 we note that the flux the DM BM $\Kp$ model is larger than the
-predicted emission from the CRs in the $1-100$~GeV energy
-regime. \C{Hence, for an experiment with a high sensitivity even
-  for extended sources, the prospects for detecting the $\Kp$ BM model
-  over the expected gamma-ray background induced by CRs looks
-  promising in clusters. Present day Cherenkov telescopes, however,
-  have a trigger region that is smaller than the size of clusters,
-  hence it has to be increased to several degrees to overcome problems
-  with background estimation. In addition, even though the projected
-  CTA point source sensitivity ($5\sigma$, 50h) shows the potential of
-  this experiment in constraining leptophilic models as well as BM
-  models with a very large neutralino mass $m_\chi c^2 \gtrsim 1$~TeV,
-  we find that analysis techniques have to be developed that enable
-  the detection of extended sources without too much degradation of
-  sensitivity.}
+predicted emission from the CRs in the $0.1-100$~GeV energy
+regime. Hence, for an experiment with a high sensitivity even for
+extended sources, the prospects for detecting the $\Kp$ BM model over
+the expected gamma-ray background induced by CRs looks promising in
+clusters. Present day Cherenkov telescopes, however, have a trigger
+region that is smaller than the size of clusters, hence it has to be
+increased to several degrees to overcome problems with background
+estimation. In addition, even though the projected CTA point source
+sensitivity ($5\sigma$, 50h) shows the potential of this experiment in
+constraining leptophilic models as well as BM models with a very large
+neutralino mass $m_\chi c^2 \gtrsim 1$~TeV, we find that analysis
+techniques have to be developed that enable the detection of extended
+sources without too much degradation of sensitivity.
 
 \begin{figure}
- \includegraphics[width=0.99\columnwidth]{figures/flux.int.v13.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/flux.int.v14.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
  \caption{\it Comparing the energy integrated flux from different
@@
    Fornax cluster using a point spread function of $0.1\deg$. The
-   boost from Sommerfeld and substructures is about 530 and 730,
+   boost from Sommerfeld and substructures is about 530 and 890,
    respectively.}
@@
 from the Fornax and Virgo clusters, which confirms them as promising
-targets for indirect DM searches. \C{Especially in the $1-10$~GeV
-  energy range it is quite striking how constraining the upper limits
-  are for some of the clusters. At these energies, \Fermi-LAT has its
-  peak sensitivity due to a combination of increasing effective area
-  and decreasing source spectra as a function of energy. The upper
-  limits for Virgo and Perseus are unfortunately background
-  contaminated by AGN activity from M87 and NGC 1267, respectively,
-  and do not gain much from the increased sensitivity. In addition,
-  the angular radius of Virgo is about $6^\circ$, while the extended
-  upper limit from \Fermi-LAT is calculated assuming a
-  $\sigma=1.2^\circ$ radius. In fact, the ratio of the virial radius
-  to the assumed extension for the upper limits $\rvir/\sigma$ for
-  $($Fornax, Coma, Virgo$)$ are $(2.8,\,1.6,\,5.3)$,
-  respectively. Similarly, it is interesting to compare the radius
-  that contains 68\% of the flux to the assumed extension,
-  $r_{68}/\sigma$, which is given by $(1.7,\,1.0,\,3.3)$ for
+targets for indirect DM searches. Especially in the $1-10$~GeV energy
+range it is quite striking how constraining the upper limits are for
+some of the clusters. At these energies, \Fermi-LAT has its peak
+sensitivity due to a combination of increasing effective area and
+decreasing source spectra as a function of energy. The upper limits
+for Virgo and Perseus are unfortunately background contaminated by AGN
+activity from M87 and NGC 1267, respectively, and do not gain much
+from the increased sensitivity. In addition, the angular radius of
+Virgo is about $6^\circ$, while the extended upper limit from
+\Fermi-LAT is calculated assuming a $\sigma=1.2^\circ$ radius. In
+fact, the ratio of the virial radius to the assumed extension for the
+upper limits $\rvir/\sigma$ for $($Fornax, Coma, Virgo$)$ are
+$(3.7,\,1.6,\,5.3)$, respectively. Similarly, it is interesting to
+compare the radius that contains 68\% of the flux to the assumed
+extension, $r_{68}/\sigma$, which is given by $(2.3,\,1.0,\,3.3)$ for
 $($Fornax, Coma, Virgo$)$, respectively. This further motivates a
 re-calculation of the \Fermi upper limits to account for the full
-  extension of the galaxy clusters.}  \del{Note, however, that we have
-  used spatially unresolved upper limits, which is quite optimistic
-  for the Virgo cluster which has an angular extended of $7^\circ$. It
-  is quite striking how constraining the upper limits are for the
-  Fornax cluster are compared to the other clusters, especially in the
-  $1-10$~GeV energy regime.}  \C{We also find that the theoretical
+extension of the galaxy clusters. We also find that the theoretical
 expectation of a high CR-induced flux in Coma and Perseus may
-  significantly complicate indirect DM searches in those clusters if
-  the boost factors are much lower than assumed in this work.} \del{is
-  of the same magnitude as the DM flux from LP models, making it
-  difficult for indirect DM searches in those clusters.
-  The Fornax cluster, however,} is a great target for indirect DM
-studies because the relative low gamma-ray flux from CRs, absents of
-an active AGN, and high DM gamma-ray flux. \del{The \Fermi-LAT
-  three-year data will be able to constrain the smallest mass of
-  substructures using the DM BM models.}
+significantly complicate indirect DM searches in those clusters if the
+boost factors are much lower than assumed in this work. The Fornax
+cluster, however, is a great target for indirect DM studies because
+the relative low gamma-ray flux from CRs, absents of an active AGN,
+and high DM gamma-ray flux.
 
@@
 \end{equation}
-\del{and the total DM luminosity that includes boost factors for the LP and
-the BM models are given by}
-%\begin{eqnarray}
-%\label{eq:LP_scaling}
-%L_{\gamma,\rmn{LP}} &=& L_{\gamma,\rmn{smLP}} \B_\rmn{LP} \propto \frac{\mvir^{0.73}}{D_\rmn{lum}^2},\\
-%\label{eq:BM_scaling}
-%L_{\gamma,\rmn{BM}} &=& L_{\gamma,\rmn{smBM}} \B_\rmn{BM} \propto  \frac{\mvir^{1.06}}{D_\rmn{lum}^2},\\
-%\B_\rmn{LP}&=&\B_\sfe \B_\sub \propto \mvir^{-1/3}\mvir^{0.23} \propto
-% \mvir^{-0.1}\,,\\
-%\B_\rmn{BM}&=&\B_\sub \propto \mvir^{0.23}\,.
-%\end{eqnarray}
-\del{Hence, increasing the cluster mass in the BM model by a factor two
-more than doubles the luminosity, but increasing the luminosity
-distance, $D_\rmn{lum}$, by a factor two decrease the flux by a factor
-four. We note that the IC from upscattered SD photons scales slightly
-softer with mass, hence gives rise to a larger fraction of gamma-rays
-in low mass clusters compared to the total gamma-ray flux.}
-\C{and the total DM luminosity that includes boost factors for the LP and
+and the total DM luminosity that includes boost factors for the LP and
 the BM models is given by
@@
 \begin{eqnarray}
-L_{\gamma,LP~nosub} &=& L_{\gamma,\rmn{sm}} \B_\rmn{sfe} 
+L_{\gamma,\rmn{LP~nosub}} &=& L_{\gamma,\rmn{sm}} \B_\rmn{sfe} 
 \propto \frac{\mvir^{0.5}}{D_\rmn{lum}^2},\\
 \rmn{where} &\quad&\B_\rmn{sfe} \propto \mvir^{-1/3}.
-\end{eqnarray}}
+\end{eqnarray}
 
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v13.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v13.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v13.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v13.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Fornax.v14.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Coma.v14.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Virgo.v14.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v14.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
 \caption{\it Comparing the gamma-ray emission from different
-  clusters. We show the differential flux of clusters \C{in the upper
-    panel of each figure}: Fornax (upper left), Coma (upper right),
-  Virgo (lower left), and Perseus (lower right). We show CR induced
-  emission (red solid), a leptophilic (LP) model that includes both
-  final state radiation and IC upscattered CMB, dust and starlight
-  (green dash-dotted), and the benchmark $\Kp$ model (BM) that
-  includes continuum emission, and IC upscattered CMB, dust and
-  starlight (blue dashed). The arrows show the spatially extended
-  differential upper limits set by \Fermi-LAT in the energy ranges
-  $0.2-1$~GeV, $1-10$~GeV, and $10-100$~GeV from left to right
-  \C{(using Gau{\ss} profiles for the source extension with
-    $\sigma=\{1.2,1.0,0.8\}$ for \{Virgo, Coma, Fornax\} and an
-    X-ray-inferred King profile for Perseus)
-    \cite{2010ApJ...717L..71A}}. We show the individual components for
-  the BM model and LP model for Virgo and Perseus, respectively. \C{In
-    the lower panel of each figure we show differential spectral
-    indices, $\alpha_\gamma$, where $\dd F_\gamma/\dd E_\gamma \sim
-    E_\gamma^{-\alpha_\gamma}$.}  The flux from the clusters is
+  clusters. We show the differential flux of clusters in the upper
+  panel of each figure: Fornax (upper left), Coma (upper right), Virgo
+  (lower left), and Perseus (lower right). We show CR induced emission
+  (red solid), a leptophilic (LP) model that includes both final state
+  radiation and IC upscattered CMB, dust and starlight (green
+  dash-dotted), and the benchmark $\Kp$ model (BM) that includes
+  continuum emission, and IC upscattered CMB, dust and starlight (blue
+  dashed). The arrows show the spatially extended differential upper
+  limits set by \Fermi-LAT in the energy ranges $0.2-1$~GeV,
+  $1-10$~GeV, and $10-100$~GeV from left to right (using Gauss
+  profiles for the source extension with $\sigma=\{1.2,1.0,0.8\}$ for
+  \{Virgo, Coma, Fornax\} and an X-ray-inferred King profile for
+  Perseus) \cite{2010ApJ...717L..71A}. We show the individual
+  components for the BM model and LP model for Virgo and Perseus,
+  respectively. In the lower panel of each figure we show differential
+  spectral indices, $\alpha_\gamma$, where $\dd F_\gamma/\dd E_\gamma
+  \sim E_\gamma^{-\alpha_\gamma}$. The flux from the clusters is
   integrated out to $\rvir$ using a point spread function of $0.1\deg$
@@
   of \Fermi at these energies and use this regime to get upper limits
-  on boost factors.}
+  on boost factors. \C{Also notice that the CR induced emission in
+    Coma is close to the upper limits set by \Fermi and will be tested
+    in the coming years.}}
  \label{fig:clu_comp}
@@
 
-\C{In the lower panels of Fig.~\ref{fig:clu_comp}, we also provide the
-  differential spectral index, $\alpha_\gamma=-\dd \log(\dd F/\dd
-  E)/\dd \log(E)$, for the different emission models. We find very
-  similar spectral indices for different clusters assuming a
-  substantial boost from substructures, while for models without
-  substructures the relative contribution from the upscattered dust
-  and starlight breaks the spectral universality for the DM models. In
-  the $1~\gev-1~\tev$ energy regime the CR spectral index is
-  approximately constant $\sim (2.1-2.3)$, while the spectral index
-  for the LP model varies substantially between $1.2-4.0$, hence
-  implying that gamma-ray upper limits are more sensitive to the
-  specific energy regime for these models. Similarly, the index for
-  the BM $\Kp$ model is about 1.0 at 1~GeV and increases monotonically
-  toward higher energies. To maximize photon count statistics,
-  experiments calculate band-integrated fluxes which implies a fixed
-  spectral index over that energy range. Hence, we show $\alpha_\gamma$ in
-  Table~\ref{tab:spectral_index} for our emission models in four
-  different energy bands. We find smaller variations for the banded
-  $\alpha_\gamma$-values, hence reducing the importance of the specific
-  energy regimes.}
-
-\del{ For further discussion about the impact of different
-  spectral indices on the gamma-ray upper limits see
-  Eq.~(\ref{sect:spectral}) and related text.}
+In the lower panels of Fig.~\ref{fig:clu_comp}, we also provide the
+differential spectral index, $\alpha_\gamma=-\dd \log(\dd F/\dd E)/\dd
+\log(E)$, for the different emission models. We find very similar
+spectral indices for different clusters assuming a substantial boost
+from substructures, while for models without substructures the
+relative contribution from the upscattered dust and starlight breaks
+the spectral universality for the DM models. In the $1~\gev-1~\tev$
+energy regime the CR spectral index is approximately constant $\sim
+(2.1-2.3)$, while the spectral index for the LP model varies
+substantially between $1.2-4.0$, hence implying that gamma-ray upper
+limits are more sensitive to the specific energy regime for these
+models. Similarly, the index for the BM $\Kp$ model is about 1.0 at
+1~GeV and increases monotonically toward higher energies. To maximize
+photon count statistics, experiments calculate band-integrated fluxes
+which implies a fixed spectral index over that energy range. Hence, we
+show $\alpha_\gamma$ in Table~\ref{tab:spectral_index} for our
+emission models in four different energy bands. We find smaller
+variations for the banded $\alpha_\gamma$-values, hence reducing the
+importance of the specific energy regimes.
 
@@
 \end{tabular}
-\caption{\C{Banded gamma-ray spectral index $\alpha_{E_1}^{E_2}$ between
+\caption{Banded gamma-ray spectral index $\alpha_{E_1}^{E_2}$ between
   energies $E_1$ and $E_2$. We show the spectral index for three
   different emission models where the boost from substructures is
-    included; the CR induced emission, the leptophilic (LP) model
-    that includes both final state radiation and IC upscattered CMB,
-    dust and starlight, and the benchmark (BM) $\Kp$ model that
-    includes continuum emission, and IC upscattered CMB, dust and
-    starlight. $\alpha_\gamma$-values are derived for the Fornax cluster,
-    although the variance between clusters is very small when we account for the
-    enhancement from substructures. This  suppresses the
-    relative contribution from the upscattered dust and starlight
-    component that depends on  cluster mass. \label{tab:spectral_index}}}
+  included; the CR induced emission, the leptophilic (LP) model that
+  includes both final state radiation and IC upscattered CMB, dust and
+  starlight, and the benchmark (BM) $\Kp$ model that includes
+  continuum emission, and IC upscattered CMB, dust and
+  starlight. $\alpha_\gamma$-values are derived for the Fornax
+  cluster, although the variance between clusters is very small when
+  we account for the enhancement from substructures. This suppresses
+  the relative contribution from the upscattered dust and starlight
+  component that depends on cluster mass. \label{tab:spectral_index}}
 \end{table}
@@
 excess of electrons and positrons observed in the vicinity of Earth by
-PAMELA/\Fermi/H.E.S.S. In Fig.~\ref{fig:boost_const} we use the estimated
-flux \C{within $\rvir$ of four bright and maximal constraining
-  clusters (Fornax, M49, Norma, and Coma, where we have excluded Virgo
-  due to its large angular extent) to limit} the SFE as well as the
+PAMELA/\Fermi/H.E.S.S. In Fig.~\ref{fig:boost_const} we use the
+estimated flux within $\rvir$ of four bright and maximal constraining
+clusters (Fornax, M49, NGC4636, and Coma, where we have excluded Virgo
+due to its large angular extent) to limit the SFE as well as the
 minimum mass of substructures where
@@
   limits.}  $1-10$~GeV, we can constrain the smallest mass of
-substructures to $M_\rmn{lim}\gtrsim 10\,\msun$. Instead, assuming the
-standard mass of the smallest substructures of $M_\rmn{lim}\approx
-10^{-6}\,\msun$, we can constrain the \C{saturated boost from SFE to
-  about 14 in M49 and 22 in Fornax, which corresponds to a maximum SFE
-  in the MW of about 8 and 13, respectively. Hence, we conclude that
-  without substantial improvement in the modelling of these extended
-  sources, \Fermi-LAT will not be able to rule out LP models in their
-  current form using clusters.} \del{Note that after about six years
-  of observations with \Fermi-LAT, we will be able to rule out the LP
-  model assuming a substructure boost with a smallest mass of
-  $M_\rmn{lim} \approx 10^{-6}\,\msun$.}
+substructures to $M_\rmn{lim}\gtrsim 10^4\,\msun$. Instead, assuming
+the standard mass of the smallest substructures of $M_\rmn{lim}\approx
+10^{-6}\,\msun$, we can constrain the saturated boost from SFE to
+about \C{5 in M49 and Fornax}, which corresponds to a maximum SFE in the
+MW of about 3. Hence, we conclude that without substantial improvement
+in the modelling of these extended sources, \Fermi-LAT will not be
+able to rule out LP models in their current form using clusters.
 
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v13.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v14.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
  \caption{\it Constraining boost factors using flux upper limits. The
@@
    a point spread function of $0.1\deg$. In order not to overproduce
-   the \Fermi-LAT differential flux upper limits in the energy interval
-   $1-10$~GeV the boost from substructures and Sommerfeld enhancement
-   (SFE) is constrained for four clusters; Fornax (red), Norma
-   (orange), M49 (green), and Coma (blue). \C{We indicate both the
-     saturated SFE of 530 (right black arrow) as well as the the local
+   the \Fermi-LAT differential flux upper limits in the energy
+   interval $1-10$~GeV the boost from substructures and Sommerfeld
+   enhancement (SFE) is constrained for four clusters; Fornax (red),
+   NGC4636 (orange), M49 (green), and Coma (blue). We indicate both
+   the saturated SFE of 530 (right black arrow) as well as the local
    boost in the Milky Way of 300 (c.f. Eq.~\ref{eq:B_sfe}) that is
@@
    correct, we can constrain the smallest size of halos to be larger
-     than $10\,\msun$. Contrarily, if the smallest size of DM halos is
-     $10^{-6}\,\msun$, we can constrain the SFE to about 14 in M49 and
-     22 in Fornax. This corresponds to a maximum SFE in the MW of
-     about 8 and 13, respectively, which would be too small to support
-     the DM annihilation hypothesis for the PAMELA/\Fermi excess.}}
+   than $10^4\,\msun$. Contrarily, if the smallest size of DM halos is
+   $10^{-6}\,\msun$, we can constrain the SFE to about 5 in M49 and
+   Fornax. This corresponds to a maximum SFE in the MW of about 3,
+   which would be too small to support the DM annihilation hypothesis
+   for the PAMELA/\Fermi excess.}
  \label{fig:boost_const}
@@
 annihilating DM is independent of the type of DM model, and can not be
-used to separate different models. The surface brightness, $S_\gamma$,
-of the DM scales as $S_\gamma\propto\bsub L_{\gamma} \mvir^{-2/3}
-\propto \mvir^{0.59}$, which explains the factor three difference in
+used to separate different models. \C{The surface brightness, $S_\gamma$,
+of the DM scales as $S_\gamma\propto L_{\gamma,\rmn{sm}}\bsub\mvir^{-2/3}
+\propto \mvir^{0.40}$}, which explains the factor \C{two} difference in
 normalization between the most massive cluster Coma and the least
-massive cluster Fornax with a mass ratio of about 10. \del{The flux
-  from the LP model shows a smaller spread in the normalization which
-  is due to the additional contribution from SFE with a negative mass
-  trend, hence a flux normalization with a softer mass-scaling of
-  $S_\gamma\propto\mvir^{0.06}$.} The surface brightness induced by
-CRs is proportional to the projected squared gas profile with an
-additional enhancement in the center of cool core clusters due to the
-adiabatic compression of CRs during the formation of the cool
-core. Hence, we see a much larger variation in these profiles driven
-by the large variation of the gas mass fraction. It is noticeable that
-Fornax shows such a small surface brightness. This is explained by the
-low gas density outside the BCG and the less abundant CR population in
-a small cluster compared to a massive cluster
+massive cluster Fornax with a mass ratio of about 10. The surface
+brightness induced by CRs is proportional to the projected squared gas
+profile with an additional enhancement in the center of cool core
+clusters due to the adiabatic compression of CRs during the formation
+of the cool core. Hence, we see a much larger variation in these
+profiles driven by the large variation of the gas mass fraction. It is
+noticeable that Fornax shows such a small surface brightness. This is
+explained by the low gas density outside the BCG and the less abundant
+CR population in a small cluster compared to a massive cluster
 \cite{2010MNRAS.409..449P}.  This is the reason why Fornax is such a
@@
 \begin{figure}
- \includegraphics[width=0.99\columnwidth]{figures/SB.v13.1GeV.SF700.SubMass.elmu.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.v14.1GeV.SF700.SubMass.elmu.eps}
  \caption{\it Comparing the intrinsic surface brightness from
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v13.1GeV.SF700.noSuB.vs.SubMass.elmu.eps}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v14.1GeV.SF700.noSuB.vs.SubMass.elmu.eps}
  \caption{\it The impact of substructures on the intrinsic surface
@@
    excluded for the dotted lines. The boost from Sommerfeld
-   \C{enhancement with and without substructures is 130 and 530
-     respectively. The boost due to substructures is
-     about 730.} Notice the nearly flat profiles when substructures
-   are included, and the relative large boost at $0.01\rvir$ that is
-   due to projection of peripheral substructures onto the cluster
-   center.}
+   enhancement with and without substructures is 110 and 530
+   respectively. The boost due to substructures is about 890. Notice
+   the nearly flat profiles when substructures are included, and the
+   relative large boost at $0.01\rvir$ that is due to projection of
+   peripheral substructures onto the cluster center.}
  \label{fig:SB_sub}
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.v13.1GeV.SF700.noSuB.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v13.1GeV.SF700.noSuB.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.v14.1GeV.SF700.noSuB.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v14.1GeV.SF700.noSuB.elmu.eps}
   \caption{\it The intrinsic surface brightness profiles without
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v13.SF700.SubMass.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v13.SF700.SubMass.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v14.SF700.SubMass.elmu.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v14.SF700.SubMass.elmu.eps}
 \caption{\it Surface brightness predicted for Cherenkov telescopes at
@@
   \includegraphics[width=0.99\columnwidth]{figures/MLscaling.10G.eps}
-  \caption{\it Scaling relations of the cluster's virial mass $\mvir$ and the
-    gamma-ray luminosity for energies $E_\gamma>100$~MeV (left) and
-    $E_\gamma>10$~GeV (right).  Shown are the relations for the CR-induced
-    emission that is dominated by pion decay resulting from hadronic CR
-    interactions (solid), the leptophilic model of DM annihilations
-    \C{(dash-dotted) as well as the benchmark model $K'$ of DM
-      annihilation. Both DM models include the scaling of the substructure boost
-      with cluster mass of Eq.~(\ref{eq:DM_scaling}) (dashed). Note that the
-      scaling of the DM models are indicative for all DM annihilation models (as
-      long as there is no additional mass scaling from, e.g., non-saturated SFE
-      models) while the normalization depends on the particular cross section
-      and neutralino mass.}}
+  \caption{\it Scaling relations of the cluster's virial mass $\mvir$
+    and the gamma-ray luminosity for energies $E_\gamma>100$~MeV
+    (left) and $E_\gamma>10$~GeV (right).  Shown are the relations for
+    the CR-induced emission that is dominated by pion decay resulting
+    from hadronic CR interactions (solid), the leptophilic model of DM
+    annihilations (dash-dotted) as well as the benchmark model $K'$ of
+    DM annihilation. Both DM models include the scaling of the
+    substructure boost with cluster mass of Eq.~(\ref{eq:DM_scaling})
+    (dashed). Note that the scaling of the DM models are indicative
+    for all DM annihilation models (as long as there is no additional
+    mass scaling from, e.g., non-saturated SFE models) while the
+    normalization depends on the particular cross section and
+    neutralino mass.}
 \label{fig:lum_mass_scaling}
 \end{figure*}
-\C{The mass scaling of the substructure boost steepens the
-  intrinsically shallower DM annihilation relation in
-  Eq.~(\ref{eq:DM_scaling}) to $L_\gamma\propto \mvir^{1.06}$.
-  However, the CR scaling relation is still considerably steeper as
-  shown by reference} \cite{2010MNRAS.409..449P}:
+The mass scaling of the substructure boost steepens the intrinsically
+shallower DM annihilation relation in Eq.~(\ref{eq:DM_scaling}) to
+$L_\gamma\propto \mvir^{1.06}$.  However, the CR scaling relation is
+still considerably steeper as shown by reference
+  \cite{2010MNRAS.409..449P}:
 \begin{eqnarray}
@@
 \end{eqnarray}
-Note that the CR luminosity scaling relations\footnote{The scaling relations
-  show the flux inside $\rvir$ and do not include the contribution from
-  galaxies. Also note that in this paper the scaling relations are normalized at
-  $10^{15}\,h_{70}^{-1}\,\msun$. \C{In contrast, the corresponding scaling
-    relations in Table 5 in \cite{2010MNRAS.409..449P} are normalized at
+Note that the CR luminosity scaling relations\footnote{The scaling
+  relations show the flux inside $\rvir$ and do not include the
+  contribution from galaxies. Also note that in this paper the scaling
+  relations are normalized at $10^{15}\,h_{70}^{-1}\,\msun$. In
+  contrast, the corresponding scaling relations in Table 5 in
+  \cite{2010MNRAS.409..449P} are normalized at
   $10^{15}\,h^{-1}\,\msun$ instead of the mentioned
   $10^{15}\,h_{70}^{-1}\,\msun$ in the caption. However, all
-    figures/tables/equations including the scaling relation figures are derived
-    for masses in units of $10^{15}\,h_{70}^{-1}\,\msun$.}}  include the IC
-gamma-ray contribution from shock-accelerated electrons as well as secondary
-electrons created in CR-proton interactions. The gamma-ray flux from the
-electrons is, however, dominated by the decaying neutral pions and only shows up
-as a small flattening of the scaling relation at energies around
-$10-100\,\gev$. The steeper mass scaling of CR emission compared to DM
-annihilation already implies a general strategy to minimize the CR-induced
-foreground for DM annihilation and argues for very nearby groups. We note that
-these simulations do not include AGN feedback that is thought to furthermore
+  figures/tables/equations including the scaling relation figures are
+  derived for masses in units of $10^{15}\,h_{70}^{-1}\,\msun$.}
+include the IC gamma-ray contribution from shock-accelerated electrons
+as well as secondary electrons created in CR-proton interactions. The
+gamma-ray flux from the electrons is, however, dominated by the
+decaying neutral pions and only shows up as a small flattening of the
+scaling relation at energies around $10-100\,\gev$. The steeper mass
+scaling of CR emission compared to DM annihilation already implies a
+general strategy to minimize the CR-induced foreground for DM
+annihilation and argues for very nearby groups. We note that these
+simulations do not include AGN feedback that is thought to furthermore
 reduce the baryon fraction in groups relative to that in clusters
-\cite{2008ApJ...687L..53P}. The resulting smaller target density for hadronic CR
-interactions steepens the $L_\gamma-M$ relation of CR induced emission, making
-the case for groups even stronger.
+\cite{2008ApJ...687L..53P}. The resulting smaller target density for
+hadronic CR interactions steepens the $L_\gamma-M$ relation of CR
+induced emission, making the case for groups even stronger.
 
@@
   \caption{\it \Fermi gamma-ray flux upper limits are contrasted to
-    predicted DM gamma-ray fluxes. We show the mean differential flux in
-    the energy range $E_\gamma=1-10$~GeV for 32 clusters. The
-    \C{maximally extended \Fermi-LAT upper limits are shown with black
-      arrows, while the point source limits are shown in grey.} The
+    predicted DM gamma-ray fluxes. We show the mean differential flux
+    in the energy range $E_\gamma=1-10$~GeV for 32 clusters. The
+    maximally extended \Fermi-LAT upper limits are shown with black
+    arrows, while the point source limits are shown in grey. The
     predicted fluxes are derived from the dominant inverse
@@
     mass spectrum extending down to an Earth mass, the expected
-    leptophilic fluxes are ruled out by upper limits in 26 of the
-    clusters, with the strongest constraints set by Fornax and
-    Ophiuchus. We can not yet constrain the benchmark models,
-    although improved modelling of extended sources as well as
-    stacking of clusters will allow to test these in the upcoming
-    years with better data.}
+    leptophilic fluxes are ruled out by upper limits in 28 of the
+    clusters, with the strongest constraints set by M49 and
+    Fornax. \C{We can not yet constrain the benchmark models, although
+      \Fermi-LAT start to probe these models within its lifetime. In
+      particular, improved modelling of extended sources as well as
+      stacking of clusters will push these test into the near
+      future.}}
  \label{fig14}
@@
    function of HIFLUGCS cluster ID. For comparison we show the
-   estimated point source sensitivity of the \Fermi-LAT after two years
-   of data taking $F_\gamma(>100\,\rmn{MeV})\sim
+   estimated point source sensitivity of the \Fermi-LAT after two
+   years of data taking $F_\gamma(>100\,\rmn{MeV})\sim
    2\times10^{-9}\,\rmn{ph}\, \rmn{cm}^{-2}\,\rmn{s}^{-1}$ and
@@
    \rmn{cm}^{-2}\,\rmn{s}^{-1}$ (dashed lines). The four brightest
-   clusters are labelled yielding Fornax and Ophiuchus as the
-   brightest targets.}
+   clusters are labelled yielding M49 and Fornax as the brightest
+   targets.}
  \label{fig21}
@@
 To obtain the gamma-ray fluxes, we scale the virial mass of clusters
-in the extended HIFLUGCS catalogue \cite{2002ApJ...567..716R} with our
+in the extended HIFLUGCS catalogue \cite{2007A&A...466..805C} with our
 scaling relation of Eq.~(\ref{eq:DM_scaling}). In those, we assume a
@@
 SFE. \Fermi limits rule out the LP models in their present form with
-the mentioned assumptions in 26 clusters, and limit the boost from SFE
-to less than 14 in M49. Assuming universality, this limits the
-Sommerfeld boost in the MW to less than 8 (see
+the mentioned assumptions in 28 clusters, and limit the boost from SFE
+to less than 5 in M49 and Fornax. Assuming universality, this limits
+the Sommerfeld boost in the MW to less than 3 (see
 Fig.~\ref{fig:boost_const}).  The flux level of the \Fermi limits are
@@
 cluster candidates for indirect DM experiments. We identify Fornax,
-M49, Norma, Coma, and Virgo to be prime candidates. Note however, that
+M49, NGC4636, and Virgo to be prime candidates. Note however, that
 Virgo extends of $12^\circ$ over the sky which implies a lower surface
@@
 extended while the sensitivity of Cherenkov telescopes scales
-\C{approximately linearly with source extension}. Hence the fluxes
+approximately linearly with source extension. Hence the fluxes
 quoted in Fig.~\ref{fig21} will have to be compared to a sensitivity
@@
     emission using an analytical CR model \protect
-    \cite{2010MNRAS.409..449P} to \Fermi-LAT flux upper limits. We show
-    the mean differential flux in the energy range $E_\gamma=1-10$~GeV
-    for 32 clusters. \C{The extended \Fermi upper limits assume King
-      profiles and are shown with black arrows, while the point source
-      limits are show with grey arrows.} The blue boxes show the
-    gamma-ray emission from CR-induced $\pi^0$-decay, where the upper
-    (lower) bounds show the estimates for an optimistic (conservative)
-    model (see Sect.~\ref{sec:CRemission} and
+    \cite{2010MNRAS.409..449P} to \Fermi-LAT flux upper limits. We
+    show the mean differential flux in the energy range
+    $E_\gamma=1-10$~GeV for 32 clusters. The extended \Fermi upper
+    limits assume King profiles and are shown with black arrows, while
+    the point source limits are show with grey arrows. The blue boxes
+    show the gamma-ray emission from CR-induced $\pi^0$-decay, where
+    the upper (lower) bounds show the estimates for an optimistic
+    (conservative) model (see Sect.~\ref{sec:CRemission} and
     \cite{2010MNRAS.409..449P} for details). Note that our models are
@@
     \Fermi. Interestingly, the limits of Virgo, Norma, and Coma are
-    closing in on our predictions and will enforce constraints on the
-    parameters of hadronic models such as shock acceleration
-    efficiencies or CR transport properties in the coming years.}
+    closing in on our \C{conservative} predictions and will enforce
+    constraints on the parameters of hadronic models such as shock
+    acceleration efficiencies or CR transport properties in the coming
+    years.}
  \label{fig15}
@@
   \includegraphics[width=0.99\columnwidth]{figures/XCR.Fermi.eps}
-  \caption{\it Limits on the relative CR pressure, $\bra X_\rmn{CR}\ket = \bra
-    P_\rmn{CR} \ket / \bra P_\rmn{th}\ket$ averaged across the cluster. Our
-    constraints are obtained with the extended \Fermi-LAT limits in the energy
-    range $E_\gamma=1-10$~GeV that assume a King profile which matches the
-    extension of the thermal X-ray emission (black) and for comparison with
-    \Fermi-LAT point-source limits (grey) \cite{2010ApJ...717L..71A}. In
-    computing those limits, we adopted our (conservative) analytic model
-    \cite{2010MNRAS.409..449P} and an averaged relative CR flux as obtained from
-    our simulations.}
+  \caption{\it Limits on the relative CR pressure, $\bra
+    X_\rmn{CR}\ket = \bra P_\rmn{CR} \ket / \bra P_\rmn{th}\ket$
+    averaged across the cluster. Our constraints are obtained with the
+    extended \Fermi-LAT limits in the energy range $E_\gamma=1-10$~GeV
+    that assume a King profile which matches the extension of the
+    thermal X-ray emission (black) and for comparison with \Fermi-LAT
+    point-source limits (grey) \cite{2010ApJ...717L..71A}. In
+    computing those limits, we adopted our (conservative) analytic
+    model \cite{2010MNRAS.409..449P} and an averaged relative CR flux
+    as obtained from our simulations.}
  \label{fig:XCR}
@@
    distribution follows the analytical model derived through
-   hydrodynamical cosmological cluster simulations \protect
-   \cite{2010MNRAS.409..449P} (see text for details).  Gamma-ray
-   fluxes are calculated within $\rvir$ and are derived using a single
-   beta profile for each cluster's gas density profile as obtained by
-   ROSAT X-ray observations. The upper panel shows the energy
+   hydrodynamical cosmological cluster simulations\C{, where the
+     spectral shape is independent of cluster mass} \protect
+   \cite{2010MNRAS.409..449P} (see text for details). Gamma-ray fluxes
+   are calculated within $\rvir$ and are derived using a single or
+   double beta profile for each cluster's gas density profile as
+   obtained by ROSAT X-ray observations
+   \cite{2007A&A...466..805C}. The upper panel shows the energy
    integrated flux above 100~MeV (left side) and above 100~GeV (right
@@
    brightest clusters are labelled. The lower panel shows the relative
-   difference between the the flux computed using the analytical model
-   and the gamma-ray flux predicted by the mass-luminosity scaling
-   relation \cite{2010MNRAS.409..449P}. The clusters with the largest
-   positive offset are labelled. As expected, they all are cool core
-   clusters.}
+   difference between the flux \C{above 100~MeV} computed using the
+   analytical model and the gamma-ray flux predicted by the
+   mass-luminosity scaling relation
+   \cite{2010MNRAS.409..449P}. \del{For this figure we have used that
+     $F_\gamma(100\,\rmn{GeV})\propto F_\gamma(100\,\rmn{MeV})\propto
+     M^{1.46}$, which introduce an error of 50\% in the mass range
+     $5\times10^{13}\msun<\mvir<10^{15}\msun$.} The clusters with the
+   largest positive offset are labelled. As expected, they all are
+   cool core clusters.}
  \label{fig19}
@@
 
-\C{Figure~\ref{fig15} shows flux predictions by an analytical CR model
-  \cite{2010MNRAS.409..449P} for CR induced gamma-rays and compare those to the
-  extended \Fermi-LAT flux upper limits that assume King profiles which trace
-  the X-ray emitting gas.}  For consistency, we use beta-model fits to ROSAT
-data of X-ray bright clusters for our gamma-ray flux estimates as an input
-\cite{2002ApJ...567..716R}). We derive the central gas densities for each
-cluster by following the approach outlined in \cite{1999ApJ...517..627M} which
-assumes that the ICM is isothermal. The central gas density is found by
-combining X-ray temperature with X-ray luminosity, X-ray detection radius,
-density core radius and density slope for each cluster. These predictions are
-superior to those that use luminosity-mass scaling relation to infer the
-expected gamma-ray flux---a method used by reference \cite{2010ApJ...717L..71A}
-to compare to \Fermi limits.  In this CR analytic model, we model
-CR-acceleration at structure formation shocks and their transport over cosmic
-time. This leads to a CR distribution with a universal spectral form and an
-almost universal spatial distribution. Depending on whether or not we account
-for the bias of ``artificial galaxies'' in cosmological simulations, we derive
-an optimistic or conservative limit of the expected gamma-ray emission from
-decaying pions (bracketing our ignorance of the contribution of cluster galaxies
-to the overall gamma-ray flux from a cluster).
-
-\C{We highlight two main uncertainties of the models, namely the acceleration
-  efficiency at formation shocks and CR transport parameters. First, we note}
-that both models assume the maximally allowed acceleration efficiency for {\em
-  strong} shocks that transfers 50\% of the shock-dissipated energy (kinetic
-energy corrected for adiabatic compressional heating at the shock) to CRs. These
-efficiencies drop quickly for weaker shocks \cite{2007A&A...473...41E} which
-dominate the gravitational energy dissipation inside galaxy clusters
-\cite{2006MNRAS.367..113P}. These efficiencies will have to be corrected down if
-this value is not realized at structure formation shocks. Second, these
-simulations \C{(and by extension the analytic model)} neglect active CR
-transport such as streaming and diffusion relative to the gas, i.e., we assume
-that advective transport dominates and CRs are tightly coupled to the gas via
-flux-frozen magnetic fields tangled on sufficiently small scales. Evidence from
-the statistics of radio halos suggests that this might not be the case for
-relaxed clusters, arguing that CR streaming \C{(and diffusion)} in those objects
-could be responsible for a decrease in the central CR number density. This
-effect would also reduce the expected gamma-ray flux by up to a factor of five
-\cite{2011A&A...527A..99E}.
-
-We note that the tightest \Fermi limits are obtained in the 1-10 GeV regime due
-to the highest sensitivity of \Fermi-LAT there. While the effective area of LAT
-increases up to these energies, the typical photon spectra decrease as a
-function of energy: combining those effects selects this energy range to be most
-sensitive.  In this energy band, the \Fermi limits come close to the flux
-predictions of Virgo, Coma and Norma. Using integrated flux limits from \Fermi,
-we arrive at very similar results.  We emphasize that by using our analytic
-modeling, the slight discrepancy of the scaling relation-based prediction with
-the \Fermi limit on Norma \cite{2010ApJ...717L..71A} is resolved: Norma simply
-seems to be less bright than an average cluster of the same mass as Norma. The
-insensitive limit on Perseus \C{is due to the bright central source NGC1275 with
-  an AGN in the center \cite{2010ATel.2916....1M} making it hard to determine a
-  comparable limit as obtained for the other clusters. In addition, there are
-  recent gamma-ray observations of the head-tail radio galaxy IC310 in the
-  cluster outskirts \cite{2010ApJ...723L.207A,2010A&A...519L...6N}.}
-
-\C{A quantity that is of great scientific interest is the CR pressure ($P_\CR$)
-  relative to the thermal pressure ($P_\rmn{th}$) as it may bias galaxy cluster
-  observables, e.g., the Sunyaev-Zel’dovich signal or hydrostatic mass
-  estimates, and the resulting cosmological constraints if the analyses do not
-  marginalize over a potential pressure contribution from CRs. Before we turn to
-  the newly derived constraints on the relative CR pressure, $X_\CR =
-  P_\CR/P_\rmn{th}$, we study the Bayesian prior that different models (a
-  simulation based and a simple analytic model) impose on the scaling of $X_\CR$
-  with cluster mass.}
-
-\C{In the simulation based analytic CR model \cite{2010MNRAS.409..449P}, the CR
-  pressure derives from the CR distribution function, $f\dd p =
-  C\,p^{-\alpha}\dd p$, where $C$ is the normalization, $p=P/m_\rmn{p} c$ is the
-  normalized CR proton momentum, and $\alpha$ is the CR spectral index. The
-  pressure is given by $P_\CR \propto C\propto \tilde{C} \,\rho_\rmn{gas}$,
-  where the volume weighted, dimensionless normalization,
-  $\bra\tilde{C}\ket\propto \mvir^{0.44}$ for clusters with a mass $\mvir\gtrsim
-  10^{14}\,\msun$ \cite{2010MNRAS.409..449P}. The thermal pressure is derived
-  from the temperature in virial equilibrium, and scales as $P_\rmn{th}= n k_\B
-  T \propto G \mvir/R_{200} \propto \mvir^{2/3}$. Hence, the volume weighted
-  relative CR pressure scales as
+Figure~\ref{fig15} shows flux predictions by an analytical CR model
+\cite{2010MNRAS.409..449P} for CR induced gamma-rays and compare those
+to the extended \Fermi-LAT flux upper limits that assume King profiles
+which trace the X-ray emitting gas. \C{For consistency, we use single-
+  and double-beta model fits to ROSAT data of X-ray bright clusters
+  for our gamma-ray flux estimates as an input
+  \cite{2007A&A...466..805C}. The deprojection is performed following
+  the formalism developed in e.g. \cite{2004A&A...413...17P}. These
+  gamma-ray flux predictions are superior to those that use
+  luminosity-mass scaling relation---a method used by reference
+  \cite{2010ApJ...717L..71A} to compare to \Fermi limits.}  In this CR
+analytic model, we model CR-acceleration at structure formation shocks
+and their transport over cosmic time. This leads to a CR distribution
+with a universal spectral form and an almost universal spatial
+distribution. Depending on whether or not we account for the bias of
+``artificial galaxies'' in cosmological simulations, we derive an
+optimistic or conservative limit of the expected gamma-ray emission
+from decaying pions (bracketing our ignorance of the contribution of
+cluster galaxies to the overall gamma-ray flux from a cluster).
+
+We highlight two main uncertainties of the models, namely the
+acceleration efficiency at formation shocks and CR transport
+parameters. First, we note that both models assume the maximally
+allowed acceleration efficiency for {\em strong} shocks that transfers
+50\% of the shock-dissipated energy (kinetic energy corrected for
+adiabatic compressional heating at the shock) to CRs. These
+efficiencies drop quickly for weaker shocks \cite{2007A&A...473...41E}
+which dominate the gravitational energy dissipation inside galaxy
+clusters \cite{2006MNRAS.367..113P}. These efficiencies will have to
+be corrected down if this value is not realized at structure formation
+shocks. Second, these simulations (and by extension the analytic
+model) neglect active CR transport such as streaming and diffusion
+relative to the gas, i.e., we assume that advective transport
+dominates and CRs are tightly coupled to the gas via flux-frozen
+magnetic fields tangled on sufficiently small scales. Evidence from
+the statistics of radio halos suggests that this might not be the case
+for relaxed clusters, arguing that CR streaming (and diffusion) in
+those objects could be responsible for a decrease in the central CR
+number density. This effect would also reduce the expected gamma-ray
+flux by up to a factor of five \cite{2011A&A...527A..99E}.
+
+We note that the tightest \Fermi limits are obtained in the 1-10 GeV
+regime due to the highest sensitivity of \Fermi-LAT there. While the
+effective area of LAT increases up to these energies, the typical
+photon spectra decrease as a function of energy: combining those
+effects selects this energy range to be most sensitive.  In this
+energy band, the \Fermi limits come close to the \C{conservative flux
+  predictions of Virgo, Coma and Norma}. Using integrated flux limits
+  from \Fermi, we arrive at very similar results.  \del{We emphasize that
+  by using our analytic modeling, the slight discrepancy of the
+  scaling relation-based prediction with the \Fermi limit on Norma
+  \cite{2010ApJ...717L..71A} is resolved: Norma simply seems to be
+  less bright than an average cluster of the same mass as Norma.} The
+  insensitive limit on Perseus is due to the bright central source
+  NGC1275 with an AGN in the center \cite{2010ATel.2916....1M} making
+  it hard to determine a comparable limit as obtained for the other
+  clusters. In addition, there are recent gamma-ray observations of
+  the head-tail radio galaxy IC310 in the cluster outskirts
+  \cite{2010ApJ...723L.207A,2010A&A...519L...6N}.
+
+A quantity that is of great scientific interest is the CR pressure
+($P_\CR$) relative to the thermal pressure ($P_\rmn{th}$) as it may
+bias galaxy cluster observables, e.g., the Sunyaev-Zel’dovich signal
+or hydrostatic mass estimates, and the resulting cosmological
+constraints if the analysis do not marginalize over a potential
+pressure contribution from CRs. Before we turn to the newly derived
+constraints on the relative CR pressure, $X_\CR = P_\CR/P_\rmn{th}$,
+we study the Bayesian prior that different models (a simulation based
+and a simple analytic model) impose on the scaling of $X_\CR$ with
+cluster mass.
+
+In the simulation based analytic CR model \cite{2010MNRAS.409..449P},
+the CR pressure derives from the CR distribution function, $f\dd p =
+C\,p^{-\alpha}\dd p$, where $C$ is the normalization, $p=P/m_\rmn{p}
+c$ is the normalized CR proton momentum, and $\alpha$ is the CR
+spectral index. The pressure is given by $P_\CR \propto C\propto
+\tilde{C} \,\rho_\rmn{gas}$, where the volume weighted, dimensionless
+normalization, $\bra\tilde{C}\ket\propto \mvir^{0.44}$ for clusters
+with a mass $\mvir\gtrsim 10^{14}\,\msun$
+\cite{2010MNRAS.409..449P}. The thermal pressure $P_\rmn{th} =
+n_\rmn{gas} k_\B T$ and is derived from the temperature in virial
+equilibrium that scales as $k_\B T \propto G \mvir/R_{200} \propto
+\mvir^{2/3}$. Hence, the volume weighted relative CR pressure scales
+as
 \begin{equation}
-    \bra X_{\CR,\,\rmn{sim}}\ket = \frac{\bra P_\CR\ket}{\bra P_\rmn{th}\ket} 
-    \propto \frac{\bra\tilde{C}\ket}{\bra k_\B T\ket} \propto M^{-0.22}\,,
+    \bra X_{\CR,\,\rmn{sim}}\ket = \frac{\bra P_\CR\ket}{\bra
+      P_\rmn{th}\ket} \propto \frac{\bra\tilde{C}\ket}{\bra k_\B
+      T\ket} \propto M^{-0.22}\,,
 \end{equation}
@@
 history in the form of adiabatic compression or encounter shocks of
-  similar (weak) strength.}
-
-\C{In contrast, the analytic (isobaric) CR model \cite{2004A&A...413...17}, that
-  was used by the \Fermi collaboration to derive CR pressure constraints
-  \cite{2010ApJ...717L..71A}, assumes $P_\CR = X_\CR P_\rmn{th}$ and constrains
-  $X_\CR$ by assuming no intrinsic cluster mass dependence of the CR pressure.
-  While apparently very natural, this implies a strong cluster mass dependence
+similar (weak) strength.
+
+In contrast, the analytic (isobaric) CR model
+\cite{2004A&A...413...17P}, that was used by the \Fermi collaboration
+to derive CR pressure constraints \cite{2010ApJ...717L..71A}, assumes
+$P_\CR = X_\CR P_\rmn{th}$ and constrains $X_\CR$ by assuming no
+intrinsic cluster mass dependence of the CR pressure.  While
+apparently very natural, this implies a strong cluster mass dependence
 of $X_\CR$ as the following estimate shows:
@@
     \bra X_{\CR,\,\rmn{iso}}\ket = \frac{\bra P_\CR\ket}{\bra P_\rmn{th}\ket} 
-    \propto \frac{C}{\bra n k_\B T\ket} \propto M^{-0.8}\,.
+    \propto \frac{1}{\bra n_\rmn{gas} k_\B T\ket} \propto M^{-0.8}\,.
 \end{equation}
-  Here, we determine the mass scaling of the average gas density
-  through its relation to the enclosed gas fraction, $f_\rmn{gas}$, and find that
-  $n_\rmn{gas}\propto f_\rmn{gas} \propto M^{0.135}$
-  \cite{2009ApJ...693.1142S}.}
-
-\C{Figure~\ref{fig:XCR} shows the volume weighted relative CR pressure for 32
-  clusters, for which extended \Fermi-LAT upper limits are derived (that assume
-  King profiles). We adopt a constant $\bra X_\CR\ket\approx 0.02$ derived from
-  the average of the large clusters in our simulation sample
-  \cite{2008MNRAS.385.1211P, 2010MNRAS.409..449P}. We can constrain $X_\CR <
-  (0.1-0.2)$ using the extended gamma-ray upper limits on most of the clusters
-  in the \Fermi sample. The most constraining clusters are Norma and Coma with
-  $X_\CR < 0.07$. Most of the 32 clusters have limits on $X_\CR$ within a factor
-  few from the best constraining clusters suggesting that stacking of clusters
-  will be able to improve these limits.  These limits may improved upon by using
-  a stacking approach that adopts our simulation-based analytic model as a
-  prior.}
-
-\C{In a recent work by the \Fermi collaboration \cite{2010ApJ...717L..71A},
-  where the 1.5 year \Fermi data was used to derive limits on $X_\CR$, they
-  found that the most massive clusters are on average more constraining yielding
-  the best constraints of the order of 5\% (by adopting, however, point-like
-  upper limits). In contrast, we find better limits on the low mass
-  clusters. This difference is explained by the different priors on $P_\CR$.  We
-  adopt a prior inferred from cosmological simulations that dynamically trace
-  the CRs during cluster assembly suggesting that adiabatic transport is
-  dominant in shaping the CR population in clusters and implying a weak mass
-  dependence of $X_\CR$. Their analysis assumes a CR pressure that is
-  independent of cluster mass, i.e., constraints on $X_\CR$ inherit the inverse
-  mass dependence of the thermal pressure, $X_\CR\propto 1/P_\rmn{th}\propto
-  M^{-0.8}$. While it is not clear which mass scaling of $X_\CR$ is realized in
-  Nature, these considerations suggest that it will be critical for future work
-  to account for the Bayesian prior in deriving limits on their pressure.}
-
- %%%%%
-\del{ In the following we
-  estimate the mass scaling of the relative CR pressure, $X_\CR =
-  P_\CR/P_\rmn{th}$, using the CR formalism outlined in
-  \cite{2007A&A...473...41E,2010MNRAS.409..449P}. We derive the CR pressure from
-  the CR distribution function $f = C\,p^{-\alpha}$, where $C$ is the
-  normalization of each power-law, $p=P/m_\rmn{p} c$ is the normalized CR proton
-  momentum, and $\alpha$ is the CR spectral index. The pressure is given by
-  $P_\CR \propto C=\tilde{C} \,\rho_\rmn{gas}$, where $\tilde{C}\propto
-  M^{0.44}$ for clusters with a mass $\mvir\gtrsim 10^{14}\,\msun$
-  \cite{2010MNRAS.409..449P}. We determine the mass scaling of the gas density
-  through its relation to the enclosed gas fraction $f_\rmn{gas}$, and find that
-  $\rho_\rmn{gas}\propto f_\rmn{gas} \propto M^{0.135}$
-  \cite{2009ApJ...693.1142S}. The thermal pressure is derived from the
-  temperature in virial equilibrium, and scales as $P_\rmn{th}\propto k_\B T
-  \propto G M/R \propto M^{0.67}$. Finally we can derive the mass scaling of the
-  volume weighted relative CR pressure from
-  \begin{equation}
-    <X_\CR> = \frac{<P_\CR>}{<P_\rmn{th}>} \propto \frac{<\rho_\rmn{gas}\,
-      \tilde{C}>}{<k_\B T>} \propto M^{-0.1}\,,
-  \end{equation}
-  which is roughly a constant, i.e. almost independent on halo
-  mass. This suggests that CRs are accelerated at the strongest
-  shocks, in the early universe or between voids and pre-collapsed
-  IGM, and then experience a similar transport history in the form of
-  adiabatic compression or similarly weaker shocks. Since the CRs that
-  build up the bulk of the CR pressure also give rise to gamma-ray
-  emission through the production of decaying pions, we use gamma-ray
-  upper limits from \Fermi-LAT to constrain $X_\CR$. In
-  Fig.~\ref{fig:XCR} we show the volume weighted relative CR pressure
-  for 32 clusters, for which LAT upper limits that assume King
-  profiles are derived. We adopt a constant $<X_\CR>\approx 0.02$
-  derived from a representative simulated cluster
-  \cite{2008MNRAS.385.1211P} and find that for most of the clusters in
-  the sample we can constrain $X_\CR < (0.1-0.2)$ using the extended
-  gamma-ray upper limits, where the most constraining clusters are
-  Norma and Coma with $X_\CR < 0.07$. Most of the 32 clusters have
-  $X_\CR$ upper limits within a factor few from the best constraining
-  clusters, which suggests that stacking of clusters will be able to
-  improve these limits. This might even be improved further using a
-  scaled stacking with our model as a prior. In a recent work
-  \cite{2010ApJ...717L..71A}, where the 1.5 year \Fermi data was used
-  to derive limits on $X_\CR$, they found that the most massive
-  clusters are on average more constraining, while we find better
-  limits on the low mass clusters. This difference is explained by the
-  different priors on $P_\CR$; they assumed a mass independent CR
-  pressure derived from a single CR power-law distribution function,
-  while we adopt a prior inferred from cosmological simulations that
-  dynamically trace the CRs during cluster assembly and allow for a
-  varying spectral index where $P_\CR\sim M^{0.44}$. Furthermore, the
-  gamma-ray flux predictions that we use in this work to constrain
-  $X_\CR$ assumes the true gas density distribution for each cluster
-  \footnote{Derived from the parameters in the extended HIFLUGCS
-    catalogue.} that accounts for cluster-to-cluster scatter, in
-  contrast to the mass-to-luminosity scaling relations that was used
-  in previous work.}
+Here, we determine the mass scaling of the average gas density through
+its relation to the enclosed gas fraction, $f_\rmn{gas}$, and find
+that $n_\rmn{gas}\propto f_\rmn{gas} \propto M^{0.135}$
+\cite{2009ApJ...693.1142S}.
+
+Figure~\ref{fig:XCR} shows the volume weighted relative CR pressure
+for 32 clusters, for which extended \Fermi-LAT upper limits are
+derived (that assume King profiles). We adopt a constant $\bra
+X_\CR\ket\approx 0.02$ derived from the average of the large clusters
+in our simulation sample \cite{2008MNRAS.385.1211P,
+  2010MNRAS.409..449P}. We can constrain $X_\CR < 0.1$ using the
+extended gamma-ray upper limits on most of the clusters in the \Fermi
+sample. The most constraining clusters are Norma, Ophiuchus, and Coma
+with $X_\CR < 0.03$. Most of the 32 clusters have limits on $X_\CR$
+within a factor few from the best constraining clusters suggesting
+that stacking of clusters will be able to improve these limits.  These
+limits may improved upon by using a stacking approach that adopts our
+simulation-based analytic model as a prior.
+
+In a recent work by the \Fermi collaboration
+\cite{2010ApJ...717L..71A}, where the 1.5 year \Fermi data was used to
+derive limits on $X_\CR$, they found that the most massive clusters
+are on average more constraining yielding the best constraints of the
+order of 5\% (by adopting, however, point-like upper limits). \C{In
+  this work we find in addition that medium size clusters provide
+  strong constraints.}  This difference is explained by the different
+priors on $P_\CR$.  We adopt a prior inferred from cosmological
+simulations that dynamically trace the CRs during cluster assembly
+suggesting that adiabatic transport is dominant in shaping the CR
+population in clusters and implying a weak mass dependence of
+$X_\CR$. Their analysis assumes a CR pressure that is independent of
+cluster mass, i.e., constraints on $X_\CR$ inherit the inverse mass
+dependence of the thermal pressure, $X_\CR\propto 1/P_\rmn{th}\propto
+M^{-0.8}$. While it is not clear which mass scaling of $X_\CR$ is
+realized in Nature, these considerations suggest that it will be
+critical for future work to account for the Bayesian prior in deriving
+limits on their pressure.
 
@@
 
-{\em Dark matter annihilation.} Once supersymmetric cold dark matter decouples
-from the expanding universe it streams and erases any potentially present
-smaller scales. When gravitational instability causes halos to collapse, this
-free-streaming scale imprints as a characteristic minimum halo mass
-$M_\mathrm{min}$ into the hierarchy of structure formation and should still
-survive until the present time as substructure within larger halos. We show that
-the boost due to substructures dominates over the smooth component for halo
-masses $\mvir>10^3 \msun$ and contributes a constant luminosity for each decade
-in halo mass. The ratio of halo-to-minimum subhalo mass $\mvir/M_\mathrm{min}$
-is maximized for the largest virialized systems in the Universe -- galaxy
-clusters. The corresponding substructure boost can reach values exceeding $10^3$
-which should make nearby clusters the brightest DM annihilation sources after
-the MW center and hypothetical very close-by DM substructures. \C{We stress that
-  this conclusion relies on two hypotheses that are still open problems in
-  particle physics and numerical cosmology. We assume (i) the existence of cold
-  DM, i.e., the density fluctuation power spectrum extends down to the DM free
-  streaming scale of about an Earth mass, and (ii) assume that structure
-  formation at scales smaller than currently resolved ones ($\sim 10^5\,\msun$)
-  proceeds scale-invariant, i.e., there is no non-linear mode coupling between
-  different scales that could potentially erase structure smaller than a
-  characteristic one as the linear power spectrum approaches $\Delta^2(k)
-  \propto k^3 P(k)=\rmn{const.}$ and structure on different scales forms not any
-  more hierarchically, but collapses at the same time.}
+{\em Dark matter annihilation.} Once supersymmetric cold dark matter
+decouples from the expanding universe it streams and erases any
+potentially present smaller scales. When gravitational instability
+causes halos to collapse, this free-streaming scale imprints as a
+characteristic minimum halo mass $M_\mathrm{min}$ into the hierarchy
+of structure formation and should still survive until the present time
+as substructure within larger halos. We show that the boost due to
+substructures dominates over the smooth component for halo masses
+$\mvir>10^3 \msun$ and contributes a constant luminosity for each
+decade in halo mass. The ratio of halo-to-minimum subhalo mass
+$\mvir/M_\mathrm{min}$ is maximized for the largest virialized systems
+in the Universe -- galaxy clusters. The corresponding substructure
+boost can reach values exceeding $10^3$ which should make nearby
+clusters the brightest DM annihilation sources after the MW center and
+hypothetical very close-by DM substructures. We stress that this
+conclusion relies on two hypotheses that are still open problems in
+particle physics and numerical cosmology. We assume (i) the existence
+of cold DM, i.e., the density fluctuation power spectrum extends down
+to the DM free streaming scale of about an Earth mass, and (ii) assume
+that structure formation at scales smaller than currently resolved
+ones ($\sim 10^5\,\msun$) proceeds scale-invariant, i.e., there is no
+non-linear mode coupling between different scales that could
+potentially erase structure smaller than a characteristic one as the
+linear power spectrum approaches $\Delta^2(k) \propto k^3
+P(k)=\rmn{const.}$ and structure on different scales forms not any
+more hierarchically, but collapses at the same time.
 
@@
 continuum emission is low, the IC up-scattering of the CMB dominates
-below 60 GeV. \C{For larger energies, the final state radiation
-  dominates the emission up to the cutoff at $m_\chi c^2 \sim
-  1$~TeV. The IC up-scattering of the dust and starlight is always
-  subdominant compared to the upscattered CMB (below 60~GeV) and the
-  final state radiation (above 60~GeV).}  We stress, that the
-inclusion of the dust and starlight radiation fields are negligible in
-the cooling function for the leptons.  The main reason why the IC
-emission from starlight and dust remains subdominant is the small
-overlap of this component with the peripherally peaked substructure
-mass density profiles. If for some reason, DM has less substructure,
-the relative importance of this IC component increases considerably.
-
-\C{We identify Virgo and Fornax to be the best cluster/group
+below 60 GeV. For larger energies, the final state radiation dominates
+the emission up to the cutoff at $m_\chi c^2 \sim 1$~TeV. The IC
+up-scattering of the dust and starlight is always subdominant compared
+to the upscattered CMB (below 60~GeV) and the final state radiation
+(above 60~GeV).  We stress, that the inclusion of the dust and
+starlight radiation fields are negligible in the cooling function for
+the leptons.  The main reason why the IC emission from starlight and
+dust remains subdominant is the small overlap of this component with
+the peripherally peaked substructure mass density profiles. If for
+some reason, DM has less substructure, the relative importance of this
+IC component increases considerably.
+
+We identify \C{Virgo, Fornax and M49} to be the best cluster/group
 candidates for indirect DM studies as they are expected to emit the
-  brightest annihilation flux.\footnote{\C{We excluded Virgo from our
+brightest annihilation flux.\footnote{We excluded Virgo from our
   further analysis due to its large angular extent that needs a
-    separate treatment.}}  More importantly, Fornax has a comparably
-  low CR induced gamma-ray flux which may enable an indirect DM
-  detection or a particularly tight limit on DM properties}.  Other
-nearby bright sources of the extended HIFLUGCS sample of nearby bright
-X-ray cluster/groups are \C{Ophiuchus, Coma, and Centaurus}.
-
-The non-detection of gamma-ray emission by \Fermi in a total of 26
+  separate treatment.}  More importantly, Fornax has a comparably low
+CR induced gamma-ray flux which may enable an indirect DM detection or
+a particularly tight limit on DM properties.  Other nearby bright
+sources of the extended HIFLUGCS sample of nearby bright X-ray
+cluster/groups are Ophiuchus, and Centaurus.
+
+The non-detection of gamma-ray emission by \Fermi in a total of 28
 clusters/groups considerably constrains LP models for DM annihilation
 which were introduced to explain the increasing positron-to-lepton
-ratio beyond 10 GeV. \C{Assuming that the minimum DM substructure mass
+ratio beyond 10 GeV. Assuming that the minimum DM substructure mass
 extends down to an Earth mass and that the DM annihilation flux is
-  dominated by small scale substructure, we limit the saturated
-  Sommerfeld enhancement factor in M49 (that has a particularly tight
-  upper limit) and Fornax to about 14 and 22, respectively. This
-  corresponds to a value in the Milky Way (MW) of less than 8 and 13,
-  respectively, due to the larger Sommerfeld boost factor in smaller
-  mass halos which have a lower velocity dispersion that enhances the
-  particle cross section (while assuming universality of the DM
-  model).} This would rule out LP models in their current form based
-on the non-observation of gamma-rays in any of the fore-mentioned
+dominated by small scale substructure, \C{we limit the saturated
+Sommerfeld enhancement factor in M49 and Fornax to about 5. This
+corresponds to a value in the Milky Way (MW) of less than 3}, due to
+the larger Sommerfeld boost factor in smaller mass halos which have a
+lower velocity dispersion that enhances the particle cross section
+(while assuming universality of the DM model). This would rule out LP
+models in their current form based on the non-observation of
+gamma-rays in any of the fore-mentioned
 clusters/groups. Alternatively, assuming the LP models to be correct,
-we limit the minimum substructure mass to $>10~\msun$ in M49.
+we limit the minimum substructure mass to $>10^4~\msun$ in M49 and
+Fornax.
 
@@
 expected gamma-ray emission to that inferred from using
-$L_\gamma$-cluster mass scaling relation. We note that the predictions
-of our ``optimistic'' model are perfectly in agreement with \Fermi
-upper limits for all clusters.  The hint of a tension that the scaling
-relation modeling showed for Norma \citep{2010ApJ...717L..71A} could
-not be confirmed due to the lower gas density of this cluster relative
-to the average.
+$L_\gamma$-cluster mass scaling relation. \C{We note that the
+  predictions of our ``optimistic'' model are in tension with \Fermi
+  upper limits for Norma, Coma, and Ophiuchus. In the next 2-3 years
+  \Fermi will be able to probe the predictions of our ``conservative''
+  CR model, hence start to put realistic limits on the acceleration
+  efficency of CRs in structure formation shocks.}  \del{agreement
+  with \Fermi upper limits for all clusters. The hint of a tension
+  that the scaling relation modeling showed for Norma
+  \citep{2010ApJ...717L..71A} could not be confirmed due to the lower
+  gas density of this cluster relative to the average.  }
 
@@
 the scaling relation and biases the gamma-ray flux high for prominent
-cool core clusters by up to a factor of 6 relative to the expectation
+cool core clusters by up to a factor of 10 relative to the expectation
 from the scaling relation. This is due to the high target gas
@@
 CR distribution \citep{2011A&A...527A..99E}. The CR spectrum $E^2
-dN/dE$ shows the characteristic pion bump at energies around 1~GeV. It
-is expected to dominate the DM annihilation signal of BM models for
-all clusters/groups but Fornax.
-
-\C{Combining extended \Fermi upper limits and our model flux predictions, we
-  limit the relative CR pressure, $X_\CR = P_\CR/P_\rmn{th}$, in 32 nearby
-  bright galaxy clusters of the \Fermi sample. The best limits are found in
-  Norma and Coma of the order of 7\%, with typical limits ranging between 10\%
-  to 30\%. This is somewhat larger that those inferred by the \Fermi
-  collaboration \citep{2010ApJ...717L..71A} and due to the differently assumed
-  Bayesian prior on the CR pressure which implies a different cluster mass
-  dependence of the resulting limits on $X_\CR$. }
-
-\C{We conclude that due to the large spatial extension of the
-  brightest clusters it is not possible for \Fermi to rule out the LP
-  model or to constrain the BM DM models without improved
-  modelling. However, we can put tight constraints on the boost from
-  substructures and Sommerfeld enhancement using the LP model. Hence,
-  clusters are a valuable complement to direct and accelerator
-  searches for the nature of DM.}
+dN/dE$ shows the characteristic pion bump at energies around
+1~GeV. \C{It is expected to dominate the DM annihilation signal of BM
+  models for clusters/groups, although we find that the gamma-ray
+  flux induced by the BM is higher for about 1/5 of the clusters in the
+  HIFLUGCS catalouge, where Fornax and M49 have the highest signal to
+  noise. We find that \Fermi-LAT will be able to start constraining
+  these DM models within the coming five years using clusters of
+  galaxies.} \del{It is expected to dominate the DM annihilation
+  signal of BM models for all clusters/groups but Fornax.}
+
+Combining extended \Fermi upper limits and our model flux predictions,
+we limit the relative CR pressure, $X_\CR = P_\CR/P_\rmn{th}$, in 32
+nearby bright galaxy clusters of the \Fermi sample. \C{The best limits
+  are found in Norma and Coma of the order of 3\%, with typical limits
+  around 10\%. This is comparable to those inferred by the \Fermi
+  collaboration \citep{2010ApJ...717L..71A} and mainly due to two
+  different effects that cancel; the differently assumed Bayesian
+  prior on the CR pressure which implies a different cluster mass
+  dependence of the resulting limits on $X_\CR$ and the different
+  masses in our cluster sample which is based on a more recent and
+  more detailed analisys of the clusters in the HIFLUGCS
+  catalouge \cite{2007A&A...466..805C}.}
+
+We conclude that due to the large spatial extension of the brightest
+clusters it is not possible for \Fermi to rule out the LP model or to
+constrain the BM DM models without improved modelling. However, we can
+put tight constraints on the boost from substructures and Sommerfeld
+enhancement using the LP model. Hence, clusters are a valuable
+complement to direct and accelerator searches for the nature of DM.
 
@@
 349-2007-8709 (the Oskar Klein Centre).
-
-%-) Consider having one figure where we compare the Einasto profile, to
-%NFW, NFW w/ beta 0.6, and also the effect of a different concentration
-%mass-scaling relation
-%
-%-) also, plot BM flux vs. psf, for models w/ and w/o substructures
 
@@
 
-\C{Finally, we use the data from
-  \cite{2011JCAP...03..019C,2011JCAP...03..051C} to derive the
-  electron and positron yield resulting from leptophilic (LP) DM
-  annihilating indirectly into decaying muons or electrons and
-  positrons. In the energy regime $30\,\rmn{MeV}<\ee< m_\chi c^2$ we
-  find the following best fit for the annihilation into muons:}
+Finally, we use the data from
+\cite{2011JCAP...03..019C,2011JCAP...03..051C} to derive the electron
+and positron yield resulting from leptophilic (LP) DM annihilating
+indirectly into decaying muons or electrons and positrons. In the
+energy regime $30\,\rmn{MeV}<\ee< m_\chi c^2$ we find the following
+best fit for the annihilation into muons:
 \begin{eqnarray}
@@
 
-\section{Gas density profile of Fornax}
+\section{Gas density profiles}
+The production of gamma-rays and secondaries from hadronic CRs in
+clusters depend both on the gas density and the CR number density,
+which roughly trace the gas outside the core regime and is slightly
+enhanced in the center. These gas density profile of galaxy clusters
+are derived from X-ray observations, where the measurements are mainly
+sensitive to the central parts of the clusters where there X-ray flux
+is high, while the core and outerparts are more difficult to measure
+due to the low signal to noise and often involves extrapolation from
+the center. The uncertainties in measurements and modelling, in
+combination with different specifications of active X-ray satellites,
+give rise to important differences in the gas profiles. Since the
+gamma-ray flux from a galaxy cluster is sensitive to the details of
+the gas profile, we choose to model the density profile of four bright
+clusters (Fornax, Virgo, Coma, Perseus) in more detail where we use
+the most recent and detailed modelled gas profile available in the
+literature. We show these profiles in table~\ref{tab:dens_prof}. 
+\begin{table*}
+\begin{minipage}{2.0\columnwidth}  
+\caption{Electron number density profiles for selected clusters.}
+\begin{tabular}{ccccccccccc}
+\hline
+\hline
+Cluster & \multicolumn{9}{c}{$\rho_\rmn{gas} = \left\{\sum_i n_i^2(0)\left[1+\left(\frac{r}{r_{c,i}}\right)^2\right]^{-3\beta_i}\right\}^{1/2}$} & Reference \\
+&  $n_\rmn{1}(0)\,[\el\,/\cm^3]$  & $r_\rmn{c,1}\,[\kpc]$ & $\beta_1$ &
+$n_\rmn{2}(0)\,[\el\,/\cm^3]$  & $r_\rmn{c,2}\,[\kpc]$ & $\beta_2$ & 
+$n_\rmn{3}(0)\,[\el\,/\cm^3]$  & $r_\rmn{c,3}\,[\kpc]$ & $\beta_3$ &  \\ 
+ \hline
+Fornax & 0.35 & 0.36 & 0.54 &  $2.2\times 10^{-3}$ & 190 & 41 & $5.4\times 10^{-4}$ & 183 & 0.8 & \protect{\cite{2002ApJ...565..883P}} \\
+Coma   & $3.55\times 10^{-3}$ & 245 & 0.65 & & & & & & & \protect{\cite{2007A&A...466..805C}} \\
+Virgo & 0.15 & 1.6 & 0.42 & $1.2\times 10^{-2}$ & 20 & 0.47 & & & & \protect{\cite{2002A&A...386...77M}} \\
+\hline
+Perseus & \multicolumn{9}{c}{$46\times10^{-3}\,[1+(r/57\,\rmn{kpc})^2]^{-1.8}+
+            4.8\times10^{-3}\,[1+(r/200\,\rmn{kpc})^2]^{-0.87} \,[\el\,/\cm^3]$} &  \protect{\cite{2003ApJ...590..225C}} \\
+\hline
+\hline
+\end{tabular}
+\caption{
+ \label{tab:dens_prof}}
+\end{minipage}
+\end{table*}
+
 The X-ray emitting gas in Fornax does not follow a simple
@@
 fit. Instead we assume that the outer slop of $n_\e$ follows the outer
-slope of Fornax in the HIFLUGCS catalogue that is very similar to that
-of the Coma cluster. Deprojecting the fitted surface brightness
+slope of Fornax in the HIFLUGCS catalogue
+\cite{2007A&A...466..805C}. Deprojecting the fitted surface brightness
 components yields the following electron number density profile:
 \begin{equation}
-n_\e(r) = \left[\sum_i n_i^2\left[1+\left(\frac{r}{r_{c,i}}\right)^2\right]^{-3\beta_i}\right]^{1/2}
+n_\e(r) = \left\{\sum_i n_i^2\left[1+\left(\frac{r}{r_{c,i}}\right)^2\right]^{-3\beta_i}\right\}^{1/2}
 \end{equation}
@@
 \begin{align}
-&n_1 = 0.35\, \rmn{el}\,\rmn{cm}^{-3}\,,
+&n_1 = 0.35\, \el\,\rmn{cm}^{-3}\,,
 &&r_{c,1} = 0.36\,\kpc\,,\,\,\,
 \beta_1 = 0.54\,, \nonumber\\
-&n_2 = 2.2\times10^{-3}\,\rmn{el}\,\rmn{cm}^{-3}\,,
+&n_2 = 2.2\times10^{-3}\,\el\,\rmn{cm}^{-3}\,,
 &&r_{c,2} = 190\,\kpc\,,\,\,\,\,
 \beta_2 = 41\,, \nonumber\\
-&n_3 = 5.4\times10^{-4}\,\rmn{el}\,\rmn{cm}^{-3}\,,
+&n_3 = 5.4\times10^{-4}\,\el\,\rmn{cm}^{-3}\,,
 &&r_{c,3} = 183\,\kpc\,,\,\,\,\,
@@
    sensitivity of the data to the outer cluster part, we use the outer
-   slope from the HIFLUGCS catalogue that is very similar to that of
-   the Coma cluster.}
+   slope from the HIFLUGCS catalogue \cite{2007A&A...466..805C}.}
  \label{fig:dens_fornax}
@@
 
+For 106 X-ray bright clusters extended HIFLUGCS catalogue we adopt
+more general density profiles derived in the recent paper by Chen et
+al. \cite{2007A&A...466..805C}. They provide single beta-model density
+fits for all clusters, as well as the double beta-model fits to the
+surface profiles. We follow the deprojection procedure in
+\cite{2004A&A...413...17P}, and only choose the fitted double beta
+profiles with a $\chi^2$ that is smaller compared to the single beta
+profile. \footnote{We adopt the single beta density profile for A2255
+  since it harbors a giant radio halo and most likely has a disturbed
+  morphology that might have given the fit the impression of a cool
+  core. Furthermore, the difference in $\chi^2$ between the single-
+  and double-beta profiles is marginal for this cluster.}
+
 \section{Flux tables for the HIFLUGCS catalogue}
 
-\C{In this section we present the gamma-ray flux predictions using the
-  clusters in the extended HIFLUGCS catalogue. We show the brightest
-  50 clusters in descending order; CR proton induced $\pi^0$ that
-  decays into gamma-rays in Table~\ref{tab:flux_tab_CRs}, the
-  supersymmetric DM BM-$\Kp$ model where the Neutralino emit a
-  continuum as well as final state radiation in
-  Table~\ref{tab:flux_tab_BM}, and LP DM that emit final state
-  radiation and annihilate either indirectly to $\rmn{e}^+/\rmn{e}^-$
-  or through $\mu^+/\mu^-$ to $\rmn{e}^+/\rmn{e}^-$ that IC upscatter
-  CMB photons in Table~\ref{tab:flux_tab_LP}. The flux from DM has
-  been boosted by the substructures, where we in addition include the
-  Sommerfeld enhancement for the LP model. For completeness, we show
-  in Table~\ref{tab:flux_tab_CLp} the parameters that we use to derive
-  the fluxes for the clusters in the HIFLUGCS sample.}
+In this section we present the gamma-ray flux predictions using the
+clusters in the extended HIFLUGCS catalogue. We show the brightest 50
+clusters in descending order; CR proton induced $\pi^0$ that decays
+into gamma-rays in Table~\ref{tab:flux_tab_CRs}, the supersymmetric DM
+BM-$\Kp$ model where the Neutralino emit a continuum as well as final
+state radiation in Table~\ref{tab:flux_tab_BM}, and LP DM that emit
+final state radiation and annihilate either indirectly to
+$\rmn{e}^+/\rmn{e}^-$ or through $\mu^+/\mu^-$ to
+$\rmn{e}^+/\rmn{e}^-$ that IC upscatter CMB photons in
+Table~\ref{tab:flux_tab_LP}. The flux from DM has been boosted by the
+substructures, where we in addition include the Sommerfeld enhancement
+for the LP model. For completeness, we show in
+Table~\ref{tab:flux_tab_CLp} the parameters that we use to derive the
+fluxes for the clusters in the HIFLUGCS sample.
 
@@
  \hline
-PERSEUS  &  68 &  56.14 &  75.31 &  20.64 &  63.95 &  13.92 &  24.52 \\
-OPHIUCHUS &  96 &  23.31 &  31.27 &   8.57 &  26.55 &   5.88 &  10.28 \\
-COMA     &  34 &  17.50 &  23.48 &   6.43 &  19.94 &   2.62 &   7.56 \\
-NORMA    &  94 &  13.39 &  17.97 &   4.92 &  15.26 &   1.16 &   5.57 \\
-CENTAURUS &  30 &  12.06 &  16.17 &   4.43 &  13.73 &   2.45 &   5.04 \\
-AWM7     &  67 &   8.24 &  11.05 &   3.03 &   9.38 &   1.85 &   3.63 \\
-A3571    &  39 &   6.10 &   8.19 &   2.24 &   6.95 &   1.80 &   2.83 \\
-TRIANGULUM &  95 &   5.92 &   7.95 &   2.18 &   6.75 &   1.61 &   2.81 \\
-A2319    &  98 &   5.58 &   7.48 &   2.05 &   6.35 &   1.54 &   2.74 \\
-A2199    &  51 &   5.18 &   6.94 &   1.90 &   5.90 &   1.68 &   2.35 \\
-3C129    &  70 &   5.15 &   6.91 &   1.89 &   5.87 &   0.71 &   2.30 \\
-HYDRA    &  25 &   5.15 &   6.91 &   1.89 &   5.86 &   1.11 &   2.22 \\
-2A0335   &  11 &   4.91 &   6.59 &   1.81 &   5.59 &   1.94 &   2.33 \\
-FORNAX   &  10 &   4.09 &   5.48 &   1.50 &   4.66 &   0.33 &   1.65 \\
-A2029    &  43 &   3.73 &   5.00 &   1.37 &   4.25 &   1.45 &   1.80 \\
-A0496    &  18 &   3.59 &   4.81 &   1.32 &   4.09 &   1.13 &   1.84 \\
-A0085    &   1 &   3.54 &   4.75 &   1.30 &   4.04 &   1.20 &   1.79 \\
-A1795    &  40 &   3.52 &   4.73 &   1.29 &   4.01 &   1.37 &   1.66 \\
-A2256    &  54 &   3.45 &   4.63 &   1.27 &   3.93 &   1.11 &   1.55 \\
-PKS0745  &  77 &   3.28 &   4.40 &   1.20 &   3.73 &   1.39 &   1.57 \\
-A3266    &  17 &   3.18 &   4.27 &   1.17 &   3.63 &   0.92 &   1.45 \\
-A2142    &  48 &   3.09 &   4.14 &   1.13 &   3.52 &   1.16 &   1.50 \\
-NGC5044  &  35 &   2.97 &   3.98 &   1.09 &   3.38 &   1.01 &   1.34 \\
-A3558    &  37 &   2.89 &   3.88 &   1.06 &   3.29 &   0.82 &   1.44 \\
-A3667    &  56 &   2.85 &   3.82 &   1.05 &   3.25 &   0.73 &   1.55 \\
-A0262    &   5 &   2.76 &   3.70 &   1.01 &   3.14 &   0.57 &   1.41 \\
-A0478    &  14 &   2.72 &   3.64 &   1.00 &   3.09 &   1.11 &   1.30 \\
-A1367    &  26 &   2.65 &   3.55 &   0.97 &   3.02 &   0.40 &   1.19 \\
-A4038    &  62 &   2.56 &   3.43 &   0.94 &   2.91 &   0.83 &   1.22 \\
-HYDRA-A  &  24 &   2.46 &   3.30 &   0.90 &   2.80 &   0.98 &   1.19 \\
-A0401    &   8 &   2.39 &   3.21 &   0.88 &   2.72 &   0.82 &   1.16 \\
-A2052    &  44 &   2.25 &   3.02 &   0.83 &   2.57 &   0.81 &   1.11 \\
-A0644    &  78 &   2.17 &   2.91 &   0.80 &   2.47 &   0.84 &   0.98 \\
-NGC1550  &  15 &   2.06 &   2.76 &   0.76 &   2.35 &   0.59 &   0.93 \\
-NGC4636  &  29 &   2.06 &   2.76 &   0.76 &   2.34 &   0.55 &   0.86 \\
-A0754    &  23 &   2.03 &   2.73 &   0.75 &   2.32 &   0.69 &   0.92 \\
-ANTLIA   &  79 &   1.87 &   2.50 &   0.69 &   2.13 &   0.19 &   0.82 \\
-A3158    &  13 &   1.83 &   2.45 &   0.67 &   2.08 &   0.61 &   0.86 \\
-A2147    &  49 &   1.80 &   2.41 &   0.66 &   2.05 &   0.29 &   1.19 \\
-A0119    &   2 &   1.75 &   2.35 &   0.65 &   2.00 &   0.38 &   0.84 \\
-A2063    &  47 &   1.70 &   2.28 &   0.63 &   1.94 &   0.53 &   0.82 \\
-A3581    &  41 &   1.66 &   2.22 &   0.61 &   1.89 &   0.58 &   0.78 \\
-A1644    &  31 &   1.63 &   2.19 &   0.60 &   1.86 &   0.42 &   0.85 \\
-MKW3S    &  45 &   1.62 &   2.18 &   0.60 &   1.85 &   0.62 &   0.77 \\
-A2065    &  46 &   1.56 &   2.09 &   0.57 &   1.78 &   0.58 &   0.70 \\
-A0399    &   7 &   1.55 &   2.07 &   0.57 &   1.76 &   0.50 &   0.73 \\
-A3112    &   9 &   1.54 &   2.07 &   0.57 &   1.76 &   0.63 &   0.76 \\
-EXO0422  &  16 &   1.53 &   2.05 &   0.56 &   1.74 &   0.58 &   0.69 \\
-A4059    &  63 &   1.51 &   2.02 &   0.55 &   1.72 &   0.54 &   0.72 \\
-A0576    &  22 &   1.47 &   1.97 &   0.54 &   1.68 &   0.42 &   0.66 \\
+PERSEUS  &  68 &  14.28 &  19.15 &  52.49 &  16.26 &  16.25 &  10.06 \\
+OPHIUCHU &  96 &   7.71 &  10.34 &  28.33 &   8.78 &   8.78 &   6.01 \\
+COMA     &  34 &   4.15 &   5.56 &  15.24 &   4.72 &   4.72 &   2.55 \\
+NORMA    &  94 &   2.98 &   3.99 &  10.94 &   3.39 &   3.38 &   2.19 \\
+CENTAURU &  30 &   2.61 &   3.50 &   9.58 &   2.97 &   2.97 &   2.62 \\
+TRIANGUL &  95 &   1.77 &   2.37 &   6.50 &   2.01 &   2.01 &   0.37 \\
+AWM7     &  67 &   1.75 &   2.35 &   6.43 &   1.99 &   1.99 &   1.24 \\
+A2319    &  98 &   1.71 &   2.30 &   6.30 &   1.95 &   1.94 &   0.28 \\
+A3571    &  39 &   1.61 &   2.15 &   5.90 &   1.83 &   1.82 &   0.41 \\
+3C129    &  70 &   1.35 &   1.82 &   4.98 &   1.54 &   1.54 &   0.71 \\
+A2199    &  51 &   1.11 &   1.49 &   4.10 &   1.27 &   1.27 &   0.33 \\
+2A0335   &  11 &   1.04 &   1.40 &   3.83 &   1.19 &   1.19 &   0.19 \\
+A2029    &  43 &   1.04 &   1.39 &   3.81 &   1.18 &   1.17 &   0.08 \\
+A0496    &  18 &   1.02 &   1.36 &   3.73 &   1.16 &   1.15 &   0.27 \\
+HYDRA    &  25 &   0.95 &   1.27 &   3.48 &   1.08 &   1.08 &   0.84 \\
+A0085    &   1 &   0.93 &   1.25 &   3.44 &   1.06 &   1.06 &   0.12 \\
+A2142    &  48 &   0.92 &   1.24 &   3.39 &   1.05 &   1.04 &   0.06 \\
+A3266    &  17 &   0.92 &   1.23 &   3.37 &   1.05 &   1.04 &   0.16 \\
+A1795    &  40 &   0.91 &   1.22 &   3.35 &   1.04 &   1.04 &   0.11 \\
+PKS0745  &  77 &   0.82 &   1.10 &   3.02 &   0.94 &   0.88 &   0.03 \\
+A2256    &  54 &   0.78 &   1.04 &   2.86 &   0.89 &   0.88 &   0.11 \\
+A3558    &  37 &   0.75 &   1.01 &   2.77 &   0.86 &   0.86 &   0.12 \\
+A3667    &  56 &   0.71 &   0.96 &   2.62 &   0.81 &   0.80 &   0.07 \\
+A1367    &  26 &   0.70 &   0.94 &   2.59 &   0.80 &   0.80 &   0.43 \\
+A0478    &  14 &   0.68 &   0.91 &   2.48 &   0.77 &   0.75 &   0.03 \\
+A0401    &   8 &   0.61 &   0.82 &   2.25 &   0.70 &   0.68 &   0.05 \\
+A0262    &   5 &   0.57 &   0.77 &   2.10 &   0.65 &   0.65 &   0.26 \\
+HYDRA-A  &  24 &   0.56 &   0.75 &   2.05 &   0.63 &   0.63 &   0.05 \\
+A0754    &  23 &   0.52 &   0.70 &   1.92 &   0.59 &   0.59 &   0.10 \\
+A4038    &  62 &   0.52 &   0.69 &   1.90 &   0.59 &   0.59 &   0.13 \\
+A2052    &  44 &   0.51 &   0.68 &   1.87 &   0.58 &   0.58 &   0.09 \\
+A2147    &  49 &   0.50 &   0.66 &   1.82 &   0.56 &   0.55 &   0.11 \\
+A0119    &   2 &   0.48 &   0.64 &   1.76 &   0.54 &   0.54 &   0.10 \\
+A0644    &  78 &   0.47 &   0.63 &   1.73 &   0.54 &   0.53 &   0.04 \\
+A1644    &  31 &   0.43 &   0.58 &   1.60 &   0.49 &   0.49 &   0.07 \\
+A3158    &  13 &   0.39 &   0.53 &   1.45 &   0.45 &   0.44 &   0.04 \\
+FORNAX   &  10 &   0.36 &   0.49 &   1.34 &   0.42 &   0.42 &   0.41 \\
+A2063    &  47 &   0.36 &   0.48 &   1.33 &   0.41 &   0.41 &   0.06 \\
+MKW3S    &  45 &   0.35 &   0.47 &   1.29 &   0.40 &   0.40 &   0.04 \\
+A3112    &   9 &   0.34 &   0.46 &   1.26 &   0.39 &   0.38 &   0.02 \\
+ZwCl1742 &  97 &   0.34 &   0.46 &   1.25 &   0.39 &   0.38 &   0.03 \\
+A4059    &  63 &   0.33 &   0.45 &   1.23 &   0.38 &   0.38 &   0.05 \\
+A1651    &  33 &   0.31 &   0.41 &   1.13 &   0.35 &   0.34 &   0.02 \\
+A0399    &   7 &   0.31 &   0.41 &   1.13 &   0.35 &   0.34 &   0.02 \\
+NGC1550  &  15 &   0.30 &   0.40 &   1.09 &   0.34 &   0.34 &   0.16 \\
+ANTLIA   &  79 &   0.29 &   0.39 &   1.06 &   0.33 &   0.33 &   0.22 \\
+A2657    &  61 &   0.29 &   0.38 &   1.05 &   0.32 &   0.32 &   0.06 \\
+A0539    &  71 &   0.28 &   0.38 &   1.03 &   0.32 &   0.32 &   0.07 \\
+A3581    &  41 &   0.28 &   0.37 &   1.03 &   0.32 &   0.32 &   0.07 \\
+A2204    &  52 &   0.28 &   0.37 &   1.02 &   0.32 &   0.21 &   0.01 \\
 \hline
@@
    (1) The HIFLUGCS cluster ID.
-   (2) In units of  $10^{-10} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
-   (3) In units of  $10^{-11} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (2) In units of  $10^{-9} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (3) In units of  $10^{-10} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
    (4) In units of  $10^{-13} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
-   (5) In units of  $10^{-11} \rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (5) In units of  $10^{-10} \rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
    (6) The flux within $0.1^\circ$, smoothed with a point spread function of $0.1^\circ$. 
-   (7) The flux within $0.1^\circ$, smoothed with a point spread function of $0.1^\circ$. 
+   (7) The flux within $1.0^\circ$, smoothed with a point spread function of $0.1^\circ$. 
  \label{tab:flux_tab_CRs}
@@
   \caption{Gamma-ray BM-$\Kp$ Continuum flux within $\rvir$ from brightest 50 clusters in HIFLUGCS catalogue.}
-\begin{tabular}{l  c c c c c c c}
-\hline
-\hline
- Cluster & ID$^{(1)}$ & $F_{\gamma}$$^{(2)}$ & $F_{\gamma}$$^{(3)}$& 
- $F_{\gamma}$$^{(4)}$ & $\eg^2\,\dd F_{\gamma}/\dd \eg$$^{(5)}$ &
- $\eg^2\,\dd F_{\gamma,0.1}/\dd \eg$$^{(5,6)}$ & 
- $\eg^2\,\dd F_{\gamma,1.0}/\dd \eg$$^{(5,7)}$\\
+\begin{tabular}{l  c c c c c c c c}
+\hline
+\hline
+ Cluster & ID$^{(1)}$ & $F_{\gamma}$$^{(2)}$ & $F_{\gamma}$$^{(2)}$& 
+ $F_{\gamma}$$^{(3)}$ & $\eg^2\,\dd F_{\gamma}/\dd \eg$$^{(4)}$ &
+ $\eg^2\,\dd F_{\gamma,0.1}/\dd \eg$$^{(4,5)}$ & 
+ $\eg^2\,\dd F_{\gamma,1.0}/\dd \eg$$^{(4,6)}$ & S/N$^{(7)}$ \\
   & & $(>100\,\rmn{MeV})$ & $(>1\,\rmn{GeV})$ & $(>100\,\rmn{GeV})$ & 
- $(5\,\rmn{GeV})$ & $(5\,\rmn{GeV})$ &  $(5\,\rmn{GeV})$\\
- \hline
-FORNAX   &  10 &  12.71 &  80.57 &  44.45 &  12.76 &   0.09 &   2.61 \\
-OPHIUCHUS &  96 &   9.95 &  63.10 &  34.81 &   9.99 &   0.27 &   3.90 \\
-COMA     &  34 &   8.26 &  52.38 &  28.89 &   8.29 &   0.22 &   3.20 \\
-NORMA    &  94 &   7.48 &  47.43 &  26.16 &   7.51 &   0.17 &   2.68 \\
-CENTAURUS &  30 &   7.24 &  45.87 &  25.31 &   7.26 &   0.12 &   2.28 \\
-PERSEUS  &  68 &   7.15 &  45.30 &  24.99 &   7.17 &   0.18 &   2.67 \\
-HYDRA    &  25 &   6.75 &  42.81 &  23.61 &   6.78 &   0.12 &   2.23 \\
-M49      &  81 &   5.98 &  37.93 &  20.92 &   6.00 &   0.06 &   1.51 \\
-NGC4636  &  29 &   4.42 &  28.01 &  15.45 &   4.44 &   0.05 &   1.14 \\
-AWM7     &  67 &   4.30 &  27.24 &  15.03 &   4.31 &   0.13 &   1.76 \\
-3C129    &  70 &   4.06 &  25.74 &  14.20 &   4.08 &   0.15 &   1.79 \\
-A1367    &  26 &   2.51 &  15.92 &   8.78 &   2.52 &   0.11 &   1.20 \\
-NGC5846  &  92 &   2.48 &  15.73 &   8.68 &   2.49 &   0.05 &   0.86 \\
-A0754    &  23 &   2.14 &  13.57 &   7.49 &   2.15 &   0.17 &   1.26 \\
-TRIANGULUM &  95 &   1.85 &  11.72 &   6.47 &   1.86 &   0.16 &   1.10 \\
-A3571    &  39 &   1.84 &  11.68 &   6.45 &   1.85 &   0.14 &   1.05 \\
-NGC5813  &  91 &   1.59 &  10.06 &   5.55 &   1.59 &   0.04 &   0.62 \\
-ANTLIA   &  79 &   1.58 &  10.03 &   5.53 &   1.59 &   0.06 &   0.71 \\
-A2199    &  51 &   1.54 &   9.73 &   5.37 &   1.54 &   0.11 &   0.85 \\
-A3266    &  17 &   1.50 &   9.49 &   5.24 &   1.50 &   0.15 &   0.94 \\
-A2877    &  65 &   1.48 &   9.40 &   5.18 &   1.49 &   0.09 &   0.79 \\
-NGC5044  &  35 &   1.42 &   9.00 &   4.97 &   1.43 &   0.05 &   0.61 \\
-A3395n   &  75 &   1.35 &   8.57 &   4.73 &   1.36 &   0.13 &   0.83 \\
-A3395s   &  21 &   1.35 &   8.56 &   4.72 &   1.36 &   0.13 &   0.83 \\
-A2256    &  54 &   1.34 &   8.49 &   4.68 &   1.34 &   0.14 &   0.85 \\
-A0576    &  22 &   1.31 &   8.28 &   4.57 &   1.31 &   0.11 &   0.77 \\
-NGC1550  &  15 &   1.30 &   8.25 &   4.55 &   1.31 &   0.06 &   0.62 \\
-A2319    &  98 &   1.25 &   7.92 &   4.37 &   1.25 &   0.13 &   0.80 \\
-A3376    &  19 &   1.24 &   7.85 &   4.33 &   1.24 &   0.12 &   0.76 \\
-A0119    &   2 &   1.19 &   7.54 &   4.16 &   1.19 &   0.11 &   0.73 \\
-A2634    &  60 &   1.11 &   7.07 &   3.90 &   1.12 &   0.09 &   0.65 \\
-A0262    &   5 &   1.02 &   6.46 &   3.57 &   1.02 &   0.06 &   0.53 \\
-A2065    &  46 &   0.98 &   6.21 &   3.42 &   0.98 &   0.13 &   0.67 \\
-A0539    &  71 &   0.90 &   5.70 &   3.14 &   0.90 &   0.08 &   0.53 \\
-MKW8     &  42 &   0.89 &   5.65 &   3.12 &   0.89 &   0.07 &   0.52 \\
-A1795    &  40 &   0.87 &   5.50 &   3.03 &   0.87 &   0.11 &   0.58 \\
-A0644    &  78 &   0.85 &   5.42 &   2.99 &   0.86 &   0.11 &   0.59 \\
-A4038    &  62 &   0.82 &   5.23 &   2.88 &   0.83 &   0.07 &   0.49 \\
-A0496    &  18 &   0.80 &   5.09 &   2.81 &   0.81 &   0.08 &   0.49 \\
-IIIZw54  &  12 &   0.80 &   5.05 &   2.79 &   0.80 &   0.07 &   0.49 \\
-A2147    &  49 &   0.78 &   4.97 &   2.74 &   0.79 &   0.08 &   0.49 \\
-A3558    &  37 &   0.77 &   4.88 &   2.69 &   0.77 &   0.09 &   0.51 \\
-A3667    &  56 &   0.75 &   4.74 &   2.62 &   0.75 &   0.09 &   0.51 \\
-A0085    &   1 &   0.73 &   4.64 &   2.56 &   0.73 &   0.09 &   0.50 \\
-A2063    &  47 &   0.72 &   4.58 &   2.52 &   0.72 &   0.07 &   0.46 \\
-A0399    &   7 &   0.69 &   4.39 &   2.42 &   0.69 &   0.10 &   0.49 \\
-UGC03957 &  76 &   0.69 &   4.35 &   2.40 &   0.69 &   0.07 &   0.43 \\
-A2029    &  43 &   0.68 &   4.34 &   2.39 &   0.69 &   0.10 &   0.49 \\
-A0400    &   6 &   0.68 &   4.31 &   2.38 &   0.68 &   0.06 &   0.41 \\
-A3158    &  13 &   0.67 &   4.26 &   2.35 &   0.67 &   0.09 &   0.46 \\
+ $(5\,\rmn{GeV})$ & $(5\,\rmn{GeV})$ &  $(5\,\rmn{GeV})$ & \\
+ \hline
+FORNAX   &  10 &  31.88 &  20.21 &  11.15 &  32.00 &  31.98 &  30.27 &   9.93 \\
+M49      &  81 &  19.48 &  12.35 &   6.81 &  19.55 &  19.54 &  18.13 &   9.29 \\
+OPHIUCHU &  96 &  18.13 &  11.49 &   6.34 &  18.19 &  18.14 &  12.31 &   1.66 \\
+CENTAURU &  30 &  14.99 &   9.50 &   5.24 &  15.05 &  15.02 &  12.40 &   2.32 \\
+HYDRA    &  25 &   9.19 &   5.82 &   3.21 &   9.22 &   9.20 &   6.89 &   2.32 \\
+NGC4636  &  29 &   9.12 &   5.78 &   3.19 &   9.15 &   9.14 &   8.19 &   5.38 \\
+NORMA    &  94 &   8.15 &   5.17 &   2.85 &   8.18 &   8.16 &   5.42 &   1.20 \\
+PERSEUS  &  68 &   7.80 &   4.95 &   2.73 &   7.83 &   7.80 &   4.95 &   0.53 \\
+COMA     &  34 &   7.58 &   4.81 &   2.65 &   7.61 &   7.58 &   4.41 &   0.95 \\
+AWM7     &  67 &   7.31 &   4.64 &   2.56 &   7.34 &   7.31 &   4.66 &   1.39 \\
+A1367    &  26 &   6.67 &   4.23 &   2.33 &   6.69 &   6.66 &   3.84 &   1.95 \\
+NGC5813  &  91 &   6.25 &   3.96 &   2.19 &   6.28 &   6.27 &   4.97 &   4.26 \\
+ANTLIA   &  79 &   5.90 &   3.74 &   2.06 &   5.92 &   5.90 &   4.02 &   2.58 \\
+A2877    &  65 &   5.00 &   3.17 &   1.75 &   5.02 &   4.99 &   2.54 &   2.66 \\
+3C129    &  70 &   4.71 &   2.99 &   1.65 &   4.73 &   4.70 &   2.42 &   1.02 \\
+NGC5044  &  35 &   3.59 &   2.28 &   1.26 &   3.61 &   3.59 &   2.35 &   1.67 \\
+NGC5846  &  92 &   3.34 &   2.12 &   1.17 &   3.36 &   3.35 &   2.40 &   3.40 \\
+NGC1550  &  15 &   2.53 &   1.61 &   0.89 &   2.54 &   2.53 &   1.36 &   1.15 \\
+A3571    &  39 &   2.24 &   1.42 &   0.78 &   2.25 &   2.22 &   0.67 &   0.45 \\
+TRIANGUL &  95 &   2.16 &   1.37 &   0.76 &   2.17 &   2.13 &   0.56 &   0.42 \\
+A2199    &  51 &   2.05 &   1.30 &   0.72 &   2.06 &   2.03 &   0.68 &   0.50 \\
+A2634    &  60 &   2.02 &   1.28 &   0.71 &   2.03 &   2.01 &   0.66 &   1.03 \\
+A3266    &  17 &   2.00 &   1.27 &   0.70 &   2.01 &   1.97 &   0.46 &   0.53 \\
+A0496    &  18 &   1.93 &   1.22 &   0.67 &   1.94 &   1.91 &   0.60 &   0.49 \\
+A0262    &   5 &   1.92 &   1.21 &   0.67 &   1.92 &   1.91 &   0.84 &   0.64 \\
+A0754    &  23 &   1.88 &   1.19 &   0.66 &   1.89 &   1.85 &   0.45 &   0.66 \\
+A0119    &   2 &   1.87 &   1.19 &   0.65 &   1.88 &   1.84 &   0.49 &   0.68 \\
+IIIZw54  &  12 &   1.72 &   1.09 &   0.60 &   1.73 &   1.71 &   0.53 &   1.03 \\
+A2319    &  98 &   1.62 &   1.03 &   0.57 &   1.62 &   1.59 &   0.35 &   0.32 \\
+A2657    &  61 &   1.55 &   0.98 &   0.54 &   1.55 &   1.53 &   0.40 &   0.73 \\
+A3395s   &  21 &   1.51 &   0.96 &   0.53 &   1.52 &   1.49 &   0.34 &   0.76 \\
+A0539    &  71 &   1.50 &   0.95 &   0.52 &   1.50 &   1.48 &   0.45 &   0.71 \\
+A4038    &  62 &   1.48 &   0.94 &   0.52 &   1.49 &   1.47 &   0.45 &   0.52 \\
+A0576    &  22 &   1.37 &   0.87 &   0.48 &   1.37 &   1.35 &   0.34 &   0.72 \\
+A3376    &  19 &   1.34 &   0.85 &   0.47 &   1.34 &   1.31 &   0.30 &   0.69 \\
+A1644    &  31 &   1.33 &   0.84 &   0.47 &   1.34 &   1.31 &   0.29 &   0.51 \\
+A3395n   &  75 &   1.32 &   0.84 &   0.46 &   1.32 &   1.29 &   0.28 &   0.78 \\
+MKW8     &  42 &   1.32 &   0.83 &   0.46 &   1.32 &   1.30 &   0.39 &   0.87 \\
+UGC03957 &  76 &   1.28 &   0.81 &   0.45 &   1.28 &   1.26 &   0.33 &   0.74 \\
+A2256    &  54 &   1.27 &   0.81 &   0.44 &   1.28 &   1.24 &   0.24 &   0.37 \\
+A3558    &  37 &   1.20 &   0.76 &   0.42 &   1.20 &   1.17 &   0.25 &   0.35 \\
+A0400    &   6 &   1.17 &   0.74 &   0.41 &   1.17 &   1.16 &   0.35 &   0.66 \\
+A3581    &  41 &   1.07 &   0.68 &   0.37 &   1.07 &   1.06 &   0.33 &   0.51 \\
+2A0335   &  11 &   1.05 &   0.67 &   0.37 &   1.05 &   1.03 &   0.25 &   0.26 \\
+A0085    &   1 &   1.04 &   0.66 &   0.36 &   1.04 &   1.01 &   0.18 &   0.27 \\
+A2052    &  44 &   1.01 &   0.64 &   0.35 &   1.02 &   1.00 &   0.24 &   0.36 \\
+A1795    &  40 &   1.00 &   0.64 &   0.35 &   1.01 &   0.97 &   0.16 &   0.27 \\
+NGC507   &   4 &   0.99 &   0.63 &   0.35 &   1.00 &   0.99 &   0.34 &   1.28 \\
+MKW4     &  27 &   0.95 &   0.60 &   0.33 &   0.95 &   0.94 &   0.29 &   0.65 \\
+NGC499   &  66 &   0.95 &   0.60 &   0.33 &   0.95 &   0.94 &   0.33 &   1.53 \\
 \hline
@@
    (2) In units of  $10^{-11} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
-   (3) In units of  $10^{-12} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
-   (4) In units of  $10^{-14} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
-   (5) In units of  $10^{-11} \rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
-   (6) The flux within $0.1^\circ$, smoothed with a point spread function of $0.1^\circ$. 
-   (7) The flux within $0.1^\circ$, smoothed with a point spread function of $0.1^\circ$. 
+   (3) In units of  $10^{-13} \rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (4) In units of  $10^{-11} \rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$.
+   (5) The flux within $0.1^\circ$, smoothed with a point spread function of $0.1^\circ$. 
+   (6) The flux within $1.0^\circ$, smoothed with a point spread function of $0.1^\circ$. 
+   (7) Signal to noise (S/N) within $\rvir$ above $1\,$GeV. We estimate the signal to 
+  noise through $\sqrt{t_\rmn{obs}\,A_\rmn{eff}}\,F_{\gamma}/\sqrt{F_{\gamma}+F_{\gamma,\CR}}$, 
+  where $t_\rmn{obs}=3\,$yrs is the observation time and $A_\rmn{eff} = 7000\,\cm^2$ 
+    is the effective area of Fermi-Lat at $1\,$GeV.
   \label{tab:flux_tab_BM}
@@
   \caption{Gamma-ray LP-IC-CMB and LP-BS flux within $\rvir$ from brightest 50 clusters in HIFLUGCS catalogue.}
-\begin{tabular}{l  c c c c c c c}
+\begin{tabular}{l  c c c c c c c c}
 \hline
@@
  $\eg^2\,\dd F_{\gamma,0.1}/\dd \eg$$^{(5,6)}$ & 
- $\eg^2\,\dd F_{\gamma,1.0}/\dd \eg$$^{(5,7)}$\\
+ $\eg^2\,\dd F_{\gamma,1.0}/\dd \eg$$^{(5,7)}$ & S/N$^{(8)}$ \\
   & & $(>100\,\rmn{MeV})$ & $(>1\,\rmn{GeV})$ & $(>100\,\rmn{GeV})$ & 
- $(5\,\rmn{GeV})$ & $(5\,\rmn{GeV})$ &  $(5\,\rmn{GeV})$\\
- \hline
-FORNAX   &  10 &  13.70 &  17.37 &  20.12 &  16.99 &   0.05 &   1.91 \\
-OPHIUCHU &  96 &  11.00 &  13.95 &  15.76 &  13.64 &   0.20 &   3.01 \\
-COMA     &  34 &   8.97 &  11.38 &  13.08 &  11.13 &   0.15 &   2.42 \\
-CENTAURU &  30 &   8.00 &  10.14 &  11.46 &   9.92 &   0.08 &   1.75 \\
-NORMA    &  94 &   7.98 &  10.11 &  11.85 &   9.89 &   0.10 &   1.99 \\
-PERSEUS  &  68 &   7.93 &  10.06 &  11.31 &   9.83 &   0.13 &   2.07 \\
-HYDRA    &  25 &   7.44 &   9.43 &  10.69 &   9.22 &   0.09 &   1.71 \\
-M49      &  81 &   6.53 &   8.28 &   9.47 &   8.10 &   0.04 &   1.13 \\
-NGC4636  &  29 &   4.78 &   6.06 &   7.00 &   5.93 &   0.03 &   0.85 \\
-AWM7     &  67 &   4.71 &   5.97 &   6.80 &   5.84 &   0.09 &   1.34 \\
-3C129    &  70 &   4.34 &   5.51 &   6.43 &   5.38 &   0.10 &   1.34 \\
-NGC5846  &  92 &   2.70 &   3.42 &   3.93 &   3.35 &   0.03 &   0.65 \\
-A1367    &  26 &   2.64 &   3.35 &   3.98 &   3.28 &   0.07 &   0.89 \\
-A0754    &  23 &   2.37 &   3.00 &   3.39 &   2.93 &   0.13 &   0.97 \\
-A3571    &  39 &   2.03 &   2.57 &   2.92 &   2.52 &   0.10 &   0.81 \\
-TRIANGUL &  95 &   2.02 &   2.56 &   2.93 &   2.51 &   0.11 &   0.85 \\
-NGC5813  &  91 &   1.72 &   2.18 &   2.51 &   2.13 &   0.03 &   0.47 \\
-A2199    &  51 &   1.69 &   2.14 &   2.43 &   2.10 &   0.08 &   0.66 \\
-A3266    &  17 &   1.61 &   2.04 &   2.37 &   1.99 &   0.10 &   0.72 \\
-A2877    &  65 &   1.60 &   2.03 &   2.35 &   1.98 &   0.06 &   0.60 \\
-ANTLIA   &  79 &   1.60 &   2.02 &   2.51 &   1.98 &   0.03 &   0.51 \\
-NGC5044  &  35 &   1.55 &   1.96 &   2.25 &   1.92 &   0.03 &   0.47 \\
-A3395s   &  21 &   1.45 &   1.83 &   2.14 &   1.79 &   0.09 &   0.63 \\
-A2256    &  54 &   1.44 &   1.83 &   2.12 &   1.79 &   0.10 &   0.65 \\
-A3395n   &  75 &   1.44 &   1.82 &   2.14 &   1.78 &   0.09 &   0.63 \\
-NGC1550  &  15 &   1.42 &   1.80 &   2.06 &   1.76 &   0.04 &   0.47 \\
-A0576    &  22 &   1.41 &   1.78 &   2.07 &   1.74 &   0.08 &   0.59 \\
-A2319    &  98 &   1.36 &   1.72 &   1.98 &   1.69 &   0.09 &   0.61 \\
-A3376    &  19 &   1.30 &   1.65 &   1.96 &   1.61 &   0.08 &   0.57 \\
-A0119    &   2 &   1.24 &   1.58 &   1.88 &   1.54 &   0.07 &   0.55 \\
-A2634    &  60 &   1.17 &   1.48 &   1.77 &   1.45 &   0.06 &   0.49 \\
-A0262    &   5 &   1.11 &   1.41 &   1.61 &   1.38 &   0.04 &   0.41 \\
-A2065    &  46 &   1.06 &   1.34 &   1.55 &   1.31 &   0.09 &   0.51 \\
-A0539    &  71 &   0.98 &   1.24 &   1.42 &   1.21 &   0.05 &   0.41 \\
-MKW8     &  42 &   0.97 &   1.23 &   1.41 &   1.20 &   0.05 &   0.40 \\
-A1795    &  40 &   0.96 &   1.22 &   1.37 &   1.20 &   0.08 &   0.45 \\
-A0644    &  78 &   0.94 &   1.20 &   1.35 &   1.17 &   0.09 &   0.46 \\
-A4038    &  62 &   0.91 &   1.15 &   1.31 &   1.13 &   0.05 &   0.38 \\
-A0496    &  18 &   0.89 &   1.13 &   1.27 &   1.10 &   0.06 &   0.38 \\
-IIIZw54  &  12 &   0.86 &   1.09 &   1.26 &   1.07 &   0.05 &   0.37 \\
-A3558    &  37 &   0.84 &   1.06 &   1.22 &   1.04 &   0.06 &   0.39 \\
-A2147    &  49 &   0.82 &   1.04 &   1.24 &   1.01 &   0.05 &   0.37 \\
-A0085    &   1 &   0.81 &   1.03 &   1.16 &   1.01 &   0.07 &   0.38 \\
-A3667    &  56 &   0.80 &   1.02 &   1.19 &   1.00 &   0.07 &   0.38 \\
-A2063    &  47 &   0.79 &   1.00 &   1.14 &   0.98 &   0.05 &   0.35 \\
-A2029    &  43 &   0.76 &   0.96 &   1.08 &   0.94 &   0.08 &   0.38 \\
-UGC03957 &  76 &   0.75 &   0.96 &   1.09 &   0.93 &   0.05 &   0.33 \\
-A0399    &   7 &   0.74 &   0.94 &   1.10 &   0.92 &   0.07 &   0.37 \\
-A3158    &  13 &   0.73 &   0.93 &   1.06 &   0.91 &   0.07 &   0.36 \\
-A0400    &   6 &   0.73 &   0.92 &   1.08 &   0.90 &   0.04 &   0.31 \\
+ $(5\,\rmn{GeV})$ & $(5\,\rmn{GeV})$ &  $(5\,\rmn{GeV})$ & \\
+ \hline
+FORNAX   &  10 &  34.87 &  44.21 &  50.48 &  43.11 &  43.09 &  40.74 & 363.17 \\
+M49      &  81 &  21.48 &  27.24 &  30.84 &  26.57 &  26.55 &  24.62 & 285.17 \\
+OPHIUCHU &  96 &  20.12 &  25.51 &  28.70 &  24.88 &  24.80 &  16.83 & 270.87 \\
+CENTAURU &  30 &  16.64 &  21.10 &  23.74 &  20.58 &  20.54 &  16.94 & 249.07 \\
+HYDRA    &  25 &  10.14 &  12.86 &  14.54 &  12.54 &  12.52 &   9.37 & 195.09 \\
+NGC4636  &  29 &   9.96 &  12.63 &  14.44 &  12.32 &  12.31 &  11.00 & 194.11 \\
+NORMA    &  94 &   8.72 &  11.05 &  12.91 &  10.78 &  10.75 &   7.15 & 178.66 \\
+PERSEUS  &  68 &   8.66 &  10.98 &  12.35 &  10.71 &  10.67 &   6.77 & 167.81 \\
+COMA     &  34 &   8.22 &  10.43 &  12.00 &  10.17 &  10.12 &   5.90 & 172.16 \\
+AWM7     &  67 &   8.08 &  10.24 &  11.58 &   9.99 &   9.96 &   6.34 & 173.06 \\
+A1367    &  26 &   7.24 &   9.18 &  10.56 &   8.95 &   8.91 &   5.14 & 164.76 \\
+NGC5813  &  91 &   6.88 &   8.72 &   9.90 &   8.50 &   8.49 &   6.73 & 161.29 \\
+ANTLIA   &  79 &   6.23 &   7.90 &   9.34 &   7.71 &   7.68 &   5.24 & 153.26 \\
+A2877    &  65 &   5.52 &   7.00 &   7.92 &   6.82 &   6.78 &   3.45 & 144.31 \\
+3C129    &  70 &   5.05 &   6.41 &   7.46 &   6.25 &   6.21 &   3.21 & 136.52 \\
+NGC5044  &  35 &   3.95 &   5.01 &   5.69 &   4.89 &   4.87 &   3.19 & 121.95 \\
+NGC5846  &  92 &   3.65 &   4.63 &   5.29 &   4.52 &   4.50 &   3.23 & 117.54 \\
+NGC1550  &  15 &   2.79 &   3.53 &   4.01 &   3.45 &   3.43 &   1.84 & 102.18 \\
+A3571    &  39 &   2.48 &   3.15 &   3.55 &   3.07 &   3.03 &   0.92 &  93.98 \\
+TRIANGUL &  95 &   2.37 &   3.01 &   3.42 &   2.93 &   2.88 &   0.76 &  91.42 \\
+A2199    &  51 &   2.26 &   2.87 &   3.24 &   2.80 &   2.76 &   0.93 &  90.34 \\
+A2634    &  60 &   2.22 &   2.81 &   3.20 &   2.74 &   2.71 &   0.90 &  91.15 \\
+A3266    &  17 &   2.18 &   2.76 &   3.17 &   2.69 &   2.63 &   0.62 &  88.94 \\
+A0496    &  18 &   2.14 &   2.72 &   3.06 &   2.65 &   2.62 &   0.83 &  88.06 \\
+A0262    &   5 &   2.11 &   2.67 &   3.03 &   2.60 &   2.58 &   1.14 &  88.12 \\
+A0754    &  23 &   2.08 &   2.63 &   2.98 &   2.57 &   2.52 &   0.61 &  87.59 \\
+A0119    &   2 &   2.00 &   2.53 &   2.96 &   2.47 &   2.43 &   0.66 &  85.95 \\
+IIIZw54  &  12 &   1.89 &   2.39 &   2.73 &   2.33 &   2.30 &   0.72 &  84.11 \\
+A2319    &  98 &   1.77 &   2.24 &   2.56 &   2.19 &   2.13 &   0.47 &  78.11 \\
+A2657    &  61 &   1.71 &   2.17 &   2.45 &   2.12 &   2.08 &   0.54 &  79.87 \\
+A0539    &  71 &   1.65 &   2.09 &   2.37 &   2.04 &   2.01 &   0.62 &  78.43 \\
+A4038    &  62 &   1.64 &   2.08 &   2.35 &   2.03 &   2.01 &   0.62 &  77.70 \\
+A3395s   &  21 &   1.62 &   2.06 &   2.40 &   2.01 &   1.96 &   0.46 &  77.82 \\
+A0576    &  22 &   1.47 &   1.87 &   2.17 &   1.82 &   1.79 &   0.46 &  74.13 \\
+A1644    &  31 &   1.45 &   1.84 &   2.11 &   1.79 &   1.75 &   0.39 &  72.99 \\
+MKW8     &  42 &   1.44 &   1.83 &   2.08 &   1.78 &   1.76 &   0.53 &  73.51 \\
+UGC03957 &  76 &   1.41 &   1.79 &   2.02 &   1.75 &   1.71 &   0.45 &  72.64 \\
+A3376    &  19 &   1.41 &   1.78 &   2.12 &   1.74 &   1.70 &   0.40 &  72.39 \\
+A3395n   &  75 &   1.40 &   1.78 &   2.09 &   1.73 &   1.69 &   0.37 &  72.41 \\
+A2256    &  54 &   1.37 &   1.73 &   2.01 &   1.69 &   1.64 &   0.32 &  70.00 \\
+A3558    &  37 &   1.31 &   1.66 &   1.89 &   1.62 &   1.58 &   0.34 &  68.43 \\
+A0400    &   6 &   1.26 &   1.60 &   1.85 &   1.56 &   1.54 &   0.47 &  68.55 \\
+A3581    &  41 &   1.18 &   1.50 &   1.70 &   1.46 &   1.44 &   0.45 &  66.12 \\
+2A0335   &  11 &   1.17 &   1.48 &   1.66 &   1.44 &   1.41 &   0.34 &  63.65 \\
+A0085    &   1 &   1.15 &   1.46 &   1.64 &   1.42 &   1.38 &   0.25 &  63.47 \\
+A2052    &  44 &   1.13 &   1.43 &   1.61 &   1.39 &   1.36 &   0.32 &  63.85 \\
+A1795    &  40 &   1.11 &   1.41 &   1.59 &   1.38 &   1.33 &   0.23 &  62.45 \\
+NGC507   &   4 &   1.09 &   1.39 &   1.57 &   1.35 &   1.34 &   0.46 &  64.25 \\
+MKW4     &  27 &   1.04 &   1.32 &   1.50 &   1.29 &   1.27 &   0.39 &  62.49 \\
+NGC499   &  66 &   1.04 &   1.32 &   1.50 &   1.28 &   1.27 &   0.45 &  62.65 \\
 \hline
@@
    (6) The flux within $0.1^\circ$, smoothed with a point spread function of $0.1^\circ$. 
-   (7) The flux within $0.1^\circ$, smoothed with a point spread function of $0.1^\circ$. 
+   (7) The flux within $1.0^\circ$, smoothed with a point spread function of $0.1^\circ$. 
+   (8) Signal to noise (S/N) within $\rvir$ above $1\,$GeV. We estimate the signal to 
+  noise through $\sqrt{t_\rmn{obs}\,A_\rmn{eff}}\,F_{\gamma}/\sqrt{F_{\gamma}+F_{\gamma,\CR}}$, 
+  where $t_\rmn{obs}=3\,$yrs is the observation time and $A_\rmn{eff} = 7000\,\cm^2$ 
+    is the effective area of Fermi-Lat at $1\,$GeV.
  \label{tab:flux_tab_LP}
@@
   \caption{Galaxy cluster parameters for to all clusters in the HIFLUGCS catalogue.}
-\begin{tabular}{l  c c c c c c c c c c c}
-\hline
-\hline
-Cluster & ID$^{(1)}$ & $D_\clu$$^{(1)}$ & $\rvir$$^{(1)}$ & $\rvir$ & 
-$\mvir$$^{(1)}$ & $\rho_\rmn{gas}(0)$$^{(2)}$ & $r_\rmn{core}$$^{(2)}$ & 
-$\beta$$^{(2)}$ & $r_\rmn{hlr,CR}$$^{(3)}$ & $r_\rmn{hlr,DM}$  $^{(4)}$ \\
-& & [Mpc] & [Mpc] & [deg] & [$10^{14}\,\msun$] & 
-[$10^{-27}\,\rmn{g}\,\rmn{cm}^{-3}$] & [kpc] &  & [deg] & [deg] \\
- \hline
-A0085    &   1 & 248.29 &   1.90 &   0.44 &   7.71 &  24.54 &  59.29 &   0.53 &   0.04 &   0.20 \\
-A0119    &   2 & 194.82 &   1.90 &   0.56 &   7.69 &   1.93 & 357.86 &   0.68 &   0.13 &   0.26 \\
-A0133    &   3 & 254.34 &   1.41 &   0.32 &   3.15 &  35.76 &  32.14 &   0.53 &   0.02 &   0.15 \\
-NGC507   &   4 &  71.57 &   0.74 &   0.59 &   0.46 &  23.05 &  13.57 &   0.44 &   0.07 &   0.28 \\
-A0262    &   5 &  69.81 &   0.96 &   0.79 &   1.01 &  14.38 &  30.00 &   0.44 &   0.14 &   0.37 \\
-A0400    &   6 & 104.69 &   1.09 &   0.60 &   1.48 &   3.40 & 110.00 &   0.53 &   0.12 &   0.28 \\
-A0399    &   7 & 323.00 &   2.19 &   0.39 &  11.89 &   3.40 & 321.43 &   0.71 &   0.07 &   0.18 \\
-A0401    &   8 & 338.70 &   2.19 &   0.37 &  11.85 &   7.84 & 175.71 &   0.61 &   0.05 &   0.17 \\
-A3112    &   9 & 339.66 &   1.74 &   0.29 &   5.87 &  43.07 &  43.57 &   0.58 &   0.02 &   0.14 \\
-FORNAX   &  10 &  19.77 &   0.96 &   2.79 &   1.01 &   2.48 & 124.29 &   0.80 &   0.31 &   1.30 \\
-2A0335   &  11 & 153.49 &   1.31 &   0.49 &   2.51 &  93.06 &  23.57 &   0.57 &   0.02 &   0.23 \\
-IIIZw54  &  12 & 136.39 &   1.35 &   0.57 &   2.81 &   3.86 & 206.43 &   0.89 &   0.07 &   0.26 \\
-A3158    &  13 & 264.13 &   1.92 &   0.42 &   8.06 &   5.96 & 192.14 &   0.66 &   0.06 &   0.19 \\
-A0478    &  14 & 411.96 &   2.24 &   0.31 &  12.78 &  35.47 &  70.00 &   0.61 &   0.02 &   0.14 \\
-NGC1550  &  15 &  53.18 &   0.88 &   0.95 &   0.78 &  15.86 &  32.14 &   0.55 &   0.07 &   0.44 \\
-EXO0422  &  16 & 172.04 &   1.43 &   0.48 &   3.31 &  11.91 & 101.43 &   0.72 &   0.04 &   0.22 \\
-A3266    &  17 & 266.00 &   2.46 &   0.53 &  16.97 &   3.17 & 402.86 &   0.80 &   0.08 &   0.25 \\
-A0496    &  18 & 144.03 &   1.40 &   0.56 &   3.11 &  51.30 &  21.43 &   0.48 &   0.05 &   0.26 \\
-A3376    &  19 & 201.69 &   1.96 &   0.56 &   8.54 &   1.70 & 539.29 &   1.05 &   0.10 &   0.26 \\
-A3391    &  20 & 236.69 &   1.74 &   0.42 &   6.01 &   3.93 & 167.14 &   0.58 &   0.07 &   0.20 \\
-A3395s   &  21 & 221.45 &   2.14 &   0.55 &  10.96 &   2.07 & 431.43 &   0.96 &   0.08 &   0.26 \\
-A0576    &  22 & 167.96 &   1.79 &   0.61 &   6.40 &   2.97 & 281.43 &   0.82 &   0.08 &   0.28 \\
-A0754    &  23 & 235.31 &   2.55 &   0.62 &  18.71 &   5.98 & 170.71 &   0.70 &   0.05 &   0.29 \\
-HYDRA-A  &  24 & 239.94 &   1.55 &   0.37 &   4.24 &  53.04 &  35.71 &   0.57 &   0.02 &   0.17 \\
-HYDRA    &  25 &  49.25 &   1.39 &   1.62 &   3.03 &   8.20 &  67.14 &   0.61 &   0.13 &   0.75 \\
-A1367    &  26 &  94.05 &   1.53 &   0.93 &   4.06 &   2.02 & 273.57 &   0.69 &   0.19 &   0.43 \\
-MKW4     &  27 &  86.98 &   0.86 &   0.56 &   0.71 &  50.43 &   7.86 &   0.44 &   0.06 &   0.26 \\
-ZwCl1215 &  28 & 339.66 &   2.09 &   0.35 &  10.37 &   4.07 & 307.86 &   0.82 &   0.05 &   0.16 \\
-NGC4636  &  29 &  15.89 &   0.61 &   2.19 &   0.25 &  55.18 &   4.29 &   0.49 &   0.07 &   1.02 \\
-CENTAURU &  30 &  44.46 &   1.34 &   1.72 &   2.70 &  24.45 &  26.43 &   0.49 &   0.14 &   0.80 \\
-A1644    &  31 & 210.40 &   1.62 &   0.44 &   4.81 &   3.49 & 214.29 &   0.58 &   0.10 &   0.21 \\
-A1650    &  32 & 385.28 &   2.15 &   0.32 &  11.14 &   6.77 & 200.71 &   0.70 &   0.04 &   0.15 \\
-A1651    &  33 & 392.54 &   1.96 &   0.29 &   8.51 &  11.72 & 129.29 &   0.64 &   0.03 &   0.13 \\
-COMA     &  34 & 101.14 &   2.30 &   1.30 &  13.84 &   4.34 & 245.71 &   0.65 &   0.20 &   0.60 \\
-NGC5044  &  35 &  38.81 &   0.74 &   1.10 &   0.46 &  81.77 &   7.86 &   0.52 &   0.03 &   0.51 \\
-A1736    &  36 & 204.44 &   1.34 &   0.37 &   2.70 &   2.10 & 267.14 &   0.54 &   0.12 &   0.17 \\
-A3558    &  37 & 213.16 &   1.76 &   0.47 &   6.17 &   6.51 & 160.00 &   0.58 &   0.08 &   0.22 \\
-A3562    &  38 & 221.91 &   1.54 &   0.40 &   4.16 &   8.30 &  70.71 &   0.47 &   0.08 &   0.18 \\
-A3571    &  39 & 175.22 &   2.04 &   0.67 &   9.51 &  10.39 & 129.29 &   0.61 &   0.07 &   0.31 \\
-A1795    &  40 & 276.29 &   2.14 &   0.44 &  10.99 &  35.96 &  55.71 &   0.60 &   0.02 &   0.21 \\
-A3581    &  41 &  93.17 &   0.99 &   0.61 &   1.09 &  31.10 &  25.00 &   0.54 &   0.03 &   0.28 \\
-MKW8     &  42 & 118.04 &   1.28 &   0.62 &   2.38 &   5.06 &  76.43 &   0.51 &   0.10 &   0.29 \\
-A2029    &  43 & 347.78 &   2.29 &   0.38 &  13.42 &  38.80 &  59.29 &   0.58 &   0.02 &   0.17 \\
-A2052    &  44 & 153.04 &   1.25 &   0.47 &   2.21 &  44.71 &  26.43 &   0.53 &   0.03 &   0.22 \\
-MKW3S    &  45 & 199.40 &   1.45 &   0.42 &   3.46 &  26.57 &  47.14 &   0.58 &   0.02 &   0.19 \\
-A2065    &  46 & 325.85 &   2.45 &   0.43 &  16.69 &   3.31 & 492.86 &   1.16 &   0.05 &   0.20 \\
-A2063    &  47 & 155.75 &   1.42 &   0.52 &   3.24 &  10.17 &  78.57 &   0.56 &   0.06 &   0.24 \\
-A2142    &  48 & 411.47 &   2.36 &   0.33 &  15.03 &  18.05 & 110.00 &   0.59 &   0.03 &   0.15 \\
-A2147    &  49 & 154.39 &   1.45 &   0.54 &   3.46 &   2.41 & 170.00 &   0.44 &   0.18 &   0.25 \\
-A2163    &  50 & 990.91 &   3.21 &   0.19 &  37.14 &   6.43 & 370.71 &   0.80 &   0.02 &   0.09 \\
-A2199    &  51 & 132.35 &   1.62 &   0.70 &   4.81 &  13.66 &  99.29 &   0.66 &   0.06 &   0.33 \\
-A2204    &  52 & 727.47 &   2.06 &   0.16 &   9.85 &  73.26 &  47.86 &   0.60 &   0.01 &   0.08 \\
-A2244    &  53 & 446.19 &   2.06 &   0.27 &   9.84 &  17.26 &  90.00 &   0.61 &   0.02 &   0.12 \\
-A2256    &  54 & 269.27 &   2.40 &   0.51 &  15.58 &   3.90 & 419.29 &   0.91 &   0.07 &   0.24 \\
-A2255    &  55 & 363.60 &   2.27 &   0.36 &  13.32 &   2.40 & 423.57 &   0.80 &   0.06 &   0.17 \\
+\begin{tabular}{l  c c c c c c c c c c c c c}
+\hline
+\hline
+Cluster & ID$^{(1)}$ & $D_\clu$$^{(1)}$ & $\rvir$$^{(2)}$ & $\rvir$ & 
+$\mvir$$^{(2)}$ & $n_\rmn{e,1}(0)$$^{(3)}$ & $r_\rmn{core,1}$$^{(3)}$ & 
+$\beta_1$$^{(3)}$ & $n_\rmn{e,2}(0)$$^{(3)}$ & $r_\rmn{core,2}$$^{(3)}$ & 
+$\beta_2$$^{(3)}$ & $r_\rmn{hlr,CR}$$^{(4)}$ & $r_\rmn{hlr,DM}$  $^{(5)}$ \\
+& & [Mpc] & [Mpc] & [deg] & [$10^{14}\,\msun$] 
+& [$10^{-2}\,\rmn{cm}^{-3}$] & [kpc] &  & 
+  [$10^{-2}\,\rmn{cm}^{-3}$] & [kpc] &  & [deg] & [deg] \\
+ \hline
+A0085    &   1 & 248.29 &   2.11 &   0.49 &  10.90 &   3.02 &  41 &   0.60 &   0.32 &  275 &   0.73 &   0.04 &   0.22 \vst \\
+A0119    &   2 & 194.82 &   2.18 &   0.64 &  11.90 &   0.17 & 285 &   0.76 &   0.06 & 1079 &   1.46 &   0.12 &   0.29 \vst \\
+A0133    &   3 & 254.34 &   1.78 &   0.40 &   6.50 &   3.30 &  30 &   0.65 &   0.24 &  229 &   0.78 &   0.02 &   0.18 \vst \\
+NGC507   &   4 &  71.57 &   0.97 &   0.78 &   1.10 &   0.59 &  29 &   0.76 &   1.24 &   52 &   4.29 &   0.01 &   0.35 \vst \\
+A0262    &   5 &  69.81 &   1.17 &   0.96 &   1.90 &   0.96 &  29 &   0.44 &   0.00 &    0 &   0.00 &   0.17 &   0.44 \vst \\
+A0400    &   6 & 104.69 &   1.29 &   0.71 &   2.50 &   0.24 & 110 &   0.53 &   0.00 &    0 &   0.00 &   0.13 &   0.32 \vst \\
+A0399    &   7 & 323.00 &   2.09 &   0.37 &  10.50 &   0.26 & 320 &   0.71 &   0.00 &    0 &   0.00 &   0.07 &   0.17 \vst \\
+A0401    &   8 & 338.70 &   2.13 &   0.36 &  11.20 &   0.69 & 170 &   0.69 &   0.17 &  375 &   0.66 &   0.05 &   0.16 \vst \\
+A3112    &   9 & 339.66 &   1.78 &   0.30 &   6.50 &   4.12 &  36 &   0.63 &   0.62 &  117 &   0.62 &   0.01 &   0.14 \vst \\
+FORNAX   &  10 &  19.77 &   1.28 &   3.70 &   2.40 &   0.11 & 123 &   0.80 &   0.00 &    0 &   0.00 &   0.31 &   1.69 \vst \\
+2A0335   &  11 & 153.49 &   1.58 &   0.59 &   4.50 &   6.47 &  23 &   0.57 &   0.00 &    0 &   0.00 &   0.02 &   0.27 \vst \\
+IIIZw54  &  12 & 136.39 &   1.71 &   0.72 &   5.80 &   0.24 & 206 &   0.89 &   0.00 &    0 &   0.00 &   0.07 &   0.33 \vst \\
+A3158    &  13 & 264.13 &   1.92 &   0.42 &   8.20 &   0.46 & 191 &   0.66 &   0.00 &    0 &   0.00 &   0.05 &   0.19 \vst \\
+A0478    &  14 & 411.96 &   2.17 &   0.30 &  11.70 &   4.14 &  51 &   0.68 &   0.73 &  180 &   0.71 &   0.02 &   0.14 \vst \\
+NGC1550  &  15 &  53.18 &   1.08 &   1.16 &   1.40 &   0.89 &  32 &   0.55 &   0.00 &    0 &   0.00 &   0.07 &   0.53 \vst \\
+EXO0422  &  16 & 172.04 &   1.57 &   0.52 &   4.40 &   0.78 & 101 &   0.72 &   0.00 &    0 &   0.00 &   0.04 &   0.24 \vst \\
+A3266    &  17 & 266.00 &   2.69 &   0.58 &  22.40 &   0.30 & 321 &   1.20 &   0.15 &  830 &   1.27 &   0.08 &   0.26 \vst \\
+A0496    &  18 & 144.03 &   1.83 &   0.73 &   7.10 &   4.80 &  21 &   0.59 &   0.34 &  183 &   0.69 &   0.04 &   0.33 \vst \\
+A3376    &  19 & 201.69 &   2.01 &   0.57 &   9.40 &   0.12 & 538 &   1.05 &   0.00 &    0 &   0.00 &   0.10 &   0.26 \vst \\
+A3391    &  20 & 236.69 &   1.95 &   0.47 &   8.50 &   0.46 &  50 &   0.50 &   0.21 &  239 &   0.66 &   0.07 &   0.22 \vst \\
+A3395s   &  21 & 221.45 &   2.21 &   0.57 &  12.40 &   0.15 & 431 &   0.96 &   0.00 &    0 &   0.00 &   0.08 &   0.26 \vst \\
+A0576    &  22 & 167.96 &   1.81 &   0.62 &   6.80 &   0.19 & 281 &   0.82 &   0.00 &    0 &   0.00 &   0.09 &   0.28 \vst \\
+A0754    &  23 & 235.31 &   2.45 &   0.60 &  17.00 &   0.52 & 170 &   0.70 &   0.00 &    0 &   0.00 &   0.05 &   0.27 \vst \\
+HYDRA-A  &  24 & 239.94 &   1.75 &   0.42 &   6.20 &   4.15 &  70 &   1.84 &   0.85 &  130 &   0.73 &   0.02 &   0.19 \vst \\
+HYDRA    &  25 &  49.25 &   1.53 &   1.78 &   4.10 &   0.56 &  67 &   0.61 &   0.00 &    0 &   0.00 &   0.13 &   0.81 \vst \\
+A1367    &  26 &  94.05 &   2.06 &   1.25 &  10.10 &   0.16 & 207 &   0.96 &   0.08 &  697 &   1.51 &   0.17 &   0.57 \vst \\
+MKW4     &  27 &  86.98 &   1.08 &   0.71 &   1.40 &   3.45 &   7 &   0.44 &   0.00 &    0 &   0.00 &   0.07 &   0.33 \vst \\
+ZwCl1215 &  28 & 339.66 &   2.21 &   0.37 &  12.40 &   0.32 & 307 &   0.82 &   0.00 &    0 &   0.00 &   0.05 &   0.17 \vst \\
+NGC4636  &  29 &  15.89 &   0.76 &   2.74 &   0.50 &   1.99 &   4 &   0.49 &   0.00 &    0 &   0.00 &   0.07 &   1.25 \vst \\
+CENTAURU &  30 &  44.46 &   1.67 &   2.15 &   5.30 &   2.16 &  23 &   0.57 &   0.16 &  194 &   0.70 &   0.15 &   0.98 \vst \\
+A1644    &  31 & 210.40 &   2.06 &   0.56 &  10.00 &   0.33 & 195 &   0.83 &   0.06 & 1549 &   2.38 &   0.10 &   0.26 \vst \\
+A1650    &  32 & 385.28 &   1.99 &   0.30 &   9.10 &   0.51 & 200 &   0.70 &   0.00 &    0 &   0.00 &   0.04 &   0.14 \vst \\
+A1651    &  33 & 392.54 &   2.13 &   0.31 &  11.10 &   1.24 &  85 &   0.75 &   0.39 &  254 &   0.76 &   0.03 &   0.14 \vst \\
+COMA     &  34 & 101.14 &   2.24 &   1.27 &  12.90 &   0.36 & 245 &   0.65 &   0.00 &    0 &   0.00 &   0.20 &   0.58 \vst \\
+NGC5044  &  35 &  38.81 &   0.99 &   1.46 &   1.10 &   4.08 &   7 &   0.52 &   0.00 &    0 &   0.00 &   0.03 &   0.67 \vst \\
+A1736    &  36 & 204.44 &   1.47 &   0.41 &   3.70 &   0.15 & 267 &   0.54 &   0.00 &    0 &   0.00 &   0.12 &   0.19 \vst \\
+A3558    &  37 & 213.16 &   2.01 &   0.54 &   9.30 &   0.54 & 165 &   0.68 &   0.07 &  855 &   1.17 &   0.08 &   0.25 \vst \\
+A3562    &  38 & 221.91 &   1.68 &   0.43 &   5.50 &   0.69 &  73 &   0.52 &   0.04 &  957 &   1.26 &   0.07 &   0.20 \vst \\
+A3571    &  39 & 175.22 &   2.16 &   0.71 &  11.60 &   1.14 &  67 &   0.82 &   0.60 &  182 &   0.68 &   0.07 &   0.32 \vst \\
+A1795    &  40 & 276.29 &   2.23 &   0.46 &  12.80 &   3.39 &  56 &   0.72 &   0.32 &  308 &   0.89 &   0.02 &   0.21 \vst \\
+A3581    &  41 &  93.17 &   1.17 &   0.72 &   1.80 &   1.91 &  25 &   0.54 &   0.00 &    0 &   0.00 &   0.04 &   0.33 \vst \\
+MKW8     &  42 & 118.04 &   1.44 &   0.70 &   3.50 &   0.31 &  75 &   0.51 &   0.00 &    0 &   0.00 &   0.11 &   0.32 \vst \\
+A2029    &  43 & 347.78 &   2.24 &   0.37 &  12.90 &   4.54 &  44 &   0.63 &   0.80 &  152 &   0.65 &   0.02 &   0.17 \vst \\
+A2052    &  44 & 153.04 &   1.56 &   0.58 &   4.40 &   3.30 &  60 &   2.10 &   0.71 &  100 &   0.66 &   0.03 &   0.27 \vst \\
+MKW3S    &  45 & 199.40 &   1.64 &   0.47 &   5.10 &   2.12 &  65 &   1.42 &   0.71 &  108 &   0.68 &   0.02 &   0.22 \vst \\
+A2065    &  46 & 325.85 &   2.31 &   0.41 &  14.20 &   0.24 & 492 &   1.16 &   0.00 &    0 &   0.00 &   0.05 &   0.19 \vst \\
+A2063    &  47 & 155.75 &   1.51 &   0.56 &   4.00 &   1.12 &  39 &   0.49 &   0.18 &  457 &   2.02 &   0.06 &   0.25 \vst \\
+A2142    &  48 & 411.47 &   2.48 &   0.35 &  17.50 &   1.90 & 100 &   0.67 &   0.18 &  637 &   1.01 &   0.03 &   0.16 \vst \\
+A2147    &  49 & 154.39 &   1.50 &   0.56 &   3.90 &   0.20 & 169 &   0.44 &   0.00 &    0 &   0.00 &   0.16 &   0.25 \vst \\
+A2163    &  50 & 990.91 &   2.55 &   0.15 &  19.20 &   0.63 & 370 &   0.80 &   0.00 &    0 &   0.00 &   0.02 &   0.07 \vst \\
+A2199    &  51 & 132.35 &   1.77 &   0.77 &   6.40 &   0.98 &  99 &   0.65 &   0.00 &    0 &   0.00 &   0.06 &   0.35 \vst \\
+A2204    &  52 & 727.47 &   1.93 &   0.15 &   8.30 &   6.00 &  47 &   0.60 &   0.00 &    0 &   0.00 &   0.01 &   0.07 \vst \\
+A2244    &  53 & 446.19 &   1.90 &   0.24 &   7.90 &   1.42 &  89 &   0.61 &   0.00 &    0 &   0.00 &   0.02 &   0.11 \vst \\
+A2256    &  54 & 269.27 &   2.36 &   0.50 &  15.20 &   0.31 & 419 &   0.91 &   0.00 &    0 &   0.00 &   0.07 &   0.23 \vst \\
+A2255    &  55 & 363.60 &   2.10 &   0.33 &  10.60 &   0.21 & 423 &   0.80 &   0.00 &    0 &   0.00 &   0.06 &   0.15 \vst \\
 \end{tabular}
@@
 \begin{minipage}{2.0\columnwidth}
-\begin{tabular}{l  c c c c c c c c c c c}
-\hline
-\hline
-Cluster & ID$^{(1)}$ & $D_\clu$$^{(1)}$ & $\rvir$$^{(1)}$ & $\rvir$ & 
-$\mvir$$^{(1)}$ & $\rho_\rmn{gas}(0)$$^{(2)}$ & $r_\rmn{core}$$^{(2)}$ & 
-$\beta$$^{(2)}$ & $r_\rmn{hlr,CR}$$^{(3)}$ & $r_\rmn{hlr,DM}$  $^{(4)}$ \\
-& & [Mpc] & [Mpc] & [deg] & [$10^{14}\,\msun$] & 
-[$10^{-27}\,\rmn{g}\,\rmn{cm}^{-3}$] & [kpc] &  & [deg] & [deg] \\
- \hline
-A3667    &  56 & 250.15 &   1.92 &   0.44 &   7.99 &   4.64 & 199.29 &   0.54 &   0.10 &   0.20 \\
-S1101    &  57 & 259.46 &   1.37 &   0.30 &   2.91 &  48.52 &  40.00 &   0.64 &   0.01 &   0.14 \\
-A2589    &  58 & 183.87 &   1.47 &   0.46 &   3.58 &  10.07 &  84.29 &   0.60 &   0.04 &   0.21 \\
-A2597    &  59 & 388.66 &   1.65 &   0.24 &   5.10 &  59.06 &  41.43 &   0.63 &   0.01 &   0.11 \\
-A2634    &  60 & 136.84 &   1.50 &   0.63 &   3.82 &   1.70 & 260.00 &   0.64 &   0.14 &   0.29 \\
-A2657    &  61 & 178.41 &   1.42 &   0.46 &   3.23 &   8.16 &  85.00 &   0.56 &   0.06 &   0.21 \\
-A4038    &  62 & 123.85 &   1.29 &   0.59 &   2.44 &  22.03 &  42.14 &   0.54 &   0.05 &   0.28 \\
-A4059    &  63 & 203.98 &   1.59 &   0.45 &   4.50 &  16.44 &  64.29 &   0.58 &   0.03 &   0.21 \\
-A2734    &  64 & 278.16 &   1.53 &   0.31 &   4.05 &   5.24 & 151.43 &   0.62 &   0.05 &   0.15 \\
-A2877    &  65 & 105.13 &   1.39 &   0.76 &   3.03 &   2.30 & 135.71 &   0.57 &   0.13 &   0.35 \\
-NGC499   &  66 &  63.67 &   0.71 &   0.64 &   0.41 &  28.76 &  17.14 &   0.72 &   0.02 &   0.30 \\
-AWM7     &  67 &  74.64 &   1.56 &   1.20 &   4.34 &   7.70 & 123.57 &   0.67 &   0.12 &   0.56 \\
-PERSEUS  &  68 &  79.48 &   1.90 &   1.37 &   7.71 &  45.94 &  45.71 &   0.54 &   0.10 &   0.64 \\
-S405     &  69 & 274.88 &   1.62 &   0.34 &   4.82 &   2.13 & 327.86 &   0.66 &   0.08 &   0.16 \\
-3C129    &  70 &  97.15 &   1.81 &   1.07 &   6.64 &   2.61 & 227.14 &   0.60 &   0.21 &   0.49 \\
-A0539    &  71 & 126.08 &   1.34 &   0.61 &   2.67 &   5.11 & 105.71 &   0.56 &   0.09 &   0.28 \\
-S540     &  72 & 157.55 &   1.23 &   0.45 &   2.09 &   7.70 &  92.86 &   0.64 &   0.04 &   0.21 \\
-A0548w   &  73 & 187.52 &   0.88 &   0.27 &   0.76 &   2.30 & 141.43 &   0.67 &   0.05 &   0.12 \\
-A0548e   &  74 & 181.14 &   1.20 &   0.38 &   1.98 &   4.44 &  84.29 &   0.48 &   0.08 &   0.18 \\
-A3395n   &  75 & 221.45 &   2.14 &   0.55 &  11.05 &   1.61 & 480.00 &   0.98 &   0.09 &   0.26 \\
-UGC03957 &  76 & 149.43 &   1.36 &   0.52 &   2.87 &   8.93 & 101.43 &   0.74 &   0.04 &   0.24 \\
-PKS0745  &  77 & 474.79 &   2.08 &   0.25 &  10.09 &  72.11 &  50.71 &   0.61 &   0.01 &   0.12 \\
-A0644    &  78 & 317.77 &   2.31 &   0.42 &  14.16 &  11.21 & 145.00 &   0.70 &   0.03 &   0.19 \\
-ANTLIA   &  79 &  50.13 &   0.90 &   1.03 &   0.83 &   1.64 & 245.71 &   0.75 &   0.26 &   0.48 \\
-A1413    &  80 & 677.27 &   2.18 &   0.18 &  11.64 &  14.19 & 127.86 &   0.66 &   0.02 &   0.09 \\
-M49      &  81 &  18.91 &   0.74 &   2.25 &   0.46 &  34.18 &   7.86 &   0.59 &   0.04 &   1.04 \\
-A3528n   &  82 & 240.86 &   1.43 &   0.34 &   3.32 &   5.61 & 127.14 &   0.62 &   0.04 &   0.16 \\
-A3528s   &  83 & 245.97 &   1.19 &   0.28 &   1.93 &   7.70 &  72.14 &   0.46 &   0.06 &   0.13 \\
-A3530    &  84 & 242.72 &   1.69 &   0.40 &   5.46 &   2.07 & 300.71 &   0.77 &   0.07 &   0.18 \\
-A3532    &  85 & 240.40 &   1.70 &   0.41 &   5.56 &   3.63 & 201.43 &   0.65 &   0.06 &   0.19 \\
-A1689    &  86 & 897.29 &   2.50 &   0.16 &  17.63 &  23.21 & 116.43 &   0.69 &   0.01 &   0.07 \\
-A3560    &  87 & 220.07 &   1.31 &   0.34 &   2.56 &   2.80 & 182.86 &   0.57 &   0.08 &   0.16 \\
-A1775    &  88 & 343.00 &   1.55 &   0.26 &   4.22 &   5.19 & 185.71 &   0.67 &   0.04 &   0.12 \\
-A1800    &  89 & 338.70 &   1.71 &   0.29 &   5.69 &   3.32 & 280.00 &   0.77 &   0.05 &   0.13 \\
-A1914    &  90 & 827.98 &   2.77 &   0.19 &  24.28 &  14.68 & 165.00 &   0.75 &   0.01 &   0.09 \\
-NGC5813  &  91 &  27.55 &   0.62 &   1.29 &   0.27 &  22.37 &  17.86 &   0.77 &   0.03 &   0.60 \\
-NGC5846  &  92 &  26.25 &   0.69 &   1.51 &   0.38 &  66.64 &   5.00 &   0.60 &   0.02 &   0.70 \\
-A2151w   &  93 & 162.53 &   1.15 &   0.41 &   1.73 &  14.20 &  48.57 &   0.56 &   0.03 &   0.19 \\
-NORMA    &  94 &  70.69 &   1.79 &   1.45 &   6.57 &   2.88 & 213.57 &   0.56 &   0.33 &   0.67 \\
-TRIANGUL &  95 & 226.98 &   2.39 &   0.60 &  15.39 &   6.47 & 199.29 &   0.61 &   0.09 &   0.28 \\
-OPHIUCHU &  96 & 122.51 &   2.74 &   1.28 &  23.16 &   9.08 & 199.29 &   0.75 &   0.10 &   0.59 \\
-ZwCl1742 &  97 & 343.00 &   1.91 &   0.32 &   7.89 &   7.76 & 165.71 &   0.72 &   0.03 &   0.15 \\
-A2319    &  98 & 252.01 &   2.26 &   0.51 &  12.91 &   6.66 & 203.57 &   0.59 &   0.09 &   0.24 \\
-A3695    &  99 & 407.09 &   1.81 &   0.25 &   6.66 &   3.28 & 285.00 &   0.64 &   0.05 &   0.12 \\
-IIZw108  & 100 & 219.60 &   1.47 &   0.38 &   3.60 &   2.47 & 260.71 &   0.66 &   0.08 &   0.18 \\
-A3822    & 101 & 344.43 &   1.74 &   0.29 &   5.90 &   3.48 & 250.71 &   0.64 &   0.06 &   0.13 \\
-A3827    & 102 & 451.10 &   2.59 &   0.33 &  19.60 &   3.95 & 423.57 &   0.99 &   0.04 &   0.15 \\
-A3888    & 103 & 720.64 &   2.83 &   0.22 &  25.53 &   7.16 & 286.43 &   0.93 &   0.02 &   0.10 \\
-A3921    & 104 & 429.52 &   2.06 &   0.28 &   9.86 &   5.23 & 234.29 &   0.76 &   0.03 &   0.13 \\
-HCG94    & 105 & 184.32 &   1.31 &   0.41 &   2.59 &   8.77 &  61.43 &   0.51 &   0.06 &   0.19 \\
-RXJ2344  & 106 & 356.88 &   1.92 &   0.31 &   8.05 &   5.89 & 215.00 &   0.81 &   0.03 &   0.14 \\
+\begin{tabular}{l  c c c c c c c c c c c c c}
+\hline
+\hline
+Cluster & ID$^{(1)}$ & $D_\clu$$^{(1)}$ & $\rvir$$^{(2)}$ & $\rvir$ & 
+$\mvir$$^{(2)}$ & $n_\rmn{e,1}(0)$$^{(3)}$ & $r_\rmn{core,1}$$^{(3)}$ & 
+$\beta_1$$^{(3)}$ & $n_\rmn{e,2}(0)$$^{(3)}$ & $r_\rmn{core,2}$$^{(3)}$ & 
+$\beta_2$$^{(3)}$ & $r_\rmn{hlr,CR}$$^{(4)}$ & $r_\rmn{hlr,DM}$  $^{(5)}$ \\
+& & [Mpc] & [Mpc] & [deg] & [$10^{14}\,\msun$] 
+& [$10^{-2}\,\rmn{cm}^{-3}$] & [kpc] &  & 
+  [$10^{-2}\,\rmn{cm}^{-3}$] & [kpc] &  & [deg] & [deg] \\
+ \hline
+A3667    &  56 & 250.15 &   1.88 &   0.43 &   7.60 &   0.39 & 287 &   0.89 &   0.06 & 1696 &   1.70 &   0.09 &   0.20 \vst \\
+S1101    &  57 & 259.46 &   1.60 &   0.35 &   4.70 &   3.43 &  47 &   0.79 &   0.20 &  272 &   0.96 &   0.01 &   0.16 \vst \\
+A2589    &  58 & 183.87 &   1.64 &   0.51 &   5.10 &   0.85 &  67 &   0.66 &   0.19 &  222 &   0.74 &   0.04 &   0.23 \vst \\
+A2597    &  59 & 388.66 &   1.71 &   0.25 &   5.70 &   4.29 &  40 &   0.63 &   0.00 &    0 &   0.00 &   0.01 &   0.12 \vst \\
+A2634    &  60 & 136.84 &   1.80 &   0.75 &   6.70 &   0.28 &  57 &   0.47 &   0.07 &  849 &   1.89 &   0.14 &   0.34 \vst \\
+A2657    &  61 & 178.41 &   1.95 &   0.63 &   8.60 &   0.63 & 105 &   0.89 &   0.10 &  568 &   1.27 &   0.05 &   0.29 \vst \\
+A4038    &  62 & 123.85 &   1.54 &   0.71 &   4.20 &   1.75 &  37 &   0.58 &   0.19 &  172 &   0.70 &   0.05 &   0.33 \vst \\
+A4059    &  63 & 203.98 &   1.79 &   0.50 &   6.60 &   1.39 &  58 &   0.64 &   0.15 &  312 &   0.90 &   0.03 &   0.23 \vst \\
+A2734    &  64 & 278.16 &   1.83 &   0.38 &   7.10 &   0.38 & 150 &   0.62 &   0.00 &    0 &   0.00 &   0.05 &   0.17 \vst \\
+A2877    &  65 & 105.13 &   2.02 &   1.10 &   9.50 &   0.21 & 230 &   3.58 &   0.08 &  432 &   1.23 &   0.11 &   0.50 \vst \\
+NGC499   &  66 &  63.67 &   0.89 &   0.80 &   0.80 &   1.11 &  16 &   0.72 &   0.00 &    0 &   0.00 &   0.01 &   0.37 \vst \\
+AWM7     &  67 &  74.64 &   1.84 &   1.41 &   7.20 &   0.69 &  89 &   0.78 &   0.19 &  290 &   0.88 &   0.12 &   0.65 \vst \\
+PERSEUS  &  68 &  79.48 &   1.95 &   1.41 &   8.60 &   3.84 &  45 &   0.54 &   0.00 &    0 &   0.00 &   0.10 &   0.64 \vst \\
+S405     &  69 & 274.88 &   1.81 &   0.38 &   6.80 &   0.14 & 327 &   0.66 &   0.00 &    0 &   0.00 &   0.09 &   0.17 \vst \\
+3C129    &  70 &  97.15 &   1.89 &   1.11 &   7.80 &   0.21 & 227 &   0.60 &   0.00 &    0 &   0.00 &   0.22 &   0.51 \vst \\
+A0539    &  71 & 126.08 &   1.56 &   0.71 &   4.40 &   0.83 &  30 &   0.53 &   0.18 &  223 &   0.75 &   0.09 &   0.32 \vst \\
+S540     &  72 & 157.55 &   1.53 &   0.56 &   4.20 &   0.47 &  92 &   0.64 &   0.00 &    0 &   0.00 &   0.05 &   0.25 \vst \\
+A0548w   &  73 & 187.52 &   1.19 &   0.36 &   2.00 &   0.12 & 141 &   0.67 &   0.00 &    0 &   0.00 &   0.05 &   0.17 \vst \\
+A0548e   &  74 & 181.14 &   1.33 &   0.42 &   2.70 &   0.33 &  84 &   0.48 &   0.00 &    0 &   0.00 &   0.09 &   0.19 \vst \\
+A3395n   &  75 & 221.45 &   2.12 &   0.55 &  10.90 &   0.12 & 480 &   0.98 &   0.00 &    0 &   0.00 &   0.09 &   0.25 \vst \\
+UGC03957 &  76 & 149.43 &   1.65 &   0.63 &   5.20 &   0.57 & 101 &   0.74 &   0.00 &    0 &   0.00 &   0.04 &   0.29 \vst \\
+PKS0745  &  77 & 474.79 &   2.04 &   0.25 &   9.80 &   6.71 &  51 &   0.70 &   0.70 &  167 &   0.65 &   0.01 &   0.11 \vst \\
+A0644    &  78 & 317.77 &   2.14 &   0.39 &  11.20 &   0.92 & 144 &   0.70 &   0.00 &    0 &   0.00 &   0.03 &   0.18 \vst \\
+ANTLIA   &  79 &  50.13 &   1.35 &   1.54 &   2.80 &   0.08 & 245 &   0.75 &   0.00 &    0 &   0.00 &   0.28 &   0.71 \vst \\
+A1413    &  80 & 677.27 &   2.23 &   0.19 &  12.70 &   1.44 & 110 &   0.80 &   0.26 &  399 &   0.91 &   0.01 &   0.09 \vst \\
+M49      &  81 &  18.91 &   1.07 &   3.24 &   1.40 &   1.57 &   7 &   0.59 &   0.00 &    0 &   0.00 &   0.04 &   1.48 \vst \\
+A3528n   &  82 & 240.86 &   1.80 &   0.43 &   6.70 &   0.40 & 126 &   0.62 &   0.00 &    0 &   0.00 &   0.05 &   0.20 \vst \\
+A3528s   &  83 & 245.97 &   1.57 &   0.37 &   4.50 &   0.57 &  71 &   0.46 &   0.00 &    0 &   0.00 &   0.08 &   0.17 \vst \\
+A3530    &  84 & 242.72 &   1.78 &   0.42 &   6.50 &   0.15 & 300 &   0.77 &   0.00 &    0 &   0.00 &   0.07 &   0.19 \vst \\
+A3532    &  85 & 240.40 &   2.00 &   0.48 &   9.20 &   0.34 & 137 &   0.74 &   0.11 &  543 &   1.09 &   0.06 &   0.22 \vst \\
+A1689    &  86 & 897.29 &   2.51 &   0.16 &  18.20 &   2.46 & 108 &   0.88 &   0.46 &  336 &   0.91 &   0.01 &   0.07 \vst \\
+A3560    &  87 & 220.07 &   1.58 &   0.41 &   4.50 &   0.20 & 182 &   0.57 &   0.00 &    0 &   0.00 &   0.09 &   0.19 \vst \\
+A1775    &  88 & 343.00 &   1.76 &   0.29 &   6.30 &   0.35 & 385 &   2.05 &   0.07 & 1030 &   1.70 &   0.04 &   0.13 \vst \\
+A1800    &  89 & 338.70 &   1.94 &   0.33 &   8.40 &   0.21 & 279 &   0.77 &   0.00 &    0 &   0.00 &   0.05 &   0.15 \vst \\
+A1914    &  90 & 827.98 &   2.35 &   0.16 &  14.90 &   1.32 & 164 &   0.75 &   0.00 &    0 &   0.00 &   0.01 &   0.07 \vst \\
+NGC5813  &  91 &  27.55 &   0.95 &   1.98 &   1.00 &   1.06 &  17 &   0.77 &   0.00 &    0 &   0.00 &   0.03 &   0.90 \vst \\
+NGC5846  &  92 &  26.25 &   0.76 &   1.66 &   0.50 &   4.15 &   2 &   0.51 &   0.70 &   39 &   4.78 &   0.02 &   0.76 \vst \\
+A2151w   &  93 & 162.53 &   1.36 &   0.48 &   2.90 &   0.97 &  48 &   0.56 &   0.00 &    0 &   0.00 &   0.04 &   0.22 \vst \\
+NORMA    &  94 &  70.69 &   1.84 &   1.49 &   7.20 &   0.22 & 213 &   0.56 &   0.00 &    0 &   0.00 &   0.33 &   0.68 \vst \\
+TRIANGUL &  95 & 226.98 &   2.50 &   0.63 &  18.00 &   0.63 & 177 &   0.71 &   0.17 &  500 &   0.80 &   0.08 &   0.29 \vst \\
+OPHIUCHU &  96 & 122.51 &   3.28 &   1.53 &  40.50 &   0.80 & 234 &   1.04 &   0.12 &  850 &   1.40 &   0.10 &   0.70 \vst \\
+ZwCl1742 &  97 & 343.00 &   2.25 &   0.38 &  13.10 &   0.71 & 165 &   0.72 &   0.00 &    0 &   0.00 &   0.03 &   0.17 \vst \\
+A2319    &  98 & 252.01 &   2.44 &   0.55 &  16.70 &   0.58 & 273 &   1.06 &   0.16 &  624 &   0.82 &   0.08 &   0.25 \vst \\
+A3695    &  99 & 407.09 &   2.03 &   0.29 &   9.70 &   0.24 & 284 &   0.64 &   0.00 &    0 &   0.00 &   0.06 &   0.13 \vst \\
+IIZw108  & 100 & 219.60 &   1.72 &   0.45 &   5.90 &   0.17 & 260 &   0.66 &   0.00 &    0 &   0.00 &   0.08 &   0.21 \vst \\
+A3822    & 101 & 344.43 &   1.82 &   0.30 &   6.90 &   0.25 & 250 &   0.64 &   0.00 &    0 &   0.00 &   0.06 &   0.14 \vst \\
+A3827    & 102 & 451.10 &   2.53 &   0.32 &  18.70 &   0.31 & 423 &   0.99 &   0.00 &    0 &   0.00 &   0.04 &   0.15 \vst \\
+A3888    & 103 & 720.64 &   3.04 &   0.24 &  32.40 &   0.61 & 285 &   0.93 &   0.00 &    0 &   0.00 &   0.02 &   0.11 \vst \\
+A3921    & 104 & 429.52 &   2.00 &   0.27 &   9.20 &   0.40 & 234 &   0.76 &   0.00 &    0 &   0.00 &   0.03 &   0.12 \vst \\
+HCG94    & 105 & 184.32 &   1.49 &   0.46 &   3.80 &   0.80 &  42 &   0.53 &   0.19 &  142 &   0.58 &   0.06 &   0.21 \vst \\
+RXJ2344  & 106 & 356.88 &   2.17 &   0.35 &  11.80 &   0.51 &  91 &   0.72 &   0.32 &  285 &   0.92 &   0.03 &   0.16 \vst \\
 \hline
@@
   Notes: 
-  (1) The HIFLUGCS cluster ID, luminosity distance
-  ($D_\rmn{lum}$), virial radius ($\rvir$), and virial mass ($\mvir$),
-  are taken from \cite{2002ApJ...567..716R}.
-  (2) We parametrize the
-  gas density profile of each cluster with a single beta profile;
-  $\rho_\rmn{gas}=\rho_\rmn{gas}(0)(1+r^2/r_\rmn{c}^2)^{3\beta/2}$
-  where the core radius, $r_\rmn{c}$, and the slope, $\beta$, are taken from
-  \cite{2002ApJ...567..716R}. The central gas density
-  $\rho_\rmn{gas}(0)$ is determined through he procedure outlined in
-  \cite{1999ApJ...517..627M}.
-  (3) Half light radius ($r_\rmn{hlr,CR}$) of the flux from CR-$\pi^0$.
-  (4) Half light radius ($r_\rmn{hlr,DM}$) of the flux from the BM-$\Kp$ 
+  (1) The HIFLUGCS cluster ID and luminosity distance
+  ($D_\rmn{lum}$) are taken from \cite{2002ApJ...567..716R}.
+  (2) The virial mass ($\mvir$) for each cluster is derived from the $M_{500}$ 
+  mass in \cite{2007A&A...466..805C}. We solve for $\mvir$ using 
+  $\mvir=M_{500}\,200/500\,(c_{200}(\mvir)/c_{500}(\mvir))^3$ \cite{2005RvMP...77..207V}. 
+  The virial radius ($\rvir$) is derived from $\mvir$.
+  (3) The electron number density profile of each cluster follows either a single- or double-beta profile;
+  $n_\rmn{e}(r) = \sqrt{\sum_i n_\rmn{e,i}(0)^2(1+r^2/r_\rmn{c,i}^2)^{3\beta_i}}$
+  where the central electron density, $n_\rmn{e}(0)$, core radius, $r_\rmn{c}$, and slope, $\beta$, are derived from
+  \cite{2007A&A...466..805C}.
+  (4) Half light radius ($r_\rmn{hlr,CR}$) of the flux from CR-$\pi^0$.
+  (5) Half light radius ($r_\rmn{hlr,DM}$) of the flux from the BM-$\Kp$ 
   continuum and LP-IC-CMB emission. The flux has been
-  boosted by substructures and includes the
-  Sommerfeld enhancement for the LP model. 
+  boosted by substructures and includes the Sommerfeld enhancement for the LP model. 
   \end{quote}

### 2011-08-02 paper.tex
corrections and improvements to final version

@@
 \begin{abstract}
-  We study the possibility for detecting gamma-ray emission in galaxy
-  clusters. We consider 1) cosmic ray (CR) induced pion decay which is
-  thought to dominate the astrophysical signal from clusters, 2)
-  different representative benchmark models of supersymmetric dark
-  matter (DM), and 3) leptophilic models of DM annihilation that
-  recently have been proposed to explain the positron excess seen by
-  PAMELA and include a Sommerfeld enhancement of the particle physics
-  cross section over its standard value. To model DM annihilation, we
-  consider continuum emission as a result of the hadronization of
-  annihilating neutralinos, internal bremsstrahlung, and inverse
-  Compton emission from the cosmic microwave background as well as
-  from a realistic spatial and spectral distribution of dust and
-  stellar light. We predict the Virgo, Fornax and \C{M49} clusters to
-  be the brightest DM sources and find a particularly low CR induced
-  background for Fornax. For a minimum substructure mass given by the
-  DM free-streaming scale, the largest DM halo mass maximizes the
-  substructure boost over the smoothly distributed annihilation flux:
-  for galaxy clusters as the largest collapsed objects, we find a
-  boost factor of more than 1000. Since the annihilation flux of
-  substructures is mostly contributed by the regions around the virial
-  radius, the resulting surface brightness profiles are almost
-  flat. This makes it very challenging to detect this flux with
-  imaging air Cherenkov telescopes since their sensitivity drops
-  linearly with radius and they typically have $5-10$ linear
-  resolution elements across a cluster; the gamma-ray satellite \Fermi
-  is better suited. Assuming cold dark matter with a substructure mass
-  distribution down to an Earth mass and using \Fermi upper limits, we
-  rule out the leptophilic models in their present form in 28
-  clusters, and limit the boost from Sommerfeld enhancement in the
-  most constraining clusters, \C{M49 and Fornax, } to be less than 5. This
-  corresponds to a Sommerfeld enhancement in the Milky Way of less
-  than 5. Alternatively, if the Sommerfeld enhancement factor is
-  realized in Nature, this would imply a limiting substructure mass of
-  $\mlim > 10^4\,\msun$ which would be a challenge for structure
-  formation. We find it challenging for \Fermi to constrain our
-  selection of DM benchmark models in the \C{near future} using clusters
-  without improved modelling of extended sources in addition to a
-  stacked likelihood analysis. The \Fermi upper limits are, however,
-  closing in on our predictions for the CR flux using an analytic
-  model based on cosmological hydrodynamical cluster simulations. Thus
-  we will soon start to constrain the underlying CR physics such as
-  shock acceleration efficiencies or CR transport properties.
+  We study the possibility for detecting gamma-ray emission from galaxy
+  clusters. We consider 1) cosmic ray (CR) induced pion decay, 2) different
+  representative benchmark models of supersymmetric dark matter (DM), and 3)
+  leptophilic models of DM annihilation that include a Sommerfeld enhancement
+  (SFE). To model DM annihilation, we consider continuum emission as a result of
+  the hadronization of annihilating neutralinos, internal bremsstrahlung, and
+  inverse Compton emission from the cosmic microwave background as well as from
+  a realistic spatial and spectral distribution of dust and stellar light. Among
+  all clusters/groups, we predict Virgo, Fornax and M49 to be the brightest DM
+  sources and find a particularly low CR-induced background for Fornax.  For a
+  minimum substructure mass given by the DM free-streaming scale, cluster halos
+  maximize the substructure boost for which we find a factor of $\gtrsim 1000$.
+  Since the annihilation flux of substructures is mostly contributed by the
+  regions around the virial radius, the resulting surface brightness profiles
+  are almost flat. This makes it very challenging to detect this flux with
+  imaging atmospheric Cherenkov telescopes since their sensitivity drops
+  linearly with radius and they typically have $5-10$ linear resolution elements
+  across a cluster; the gamma-ray satellite \Fermi is better suited.  Assuming
+  cold dark matter with a substructure mass distribution down to an Earth mass
+  and using \Fermi upper limits, we rule out the leptophilic models in their
+  present form in 28 clusters, and limit the boost from SFE in M49 and Fornax to
+  be $\lesssim 5$. This corresponds to a limit on SFE in the Milky Way of
+  $\lesssim 3$. Alternatively, if the SFE is realized in Nature, this
+  would imply a limiting substructure mass of $\mlim > 10^4\,\msun$---a
+  challenge for structure formation. Without improved modelling of extended
+  sources or stacked likelihood analyses, \Fermi will face difficulties in
+  constraining our selection of DM benchmark models in the near future. The
+  \Fermi upper limits are, however, closing in on our predictions for the CR
+  flux using an analytic model based on cosmological hydrodynamical cluster
+  simulations. We limit the CR-to-thermal pressure in nearby bright galaxy
+  clusters of the \Fermi sample to $\lesssim 10\%$ and in Norma and Coma to
+  $\lesssim 3\%$.  Thus we will soon start to constrain the underlying CR
+  physics such as shock acceleration efficiencies or CR transport properties.
 \end{abstract}
@@
 Among the astrophysical systems which will be very interesting to detect, and
-study, with coming gamma-ray detectors (\Fermi, H.E.S.S., MAGIC, VERITAS, and
+study, with gamma-ray detectors (\Fermi, H.E.S.S., MAGIC, VERITAS, and
 eventually large detectors like CTA)\footnote{{High Energy Stereoscopic System,
@@
 annihilation gamma-ray yield which could be observable with present
-and planned gamma-ray detectors. For convenience, we summarize already
-in Table~\ref{tab:flux_tab} our results for the gamma-ray flux from
-four promising clusters with a high gamma-ray yield. We will in the
+and planned gamma-ray detectors. For convenience, we summarize in
+Table~\ref{tab:flux_tab} our results for the gamma-ray flux from four
+promising clusters with a high gamma-ray yield. We will in the
 following derive the emission from two different DM models and a
 hadronic CR model to show that Virgo has the highest gamma-ray flux
-from annihilating DM. If the boost from Sommerfeld enhancement (SFE)
-is small, however, then the gamma-ray emission induced by CRs is
-dominating most clusters with the exception of a few clusters where
-Fornax had the highest flux from DM. In particular, we find Fornax and
-Virgo as the prime targets for DM observations, Perseus for CR induced
+from annihilating DM. \C{However, if the boost from Sommerfeld
+  enhancement (SFE) is small then the gamma-ray emission induced by
+  CRs is dominating most clusters with the exception of a few
+  clusters; most notably Fornax that shows the largest ratio of DM
+  annihilation-to-CR flux. In particular, we identify Fornax and Virgo
+  as prime targets for DM observations,} Perseus for CR induced
 emission and we additionally decide in favor of the well studied
@@
   Sommerfeld boost realized when substructures are present, the latter is the Sommerfeld 
-  boost without substructures. See Section II A 1.\\
-  (3) We integrate the emission in a cylinder with a radial extent of $2.5
-  R_{200}$ along the line-of-sight and an angular size corresponding to $\rvir$
-  (both measured from the cluster center).\\
+  boost without substructures (see Section II A 1).\\
+  (3) \C{The boost due to substructures relative a the smooth DM
+  distribution.} We integrate the emission in a cylinder with a radial
+  extent of $2.5 R_{200}$ along the line-of-sight and an angular size
+  corresponding to $\rvir$  (both measured from the cluster center).\\
   (4) The total gamma-ray flux from leptophilic (LP) DM where both the
@@
 use a DM mass $m_\chi=1.6$~TeV and a branching ratio of
-($1/4:1/4:1/2$) into ($\mu^+\mu^-:\e^+\e^-:\pi^+\pi^-$). Furthermore,
-since most of gamma-ray flux is expected from come from dense subhalos
-at which the velocity dispersion is close to the velocity limit
+($1/4:1/4:1/2$) into ($\mu^+\mu^-:\e^+\e^-:\pi^+\pi^-$). \C{Furthermore,
+since most of the gamma-ray flux is expected to come from dense
+subhalos within clusters which have 
+a velocity dispersion}  close to the velocity limit
 $v_\rmn{sat}$ where the SFE saturates, we use
-$S=\B_\sfe(\sigv=v_\rmn{sat})\approx 530$ for the cluster
-halos.\footnote{Note that, $S$ is strictly speaking the Sommerfeld
-  enhanced annihilation cross-section, but here we have in addition
-  included the order unity constraint that make sure that the relic
+$S=\B_\sfe(v_\rmn{sat})\approx 530$ for the cluster
+halos.\footnote{Note that $S$ is strictly speaking the Sommerfeld
+  enhanced annihilation cross-section, but here we have additionally
+  included the order unity constraint that ensures that the relic
   density is not over-depleted at freeze-out.} However, for figures
@@
   electrons and positrons $\B_\rmn{sfe,MW}=300$, the velocity
-  dispersion for the MW $v_\rmn{MW} \approx 220\,$~km/s and the
+  dispersion for the MW $v_\rmn{MW} \approx 220\,\rmn{km\,s}^{-1}$, and the
   velocity dispersion $\sigv$ for clusters is derived in
@@
 flux from substructures is boosted compared to the smooth density
-distribution. Recent high resolution simulations suggest a flux
-enhancement from substructures of more than 100
-\cite{2008MNRAS.391.1685S, 2010ApJ...718..899A} for a MW size halo.
-We adopt a boost from substructures of 230 which is the enhancement
-found in one of the highest resolved MW halos ever simulated. While
-there is still a discrepancy in the literature of the exact value of
-the predicted boost factor of the DM annihilation luminosity from
-substructures in DM halos, this inconsistency starts to become
-resolved, apparently converging toward predictions at the high end,
-e.g. those by the Aquarius simulations \protect
-\cite{2008MNRAS.391.1685S, 2008Natur.456...73S}. The initial
-suggestions of a small {\em total} boost ($<R_{200}$) of order unity
-by the Via Lactea simulations \cite{2008JPhCS.125a2008K} made
-assumptions of computing the boost assuming that the substructure
+distribution.  While there is still a discrepancy in the literature of
+the exact value of the predicted boost factor of the DM annihilation
+luminosity from substructures in DM halos, this inconsistency starts
+to become resolved, apparently converging toward predictions at the
+high end \protect \cite{2008MNRAS.391.1685S, 2008Natur.456...73S,
+  2010ApJ...718..899A}. \C{Following recent high-resolution
+  simulations of Galaxy-sized halos, we adopt a boost factor due to
+  substructures of 230 for such a halo \cite{2008MNRAS.391.1685S}
+  (which needs to be scaled to cluster halos as we will discuss
+  below).}
+
+The initial suggestions of a small {\em total} boost ($<R_{200}$) of
+order unity by the Via Lactea simulations \cite{2008JPhCS.125a2008K}
+made assumptions of computing the boost assuming that the substructure
 luminosity follows that of the smooth DM distribution. Physically,
 this would imply substructure to follow the smooth DM distribution and
-a radially independent concentration parameter of substructures; both
-following from neglecting tidal mass loss of satellites. Tidal losses,
-however, are at work in simulations and cause the radial number
-density to be anti-biased with respect to the host's mass density
-profile yielding a significantly flatter subhalo distribution compared
-to the smooth DM distribution \cite{2010ApJ...718..899A}. This
-increases the substructure boost preferentially in the outer parts of
-DM halos with a factor that ranges between 20 and 1000 (for dwarfs and
-galaxy clusters), hence depending sensitively on the host halo mass
-(see Figure~\ref{fig:radial_lum}). \C{It should be noted that the very
-  recent {\it Phoenix} simulations by Chen et
-  al. \cite{2011arXiv1107.1916G} confirms the large enhancement due to
-  substructures in clusters. In fact they find a boost of 1125 for a
-  Coma like cluster which agrees within 10\% with our estimated boost
-  (see e.g. Table~\ref{tab:flux_tab}).}
+a radially independent concentration parameter of substructures. Both
+assumptions are in conflict with tidal mass loss of satellites which
+is at work in simulations and cause the radial number density to be
+anti-biased with respect to the host's mass density profile yielding a
+significantly flatter subhalo distribution compared to the smooth DM
+distribution \cite{2010ApJ...718..899A}.  This increases the
+substructure boost preferentially in the outer parts of DM halos with
+a factor that ranges between 20 and 1000 (for dwarfs and galaxy
+clusters), hence depending sensitively on the host halo mass (see
+Figure~\ref{fig:radial_lum}). \C{Recent {\it Phoenix} simulations by
+  Gao et al. \cite{2011arXiv1107.1916G} confirm the large enhancement
+  due to substructures in clusters. In fact they find a boost of 1125
+  for a Coma like cluster which agrees within 10\% with our estimated
+  boost (see e.g. Table~\ref{tab:flux_tab}).}
 
@@
 Here, $A_{\rmn{dm}} = q_{\rmn{sm},i}(\eg,R) / \rho(R)^2$ represents
-the particle physics, where $q_{\rmn{sm},i}(\eg,R)$ is defined by
+the particle physics factor, where $q_{\rmn{sm},i}(\eg,R)$ is defined by
 Eq.~(\ref{eq:q_sm}). The different density profiles have some impact
@@
   $1-10$~GeV, and $10-100$~GeV from left to right (using Gauss
-  profiles for the source extension with $\sigma=\{1.2,1.0,0.8\}$ for
-  \{Virgo, Coma, Fornax\} and an X-ray-inferred King profile for
+  profiles for the source extension with $\sigma=(1.2,1.0,0.8)$ for
+  (Virgo, Coma, Fornax) and an X-ray-inferred King profile for
   Perseus) \cite{2010ApJ...717L..71A}. We show the individual
@@
   and includes the boost from substructures. We find that the lower
-  GeV energy regime is most constraining due to the peak sensitivity
+  GeV-energy regime is most constraining due to the peak sensitivity
   of \Fermi at these energies and use this regime to get upper limits
-  on boost factors. \C{Also notice that the CR induced emission in
+  on boost factors. \C{Note that the CR-induced emission in
     Coma is close to the upper limits set by \Fermi and will be tested
-    in the coming years.}}
+    in the upcoming years.}}
  \label{fig:clu_comp}
@@
 10^{-6}\,\msun$, we can constrain the saturated boost from SFE to
-about \C{5 in M49 and Fornax}, which corresponds to a maximum SFE in the
-MW of about 3. Hence, we conclude that without substantial improvement
-in the modelling of these extended sources, \Fermi-LAT will not be
-able to rule out LP models in their current form using clusters.
+\C{$\lesssim 5$ in M49 and Fornax}, which corresponds to a maximum SFE
+in the MW of $\lesssim3$. Hence, we conclude that without substantial
+improvement in the modelling of these extended sources, \Fermi-LAT
+will not be able to rule out LP models in their current form using
+clusters but can put impressive constraints on them.
 
@@
    than $10^4\,\msun$. Contrarily, if the smallest size of DM halos is
-   $10^{-6}\,\msun$, we can constrain the SFE to about 5 in M49 and
-   Fornax. This corresponds to a maximum SFE in the MW of about 3,
+   $10^{-6}\,\msun$, we can constrain the SFE to $\lesssim 5$ in M49 and
+   Fornax. This corresponds to a maximum SFE in the MW of $\lesssim 3$,
    which would be too small to support the DM annihilation hypothesis
@@
 annihilating DM is independent of the type of DM model, and can not be
-used to separate different models. \C{The surface brightness, $S_\gamma$,
-of the DM scales as $S_\gamma\propto L_{\gamma,\rmn{sm}}\bsub\mvir^{-2/3}
-\propto \mvir^{0.40}$}, which explains the factor \C{two} difference in
-normalization between the most massive cluster Coma and the least
-massive cluster Fornax with a mass ratio of about 10. The surface
-brightness induced by CRs is proportional to the projected squared gas
-profile with an additional enhancement in the center of cool core
-clusters due to the adiabatic compression of CRs during the formation
-of the cool core. Hence, we see a much larger variation in these
-profiles driven by the large variation of the gas mass fraction. It is
-noticeable that Fornax shows such a small surface brightness. This is
-explained by the low gas density outside the BCG and the less abundant
-CR population in a small cluster compared to a massive cluster
-\cite{2010MNRAS.409..449P}.  This is the reason why Fornax is such a
+used to separate different models. \C{The surface brightness,
+  $S_\gamma$, of the DM scales as $S_\gamma\propto
+  L_{\gamma,\rmn{sm}}\bsub\mvir^{-2/3} \propto \mvir^{0.40}$}, which
+explains the factor \C{two} difference in normalization between the
+most massive cluster Coma and the least massive cluster Fornax with a
+mass ratio of about 10. The surface brightness induced by CRs is
+proportional to the projected squared gas profile with an additional
+enhancement in the center of cool core clusters due to the adiabatic
+compression of CRs during the formation of the cool core. Hence, we
+see a much larger variation in these profiles driven by the large
+variation of the gas mass fraction. It is noticeable that Fornax shows
+a small surface brightness. \C{This is explained by the low gas
+  density outside the BCG and the expected small abundance of CRs in a
+  small cluster in comparison} to a massive cluster
+\cite{2010MNRAS.409..449P}.  This is the reason why Fornax is  a
 good target for indirect DM searches, and superior to DM searches in
@@
    Virgo (dashed), and Perseus (dash-dotted). We include the boost
-   from both substructures and Sommerfeld effect. Notice the very
-   similar shape and normalization of the DM models, while the CRs
-   have a much larger scatter in the profiles due to the large
-   variation of the gas fraction in these clusters.}
+   from both substructures and Sommerfeld effect. The shape and
+   normalization of the different DM models are very similar. In
+   contrast, the CR-induced emission profiles have a much larger
+   scatter due to the large variation of the gas fraction and expected
+   CR fraction in these clusters.}
  \label{fig:SB_clu}
@@
    excluded for the dotted lines. The boost from Sommerfeld
-   enhancement with and without substructures is 110 and 530
+   enhancement with and without substructures is 110 and 530,
    respectively. The boost due to substructures is about 890. Notice
@@
 \end{eqnarray}
-Note that the CR luminosity scaling relations\footnote{The scaling
-  relations show the flux inside $\rvir$ and do not include the
-  contribution from galaxies. Also note that in this paper the scaling
-  relations are normalized at $10^{15}\,h_{70}^{-1}\,\msun$. In
-  contrast, the corresponding scaling relations in Table 5 in
+The CR luminosity scaling relations\footnote{The scaling relations
+  show the flux inside $\rvir$ and do not include the contribution
+  from galaxies. Also note that in this paper the scaling relations
+  are normalized at $10^{15}\,h_{70}^{-1}\,\msun$. In contrast, the
+  corresponding scaling relations in Table 5 in
   \cite{2010MNRAS.409..449P} are normalized at
@@
   $10^{15}\,h_{70}^{-1}\,\msun$ in the caption. However, all
-  figures/tables/equations including the scaling relation figures are
-  derived for masses in units of $10^{15}\,h_{70}^{-1}\,\msun$.}
-include the IC gamma-ray contribution from shock-accelerated electrons
-as well as secondary electrons created in CR-proton interactions. The
-gamma-ray flux from the electrons is, however, dominated by the
-decaying neutral pions and only shows up as a small flattening of the
-scaling relation at energies around $10-100\,\gev$. The steeper mass
+  figures/tables/equations including the scaling relation figures in
+  \cite{2010MNRAS.409..449P} are derived for masses in units of
+  $10^{15}\,h_{70}^{-1}\,\msun$.}  include the IC gamma-ray
+contribution from shock-accelerated primary electrons as well as
+secondary electrons created in CR-proton interactions. \C{However, the
+  gamma-ray flux is dominated by the decaying neutral pions. The
+  difference in the mass scaling arises from the larger contribution
+  of primary IC emission for higher-mass clusters at 100~MeV that have
+  a larger fraction of radio relics due to their greater mass
+  accretion rates in comparison to galaxy groups---a direct
+  consequence of hierarchical growth of structure \protect
+  \cite{2009ApJ...707..354Z,2011arXiv1106.5505P}.}  The steeper mass
 scaling of CR emission compared to DM annihilation already implies a
@@
     clusters, with the strongest constraints set by M49 and
-    Fornax. \C{We can not yet constrain the benchmark models, although
-      \Fermi-LAT start to probe these models within its lifetime. In
-      particular, improved modelling of extended sources as well as
-      stacking of clusters will push these test into the near
-      future.}}
+    Fornax. \C{At the present time, we cannot constrain the benchmark
+      models, although \Fermi-LAT will soon start to probe these
+      models. In particular, improved modelling of extended sources as
+      well as stacking of clusters appears promising in testing
+      benchmark models.}}
  \label{fig14}
@@
 ($5\sigma$, 50h) of the future Cherenkov telescope array (CTA) of
-$F_\gamma(>E_\gamma) = \{4\times10^{-11}, 2\times10^{-12},
-2\times10^{-14}\}\,\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$ at energies
-of $E_\gamma=\{10~\rmn{GeV}, 100~\rmn{GeV}, 1~\rmn{TeV}\}$
+$F_\gamma(>E_\gamma) = (4\times10^{-11}, 2\times10^{-12},
+2\times10^{-14})\,\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$ at energies
+of $E_\gamma=(10~\rmn{GeV}, 100~\rmn{GeV}, 1~\rmn{TeV})$
 \cite{Doro:2009qs}, we note that it will be very challenging to detect
@@
   gamma-ray flux predictions are superior to those that use
-  luminosity-mass scaling relation---a method used by reference
-  \cite{2010ApJ...717L..71A} to compare to \Fermi limits.}  In this CR
-analytic model, we model CR-acceleration at structure formation shocks
-and their transport over cosmic time. This leads to a CR distribution
-with a universal spectral form and an almost universal spatial
-distribution. Depending on whether or not we account for the bias of
-``artificial galaxies'' in cosmological simulations, we derive an
-optimistic or conservative limit of the expected gamma-ray emission
-from decaying pions (bracketing our ignorance of the contribution of
-cluster galaxies to the overall gamma-ray flux from a cluster).
+  luminosity-mass scaling relation (a method used by reference
+  \cite{2010ApJ...717L..71A} to compare to \Fermi limits) which do not
+  account for the substantial scatter in the scaling relation.}  The
+analytic CR model that we employ here follows CR-acceleration at
+structure formation shocks and their advective transport over cosmic
+time. This leads to a CR distribution with a universal spectral form
+and an almost universal spatial distribution. Depending on whether or
+not we account for the bias of ``artificial galaxies'' in cosmological
+simulations, we derive an optimistic or conservative limit of the
+expected gamma-ray emission from decaying pions (bracketing our
+ignorance of the contribution of cluster galaxies \C{and ram-pressure
+  stripped gas parcels from infalling galaxies} to the overall
+gamma-ray flux from a cluster).
 
@@
 clusters \cite{2006MNRAS.367..113P}. These efficiencies will have to
-be corrected down if this value is not realized at structure formation
+be corrected down if this value is not realized at strong structure formation
 shocks. Second, these simulations (and by extension the analytic
@@
 
-We note that the tightest \Fermi limits are obtained in the 1-10 GeV
+The tightest \Fermi limits are obtained in the 1-10 GeV
 regime due to the highest sensitivity of \Fermi-LAT there. While the
@@
 effects selects this energy range to be most sensitive.  In this
-energy band, the \Fermi limits come close to the \C{conservative flux
+energy band, the \Fermi limits close in on the \C{conservative flux
   predictions of Virgo, Coma and Norma}. Using integrated flux limits
@@
   it hard to determine a comparable limit as obtained for the other
-  clusters. In addition, there are recent gamma-ray observations of
-  the head-tail radio galaxy IC310 in the cluster outskirts
+  clusters. Additionally, recent gamma-ray observations of
+  the head-tail radio galaxy IC310 complicate matters furthermore
   \cite{2010ApJ...723L.207A,2010A&A...519L...6N}.
@@
 or hydrostatic mass estimates, and the resulting cosmological
-constraints if the analysis do not marginalize over a potential
+constraints if the analysis does not marginalize over a potential
 pressure contribution from CRs. Before we turn to the newly derived
@@
 In the simulation based analytic CR model \cite{2010MNRAS.409..449P},
-the CR pressure derives from the CR distribution function, $f\dd p =
+the CR pressure derives from the CR distribution function, $f(p)\dd p =
 C\,p^{-\alpha}\dd p$, where $C$ is the normalization, $p=P/m_\rmn{p}
@@
 \tilde{C} \,\rho_\rmn{gas}$, where the volume weighted, dimensionless
-normalization, $\bra\tilde{C}\ket\propto \mvir^{0.44}$ for clusters
+normalization scales as $\bra\tilde{C}\ket\propto \mvir^{0.44}$ for clusters
 with a mass $\mvir\gtrsim 10^{14}\,\msun$
@@
 which depends only weakly on cluster virial mass. This suggests that
-CRs are accelerated at the strongest formation shocks, i.e. during
-proto-cluster formation at high$-z$ or in between voids and
-pre-collapsed IGM. These CRs experience then a similar transport
-history in the form of adiabatic compression or encounter shocks of
-similar (weak) strength.
+CRs, which end up in a cluster, are accelerated at the strongest
+formation shocks, i.e. during proto-cluster formation at high$-z$ or
+in between voids and pre-collapsed IGM. \C{These CRs experience a
+similar transport history in the form of adiabatic compression or
+encounter shocks of similarly (weak) strength so that their
+distribution becomes only weakly dependent upon cluster mass.}
 
@@
 in our simulation sample \cite{2008MNRAS.385.1211P,
-  2010MNRAS.409..449P}. We can constrain $X_\CR < 0.1$ using the
-extended gamma-ray upper limits on most of the clusters in the \Fermi
-sample. The most constraining clusters are Norma, Ophiuchus, and Coma
-with $X_\CR < 0.03$. Most of the 32 clusters have limits on $X_\CR$
-within a factor few from the best constraining clusters suggesting
-that stacking of clusters will be able to improve these limits.  These
-limits may improved upon by using a stacking approach that adopts our
-simulation-based analytic model as a prior.
+  2010MNRAS.409..449P}. Using the extended gamma-ray upper limits on
+most of the clusters in the \Fermi sample, we can constrain $\bra
+X_\CR \ket< 0.1$. The most constraining clusters are Norma, Ophiuchus,
+and Coma with $\bra X_\CR\ket < 0.03$. Most of the 32 clusters have
+limits on $\bra X_\CR\ket$ within a factor few from the best
+constraining clusters suggesting that stacking of clusters will be
+able to improve these limits \C{(provided these analyses adopt the
+simulation-based analytic model \cite{2010MNRAS.409..449P} as a
+prior).}
 
@@
 order of 5\% (by adopting, however, point-like upper limits). \C{In
-  this work we find in addition that medium size clusters provide
+  this work we find that medium-sized clusters provide similarly
   strong constraints.}  This difference is explained by the different
@@
 $\mvir/M_\mathrm{min}$ is maximized for the largest virialized systems
-in the Universe -- galaxy clusters. The corresponding substructure
+in the Universe---galaxy clusters. The corresponding substructure
 boost can reach values exceeding $10^3$ which should make nearby
@@
 ones ($\sim 10^5\,\msun$) proceeds scale-invariant, i.e., there is no
-non-linear mode coupling between different scales that could
-potentially erase structure smaller than a characteristic one as the
+non-linear mode coupling between different scales. This could
+potentially erase structures smaller than a characteristic one as the
 linear power spectrum approaches $\Delta^2(k) \propto k^3
-P(k)=\rmn{const.}$ and structure on different scales forms not any
-more hierarchically, but collapses at the same time.
+P(k)=\rmn{const.}$ implying that structure on different scales may not
+form any more hierarchically, but may collapse at the same time.
 
@@
 dominated by small scale substructure, \C{we limit the saturated
-Sommerfeld enhancement factor in M49 and Fornax to about 5. This
-corresponds to a value in the Milky Way (MW) of less than 3}, due to
+Sommerfeld enhancement factor in M49 and Fornax to $\lesssim 5$. This
+corresponds to a value in the Milky Way (MW) of $\lesssim3$}, due to
 the larger Sommerfeld boost factor in smaller mass halos which have a
@@
 from hadronic CR interactions with gas protons over previous work
-\citep{2010ApJ...717L..71A}. We employ the analytic model of the CR
+\cite{2010ApJ...717L..71A}. We employ the analytic model of the CR
 spectrum and spatial distribution that is based on cosmological
@@
 follow the evolution of CRs in cosmic structure formation
-\citet{2010MNRAS.409..449P}. Adopting the model for all clusters in
-the HIFLUGCS sample of flux-limited X-ray clusters, we compare the
+\cite{2010MNRAS.409..449P}. Adopting the model for all clusters in the
+HIFLUGCS sample of flux-limited X-ray clusters, we compare the
 expected gamma-ray emission to that inferred from using
 $L_\gamma$-cluster mass scaling relation. \C{We note that the
-  predictions of our ``optimistic'' model are in tension with \Fermi
-  upper limits for Norma, Coma, and Ophiuchus. In the next 2-3 years
-  \Fermi will be able to probe the predictions of our ``conservative''
-  CR model, hence start to put realistic limits on the acceleration
-  efficency of CRs in structure formation shocks.}  \del{agreement
-  with \Fermi upper limits for all clusters. The hint of a tension
-  that the scaling relation modeling showed for Norma
-  \citep{2010ApJ...717L..71A} could not be confirmed due to the lower
-  gas density of this cluster relative to the average.  }
+  predictions of the ``optimistic'' model in
+  \cite{2010MNRAS.409..449P} are in tension with \Fermi upper limits
+  for Norma, Coma, and Ophiuchus. In the next 2-3 years \Fermi will be
+  able to probe the predictions of their ``conservative'' CR
+  model. This will enable to put realistic limits on a combination of
+  the acceleration efficiency of CRs in structure formation shocks and
+  CR transport coefficients in clusters.}
 
@@
 1~GeV. \C{It is expected to dominate the DM annihilation signal of BM
-  models for clusters/groups, although we find that the gamma-ray
-  flux induced by the BM is higher for about 1/5 of the clusters in the
-  HIFLUGCS catalouge, where Fornax and M49 have the highest signal to
+  models for clusters/groups, although we find that the gamma-ray flux
+  induced by the BM is higher for about 1/5 of the clusters in the
+  HIFLUGCS catalogue, where Fornax and M49 have the highest signal to
   noise. We find that \Fermi-LAT will be able to start constraining
-  these DM models within the coming five years using clusters of
-  galaxies.} \del{It is expected to dominate the DM annihilation
-  signal of BM models for all clusters/groups but Fornax.}
+  these DM models within five years using clusters of galaxies.}
+\del{It is expected to dominate the DM annihilation signal of BM
+  models for all clusters/groups but Fornax.}
 
@@
   around 10\%. This is comparable to those inferred by the \Fermi
-  collaboration \citep{2010ApJ...717L..71A} and mainly due to two
-  different effects that cancel; the differently assumed Bayesian
-  prior on the CR pressure which implies a different cluster mass
-  dependence of the resulting limits on $X_\CR$ and the different
-  masses in our cluster sample which is based on a more recent and
-  more detailed analisys of the clusters in the HIFLUGCS
-  catalouge \cite{2007A&A...466..805C}.}
+  collaboration \citep{2010ApJ...717L..71A} and mainly due to the
+  differently assumed Bayesian prior on the CR pressure which implies
+  a different cluster mass dependence of the resulting limits on
+  $X_\CR$.}
 
@@
 sensitive to the central parts of the clusters where there X-ray flux
-is high, while the core and outerparts are more difficult to measure
+is high, while the core and outer parts are more difficult to measure
 due to the low signal to noise and often involves extrapolation from

### 2011-08-03 paper.tex
typos fixed

--- 2011-08-02 paper.tex
@@
 Galaxy Cluster Sample, HIFLUGCS,
-\citealt{2002ApJ...567..716R,2007A&A...466..805C}).\footnote{Note that
+\cite{2002ApJ...567..716R,2007A&A...466..805C}).\footnote{Note that
   we have added the Virgo cluster to the sample that we nevertheless
@@
 population of CRs to build up over the cluster history
-\citep{1996SSRv...75..279V, 1997ApJ...477..560E,
+\cite{1996SSRv...75..279V, 1997ApJ...477..560E,
   1997ApJ...487..529B}. The production of these secondaries depend
@@
 diffuse radio(-mini) halo that might point to a centrally concentrated
-CR distribution \citep{2011A&A...527A..99E}. The CR spectrum $E^2
+CR distribution \cite{2011A&A...527A..99E}. The CR spectrum $E^2
 dN/dE$ shows the characteristic pion bump at energies around
@@
   around 10\%. This is comparable to those inferred by the \Fermi
-  collaboration \citep{2010ApJ...717L..71A} and mainly due to the
+  collaboration \cite{2010ApJ...717L..71A} and mainly due to the
   differently assumed Bayesian prior on the CR pressure which implies

### 2011-08-03 paper.tex
removed C and del

--- 2011-08-02 paper.tex
@@
 hadronic CR model to show that Virgo has the highest gamma-ray flux
-from annihilating DM. \C{However, if the boost from Sommerfeld
-  enhancement (SFE) is small then the gamma-ray emission induced by
-  CRs is dominating most clusters with the exception of a few
-  clusters; most notably Fornax that shows the largest ratio of DM
-  annihilation-to-CR flux. In particular, we identify Fornax and Virgo
-  as prime targets for DM observations,} Perseus for CR induced
-emission and we additionally decide in favor of the well studied
-cluster Coma for comparison. While studying these four clusters in
-great detail, we complement the analysis by calculating the expected
-gamma-ray fluxes of a nearby X-ray flux complete sample of galaxy
-clusters from the Rosat all-sky survey (extended HIghest X-ray FLUx
-Galaxy Cluster Sample, HIFLUGCS,
+from annihilating DM. However, if the boost from Sommerfeld
+enhancement (SFE) is small then the gamma-ray emission induced by CRs
+is dominating most clusters with the exception of a few clusters; most
+notably Fornax that shows the largest ratio of DM annihilation-to-CR
+flux. In particular, we identify Fornax and Virgo as prime targets for
+DM observations, Perseus for CR induced emission and we additionally
+decide in favor of the well studied cluster Coma for comparison. While
+studying these four clusters in great detail, we complement the
+analysis by calculating the expected gamma-ray fluxes of a nearby
+X-ray flux complete sample of galaxy clusters from the Rosat all-sky
+survey (extended HIghest X-ray FLUx Galaxy Cluster Sample, HIFLUGCS,
 \citealt{2002ApJ...567..716R,2007A&A...466..805C}).\footnote{Note that
@@
   boost without substructures (see Section II A 1).\\
-  (3) \C{The boost due to substructures relative a the smooth DM
-  distribution.} We integrate the emission in a cylinder with a radial
+  (3) The boost due to substructures relative a the smooth DM
+  distribution. We integrate the emission in a cylinder with a radial
   extent of $2.5 R_{200}$ along the line-of-sight and an angular size
@@
 use a DM mass $m_\chi=1.6$~TeV and a branching ratio of
-($1/4:1/4:1/2$) into ($\mu^+\mu^-:\e^+\e^-:\pi^+\pi^-$). \C{Furthermore,
+($1/4:1/4:1/2$) into ($\mu^+\mu^-:\e^+\e^-:\pi^+\pi^-$). Furthermore,
 since most of the gamma-ray flux is expected to come from dense
-subhalos within clusters which have
-a velocity dispersion} close to the velocity limit
-$v_\rmn{sat}$ where the SFE saturates, we use
+subhalos within clusters which have a velocity dispersion close to the
+velocity limit $v_\rmn{sat}$ where the SFE saturates, we use
 $S=\B_\sfe(v_\rmn{sat})\approx 530$ for the cluster
@@
 %121 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-1/3}\,.
-\C{\B_\sfe(\sigv) = \B_\rmn{sfe,MW} \frac{v_\rmn{MW}}{\sigv} =
-70 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-1/3}\,.}
+\B_\sfe(\sigv) = \B_\rmn{sfe,MW} \frac{v_\rmn{MW}}{\sigv} =
+70 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-1/3}\,.
 \label{eq:B_sfe}
 \end{equation}
-\C{Here the boost factor needed to explain the PAMELA/\Fermi excess of
-  electrons and positrons $\B_\rmn{sfe,MW}=300$, the velocity
-  dispersion for the MW $v_\rmn{MW} \approx 220\,\rmn{km\,s}^{-1}$, and the
+Here the boost factor needed to explain the PAMELA/\Fermi excess of
+electrons and positrons $\B_\rmn{sfe,MW}=300$, the velocity dispersion
+for the MW $v_\rmn{MW} \approx 220\,\rmn{km\,s}^{-1}$, and the
 velocity dispersion $\sigv$ for clusters is derived in
-  \cite{2005RvMP...77..207V}.} Clusters have a larger velocity
-dispersion and an accordingly smaller Sommerfeld boost factor.
+\cite{2005RvMP...77..207V}. Clusters have a larger velocity dispersion
+and an accordingly smaller Sommerfeld boost factor.
 
@@
 high end \protect \cite{2008MNRAS.391.1685S, 2008Natur.456...73S,
-  2010ApJ...718..899A}. \C{Following recent high-resolution
-  simulations of Galaxy-sized halos, we adopt a boost factor due to
-  substructures of 230 for such a halo \cite{2008MNRAS.391.1685S}
-  (which needs to be scaled to cluster halos as we will discuss
-  below).}
+  2010ApJ...718..899A}. Following recent high-resolution simulations
+of Galaxy-sized halos, we adopt a boost factor due to substructures of
+230 for such a halo \cite{2008MNRAS.391.1685S} (which needs to be
+scaled to cluster halos as we will discuss below).
 
@@
 clusters), hence depending sensitively on the host halo mass (see
-Figure~\ref{fig:radial_lum}). \C{Recent {\it Phoenix} simulations by
-  Gao et al. \cite{2011arXiv1107.1916G} confirm the large enhancement
-  due to substructures in clusters. In fact they find a boost of 1125
-  for a Coma like cluster which agrees within 10\% with our estimated
-  boost (see e.g. Table~\ref{tab:flux_tab}).}
+Figure~\ref{fig:radial_lum}). Recent {\it Phoenix} simulations by Gao
+et al. \cite{2011arXiv1107.1916G} confirm the large enhancement due to
+substructures in clusters. In fact they find a boost of 1125 for a
+Coma like cluster which agrees within 10\% with our estimated boost
+(see e.g. Table~\ref{tab:flux_tab}).
 
@@
 that is dominated by the continuum emission from $\Kp$ and $\Ip$
-models (shown in the left panels) are about \C{a factor few} below the
+models (shown in the left panels) are about a factor few below the
 upper limits, making it hard for \Fermi to probe these kind of DM
-models \C{in the near future} without a significant improvement in the
+models in the near future without a significant improvement in the
 analysis from e.g. stacking of clusters and improved methods for
 analyzing extended sources. Furthermore, the gamma-ray signal induced
-by CRs is expected to be about a factor 10 below the DM continuum
-flux from the $\Kp$ and $\Ip$ BM models at 10~GeV. However, the IC
-emission from upscattered CMB and SD photons is at least a factor of a
-few lower for $\Kp$ and a factor 1000 lower for $\Ip,\Jp,\Js$, than
-the expected flux from CRs above 100~MeV, making it very hard to
+by CRs is expected to be about a factor 10 below the DM continuum flux
+from the $\Kp$ and $\Ip$ BM models at 10~GeV. However, the IC emission
+from upscattered CMB and SD photons is at least a factor of a few
+lower for $\Kp$ and a factor 1000 lower for $\Ip,\Jp,\Js$, than the
+expected flux from CRs above 100~MeV, making it very hard to
 distinguish such a signal from the foreground due to the similar
@@
   by 20. Extended upper limits ($<1^\circ$) from \Fermi-LAT after 18
-  months \protect \cite{2010ApJ...717L..71A} are also shown. \C{In the
-    near future} we find it hard to detect even the brightest BM
-  models, $\Ip$ and $\Kp$, where the continuum emission is dominating
-  the total emission in the GeV energy range.}
+  months \protect \cite{2010ApJ...717L..71A} are also shown. In the
+  near future we find it hard to detect even the brightest BM models,
+  $\Ip$ and $\Kp$, where the continuum emission is dominating the
+  total emission in the GeV energy range.}
  \label{fig:diff_BM}
@@
 in conflict with the upper limits by \Fermi-LAT, although only by a
-factor of 30 which is \C{a factor few} less constraining than the
+factor of 30 which is a factor few less constraining than the
 differential flux in the energy range $1-10$~GeV. As shown in this
@@
   of \Fermi at these energies and use this regime to get upper limits
-  on boost factors. \C{Note that the CR-induced emission in
-    Coma is close to the upper limits set by \Fermi and will be tested
-    in the upcoming years.}}
+  on boost factors. Note that the CR-induced emission in Coma is close
+  to the upper limits set by \Fermi and will be tested in the upcoming
+  years.}
  \label{fig:clu_comp}
@@
 10^{-6}\,\msun$, we can constrain the saturated boost from SFE to
-\C{$\lesssim 5$ in M49 and Fornax}, which corresponds to a maximum SFE
-in the MW of $\lesssim3$. Hence, we conclude that without substantial
+$\lesssim 5$ in M49 and Fornax, which corresponds to a maximum SFE in
+the MW of $\lesssim3$. Hence, we conclude that without substantial
 improvement in the modelling of these extended sources, \Fermi-LAT
@@
 annihilating DM is independent of the type of DM model, and can not be
-used to separate different models. \C{The surface brightness,
-  $S_\gamma$, of the DM scales as $S_\gamma\propto
-  L_{\gamma,\rmn{sm}}\bsub\mvir^{-2/3} \propto \mvir^{0.40}$}, which
-explains the factor \C{two} difference in normalization between the
-most massive cluster Coma and the least massive cluster Fornax with a
-mass ratio of about 10. The surface brightness induced by CRs is
+used to separate different models. The surface brightness, $S_\gamma$,
+of the DM scales as $S_\gamma\propto
+L_{\gamma,\rmn{sm}}\bsub\mvir^{-2/3} \propto \mvir^{0.40}$, which
+explains the factor two difference in normalization between the most
+massive cluster Coma and the least massive cluster Fornax with a mass
+ratio of about 10. The surface brightness induced by CRs is
 proportional to the projected squared gas profile with an additional
@@
 variation of the gas mass fraction. It is noticeable that Fornax shows
-a small surface brightness. \C{This is explained by the low gas
-  density outside the BCG and the expected small abundance of CRs in a
-  small cluster in comparison} to a massive cluster
-\cite{2010MNRAS.409..449P}. This is the reason why Fornax is a
-good target for indirect DM searches, and superior to DM searches in
-dwarf galaxies.
+a small surface brightness. This is explained by the low gas density
+outside the BCG and the expected small abundance of CRs in a small
+cluster in comparison to a massive cluster
+\cite{2010MNRAS.409..449P}. This is the reason why Fornax is a good
+target for indirect DM searches, and superior to DM searches in dwarf
+galaxies.
 
@@
 L_{\gamma}(>100\,\mev) = 1.8\times10^{45}
-\left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.46}\mbox{erg~s}^{-1}\nonumber\\
+\left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.46}\mbox{ph~s}^{-1}\nonumber\\
 L_{\gamma}(>10\,\gev) = 1.4\times10^{43}
-\left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.34}\mbox{erg~s}^{-1}\,.\nonumber\\
+\left(\frac{\mvir}{10^{15}\,\msun}\right)^{1.34}\mbox{ph~s}^{-1}\,.\nonumber\\
 \end{eqnarray}
@@
 contribution from shock-accelerated primary electrons as well as
-secondary electrons created in CR-proton interactions. \C{However, the
+secondary electrons created in CR-proton interactions. However, the
 gamma-ray flux is dominated by the decaying neutral pions. The
-  difference in the mass scaling arises from the larger contribution
-  of primary IC emission for higher-mass clusters at 100~MeV that have
-  a larger fraction of radio relics due to their greater mass
-  accretion rates in comparison to galaxy groups---a direct
-  consequence of hierarchical growth of structure \protect
-  \cite{2009ApJ...707..354Z,2011arXiv1106.5505P}.} The steeper mass
+difference in the mass scaling arises from the larger contribution of
+primary IC emission for higher-mass clusters at 100~MeV that have a
+larger fraction of radio relics due to their greater mass accretion
+rates in comparison to galaxy groups---a direct consequence of
+hierarchical growth of structure \protect
+\cite{2009ApJ...707..354Z,2011arXiv1106.5505P}. The steeper mass
 scaling of CR emission compared to DM annihilation already implies a
@@
     leptophilic fluxes are ruled out by upper limits in 28 of the
-    clusters, with the strongest constraints set by M49 and
-    Fornax. \C{At the present time, we cannot constrain the benchmark
-      models, although \Fermi-LAT will soon start to probe these
-      models. In particular, improved modelling of extended sources as
-      well as stacking of clusters appears promising in testing
-      benchmark models.}}
+    clusters, with the strongest constraints set by M49 and Fornax. At
+    the present time, we cannot constrain the benchmark models,
+    although \Fermi-LAT will soon start to probe these models. In
+    particular, improved modelling of extended sources as well as
+    stacking of clusters appears promising in testing benchmark
+    models.}
  \label{fig14}
@@
     \Fermi. Interestingly, the limits of Virgo, Norma, and Coma are
-    closing in on our \C{conservative} predictions and will enforce
+    closing in on our conservative predictions and will enforce
     constraints on the parameters of hadronic models such as shock
@@
    distribution follows the analytical model derived through
-   hydrodynamical cosmological cluster simulations\C{, where the
-     spectral shape is independent of cluster mass} \protect
+   hydrodynamical cosmological cluster simulations, where the spectral
+   shape is independent of cluster mass \protect
    \cite{2010MNRAS.409..449P} (see text for details). Gamma-ray fluxes
@@
    brightest clusters are labelled. The lower panel shows the relative
-   difference between the flux \C{above 100~MeV} computed using the
+   difference between the flux above 100~MeV computed using the
    analytical model and the gamma-ray flux predicted by the
-   mass-luminosity scaling relation
-   \cite{2010MNRAS.409..449P}. \del{For this figure we have used that
-     $F_\gamma(100\,\rmn{GeV})\propto F_\gamma(100\,\rmn{MeV})\propto
-     M^{1.46}$, which introduce an error of 50\% in the mass range
-     $5\times10^{13}\msun<\mvir<10^{15}\msun$.} The clusters with the
-   largest positive offset are labelled. As expected, they all are
-   cool core clusters.}
+   mass-luminosity scaling relation \cite{2010MNRAS.409..449P}. The
+   clusters with the largest positive offset are labelled. As
+   expected, they all are cool core clusters.}
  \label{fig19}
@@
 to the extended \Fermi-LAT flux upper limits that assume King profiles
-which trace the X-ray emitting gas. \C{For consistency, we use single-
-  and double-beta model fits to ROSAT data of X-ray bright clusters
-  for our gamma-ray flux estimates as an input
+which trace the X-ray emitting gas. For consistency, we use single-
+and double-beta model fits to ROSAT data of X-ray bright clusters for
+our gamma-ray flux estimates as an input
 \cite{2007A&A...466..805C}. The deprojection is performed following
@@
 \cite{2010ApJ...717L..71A} to compare to \Fermi limits) which do not
-  account for the substantial scatter in the scaling relation.} The
+account for the substantial scatter in the scaling relation. The
 analytic CR model that we employ here follows CR-acceleration at
@@
 expected gamma-ray emission from decaying pions (bracketing our
-ignorance of the contribution of cluster galaxies \C{and ram-pressure
-  stripped gas parcels from infalling galaxies} to the overall
-gamma-ray flux from a cluster).
+ignorance of the contribution of cluster galaxies and ram-pressure
+stripped gas parcels from infalling galaxies to the overall gamma-ray
+flux from a cluster).
 
@@
 
-The tightest \Fermi limits are obtained in the 1-10 GeV
-regime due to the highest sensitivity of \Fermi-LAT there. While the
-effective area of LAT increases up to these energies, the typical
-photon spectra decrease as a function of energy: combining those
-effects selects this energy range to be most sensitive. In this
-energy band, the \Fermi limits close in on the \C{conservative flux
-  predictions of Virgo, Coma and Norma}. Using integrated flux limits
-  from \Fermi, we arrive at very similar results. \del{We emphasize that
-  by using our analytic modeling, the slight discrepancy of the
-  scaling relation-based prediction with the \Fermi limit on Norma
-  \cite{2010ApJ...717L..71A} is resolved: Norma simply seems to be
-  less bright than an average cluster of the same mass as Norma.} The
-  insensitive limit on Perseus is due to the bright central source
-  NGC1275 with an AGN in the center \cite{2010ATel.2916....1M} making
-  it hard to determine a comparable limit as obtained for the other
-  clusters. Additionally, recent gamma-ray observations of
-  the head-tail radio galaxy IC310 complicate matters furthermore
-  \cite{2010ApJ...723L.207A,2010A&A...519L...6N}.
+The tightest \Fermi limits are obtained in the 1-10 GeV regime due to
+the highest sensitivity of \Fermi-LAT there. While the effective area
+of LAT increases up to these energies, the typical photon spectra
+decrease as a function of energy: combining those effects selects this
+energy range to be most sensitive. In this energy band, the \Fermi
+limits close in on the conservative flux predictions of Virgo, Coma
+and Norma. Using integrated flux limits from \Fermi, we arrive at very
+similar results. The insensitive limit on Perseus is due to the
+bright central source NGC1275 with an AGN in the center
+\cite{2010ATel.2916....1M} making it hard to determine a comparable
+limit as obtained for the other clusters. Additionally, recent
+gamma-ray observations of the head-tail radio galaxy IC310 complicate
+matters furthermore \cite{2010ApJ...723L.207A,2010A&A...519L...6N}.
 
@@
 formation shocks, i.e. during proto-cluster formation at high$-z$ or
-in between voids and pre-collapsed IGM. \C{These CRs experience a
+in between voids and pre-collapsed IGM. These CRs experience a
 similar transport history in the form of adiabatic compression or
 encounter shocks of similarly (weak) strength so that their
-distribution becomes only weakly dependent upon cluster mass.}
+distribution becomes only weakly dependent upon cluster mass.
 
@@
 constraining clusters suggesting that stacking of clusters will be
-able to improve these limits \C{(provided these analyses adopt the
+able to improve these limits (provided these analyses adopt the
 simulation-based analytic model \cite{2010MNRAS.409..449P} as a
-prior).}
+prior).
 
@@
 are on average more constraining yielding the best constraints of the
-order of 5\% (by adopting, however, point-like upper limits). \C{In
-  this work we find that medium-sized clusters provide similarly
-  strong constraints.} This difference is explained by the different
-priors on $P_\CR$. We adopt a prior inferred from cosmological
-simulations that dynamically trace the CRs during cluster assembly
-suggesting that adiabatic transport is dominant in shaping the CR
-population in clusters and implying a weak mass dependence of
-$X_\CR$. Their analysis assumes a CR pressure that is independent of
-cluster mass, i.e., constraints on $X_\CR$ inherit the inverse mass
-dependence of the thermal pressure, $X_\CR\propto 1/P_\rmn{th}\propto
+order of 5\% (by adopting, however, point-like upper limits). In this
+work we find that medium-sized clusters provide similarly strong
+constraints. This difference is explained by the different priors on
+$P_\CR$. We adopt a prior inferred from cosmological simulations that
+dynamically trace the CRs during cluster assembly suggesting that
+adiabatic transport is dominant in shaping the CR population in
+clusters and implying a weak mass dependence of $X_\CR$. Their
+analysis assumes a CR pressure that is independent of cluster mass,
+i.e., constraints on $X_\CR$ inherit the inverse mass dependence of
+the thermal pressure, $X_\CR\propto 1/P_\rmn{th}\propto
 M^{-0.8}$. While it is not clear which mass scaling of $X_\CR$ is
@@
 
-We identify \C{Virgo, Fornax and M49} to be the best cluster/group
+We identify Virgo, Fornax and M49 to be the best cluster/group
 candidates for indirect DM studies as they are expected to emit the
@@
 extends down to an Earth mass and that the DM annihilation flux is
-dominated by small scale substructure, \C{we limit the saturated
+dominated by small scale substructure, we limit the saturated
 Sommerfeld enhancement factor in M49 and Fornax to $\lesssim 5$. This
-corresponds to a value in the Milky Way (MW) of $\lesssim3$}, due to
+corresponds to a value in the Milky Way (MW) of $\lesssim3$, due to
 the larger Sommerfeld boost factor in smaller mass halos which have a
@@
 expected gamma-ray emission to that inferred from using
-$L_\gamma$-cluster mass scaling relation. \C{We note that the
-  predictions of the ``optimistic'' model in
-  \cite{2010MNRAS.409..449P} are in tension with \Fermi upper limits
-  for Norma, Coma, and Ophiuchus. In the next 2-3 years \Fermi will be
-  able to probe the predictions of their ``conservative'' CR
-  model. This will enable to put realistic limits on a combination of
-  the acceleration efficiency of CRs in structure formation shocks and
-  CR transport coefficients in clusters.}
+$L_\gamma$-cluster mass scaling relation. We note that the predictions
+of the ``optimistic'' model in \cite{2010MNRAS.409..449P} are in
+tension with \Fermi upper limits for Norma, Coma, and Ophiuchus. In
+the next 2-3 years \Fermi will be able to probe the predictions of
+their ``conservative'' CR model. This will enable to put realistic
+limits on a combination of the acceleration efficiency of CRs in
+structure formation shocks and CR transport coefficients in clusters.
 
@@
 CR distribution \citep{2011A&A...527A..99E}. The CR spectrum $E^2
-dN/dE$ shows the characteristic pion bump at energies around
-1~GeV. \C{It is expected to dominate the DM annihilation signal of BM
-  models for clusters/groups, although we find that the gamma-ray flux
-  induced by the BM is higher for about 1/5 of the clusters in the
-  HIFLUGCS catalogue, where Fornax and M49 have the highest signal to
-  noise. We find that \Fermi-LAT will be able to start constraining
-  these DM models within five years using clusters of galaxies.}
-\del{It is expected to dominate the DM annihilation signal of BM
-  models for all clusters/groups but Fornax.}
+dN/dE$ shows the characteristic pion bump at energies around 1~GeV. It
+is expected to dominate the DM annihilation signal of BM models for
+clusters/groups, although we find that the gamma-ray flux induced by
+the BM is higher for about 1/5 of the clusters in the HIFLUGCS
+catalogue, where Fornax and M49 have the highest signal to noise. We
+find that \Fermi-LAT will be able to start constraining these DM
+models within five years using clusters of galaxies.
 
@@
 we limit the relative CR pressure, $X_\CR = P_\CR/P_\rmn{th}$, in 32
-nearby bright galaxy clusters of the \Fermi sample. \C{The best limits
+nearby bright galaxy clusters of the \Fermi sample. The best limits
 are found in Norma and Coma of the order of 3\%, with typical limits
@@
 collaboration \citep{2010ApJ...717L..71A} and mainly due to the
-  differently assumed Bayesian prior on the CR pressure which implies
-  a different cluster mass dependence of the resulting limits on
-  $X_\CR$.}
+differently assumed Bayesian prior on the CR pressure which implies a
+different cluster mass dependence of the resulting limits on $X_\CR$.
 

### 2011-08-03 paper.tex

@@
 survey (extended HIghest X-ray FLUx Galaxy Cluster Sample, HIFLUGCS,
-\citealt{2002ApJ...567..716R,2007A&A...466..805C}).\footnote{Note that
+\cite{2002ApJ...567..716R,2007A&A...466..805C}).\footnote{Note that
   we have added the Virgo cluster to the sample that we nevertheless
@@
 diffuse radio(-mini) halo that might point to a centrally concentrated
-CR distribution \citep{2011A&A...527A..99E}. The CR spectrum $E^2
+CR distribution \cite{2011A&A...527A..99E}. The CR spectrum $E^2
 dN/dE$ shows the characteristic pion bump at energies around 1~GeV. It
@@
 around 10\%. This is comparable to those inferred by the \Fermi
-collaboration \citep{2010ApJ...717L..71A} and mainly due to the
+collaboration \cite{2010ApJ...717L..71A} and mainly due to the
 differently assumed Bayesian prior on the CR pressure which implies a

### 2011-10-06 paper.tex
abstract, intro, concl. improved as a result of eth referee report

@@
   We study the possibility for detecting gamma-ray emission from galaxy
-  clusters. We consider 1) cosmic ray (CR) induced pion decay, 2) different
-  representative benchmark models of supersymmetric dark matter (DM), and 3)
-  leptophilic models of DM annihilation that include a Sommerfeld enhancement
-  (SFE). To model DM annihilation, we consider continuum emission as a result of
+  clusters. We consider 1) leptophilic models of dark matter (DM) annihilation
+  that include a Sommerfeld enhancement (SFE), 2) different representative
+  benchmark models of supersymmetric DM, and 3) cosmic ray (CR) induced pion
+  decay. To model DM annihilation, we consider continuum emission as a result of
   the hadronization of annihilating neutralinos, internal bremsstrahlung, and
@@
   a realistic spatial and spectral distribution of dust and stellar light. Among
-  all clusters/groups, we predict Virgo, Fornax and M49 to be the brightest DM
-  sources and find a particularly low CR-induced background for Fornax. For a
-  minimum substructure mass given by the DM free-streaming scale, cluster halos
-  maximize the substructure boost for which we find a factor of $\gtrsim 1000$.
-  Since the annihilation flux of substructures is mostly contributed by the
-  regions around the virial radius, the resulting surface brightness profiles
-  are almost flat. This makes it very challenging to detect this flux with
-  imaging atmospheric Cherenkov telescopes since their sensitivity drops
-  linearly with radius and they typically have $5-10$ linear resolution elements
-  across a cluster; the gamma-ray satellite \Fermi is better suited. Assuming
-  cold dark matter with a substructure mass distribution down to an Earth mass
-  and using \Fermi upper limits, we rule out the leptophilic models in their
-  present form in 28 clusters, and limit the boost from SFE in M49 and Fornax to
-  be $\lesssim 5$. This corresponds to a limit on SFE in the Milky Way of
-  $\lesssim 3$. Alternatively, if the SFE is realized in Nature, this
-  would imply a limiting substructure mass of $\mlim > 10^4\,\msun$---a
-  challenge for structure formation. Without improved modelling of extended
-  sources or stacked likelihood analyses, \Fermi will face difficulties in
-  constraining our selection of DM benchmark models in the near future. The
-  \Fermi upper limits are, however, closing in on our predictions for the CR
-  flux using an analytic model based on cosmological hydrodynamical cluster
-  simulations. We limit the CR-to-thermal pressure in nearby bright galaxy
-  clusters of the \Fermi sample to $\lesssim 10\%$ and in Norma and Coma to
-  $\lesssim 3\%$. Thus we will soon start to constrain the underlying CR
-  physics such as shock acceleration efficiencies or CR transport properties.
+  all clusters/groups of a flux-limited X-ray sample, we predict Virgo, Fornax
+  and M49 to be the brightest DM sources and find a particularly low CR-induced
+  background for Fornax. For a minimum substructure mass given by the DM
+  free-streaming scale, cluster halos maximize the substructure boost for which
+  we find a factor of $\gtrsim 1000$. Since regions around the virial radius
+  dominate the annihilation flux of substructures, the resulting surface
+  brightness profiles are almost flat. This makes it very challenging to detect
+  this flux with imaging atmospheric Cherenkov telescopes since their
+  sensitivity drops approximately linearly with radius and they typically have
+  $5-10$ linear resolution elements across a cluster. Assuming cold dark matter
+  with a substructure mass distribution down to an Earth mass and using extended
+  \Fermi upper limits, we rule out the leptophilic models in their present form
+  in 28 clusters, and limit the boost from SFE in M49 and Fornax to be $\lesssim
+  5$. This corresponds to a limit on SFE in the Milky Way of $\lesssim 3$ which
+  is too small to account for the increasing positron fraction with energy as
+  seen by PAMELA. Alternatively, if SFE is realized in Nature, this would imply
+  a limiting substructure mass of $\mlim > 10^4\,\msun$---a problem for
+  structure formation in most particle physics models. Using individual cluster
+  observations, it will be challenging for \Fermi to constrain our selection of
+  DM benchmark models without SFE. The \Fermi upper limits are, however, closing
+  in on our predictions for the CR flux using an analytic model based on
+  cosmological hydrodynamical cluster simulations. We limit the CR-to-thermal
+  pressure in nearby bright galaxy clusters of the \Fermi sample to $\lesssim
+  10\%$ and in Norma and Coma to $\lesssim 3\%$. Thus we will soon start to
+  constrain the underlying CR physics such as shock acceleration efficiencies or
+  CR transport properties.
 \end{abstract}
@@
 indirect detection experiments looking for signals in the cosmic-ray
-spectra of antiprotons, positrons, neutrinos and all of the
+(CR) spectra of antiprotons, positrons, neutrinos and all of the
 electromagnetic spectrum from radio waves to gamma-rays
@@
 
-1. The galactic center (g.c.). This is where all numerical simulations
-of cold dark matter (CDM) predict the highest density. However, the
-detailed DM density in the very central part is difficult to predict,
-due a to a possibly very complicated interplay between baryons, DM,
-and the central galactic black hole. Also, it is a very crowded region
-with many gamma-ray sources like pulsars and other supernova remnants,
-which have to be subtracted from the data to extract the DM induced
-signal. In fact, there is a recent claim of an indication of a
-relatively light DM particle contribution to the gamma-ray flux from
-the g.c. \cite{2010arXiv1010.2752H},
-but other hypotheses seem to work
-at least as well \cite{2010arXiv1012.5839B}.
-
-2. The dwarf spheroidal galaxies orbiting the Milky Way (MW), like
-Segue-1, Ursa Minor, Draco, Sagittarius, Sculptor, Carina or Willman-1
+1. The galactic center (g.c.). This is where all numerical simulations of cold
+dark matter (CDM) predict the highest density. However, the detailed DM density
+in the very central part is difficult to predict, due a to a possibly very
+complicated interplay between baryons, DM, and the central galactic black
+hole. Also, it is a very crowded region with many gamma-ray sources like
+pulsars, CR-illuminated molecular clouds, and other supernova remnants, which
+have to be subtracted from the data to extract the DM induced signal. In fact,
+there is a recent claim of an indication of a relatively light DM particle
+contribution to the gamma-ray flux from the g.c. \cite{2010arXiv1010.2752H}, but
+other hypotheses seem to work at least as well \cite{2010arXiv1012.5839B}.
+
+2. The dwarf spheroidal galaxies orbiting the Milky Way (MW), like Segue-1, Ursa
+Minor, Draco, Sagittarius, Sculptor, Carina or Willman-1
 \cite{2009JCAP...01..016B,2010ApJ...720.1174A,2010JCAP...01..031S,2010JCAP...01..031S,2011arXiv1103.0477T,2011APh....34..608H}. The
-problem here is that the nature of many of these small, dark
-matter-dominated galaxies is not entirely clear, and the velocity
-dispersion estimates are based on rather small numbers of stars. Tidal
-disruption and confusion with star clusters are other
-complications. Thus the DM density profile is very uncertain for most
-of them. Nonetheless, by stacking the data together from many dwarf
-spheroidals these uncertainties can be made less severe, and
-preliminary results from \Fermi-LAT shows this method to give quite
-promising results \cite{garde}.
+problem here is that the nature of many of these small, dark matter-dominated
+galaxies is not entirely clear, and the velocity dispersion estimates are based
+on rather small numbers of stars.  Confusion with star clusters and tidal
+disruption are other complications. Once a satellite dwarf galaxy is accreted by
+the MW, the outer regions are severely affected by tidal stripping. The longer a
+satellite has been part of our Galaxy, and the closer it comes to the center
+during its pericentral passage, the more material is removed
+\cite{2004MNRAS.355..819G}.  Thus the DM density profile is very uncertain for
+most of them, especially for radii larger than those probed by the
+stars. Nonetheless, by stacking the data together from many dwarf spheroidals
+these uncertainties can be made less severe, and preliminary results from
+\Fermi-LAT shows this method to give quite promising results \cite{garde}.
+
+%For a satellite dwarf galaxy, however, once it is accreted by the MW,
+%the outer regions are severely affected by tidal stripping. The longer
+%a satellite has been part of our Galaxy, and the closer it comes to
+%the center during its pericentral passage, the more material is
+%removed \cite{2004MNRAS.355..819G}.
 
@@
 campaign to detect gamma-ray emission from galaxy clusters
-\cite{2010ApJ...710..634A,2010JCAP...05..025A,2009A&A...495...27A,2009IJMPD..18.1627D,2009A&A...502..437A,2009arXiv0907.5000G,2009ApJ...704..240K,2009ApJ...706L.275A,2010ApJ...717L..71A}. In
-fact, we noted in a previous Letter \cite{2009PhRvL.103r1302P} that
+\cite{2003ApJ...588..155R,2006ApJ...644..148P,2008AIPC.1085..569P,2009A&A...495...27A,2009arXiv0907.0727T,2009arXiv0907.5000G,2009IJMPD..18.1627D,2009A&A...495...27A,2009A&A...502..437A,2009ApJ...704..240K,2009ApJ...706L.275A,2010ApJ...710..634A,2010JCAP...05..025A,2010ApJ...717L..71A}.
+In fact, we noted in a previous Letter \cite{2009PhRvL.103r1302P} that
 there are certain advantages that work in favour of this possible
@@
 
-For a satellite dwarf galaxy, however, once it is accreted by the MW,
-the outer regions are severely affected by tidal stripping. The longer
-a satellite has been part of our Galaxy, and the closer it comes to
-the center during its pericentral passage, the more material is
-removed \cite{2004MNRAS.355..819G}.
-
-In this paper, we will investigate in some more detail the potential
-of several of the most promising galaxy clusters to produce an
-annihilation gamma-ray yield which could be observable with present
-and planned gamma-ray detectors. For convenience, we summarize in
-Table~\ref{tab:flux_tab} our results for the gamma-ray flux from four
-promising clusters with a high gamma-ray yield. We will in the
-following derive the emission from two different DM models and a
-hadronic CR model to show that Virgo has the highest gamma-ray flux
-from annihilating DM. However, if the boost from Sommerfeld
-enhancement (SFE) is small then the gamma-ray emission induced by CRs
-is dominating most clusters with the exception of a few clusters; most
-notably Fornax that shows the largest ratio of DM annihilation-to-CR
-flux. In particular, we identify Fornax and Virgo as prime targets for
-DM observations, Perseus for CR induced emission and we additionally
-decide in favor of the well studied cluster Coma for comparison. While
-studying these four clusters in great detail, we complement the
-analysis by calculating the expected gamma-ray fluxes of a nearby
-X-ray flux complete sample of galaxy clusters from the Rosat all-sky
-survey (extended HIghest X-ray FLUx Galaxy Cluster Sample, HIFLUGCS,
-\cite{2002ApJ...567..716R,2007A&A...466..805C}).\footnote{Note that
-  we have added the Virgo cluster to the sample that we nevertheless
-  refer to as extended HIFLUGCS catalogue in the following.} For
-previous work related to DM in clusters, see, e.g.,
-\cite{2006A&A...455...21C,2009PhRvD..80b3005J,2011arXiv1104.3530S,2011ApJ...726L...6C,2010JCAP...05..025A}
-and for recent work on CRs in clusters see
+In this paper, we will investigate in detail the potential of several
+of the most promising galaxy clusters to produce an annihilation
+gamma-ray yield which could be observable with present and planned
+gamma-ray detectors. Here, we sketch out the main arguments that need
+to be considered for maximizing the expected signal-to-noise ratio of
+a promising target cluster. First, we need to maximize the DM
+annihilation flux of an unresolved cluster, $F=A_\rmn{dm} \int dV
+\rho^2 / D^2 \sim \mvir^\alpha/D^2$, where $A_\rmn{dm}$ depends on the
+particle physics model of DM, $\rho$ is the smooth DM density profile,
+$D$ is the luminosity distance, and $\alpha=1$ if we assume
+universality of the DM density profile. The dependence of $\rho$ on
+the halo formation epoch breaks the universality and slightly modifies
+the mass dependence, yielding $\alpha=0.83$
+\cite{2009PhRvL.103r1302P}. Additionally, the presence of a hierarchy
+of substructures down to small scales \cite{2008Natur.456...73S} and
+the potential dependence of the particle physics cross section on the
+relative DM particle velocities \cite{ArkaniHamed:2008qn} may
+furthermore modify the scaling parameter $\alpha$ and shall be one of
+the focus points of this work. Second, we need to minimize the
+expected noise which is a sum of galactic and cluster-intrinsic
+foreground. While the galactic foreground varies across the sky, it is
+typically lower for increasing latitude (away from the galactic
+plane). It is thought that the gamma-ray foreground from clusters is
+dominated by CRs which are accelerated at cosmological formation
+shocks and transported over time although there could be a substantial
+contribution of CRs from AGNs and supernova-driven galactic winds. In
+this work we will also study (and constrain) the CR-induced emission
+from clusters to identify those objects that are expected to be
+especially dim which would imply a low CR-induced background.  Since
+the CR-induced emission is expected to scale with the thermal X-ray
+emission of clusters \cite{2004A&A...413...17P}, we estimate gamma-ray
+fluxes of a nearby X-ray flux complete sample of galaxy clusters from
+the Rosat all-sky survey (extended HIghest X-ray FLUx Galaxy Cluster
+Sample, HIFLUGCS,
+\cite{2002ApJ...567..716R,2007A&A...466..805C}).\footnote{Note that we
+  have added the Virgo cluster to the sample that we nevertheless
+  refer to as extended HIFLUGCS catalogue in the following.}  This
+complements and extends previous work related to DM in clusters
+\cite{2006A&A...455...21C,2009PhRvD..80b3005J,2011arXiv1104.3530S,2011ApJ...726L...6C}
+and to CRs in clusters
 \cite{2010MNRAS.409..449P,2011MNRAS.410..127B,2008MNRAS.385.1211P,2009JCAP...08..002K,2010MNRAS.407.1565D}.
 
-\begin{table*}
-\begin{minipage}{2.0\columnwidth}
-  \caption{Gamma-ray flux from various clusters within $\rvir$.}
-\begin{tabular}{l c c c c c c c c c c}
-\hline
-\hline
- Cluster &
-\multicolumn{3}{c}{$F_{\gamma}(>100\,\rmn{MeV})$ $[\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}]$:} & &
-\multicolumn{3}{c}{$F_{\gamma}(>100\,\rmn{GeV})$ $[\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}]$:} &
-$\mvir$ $^{(1)}$ & $\B_\rmn{sfe} $$^{(2)}$ & $\B_\rmn{sub} $$^{(3)}$ \\
-         & DM-LP $^{(4)}$ & DM-BM-$\Kp$ $^{(5)}$ & CR-$\pi^0$ $^{(6)}$
-         & & DM-LP $^{(4)}$ & DM-BM-$\Kp$ $^{(5)}$ & CR-$\pi^0$ $^{(6)}$ & $[10^{14}\,\msun]$ && \\
- \hline
- Coma & $8.2\times10^{-8}$ & $7.6\times10^{-11}$ & $4.1\times10^{-9}$
- & \,\,\,\,\, & $1.2\times10^{-11}$ & $2.8\times10^{-13}$ & $1.5\times10^{-12}$
- & $12.9$ & $530/65$ & $1290$ \\
- Perseus \,\,\,\,\,\, & $8.6\times10^{-8}$ & $7.8\times10^{-11}$ & $1.5\times10^{-8}$
- & \,\,\,\,\, & $1.2\times10^{-11}$ & $2.9\times10^{-13}$ & $5.5\times10^{-12}$
- & $8.6$ & $530/75$ & $1190$ \\
- Virgo & $1.6\times10^{-6}$ & $1.5\times10^{-9}$ & $1.5\times10^{-8}$
- & \,\,\,\,\, & $2.3\times10^{-10}$ & $5.4\times10^{-12}$ & $5.7\times10^{-12}$
- & $6.9$ & $530/80$ & $1120$ \\
- Fornax & $3.5\times10^{-7}$ & $3.2\times10^{-10}$ & $3.1\times10^{-10}$
- & \,\,\,\,\, & $5.1\times10^{-11}$ & $1.2\times10^{-12}$ & $1.1\times10^{-13}$
- & $2.4$ & $530/110$ & $890$ \\
-\hline
-\hline
-\end{tabular}
-\begin{quote}
-  Notes: \\
-  (1) The mass of Fornax, Coma, and Perseus are derived from \cite{2007A&A...466..805C},
-  while the mass of Virgo is derived from \cite{1984ApJ...281...31T}.\\
-  (2) The boost due to Sommerfeld enhancement. The first value shows the saturated
-  Sommerfeld boost realized when substructures are present, the latter is the Sommerfeld
-  boost without substructures (see Section II A 1).\\
-  (3) The boost due to substructures relative a the smooth DM
-  distribution. We integrate the emission in a cylinder with a radial
-  extent of $2.5 R_{200}$ along the line-of-sight and an angular size
-  corresponding to $\rvir$ (both measured from the cluster center).\\
-  (4) The total gamma-ray flux from leptophilic (LP) DM where both the
-  boost from substructures and Sommerfeld enhancement are
-  included. Note that all these values are in conflict with upper limits from
-  \Fermi (see the following sections for detail).\\
-  (5) The total gamma-ray flux from the supersymmetric $\Kp$ benchmark (BM)
-  model where the boost from substructures is included. See Sections II A 2 and II B 3.\\
-  (6) Gamma-ray flux induced by CR protons. See Section V C.
- \label{tab:flux_tab}
-  \end{quote}
-\end{minipage}
-\end{table*}
-
-This work studies the prospects for detecting extended gamma-ray
-emission from galaxy clusters induced by both DM as well as CR
-protons. In Section 2 we discuss the theory of DM and gamma-rays. In
+In Section 2 we discuss the theory of DM and gamma-rays. In
 particular, we focus on the leptophilic (LP) and supersymmetric
-benchmark (BM) DM models in this work, and outline the framework
-for estimating the gamma-ray emission from various radiative
-processes. In Section 3 we calculate the gamma-ray fluxes and spectral
-distributions from four clusters and compare it to upper limits set by
-\Fermi-LAT. For the same clusters we derive the gamma-ray surface
-brightness profiles in Section 4. To extend the analysis to more
-clusters and find promising targets we estimate the fluxes from DM and
-CRs of all clusters in the extended HIFLUGCS sample in Section 5. In
-Section 6 we conclude and discuss our results.
+benchmark (BM) DM models in this work, and outline the framework for
+estimating the gamma-ray emission from various radiative processes. In
+Section 3 we calculate the gamma-ray fluxes and spectral distributions
+of four clusters that are identified as prime targets for DM
+observations (Fornax and Virgo) as well as to have a high CR-induced
+gamma-ray yield (Perseus and Coma). For the same clusters we derive
+the gamma-ray surface brightness profiles in Section 4. To extend the
+analysis to more clusters and increase the list of promising targets we
+estimate the fluxes from DM and CRs of all clusters in the extended
+HIFLUGCS sample in Section 5. In Section 6 we conclude and discuss our
+results.
+
+% In this paper, we will investigate in some more detail the potential
+% of several of the most promising galaxy clusters to produce an
+% annihilation gamma-ray yield which could be observable with present
+% and planned gamma-ray detectors. For convenience, we summarize in
+% Table~\ref{tab:flux_tab} our results for the gamma-ray flux from four
+% promising clusters with a high gamma-ray yield. We will in the
+% following derive the emission from two different DM models and a
+% hadronic CR model to show that Virgo has the highest gamma-ray flux
+% from annihilating DM. However, if the boost from Sommerfeld
+% enhancement (SFE) is small then the gamma-ray emission induced by CRs
+% is dominating most clusters with the exception of a few clusters; most
+% notably Fornax that shows the largest ratio of DM annihilation-to-CR
+% flux. In particular, we identify Fornax and Virgo as prime targets for
+% DM observations, Perseus for CR induced emission and we additionally
+% decide in favor of the well studied cluster Coma for comparison. While
+% studying these four clusters in great detail, we complement the
+% analysis by calculating the expected gamma-ray fluxes of a nearby
+% X-ray flux complete sample of galaxy clusters from the Rosat all-sky
+% survey (extended HIghest X-ray FLUx Galaxy Cluster Sample, HIFLUGCS,
+% \cite{2002ApJ...567..716R,2007A&A...466..805C}).\footnote{Note that
+%   we have added the Virgo cluster to the sample that we nevertheless
+%   refer to as extended HIFLUGCS catalogue in the following.} For
+% previous work related to DM in clusters, see, e.g.,
+% \cite{2006A&A...455...21C,2009PhRvD..80b3005J,2011arXiv1104.3530S,2011ApJ...726L...6C,2010JCAP...05..025A}
+% and for recent work on CRs in clusters see
+% \cite{2010MNRAS.409..449P,2011MNRAS.410..127B,2008MNRAS.385.1211P,2009JCAP...08..002K,2010MNRAS.407.1565D}.
 
@@
 well studied Virgo cluster, the X-ray bright Perseus clusters, and the
-massive merging Coma cluster. We find high DM induced gamma-ray fluxes
+massive merging Coma cluster. We summarize in Table~\ref{tab:flux_tab}
+the expected gamma-ray flux in our DM and CR models and the
+corresponding boost factors.  We find high DM induced gamma-ray fluxes
 from the Fornax and Virgo clusters, which confirms them as promising
@@
 for Virgo and Perseus are unfortunately background contaminated by AGN
-activity from M87 and NGC 1267, respectively, and do not gain much
+activity from M87 and NGC 1275, respectively, and do not gain much
 from the increased sensitivity. In addition, the angular radius of
@@
 \end{eqnarray}
+
+\begin{table*}
+\begin{minipage}{2.0\columnwidth}
+  \caption{Gamma-ray flux from various clusters within $\rvir$.}
+\begin{tabular}{l c c c c c c c c c c}
+\hline
+\hline
+ Cluster &
+\multicolumn{3}{c}{$F_{\gamma}(>100\,\rmn{MeV})$ $[\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}]$:} & &
+\multicolumn{3}{c}{$F_{\gamma}(>100\,\rmn{GeV})$ $[\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}]$:} &
+$\mvir$ $^{(1)}$ & $\B_\rmn{sfe} $$^{(2)}$ & $\B_\rmn{sub} $$^{(3)}$ \\
+         & DM-LP $^{(4)}$ & DM-BM-$\Kp$ $^{(5)}$ & CR-$\pi^0$ $^{(6)}$
+         & & DM-LP $^{(4)}$ & DM-BM-$\Kp$ $^{(5)}$ & CR-$\pi^0$ $^{(6)}$ & $[10^{14}\,\msun]$ && \\
+ \hline
+ Coma & $8.2\times10^{-8}$ & $7.6\times10^{-11}$ & $4.1\times10^{-9}$
+ & \,\,\,\,\, & $1.2\times10^{-11}$ & $2.8\times10^{-13}$ & $1.5\times10^{-12}$
+ & $12.9$ & $530/65$ & $1290$ \\
+ Perseus \,\,\,\,\,\, & $8.6\times10^{-8}$ & $7.8\times10^{-11}$ & $1.5\times10^{-8}$
+ & \,\,\,\,\, & $1.2\times10^{-11}$ & $2.9\times10^{-13}$ & $5.5\times10^{-12}$
+ & $8.6$ & $530/75$ & $1190$ \\
+ Virgo & $1.6\times10^{-6}$ & $1.5\times10^{-9}$ & $1.5\times10^{-8}$
+ & \,\,\,\,\, & $2.3\times10^{-10}$ & $5.4\times10^{-12}$ & $5.7\times10^{-12}$
+ & $6.9$ & $530/80$ & $1120$ \\
+ Fornax & $3.5\times10^{-7}$ & $3.2\times10^{-10}$ & $3.1\times10^{-10}$
+ & \,\,\,\,\, & $5.1\times10^{-11}$ & $1.2\times10^{-12}$ & $1.1\times10^{-13}$
+ & $2.4$ & $530/110$ & $890$ \\
+\hline
+\hline
+\end{tabular}
+\begin{quote}
+  Notes: \\
+  (1) The mass of Fornax, Coma, and Perseus are derived from \cite{2007A&A...466..805C},
+  while the mass of Virgo is derived from \cite{1984ApJ...281...31T}.\\
+  (2) The boost due to Sommerfeld enhancement. The first value shows the saturated
+  Sommerfeld boost realized when substructures are present, the latter is the Sommerfeld
+  boost without substructures (see Section II A 1).\\
+  (3) The boost due to substructures relative a the smooth DM
+  distribution. We integrate the emission in a cylinder with a radial
+  extent of $2.5 R_{200}$ along the line-of-sight and an angular size
+  corresponding to $\rvir$ (both measured from the cluster center).\\
+  (4) The total gamma-ray flux from leptophilic (LP) DM where both the
+  boost from substructures and Sommerfeld enhancement are
+  included. Note that all these values are in conflict with upper limits from
+  \Fermi (see the following sections for detail).\\
+  (5) The total gamma-ray flux from the supersymmetric $\Kp$ benchmark (BM)
+  model where the boost from substructures is included. See Sections II A 2 and II B 3.\\
+  (6) Gamma-ray flux induced by CR protons. See Section V C.
+ \label{tab:flux_tab}
+  \end{quote}
+\end{minipage}
+\end{table*}
 
@@
 
-In this paper, we study the possibility for detecting gamma-ray
-emission in galaxy clusters. We consider benchmark (BM) and
-leptophilic (LP) models of supersymmetric dark matter (DM) as well as
-cosmic ray (CR) induced pion decay which is thought to dominate the
-astrophysical signal from clusters.
-
-{\em Dark matter annihilation.} Once supersymmetric cold dark matter
-decouples from the expanding universe it streams and erases any
-potentially present smaller scales. When gravitational instability
-causes halos to collapse, this free-streaming scale imprints as a
-characteristic minimum halo mass $M_\mathrm{min}$ into the hierarchy
-of structure formation and should still survive until the present time
-as substructure within larger halos. We show that the boost due to
-substructures dominates over the smooth component for halo masses
-$\mvir>10^3 \msun$ and contributes a constant luminosity for each
-decade in halo mass. The ratio of halo-to-minimum subhalo mass
-$\mvir/M_\mathrm{min}$ is maximized for the largest virialized systems
-in the Universe---galaxy clusters. The corresponding substructure
-boost can reach values exceeding $10^3$ which should make nearby
+In this paper, we study the possibility for detecting gamma-ray emission in
+galaxy clusters. We consider benchmark (BM) and leptophilic (LP) models of
+supersymmetric dark matter (DM) as well as cosmic ray (CR) induced pion decay
+which is thought to dominate the astrophysical signal from clusters.
+
+{\em Dark matter annihilation.} Once supersymmetric cold DM decouples from the
+expanding universe it streams and erases any potentially present smaller
+scales. When gravitational instability causes halos to collapse, this
+free-streaming scale imprints as a characteristic minimum halo mass
+$M_\mathrm{min}$ into the hierarchy of structure formation and should still
+survive until the present time as a mass cutoff in the substructure mass
+function within larger halos. We show that the boost due to substructures
+dominates over the smooth component for halo masses $\mvir>10^3 \msun$ and
+contributes a constant luminosity for each decade in subhalo mass. The ratio of
+halo-to-minimum subhalo mass $\mvir/M_\mathrm{min}$ is maximized for the largest
+virialized systems in the Universe---galaxy clusters. The corresponding
+substructure boost can reach values exceeding $10^3$ which should make nearby
 clusters the brightest DM annihilation sources after the MW center and
-hypothetical very close-by DM substructures. We stress that this
-conclusion relies on two hypotheses that are still open problems in
-particle physics and numerical cosmology. We assume (i) the existence
-of cold DM, i.e., the density fluctuation power spectrum extends down
-to the DM free streaming scale of about an Earth mass, and (ii) assume
-that structure formation at scales smaller than currently resolved
-ones ($\sim 10^5\,\msun$) proceeds scale-invariant, i.e., there is no
-non-linear mode coupling between different scales. This could
-potentially erase structures smaller than a characteristic one as the
-linear power spectrum approaches $\Delta^2(k) \propto k^3
-P(k)=\rmn{const.}$ implying that structure on different scales may not
-form any more hierarchically, but may collapse at the same time.
-
-Since the mass density of substructures peaks at radii close to
-$\rvir$, the contribution to the annihilation emission from
-substructures is also dominated from these outer cluster regions.
-This implies an almost flat surface brightness profile of the
-annihilation emission which makes it necessary to have the entire
-cluster in the field-of-view to take advantage of the total
-substructure boost. This property makes it difficult to detect DM
-annihilation emission without an enhancement of the particle physics
-cross section over its standard value of $\sigma v\sim 3\times
-10^{-26} ~\mathrm{cm}^3~\mathrm{s}^{-1}$ with imaging air Cherenkov
-telescopes due to the spatially extended boost from substructures of
-angular extent $\sim 0.5-1\deg$ (as independently found by reference
-\cite{2011arXiv1104.3530S}). In contrast, the sensitivity of Cherenkov
-telescopes drops linearly with radius outside the point spread
-function $\sim 0.1\deg$, unless new background subtraction schemes can
-be found, e.g., for the survey mode of CTA.
-
-In this work, we thoroughly study the spectral emission
-characteristics of the DM emission. In general there are different
-radiation mechanism that emit in the gamma-ray regime, namely (i)
-continuum emission following the hadronization of the annihilating
-neutralinos in BM models which leads to the production of charged and
-neutral mesons which decay finally into electrons, neutrinos, and
-gammas, (ii) inverse Compton (IC) emission by the leptons in the final
-state which up-scatter radiation fields from the cosmic microwave
-background (CMB), dust, and starlight, and (iii) final state radiation
-or internal bremsstrahlung which dominates the highest energy emission
-close to the rest mass of the self-annihilating neutralinos (if
-present in the model under consideration).\footnote{While this final
-  state radiation is sometimes not distinguished from the continuum
-  emission contribution, we keep it separate as it dominates the very
-  high-energy tail of the gamma-ray spectrum in LP models while there
-  the continuum emission is negligibly low.}
-
-For the first time, we compute the IC emission component not only from
-the upscattered CMB photons but also from a realistically modeled
-photon field due to dust and starlight extending from infra-red to
-optical wavelengths. To this end, we construct a rather simple
-analytic model for the spatial and spectral distribution of dust and
-starlight in clusters (which can also be used for the annihilation
-emission in galaxies after adopting a different spatial profile). We
-find that in BM models, the continuum emission dominates over the IC
-emission of any available radiation field. In the LP models, where the
-continuum emission is low, the IC up-scattering of the CMB dominates
-below 60 GeV. For larger energies, the final state radiation dominates
-the emission up to the cutoff at $m_\chi c^2 \sim 1$~TeV. The IC
-up-scattering of the dust and starlight is always subdominant compared
-to the upscattered CMB (below 60~GeV) and the final state radiation
-(above 60~GeV). We stress, that the inclusion of the dust and
-starlight radiation fields are negligible in the cooling function for
-the leptons. The main reason why the IC emission from starlight and
-dust remains subdominant is the small overlap of this component with
-the peripherally peaked substructure mass density profiles. If for
-some reason, DM has less substructure, the relative importance of this
-IC component increases considerably.
-
-We identify Virgo, Fornax and M49 to be the best cluster/group
-candidates for indirect DM studies as they are expected to emit the
-brightest annihilation flux.\footnote{We excluded Virgo from our
-  further analysis due to its large angular extent that needs a
-  separate treatment.} More importantly, Fornax has a comparably low
-CR induced gamma-ray flux which may enable an indirect DM detection or
-a particularly tight limit on DM properties. Other nearby bright
-sources of the extended HIFLUGCS sample of nearby bright X-ray
-cluster/groups are Ophiuchus, and Centaurus.
+hypothetical very close-by DM substructures. We stress that this conclusion
+relies on two hypotheses that are still open problems in particle physics and
+numerical cosmology. We assume (i) the existence of cold DM, i.e., the density
+fluctuation power spectrum extends down to the DM free streaming scale of about
+an Earth mass, and (ii) assume that structure formation at scales smaller than
+currently resolved ones ($\sim 10^5\,\msun$) proceeds scale-invariant, i.e.,
+there is no non-linear mode coupling between different scales. This could
+potentially erase structures smaller than a characteristic one as the linear
+power spectrum approaches $\Delta^2(k) \propto k^3 P(k)=\rmn{const.}$ implying
+that structure on different scales may not form any more hierarchically, but may
+collapse at the same time.
+
+Since the mass density of substructures peaks at radii close to $\rvir$, the
+contribution to the annihilation emission from substructures is also dominated
+from these outer cluster regions.  This implies an almost flat surface
+brightness profile of the annihilation emission which makes it necessary to have
+the entire cluster in the field-of-view to take advantage of the total
+substructure boost. This property makes it difficult to detect DM annihilation
+emission without an enhancement of the particle physics cross section over its
+standard value of $\sigma v\sim 3\times 10^{-26} ~\mathrm{cm}^3~\mathrm{s}^{-1}$
+with imaging air Cherenkov telescopes due to the spatially extended boost from
+substructures over an angular extent of $\sim 0.5-1\deg$ (as independently found
+by reference \cite{2011arXiv1104.3530S}). This large angular extent is not well
+matched with the sensitivity of Cherenkov telescopes which drops approximately
+linearly with radius outside the point spread function (with a characteristic
+scale of $\sim 0.1\deg$), unless new background subtraction schemes can be
+found, e.g., for the survey mode of CTA.
+
+In this work, we thoroughly study the spectral emission characteristics of the
+DM emission. In general there are different radiation mechanism that emit in the
+gamma-ray regime, namely (i) continuum emission following the hadronization of
+the annihilating neutralinos in BM models which leads to the production of
+charged and neutral mesons which decay finally into electrons, neutrinos, and
+gammas, (ii) inverse Compton (IC) emission by the leptons in the final state
+which up-scatter radiation fields from the cosmic microwave background (CMB),
+dust, and starlight, and (iii) final state radiation or internal bremsstrahlung
+which dominates the highest energy emission close to the rest mass of the
+self-annihilating neutralinos (if present in the model under
+consideration).\footnote{While this final state radiation is sometimes not
+  distinguished from the continuum emission contribution, we keep it separate as
+  it dominates the very high-energy tail of the gamma-ray spectrum in LP models
+  while there the continuum emission is negligibly low.}
+
+For the first time, we compute the IC emission component not only from the
+upscattered CMB photons but also from a realistically modeled photon field due
+to dust and starlight extending from infra-red to optical wavelengths. To this
+end, we construct a rather simple analytic model for the spatial and spectral
+distribution of dust and starlight in clusters (which can also be used for the
+annihilation emission in galaxies after adopting a different spatial
+profile). We find that in BM models, the continuum emission dominates over the
+IC emission of any available radiation field. In the LP models, where the
+continuum emission is low, the IC up-scattering of the CMB dominates below 60
+GeV. For larger energies, the final state radiation dominates the emission up to
+the cutoff at $m_\chi c^2 \sim 1$~TeV. The IC up-scattering of the dust and
+starlight is always subdominant compared to the upscattered CMB (below 60~GeV)
+and the final state radiation (above 60~GeV). We stress, that the inclusion of
+the dust and starlight radiation fields are negligible in the cooling function
+for the leptons. The main reason why the IC emission from starlight and dust
+remains subdominant is the small overlap of this component with the peripherally
+peaked substructure mass density profiles. If for some reason, DM has less
+substructure, the relative importance of this IC component increases
+considerably.
+
+We identify Virgo, Fornax and M49 to be the best cluster/group candidates for
+indirect DM studies as they are expected to emit the brightest annihilation
+flux.\footnote{We excluded Virgo from our further analysis due to its large
+  angular extent that needs a separate treatment.} More importantly, Fornax has
+a comparably low CR-induced gamma-ray flux which may enable an indirect DM
+detection or a particularly tight limit on DM properties. Other nearby bright
+sources of the extended HIFLUGCS sample are Ophiuchus, and Centaurus.
 
 The non-detection of gamma-ray emission by \Fermi in a total of 28
-clusters/groups considerably constrains LP models for DM annihilation
-which were introduced to explain the increasing positron-to-lepton
-ratio beyond 10 GeV. Assuming that the minimum DM substructure mass
-extends down to an Earth mass and that the DM annihilation flux is
-dominated by small scale substructure, we limit the saturated
-Sommerfeld enhancement factor in M49 and Fornax to $\lesssim 5$. This
-corresponds to a value in the Milky Way (MW) of $\lesssim3$, due to
-the larger Sommerfeld boost factor in smaller mass halos which have a
-lower velocity dispersion that enhances the particle cross section
-(while assuming universality of the DM model). This would rule out LP
-models in their current form based on the non-observation of
-gamma-rays in any of the fore-mentioned
-clusters/groups. Alternatively, assuming the LP models to be correct,
-we limit the minimum substructure mass to $>10^4~\msun$ in M49 and
-Fornax.
-
-{\em Cosmic ray induced emission.} We substantially improve the
-modelling of the expected gamma-ray signal from pion-decay resulting
-from hadronic CR interactions with gas protons over previous work
-\cite{2010ApJ...717L..71A}. We employ the analytic model of the CR
-spectrum and spatial distribution that is based on cosmological
-hydrodynamical simulations of galaxy clusters that self-consistently
-follow the evolution of CRs in cosmic structure formation
-\cite{2010MNRAS.409..449P}. Adopting the model for all clusters in the
-HIFLUGCS sample of flux-limited X-ray clusters, we compare the
-expected gamma-ray emission to that inferred from using
-$L_\gamma$-cluster mass scaling relation. We note that the predictions
-of the ``optimistic'' model in \cite{2010MNRAS.409..449P} are in
-tension with \Fermi upper limits for Norma, Coma, and Ophiuchus. In
-the next 2-3 years \Fermi will be able to probe the predictions of
-their ``conservative'' CR model. This will enable to put realistic
-limits on a combination of the acceleration efficiency of CRs in
-structure formation shocks and CR transport coefficients in clusters.
-
-As expected, the analytical CR model accounts for the ``scatter'' to
-the scaling relation and biases the gamma-ray flux high for prominent
-cool core clusters by up to a factor of 10 relative to the expectation
-from the scaling relation. This is due to the high target gas
-densities and associated CR densities in those cool cores that shape
-the spatial emission characteristic to be very similar to that
-observed in thermal X-rays. We caution that these predictions only
-apply for the case of negligible active CR transport such as CR
-streaming and diffusion relative to the gas. Gamma-ray fluxes might be
-considerably smaller in those cluster that do not show an extended
-diffuse radio(-mini) halo that might point to a centrally concentrated
-CR distribution \cite{2011A&A...527A..99E}. The CR spectrum $E^2
-dN/dE$ shows the characteristic pion bump at energies around 1~GeV. It
-is expected to dominate the DM annihilation signal of BM models for
-clusters/groups, although we find that the gamma-ray flux induced by
-the BM is higher for about 1/5 of the clusters in the HIFLUGCS
-catalogue, where Fornax and M49 have the highest signal to noise. We
-find that \Fermi-LAT will be able to start constraining these DM
-models within five years using clusters of galaxies.
-
-Combining extended \Fermi upper limits and our model flux predictions,
-we limit the relative CR pressure, $X_\CR = P_\CR/P_\rmn{th}$, in 32
-nearby bright galaxy clusters of the \Fermi sample. The best limits
-are found in Norma and Coma of the order of 3\%, with typical limits
-around 10\%. This is comparable to those inferred by the \Fermi
-collaboration \cite{2010ApJ...717L..71A} and mainly due to the
-differently assumed Bayesian prior on the CR pressure which implies a
+clusters/groups considerably constrains LP models for DM annihilation which were
+introduced to explain the increasing positron-to-lepton ratio beyond 10
+GeV. Assuming that the minimum DM substructure mass extends down to an Earth
+mass and that the DM annihilation flux is dominated by small scale substructure,
+we limit the saturated Sommerfeld enhancement factor in M49 and Fornax to
+$\lesssim 5$. This corresponds to a value in the Milky Way (MW) of $\lesssim3$,
+due to the larger Sommerfeld boost factor in smaller mass halos which have a
+lower velocity dispersion that enhances the particle cross section (while
+assuming universality of the DM model). This would rule out LP models in their
+current form based on the non-observation of gamma-rays in any of the
+fore-mentioned clusters/groups and hence strongly challenge the DM
+interpretation of the increasing positron fraction with energy as seen by
+PAMELA. Alternatively, assuming the LP models to be correct, this would limit
+the minimum substructure mass to $>10^4~\msun$ in M49 and Fornax which presents
+a problem for structure formation in most particle physics models
+\cite{2009NJPh...11j5027B}.
+
+{\em Cosmic ray-induced emission.} We substantially improve the modelling of the
+expected gamma-ray signal from pion-decay resulting from hadronic CR
+interactions with gas protons over previous work \cite{2010ApJ...717L..71A}. We
+employ the analytic model of the CR spectrum and spatial distribution that is
+based on cosmological hydrodynamical simulations of galaxy clusters that
+self-consistently follow the evolution of CRs in cosmic structure formation
+\cite{2010MNRAS.409..449P}. Adopting the model for all clusters in the HIFLUGCS
+sample of flux-limited X-ray clusters, we compare the expected gamma-ray
+emission to that inferred from using an $L_\gamma-\mvir$ scaling relation. We note
+that the predictions of the ``optimistic'' model in \cite{2010MNRAS.409..449P}
+are in tension with \Fermi upper limits for Norma, Coma, and Ophiuchus. In the
+next 2-3 years \Fermi will be able to probe the predictions of their
+``conservative'' CR model. This will enable us to put realistic limits on a
+combination of the acceleration efficiency of CRs in structure formation shocks
+and CR transport coefficients in clusters.
+
+As expected, the analytical CR model accounts for the ``scatter'' in the scaling
+relation and biases the gamma-ray flux high for prominent cool core clusters by
+up to a factor of 10 relative to the expectation from the scaling relation. This
+is due to the high target gas densities and associated CR densities in those
+cool cores that shape the spatial emission characteristic to be very similar to
+that observed in thermal X-rays. We caution that these predictions only apply
+for the case of negligible active CR transport such as CR streaming and
+diffusion relative to the gas. Gamma-ray fluxes might be considerably smaller in
+those cluster that do not show an extended diffuse radio(-mini) halo that might
+point to a centrally concentrated CR distribution
+\cite{2011A&A...527A..99E}. The CR spectrum $E^2 dN/dE$ shows the characteristic
+pion bump at energies around 1~GeV. It is expected to dominate the DM
+annihilation signal of BM models for clusters/groups, although we find that the
+gamma-ray flux induced by the BM is higher for about 1/5 of the clusters in the
+HIFLUGCS catalogue, where Fornax and M49 have the highest signal-to-noise
+ratio. (Note that we only include the cluster-intrinsic CR foreground and do not
+consider the dominant galactic and instrumental noise sources here.) We find that
+\Fermi-LAT will be able to start constraining these DM models within five years
+using clusters of galaxies.
+
+Combining extended \Fermi upper limits and our model flux predictions, we limit
+the relative CR pressure, $X_\CR = P_\CR/P_\rmn{th}$, in 32 nearby bright galaxy
+clusters of the \Fermi sample. The best limits are found in Norma and Coma of
+the order of 3\%, with typical limits around 10\%. This is comparable to those
+inferred by the \Fermi collaboration \cite{2010ApJ...717L..71A} and mainly due
+to the differently assumed Bayesian prior on the CR pressure which implies a
 different cluster mass dependence of the resulting limits on $X_\CR$.
 
-We conclude that due to the large spatial extension of the brightest
-clusters it is not possible for \Fermi to rule out the LP model or to
-constrain the BM DM models without improved modelling. However, we can
-put tight constraints on the boost from substructures and Sommerfeld
-enhancement using the LP model. Hence, clusters are a valuable
-complement to direct and accelerator searches for the nature of DM.
+% We conclude that due to the large spatial extension of the brightest
+% clusters it is not possible for \Fermi to rule out the LP model or to
+% constrain the BM DM models without improved modelling. However, we can
+% put tight constraints on the boost from substructures and Sommerfeld
+% enhancement using the LP model. Hence, clusters are a valuable
+% complement to direct and accelerator searches for the nature of DM.
 

### 2011-10-12 paper.tex
small changes
updated figures+paper+bib

@@
 \newcommand{\vst}{\vspace{-0.14mm}}
+\newcommand{\vstt}{\vspace{-0.0mm}}
 \newcommand{\el}{\rmn{el}}
+\newcommand{\mytimes}{\hspace{-0.5mm}\times\hspace{-0.5mm}}
+\newcommand{\hst}{\hspace{-1.0mm}}
 
@@
 \begin{abstract}
-  We study the possibility for detecting gamma-ray emission from galaxy
-  clusters. We consider 1) leptophilic models of dark matter (DM) annihilation
-  that include a Sommerfeld enhancement (SFE), 2) different representative
-  benchmark models of supersymmetric DM, and 3) cosmic ray (CR) induced pion
-  decay. To model DM annihilation, we consider continuum emission as a result of
-  the hadronization of annihilating neutralinos, internal bremsstrahlung, and
-  inverse Compton emission from the cosmic microwave background as well as from
-  a realistic spatial and spectral distribution of dust and stellar light. Among
-  all clusters/groups of a flux-limited X-ray sample, we predict Virgo, Fornax
-  and M49 to be the brightest DM sources and find a particularly low CR-induced
-  background for Fornax. For a minimum substructure mass given by the DM
-  free-streaming scale, cluster halos maximize the substructure boost for which
-  we find a factor of $\gtrsim 1000$. Since regions around the virial radius
-  dominate the annihilation flux of substructures, the resulting surface
-  brightness profiles are almost flat. This makes it very challenging to detect
-  this flux with imaging atmospheric Cherenkov telescopes since their
-  sensitivity drops approximately linearly with radius and they typically have
-  $5-10$ linear resolution elements across a cluster. Assuming cold dark matter
-  with a substructure mass distribution down to an Earth mass and using extended
-  \Fermi upper limits, we rule out the leptophilic models in their present form
-  in 28 clusters, and limit the boost from SFE in M49 and Fornax to be $\lesssim
-  5$. This corresponds to a limit on SFE in the Milky Way of $\lesssim 3$ which
-  is too small to account for the increasing positron fraction with energy as
-  seen by PAMELA. Alternatively, if SFE is realized in Nature, this would imply
-  a limiting substructure mass of $\mlim > 10^4\,\msun$---a problem for
-  structure formation in most particle physics models. Using individual cluster
-  observations, it will be challenging for \Fermi to constrain our selection of
-  DM benchmark models without SFE. The \Fermi upper limits are, however, closing
-  in on our predictions for the CR flux using an analytic model based on
-  cosmological hydrodynamical cluster simulations. We limit the CR-to-thermal
-  pressure in nearby bright galaxy clusters of the \Fermi sample to $\lesssim
-  10\%$ and in Norma and Coma to $\lesssim 3\%$. Thus we will soon start to
-  constrain the underlying CR physics such as shock acceleration efficiencies or
-  CR transport properties.
+  \C{We study the possibility for detecting gamma-ray emission from
+  galaxy clusters. We consider 1) leptophilic models of dark matter
+  (DM) annihilation that include a Sommerfeld enhancement (SFE), 2)
+  different representative benchmark models of supersymmetric DM, and
+  3) cosmic ray (CR) induced pion decay. To model DM annihilation, we
+  consider continuum emission as a result of the hadronization of
+  annihilating neutralinos, internal bremsstrahlung, and inverse
+  Compton emission from the cosmic microwave background as well as
+  from a realistic spatial and spectral distribution of dust and
+  stellar light. Among all clusters/groups of a flux-limited X-ray
+  sample, we predict Virgo, Fornax and M49 to be the brightest DM
+  sources and find a particularly low CR-induced background for
+  Fornax. For a minimum substructure mass given by the DM
+  free-streaming scale, cluster halos maximize the substructure boost
+  for which we find a factor of $\gtrsim 1000$. Since regions around
+  the virial radius dominate the annihilation flux of substructures,
+  the resulting surface brightness profiles are almost flat. This
+  makes it very challenging to detect this flux with imaging
+  atmospheric Cherenkov telescopes since their sensitivity drops
+  approximately linearly with radius and they typically have $5-10$
+  linear resolution elements across a cluster. Assuming cold dark
+  matter with a substructure mass distribution down to an Earth mass
+  and using extended \Fermi upper limits, we rule out the leptophilic
+  models in their present form in 28 clusters, and limit the boost
+  from SFE in M49 and Fornax to be $\lesssim 5$. This corresponds to a
+  limit on SFE in the Milky Way of $\lesssim 3$ which is too small to
+  account for the increasing positron fraction with energy as seen by
+  PAMELA. Alternatively, if SFE is realized in Nature, this would
+  imply a limiting substructure mass of $\mlim > 10^4\,\msun$---a
+  problem for structure formation in most particle physics
+  models. Using individual cluster observations, it will be
+  challenging for \Fermi to constrain our selection of DM benchmark
+  models without SFE. The \Fermi upper limits are, however, closing in
+  on our predictions for the CR flux using an analytic model based on
+  cosmological hydrodynamical cluster simulations. We limit the
+  CR-to-thermal pressure in nearby bright galaxy clusters of the
+  \Fermi sample to $\lesssim 10\%$ and in Norma and Coma to $\lesssim
+  3\%$. Thus we will soon start to constrain the underlying CR physics
+  such as shock acceleration efficiencies or CR transport properties.}
 \end{abstract}
@@
 
-Dark matter (DM) has been searched for in direct detection experiments
-\cite{Pato:2010zk}, at accelerators
+\C{Dark matter (DM) has been searched for in direct detection
+  experiments \cite{Pato:2010zk}, at accelerators
   \cite{Ellis:2001hv,Baer:2006ff,Khachatryan:2011tk} and also in
@@
   electromagnetic spectrum from radio waves to gamma-rays
-\cite{Bergstrom:2009ib}. So far, the improvements in direct detection
-sensitivity have put this method into focus, but the situation may
-change considerably the coming few years as the CERN LHC experiments
-collect data, and new gamma-ray detectors are being planned, such as
-the CTA \cite{Consortium:2010bc}. In fact, it has recently been
-pointed out \cite{Bergstrom:2010gh} that a dedicated ground-based
-gamma-ray detector would have potential that goes far beyond that of
-the other methods, depending on presently unknown parameters in the
-particle physics models for DM.
-
-Among the astrophysical systems which will be very interesting to detect, and
-study, with gamma-ray detectors (\Fermi, H.E.S.S., MAGIC, VERITAS, and
-eventually large detectors like CTA)\footnote{{High Energy Stereoscopic System,
-    Major Atmospheric Gamma Imaging Cerenkov Telescope, Very Energetic Radiation
-    Imaging Telescope Array System, Cerenkov Telescope Array.}} belong galaxy
-clusters. The most promising directions in which to search for a gamma-ray
-annihilation signal (from the annihilation process itself, and also the
-accompanying bremsstrahlung and inverse Compton (IC) components coming from
-charged particles produced in the annihilations) are basically three:
-
-1. The galactic center (g.c.). This is where all numerical simulations of cold
-dark matter (CDM) predict the highest density. However, the detailed DM density
-in the very central part is difficult to predict, due a to a possibly very
-complicated interplay between baryons, DM, and the central galactic black
-hole. Also, it is a very crowded region with many gamma-ray sources like
-pulsars, CR-illuminated molecular clouds, and other supernova remnants, which
-have to be subtracted from the data to extract the DM induced signal. In fact,
-there is a recent claim of an indication of a relatively light DM particle
-contribution to the gamma-ray flux from the g.c. \cite{2010arXiv1010.2752H}, but
-other hypotheses seem to work at least as well \cite{2010arXiv1012.5839B}.
-
-2. The dwarf spheroidal galaxies orbiting the Milky Way (MW), like Segue-1, Ursa
-Minor, Draco, Sagittarius, Sculptor, Carina or Willman-1
+  \cite{Bergstrom:2009ib}. So far, the improvements in direct
+  detection sensitivity have put this method into focus, but the
+  situation may change considerably the coming few years as the CERN
+  LHC experiments collect data, and new gamma-ray detectors are being
+  planned, such as the CTA \cite{Consortium:2010bc}. In fact, it has
+  recently been pointed out \cite{Bergstrom:2010gh} that a dedicated
+  ground-based gamma-ray detector would have potential that goes far
+  beyond that of the other methods, depending on presently unknown
+  parameters in the particle physics models for DM.}
+
+\C{Among the astrophysical systems which will be very interesting to
+  detect, and study, with gamma-ray detectors (\Fermi, H.E.S.S.,
+  MAGIC, VERITAS, and eventually large detectors like
+  CTA)\footnote{{High Energy Stereoscopic System, Major Atmospheric
+      Gamma Imaging Cerenkov Telescope, Very Energetic Radiation
+      Imaging Telescope Array System, Cerenkov Telescope Array.}}
+  belong galaxy clusters. The most promising directions in which to
+  search for a gamma-ray annihilation signal (from the annihilation
+  process itself, and also the accompanying bremsstrahlung and inverse
+  Compton (IC) components coming from charged particles produced in
+  the annihilations) are basically three:}
+
+\C{1. The galactic center (g.c.). This is where all numerical
+  simulations of cold dark matter (CDM) predict the highest
+  density. However, the detailed DM density in the very central part
+  is difficult to predict, due a to a possibly very complicated
+  interplay between baryons, DM, and the central galactic black
+  hole. Also, it is a very crowded region with many gamma-ray sources
+  like pulsars, CR-illuminated molecular clouds, and other supernova
+  remnants, which have to be subtracted from the data to extract the
+  DM induced signal. In fact, there is a recent claim of an indication
+  of a relatively light DM particle contribution to the gamma-ray flux
+  from the g.c. \cite{2011PhLB..697..412H}, but other hypotheses seem
+  to work at least as well \cite{2010arXiv1012.5839B}.}
+
+\C{2. The dwarf spheroidal galaxies orbiting the Milky Way (MW), like
+  Segue-1, Ursa Minor, Draco, Sagittarius, Sculptor, Carina or
+  Willman-1
   \cite{2009JCAP...01..016B,2010ApJ...720.1174A,2010JCAP...01..031S,2010JCAP...01..031S,2011arXiv1103.0477T,2011APh....34..608H}. The
-problem here is that the nature of many of these small, dark matter-dominated
-galaxies is not entirely clear, and the velocity dispersion estimates are based
-on rather small numbers of stars.  Confusion with star clusters and tidal
-disruption are other complications. Once a satellite dwarf galaxy is accreted by
-the MW, the outer regions are severely affected by tidal stripping. The longer a
-satellite has been part of our Galaxy, and the closer it comes to the center
-during its pericentral passage, the more material is removed
-\cite{2004MNRAS.355..819G}.  Thus the DM density profile is very uncertain for
-most of them, especially for radii larger than those probed by the
-stars. Nonetheless, by stacking the data together from many dwarf spheroidals
-these uncertainties can be made less severe, and preliminary results from
-\Fermi-LAT shows this method to give quite promising results \cite{garde}.
-
-%For a satellite dwarf galaxy, however, once it is accreted by the MW,
-%the outer regions are severely affected by tidal stripping. The longer
-%a satellite has been part of our Galaxy, and the closer it comes to
-%the center during its pericentral passage, the more material is
-%removed \cite{2004MNRAS.355..819G}.
-
-3. Galaxy clusters. This possibility has been less studied
+  problem here is that the nature of many of these small, dark
+  matter-dominated galaxies is not entirely clear, and the velocity
+  dispersion estimates are based on rather small numbers of stars.
+  Confusion with star clusters and tidal disruption are other
+  complications. Once a satellite dwarf galaxy is accreted by the MW,
+  the outer regions are severely affected by tidal stripping. The
+  longer a satellite has been part of our Galaxy, and the closer it
+  comes to the center during its pericentral passage, the more
+  material is removed \cite{2004MNRAS.355..819G}.  Thus the DM density
+  profile is very uncertain for most of them, especially for radii
+  larger than those probed by the stars. Nonetheless, by stacking the
+  data together from many dwarf spheroidals these uncertainties can be
+  made less severe, and preliminary results from \Fermi-LAT shows this
+  method to give quite promising results \cite{garde}.}
+
+\C{3. Galaxy clusters. This possibility has been less studied
   theoretically, however currently there is an ongoing observational
   campaign to detect gamma-ray emission from galaxy clusters
-\cite{2003ApJ...588..155R,2006ApJ...644..148P,2008AIPC.1085..569P,2009A&A...495...27A,2009arXiv0907.0727T,2009arXiv0907.5000G,2009IJMPD..18.1627D,2009A&A...495...27A,2009A&A...502..437A,2009ApJ...704..240K,2009ApJ...706L.275A,2010ApJ...710..634A,2010JCAP...05..025A,2010ApJ...717L..71A}.
-In fact, we noted in a previous Letter \cite{2009PhRvL.103r1302P} that
-there are certain advantages that work in favour of this possible
-target for gamma-ray detection of DM annihilation. Galaxy clusters
-constitute the most massive objects in our Universe that are forming
-today. This causes their DM subhalo mass function to be less affected
-by tidal stripping compared to galaxy sized halos that formed long
-ago. The annihilation luminosities of the DM halo component for
-e.g. the Virgo cluster and the Draco dwarf scales in a way (see
-\cite{2009PhRvL.103r1302P}) that the ratio of gamma-ray luminosities
-from the smooth components is around 4, in favour of Virgo. In
-addition, there may be a further enhancement due to substructure,
-which to a large extent should be unaffected by tidal disruption, at
-least in the outer regions. According to a recent estimate
-\cite{2011MNRAS.410.2309G}, more massive haloes tend to have a larger
-mass fraction in subhalos. For example, cluster size haloes typically
-have 7.5 per cent of the mass within $r_{200}$ in substructures of
-fractional mass larger than $10^{-5}$, which is 25 per cent higher
-than for galactic haloes.\footnote{All halo masses and length scales
-  in this paper are scaled to the currently favored value of Hubble's
-  constant, $H_0 = 70\, \rmn{km~s}^{-1}\,\rmn{Mpc}^{-1}$. We define
-  the virial mass $\mvir$ and virial radius $\rvir$ as the mass and
-  radius of a sphere enclosing a mean density that is 200 times the
-  critical density of the Universe $\rho_{\rmn{cr}}$.}
-
-In this paper, we will investigate in detail the potential of several
-of the most promising galaxy clusters to produce an annihilation
-gamma-ray yield which could be observable with present and planned
-gamma-ray detectors. Here, we sketch out the main arguments that need
-to be considered for maximizing the expected signal-to-noise ratio of
-a promising target cluster. First, we need to maximize the DM
-annihilation flux of an unresolved cluster, $F=A_\rmn{dm} \int dV
-\rho^2 / D^2 \sim \mvir^\alpha/D^2$, where $A_\rmn{dm}$ depends on the
-particle physics model of DM, $\rho$ is the smooth DM density profile,
-$D$ is the luminosity distance, and $\alpha=1$ if we assume
-universality of the DM density profile. The dependence of $\rho$ on
-the halo formation epoch breaks the universality and slightly modifies
-the mass dependence, yielding $\alpha=0.83$
-\cite{2009PhRvL.103r1302P}. Additionally, the presence of a hierarchy
-of substructures down to small scales \cite{2008Natur.456...73S} and
-the potential dependence of the particle physics cross section on the
-relative DM particle velocities \cite{ArkaniHamed:2008qn} may
-furthermore modify the scaling parameter $\alpha$ and shall be one of
-the focus points of this work. Second, we need to minimize the
-expected noise which is a sum of galactic and cluster-intrinsic
-foreground. While the galactic foreground varies across the sky, it is
-typically lower for increasing latitude (away from the galactic
-plane). It is thought that the gamma-ray foreground from clusters is
-dominated by CRs which are accelerated at cosmological formation
-shocks and transported over time although there could be a substantial
-contribution of CRs from AGNs and supernova-driven galactic winds. In
-this work we will also study (and constrain) the CR-induced emission
-from clusters to identify those objects that are expected to be
-especially dim which would imply a low CR-induced background.  Since
-the CR-induced emission is expected to scale with the thermal X-ray
-emission of clusters \cite{2004A&A...413...17P}, we estimate gamma-ray
-fluxes of a nearby X-ray flux complete sample of galaxy clusters from
-the Rosat all-sky survey (extended HIghest X-ray FLUx Galaxy Cluster
-Sample, HIFLUGCS,
-\cite{2002ApJ...567..716R,2007A&A...466..805C}).\footnote{Note that we
-  have added the Virgo cluster to the sample that we nevertheless
+  \cite{2003ApJ...588..155R,2006ApJ...644..148P,2008AIPC.1085..569P,2009A&A...495...27A,2009arXiv0907.5000G,2009IJMPD..18.1627D,2009A&A...495...27A,2009A&A...502..437A,2009ApJ...704..240K,2009ApJ...706L.275A,2010ApJ...710..634A,2010JCAP...05..025A,2010ApJ...717L..71A}.
+  In fact, we noted in a previous Letter \cite{2009PhRvL.103r1302P}
+  that there are certain advantages that work in favour of this
+  possible target for gamma-ray detection of DM annihilation. Galaxy
+  clusters constitute the most massive objects in our Universe that
+  are forming today. This causes their DM subhalo mass function to be
+  less affected by tidal stripping compared to galaxy sized halos that
+  formed long ago. The annihilation luminosities of the DM halo
+  component for e.g. the Virgo cluster and the Draco dwarf scales in a
+  way (see \cite{2009PhRvL.103r1302P}) that the ratio of gamma-ray
+  luminosities from the smooth components is around 4, in favour of
+  Virgo. In addition, there may be a further enhancement due to
+  substructure, which to a large extent should be unaffected by tidal
+  disruption, at least in the outer regions. According to a recent
+  estimate \cite{2011MNRAS.410.2309G}, more massive haloes tend to
+  have a larger mass fraction in subhalos. For example, cluster size
+  haloes typically have 7.5 per cent of the mass within $r_{200}$ in
+  substructures of fractional mass larger than $10^{-5}$, which is 25
+  per cent higher than for galactic haloes.\footnote{All halo masses
+    and length scales in this paper are scaled to the currently
+    favored value of Hubble's constant, $H_0 = 70\,
+    \rmn{km~s}^{-1}\,\rmn{Mpc}^{-1}$. We define the virial mass
+    $\mvir$ and virial radius $\rvir$ as the mass and radius of a
+    sphere enclosing a mean density that is 200 times the critical
+    density of the Universe $\rho_{\rmn{cr}}$.}}
+
+\C{In this paper, we will investigate in detail the potential of
+  several of the most promising galaxy clusters to produce an
+  annihilation gamma-ray yield which could be observable with present
+  and planned gamma-ray detectors. Here, we sketch out the main
+  arguments that need to be considered for maximizing the expected
+  signal-to-noise ratio of a promising target cluster. First, we need
+  to maximize the DM annihilation flux of an unresolved cluster,
+  $F=A_\rmn{dm} \int dV \rho^2 / D^2 \sim \mvir^\alpha/D^2$, where
+  $A_\rmn{dm}$ depends on the particle physics model of DM, $\rho$ is
+  the smooth DM density profile, $D$ is the luminosity distance, and
+  $\alpha=1$ if we assume universality of the DM density profile. The
+  dependence of $\rho$ on the halo formation epoch breaks the
+  universality and slightly modifies the mass dependence, yielding
+  $\alpha=0.83$ \cite{2009PhRvL.103r1302P}. Additionally, the presence
+  of a hierarchy of substructures down to small scales
+  \cite{2008Natur.456...73S} and the potential dependence of the
+  particle physics cross section on the relative DM particle
+  velocities \cite{ArkaniHamed:2008qn} may furthermore modify the
+  scaling parameter $\alpha$ and shall be one of the focus points of
+  this work. Second, we need to minimize the expected noise which is a
+  sum of galactic and cluster-intrinsic foreground. While the galactic
+  foreground varies across the sky, it is typically lower for
+  increasing latitude (away from the galactic plane). It is thought
+  that the gamma-ray foreground from clusters is dominated by CRs
+  which are accelerated at cosmological formation shocks and
+  transported over time although there could be a substantial
+  contribution of CRs from AGNs and supernova-driven galactic
+  winds. In this work we will also study (and constrain) the
+  CR-induced emission from clusters to identify those objects that are
+  expected to be especially dim which would imply a low CR-induced
+  background.  Since the CR-induced emission is expected to scale with
+  the thermal X-ray emission of clusters \cite{2004A&A...413...17P},
+  we estimate gamma-ray fluxes of a nearby X-ray flux complete sample
+  of galaxy clusters from the Rosat all-sky survey (extended HIghest
+  X-ray FLUx Galaxy Cluster Sample, HIFLUGCS,
+  \cite{2002ApJ...567..716R,2007A&A...466..805C}).\footnote{Note that
+    we have added the Virgo cluster to the sample that we nevertheless
     refer to as extended HIFLUGCS catalogue in the following.}  This
   complements and extends previous work related to DM in clusters
-\cite{2006A&A...455...21C,2009PhRvD..80b3005J,2011arXiv1104.3530S,2011ApJ...726L...6C}
+  \cite{2006A&A...455...21C,2009PhRvD..80b3005J,2011arXiv1104.3530S,2011ApJ...726L...6C,2011arXiv1110.1529H}
   and to CRs in clusters
-\cite{2010MNRAS.409..449P,2011MNRAS.410..127B,2008MNRAS.385.1211P,2009JCAP...08..002K,2010MNRAS.407.1565D}.
-
-In Section 2 we discuss the theory of DM and gamma-rays. In
+  \cite{2010MNRAS.409..449P,2011MNRAS.410..127B,2008MNRAS.385.1211P,2009JCAP...08..002K,2010MNRAS.407.1565D}.}
+
+\C{In Section 2 we discuss the theory of DM and gamma-rays. In
 particular, we focus on the leptophilic (LP) and supersymmetric
@@
 HIFLUGCS sample in Section 5. In Section 6 we conclude and discuss our
-results.
-
-% In this paper, we will investigate in some more detail the potential
-% of several of the most promising galaxy clusters to produce an
-% annihilation gamma-ray yield which could be observable with present
-% and planned gamma-ray detectors. For convenience, we summarize in
-% Table~\ref{tab:flux_tab} our results for the gamma-ray flux from four
-% promising clusters with a high gamma-ray yield. We will in the
-% following derive the emission from two different DM models and a
-% hadronic CR model to show that Virgo has the highest gamma-ray flux
-% from annihilating DM. However, if the boost from Sommerfeld
-% enhancement (SFE) is small then the gamma-ray emission induced by CRs
-% is dominating most clusters with the exception of a few clusters; most
-% notably Fornax that shows the largest ratio of DM annihilation-to-CR
-% flux. In particular, we identify Fornax and Virgo as prime targets for
-% DM observations, Perseus for CR induced emission and we additionally
-% decide in favor of the well studied cluster Coma for comparison. While
-% studying these four clusters in great detail, we complement the
-% analysis by calculating the expected gamma-ray fluxes of a nearby
-% X-ray flux complete sample of galaxy clusters from the Rosat all-sky
-% survey (extended HIghest X-ray FLUx Galaxy Cluster Sample, HIFLUGCS,
-% \cite{2002ApJ...567..716R,2007A&A...466..805C}).\footnote{Note that
-%   we have added the Virgo cluster to the sample that we nevertheless
-%   refer to as extended HIFLUGCS catalogue in the following.} For
-% previous work related to DM in clusters, see, e.g.,
-% \cite{2006A&A...455...21C,2009PhRvD..80b3005J,2011arXiv1104.3530S,2011ApJ...726L...6C,2010JCAP...05..025A}
-% and for recent work on CRs in clusters see
-% \cite{2010MNRAS.409..449P,2011MNRAS.410..127B,2008MNRAS.385.1211P,2009JCAP...08..002K,2010MNRAS.407.1565D}.
+results.}
 
@@
 the two other methods available for the DM search, namely direct and
-indirect detection. Direct detection methods, which are presently
-evolving rapidly use the feeble interaction between DM particles of
-the galactic halo and nuclei such as Germanium, Sodium, Iodine, Argon
-or Xenon to infer the scattering cross section and a rough estimate of
-the mass of the DM particle (for the currently most sensitive search,
-see \cite{Aprile:2010um,Aprile:2011hi}). A characteristic of this
-method is that it basically only depends on the local DM density
-(which is rather well determined to be around $0.4$ GeV/cm$^3$) and
-the basic cross section for DM - nucleus scattering. A disadvantage is
-that it does not benefit from the two enhancement mechanisms mentioned
-above, boost from substructure and/or the Sommerfeld effect. Also, it
-cannot be excluded - although it seems at present improbable - that
-the local halo structure is such that the solar system happens to be
-in an underdense region.
-
-In indirect detection, on the other hand, in particular in the photon
-channel, one searches for products of DM annihilation in the galactic
-halo and beyond. Particularly interesting targets are the galactic
-center (for a recent possible indication of a signal, see
-\cite{2010arXiv1010.2752H}, however, see also
+indirect detection. \C{Second,} direct detection methods, which are
+presently evolving rapidly, use the feeble interaction between DM
+particles of the galactic halo and nuclei such as Germanium, Sodium,
+Iodine, Argon or Xenon to infer the scattering cross section and a
+rough estimate of the mass of the DM particle (for the currently most
+sensitive search, see \cite{Aprile:2010um,Aprile:2011hi}). A
+characteristic of this method is that it basically only depends on the
+local DM density (which is rather well determined to be around $0.4$
+GeV/cm$^3$) and the basic cross section for DM - nucleus scattering. A
+disadvantage is that it does not benefit from the two enhancement
+mechanisms mentioned above, boost from substructure and/or the
+Sommerfeld effect. Also, it cannot be excluded - although it seems at
+present improbable - that the local halo structure is such that the
+solar system happens to be in an underdense region.
+
+\C{Third}, in indirect detection, \del{on the other hand,} in
+particular in the photon channel, one searches for products of DM
+annihilation in the galactic halo and beyond. Particularly interesting
+targets are the galactic center (for a recent possible indication of a
+signal, see \cite{2011PhLB..697..412H}, however, see also
 \cite{2010arXiv1012.5839B}), the dwarf galaxies surrounding the MW
@@
 
-There is also a possibility to search for DM annihilation indirectly
-in antimatter channels, like antiprotons or positrons. Here diffusion
-is, however, very efficient which means that the directional signature
-which is so important for gamma-rays, is completely erased. This
-method has, however, recently been much in focus due to the surprising
-rise with energy of the positron-to-total lepton ratio measured by the
-PAMELA satellite experiment \cite{Adriani:2008zr} and the ``bump'' in
-the total electron plus positron spectrum detected by \Fermi
-\cite{Abdo:2009zk}. The viable particle physics models describing
-these results contain some non-trivial, or even unnatural elements,
-however. First of all, annihilation to quarks has to be very much
-suppressed, due to the non-observation of an enhanced antiproton flux
-by PAMELA \cite{Adriani:2010rc}. This means that only so-called {\em
-  leptophilic} models, where the annihilation only goes to leptons
-have to be considered. Here, one has to have a sizeable fraction going
-to muons and tau leptons, as the shape of the spectrum disfavors
-direct annihilation into electrons and positrons. To get agreement
-with the measured absolute rates, one also has to have a large boost
-factor (of the order of at least several hundred), which is difficult
-to achieve with substructure alone. An additional enhancement of the
-annihilation rate has to be invoked, for example given by the {\em
-  Sommerfeld effect}. This basically means that the usual connection
-between annihilation rate at decoupling (when velocities $v$ relative
-to the speed of light were of order $0.2 - 0.3$), which gives the
-relic density, and present-day annihilation in the halo (with relative
-velocities $v\sim 10^{-3}$) is broken. This would come about because
-the DM sector contains additional light particles which mediates an
-interaction with almost bound states which enhance the wave function
-at the relative origin, and therefore the annihilation rate (for a
-pedagogical review of viable scenarios, see
-\cite{ArkaniHamed:2008qn}). As a final difficulty of these models, the
-lack of an IC signature from the galactic center means that only
-shallow density profiles can describe the galactic DM density
-distribution
+\subsubsection{Leptophilic models}
+\label{sect:LP}
+\C{There is also a possibility to search for DM annihilation in the Milky
+Way indirectly through annihilation to antimatter channels, which
+however lacks the important directional signature of
+gamma-rays. Recently, it has however been much in focus due to the
+surprising findings of PAMELA \cite{Adriani:2008zr} and \Fermi
+\cite{Abdo:2009zk}. Viable particle physics models are rather
+constrained by other observations, however. For example, the
+non-observation of an enhanced antiproton flux by PAMELA
+\cite{Adriani:2010rc} means that quark-antiquark final states have to
+be suppressed. This has led to the postulate of a whole class of
+{\em leptophilic} models with mainly or exclusively annihilation to
+leptons and antileptons. In addition, one has to have a sizeable
+fraction to final states containing muons or tau leptons as the shape
+of the spectrum disfavors direct annihilation to electrons and
+positrons only. A large enhancement, of the order of at least several
+hundred, of the annihilation rate is also needed, something that may
+be given by the {\em Sommerfeld effect} (for a pedagogical review of
+viable scenarios, see \cite{ArkaniHamed:2008qn}). As still another
+difficulty for these models, the lack of an IC signature from the
+Galactic center means that the DM density distribution must be cored
+rather than cuspy
 \cite{Bertone:2008xr,Cirelli:2008pk,Bergstrom:2008ag}. (For a review
-of the DM modelling of these effects, see \cite{Bergstrom:2009ib}. For
+of the DM modeling of these effects, see \cite{Bergstrom:2009ib}. For
 a recent treatment, showing still viable models, see
-\cite{Finkbeiner:2010sm}.)
-
-A more standard explanation of the PAMELA/\Fermi excess would be
+\cite{Finkbeiner:2010sm}.)}
+
+\C{A more standard explanation of the PAMELA/\Fermi excess would be
 pulsars or other supernova remnants (e.g.,
 \cite{1995PhRvD..52.3265A,Hooper:2008kg,Ahlers:2009ae}). In that case,
-DM would more likely be explained by the conventional scenario of a WIMP,
-for example the thoroughly studied lightest supersymmetric neutralino
-(for reviews, see
+DM would more likely be explained by the conventional scenario of a
+WIMP, for example the thoroughly studied lightest supersymmetric
+neutralino (for reviews, see
 \cite{Jungman:1995df,Bergstrom:2000pn,Bertone:2004pz}). We note that
-the soon to be launched AMS-02 experiment on the International Space
-Station \cite{ams02} may give interesting clues to the origin of the
-antimatter excess.
-
-\subsubsection{Leptophilic models}
-\label{sect:LP}
-The results of PAMELA \cite{Adriani:2008zr} and \Fermi-LAT
-\cite{Abdo:2009zk} (and to some extent ATIC
-\cite{2008Natur.456..362C}, although the bump seen there at 600 GeV
-has not been reproduced by other experiments) caused intense
-activity in the theoretical DM community. At first, there was
-scepticism whether such a large signal could be compatible with a
-WIMP. However, the possibility of an enhanced annihilation rate due to
-DM halo substructure has been realized for a long time
-\cite{1993ApJ...411..439S,Bergstrom:1998zs,Moore:1999nt}, although it
-is difficult to achieve the boost factor of the order of a few hundred
-to a thousand in the solar neighborhood, as substructure according to
-numerical simulations is most important in the outer portions of the
-halo, due to tidal stripping of subhalos in the inner part. Another
-potentially very important effect which may explain the large boost
-had been found a few years earlier, namely the Sommerfeld enhancement
-(SFE). This effect, was computed for electromagnetism by Arnold
+AMS-02 experiment on the International Space Station \cite{ams02} may give
+interesting clues to the origin of the antimatter excess.}
+
+\C{In the scenario with leptophilic DM, one has to rely on some
+enhancement of the annihilation rate from the effects of DM halo
+substructure, a possibility which was realized long ago
+\cite{1993ApJ...411..439S,Bergstrom:1998zs,Moore:1999nt}. However, a
+boost factor as large as several hundred is difficult to achieve in
+the solar neighborhood, due to tidal stripping of subhalos in the
+inner part of the Galaxy. Sommerfeld enhancement is thus important for
+leptophilic models that claim to explain the PAMELA/\Fermi
+result. This effect was computed for electromagnetism by Arnold
 Sommerfeld many years ago \cite{sommerfeld} and recently rediscovered
 in the quantum field theory of DM
-\cite{2005PhRvD..71f3528H,2007NuPhB.787..152C,2009PhRvD..79a5014A}.
+\cite{2005PhRvD..71f3528H,2007NuPhB.787..152C,2009PhRvD..79a5014A}.}
 In quantum mechanics describing electron scattering and electron
@@
 where we neglect the substructure boost, we adopt a velocity dependent
-SFE that is normalized to fit the electron and positron excess at
-Earth observed by the PAMELA and \Fermi satellites,
+SFE that is normalized to fit the electron and positron excess observed at
+Earth\del{observed by the PAMELA and \Fermi satellites},
 \begin{equation}
-%\B_\sfe(\sigv) = 0.266\, \frac{c}{v_\rmn{sat}}\, \frac{v_\rmn{MW}}{\sigv} =
-%121 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-1/3}\,.
 \B_\sfe(\sigv) = \B_\rmn{sfe,MW} \frac{v_\rmn{MW}}{\sigv} =
-70 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-1/3}\,.
+70 \left(\frac{\mvir}{10^{15}\,\msun}\right)^{-1/3}\,,
 \label{eq:B_sfe}
 \end{equation}
-Here the boost factor needed to explain the PAMELA/\Fermi excess of
-electrons and positrons $\B_\rmn{sfe,MW}=300$, the velocity dispersion
-for the MW $v_\rmn{MW} \approx 220\,\rmn{km\,s}^{-1}$, and the
+\C{where the local boost factor required to explain the data
+  $\B_\rmn{sfe,MW}=300$.} \del{Here the boost factor needed to explain
+  the PAMELA/\Fermi excess of electrons and positrons
+  $\B_\rmn{sfe,MW}=300$,} The velocity dispersion for the MW
+$v_\rmn{MW} \approx 220\,\rmn{km\,s}^{-1}$, and the \C{mass dependent}
 velocity dispersion $\sigv$ for clusters is derived in
-\cite{2005RvMP...77..207V}. Clusters have a larger velocity dispersion
-and an accordingly smaller Sommerfeld boost factor.
+\cite{2005RvMP...77..207V}. Note that, clusters have a larger velocity
+dispersion and an accordingly smaller Sommerfeld boost factor.
 
@@
 advantage of so-called benchmark (BM) models, which have been proposed
-in different contexts (in particular in \cite{Bringmann:2008kj} giving
-predictions for imaging air Cherenkov telescopes, like MAGIC II and
-CTA). They give a good representation of models with high enough
-gamma-ray rates to become the first candidates for DM indirect
-detection in imaging air Cherenkov telescopes. We use the following
-supersymmetric BM models:
+in different contexts (in particular in \cite{2009JCAP...01..016B}
+giving predictions for imaging air Cherenkov telescopes, like MAGIC II
+and CTA). They give a {\em good representation of models with high
+  enough gamma-ray rates to become the first candidates for DM
+  indirect detection} in imaging air Cherenkov telescopes. We use the
+following supersymmetric BM models:
 
@@
 \begin{minipage}{2.0\columnwidth}
- \includegraphics[width=0.49\columnwidth]{figures/fit.ds.flux.eps}
- \includegraphics[width=0.49\columnwidth]{figures/fit.epflux.int.eps}
- \caption{\it Source functions for different dark matter (DM)
-   models. We show the simulated data from {\sc DarkSUSY} \cite{ds}
-   ($+$), and that generated by
-   \protect\cite{2011JCAP...03..019C,2011JCAP...03..051C} ($\times$);
-   the solid lines show the fit to the data. LEFT PANEL: normalized
-   differential continuum spectra for four different DM benchmark (BM)
-   models; $\Ip$ model (red), $\Jp$ (orange), $\Kp$ (green), and $\Js$
-   (blue). We use Eq.~(\ref{eq:bm_cont}) to fit the continuum
-   spectra. RIGHT PANEL: number of electron and positron per DM
-   annihilation above the electron energy $\ee$ for different DM
-   models; $\Ip$ BM model (red), $\Jp$ BM model (orange), $\Kp$ BM
-   model (green), and $\Js$ BM model (blue), leptophilic (LP) DM
-     annihilating indirectly into electrons and positrons (purple) and
-     into muons (black) without considering Sommerfeld boosts. We use
+ \includegraphics[width=0.49\columnwidth]{figures/fit.ds.flux.bw.eps}
+ \includegraphics[width=0.49\columnwidth]{figures/fit.epflux.int.bw.eps}
+ \caption{\it (Color online) Source functions for different dark
+   matter (DM) models. We show the simulated data from {\sc DarkSUSY}
+   \cite{ds}, and that generated by
+   \protect\cite{2011JCAP...03..019C,2011JCAP...03..051C}; the solid
+   lines show the fit to the data. LEFT PANEL: normalized differential
+   continuum spectra for four different DM benchmark (BM) models;
+   $\Ip$ model (red circles), $\Jp$ (orange squares), $\Kp$ (green
+   diamonds), and $\Js$ (blue triangles). We use Eq.~(\ref{eq:bm_cont})
+   to fit the continuum spectra. RIGHT PANEL: number of electron and
+   positron per DM annihilation above the electron energy $\ee$ for
+   different DM models; $\Ip$ BM model (red circles), $\Jp$ BM model
+   (orange squares), $\Kp$ BM model (green diamonds), and $\Js$ BM
+   model (blue triangles), leptophilic (LP) DM annihilating indirectly
+   into electrons and positrons (purple $+$) and into muons (black
+   $\times$) without considering Sommerfeld boosts. We use
    Eq.~(\ref{eq:bm_elec}) and Eqs.~(\ref{eq:lp_mu}-\ref{eq:lp_ep}) to
@@
 compared to the virial mass that is subject to tidal stripping. For
-comparison, we quote typical values for a large galaxy cluster and a galaxy group:
+comparison, we quote typical values for a large galaxy cluster and a
+galaxy group:
 \begin{eqnarray}
@@
 Here, $A_{\rmn{dm}} = q_{\rmn{sm},i}(\eg,R) / \rho(R)^2$ represents
-the particle physics factor, where $q_{\rmn{sm},i}(\eg,R)$ is defined by
-Eq.~(\ref{eq:q_sm}). The different density profiles have some impact
-on the luminosity from annihilating DM, although the details of the
-density profile can be neglected compared to the dominating boost from
-substructures (assuming DM to be cold). In Fig.~\ref{fig:radial_lum}
-we compare the radial dependence of the accumulative luminosity from
-different smooth cluster density profiles to the boosted luminosity
-due to substructure for different mass scales. We recalculate the
-overdensity, $\rhos$, for the shallower density profile with
-$\beta=0.6$ and rescale the concentration parameter in
-Eq.~(\ref{eq:cfit}) with $300/160$ \cite{2011ApJ...728L..39N} to
-account for the more centralized scale radius in cluster with a
-shallow inner slope. The emission of this profile with $\beta=0.6$ is
-about 30\% larger within $\rvir$ compared to a cuspy NFW
-($\beta=1.0$). This difference is built up within $0.1\rvir$
-(i.e. close to $r_\s$). Hence the slope of the central part of a
-cluster has little influence for the DM luminosity within $\rvir$ as
-long as the degeneracy in the lensing mass measurements with $r_\s$
+the particle physics factor, where $q_{\rmn{sm},i}(\eg,R)$ is defined
+by Eq.~(\ref{eq:q_sm}). The different density profiles have some
+impact on the luminosity from annihilating DM, although the details of
+the density profile can be neglected compared to the dominating boost
+from substructures (assuming DM to be cold). In
+Fig.~\ref{fig:radial_lum} we compare the radial dependence of the
+accumulative luminosity from different smooth cluster density profiles
+to the boosted luminosity due to substructure for different mass
+scales. We recalculate the overdensity, $\rhos$, for the shallower
+density profile with $\beta=0.6$ and rescale the concentration
+parameter in Eq.~(\ref{eq:cfit}) with $300/160$
+\cite{2011ApJ...728L..39N} to account for the more centralized scale
+radius in cluster with a shallow inner slope. The emission of this
+profile with $\beta=0.6$ is about 30\% larger within $\rvir$ compared
+to a cuspy NFW ($\beta=1.0$). This difference is built up within
+$0.1\rvir$ (i.e. close to $r_\s$). Hence the slope of the central part
+of a cluster has little influence for the DM luminosity within $\rvir$
+as long as the degeneracy in the lensing mass measurements with $r_\s$
 (which decreases for decreasing inner slope) has been taken into
@@
 for dwarf galaxies, $200$ for galaxies, and $10^3$ for galaxy
-clusters. These boost factors are only realized for direct
-annihilation emission (continuum emission or final state radiation) or
-IC scattering off homogeneous seed photon fields (CMB). For IC
-scattering of SD photons, the overlap of final state leptons and SD
-photons is smaller which causes the substructure boost over the smooth
-emission to be reduced by roughly two orders of magnitudes. It should
-also be noted that the substructure boosted fluxes from clusters are
-much more extended than for dwarf galaxies, hence more difficult to
-detect with Cherenkov telescopes. In fact, it was shown in
-Sanchez-Conde et al. \cite{2011arXiv1104.3530S} that inside $0.1$~deg,
-where the sensitivity of Cherenkov telescopes is maximized, the
-expected DM flux including substructures from the brightest dwarf
-galaxy is about an order magnitude higher than the brightest
-cluster. However, that work assumed a substructure boost of about 50
-in the most massive cluster halos which is more than an order
+clusters. \C{We stress that these boost factors are only realized in
+  the region around the virial radius of each respective halo which
+  are mostly stripped for dwarf substructures in the MW. Hence a more
+  realistic boost from substructures is probably much smaller in Dwarf
+  galaxies. In addition,} these boost factors are only realized for
+direct annihilation emission (continuum emission or final state
+radiation) or IC scattering off homogeneous seed photon fields
+(CMB). For IC scattering of SD photons, the overlap of final state
+leptons and SD photons is smaller which causes the substructure boost
+over the smooth emission to be reduced by roughly two orders of
+magnitudes. It should also be noted that the substructure boosted
+fluxes from clusters are much more extended than for dwarf galaxies,
+hence more difficult to detect with Cherenkov telescopes. In fact, it
+was shown in Sanchez-Conde et al. \cite{2011arXiv1104.3530S} that
+inside $0.1$~deg, where the sensitivity of Cherenkov telescopes is
+maximized, the expected DM flux including substructures from the
+brightest dwarf galaxy is about an order magnitude higher than the
+brightest cluster. However, that work assumed a substructure boost of
+about 50 in the most massive cluster halos which is more than an order
 magnitude smaller than what we use in this work, hence in projection
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/dens.prof.eps}
- \caption{\it Radial dependence of DM annihilation luminosity of
-   smooth halo and substructures. The solid lines show the
-   accumulative smooth luminosity from a cluster with the mass
+ \includegraphics[width=0.99\columnwidth]{figures/dens.prof.bw.eps}
+ \caption{\it (Color online) Radial dependence of DM annihilation
+   luminosity of smooth halo and substructures. The solid lines show
+   the accumulative smooth luminosity from a cluster with the mass
    $\mvir=10^{15}\,\msun$ for three different density profiles; an
    Einasto profile with $\alpha=0.17$ (light blue), a cuspy NFW
-   profile with $\beta=1.0$ (dark blue), and a core NFW profile with
-   $\beta=0.6$ (purple). The dashed lines show the accumulative
-   luminosity from substructures for three different mass scales; an
-   $\mvir=10^{15}\,\msun$ galaxy cluster (red), an
+   profile with $\beta=1.0$ (thick dark blue), and a core NFW profile
+   with $\beta=0.6$ (thin purple). The dashed lines show the
+   accumulative luminosity from substructures for three different mass
+   scales; an $\mvir=10^{15}\,\msun$ galaxy cluster (thick red), an
    $\mvir=10^{12}\,\msun$ galaxy (orange), and an
-   $\mvir=10^{8}\,\msun$ dwarf galaxy (green). All luminosities have
-   been normalized with the luminosity within $\rvir$ from a cuspy NFW
-   profile. We have assumed the standard value for the limiting
-   substructure mass of $M_\rmn{lim}=10^{-6}\,\msun$. Note the large
-   expected boost from substructures in clusters ($\sim1000$), and the
-   relative small boost in dwarf galaxies ($\sim20$).}
+   $\mvir=10^{8}\,\msun$ dwarf galaxy (thin green). All luminosities
+   have been normalized with the luminosity within $\rvir$ from a
+   cuspy NFW profile. We have assumed the standard value for the
+   limiting substructure mass of $M_\rmn{lim}=10^{-6}\,\msun$. Note
+   the large expected boost from substructures in clusters
+   ($\sim1000$), and the relative small boost in dwarf galaxies
+   ($\sim20$).}
  \label{fig:radial_lum}
@@
 \begin{figure}
-  \includegraphics[width=0.99\columnwidth]{figures/emissiv.sub.eps}
-  \caption{\it Plot that shows where most of the DM annihilation
-    luminosity originates. We show the differential contribution to
-    the DM annihilation luminosity per logarithmic interval in radius
-    which corresponds to $x^3\rho^2/\rho^2_{200}$ where $\rho_{200}$
-    is the density at $\rvir$. The solid lines represent cuspy
-    $\beta=1.0$ NFW density profiles for three different mass scales;
-    an $\mvir=10^{15}\,\msun$ galaxy cluster (red), an
-    $\mvir=10^{12}\,\msun$ galaxy (orange), and an
-    $\mvir=10^{8}\,\msun$ dwarf galaxy (green). The dashed lines show
-    the contribution from substructures for the same three mass
+  \includegraphics[width=0.99\columnwidth]{figures/emissiv.sub.bw.eps}
+  \caption{\it (Color online) Plot that shows where most of the DM
+    annihilation luminosity originates. We show the differential
+    contribution to the DM annihilation luminosity per logarithmic
+    interval in radius which corresponds to $x^3\rho^2/\rho^2_{200}$
+    where $\rho_{200}$ is the density at $\rvir$. The solid lines
+    represent cuspy $\beta=1.0$ NFW density profiles for three
+    different mass scales; an $\mvir=10^{15}\,\msun$ galaxy cluster
+    (thick red), an $\mvir=10^{12}\,\msun$ galaxy (orange), and an
+    $\mvir=10^{8}\,\msun$ dwarf galaxy (thin green). The dashed lines
+    show the contribution from substructures for the same three mass
     scales. All luminosities have been normalized with the luminosity
@@
 (see Sect.~\ref{sect:PF} and Fig.~\ref{fig:q_DM} for further details).
-%(see \cite{2009JCAP...01..016B} and references therein,
-%also see fit).
 
@@
 
-The spatial distribution of light emitted by SD is quite different
-from what is expected for the IC upscattered SD photons. We illustrate
-this in Fig.~\ref{fig:SD_lum}, where the accumulative luminosity from
-SD is compared to the IC SD photons for a
+The spatial distribution of \C{far-IR to UV} light emitted by SD
+is quite different from what is expected for the IC upscattered SD
+photons. We illustrate this in Fig.~\ref{fig:SD_lum}, where the
+accumulative luminosity from SD is compared to the IC SD photons for a
 $\mvir=6.0\times10^{14}\,\msun$ cluster where the boost from
@@
  \includegraphics[width=0.99\columnwidth]{figures/fit.porter.v2.eps}
- \caption{\it Spectral dependence of radiation fields in a cluster of
-   galaxies. The black dotted line of the left peak show the spectrum
-   of CMB photons using a black body with a temperature of
-   $2.73$~K. The crosses of the middle and right peaks represent the
-   measured spectra from stars extending from the near IR to UV and
-   dust at far IR wavelengths (SD), respectively, and are derived in
-   \protect \cite{2006ApJ...648L..29P} for a galaxy. We normalize the
-   individual SD spectrum separately using the observed luminosity
-   from SD in clusters. The SD luminosity is related to the cluster
-   mass through Eqs.~(\ref{eq:E_SD}-\ref{eq:N_dust}), where we use
-   have used the mass $\mvir=6.0\times10^{14}\msun$ in this figure. We
-   renormalize the SD spectra to the radius $r=0.03\rvir$, where the
-   smooth energy density of the SD light (see Fig.~\ref{fig:SD_Edens})
-   equals the energy density of the CMB. The red dashed lines show the
-   fitted SD spectral model.}
+ \caption{\it (Color online) Spectral dependence of radiation fields
+   in a cluster of galaxies. The black dotted line of the left peak
+   show the spectrum of CMB photons using a black body with a
+   temperature of $2.73$~K. The crosses of the middle and right peaks
+   represent the measured spectra from stars extending from the near
+   IR to UV and dust at far IR wavelengths (SD), respectively, and are
+   derived in \protect \cite{2006ApJ...648L..29P} for a galaxy. We
+   normalize the individual SD spectrum separately using the observed
+   luminosity from SD in clusters. The SD luminosity is related to the
+   cluster mass through Eqs.~(\ref{eq:E_SD}-\ref{eq:N_dust}), where we
+   use have used the mass $\mvir=6.0\times10^{14}\msun$ in this
+   figure. We renormalize the SD spectra to the radius $r=0.03\rvir$,
+   where the smooth energy density of the SD light (see
+   Fig.~\ref{fig:SD_Edens}) equals the energy density of the CMB. The
+   red dashed lines show the fitted SD spectral model.}
  \label{fig:SD_spectra}
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/ucool.eps}
- \caption{\it Spatial dependence of the energy density of radiation
-   fields in a cluster of galaxies. The energy density of the CMB
-   (blue dotted line) is isotropic with
+ \includegraphics[width=0.99\columnwidth]{figures/ucool.bw.eps}
+ \caption{\it (Color online) Spatial dependence of the energy density
+   of radiation fields in a cluster of galaxies. The energy density of
+   the CMB (blue dotted line) is isotropic with
    $u_\rmn{cmb}=0.26\,\rmn{eV}\,\rmn{cm}^{-3}$. The energy density of
    the light from stars and dust (SD) is denoted by the red dashed
-   line and the solid purple line for the total SD light and the
+   line and the solid orange line for the total SD light and the
    smooth SD light, respectively. For comparison we show the energy
-   density of the stars and a low dust model (SLD) with the light grey
-   line. The SD light has been renormalized to a cluster with the mass
-   $\mvir=6.0\times10^{14}\msun$. Finally we show the energy density of two
-   magnetic field models with a central magnetic field of 3~$\mu
-   G$. The magnetic field scales with the gas density to the power
-   $\alpha_\rmn{B}$; green dash-dotted line ($\alpha_\rmn{B}=0.5$) and
-   orange dash-dotted line ($\alpha_\rmn{B}=0.7$). Note that the SD
-   radiation is dominating the energy density inside
-   $\sim0.03\,\rvir$.}
+   density of the stars and a low dust model (SLD) with the solid
+   yellow line. The SD light has been renormalized to a cluster with
+   the mass $\mvir=6.0\times10^{14}\msun$. Finally we show the energy
+   density of two magnetic field models with a central magnetic field
+   of 3~$\mu G$. The magnetic field scales with the gas density to the
+   power $\alpha_\rmn{B}$; dark green dash-dotted line
+   ($\alpha_\rmn{B}=0.5$) and light green dash-dotted line
+   ($\alpha_\rmn{B}=0.7$). Note that the SD radiation is dominating
+   the energy density inside $\sim0.03\,\rvir$.}
  \label{fig:SD_Edens}
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/lum.stars.eps}
- \caption{\it Accumulative luminosity as a function of radius. We show
-   the luminosity without substructures inside radius $r$. The solid
-   lines show the optical/IR emission from stars and dust (SD) and the
-   IC upscattered SD light is shown by the dashed lines. The red lines
-   show the total emission including the brightest cluster galaxy, the
+ \includegraphics[width=0.99\columnwidth]{figures/lum.stars.bw.eps}
+ \caption{\it (Color online) \C{Comparing the spatial dependence of
+     emission from stars and dust (SD) to IC upscattered SD light.}
+   \del{Accumulative luminosity as a function of radius.}  We show the
+   luminosity without substructures inside radius $r$. The solid lines
+   show the optical/IR emission from SD and the IC upscattered SD
+   light is shown by the dashed lines. The thick red lines show the
+   total emission including the brightest cluster galaxy, the
    intra-cluster light and the additional intra-cluster galaxies,
    while these galaxies have been cut out in the smooth component
-   shown by the orange lines. We normalize the SD light and the IC
-   upscattered SD with the smooth luminosity within $\rvir$ for each
-   component. We find that the gamma-ray IC luminosities are dominated
-   by the central regime, while the SD light is mainly build up in the
-   outer parts of the cluster. For comparison, we show that the SD
-   light traces the NFW mass profile (blue) outside $0.1\rvir$.}
+   shown by the thin orange lines. We normalize the SD light and the
+   IC upscattered SD with the smooth luminosity within $\rvir$ for
+   each component. We find that the gamma-ray IC luminosities are
+   dominated by the central regime, while the SD light is mainly build
+   up in the outer parts of the cluster. For comparison, we show that
+   the SD light traces the NFW mass profile (dotted blue) outside
+   $0.1\rvir$.}
  \label{fig:SD_lum}
@@
 induced emission. In addition to the annihilating DM, we estimate the
-gamma-ray flux induced by shock-accelerated CRs.
+gamma-ray flux induced by shock-accelerated CRs. \C{Note that all
+  fluxes in this section are derived within an angle corresponding to
+  $\rvir$ and are smoothed over using a PSF of $0.1\deg$.}
 
@@
 \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v14.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\caption{\it Comparing the differential flux from different models: we
-  show the continuum emission from DM benchmark (BM) models (blue
-  dashed), electrons and positrons from DM BM models that
-  Compton-upscatter CMB photons (green dotted) as well as dust and
-  star photons (orange dash-dotted), and CR induced gamma-ray emission
-  (red solid). Each panel is associated with an individual DM BM
-  model; upper left $\Ip$, lower left $\Kp$, upper right $\Jp$, and
+\caption{\it (Color online) Comparing the differential flux from
+  different models: we show the continuum emission from DM benchmark
+  (BM) models (blue dashed), electrons and positrons from DM BM models
+  that Compton-upscatter CMB photons (green dotted) as well as dust
+  and star photons (orange dash-dotted), and CR induced gamma-ray
+  emission (red solid). Each panel is associated with an individual DM
+  BM model; upper left $\Ip$, lower left $\Kp$, upper right $\Jp$, and
   lower right $\Js$. The emission is calculated for the Fornax cluster
@@
 \begin{minipage}{2.0\columnwidth}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v14.0.1deg.1.6T.SubMass.elmu.SF700.noMW.woGal.eps}
-\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv14.0.1deg.SubMass.noMW.woGal.eps}
-\caption{\it Comparing the flux from different inverse Compton
-  upscattered radiation fields. We show the differential inverse
-  Compton emission induced by leptophilic DM in the left panel and by
-  the $\Kp$ benchmark model in the right panel. The contribution from
-  each individual radiation field from top line to bottom line; CMB
-  (green dashed-triple-dotted), dust (purple dashed), stars (blue
-  dashed-dotted). The sum of the three components are shown with the
-  orange solid line. The red solid lines show the CR induced gamma-ray
-  flux. The black arrow shows the spatially extended differential
-  upper limit from \Fermi \protect \cite{2010ApJ...717L..71A}
-  indicating that the LP model assumptions such as Sommerfeld and/or
-  substructure boost are in conflict with the upper limit. All fluxes
-  are calculated for the Fornax cluster within $\rvir$ using a point
-  spread function of $0.1\deg$. For this cluster, the enhancement due
-  to substructures from IC upscattered CMB and SD photons is 890. The
-  saturated Sommerfeld boost is 530.}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.v14.0.1deg.1.6T.SubMass.elmu.SF700.noMW.woGal.bw.eps}
+\includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv14.0.1deg.SubMass.noMW.woGal.bw.eps}
+\caption{\it (Color online) Comparing the flux from different inverse
+  Compton upscattered radiation fields. We show the differential
+  inverse Compton emission induced by leptophilic DM in the left panel
+  and by the $\Kp$ benchmark model in the right panel. The
+  contribution from each individual radiation field from top line to
+  bottom line; CMB (green dashed-triple-dotted), dust (purple dashed),
+  low dust model (grey dashed), and stars (blue dashed-dotted). The
+  sum of the three components are shown with the orange solid
+  line. The red solid lines show the CR induced gamma-ray flux. The
+  black arrow shows the spatially extended differential upper limit
+  from \Fermi \protect \cite{2010ApJ...717L..71A} indicating that the
+  LP model assumptions such as Sommerfeld and/or substructure boost
+  are in conflict with the upper limit. All fluxes are calculated for
+  the Fornax cluster within $\rvir$ using a point spread function of
+  $0.1\deg$. For this cluster, the enhancement due to substructures
+  from IC upscattered CMB and SD photons is 890. The saturated
+  Sommerfeld boost is 530.}
  \label{fig:IR_comp}
@@
  \includegraphics[width=0.99\columnwidth]{figures/flux.int.v14.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
- \caption{\it Comparing the energy integrated flux from different
-   models. We show the emission from CR induced emission (red solid),
-   a leptophilic (LP) model that includes both final state radiation
-   and IC upscattered CMB, dust and starlight (green dash-dotted), and
-   the benchmark $\Kp$ model (BM) that includes continuum emission,
-   and IC upscattered CMB, dust and starlight (blue dashed). The black
-   arrow shows the spatially extended integrated flux upper limit set
-   by \Fermi-LAT again indicating challenges for the assumptions
-   underlying the LP model. We also show projected CTA point source
-   sensitivities ($5\sigma$, 50h). The emission is calculated for the
-   Fornax cluster using a point spread function of $0.1\deg$. The
-   boost from Sommerfeld and substructures is about 530 and 890,
-   respectively.}
+ \caption{\it (Color online) Comparing the energy integrated flux from
+   different models. We show the emission from CR induced emission
+   (red solid), a leptophilic (LP) model that includes both final
+   state radiation and IC upscattered CMB, dust and starlight (green
+   dash-dotted), and the benchmark $\Kp$ model (BM) that includes
+   continuum emission, and IC upscattered CMB, dust and starlight
+   (blue dashed). The black arrow shows the spatially extended
+   integrated flux upper limit set by \Fermi-LAT again indicating
+   challenges for the assumptions underlying the LP model. We also
+   show projected CTA point source sensitivities ($5\sigma$, 50h). The
+   emission is calculated for the Fornax cluster using a point spread
+   function of $0.1\deg$. The boost from Sommerfeld and substructures
+   is about 530 and 890, respectively.}
  \label{fig:flux_int}
@@
 
-\begin{table*}
+\begin{table*}\hst\hst\hst\hst\hst\hst\hst
 \begin{minipage}{2.0\columnwidth}
   \caption{Gamma-ray flux from various clusters within $\rvir$.}
-\begin{tabular}{l c c c c c c c c c c}
+\begin{tabular}{l c c c c c c c c c c c}
 \hline
@@
 \multicolumn{3}{c}{$F_{\gamma}(>100\,\rmn{GeV})$ $[\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}]$:} &
-$\mvir$ $^{(1)}$ & $\B_\rmn{sfe} $$^{(2)}$ & $\B_\rmn{sub} $$^{(3)}$ \\
-         & DM-LP $^{(4)}$ & DM-BM-$\Kp$ $^{(5)}$ & CR-$\pi^0$ $^{(6)}$
-         & & DM-LP $^{(4)}$ & DM-BM-$\Kp$ $^{(5)}$ & CR-$\pi^0$ $^{(6)}$ & $[10^{14}\,\msun]$ && \\
- \hline
- Coma & $8.2\times10^{-8}$ & $7.6\times10^{-11}$ & $4.1\times10^{-9}$
- & \,\,\,\,\, & $1.2\times10^{-11}$ & $2.8\times10^{-13}$ & $1.5\times10^{-12}$
- & $12.9$ & $530/65$ & $1290$ \\
- Perseus \,\,\,\,\,\, & $8.6\times10^{-8}$ & $7.8\times10^{-11}$ & $1.5\times10^{-8}$
- & \,\,\,\,\, & $1.2\times10^{-11}$ & $2.9\times10^{-13}$ & $5.5\times10^{-12}$
- & $8.6$ & $530/75$ & $1190$ \\
- Virgo & $1.6\times10^{-6}$ & $1.5\times10^{-9}$ & $1.5\times10^{-8}$
- & \,\,\,\,\, & $2.3\times10^{-10}$ & $5.4\times10^{-12}$ & $5.7\times10^{-12}$
- & $6.9$ & $530/80$ & $1120$ \\
- Fornax & $3.5\times10^{-7}$ & $3.2\times10^{-10}$ & $3.1\times10^{-10}$
- & \,\,\,\,\, & $5.1\times10^{-11}$ & $1.2\times10^{-12}$ & $1.1\times10^{-13}$
- & $2.4$ & $530/110$ & $890$ \\
+$\mvir$$^{(1)}$ & $D_\rmn{lum}$$^{(1)}$ & $\B_\rmn{sfe}$$^{(2)}$ & $\B_\rmn{sub}$$^{(3)}$ \\
+         & DM-LP$^{(4)}$ & DM-BM-$\Kp$$^{(5)}$ & CR-$\pi^0$$^{(6)}$
+         & & DM-LP$^{(4)}$ & DM-BM-$\Kp$$^{(5)}$ & CR-$\pi^0$$^{(6)}$ 
+         & $[10^{14}\,\msun]$ & [Mpc] && \\
+ \hline
+ Coma & $8.2\mytimes10^{-8}$ & $7.6\mytimes10^{-11}$ & $4.1\mytimes10^{-9}$
+ & \,\,\,\,\, & $1.2\mytimes10^{-11}$ & $2.8\mytimes10^{-13}$ & $1.5\mytimes10^{-12}$
+ & $12.9$ & $101$ & $530/65$ & $1290$ \\
+ Perseus \,\,\,\,\,\, & $8.6\mytimes10^{-8}$ & $7.8\mytimes10^{-11}$ & $1.5\mytimes10^{-8}$
+ & \,\,\,\,\, & $1.2\mytimes10^{-11}$ & $2.9\mytimes10^{-13}$ & $5.5\mytimes10^{-12}$
+ & $8.6$ & $79.5$ & $530/75$ & $1190$ \\
+ Virgo & $1.6\mytimes10^{-6}$ & $1.5\mytimes10^{-9}$ & $1.5\mytimes10^{-8}$
+ & \,\,\,\,\, & $2.3\mytimes10^{-10}$ & $5.4\mytimes10^{-12}$ & $5.7\mytimes10^{-12}$
+ & $6.9$ & $17.2$ & $530/80$ & $1120$ \\
+ Fornax & $3.5\mytimes10^{-7}$ & $3.2\mytimes10^{-10}$ & $3.1\mytimes10^{-10}$
+ & \,\,\,\,\, & $5.1\mytimes10^{-11}$ & $1.2\mytimes10^{-12}$ & $1.1\mytimes10^{-13}$
+ & $2.4$ & $19.8$ & $530/110$ & $890$ \\
 \hline
@@
   (1) The mass of Fornax, Coma, and Perseus are derived from \cite{2007A&A...466..805C},
-  while the mass of Virgo is derived from \cite{1984ApJ...281...31T}.\\
+  while the mass of Virgo is derived from \cite{1984ApJ...281...31T}. \C{The luminosity 
+    distance to Fornax, Coma, and Perseus are derived from \cite{2007A&A...466..805C},
+    while the distance to Virgo is derived from \cite{2007ApJ...655..144M}. All distances 
+    and masses assume $H_0= 70\,[\rmn{km}/\rmn{s}/\rmn{Mpc}]$.}\\
   (2) The boost due to Sommerfeld enhancement. The first value shows the saturated
@@
 \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v14.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
-\caption{\it Comparing the gamma-ray emission from different
-  clusters. We show the differential flux of clusters in the upper
-  panel of each figure: Fornax (upper left), Coma (upper right), Virgo
-  (lower left), and Perseus (lower right). We show CR induced emission
-  (red solid), a leptophilic (LP) model that includes both final state
-  radiation and IC upscattered CMB, dust and starlight (green
-  dash-dotted), and the benchmark $\Kp$ model (BM) that includes
-  continuum emission, and IC upscattered CMB, dust and starlight (blue
-  dashed). The arrows show the spatially extended differential upper
-  limits set by \Fermi-LAT in the energy ranges $0.2-1$~GeV,
-  $1-10$~GeV, and $10-100$~GeV from left to right (using Gauss
-  profiles for the source extension with $\sigma=(1.2,1.0,0.8)$ for
-  (Virgo, Coma, Fornax) and an X-ray-inferred King profile for
+\caption{\it (Color online) Comparing the gamma-ray emission from
+  different clusters. We show the differential flux of clusters in the
+  upper panel of each figure: Fornax (upper left), Coma (upper right),
+  Virgo (lower left), and Perseus (lower right). We show CR induced
+  emission (red solid), a leptophilic (LP) model that includes both
+  final state radiation and IC upscattered CMB, dust and starlight
+  (green dash-dotted), and the benchmark $\Kp$ model (BM) that
+  includes continuum emission, and IC upscattered CMB, dust and
+  starlight (blue dashed). The arrows show the spatially extended
+  differential upper limits set by \Fermi-LAT in the energy ranges
+  $0.2-1$~GeV, $1-10$~GeV, and $10-100$~GeV from left to right (using
+  Gauss profiles for the source extension with $\sigma=(1.2,1.0,0.8)$
+  for (Virgo, Coma, Fornax) and an X-ray-inferred King profile for
   Perseus) \cite{2010ApJ...717L..71A}. We show the individual
@@
 limits are not good enough to rule out the boost from substructures or
-SFE. Assuming that the PAMELA positron excess is due to SFE DM, then
-in order not to overproduce the differential upper limits set by
-\Fermi-LAT in the energy range\footnote{We average the LP DM flux in
-  the energy range $1-10$~GeV before we compare it to the upper
-  limits.} $1-10$~GeV, we can constrain the smallest mass of
-substructures to $M_\rmn{lim}\gtrsim 10^4\,\msun$. Instead, assuming
-the standard mass of the smallest substructures of $M_\rmn{lim}\approx
-10^{-6}\,\msun$, we can constrain the saturated boost from SFE to
-$\lesssim 5$ in M49 and Fornax, which corresponds to a maximum SFE in
-the MW of $\lesssim3$. Hence, we conclude that without substantial
-improvement in the modelling of these extended sources, \Fermi-LAT
-will not be able to rule out LP models in their current form using
-clusters but can put impressive constraints on them.
+SFE. Assuming that \C{measured $e^+/e^-$ excess} \del{the PAMELA
+  positron excess} is due to SFE DM, then in order not to overproduce
+the differential \C{gamma-ray} upper limits set by \Fermi-LAT in the
+energy range\footnote{We average the LP DM flux in the energy range
+  $1-10$~GeV before we compare it to the upper limits.} $1-10$~GeV, we
+can constrain the smallest mass of substructures to
+$M_\rmn{lim}\gtrsim 10^4\,\msun$. Instead, assuming the standard mass
+of the smallest substructures of $M_\rmn{lim}\approx 10^{-6}\,\msun$,
+we can constrain the saturated boost from SFE to $\lesssim 5$ in M49
+and Fornax, which corresponds to a maximum SFE in the MW of
+$\lesssim3$. Hence, we conclude that without substantial improvement
+in the modelling of these extended sources, \Fermi-LAT will not be
+able to rule out LP models in their current form using clusters but
+can put impressive constraints on them.
 
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v14.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
- \caption{\it Constraining boost factors using flux upper limits. The
-   leptophilic (LP) gamma-ray emission is derived within $\rvir$ using
-   a point spread function of $0.1\deg$. In order not to overproduce
-   the \Fermi-LAT differential flux upper limits in the energy
-   interval $1-10$~GeV the boost from substructures and Sommerfeld
-   enhancement (SFE) is constrained for four clusters; Fornax (red),
-   NGC4636 (orange), M49 (green), and Coma (blue). We indicate both
-   the saturated SFE of 530 (right black arrow) as well as the local
-   boost in the Milky Way of 300 (c.f. Eq.~\ref{eq:B_sfe}) that is
-   required to explain the electron and positron excess observed at
-   Earth with LP DM (left black arrow). If the DM interpretation is
-   correct, we can constrain the smallest size of halos to be larger
-   than $10^4\,\msun$. Contrarily, if the smallest size of DM halos is
-   $10^{-6}\,\msun$, we can constrain the SFE to $\lesssim 5$ in M49 and
-   Fornax. This corresponds to a maximum SFE in the MW of $\lesssim 3$,
-   which would be too small to support the DM annihilation hypothesis
-   for the PAMELA/\Fermi excess.}
+ \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v14.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.bw.eps}
+ \caption{\it (Color online) Constraining boost factors using flux
+   upper limits. The leptophilic (LP) gamma-ray emission is derived
+   within $\rvir$ using a point spread function of $0.1\deg$. In order
+   not to overproduce the \Fermi-LAT differential flux upper limits in
+   the energy interval $1-10$~GeV the boost from substructures and
+   Sommerfeld enhancement (SFE) is constrained for four clusters; M49
+   (green dashed), Fornax (red solid), NGC4636 (orange dash-dotted),
+   and Coma (blue dotted). We indicate both the saturated SFE of 530
+   (right black arrow) as well as the local boost in the Milky Way of
+   300 (c.f. Eq.~\ref{eq:B_sfe}) that is required to explain the
+   electron and positron excess observed at Earth with LP DM (left
+   black arrow). If the DM interpretation is correct, we can constrain
+   the smallest size of halos to be larger than
+   $10^4\,\msun$. Contrarily, if the smallest size of DM halos is
+   $10^{-6}\,\msun$, we can constrain the SFE to $\lesssim 5$ in M49
+   and Fornax. This corresponds to a maximum SFE in the MW of
+   $\lesssim 3$, which would be too small to support the DM
+   annihilation hypothesis for the PAMELA/\Fermi excess.}
  \label{fig:boost_const}
@@
 \begin{figure}
- \includegraphics[width=0.99\columnwidth]{figures/SB.v14.1GeV.SF700.SubMass.elmu.eps}
- \caption{\it Comparing the intrinsic surface brightness from
-   different clusters without taking PSF effects into account. We show
-   the CR induced emission (red), leptophilic emission (green), and
-   emission from the $\Kp$ benchmark model (blue). The different line
-   styles each represent a cluster; Fornax (solid), Coma (dotted),
-   Virgo (dashed), and Perseus (dash-dotted). We include the boost
-   from both substructures and Sommerfeld effect. The shape and
-   normalization of the different DM models are very similar. In
-   contrast, the CR-induced emission profiles have a much larger
-   scatter due to the large variation of the gas fraction and expected
-   CR fraction in these clusters.}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.v14.1GeV.SF700.SubMass.elmu.bw.eps}
+ \caption{\it (Color online) Comparing the intrinsic surface
+   brightness from different clusters without taking PSF effects into
+   account. We show the CR induced emission (red), leptophilic
+   emission (light green), and emission from the $\Kp$ benchmark model
+   (dark blue). The different line styles each represent a cluster;
+   Fornax (solid), Coma (dotted), Virgo (dashed), and Perseus
+   (dash-dotted). We include the boost from both substructures and
+   Sommerfeld effect. The shape and normalization of the different DM
+   models are very similar. In contrast, the CR-induced emission
+   profiles have a much larger scatter due to the large variation of
+   the gas fraction and expected CR fraction in these clusters.}
  \label{fig:SB_clu}
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v14.1GeV.SF700.noSuB.vs.SubMass.elmu.eps}
- \caption{\it The impact of substructures on the intrinsic surface
-   brightness profile o the Fornax cluster at 1~GeV. The emission
-   induced by CRs is denoted by the red solid line, the leptophilic
-   model by green lines, and the DM $\Kp$ benchmark model by blue
-   lines. The dashed lines show the brightness profiles where the
-   boost from substructures is included while the substructures are
-   excluded for the dotted lines. The boost from Sommerfeld
-   enhancement with and without substructures is 110 and 530,
-   respectively. The boost due to substructures is about 890. Notice
-   the nearly flat profiles when substructures are included, and the
-   relative large boost at $0.01\rvir$ that is due to projection of
-   peripheral substructures onto the cluster center.}
+ \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v14.1GeV.SF700.noSuB.vs.SubMass.elmu.bw.eps}
+ \caption{\it (Color online) The impact of substructures on the
+   intrinsic surface brightness profile o the Fornax cluster at
+   1~GeV. The emission induced by CRs is denoted by the thin red solid
+   line, the leptophilic model by thick light green lines, and the DM
+   $\Kp$ benchmark model by dark blue lines. The dashed lines show the
+   brightness profiles where the boost from substructures is included
+   while the substructures are excluded for the dotted lines. The
+   boost from Sommerfeld enhancement with and without substructures is
+   110 and 530, respectively. The boost due to substructures is about
+   890. Notice the nearly flat profiles when substructures are
+   included, and the relative large boost at $0.01\rvir$ that is due
+   to projection of peripheral substructures onto the cluster center.}
  \label{fig:SB_sub}
@@
 four representative clusters that were shown previously in
-Fig.~\ref{fig:SB_clu}. We find that the surface brightness,
-$S_\gamma$ of the DM emission above 1~GeV in the outer parts of all
-clusters have the same shape. In addition, we show the spatial
-dependence of the individual gamma-ray components for the Fornax
-cluster in the right panel. We see that in the BM model, the emission
-is dominated by the continuum emission. In the LP model, the emission
-at intermediate and large radii is dominated by IC-upscattered CMB
-photons while at small radii, IC-upscattered SD photons dominate the
-emission. The fact that the sum of both IC components resembles the
-profile of the BM model is not surprising: in this energy range, all
-the energy of the annihilation is imparted on leptons which radiate
-all their energy away through IC emission and the sum of the IC components represents a
+Fig.~\ref{fig:SB_clu}. We find that the surface brightness, $S_\gamma$
+of the DM emission above 1~GeV in the outer parts of all clusters have
+the same shape. In addition, we show the spatial dependence of the
+individual gamma-ray components for the Fornax cluster in the right
+panel. We see that in the BM model, the emission is dominated by the
+continuum emission. In the LP model, the emission at intermediate and
+large radii is dominated by IC-upscattered CMB photons while at small
+radii, IC-upscattered SD photons dominate the emission. The fact that
+the sum of both IC components resembles the profile of the BM model is
+not surprising: in this energy range, all the energy of the
+annihilation is imparted on leptons which radiate all their energy
+away through IC emission and the sum of the IC components represents a
 calorimeter for these radiating leptons. We note that the surface
@@
 difference in outer parts of the different clusters from these type of
-models. The DM BM models scale as $S_\gamma\sim\mvir^{0.16}$,
-hence more massive clusters show a slightly higher surface
+models. The DM BM models scale as $S_\gamma\sim\mvir^{0.16}$, hence
+more massive clusters show a slightly higher surface
 brightness. Finally, we note that the flux from DM without
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.v14.1GeV.SF700.noSuB.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v14.1GeV.SF700.noSuB.elmu.eps}
-  \caption{\it The intrinsic surface brightness profiles without
-    substructures at energies $E>1\ GeV$. We show the CR induced
-    emission (red), leptophilic emission (green), and emission from
-    the $\Kp$ benchmark model (blue). LEFT PANEL: comparison of the surface
-    brightness of different clusters; Fornax (solid), Coma (dotted),
-    Virgo (dashed), and Perseus (dash-dotted). RIGHT PANEL: comparison of
-    different emission components in Fornax; dotted lines show the
-    inverse Compton (IC) upscattered CMB photons, dashed lines show
-    the IC upscattered photons from stars and dust, and blue solid
-    lines show the continuum emission from the $\Kp$ benchmark model.}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.v14.1GeV.SF700.noSuB.elmu.bw.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v14.1GeV.SF700.noSuB.elmu.bw.eps}
+  \caption{\it (Color online) The intrinsic surface brightness
+    profiles without substructures at energies $E>1\ GeV$. We show the
+    CR induced emission (red), leptophilic emission (light green), and
+    emission from the $\Kp$ benchmark model (dark blue). LEFT PANEL:
+    comparison of the surface brightness of different clusters; Fornax
+    (solid), Coma (dotted), Virgo (dashed), and Perseus
+    (dash-dotted). RIGHT PANEL: comparison of different emission
+    components in Fornax; dotted lines show the inverse Compton (IC)
+    upscattered CMB photons, dashed lines show the IC upscattered
+    photons from stars and dust, and blue solid lines show the
+    continuum emission from the $\Kp$ benchmark model.}
  \label{fig:SB_clu_nosub}
@@
 \begin{minipage}{2.0\columnwidth}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v14.SF700.SubMass.elmu.eps}
-  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v14.SF700.SubMass.elmu.eps}
-\caption{\it Surface brightness predicted for Cherenkov telescopes at
-  high energies. We show the emission above $100$~GeV and include the
-  boost from substructures. We use a point spread function of
-  $\psf=0.1\deg$ that is typical for Cherenkov
-  telescopes as well as the \Fermi-LAT at this energy. Left panel shows
-  the Fornax cluster and right panel the Virgo cluster. The gamma-ray
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Fornax.v14.SF700.SubMass.elmu.bw.eps}
+  \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v14.SF700.SubMass.elmu.bw.eps}
+\caption{\it (Color online) Surface brightness predicted for Cherenkov
+  telescopes at high energies. We show the emission above $100$~GeV
+  and include the boost from substructures. We use a point spread
+  function of $\psf=0.1\deg$ that is typical for Cherenkov telescopes
+  as well as the \Fermi-LAT at this energy. Left panel shows the
+  Fornax cluster and right panel the Virgo cluster. The gamma-ray
   emission is derived for the following components; CRs (red solid),
-  continuum emission from the DM $\Kp$ benchmark model (blue
-  dash-dotted), as well as final state radiation (green dashed) and
-  inverse Compton upscattered dust and starlight (green dotted) from
-  leptophilic DM.}
+  continuum emission from the DM $\Kp$ benchmark model (dark blue
+  dash-dotted), as well as final state radiation (light green dashed)
+  and inverse Compton upscattered dust and starlight (light green
+  dotted) from leptophilic DM.}
  \label{fig:SB_IACTs}
@@
 annihilation and CR interactions of the brightest clusters of the
-X-ray flux-complete sample in the local universe. We confront these
-predictions to upper limits obtained by \Fermi 1.5-year data and
-conclude on the viability of the underlying models and perspectives
-for the next years of \Fermi observations.
+X-ray flux-complete sample in the local universe. \C{All fluxes in
+  this section are derived within an angle corresponding to $\rvir$,
+  in addition we neglegt the smoothing over the PSF if nothing else is
+  stated.}  We confront these predictions to upper limits obtained by
+\Fermi 1.5-year data and conclude on the viability of the underlying
+models and perspectives for the next years of \Fermi observations.
 
@@
   \includegraphics[width=0.99\columnwidth]{figures/MLscaling.10G.eps}
-  \caption{\it Scaling relations of the cluster's virial mass $\mvir$
-    and the gamma-ray luminosity for energies $E_\gamma>100$~MeV
-    (left) and $E_\gamma>10$~GeV (right). Shown are the relations for
-    the CR-induced emission that is dominated by pion decay resulting
-    from hadronic CR interactions (solid), the leptophilic model of DM
-    annihilations (dash-dotted) as well as the benchmark model $K'$ of
-    DM annihilation. Both DM models include the scaling of the
-    substructure boost with cluster mass of Eq.~(\ref{eq:DM_scaling})
-    (dashed). Note that the scaling of the DM models are indicative
-    for all DM annihilation models (as long as there is no additional
-    mass scaling from, e.g., non-saturated SFE models) while the
-    normalization depends on the particular cross section and
-    neutralino mass.}
+  \caption{\it (Color online) Scaling relations of the cluster's
+    virial mass $\mvir$ and the gamma-ray luminosity for energies
+    $E_\gamma>100$~MeV (left) and $E_\gamma>10$~GeV (right). Shown are
+    the relations for the CR-induced emission that is dominated by
+    pion decay resulting from hadronic CR interactions (solid), the
+    leptophilic model of DM annihilations (dash-dotted) as well as the
+    benchmark model $K'$ of DM annihilation. Both DM models include
+    the scaling of the substructure boost with cluster mass of
+    Eq.~(\ref{eq:DM_scaling}) (dashed). Note that the scaling of the
+    DM models are indicative for all DM annihilation models (as long
+    as there is no additional mass scaling from, e.g., non-saturated
+    SFE models) while the normalization depends on the particular
+    cross section and neutralino mass.}
 \label{fig:lum_mass_scaling}
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.DM.eps}
-  \caption{\it \Fermi gamma-ray flux upper limits are contrasted to
-    predicted DM gamma-ray fluxes. We show the mean differential flux
-    in the energy range $E_\gamma=1-10$~GeV for 32 clusters. The
-    maximally extended \Fermi-LAT upper limits are shown with black
-    arrows, while the point source limits are shown in grey. The
-    predicted fluxes are derived from the dominant inverse
-    Compton-scattering of CMB photons in a leptophilic DM model (red),
-    and the continuum emission from the DM $\Kp$ benchmark model
-    (blue). Assuming a boost factor due to substructures that has a
-    mass spectrum extending down to an Earth mass, the expected
-    leptophilic fluxes are ruled out by upper limits in 28 of the
-    clusters, with the strongest constraints set by M49 and Fornax. At
-    the present time, we cannot constrain the benchmark models,
-    although \Fermi-LAT will soon start to probe these models. In
-    particular, improved modelling of extended sources as well as
-    stacking of clusters appears promising in testing benchmark
-    models.}
+  \caption{\it (Color online) \Fermi gamma-ray flux upper limits are
+    contrasted to predicted DM gamma-ray fluxes. We show the mean
+    differential flux in the energy range $E_\gamma=1-10$~GeV for 32
+    clusters. The extended \Fermi-LAT upper limits are shown with
+    black arrows (King profiles) and grey arrows (Gaussian profiles --
+    Virgo, Coma, Fornax), while the point source limits are shown in
+    light grey. The predicted fluxes are derived from the dominant
+    inverse Compton-scattering of CMB photons in a leptophilic DM
+    model (light red), and the continuum emission from the DM $\Kp$
+    benchmark model (blue). Assuming a boost factor due to
+    substructures that has a mass spectrum extending down to an Earth
+    mass, the expected leptophilic fluxes are ruled out by upper
+    limits in 28 of the clusters, with the strongest constraints set
+    by M49 and Fornax. At the present time, we cannot constrain the
+    benchmark models, although \Fermi-LAT will soon start to probe
+    these models. In particular, improved modelling of extended
+    sources as well as stacking of clusters appears promising in
+    testing benchmark models.}
  \label{fig14}
@@
  \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.DM.eps}
- \caption{\it Comparing the DM annihilation flux from clusters in the
-   extended HIFLUGCS catalogue. We show the energy integrated
-   gamma-ray fluxes derived from both leptophilic DM that result in
-   inverse Compton upscattered CMB photons (red), and the continuum
-   emission from the DM $\Kp$ benchmark model (blue). The fluxes are
-   calculated within $\rvir$ for each of the 106 clusters included in
-   the extended HIFLUGCS catalogue. The CR emission is derived using a
-   single beta profile for each cluster's gas density profile (see
-   text for details). The upper panel shows the energy integrated flux
-   above 100~MeV and the lower panel that above 10~GeV, both as a
-   function of HIFLUGCS cluster ID. For comparison we show the
-   estimated point source sensitivity of the \Fermi-LAT after two
-   years of data taking $F_\gamma(>100\,\rmn{MeV})\sim
-   2\times10^{-9}\,\rmn{ph}\, \rmn{cm}^{-2}\,\rmn{s}^{-1}$ and
-   $F_\gamma(>10\,\rmn{GeV})\sim 9\times10^{-11}\,\rmn{ph}\,
-   \rmn{cm}^{-2}\,\rmn{s}^{-1}$ (dashed lines). The four brightest
-   clusters are labelled yielding M49 and Fornax as the brightest
-   targets.}
+ \caption{\it (Color online) Comparing the DM annihilation flux from
+   clusters in the extended HIFLUGCS catalogue. We show the energy
+   integrated gamma-ray fluxes derived from both leptophilic DM that
+   result in inverse Compton upscattered CMB photons (light red), and
+   the continuum emission from the DM $\Kp$ benchmark model
+   (blue). The fluxes are calculated within $\rvir$ for each of the
+   106 clusters included in the extended HIFLUGCS catalogue. The CR
+   emission is derived using a single beta profile for each cluster's
+   gas density profile (see text for details). The upper panel shows
+   the energy integrated flux above 100~MeV and the lower panel that
+   above 10~GeV, both as a function of HIFLUGCS cluster ID. For
+   comparison we show the estimated point source sensitivity of the
+   \Fermi-LAT after two years of data taking
+   $F_\gamma(>100\,\rmn{MeV})\sim 2\times10^{-9}\,\rmn{ph}\,
+   \rmn{cm}^{-2}\,\rmn{s}^{-1}$ and $F_\gamma(>10\,\rmn{GeV})\sim
+   9\times10^{-11}\,\rmn{ph}\, \rmn{cm}^{-2}\,\rmn{s}^{-1}$ (dashed
+   lines). The four brightest clusters are labelled yielding M49 and
+   Fornax as the brightest targets.}
  \label{fig21}
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.CR.diff.eps}
-  \caption{\it We contrast predictions of the CR induced gamma-ray
-    emission using an analytical CR model \protect
+  \caption{\it (Color online) We contrast predictions of the CR
+    induced gamma-ray emission using an analytical CR model \protect
     \cite{2010MNRAS.409..449P} to \Fermi-LAT flux upper limits. We
@@
 
-We highlight two main uncertainties of the models, namely the
+\del{We highlight two main uncertainties of the models, namely the
   acceleration efficiency at formation shocks and CR transport
   parameters. First, we note that both models assume the maximally
-allowed acceleration efficiency for {\em strong} shocks that transfers
-50\% of the shock-dissipated energy (kinetic energy corrected for
-adiabatic compressional heating at the shock) to CRs. These
-efficiencies drop quickly for weaker shocks \cite{2007A&A...473...41E}
-which dominate the gravitational energy dissipation inside galaxy
-clusters \cite{2006MNRAS.367..113P}. These efficiencies will have to
-be corrected down if this value is not realized at strong structure formation
-shocks. Second, these simulations (and by extension the analytic
-model) neglect active CR transport such as streaming and diffusion
-relative to the gas, i.e., we assume that advective transport
-dominates and CRs are tightly coupled to the gas via flux-frozen
-magnetic fields tangled on sufficiently small scales. Evidence from
-the statistics of radio halos suggests that this might not be the case
-for relaxed clusters, arguing that CR streaming (and diffusion) in
-those objects could be responsible for a decrease in the central CR
-number density. This effect would also reduce the expected gamma-ray
-flux by up to a factor of five \cite{2011A&A...527A..99E}.
+  allowed acceleration efficiency for {\em strong} shocks that
+  transfers 50\% of the shock-dissipated energy (kinetic energy
+  corrected for adiabatic compressional heating at the shock) to
+  CRs. These efficiencies drop quickly for weaker shocks
+  \cite{2007A&A...473...41E} which dominate the gravitational energy
+  dissipation inside galaxy clusters \cite{2006MNRAS.367..113P}. These
+  efficiencies will have to be corrected down if this value is not
+  realized at strong structure formation shocks. Second, these
+  simulations (and by extension the analytic model) neglect active CR
+  transport such as streaming and diffusion relative to the gas, i.e.,
+  we assume that advective transport dominates and CRs are tightly
+  coupled to the gas via flux-frozen magnetic fields tangled on
+  sufficiently small scales. Evidence from the statistics of radio
+  halos suggests that this might not be the case for relaxed clusters,
+  arguing that CR streaming (and diffusion) in those objects could be
+  responsible for a decrease in the central CR number density. This
+  effect would also reduce the expected gamma-ray flux by up to a
+  factor of five \cite{2011A&A...527A..99E}.}
 
@@
 constraining clusters suggesting that stacking of clusters will be
-able to improve these limits (provided these analyses adopt the
+able to improve these limits (provided these analysis adopt the
 simulation-based analytic model \cite{2010MNRAS.409..449P} as a
@@
 
-In this paper, we study the possibility for detecting gamma-ray emission in
-galaxy clusters. We consider benchmark (BM) and leptophilic (LP) models of
-supersymmetric dark matter (DM) as well as cosmic ray (CR) induced pion decay
-which is thought to dominate the astrophysical signal from clusters.
-
-{\em Dark matter annihilation.} Once supersymmetric cold DM decouples from the
-expanding universe it streams and erases any potentially present smaller
-scales. When gravitational instability causes halos to collapse, this
-free-streaming scale imprints as a characteristic minimum halo mass
-$M_\mathrm{min}$ into the hierarchy of structure formation and should still
-survive until the present time as a mass cutoff in the substructure mass
-function within larger halos. We show that the boost due to substructures
-dominates over the smooth component for halo masses $\mvir>10^3 \msun$ and
-contributes a constant luminosity for each decade in subhalo mass. The ratio of
-halo-to-minimum subhalo mass $\mvir/M_\mathrm{min}$ is maximized for the largest
-virialized systems in the Universe---galaxy clusters. The corresponding
-substructure boost can reach values exceeding $10^3$ which should make nearby
-clusters the brightest DM annihilation sources after the MW center and
-hypothetical very close-by DM substructures. We stress that this conclusion
-relies on two hypotheses that are still open problems in particle physics and
-numerical cosmology. We assume (i) the existence of cold DM, i.e., the density
-fluctuation power spectrum extends down to the DM free streaming scale of about
-an Earth mass, and (ii) assume that structure formation at scales smaller than
-currently resolved ones ($\sim 10^5\,\msun$) proceeds scale-invariant, i.e.,
-there is no non-linear mode coupling between different scales. This could
-potentially erase structures smaller than a characteristic one as the linear
-power spectrum approaches $\Delta^2(k) \propto k^3 P(k)=\rmn{const.}$ implying
-that structure on different scales may not form any more hierarchically, but may
-collapse at the same time.
-
-Since the mass density of substructures peaks at radii close to $\rvir$, the
-contribution to the annihilation emission from substructures is also dominated
-from these outer cluster regions.  This implies an almost flat surface
-brightness profile of the annihilation emission which makes it necessary to have
-the entire cluster in the field-of-view to take advantage of the total
-substructure boost. This property makes it difficult to detect DM annihilation
-emission without an enhancement of the particle physics cross section over its
-standard value of $\sigma v\sim 3\times 10^{-26} ~\mathrm{cm}^3~\mathrm{s}^{-1}$
-with imaging air Cherenkov telescopes due to the spatially extended boost from
-substructures over an angular extent of $\sim 0.5-1\deg$ (as independently found
-by reference \cite{2011arXiv1104.3530S}). This large angular extent is not well
-matched with the sensitivity of Cherenkov telescopes which drops approximately
-linearly with radius outside the point spread function (with a characteristic
-scale of $\sim 0.1\deg$), unless new background subtraction schemes can be
-found, e.g., for the survey mode of CTA.
-
-In this work, we thoroughly study the spectral emission characteristics of the
-DM emission. In general there are different radiation mechanism that emit in the
-gamma-ray regime, namely (i) continuum emission following the hadronization of
-the annihilating neutralinos in BM models which leads to the production of
-charged and neutral mesons which decay finally into electrons, neutrinos, and
-gammas, (ii) inverse Compton (IC) emission by the leptons in the final state
-which up-scatter radiation fields from the cosmic microwave background (CMB),
-dust, and starlight, and (iii) final state radiation or internal bremsstrahlung
-which dominates the highest energy emission close to the rest mass of the
+\C{In this paper, we study the possibility for detecting gamma-ray
+  emission in galaxy clusters. We consider benchmark (BM) and
+  leptophilic (LP) models of supersymmetric dark matter (DM) as well
+  as cosmic ray (CR) induced pion decay which is thought to dominate
+  the astrophysical signal from clusters.}
+
+\C{{\em Dark matter annihilation.} Once supersymmetric cold DM
+  decouples from the expanding universe it streams and erases any
+  potentially present smaller scales. When gravitational instability
+  causes halos to collapse, this free-streaming scale imprints as a
+  characteristic minimum halo mass $M_\mathrm{min}$ into the hierarchy
+  of structure formation and should still survive until the present
+  time as a mass cutoff in the substructure mass function within
+  larger halos. We show that the boost due to substructures dominates
+  over the smooth component for halo masses $\mvir>10^3 \msun$ and
+  contributes a constant luminosity for each decade in subhalo
+  mass. The ratio of halo-to-minimum subhalo mass
+  $\mvir/M_\mathrm{min}$ is maximized for the largest virialized
+  systems in the Universe---galaxy clusters. The corresponding
+  substructure boost can reach values exceeding $10^3$ which should
+  make nearby clusters the brightest DM annihilation sources after the
+  MW center and hypothetical very close-by DM substructures. We stress
+  that this conclusion relies on two hypotheses that are still open
+  problems in particle physics and numerical cosmology. We assume (i)
+  the existence of cold DM, i.e., the density fluctuation power
+  spectrum extends down to the DM free streaming scale of about an
+  Earth mass, and (ii) assume that structure formation at scales
+  smaller than currently resolved ones ($\sim 10^5\,\msun$) proceeds
+  scale-invariant, i.e., there is no non-linear mode coupling between
+  different scales. This could potentially erase structures smaller
+  than a characteristic one as the linear power spectrum approaches
+  $\Delta^2(k) \propto k^3 P(k)=\rmn{const.}$, implying that structure
+  on different scales may not form any more hierarchically, but may
+  collapse at the same time.}
+
+\C{Since the mass density of substructures peaks at radii close to
+  $\rvir$, the contribution to the annihilation emission from
+  substructures is also dominated from these outer cluster regions.
+  This implies an almost flat surface brightness profile of the
+  annihilation emission which makes it necessary to have the entire
+  cluster in the field-of-view to take advantage of the total
+  substructure boost. This property makes it difficult to detect DM
+  annihilation emission without an enhancement of the particle physics
+  cross section over its standard value of $\sigma v\sim 3\times
+  10^{-26} ~\mathrm{cm}^3~\mathrm{s}^{-1}$ with imaging air Cherenkov
+  telescopes due to the spatially extended boost from substructures
+  over an angular extent of $\sim 0.5-1\deg$ (as independently found
+  by reference \cite{2011arXiv1104.3530S}). This large angular extent
+  is not well matched with the sensitivity of Cherenkov telescopes
+  which drops approximately linearly with radius outside the point
+  spread function (with a characteristic scale of $\sim 0.1\deg$),
+  unless new background subtraction schemes can be found, e.g., for
+  the survey mode of CTA.}
+
+\C{In this work, we thoroughly study the spectral emission
+  characteristics of the DM emission. In general there are different
+  radiation mechanism that emit in the gamma-ray regime, namely (i)
+  continuum emission following the hadronization of the annihilating
+  neutralinos in BM models which leads to the production of charged
+  and neutral mesons which decay finally into electrons, neutrinos,
+  and gammas, (ii) inverse Compton (IC) emission by the leptons in the
+  final state which up-scatter radiation fields from the cosmic
+  microwave background (CMB), dust, and starlight, and (iii) final
+  state radiation or internal bremsstrahlung which dominates the
+  highest energy emission close to the rest mass of the
   self-annihilating neutralinos (if present in the model under
-consideration).\footnote{While this final state radiation is sometimes not
-  distinguished from the continuum emission contribution, we keep it separate as
-  it dominates the very high-energy tail of the gamma-ray spectrum in LP models
-  while there the continuum emission is negligibly low.}
-
-For the first time, we compute the IC emission component not only from the
-upscattered CMB photons but also from a realistically modeled photon field due
-to dust and starlight extending from infra-red to optical wavelengths. To this
-end, we construct a rather simple analytic model for the spatial and spectral
-distribution of dust and starlight in clusters (which can also be used for the
+  consideration).\footnote{While this final state radiation is
+    sometimes not distinguished from the continuum emission
+    contribution, we keep it separate as it dominates the very
+    high-energy tail of the gamma-ray spectrum in LP models while
+    there the continuum emission is negligibly low.}}
+
+\C{For the first time, we compute the IC emission component not only
+  from the upscattered CMB photons but also from a realistically
+  modeled photon field due to dust and starlight extending from
+  infra-red to optical wavelengths. To this end, we construct a rather
+  simple analytic model for the spatial and spectral distribution of
+  dust and starlight in clusters (which can also be used for the
   annihilation emission in galaxies after adopting a different spatial
-profile). We find that in BM models, the continuum emission dominates over the
-IC emission of any available radiation field. In the LP models, where the
-continuum emission is low, the IC up-scattering of the CMB dominates below 60
-GeV. For larger energies, the final state radiation dominates the emission up to
-the cutoff at $m_\chi c^2 \sim 1$~TeV. The IC up-scattering of the dust and
-starlight is always subdominant compared to the upscattered CMB (below 60~GeV)
-and the final state radiation (above 60~GeV). We stress, that the inclusion of
-the dust and starlight radiation fields are negligible in the cooling function
-for the leptons. The main reason why the IC emission from starlight and dust
-remains subdominant is the small overlap of this component with the peripherally
-peaked substructure mass density profiles. If for some reason, DM has less
-substructure, the relative importance of this IC component increases
-considerably.
-
-We identify Virgo, Fornax and M49 to be the best cluster/group candidates for
-indirect DM studies as they are expected to emit the brightest annihilation
-flux.\footnote{We excluded Virgo from our further analysis due to its large
-  angular extent that needs a separate treatment.} More importantly, Fornax has
-a comparably low CR-induced gamma-ray flux which may enable an indirect DM
-detection or a particularly tight limit on DM properties. Other nearby bright
-sources of the extended HIFLUGCS sample are Ophiuchus, and Centaurus.
-
-The non-detection of gamma-ray emission by \Fermi in a total of 28
-clusters/groups considerably constrains LP models for DM annihilation which were
-introduced to explain the increasing positron-to-lepton ratio beyond 10
-GeV. Assuming that the minimum DM substructure mass extends down to an Earth
-mass and that the DM annihilation flux is dominated by small scale substructure,
-we limit the saturated Sommerfeld enhancement factor in M49 and Fornax to
-$\lesssim 5$. This corresponds to a value in the Milky Way (MW) of $\lesssim3$,
-due to the larger Sommerfeld boost factor in smaller mass halos which have a
-lower velocity dispersion that enhances the particle cross section (while
-assuming universality of the DM model). This would rule out LP models in their
-current form based on the non-observation of gamma-rays in any of the
-fore-mentioned clusters/groups and hence strongly challenge the DM
-interpretation of the increasing positron fraction with energy as seen by
-PAMELA. Alternatively, assuming the LP models to be correct, this would limit
-the minimum substructure mass to $>10^4~\msun$ in M49 and Fornax which presents
-a problem for structure formation in most particle physics models
-\cite{2009NJPh...11j5027B}.
-
-{\em Cosmic ray-induced emission.} We substantially improve the modelling of the
-expected gamma-ray signal from pion-decay resulting from hadronic CR
-interactions with gas protons over previous work \cite{2010ApJ...717L..71A}. We
-employ the analytic model of the CR spectrum and spatial distribution that is
-based on cosmological hydrodynamical simulations of galaxy clusters that
-self-consistently follow the evolution of CRs in cosmic structure formation
-\cite{2010MNRAS.409..449P}. Adopting the model for all clusters in the HIFLUGCS
-sample of flux-limited X-ray clusters, we compare the expected gamma-ray
-emission to that inferred from using an $L_\gamma-\mvir$ scaling relation. We note
-that the predictions of the ``optimistic'' model in \cite{2010MNRAS.409..449P}
-are in tension with \Fermi upper limits for Norma, Coma, and Ophiuchus. In the
-next 2-3 years \Fermi will be able to probe the predictions of their
-``conservative'' CR model. This will enable us to put realistic limits on a
-combination of the acceleration efficiency of CRs in structure formation shocks
-and CR transport coefficients in clusters.
-
-As expected, the analytical CR model accounts for the ``scatter'' in the scaling
-relation and biases the gamma-ray flux high for prominent cool core clusters by
-up to a factor of 10 relative to the expectation from the scaling relation. This
-is due to the high target gas densities and associated CR densities in those
-cool cores that shape the spatial emission characteristic to be very similar to
-that observed in thermal X-rays. We caution that these predictions only apply
-for the case of negligible active CR transport such as CR streaming and
-diffusion relative to the gas. Gamma-ray fluxes might be considerably smaller in
-those cluster that do not show an extended diffuse radio(-mini) halo that might
-point to a centrally concentrated CR distribution
-\cite{2011A&A...527A..99E}. The CR spectrum $E^2 dN/dE$ shows the characteristic
-pion bump at energies around 1~GeV. It is expected to dominate the DM
-annihilation signal of BM models for clusters/groups, although we find that the
-gamma-ray flux induced by the BM is higher for about 1/5 of the clusters in the
-HIFLUGCS catalogue, where Fornax and M49 have the highest signal-to-noise
-ratio. (Note that we only include the cluster-intrinsic CR foreground and do not
-consider the dominant galactic and instrumental noise sources here.) We find that
-\Fermi-LAT will be able to start constraining these DM models within five years
-using clusters of galaxies.
-
-Combining extended \Fermi upper limits and our model flux predictions, we limit
-the relative CR pressure, $X_\CR = P_\CR/P_\rmn{th}$, in 32 nearby bright galaxy
-clusters of the \Fermi sample. The best limits are found in Norma and Coma of
-the order of 3\%, with typical limits around 10\%. This is comparable to those
-inferred by the \Fermi collaboration \cite{2010ApJ...717L..71A} and mainly due
-to the differently assumed Bayesian prior on the CR pressure which implies a
-different cluster mass dependence of the resulting limits on $X_\CR$.
+  profile). We find that in BM models, the continuum emission
+  dominates over the IC emission of any available radiation field. In
+  the LP models, where the continuum emission is low, the IC
+  up-scattering of the CMB dominates below 60 GeV. For larger
+  energies, the final state radiation dominates the emission up to the
+  cutoff at $m_\chi c^2 \sim 1$~TeV. The IC up-scattering of the dust
+  and starlight is always subdominant compared to the upscattered CMB
+  (below 60~GeV) and the final state radiation (above 60~GeV). We
+  stress, that the inclusion of the dust and starlight radiation
+  fields are negligible in the cooling function for the leptons. The
+  main reason why the IC emission from starlight and dust remains
+  subdominant is the small overlap of this component with the
+  peripherally peaked substructure mass density profiles. If for some
+  reason, DM has less substructure, the relative importance of this IC
+  component increases considerably.}
+
+\C{We identify Virgo, Fornax and M49 to be the best cluster/group
+  candidates for indirect DM studies as they are expected to emit the
+  brightest annihilation flux.\footnote{We excluded Virgo from our
+    further analysis due to its large angular extent that needs a
+    separate treatment.} More importantly, Fornax has a comparably low
+  CR-induced gamma-ray flux which may enable an indirect DM detection
+  or a particularly tight limit on DM properties. Other nearby bright
+  sources of the extended HIFLUGCS sample are Ophiuchus, and
+  Centaurus.}
+
+\C{The non-detection of gamma-ray emission by \Fermi in a total of 28
+  clusters/groups considerably constrains LP models for DM
+  annihilation which were introduced to explain the increasing
+  positron-to-lepton ratio beyond 10 GeV. Assuming that the minimum DM
+  substructure mass extends down to an Earth mass and that the DM
+  annihilation flux is dominated by small scale substructure, we limit
+  the saturated Sommerfeld enhancement factor in M49 and Fornax to
+  $\lesssim 5$. This corresponds to a value in the Milky Way (MW) of
+  $\lesssim3$, due to the larger Sommerfeld boost factor in smaller
+  mass halos which have a lower velocity dispersion that enhances the
+  particle cross section (while assuming universality of the DM
+  model). This would rule out LP models in their current form based on
+  the non-observation of gamma-rays in any of the fore-mentioned
+  clusters/groups and hence strongly challenge the DM interpretation
+  of the increasing positron fraction with energy as seen by
+  PAMELA. Alternatively, assuming the LP models to be correct, this
+  would limit the minimum substructure mass to $>10^4~\msun$ in M49
+  and Fornax which presents a problem for structure formation in most
+  particle physics models \cite{2009NJPh...11j5027B}.}
+
+\C{{\em Cosmic ray-induced emission.} We substantially improve the
+  modelling of the expected gamma-ray signal from pion-decay resulting
+  from hadronic CR interactions with gas protons over previous work
+  \cite{2010ApJ...717L..71A}. We employ the analytic model of the CR
+  spectrum and spatial distribution that is based on cosmological
+  hydrodynamical simulations of galaxy clusters that self-consistently
+  follow the evolution of CRs in cosmic structure formation
+  \cite{2010MNRAS.409..449P}. Adopting the model for all clusters in
+  the HIFLUGCS sample of flux-limited X-ray clusters, we compare the
+  expected gamma-ray emission to that inferred from using an
+  $L_\gamma-\mvir$ scaling relation. We note that the predictions of
+  the ``optimistic'' model in \cite{2010MNRAS.409..449P} are in
+  tension with \Fermi upper limits for Norma, Coma, and Ophiuchus. In
+  the next 2-3 years \Fermi will be able to probe the predictions of
+  their ``conservative'' CR model. This will enable us to put
+  realistic limits on a combination of the acceleration efficiency of
+  CRs in structure formation shocks and CR transport coefficients in
+  clusters.}
+
+\C{As expected, the analytical CR model accounts for the ``scatter''
+  in the scaling relation and biases the gamma-ray flux high for
+  prominent cool core clusters by up to a factor of 10 relative to the
+  expectation from the scaling relation. This is due to the high
+  target gas densities and associated CR densities in those cool cores
+  that shape the spatial emission characteristic to be very similar to
+  that observed in thermal X-rays. We caution that these predictions
+  only apply for the case of negligible active CR transport such as CR
+  streaming and diffusion relative to the gas. Gamma-ray fluxes might
+  be considerably smaller in those cluster that do not show an
+  extended diffuse radio(-mini) halo that might point to a centrally
+  concentrated CR distribution \cite{2011A&A...527A..99E}. The CR
+  spectrum $E^2 dN/dE$ shows the characteristic pion bump at energies
+  around 1~GeV. It is expected to dominate the DM annihilation signal
+  of BM models for clusters/groups, although we find that the
+  gamma-ray flux induced by the BM is higher for about 1/5 of the
+  clusters in the HIFLUGCS catalogue, where Fornax and M49 have the
+  highest signal-to-noise ratio. (Note that we only include the
+  cluster-intrinsic CR foreground and do not consider the dominant
+  galactic and instrumental noise sources here.) We find that
+  \Fermi-LAT will be able to start constraining these DM models within
+  five years using clusters of galaxies.}
+
+\C{Combining extended \Fermi upper limits and our model flux
+  predictions, we limit the relative CR pressure, $X_\CR =
+  P_\CR/P_\rmn{th}$, in 32 nearby bright galaxy clusters of the \Fermi
+  sample. The best limits are found in Norma and Coma of the order of
+  3\%, with typical limits around 10\%. This is comparable to those
+  inferred by the \Fermi collaboration \cite{2010ApJ...717L..71A} and
+  mainly due to the differently assumed Bayesian prior on the CR
+  pressure which implies a different cluster mass dependence of the
+  resulting limits on $X_\CR$.}
 
@@
 dependent normalization for the SD. This function is determined using
-the total energy of the light from SD within $\rvir$ which is
+the total energy of the light from SD within $\rvir$, which is
 represented by $E_{i,\vir}$. We relate this energy to the luminosity
@@
 
-The {\em luminosity from star light} is given by
+The {\em luminosity from starlight} is given by
 \begin{eqnarray}
@@
 
-%***********************************************
-
 \section{Source functions of different DM models}
@@
 \begin{minipage}{2.0\columnwidth}
-\caption{Electron number density profiles for selected clusters.}
 \begin{tabular}{ccccccccccc}
@@
 \end{tabular}
-\caption{
- \label{tab:dens_prof}}
+\caption{Electron number density profiles for selected
+  clusters. \label{tab:dens_prof}}
 \end{minipage}
@@
 \begin{figure}%[t]
- \includegraphics[width=0.99\columnwidth]{figures/dens.fornax.eps}
- \caption{\it Comparing different electron number density profiles for
-   the Fornax cluster. Black crosses show the density profile inferred
-   from deprojected deep Rosat X-ray surface brightness observations
-   \protect \cite{2002ApJ...565..883P}. The total hybrid profile shown
-   by the red solid line represent the best fit to the data, where the
-   fitted individual density components are shown by the black dotted
-   lines. The blue solid line shows the single beta density profile
-   inferred from the HIFLUGCS catalogue. Due to insufficient
-   sensitivity of the data to the outer cluster part, we use the outer
-   slope from the HIFLUGCS catalogue \cite{2007A&A...466..805C}.}
+ \includegraphics[width=0.99\columnwidth]{figures/dens.fornax.bw.eps}
+ \caption{\it (Color online) Comparing different electron number
+   density profiles for the Fornax cluster. Black crosses show the
+   density profile inferred from deprojected deep Rosat X-ray surface
+   brightness observations \protect \cite{2002ApJ...565..883P}. The
+   total hybrid profile shown by the red solid line represent the best
+   fit to the data, where the fitted individual density components are
+   shown by the black dotted lines. The blue dashed line shows the
+   single beta density profile inferred from the HIFLUGCS
+   catalogue. Due to insufficient sensitivity of the data to the outer
+   cluster part, we use the outer slope from the HIFLUGCS catalogue
+   \cite{2007A&A...466..805C}.}
  \label{fig:dens_fornax}
@@
  \hline
-PERSEUS & 68 & 14.28 & 19.15 & 52.49 & 16.26 & 16.25 & 10.06 \\
-OPHIUCHU & 96 & 7.71 & 10.34 & 28.33 & 8.78 & 8.78 & 6.01 \\
-COMA & 34 & 4.15 & 5.56 & 15.24 & 4.72 & 4.72 & 2.55 \\
-NORMA & 94 & 2.98 & 3.99 & 10.94 & 3.39 & 3.38 & 2.19 \\
-CENTAURU & 30 & 2.61 & 3.50 & 9.58 & 2.97 & 2.97 & 2.62 \\
-TRIANGUL & 95 & 1.77 & 2.37 & 6.50 & 2.01 & 2.01 & 0.37 \\
-AWM7 & 67 & 1.75 & 2.35 & 6.43 & 1.99 & 1.99 & 1.24 \\
-A2319 & 98 & 1.71 & 2.30 & 6.30 & 1.95 & 1.94 & 0.28 \\
-A3571 & 39 & 1.61 & 2.15 & 5.90 & 1.83 & 1.82 & 0.41 \\
-3C129 & 70 & 1.35 & 1.82 & 4.98 & 1.54 & 1.54 & 0.71 \\
-A2199 & 51 & 1.11 & 1.49 & 4.10 & 1.27 & 1.27 & 0.33 \\
-2A0335 & 11 & 1.04 & 1.40 & 3.83 & 1.19 & 1.19 & 0.19 \\
-A2029 & 43 & 1.04 & 1.39 & 3.81 & 1.18 & 1.17 & 0.08 \\
-A0496 & 18 & 1.02 & 1.36 & 3.73 & 1.16 & 1.15 & 0.27 \\
-HYDRA & 25 & 0.95 & 1.27 & 3.48 & 1.08 & 1.08 & 0.84 \\
-A0085 & 1 & 0.93 & 1.25 & 3.44 & 1.06 & 1.06 & 0.12 \\
-A2142 & 48 & 0.92 & 1.24 & 3.39 & 1.05 & 1.04 & 0.06 \\
-A3266 & 17 & 0.92 & 1.23 & 3.37 & 1.05 & 1.04 & 0.16 \\
-A1795 & 40 & 0.91 & 1.22 & 3.35 & 1.04 & 1.04 & 0.11 \\
-PKS0745 & 77 & 0.82 & 1.10 & 3.02 & 0.94 & 0.88 & 0.03 \\
-A2256 & 54 & 0.78 & 1.04 & 2.86 & 0.89 & 0.88 & 0.11 \\
-A3558 & 37 & 0.75 & 1.01 & 2.77 & 0.86 & 0.86 & 0.12 \\
-A3667 & 56 & 0.71 & 0.96 & 2.62 & 0.81 & 0.80 & 0.07 \\
-A1367 & 26 & 0.70 & 0.94 & 2.59 & 0.80 & 0.80 & 0.43 \\
-A0478 & 14 & 0.68 & 0.91 & 2.48 & 0.77 & 0.75 & 0.03 \\
-A0401 & 8 & 0.61 & 0.82 & 2.25 & 0.70 & 0.68 & 0.05 \\
-A0262 & 5 & 0.57 & 0.77 & 2.10 & 0.65 & 0.65 & 0.26 \\
-HYDRA-A & 24 & 0.56 & 0.75 & 2.05 & 0.63 & 0.63 & 0.05 \\
-A0754 & 23 & 0.52 & 0.70 & 1.92 & 0.59 & 0.59 & 0.10 \\
-A4038 & 62 & 0.52 & 0.69 & 1.90 & 0.59 & 0.59 & 0.13 \\
-A2052 & 44 & 0.51 & 0.68 & 1.87 & 0.58 & 0.58 & 0.09 \\
-A2147 & 49 & 0.50 & 0.66 & 1.82 & 0.56 & 0.55 & 0.11 \\
-A0119 & 2 & 0.48 & 0.64 & 1.76 & 0.54 & 0.54 & 0.10 \\
-A0644 & 78 & 0.47 & 0.63 & 1.73 & 0.54 & 0.53 & 0.04 \\
-A1644 & 31 & 0.43 & 0.58 & 1.60 & 0.49 & 0.49 & 0.07 \\
-A3158 & 13 & 0.39 & 0.53 & 1.45 & 0.45 & 0.44 & 0.04 \\
-FORNAX & 10 & 0.36 & 0.49 & 1.34 & 0.42 & 0.42 & 0.41 \\
-A2063 & 47 & 0.36 & 0.48 & 1.33 & 0.41 & 0.41 & 0.06 \\
-MKW3S & 45 & 0.35 & 0.47 & 1.29 & 0.40 & 0.40 & 0.04 \\
-A3112 & 9 & 0.34 & 0.46 & 1.26 & 0.39 & 0.38 & 0.02 \\
-ZwCl1742 & 97 & 0.34 & 0.46 & 1.25 & 0.39 & 0.38 & 0.03 \\
-A4059 & 63 & 0.33 & 0.45 & 1.23 & 0.38 & 0.38 & 0.05 \\
-A1651 & 33 & 0.31 & 0.41 & 1.13 & 0.35 & 0.34 & 0.02 \\
-A0399 & 7 & 0.31 & 0.41 & 1.13 & 0.35 & 0.34 & 0.02 \\
-NGC1550 & 15 & 0.30 & 0.40 & 1.09 & 0.34 & 0.34 & 0.16 \\
-ANTLIA & 79 & 0.29 & 0.39 & 1.06 & 0.33 & 0.33 & 0.22 \\
-A2657 & 61 & 0.29 & 0.38 & 1.05 & 0.32 & 0.32 & 0.06 \\
-A0539 & 71 & 0.28 & 0.38 & 1.03 & 0.32 & 0.32 & 0.07 \\
-A3581 & 41 & 0.28 & 0.37 & 1.03 & 0.32 & 0.32 & 0.07 \\
-A2204 & 52 & 0.28 & 0.37 & 1.02 & 0.32 & 0.21 & 0.01 \\
+PERSEUS  &  68 &  14.28 &  19.15 &  52.49 &  16.26 &  16.25 &  10.06 \vstt \\
+OPHIUCHU &  96 &   7.71 &  10.34 &  28.33 &   8.78 &   8.78 &   6.01 \vstt \\
+COMA     &  34 &   4.15 &   5.56 &  15.24 &   4.72 &   4.72 &   2.55 \vstt \\
+NORMA    &  94 &   2.98 &   3.99 &  10.94 &   3.39 &   3.38 &   2.19 \vstt \\
+CENTAURU &  30 &   2.61 &   3.50 &   9.58 &   2.97 &   2.97 &   2.62 \vstt \\
+TRIANGUL &  95 &   1.77 &   2.37 &   6.50 &   2.01 &   2.01 &   0.37 \vstt \\
+AWM7     &  67 &   1.75 &   2.35 &   6.43 &   1.99 &   1.99 &   1.24 \vstt \\
+A2319    &  98 &   1.71 &   2.30 &   6.30 &   1.95 &   1.94 &   0.28 \vstt \\
+A3571    &  39 &   1.61 &   2.15 &   5.90 &   1.83 &   1.82 &   0.41 \vstt \\
+3C129    &  70 &   1.35 &   1.82 &   4.98 &   1.54 &   1.54 &   0.71 \vstt \\
+A2199    &  51 &   1.11 &   1.49 &   4.10 &   1.27 &   1.27 &   0.33 \vstt \\
+2A0335   &  11 &   1.04 &   1.40 &   3.83 &   1.19 &   1.19 &   0.19 \vstt \\
+A2029    &  43 &   1.04 &   1.39 &   3.81 &   1.18 &   1.17 &   0.08 \vstt \\
+A0496    &  18 &   1.02 &   1.36 &   3.73 &   1.16 &   1.15 &   0.27 \vstt \\
+HYDRA    &  25 &   0.95 &   1.27 &   3.48 &   1.08 &   1.08 &   0.84 \vstt \\
+A0085    &   1 &   0.93 &   1.25 &   3.44 &   1.06 &   1.06 &   0.12 \vstt \\
+A2142    &  48 &   0.92 &   1.24 &   3.39 &   1.05 &   1.04 &   0.06 \vstt \\
+A3266    &  17 &   0.92 &   1.23 &   3.37 &   1.05 &   1.04 &   0.16 \vstt \\
+A1795    &  40 &   0.91 &   1.22 &   3.35 &   1.04 &   1.04 &   0.11 \vstt \\
+PKS0745  &  77 &   0.82 &   1.10 &   3.02 &   0.94 &   0.88 &   0.03 \vstt \\
+A2256    &  54 &   0.78 &   1.04 &   2.86 &   0.89 &   0.88 &   0.11 \vstt \\
+A3558    &  37 &   0.75 &   1.01 &   2.77 &   0.86 &   0.86 &   0.12 \vstt \\
+A3667    &  56 &   0.71 &   0.96 &   2.62 &   0.81 &   0.80 &   0.07 \vstt \\
+A1367    &  26 &   0.70 &   0.94 &   2.59 &   0.80 &   0.80 &   0.43 \vstt \\
+A0478    &  14 &   0.68 &   0.91 &   2.48 &   0.77 &   0.75 &   0.03 \vstt \\
+A0401    &   8 &   0.61 &   0.82 &   2.25 &   0.70 &   0.68 &   0.05 \vstt \\
+A0262    &   5 &   0.57 &   0.77 &   2.10 &   0.65 &   0.65 &   0.26 \vstt \\
+HYDRA-A  &  24 &   0.56 &   0.75 &   2.05 &   0.63 &   0.63 &   0.05 \vstt \\
+A0754    &  23 &   0.52 &   0.70 &   1.92 &   0.59 &   0.59 &   0.10 \vstt \\
+A4038    &  62 &   0.52 &   0.69 &   1.90 &   0.59 &   0.59 &   0.13 \vstt \\
+A2052    &  44 &   0.51 &   0.68 &   1.87 &   0.58 &   0.58 &   0.09 \vstt \\
+A2147    &  49 &   0.50 &   0.66 &   1.82 &   0.56 &   0.55 &   0.11 \vstt \\
+A0119    &   2 &   0.48 &   0.64 &   1.76 &   0.54 &   0.54 &   0.10 \vstt \\
+A0644    &  78 &   0.47 &   0.63 &   1.73 &   0.54 &   0.53 &   0.04 \vstt \\
+A1644    &  31 &   0.43 &   0.58 &   1.60 &   0.49 &   0.49 &   0.07 \vstt \\
+A3158    &  13 &   0.39 &   0.53 &   1.45 &   0.45 &   0.44 &   0.04 \vstt \\
+FORNAX   &  10 &   0.36 &   0.49 &   1.34 &   0.42 &   0.42 &   0.41 \vstt \\
+A2063    &  47 &   0.36 &   0.48 &   1.33 &   0.41 &   0.41 &   0.06 \vstt \\
+MKW3S    &  45 &   0.35 &   0.47 &   1.29 &   0.40 &   0.40 &   0.04 \vstt \\
+A3112    &   9 &   0.34 &   0.46 &   1.26 &   0.39 &   0.38 &   0.02 \vstt \\
+ZwCl1742 &  97 &   0.34 &   0.46 &   1.25 &   0.39 &   0.38 &   0.03 \vstt \\
+A4059    &  63 &   0.33 &   0.45 &   1.23 &   0.38 &   0.38 &   0.05 \vstt \\
+A1651    &  33 &   0.31 &   0.41 &   1.13 &   0.35 &   0.34 &   0.02 \vstt \\
+A0399    &   7 &   0.31 &   0.41 &   1.13 &   0.35 &   0.34 &   0.02 \vstt \\
+NGC1550  &  15 &   0.30 &   0.40 &   1.09 &   0.34 &   0.34 &   0.16 \vstt \\
+ANTLIA   &  79 &   0.29 &   0.39 &   1.06 &   0.33 &   0.33 &   0.22 \vstt \\
+A2657    &  61 &   0.29 &   0.38 &   1.05 &   0.32 &   0.32 &   0.06 \vstt \\
+A0539    &  71 &   0.28 &   0.38 &   1.03 &   0.32 &   0.32 &   0.07 \vstt \\
+A3581    &  41 &   0.28 &   0.37 &   1.03 &   0.32 &   0.32 &   0.07 \vstt \\
+A2204    &  52 &   0.28 &   0.37 &   1.02 &   0.32 &   0.21 &   0.01 \vstt \\
 \hline
@@
  \hline
-FORNAX & 10 & 31.88 & 20.21 & 11.15 & 32.00 & 31.98 & 30.27 & 9.93 \\
-M49 & 81 & 19.48 & 12.35 & 6.81 & 19.55 & 19.54 & 18.13 & 9.29 \\
-OPHIUCHU & 96 & 18.13 & 11.49 & 6.34 & 18.19 & 18.14 & 12.31 & 1.66 \\
-CENTAURU & 30 & 14.99 & 9.50 & 5.24 & 15.05 & 15.02 & 12.40 & 2.32 \\
-HYDRA & 25 & 9.19 & 5.82 & 3.21 & 9.22 & 9.20 & 6.89 & 2.32 \\
-NGC4636 & 29 & 9.12 & 5.78 & 3.19 & 9.15 & 9.14 & 8.19 & 5.38 \\
-NORMA & 94 & 8.15 & 5.17 & 2.85 & 8.18 & 8.16 & 5.42 & 1.20 \\
-PERSEUS & 68 & 7.80 & 4.95 & 2.73 & 7.83 & 7.80 & 4.95 & 0.53 \\
-COMA & 34 & 7.58 & 4.81 & 2.65 & 7.61 & 7.58 & 4.41 & 0.95 \\
-AWM7 & 67 & 7.31 & 4.64 & 2.56 & 7.34 & 7.31 & 4.66 & 1.39 \\
-A1367 & 26 & 6.67 & 4.23 & 2.33 & 6.69 & 6.66 & 3.84 & 1.95 \\
-NGC5813 & 91 & 6.25 & 3.96 & 2.19 & 6.28 & 6.27 & 4.97 & 4.26 \\
-ANTLIA & 79 & 5.90 & 3.74 & 2.06 & 5.92 & 5.90 & 4.02 & 2.58 \\
-A2877 & 65 & 5.00 & 3.17 & 1.75 & 5.02 & 4.99 & 2.54 & 2.66 \\
-3C129 & 70 & 4.71 & 2.99 & 1.65 & 4.73 & 4.70 & 2.42 & 1.02 \\
-NGC5044 & 35 & 3.59 & 2.28 & 1.26 & 3.61 & 3.59 & 2.35 & 1.67 \\
-NGC5846 & 92 & 3.34 & 2.12 & 1.17 & 3.36 & 3.35 & 2.40 & 3.40 \\
-NGC1550 & 15 & 2.53 & 1.61 & 0.89 & 2.54 & 2.53 & 1.36 & 1.15 \\
-A3571 & 39 & 2.24 & 1.42 & 0.78 & 2.25 & 2.22 & 0.67 & 0.45 \\
-TRIANGUL & 95 & 2.16 & 1.37 & 0.76 & 2.17 & 2.13 & 0.56 & 0.42 \\
-A2199 & 51 & 2.05 & 1.30 & 0.72 & 2.06 & 2.03 & 0.68 & 0.50 \\
-A2634 & 60 & 2.02 & 1.28 & 0.71 & 2.03 & 2.01 & 0.66 & 1.03 \\
-A3266 & 17 & 2.00 & 1.27 & 0.70 & 2.01 & 1.97 & 0.46 & 0.53 \\
-A0496 & 18 & 1.93 & 1.22 & 0.67 & 1.94 & 1.91 & 0.60 & 0.49 \\
-A0262 & 5 & 1.92 & 1.21 & 0.67 & 1.92 & 1.91 & 0.84 & 0.64 \\
-A0754 & 23 & 1.88 & 1.19 & 0.66 & 1.89 & 1.85 & 0.45 & 0.66 \\
-A0119 & 2 & 1.87 & 1.19 & 0.65 & 1.88 & 1.84 & 0.49 & 0.68 \\
-IIIZw54 & 12 & 1.72 & 1.09 & 0.60 & 1.73 & 1.71 & 0.53 & 1.03 \\
-A2319 & 98 & 1.62 & 1.03 & 0.57 & 1.62 & 1.59 & 0.35 & 0.32 \\
-A2657 & 61 & 1.55 & 0.98 & 0.54 & 1.55 & 1.53 & 0.40 & 0.73 \\
-A3395s & 21 & 1.51 & 0.96 & 0.53 & 1.52 & 1.49 & 0.34 & 0.76 \\
-A0539 & 71 & 1.50 & 0.95 & 0.52 & 1.50 & 1.48 & 0.45 & 0.71 \\
-A4038 & 62 & 1.48 & 0.94 & 0.52 & 1.49 & 1.47 & 0.45 & 0.52 \\
-A0576 & 22 & 1.37 & 0.87 & 0.48 & 1.37 & 1.35 & 0.34 & 0.72 \\
-A3376 & 19 & 1.34 & 0.85 & 0.47 & 1.34 & 1.31 & 0.30 & 0.69 \\
-A1644 & 31 & 1.33 & 0.84 & 0.47 & 1.34 & 1.31 & 0.29 & 0.51 \\
-A3395n & 75 & 1.32 & 0.84 & 0.46 & 1.32 & 1.29 & 0.28 & 0.78 \\
-MKW8 & 42 & 1.32 & 0.83 & 0.46 & 1.32 & 1.30 & 0.39 & 0.87 \\
-UGC03957 & 76 & 1.28 & 0.81 & 0.45 & 1.28 & 1.26 & 0.33 & 0.74 \\
-A2256 & 54 & 1.27 & 0.81 & 0.44 & 1.28 & 1.24 & 0.24 & 0.37 \\
-A3558 & 37 & 1.20 & 0.76 & 0.42 & 1.20 & 1.17 & 0.25 & 0.35 \\
-A0400 & 6 & 1.17 & 0.74 & 0.41 & 1.17 & 1.16 & 0.35 & 0.66 \\
-A3581 & 41 & 1.07 & 0.68 & 0.37 & 1.07 & 1.06 & 0.33 & 0.51 \\
-2A0335 & 11 & 1.05 & 0.67 & 0.37 & 1.05 & 1.03 & 0.25 & 0.26 \\
-A0085 & 1 & 1.04 & 0.66 & 0.36 & 1.04 & 1.01 & 0.18 & 0.27 \\
-A2052 & 44 & 1.01 & 0.64 & 0.35 & 1.02 & 1.00 & 0.24 & 0.36 \\
-A1795 & 40 & 1.00 & 0.64 & 0.35 & 1.01 & 0.97 & 0.16 & 0.27 \\
-NGC507 & 4 & 0.99 & 0.63 & 0.35 & 1.00 & 0.99 & 0.34 & 1.28 \\
-MKW4 & 27 & 0.95 & 0.60 & 0.33 & 0.95 & 0.94 & 0.29 & 0.65 \\
-NGC499 & 66 & 0.95 & 0.60 & 0.33 & 0.95 & 0.94 & 0.33 & 1.53 \\
+FORNAX   &  10 &  31.88 &  20.21 &  11.15 &  32.00 &  31.98 &  30.27 &   9.93 \vstt \\
+M49      &  81 &  19.48 &  12.35 &   6.81 &  19.55 &  19.54 &  18.13 &   9.29 \vstt \\
+OPHIUCHU &  96 &  18.13 &  11.49 &   6.34 &  18.19 &  18.14 &  12.31 &   1.66 \vstt \\
+CENTAURU &  30 &  14.99 &   9.50 &   5.24 &  15.05 &  15.02 &  12.40 &   2.32 \vstt \\
+HYDRA    &  25 &   9.19 &   5.82 &   3.21 &   9.22 &   9.20 &   6.89 &   2.32 \vstt \\
+NGC4636  &  29 &   9.12 &   5.78 &   3.19 &   9.15 &   9.14 &   8.19 &   5.38 \vstt \\
+NORMA    &  94 &   8.15 &   5.17 &   2.85 &   8.18 &   8.16 &   5.42 &   1.20 \vstt \\
+PERSEUS  &  68 &   7.80 &   4.95 &   2.73 &   7.83 &   7.80 &   4.95 &   0.53 \vstt \\
+COMA     &  34 &   7.58 &   4.81 &   2.65 &   7.61 &   7.58 &   4.41 &   0.95 \vstt \\
+AWM7     &  67 &   7.31 &   4.64 &   2.56 &   7.34 &   7.31 &   4.66 &   1.39 \vstt \\
+A1367    &  26 &   6.67 &   4.23 &   2.33 &   6.69 &   6.66 &   3.84 &   1.95 \vstt \\
+NGC5813  &  91 &   6.25 &   3.96 &   2.19 &   6.28 &   6.27 &   4.97 &   4.26 \vstt \\
+ANTLIA   &  79 &   5.90 &   3.74 &   2.06 &   5.92 &   5.90 &   4.02 &   2.58 \vstt \\
+A2877    &  65 &   5.00 &   3.17 &   1.75 &   5.02 &   4.99 &   2.54 &   2.66 \vstt \\
+3C129    &  70 &   4.71 &   2.99 &   1.65 &   4.73 &   4.70 &   2.42 &   1.02 \vstt \\
+NGC5044  &  35 &   3.59 &   2.28 &   1.26 &   3.61 &   3.59 &   2.35 &   1.67 \vstt \\
+NGC5846  &  92 &   3.34 &   2.12 &   1.17 &   3.36 &   3.35 &   2.40 &   3.40 \vstt \\
+NGC1550  &  15 &   2.53 &   1.61 &   0.89 &   2.54 &   2.53 &   1.36 &   1.15 \vstt \\
+A3571    &  39 &   2.24 &   1.42 &   0.78 &   2.25 &   2.22 &   0.67 &   0.45 \vstt \\
+TRIANGUL &  95 &   2.16 &   1.37 &   0.76 &   2.17 &   2.13 &   0.56 &   0.42 \vstt \\
+A2199    &  51 &   2.05 &   1.30 &   0.72 &   2.06 &   2.03 &   0.68 &   0.50 \vstt \\
+A2634    &  60 &   2.02 &   1.28 &   0.71 &   2.03 &   2.01 &   0.66 &   1.03 \vstt \\
+A3266    &  17 &   2.00 &   1.27 &   0.70 &   2.01 &   1.97 &   0.46 &   0.53 \vstt \\
+A0496    &  18 &   1.93 &   1.22 &   0.67 &   1.94 &   1.91 &   0.60 &   0.49 \vstt \\
+A0262    &   5 &   1.92 &   1.21 &   0.67 &   1.92 &   1.91 &   0.84 &   0.64 \vstt \\
+A0754    &  23 &   1.88 &   1.19 &   0.66 &   1.89 &   1.85 &   0.45 &   0.66 \vstt \\
+A0119    &   2 &   1.87 &   1.19 &   0.65 &   1.88 &   1.84 &   0.49 &   0.68 \vstt \\
+IIIZw54  &  12 &   1.72 &   1.09 &   0.60 &   1.73 &   1.71 &   0.53 &   1.03 \vstt \\
+A2319    &  98 &   1.62 &   1.03 &   0.57 &   1.62 &   1.59 &   0.35 &   0.32 \vstt \\
+A2657    &  61 &   1.55 &   0.98 &   0.54 &   1.55 &   1.53 &   0.40 &   0.73 \vstt \\
+A3395s   &  21 &   1.51 &   0.96 &   0.53 &   1.52 &   1.49 &   0.34 &   0.76 \vstt \\
+A0539    &  71 &   1.50 &   0.95 &   0.52 &   1.50 &   1.48 &   0.45 &   0.71 \vstt \\
+A4038    &  62 &   1.48 &   0.94 &   0.52 &   1.49 &   1.47 &   0.45 &   0.52 \vstt \\
+A0576    &  22 &   1.37 &   0.87 &   0.48 &   1.37 &   1.35 &   0.34 &   0.72 \vstt \\
+A3376    &  19 &   1.34 &   0.85 &   0.47 &   1.34 &   1.31 &   0.30 &   0.69 \vstt \\
+A1644    &  31 &   1.33 &   0.84 &   0.47 &   1.34 &   1.31 &   0.29 &   0.51 \vstt \\
+A3395n   &  75 &   1.32 &   0.84 &   0.46 &   1.32 &   1.29 &   0.28 &   0.78 \vstt \\
+MKW8     &  42 &   1.32 &   0.83 &   0.46 &   1.32 &   1.30 &   0.39 &   0.87 \vstt \\
+UGC03957 &  76 &   1.28 &   0.81 &   0.45 &   1.28 &   1.26 &   0.33 &   0.74 \vstt \\
+A2256    &  54 &   1.27 &   0.81 &   0.44 &   1.28 &   1.24 &   0.24 &   0.37 \vstt \\
+A3558    &  37 &   1.20 &   0.76 &   0.42 &   1.20 &   1.17 &   0.25 &   0.35 \vstt \\
+A0400    &   6 &   1.17 &   0.74 &   0.41 &   1.17 &   1.16 &   0.35 &   0.66 \vstt \\
+A3581    &  41 &   1.07 &   0.68 &   0.37 &   1.07 &   1.06 &   0.33 &   0.51 \vstt \\
+2A0335   &  11 &   1.05 &   0.67 &   0.37 &   1.05 &   1.03 &   0.25 &   0.26 \vstt \\
+A0085    &   1 &   1.04 &   0.66 &   0.36 &   1.04 &   1.01 &   0.18 &   0.27 \vstt \\
+A2052    &  44 &   1.01 &   0.64 &   0.35 &   1.02 &   1.00 &   0.24 &   0.36 \vstt \\
+A1795    &  40 &   1.00 &   0.64 &   0.35 &   1.01 &   0.97 &   0.16 &   0.27 \vstt \\
+NGC507   &   4 &   0.99 &   0.63 &   0.35 &   1.00 &   0.99 &   0.34 &   1.28 \vstt \\
+MKW4     &  27 &   0.95 &   0.60 &   0.33 &   0.95 &   0.94 &   0.29 &   0.65 \vstt \\
+NGC499   &  66 &   0.95 &   0.60 &   0.33 &   0.95 &   0.94 &   0.33 &   1.53 \vstt \\
 \hline
@@
  \hline
-FORNAX & 10 & 34.87 & 44.21 & 50.48 & 43.11 & 43.09 & 40.74 & 363.17 \\
-M49 & 81 & 21.48 & 27.24 & 30.84 & 26.57 & 26.55 & 24.62 & 285.17 \\
-OPHIUCHU & 96 & 20.12 & 25.51 & 28.70 & 24.88 & 24.80 & 16.83 & 270.87 \\
-CENTAURU & 30 & 16.64 & 21.10 & 23.74 & 20.58 & 20.54 & 16.94 & 249.07 \\
-HYDRA & 25 & 10.14 & 12.86 & 14.54 & 12.54 & 12.52 & 9.37 & 195.09 \\
-NGC4636 & 29 & 9.96 & 12.63 & 14.44 & 12.32 & 12.31 & 11.00 & 194.11 \\
-NORMA & 94 & 8.72 & 11.05 & 12.91 & 10.78 & 10.75 & 7.15 & 178.66 \\
-PERSEUS & 68 & 8.66 & 10.98 & 12.35 & 10.71 & 10.67 & 6.77 & 167.81 \\
-COMA & 34 & 8.22 & 10.43 & 12.00 & 10.17 & 10.12 & 5.90 & 172.16 \\
-AWM7 & 67 & 8.08 & 10.24 & 11.58 & 9.99 & 9.96 & 6.34 & 173.06 \\
-A1367 & 26 & 7.24 & 9.18 & 10.56 & 8.95 & 8.91 & 5.14 & 164.76 \\
-NGC5813 & 91 & 6.88 & 8.72 & 9.90 & 8.50 & 8.49 & 6.73 & 161.29 \\
-ANTLIA & 79 & 6.23 & 7.90 & 9.34 & 7.71 & 7.68 & 5.24 & 153.26 \\
-A2877 & 65 & 5.52 & 7.00 & 7.92 & 6.82 & 6.78 & 3.45 & 144.31 \\
-3C129 & 70 & 5.05 & 6.41 & 7.46 & 6.25 & 6.21 & 3.21 & 136.52 \\
-NGC5044 & 35 & 3.95 & 5.01 & 5.69 & 4.89 & 4.87 & 3.19 & 121.95 \\
-NGC5846 & 92 & 3.65 & 4.63 & 5.29 & 4.52 & 4.50 & 3.23 & 117.54 \\
-NGC1550 & 15 & 2.79 & 3.53 & 4.01 & 3.45 & 3.43 & 1.84 & 102.18 \\
-A3571 & 39 & 2.48 & 3.15 & 3.55 & 3.07 & 3.03 & 0.92 & 93.98 \\
-TRIANGUL & 95 & 2.37 & 3.01 & 3.42 & 2.93 & 2.88 & 0.76 & 91.42 \\
-A2199 & 51 & 2.26 & 2.87 & 3.24 & 2.80 & 2.76 & 0.93 & 90.34 \\
-A2634 & 60 & 2.22 & 2.81 & 3.20 & 2.74 & 2.71 & 0.90 & 91.15 \\
-A3266 & 17 & 2.18 & 2.76 & 3.17 & 2.69 & 2.63 & 0.62 & 88.94 \\
-A0496 & 18 & 2.14 & 2.72 & 3.06 & 2.65 & 2.62 & 0.83 & 88.06 \\
-A0262 & 5 & 2.11 & 2.67 & 3.03 & 2.60 & 2.58 & 1.14 & 88.12 \\
-A0754 & 23 & 2.08 & 2.63 & 2.98 & 2.57 & 2.52 & 0.61 & 87.59 \\
-A0119 & 2 & 2.00 & 2.53 & 2.96 & 2.47 & 2.43 & 0.66 & 85.95 \\
-IIIZw54 & 12 & 1.89 & 2.39 & 2.73 & 2.33 & 2.30 & 0.72 & 84.11 \\
-A2319 & 98 & 1.77 & 2.24 & 2.56 & 2.19 & 2.13 & 0.47 & 78.11 \\
-A2657 & 61 & 1.71 & 2.17 & 2.45 & 2.12 & 2.08 & 0.54 & 79.87 \\
-A0539 & 71 & 1.65 & 2.09 & 2.37 & 2.04 & 2.01 & 0.62 & 78.43 \\
-A4038 & 62 & 1.64 & 2.08 & 2.35 & 2.03 & 2.01 & 0.62 & 77.70 \\
-A3395s & 21 & 1.62 & 2.06 & 2.40 & 2.01 & 1.96 & 0.46 & 77.82 \\
-A0576 & 22 & 1.47 & 1.87 & 2.17 & 1.82 & 1.79 & 0.46 & 74.13 \\
-A1644 & 31 & 1.45 & 1.84 & 2.11 & 1.79 & 1.75 & 0.39 & 72.99 \\
-MKW8 & 42 & 1.44 & 1.83 & 2.08 & 1.78 & 1.76 & 0.53 & 73.51 \\
-UGC03957 & 76 & 1.41 & 1.79 & 2.02 & 1.75 & 1.71 & 0.45 & 72.64 \\
-A3376 & 19 & 1.41 & 1.78 & 2.12 & 1.74 & 1.70 & 0.40 & 72.39 \\
-A3395n & 75 & 1.40 & 1.78 & 2.09 & 1.73 & 1.69 & 0.37 & 72.41 \\
-A2256 & 54 & 1.37 & 1.73 & 2.01 & 1.69 & 1.64 & 0.32 & 70.00 \\
-A3558 & 37 & 1.31 & 1.66 & 1.89 & 1.62 & 1.58 & 0.34 & 68.43 \\
-A0400 & 6 & 1.26 & 1.60 & 1.85 & 1.56 & 1.54 & 0.47 & 68.55 \\
-A3581 & 41 & 1.18 & 1.50 & 1.70 & 1.46 & 1.44 & 0.45 & 66.12 \\
-2A0335 & 11 & 1.17 & 1.48 & 1.66 & 1.44 & 1.41 & 0.34 & 63.65 \\
-A0085 & 1 & 1.15 & 1.46 & 1.64 & 1.42 & 1.38 & 0.25 & 63.47 \\
-A2052 & 44 & 1.13 & 1.43 & 1.61 & 1.39 & 1.36 & 0.32 & 63.85 \\
-A1795 & 40 & 1.11 & 1.41 & 1.59 & 1.38 & 1.33 & 0.23 & 62.45 \\
-NGC507 & 4 & 1.09 & 1.39 & 1.57 & 1.35 & 1.34 & 0.46 & 64.25 \\
-MKW4 & 27 & 1.04 & 1.32 & 1.50 & 1.29 & 1.27 & 0.39 & 62.49 \\
-NGC499 & 66 & 1.04 & 1.32 & 1.50 & 1.28 & 1.27 & 0.45 & 62.65 \\
+FORNAX   &  10 &  34.87 &  44.21 &  50.48 &  43.11 &  43.09 &  40.74 & 480.43 \vstt \\
+M49      &  81 &  21.48 &  27.24 &  30.84 &  26.57 &  26.55 &  24.62 & 377.24 \vstt \\
+OPHIUCHU &  96 &  20.12 &  25.51 &  28.70 &  24.88 &  24.80 &  16.83 & 358.32 \vstt \\
+CENTAURU &  30 &  16.64 &  21.10 &  23.74 &  20.58 &  20.54 &  16.94 & 329.49 \vstt \\
+HYDRA    &  25 &  10.14 &  12.86 &  14.54 &  12.54 &  12.52 &   9.37 & 258.08 \vstt \\
+NGC4636  &  29 &   9.96 &  12.63 &  14.44 &  12.32 &  12.31 &  11.00 & 256.79 \vstt \\
+NORMA    &  94 &   8.72 &  11.05 &  12.91 &  10.78 &  10.75 &   7.15 & 236.35 \vstt \\
+PERSEUS  &  68 &   8.66 &  10.98 &  12.35 &  10.71 &  10.67 &   6.77 & 221.99 \vstt \\
+COMA     &  34 &   8.22 &  10.43 &  12.00 &  10.17 &  10.12 &   5.90 & 227.75 \vstt \\
+AWM7     &  67 &   8.08 &  10.24 &  11.58 &   9.99 &   9.96 &   6.34 & 228.93 \vstt \\
+A1367    &  26 &   7.24 &   9.18 &  10.56 &   8.95 &   8.91 &   5.14 & 217.96 \vstt \\
+NGC5813  &  91 &   6.88 &   8.72 &   9.90 &   8.50 &   8.49 &   6.73 & 213.36 \vstt \\
+ANTLIA   &  79 &   6.23 &   7.90 &   9.34 &   7.71 &   7.68 &   5.24 & 202.74 \vstt \\
+A2877    &  65 &   5.52 &   7.00 &   7.92 &   6.82 &   6.78 &   3.45 & 190.91 \vstt \\
+3C129    &  70 &   5.05 &   6.41 &   7.46 &   6.25 &   6.21 &   3.21 & 180.60 \vstt \\
+NGC5044  &  35 &   3.95 &   5.01 &   5.69 &   4.89 &   4.87 &   3.19 & 161.33 \vstt \\
+NGC5846  &  92 &   3.65 &   4.63 &   5.29 &   4.52 &   4.50 &   3.23 & 155.50 \vstt \\
+NGC1550  &  15 &   2.79 &   3.53 &   4.01 &   3.45 &   3.43 &   1.84 & 135.18 \vstt \\
+A3571    &  39 &   2.48 &   3.15 &   3.55 &   3.07 &   3.03 &   0.92 & 124.33 \vstt \\
+TRIANGUL &  95 &   2.37 &   3.01 &   3.42 &   2.93 &   2.88 &   0.76 & 120.94 \vstt \\
+A2199    &  51 &   2.26 &   2.87 &   3.24 &   2.80 &   2.76 &   0.93 & 119.51 \vstt \\
+A2634    &  60 &   2.22 &   2.81 &   3.20 &   2.74 &   2.71 &   0.90 & 120.59 \vstt \\
+A3266    &  17 &   2.18 &   2.76 &   3.17 &   2.69 &   2.63 &   0.62 & 117.65 \vstt \\
+A0496    &  18 &   2.14 &   2.72 &   3.06 &   2.65 &   2.62 &   0.83 & 116.49 \vstt \\
+A0262    &   5 &   2.11 &   2.67 &   3.03 &   2.60 &   2.58 &   1.14 & 116.57 \vstt \\
+A0754    &  23 &   2.08 &   2.63 &   2.98 &   2.57 &   2.52 &   0.61 & 115.87 \vstt \\
+A0119    &   2 &   2.00 &   2.53 &   2.96 &   2.47 &   2.43 &   0.66 & 113.70 \vstt \\
+IIIZw54  &  12 &   1.89 &   2.39 &   2.73 &   2.33 &   2.30 &   0.72 & 111.27 \vstt \\
+A2319    &  98 &   1.77 &   2.24 &   2.56 &   2.19 &   2.13 &   0.47 & 103.33 \vstt \\
+A2657    &  61 &   1.71 &   2.17 &   2.45 &   2.12 &   2.08 &   0.54 & 105.65 \vstt \\
+A0539    &  71 &   1.65 &   2.09 &   2.37 &   2.04 &   2.01 &   0.62 & 103.75 \vstt \\
+A4038    &  62 &   1.64 &   2.08 &   2.35 &   2.03 &   2.01 &   0.62 & 102.79 \vstt \\
+A3395s   &  21 &   1.62 &   2.06 &   2.40 &   2.01 &   1.96 &   0.46 & 102.94 \vstt \\
+A0576    &  22 &   1.47 &   1.87 &   2.17 &   1.82 &   1.79 &   0.46 &  98.07 \vstt \\
+A1644    &  31 &   1.45 &   1.84 &   2.11 &   1.79 &   1.75 &   0.39 &  96.55 \vstt \\
+MKW8     &  42 &   1.44 &   1.83 &   2.08 &   1.78 &   1.76 &   0.53 &  97.25 \vstt \\
+UGC03957 &  76 &   1.41 &   1.79 &   2.02 &   1.75 &   1.71 &   0.45 &  96.10 \vstt \\
+A3376    &  19 &   1.41 &   1.78 &   2.12 &   1.74 &   1.70 &   0.40 &  95.76 \vstt \\
+A3395n   &  75 &   1.40 &   1.78 &   2.09 &   1.73 &   1.69 &   0.37 &  95.79 \vstt \\
+A2256    &  54 &   1.37 &   1.73 &   2.01 &   1.69 &   1.64 &   0.32 &  92.60 \vstt \\
+A3558    &  37 &   1.31 &   1.66 &   1.89 &   1.62 &   1.58 &   0.34 &  90.53 \vstt \\
+A0400    &   6 &   1.26 &   1.60 &   1.85 &   1.56 &   1.54 &   0.47 &  90.68 \vstt \\
+A3581    &  41 &   1.18 &   1.50 &   1.70 &   1.46 &   1.44 &   0.45 &  87.46 \vstt \\
+2A0335   &  11 &   1.17 &   1.48 &   1.66 &   1.44 &   1.41 &   0.34 &  84.20 \vstt \\
+A0085    &   1 &   1.15 &   1.46 &   1.64 &   1.42 &   1.38 &   0.25 &  83.97 \vstt \\
+A2052    &  44 &   1.13 &   1.43 &   1.61 &   1.39 &   1.36 &   0.32 &  84.47 \vstt \\
+A1795    &  40 &   1.11 &   1.41 &   1.59 &   1.38 &   1.33 &   0.23 &  82.62 \vstt \\
+NGC507   &   4 &   1.09 &   1.39 &   1.57 &   1.35 &   1.34 &   0.46 &  85.00 \vstt \\
+MKW4     &  27 &   1.04 &   1.32 &   1.50 &   1.29 &   1.27 &   0.39 &  82.67 \vstt \\
+NGC499   &  66 &   1.04 &   1.32 &   1.50 &   1.28 &   1.27 &   0.45 &  82.88 \vstt \\
 \hline

### 2011-10-12 paper.tex
changes in response to the referee

@@
 \begin{abstract}
-  \C{We study the possibility for detecting gamma-ray emission from
-  galaxy clusters. We consider 1) leptophilic models of dark matter
-  (DM) annihilation that include a Sommerfeld enhancement (SFE), 2)
-  different representative benchmark models of supersymmetric DM, and
-  3) cosmic ray (CR) induced pion decay. To model DM annihilation, we
-  consider continuum emission as a result of the hadronization of
-  annihilating neutralinos, internal bremsstrahlung, and inverse
-  Compton emission from the cosmic microwave background as well as
-  from a realistic spatial and spectral distribution of dust and
-  stellar light. Among all clusters/groups of a flux-limited X-ray
-  sample, we predict Virgo, Fornax and M49 to be the brightest DM
-  sources and find a particularly low CR-induced background for
-  Fornax. For a minimum substructure mass given by the DM
-  free-streaming scale, cluster halos maximize the substructure boost
-  for which we find a factor of $\gtrsim 1000$. Since regions around
-  the virial radius dominate the annihilation flux of substructures,
-  the resulting surface brightness profiles are almost flat. This
-  makes it very challenging to detect this flux with imaging
-  atmospheric Cherenkov telescopes since their sensitivity drops
-  approximately linearly with radius and they typically have $5-10$
-  linear resolution elements across a cluster. Assuming cold dark
-  matter with a substructure mass distribution down to an Earth mass
-  and using extended \Fermi upper limits, we rule out the leptophilic
-  models in their present form in 28 clusters, and limit the boost
-  from SFE in M49 and Fornax to be $\lesssim 5$. This corresponds to a
-  limit on SFE in the Milky Way of $\lesssim 3$ which is too small to
-  account for the increasing positron fraction with energy as seen by
-  PAMELA. Alternatively, if SFE is realized in Nature, this would
-  imply a limiting substructure mass of $\mlim > 10^4\,\msun$---a
-  problem for structure formation in most particle physics
-  models. Using individual cluster observations, it will be
-  challenging for \Fermi to constrain our selection of DM benchmark
-  models without SFE. The \Fermi upper limits are, however, closing in
-  on our predictions for the CR flux using an analytic model based on
-  cosmological hydrodynamical cluster simulations. We limit the
-  CR-to-thermal pressure in nearby bright galaxy clusters of the
-  \Fermi sample to $\lesssim 10\%$ and in Norma and Coma to $\lesssim
-  3\%$. Thus we will soon start to constrain the underlying CR physics
-  such as shock acceleration efficiencies or CR transport properties.}
+  \C{We study the possibility for detecting gamma-ray emission from galaxy
+    clusters. We consider 1) leptophilic models of dark matter (DM) annihilation
+    that include a Sommerfeld enhancement (SFE), 2) different representative
+    benchmark models of supersymmetric DM, and 3) cosmic ray (CR) induced pion
+    decay. Among all clusters/groups of a flux-limited X-ray sample, we predict
+    Virgo, Fornax and M49 to be the brightest DM sources and find a particularly
+    low CR-induced background for Fornax. For a minimum substructure mass given
+    by the DM free-streaming scale, cluster halos maximize the substructure
+    boost for which we find a factor of $\gtrsim 1000$. Since regions around the
+    virial radius dominate the annihilation flux of substructures, the resulting
+    surface brightness profiles are almost flat. This makes it very challenging
+    to detect this flux with imaging atmospheric Cherenkov telescopes since
+    their sensitivity drops approximately linearly with radius and they
+    typically have $5-10$ linear resolution elements across a cluster. Assuming
+    cold dark matter with a substructure mass distribution down to an Earth mass
+    and using extended \Fermi upper limits, we rule out the leptophilic models
+    in their present form in 28 clusters, and limit the boost from SFE in M49
+    and Fornax to be $\lesssim 5$. This corresponds to a limit on SFE in the
+    Milky Way of $\lesssim 3$ which is too small to account for the increasing
+    positron fraction with energy as seen by PAMELA and challenges the DM
+    interpretation. Alternatively, if SFE is realized in Nature, this would
+    imply a limiting substructure mass of $\mlim > 10^4\,\msun$---a problem for
+    structure formation in most particle physics models. Using individual
+    cluster observations, it will be challenging for \Fermi to constrain our
+    selection of DM benchmark models without SFE. The \Fermi upper limits are,
+    however, closing in on our predictions for the CR flux using an analytic
+    model based on cosmological hydrodynamical cluster simulations. We limit the
+    CR-to-thermal pressure in nearby bright galaxy clusters of the \Fermi sample
+    to $\lesssim 10\%$ and in Norma and Coma to $\lesssim 3\%$. Thus we will
+    soon start to constrain the underlying CR physics such as shock acceleration
+    efficiencies or CR transport properties.}
 \end{abstract}
+
+% To model DM annihilation, we
+%   consider continuum emission as a result of the hadronization of
+%   annihilating neutralinos, internal bremsstrahlung, and inverse
+%   Compton emission from the cosmic microwave background as well as
+%   from a realistic spatial and spectral distribution of dust and
+%   stellar light.
 
@@
   to maximize the DM annihilation flux of an unresolved cluster,
-  $F=A_\rmn{dm} \int dV \rho^2 / D^2 \sim \mvir^\alpha/D^2$, where
+  $F=A_\rmn{dm} \int dV \rho^2 / D^2 \propto \mvir^\alpha/D^2$, where
   $A_\rmn{dm}$ depends on the particle physics model of DM, $\rho$ is
@@
   this work. Second, we need to minimize the expected noise which is a
-  sum of galactic and cluster-intrinsic foreground. While the galactic
-  foreground varies across the sky, it is typically lower for
-  increasing latitude (away from the galactic plane). It is thought
-  that the gamma-ray foreground from clusters is dominated by CRs
-  which are accelerated at cosmological formation shocks and
-  transported over time although there could be a substantial
-  contribution of CRs from AGNs and supernova-driven galactic
-  winds. In this work we will also study (and constrain) the
+  sum of instrumental noise, galactic and cluster-intrinsic
+  foreground. While the galactic foreground varies across the sky, it
+  is typically lower for increasing latitude (away from the galactic
+  plane). It is thought that the gamma-ray foreground from clusters is
+  dominated by CRs which are accelerated at cosmological formation
+  shocks and transported over time although there could be a
+  substantial contribution of CRs from AGNs and supernova-driven
+  galactic winds. In this work we will also study (and constrain) the
   CR-induced emission from clusters to identify those objects that are
@@
 leptons and antileptons. In addition, one has to have a sizeable
-fraction to final states containing muons or tau leptons as the shape
+fraction of final states containing muons or tau leptons as the shape
 of the spectrum disfavors direct annihilation to electrons and
@@
 \end{equation}
-\C{where the local boost factor required to explain the data
+\C{where the local boost factor required to explain the data is
   $\B_\rmn{sfe,MW}=300$.} \del{Here the boost factor needed to explain
   the PAMELA/\Fermi excess of electrons and positrons
-  $\B_\rmn{sfe,MW}=300$,} The velocity dispersion for the MW
+  $\B_\rmn{sfe,MW}=300$,} The velocity dispersion for the MW,
 $v_\rmn{MW} \approx 220\,\rmn{km\,s}^{-1}$, and the \C{mass dependent}
 velocity dispersion $\sigv$ for clusters is derived in
-\cite{2005RvMP...77..207V}. Note that, clusters have a larger velocity
-dispersion and an accordingly smaller Sommerfeld boost factor.
+\cite{2005RvMP...77..207V}. \del{Note that, clusters have a larger velocity
+dispersion and an accordingly smaller Sommerfeld boost factor.}
 
@@
   the region around the virial radius of each respective halo which
-  are mostly stripped for dwarf substructures in the MW. Hence a more
-  realistic boost from substructures is probably much smaller in Dwarf
-  galaxies. In addition,} these boost factors are only realized for
-direct annihilation emission (continuum emission or final state
-radiation) or IC scattering off homogeneous seed photon fields
+  is mostly tidally stripped for dwarfs in the MW. Hence a more
+  realistic boost from substructures is probably much smaller in
+  satellite dwarf galaxies. In addition,} these boost factors are only
+realized for direct annihilation emission (continuum emission or final
+state radiation) or IC scattering off homogeneous seed photon fields
 (CMB). For IC scattering of SD photons, the overlap of final state
@@
 
-In supernovae remnants and on scales of galaxies, there are convincing
-evidences of non-thermal populations. Especially, in the MW, the
-cosmic rays are observed directly as well as indirectly through radio,
-X-ray, and gamma-ray emission. On larger scales of the order of few
-100~kpc up to Mpc, there are currently a vast number of observations
-of radio emission coming from radio mini halos in the center of
-cooling flow clusters, radio relics in the periphery of clusters
-\cite{2004rcfg.proc..335K} as well as smooth giant radio halos that
-have been observed in more than 50 clusters
-\cite{2003ASPC..301..143F,2008SSRv..134...93F}. This type of emission
-is expected in clusters since the formation process of a galaxy
-cluster is a very energetic processes that induces both turbulence as
-well as frequently occurring merging and accretion shocks which both
-are thought to accelerate relativistic non-thermal protons and radio
-emitting electrons to high energies. Thus most of the observed radio
-emission in clusters is expected to emerge from cosmic-ray electron
-induced radio synchrotron emission. The precise origin of these
-electrons, in especially relics and giant radio halos, is still not
-settled. One possible scenario for the production of these electrons
-are hadronic CR interactions with ambient gas protons which results in
-the production of both charged and neutral pions that decay into
-electrons, neutrinos, and gamma-rays (see
+In supernovae remnants and on scales of galaxies, there are convincing evidences
+of non-thermal populations. Especially, in the MW, the cosmic rays are observed
+directly as well as indirectly through radio, X-ray, and gamma-ray emission. On
+larger scales of the order of few 100~kpc up to Mpc, there are currently a vast
+number of observations of radio emission coming from radio mini halos in the
+centers of cooling flow clusters, radio relics in the periphery of clusters
+\cite{2004rcfg.proc..335K}, as well as giant radio halos amounting to a total
+number of more than 50 diffuse radio sources in clusters
+\cite{2003ASPC..301..143F,2008SSRv..134...93F}. This type of emission is
+expected in clusters since the formation process of a galaxy cluster is a very
+energetic processes that induces both turbulence as well as frequently occurring
+merging and accretion shocks which both are thought to accelerate relativistic
+non-thermal protons and radio emitting electrons to high energies. The precise
+origin of these electrons, in especially relics and giant radio halos, is still
+not settled. One possible scenario for the production of these electrons are
+hadronic CR interactions with ambient gas protons which results in charged and
+neutral pions that decay into electrons, neutrinos, and gamma-rays (see
 \cite{1980ApJ...239L..93D,1982AJ.....87.1266V,1999APh....12..169B,2000A&A...362..151D,2001ApJ...559...59M,2003MNRAS.342.1009M,2004A&A...413...17P,2004MNRAS.352...76P,2008MNRAS.385.1211P,2008MNRAS.385.1242P,2009JCAP...09..024K,2010MNRAS.401...47D,2010MNRAS.407.1565D,2010ApJ...722..737K,2011A&A...527A..99E}
 ).\footnote{An alternative scenario is the second order turbulent
-  re-acceleration through the interaction of a previously injected
-  relativistic population of electrons by supernova driven winds or
-  active galactic nuclei with plasma waves and
-  magneto-turbulence. \protect
+  re-acceleration through the interaction of a previously injected relativistic
+  population of electrons by supernova driven winds or active galactic nuclei
+  with plasma waves and magneto-turbulence. \protect
   \cite{1987A&A...182...21S,1993ApJ...406..399G,2004MNRAS.350.1174B,2005MNRAS.363.1173B,2007MNRAS.378..245B,2011MNRAS.410..127B,2009A&A...507..661B}}
-Supporting evidence comes from the smoothness of the extended radio
-emission that often resembles that observed in thermal X-rays. This
-can be easily achieve in the hadronic model since the long cooling
-time of cosmic ray protons (CRs) allows for an extended and large
-population of CRs to build up over the cluster history
-\cite{1996SSRv...75..279V, 1997ApJ...477..560E,
-  1997ApJ...487..529B}. The production of these secondaries depend
-both on the gas and CR densities in the cluster, where the CR
-density roughly traces the gas outside the core regime and is slightly
-enhanced in the center. This density scaling implies that clusters
-are great targets for Cherenkov telescopes with a high sensitivity for
-the central parts of nearby clusters. Detecting the cluster gamma-ray
-emission is crucial in this respect as it potentially provides the
-unique and unambiguous evidence of CR populations in clusters through
-observing the $\pi^0$ bump at about 100~MeV in the spectra.
-
-We adopt the universal spectral and spatial gamma-ray model developed
-by Pinzke \& Pfrommer \cite{2010MNRAS.409..449P} to estimate the
-emission from decaying $\pi^0$:s that dominates over the IC emission
-from primary and secondary electrons above 100~MeV in clusters. The
-gamma-ray formalism was derived from high resolution simulations of
-clusters of galaxies that included radiative hydrodynamics, star
-formation, supernova feedback, and followed CR physics using a novel
-formulation that trace the most important injection and loss processes
-self-consistently while accounting for the CR pressure in the
-equation of motion
-\cite{2008A&A...481...33J,2007A&A...473...41E,2006MNRAS.367..113P}.
-We note that the overall normalization of the CR and gamma-ray
-distribution scales with the maximum acceleration efficiency at
-structure formation shock waves. Following recent observations at
-supernova remnants \cite{2009Sci...325..719H} as well as theoretical
-studies \cite{2005ApJ...620...44K}, we adopt a realistic value of this
-parameter and assume that 50\% of the dissipated energy at strong
-shocks is injected into CRs while this efficiency rapidly decreases
-for weaker shocks \cite{2007A&A...473...41E}. As a caveat we note that
-the analytic model is based on simulations that only considered
-advective transport of CRs by turbulent gas motions which produces
-centrally enhanced profiles. However active CR transport such as CR
-diffusion and streaming tends to drive the CR radial profiles towards
-being flat, with equal CR number density everywhere. While the CR
-streaming is then usually larger than typical advection velocities and
-becomes comparable or lower than this only for periods with trans- and
-supersonic cluster turbulence during a cluster merger. As a
-consequence a bimodality of the CR spatial distribution results with
-merging (relaxed) clusters showing a centrally concentrated (flat) CR
-energy density profile \cite{2011A&A...527A..99E}. This translates
-into a bimodality of the expected diffuse radio and gamma-ray emission
-of clusters, since more centrally concentrated CR will find higher
-target densities for hadronic CR proton interactions
-\cite{2011A&A...527A..99E}. As a result of this, relaxed clusters
+Supporting evidence comes from the smoothness of the extended radio emission
+that often resembles that observed in thermal X-rays. This can be easily
+explained in the hadronic model since the long cooling time of cosmic ray
+protons (CRs) of order the Hubble time allows for a cluster-filling population
+of CRs to build up over the formation history \cite{1996SSRv...75..279V,
+  1997ApJ...477..560E, 1997ApJ...487..529B}. The production of these secondaries
+depend both on the gas and CR densities in the cluster, where the CR density
+roughly traces the gas outside the core regime and is slightly enhanced in the
+center. This density scaling implies that clusters are great targets for
+Cherenkov telescopes with a high sensitivity for the central parts of nearby
+clusters. Detecting the cluster gamma-ray emission is crucial in this respect as
+it potentially provides the unique and unambiguous evidence of CR populations in
+clusters through observing the $\pi^0$ bump at about 100~MeV in the spectra.
+
+We adopt the universal spectral and spatial gamma-ray model developed by Pinzke
+\& Pfrommer \cite{2010MNRAS.409..449P} to estimate the emission from decaying
+$\pi^0$:s that dominates over the IC emission from primary and secondary
+electrons above 100~MeV in clusters. The gamma-ray formalism was derived from
+high-resolution simulations of clusters of galaxies that included radiative
+hydrodynamics, star formation, supernova feedback, and followed CR physics using
+a novel formulation that trace the most important injection and loss processes
+self-consistently while accounting for the CR pressure in the equation of motion
+\cite{2008A&A...481...33J,2007A&A...473...41E,2006MNRAS.367..113P}.  We
+highlight two main uncertainties of the models, namely the acceleration
+efficiency at formation shocks and CR transport parameters. First, we note that
+the overall normalization of the CR and gamma-ray distribution scales with the
+maximum acceleration efficiency at structure formation shock waves. Following
+recent observations at supernova remnants \cite{2009Sci...325..719H} as well as
+theoretical studies \cite{2005ApJ...620...44K}, we assume the maximally allowed
+acceleration efficiency for {\em strong} shocks that transfers 50\% of the
+shock-dissipated energy (kinetic energy corrected for adiabatic compressional
+heating at the shock) to CRs. These efficiencies drop quickly for weaker shocks
+\cite{2007A&A...473...41E} which dominate the gravitational energy dissipation
+inside galaxy clusters \cite{2006MNRAS.367..113P}. These efficiencies will have
+to be corrected down if this value is not realized at strong structure formation
+shocks. Second, these simulations (and by extension the analytic model) neglect
+active CR transport such as streaming and diffusion relative to the gas, i.e.,
+we assume that advective transport dominates and CRs are tightly coupled to the
+gas via magnetic fields tangled on sufficiently small scales which produces
+centrally enhanced profiles. However, CR diffusion and streaming tends to drive
+the CR radial profiles towards being flat, with equal CR number density
+everywhere. While the CR streaming velocity is usually larger than typical
+advection velocities and becomes comparable or lower than this only for periods
+with trans- and supersonic cluster turbulence during a cluster merger. As a
+consequence a bimodality of the CR spatial distribution may result with merging
+(relaxed) clusters showing a centrally concentrated (flat) CR energy density
+profile \cite{2011A&A...527A..99E}. This translates into a bimodality of the
+expected diffuse radio and gamma-ray emission of clusters, since more centrally
+concentrated CR will find higher target densities for hadronic CR proton
+interactions \cite{2011A&A...527A..99E}. As a result of this, relaxed clusters
 could have a reduced gamma-ray luminosity by up to a factor of five.
@@
   fluxes in this section are derived within an angle corresponding to
-  $\rvir$ and are smoothed over using a PSF of $0.1\deg$.}
+  $\rvir$ and are convolved with a PSF of $0.1\deg$.}
 
@@
 very flat brightness profile $r<0.1\rvir$, due to both the effect from
-substructures and the smoothing over the PSF. The CR induced emission
-also show a smoothing in the central parts due to the PSF. In the
+substructures and the convolution with the PSF. The CR induced emission
+also show a smoothing of the central parts due to the PSF. In the
 outer part of the Fornax cluster the CR flux is suppressed compared to
@@
 X-ray flux-complete sample in the local universe. \C{All fluxes in
-  this section are derived within an angle corresponding to $\rvir$,
-  in addition we neglegt the smoothing over the PSF if nothing else is
+  this section are derived within an angle corresponding to $\rvir$;
+  in addition we neglect the convolution with the PSF if nothing else is
   stated.}  We confront these predictions to upper limits obtained by
@@
 stripped gas parcels from infalling galaxies to the overall gamma-ray
-flux from a cluster).
-
-\del{We highlight two main uncertainties of the models, namely the
-  acceleration efficiency at formation shocks and CR transport
-  parameters. First, we note that both models assume the maximally
-  allowed acceleration efficiency for {\em strong} shocks that
-  transfers 50\% of the shock-dissipated energy (kinetic energy
-  corrected for adiabatic compressional heating at the shock) to
-  CRs. These efficiencies drop quickly for weaker shocks
-  \cite{2007A&A...473...41E} which dominate the gravitational energy
-  dissipation inside galaxy clusters \cite{2006MNRAS.367..113P}. These
-  efficiencies will have to be corrected down if this value is not
-  realized at strong structure formation shocks. Second, these
-  simulations (and by extension the analytic model) neglect active CR
-  transport such as streaming and diffusion relative to the gas, i.e.,
-  we assume that advective transport dominates and CRs are tightly
-  coupled to the gas via flux-frozen magnetic fields tangled on
-  sufficiently small scales. Evidence from the statistics of radio
-  halos suggests that this might not be the case for relaxed clusters,
-  arguing that CR streaming (and diffusion) in those objects could be
-  responsible for a decrease in the central CR number density. This
-  effect would also reduce the expected gamma-ray flux by up to a
-  factor of five \cite{2011A&A...527A..99E}.}
+flux from a cluster). As discussed in Sect.~\ref{sect:CRs}, the model
+predictions are subject to two main uncertainties, the acceleration
+efficiency at formation shocks and CR transport parameters and hence
+may be scaled down depending on specific values realized in clusters.
 
@@
   cluster-intrinsic CR foreground and do not consider the dominant
-  galactic and instrumental noise sources here.) We find that
+  galactic and instrumental noise sources here.)}
+
+\del{ We find that
   \Fermi-LAT will be able to start constraining these DM models within

### 2011-10-13 paper.tex
updated captions+sec.VB

@@
 \newcommand{\jcap}{JCAP}
-
 \newcommand{\Fermi}{{\em Fermi}\xspace}
@@
 \newcommand{\hst}{\hspace{-1.0mm}}
+\newcommand{\degs}{^\circ}
+\newcommand{\colo}{(color online). }
 
@@
 halos.\footnote{Note that $S$ is strictly speaking the Sommerfeld
-  enhanced annihilation cross-section, but here we have additionally
+  enhanced annihilation cross section, but here we have additionally
   included the order unity constraint that ensures that the relic
@@
  \includegraphics[width=0.49\columnwidth]{figures/fit.epflux.int.bw.eps}
- \caption{\it (Color online) Source functions for different dark
+ \caption{\colo Source functions for different dark
    matter (DM) models. We show the simulated data from {\sc DarkSUSY}
@@
    \protect\cite{2011JCAP...03..019C,2011JCAP...03..051C}; the solid
-   lines show the fit to the data. LEFT PANEL: normalized differential
+   lines show the fit to the data. Left panel: normalized differential
    continuum spectra for four different DM benchmark (BM) models;
@@
    diamonds), and $\Js$ (blue triangles). We use Eq.~(\ref{eq:bm_cont})
-   to fit the continuum spectra. RIGHT PANEL: number of electron and
+   to fit the continuum spectra. Right panel: number of electron and
    positron per DM annihilation above the electron energy $\ee$ for
@@
 where the differential CR to gamma-ray source function is denoted
-by $\qCR(\eg,r)$ (see Sect.~\ref{sect:CRs} and
+by $\qCR(\eg,r)$ (see Sec.~\ref{sect:CRs} and
 \cite{2010MNRAS.409..449P} for further details). The subscript $i$
@@
 It is the product of enhancement factors from SFE $\B_\sfe(\sigv)$
-(see Eq.~\ref{eq:B_sfe} and Sect.~\ref{sect:LP}) and from substructure
+(see Eq.~\ref{eq:B_sfe} and Sec.~\ref{sect:LP}) and from substructure
 enhancement over the smooth halo contribution $\B_{\sub,i}(r) =
@@
     approaches the constant saturated boost of 530.} (see
-Eqs.~\ref{eq:rho_sub}-\ref{eq:xvir} and Sect.~\ref{sect:subst}). The
+Eqs.~\ref{eq:rho_sub}-\ref{eq:xvir} and Sec.~\ref{sect:subst}). The
 DM source function from the smooth halo for each process is written in
@@
 was shown in Sanchez-Conde et al. \cite{2011arXiv1104.3530S} that
-inside $0.1$~deg, where the sensitivity of Cherenkov telescopes is
+inside $0.1\degs$, where the sensitivity of Cherenkov telescopes is
 maximized, the expected DM flux including substructures from the
@@
  \includegraphics[width=0.99\columnwidth]{figures/dens.prof.bw.eps}
- \caption{\it (Color online) Radial dependence of DM annihilation
+ \caption{\colo Radial dependence of DM annihilation
    luminosity of smooth halo and substructures. The solid lines show
@@
   \includegraphics[width=0.99\columnwidth]{figures/emissiv.sub.bw.eps}
-  \caption{\it (Color online) Plot that shows where most of the DM
+  \caption{\colo Plot that shows where most of the DM
     annihilation luminosity originates. We show the differential
@@
 annihilating neutralinos is converted into electrons and positrons
-(see Sect.~\ref{sect:PF} and Fig.~\ref{fig:q_DM} for further details).
+(see Sec.~\ref{sect:PF} and Fig.~\ref{fig:q_DM} for further details).
 
@@
  \includegraphics[width=0.99\columnwidth]{figures/fit.porter.v2.eps}
- \caption{\it (Color online) Spectral dependence of radiation fields
+ \caption{\colo Spectral dependence of radiation fields
    in a cluster of galaxies. The black dotted line of the left peak
@@
  \includegraphics[width=0.99\columnwidth]{figures/ucool.bw.eps}
- \caption{\it (Color online) Spatial dependence of the energy density
+ \caption{\colo Spatial dependence of the energy density
    of radiation fields in a cluster of galaxies. The energy density of
@@
  \includegraphics[width=0.99\columnwidth]{figures/lum.stars.bw.eps}
- \caption{\it (Color online) \C{Comparing the spatial dependence of
+ \caption{\colo \C{Comparing the spatial dependence of
      emission from stars and dust (SD) to IC upscattered SD light.}
@@
   fluxes in this section are derived within an angle corresponding to
-  $\rvir$ and are convolved with a PSF of $0.1\deg$.}
+  $\rvir$ and are convolved with a PSF of $0.1\degs$.}
 
@@
 \includegraphics[width=0.49\columnwidth]{figures/flux.BMcompJs.v14.0.1deg.1.6T.SubMass.IR2.noMW.woGal.eps}
-\caption{\it (Color online) Comparing the differential flux from
+\caption{\colo Comparing the differential flux from
   different models: we show the continuum emission from DM benchmark
@@
   lower right $\Js$. The emission is calculated for the Fornax cluster
-  using a point spread function of $0.1\deg$. The substructures boost
+  using a point spread function of $0.1\degs$. The substructures boost
   the gamma-ray flux from IC upscattered CMB and continuum emission by
@@
   no longer dominated by the low velocity DM particles living in the
-  subhalos (see Sect.~\ref{sect:LP} for more details).}. A larger
+  subhalos (see Sec.~\ref{sect:LP} for more details).}. A larger
 fraction of electrons (in the core) will now also cool by
@@
 \includegraphics[width=0.49\columnwidth]{figures/flux.IRcomp.BMv14.0.1deg.SubMass.noMW.woGal.bw.eps}
-\caption{\it (Color online) Comparing the flux from different inverse
+\caption{\colo Comparing the flux from different inverse
   Compton upscattered radiation fields. We show the differential
@@
   the Fornax cluster within $\rvir$ using a point spread function of
-  $0.1\deg$. For this cluster, the enhancement due to substructures
+  $0.1\degs$. For this cluster, the enhancement due to substructures
   from IC upscattered CMB and SD photons is 890. The saturated
@@
  \includegraphics[width=0.99\columnwidth]{figures/flux.int.v14.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
- \caption{\it (Color online) Comparing the energy integrated flux from
+ \caption{\colo Comparing the energy integrated flux from
    different models. We show the emission from CR induced emission
@@
    emission is calculated for the Fornax cluster using a point spread
-   function of $0.1\deg$. The boost from Sommerfeld and substructures
+   function of $0.1\degs$. The boost from Sommerfeld and substructures
    is about 530 and 890, respectively.}
@@
   Sommerfeld boost realized when substructures are present, the latter is the Sommerfeld
-  boost without substructures (see Section II A 1).\\
+  boost without substructures (see Sec. II A 1).\\
   (3) The boost due to substructures relative a the smooth DM
@@
   (5) The total gamma-ray flux from the supersymmetric $\Kp$ benchmark (BM)
-  model where the boost from substructures is included. See Sections II A 2 and II B 3.\\
-  (6) Gamma-ray flux induced by CR protons. See Section V C.
+  model where the boost from substructures is included. See Secs. II A 2 and II B 3.\\
+  (6) Gamma-ray flux induced by CR protons. See Sec. V C.
  \label{tab:flux_tab}
@@
 \includegraphics[width=0.49\columnwidth]{figures/flux.cluster.Perseus.v14.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.eps}
-\caption{\it (Color online) Comparing the gamma-ray emission from
+\caption{\colo Comparing the gamma-ray emission from
   different clusters. We show the differential flux of clusters in the
@@
   \sim E_\gamma^{-\alpha_\gamma}$. The flux from the clusters is
-  integrated out to $\rvir$ using a point spread function of $0.1\deg$
+  integrated out to $\rvir$ using a point spread function of $0.1\degs$
   and includes the boost from substructures. We find that the lower
@@
  \includegraphics[width=0.99\columnwidth]{figures/LP.const.diff.v14.0.1deg.1.6T.SubMass.SF700.IR2.noMW.woGal.bw.eps}
- \caption{\it (Color online) Constraining boost factors using flux
+ \caption{\colo Constraining boost factors using flux
    upper limits. The leptophilic (LP) gamma-ray emission is derived
-   within $\rvir$ using a point spread function of $0.1\deg$. In order
+   within $\rvir$ using a point spread function of $0.1\degs$. In order
    not to overproduce the \Fermi-LAT differential flux upper limits in
@@
 The large angular extent of clusters on the sky in combination with
-the small PSF of most gamma-ray probes ($\sim 0.1$~deg) suggest that
+the small PSF of most gamma-ray probes ($\sim 0.1\degs$) suggest that
 we would be able to probe the different spatial regimes of a
@@
 substructures due to the projection of their peaked distribution the
-outer cluster regions (see Sect.~\ref{sect:subst} for a longer
+outer cluster regions (see Sec.~\ref{sect:subst} for a longer
 discussion). This implies that the spatial distribution of
@@
  \includegraphics[width=0.99\columnwidth]{figures/SB.v14.1GeV.SF700.SubMass.elmu.bw.eps}
- \caption{\it (Color online) Comparing the intrinsic surface
+ \caption{\colo Comparing the intrinsic surface
    brightness from different clusters without taking PSF effects into
@@
  \includegraphics[width=0.99\columnwidth]{figures/SB.resolved.v14.1GeV.SF700.noSuB.vs.SubMass.elmu.bw.eps}
- \caption{\it (Color online) The impact of substructures on the
+ \caption{\colo The impact of substructures on the
    intrinsic surface brightness profile o the Fornax cluster at
@@
   \includegraphics[width=0.49\columnwidth]{figures/SB.fornax.v14.1GeV.SF700.noSuB.elmu.bw.eps}
-  \caption{\it (Color online) The intrinsic surface brightness
-    profiles without substructures at energies $E>1\ GeV$. We show the
-    CR induced emission (red), leptophilic emission (light green), and
-    emission from the $\Kp$ benchmark model (dark blue). LEFT PANEL:
-    comparison of the surface brightness of different clusters; Fornax
-    (solid), Coma (dotted), Virgo (dashed), and Perseus
-    (dash-dotted). RIGHT PANEL: comparison of different emission
-    components in Fornax; dotted lines show the inverse Compton (IC)
-    upscattered CMB photons, dashed lines show the IC upscattered
-    photons from stars and dust, and blue solid lines show the
-    continuum emission from the $\Kp$ benchmark model.}
+  \caption{\colo The intrinsic surface brightness profiles without
+    substructures at energies $E>1\ GeV$. We show the CR induced
+    emission (red), leptophilic emission (light green), and emission
+    from the $\Kp$ benchmark model (dark blue). Left panel: comparison
+    of the surface brightness of different clusters; Fornax (solid),
+    Coma (dotted), Virgo (dashed), and Perseus (dash-dotted). Right
+    panel: comparison of different emission components in Fornax;
+    dotted lines show the inverse Compton (IC) upscattered CMB
+    photons, dashed lines show the IC upscattered photons from stars
+    and dust, and blue solid lines show the continuum emission from
+    the $\Kp$ benchmark model.}
  \label{fig:SB_clu_nosub}
@@
 
-In Sect.~\ref{sect:spectral} we saw that the spectral distribution of
+In Sec.~\ref{sect:spectral} we saw that the spectral distribution of
 gamma-ray flux from the LP model was dominated at high energies of
@@
 Fig.~\ref{fig:SB_IACTs}, we thus show the surface brightness above
-$100\,$~GeV for a realistic PSF of $0.1\deg$ where we include the
+$100\,$~GeV for a realistic PSF of $0.1\degs$ where we include the
 boost from substructures. We investigate two clusters with an expected
@@
   \includegraphics[width=0.49\columnwidth]{figures/SB.Virgo.v14.SF700.SubMass.elmu.bw.eps}
-\caption{\it (Color online) Surface brightness predicted for Cherenkov
+\caption{\colo Surface brightness predicted for Cherenkov
   telescopes at high energies. We show the emission above $100$~GeV
   and include the boost from substructures. We use a point spread
-  function of $\psf=0.1\deg$ that is typical for Cherenkov telescopes
+  function of $\psf=0.1\degs$ that is typical for Cherenkov telescopes
   as well as the \Fermi-LAT at this energy. Left panel shows the
@@
   \includegraphics[width=0.99\columnwidth]{figures/MLscaling.10G.eps}
-  \caption{\it (Color online) Scaling relations of the cluster's
+  \caption{\colo Scaling relations of the cluster's
     virial mass $\mvir$ and the gamma-ray luminosity for energies
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.DM.eps}
-  \caption{\it (Color online) \Fermi gamma-ray flux upper limits are
-    contrasted to predicted DM gamma-ray fluxes. We show the mean
-    differential flux in the energy range $E_\gamma=1-10$~GeV for 32
-    clusters. The extended \Fermi-LAT upper limits are shown with
-    black arrows (King profiles) and grey arrows (Gaussian profiles --
-    Virgo, Coma, Fornax), while the point source limits are shown in
-    light grey. The predicted fluxes are derived from the dominant
-    inverse Compton-scattering of CMB photons in a leptophilic DM
-    model (light red), and the continuum emission from the DM $\Kp$
-    benchmark model (blue). Assuming a boost factor due to
-    substructures that has a mass spectrum extending down to an Earth
-    mass, the expected leptophilic fluxes are ruled out by upper
-    limits in 28 of the clusters, with the strongest constraints set
-    by M49 and Fornax. At the present time, we cannot constrain the
-    benchmark models, although \Fermi-LAT will soon start to probe
-    these models. In particular, improved modelling of extended
-    sources as well as stacking of clusters appears promising in
-    testing benchmark models.}
+  \caption{\colo \Fermi gamma-ray flux upper limits are contrasted to
+    predicted DM gamma-ray fluxes. We show the mean differential flux
+    in the energy range $E_\gamma=1-10$~GeV for 32 clusters. The
+    extended \Fermi-LAT upper limits are shown with black arrows (King
+    profiles) and grey arrows (Gaussian profiles -- Virgo, Coma,
+    Fornax), while the point source limits are shown in light
+    grey. The predicted fluxes are derived from the dominant inverse
+    Compton-scattering of CMB photons in a leptophilic DM model (light
+    red), and the continuum emission from the DM $\Kp$ benchmark model
+    (blue). Assuming a boost factor due to substructures that has a
+    mass spectrum extending down to an Earth mass, the expected
+    leptophilic fluxes are ruled out by upper limits in 28 of the
+    clusters, with the strongest constraints set by M49 and
+    Fornax. \C{At the present time, we cannot constrain the benchmark
+      models with \Fermi-LAT data, although improved modelling of
+      extended sources as well as stacking of clusters appears
+      promising in testing benchmark models in the future.} \del{At
+      the present time, we cannot constrain the benchmark models,
+      although \Fermi-LAT will soon start to probe these models. In
+      particular, improved modelling of extended sources as well as
+      stacking of clusters appears promising in testing benchmark
+      models.}}
  \label{fig14}
@@
  \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.DM.eps}
- \caption{\it (Color online) Comparing the DM annihilation flux from
-   clusters in the extended HIFLUGCS catalogue. We show the energy
-   integrated gamma-ray fluxes derived from both leptophilic DM that
-   result in inverse Compton upscattered CMB photons (light red), and
-   the continuum emission from the DM $\Kp$ benchmark model
-   (blue). The fluxes are calculated within $\rvir$ for each of the
-   106 clusters included in the extended HIFLUGCS catalogue. The CR
-   emission is derived using a single beta profile for each cluster's
-   gas density profile (see text for details). The upper panel shows
+ \caption{\colo Comparing the DM annihilation flux from clusters in
+   the extended HIFLUGCS catalogue. We show the energy integrated
+   gamma-ray fluxes derived from both leptophilic DM that result in
+   inverse Compton upscattered CMB photons (light red), and the
+   continuum emission from the DM $\Kp$ benchmark model (blue). The
+   fluxes are calculated within $\rvir$ for each of the 106 clusters
+   included in the extended HIFLUGCS catalogue. The upper panel shows
    the energy integrated flux above 100~MeV and the lower panel that
@@
 Figure~\ref{fig14} compares \Fermi upper limits on the gamma-ray flux
-with predictions of DM annihilation fluxes in the LP and BM models.
-To obtain the gamma-ray fluxes, we scale the virial mass of clusters
-in the extended HIFLUGCS catalogue \cite{2007A&A...466..805C} with our
+with predictions of DM annihilation fluxes in the LP and BM
+models. \C{We assume a boost factor due to substructures that has a
+  constant contribution per decade in substructure mass and has a mass
+  spectrum extending down to Earth masses for our LP and BM DM
+  annihilation models. In the LP models we additionally assume a
+  cluster-mass dependent boost due to SFE. The gamma-ray fluxes are
+  calculated for those clusters where 18 months \Fermi-LAT upper
+  limits are derived (see \cite{2010ApJ...717L..71A}).} \del{To obtain
+  the gamma-ray fluxes, we scale the virial mass of clusters in the
+  extended HIFLUGCS catalogue \cite{2007A&A...466..805C} with our
   scaling relation of Eq.~(\ref{eq:DM_scaling}). In those, we assume a
-boost factor due to substructures that has a constant contribution per
-decade in substructure mass and has a mass spectrum extending down to
-Earth masses for our LP and BM DM annihilation models. In the LP
-models we additionally assume a cluster-mass dependent boost due to
-SFE. \Fermi limits rule out the LP models in their present form with
-the mentioned assumptions in 28 clusters, and limit the boost from SFE
-to less than 5 in M49 and Fornax. Assuming universality, this limits
-the Sommerfeld boost in the MW to less than 3 (see
-Fig.~\ref{fig:boost_const}). The flux level of the \Fermi limits are
-an indirect measure of the ambient background flux in the gamma-ray
-sky and/or the presence of strong point sources such as AGN in the
-immediate vicinity of the cluster position. Hence, the ratio of the
-\Fermi upper limits to the predicted annihilation fluxes,
-$F_{\mathrm{UL}}/F_{\mathrm{DM}}$, is a good indication of the best
-cluster candidates for indirect DM experiments. We identify Fornax,
-M49, NGC4636, and Virgo to be prime candidates. Note however, that
-Virgo extends of $12^\circ$ over the sky which implies a lower surface
-brightness and lower signal-to-noise. \Fermi limits on individual
-clusters are expected to improve as $\sqrt{T/1.5 \mathrm{yr}}$, where
-$T$ is the total elapsed time of the \Fermi mission. We emphasize that
-the very inhomogeneous distribution of $F_{\mathrm{UL}}/
-F_{\mathrm{DM}}$ makes it unlikely to dramatically improve the limits
-through a stacking analysis as the weak signal will dilute the average
-constraints.
-
-In Figure~\ref{fig21}, we show the DM annihilation flux predictions of
-the entire sample. Assuming the projected point source sensitivity
-($5\sigma$, 50h) of the future Cherenkov telescope array (CTA) of
-$F_\gamma(>E_\gamma) = (4\times10^{-11}, 2\times10^{-12},
+  boost factor due to substructures that has a constant contribution
+  per decade in substructure mass and has a mass spectrum extending
+  down to Earth masses for our LP and BM DM annihilation models. In
+  the LP models we additionally assume a cluster-mass dependent boost
+  due to SFE.}  \del{\Fermi} \C{These} limits rule out the LP models
+in their present form with the mentioned assumptions in 28 clusters,
+and limit the boost from SFE to less than 5 in M49 and
+Fornax. Assuming universality, this limits the Sommerfeld boost in the
+MW to less than 3 (see Fig.~\ref{fig:boost_const}). The flux level of
+the \Fermi limits are an indirect measure of the ambient background
+flux in the gamma-ray sky and/or the presence of strong point sources
+such as AGN in the immediate vicinity of the cluster position. Hence,
+the ratio of the \Fermi upper limits to the predicted annihilation
+fluxes, $F_{\mathrm{UL}}/F_{\mathrm{DM}}$, is a good indication of the
+best cluster candidates for indirect DM experiments. We identify
+Fornax, M49, NGC4636, and Virgo to be prime candidates. Note however,
+that Virgo extends of $12^\circ$ over the sky which implies a lower
+surface brightness and lower signal-to-noise. \Fermi limits on
+individual clusters are expected to improve as $\sqrt{T/1.5
+  \mathrm{yr}}$, where $T$ is the total elapsed time of the \Fermi
+mission. We emphasize that the very inhomogeneous distribution of
+$F_{\mathrm{UL}} / F_{\mathrm{DM}}$ makes it unlikely to dramatically
+improve the limits through a stacking analysis as the weak signal will
+dilute the average constraints.
+
+In Figure~\ref{fig21}, we show the DM annihilation flux predictions
+\del{of the entire sample} \C{of all the clusters in the extended
+  HIFLUGCS catalogue \cite{2007A&A...466..805C}. We find M49 and
+  Fornax to be that brightest clusters in the entire sample. While the
+  LP model predicts that almost all clusters in the sample should be
+  observed by \Fermi after two years of data taking, the fluxes from
+  the BM models are too low to be detected in the near future without
+  improved modelling.} Assuming the projected point source
+sensitivity ($5\sigma$, 50h) of the future Cherenkov telescope array
+(CTA) of $F_\gamma(>E_\gamma) = (4\times10^{-11}, 2\times10^{-12},
 2\times10^{-14})\,\rmn{ph}\,\rmn{cm}^{-2}\,\rmn{s}^{-1}$ at energies
@@
 extended while the sensitivity of Cherenkov telescopes scales
-approximately linearly with source extension. Hence the fluxes
-quoted in Fig.~\ref{fig21} will have to be compared to a sensitivity
-that is scaled down by the ratio of cluster radius to angular
-resolution of $0.1^\circ$ assuming current background subtraction
-techniques of Cherenkov telescopes. This important finding should
-encourage the development of new methods to overcome the degradation
-of sensitivity for diffuse and very extended sources. Such a
-break-through would be needed to probe and potentially detect the
-presented class of BM models with a large investment of observational
-time.
+approximately linearly with source extension. Hence the fluxes quoted
+in Fig.~\ref{fig21} will have to be compared to a sensitivity that is
+scaled down by the ratio of cluster radius to angular resolution of
+$0.1^\circ$ assuming current background subtraction techniques of
+Cherenkov telescopes. This important finding should encourage the
+development of new methods to overcome the degradation of sensitivity
+for diffuse and very extended sources. Such a break-through would be
+needed to probe and potentially detect the presented class of BM
+models with a large investment of observational time.
 
@@
   \includegraphics[width=0.99\columnwidth]{figures/Fermi.comp.CR.diff.eps}
-  \caption{\it (Color online) We contrast predictions of the CR
+  \caption{\colo We contrast predictions of the CR
     induced gamma-ray emission using an analytical CR model \protect
@@
     the upper (lower) bounds show the estimates for an optimistic
-    (conservative) model (see Sect.~\ref{sec:CRemission} and
+    (conservative) model (see Sec.~\ref{sec:CRemission} and
     \cite{2010MNRAS.409..449P} for details). Note that our models are
@@
   \includegraphics[width=0.99\columnwidth]{figures/XCR.Fermi.eps}
-  \caption{\it Limits on the relative CR pressure, $\bra
+  \caption{Limits on the relative CR pressure, $\bra
     X_\rmn{CR}\ket = \bra P_\rmn{CR} \ket / \bra P_\rmn{th}\ket$
@@
  \includegraphics[width=0.99\columnwidth]{figures/Flux.comp.CR.eps}
- \caption{\it Comparison of the gamma-ray flux induced by CRs for the
+ \caption{Comparison of the gamma-ray flux induced by CRs for the
    106 clusters included in the extended HIFLUGCS catalogue. The CR
@@
 stripped gas parcels from infalling galaxies to the overall gamma-ray
-flux from a cluster). As discussed in Sect.~\ref{sect:CRs}, the model
+flux from a cluster). As discussed in Sec.~\ref{sect:CRs}, the model
 predictions are subject to two main uncertainties, the acceleration
@@
   telescopes due to the spatially extended boost from substructures
-  over an angular extent of $\sim 0.5-1\deg$ (as independently found
+  over an angular extent of $\sim 0.5-1\degs$ (as independently found
   by reference \cite{2011arXiv1104.3530S}). This large angular extent
@@
   which drops approximately linearly with radius outside the point
-  spread function (with a characteristic scale of $\sim 0.1\deg$),
+  spread function (with a characteristic scale of $\sim 0.1\degs$),
   unless new background subtraction schemes can be found, e.g., for
@@
 unitless spatial distribution of SD (derived in
-Sect.~\ref{sect:SD_radial}), and $N_i(\mvir)$ denotes the mass
+Sec.~\ref{sect:SD_radial}), and $N_i(\mvir)$ denotes the mass
 dependent normalization for the SD. This function is determined using
@@
  \includegraphics[width=0.99\columnwidth]{figures/SB.photon.eps}
- \caption{\it Surface brightness profiles of the $r$-band $(h\nu\sim
+ \caption{Surface brightness profiles of the $r$-band $(h\nu\sim
    1\,\ev)$ obtained from stacked clusters in the Sloan Digital Sky
@@
  \includegraphics[width=0.99\columnwidth]{figures/dens.fornax.bw.eps}
- \caption{\it (Color online) Comparing different electron number
+ \caption{\colo Comparing different electron number
    density profiles for the Fornax cluster. Black crosses show the

### 2011-10-13 paper.tex
small changes

@@
   spectrum extending down to Earth masses for our LP and BM DM
-  annihilation models. In the LP models we additionally assume a
-  cluster-mass dependent boost due to SFE. The gamma-ray fluxes are
-  calculated for those clusters where 18 months \Fermi-LAT upper
+  annihilation models.}  \del{In the LP models we additionally assume
+  a cluster-mass dependent boost due to SFE.}\C{The gamma-ray fluxes
+  are calculated for those clusters where 18 months \Fermi-LAT upper
   limits are derived (see \cite{2010ApJ...717L..71A}).} \del{To obtain
@@
 Fornax, M49, NGC4636, and Virgo to be prime candidates. Note however,
-that Virgo extends of $12^\circ$ over the sky which implies a lower
+that Virgo extends $12^\circ$ over the sky which implies a lower
 surface brightness and lower signal-to-noise. \Fermi limits on
@@
   \mathrm{yr}}$, where $T$ is the total elapsed time of the \Fermi
-mission. We emphasize that the very inhomogeneous distribution of
-$F_{\mathrm{UL}} / F_{\mathrm{DM}}$ makes it unlikely to dramatically
-improve the limits through a stacking analysis as the weak signal will
-dilute the average constraints.
+mission. \C{We emphasize that the very inhomogeneous distribution of
+  $F_{\mathrm{UL}} / F_{\mathrm{DM}}$ makes it unlikely to
+  dramatically improve the limits through a likelihood stacking
+  analysis as there are only a few clusters with comparably good
+  $F_{\mathrm{UL}}/F_{\mathrm{DM}}$ values as well as
 
 In Figure~\ref{fig21}, we show the DM annihilation flux predictions
-\del{of the entire sample} \C{of all the clusters in the extended
+\del{of the entire sample}\C{of all the clusters in the extended
   HIFLUGCS catalogue \cite{2007A&A...466..805C}. We find M49 and
